### 2022-09-13 Thesis-Janeth/chapters/1_intro.tex
organized file folder FACEPE and THESIS

\chapter{Introduction}\label{chp:int}
%------------------------------------
%	INTRO INTRO
%------------------------------------

The use of Statistical Information Theory (SIT) and Statistical Information Geometry (SIG) in image processing and analysis problems has the potential to provide several solutions to the same problem. Considering that these solutions are evidences, or estimates of the solution, this project aims to propose techniques for fusing them into a single solution potentially better than the individual evidences.

The starting point is the paper by de Borba et al. \cite{de2020fusion}, in which the authors obtain several evidences of the location of edge points in images with low signal/noise relation. In this work, the estimations are treated deterministically, that is, without taking into account the variability of the estimator that produces them. These estimations go through fusion processes to obtain an edge point that summarizes the evidence.

The project proposes to create fusion techniques that take into account the quality of each evidence. In this way, evidence that is subject to high variability, or that is inconsistent with most other evidence, will have less influence on the final result.

On the one hand, the project is challenging because there are no theoretical results to assess the quality (bias, variance, etc.) of the evidence. On the other hand, when they come from an analysis based on the SIT/GIS approach, there is the possibility of advancing the frontier of knowledge since there is a powerful statistical tool (although little explored) for this purpose.

An explainable fusion of this type of evidence will be able to provide semantically valuable information on the contribution of each component to the composition of the final result. With this, end-users will be able to extract relevant information about the information content (and reliability) of each source of evidence. This knowledge will allow, for example, discarding unreliable sources, or those that, being redundant, contribute little to the quality of the product.

The work will focus on SAR/PolSAR (Synthetic Aperture Radar/Polarimetric SAR) images. These images are of great relevance in Remote Sensing \cite{cloude2009polarisation}, and present high levels of non-Gaussian and non-additive noise. This last feature makes them attractive and challenging for the development of new techniques \cite{lee2017polarimetric}.

The statistical approach to edge detection in SAR/PolSAR images has provided comparable or better results than techniques previously considered state-of-the-art. Among the edge detection results to be highlighted for SAR images (in which each pixel has a non-negative value), we mention the works of \cite{gambini2008accuracy, giron2012nonparametric}.

\section{Literature Review}
A. Fink \cite{fink2019conducting} provides the following definition: ``A literature review is a systematic, explicit, and reproducible project to identify, evaluate, and interpret the existing body of recorded documents.''  Literature reviews generally aim at two goals: first, they summarize existing research by identifying patterns, themes, and issues. Second, this helps identify the conceptual content of the field and can contribute to theory development.

\subsection{Search Strategy}

In order to select the most relevant articles for this study, we started by searching for papers on edge detection in SAR/PolSAR images in the most common scientific databases: Scopus, Web of Science (WoS), Science Direct (SD), Google Scholar (GS), Emerald insight (Emerald), Wiley Online Library (Wiley), Taylor \& Francis Online (T\&F), Springer Link (Springer), Inderscience (IS), and Informs PubsOnline (IPO). \\ %The Search Terms employed in the field of Title are the following:
The employed keywords were the following focused on the fields Title-Abstract-Keywords:
\begin{itemize}
	\item ("bias correction" OR "improve estimators" OR "new estimator" OR "MLE" OR "efficient estimators" OR "maximum-likelihood estimation" OR "statistical information theory")  
\item	AND ("boundary detection" OR "edge detection" OR "edge detection method" OR "edge detector") 
\item ("PolSAR images" OR "Polarimetric Synthetic Aperture Radar" OR "single-polarimetric synthetic aperture radar images" OR "SAR images")
\end{itemize}
Some works related to this topic can be seen in Table \ref{tab:1}.
\begin{longtable}{P{\dimexpr0.26\textwidth-2\tabcolsep-2\arrayrulewidth\relax}
                        P{\dimexpr0.39\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        P{\dimexpr0.30\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        %P{\dimexpr0.20\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        }
\toprule
Author & Title & Source \\\midrule
\rowcolor{Gray}\multicolumn{3}{c}{Edge detection}\\
Nascimento, A. D., Horta, M. M., Frery, A. C., and Cintra, R. J. (2013)\cite{nascimento2013comparing}. & Comparing edge detection methods based on stochastic entropies and distances for PolSAR imagery & IEEE journal of selected topics in applied earth observations and remote sensing\\ \midrule
%\rowcolor{gray!20}\multicolumn{3}{c}{Music}\\
Xiang, Y., Wang, F., Wan, L., and You, H. (2017) \cite{xiang2017sar} & SAR-PC: Edge detection in SAR images via an advanced phase congruency model. & Remote Sensing\\ \midrule

Qin, X., Hu, T., Yu, W., Wang, P., Li, J.,  Zou, H. (2018) \cite{qin2018edge}& Edge detection of PolSAR images using statistical distance between automatically refined samples.& IEEE International Geoscience and Remote Sensing Symposium\\
\bottomrule
Nascimento, A. D., Frery, A. C.,  Cintra, R. J. (2019) \cite{nascimento2018detecting}& Detecting changes in fully polarimetric SAR imagery with statistical information theory.& IEEE Transactions on Geoscience and Remote Sensing\\
\bottomrule
Quan, S., Xiang, D., Xiong, B.,  Kuang, G. (2020) \cite{quan2019edge}& Edge detection for PolSAR images integrating scattering characteristics and optimal contrast.& IEEE Geoscience and Remote Sensing Letters\\
\bottomrule
\caption[Papers related to edge detection]{Papers related to edge detection}\label{tab:1}
%\caption{\label{Pesquisa de documentos.} works that use Machine Learning}
\end{longtable}

%("REVIEW" OR "STATE OF THE ART" OR "SURVEY" OR "CONCEPTUAL FRAMEWORK" ) AND ("LAYOUT DESIGN" OR "DESIGN OF LAYOUT" OR "MANUFACTURING LAYOUT"
%OR "FACILITY LAYOUT" OR "PLANT LAYOUT" OR "FACILITY LAYOUT PLANNING" ).

%---------------------------------------------------------------------------------------------------------------------
\section{Project objectives}
The objective of this thesis is to contribute to the state of the art in the fusion of evidence using a statistical approach to achieve explainable and relevant results. \\

The main specific objectives are:

\begin{itemize}
	\item Obtain the statistical properties (bias, variance) of edge point estimators in SAR/PolSAR images.
	\item Propose and evaluate new fusion and evidence selection techniques that take these properties into account.
	\item Develop new features for production software, e.g. PolSARpro and SNAP.
\end{itemize}

\section{Thesis organization}\label{sec:research_questions}

% colocar para citar los capitulos
\hypersetup{linkcolor=blue}

This thesis is structured in 5 chapters. In the upcoming sections of the current chapter a general overview on ... \\
 Chapter~\ref{chp:obs} details ...\\
Chapter ~\ref{chp:models} explains ...
%------------------------------------
%	HAZARD: OVERVIEW
%------------------------------------

\section{Computing platforms}
This  project required a vast amount of computing, preprocessing, analysis and plotting.

%------------------------------------
%	TODO STUFF
%------------------------------------
% \section{Additional sources to integrate in this chapter}
% \begin{itemize}
% \item check all TODOs
% \item read again \url{http://ec.europa.eu/environment/water/flood_risk/flood_atlas/pdf/handbook_goodpractice.pdf}
% \item include citation EU Floods Directive (2007/60/EC) , \cite{Mysiak2013, EUFD2007}
% \item section to talk about uncertainties? \citet{alfieri2014} has a good section about it
% \item Alps are the water tower of the Po plain, and for this reason I might want to give them a closer look. I could cite one of the many kotlarski works, or e.g. \citet[][]{Gobiet2014}. View the 'Alps' category in my Mendeley, it contains about 30 works on the subject
% \end{itemize}

### 2022-09-13 Thesis-Janeth/parts/abstract.tex
organized file folder FACEPE and THESIS

%\begin{otherlanguage}{spanish}
\begin{abstract}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}
%\addchaptertocentry{\abstrname}
%\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
Edge detection has an essential role in post-processing of Polarimetric synthetic aperture radar (PolSAR) images. It is still a big challenge to extract all the edge features and suppress speckle noises, especially when weak/strong edges appear simultaneously inside and outside heterogeneous areas.

PolSAR images can provide more information than single-polarimetric synthetic aperture radar (SAR) images. As the prerequisite step of image processing, PolSAR edge detection is very important, which can provide important structural information for further object recognition and image interpretation of PolSAR images. However, a complex PolSAR scene usually includes both heterogenous and homogenous terrain types such as urban areas, forests, farmlands, waters, and so on.

In this thesis, we obtain the statistical properties (bias, variance) of edge point estimators in SAR/PolSAR images. In this way, we propose and evaluate new fusion and evidence selection techniques that take these properties into account.

\end{abstract}
%\end{otherlanguage}

### 2022-09-13 Thesis-Janeth/parts/declaration.tex
organized file folder FACEPE and THESIS

\begin{declaration}
%\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

### 2022-09-13 Thesis-Janeth/parts/resumo.tex
organized file folder FACEPE and THESIS

\begin{otherlanguage}{portuguese}

\begin{resumo}
\phantomsection
\addcontentsline{toc}{chapter}{Resumo}
%\addchaptertocentry{\resumenname} % Add the abstract to the table of contents
A detecção de bordas tem um papel essencial no pós-processamento das imagens PolSAR. A extração de todas as características das bordas e a supressão de ruídos speckle, especialmente quando bordas fracas/fortes aparecem simultaneamente dentro e fora de áreas heterogêneas, ainda é um grande desafio.

As imagens PolSAR podem fornecer mais informações do que as imagens de radar de abertura sintética (SAR) de polarimetria única. Como a etapa de pré-requisito do processamento de imagem, a detecção de bordas PolSAR é muito importante, o que pode fornecer informações estruturais importantes para reconhecimento adicional de objetos e interpretação de imagens PolSAR. No entanto, uma cena PolSAR complexa geralmente inclui tipos de terreno heterogêneos e homogêneos, como áreas urbanas, florestas, terras agrícolas, águas e assim por diante.

Nesta tese, obtemos as propriedades estatísticas (bias, variância) dos estimadores de pontos de borda em imagens SAR/PolSAR. Desta forma, propomos e avaliamos novas técnicas de fusão e seleção de evidências que levem em consideração essas propriedades.

\end{resumo}
\end{otherlanguage}

### 2022-11-01 Text/Reports/report-systematic-review/systematic_review.tex
Update files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                   File: OSAmeetings.tex             %
%                  Date: 29 Novemver 2018              %
%                                                     %
%     For preparing LaTeX manuscripts for submission  %
%       submission to OSA meetings and conferences    %
%                                                     %
%       (c) 2018 Optical Society of America           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt]{article} 
%% if A4 paper needed, change letterpaper to A4

\usepackage{./styles/osameet3} %% use version 3 for proper copyright statement

%% provide authormark
%\newcommand\authormark[1]{\textsuperscript{#1}}

%% standard packages and arguments should be modified as needed
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %pdflatex
%\usepackage[breaklinks,colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %latex w/dvipdf

\begin{document}

\title{Systematic Literature Reviews (SLR)}

% \author{Author name(s)}
% \address{Author affiliation and full address}
% \email{e-mail address}
%%Uncomment the following line to override copyright year from the default current year.
%\copyrightyear{2022}

\author{Janeth Alpala }

\address{  Universidade Federal de Pernambuco\\
}

%\email{\authormark{*}opex@optica.org} %% email address is required

%\begin{abstract}

%\end{abstract}

\section{Introduction}

Literature reviews have a fundamental role in academic research to assemble available knowledge and examine the state of a field.
Fink \cite{fink2019conducting} provides the following definition: ‘‘A literature review is a systematic, explicit, and reproducible design for identifying, evaluating, and interpreting the existing body of recorded documents’’.  Literature reviews generally serve two purposes: First, they summarize existing research by identifying patterns, themes, and issues. Second, it helps to identify the conceptual content of the field and can contribute to theory development.\\

Researchers typically collect available evidence on a topic or issue prior to conducting new research to assess the state of the
already available evidence. The idea behind a systematic review is to systematically collect available evidence and then provide an evaluation of the evidence based on predetermined criteria \cite{Tranfield2003}.

The different steps in conducting a systematic literature review include: identification of the literature to be included, data cleaning, analysis and synthesis, and presentation of the results \cite{Linnenluecke2019}.

\section{ Methodology: towards a systematic review}

The essential idea of a systematic literature review is that the review is replicable, which means that another researcher can replicate the review process and arrive at the same set of evidence and the same conclusion.

A systematic review includes an exhaustive search of the designated databases additional literature that may not be available through these databases and requires an exhaustive process to analyze and synthesize the relevant information.

\subsection{Identification of literature for inclusion}
An important step is to clarify the topic or issue under investigation. The researcher should investigate: Are there already existing reviews on the specific issue or research question under investigation? In this case, a replication might not be warranted, but an extension or update could prove useful.
\subsection{Data cleaning}
Once a range of suitable studies is identified, duplicates need to be removed from the analysis. In
addition, studies that are not relevant need to be removed. ‘False positives’ in the search process
can occur.

\subsection{Analysis and synthesis}

A vital step for any systematic review is the analysis and synthesis of the available evidence and depends on the number of studies that will be included in the review; the type of research method(s) used by individual studies and the quality of the evidence, and the chosen analytical or visualisation technique.

\subsection{Presentation of results}
There are numerous ways to present the results of a systematic literature review. If the studies
underlying the review use mainly qualitative data, the researcher can prepare a qualitative analysis,
but would not necessarily offer a statistical combination – aside from perhaps incorporating some
traditional descriptive statistics to summarise basic information, such as the
number of publications on a topic over time.\\

Alternative options for the presentation of results are offered by various software packages and
bibliographic mapping approaches that can be used for visualising research on a topic or theme.

\subsection{Material collection}

The first step consisting in the delimitation and compilation of the material. The literature search about edge detection was performed by considering scientific articles  in Web of Science (WoS) and Scopus, which are the two main bibliographic databases \cite{Pranckute2021}.

The employed keywords were the following focused on the fields Title-Abstract-Keywords:

\begin{itemize}
	\item (explainable edge detection)
\end{itemize}

\begin{longtable}{P{\dimexpr0.26\textwidth-2\tabcolsep-2\arrayrulewidth\relax}
                        P{\dimexpr0.39\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        P{\dimexpr0.30\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        %P{\dimexpr0.20\textwidth-2\tabcolsep-\arrayrulewidth\relax}
                        }
\toprule
Author & Title & Source \\\midrule
\rowcolor{gray!20}\multicolumn{3}{c}{Edge detection}\\
Nascimento, A. D., Horta, M. M., Frery, A. C., and Cintra, R. J. (2013)\cite{nascimento2013comparing}. & Comparing edge detection methods based on stochastic entropies and distances for PolSAR imagery & IEEE journal of selected topics in applied earth observations and remote sensing\\ \midrule
%\rowcolor{gray!20}\multicolumn{3}{c}{Music}\\
Xiang, Y., Wang, F., Wan, L., and You, H. (2017) \cite{xiang2017sar} & SAR-PC: Edge detection in SAR images via an advanced phase congruency model. & Remote Sensing\\ \midrule

Qin, X., Hu, T., Yu, W., Wang, P., Li, J.,  Zou, H. (2018) \cite{qin2018edge}& Edge detection of PolSAR images using statistical distance between automatically refined samples.& IEEE International Geoscience and Remote Sensing Symposium\\
\bottomrule
Quan, S., Xiang, D., Xiong, B.,  Kuang, G. (2020) \cite{quan2019edge}& Edge detection for PolSAR images integrating scattering characteristics and optimal contrast.& IEEE Geoscience and Remote Sensing Letters\\
\bottomrule
\caption{\label{Pesquisa de documentos.}}
\end{longtable}

%\begin{figure}[H]\vspace{-1em}
%\centering
% \includegraphics[width=1.0\textwidth]{ss.png}\vspace{-0.5em}
%\caption{\label{f1}}
%\vspace{-1em}
%    \end{figure}
%\begin{thebibliography}{99} %% use BibTeX or add references manually

\bibliographystyle{ieeetr}
\bibliography{../Common/references}  % e.g., \bibliography{cribari_01}
%\printbibliography

\end{document}

### 2022-11-01 Code/R/example.R

@@ -1,0 +1,16 @@
+rm(list = ls(all = TRUE))
+graphics.off()
+shell("cls")
+
+getwd()
+
+
+
+library(dplyr) 
+library(pROC) 
+library(MASS)
+library(broom) 
+library(AUC)
+library(pROC)
+library(tidyverse)
+dplyr::roc()

### 2023-01-25 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
files upload IGARSS

% Template for IGARSS-2020 paper; to be used with:
%          spconf.sty  - LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,epsfig}
\usepackage{bm,bbm}
% \newcommand{\mcite}[1]{\mbox{\cite{#1}}}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

\DeclareMathOperator{\Tr}{Tr}

% Title.
% ------
\title{Quality assessment measures for explainable fusion of statistical evidences of edges in PolSAR images: A First Approach}
% Single address.
% ---------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}} 
%\address{Author Affiliation(s)}
\name{Rosa Janeth Alpala$^a$, Anderson A.\ de Borba$^{b,c}$, and Alejandro C.\ Frery$^c$.\thanks{e-mail:$^{a}$janeth.alpala@ufpe.br,$^{b}$anderson.borba@mackenzie.br, $^c$alejandro.freryorgambide@vuw.ac.nz }}
\address{$^a$ Universidade Federal de Pernambuco, 50740-540, Recife, PE, Brazil,           \\
$^b$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil, \\
$^c$School of Mathematics and Statistics, Victoria University of Wellington, 6140, New Zealand.}

%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
This work aims to develop techniques for the fusion of statistical evidences obtained from the application of Statistical Information Theory (SIT) and Statistical Information Geometry (SIG) in image processing and analysis, with a specific focus on Polarimetric Synthetic Aperture Radar (PolSAR) imagery. The goal is to generate a single solution superior to individual solutions. Furthermore, properties or measures that assess the quality of results will also be employed to evaluate the effectiveness of fusion methods in detecting edge evidence.

%
\begin{keywords}
PolSAR, edge detection,  information fusion,  quality
measures 
\end{keywords}
%
\end{abstract}
\section{Introduction}
PolSAR images offer a distinct advantage over other remote sensing images by utilizing four different polarization combinations, specifically HH, HV, VH, and VV~\cite{Hua2022}. These combinations are based on the horizontal (H), and vertical (V) polarizations of the received and transmitted signals. The polarization allows for the acquisition of detailed and comprehensive data, providing significantly more information than the simple polarization mode~\cite{Zhai2015}.\par

The study on the applications of PolSAR data, particularly edge detection, has received increasing attention~\cite{Jin2016,Wang2018}. Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}. In order to achieve the goal of PolSAR image detection, several methods and algorithms have been proposed~\cite{Schou2003,Gambini2007,Nascimento2014}. \par

A new method for extracting all edge-related features is proposed in~\cite{Shi2020}. This method is designed to reduce speckle noise in regions with both weak and strong edges, particularly in heterogeneous areas. Another approach involves the fusion of evidence obtained from intensity channels to detect edges in PolSAR image. This can be done using a simple average, principal component analysis, ROC statistics, etc. See~\cite{DeBorba2020}.

The study by de Borba et al.~\cite{DeBorba2020} is the foundation for this research. It presents evidence of the location of edge points in images with low signal-to-noise ratio by using a deterministic approach that does not take into account the variability of the estimator. We extended this investigation using new edge detectors following the work of~\cite{Xiang2016, Nascimento2014,Shi2020}. In addition, various quality metrics will be employed to evaluate and compare the results of edge evidence fusion in PolSAR images.
\section{Background}
\subsection{PolSAR data representation }
Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted. The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information.
\begin{align}
 \mathbf{S} = \begin{bmatrix}
S_{\text{HH}} & S_{\text{HV}} \\
S_{\text{VH}} & S_{\text{VV}}
\end{bmatrix},  
\label{E:a1}
\end{align}
where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ generate the power return in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ are responsible for the power return in the cross-polarized channels.\par
If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, the single-look PolSAR data can be represented using a scattering vector:
\begin{align}
\mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
\label{E:21}
\end{align}
where  the superscript $t$ stands for the transpose operation. The multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^H \rangle= \frac{1}{L} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), here $\langle \cdot \rangle$ is the ensemble average, H  the is complex conjugate transpose operator, and $L$ is the number of looks. Covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$
see~\cite{Qin2022}.
\subsection{Gamma distribution}
%Over the past decades, several distributions have been created for modeling PolSAR image data. The most commonly used distribution for working with images generated from polarimetric multilook data is the complex Wishart distribution~\cite{Nielsen2007}. This distribution is characterized by two parameters, the covariance matrix $\mathbf{\Sigma}$ and the number of looks L of the image. Thus, the polarimetric matrix $\mathbf{Z} = \mathbf{C}=\left\langle\mathbf{k}_s\mathbf{k}_s^H \right\rangle$ can be derived following a complex Wishart distribution, represented as $\mathbf{Z}\sim \mathcal{W}_{\mathcal{C}}(\mathbf{\Sigma}, L),$  whose probability density function
%is~\cite{Frery2014, Qin2022}:
%\begin{align}
%f_{\mathbf{Z}}(\mathbf{Z})=\frac{L^{qL}|\mathbf{Z}|^{L-q}}{|\mathbf{\Sigma}|^L\Gamma_q(L)}\exp\left\{-L \Tr\left(\mathbf{\Sigma}^{-1}\mathbf{Z}\right)\right\},
%\label{E:22}
%\end{align}
%where $\Gamma_q(L)=\pi^{q(q-1)/2}\prod_{i=0}^{q-1}\Gamma(L-i)$,  $\Gamma(\cdot)$ denotes the gamma function and $\Tr(\cdot)$ is the trace of the matrix. In this case, three channels will be used, i.e., $q = 3$.

Considering the previous section, we assume that the distribution of each intensity channel  follows a Gamma law, as described by: 
\begin{equation}
f_Z(z;\mu,L)=\frac{L^{L}z^{L-1}}{\mu^{L}\Gamma(L)} \exp\big\{-Lz/\mu\big\},\quad z>0,
\label{func_dens_uni_gamma}
\end{equation}
where $L>0$, and
$\mu>0$ is the mean.
The log-likelihood of the sample $\bm{z} = (z_1,\dots,z_n)$ under this model is
\begin{equation}
\mathcal{L}(\mu, L; \mathbf{z}) = 
n \big[L\ln (L / \mu) - \ln \Gamma(L)\big]
+L \sum_{k=1}^{n}\ln z_k -\frac{L}{\mu}\sum_{k=1}^{n} z_k.
\label{eq:LogLikelihoodGamma}
\end{equation}
Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, is obtained by maximizing~\eqref{eq:LogLikelihoodGamma}.

% A simplified derivation to obtain the complex Wishart distribution was presented in \cite{LEE1994}.
\subsection{Edge detection on a single data strip}
Finding the edges of an image is a crucial step in image analysis. These boundaries define distinct regions within the image, such as pastures, urban areas, or forested areas~\cite{monferran2020modelo}. Various techniques, including maximum likelihood, entropy, and geodesic distance, are commonly used in research studies to identify edge points~\cite{NaranjoTorres2017,Nascimento2019}. To locate edge points in these types of images, modeling the data using a suitable statistical distribution and determining the related parameters is necessary.

The Gambini algorithm~\cite{Gambini2007} is a highly appealing method for edge detection. It is designed to be localized, searching for evidence of edges within a narrow data strip. The algorithm involves the projection of rays and identifying edge evidence by maximizing a value function.

The algorithm starts by casting rays from a point inside the candidate region, e.g., the centroid.
Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$:
$$
\bm z = (\underbrace{z_1,z_2,\dots,z_j}_{\bm z_\text{I}}, 
\underbrace{z_{j+1}, z_{j+2},\dots,z_n}_{\bm z_\text{E}}).
$$
Two possibly different models are assumed for each partition:
$\bm Z_\text{I} \sim \Gamma(\mu_\text{I},L_\text{I})$, and 
$\bm Z_\text{E} \sim \Gamma(\mu_\text{E},L_\text{E})$.
We then estimate $(\mu_\text{I},L_\text{I})$ and $(\mu_\text{E},L_\text{E})$ with $\bm z_\text{I}$ and $\bm z_\text{E}$, respectively, by maximizing~\eqref{eq:LogLikelihoodGamma}, and obtain $\big(\widehat{\mu}_\text{I}, \widehat{L}_\text{I}\big)$ and $\big(\widehat{\mu}_\text{E}, \widehat{L}_\text{E}\big)$.

Then, the total log-likelihood is calculated of $\bm z_\text{I}$ and $\bm z_\text{E}$:
\begin{equation}\label{eq:TotalLogLikelihood}
\begin{aligned}
\mathcal L\big(j&;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
	\frac{\widehat{L}_\text{I}}{\widehat{\mu}_\text{I}}\sum_{k=1}^{j} z_k +
	\frac{\widehat{L}_\text{E}}{\widehat{\mu}_\text{E}}\sum_{k=j+1}^{n} z_k  
	\Bigg)\mbox{}\\
&+j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
+\widehat{L}_\text{I} \sum_{k=1}^{j}\ln z_k  \mbox{}\\
&+(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
+\widehat{L}_\text{E} \sum_{k=j+1}^{n}\ln z_k .%-\\ 
\raisetag{2.2em}
\end{aligned}
\end{equation}
The estimate of the edge position on the ray is represented by the coordinate  $\widehat\jmath$, which maximizes it.

\subsection{Fusion methods for edge evidence}
In~\cite{DeBorba2020}, a fusion of edge evidence is carried out in the channels of intensities HH, HV, and VV, of a PolSAR image to produce a unique and more accurate edge position estimator. For this purpose, six fusion methods were used:  simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).\par

Edge evidence fusion methods are essential to quantify and qualify the information obtained from each image channel. This information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.
\section{Quality assessment}
Quality assessment is a central issue in the image fusion process to compare the quality of the fused images and the performance of the method used~\cite{Somvanshi2017}. Quality measure indicators that are most used to evaluate fusion results are:  mean square error (MSE)~\cite{beaulieu2003multi}, standard deviation (SD)~\cite{choi2003biorthogonal}, average gradient (AG)~\cite{li2005color}, the correlation (CC) coefficient~\cite{aiazzi2004spectral}, entropy~\cite{han2008study}, and the peak signal-to-noise ratio (PSNR)~\cite{canga2005}. Some of these metrics are defined as follows: Mean square error measures the spectral distortion introduced by the fusion process.
    $$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
   % where $(i, j)$ denote pixel location.
The correlation coefficient measures the degree of correlation between the enhanced and the original images.
    $$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
   % where $x_i$, $y_i$ are the grey values of homologous pixel synthesised image and real image.
And, the Entropy is used for measuring the richness of data in enhanced images.
    $$H=-\sum_{i=1}^{n}d(i)\log_2d(i).$$
    %where $G$ is the number of grey level of the image’s histogram and $d(i)$ is the normalised frequency of occurrence of each grey level.

Following the image fusion quality assessment strategy proposed in~\cite{Li2010, Somvanshi2017,Nikola2015}, we intend to utilize this approach in our study for the fusion of edge evidence through statistical analysis.

%We use the criteria described in [2]  to evaluate the quality of each evidence for each fusion method.

%We expanded our research to a statistical analysis, using quality metrics to assess the efficiency in the fusion of evidence, using different methods.

\subsection{Exploring the concept of explainability}
Explainability is a crucial concern when it comes to artificial intelligence (AI)~\cite{Vilone2021}. It refers to the ability to understand and interpret the decisions and actions made by an AI system. This is particularly important in applications where the stakes are high, such as in medical diagnosis~\cite{Tjoa2021}. The term~\textit{explainable} refers to a statement, fact, or situation that provides a reason for why something happened. It helps to make something clear or interpretable.

The proposed methodology in this work focuses on identifying interpretable measures that can be used to weigh the influence of individual estimates during an evidence fusion process.
\section{RESULTS}

From Fig.~\ref{fig:res}(a)-(c), we can see the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.\par
According to the research in~\cite{DeBorba2020}, various fusion methods were utilized to detect edge evidence. As an example, the results obtained by applying PCA and ROC methods to an AIRSAR L-band image of Flevoland are shown in Fig.~\ref{fig:2}.%(a)-(b).

%%% The source is in ../../../Figures/PDF/hh.pdf
 \begin{figure}[htb]
\begin{minipage}[b]{1.0\linewidth}
  \centering
 \centerline{\epsfig{figure=../../../Figures/PDF/hh.pdf,width=4cm}}
  \vspace{-0.1cm}
  \centerline{(a) Channel HH.}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
\centerline{\epsfig{figure=../../../Figures/PDF/hv.pdf,width=4.0cm}}
  \vspace{-0.1cm}
  \centerline{(b) Channel HV.}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
 \centerline{\epsfig{figure=../../../Figures/PDF/vv.pdf,width=4.0cm}}
  \vspace{-0.1cm}
  \centerline{(c) Channel VV.}\medskip
\end{minipage}
%
\caption{Edges evidences from the three intensity channels.}
\label{fig:res}
%
\end{figure}
 \begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
\centerline{\epsfig{figure=../../../Figures/PDF/pca.pdf,width=4.0cm}}
  \vspace{-0.1cm}
  \centerline{(a) PCA fusion.}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
 \centerline{\epsfig{figure=../../../Figures/PDF/roc.pdf,width=4.0cm}}
  \vspace{-0.1cm}
  \centerline{(b) ROC fusion.}\medskip
\end{minipage}
%
\caption{Results of applying the two fusion methods.}
\label{fig:2}
%
\end{figure}
\section{CONCLUSION}
The project outlined here will develop fusion techniques that factor in the quality of each evidence. In this way, evidence subject to great variability or that may be inconsistent with other evidence, will have less influence.
An explainable fusion of statistical evidence can provide semantically rich information on the contribution of each component to the composition of the final result. This enables the extraction of relevant and dependable information about the content of the evidence from each source.

Finally, we will use several evaluation indicators presented in the literature to evaluate the quality of edge evidence fusion in PolSAR images.

%(bias, variance, etc.)
%Lastly, we expanded our research to include statistical analysis by utilizing quality metrics() to evaluate the effectiveness of the fusion of evidence.

%\newpage

% % -------------------------------------------------------------------------
% \vfill

%  \textbf{Instruction for References:} List and number all bibliographical references at the end of the paper.  The references can be numbered in alphabetic order or in order of appearance in the document.  When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{C2}.
% % -------------------------------------------------------------------------

%\pagebreak

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% ------------------------------------------------------------------------
%%% The source is in ../../Common/references
\bibliographystyle{IEEEbib}
\bibliography{../../Common/references}
\end{document}

### 2023-01-26 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
Revisado e pronto para enviar

@@
 \usepackage{bm,bbm}
+\usepackage{cite}
 % \newcommand{\mcite}[1]{\mbox{\cite{#1}}}
@@
 These combinations are based on the horizontal (H), and vertical (V) polarizations of the received and transmitted signals.
-The polarization allows for the acquisition of detailed and comprehensive data, providing significantly more information than the simple polarization mode~\cite{Zhai2015}.\par
+The polarization allows for the acquisition of detailed and comprehensive data, providing significantly more information than the single polarization mode~\cite{Zhai2015}.
 
@@
 Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}.
-In order to achieve the goal of PolSAR image detection, several methods and algorithms have been proposed~\cite{Schou2003,Gambini2007,Nascimento2014}.
-\par
+Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Schou2003,Gambini2007,Nascimento2014}.
 
-A new method for extracting all edge-related features is proposed in~\cite{Shi2020}.
+Shi et al.~\cite{Shi2020} proposed a new method for extracting all edge-related features. 
 This method is designed to reduce speckle noise in regions with both weak and strong edges, particularly in heterogeneous areas. 
-Another approach involves the fusion of evidence obtained from intensity channels to detect edges in PolSAR image.
+Another approach~\cite{DeBorba2020} involves the fusion of evidence obtained from intensity channels. 
 This can be done using a simple average, principal component analysis, ROC statistics, etc.
-See~\cite{DeBorba2020}.
 
 The study by de Borba et al.~\cite{DeBorba2020} is the foundation for this research. 
-It presents evidence of the location of edge points in images with low signal-to-noise ratio by using a deterministic approach that does not take into account the variability of the estimator.
-We extended this investigation using new edge detectors following the work of~\cite{Xiang2016, Nascimento2014,Shi2020}.
-In addition, various quality metrics will be employed to evaluate and compare the results of edge evidence fusion in PolSAR images.
+It finds evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator. 
+We extended this investigation using new edge detectors~\cite{Xiang2016, Nascimento2014,Shi2020}. 
+In addition, we employ various quality metrics to evaluate and compare the results of fusing edge evidence in PolSAR images.
+
 \section{Background}
-\subsection{PolSAR data representation }
+\subsection{PolSAR data representation}
+
 Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted.
-The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information.
-\begin{align}
+The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information:
+\begin{equation}
  \mathbf{S} = \begin{bmatrix}
@@
 \label{E:a1}
-\end{align}
-where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ generate the power return in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ are responsible for the power return in the cross-polarized channels.\par
-If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, the single-look PolSAR data can be represented using a scattering vector:
-\begin{align}
+\end{equation}
+where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
+If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, single-look PolSAR data can be represented using a scattering vector:
+\begin{equation}
 \mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
 \label{E:21}
-\end{align}
-where  the superscript $t$ stands for the transpose operation. The multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
-\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^H \rangle= \frac{1}{L} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), here $\langle \cdot \rangle$ is the ensemble average, H  the is complex conjugate transpose operator, and $L$ is the number of looks.
-Covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$
-see~\cite{Qin2022}.
+\end{equation}
+where  the superscript $t$ stands for the transpose operation. 
+Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
+\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
+The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite;
+see Ref.~\cite{Qin2022}.
+
 \subsection{Gamma distribution}
@@
 
-Considering the previous section, we assume that the distribution of each intensity channel  follows a Gamma law, as described by: 
+We assume that the distribution of each intensity channel  follows a Gamma law, characterized by the probability density function
 \begin{equation}
@@
 \begin{equation}
-\mathcal{L}(\mu, L; \mathbf{z}) = 
+\mathcal{L}(\mu, L; \bm{z}) = 
 n \big[L\ln (L / \mu) - \ln \Gamma(L)\big]
@@
 \end{equation}
-Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, is obtained by maximizing~\eqref{eq:LogLikelihoodGamma}.
+Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
 
@@
 Various techniques, including maximum likelihood, entropy, and geodesic distance, are commonly used in research studies to identify edge points~\cite{NaranjoTorres2017,Nascimento2019}.
-To locate edge points in these types of images, modeling the data using a suitable statistical distribution and determining the related parameters is necessary.
+Suitable statistical models are needed for locating edge points in these types of images.
 
 The Gambini algorithm~\cite{Gambini2007} is a highly appealing method for edge detection. 
-It is designed to be localized, searching for evidence of edges within a narrow data strip.
-The algorithm involves the projection of rays and identifying edge evidence by maximizing a value function.
+It searches for evidence of edges within a narrow data strip. 
+The algorithm involves projecting rays and identifying edge evidence by maximizing a value function.
 
 The algorithm starts by casting rays from a point inside the candidate region, e.g., the centroid.
-Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$:
+Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$ into the interior $\bm z_\text{I}$ and exterior $\bm z_\text{E}$ samples:
 $$
@@
 
-Then, the total log-likelihood is calculated of $\bm z_\text{I}$ and $\bm z_\text{E}$:
+Then, the total log-likelihood is
 \begin{equation}\label{eq:TotalLogLikelihood}
@@
 \end{equation}
-The estimate of the edge position on the ray is represented by the coordinate  $\widehat\jmath$, which maximizes it.
+The estimate of the edge position on the ray is the coordinate  $\widehat\jmath$ which maximizes $\mathcal L$.
 
 \subsection{Fusion methods for edge evidence}
-In~\cite{DeBorba2020}, a fusion of edge evidence is carried out in the channels of intensities HH, HV, and VV, of a PolSAR image to produce a unique and more accurate edge position estimator.
-For this purpose, six fusion methods were used:  simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).\par
+
+De Borba et al.~\cite{DeBorba2020} fused the edges evidence obtained in intensities channels HH, HV, and VV to produce a unique and more accurate edge position estimator. 
+The authors used six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).
 
 Edge evidence fusion methods are essential to quantify and qualify the information obtained from each image channel. 
-This information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.
+Such information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.
+
 \section{Quality assessment}
-Quality assessment is a central issue in the image fusion process to compare the quality of the fused images and the performance of the method used~\cite{Somvanshi2017}.
-Quality measure indicators that are most used to evaluate fusion results are:  mean square error (MSE)~\cite{beaulieu2003multi}, standard deviation (SD)~\cite{choi2003biorthogonal}, average gradient (AG)~\cite{li2005color}, the correlation (CC) coefficient~\cite{aiazzi2004spectral}, entropy~\cite{han2008study}, and the peak signal-to-noise ratio (PSNR)~\cite{canga2005}.
-Some of these metrics are defined as follows: Mean square error measures the spectral distortion introduced by the fusion process.
+
+Some of the most frequently used indicators of quality are the mean square error (MSE)~\cite{beaulieu2003multi}, 
+the correlation (CC) coefficient~\cite{aiazzi2004spectral}, and the entropy~\cite{han2008study}:
+\begin{itemize}
+	\item Mean square error measures the spectral distortion introduced by the fusion process.
 	$$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
-   % where $(i, j)$ denote pixel location.
-The correlation coefficient measures the degree of correlation between the enhanced and the original images.
+	\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.
 	$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
-   % where $x_i$, $y_i$ are the grey values of homologous pixel synthesised image and real image.
-And, the Entropy is used for measuring the richness of data in enhanced images.
+	\item The Entropy is used for measuring the richness of data in enhanced images.
 	$$H=-\sum_{i=1}^{n}d(i)\log_2d(i).$$
-    %where $G$ is the number of grey level of the image’s histogram and $d(i)$ is the normalised frequency of occurrence of each grey level.
+	%%% ACF O que é d(i)?
+\end{itemize}
 
-Following the image fusion quality assessment strategy proposed in~\cite{Li2010, Somvanshi2017,Nikola2015}, we intend to utilize this approach in our study for the fusion of edge evidence through statistical analysis.
+We follow the image fusion quality assessment strategy proposed in~\cite{Li2010, Somvanshi2017,Nikola2015} for the problem at hand, using statistical analyses.
 
@@
 \subsection{Exploring the concept of explainability}
-Explainability is a crucial concern when it comes to artificial intelligence (AI)~\cite{Vilone2021}.
-It refers to the ability to understand and interpret the decisions and actions made by an AI system.
-This is particularly important in applications where the stakes are high, such as in medical diagnosis~\cite{Tjoa2021}.
-The term~\textit{explainable} refers to a statement, fact, or situation that provides a reason for why something happened.
-It helps to make something clear or interpretable.
+
+Explainability is crucial when it comes to artificial intelligence (AI) and related fields~\cite{Vilone2021}. 
+It refers to the ability to understand and interpret the decisions and actions made by an automatic system.
 
 The proposed methodology in this work focuses on identifying interpretable measures that can be used to weigh the influence of individual estimates during an evidence fusion process.
+
 \section{RESULTS}
 
-From Fig.~\ref{fig:res}(a)-(c), we can see the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.\par
-According to the research in~\cite{DeBorba2020}, various fusion methods were utilized to detect edge evidence.
+Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
+De Borba et al.~\cite{DeBorba2020} applied various fusion methods to detect edge evidence. 
 As an example, the results obtained by applying PCA and ROC methods to an AIRSAR L-band image of Flevoland are shown in Fig.~\ref{fig:2}.%(a)-(b).
@@
 \end{figure}
+
 \section{CONCLUSION}
 The project outlined here will develop fusion techniques that factor in the quality of each evidence.
-In this way, evidence subject to great variability or that may be inconsistent with other evidence, will have less influence.
+In this way, evidence subjected to great variability or that may be inconsistent with other pieces of evidence, will have less influence.
+
 An explainable fusion of statistical evidence can provide semantically rich information on the contribution of each component to the composition of the final result. 
@@
 %%% The source is in ../../Common/references
-\bibliographystyle{IEEEbib}
+\bibliographystyle{IEEEtranS}
 \bibliography{../../Common/references}

### 2023-01-26 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
some update in notation

@@
 
-The study on the applications of PolSAR data, particularly edge detection, has received increasing attention~\cite{Jin2016,Wang2018}.
+The study on the applications of PolSAR data, including edge detection, has received increasing attention~\cite{Jin2016,Wang2018}.
 Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}.
@@
 Some of the most frequently used indicators of quality are the mean square error (MSE)~\cite{beaulieu2003multi}, 
-the correlation (CC) coefficient~\cite{aiazzi2004spectral}, and the entropy~\cite{han2008study}:
+the correlation coefficient (CC)~\cite{aiazzi2004spectral}, and the entropy (H)~\cite{han2008study}:
 \begin{itemize}
@@
 	$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
-	\item The Entropy is used for measuring the richness of data in enhanced images.
-	$$H=-\sum_{i=1}^{n}d(i)\log_2d(i).$$
+	\item The entropy is used for measuring the richness of data in enhanced images.
+	$$H=-\sum_{i=1}^{n}p(i)\log_2p(i).$$
 	%%% ACF O que é d(i)?

### 2023-01-28 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
Reduce paper to 3 pages

--- 2023-01-26 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
@@
 \end{abstract}
+\vspace{-0.3cm}
 \section{Introduction}
+\vspace{-0.2cm}
 PolSAR images offer a distinct advantage over other remote sensing images by utilizing four different polarization combinations, specifically HH, HV, VH, and VV~\cite{Hua2022}.
 These combinations are based on the horizontal (H), and vertical (V) polarizations of the received and transmitted signals.
-The polarization allows for the acquisition of detailed and comprehensive data, providing significantly more information than the single polarization mode~\cite{Zhai2015}.
+%The polarization allows for the acquisition of detailed and comprehensive data, providing significantly more information than the single polarization mode~\cite{Zhai2015}.
 
-The study on the applications of PolSAR data, particularly edge detection, has received increasing attention~\cite{Jin2016,Wang2018}.
-Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Xiang2016}.
-Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Schou2003,Gambini2007,Nascimento2014}.
+%The study on the applications of PolSAR data, including edge detection, has received increasing attention~\cite{Jin2016}. 
+Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Jin2016}.
+Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Gambini2007,Nascimento2014}.
 
-Shi et al.~\cite{Shi2020} proposed a new method for extracting all edge-related features. 
-This method is designed to reduce speckle noise in regions with both weak and strong edges, particularly in heterogeneous areas. 
-Another approach~\cite{DeBorba2020} involves the fusion of evidence obtained from intensity channels. 
-This can be done using a simple average, principal component analysis, ROC statistics, etc.
+% Shi et al.~\cite{Shi2020} proposed a new method for extracting all edge-related features. 
+% This method is designed to reduce speckle noise in regions with both weak and strong edges, particularly in heterogeneous areas. 
+% Another approach~\cite{DeBorba2020} involves the fusion of evidence obtained from intensity channels. 
+% This can be done using a simple average, principal component analysis, ROC statistics, etc.
 
@@
 It finds evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator. 
-We extended this investigation using new edge detectors~\cite{Xiang2016, Nascimento2014,Shi2020}. 
+We extended this investigation using new edge detectors~\cite{Shi2020,Xiang2016}. 
 In addition, we employ various quality metrics to evaluate and compare the results of fusing edge evidence in PolSAR images.
 
+\vspace{-0.2cm}
 \section{Background}
-\subsection{PolSAR data representation}
-
-Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted.
+\vspace{-0.2cm}
+\subsection{PolSAR data representation}\vspace{-0.2cm}
+%Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted. ~\cite{Lee2017}
 The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information:
+\vspace{-0.2cm}
 \begin{equation}
@@
 S_{\text{VH}} & S_{\text{VV}}
-\end{bmatrix},  
-\label{E:a1}
+\end{bmatrix}.  
+\label{E:a1}\vspace{-0.2cm}
 \end{equation}
-where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
-If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, single-look PolSAR data can be represented using a scattering vector:
+%where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
+%If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$,
+Single-look PolSAR data can be represented using a scattering vector:
 \begin{equation}
 \mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
-\label{E:21}
+\label{E:21}%\vspace{-0.1cm}
 \end{equation}
@@
 Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
-\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
-The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite;
-see Ref.~\cite{Qin2022}.
-
-\subsection{Gamma distribution}
-%Over the past decades, several distributions have been created for modeling PolSAR image data.
-The most commonly used distribution for working with images generated from polarimetric multilook data is the complex Wishart distribution~\cite{Nielsen2007}.
-This distribution is characterized by two parameters, the covariance matrix $\mathbf{\Sigma}$ and the number of looks L of the image.
-Thus, the polarimetric matrix $\mathbf{Z} = \mathbf{C}=\left\langle\mathbf{k}_s\mathbf{k}_s^H \right\rangle$ can be derived following a complex Wishart distribution, represented as $\mathbf{Z}\sim \mathcal{W}_{\mathcal{C}}(\mathbf{\Sigma}, L),$  whose probability density function
-%is~\cite{Frery2014, Qin2022}:
-%\begin{align}
-%f_{\mathbf{Z}}(\mathbf{Z})=\frac{L^{qL}|\mathbf{Z}|^{L-q}}{|\mathbf{\Sigma}|^L\Gamma_q(L)}\exp\left\{-L \Tr\left(\mathbf{\Sigma}^{-1}\mathbf{Z}\right)\right\},
-%\label{E:22}
-%\end{align}
-%where $\Gamma_q(L)=\pi^{q(q-1)/2}\prod_{i=0}^{q-1}\Gamma(L-i)$,  $\Gamma(\cdot)$ denotes the gamma function and $\Tr(\cdot)$ is the trace of the matrix.
-In this case, three channels will be used, i.e., $q = 3$.
+$\mathbf{C}=\langle\mathbf{k}_s\mathbf{k}_s^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H}$, where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
+The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite; see Ref.~\cite{Qin2022}.
+%-------------------------------------------------------------------------------------------------------------
+\subsection{Gamma distribution}\vspace{-0.1cm}
 
 We assume that the distribution of each intensity channel  follows a Gamma law, characterized by the probability density function
+\vspace{-0.3cm}
 \begin{equation}
 f_Z(z;\mu,L)=\frac{L^{L}z^{L-1}}{\mu^{L}\Gamma(L)} \exp\big\{-Lz/\mu\big\},\quad z>0,
-\label{func_dens_uni_gamma}
+\label{func_dens_uni_gamma}\vspace{-0.2cm}
 \end{equation}
@@
 The log-likelihood of the sample $\bm{z} = (z_1,\dots,z_n)$ under this model is
+\vspace{-0.3cm}
 \begin{equation}
@@
 \end{equation}
-Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
+Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
+\subsection{Edge detection on a single data strip}\vspace{-0.1cm}
+%Finding the edges of an image is a crucial step in image analysis.
+These boundaries define distinct regions within the image, such as pastures, urban areas, or forested areas~\cite{monferran2020modelo}.
 
-% A simplified derivation to obtain the complex Wishart distribution was presented in \cite{LEE1994}.
-\subsection{Edge detection on a single data strip}
-Finding the edges of an image is a crucial step in image analysis.
-These boundaries define distinct regions within the image, such as pastures, urban areas, or forested areas~\cite{monferran2020modelo}.
 Various techniques, including maximum likelihood, entropy, and geodesic distance, are commonly used in research studies to identify edge points~\cite{NaranjoTorres2017,Nascimento2019}. 
@@
 It searches for evidence of edges within a narrow data strip. 
-The algorithm involves projecting rays and identifying edge evidence by maximizing a value function.
-
+%The algorithm involves projecting rays and identifying edge evidence by maximizing a value function.
 The algorithm starts by casting rays from a point inside the candidate region, e.g., the centroid.
 Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$ into the interior $\bm z_\text{I}$ and exterior $\bm z_\text{E}$ samples:
+\vspace{-0.2cm}
 $$
@@
 We then estimate $(\mu_\text{I},L_\text{I})$ and $(\mu_\text{E},L_\text{E})$ with $\bm z_\text{I}$ and $\bm z_\text{E}$, respectively, by maximizing~\eqref{eq:LogLikelihoodGamma}, and obtain $\big(\widehat{\mu}_\text{I}, \widehat{L}_\text{I}\big)$ and $\big(\widehat{\mu}_\text{E}, \widehat{L}_\text{E}\big)$.
-
-Then, the total log-likelihood is
-\begin{equation}\label{eq:TotalLogLikelihood}
-\begin{aligned}
-\mathcal L\big(j&;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
-	\frac{\widehat{L}_\text{I}}{\widehat{\mu}_\text{I}}\sum_{k=1}^{j} z_k +
-	\frac{\widehat{L}_\text{E}}{\widehat{\mu}_\text{E}}\sum_{k=j+1}^{n} z_k  
-	\Bigg)\mbox{}\\
-&+j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
-+\widehat{L}_\text{I} \sum_{k=1}^{j}\ln z_k  \mbox{}\\
-&+(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
-+\widehat{L}_\text{E} \sum_{k=j+1}^{n}\ln z_k .%-\\ 
-\raisetag{2.2em}
-\end{aligned}
-\end{equation}
+% Then, the total log-likelihood is
+% \begin{equation}\label{eq:TotalLogLikelihood}
+% \begin{aligned}
+% \mathcal L\big(j&;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
+% 	\frac{\widehat{L}_\text{I}}{\widehat{\mu}_\text{I}}\sum_{k=1}^{j} z_k +
+% 	\frac{\widehat{L}_\text{E}}{\widehat{\mu}_\text{E}}\sum_{k=j+1}^{n} z_k  
+% 	\Bigg)\mbox{}\\
+% &+j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
+% +\widehat{L}_\text{I} \sum_{k=1}^{j}\ln z_k  \mbox{}\\
+% &+(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
+% +\widehat{L}_\text{E} \sum_{k=j+1}^{n}\ln z_k .%-\\ 
+% \raisetag{2.2em}
+% \end{aligned}
+% \end{equation}
 The estimate of the edge position on the ray is the coordinate  $\widehat\jmath$ which maximizes $\mathcal L$.
-
-\subsection{Fusion methods for edge evidence}
+\vspace{-0.2cm}
+\subsection{Fusion methods for edge evidence}%\vspace{-0.1cm}
 
@@
 
+\vspace{-0.2cm}
 \section{Quality assessment}
-
+\vspace{-0.2cm}
 Some of the most frequently used indicators of quality are the mean square error (MSE)~\cite{beaulieu2003multi}, 
-the correlation (CC) coefficient~\cite{aiazzi2004spectral}, and the entropy~\cite{han2008study}:
+the correlation coefficient (CC)~\cite{aiazzi2004spectral}, and the entropy (H)~\cite{han2008study}:
 \begin{itemize}
-	\item Mean square error measures the spectral distortion introduced by the fusion process.
-	$$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
-	\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.
-	$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
-	\item The Entropy is used for measuring the richness of data in enhanced images.
-	$$H=-\sum_{i=1}^{n}d(i)\log_2d(i).$$
+\itemsep0em 
+ \vspace{-0.1cm}\item Mean square error measures the spectral distortion introduced by the fusion process.
+%$$MSE= \displaystyle \frac{\sum_{i=1}^{M}\sum_{i=1}^{N}(f(i,j)-r(i,j))^2}{M\times N}.$$
+% where $(i, j)$ denote pixel location.
+\vspace{-0.2cm}\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.\vspace{-0.35cm}
+%$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
+% where $x_i$, $y_i$ are the grey values of homologous pixel synthesised image and real image.
+\vspace{-0.2cm}\item The entropy is used for measuring the richness of data in enhanced images.
+%$$H=-\sum_{i=1}^{n}p(i)\log_2p(i).$$
 %%% ACF O que é d(i)?
+% p(i) is probability of occurrence of a particular gray level i,
+% or $p(i)$ is the normalised frequency of occurrence of each grey level. 
 \end{itemize}
+%We follow the image fusion quality assessment strategy proposed in~\cite{Li2010,Nikola2015,Somvanshi2017} for the problem at hand, using statistical analyses.
 
@@
 
-%We use the criteria described in [2]  to evaluate the quality of each evidence for each fusion method.
-
-%We expanded our research to a statistical analysis, using quality metrics to assess the efficiency in the fusion of evidence, using different methods.
-
+%
 \subsection{Exploring the concept of explainability}
@@
 The proposed methodology in this work focuses on identifying interpretable measures that can be used to weigh the influence of individual estimates during an evidence fusion process.
-
+%
+ \vspace{-0.2cm}
 \section{RESULTS}
-
+\vspace{-0.2cm}
+%
 Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
@@
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/hh.pdf,width=4cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/hh.pdf,width=3.9cm}}
   \vspace{-0.1cm}
@@
   \centering
-\centerline{\epsfig{figure=../../../Figures/PDF/hv.pdf,width=4.0cm}}
+\centerline{\epsfig{figure=../../../Figures/PDF/hv.pdf,width=3.9cm}}
   \vspace{-0.1cm}
@@
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/vv.pdf,width=4.0cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/vv.pdf,width=3.8cm}}
   \vspace{-0.1cm}
   \centerline{(c) Channel VV.}\medskip
-\end{minipage}
+\end{minipage}\vspace{-0.3cm}
 %
@@
 \label{fig:res}
-%
+\vspace{-0.4cm}
 \end{figure}
@@
   \centering
-\centerline{\epsfig{figure=../../../Figures/PDF/pca.pdf,width=4.0cm}}
+\centerline{\epsfig{figure=../../../Figures/PDF/pca.pdf,width=3.9cm}}
   \vspace{-0.1cm}
@@
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/roc.pdf,width=4.0cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/roc.pdf,width=3.9cm}}
   \vspace{-0.1cm}
   \centerline{(b) ROC fusion.}\medskip
-\end{minipage}
+\end{minipage}\vspace{-0.3cm}
 %
@@
 
+ \vspace{-0.2cm}
 \section{CONCLUSION}
+\vspace{-0.2cm}
 The project outlined here will develop fusion techniques that factor in the quality of each evidence.
@@
 
-%(bias, variance, etc.)
-%Lastly, we expanded our research to include statistical analysis by utilizing quality metrics() to evaluate the effectiveness of the fusion of evidence.
-
-%\newpage
+\newpage
 

### 2023-05-31 Text/Articles/IGARSS_2023/IG23_2023.tex
update files

% Template for IGARSS-2020 paper; to be used with:
%          spconf.sty  - LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,epsfig}
\usepackage{bm,bbm}
\usepackage{float}
\usepackage{epstopdf} %para imagenes en eps y 
%%%
\usepackage{url}
\usepackage{booktabs,chemformula}
\addtolength{\tabcolsep}{-0.3em}
%\usepackage[backend=biber,style=phys,doi=false,eprint=false,url=false]{biblatex}
%\usepackage{booktabs, longtable,array}
%\usepackage[table]{xcolor}
%\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
%\usepackage[a4paper,margin=1in]{geometry}
%%%
%\addbibresource{\jobname.bib}
% \newcommand{\mcite}[1]{\mbox{\cite{#1}}}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

\DeclareMathOperator{\Tr}{Tr}

%

% Title.
% ------
\title{Quality assessment measures for explainable fusion of statistical evidences of edges in PolSAR images: A First Approach}
% Single address.
% ---------------

%\address{Author Affiliation(s)}
\name{Rosa Janeth Alpala$^a$, Anderson A.\ de Borba$^{b,c}$, and Alejandro C.\ Frery$^c$.\thanks{e-mail:$^{a}$janeth.alpala@ufpe.br,$^{b}$anderson.borba@mackenzie.br, $^c$alejandro.frery@vuw.ac.nz}}
\address{$^a$ Universidade Federal de Pernambuco, 50740-540, Recife, PE, Brazil,           \\
$^b$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil, \\
$^c$School of Mathematics and Statistics, Victoria University of Wellington, 6140, New Zealand.}

%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
\vspace{-0.2cm}
This work aims to develop techniques for the fusion of statistical evidences obtained from the application of Statistical Information Theory (SIT) and Statistical Information Geometry (SIG) in image processing and analysis, with a specific focus on Polarimetric Synthetic Aperture Radar (PolSAR) imagery. The goal is to generate a single solution superior to individual solutions. Furthermore, properties or measures that assess the quality of results will also be employed to evaluate the effectiveness of fusion methods in detecting edge evidence.

%
\begin{keywords}
PolSAR, edge detection,  information fusion,  quality
measures 
\end{keywords}
%
\end{abstract}
\vspace{-0.3cm}
\section{Introduction}
\vspace{-0.2cm}
PolSAR images offer a distinct advantage over other remote sensing images by utilizing four different polarization combinations, specifically HH, HV, VH, and VV~\cite{Hua2022}. These combinations are based on the horizontal (H), and vertical (V) polarizations of the received and transmitted signals.

Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Jin2016}.

The study by de Borba et al.~\cite{DeBorba2020} is the foundation for this research. 
It finds evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator. We extended this research by incorporating several quality metrics that not only assess the accuracy of the edge estimate, but also provide insight into the explainability of the fused edge evidence.
%We extended this investigation using various quality metrics to evaluate and compare the results of fusing edge evidence in PolSAR images.

The remaining of this paper is organized as follows: Section \ref{sec_2} provides a brief introduction to the background knowledge, including PolSAR data and edge detection. Section 3 presents an overview of the quality measures employed. The evaluation of edge estimation quality using various metrics is discussed in Section 4. Lastly, conclusion is provided in Section 5.

\section{Background}\label{sec_2}
\vspace{-0.2cm}
\subsection{PolSAR data representation}
Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted. The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information:
\begin{equation}
 \mathbf{S} = \begin{bmatrix}
S_{\text{HH}} & S_{\text{HV}} \\
S_{\text{VH}} & S_{\text{VV}}
\end{bmatrix},  
\label{E:a1}
\end{equation}
where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, single-look PolSAR data can be represented using a scattering vector:
\begin{equation}
\mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
\label{E:21}
\end{equation}
where  the superscript $t$ stands for the transpose operation. 
Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks. 
The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite;
see Ref.~\cite{Qin2022}.

\subsection{Gamma distribution}
%Over the past decades, several distributions have been created for modeling PolSAR image data. The most commonly used distribution for working with images generated from polarimetric multilook data is the complex Wishart distribution~\cite{Nielsen2007}. This distribution is characterized by two parameters, the covariance matrix $\mathbf{\Sigma}$ and the number of looks L of the image. Thus, the polarimetric matrix $\mathbf{Z} = \mathbf{C}=\left\langle\mathbf{k}_s\mathbf{k}_s^H \right\rangle$ can be derived following a complex Wishart distribution, represented as $\mathbf{Z}\sim \mathcal{W}_{\mathcal{C}}(\mathbf{\Sigma}, L),$  whose probability density function
%is~\cite{Frery2014, Qin2022}:
%\begin{align}
%f_{\mathbf{Z}}(\mathbf{Z})=\frac{L^{qL}|\mathbf{Z}|^{L-q}}{|\mathbf{\Sigma}|^L\Gamma_q(L)}\exp\left\{-L \Tr\left(\mathbf{\Sigma}^{-1}\mathbf{Z}\right)\right\},
%\label{E:22}
%\end{align}
%where $\Gamma_q(L)=\pi^{q(q-1)/2}\prod_{i=0}^{q-1}\Gamma(L-i)$,  $\Gamma(\cdot)$ denotes the gamma function and $\Tr(\cdot)$ is the trace of the matrix. In this case, three channels will be used, i.e., $q = 3$.

We assume that the distribution of each intensity channel  follows a Gamma law, characterized by the probability density function
\begin{equation}
f_Z(z;\mu,L)=\frac{L^{L}z^{L-1}}{\mu^{L}\Gamma(L)} \exp\big\{-Lz/\mu\big\},\quad z>0,
\label{func_dens_uni_gamma}
\end{equation}
where $L>0$, and
$\mu>0$ is the mean.
The log-likelihood of the sample $\bm{z} = (z_1,\dots,z_n)$ under this model is
\begin{equation}
\mathcal{L}(\mu, L; \bm{z}) = 
n \big[L\ln (L / \mu) - \ln \Gamma(L)\big]
+L \sum_{k=1}^{n}\ln z_k -\frac{L}{\mu}\sum_{k=1}^{n} z_k.
\label{eq:LogLikelihoodGamma}
\end{equation}
Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.

% A simplified derivation to obtain the complex Wishart distribution was presented in \cite{LEE1994}.
\subsection{Edge detection on a single data strip}
Finding the edges of an image is a crucial step in image analysis. These boundaries define distinct regions within the image, such as pastures, urban areas, or forested areas~\cite{monferran2020modelo}. Various techniques, including maximum likelihood, entropy, and geodesic distance, are commonly used in research studies to identify edge points~\cite{NaranjoTorres2017,Nascimento2019}. 
Suitable statistical models are needed for locating edge points in these types of images.

The Gambini algorithm~\cite{Gambini2007} is a highly appealing method for edge detection. 
It searches for evidence of edges within a narrow data strip. 
The algorithm involves projecting rays and identifying edge evidence by maximizing a value function.

The algorithm starts by casting rays from a point inside the candidate region, e.g., the centroid.
Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$ into the interior $\bm z_\text{I}$ and exterior $\bm z_\text{E}$ samples:
$$
\bm z = (\underbrace{z_1,z_2,\dots,z_j}_{\bm z_\text{I}}, 
\underbrace{z_{j+1}, z_{j+2},\dots,z_n}_{\bm z_\text{E}}).
$$
Two possibly different models are assumed for each partition:
$\bm Z_\text{I} \sim \Gamma(\mu_\text{I},L_\text{I})$, and 
$\bm Z_\text{E} \sim \Gamma(\mu_\text{E},L_\text{E})$.
We then estimate $(\mu_\text{I},L_\text{I})$ and $(\mu_\text{E},L_\text{E})$ with $\bm z_\text{I}$ and $\bm z_\text{E}$, respectively, by maximizing~\eqref{eq:LogLikelihoodGamma}, and obtain $\big(\widehat{\mu}_\text{I}, \widehat{L}_\text{I}\big)$ and $\big(\widehat{\mu}_\text{E}, \widehat{L}_\text{E}\big)$.

Then, the total log-likelihood is
\begin{equation}\label{eq:TotalLogLikelihood}
\begin{aligned}
\mathcal L\big(j&;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
	\frac{\widehat{L}_\text{I}}{\widehat{\mu}_\text{I}}\sum_{k=1}^{j} z_k +
	\frac{\widehat{L}_\text{E}}{\widehat{\mu}_\text{E}}\sum_{k=j+1}^{n} z_k  
	\Bigg)\mbox{}\\
&+j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
+\widehat{L}_\text{I} \sum_{k=1}^{j}\ln z_k  \mbox{}\\
&+(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
+\widehat{L}_\text{E} \sum_{k=j+1}^{n}\ln z_k .%-\\ 
\raisetag{2.2em}
\end{aligned}
\end{equation}
The estimate of the edge position on the ray is the coordinate  $\widehat\jmath$ which maximizes $\mathcal L$.
\vspace{-0.2cm}
\subsection{Fusion methods for edge evidence}
De Borba et al.~\cite{DeBorba2020} fused the edges evidence obtained in intensities channels HH, HV, and VV to produce a unique and more accurate edge position estimator. 
The authors used six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).

Edge evidence fusion methods are essential to quantify and qualify the information obtained from each image channel. 
Such information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.

\section{Quality assessment}
\vspace{-0.2cm}
Commonly used quality measures for performance evaluation include Mean Absolute Error (MAE) and Root Mean Square Error (RMSE). MAE calculates the average absolute difference between estimated and reference values, being robust against outliers and independent of error signs. In contrast, RMSE emphasizes larger errors, making it more sensitive to outliers \cite{Ritter2013}. Additional precision evaluation measures include Standard Deviation (SD) and Correlation Coefficient (CC). SD measures the dispersion of values relative to their average, higher SD indicates lower precision. CC quantifies the linear relationship between the value sets~\cite{Vijayaraj}. The formulas are as follows:
\begin{align*}
	\text{RMSE} =\sqrt{\frac{1}{n}\sum_{i=1}^{n}\left(y_i-\hat{y}_i\right)^2},
	%\label{rmse}
\end{align*}
\vspace{-0.3cm}
\begin{align*}
	\text{MAE} =\frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y}_i|,
	%\label{mae}
\end{align*}
\begin{align*}
	\text{SD} =\sqrt{\frac{1}{n-1}\sum_{i=1}^{n}\left(y_i-\bar{y}\right)^2},
	%\label{sd}
\end{align*}
\begin{align*}
\text{CC}=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2\sum_{i=1}^{n}(y_i-\Bar{y})^2}},
%\label{cc}
\end{align*}
where $n$ represents the number of observations, $y_i$ denotes the estimated values, $\hat{y}_i$ are the reference measured values, and  $\Bar{x}$ and $\Bar{y}$ are the mean values.

 Another metric that is used is the entropy, this quantifies the uncertainty of a probability distribution. In information theory, it reflects the level of uncertainty in a random experiment or signal. A peaked distribution has low entropy and low uncertainty, while a homogeneous distribution has high entropy and high uncertainty \cite{Mays2002}. For a discrete random variable $X$ with $\left\{x_1, x_2, \ldots, x_N\right\}$ the set of possible values it can take, Shannon entropy is defined as:
\begin{align}
	H(X)=-\sum_{i=1}^{N}p(x_i)\log_2p(x_i),
	\label{eq:H}
\end{align}
where $p(x_i)$ represents the probability of $i$th element in the vector.

Entropy is commonly used in remote sensing to describe the information content of images. It employs expression \eqref{eq:H}  to assess the amount of information conveyed by each pixel within an image.

\vspace{-0.2cm}
\section{RESULTS}
\vspace{-0.2cm}
Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
De Borba et al.~\cite{DeBorba2020} applied various fusion methods to detect edge evidence. 
As an example, the results obtained by applying PCA, ROC and MR-SWT methods to an AIRSAR L-band image of Flevoland are shown in Fig.~\ref{fig:fus}.%(a)-(b).

\begin{figure}[H]
   % \centering
    \begin{minipage}{0.5\textwidth}
       \begin{minipage}[b]{.32\linewidth}
  \centering
 \centerline{\epsfig{figure=figures/hh_f.pdf,width=2.8cm}}
  \vspace{-0.1cm}
  \centerline{\small{(a) Channel HH.}}\medskip
\end{minipage}
\begin{minipage}[b]{.31\linewidth}
  \centering
\centerline{\epsfig{figure=figures/hv.pdf,width=2.8cm}}
  \vspace{-0.1cm}
  \centerline{\small{(b) Channel HV.}}\medskip
\end{minipage}
%\hfill
\begin{minipage}[b]{0.31\linewidth}
  \centering
 \centerline{\epsfig{figure=figures/vv_c.pdf,width=2.8cm}}
  \vspace{-0.1cm}
  \centerline{\small{(c) Channel VV.}}\medskip
\end{minipage}\vspace{-0.3cm}
       \caption{Edges evidences from the three intensity channels.}
\label{fig:res}
    \end{minipage}%\hfill
\end{figure}
\vspace{-0.4cm}
\begin{figure}[H]
   % \centering
    \begin{minipage}{0.5\textwidth}
       \begin{minipage}[b]{.32\linewidth}
  \centering
 \centerline{\epsfig{figure=figures/roc.pdf,width=2.75cm}}
  \vspace{-0.1cm}
  \centerline{\small{(a) ROC fusion.}}\medskip
\end{minipage}
\begin{minipage}[b]{.31\linewidth}
  \centering
\centerline{\epsfig{figure=figures/pca_1.pdf,width=2.8cm}}
  \vspace{-0.1cm}
  \centerline{\small{(b) PCA fusion.}}\medskip
\end{minipage}
%\hfill
\begin{minipage}[b]{0.31\linewidth}
  %\centering
 \centerline{\epsfig{figure=figures/swt.pdf,width=2.75cm}}
  \vspace{-0.1cm}
  \centerline{\small{(c) MR-SWT fusion.}}\medskip
\end{minipage}\vspace{-0.3cm}
       \caption{Fusion methods.}
\label{fig:fus}
    \end{minipage}%\hfill
\end{figure}\vspace{-0.2cm}

Figs.~\ref{fig:entropy1}(a)-(c), illustrate the total log-likelihood $\mathcal L$ functions with respect to the $j$th position, where these functions exhibit peaks that potentially serve as indicators of edge position. Specifically, the concept of entropy is used as a means of evaluating the accuracy of edge position.\vspace{-0.3cm}
\begin{figure}[H]
   % \centering
    \begin{minipage}{0.5\textwidth}
       \begin{minipage}[b]{.5\linewidth}
  \centering
 \centerline{\epsfig{figure=figures/likelihood_hh.pdf,width=5cm}}
  \vspace{-0.1cm}
  \centerline{\footnotesize{ (a) Channel HH (\textbf{Entropy = 0.0546}).}}\medskip
\end{minipage}%\hfill
\begin{minipage}[b]{.5\linewidth}
  \centering
\centerline{\epsfig{figure=figures/likelihood_hv.pdf,width=5cm}}
  \vspace{-0.2cm}
  \centerline{\footnotesize{(b) Channel HV (\textbf{Entropy =  0.6361}).}}\medskip
\end{minipage}\\
\hfill 
\vspace{-0.3cm}
 \centering
\begin{minipage}[b]{0.5\linewidth}
  \centering
 \centerline{\epsfig{figure=figures/likelihood_vv.pdf,width=5cm}}
  \vspace{-0.1cm}
  \centerline{\footnotesize{(c) \, Channel VV  (\textbf{Entropy =  0.8577}).}}\medskip
\end{minipage}\vspace{-0.2cm}
       \caption{Entropy as a quality measure for edge evidence.} 
\label{fig:entropy1}
    \end{minipage}%\hfill
\end{figure}
\vspace{-0.3cm}
To calculate entropy,  we employ the transformation of the total log-likelihood function, into a discrete probability function, the sample is taken from a single data strip (ray) of length 120 pixels.  Subsequently, expression~\eqref{eq:H} is used to calculate the Shannon entropy, $H(X)$. The resulting value provides an objective metric for evaluating the accuracy of edge point detection. A low entropy value signifies precise estimation, characterized by a compact and peaked curve, see Fig.~\ref{fig:entropy1}(a). Conversely, a high entropy value suggests less accurate estimation, featuring a more dispersed probability distribution and a graph with a flatter and elongated shape, see Fig.~\ref{fig:entropy1}(b)-(c).\par
%\vspace{-0.1cm}
On the other hand, the aim of this study is to determine whether evidence fusion in PolSAR images provides more information, leading to accurate edge detection, compared to edge detection of individual channels.\par
%\vspace{-0.1cm}
Table~\ref{tab_1} illustrates the evaluation metrics employed to assess the quality of the estimated edge points by comparing their similarity with a predefined set of reference points. These metrics offer an objective evaluation of the accuracy of the obtained results. Entropy is calculated exclusively using the estimated edge point dataset ($\hat{x},\hat{y}$), while the remaining metrics (MAE, RMSE, SD, and CC) utilize both datasets. 
\begin{table}[H]
  \centering
  \begin{tabular}{@{}cccccc@{}}
    \toprule
Method  &Entropy    & MAE        & RMSE       &SD       & CC \\
    \midrule
   hh  & 6.6439      & 1.8400       & 3.7175   & 2.6291   & 0.9986 \\
   hv  & 6.6293      & 1.6700       & 2.9275   & 2.0640   & 0.9992 \\
   vv  & 6.6438      & 4.2400      & 7.9461    & 5.5649   & 0.9941 \\
   ROC & 6.0223      & 1.4154      & 2.3664    & 1.6311    & 0.9994 \\
   PCA & 7.7944      & 3.0180       & 6.0657   & 4.2788  & 0.9964 \\
   SWT & 12.0914     & 5.8006      & 9.2486   & 6.4161  & 0.9932 \\
    \bottomrule
  \end{tabular}\vspace{-0.1cm}
  \caption{\small{Assessment metrics.}}
  \label{tab_1}
\end{table}\vspace{-0.3cm}
The importance of entropy calculation is highlighted. For instance, with the ROC method, we observe low error and high correlation, indicating significant similarity between edge point positions. However, the low entropy value suggests a relatively small amount of information in the fused image. This implies precise edge detection with few outliers, but exhibiting a sparse distribution of points, as shown in Fig.~\ref{F4}. \vspace{-0.45cm}
\begin{figure}[H] %\vspace{-2.0mm} 
	\includegraphics[scale=0.55]{figures/roc_f.pdf}\vspace{-1.5mm} 
	\caption{Comparison of estimated points with reference points.}
	\label{F4}
\end{figure}
On the other hand, the PCA method demonstrates superior performance, as it exhibits a moderate entropy value along with low values of MAE, RMSE, and SD.

This approach enables a comprehensive evaluation of the characteristics and performance of fusion methods and individual channels. All metrics are depicted in Fig.~\ref{F5}. \vspace{-0.3cm}
\begin{figure}[H] 
	\includegraphics[scale=0.55]{figures/metricas.pdf}\vspace{-3.5mm} 
	\caption{illustration of quality metrics.}\vspace{-0.3cm}
	\label{F5}
\end{figure}%\vspace{-0.1cm}
The method for detecting edge evidence  and fusion methods were implemented in Python. Code and data are available for download at:  \url{ https://github.com/rjaneth/code_igarss_23.git}
\vspace{-0.3cm}
\section{CONCLUSION}
\vspace{-0.3cm}
This paper presents some fusion methods for edge evidence and assesses their estimation precision using commonly employed metrics in the literature, with a specific emphasis on entropy as the primary measure.

By incorporating entropy as an evaluation metric, we enhance the explainability of our fusion methodology. Entropy provides a quantitative measure of the diversity and variability of the detected edges, allowing us to assess the amount of information captured by the fusion process. This transparency in evaluating the results enhances the interpretability and trustworthiness of our approach.

Overall, the results demonstrate the effectiveness of the proposed fusion methods for edge evidence and highlight the importance of incorporating explainability measures, such as entropy, in the evaluation process. These findings contribute to the field of image and data fusion, providing insights into the information content and accuracy of the detected edges.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% ------------------------------------------------------------------------
%\bibliographystyle{IEEEtranS}
%\bibliographystyle{IEEEbib-abbrev}
\bibliographystyle{IEEEtran}
%\bibliography{strings,refs}

\bibliography{../../Common/references}
\end{document}

### 2023-05-31 Text/Articles/pages_2_ig/IG23_AbstractTemplate.tex
update files

--- 2023-01-28 Text/Articles/IGARSS_2023/IG23_AbstractTemplate.tex
@@
 %
+\maketitle
+\vspace{-0.4cm}
 \begin{abstract}
+%\vspace{-1.0cm}
 This work aims to develop techniques for the fusion of statistical evidences obtained from the application of Statistical Information Theory (SIT) and Statistical Information Geometry (SIG) in image processing and analysis, with a specific focus on Polarimetric Synthetic Aperture Radar (PolSAR) imagery.
@@
 Several methods and algorithms have been proposed for edge detection in PolSAR imagery~\cite{Gambini2007,Nascimento2014}. 
-
 % Shi et al.~\cite{Shi2020} proposed a new method for extracting all edge-related features. 
@@
 % This can be done using a simple average, principal component analysis, ROC statistics, etc.
-
 The study by de Borba et al.~\cite{DeBorba2020} is the foundation for this research. 
 It finds evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator.
+
 We extended this investigation using new edge detectors~\cite{Shi2020,Xiang2016}. 
 In addition, we employ various quality metrics to evaluate and compare the results of fusing edge evidence in PolSAR images.
-
 \vspace{-0.2cm}
 \section{Background}
-\vspace{-0.2cm}
-\subsection{PolSAR data representation}\vspace{-0.2cm}
+\vspace{-0.3cm}
+% \subsection{PolSAR data representation}\vspace{-0.2cm}
 %Using PolSAR data, a wide range of biophysical and geophysical parameters related to the Earth's surface can be efficiently and reliably extracted. ~\cite{Lee2017}
-The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information:
-\vspace{-0.2cm}
-\begin{equation}
- \mathbf{S} = \begin{bmatrix}
-S_{\text{HH}} & S_{\text{HV}} \\
-S_{\text{VH}} & S_{\text{VV}}
-\end{bmatrix}.  
-\label{E:a1}\vspace{-0.2cm}
-\end{equation}
-%where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
-%If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$,
-Single-look PolSAR data can be represented using a scattering vector:
-\begin{equation}
-\mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
-\label{E:21}%\vspace{-0.1cm}
-\end{equation}
-where  the superscript $t$ stands for the transpose operation. 
-Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
-$\mathbf{C}=\langle\mathbf{k}_s\mathbf{k}_s^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H}$, where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
-The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite; see Ref.~\cite{Qin2022}.
-%-------------------------------------------------------------------------------------------------------------
+% The polarimetric scattering matrix~\cite{Lee2017} serves as an instrumental tool to represent the polarimetric target information:
+% \vspace{-0.2cm}
+% \begin{equation}
+%  \mathbf{S} = \begin{bmatrix}
+% S_{\text{HH}} & S_{\text{HV}} \\
+% S_{\text{VH}} & S_{\text{VV}}
+% \end{bmatrix}, 
+% \label{E:a1}\vspace{-0.2cm}
+% \end{equation}
+% where the elements $S_{\text{HH}}$ and $S_{\text{VV}}$ are the returned power in the co-polarized channels, while the elements $S_{\text{HV}}$ and $S_{\text{VH}}$ relate to the cross-polarized channels.
+If the PolSAR targets comply with the reciprocal condition $(S_{\text{HV}} = S_{\text{VH}})$, single-look PolSAR data can be represented using a scattering vector:
+% \vspace{-0.2cm}
+% \begin{equation}
+% \mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
+% \label{E:21}\vspace{-0.1cm}
+% \end{equation}
+% where  the superscript $t$ stands for the transpose operation. 
+% Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
+% $\mathbf{C}=\langle\mathbf{k}_s\mathbf{k}_s^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H}$, where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
+% The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite; see Ref.~\cite{Qin2022}.
 \subsection{Gamma distribution}\vspace{-0.1cm}
-
-We assume that the distribution of each intensity channel  follows a Gamma law, characterized by the probability density function
+%Over the past decades, several distributions have been created for modeling PolSAR image data.
+The most commonly used distribution for working with images generated from polarimetric multilook data is the complex Wishart distribution~\cite{Nielsen2007}.
+This distribution is characterized by two parameters, the covariance matrix $\mathbf{\Sigma}$ and the number of looks L of the image.
+Thus, the polarimetric matrix $\mathbf{Z} = \mathbf{C}=\left\langle\mathbf{k}_s\mathbf{k}_s^H \right\rangle$ can be derived following a complex Wishart distribution, represented as $\mathbf{Z}\sim \mathcal{W}_{\mathcal{C}}(\mathbf{\Sigma}, L),$  whose probability density function
+%is~\cite{Frery2014, Qin2022}:
+%\begin{align}
+%f_{\mathbf{Z}}(\mathbf{Z})=\frac{L^{qL}|\mathbf{Z}|^{L-q}}{|\mathbf{\Sigma}|^L\Gamma_q(L)}\exp\left\{-L \Tr\left(\mathbf{\Sigma}^{-1}\mathbf{Z}\right)\right\},
+%\label{E:22}
+%\end{align}
+%where $\Gamma_q(L)=\pi^{q(q-1)/2}\prod_{i=0}^{q-1}\Gamma(L-i)$,  $\Gamma(\cdot)$ denotes the gamma function and $\Tr(\cdot)$ is the trace of the matrix.
+In this case, three channels will be used, i.e., $q = 3$.
+We assume that the distribution of each intensity channel  follows a Gamma law, characterized by the probability density function:
 \vspace{-0.3cm}
@@
 +L \sum_{k=1}^{n}\ln z_k -\frac{L}{\mu}\sum_{k=1}^{n} z_k.
-\label{eq:LogLikelihoodGamma}
+\label{eq:LogLikelihoodGamma}\vspace{-0.3cm}
 \end{equation}
-Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
+Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.\vspace{-0.2cm}
 \subsection{Edge detection on a single data strip}\vspace{-0.1cm}
@@
 These boundaries define distinct regions within the image, such as pastures, urban areas, or forested areas~\cite{monferran2020modelo}.
-
 Various techniques, including maximum likelihood, entropy, and geodesic distance, are commonly used in research studies to identify edge points~\cite{NaranjoTorres2017,Nascimento2019}. 
-Suitable statistical models are needed for locating edge points in these types of images.
-
+%Suitable statistical models are needed for locating edge points in these types of images.
 The Gambini algorithm~\cite{Gambini2007} is a highly appealing method for edge detection. 
@@
 \vspace{-0.2cm}
-\subsection{Fusion methods for edge evidence}%\vspace{-0.1cm}
-
+\subsection{Fusion methods for edge evidence}
 De Borba et al.~\cite{DeBorba2020} fused the edges evidence obtained in intensities channels HH, HV, and VV to produce a unique and more accurate edge position estimator. 
@@
 Such information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.
-
+%%%%%
 \vspace{-0.2cm}
@@
        % where $(i, j)$ denote pixel location.
-\vspace{-0.2cm}\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.\vspace{-0.35cm}
+     \vspace{-0.2cm}\item The correlation coefficient measures the degree of correlation between the enhanced and the original images.
     	%$$CC=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2(y_i-\Bar{y})^2}}.$$
@@
     \end{itemize}
-%We follow the image fusion quality assessment strategy proposed in~\cite{Li2010,Nikola2015,Somvanshi2017} for the problem at hand, using statistical analyses.
+    We follow the image fusion quality assessment strategy proposed in~\cite{Li2010,Nikola2015,Somvanshi2017} for the problem at hand, using statistical analyses.
 
-We follow the image fusion quality assessment strategy proposed in~\cite{Li2010, Somvanshi2017,Nikola2015} for the problem at hand, using statistical analyses.
+%We use the criteria described in [2]  to evaluate the quality of each evidence for each fusion method.
 
-%
+%We expanded our research to a statistical analysis, using quality metrics to assess the efficiency in the fusion of evidence, using different methods. 
+   \vspace{-0.3cm}
 \subsection{Exploring the concept of explainability}
@@
 The proposed methodology in this work focuses on identifying interpretable measures that can be used to weigh the influence of individual estimates during an evidence fusion process.
-%
- \vspace{-0.2cm}
+%%
+ \vspace{-0.3cm}
 \section{RESULTS}
 \vspace{-0.2cm}
-%
 Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
 De Borba et al.~\cite{DeBorba2020} applied various fusion methods to detect edge evidence. 
-As an example, the results obtained by applying PCA and ROC methods to an AIRSAR L-band image of Flevoland are shown in Fig.~\ref{fig:2}.%(a)-(b).
-
-%%% The source is in ../../../Figures/PDF/hh.pdf
+As an example, the results obtained by applying PCA and ROC methods to an AIRSAR L-band image of Flevoland are shown in Figs.~\ref{fig:2}(a)-(b).
+Figs.~\ref{fig:2}(a)-(b).
 \begin{figure}[htb]
-\begin{minipage}[b]{1.0\linewidth}
+   % \centering
+    \begin{minipage}{0.6\textwidth}
+       \begin{minipage}[b]{.32\linewidth}
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/hh.pdf,width=3.9cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/hh.pdf,width=3.4cm}}
   \vspace{-0.1cm}
@@
 \end{minipage}
-%
-\begin{minipage}[b]{.48\linewidth}
+\begin{minipage}[b]{.32\linewidth}
   \centering
-\centerline{\epsfig{figure=../../../Figures/PDF/hv.pdf,width=3.9cm}}
+\centerline{\epsfig{figure=../../../Figures/PDF/hv.pdf,width=3.4cm}}
   \vspace{-0.1cm}
@@
 \end{minipage}
-\hfill
-\begin{minipage}[b]{0.48\linewidth}
+%\hfill
+\begin{minipage}[b]{0.31\linewidth}
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/vv.pdf,width=3.8cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/vv.pdf,width=3.3cm}}
   \vspace{-0.1cm}
@@
 \end{minipage}\vspace{-0.3cm}
-%
        \caption{Edges evidences from the three intensity channels.}
 \label{fig:res}
-\vspace{-0.4cm}
-\end{figure}
- \begin{figure}[htb]
-\begin{minipage}[b]{.48\linewidth}
+    \end{minipage}%\hfill
+    \begin{minipage}{0.4\textwidth}
         \centering
-\centerline{\epsfig{figure=../../../Figures/PDF/pca.pdf,width=3.9cm}}
+       \begin{minipage}[b]{.49\linewidth}
+  \centering
+\centerline{\epsfig{figure=../../../Figures/PDF/pca.pdf,width=3.5cm}}
   \vspace{-0.1cm}
@@
 \hfill
-\begin{minipage}[b]{0.48\linewidth}
+\begin{minipage}[b]{0.49\linewidth}
   \centering
- \centerline{\epsfig{figure=../../../Figures/PDF/roc.pdf,width=3.9cm}}
+ \centerline{\epsfig{figure=../../../Figures/PDF/roc.pdf,width=3.5cm}}
   \vspace{-0.1cm}
@@
 \end{minipage}\vspace{-0.3cm}
-%
         \caption{Results of applying the two fusion methods.}
 \label{fig:2}
-%
+    \end{minipage}
 \end{figure}

### 2023-05-31 Text/Reports/Template-git/Template.tex
update files

% 
%          spconf.sty  - LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,epsfig}
\usepackage{bm,bbm}
%\usepackage[style=numeric-comp, sorting=none, backend=bibtex,bibstyle=ieee, doi=true,url=false, isbn=false, natbib=false, giveninits]{biblatex}
%\addbibresource{../../Common/references.bib}

% \newcommand{\mcite}[1]{\mbox{\cite{#1}}}
%\usepackage[round]{natbib}   % omit 'round' option if you prefer square brackets

% Example definitions.
% --------------------

%\DeclareMathOperator{\Tr}{Tr}

% Title.
% ------

\title{Title}
% Single address.
% ---------------
%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}} 
%\address{Author Affiliation(s)}
\name{Name}
\address{University}

%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Dictum sit amet justo donec enim diam vulputate. Phasellus faucibus scelerisque eleifend donec pretium. In ornare quam viverra orci sagittis eu volutpat odio facilisis. Sit amet consectetur adipiscing elit. Velit aliquet sagittis id consectetur purus ut. Accumsan in nisl nisi scelerisque eu ultrices vitae auctor. Amet mattis vulputate enim nulla. Ut pharetra sit amet aliquam id. In metus vulputate eu scelerisque. Dignissim enim sit amet venenatis urna cursus eget. Egestas maecenas pharetra convallis posuere. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Facilisis leo vel fringilla est ullamcorper. Orci phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. At quis risus sed vulputate odio ut enim blandit volutpat. Mi eget mauris pharetra et ultrices neque ornare aenean euismod.

%
\begin{keywords}

\end{keywords}
%
\end{abstract}
\section{Introduction}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Dictum sit amet justo donec enim diam vulputate. Phasellus faucibus scelerisque eleifend donec pretium \cite{xiang2017sar}. In ornare quam viverra orci sagittis eu volutpat odio facilisis. Sit amet consectetur adipiscing elit. Velit aliquet sagittis id consectetur purus ut. Accumsan in nisl nisi scelerisque eu ultrices vitae auctor \cite{qin2018edge}. Amet mattis vulputate enim nulla. Ut pharetra sit amet aliquam id. In metus vulputate eu scelerisque. Dignissim enim sit amet venenatis urna cursus eget. Egestas maecenas pharetra convallis posuere. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Facilisis leo vel fringilla est ullamcorper. Orci phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. At quis risus sed vulputate odio ut enim blandit volutpat. Mi eget mauris pharetra et ultrices neque ornare aenean euismod.

%\section{Background}

%\section{Methodology}

%\section{Results}

%\section{CONCLUSION}

%\newpage

% % -------------------------------------------------------------------------
% % -------------------------------------------------------------------------

%\pagebreak

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% ------------------------------------------------------------------------
%\printbibliography[heading=bibintoc]

\bibliographystyle{IEEEtranS}
%\bibliographystyle{apa}
\bibliography{../../Common/references}
\end{document}

### 2023-05-31 Text/Reports/Template-report/example.tex
update files

\documentclass[letterpaper,10pt]{article} 
%% if A4 paper needed, change letterpaper to A4

\usepackage{./styles/osameet3} %% use version 3 for proper copyright statement

%% provide authormark
%\newcommand\authormark[1]{\textsuperscript{#1}}

%% standard packages and arguments should be modified as needed
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %pdflatex
%\usepackage[breaklinks,colorlinks=true,bookmarks=false,citecolor=blue,urlcolor=blue]{hyperref} %latex w/dvipdf

\begin{document}

\title{Title}

% \author{Author name(s)}
% \address{Author affiliation and full address}
% \email{e-mail address}
%%Uncomment the following line to override copyright year from the default current year.
%\copyrightyear{2022}

\author{name }

\address{  University..}

%\email{\authormark{*}opex@optica.org} %% email address is required

%\begin{abstract}

%\end{abstract}

\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Dictum sit amet justo donec enim diam vulputate. Phasellus faucibus scelerisque eleifend donec pretium. In ornare quam viverra orci sagittis eu volutpat odio facilisis. Sit amet consectetur adipiscing elit. Velit aliquet sagittis id consectetur purus ut \cite{quan2019edge,Tranfield2003,Wang2018}. Accumsan in nisl nisi scelerisque eu ultrices vitae auctor. Amet mattis vulputate enim nulla. Ut pharetra sit amet aliquam id. In metus vulputate eu scelerisque. Dignissim enim sit amet venenatis urna cursus eget. Egestas maecenas pharetra convallis posuere. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Facilisis leo vel fringilla est ullamcorper. Orci phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. At quis risus sed vulputate odio ut enim blandit volutpat. Mi eget mauris pharetra et ultrices neque ornare aenean euismod.
\section{Methodololy}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Dictum sit amet justo donec enim diam vulputate. Phasellus faucibus scelerisque eleifend donec pretium \cite{xiang2017sar}. In ornare quam viverra orci sagittis eu volutpat odio facilisis. Sit amet consectetur adipiscing elit. Velit aliquet sagittis id consectetur purus ut. Accumsan in nisl nisi scelerisque eu ultrices vitae auctor\cite{qin2018edge}. Amet mattis vulputate enim nulla. Ut pharetra sit amet aliquam id. In metus vulputate eu scelerisque. Dignissim enim sit amet venenatis urna cursus eget. Egestas maecenas pharetra convallis posuere. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Facilisis leo vel fringilla est ullamcorper. Orci phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. At quis risus sed vulputate odio ut enim blandit volutpat. Mi eget mauris pharetra et ultrices neque ornare aenean euismod.
\section{Results}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Dictum sit amet justo donec enim diam vulputate. Phasellus faucibus scelerisque eleifend donec pretium. In ornare quam viverra orci sagittis eu volutpat odio facilisis. Sit amet consectetur adipiscing elit. Velit aliquet sagittis id consectetur purus ut. Accumsan in nisl nisi scelerisque eu ultrices vitae auctor. Amet mattis vulputate enim nulla. Ut pharetra sit amet aliquam id. In metus vulputate eu scelerisque. Dignissim enim sit amet venenatis urna cursus eget. Egestas maecenas pharetra convallis posuere. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Facilisis leo vel fringilla est ullamcorper. Orci phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. At quis risus sed vulputate odio ut enim blandit volutpat. Mi eget mauris pharetra et ultrices neque ornare aenean euismod.

\bibliographystyle{ieeetr} %

\bibliography{../../Common/references}

\end{document}

### 2023-05-31 Text/Articles/IGARSS_2023/IG23_2023.tex
Pronto para Anderson

@@
 %\address{Author Affiliation(s)}
-\name{Rosa Janeth Alpala$^a$, Anderson A.\ de Borba$^{b,c}$, and Alejandro C.\ Frery$^c$.\thanks{e-mail:$^{a}$janeth.alpala@ufpe.br,$^{b}$anderson.borba@mackenzie.br, $^c$alejandro.frery@vuw.ac.nz}}
+\name{Rosa Janeth Alpala$^a$, Anderson A.\ de Borba$^{b,c}$, and Alejandro C.\ Frery$^c$\thanks{e-mail:$^{a}$janeth.alpala@ufpe.br,$^{b}$anderson.borba@mackenzie.br, $^c$alejandro.frery@vuw.ac.nz}}
 \address{$^a$ Universidade Federal de Pernambuco, 50740-540, Recife, PE, Brazil,           \\
@@
 
-The study by de Borba et al.~\cite{DeBorba2020} is the foundation for this research. 
-It finds evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator.
+The studies by de Borba et al.~\cite{DeBorba2020,FeatureSelectionforEdgeDetectioninPolSARImages} are the foundation for this research. 
+The authors find evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator. 
 We extended this research by incorporating several quality metrics that not only assess the accuracy of the edge estimate, but also provide insight into the explainability of the fused edge evidence.
@@
 
-The remaining of this paper is organized as follows: Section \ref{sec_2} provides a brief introduction to the background knowledge, including PolSAR data and edge detection.
+The remaining of this paper is organized as follows: 
+Section~\ref{sec_2} provides a brief introduction to the background knowledge, including PolSAR data and edge detection. 
+%%% ACF Não use números, use \ref
 Section 3 presents an overview of the quality measures employed. 
 The evaluation of edge estimation quality using various metrics is discussed in Section 4. 
-Lastly, conclusion is provided in Section 5.
+Lastly, the conclusions are provided in Section 5.
 
 \section{Background}\label{sec_2}
-\vspace{-0.2cm}
+
 \subsection{PolSAR data representation}
@@
 \begin{equation}
-\mathbf{k}_s=[S_{\text{HH}}, \sqrt{2}S_{\text{HV}}, S_{\text{VV}} ]^t,
+\mathbf{k}_s=\begin{bmatrix}
+S_{\text{HH}} & \sqrt{2}S_{\text{HV}} & S_{\text{VV}}
+\end{bmatrix}^t,
 \label{E:21}
 \end{equation}
-where  the superscript $t$ stands for the transpose operation. 
+where  the superscript $t$ is the transpose operation. 
 Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
@@
 Then, the total log-likelihood is
-\begin{equation}\label{eq:TotalLogLikelihood}
-\begin{aligned}
-\mathcal L\big(j&;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
+\begin{multline}\label{eq:TotalLogLikelihood}
+\mathcal L\big(j;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
 	\frac{\widehat{L}_\text{I}}{\widehat{\mu}_\text{I}}\sum_{k=1}^{j} z_k +
@@
 	\Bigg)\mbox{}\\
-&+j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
++j \big[\widehat{L}_\text{I}\ln (\widehat{L}_\text{I} / \widehat{\mu}_\text{I}) - \ln \Gamma(\widehat{L}_\text{I})\big]
 +\widehat{L}_\text{I} \sum_{k=1}^{j}\ln z_k  \mbox{}\\
-&+(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
++(n-j) \big[\widehat{L}_\text{E}\ln (\widehat{L}_\text{E} / \widehat{\mu}_\text{E}) - \ln \Gamma(\widehat{L}_\text{E})\big]
 +\widehat{L}_\text{E} \sum_{k=j+1}^{n}\ln z_k .%-\\ 
 \raisetag{2.2em}
-\end{aligned}
-\end{equation}
+\end{multline}
 The estimate of the edge position on the ray is the coordinate  $\widehat\jmath$ which maximizes $\mathcal L$.
-\vspace{-0.2cm}
+
 \subsection{Fusion methods for edge evidence}
-De Borba et al.~\cite{DeBorba2020} fused the edges evidence obtained in intensities channels HH, HV, and VV to produce a unique and more accurate edge position estimator. 
-The authors used six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).
+De Borba et al.~\cite{DeBorba2020,FeatureSelectionforEdgeDetectioninPolSARImages} fused the edges evidence to produce a unique and more accurate edge position estimator with six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).
 
 Edge evidence fusion methods are essential to quantify and qualify the information obtained from each image channel. 
-Such information enables the decision to utilize or discard data from a specific channel to enhance edge detection accuracy.
+Such information enables the decision to utilize or discard data from a specific channel for improved edge detection.
 
 \section{Quality assessment}
-\vspace{-0.2cm}
+
 Commonly used quality measures for performance evaluation include Mean Absolute Error (MAE) and Root Mean Square Error (RMSE).
@@
 \begin{align*}
-	\text{RMSE} =\sqrt{\frac{1}{n}\sum_{i=1}^{n}\left(y_i-\hat{y}_i\right)^2},
-	%\label{rmse}
-\end{align*}
-\vspace{-0.3cm}
-\begin{align*}
-	\text{MAE} =\frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y}_i|,
-	%\label{mae}
-\end{align*}
-\begin{align*}
-	\text{SD} =\sqrt{\frac{1}{n-1}\sum_{i=1}^{n}\left(y_i-\bar{y}\right)^2},
-	%\label{sd}
-\end{align*}
-\begin{align*}
-\text{CC}=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2\sum_{i=1}^{n}(y_i-\Bar{y})^2}},
+	\text{RMSE} &=\sqrt{\frac{1}{n}\sum_{i=1}^{n}\left(y_i-\hat{y}_i\right)^2},\\
+	\text{MAE} &=\frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y}_i|,\\
+	\text{SD} &=\sqrt{\frac{1}{n-1}\sum_{i=1}^{n}\left(y_i-\bar{y}\right)^2},\\
+\text{CC}&=  \frac{\sum_{i=1}^{n}(x_i-\Bar{x})(y_i-\Bar{y})}{\sqrt{\sum_{i=1}^{n}(x_i-\Bar{x})^2\sum_{i=1}^{n}(y_i-\Bar{y})^2}},
 %\label{cc}
@@
 For a discrete random variable $X$ with $\left\{x_1, x_2, \ldots, x_N\right\}$ the set of possible values it can take, Shannon entropy is defined as:
-\begin{align}
+\begin{equation}
 	H(X)=-\sum_{i=1}^{N}p(x_i)\log_2p(x_i),
 	\label{eq:H}
-\end{align}
-where $p(x_i)$ represents the probability of $i$th element in the vector.
+\end{equation}
+where $p(x_i)$ is the probability of the $i$th element.
 
-Entropy is commonly used in remote sensing to describe the information content of images.
+%Entropy is commonly used in remote sensing to describe the information content of images.
 It employs expression \eqref{eq:H}  to assess the amount of information conveyed by each pixel within an image.
 
-\vspace{-0.2cm}
 \section{RESULTS}
-\vspace{-0.2cm}
+
 Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
@@
 
-\begin{figure}[H]
+%%% ACF Use subcaption
+\begin{figure}[hbt]
    % \centering
@@
 \vspace{-0.4cm}
-\begin{figure}[H]
+\begin{figure}[hbt]
    % \centering
@@
     \end{minipage}%\hfill
-\end{figure}\vspace{-0.2cm}
+\end{figure}
 
 Figs.~\ref{fig:entropy1}(a)-(c), illustrate the total log-likelihood $\mathcal L$ functions with respect to the $j$th position, where these functions exhibit peaks that potentially serve as indicators of edge position.
-Specifically, the concept of entropy is used as a means of evaluating the accuracy of edge position.\vspace{-0.3cm}
-\begin{figure}[H]
+Specifically, the concept of entropy is used as a means of evaluating the accuracy of edge position.
+
+\begin{figure}[hbt]
    % \centering
@@
 \end{figure}
-\vspace{-0.3cm}
+
 To calculate entropy,  we employ the transformation of the total log-likelihood function, into a discrete probability function, the sample is taken from a single data strip (ray) of length 120 pixels.
@@
 Entropy is calculated exclusively using the estimated edge point dataset ($\hat{x},\hat{y}$), while the remaining metrics (MAE, RMSE, SD, and CC) utilize both datasets.
-\begin{table}[H]
+
+\begin{table}[hbt]
   \centering
@@
   \label{tab_1}
-\end{table}\vspace{-0.3cm}
-The importance of entropy calculation is highlighted.
+\end{table}
+
+Computing the entropy is important. 
 For instance, with the ROC method, we observe low error and high correlation, indicating significant similarity between edge point positions. 
@@
 This implies precise edge detection with few outliers, but exhibiting a sparse distribution of points, as shown in Fig.~\ref{F4}.
-\vspace{-0.45cm}
-\begin{figure}[H] %\vspace{-2.0mm} 
+
+\begin{figure}[hbt] %\vspace{-2.0mm} 
 	\includegraphics[scale=0.55]{figures/roc_f.pdf}\vspace{-1.5mm} 
@@
 
-This approach enables a comprehensive evaluation of the characteristics and performance of fusion methods and individual channels. All metrics are depicted in Fig.~\ref{F5}. \vspace{-0.3cm}
-\begin{figure}[H] 
+This approach enables a comprehensive evaluation of the characteristics and performance of fusion methods and individual channels. All metrics are depicted in Fig.~\ref{F5}.
+
+\begin{figure}[hbt] 
 	\includegraphics[scale=0.55]{figures/metricas.pdf}\vspace{-3.5mm} 
@@
 \end{figure}%\vspace{-0.1cm}
-The method for detecting edge evidence  and fusion methods were implemented in Python. Code and data are available for download at:  \url{ https://github.com/rjaneth/code_igarss_23.git}
-\vspace{-0.3cm}
+
+The edge detection and fusion methods were implemented in Python. 
+Code and data are available at \url{ https://github.com/rjaneth/code_igarss_23.git}
+
 \section{CONCLUSION}
-\vspace{-0.3cm}
+
 This paper presents some fusion methods for edge evidence and assesses their estimation precision using commonly employed metrics in the literature, with a specific emphasis on entropy as the primary measure.

### 2023-06-07 Text/Articles/IGARSS_2023/IG23_2023.tex
Last versíon of paper after corrections

@@
 \addtolength{\tabcolsep}{-0.3em}
-%\usepackage[backend=biber,style=phys,doi=false,eprint=false,url=false]{biblatex}
-%\usepackage{booktabs, longtable,array}
-%\usepackage[table]{xcolor}
-%\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}
-%\usepackage[a4paper,margin=1in]{geometry}
-%%%
-%\addbibresource{\jobname.bib}
-% \newcommand{\mcite}[1]{\mbox{\cite{#1}}}
+\usepackage[none]{hyphenat}
+\usepackage{microtype}
 
-% Example definitions.
+\usepackage{subcaption}
+\labelformat{subfigure}{(#1)}%() number
+% --------------------
+
 % --------------------
@@
 \begin{abstract}
-\vspace{-0.2cm}
+
 This work aims to develop techniques for the fusion of statistical evidences obtained from the application of Statistical Information Theory (SIT) and Statistical Information Geometry (SIG) in image processing and analysis, with a specific focus on Polarimetric Synthetic Aperture Radar (PolSAR) imagery.
@@
 
-%
+%% AAB: Olá Janeth, eu vou passar um verificador gramatical e ortográfico no texto.
+% AAB: Está extranho a separação silábica nas palavras na quebra de linhas.
+Verifica como melhorar isso, é uma biblioteca não lembro qual.
+RSRSRSRSRS Talvez essa biblioteca \usepackage[english]{babel}.
+Mas, não tenho certeza.
+% AAB: A ideia acima não funcionou, pesquisar!!!!!
+% RJA : corrigido melhorei com os pacotes  %\usepackage{microtype} e %\usepackage[none]{hyphenat}
 \begin{keywords}
-PolSAR, edge detection,  information fusion,  quality
-measures 
+PolSAR, edge detection,  information fusion,  quality measures 
 \end{keywords}
@@
 \end{abstract}
+
 \vspace{-0.3cm}
-\section{Introduction}
+\section{Introduction} \sloppy
 \vspace{-0.2cm}
-PolSAR images offer a distinct advantage over other remote sensing images by utilizing four different polarization combinations, specifically HH, HV, VH, and VV~\cite{Hua2022}.
-These combinations are based on the horizontal (H), and vertical (V) polarizations of the received and transmitted signals.
+PolSAR imaging system captures valuable information in diverse conditions, including day and night, distinguishing it from optical sensors that depend on optimal weather conditions and daylight for effective operation~\cite{Hua2022}.
+It gains an advantage by utilizing four polarization combinations, specifically HH, HV, VH, and VV, based on horizontal and vertical polarization of transmitted and received signals.
+% AAB: Eu colocaria aqui informação das vantagens dos sensores PolSAR em realção a outros sensors, por exemplo,  sensores ópticos. 
+% RJA : corrigido melhorei
 
-Edge detection in PolSAR images plays an essential role in many applications, such as speckle noise reduction, superpixel segmentation, land-cover classification, and target recognition~\cite{Jin2016}.
+Edge detection in PolSAR images is essential in many applications, such as speckle noise reduction, land-cover classification, and target recognition~\cite{Jin2016}.
 
+%AAB: Eu explicaria melhor como encontramos evidências de bordas. Eu pensaria melhor na palavra "deterministic".
+% RJA : corrigido
 The studies by de Borba et al.~\cite{DeBorba2020,FeatureSelectionforEdgeDetectioninPolSARImages} are the foundation for this research.
-The authors find evidence of the location of edge points by using a deterministic approach that does not take into account the variability of the estimator. 
+The authors acquire numerous pieces of evidence regarding the location of edge points in PolSAR images.
+These estimations are then subjected to fusion processes to obtain an edge point that summarizes the evidence.
 We extended this research by incorporating several quality metrics that not only assess the accuracy of the edge estimate, but also provide insight into the explainability of the fused edge evidence.
-%We extended this investigation using various quality metrics to evaluate and compare the results of fusing edge evidence in PolSAR images.
+%%% ACF Não use números, use \ref
+% RJA : corrigido
 
-The remaining of this paper is organized as follows: 
-Section~\ref{sec_2} provides a brief introduction to the background knowledge, including PolSAR data and edge detection. 
-%%% ACF Não use números, use \ref
-Section 3 presents an overview of the quality measures employed. 
-The evaluation of edge estimation quality using various metrics is discussed in Section 4. 
-Lastly, the conclusions are provided in Section 5.
+This paper is organized as follows:
+Section \ref{sec_2} provides a brief introduction to the background knowledge, including PolSAR data and edge detection.
+Section \ref{sec_3} presents an overview of the quality measures employed.
+The evaluation of edge estimation quality using various metrics is discussed in Section \ref{sec_4}.
+Lastly, the conclusions are provided in Section \ref{sec_5}.
 
 \section{Background}\label{sec_2}
-
+\vspace{-0.2cm}
 \subsection{PolSAR data representation}
@@
 \end{equation}
+% AAB: Cuidado!!! Você está usando s minusculo na eq acima e depois usa s maiusculo logo abaixo.
+% RJA : corrigido
 where  the superscript $t$ is the transpose operation. 
-Multi‑look PolSAR data can be expressed  by a covariance matrix  given as 
-\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_s(i)\mathbf{k}_s(i)^\text{H} \), where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
+Multi-look PolSAR data can be expressed  by a covariance matrix  given as 
+\(\mathbf{C}=\langle\mathbf{k}_S\mathbf{k}_S^\text{H} \rangle= {L}^{-1} \sum_{i=1}^{L} \mathbf{k}_S(i)\mathbf{k}_S(i)^\text{H} \), where $\langle \cdot \rangle$ is the ensemble average, $\text{H}$  the is complex conjugate transpose operator, and $L$ is the number of looks.
 The covariance matrix is hermitian, i.e., $\mathbf{C}= \mathbf{C}^\text{H}$, and positive definite;
@@
 \subsection{Gamma distribution}
-%Over the past decades, several distributions have been created for modeling PolSAR image data.
-The most commonly used distribution for working with images generated from polarimetric multilook data is the complex Wishart distribution~\cite{Nielsen2007}.
-This distribution is characterized by two parameters, the covariance matrix $\mathbf{\Sigma}$ and the number of looks L of the image.
-Thus, the polarimetric matrix $\mathbf{Z} = \mathbf{C}=\left\langle\mathbf{k}_s\mathbf{k}_s^H \right\rangle$ can be derived following a complex Wishart distribution, represented as $\mathbf{Z}\sim \mathcal{W}_{\mathcal{C}}(\mathbf{\Sigma}, L),$  whose probability density function
-%is~\cite{Frery2014, Qin2022}:
-%\begin{align}
-%f_{\mathbf{Z}}(\mathbf{Z})=\frac{L^{qL}|\mathbf{Z}|^{L-q}}{|\mathbf{\Sigma}|^L\Gamma_q(L)}\exp\left\{-L \Tr\left(\mathbf{\Sigma}^{-1}\mathbf{Z}\right)\right\},
-%\label{E:22}
-%\end{align}
-%where $\Gamma_q(L)=\pi^{q(q-1)/2}\prod_{i=0}^{q-1}\Gamma(L-i)$,  $\Gamma(\cdot)$ denotes the gamma function and $\Tr(\cdot)$ is the trace of the matrix.
-In this case, three channels will be used, i.e., $q = 3$.
 
@@
 \end{equation}
-Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator (MLE) of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
+Then, we find $\big(\widehat \mu, \widehat L\big)$, the maximum likelihood estimator of $(\mu, L)$ from $\bm{z}$, by maximizing~\eqref{eq:LogLikelihoodGamma}.
 
-% A simplified derivation to obtain the complex Wishart distribution was presented in \cite{LEE1994}.
 \subsection{Edge detection on a single data strip}
@@
 Suitable statistical models are needed for locating edge points in these types of images.
-
+% AAB: Os dois paragrafos abaixo está redundante, tente reescrever fazendo uma fusãode informação entre eles. RSRSRS
+% RJA : corrigido
 The Gambini algorithm~\cite{Gambini2007} is a highly appealing method for edge detection. 
-It searches for evidence of edges within a narrow data strip. 
-The algorithm involves projecting rays and identifying edge evidence by maximizing a value function.
-
-The algorithm starts by casting rays from a point inside the candidate region, e.g., the centroid.
-Data are collected around each ray to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$ into the interior $\bm z_\text{I}$ and exterior $\bm z_\text{E}$ samples:
+Data are collected within a narrow data strip to form the sample $\bm z = (z_1,z_2,\dots,z_n)$, which is partitioned at position $j$ into the interior $\bm z_\text{I}$ and exterior $\bm z_\text{E}$ samples:
 $$
@@
 Then, the total log-likelihood is
-\begin{multline}\label{eq:TotalLogLikelihood}
+\begin{multline*}%\label{eq:TotalLogLikelihood}
 \mathcal L\big(j;\widehat{\mu}_I, \widehat{L}_I,\widehat{\mu}_E, \widehat{L}_E\big)= -\Bigg(
@@
 \raisetag{2.2em}
-\end{multline}
+\end{multline*}
 The estimate of the edge position on the ray is the coordinate  $\widehat\jmath$ which maximizes $\mathcal L$.
@@
 \subsection{Fusion methods for edge evidence}
-De Borba et al.~\cite{DeBorba2020,FeatureSelectionforEdgeDetectioninPolSARImages} fused the edges evidence to produce a unique and more accurate edge position estimator with six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA), receiver operating characteristic (ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).
+% AAB: Não estamos usando de fato o PCA, eu acho melhor escrever PCA based.
+% AAB: Verifica no artigo (https://www.mdpi.com/2072-4292/15/9/2479) como nos referimos a fusão ROC, S-ROC. Talvez seja legal citar este artigo ele é mais atual. 
+% RJA : corrigido
+De Borba et al.~\cite{DeBorba2020,FeatureSelectionforEdgeDetectioninPolSARImages} fused the edges evidence to produce a unique and more accurate edge position estimator with six fusion methods: simple average, multiresolution discrete wavelet transform (MRDWT), principal component analysis (PCA) based method, receiver operating characteristic (S-ROC) statistics, multiresolution stationary wavelet transform (MR-SWT), and a multiresolution method based on singular value decomposition (MR-SVD).
 
@@
 
-\section{Quality assessment}
+\section{Quality assessment}\label{sec_3}
 
@@
 where $n$ represents the number of observations, $y_i$ denotes the estimated values, $\hat{y}_i$ are the reference measured values, and  $\Bar{x}$ and $\Bar{y}$ are the mean values.
-
+% AAB: Não está claro como você está usando a entropia
+% Parece que você está usando de duas formas
+% 1) Para calcular a entropia na figura 3. É uma ótima ideia e podendo ter uma boa medida % para definir se á borda ou não definindo um limiar
+% 2) Você esta usando a entropia como um erro na tabela 1.
+% Não esta bem explicado a diferênça entre as duas medidas.
+% AAB: Outro ponto como você definiu a linha cor de laranja na figura 4. Descrever que é uma GR- Ground Reference
+% RJA: ainda preciso melhorar essa ideia
 Another metric that is used is the entropy, this quantifies the uncertainty of a probability distribution.
@@
 A peaked distribution has low entropy and low uncertainty, while a homogeneous distribution has high entropy and high uncertainty \cite{Mays2002}.
-For a discrete random variable $X$ with $\left\{x_1, x_2, \ldots, x_N\right\}$ the set of possible values it can take, Shannon entropy is defined as:
+For a discrete random variable $X$ with $\left\{x_1, x_2, \ldots, x_n\right\}$ the set of possible values it can take, Shannon entropy is defined as:
 \begin{equation}
-	H(X)=-\sum_{i=1}^{N}p(x_i)\log_2p(x_i),
+	H(X)=-\sum_{i=1}^{n}p(x_i)\log_2p(x_i),
 	\label{eq:H}
@@
 
-\section{RESULTS}
+\section{RESULTS} \label{sec_4}
 
-Figs.~\ref{fig:res}(a)-(c) show the edge evidences in the HH, HV and VV channels obtained through maximum likelihood estimation.
+Figs.~\ref{fig:all-ed}\ref{subfig:1ed}-\ref{subfig:3ed} show the edge evidences in the HH, HV, and VV channels obtained through maximum likelihood estimation.
 De Borba et al.~\cite{DeBorba2020} applied various fusion methods to detect edge evidence. 
-As an example, the results obtained by applying PCA, ROC and MR-SWT methods to an AIRSAR L-band image of Flevoland are shown in Fig.~\ref{fig:fus}.%(a)-(b).
-
-%%% ACF Use subcaption
 \begin{figure}[hbt]
-   % \centering
-    \begin{minipage}{0.5\textwidth}
-       \begin{minipage}[b]{.32\linewidth}
+    \begin{subfigure}{0.32\linewidth}
     \centering
- \centerline{\epsfig{figure=figures/hh_f.pdf,width=2.8cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(a) Channel HH.}}\medskip
-\end{minipage}
-\begin{minipage}[b]{.31\linewidth}
+    \includegraphics[width=\linewidth]{figures/hh_f.pdf}
+    \caption{Channel HH.}
+    \label{subfig:1ed}
+  \end{subfigure}
+  \begin{subfigure}{0.32\linewidth}
     \centering
-\centerline{\epsfig{figure=figures/hv.pdf,width=2.8cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(b) Channel HV.}}\medskip
-\end{minipage}
-%\hfill
-\begin{minipage}[b]{0.31\linewidth}
+    \includegraphics[width=\linewidth]{figures/hv.pdf}
+    \caption{Channel HV.}
+    \label{subfig:2ed}
+  \end{subfigure}
+  \begin{subfigure}{0.32\linewidth}
     \centering
- \centerline{\epsfig{figure=figures/vv_c.pdf,width=2.8cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(c) Channel VV.}}\medskip
-\end{minipage}\vspace{-0.3cm}
+    \includegraphics[width=\linewidth]{figures/vv_c.pdf}
+    \caption{Channel VV.}
+    \label{subfig:3ed}
+  \end{subfigure}
+  %\label{fig:1}
   \caption{Edges evidences from the three intensity channels.}
-\label{fig:res}
-    \end{minipage}%\hfill
+  \label{fig:all-ed}
 \end{figure}
-\vspace{-0.4cm}
+%\vspace{-0.4cm}
+As an example, the results obtained by applying PCA, S-ROC, and MR-SWT methods to an AIRSAR L-band image of Flevoland are shown in Figs.~\ref{fig:all-fus}\ref{subfig:1fus}-\ref{subfig:3fus}.
+%--------------------------------------------------
 \begin{figure}[hbt]
-   % \centering
-    \begin{minipage}{0.5\textwidth}
-       \begin{minipage}[b]{.32\linewidth}
+    \begin{subfigure}{0.32\linewidth}
     \centering
- \centerline{\epsfig{figure=figures/roc.pdf,width=2.75cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(a) ROC fusion.}}\medskip
-\end{minipage}
-\begin{minipage}[b]{.31\linewidth}
+    \includegraphics[width=\linewidth]{figures/roc.pdf}
+    \caption{S-ROC fusion.}
+    \label{subfig:1fus}
+  \end{subfigure}
+  \begin{subfigure}{0.33\linewidth}
     \centering
-\centerline{\epsfig{figure=figures/pca_1.pdf,width=2.8cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(b) PCA fusion.}}\medskip
-\end{minipage}
-%\hfill
-\begin{minipage}[b]{0.31\linewidth}
-  %\centering
- \centerline{\epsfig{figure=figures/swt.pdf,width=2.75cm}}
-  \vspace{-0.1cm}
-  \centerline{\small{(c) MR-SWT fusion.}}\medskip
-\end{minipage}\vspace{-0.3cm}
+    \includegraphics[width=\linewidth]{figures/pca_1.pdf}
+    \caption{PCA fusion.}
+    \label{subfig:2fus}
+  \end{subfigure}
+  \begin{subfigure}{0.32\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/swt.pdf}
+    \caption{MR-SWT fusion.}
+    \label{subfig:3fus}
+  \end{subfigure}
+  %\label{fig:1}
   \caption{Fusion methods.}
-\label{fig:fus}
-    \end{minipage}%\hfill
+  \label{fig:all-fus}
 \end{figure}
-
-Figs.~\ref{fig:entropy1}(a)-(c), illustrate the total log-likelihood $\mathcal L$ functions with respect to the $j$th position, where these functions exhibit peaks that potentially serve as indicators of edge position.
+Figs.~\ref{fig:entropy1}\ref{subfig:1en}-\ref{subfig:3en}, illustrate the total log-likelihood $\mathcal L$ functions with respect to the $j$th position, where these functions exhibit peaks that potentially serve as indicators of edge position.
 Specifically, the concept of entropy is used as a means of evaluating the accuracy of edge position.
 
-\begin{figure}[hbt]
+\begin{figure}[H]
+\captionsetup[subfigure]{justification=centering}
+   \centering
+    \begin{subfigure}{0.49\linewidth}
+    %\centering
+    \includegraphics[width=4.2cm]{figures/likelihood_hh.pdf}
+    \caption{\scriptsize{Channel HH (\textbf{Entropy = 0.0546}).}}
+    \label{subfig:1en}
+  \end{subfigure}
+  \begin{subfigure}{0.49\linewidth}
    % \centering
-    \begin{minipage}{0.5\textwidth}
-       \begin{minipage}[b]{.5\linewidth}
-  \centering
- \centerline{\epsfig{figure=figures/likelihood_hh.pdf,width=5cm}}
-  \vspace{-0.1cm}
-  \centerline{\footnotesize{ (a) Channel HH (\textbf{Entropy = 0.0546}).}}\medskip
-\end{minipage}%\hfill
-\begin{minipage}[b]{.5\linewidth}
-  \centering
-\centerline{\epsfig{figure=figures/likelihood_hv.pdf,width=5cm}}
-  \vspace{-0.2cm}
-  \centerline{\footnotesize{(b) Channel HV (\textbf{Entropy =  0.6361}).}}\medskip
-\end{minipage}\\
-\hfill 
-\vspace{-0.3cm}
- \centering
-\begin{minipage}[b]{0.5\linewidth}
-  \centering
- \centerline{\epsfig{figure=figures/likelihood_vv.pdf,width=5cm}}
-  \vspace{-0.1cm}
-  \centerline{\footnotesize{(c) \, Channel VV  (\textbf{Entropy =  0.8577}).}}\medskip
-\end{minipage}\vspace{-0.2cm}
+    \includegraphics[width=4.2cm]{figures/likelihood_hv.pdf}
+ \caption{\scriptsize{Channel HV (\textbf{Entropy =  0.6361}).}}
+    \label{subfig:2en}
+  \end{subfigure}\\
+   \begin{subfigure}{0.6\linewidth}
+    %\centering
+    \includegraphics[width=4.5cm]{figures/likelihood_vv.pdf}
+   % \centering
+   \caption{\scriptsize{Channel VV (\textbf{Entropy = 0.8577}).}}
+    \label{subfig:3en}
+  \end{subfigure}
+  \label{fig:1}
   \caption{Entropy as a quality measure for edge evidence.}
   \label{fig:entropy1}
-    \end{minipage}%\hfill
 \end{figure}
-
-To calculate entropy,  we employ the transformation of the total log-likelihood function, into a discrete probability function, the sample is taken from a single data strip (ray) of length 120 pixels.
+%--------------------------------------------------
+To calculate entropy,  we employ the transformation of the total log-likelihood function into a discrete probability function.
+The sample is taken from a single data strip (ray) of length 120 pixels.
 Subsequently, expression~\eqref{eq:H} is used to calculate the Shannon entropy, $H(X)$.
 The resulting value provides an objective metric for evaluating the accuracy of edge point detection.
-A low entropy value signifies precise estimation, characterized by a compact and peaked curve, see Fig.~\ref{fig:entropy1}(a).
-Conversely, a high entropy value suggests less accurate estimation, featuring a more dispersed probability distribution and a graph with a flatter and elongated shape, see Fig.~\ref{fig:entropy1}(b)-(c).\par
-%\vspace{-0.1cm}
-On the other hand, the aim of this study is to determine whether evidence fusion in PolSAR images provides more information, leading to accurate edge detection, compared to edge detection of individual channels.\par
-%\vspace{-0.1cm}
-Table~\ref{tab_1} illustrates the evaluation metrics employed to assess the quality of the estimated edge points by comparing their similarity with a predefined set of reference points.
+A low entropy value signifies precise estimation, characterized by a compact and peaked curve, see Fig.~\ref{fig:entropy1}\ref{subfig:1en}.
+Conversely, a high entropy value suggests less accurate estimation, featuring a more dispersed probability distribution and a graph with a flatter and elongated shape, see Fig.~\ref{fig:entropy1}\ref{subfig:2en}-\ref{subfig:3en}.
+
+On the other hand, this study aims to determine whether evidence fusion in PolSAR images provides more information, leading to accurate edge detection, compared to edge detection of individual channels.
+To accomplish this, we use entropy as a measure of information content, in contrast to its usage as an estimation precision measure, as illustrated in Figs.~\ref{fig:entropy1}.
+
+Table~\ref{tab_1} shows the evaluation metrics employed to assess the quality of the estimated edge points by comparing their similarity with a predefined set of reference points (ground reference).
 These metrics offer an objective evaluation of the accuracy of the obtained results.
 Entropy is calculated exclusively using the estimated edge point dataset ($\hat{x},\hat{y}$), while the remaining metrics (MAE, RMSE, SD, and CC) utilize both datasets.
-
 \begin{table}[hbt]
@@
     \midrule
-   hh  & 6.6439      & 1.8400       & 3.7175   & 2.6291   & 0.9986 \\
-   hv  & 6.6293      & 1.6700       & 2.9275   & 2.0640   & 0.9992 \\
-   vv  & 6.6438      & 4.2400      & 7.9461    & 5.5649   & 0.9941 \\
-   ROC & 6.0223      & 1.4154      & 2.3664    & 1.6311    & 0.9994 \\
+   HH  & 6.6439      & 1.8400       & 3.7175   & 2.6291   & 0.9986 \\
+   HV  & 6.6293      & 1.6700       & 2.9275   & 2.0640   & 0.9992 \\
+   VV  & 6.6438      & 4.2400      & 7.9461    & 5.5649   & 0.9941 \\
+   S-ROC & 6.0223      & 1.4154      & 2.3664    & 1.6311    & 0.9994 \\
    PCA & 7.7944      & 3.0180       & 6.0657   & 4.2788  & 0.9964 \\
@@
   \end{tabular}\vspace{-0.1cm}
-  \caption{\small{Assessment metrics.}}
+  \caption{Assessment metrics.}
   \label{tab_1}
@@
 
-Computing the entropy is important. 
-For instance, with the ROC method, we observe low error and high correlation, indicating significant similarity between edge point positions. 
+The importance of entropy  as a measure of information content is highlighted.
+For instance,  we observe low error and high correlation with the S-ROC method, indicating significant similarity between edge point positions.
 However, the low entropy value suggests a relatively small amount of information in the fused image.
-This implies precise edge detection with few outliers, but exhibiting a sparse distribution of points, as shown in Fig.~\ref{F4}.
-
-\begin{figure}[hbt] %\vspace{-2.0mm} 
-	\includegraphics[scale=0.55]{figures/roc_f.pdf}\vspace{-1.5mm} 
-	\caption{Comparison of estimated points with reference points.}
+This implies precise edge detection with few outliers but exhibiting a sparse distribution of points, as shown in Fig.~\ref{F4}, where the orange rectangle indicates the ground reference.
+\vspace{-0.45cm}
+% AAB: Acho legal deixar claro que estes resultados são para a S-ROC
+\begin{figure}[H] 
+\centering
+	\includegraphics[scale=0.5]{figures/roc_f.pdf}\vspace{-1.5mm} 
+	\caption{Comparison of estimated points with ground reference using S-ROC method.}
 	\label{F4}
 \end{figure}
-On the other hand, the PCA method demonstrates superior performance, as it exhibits a moderate entropy value along with low values of MAE, RMSE, and SD.
+Meanwhile, the PCA based method demonstrates superior performance, as it exhibits a moderate entropy value along with low values of MAE, RMSE, and SD.
 
@@
 
-\begin{figure}[hbt] 
-	\includegraphics[scale=0.55]{figures/metricas.pdf}\vspace{-3.5mm} 
-	\caption{illustration of quality metrics.}\vspace{-0.3cm}
+ \vspace{-0.45cm}
+\begin{figure}[H] 
+\centering
+	\includegraphics[scale=0.5]{figures/metricas.pdf}
+	\caption{Illustration of quality metrics.}\vspace{-0.3cm}
 	\label{F5}
-\end{figure}%\vspace{-0.1cm}
-
+\end{figure}
 The edge detection and fusion methods were implemented in Python. 
@@
 
-\section{CONCLUSION}
+\section{CONCLUSION} \label{sec_5}
 

### 2023-07-01 Text/Poster/poster_Igarss_23.tex
IGARSS Poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.1 (14/06/14)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.0]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage{lmodern} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{subcaption}
\labelformat{subfigure}{}%() number
\usetheme{confposter} % Use the confposter theme supplied with this template
\usepackage{graphicx}
\usepackage{graphicx}  % Required for including images
\usepackage{tabularx}
\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{tikz}
\usetikzlibrary{arrows.meta,
positioning,
quotes, shapes}

\usetikzlibrary{arrows}
\tikzset{
  double -latex/.style args={#1 colored by #2 and #3}{    
    -latex,line width=#1,#2,
    postaction={draw,-latex,#3,line width=(#1)/3,shorten <=(#1)/4,shorten >=4.5*(#1)/3},
  },
  double round cap-latex/.style args={#1 colored by #2 and #3}{    
    round cap-latex,line width=#1,#2,
    postaction={draw,round cap-latex,#3,line width=(#1)/3,shorten <=(#1)/4,shorten >=4.5*(#1)/3},
  },
  double round cap-stealth/.style args={#1 colored by #2 and #3}{
    round cap-stealth,line width=#1,#2,
    postaction={round cap-stealth,draw,,#3,line width=(#1)/3,shorten <=(#1)/3,shorten >=2*(#1)/3},
  },
  double -stealth/.style args={#1 colored by #2 and #3}{
    -stealth,line width=#1,#2,
    postaction={-stealth,draw,,#3,line width=(#1)/3,shorten <=(#1)/3,shorten >=2*(#1)/3},
  },
}
\usepackage[most]{tcolorbox}
\setbeamercolor{block title}{fg=dblue!80,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty
% declare `cmex` to be arbitrary scalable
\DeclareFontShape{OMX}{cmex}{m}{n}{
  <-7.5> cmex7
  <7.5-8.5> cmex8
  <8.5-9.5> cmex9
  <9.5-> cmex10
}{}

\SetSymbolFont{largesymbols}{normal}{OMX}{cmex}{m}{n}
\SetSymbolFont{largesymbols}{bold}  {OMX}{cmex}{m}{n}

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. 
% (1-(3+1)*0.025)/3 = 0.3
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{32in} % A0 height: 33.1in
\setlength{\textwidth}{46in} % A0 width: 46.8in
\setlength{\textheight}{34in} % A0 height: 33.1in
\setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
\setlength{\twocolwid}{0.625\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
\setlength{\topmargin}{0.5in} % Reduce the top margin size
\setlength{\leftmargin}{0.5in} % Reduce the top margin size
%-----------------------------------------------------------

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{%
  \texorpdfstring{%
    \makebox[\linewidth]{	%
      \makebox[100pt][l]{%
        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          {\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}% Left logo
      }\hfill
			\makebox[\dimexpr\linewidth-4em][c]{%
        \begin{minipage}{\linewidth}
          \centering
          \LARGE QUALITY ASSESSMENT MEASURES FOR EXPLAINABLE FUSION OF STATISTICAL\\ EVIDENCES OF EDGES IN POLSAR IMAGES: A FIRST APPROACH
        \end{minipage}
      }%

      \hfill\makebox[-50pt][r]{%
        \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
          {\includegraphics[height=3.0\baselineskip]{figures/logos.pdf}}% Right logo
      }%
    }%
  }
  } % Poster title

	\author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
\institute[]{$^1$Universidade Federal de Pernambuco, Recife, Brazil\\
$^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
$^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}

%%----------------------------------------------------------------------------------------

\begin{document}

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t,totalwidth=\threecolwid] % The whole poster consists of three major columns

\begin{column}{0.5\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} %

%----------------------------------------------------------------------------------------
%	The first column
%----------------------------------------------------------------------------------------

\begin{block}{\LARGE{SETUP}}
\vspace{0.7em}
\begin{figure}[h]
  \centering
  \caption*{\large{Flevoland}}
  \vspace{-15pt}
  \begin{tikzpicture}%%[trim={left bottom right top},clip] reduce image borders
    \node (figure) at (0,0) {\includegraphics[trim={2cm 8cm 15cm 3cm},clip,width=25cm]{figures/flev_pauli_total.pdf}};
    \draw[double -stealth=10pt colored by blue!50!black and white] (figure.south) -- ++(0,-4cm);
    \node[below=of figure, yshift=-3cm] (text) {\begin{tcolorbox}[colback=blue!10,colframe=blue!30!black, arc=2pt, outer arc=2pt, nobeforeafter, width=7cm, center upper]
      \textbf{Edge Detection}
    \end{tcolorbox}};
    \node[below left=of text, xshift=-2.5cm] (text1) {\begin{tcolorbox}[colback=green!10,colframe=green!30!black, arc=2pt, outer arc=2pt, nobeforeafter, width=7cm, center upper]
      \textbf{Statistical Modeling}
    \end{tcolorbox}};
    \node[below right=of text, xshift=2.5cm] (text2) {\begin{tcolorbox}[colback=orange!10,colframe=orange!30!black, arc=2pt, outer arc=2pt, nobeforeafter, width=8cm, center upper]
      \textbf{The Gambini Algorithm}
    \end{tcolorbox}};
    \node[below=of text1, yshift=-2.5cm] (text4) {\begin{tcolorbox}[colback=blue!10,colframe=blue!30!black, arc=2pt, outer arc=2pt, nobeforeafter, width=16cm, center upper]
      \textcolor{blue}{\large{\textbf{Gamma Distribution}}}
      \begin{equation*}
        f_Z(z;\mu,L)=\frac{L^{L}z^{L-1}}{\mu^{L}\Gamma(L)} \exp\big\{-Lz/\mu\big\}
      \end{equation*}
    \end{tcolorbox}};
    \node[below=of text, yshift=-1.5cm] (figure2) {\includegraphics[width=13cm]{figures/single_data.pdf}};
    \node[above=-1pt of figure2] {Thin data strip};
    \node[below=-1pt of figure2] {$\bm z = (\underbrace{z_1,z_2,\dots,z_j}_{\bm z_\text{I}},\underbrace{z_{j+1}, z_{j+2},\dots,z_n}_{\bm z_\text{E}})$};
    \draw[-stealth, blue, line width=3pt] (text) -- (text1.north);
    \draw[-stealth, blue, line width=3pt] (text) -- (text2.north);
    \draw[-stealth, blue, line width=3pt] (text1.south) -- (text4.north);

	\draw[-stealth, blue, line width=3pt] (text4.south) to[out=-60,in=-120, looseness=1.2] node[midway, below, sloped, text=red] {\textbf{Maximum likelihood}} (text2.south);
	 % 
    \draw[-stealth, blue, line width=3pt] (text2.east) -- ++(1,0) -- ++(0,30) -- ++(2,0);		
  \end{tikzpicture}
\end{figure}

\end{block}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

%----------------------------------------------------------------------------------------

\begin{column}{\onecolwid} % The second column
%----------------------------------------------------------------------------------------
%	The second column
%----------------------------------------------------------------------------------------

\begin{block}{\LARGE{EVIDENCES}}
\vspace{0.7em}

\begin{figure}[hbt]
%\label{fig:1}

  %\caption*{Intensity channels}
	\captionsetup[subfigure]{labelformat=empty}
    \begin{subfigure}{0.32\linewidth}
		    \centering
    \includegraphics[width=\linewidth]{figures/hh_f.pdf}
    \caption{\large{Channel HH}}
    %\label{subfig:1ed}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/hv.pdf}
    \caption{\large{Channel HV}}
    %\label{subfig:2ed}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/vv_c.pdf}
    \caption{\large{Channel VV}}
    %\label{subfig:3ed}
  \end{subfigure}

\end{figure}
\vspace{-1.2cm}

	%-------------------------------------------------------------
\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    \draw[double -stealth=10pt colored by blue!50!black and white] (0,0) -- (0,-2cm);
    \node[below] at (0,-2.5cm) {\textbf{\textcolor{blue!80!black}{\large{Fusion results}}}};
  \end{tikzpicture}
  % \caption{Figure}
\end{figure}
%-------------------------------------------------------------
\begin{figure}[hbt]
 %\caption*{Fusion methods.}
\captionsetup[subfigure]{labelformat=empty}
    \begin{subfigure}{0.32\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/roc.pdf}
    \caption{\large{S-ROC fusion}}
    %\label{subfig:1fus}
  \end{subfigure}
  \begin{subfigure}{0.33\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/pca_1.pdf}
    \caption{\large{PCA fusion}}
    %\label{subfig:2fus}
  \end{subfigure}
  \begin{subfigure}{0.32\linewidth}
    \centering
    \includegraphics[width=\linewidth]{figures/swt.pdf}
    \caption{\large{MR-SWT fusion}}
   % \label{subfig:3fus}
  \end{subfigure}
  %\label{fig:1}
  \end{figure}

	%-------------------------------------------------------------
	\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    \node[below=of text1, yshift=-1.5cm] (text4) {
      \begin{tcolorbox}[colback=blue!10,colframe=blue!30!black, arc=2pt, outer arc=2pt, nobeforeafter, width=16cm, center upper]
        \textcolor{blue}{\large{\textbf{{Shannon Entropy}}}}
				 \begin{equation*} 
         H(X)=-\sum_{i=1}^{n}p(x_i)\log_2p(x_i)
        \end{equation*}
      \end{tcolorbox}
    };
  \end{tikzpicture}
\end{figure}

	%-------------------------------------------------------------

	\begin{figure}[H]
	\captionsetup[subfigure]{labelformat=empty}
\captionsetup[subfigure]{justification=centering}
   \centering
    \begin{subfigure}{0.48\linewidth}
    %\centering
    \includegraphics[width=17cm]{figures/likelihood_hh.pdf}
    \caption{\small{Channel HH (\textbf{Entropy = 0.0546}).}}
    %\label{subfig:1en}
  \end{subfigure}
  %\begin{subfigure}{0.49\linewidth}
   %% \centering
    %\includegraphics[width=4.2cm]{../figures/likelihood_hv.pdf}
 %\caption{\scriptsize{Channel HV (\textbf{Entropy =  0.6361}).}}
    %\label{subfig:2en}
  %\end{subfigure}\\
   \begin{subfigure}{0.48\linewidth}
    %\centering
    \includegraphics[width=17cm]{figures/likelihood_vv.pdf}
   % \centering
   \caption{\small{Channel VV (\textbf{Entropy = 0.8577}).}}
   % \label{subfig:3en}
  \end{subfigure}
 \end{figure}

\end{block}

\end{column} % End of column 2
%----------------------------------------------------------------------------------------

\begin{column}{\sepwid}\end{column} % Empty spacer column
%----------------------------------------------------------------------------------------
%	The third column
%----------------------------------------------------------------------------------------

\begin{column}{\onecolwid} % The third column

\begin{block}{\LARGE{ASSESSMENT}}
\vspace{0.7em}
\begin{table}[hbt]
  \centering
  \colorbox{violet!10}{%
 	\resizebox{0.7\textwidth}{!}{%
  \renewcommand{\arraystretch}{1.3}
  \begin{tabular}{@{}>{\bfseries}p{5.5cm}cccccc@{}}
	    \toprule

    \textcolor{blue!60}{\textbf{Method}}  & \textcolor{blue!60}{\textbf{Entropy}} & \textcolor{blue!60}{\textbf{MAE}}
		& \textcolor{blue!60}{\textbf{RMSE}} & \textcolor{blue!60}{\textbf{SD}} & \textcolor{blue!60}{\textbf{CC}} \\
    \midrule
    \textbf{HH}  & 6.6439      & 1.8400       & 3.7175   & 2.6291   & 0.9986 \\
    \textbf{HV}  & 6.6293      & 1.6700       & 2.9275   & 2.0640   & 0.9992 \\
    \textbf{VV}  & 6.6438      & 4.2400      & 7.9461    & 5.5649   & 0.9941 \\
    \textbf{S-ROC} & \textcolor{red}{6.0223}      & 1.4154      & 2.3664    & 1.6311    & \textcolor{red}{0.9994} \\
    \textbf{PCA} & 7.7944      & 3.0180       & 6.0657   & 4.2788  & 0.9964 \\
    \textbf{SWT} & 12.0914     & 5.8006      & 9.2486   & 6.4161  & 0.9932 \\
    \bottomrule
  \end{tabular}}}
\end{table}
\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    \draw[double -stealth=10pt colored by blue!50!black and white] (0,0) -- (0,-2cm);
     \end{tikzpicture}
  % \caption{Figure}
\end{figure}

\vspace{-0.8cm}
\begin{figure}[h]
  \centering
  \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] (image) at (0,0) {\includegraphics[width=29cm,height=17cm]{figures/roc_f.pdf}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
      \node[above right, font=\bfseries\small, blue] at (0.4,0.1) {S-ROC Method};
    \end{scope}
  \end{tikzpicture}\vspace{-0.5cm}
  \caption*{\large{Estimated points vs. ground reference}}
\end{figure}
\vspace{-1.2cm}

\begin{figure}[H] 
\centering
	\includegraphics[width=29cm,height=17cm]{figures/metricas.pdf}
	%\caption*{\large{Quality metrics}}
	%\label{F5}
\end{figure}

\end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

%\setbeamercolor{block title}{fg=norange,bg=white} % Change the block title color
%
%\begin{block}{Acknowledgements}
	%
%
	%
%\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%\begin{block}{References}
%
	%{\footnotesize\bibliographystyle{abbrv} 
	%\bibliography{poster}}
%\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}
\begin{column}{\sepwid}\end{column} % Empty spacer column

### 2023-07-01 Text/Poster/poster_Igarss_23.tex
QR code added to poster

@@
   \texorpdfstring{%
-    \makebox[\linewidth]{	%
-      \makebox[100pt][l]{%
+    \makebox[\linewidth]{%
+      \makebox[-200pt][l]{%
         \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
-          {\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}% Left logo
-      }\hfill
+          {\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}}% Left logo
+      \hfill
       \makebox[\dimexpr\linewidth-4em][c]{%
@@
       }%
-
-      \hfill\makebox[-50pt][r]{%
+      \hfill\hspace{-50cm} %
+      \raisebox{\dimexpr-\height-1.1\baselineskip}[0pt][0pt] % 
+        {\includegraphics[height=2.9\baselineskip]{../../Figures/PNG/QRCode-WebPageVUW.png}}% New figure
+      \hfill
       \raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
@@
 }
-  } % Poster title
 
 \author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
-\institute[]{$^1$Universidade Federal de Pernambuco, Recife, Brazil\\
+\institute[]{%
+  \makebox[\linewidth]{%
+    \begin{minipage}[c]{0.6\linewidth}
+      \centering
+      \vspace{0.5cm}
+      $^1$Universidade Federal de Pernambuco, Recife, Brazil\\
       $^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
-$^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
+      $^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand
+    \end{minipage}%
+
+}}
+
+%\title{%
+  %\texorpdfstring{%
+    %\makebox[\linewidth]{	%
+      %\makebox[-100pt][l]{%
+        %\raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
+          %{\includegraphics[height=2.7\baselineskip]{figures/logo_IG23.pdf}}% Left logo
+      %}\hfill
+			%\makebox[\dimexpr\linewidth-4em][c]{%
+        %\begin{minipage}{\linewidth}
+          %\centering
+          %\LARGE QUALITY ASSESSMENT MEASURES FOR EXPLAINABLE FUSION OF STATISTICAL\\ EVIDENCES OF EDGES IN POLSAR IMAGES: A FIRST APPROACH
+        %\end{minipage}
+      %}%
+      %\hfill\hspace{-20cm} % Ajusta la cantidad de espacio según tus necesidades
+      %\raisebox{\dimexpr-\height-1.5\baselineskip}[0pt][0pt] % Ajusta la cantidad de espacio según tus necesidades
+        %{\includegraphics[height=2.7\baselineskip]{../../Figures/PNG/QRCode-WebPageVUW.png}}% New logo
+            %\hfill\makebox[-50pt][r]{%
+        %\raisebox{\dimexpr-\height+\baselineskip}[0pt][0pt]
+          %{\includegraphics[height=3.0\baselineskip]{figures/logos.pdf}}% Right logo
+      %}%
+    %}%
+  %}
+  %} % Poster title
+	%
+	%\author{\vspace*{2cm}Rosa Janeth Alpala$^1$,  Anderson A.\ de Borba$^{2,3}$  and \textbf{Alejandro C.\ Frery}$^3$}
+%\institute[]{$^1$Universidade Federal de Pernambuco, Recife, Brazil\\
+%$^2$Mackenzie Presbyterian University--UPM, FCI, BigMAAp, SP -- Brazil\\
+%$^3$School of Mathematics and Statistics, Victoria University of Wellington, New Zealand}
 

### 2023-09-24 Text/Articles/MIGARS_2024/migars2024_abstract.tex
paper template

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}                        %
\usepackage[utf8]{inputenc}                  % 
\usepackage{rotating}                        %
%\usepackage{subfigure}                       
%\usepackage[export]{adjustbox}              
\usepackage{bbm}

\DeclareRobustCommand{\bbone}{\text{\usefont{U}{bbold}{m}{n}1}}

\DeclareMathOperator{\EX}{\mathbb{E}}% expected value

\ifCLASSOPTIONcompsoc                        %
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[caption=false,font=footnotesize]{subfig}
\fi
%
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\DeclareMathOperator{\traco}{tr}

\begin{document}

\title{Identifying Departures from the Fully Developed Speckle Hypothesis In Intensity SAR Data with Non-Parametric Estimation of the Entropy\\

\thanks{Grantee Capes.}
}

\author{
\begin{minipage}[t]{0.3\textwidth}
\centering
1st Given Name Surname \\
\textit{Dept. name of organization } \\
\textit{Name of organization }\\
City, Country \\
Email address 
\end{minipage}%
\begin{minipage}[t]{0.3\textwidth}
\centering
2nd  Given Name Surname \\
\textit{Dept. name of organization } \\
\textit{Name of organization }\\
City, Country \\
Email address 
\end{minipage}%
\begin{minipage}[t]{0.3\textwidth}
\centering
3rd Given Name Surname \\
\textit{Dept. name of organization } \\
\textit{Name of organization }\\
City, Country \\
Email address 
\end{minipage}
}

\maketitle\begin{abstract}
This study focuses on the analysis of Intensity SAR Data, which is commonly affected by speckle noise, introducing complexity into data analysis and necessitating specialized models and techniques for effective information extraction. 
The main goal is to identify departures from the fully developed speckle hypothesis within SAR intensity data. 
The study highlights the suitability of the $G^0$ distribution family and underscores the significance of entropy as a meaningful metric. 
Additionally, a non-parametric approach employing order statistics is applied to estimate entropy for this analysis, enhancing the understanding of these data characteristics.
\end{abstract}

\begin{IEEEkeywords}
SAR, Entropy estimation, Non-parametric analysis, Order statistics
\end{IEEEkeywords}

\section{Introduction}\label{sec_01}

emote sensing data obtained through sensors, particularly Synthetic Aperture Radar (SAR), play a pivotal role in understanding environmental dynamics, enabling predictive capabilities, and facilitating early disaster detection. Unlike optical spectrum observations, microwave remote sensing sensors, operating in the microwave band, offer significant advantages, including reduced sensitivity to adverse atmospheric conditions and their self-illuminating properties.

This study is dedicated to the analysis of SAR intensity data, which frequently contends with the presence of speckle noise. Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction. In this context, we propose the adoption of the G0 distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.

The article is structured as follows: 
Section~\ref{sec_02} describes

\section{Statistical modeling for SAR data}\label{sec_02}

\section{Nonparametric entropy estimation}

Let $X_1,\ldots,X_n$ be a random sample from $X$, with density $f$, consider the nonparametric estimation of functional
\begin{equation}
  \label{E:entropy1}
  T(f)=\int_{-\infty }^\infty \!\! f(x)\Phi(f(x))w(x)\,dx,
\end{equation}
where, $\Phi=\phi(x)/x$, and $w(x)= \mathbbm{I}_E(x)$ for any set $E$.
And the entropy of the density $f$, obtained by taking $\Phi(x)=-\log (x)$, where $w=1$.
\begin{equation}
  \label{E:entropy2}
  H(f)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx,=\EX(-\log(f(X)).
\end{equation}
The problem of estimating $H(f)$ has been considered by many authors including
Correa \cite{correa1995new}, van Es \cite{van1992}, Wieczorkowski and Grzegorzewski, and Vasicek.

\begin{itemize}
	\item Van Es

\begin{align*}
%\label{E:VanEs}
	\widehat{H}_{VE}=\frac{1}{n-m}&\sum_{i=1}^{n-m}\log\left\{\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right\}\\
	&\sum_{k=m}^n\frac{1}{k}+\log\left(\frac{m}{n+1}\right)
\end{align*}
Van Es, showed that, under general conditions, \ref{E:VanEs} can be converges almost surely 
%$H(X)=-\sum_{i=1}^k{p_i\log p_i}$
\end{itemize}

\section{Results}

\section{Conclusion}\label{sec_09}

In this article,

\bibliographystyle{IEEEtran}
%\bibliography{strings,refs}

\bibliography{../../Common/references}\end{document}

### 2023-09-26 Text/Articles/MIGARS_2024/migars2024_abstract.tex
update content

@@
 %\usepackage[export]{adjustbox}              
-\usepackage{bbm}
+\usepackage{bm}
 
@@
 
-\title{Identifying Departures from the Fully Developed Speckle Hypothesis In Intensity SAR Data with Non-Parametric Estimation of the Entropy\\
+\title{Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy\\
 
@@
 The main goal is to identify departures from the fully developed speckle hypothesis within SAR intensity data. 
-The study highlights the suitability of the $G^0$ distribution family and underscores the significance of entropy as a meaningful metric. 
+The study highlights the suitability of the $\mathcal{G}^0$ distribution family and underscores the significance of entropy as a meaningful metric. 
 Additionally, a non-parametric approach employing order statistics is applied to estimate entropy for this analysis, enhancing the understanding of these data characteristics.
@@
 \begin{IEEEkeywords}
-SAR, Entropy estimation, Non-parametric analysis, Order statistics
+SAR, entropy estimation, non-parametric analysis, order statistics
 \end{IEEEkeywords}
@@
 
-emote sensing data obtained through sensors, particularly Synthetic Aperture Radar (SAR), play a pivotal role in understanding environmental dynamics, enabling predictive capabilities, and facilitating early disaster detection.
+Remote sensing data from sensors, in particular synthetic aperture radar (SAR), play a key role in understanding the dynamics of the environment, enabling predictive capabilities and facilitating the early detection of disasters.
 Unlike optical spectrum observations, microwave remote sensing sensors, operating in the microwave band, offer significant advantages, including reduced sensitivity to adverse atmospheric conditions and their self-illuminating properties.
+
+Entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
+Shannon introduced it for a random variables in 1948~\cite{Shannon1948} as a measure of information and uncertainty. 
+In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity~\cite{Wieczorkowski1999}.
+
+Estimating entropy presents practical challenges, especially when the true probability density function (pdf) is unknown.
+In such cases, nonparametric methods are employed for entropy estimation. 
+In the parametric approach, the form of the pdf is assumed to be known, and its parameters are inferred from the available samples. 
+Conversely, nonparametric methods, like histogram or kernel density estimators, do not make such assumptions. 
+They estimate the pdf using these techniques and then calculate entropy through numerical or Monte Carlo integration. 
+Other nonparametric approaches involve spacing methods, which allow the estimation of the entropy of a random variable with an unknown distribution function when independent and identically distributed (i.i.d.) observations of the random variable are available.
+
+In this paper we consider an estimator based on spacings
 
@@
 Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction.
-In this context, we propose the adoption of the G0 distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.
+In this context, we propose the adoption of the $G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.
 
@@
 
+\subsection{Intensity data}
+
+The primary models used for intensity SAR data include the Gamma, $\mathcal{K}$, and $\mathcal{G}^0$ distributions.
+
+\begin{align}
+	f(z; \mu, L)=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\}
+\end{align}
+
+\begin{align}
+	f(z; \alpha, \gamma, L)=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
+\end{align}
+
 \section{Nonparametric entropy estimation}
 
-Let $X_1,\ldots,X_n$ be a random sample from $X$, with density $f$, consider the nonparametric estimation of functional
-\begin{equation}
-  \label{E:entropy1}
-  T(f)=\int_{-\infty }^\infty \!\! f(x)\Phi(f(x))w(x)\,dx,
-\end{equation}
-where, $\Phi=\phi(x)/x$, and $w(x)= \mathbbm{I}_E(x)$ for any set $E$.
-And the entropy of the density $f$, obtained by taking $\Phi(x)=-\log (x)$, where $w=1$.
-\begin{equation}
-  \label{E:entropy2}
-  H(f)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx,=\EX(-\log(f(X)).
-\end{equation}
-The problem of estimating $H(f)$ has been considered by many authors including
-Correa \cite{correa1995new}, van Es \cite{van1992}, Wieczorkowski and Grzegorzewski, and Vasicek.
+Suppose a random variable $X$ has a distribution function $F(x)$ with a continuous density function $f(x)$. Then, the Shannon entropy $H(X)$ is defined as
+\begin{equation*}
+  %\label{E:entropy2}
+  H(X)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx.
+\end{equation*}
+The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, van1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
 
-\begin{itemize}
-	\item Van Es
+Vasicek \cite{vasicek1976test}, used $f(x)=p$  to express $ H(f)$ as
+\begin{align*}
+	H(X)= \int_0^1 \log\left(\frac{d}{dp}Q(p)\right)dp,
+\end{align*}
 
+where $Q(p)=F^{-1}(p)=\inf\left\{x: F(x)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.
+Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is given by
 \begin{align*}
 %\label{E:VanEs}
-	\widehat{H}_{VE}=\frac{1}{n-m}&\sum_{i=1}^{n-m}\log\left\{\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right\}\\
-	&\sum_{k=m}^n\frac{1}{k}+\log\left(\frac{m}{n+1}\right)
+	\widehat{H}_{V}(\bm{X})=\frac{1}{n}&\sum_{i=1}^{n}\log\left\{\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right\},
 	\end{align*}
-Van Es, showed that, under general conditions, \ref{E:VanEs} can be converges almost surely 
-%$H(X)=-\sum_{i=1}^k{p_i\log p_i}$
-\end{itemize}
+where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $X_{(i)}= X_{(n)}$ if $i>n$.
+
+Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{van1992}, who proposed a new estimator of entropy given by
+
+\begin{align}
+%\label{E:VanEs}
+	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}&\sum_{i=1}^{n-m}\log\left\{\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right\}.\\
+	+&\sum_{k=m}^n\frac{1}{k}+\log\left(\frac{m}{n+1}\right)\nonumber
+\end{align}
+Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.
+
+\section{Fully Developed Speckle}
 

### 2023-09-27 Text/Articles/MIGARS_2024/DiscreteEntropy.tex
hypothesis testing

\documentclass[12pt]{article}

%\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage{epsfig}

\usepackage{amsmath}
\usepackage{natbib}
\usepackage{fourier}
\usepackage{xcolor}

%\theoremstyle{plain}% Theorem-like structures
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}[prop]{Corollary}
\newtheorem{lemma}[prop]{Lemma}

\title{Hypothesis testing based on nonparametric entropies}

\begin{document}
\maketitle

Consider the problem of planning hypothesis tests based on nonparametric entropies from the functional \citep{Khashimov1990} and \citep{Bert1992}:
Let $f(\cdot)$ be a density,
\begin{equation}
T_{\mathcal{D}}(f)=\int_{-\infty}^\infty f(x)\Phi(f(x))\mathrm{d}x=\int_{-\infty}^\infty f(x)h\Big(\frac 1{f(x)}\Big)\mathrm{d}x,
\label{Eq:1}
\end{equation}
where $\Phi(x)$ and $h(x)$ are real-valued functions on $[0,\infty)$ satisfying certain regularity conditions.
As an example of \eqref{Eq:1}, the definition of $\Phi(x)=h(1/x)=-\log(x)$ becomes $T_{\mathcal{D}}(f)$ the Shannon entropy formula of a distribution on $(-\infty, \infty)$.
From now on, we use $T_{\mathcal{D}}:=T_{\mathcal{D}}(f)$ as a notation for a possible or well-defined entropy (such as Shannon, R\'enyi, and Tsallis).

A consistent estimator for $T_{\mathcal{D}}$ is given for the next class of statistics:
Let $X_{1:n}\leq X_{2:n}\leq\cdots\leq X_{n:n}$ be the ordered sample from an n-point random sample and $m$ be an integer such that $1\leq m\leq n$,
$$
T_{n,m}
=
{\frac 12}\frac{1}{n-m}\sum_{j=1}^{n-m}\Phi\Big(\frac{m}{n+1}\Big[X_{j+m:n}-X_{j:n}\Big]^{-1}\Big)
=
\frac{1}{n}\sum_{j=1}^{n-m}h\Big(\frac{n}{m}\Big[X_{j+m:n}-X_{j:n}\Big]\Big).
$$
\citet{Khashimov1990} have derived general asymptotic results for functions of spacings; while \citet{Bert1992} have developed a correction for the case of Shannon entropy.]After \citet{Khashimov1990} and \citet{Bert1992}, the next result applies.

\begin{lemma}
Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
\begin{itemize}
\item[(i)]
$$
\sqrt{n}\,\Big(V^*_{m,n}+\int_{-\infty}^\infty f(x)\log f(x) \mathrm{d}x\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,\operatorname{Var}(\log f(X))),
$$
where $o(\cdot)$ represents the little-o and
$$
V^*_{m,n}=\frac{1}{n-m} \sum_{j=1}^{n-m} \log\Big(\frac{n+1}{m}\Big[X_{j+m:n}-X_{j:n}\Big]\Big)+\sum_{k=m}^n{\frac 1k}+\log m -\log(n+1).
$$
\item[(ii)]
$$
\sigma^{-1}\sqrt{n}\Big(T_{m,n}^*-\int_{-\infty}^{\infty}h(1/f(x))f(x)\mathrm{d}x\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,1),
$$
where $h(1/f(x))=\Phi(f(x))$ provides a unification between the results of \citet{Khashimov1990} and \citet{Bert1992}, $F(x)$ means the cumulative distribution function (cdf) with respect to $f(x)$,
\begin{multline*}
T_{n,m}^*= {\frac 1n}\sum_{j=1}^{n-m}\Bigg[h\Big({\frac nm}\Big[X_{j+m:n}-X_{j:n}\Big]\Big)\\+\frac{[(n/m)(X_{j+m:n}-X_{j:n})]^2}{2m}h''\Big({\frac nm}\Big[X_{j+m:n}-X_{j:n}\Big]\Big)\Bigg]
\end{multline*}
and
\begin{multline*}
\sigma^2=\int_{-\infty}^{\infty}h'\Big(\frac{1}{f(x)}\Big)\frac{1}{f(x)}\mathrm{d}x\\
+\int_{-\infty}^\infty \Big[\int_{-\infty}^y\Big(\frac{1}{f(x)}-\frac{F(x)f'(x)}{f^3(x)}\Big)h'\Big(\frac{1}{f(x)}\Big)f(x)\mathrm{d}x\Big]^2\frac{f(y)}{F^2(y)}\mathrm{d}x
\end{multline*}
for $h'(x)$ and $h''(x)$ as first and second order derivatives, respectively.
\end{itemize}
\end{lemma}

Let us now consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
$$
(i) \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \quad (ii) \mathcal{H}_1:T_{\mathcal{D}}> D_0, \quad\text{or}\quad (iii) \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
$$
For this purpose, we can use the test statistics:
$$
Z_{m,n} = 
\left\{
\begin{array}{ll}
\frac{\sqrt{n}(V^*_{m,n}-D_0)}{\sqrt{\operatorname{Var}(\log f(X))}}, 
\quad \text{ for }\Phi(x)=\log(x),\\
\frac{\sqrt{n}(T^*_{m,n}-D_0)}{\sigma},
\quad \text{ for any }h(x)\text{ possible}. 
\end{array}
\right.
$$
So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.

The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
$$
\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
$$
for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(x)$.

\bibliographystyle{agsm}
\bibliography{../../Common/references}
\end{document}

### 2023-09-27 Text/Articles/MIGARS_2024/migars2024_abstract.tex
hypothesis testing

@@
 \end{equation*}
-The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, van1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
+The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
 
@@
 
-Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{van1992}, who proposed a new estimator of entropy given by
+Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by
 

### 2023-09-30 Text/Articles/MIGARS_2024/migars2024_abstract.tex
Authors
Abstract

@@
 \author{
-\begin{minipage}[t]{0.3\textwidth}
+\begin{minipage}[t]{0.5\textwidth}
 \centering
-1st Given Name Surname \\
-\textit{Dept. name of organization } \\
-\textit{Name of organization }\\
-City, Country \\
-Email address 
+Rosa Janeth Alpala, Abraão D.\ C. Nascimento \\
+\textit{Departamento de Estatística} \\
+\textit{Universidade Federal de Pernambuco}\\
+Recife, PE, Brazil\\
+janeth.alpala@ufpe.br, abraao@de.ufpe.br 
 \end{minipage}%
-\begin{minipage}[t]{0.3\textwidth}
+%\begin{minipage}[t]{0.3\textwidth}
+%\centering
+%2nd  Given Name Surname \\
+%\textit{Dept. name of organization } \\
+%\textit{Name of organization }\\
+%City, Country \\
+%Email address 
+%\end{minipage}%
+\begin{minipage}[t]{0.4\textwidth}
 \centering
-2nd  Given Name Surname \\
-\textit{Dept. name of organization } \\
-\textit{Name of organization }\\
-City, Country \\
-Email address 
-\end{minipage}%
-\begin{minipage}[t]{0.3\textwidth}
-\centering
-3rd Given Name Surname \\
-\textit{Dept. name of organization } \\
-\textit{Name of organization }\\
-City, Country \\
-Email address 
+Alejandro C.\ Frery\\
+\textit{School of Mathematics and Statistics} \\
+\textit{Victoria University of Wellington}\\
+Wellington, New Zealand\\
+alejandro.frery@vuw.ac.nz
 \end{minipage}
@@
 \maketitle\begin{abstract}
-This study focuses on the analysis of Intensity SAR Data, which is commonly affected by speckle noise, introducing complexity into data analysis and necessitating specialized models and techniques for effective information extraction.
-The main goal is to identify departures from the fully developed speckle hypothesis within SAR intensity data. 
-The study highlights the suitability of the $\mathcal{G}^0$ distribution family and underscores the significance of entropy as a meaningful metric. 
-Additionally, a non-parametric approach employing order statistics is applied to estimate entropy for this analysis, enhancing the understanding of these data characteristics.
+SAR Data are affected by speckle in a non-additive and non-Gaussian way.
+The type of distribution these data follow is paramount for their processing and analysis.
+Good statistical models provide flexibility and accuracy, often at the cost of using several parameters.
+The $\mathcal{G}^0$ distribution is one of the most successful models for SAR data. 
+It includes the Gamma law as particular case which arises in the presence of fully developed speckle.
+Although the latter is a limit distribution of the former, using the same estimation technique for the more general model is numerically unfeasible.
+We propose a two-stage estimation procedure: first, we verify the hypothesis that the data are fully-developed speckle and, if this assumption is rejected, we proceed to estimate the parameters that index the $\mathcal G^0$ distribution.
+Given the uncertainty of the underlying distribution, and the negative impact that using an inadequate model has on maximum likelihood estimation, we employ a non-parametric approach to estimate entropy under the fully-developed speckle hypothesis.
 \end{abstract}

### 2023-09-30 Text/Articles/MIGARS_2024/migars2024_abstract.tex
Improving LaTeX code

@@
 
-In this paper we consider an estimator based on spacings
+In this paper we consider an estimator based on spacings.
 
@@
 Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction. 
-In this context, we propose the adoption of the $G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.
+We adopt the $\mathcal G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.
 
@@
 \begin{align}
-	f(z; \mu, L)=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\}
-\end{align}
-
-\begin{align}
-	f(z; \alpha, \gamma, L)=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
+	f(z; \mu, L)&=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\},\\
+	f(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
 \end{align}
@@
 Vasicek \cite{vasicek1976test}, used $f(x)=p$  to express $ H(f)$ as
-\begin{align*}
+\begin{equation*}
 	H(X)= \int_0^1 \log\left(\frac{d}{dp}Q(p)\right)dp,
-\end{align*}
-
+\end{equation*}
 where $Q(p)=F^{-1}(p)=\inf\left\{x: F(x)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.
 Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is given by
-\begin{align*}
+\begin{equation*}
 %\label{E:VanEs}
-	\widehat{H}_{V}(\bm{X})=\frac{1}{n}&\sum_{i=1}^{n}\log\left\{\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right\},
-	\end{align*}
+	\widehat{H}_{V}(\bm{X})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
+	\end{equation*}
 where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $X_{(i)}= X_{(n)}$ if $i>n$.
@@
 Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by
-
-\begin{align}
+\begin{multline}
 %\label{E:VanEs}
-	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}&\sum_{i=1}^{n-m}\log\left\{\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right\}.\\
-	+&\sum_{k=m}^n\frac{1}{k}+\log\left(\frac{m}{n+1}\right)\nonumber
-\end{align}
+	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right]\\
+	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
+\end{multline}
 Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.

### 2023-10-16 Text/Articles/MIGARS_2024/migars2024_abstract.tex
report and code

@@
 \usepackage{xcolor}
-\usepackage{booktabs}                        %
+\usepackage{booktabs}  
+\usepackage{enumitem}
+\usepackage{float}
+                      %
 \usepackage[utf8]{inputenc}                  % 
@@
 \DeclareMathOperator{\traco}{tr}
+%\theoremstyle{plain}
+\newtheorem{lemma}{Lemma}
 
@@
 
-In this paper we consider an estimator based on spacings.
+%In this paper we consider an estimator based on spacings.
 
@@
 
-\section{Statistical modeling for SAR data}\label{sec_02}
+\section{BACKGROUND}\label{sec_02}
 
-\subsection{Intensity data}
+\subsection{Statistical modeling for Intensity SAR data}
 
-The primary models used for intensity SAR data include the Gamma, $\mathcal{K}$, and $\mathcal{G}^0$ distributions.
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions~\cite{Frery1997}. 
+The first is suitable for fully developed speckle and can also be considered a limiting case within the $\mathcal{G}_I^0$ distribution.
+Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics~\cite{Cassetti2022}.
+We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
 
 \begin{align}
-	f(z; \mu, L)&=\frac{L^L}{\Gamma(L)\mu(L)}z^{L-1}\exp\left\{-Lz/\mu\right\},\\
-	f(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}z^{L-1}(\gamma+Lz)^{\alpha-L}
+	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\},\label{E:gamma1}\\
+	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}},\label{E:gi01}
+\end{align}
+where, in~\eqref{E:gamma1} $\mu > 0$ is the mean; in~\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.
+
+From \eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
+\begin{align}
+	E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
+	\label{E:rmom}
 \end{align}
 
-\section{Nonparametric entropy estimation}
+Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$~\cite{Nascimento2010}.
+In this way, we compute the expected value $\mu$ using the expression in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
+\begin{align*}
+	\mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+\end{align*}
+Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ is
+{\small % o \footnotesize
+\begin{align}
+		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{(-\mu(\alpha+1))^{\alpha}\Gamma(-\alpha)\Gamma(L)}\frac{z^{L-1}}{(-\mu(\alpha+1)+Lz)^{L-\alpha}}.\label{E:gi02}
+\end{align}
+}
 
-Suppose a random variable $X$ has a distribution function $F(x)$ with a continuous density function $f(x)$. Then, the Shannon entropy $H(X)$ is defined as
+\subsection{Parametric \& Non-Parametric Shannon Entropy}
+
+The parametric representation of Shannon entropy for a system described by a continuous random variable is as follows:
+\begin{equation}
+  \label{E:entropy2}
+  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log(f(z))\, \mathrm{d}z,
+\end{equation}
+here, $f(\cdot)$ is the probability density function that characterizes the distribution of the real-valued random variable $Z$.
+
+Using~\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$ in~\eqref{E:gamma1} and $\mathcal{G}_I^0$ in~\eqref{E:gi02} based on~\cite{Cassetti2022, A.Ferreira2020}:
+%{\small % o \footnotesize
+\begin{align}
+H_{\Gamma_{\text{SAR}}}(L, \mu) &=   L -\log(L/\mu)+\log\Gamma(L)+(1-L)\psi^{(0)}(L), \label{E:E-gamma}\\
+H_{\mathcal{G}_I^0}(\mu, \alpha, L) &= -\log(\alpha)+\log(\mu)+\log(1+\alpha)\nonumber \\
+&\quad -(1-\alpha)\psi^{(0)}(-\alpha) +\log(-\alpha)-\log(L) \nonumber \\
+&\quad + (L-\alpha)\psi^{(0)}(L-\alpha) +\log\left(\mathcal{B}(L,-\alpha)\right)\nonumber \\
+&\quad  + (1-L)\psi^{(0)}(L), \label{E:E-GIO}
+\end{align}
+where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.
+
+%-------------------------------------------------------------------------------------------------------------
+
+%\section{Nonparametric entropy estimation}
+
+The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including~\cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
+
+Vasicek \cite{vasicek1976test}, used $f(z)=p$  to express $ H(Z)$ as
 \begin{equation*}
-  %\label{E:entropy2}
-  H(X)=-\int_{-\infty }^\infty \ f(x)\log(f(x))\,dx.
+	H(Z)= \int_0^1 \log\frac{\mathrm{d}}{\mathrm{d}p}Q(p)\mathrm{d}p,
 \end{equation*}
-The problem of estimating $H(X)$ has been considered by many authors including \cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
+where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics~\cite{AlOmari2019}.
 
-Vasicek \cite{vasicek1976test}, used $f(x)=p$  to express $ H(f)$ as
-\begin{equation*}
-	H(X)= \int_0^1 \log\left(\frac{d}{dp}Q(p)\right)dp,
-\end{equation*}
-where $Q(p)=F^{-1}(p)=\inf\left\{x: F(x)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.
-Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is given by
+Assuming that  $\bm{Z}=(Z_1, Z_2, \ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
 \begin{equation*}
 %\label{E:VanEs}
-	\widehat{H}_{V}(\bm{X})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
+	\widehat{H}_{V}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 	\end{equation*}
-where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $X_{(i)}= X_{(n)}$ if $i>n$.
+where $m<n/2$ is a positive integer, $Z_{(i+m)}-Z_{(i-m)}$ is the $m$-spacing and $Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}$ are the order statistics and $Z_{(i)}= Z_{(1)}$ if $i<1$, $Z_{(i)}= Z_{(n)}$ if $i>n$.
 
-Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es \cite{Bert1992}, who proposed a new estimator of entropy given by
+Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es~\cite{Bert1992}, who proposed a new estimator of entropy given by:
 \begin{multline}
-%\label{E:VanEs}
-	\widehat{H}_{VE}(\bm{X})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right]\\
+\label{E:VanEs}
+	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]\\
 	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
 \end{multline}
-Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.
 
-\section{Fully Developed Speckle}
+Van Es proved that, under general conditions,~\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
+The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.
+\section{Hypothesis testing based on non-parametric entropy}
+
+General asymptotic results for functions of spacings are detailed in~\cite{Khashimov1990}, while Van Es~\cite{Bert1992} has developed a correction for the case of Shannon entropy.
+Following the work of these authors, the next result applies:
+
+\begin{lemma}
+Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
+Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
+$$
+\sqrt{n}\,\Big(\widehat{H}_{\text{VE}}+\int_{-\infty}^\infty f(z)\log f(z) \mathrm{d}z\Big)
+\xrightarrow[]{\mathcal{D}}
+\mathcal{N}(0,\operatorname{Var}(\log f(Z))),
+$$
+where $o(\cdot)$ represents the little-o and $\widehat{H}_{\text{VE}}$ is defined in expression~\eqref{E:VanEs}.
+
+\end{lemma}
+
+Let us consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
+%\begin{enumerate}[label=(\roman*)]
+  %\item $\mathcal{H}_1:T_{\mathcal{D}}\neq D_0,$
+  %\item $\mathcal{H}_1:T_{\mathcal{D}}> D_0,$
+  %\item $\mathcal{H}_1:T_{\mathcal{D}}< D_0.$
+%\end{enumerate}
+$$
+\text{(i)}\, \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \, \, \text{(ii)}\, \mathcal{H}_1:T_{\mathcal{D}}> D_0, \, \, \text{or}\, \,  \text{(iii)}\, \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
+$$
+
+For this purpose, we can use the test statistics:
+$$
+Z_{m,n} = \frac{\sqrt{n}(\widehat{H}_{\text{VE}}-D_0)}{\sqrt{\operatorname{Var}(\log f(Z))}},
+$$
+So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+
+The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
+\begin{multline*}
+\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
+\end{multline*}
+for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
 
@@
 
+We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases.
+%This indicates that the data appear to match the fully developed speckle hypothesis.
+
+We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
+We performed experiments to observe convergence under different scenarios, where each employed different sample sizes, i.e., $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
+
+For each sample size, we performed $10.000$ samples. Fig. \ref{F4} shows convergence of mean non-parametric entropies, for $\mu=3$ and $L=2$.
+
+%mu <- 3
+%L <- 2
+%alpha <- -5
+%
+%r <- 10000
+%n_values <- c(9, 25, 49, 81, 121, 500, 1000, 5000, 10000 ) 
+\begin{figure}[H] 
+\centering
+	\includegraphics[scale=0.5]{../../../Figures/PDF/mean_entropies1}\vspace{-1.5mm} 
+	\caption{Convergence of mean non-parametric entropies.}
+	\label{F4}
+\end{figure}
+\begin{figure}[H] 
+\centering
+	\includegraphics[scale=0.5]{../../../Figures/PDF/histo1}\vspace{-1.5mm} 
+	\caption{Histogram of entropies.}
+	\label{F5}
+\end{figure}
 \section{Conclusion}\label{sec_09}

### 2023-10-16 Code/R/example.R

@@ -1,16 +1,0 @@
-rm(list = ls(all = TRUE))
-graphics.off()
-shell("cls")
-
-getwd()
-
-
-
-library(dplyr) 
-library(pROC) 
-library(MASS)
-library(broom) 
-library(AUC)
-library(pROC)
-library(tidyverse)
-dplyr::roc()

### 2023-10-16 Code/R/test5.R

@@ -1,0 +1,126 @@
+rm(list = ls())
+
+library(gtools)
+library(stats4)
+library(rmutil)
+library(gsl)
+
+mu <- 3
+L <- 1
+alphap <- -5
+
+r <- 1000
+#n_values <- c(9, 25, 49, 81, 200, 500, 1000)
+n <- 1000
+
+entropy_gamma_sar <- function(L, mu) {
+  term1 <- L
+  term2 <- log(gamma(L))
+  term3 <- (1 - L) * digamma(L)
+  term4 <- log(L / mu)
+  
+  entropy <- term1 +term2 + term3 - term4 
+  
+  return(entropy)
+}
+
+
+entropy_gI0 <- function(mu, alpha, L) {
+  # entropía de GI0
+  term1 <- -log(alphap / (mu * (1 + alphap))) - (1 - alphap) * digamma(-alphap)
+  term2 <- log(-alphap / L) + (L - alphap) * digamma(L - alphap)
+  term3 <- log(beta(L, -alphap))
+  term4 <- (1 - L) * digamma(L)
+  
+  entropy <- term1 + term2 + term3 + term4
+  return(entropy)
+}
+
+#muestras Gamma SAR
+gamma_sar_sample <- function(L, mu, n) {
+  samples <- rgamma(n, shape = L, rate = L / mu)
+  return(samples)
+}
+
+#  estimador Van Es
+van_es_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term1 <- 0
+  sum_term2 <- 0
+  
+  for (i in 1:(n - m)) {
+    sum_term1 <- sum_term1 + log(((n + 1) / m) * (data_sorted[i + m] - data_sorted[i]))
+  }
+  
+  for (k in m:n) {
+    sum_term2 <- sum_term2 + 1 / k
+  }
+  
+  sum_term3 <- log(m / (n + 1))
+  
+  return((sum_term1 / (n - m)) + sum_term2+ sum_term3)
+}
+
+D0 <- entropy_gamma_sar(L, mu)  
+
+# ---
+alpha <- 0.05
+z_alpha_2 <- qnorm(1 - alpha / 2)
+p_values <- c()
+rechazo_h0 <- c()
+means_entropies <- c()
+
+entropies <- c()
+
+  
+  for (i in 1:r) {
+    
[…]

### 2023-10-16 Code/R/RMarkdown/EntropyPlots.Rmd
RMarkdown exercise

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
```

# Gamma-SAR entropy

We will see how the Shannon entropy of the Gamma-SAR model varies.
It is given by
\begin{align}
H_{\Gamma_{\text{SAR}}}(L_0, \mu) &=   L_0 -\ln(L_0/\mu)+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0)\\
&= \big[L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0)\big] + \ln \mu.
\end{align}
where $L_0\geq 1$ is known, and $\mu>0$ is the mean.
We see that, given $L_0$, the entropy of a random variable following the Gamma-SAR model depends on the logarithm of the mean $\mu$.

```{r FunctionsDefinitions}
entropy_gamma_sar <- function(L, mu) {

  return(L + log(gamma(L)) + (1 - L) * digamma(L) - log(L / mu))

}
```

```{r PlotGammaSAR, echo=FALSE}
mu <- seq(.1, 10, length.out=500)

EntropyL1 <- entropy_gamma_sar(L=1, mu)
EntropyL3 <- entropy_gamma_sar(L=3, mu)
EntropyL8 <- entropy_gamma_sar(L=8, mu)
EntropyL12 <- entropy_gamma_sar(L=12, mu)
EntropyL100 <- entropy_gamma_sar(L=100, mu)

muEntropy <- data.frame(
  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
)

muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")

ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
  geom_line() +
  theme_pander()

```

# GI0-SAR Entropy

The Shannon entropy of the GI0-SAR model is given by
\begin{multline}
H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) = -\ln(\alpha)+\ln(\mu)+\ln(1+\alpha)
 -(1-\alpha)\psi^{(0)}(-\alpha) +\ln(-\alpha)-\ln L_0
+ (L_0-\alpha)\psi^{(0)}(L_0-\alpha) + \\
\ln\mathcal{B}(L_0,-\alpha)
  + (1-L_0)\psi^{(0)}(L_0), \label{E:E-GIO}
\end{multline}

### 2023-10-18 Code/R/RMarkdown/EntropyPlots.Rmd
R code of entropies

@@
 output: pdf_document
+#html_document
 ---
@@
 library(reshape2)
+library(plotly)
+library(knitr)
+library(rgl)
 ```
@@
 
-  return(L + log(gamma(L)) + (1 - L) * digamma(L) - log(L / mu))
+    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
 
+}
+
+entropy_gI0 <- function(mu, alpha, L) {
+
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+
+  entropy <- term1 + term2 
+  return(entropy)
 }
@@
 The Shannon entropy of the GI0-SAR model is given by
+
 \begin{multline}
-H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) = -\ln(\alpha)+\ln(\mu)+\ln(1+\alpha)
- -(1-\alpha)\psi^{(0)}(-\alpha) +\ln(-\alpha)-\ln L_0
-+ (L_0-\alpha)\psi^{(0)}(L_0-\alpha) + \\
-\ln\mathcal{B}(L_0,-\alpha)
-  + (1-L_0)\psi^{(0)}(L_0), \label{E:E-GIO}
+\label{E:E-GIO}
+H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
+-\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
+-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L_0
 \end{multline}
+
+```{r PlotGI0, echo=FALSE}
+mu <- seq(1, 10, length.out = 500)
+alpha <- seq(-20, -2, length.out = 500)
+
+entropy <- outer(mu, alpha, FUN = function(mu, alpha) entropy_gI0(mu, alpha, L = 1))
+
+#
+persp(x = mu, y = alpha, z = entropy, col = "lightblue", border = "blue")
+
+#open3d()
+
+#persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")
+
+#-----
+# mu <- seq(1, 10, length.out=200)
+# alpha <- seq(-2, -20, length.out=200)
+# 
+# 
+# entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
+# entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
+# entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
+# entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
+# entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
+# 
+# 
+# fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
+# 
+# fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
+# fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
+# fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
+# fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
+# fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
+# 
+# 
+# fig <- fig %>% layout(
+#   scene = list(
+#     xaxis = list(title = "alpha"),
+#     yaxis = list(title = "mu"),
+#     zaxis = list(title = "Entropy")
+#   )
+# )
+# 
+# fig
+
+```

### 2023-10-18 Code/R/RMarkdown/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Working document in RMarkdown

--- 2023-10-16 Text/Articles/MIGARS_2024/migars2024_abstract.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{booktabs}  
-\usepackage{enumitem}
-\usepackage{float}
-                      %
-\usepackage[utf8]{inputenc}                  % 
-\usepackage{rotating}                        %
-%\usepackage{subfigure}                       
-%\usepackage[export]{adjustbox}              
-\usepackage{bm}
+---
+title: Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy
+affiliation:
+  ## Author mode :  use one only of the following --- +
 
-\DeclareRobustCommand{\bbone}{\text{\usefont{U}{bbold}{m}{n}1}}
+  ## one column per author - using only the institution field
+  # author-columnar: true # uncomment this line to use
 
-\DeclareMathOperator{\EX}{\mathbb{E}}% expected value
+  ## one column per institution - using only the institution field
+  # institution-columnar: true # uncomment this line to use
 
-\ifCLASSOPTIONcompsoc                        %
-\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\else
-\usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-%
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+  ## one column wide author/affiliation fields - using author or author_multiline and institution for mark
+  wide: true # uncomment this line to use
 
-\DeclareMathOperator{\traco}{tr}
-%\theoremstyle{plain}
-\newtheorem{lemma}{Lemma}
+  ## Author mode: End ----
 
-\begin{document}
+  ## A custom author ordering field that breaks institution grouping (used with `wide: true`)
+  ## Authors cited in institution field are ignored when this author field exists
+  ## Comment / Uncomment below
+  author:   
+   - name: Eldon Tyrell
+     mark: [2, 3]
+     email: eldon@starfleet-academy.star
+   - name: Michael Shell
+     mark: 1
+   - name: Roy Batty
+     mark: 4
+     email: roy@replicant.offworld
 
-\title{Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy\\
+  ## Put authors in a given order, with multiline possibility (used with `wide: true` if `authors` above unset)
+  ## Authors cited in institution are ignored if exists
+  ## Comment / Uncomment below
+  #author_multiline: 
+  #  - line:         ## Create a new author line
+  #    - name: Michael Shell
+  #      mark: 1
+  #    - name: Homer Simpson
+  #      mark: 2
+  #      email: homer@thesimsons.com
+  #    - name: Roy Batty
+  #      mark: 4
+  #      email: roy@replicant.offworld
+  #  - line:         ## Create a second author line
+  #    - name: Montgomery Scott
+  #      mark: 3
+  #    - name: Eldon Tyrell
+  #      mark: 4
 
-\thanks{Grantee Capes.}
-}
+  ## Define institution, and also authors used when `author-columnar: true` or `institution-columnar: true`
+  institution:
+    - name: Georgia Institute of Technology
+      department: School of Electrical and Computer Engineering
+      location: Atlanta, Georgia 30332--0250
+      email: ece@datech.edu # if unset, authors' email will be used
+      mark: 1
+      author:
+        - name: Michael Shell
+    - name: Twentieth Century Fox
+      location: Springfield, USA
+      mark: 2
+      author:
+        - name: Homer Simpson
+          email: homer@thesimpsons.com
+    - name: Starfleet Academy
+      location: San Francisco, California 96678-2391
+      other: "Telephone: (800) 555--1212, Fax: (888) 555--1212"
+      mark: 3
+      author:
+        - name: Montgomery Scott
+    - name: Tyrell Inc.
+      location: 123 Replicant Street, Los Angeles, USA 90210--4321
+      mark: 4
+      author:
+        - name: Eldon Tyrell
+          email: eldon@starfleet-academy.star
+        - name: Roy Batty
+          email: roy@replicant.offworld
 
-\author{
-\begin{minipage}[t]{0.5\textwidth}
-\centering
-Rosa Janeth Alpala, Abraão D.\ C. Nascimento \\
-\textit{Departamento de Estatística} \\
-\textit{Universidade Federal de Pernambuco}\\
-Recife, PE, Brazil\\
-janeth.alpala@ufpe.br, abraao@de.ufpe.br 
-\end{minipage}%
-%\begin{minipage}[t]{0.3\textwidth}
-%\centering
-%2nd  Given Name Surname \\
-%\textit{Dept. name of organization } \\
-%\textit{Name of organization }\\
-%City, Country \\
-%Email address 
-%\end{minipage}%
-\begin{minipage}[t]{0.4\textwidth}
-\centering
-Alejandro C.\ Frery\\
-\textit{School of Mathematics and Statistics} \\
-\textit{Victoria University of Wellington}\\
-Wellington, New Zealand\\
-alejandro.frery@vuw.ac.nz
-\end{minipage}
-}
-
-\maketitle\begin{abstract}
+keywords: ["SAR", "entropy estimation", "non-parametric analysis", "order statistics"]
+abstract: |
   SAR Data are affected by speckle in a non-additive and non-Gaussian way.
@@
   Given the uncertainty of the underlying distribution, and the negative impact that using an inadequate model has on maximum likelihood estimation, we employ a non-parametric approach to estimate entropy under the fully-developed speckle hypothesis.
-\end{abstract}
 
-\begin{IEEEkeywords}
-SAR, entropy estimation, non-parametric analysis, order statistics
-\end{IEEEkeywords}
+# use some specific Tex packages if needed. 
+# with_ifpdf: true
+# with_cite: true
+# amsmath need to be true to use with bookdown for referencing equations.
+with_amsmath: true
+# with_algorithmic: true
+# with_array: true
+# with_dblfloatfix: true
 
-\section{Introduction}\label{sec_01}
+header-includes:
+   - \usepackage[english]{babel}
+   - \usepackage{bm,bbm}
+   - \usepackage{siunitx}
+   - \usepackage{graphicx}
+   - \usepackage{url}
+   - \usepackage[T1]{fontenc}
+   - \usepackage{booktabs}
+   - \usepackage{color}
+
+bibliography: ["mybibfile.bib"]
+output: rticles::ieee_article
+#citation_sorting: none   ## used as sorting option of the biblatex package (if selected)
+---
+
+```{r Setup, echo=FALSE}
+library(ggplot2)
+library(ggthemes)
+
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+          )
+```
+
+# Introduction
 
@@
 
-\section{BACKGROUND}\label{sec_02}
+# Background
 
-\subsection{Statistical modeling for Intensity SAR data}
+## Statistical modeling of Intensity SAR data
 
@@
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
-
 \begin{align}
@@
 Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ is
-{\small % o \footnotesize
-\begin{align}
-		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{(-\mu(\alpha+1))^{\alpha}\Gamma(-\alpha)\Gamma(L)}\frac{z^{L-1}}{(-\mu(\alpha+1)+Lz)^{L-\alpha}}.\label{E:gi02}
-\end{align}
-}
+\begin{multline}
+		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
+\end{multline}
 
-\subsection{Parametric \& Non-Parametric Shannon Entropy}
+## Parametric \& Non-Parametric Shannon Entropy
 
@@
 Using~\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$ in~\eqref{E:gamma1} and $\mathcal{G}_I^0$ in~\eqref{E:gi02} based on~\cite{Cassetti2022, A.Ferreira2020}:
-%{\small % o \footnotesize
-\begin{align}
-H_{\Gamma_{\text{SAR}}}(L, \mu) &=   L -\log(L/\mu)+\log\Gamma(L)+(1-L)\psi^{(0)}(L), \label{E:E-gamma}\\
-H_{\mathcal{G}_I^0}(\mu, \alpha, L) &= -\log(\alpha)+\log(\mu)+\log(1+\alpha)\nonumber \\
-&\quad -(1-\alpha)\psi^{(0)}(-\alpha) +\log(-\alpha)-\log(L) \nonumber \\
-&\quad + (L-\alpha)\psi^{(0)}(L-\alpha) +\log\left(\mathcal{B}(L,-\alpha)\right)\nonumber \\
-&\quad  + (1-L)\psi^{(0)}(L), \label{E:E-GIO}
-\end{align}
+\begin{multline}
+\label{E:E-gamma}
+H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
+\end{multline}
+\begin{multline}
+\label{E:E-GIO}
+H_{\mathcal{G}_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
+-\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
+-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L
+\end{multline}
 where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.
-
-%-------------------------------------------------------------------------------------------------------------
-
-%\section{Nonparametric entropy estimation}
 
@@
 The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.
-\section{Hypothesis testing based on non-parametric entropy}
 
-General asymptotic results for functions of spacings are detailed in~\cite{Khashimov1990}, while Van Es~\cite{Bert1992} has developed a correction for the case of Shannon entropy.
-Following the work of these authors, the next result applies:
+# Hypothesis tests
 
-\begin{lemma}
-Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
-Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
-$$
-\sqrt{n}\,\Big(\widehat{H}_{\text{VE}}+\int_{-\infty}^\infty f(z)\log f(z) \mathrm{d}z\Big)
-\xrightarrow[]{\mathcal{D}}
-\mathcal{N}(0,\operatorname{Var}(\log f(Z))),
-$$
-where $o(\cdot)$ represents the little-o and $\widehat{H}_{\text{VE}}$ is defined in expression~\eqref{E:VanEs}.
+# Results
 
-\end{lemma}
+This is an example of how to produce a plot in an RMarkdown reproducible paper.
 
-Let us consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
-%\begin{enumerate}[label=(\roman*)]
-  %\item $\mathcal{H}_1:T_{\mathcal{D}}\neq D_0,$
-  %\item $\mathcal{H}_1:T_{\mathcal{D}}> D_0,$
-  %\item $\mathcal{H}_1:T_{\mathcal{D}}< D_0.$
-%\end{enumerate}
-$$
-\text{(i)}\, \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \, \, \text{(ii)}\, \mathcal{H}_1:T_{\mathcal{D}}> D_0, \, \, \text{or}\, \,  \text{(iii)}\, \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
-$$
+First, you define the functions, or you load them from a library.
 
-For this purpose, we can use the test statistics:
-$$
-Z_{m,n} = \frac{\sqrt{n}(\widehat{H}_{\text{VE}}-D_0)}{\sqrt{\operatorname{Var}(\log f(Z))}},
-$$
-So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+```{r Functions, echo=FALSE}
+myfunction <- function(x){
+  return(x^2)
+}
+```
 
-The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
-\begin{multline*}
-\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
-\end{multline*}
-for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
+Then, you produce and display the plot.
+```{r MyFirstPlot, echo=FALSE, out.width="100%", fig.cap="My first function in a reproducible RMardown document"}
+x <- seq(-3, 3, length.out=500)
+y <- myfunction(x)
 
-\section{Results}
+df <- data.frame(x, y)
 
-We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases.
-%This indicates that the data appear to match the fully developed speckle hypothesis.
+ggplot(df, aes(x=x, y=y)) +
+  geom_line() +
+  xlab(expression(italic(x))) +
+  ylab(expression(italic(y))) 
+```
 
-We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
-We performed experiments to observe convergence under different scenarios, where each employed different sample sizes, i.e., $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
+# Conclusions
 
-For each sample size, we performed $10.000$ samples. Fig. \ref{F4} shows convergence of mean non-parametric entropies, for $\mu=3$ and $L=2$.
+<!-- An example of a floating figure using the graphicx package.
+Note that \label must occur AFTER (or within) \caption.
+For figures, \caption should occur after the \includegraphics.
+Note that IEEEtran v1.7 and later has special internal code that
+is designed to preserve the operation of \label within \caption
+even when the captionsoff option is in effect. However, because
+of issues like this, it may be the safest practice to put all your
+\label just after \caption rather than within \caption{}.
 
-%mu <- 3
-%L <- 2
-%alpha <- -5
-%
-%r <- 10000
-%n_values <- c(9, 25, 49, 81, 121, 500, 1000, 5000, 10000 ) 
-\begin{figure}[H] 
+Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+option should be used if it is desired that the figures are to be
+displayed while in draft mode.
+
+\begin{figure}[!t]
 \centering
-	\includegraphics[scale=0.5]{../../../Figures/PDF/mean_entropies1}\vspace{-1.5mm} 
-	\caption{Convergence of mean non-parametric entropies.}
-	\label{F4}
+\includegraphics[width=2.5in]{myfigure}
+where an .eps filename suffix will be assumed under latex, 
+and a .pdf suffix will be assumed for pdflatex; or what has been declared
+via \DeclareGraphicsExtensions.
+\caption{Simulation results for the network.}
+\label{fig_sim}
 \end{figure}
-\begin{figure}[H] 
+
+Note that the IEEE typically puts floats only at the top, even when this
+results in a large percentage of a column being occupied by floats.
+
+An example of a double column floating figure using two subfigures.
+(The subfig.sty package must be loaded for this to work.)
+The subfigure \label commands are set within each subfloat command,
+and the \label for the overall figure must come after \caption.
+\hfil is used as a separator to get equal spacing.
+Watch out that the combined width of all the subfigures on a 
+line do not exceed the text width or a line break will occur.
+
+\begin{figure*}[!t]
 \centering
-	\includegraphics[scale=0.5]{../../../Figures/PDF/histo1}\vspace{-1.5mm} 
-	\caption{Histogram of entropies.}
-	\label{F5}
-\end{figure}
-\section{Conclusion}\label{sec_09}
+\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
+\label{fig_first_case}}
+\hfil
+\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
+\label{fig_second_case}}
+\caption{Simulation results for the network.}
+\label{fig_sim}
+\end{figure*}
 
-In this article,
+Note that often IEEE papers with subfigures do not employ subfigure
+captions (using the optional argument to \subfloat[]), but instead will
+reference/describe all of them (a), (b), etc., within the main caption.
+Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
+labels, the optional argument to \subfloat must be present. If a
+subcaption is not desired, just leave its contents blank,
+e.g., \subfloat[].
 
-\bibliographystyle{IEEEtran}
-%\bibliography{strings,refs}
+An example of a floating table. Note that, for IEEE style tables, the
+\caption command should come BEFORE the table and, given that table
+captions serve much like titles, are usually capitalized except for words
+such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
+and up, which are usually not capitalized unless they are the first or
+last word of the caption. Table text will default to \footnotesize as
+the IEEE normally uses this smaller font for tables.
+The \label must come after \caption as always.
 
-\bibliography{../../Common/references}\end{document}
+\begin{table}[!t]
+% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.3}
+if using array.sty, it might be a good idea to tweak the value of
+\extrarowheight as needed to properly center the text within the cells
+\caption{An Example of a Table}
+\label{table_example}
+\centering
+% Some packages, such as MDW tools, offer better commands for making tables
+% than the plain LaTeX2e tabular which is used here.
+\begin{tabular}{|c||c|}
+\hline
+One & Two\\
+\hline
+Three & Four\\
+\hline
+\end{tabular}
+\end{table}
+
+Note that the IEEE does not put floats in the very first column
+- or typically anywhere on the first page for that matter. Also,
+in-text middle ("here") positioning is typically not used, but it
+is allowed and encouraged for Computer Society conferences (but
+not Computer Society journals). Most IEEE journals/conferences use
+top floats exclusively. 
+Note that, LaTeX2e, unlike IEEE journals/conferences, places
+footnotes above bottom floats. This can be corrected via the
+\fnbelowfloat command of the stfloats package. -->
+
+# Conclusion
+
+The conclusion goes here.
+
+<!-- conference papers do not normally have an appendix -->
+
+# Acknowledgment {#acknowledgment}
+
+The authors would like to thank...
+
+# Bibliography styles
+
+Here are two sample references: @Feynman1963118 [@Dirac1953888].
+
+\newpage
+# References {#references .numbered}

### 2023-10-21 Code/R/RMarkdown/EntropyPlots.Rmd
paper update

@@
 date: "2023-10-16"
-output: pdf_document
+output: html_document
 #html_document
@@
 
-#open3d()
+open3d()
 
-#persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")
+persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")
 
 #-----
-# mu <- seq(1, 10, length.out=200)
-# alpha <- seq(-2, -20, length.out=200)
-# 
-# 
-# entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
-# entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
-# entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
-# entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
-# entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
-# 
-# 
-# fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
-# 
-# fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
-# fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
-# fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
-# fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
-# fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
-# 
-# 
-# fig <- fig %>% layout(
-#   scene = list(
-#     xaxis = list(title = "alpha"),
-#     yaxis = list(title = "mu"),
-#     zaxis = list(title = "Entropy")
-#   )
-# )
-# 
-# fig
+mu <- seq(1, 10, length.out=200)
+alpha <- seq(-2, -20, length.out=200)
+
+entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
+entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
+entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
+entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
+entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
+
+fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
+
+fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
+fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
+fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
+fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
+fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
+
+fig <- fig %>% layout(
+  scene = list(
+    xaxis = list(title = "alpha"),
+    yaxis = list(title = "mu"),
+    zaxis = list(title = "Entropy")
+  )
+)
+
+fig
 

### 2023-10-21 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
paper update

--- 2023-10-18 Code/R/RMarkdown/The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
 # use some specific Tex packages if needed. 
-# with_ifpdf: true
-# with_cite: true
+#with_ifpdf: true
+#with_cite: true
 # amsmath need to be true to use with bookdown for referencing equations.
@@
 
+# header-includes:
+#    - \usepackage[english]{babel}
+#    - \usepackage{bm,bbm}
+#    - \usepackage{siunitx}
+#    - \usepackage{graphicx}
+#    - \usepackage{url}
+#    - \usepackage[T1]{fontenc}
+#    - \usepackage{booktabs}
+#    - \usepackage{color}
+#    - \usepackage{cite}
+
 header-includes:
@@
    - \usepackage{bm,bbm}
+   - \usepackage{mathrsfs}
    - \usepackage{siunitx}
@@
    - \usepackage[T1]{fontenc}
+   - \usepackage{polski}
    - \usepackage{booktabs}
    - \usepackage{color}
+   - \usepackage{mathtools}
 
-bibliography: ["mybibfile.bib"]
+#bibliography: ../../Common/references.bib
+bibliography:  ../../Common/references.bib
+csl: ieee.csl
 output: rticles::ieee_article
+fig_caption: yes
+
 #citation_sorting: none   ## used as sorting option of the biblatex package (if selected)
@@
 
-```{r Setup, echo=FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 library(ggplot2)
 library(ggthemes)
+library(reshape2)
+library(plotly)
+library(knitr)
+library(rgl)
+library(gtools)
+library(stats4)
+library(rmutil)
+library(gsl)
+library(invgamma)
+```
 
@@
 
+\newtheorem{lemma}{Lemma}
+
 # Introduction
@@
 Entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
-Shannon introduced it for a random variables in 1948~\cite{Shannon1948} as a measure of information and uncertainty. 
-In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity~\cite{Wieczorkowski1999}.
+Shannon introduced it for a random variables in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty. 
+In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;[@Wieczorkowski1999].
 
@@
 The article is structured as follows: 
-Section~\ref{sec_02} describes
+Section&nbsp;\ref{sec:2} describes
 
@@
 
-## Statistical modeling of Intensity SAR data
+## Statistical modeling of Intensity SAR data {#sec:2}
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions~\cite{Frery1997}. 
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
 The first is suitable for fully developed speckle and can also be considered a limiting case within the $\mathcal{G}_I^0$ distribution.
-Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics~\cite{Cassetti2022}.
+Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
@@
 \end{align}
-where, in~\eqref{E:gamma1} $\mu > 0$ is the mean; in~\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.
+where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.
 
@@
 
-Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$~\cite{Nascimento2010}.
-In this way, we compute the expected value $\mu$ using the expression in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
+Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;[@Nascimento2010].
+In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
 \begin{align*}
@@
 
-Using~\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$ in~\eqref{E:gamma1} and $\mathcal{G}_I^0$ in~\eqref{E:gi02} based on~\cite{Cassetti2022, A.Ferreira2020}:
+Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on&nbsp;[@Cassetti2022, @Ferreira2020]:
 \begin{multline}
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including~\cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.
+The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;[@vasicek1976test, @Bert1992, @Wieczorkowski1999, @correa1995new], who proposed estimators based on spacings.
 
-Vasicek \cite{vasicek1976test}, used $f(z)=p$  to express $ H(Z)$ as
+Vasicek&nbsp;[@vasicek1976test], used $f(z)=p$  to express $ H(Z)$ as
 \begin{equation*}
@@
 \end{equation*}
-where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics~\cite{AlOmari2019}.
+where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics&nbsp;[@AlOmari2019].
 
@@
 
-Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es~\cite{Bert1992}, who proposed a new estimator of entropy given by:
+Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es&nbsp;[@Bert1992], who proposed a new estimator of entropy given by:
 \begin{multline}
@@
 
-Van Es proved that, under general conditions,~\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
+Van Es proved that, under general conditions,\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
 The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.
 
-# Hypothesis tests
+# Hypothesis testing based on non-parametric entropy
+General asymptotic results for functions of spacings are detailed in&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} has developed a correction for the case of Shannon entropy.
+Following the work of these authors, the next result applies:
+
+\begin{lemma}
+Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
+Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
+\begin{equation}
+\sqrt{n}\,\Big(\widehat{H}_{\text{VE}}+\int_{-\infty}^\infty f(z)\log f(z) \mathrm{d}z\Big)
+\xrightarrow[]{\mathcal{D}}
+\mathcal{N}(0,\operatorname{Var}(\log f(Z))),
+\end{equation}
+where $o(\cdot)$ represents the little-o and $\widehat{H}_{\text{VE}}$ is defined in expression \eqref{E:VanEs}.
+
+\end{lemma}
+
+Let us consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
+
+\begin{equation}
+\text{(i)}\, \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \, \, \text{(ii)}\, \mathcal{H}_1:T_{\mathcal{D}}> D_0, \, \, \text{or}\, \,  \text{(iii)}\, \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
+\end{equation}
+
+For this purpose, we can use the test statistics:
+\begin{equation}
+Z_{m,n} = \frac{\sqrt{n}(\widehat{H}_{\text{VE}}-D_0)}{\sqrt{\operatorname{Var}(\log f(Z))}},
+\end{equation}
+So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+
+The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
+\begin{multline*}
+\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
+\end{multline*}
+for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
 
@@
 
-This is an example of how to produce a plot in an RMarkdown reproducible paper.
+We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases.
+%This indicates that the data appear to match the fully developed speckle hypothesis.
 
-First, you define the functions, or you load them from a library.
+We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
+We performed experiments to observe convergence under different scenarios, where each employed different sample sizes, i.e., $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
 
-```{r Functions, echo=FALSE}
-myfunction <- function(x){
-  return(x^2)
+For each sample size, we performed $10.000$ samples. Fig. \ref{F4} shows convergence of mean non-parametric entropies, for $\mu=3$ and $L=2$.
+
+In Fig. \ref{fig:PlotGammaSAR} We  see how the Shannon entropy of the Gamma-SAR model varies.
+
+```{r FunctionsDefinitions, echo=FALSE}
+entropy_gamma_sar <- function(L, mu) {
+
+    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
+
+}
+
+entropy_gI0 <- function(mu, alpha, L) {
+
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+
+  entropy <- term1 + term2 
+  return(entropy)
 }
@@
 
-Then, you produce and display the plot.
-```{r MyFirstPlot, echo=FALSE, out.width="100%", fig.cap="My first function in a reproducible RMardown document"}
-x <- seq(-3, 3, length.out=500)
-y <- myfunction(x)
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation results of Entropy for Gamma SAR"}
+mu <- seq(.1, 10, length.out=500)
 
-df <- data.frame(x, y)
+EntropyL1 <- entropy_gamma_sar(L=1, mu)
+EntropyL3 <- entropy_gamma_sar(L=3, mu)
+EntropyL8 <- entropy_gamma_sar(L=8, mu)
+EntropyL12 <- entropy_gamma_sar(L=12, mu)
+EntropyL100 <- entropy_gamma_sar(L=100, mu)
 
-ggplot(df, aes(x=x, y=y)) +
+muEntropy <- data.frame(
+  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
+)
+
+muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")
+
+ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
   geom_line() +
-  xlab(expression(italic(x))) +
-  ylab(expression(italic(y))) 
+  theme_pander()
+
 ```
-
-# Conclusions
-
-<!-- An example of a floating figure using the graphicx package.
-Note that \label must occur AFTER (or within) \caption.
-For figures, \caption should occur after the \includegraphics.
-Note that IEEEtran v1.7 and later has special internal code that
-is designed to preserve the operation of \label within \caption
-even when the captionsoff option is in effect. However, because
-of issues like this, it may be the safest practice to put all your
-\label just after \caption rather than within \caption{}.
-
-Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-option should be used if it is desired that the figures are to be
-displayed while in draft mode.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=2.5in]{myfigure}
-where an .eps filename suffix will be assumed under latex, 
-and a .pdf suffix will be assumed for pdflatex; or what has been declared
-via \DeclareGraphicsExtensions.
-\caption{Simulation results for the network.}
-\label{fig_sim}
-\end{figure}
-
-Note that the IEEE typically puts floats only at the top, even when this
-results in a large percentage of a column being occupied by floats.
-
-An example of a double column floating figure using two subfigures.
-(The subfig.sty package must be loaded for this to work.)
-The subfigure \label commands are set within each subfloat command,
-and the \label for the overall figure must come after \caption.
-\hfil is used as a separator to get equal spacing.
-Watch out that the combined width of all the subfigures on a 
-line do not exceed the text width or a line break will occur.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-\label{fig_first_case}}
-\hfil
-\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-\label{fig_second_case}}
-\caption{Simulation results for the network.}
-\label{fig_sim}
-\end{figure*}
-
-Note that often IEEE papers with subfigures do not employ subfigure
-captions (using the optional argument to \subfloat[]), but instead will
-reference/describe all of them (a), (b), etc., within the main caption.
-Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-labels, the optional argument to \subfloat must be present. If a
-subcaption is not desired, just leave its contents blank,
-e.g., \subfloat[].
-
-An example of a floating table. Note that, for IEEE style tables, the
-\caption command should come BEFORE the table and, given that table
-captions serve much like titles, are usually capitalized except for words
-such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-and up, which are usually not capitalized unless they are the first or
-last word of the caption. Table text will default to \footnotesize as
-the IEEE normally uses this smaller font for tables.
-The \label must come after \caption as always.
-
-\begin{table}[!t]
-% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.3}
-if using array.sty, it might be a good idea to tweak the value of
-\extrarowheight as needed to properly center the text within the cells
-\caption{An Example of a Table}
-\label{table_example}
-\centering
-% Some packages, such as MDW tools, offer better commands for making tables
-% than the plain LaTeX2e tabular which is used here.
-\begin{tabular}{|c||c|}
-\hline
-One & Two\\
-\hline
-Three & Four\\
-\hline
-\end{tabular}
-\end{table}
-
-Note that the IEEE does not put floats in the very first column
-- or typically anywhere on the first page for that matter. Also,
-in-text middle ("here") positioning is typically not used, but it
-is allowed and encouraged for Computer Society conferences (but
-not Computer Society journals). Most IEEE journals/conferences use
-top floats exclusively. 
-Note that, LaTeX2e, unlike IEEE journals/conferences, places
-footnotes above bottom floats. This can be corrected via the
-\fnbelowfloat command of the stfloats package. -->
 
@@
 
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
-
 \newpage

### 2023-10-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Sunday 22 October 2023 at home

@@
 library(knitr)
-library(rgl)
+# library(rgl)
 library(gtools)

### 2023-10-23 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
update R codes

--- 2023-10-21 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
   ## one column per author - using only the institution field
-  # author-columnar: true # uncomment this line to use
+  author-columnar: true # uncomment this line to use
 
-  ## one column per institution - using only the institution field
-  # institution-columnar: true # uncomment this line to use
-
-  ## one column wide author/affiliation fields - using author or author_multiline and institution for mark
-  wide: true # uncomment this line to use
-
-  ## Author mode: End ----
-
-  ## A custom author ordering field that breaks institution grouping (used with `wide: true`)
-  ## Authors cited in institution field are ignored when this author field exists
-  ## Comment / Uncomment below
-  author:   
-   - name: Eldon Tyrell
-     mark: [2, 3]
-     email: eldon@starfleet-academy.star
-   - name: Michael Shell
-     mark: 1
-   - name: Roy Batty
-     mark: 4
-     email: roy@replicant.offworld
-
-  ## Put authors in a given order, with multiline possibility (used with `wide: true` if `authors` above unset)
-  ## Authors cited in institution are ignored if exists
-  ## Comment / Uncomment below
-  #author_multiline: 
-  #  - line:         ## Create a new author line
-  #    - name: Michael Shell
-  #      mark: 1
-  #    - name: Homer Simpson
-  #      mark: 2
-  #      email: homer@thesimsons.com
-  #    - name: Roy Batty
-  #      mark: 4
-  #      email: roy@replicant.offworld
-  #  - line:         ## Create a second author line
-  #    - name: Montgomery Scott
-  #      mark: 3
-  #    - name: Eldon Tyrell
-  #      mark: 4
-
-  ## Define institution, and also authors used when `author-columnar: true` or `institution-columnar: true`
   institution:
-    - name: Georgia Institute of Technology
-      department: School of Electrical and Computer Engineering
-      location: Atlanta, Georgia 30332--0250
-      email: ece@datech.edu # if unset, authors' email will be used
+    - name: Universidade Federal de Pernambuco
+      department: Departamento de Estatística
+      location: Recife, PE, Brazil
+      email: janeth.alpala@ufpe.br, abraao@de.ufpe.br 
       mark: 1
       author:
-        - name: Michael Shell
-    - name: Twentieth Century Fox
-      location: Springfield, USA
+      - name: Rosa Janeth Alpala, Abraão D. C. Nascimento
+
+    - name: Victoria University of Wellington
+      department: School of Mathematics and Statistics
+      location: Wellington, New Zealand
+      email: alejandro.frery@vuw.ac.nz
       mark: 2
       author:
-        - name: Homer Simpson
-          email: homer@thesimpsons.com
-    - name: Starfleet Academy
-      location: San Francisco, California 96678-2391
-      other: "Telephone: (800) 555--1212, Fax: (888) 555--1212"
-      mark: 3
-      author:
-        - name: Montgomery Scott
-    - name: Tyrell Inc.
-      location: 123 Replicant Street, Los Angeles, USA 90210--4321
-      mark: 4
-      author:
-        - name: Eldon Tyrell
-          email: eldon@starfleet-academy.star
-        - name: Roy Batty
-          email: roy@replicant.offworld
+        - name: Alejandro C. Frery
 
@@
 
-# header-includes:
-#    - \usepackage[english]{babel}
-#    - \usepackage{bm,bbm}
-#    - \usepackage{siunitx}
-#    - \usepackage{graphicx}
-#    - \usepackage{url}
-#    - \usepackage[T1]{fontenc}
-#    - \usepackage{booktabs}
-#    - \usepackage{color}
-#    - \usepackage{cite}
-
 header-includes:
@@
    - \usepackage{mathtools}
+   - \usepackage[utf8]{inputenc}
 
-#bibliography: ../../Common/references.bib
 bibliography:  ../../Common/references.bib
@@
 output: rticles::ieee_article
-fig_caption: yes
 
@@
 library(invgamma)
-```
 
@@
 \newtheorem{lemma}{Lemma}
+\renewcommand{\thesection}{\Alph{section}}
+# Introduction {#sec:Introduction}
 
-# Introduction
+Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;[@Cassetti2022].
+However, the utility of SAR data depends on a thorough understanding of the statistical properties governing its inherent speckle noise.
+This complex interaction, which defies simplistic assumptions of additivity and Gaussianity, requires robust statistical models that can accurately characterize SAR data for efficient processing and analysis.
 
-Remote sensing data from sensors, in particular synthetic aperture radar (SAR), play a key role in understanding the dynamics of the environment, enabling predictive capabilities and facilitating the early detection of disasters.
-Unlike optical spectrum observations, microwave remote sensing sensors, operating in the microwave band, offer significant advantages, including reduced sensitivity to adverse atmospheric conditions and their self-illuminating properties.
+Among these models, the $\mathcal{G}^0$ distribution stands out as a powerful framework for modeling SAR data.
+Notably, this distribution encompasses the well-known Gamma distribution as a special case, particularly under the assumption of fully developed speckle.
+The interplay between these two distributions is apparent, with the Gamma distribution representing a limiting case of the more general $\mathcal{G}^0$ model.
 
-Entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
+On the other hand, entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
 Shannon introduced it for a random variables in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty. 
@@
 
-Estimating entropy presents practical challenges, especially when the true probability density function (pdf) is unknown.
-In such cases, nonparametric methods are employed for entropy estimation. 
-In the parametric approach, the form of the pdf is assumed to be known, and its parameters are inferred from the available samples. 
-Conversely, nonparametric methods, like histogram or kernel density estimators, do not make such assumptions. 
-They estimate the pdf using these techniques and then calculate entropy through numerical or Monte Carlo integration. 
-Other nonparametric approaches involve spacing methods, which allow the estimation of the entropy of a random variable with an unknown distribution function when independent and identically distributed (i.i.d.) observations of the random variable are available.
+Estimating entropy faces practical challenges, particularly when the true probability density function (pdf) is unknown.
+Nonparametric methods are utilized in such cases, avoiding the assumption of a known pdf form.
+Instead, techniques like histograms or kernel density estimators are employed to estimate the pdf directly, followed by entropy calculation using numerical or Monte Carlo integration&nbsp;[@Lombardi2016].
+An alternative nonparametric approach involves spacing methods, facilitating entropy estimation&nbsp;[@Zamanzade2012].
+This non-parametric strategy offers flexibility to address a wide range of data distributions without imposing specific parametric constraints.
 
-%In this paper we consider an estimator based on spacings.
+In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data.
+The first stage of our methodology is to test the hypothesis that the data are completely speckled.
+If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.
 
-This study is dedicated to the analysis of SAR intensity data, which frequently contends with the presence of speckle noise. 
-Speckle noise can significantly complicate the analysis of these data, necessitating the use of specific models and techniques for information extraction. 
-We adopt the $\mathcal G^0$ distribution family as a suitable model for describing SAR intensity data, as it effectively characterizes areas with varying degrees of texture.
+The significance of selecting an appropriate statistical model and estimation technique is well recognized.
+In order to address uncertainties in the data distribution, we employ a non-parametric approach.
+Specifically, we focus on the entropy estimation considering estimators based on spacing.
 
-The article is structured as follows: 
-Section&nbsp;\ref{sec:2} describes
+The article is structured as follows: In Section&nbsp;\ref{sec:Background}, we provide an overview of statistical modeling for Intensity SAR data and the estimation of both parametric and non-parametric Shannon entropy.
 
-# Background
+# Background {#sec:Background}
 
-## Statistical modeling of Intensity SAR data {#sec:2}
+## Statistical modeling of Intensity SAR data
 
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;[@vasicek1976test, @Bert1992, @Wieczorkowski1999, @correa1995new], who proposed estimators based on spacings.
+The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;[@vasicek1976test; @Bert1992; @Wieczorkowski1999; @correa1995new], who proposed estimators based on spacings.
 
@@
 # Hypothesis testing based on non-parametric entropy
-General asymptotic results for functions of spacings are detailed in&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} has developed a correction for the case of Shannon entropy.
+General asymptotic results for functions of spacings are detailed in&nbsp;[@Khashimov1990], while VanEs&nbsp;[@Bert1992] has developed a correction for the case of Shannon entropy.
 Following the work of these authors, the next result applies:
@@
 We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases.
-%This indicates that the data appear to match the fully developed speckle hypothesis.
 
@@
 
-For each sample size, we performed $10.000$ samples. Fig. \ref{F4} shows convergence of mean non-parametric entropies, for $\mu=3$ and $L=2$.
+<!-- #For each sample size, we performed $1.000$ samples. Fig.&nbsp;\ref{fig:convergence} shows convergence of mean non-parametric entropies for $\mu=3$ and $L=2$. -->
 
-In Fig. \ref{fig:PlotGammaSAR} We  see how the Shannon entropy of the Gamma-SAR model varies.
+In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
 
@@
 
-```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation results of Entropy for Gamma SAR"}
-mu <- seq(.1, 10, length.out=500)
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+L <- c(1, 3, 8, 12, 100)
 
-EntropyL1 <- entropy_gamma_sar(L=1, mu)
-EntropyL3 <- entropy_gamma_sar(L=3, mu)
-EntropyL8 <- entropy_gamma_sar(L=8, mu)
-EntropyL12 <- entropy_gamma_sar(L=12, mu)
-EntropyL100 <- entropy_gamma_sar(L=100, mu)
+L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")
 
-muEntropy <- data.frame(
-  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
-)
+mu <- seq(0.1, 10, length.out = 500)
 
-muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")
+entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
 
-ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
+muEntropy <- data.frame(mu, entropies)
+
+muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
   geom_line() +
-  theme_pander()
+  theme_minimal() +
+  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
+  labs(col = "Looks") +
+  xlab(expression(paste(mu)))
 
 ```
+
+Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $\mathcal{G}_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
+
+```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
+knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
+```
+As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the GI0 distribution.
+We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
 
@@
 
-# Bibliography styles
-
-\newpage
 # References {#references .numbered}

### 2023-10-23 Code/R/MainFunctions/entropy_gI0.R

@@ -1,0 +1,21 @@
+# Function for Entropy Calculation of the gI0 Distribution
+# Description: This function computes the entropy of the GI0 distribution
+# based on provided parameters mu, alpha, and L.
+#
+# Input:
+#   - mu: Mean parameter of the distribution.
+#   - alpha: Shape parameter.
+#   - L: Shape parameter of the distribution.
+#
+# Output:
+#   - Entropy value of the gI0 distribution.
+#
+
+entropy_gI0 <- function(mu, alpha, L) {
+  
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+  
+  entropy <- term1 + term2 
+  return(entropy)
+}

### 2023-10-23 Code/R/PlottingFunctions/gamma_sar_L3.R

@@ -1,0 +1,52 @@
+# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
+# It uses non-parametric estimators to calculate the sample mean and standard deviation 
+# of the entropy for various sample sizes.
+# The code also includes error bars based on the standard deviation for visualization.
+
+
+
+rm(list = ls())
+library(ggplot2)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+set.seed(1234567890, kind="Mersenne-Twister")
+
+
+# Define sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
+R <- 10000
+mu <- 1
+L <- 3
+
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for(ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
+}
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Mean", "Std")
+output$SampleSize <- sample_sizes
+
+#plot
+ggplot(output, aes(x=SampleSize, y=Mean)) +
+  geom_hline(yintercept = entropy_gamma_sar(3, 1)) +
+  geom_line() +
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
+  xlab("Sample Size") +
+  scale_x_log10(breaks=output$SampleSize) +
+  ylab("Mean Non-parametric Entropy")
+
+# Save the plot as a PDF file
+ggsave("myplot.pdf")
+

### 2023-10-23 Code/R/PlottingFunctions/gamma_sar_L8.R

@@ -1,0 +1,53 @@
+# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
+# It uses non-parametric estimators to calculate the sample mean and standard deviation 
+# of the entropy for various sample sizes.
+# The code also includes error bars based on the standard deviation for visualization.
+
+# Clear the workspace and load necessary functions
+rm(list = ls())
+library(ggplot2)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+# Define sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
+R <- 10000
+mu <- 1
+L <- 8
+
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for(ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
+}
+
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Mean", "Std")
+output$SampleSize <- sample_sizes
+
+
+#plot
+ggplot(output, aes(x=SampleSize, y=Mean)) +
+  geom_hline(yintercept = entropy_gamma_sar(8, 1)) +
+  geom_line() +
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
+  xlab("Sample Size") +
+  scale_x_log10(breaks=output$SampleSize) +
+  ylab("Mean Non-parametric Entropy")
+
+# Save the plot as a PDF file
+ggsave("myplot.pdf")
+

### 2023-10-23 Code/R/PlottingFunctions/gamma_sar_mu3_L3.R

@@ -1,0 +1,58 @@
+# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
+# It uses non-parametric estimators to calculate the sample mean and standard deviation 
+# of the entropy for various sample sizes.
+# The code also includes error bars based on the standard deviation for visualization.
+
+
+
+rm(list = ls())
+library(ggplot2)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+
+# Define sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
+R <- 10000
+mu <- 3
+L <- 3
+
+
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for(ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
+}
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Mean", "Std")
+output$SampleSize <- sample_sizes
+
+
+#plot
+ggplot(output, aes(x = SampleSize, y = Mean)) +
+  geom_hline(yintercept = entropy_gamma_sar(3, 3)) +
+  geom_line() +
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +  #comment this line
+  xlab("Sample Size") +
+  scale_x_log10(breaks = output$SampleSize) +
+  ylab("Mean Non-parametric Entropy")
+
+# Save the plot as a PDF file
+ggsave("myplot.pdf")
+
+
+

### 2023-10-23 Code/R/Programs/NonparametricEstimators.R

@@ -1,0 +1,38 @@
+# This code runs examples of the sample mean of the non-parametric...
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+sample_sizes <- c(9, 25, 121, 1000, 10000, 100000, 1000000)
+R <- 500
+mu <- 1
+L <- 1
+
+output <- NULL
+
+for(ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for(r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- van_es_estimator(sample)
+  }
+  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
+}
+
+output <- data.frame(output)
+names(output) <- c("Mean", "Std")
+
+output$SampleSize <- sample_sizes
+
+ggplot(output, aes(x=SampleSize, y=Mean)) +
+  geom_hline(yintercept = entropy_gamma_sar(1, 1)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  scale_x_log10(breaks=output$SampleSize) +
+  ylab("Mean Non-parametric Entropy")
+
+
+### Show curves for same mu=1 and L in 1, 3, 8, 12.
+### Add confidence intervals to each point based on the standard deviation
+### Save functions on a different file; use "standard R names"
+### Each function that produces a plot must be in a different file

### 2023-10-23 Code/R/Programs/plot3d_entropy.R

@@ -1,0 +1,46 @@
+
+rm(list = ls())
+library(plotly)
+
+entropy_gI0 <- function(mu, alpha, L) {
+  
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+  
+  entropy <- term1 + term2 
+  return(entropy)
+}
+
+
+mu <- seq(1, 10, length.out=200)
+alpha <- seq(-20, -2, length.out=200)
+
+
+entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
+entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
+entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
+entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
+entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
+
+
+fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
+
+fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
+fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
+fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
+fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
+fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
+
+
+fig <- fig %>% layout(
+  scene = list(
+    xaxis = list(title = "alpha"),
[…]

### 2023-10-23 Code/R/Programs/test1.R

@@ -1,0 +1,113 @@
+
+rm(list = ls())
+library(gtools)
+library(stats4)
+library(rmutil)
+library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+
+
+alpha <- -2
+mu <- 1
+L <- 1
+
+gam=-mu*(alpha+1)
+
+r <- 500
+n_values <- c(9, 25, 49, 81, 200,1000, 5000,  10000, 20000) 
+
+
+
+
+means_entropies <- c()
+means_entropies2 <- c()
+entropies2 <- c()
+
+for (n in n_values) {
+  entropies <- c()
+  entropies2 <- c()
+  for (i in 1:r) {
+    sample_data <- gamma_sar_sample(L, mu, n)
+    GI0_samples <- Z_samples(L, alpha, mu,  n)
+    Np_entropy_gamma <- van_es_estimator(sample_data)
+    NP_entropy_GI0 <- van_es_estimator(GI0_samples)
+    entropies <- c(entropies, Np_entropy_gamma)
+    entropies2 <- c(entropies2, NP_entropy_GI0)
+    log_gamma_sar<- log(dgamma(sample_data, shape = L, rate = L / mu))
+    #log_var <- var(log_sample_data)
+    
+  }
+  #Gamma SAR
+  mean_entropy <- mean(entropies)
+  means_entropies <- c(means_entropies, mean_entropy)
+  # GIO
+  mean_entropy2 <- mean(entropies2)
+  means_entropies2 <- c(means_entropies2, mean_entropy2)
+}
+
+
+# plot(n_values, means_entropies, type = "o", main = "Convergence of Mean Non-Parametric Entropies",
+     # xlab = "Sample Size (n)", ylab = "Mean Entropy")
+# grid()
+
+### Using ggplot2
+
+df.MeanGamma <- data.frame(n_values, means_entropies)
+ggplot(df.MeanGamma, aes(x=n_values, y=means_entropies)) +
+  geom_hline(yintercept = entropy_gamma_sar(1, 1)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  scale_x_continuous(breaks=n_values) +
+  ylab("Mean Non-parametric Entropy")
+  
+
[…]

### 2023-10-23 Code/R/plot3d_entropy.R

@@ -1,46 +1,0 @@
-
-rm(list = ls())
-library(plotly)
-
-entropy_gI0 <- function(mu, alpha, L) {
-  
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-  
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-
-mu <- seq(1, 10, length.out=200)
-alpha <- seq(-20, -2, length.out=200)
-
-
-entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
-entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
-entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
-entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
-entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
-
-
-fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
-
-fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
-fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
-fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
-fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
-fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
-
-
-fig <- fig %>% layout(
-  scene = list(
-    xaxis = list(title = "alpha"),
[…]

### 2023-10-23 Code/R/test1.R

@@ -1,164 +1,0 @@
-
-rm(list = ls())
-library(gtools)
-library(stats4)
-library(rmutil)
-library(gsl)
-library(invgamma)
-
-
-
-alpha <- -2
-mu <- 1
-L <- 1
-
-gam=-mu*(alpha+1)
-
-r <- 10000
-n_values <- c(9, 25, 49, 81, 200,1000, 5000,  10000) 
-
-
-# Functions
-# Entropy Gamma SAR
-entropy_gamma_sar <- function(L, mu) {
-  
-  return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
-  
-}
-
-# Entropy GI0
-entropy_gI0 <- function(mu, alpha, L) {
-  
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-  
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-
-# only second term of GI0
-second_term <- function(alpha, L) {
-  return(-L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha)))
-
-}
-
-
-#Samples Gamma SAR
-gamma_sar_sample <- function(L, mu, n) {
-  samples <- rgamma(n, shape = L, rate = L / mu)
-  return(samples)
-}
-
-
-#Samples GI0
-Z_samples <- function(L, alpha, mu,  n) {
-
-  X_samples <- rinvgamma(n, shape = -alpha, rate =mu*(-alpha-1))
-
-  Y_samples <- rgamma(n, shape = L, rate = L)
-  Z_samples <- X_samples * Y_samples
-  return(Z_samples)
-}
-
-
-
-# nonparametric estimator
-
-
-
-van_es_estimator <- function(data) {
-  n <- length(data)
-  m <- round(sqrt(n) + 0.5)  # m-spacing
-  data_sorted <- sort(data)
-  sum_term1 <- 0
-  sum_term2 <- 0
-  
-  for (i in 1:(n - m)) {
-    sum_term1 <- sum_term1 + log(((n + 1) / m) * (data_sorted[i + m] - data_sorted[i]))
-  }
-  
[…]

### 2023-10-25 Code/R/RMarkdown/EntropyPlots.Rmd
Update R code bias

--- 2023-10-16 Code/R/RMarkdown/EntropyPlots.Rmd
@@
 library(reshape2)
+library(plotly)
+library(knitr)
+#library(rgl)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+          )
 ```
@@
 
-  return(L + log(gamma(L)) + (1 - L) * digamma(L) - log(L / mu))
+    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
 
+}
+
+entropy_gI0 <- function(mu, alpha, L) {
+
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+
+  entropy <- term1 + term2 
+  return(entropy)
+}
+
+gamma_sar_sample <- function(L, mu, n) {
+  samples <- rgamma(n, shape = L, rate = L / mu)
+  return(samples)
+}
+
+van_es_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term1 <- 0
+  sum_term2 <- 0
+
+  for (i in 1:(n - m)) {
+    sum_term1 <- sum_term1 + log(((n + 1) / m) * (data_sorted[i + m] - data_sorted[i]))
+  }
+
+  for (k in m:n) {
+    sum_term2 <- sum_term2 + 1 / k
+  }
+
+  sum_term3 <- log(m / (n + 1))
+
+  return((sum_term1 / (n - m)) + sum_term2+ sum_term3)
+
+}
+vasicek_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m <- floor(n / 2)
+  data_sorted <- sort(data)
+  sum_term <- 0
+
+  for (i in 1:n) {
+    if (i <= m) {
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+
+    sum_term <- sum_term + log((n / (2 * m)) * diff_term)
+  }
+
+  return(sum_term / n)
+}
+correa_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)
+  X_sorted <- sort(data)
+  C_mn <- 0
+
+  for (i in 1:n) {
+    i_minus_m <- max(1, i - m)
+    i_plus_m <- min(n, i + m)
+
+    X_i <- X_sorted[i]
+    X_window <- X_sorted[i_minus_m:i_plus_m]
+    X_bar_i <- mean(X_window)
+
+    num <- sum((X_window - X_bar_i) * (i_minus_m:i_plus_m - i))
+    den <- n * sum((X_window - X_bar_i)^2)
+
+    if (den == 0) {
+      b_i <- 0
+    } else {
+      b_i <- num / den
+    }
+
+    if (b_i > 0) {
+      C_mn <- C_mn - log(b_i)
+    }
+  }
+
+  C_mn <- C_mn / n
+
+  return(C_mn)
+}
+ebrahimi_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term <- 0
+
+  for (i in 1:n) {
+    if (i <= m) {
+      ci <- 1 + (i - 1) / m
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      ci <- 1 + (n - i) / m
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      ci <- 2
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+
+    sum_term <- sum_term + log((n / (ci * m)) * diff_term)
+  }
+
+  return(sum_term / n)
+}
+noughabi_arghami_estimator <- function(data) {
+    n <- length(data)
+    m <- round(sqrt(n) + 0.5)  # m-spacing
+    data_sorted <- sort(data)
+    sum_term <- 0
+
+    for (i in 1:n) {
+      if (i <= m) {
+        ai <- 1
+        diff_term <- data_sorted[i + m] - data_sorted[1]
+      } else if (i >= n - m + 1) {
+        ai <- 1
+        diff_term <- data_sorted[n] - data_sorted[i - m]
+      } else {
+        ai <- 2
+        diff_term <- data_sorted[i + m] - data_sorted[i - m]
+      }
+
+      sum_term <- sum_term + log((n / (ai * m)) * diff_term)
+    }
+
+    return(sum_term / n)
+}
+al_omari_1_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term <- 0
+
+  for (i in 1:n) {
+    if (i <= m) {
+      omega_i <- 3/2
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      omega_i <- 3/2
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      omega_i <- 2
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+
+    sum_term <- sum_term + log((n / (omega_i * m)) * diff_term)
+  }
+
+  return(sum_term / n)
+}
+al_omari_2_estimator <- function(data) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # m-spacing
+  data_sorted <- sort(data)
+  sum_term <- 0
+
+  for (i in 1:n) {
+    if (i <= m) {
+      vi <- 1 + (i - 1) / m
+      diff_term <- data_sorted[i + m] - data_sorted[1]
+    } else if (i >= n - m + 1) {
+      vi <- 1 + (n - i) / (2 * m)
+      diff_term <- data_sorted[n] - data_sorted[i - m]
+    } else {
+      vi <- 2
+      diff_term <- data_sorted[i + m] - data_sorted[i - m]
+    }
+
+    sum_term <- sum_term + log((n / (vi * m)) * diff_term)
+  }
+
+  return(sum_term / n)
 }
@@
 
-```{r PlotGammaSAR, echo=FALSE}
-mu <- seq(.1, 10, length.out=500)
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+L <- c(1, 3, 8, 12, 100)
 
-EntropyL1 <- entropy_gamma_sar(L=1, mu)
-EntropyL3 <- entropy_gamma_sar(L=3, mu)
-EntropyL8 <- entropy_gamma_sar(L=8, mu)
-EntropyL12 <- entropy_gamma_sar(L=12, mu)
-EntropyL100 <- entropy_gamma_sar(L=100, mu)
+L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")
 
-muEntropy <- data.frame(
-  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
-)
+mu <- seq(0.1, 10, length.out = 500)
 
-muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")
+entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
 
-ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
+muEntropy <- data.frame(mu, entropies)
+
+muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
   geom_line() +
-  theme_pander()
+  theme_minimal() +
+  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
+  labs(col = "Looks") +
+  xlab(expression(paste(mu)))
 
@@
 The Shannon entropy of the GI0-SAR model is given by
+
 \begin{multline}
-H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) = -\ln(\alpha)+\ln(\mu)+\ln(1+\alpha)
- -(1-\alpha)\psi^{(0)}(-\alpha) +\ln(-\alpha)-\ln L_0
-+ (L_0-\alpha)\psi^{(0)}(L_0-\alpha) + \\
-\ln\mathcal{B}(L_0,-\alpha)
-  + (1-L_0)\psi^{(0)}(L_0), \label{E:E-GIO}
+\label{E:E-GIO}
+H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
+-\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
+-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L_0
 \end{multline}
+
+```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
+knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
+```
+
+# Non-Parametric Entropy Estimators
+
+In 1995 Correa suggested a modification of Vasicek's estimator.
+In estimation the density $f$ of $F$ in the interval $\left(X_{(i-m)}, X_{(i+m)}\right)$ he used a local linear model based on $2 m+1$ points: $F\left(X_{(j)}\right)=\alpha+\beta X_{(j)}+\varepsilon, j=m-i, \ldots, m+i$.
+This yields a following estimator
+\begin{equation}
+\widehat{H}_C(\mathbf{X})=-\frac{1}{n} \sum_{i=1}^n \ln \left(b_i\right),
+\end{equation}
+where
+$$
+\begin{gathered}
+b_i=\frac{\sum_{j=i-m}^{i+m}\left(X_{(j)}-\bar{X}_{(i)}\right)(j-i)}{n \cdot \sum_{j=i-m}^{i+m}\left(X_{(j)}-\bar{X}_{(i)}\right)^2}, \\
+\bar{X}_{(i)}=\frac{1}{2 m+1} \sum_{j=i-m}^{i+m} X_{(j)},
+\end{gathered}
+$$
+$m$ is a positive integer smaller than $\frac{n}{2}, X_{(i)}=X_{(1)}$ for $i<1$ and $X_{(i)}=X_{(n)}$ for $i>n$.
+
+Ebrahimi et al.
+(1994), adjusted the weights of Vasicek's estimator, in order to take into account the fact that the differences are truncated around the smallest and the largest data points.
+i.e.
+$X_{(i+m)}-X_{(i-m)}$ is replaced by $X_{(i+m)}-X_{(1)}$ when $i \leq m$ and $X_{(i+m)}-X_{(i-m)}$ is replaced by $X_{(n)}-X_{(i-m)}$ when $i \geq n-m+1$.
+Their estimator is given by
+\begin{equation}
+\widehat{H}_E(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
+\end{equation}
+where
+$$
+c_i=\left\{\begin{array}{lr}
+1+\frac{i-1}{m}, & 1 \leq i \leq m \\
+2, & m+1 \leq i \leq n-m, \\
+1+\frac{n-i}{m}, & n-m+1 \leq i \leq n
+\end{array}\right.
+$$
+
+Noughabi and Arghami suggested an entropy estimator given by
+
+\begin{equation}
+\widehat{H}_{NA}(\mathbf{X})=\frac{1}{n}(\mathbf{X}) \sum_{i=1}^n \log \left[\frac{n}{a_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
+\end{equation}
+where
+$$
+a_i=\left\{\begin{array}{lc}
+1, & 1 \leq i \leq m, \\
+2, & m+1 \leq i \leq n-m, \\
+1, & n-m+1 \leq i \leq n,
+\end{array}\right.
+$$
+and $X_{(i-m)}=X_{(1)}$ for $i \leq m$ and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.
+
+Al-Omari suggested the following estimators of entropy:
+
+\begin{equation}
+\widehat{H}_{\mathrm{AO}_1}(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right]
+\end{equation}
+where
+$$
+\omega_i= \begin{cases}3 / 2 & \text { if } 1 \leq i \leq m \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 3 / 2 & \text { if } n-m+1 \leq i \leq n,\end{cases}
+$$
+in which $X_{(i-m)}=X_{(1)}$ for $i \leq m$, and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.
+And
+\begin{equation}
+\widehat{H}_{\mathrm{AO}_2}(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{v_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right]
+\end{equation}
+where
+$$
+v_i= \begin{cases}1+(i-1) / m & \text { if } 1 \leq i \leq m \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 1+(n-i) / 2 m & \text { if } n-m+1 \leq i \leq n\end{cases}
+$$
+in which $X_{(i-m)}=X_{(1)}$ for $i \leq m$, and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.
+
+Fig.
+\ref{fig:PlotBias}, illustrate  the bias  of each estimator as a function of sample size.
+We observe that as the sample size n increases, the bias tends to zero, for some estimators, this means that the estimators are becoming more unbiased as the amount of data available increases, because they are getting closer to the value true of entropy.
+
+```{r PlotBias, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Bias, for $L= 1$, $\\mu=1$."}
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+R <- 1000
+mu <- 1
+L <- 1
+
+#  True entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)
+
+output <- data.frame(SampleSize = integer(0), Estimator = character(0), Bias = numeric(0))
+
+#List of estimator
+estimators <- list(
+  list(func = van_es_estimator, label = "Van Es"),
+  list(func = correa_estimator, label = "Correa"),
+  list(func = ebrahimi_estimator, label = "Ebrahimi"),
+  list(func = noughabi_arghami_estimator, label = "Noughabi Arghami"),
+  list(func = vasicek_estimator, label = "Vasicek"),
+  list(func = al_omari_1_estimator, label = "Al Omari 1"),
+  list(func = al_omari_2_estimator, label = "Al Omari 2")
+)
+
+for (estimator in estimators) {
+  for (ssize in sample_sizes) {
+    v.nonparametric.entropy <- numeric(R)
+    for (r in 1:R) {
+      sample <- gamma_sar_sample(L, mu, ssize)
+      v.nonparametric.entropy[r] <- estimator$func(sample)
+    }
+
+    # Calculate the bias 
+    bias <- mean(v.nonparametric.entropy) - true_entropy
+
+    output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator$label, Bias = bias))
+  }
+}
+
+# Plot the bias as a function of the sample size 
+ggplot(output, aes(x = SampleSize, y = Bias, color = Estimator)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  ylab(expression(paste("Bias ")))
+
+```
+
+Figure \ref{fig:PlotMSE}, shows the Mean Square Error of each estimator as a function of sample size.
+We see that the lower the MSE, the better the performance of the estimator, as it indicates that the estimates are closer to the true values.
+```{r PlotMSE, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="MSE, for $L= 1$, $\\mu=1$."}
+sample_sizes <- c(9, 25, 49, 81, 121, 225)
+R <- 1000
+mu <- 1
+L <- 2
+
+# True entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)
+
+output_mse <- data.frame(SampleSize = integer(0), Estimator = character(0), MSE = numeric(0))
+#List of estimator
+estimators <- list(
+  list(func = van_es_estimator, label = "Van Es"),
+  list(func = correa_estimator, label = "Correa"),
+  list(func = ebrahimi_estimator, label = "Ebrahimi"),
+  list(func = noughabi_arghami_estimator, label = "Noughabi Arghami"),
+  list(func = vasicek_estimator, label = "Vasicek"),
+  list(func = al_omari_1_estimator, label = "Al Omari 1"),
+  list(func = al_omari_2_estimator, label = "Al Omari 2")
+)
+
+for (estimator in estimators) {
+  for (ssize in sample_sizes) {
+    squared_errors <- numeric(R)
+    for (r in 1:R) {
+      sample <- gamma_sar_sample(L, mu, ssize)
+      estimated_entropy <- estimator$func(sample)
+      squared_errors[r] <- (estimated_entropy - true_entropy)^2
+    }
+
+    # Calculate the MSE
+    mse <- mean(squared_errors)
+
+    output_mse <- rbind(output_mse, data.frame(SampleSize = ssize, Estimator = estimator$label, MSE = mse))
+  }
+}
+
+# Plot the MSE as a function of the sample size
+ggplot(output_mse, aes(x = SampleSize, y = MSE, color = Estimator)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  ylab("MSE")
+
+```

### 2023-10-25 Code/R/PlottingFunctions/bies_plot_one.R

@@ -1,0 +1,65 @@
+rm(list = ls())
+library(ggplot2)
+library(gtools)
+#library(stats4)
+#library(rmutil)
+#library(gsl)
+library(invgamma)
+library(ggplot2)
+library(ggthemes)
+theme_set(theme_pander() +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")
+)
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r") 
+source("../MainFunctions/noughabi_arghami_estimator.r") 
+source("../MainFunctions/vasicek_estimator.r") 
+source("../MainFunctions/al_omari_1_estimator.r") 
+source("../MainFunctions/al_omari_2_estimator.r") 
+#set.seed(1234567890, kind = "Mersenne-Twister")
+
+
+
+# Set sample sizes, the number of repetitions, and parameters
+sample_sizes <- c(9, 25,49,81, 121, 1225)
+R <- 1000
+mu <- 1
+L <- 1
+
+
+# Define the true entropy value for the gamma SAR distribution
+true_entropy <- entropy_gamma_sar(L, mu)  # Replace with the true entropy value
+# Initialize the output data frame
+output <- NULL
+
+# Perform non-parametric entropy estimation for different sample sizes
+for (ssize in sample_sizes) {
+  v.nonparametric.entropy <- NULL
+  for (r in 1:R) {
+    sample <- gamma_sar_sample(L, mu, ssize)
+    v.nonparametric.entropy[r] <- noughabi_arghami_estimator(sample)
+  }
+  
+  # Calculate the bias by subtracting the true entropy value
+  bias <- mean(v.nonparametric.entropy) - true_entropy
+  
+  # Store the bias in the output data frame
+  output <- rbind(output, c(bias, ssize))
+}
+
+# Create a data frame with results
+output <- data.frame(output)
+names(output) <- c("Bias")
+output$SampleSize <- sample_sizes
+
+# Plot the bias as a function of the sample size
+ggplot(output, aes(x=SampleSize, y=Bias)) +
+  geom_line() +
+  geom_point() +
+  xlab("Sample Size") +
+  ylab("Bias of Non-parametric Entropy Estimator")

### 2023-10-25 Code/R/PlottingFunctions/plot_MSE.R

@@ -60,6 +60,6 @@ ggplot(output_mse, aes(x = SampleSize, y = MSE, color = Estimator)) +
   geom_line() +
   geom_point() +
   xlab("Sample Size") +
-  ylab("Mean Squared Error (MSE)") 
+  ylab("MSE") 
 
   

### 2023-11-20 Code/R/RMarkdown/EntropyPlots.Rmd
best estimators

--- 2023-10-21 Code/R/RMarkdown/EntropyPlots.Rmd
@@
 date: "2023-10-16"
-output: html_document
+output: pdf_document
+
+# output: 
+#   pdf_document:
+#     toc: true
+#     toc_depth: 2
 #html_document
+header-includes:
+  - \usepackage{graphicx}
+  - \usepackage{float}
+  - \usepackage{bm}
+  - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage{wrapfig}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage{threeparttablex}
+  - \usepackage[normalem]{ulem}
+  - \usepackage{makecell}
+  - \usepackage{xcolor}
+
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+#knitr::opts_chunk$set(echo = TRUE)
 library(ggplot2)
+
+library(reshape2)
+#library(plotly)
+library(knitr)
+library(pandoc)
+library(gridExtra)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+library(scales)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
+library(invgamma)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggpubr)
+library(patchwork)
+options(kableExtra.latex.load_packages = FALSE)
+library(devtools)
+devtools::install_github("haozhu233/kableExtra")
+#devtools::install_github("haozhu233/kableExtra")
+library(kableExtra)
 library(ggthemes)
-library(reshape2)
-library(plotly)
-library(knitr)
-library(rgl)
+theme_set(theme_bw()  +
+            theme(text=element_text(family="serif"),
+                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+)
+# Helpful for latex tables
+# library(xtable)
+# options(xtable.caption.placement='top',
+#         xtable.table.placement='!t',
+#         xtable.include.rownames=F,
+#         xtable.comment=F)
+# #library(rgl)
+
+source("../MainFunctions/gamma_sar_sample.r")
+source("../MainFunctions/entropy_gamma_sar.r")
+
+source("../MainFunctions/van_es_estimator.r")
+source("../MainFunctions/correa_estimator.r")
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/noughabi_arghami_estimator.r")
+source("../MainFunctions/vasicek_estimator.r")
+source("../MainFunctions/al_omari_1_estimator.r")
+source("../MainFunctions/al_omari_2_estimator.r")
+
+source("../MainFunctions/bootstrap_van_es_estimator.r")
+source("../MainFunctions/bootstrap_correa_estimator.r")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../MainFunctions/bootstrap_vasicek_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
+source("../Programs/functions_sample_bias_mse.R")#
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
 ```
@@
 }
+
+gamma_sar_sample <- function(L, mu, n) {
+  samples <- rgamma(n, shape = L, rate = L / mu)
+  return(samples)
+}
+
 ```
 
-```{r PlotGammaSAR, echo=FALSE}
-mu <- seq(.1, 10, length.out=500)
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+L <- c(1, 3, 8, 12, 100)
 
-EntropyL1 <- entropy_gamma_sar(L=1, mu)
-EntropyL3 <- entropy_gamma_sar(L=3, mu)
-EntropyL8 <- entropy_gamma_sar(L=8, mu)
-EntropyL12 <- entropy_gamma_sar(L=12, mu)
-EntropyL100 <- entropy_gamma_sar(L=100, mu)
+L_labels <- c("L = 1", "L = 3", "L = 8", "L = 12", "L = 100")
 
-muEntropy <- data.frame(
-  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
-)
+mu <- seq(0.1, 10, length.out = 500)
 
-muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")
+entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
 
-ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
+muEntropy <- data.frame(mu, entropies)
+
+muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
   geom_line() +
-  theme_pander()
+  #theme_minimal() +
+  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
+  labs(col = "Looks") +
+  xlab(expression(paste(mu)))
 
@@
 
-```{r PlotGI0, echo=FALSE}
-mu <- seq(1, 10, length.out = 500)
-alpha <- seq(-20, -2, length.out = 500)
-
-entropy <- outer(mu, alpha, FUN = function(mu, alpha) entropy_gI0(mu, alpha, L = 1))
-
-#
-persp(x = mu, y = alpha, z = entropy, col = "lightblue", border = "blue")
-
-open3d()
-
-persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")
-
-#-----
-mu <- seq(1, 10, length.out=200)
-alpha <- seq(-2, -20, length.out=200)
-
-entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
-entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
-entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
-entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
-entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
-
-fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
-
-fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
-fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
-fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
-fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
-fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
-
-fig <- fig %>% layout(
-  scene = list(
-    xaxis = list(title = "alpha"),
-    yaxis = list(title = "mu"),
-    zaxis = list(title = "Entropy")
-  )
-)
-
-fig
-
+```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
+knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
 ```

### 2023-11-20 Code/R/RMarkdown/Report_Estimators.Rmd
best estimators

---
title: "Report: Exploring Non-Parametric Entropy Estimators and Bootstrap Enhancements"
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
options(kableExtra.latex.load_packages = FALSE)
library(devtools)
devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")
source("../MainFunctions/gi0_sample.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

\newcommand{\bias}{\operatorname{Bias}}

# Introduction
Understanding and measuring entropy, a fundamental concept in information theory, is crucial in various fields. 
This study delves into the evaluation of non-parametric of Shannon entropy estimators and their Bootstrap enhancements. Non-parametric estimators offer a flexible approach to parameter estimation, while Bootstrap technique provide a robust tool for refining these estimators and quantifying their uncertainty. Using various sample sizes and replications, different estimators are evaluated based on bias, variance, mean squared error (MSE), and confidence intervals. The results highlight the trade-off between bias and variance, shedding light on the efficiency and reliability of each estimator.

# Non-Parametric Entropy Estimators

The problem of non-parametric estimating of $H(X)$ has been considered by many authors, who proposed estimators based on spacings.

Vasicek (1976), used $f(z)=p$  to express $H(X)$ as
\begin{equation*}
	H(X)= \int_0^1 \log\left(\frac{\mathrm{d}}{\mathrm{d}p}Q(p)\right)\mathrm{d}p,
\end{equation*}
where $Q(p)=F^{-1}(p)=\inf\left\{x: F(X)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics.

Assuming that  $\bm{X}=(X_1, X_2, \ldots,X_n)$ is a random sample from the distribution $F(x)$, the estimator is defined as:
\begin{equation}
\label{E:Vas}
	\widehat{H}_{V}(\bm{X})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
	\end{equation}
where $m<n/2$ is a positive integer, $X_{(i+m)}-X_{(i-m)}$ is the $m$-spacing and $X_{(1)}\leq X_{(2)}\leq\ldots\leq X_{(n)}$ are the order statistics and $X_{(i)}= X_{(1)}$ if $i<1$, $Z_{(i)}= X_{(n)}$ if $i>n$.

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es (1992), who proposed a new estimator of entropy given by:
\begin{equation}
\label{E:VanEs}
	\widehat{H}_{\text{VE}}(\bm{X})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(X_{(i+m)}-X_{(i)}\right)\right]+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
\end{equation}
Van Es demonstrated that, under some conditions, this estimator exhibits consistency and asymptotic normality.

In 1995 Correa suggested a modification of Vasicek's estimator. In estimation the density $f$ of $F$ in the interval $\left(X_{(i-m)}, X_{(i+m)}\right)$ he used a local linear model based on $2 m+1$ points: $F\left(X_{(j)}\right)=\alpha+\beta X_{(j)}+\varepsilon, j=m-i, \ldots, m+i$. This yields a following estimator
\begin{equation}
\widehat{H}_C(\mathbf{X})=-\frac{1}{n} \sum_{i=1}^n \ln \left(b_i\right),
\end{equation}
where
$$
\begin{gathered}
b_i=\frac{\sum_{j=i-m}^{i+m}\left(X_{(j)}-\bar{X}_{(i)}\right)(j-i)}{n \cdot \sum_{j=i-m}^{i+m}\left(X_{(j)}-\bar{X}_{(i)}\right)^2}, \\
\bar{X}_{(i)}=\frac{1}{2 m+1} \sum_{j=i-m}^{i+m} X_{(j)},
\end{gathered}
$$
$m$ is a positive integer smaller than $\frac{n}{2}, X_{(i)}=X_{(1)}$ for $i<1$ and $X_{(i)}=X_{(n)}$ for $i>n$.

Ebrahimi et al. (1994), adjusted the weights of Vasicek's estimator, in order to take into account the fact that the differences are truncated around the smallest and the largest data points. i.e. $X_{(i+m)}-X_{(i-m)}$ is replaced by $X_{(i+m)}-X_{(1)}$ when $i \leq m$ and $X_{(i+m)}-X_{(i-m)}$ is replaced by $X_{(n)}-X_{(i-m)}$ when $i \geq n-m+1$. Their estimator is given by
\begin{equation}
\widehat{H}_E(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
\end{equation}
where
$$
c_i=\left\{\begin{array}{lr}
1+\frac{i-1}{m}, & 1 \leq i \leq m \\
2, & m+1 \leq i \leq n-m, \\
1+\frac{n-i}{m}, & n-m+1 \leq i \leq n
\end{array}\right.
$$

Noughabi and Arghami suggested an entropy estimator given by

\begin{equation}
\widehat{H}_{NA}(\mathbf{X})=\frac{1}{n}(\mathbf{X}) \sum_{i=1}^n \log \left[\frac{n}{a_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right],
\end{equation}
where
$$
a_i=\left\{\begin{array}{lc}
1, & 1 \leq i \leq m, \\
2, & m+1 \leq i \leq n-m, \\
1, & n-m+1 \leq i \leq n,
\end{array}\right.
$$
and $X_{(i-m)}=X_{(1)}$ for $i \leq m$ and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.

Al-Omari suggested the following estimators of entropy:

\begin{equation}
\widehat{H}_{\mathrm{AO}_1}(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right]
\end{equation}
where
$$
\omega_i= \begin{cases}3 / 2 & \text { if } 1 \leq i \leq m \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 3 / 2 & \text { if } n-m+1 \leq i \leq n,\end{cases}
$$
in which $X_{(i-m)}=X_{(1)}$ for $i \leq m$, and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.
And
\begin{equation}
\widehat{H}_{\mathrm{AO}_2}(\mathbf{X})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{v_i m}\left(X_{(i+m)}-X_{(i-m)}\right)\right]
\end{equation}
where
$$
v_i= \begin{cases}1+(i-1) / m & \text { if } 1 \leq i \leq m \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 1+(n-i) / 2 m & \text { if } n-m+1 \leq i \leq n\end{cases}
$$
in which $X_{(i-m)}=X_{(1)}$ for $i \leq m$, and $X_{(i+m)}=X_{(n)}$ for $i \geq n-m$.

## Results for  Nonparametric Estimators with $\Gamma_{\text{SAR}}$

Our experimental setup involves an analysis of bias and MSE for each estimator using varying sample sizes, denoted as \(n\in\left\{9, 25, 49, 81, 121\right\}\). For each specific sample size, we generate 100 random samples to ensure robust statistical insights. Additionally, we consider distinct parameter values, where $\mu$ varies within $\left\{1, 3, 10, 100\right\}$ and $L$ within $\left\{1, 3, 5, 18\right\}$. This parameter variation aims to explore potential impacts on estimator performance.
Figures \ref{fig:Plot_bias_mse_1}, \ref{fig:Plot_bias_mse_2}, \ref{fig:Plot_bias_mse_3}, and  \ref{fig:Plot_bias_mse_4}  present the bias and MSE for each of the seven non-parametric entropy estimators.

```{r Plot_bias_mse_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 1$.", fig.width=10,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 1

 mu_values <- c(1,  3, 10, 100)

#L values

L <- 1

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Vasicek" = vasicek_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Al Omari 2" = al_omari_2_estimator
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  #"Correa Bootstrap" = bootstrap_correa_estimator,
  #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator
  # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator,
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 2)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 3$.", fig.width=10,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 1
mu_values <- c(1,  3, 10, 100)
L <- 3

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Vasicek" = vasicek_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Al Omari 2" = al_omari_2_estimator
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  #"Correa Bootstrap" = bootstrap_correa_estimator,
  #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator
  # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator,
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 2)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 1
mu_values <- c(1,  3, 10, 100)
L <- 5

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Vasicek" = vasicek_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Al Omari 2" = al_omari_2_estimator
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  #"Correa Bootstrap" = bootstrap_correa_estimator,
  #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator
  # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator,
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 2)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_4, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 18$.", fig.width=10,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 1
mu_values <- c(1,  3, 10, 100)
L <- 18

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Vasicek" = vasicek_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Al Omari 2" = al_omari_2_estimator
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  #"Correa Bootstrap" = bootstrap_correa_estimator,
  #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator
  # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator,
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 2)

# Print the combined plot
print(combined_plot)

```

The simulation results for bias and MSE, where $\mu$ takes values in $\left\{1, 3, 10, 100\right\}$ and $L=5$, are presented in Table \ref{tab:bias_mse_1}.
```{r GenerateTables6, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Parámetros
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
B <- 1
mu_values <- c(1, 3, 10, 100)
L <- 5

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Vasicek" = vasicek_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Al Omari 2" = al_omari_2_estimator
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  #"Correa Bootstrap" = bootstrap_correa_estimator,
  #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator
  # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator,
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Crear una tabla para almacenar los resultados de todos los valores de mu
combined_results <- NULL

for (mu_val in mu_values) {
  # Calcular resultados para el valor actual de mu
  results <- calculate_bias_mse(sample_sizes, R, B, mu_val, L, estimators)

  # Añadir una columna con el valor actual de mu en la primera posición
  results <- cbind(mu = mu_val, results)

  # Combina los resultados con la tabla principal
  combined_results <- bind_rows(combined_results, results)
}

# Reshape the data to have Estimators as columns
reshaped_results <- combined_results %>%
  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
#\widetilde{H}_{i}

# colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$", "$\\widehat{H}_{VE}$ ", "$\\widehat{H}_{C}$", "$\\widehat{H}_{E}$", "$\\widehat{H}_{NA}$", "$\\widehat{H}_{V}$", "$\\widehat{H}_{AO_1}$",  "$\\widehat{H}_{AO_2}$", "$\\widehat{H}_{VE}$ ", "$\\widehat{H}_{C}$", "$\\widehat{H}_{E}$", "$\\widehat{H}_{NA}$", "$\\widehat{H}_{V}$", "$\\widehat{H}_{AO_1}$",  "$\\widehat{H}_{AO_2}$")

colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$", "$\\widehat{H}_{VE}$ ", "$\\widehat{H}_{C}$", "$\\widehat{H}_{E}$", "$\\widehat{H}_{NA}$", "$\\widehat{H}_{V}$", "$\\widehat{H}_{AO_1}$",  "$\\widehat{H}_{AO_2}$", "$\\widehat{H}_{VE}$ ", "$\\widehat{H}_{C}$", "$\\widehat{H}_{E}$", "$\\widehat{H}_{NA}$", "$\\widehat{H}_{V}$", "$\\widehat{H}_{AO_1}$",  "$\\widehat{H}_{AO_2}$")

# Imprime la tabla combinada con líneas divisorias y título personalizado
print(collapse_rows(kbl(reshaped_results, caption = "Bias and MSE for different $\\mu$ values, and $L=5$.",  escape=FALSE,
                        align = "ccccccc",
                        booktabs = T,
                        #longtable = T,
                        digits=4, label="bias_mse_1",# position="hbt", linesep = "",
                        row.names=FALSE) %>%
                     row_spec(0, bold = TRUE) %>%
                    add_header_above(c(" ", " ", "Bias" = 7, "MSE" = 7)) %>%
                    #collapse_rows(columns = 1:2) %>%
                     kable_styling(latex_options = c("repeat_header",  "hold_position", "scale_down"))))
```

Based on our experiments, the estimators with consistently lower bias and MSE across various scenarios are $\widehat{H}_{C}$, $\widehat{H}_{AO_2}$, and $\widehat{H}_{E}$. These estimators demonstrate robust performance and convergence under different parameter combinations.

For the Noughabi Arghami estimator, it demonstrates consistently low MSE across various scenarios. However, it is noteworthy that the bias remains constant and notably high for sample sizes larger than 25, with no indication of rapid convergence.

In contrast, the Van Es and Vasicek estimators have a larger bias, but the one with the highest MSE is undoubtedly the Vasicek estimator.

# Enhanced Bootstrap Estimators

In this section, we extend our exploration of nonparametric entropy estimators by incorporating enhanced bootstrap methodologies. The integration of bootstrap techniques aims to refine the precision and reliability of entropy estimates, offering a robust framework for information-theoretic analyses.

Bootstrap methods, renowned for their versatility in handling complex data structures, have become invaluable tools for refining statistical inferences. In the realm of entropy estimation, the application of bootstrap techniques seeks to mitigate the inherent challenges posed by finite sample sizes. By repeatedly resampling from the observed data, bootstrap enhances the stability of estimates and provides a comprehensive understanding of the uncertainty associated with each estimator.

The bootstrap technique is a powerful resampling method widely employed in statistical analyses to comprehend the variability and uncertainty associated with sample data. It operates on the fundamental principle that a sample drawn from an underlying population is a representative reflection of the entire population. Bootstrap methodology involves generating numerous resamples by drawing observations with replacement from the original dataset.

Here's a step-by-step breakdown of the bootstrap process:
\begin{itemize}
	\item Resampling with Replacement: A primary characteristic of bootstrap is the sampling with replacement, meaning that each observation selected during resampling is returned to the pool, allowing the same observation to be chosen multiple times or not at all.
	\item Creating Bootstrap Samples: Through the resampling process, multiple bootstrap samples are generated, each equivalent in size to the original dataset. This technique mimics the randomness inherent in the data collection process.
\item Estimate Computation: The statistical quantity of interest (e.g., mean, variance, or entropy) is calculated for each bootstrap sample, yielding a distribution of estimates.
\end{itemize}

## Theoretical Framework
We present an innovative approach to enhance the non-parametric entropy estimators denoted as $\widehat{H}_{i}$. Acknowledging the inherent bias in these estimators, we propose bootstrap-enhanced versions denoted as $\widetilde{H}_{i}$ to address the bias and refine the accuracy of the original estimations.

Let \( \widehat{\theta}(X)= \widehat{H}_{i}\) represent the non-parametric entropy estimators based on a sample \(X\) of size \(n\). Let's assume that these estimators are inherently biased, that is, the bias is defined as:

\begin{equation}
\label{Eq:bias1}
\bias\left(\widehat{\theta}(X)\right) = \mathbb{E}\left[\widehat{\theta}(X)\right] - \theta.
\end{equation}
Our objective is to devise unbiased estimators with reduced variance. To achieve this, we introduce an "ideal estimator" \(\check{\theta}(X)\) using the bias information:
\begin{equation}
\label{Eq:bias2}
\widecheck{\theta}(X) = \widehat{\theta}(X) - \bias\left(\widehat{\theta}(X)\right).
\end{equation}
However, \(\check{\theta}(X)\) is not an estimator, because it does not depend on the true parameter \(\theta\), prompting the formulation of a new unbiased "proper estimator" \(\widetilde{\theta}\), from \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:

\begin{align}
\label{Eq:bias3}
\widetilde{\theta}(X) &= \widehat{\theta}(X)+\widehat{\theta}(X) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(X^{(b)}),\nonumber\\
                      & =2\widehat{\theta}(X) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(X^{(b)}),
\end{align}

where $B$ represents the number of replications in the bootstrap technique.

The proposed \(\widetilde{\theta}(X)\) leverages the bootstrap technique to refine the original estimators. For each iteration \(b\) (from \(1\) to \(B\)) in the bootstrap process, a sample \(X^{(b)}\) is generated, and the corresponding bootstrap estimator \(\widehat{\theta}_b(X^{(b)})\) is calculated.

The final bootstrap-enhanced estimator \(\widetilde{H}_{i}\) is computed by incorporating these bootstrap estimators into the formulation:

\[\widetilde{H}_{i}(X) = \widetilde{\theta}(X)\]

This methodology significantly reduces bias, resulting in more accurate and robust entropy estimations. The notation \(\widetilde{H}_{i}\) denotes the improved versions of the original estimators, providing a comprehensive enhancement to their non-parametric counterparts.

## MSE Results for Bootstrap Estimators

Similar to the analysis conducted on the original estimators, we consider two parameter values for $\mu\in\left\{1,  10\right\}$ and $L=5$. To observe the behavior of the estimators under different scenarios, we perform experiments with varying sample sizes \(n\in\left\{9, 25, 49, 81, 121\right\}\). For each specific sample size, we generate 100 random samples and perform 100 replications for bootstrap.

In-depth comparisons of bias and MSE between original non-parametric entropy estimators and their respective bootstrap-enhanced versions are presented in Figures 5-10. The application of the bootstrap technique demonstrates notable improvements across the majority of methods.

<!-- The analysis involves a comparison between each original non-parametric entropy estimator and its corresponding bootstrap-enhanced version. We aim to identify estimators that exhibit enhanced precision, reduced bias, and improved convergence. -->

```{r Plot_bias_mse_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of $\\widehat{H}_{VE}$ and $\\widetilde{H}_{VE}$, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1,   10)
L <- 5

# Define a list of estimators
estimators <- list(
  "Van Es" = van_es_estimator,
  "Van Es Bootstrap" = bootstrap_van_es_estimator#"$\\widetilde{H}_{VE}$" = bootstrap_van_es_estimator
)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_6, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
  "Vasicek" = vasicek_estimator,
   "Vasicek Bootstrap" = bootstrap_vasicek_estimator
 )

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_7, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
   "Ebrahimi" = ebrahimi_estimator,
   "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator
 )
# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_8, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100
# Number of bootstrap replications
B <- 100
mu_values <- c(1, 10)
L <- 5

# Define a list of estimators
estimators <- list(
   "Correa" = correa_estimator,
   "Correa Bootstrap" = bootstrap_correa_estimator

)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_9, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100
# Number of bootstrap replications
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
  "Noughabi Arghami" = noughabi_arghami_estimator,
  "Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator
 )

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_10, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
  "Al Omari 1" = al_omari_1_estimator,
   "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```

```{r Plot_bias_mse_11, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, for $L= 5$.", fig.width=10,fig.height=3}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
    "Al Omari 2" = al_omari_2_estimator,
    "Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Generate and plot the results
combined_plot <- generate_plot(sample_sizes, R, B, mu_values, L, estimators, ncol = 2, nrow = 1)

# Print the combined plot
print(combined_plot)

```
The simulation results for Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap estimators are presented in Table \ref{tab:bias_mse_2}, where $\mu$ takes values in $\left\{1,10\right\}$ and $L=5$.

```{r Table2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Parámetros
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
B <- 100
mu_values <- c(1,  10)
L <- 5

# Define a list of estimators
estimators <- list(
  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
  "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
)

# Crear una tabla para almacenar los resultados de todos los valores de mu
combined_results <- NULL

for (mu_val in mu_values) {
  # Calcular resultados para el valor actual de mu
  results <- calculate_bias_mse(sample_sizes, R, B, mu_val, L, estimators)

  # Añadir una columna con el valor actual de mu en la primera posición
  results <- cbind(mu = mu_val, results)

  # Combina los resultados con la tabla principal
  combined_results <- bind_rows(combined_results, results)
}

# Reshape the data to have Estimators as columns
reshaped_results <- combined_results %>%
  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
#\widetilde{H}_{i}

colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO_1}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO_1}$")

# Imprime la tabla combinada con líneas divisorias y título personalizado
print(collapse_rows(kbl(reshaped_results, caption = "Bias and MSE for different $\\mu$ values, and $L=5$.",  escape=FALSE,
                        align = "ccccccc",
                        booktabs = T,
                        #longtable = T,
                        digits=4, label="bias_mse_2",# position="hbt", linesep = "",
                        row.names=FALSE) %>%
                     row_spec(0, bold = TRUE) %>%
                    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
                    #collapse_rows(columns = 1:2) %>%
                     kable_styling(latex_options = c("repeat_header",  "hold_position"))))
```

The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique. Particularly, are the enhancements achieved by the Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap estimators. These methods exhibit remarkable precision, showcasing the efficacy of the bootstrap approach in refining their accuracy.

Conversely, the application of bootstrap did not yield favorable results for the Noughabi-Arghami Bootstrap and Al Omari 2 Bootstrap estimators. The observed lack of improvement suggests that, in certain cases, the bootstrap technique may not be universally effective for all entropy estimation methods.

Motivated by the superior performance of the Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap estimators, we proceed to a more detailed analysis of their variance and confidence intervals. This selection is driven by their consistent precision improvement through bootstrap enhancement, establishing them as promising candidates for further investigation.

# Analysis of Variance and Confidence Intervals

The next phase of our investigation involves a detailed examination of the variance exhibited by three selected bootstrap-enhanced estimators: Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap. The primary objective is to assess the stability and consistency of these estimators under varying conditions.

Figures 1, 2, and 3 present a comparative analysis of the variance for each estimator across different parameter values ($\mu$ and $L$) and sample sizes ($n$). Notably, the Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap estimators consistently demonstrate lower variance compared to their non-bootstrap counterparts.

```{r Plot_var, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap=" Variance for $L= 5$.", fig.width=6,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu <- 1
L <- 5

# Define a list of estimators
estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
)

#plot

variance_data <- calculate_variance(sample_sizes, R, B, mu, L, estimators)
ggplot(variance_data, aes(x = SampleSize, y = Variance, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  labs(title = "",
       x = "Sample Size", y = "Variance") +
  guides(color = guide_legend(title = "Estimator")) +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_var2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Variance for $L= 5$.", fig.width=6,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu <- 10
L <- 5

# Define a list of estimators
estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
)

#plot

variance_data <- calculate_variance(sample_sizes, R, B, mu, L, estimators)
ggplot(variance_data, aes(x = SampleSize, y = Variance, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  labs(title = "",
       x = "Sample Size", y = "Variance") +
  guides(color = guide_legend(title = "Estimator")) +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_var3, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Variance for $L= 5$.", fig.width=6,fig.height=5}
# Define sample sizes for analysis
set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu <- 100
L <- 5

# Define a list of estimators
estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari 1" = al_omari_1_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
)

#plot

variance_data <- calculate_variance(sample_sizes, R, B, mu, L, estimators)
ggplot(variance_data, aes(x = SampleSize, y = Variance, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  labs(title = "",
       x = "Sample Size", y = "Variance") +
  guides(color = guide_legend(title = "Estimator")) +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

The results indicate that, for small sample sizes, the original estimators exhibit lower variance compared to their bootstrap counterparts. However, as the sample size increases, the variance decreases for both the original and bootstrap estimators.

# Confidence Interval Analysis
To complement our variance examination, we delve into the evaluation of confidence intervals associated with the selected bootstrap-enhanced estimators. Confidence intervals provide valuable insights into the precision and reliability of the estimators' predictions.

The narrower and more stable the confidence intervals, the higher the confidence in the accuracy of the estimators. Our analysis reveals that the Correa Bootstrap, Ebrahimi Bootstrap, and Al Omari 1 Bootstrap estimators consistently generate tighter and more reliable confidence intervals.

```{r Plot_CI1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Confidence Intervals for $L= 5$ and $\\mu=10$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

true_entropy <- entropy_gamma_sar(L, mu)
# Function to calculate Confidence Intervals for both non-parametric and bootstrap estimators
calculate_confidence_intervals <- function(sample_sizes, R, mu, L, confidence_level = 0.95) {
  true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
      "Correa Bootstrap" = bootstrap_correa_estimator
    # "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
    # "Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), 
                       LowerCI = numeric(0), UpperCI = numeric(0))

  for (ssize in sample_sizes) {

    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }

      }

      # Calculate Confidence Interval
      se <- sd(v.entropy)
      margin_of_error <- qt((1 + confidence_level) / 2, R - 1) * se / sqrt(R)
      ci_lower <- mean(v.entropy) - margin_of_error
      ci_upper <- mean(v.entropy) + margin_of_error

      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, 
                                         LowerCI = round(ci_lower, 5), UpperCI = round(ci_upper, 5)))
    }
  }

  return(output)
}

confidence_intervals_data <- calculate_confidence_intervals(sample_sizes, R, mu, L)

combined_plot <- ggplot(confidence_intervals_data, aes(x = SampleSize, y = UpperCI, ymin = LowerCI, ymax = UpperCI, color = Estimator)) +
  geom_line(aes(group = Estimator), linetype = "dashed") +
  geom_ribbon(alpha = 0.2) +
  geom_point(aes(y = (LowerCI + UpperCI) / 2), color = "#808080", size = 2) + 
  geom_line(aes(x = SampleSize, y = (LowerCI + UpperCI) / 2, color = Estimator), linetype = "solid", size = 0.5) +  
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") +  
  labs(title = "",
       x = "Sample Size", y = "Entropy")

print(combined_plot)
```

```{r Plot_CI_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Confidence Intervals for $L= 5$ and $\\mu=10$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

true_entropy <- entropy_gamma_sar(L, mu)
# Function to calculate Confidence Intervals for both non-parametric and bootstrap estimators
calculate_confidence_intervals <- function(sample_sizes, R, mu, L, confidence_level = 0.95) {
  true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
      "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator
     #"Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
    # "Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), 
                       LowerCI = numeric(0), UpperCI = numeric(0))

  for (ssize in sample_sizes) {

    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }

      }

      # Calculate Confidence Interval
      se <- sd(v.entropy)
      margin_of_error <- qt((1 + confidence_level) / 2, R - 1) * se / sqrt(R)
      ci_lower <- mean(v.entropy) - margin_of_error
      ci_upper <- mean(v.entropy) + margin_of_error

      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, 
                                         LowerCI = round(ci_lower, 5), UpperCI = round(ci_upper, 5)))
    }
  }

  return(output)
}

confidence_intervals_data <- calculate_confidence_intervals(sample_sizes, R, mu, L)

combined_plot <- ggplot(confidence_intervals_data, aes(x = SampleSize, y = UpperCI, ymin = LowerCI, ymax = UpperCI, color = Estimator)) +
  geom_line(aes(group = Estimator), linetype = "dashed") +
  geom_ribbon(alpha = 0.2) +
  geom_point(aes(y = (LowerCI + UpperCI) / 2), color = "#808080", size = 2) + 
  geom_line(aes(x = SampleSize, y = (LowerCI + UpperCI) / 2, color = Estimator), linetype = "solid", size = 0.5) +  
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") +  
  labs(title = "",
       x = "Sample Size", y = "Entropy")

print(combined_plot)
```

```{r Plot_CI_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Confidence Intervals for $L= 5$ and $\\mu=10$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

true_entropy <- entropy_gamma_sar(L, mu)
# Function to calculate Confidence Intervals for both non-parametric and bootstrap estimators
calculate_confidence_intervals <- function(sample_sizes, R, mu, L, confidence_level = 0.95) {
  true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
      #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), 
                       LowerCI = numeric(0), UpperCI = numeric(0))

  for (ssize in sample_sizes) {

    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }

      }

      # Calculate Confidence Interval
      se <- sd(v.entropy)
      margin_of_error <- qt((1 + confidence_level) / 2, R - 1) * se / sqrt(R)
      ci_lower <- mean(v.entropy) - margin_of_error
      ci_upper <- mean(v.entropy) + margin_of_error

      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, 
                                         LowerCI = round(ci_lower, 5), UpperCI = round(ci_upper, 5)))
    }
  }

  return(output)
}

confidence_intervals_data <- calculate_confidence_intervals(sample_sizes, R, mu, L)

combined_plot <- ggplot(confidence_intervals_data, aes(x = SampleSize, y = UpperCI, ymin = LowerCI, ymax = UpperCI, color = Estimator)) +
  geom_line(aes(group = Estimator), linetype = "dashed") +
  geom_ribbon(alpha = 0.2) +
  geom_point(aes(y = (LowerCI + UpperCI) / 2), color = "#808080", size = 2) + 
  geom_line(aes(x = SampleSize, y = (LowerCI + UpperCI) / 2, color = Estimator), linetype = "solid", size = 0.5) +  
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") +  
  labs(title = "",
       x = "Sample Size", y = "Entropy")

print(combined_plot)
```

# Mean Entropy for Estimators

```{r Plot_mean, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for $L= 5$ and $\\mu=10$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}
true_entropy <- entropy_gamma_sar(L, mu)
# Function to calculate Variance for both non-parametric and bootstrap estimators
calculate_entropy <- function(sample_sizes, R, mu, L) {
  #true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
     "Correa" = correa_estimator,
     "Ebrahimi" = ebrahimi_estimator,
     "Al Omari 1" = al_omari_1_estimator,
      "Correa Bootstrap" = bootstrap_correa_estimator,
     "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_mean1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121, 225)
R <- 100
mu <- 1
L <- 1

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
     "Correa" = correa_estimator,
     "Ebrahimi" = ebrahimi_estimator,
     "Al Omari 1" = al_omari_1_estimator,
      "Correa Bootstrap" = bootstrap_correa_estimator,
     "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_mean2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for $L= 5$ and $\\mu=5$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 5
L <- 5

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
     "Correa" = correa_estimator,
     "Ebrahimi" = ebrahimi_estimator,
     "Al Omari 1" = al_omari_1_estimator,
      "Correa Bootstrap" = bootstrap_correa_estimator,
     "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

## Results for  Nonparametric Estimators with  $\mathcal{G}_I^0$

```{r Plot_GI0_mean, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for $L= 5$, $\\alpha= -1000$ and $\\mu=10$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5
alpha <- -1000

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gI0(mu, alpha, L)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    "Correa" = correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
    #"Al Omari 2" = al_omari_2_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator,
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
    "Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```
In the figure we can observe that when the parameter $\alpha$ goes to $-\infty$, the entropy of $\mathcal{G}_I^0$ is close to the entropy of $\Gamma_{\text{SAR}}$.

### 2023-11-20 Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R

@@ -1,0 +1,33 @@
+
+
+
+
+source("../MainFunctions/al_omari_2_estimator.r")
+
+
+bootstrap_al_omari_2_estimator <- function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- al_omari_2_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- al_omari_2_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}

### 2023-11-20 Code/R/MainFunctions/bootstrap_correa_estimator.R

@@ -1,0 +1,38 @@
+
+
+
+
+ source("../MainFunctions/correa_estimator.r")
+
+
+bootstrap_correa_estimator <-  function(x, B){
+  
+  v.Bootstrap <- rep(0, B)
+  
+  for(b in 1:B) {
+    same_values <- TRUE
+    while (same_values) {
+      bx <- sample(x, replace = TRUE)
+      if (!all(bx == bx[1])) {
+        same_values <- FALSE
+        entropy_result <- correa_estimator(bx)
+        if (is.finite(entropy_result)) {
+          v.Bootstrap[b] <- entropy_result
+          #cat("Bootstrap Sample", b, ": ", bx, "\n")
+          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
+        }
+      }
+    }
+  }
+  
+  
+  t <- correa_estimator(x)
+  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
+  
+  return(2*t - estimated_mean)
+  
+}
+
+
+
+

### 2023-11-20 Code/R/MainFunctions/entropy_gI0.R

@@ -19,3 +19,4 @@ entropy_gI0 <- function(mu, alpha, L) {
   entropy <- term1 + term2 
   return(entropy)
 }
+

### 2023-11-20 Code/R/MainFunctions/gamma_sar_sample.R

@@ -14,3 +14,4 @@ gamma_sar_sample <- function(L, mu, n) {
   samples <- rgamma(n, shape = L, rate = L / mu)
   return(samples)
 }
+

### 2023-11-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
best estimators
Revised - good to continue

@@
       author:
-      - name: Rosa Janeth Alpala, Abraão D. C. Nascimento
+      - name: Rosa Janeth Alpala, Abraão D.\ C.\ Nascimento
 
@@
       author:
-        - name: Alejandro C. Frery
+        - name: Alejandro C.\ Frery
 
@@
 abstract: |
-  SAR Data are affected by speckle in a non-additive and non-Gaussian way.
+  SAR Data are affected by speckle, a non-additive and non-Gaussian interference noise-like pattern.
   The type of distribution these data follow is paramount for their processing and analysis.
@@
   Although the latter is a limit distribution of the former, using the same estimation technique for the more general model is numerically unfeasible.
-  We propose a two-stage estimation procedure: first, we verify the hypothesis that the data are fully-developed speckle and, if this assumption is rejected, we proceed to estimate the parameters that index the $\mathcal G^0$ distribution.
+  We propose a two-stage estimation procedure: first, we verify the hypothesis that the data are fully-developed speckle.
+If this assumption is rejected, we proceed to estimate the parameters that index the $\mathcal G^0$ distribution; otherwise, we proceed with the Gamma model.
   Given the uncertainty of the underlying distribution, and the negative impact that using an inadequate model has on maximum likelihood estimation, we employ a non-parametric approach to estimate entropy under the fully-developed speckle hypothesis.
@@
 bibliography:  ../../Common/references.bib
-csl: ieee.csl
-output: rticles::ieee_article
+#csl: "ieee.csl"
+output: 
+  rticles::ieee_article:
+    number_sections: TRUE
 
@@
 \newtheorem{lemma}{Lemma}
-\renewcommand{\thesection}{\Alph{section}}
+
 # Introduction {#sec:Introduction}
@@
 Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;[@Cassetti2022].
-However, the utility of SAR data depends on a thorough understanding of the statistical properties governing its inherent speckle noise.
-This complex interaction, which defies simplistic assumptions of additivity and Gaussianity, requires robust statistical models that can accurately characterize SAR data for efficient processing and analysis.
+However, the utility of SAR data depends on a thorough understanding of the their statistical properties.
+Speckle is part of SAR data because of the imaging process' coherent nature.
+Its non-additivity and non-Gaussianity require robust statistical models that can accurately characterize the data.
 
-Among these models, the $\mathcal{G}^0$ distribution stands out as a powerful framework for modeling SAR data.
+Among these models, the $\mathcal{G}^0$ distribution stands out as a powerful framework. 
 Notably, this distribution encompasses the well-known Gamma distribution as a special case, particularly under the assumption of fully developed speckle. 
@@
 
-On the other hand, entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
+When deciding which model is the best, practitioners face a problem.
+On the one hand, if they opt for the Gamma law when the data came from the $\mathcal{G}^0$ distribution, they loose all the information about the number of scatterers, which is revealed by one of the parameters of the latter model [@Yue2021].
+On the other hand, if they apply the $\mathcal{G}^0$ distribution under fully developed speckle,
+maximum likelihood estimation is tricky: 
+bias increases making estimation unreliable [@VasconcellosFrerySilva:CompStat], and
+the likelihood is flat, so numerical optimization may not converge [@FreryCribariSouza:JASP:04].
+
+The two-stage technique we propose tackles this problem by using the Entropy as a proxy to decide which is the best model.
+
+The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics.
 Shannon introduced it for a random variables in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty. 
@@
 
-Estimating entropy faces practical challenges, particularly when the true probability density function (pdf) is unknown.
-Nonparametric methods are utilized in such cases, avoiding the assumption of a known pdf form.
-Instead, techniques like histograms or kernel density estimators are employed to estimate the pdf directly, followed by entropy calculation using numerical or Monte Carlo integration&nbsp;[@Lombardi2016].
-An alternative nonparametric approach involves spacing methods, facilitating entropy estimation&nbsp;[@Zamanzade2012].
-This non-parametric strategy offers flexibility to address a wide range of data distributions without imposing specific parametric constraints.
+Estimating the entropy faces practical challenges, particularly when the model is unknown; nonparametric methods are utilized in such cases.
+<!-- Instead, techniques like histograms or kernel density estimators are employed to estimate the pdf directly, followed by entropy calculation using numerical or Monte Carlo integration&nbsp;[@Lombardi2016].
+-->
+Among nonparametric approaches, @Zamanzade2012 discussed the use of spacing methods.
+This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.
 
 In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data. 
-The first stage of our methodology is to test the hypothesis that the data are completely speckled.
+The first stage tests the hypothesis that the data follow the Gamma distribution, i.e., we are in the presence of fully developed speckle. 
 If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.
 
-The significance of selecting an appropriate statistical model and estimation technique is well recognized.
+<!-- The significance of selecting an appropriate statistical model and estimation technique is well recognized.
 In order to address uncertainties in the data distribution, we employ a non-parametric approach.
-Specifically, we focus on the entropy estimation considering estimators based on spacing.
+-->
+<!-- Specifically, we focus on the entropy estimation considering estimators based on spacing. -->
 
-The article is structured as follows: In Section&nbsp;\ref{sec:Background}, we provide an overview of statistical modeling for Intensity SAR data and the estimation of both parametric and non-parametric Shannon entropy.
+The article is structured as follows: 
+In Section&nbsp;\ref{sec:Background}, we provide an overview of statistical modeling for Intensity SAR data and the estimation of both parametric and non-parametric Shannon entropy.
 
@@
 The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
-The first is suitable for fully developed speckle and can also be considered a limiting case within the $\mathcal{G}_I^0$ distribution.
-Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
+The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
 \begin{align}
-	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\},\label{E:gamma1}\\
-	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}},\label{E:gi01}
+	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
+	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
 \end{align}
-where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.
+where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
 
@@
 \end{align*}
-Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ is
+Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ law is
 \begin{multline}
@@
 
-The parametric representation of Shannon entropy for a system described by a continuous random variable is as follows:
+The parametric representation of Shannon entropy for a system described by a continuous random variable is:
 \begin{equation}
   \label{E:entropy2}
-  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log(f(z))\, \mathrm{d}z,
+  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
 \end{equation}
@@
 
-Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on&nbsp;[@Cassetti2022, @Ferreira2020]:
+Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on @Cassetti2022 and @Ferreira2020:
 \begin{multline}
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;[@vasicek1976test; @Bert1992; @Wieczorkowski1999; @correa1995new], who proposed estimators based on spacings.
+The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including @vasicek1976test, @Bert1992, @Wieczorkowski1999, and @correa1995new, who proposed estimators based on spacings.
 
-Vasicek&nbsp;[@vasicek1976test], used $f(z)=p$  to express $ H(Z)$ as
+@vasicek1976test expressed $H(Z)$ as
 \begin{equation*}
@@
 \end{equation*}
-where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics&nbsp;[@AlOmari2019].
+where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is then estimated as a function of the order statistics&nbsp;[@AlOmari2019].
 
@@
 %\label{E:VanEs}
-	\widehat{H}_{V}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 	\end{equation*}
@@
 
-Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es&nbsp;[@Bert1992], who proposed a new estimator of entropy given by:
+Several authors studied adaptations and improvements to Vasicek's estimator, including @Bert1992, who proposed the following estimator:
 \begin{multline}
@@
 
-Van Es proved that, under general conditions,\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
+Van Es proved that, under general conditions, \eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
 The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.
@@
 # Hypothesis testing based on non-parametric entropy
-General asymptotic results for functions of spacings are detailed in&nbsp;[@Khashimov1990], while VanEs&nbsp;[@Bert1992] has developed a correction for the case of Shannon entropy.
+General asymptotic results for functions of spacings are detailed @Khashimov1990, while @Bert1992 developed a correction for the case of Shannon entropy.
 Following the work of these authors, the next result applies:
@@
 Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
-Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
+Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
 \begin{equation}
@@
 \end{equation}
-where $o(\cdot)$ represents the little-o and $\widehat{H}_{\text{VE}}$ is defined in expression \eqref{E:VanEs}.
-
+where $o(\cdot)$ represents the little-o.
 \end{lemma}
 
-Let us consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
-
-\begin{equation}
-\text{(i)}\, \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \, \, \text{(ii)}\, \mathcal{H}_1:T_{\mathcal{D}}> D_0, \, \, \text{or}\, \,  \text{(iii)}\, \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
-\end{equation}
+Consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
+\begin{align}
+\mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\ 
+\mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\
+\mathcal{H}_1 &: T_{\mathcal{D}}< D_0. 
+\end{align}
 
@@
 \begin{equation}
-Z_{m,n} = \frac{\sqrt{n}(\widehat{H}_{\text{VE}}-D_0)}{\sqrt{\operatorname{Var}(\log f(Z))}},
+Z_{m,n} = \frac{\sqrt{n}\big(\widehat{H}_{\text{VE}}-D_0\big)}{\sqrt{\operatorname{Var}\big(\log f(Z)\big)}},
 \end{equation}
-So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
 
@@
 \end{multline*}
-for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
+for a sequence of cumulative distribution functions $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
 
@@
 We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
-We performed experiments to observe convergence under different scenarios, where each employed different sample sizes, i.e., $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
+We performed experiments to observe convergence under different scenarios, where each employed different sample sizes: $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
 
@@
 
-```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
 L <- c(1, 3, 8, 12, 100)
@@
   labs(col = "Looks") +
-  xlab(expression(paste(mu)))
+  xlab(expression(paste(mu))) +
+  theme(text=element_text(family="serif"))
 
@@
 
-Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $\mathcal{G}_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
+Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
 
@@
 ```
-As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the GI0 distribution.
+As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
 We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
@@
 
-<!-- conference papers do not normally have an appendix -->
-
 # Acknowledgment {#acknowledgment}

### 2023-11-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Cropped PDF

@@
 
-## Parametric \& Non-Parametric Shannon Entropy
-
+## The Shannon Entropy
 The parametric representation of Shannon entropy for a system described by a continuous random variable is:
@@
 where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.
+
+In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
+
+```{r FunctionsDefinitions, echo=FALSE}
+entropy_gamma_sar <- function(L, mu) {
+
+    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
+
+}
+
+entropy_gI0 <- function(mu, alpha, L) {
+
+  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
+  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
+
+  entropy <- term1 + term2 
+  return(entropy)
+}
+```
+
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+L <- c(1, 3, 8, 12, 100)
+
+L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")
+
+mu <- seq(0.1, 10, length.out = 500)
+
+entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+muEntropy <- data.frame(mu, entropies)
+
+muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
+  geom_line() +
+  theme_minimal() +
+  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
+  labs(col = "Looks") +
+  xlab(expression(paste(mu))) +
+  theme(text=element_text(family="serif"))
+
+```
+
+Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
+
+```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
+knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
+```
+As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
+We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
+
+## Estimation of the Shannon Entropy
 
@@
 
-In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
-
-```{r FunctionsDefinitions, echo=FALSE}
-entropy_gamma_sar <- function(L, mu) {
-
-    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
-
-}
-
-entropy_gI0 <- function(mu, alpha, L) {
-
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-
-  entropy <- term1 + term2 
-  return(entropy)
-}
-```
-
-```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
-L <- c(1, 3, 8, 12, 100)
-
-L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")
-
-mu <- seq(0.1, 10, length.out = 500)
-
-entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
-
-muEntropy <- data.frame(mu, entropies)
-
-muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
-
-ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
-  geom_line() +
-  theme_minimal() +
-  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
-  labs(col = "Looks") +
-  xlab(expression(paste(mu))) +
-  theme(text=element_text(family="serif"))
-
-```
-
-Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
-
-```{r 3d_GIO, fig.align="center",  out.width = "120%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
-knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
-```
-As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
-We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
-
 # Conclusion

### 2023-11-22 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Caption of Fig. 2

@@
 
-```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="Simulation of entropy for ${G}_I^0$. ", fig.show="hold",  fig.pos="hbt"}
+```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"}
 knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")

### 2023-11-23 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
Minor typo
Fig 1 revised

@@
   \label{E:entropy2}
-  H_(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
+  H(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
 \end{equation}
@@
 
-```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
+```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="The Shannon Entropy under the Gamma SAR model."}
 L <- c(1, 3, 8, 12, 100)
 
-L_labels <- c("L=1", "L=3", "L=8", "L=12", "L=100")
+L_labels <- c(expression(italic(L)==1), 
+              expression(italic(L)==3), 
+              expression(italic(L)==8), 
+              expression(italic(L)==12), 
+              expression(italic(L)==100))
 
@@
 ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
-  geom_line() +
+  geom_line(linewidth=2) +
   theme_minimal() +
@@
   xlab(expression(paste(mu))) +
-  theme(text=element_text(family="serif"))
+  theme(text=element_text(family="serif", size = 14),
+        legend.position = "top")
 

### 2023-11-24 Code/R/RMarkdown/Report_Estimators.Rmd
update paper and codes

@@
 library(ggplot2)
-
 library(reshape2)
-#library(plotly)
 library(knitr)

### 2023-11-24 Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R

@@ -2,7 +2,7 @@
 
 
 
-source("../MainFunctions/al_omari_1_estimator.r")
+#source("../MainFunctions/al_omari_1_estimator.r")
 
 
 bootstrap_al_omari_1_estimator <- function(x, B){

### 2023-11-24 Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R

@@ -2,7 +2,7 @@
 
 
 
-source("../MainFunctions/al_omari_2_estimator.r")
+#source("../MainFunctions/al_omari_2_estimator.r")
 
 
 bootstrap_al_omari_2_estimator <- function(x, B){

### 2023-11-24 Code/R/PlottingFunctions/plot_3d_entropy_with_orca.R

@@ -42,4 +42,4 @@ fig <- fig %>% layout(
 fig
 
 #  PDF
-orca(fig, file = "Entropy_plot_3d_.pdf")
+orca(fig, file = "Entropy_plot_3d_1.pdf")

### 2023-11-24 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
some small changes

@@
 abstract: |
-  SAR Data are affected by speckle, a non-additive and non-Gaussian interference noise-like pattern.
+  SAR Data are affected by speckle, a non-additive and non-gaussian interference noise-like pattern.
   The type of distribution these data follow is paramount for their processing and analysis.
@@
   The $\mathcal{G}^0$ distribution is one of the most successful models for SAR data. 
-  It includes the Gamma law as particular case which arises in the presence of fully developed speckle.
+  It includes the Gamma law as a particular case which arises in the presence of fully developed speckle.
   Although the latter is a limit distribution of the former, using the same estimation technique for the more general model is numerically unfeasible.
@@
    - \usepackage[utf8]{inputenc}
+   - \usepackage{hyperref}
+   - \hypersetup{draft}
+   - \usepackage{graphicx}
+   - \usepackage{float}
+   - \usepackage{booktabs}
+   - \usepackage{array}
+   - \usepackage{multirow}
+   - \usepackage{wrapfig}
+   - \usepackage{colortbl}
+   - \usepackage{pdflscape}
+   - \usepackage{xcolor}
+   - \usepackage{amsmath}
+   - \usepackage{mathabx}
 
 bibliography:  ../../Common/references.bib
-#csl: "ieee.csl"
+csl: "ieee.csl"
 output: 
@@
 
-#citation_sorting: none   ## used as sorting option of the biblatex package (if selected)
+#citation_sorting: none   
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+# library(ggplot2)
+# library(ggthemes)
+# library(reshape2)
+# library(plotly)
+# library(knitr)
+# # library(rgl)
+# library(gtools)
+# library(stats4)
+# library(rmutil)
+# library(gsl)
+
 library(ggplot2)
-library(ggthemes)
+
 library(reshape2)
-library(plotly)
+#library(plotly)
 library(knitr)
-# library(rgl)
+library(pandoc)
+library(gridExtra)
+library(tidyr)
 library(gtools)
@@
 library(rmutil)
-library(gsl)
+library(scales)
+library(tidyr)
+library(gtools)
+library(stats4)
+library(rmutil)
 library(invgamma)
+library(tidyverse)
+library(scales)
+library(RColorBrewer)
+library(ggsci)
+library(wesanderson)
+library(ggpubr)
+library(patchwork)
+library(dplyr)
+options(kableExtra.latex.load_packages = FALSE)
+library(devtools)
+devtools::install_github("haozhu233/kableExtra")
+library(kableExtra)
+library(ggthemes)
 
-theme_set(theme_pander() +
+theme_set(theme_minimal() +
             theme(text=element_text(family="serif"),
-                  legend.position = "top")
+                  legend.position = "bottom")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
 )
+
+# theme_set(theme_pander() +
+#             theme(text=element_text(family="serif"),
+#                   legend.position = "top")
+#           )
+
+source("../../../Code/R/MainFunctions/gamma_sar_sample.r")
+source("../../../Code/R/MainFunctions/entropy_gamma_sar.r")
+source("../../../Code/R/MainFunctions/entropy_gI0.r")
+source("../../../Code/R/MainFunctions/gi0_sample.r")
+
+source("../../../Code/R/MainFunctions/van_es_estimator.r")
+source("../../../Code/R/MainFunctions/correa_estimator.r")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.r")
+source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.r")
+source("../../../Code/R/MainFunctions/vasicek_estimator.r")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.r")
+source("../../../Code/R/MainFunctions/al_omari_2_estimator.r")
+
+source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.r")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.r")
+#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
+source("../../../Code/R/Programs/functions_sample_bias_mse.R")#
+
 ```
@@
 
+\newcommand{\bias}{\operatorname{Bias}}
+
 # Introduction {#sec:Introduction}
 
-Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;[@Cassetti2022].
-However, the utility of SAR data depends on a thorough understanding of the their statistical properties.
+Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;[@Mu2019].
+However, the utility of SAR data depends on a thorough understanding of their statistical properties.
 Speckle is part of SAR data because of the imaging process' coherent nature.
@@
 When deciding which model is the best, practitioners face a problem.
-On the one hand, if they opt for the Gamma law when the data came from the $\mathcal{G}^0$ distribution, they loose all the information about the number of scatterers, which is revealed by one of the parameters of the latter model [@Yue2021].
+On the one hand, if they opt for the Gamma law when the data come from the $\mathcal{G}^0$ distribution, they lose all the information about the number of scatterers, which is revealed by one of the parameters of the latter model&nbsp;[@Yue2021].
 On the other hand, if they apply the $\mathcal{G}^0$ distribution under fully developed speckle,
 maximum likelihood estimation is tricky: 
-bias increases making estimation unreliable [@VasconcellosFrerySilva:CompStat], and
-the likelihood is flat, so numerical optimization may not converge [@FreryCribariSouza:JASP:04].
+bias increases making estimation unreliable&nbsp;[@VasconcellosFrerySilva:CompStat], and
+the likelihood is flat, so numerical optimization may not converge&nbsp;[@FreryCribariSouza:JASP:04].
+The two-stage technique we propose tackles this problem by using the entropy as a proxy to decide which is the best model.
 
-The two-stage technique we propose tackles this problem by using the Entropy as a proxy to decide which is the best model.
+<!-- The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics. -->
+<!-- Shannon introduced it for a random variable in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty.  -->
+<!-- In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;[@Wieczorkowski1999].
+-->
 
-The entropy is a fundamental concept in information theory with broad applications to pattern recognition, statistical physics, stochastic dynamics, and statistics.
-Shannon introduced it for a random variables in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty. 
-In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;[@Wieczorkowski1999].
+Estimating the entropy faces practical challenges, particularly when the model is unknown; non-parametric methods are utilized in such cases.
+Among non-parametric approaches,&nbsp;@Subhash2021 discussed the use of spacing methods.
+This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.
+We extend the exploration of non-parametric entropy estimators by incorporating enhanced bootstrap methodologies.
 
-Estimating the entropy faces practical challenges, particularly when the model is unknown; nonparametric methods are utilized in such cases.
-<!-- Instead, techniques like histograms or kernel density estimators are employed to estimate the pdf directly, followed by entropy calculation using numerical or Monte Carlo integration&nbsp;[@Lombardi2016].
--->
-Among nonparametric approaches, @Zamanzade2012 discussed the use of spacing methods.
-This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.
-
-In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data. 
-The first stage tests the hypothesis that the data follow the Gamma distribution, i.e., we are in the presence of fully developed speckle. 
-If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.
-
-<!-- The significance of selecting an appropriate statistical model and estimation technique is well recognized.
-In order to address uncertainties in the data distribution, we employ a non-parametric approach.
--->
-<!-- Specifically, we focus on the entropy estimation considering estimators based on spacing. -->
+<!-- In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data.  -->
+<!-- The first stage tests the hypothesis that the data follow the Gamma distribution, i.e., we are in the presence of fully developed speckle.  -->
+<!-- If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.  -->
 
 The article is structured as follows: 
-In Section&nbsp;\ref{sec:Background}, we provide an overview of statistical modeling for Intensity SAR data and the estimation of both parametric and non-parametric Shannon entropy.
+Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data. Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy. 
+In Section&nbsp;\ref{sec:results}, we present experimental results. 
+Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.
 
@@
 \end{align*}
-Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ law is
+Thus, the probability density function that characterize the $G_I^0(\mu, \alpha, L)$ law is
 \begin{multline}
@@
   \label{E:entropy2}
-  H(Z)=-\int_{-\infty }^\infty \ f(z)\log f(z)\, \mathrm{d}z,
+  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
 \end{equation}
@@
 Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on @Cassetti2022 and @Ferreira2020:
-\begin{multline}
-\label{E:E-gamma}
-H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
-\end{multline}
-\begin{multline}
-\label{E:E-GIO}
-H_{\mathcal{G}_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
--\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
--(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L
-\end{multline}
-where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.
-
-In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
+\begin{align*}
+H_{\Gamma_{\text{SAR}}}(L, \mu) &= L - \ln L + \ln\Gamma(L) + (1-L)\psi^{(0)}(L) + \ln \mu, \\
+H_{\mathcal{G}_I^0}(\mu, \alpha, L) &= L - \ln L + \ln\Gamma(L) + (1-L)\psi^{(0)}(L) + \ln \mu \\
+&\quad - \ln\Gamma(L-\alpha) + (L-\alpha)\psi^{(0)}(L-\alpha)- L\\
+&\quad - (1-\alpha)\psi^{(0)}(-\alpha) + \ln (-1-\alpha) + \ln\Gamma(-\alpha)
+\end{align*}
+where $\psi^{(0)}(\cdot)$ is the digamma function. In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
 
@@
   xlab(expression(paste(mu))) +
-  theme(text=element_text(family="serif", size = 14),
-        legend.position = "top")
+  theme(text=element_text(family="serif"),
+        legend.position = "bottom")
 
@@
 ```
-As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the Entropy of the $G_I^0$ distribution. 
-We can identify regions where Entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
+As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution. 
+We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
 
@@
 
-The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including @vasicek1976test, @Bert1992, @Wieczorkowski1999, and @correa1995new, who proposed estimators based on spacings.
-
-@vasicek1976test expressed $H(Z)$ as
+One of the earliest non-parametric estimators relying on spacings was introduced by Vasicek&nbsp;[@vasicek1976test].
+Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
 \begin{equation*}
-	H(Z)= \int_0^1 \log\frac{\mathrm{d}}{\mathrm{d}p}Q(p)\mathrm{d}p,
-\end{equation*}
-where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is then estimated as a function of the order statistics&nbsp;[@AlOmari2019].
-
-Assuming that  $\bm{Z}=(Z_1, Z_2, \ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
-\begin{equation*}
-%\label{E:VanEs}
-	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\log\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+\label{E:Vas}
+	\widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 	\end{equation*}
@@
 
-Several authors studied adaptations and improvements to Vasicek's estimator, including @Bert1992, who proposed the following estimator:
-\begin{multline}
-\label{E:VanEs}
-	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]\\
-	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
-\end{multline}
+Several authors have explored adaptations to Vasicek's estimator. In this work, we consider three entropy estimators known for their superior performance:
 
-Van Es proved that, under general conditions, \eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
-The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.
+* Correa [@correa1995new]: $\widehat{H}_{\text{C}}$.
 
-# Hypothesis testing based on non-parametric entropy
-General asymptotic results for functions of spacings are detailed @Khashimov1990, while @Bert1992 developed a correction for the case of Shannon entropy.
+* Ebrahimi [@Ebrahimi1994]: $\widehat{H}_{\mathrm{E}}(\bm{Z})$.
+
+* Al-Omari [@IbrahimAlOmari2014]: $\widehat{H}_{\mathrm{AO}}(\bm{Z})$.
+
+These estimators, along with others, are described and studied in&nbsp;[@Cassetti2022].
+
+<!-- * Correa [@correa1995new]: -->
+<!-- \begin{equation*} -->
+<!-- \widehat{H}_{\text{C}}(\bm{Z}) = -\frac{1}{n} \sum_{i=1}^n \ln \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\widebar{Z}_{(i)}\right)}{n \sum_{j=i-m}^{i+m}\left(Z_{(j)}-\widebar{Z}_{(i)}\right)^2}, -->
+<!-- \end{equation*} -->
+<!-- where $\widebar{Z}_{(i)} = (2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}$. -->
+
+<!-- * Ebrahimi [@Ebrahimi1994]: -->
+<!-- \begin{equation*} -->
+<!-- \widehat{H}_{\mathrm{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\tau_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right], -->
+<!-- \end{equation*} -->
+<!-- where -->
+<!-- $$ -->
+<!-- \tau_i= \begin{cases}1+(i-1) / m & \text { if } 1 \leq i \leq m, \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 1+(n-i) / m & \text { if } n-m+1 \leq i \leq n.\end{cases} -->
+<!-- $$ -->
+
+<!-- * Al-Omari [@IbrahimAlOmari2014]: -->
+<!-- \begin{equation*} -->
+<!-- \widehat{H}_{\mathrm{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right], -->
+<!-- \end{equation*} -->
+<!-- where -->
+<!-- $$ -->
+<!-- \omega_i= \begin{cases}3 / 2 & \text { if } 1 \leq i \leq m, \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 3 / 2 & \text { if } n-m+1 \leq i \leq n.\end{cases} -->
+<!-- $$ -->
+
+## Enhanced Bootstrap Technique
+
+We employ the bootstrap technique to refine the precision of existing non-parametric entropy estimators.
+This approach involves generating new datasets through resampling with repetition from an existing one.
+
+Let's assume that non-parametric entropy estimators \(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
+\begin{equation}
+\label{Eq:bias1}
+\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta.
+\end{equation}
+Our objective is to devise unbiased estimators with reduced variance. To achieve this, we introduce an "ideal estimator" \(\check{\theta}(\bm{Z})\) using the bias information:
+\begin{equation}
+\label{Eq:bias2}
+\widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big).
+\end{equation}
+However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it does not depend on the true parameter \(\theta\), prompting the formulation of a new unbiased  estimator \(\widetilde{H}\), from \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:
+\begin{align*}
+\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
+\end{align*}
+where $B$ represents the number of replications in the bootstrap technique.
+Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.
+
+# Hypothesis testing based on non-parametric entropy {#sec:test}
+General asymptotic results for functions of spacings are detailed&nbsp;@Khashimov1990, while&nbsp;@Bert1992 developed a correction for the case of Shannon entropy.
 Following the work of these authors, the next result applies: 
-
 \begin{lemma}
@@
 Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
-\begin{equation}
-\sqrt{n}\,\Big(\widehat{H}_{\text{VE}}+\int_{-\infty}^\infty f(z)\log f(z) \mathrm{d}z\Big)
+\begin{equation*}
+\sqrt{n}\,\Big(\label{Eq:bias_t}
+\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
 \xrightarrow[]{\mathcal{D}}
-\mathcal{N}(0,\operatorname{Var}(\log f(Z))),
-\end{equation}
-where $o(\cdot)$ represents the little-o.
+\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
+\end{equation*}
 \end{lemma} 
-
 Consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
-\begin{align}
+\begin{align*}
 \mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\ 
@@
 \mathcal{H}_1 &: T_{\mathcal{D}}< D_0. 
-\end{align}
-
+\end{align*}
 For this purpose, we can use the test statistics:
-\begin{equation}
-Z_{m,n} = \frac{\sqrt{n}\big(\widehat{H}_{\text{VE}}-D_0\big)}{\sqrt{\operatorname{Var}\big(\log f(Z)\big)}},
-\end{equation}
+\begin{equation*}
+Z_{m,n} = \frac{\sqrt{n}\big(\label{Eq:bias4}
+\widetilde{H}-D_0\big)}{\sqrt{\operatorname{Var}\big(\ln f(Z)\big)}},
+\end{equation*}
 so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
@@
 
-# Results
+# Results {#sec:results}
 
-We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases.
+Simulations are conducted using $\mathcal{G}_I^0$ distribution, with 200 synthetic samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
+In the case of the bootstrap technique, each sample is replicated 100 times through bootstrapping.
+We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
 
-We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
-We performed experiments to observe convergence under different scenarios, where each employed different sample sizes: $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.
+In Fig.
+\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
+The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
 
-<!-- #For each sample size, we performed $1.000$ samples. Fig.&nbsp;\ref{fig:convergence} shows convergence of mean non-parametric entropies for $\mu=3$ and $L=2$. -->
+The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.
+The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.
 
-# Conclusion
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6,fig.height=5}
+# Define sample sizes for analysis
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(9, 25, 49, 81, 121)
 
-The conclusion goes here.
+# Number of replications
+R <- 200
 
-# Acknowledgment {#acknowledgment}
+# Number of bootstrap replications
+B <- 100
+mu_values <- c(1, 10)
+alpha <- -20
+L <- 8
+# \widehat{H}_{\text{C}}, \widehat{H}_{\text{E}} \widehat{H}_{\text{AO}}, \widehat{H}_{\text{V}}
+# \widetilde{H}_{C}, \widetilde{H}_{E}, \widetilde{H}_{AO}
+estimators <- list(
+  "Correa" = correa_estimator,
+  "Ebrahimi" = ebrahimi_estimator,
+  "Al Omari" = al_omari_1_estimator,
+  "Correa Bootstrap" = bootstrap_correa_estimator,
+  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
+  "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
+)
 
-The authors would like to thank...
+combined_plot <- generate_plot_gi0(sample_sizes, R, B, mu_values,alpha, L, estimators,  ncol = 1, nrow = 2)
+
+# Print the combined plot with sanitize=FALSE
+print(combined_plot)
+
+```
+
+```{r Table_gi01, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(9, 25, 49, 81, 121)
+R <- 200
+B <- 100
+mu_values <- c(1,  10)
+L <- 8
+alpha<- -20
+
+# Define a list of estimators
+estimators <- list(
+  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
+  "Correa Bootstrap" = bootstrap_correa_estimator,
+  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
+  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
+  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
+  "Al Omari  Bootstrap" = bootstrap_al_omari_1_estimator
+  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
+)
+
+# 
+combined_results <- NULL
+
+for (mu_val in mu_values) {
+  # 
+  results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val,alpha,  L, estimators)
+
+  # 
+  results <- cbind(mu = mu_val, results)
+
+  # 
+  combined_results <- bind_rows(combined_results, results)
+}
+
+# 
+reshaped_results <- combined_results %>%
+  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
+#\widetilde{H}_{i}
+
+colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$")
+
+print(
+  kbl(
+    reshaped_results,
+    caption = "Bias and MSE of bootstrap estimators for $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.",
+    format = "latex",
+    booktabs = TRUE,
+    align = "c",
+    escape = FALSE, 
+    digits = 4,  
+    label = "table2"  # 
+  ) %>%
+    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
+    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")# %>%
+  %>%
+    kable_styling(latex_options = c( "striped")) 
+   # column_spec(1, bold = TRUE) 
+)
+
+```
+
+```{r Table_gama_sar12, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Tamaños de muestra
+sample_sizes <- c(9, 25, 49)
+R <- 100
+mu <- 10
+L <- 5
+alpha <- -400
+
+# Entropía verdadera de Gamma SAR
+true_entropy <- entropy_gamma_sar(L, mu)
+#
+# Función para generar muestras
+generate_samples <- function(sample_size, replication, mu, alpha, L) {
+  samples <- vector("list", replication)
+  for (r in 1:replication) {
+    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)#
+  }
+  return(samples)
+}
+
+#colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$")
+# 
+calculate_entropy_and_test_table <- function(sample_sizes, R, mu, alpha, L) {
+  estimators <- list(
+    #" " = bootstrap_vasicek_estimator,
+    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
+    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
+    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
+  )
+
+  output <- data.frame(
+    SampleSize = integer(0),
+    Estimator = character(0),
+    MeanEntropy = numeric(0),
+    ZStatistic = numeric(0),
+    PValue = numeric(0)
+  )
+
+  for (ssize in sample_sizes) {
+    samples <- generate_samples(ssize, R, mu, alpha, L)
+
+    for (estimator_name in names(estimators)) {
+      estimator <- estimators[[estimator_name]]
+      v.entropy <- numeric(R)
+
+      for (r in 1:R) {
+        sample <- samples[[r]]
+
+        if (grepl(" ", estimator_name)) {
+          v.entropy[r] <- estimator(sample, B = 30)
+        } else {
+          v.entropy[r] <- estimator(sample)
+        }
+      }
+
+      mean_entropy <- mean(v.entropy)
+
+      # 
+      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
+      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
+
+      output <- rbind(
+        output,
+        data.frame(
+          SampleSize = ssize,
+          Estimator = estimator_name,
+          MeanEntropy = round(mean_entropy, 5),
+          ZStatistic = round(z_statistic, 5),
+          PValue = round(p_value, 5)
+        )
+      )
+    }
+  }
+
+  # 
+  colnames(output) <- c("$n$", "Estimator", "Mean Entropy", "$Z$ Statistic", "$p$ Value")
+
+  # Crear la tabla con kbl
+  table_result <- kbl(
+    output,
+    caption = "Hypothesis Testing for $\\mathcal{G}_I^0$, $\\mu=10$, $L=5$, $\\alpha=-400$ , $H_{\\Gamma_{\\text{SAR}}}=2.846$.",
+    format = "latex",
+    booktabs = TRUE,
+    align = "c",
+    escape = FALSE,
+    digits = 4,
+    label = "table_hipotesis"
+  ) %>%
+    #add_header_above(c(" ", " ", "Estimador" = 1, " ", " ")) %>%
+    collapse_rows(columns = 1:3,latex_hline = "major", valign = "middle")  %>%
+    kable_styling(latex_options = c("striped"))
+
+  return(table_result)
+}
+
+# 
+result_table <- calculate_entropy_and_test_table(sample_sizes, R, mu, alpha, L)
+print(result_table)
+
+```
+
+A hypothesis testing was conducted using non-parametric entropy estimators as test statistics.
+The results in &nbsp;\ref{tab:table_hipotesis} show that data from the $\mathcal{G}_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=10$, $L=5$, and $\alpha= -400$.
+The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.846$.
+It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution.
+Hypothesis test results were conducted with a 95% confidence level.
+The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy.
+The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above 25, suggesting that the data is consistent with the null hypothesis.
+
+# Conclusion {#sec:conclusion}
+
+In this study, three estimators renowned for their robust performance across diverse distributions were chosen for evaluation.
+We examine the impact of applying bootstrap techniques on their precision by comparing each estimator's performance with its bootstrap-enhanced counterpart, utilizing metrics such as bias and MSE.
+The effectiveness of bootstrap-enhanced non-parametric entropy estimators was observed, demonstrating efficacy in most instances.
+Nonetheless, it is essential to recognize that the applicability of this technique may not be universal across all estimation methods.
+
+It is worth noting that this analysis represents an initial exploration of SAR Intensity data, and future work will include a more in-depth analysis of effect size and statistical power.
+Additionally, exploring the impact of the $\alpha$ parameter on estimates and conducting more extensive analyses to assess the generalization of results to different parameter configurations is suggested.
 

### 2023-11-26 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Rename and create new working version

--- 2023-11-24 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
 
-One of the earliest non-parametric estimators relying on spacings was introduced by Vasicek&nbsp;[@vasicek1976test].
+One of the earliest non-parametric estimators relying on spacings was introduced by @vasicek1976test. 
 Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
@@
 
-* Correa [@correa1995new]: $\widehat{H}_{\text{C}}$.
+* @correa1995new: $\widehat{H}_{\text{C}}$.
 
-* Ebrahimi [@Ebrahimi1994]: $\widehat{H}_{\mathrm{E}}(\bm{Z})$.
+* @Ebrahimi1994: $\widehat{H}_{\mathrm{E}}(\bm{Z})$.
 
-* Al-Omari [@IbrahimAlOmari2014]: $\widehat{H}_{\mathrm{AO}}(\bm{Z})$.
+* @IbrahimAlOmari2014: $\widehat{H}_{\mathrm{AO}}(\bm{Z})$.
 
-These estimators, along with others, are described and studied in&nbsp;[@Cassetti2022].
+These estimators, along with others, are described and studied in @Cassetti2022.
 
@@
 \end{equation}
-However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it does not depend on the true parameter \(\theta\), prompting the formulation of a new unbiased  estimator \(\widetilde{H}\), from \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:
+However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\). 
+From \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:
 \begin{align*}
@@
 \end{align*}
-where $B$ represents the number of replications in the bootstrap technique.
+where $B$ is the number of replications in the bootstrap technique.
 Applying this methodology, the original estimators by Correa, Ebrahimi, and Al-Omari are now denoted as the proposed bootstrap-enhanced versions: $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{E}}$, and $\widetilde{H}_{\text{AO}}$, respectively.
@@
 
-Simulations are conducted using $\mathcal{G}_I^0$ distribution, with 200 synthetic samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
-In the case of the bootstrap technique, each sample is replicated 100 times through bootstrapping.
+Simulations are conducted using $\mathcal{G}_I^0$ distribution, with $200$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
+In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
 We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6,fig.height=5}
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6, fig.height=5}
 # Define sample sizes for analysis
@@
 A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
-The results in &nbsp;\ref{tab:table_hipotesis} show that data from the $\mathcal{G}_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=10$, $L=5$, and $\alpha= -400$.
+The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $\mathcal{G}_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=10$, $L=5$, and $\alpha= -400$.
 The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.846$.  
 It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution. 
-Hypothesis test results were conducted with a 95% confidence level.
+Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 
 The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy. 
-The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above 25, suggesting that the data is consistent with the null hypothesis.
+The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above $25$, suggesting that the data are consistent with the null hypothesis.
 

### 2023-12-09 Code/R/RMarkdown/report2_plots_means.Rmd
adding improvements for code and paper

---
title: "Report: Exploring Non-Parametric Entropy Estimators and Bootstrap Enhancements"
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
#library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")
source("../MainFunctions/gi0_sample.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/adaptive_correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_estimator_m.r")
source("../MainFunctions/al_omari_2_estimator.r")
source("../MainFunctions/yee_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator_opt.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
source("../MainFunctions/bootstrap_yee_estimator.r")
source("../MainFunctions/bootstrap_yee_estimator_optimized.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

\newcommand{\bias}{\operatorname{Bias}}

# Mean Entropy for Estimators

```{r Plot_mean1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121, 225)
R <- 100
mu <- 1
L <- 1

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
     "Correa" = correa_estimator,
     "Ebrahimi" = ebrahimi_estimator,
     "Al Omari 1" = al_omari_1_estimator,
      "Yee" = yee_estimator,
      "Correa Bootstrap" = bootstrap_correa_estimator,
     "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_mean2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy Gamma SAR for $L= 2$ and $\\mu=5$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 5
L <- 2

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

# Define a list of estimators
  estimators <- list(
   # "Van Es" = van_es_estimator,
   # "Correa" = correa_estimator,
   # "Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
   # "Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
   #"Al OmariA " = al_omari_estimator_m,
    #"Al Omari 2" = al_omari_2_estimator,
    "Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator,
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
    #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

## Results for  Nonparametric Estimators with  $\mathcal{G}_I^0$

```{r Plot_GI0_mean, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for GI0, with $L= 2$, $\\mu=5$ and $\\alpha=-300$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 5
L <- 2
alpha <- -300

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gI0(mu, alpha, L)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    #"Correa" = correa_estimator,
    #"Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
    #"Al OmariA " = al_omari_estimator_m,
    #"Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator, 
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
   # "Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al O Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```
```{r Plot_GI0_mean_p, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for GI0, with $L= 2$, $\\mu=5$ and $\\alpha=-1000$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 5
L <- 2
alpha <- -1000

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gI0(mu, alpha, L)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    #"Correa" = correa_estimator,
    #"Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
    #"Al OmariA " = al_omari_estimator_m,
    #"Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator, 
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
   # "Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al O Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_GI0_mean_y, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for GI0, with $L= 5$, $\\mu=10$ and $\\alpha=-400$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c( 25, 49, 81, 121)
R <- 100
mu <- 10
L <- 5
alpha <- -400

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gI0(mu, alpha, L)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    #"Correa" = correa_estimator,
    #"Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
    #"Al OmariA " = al_omari_estimator_m,
    #"Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator, 
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
   # "Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al O Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

In the figure we can observe that when the parameter $\alpha$ goes to $-\infty$, the entropy of $\mathcal{G}_I^0$ is close to the entropy of $\Gamma_{\text{SAR}}$.

```{r Plot_GI0_mean_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for GI0, with $L= 1$,  $\\mu=1$ and $\\alpha=-300$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 100
mu <- 1
L <- 1
alpha <- -300

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gI0(mu, alpha, L)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    #"Correa" = correa_estimator,
    #"Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
    #"Al OmariA " = al_omari_estimator_m,
    "Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator, 
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
   # "Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al O Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Simulated_data_gi0, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1, 3, 5, 20)
alpha <- -20
L <- 1

estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari" = al_omari_1_estimator,
  "Yee" = yee_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
)

calculate_results_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
  results_list <- list()

  for (mu_val in mu_values) {

    results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

    results_list[[as.character(mu_val)]] <- df
  }

  return(results_list)
}

results_gi0 <- calculate_results_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)

save(results_gi0, file = "./Data/results_gi0.Rdata")

```

```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=1$, $\\alpha=-20$.", fig.width=9, fig.height=5}

load("./Data/results_gi0.Rdata")

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari","Yee",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
                            "Yee" = expression("$\\widehat{H}_{Y}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 2, nrow = 2)

print(combined_plot_gi0)

```

```{r Simulated_data_gi0_2, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1, 3, 5, 20)
alpha <- -20
L <- 2

estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari" = al_omari_1_estimator,
  "Yee" = yee_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
)

calculate_results_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
  results_list <- list()

  for (mu_val in mu_values) {

    results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

    results_list[[as.character(mu_val)]] <- df
  }

  return(results_list)
}

results_gi0 <- calculate_results_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)

save(results_gi0, file = "./Data/results_gi0_2.Rdata")

```

```{r Plot_bias_mse_gi0_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=2$, $\\alpha=-20$.", fig.width=9, fig.height=5}

load("./Data/results_gi0_2.Rdata")

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari","Yee",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
                            "Yee" = expression("$\\widehat{H}_{Y}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 2, nrow = 2)

print(combined_plot_gi0)

```

```{r Simulated_data_gi0_3, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 100
mu_values <- c(1, 3, 5, 20)
alpha <- -20
L <- 8

estimators <- list(
  "Correa" = correa_estimator,
  "Ebrahimi" = ebrahimi_estimator,
  "Al Omari" = al_omari_1_estimator,
  "Yee" = yee_estimator,
  "Correa Bootstrap" = bootstrap_correa_estimator,
  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
  "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
)

calculate_results_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
  results_list <- list()

  for (mu_val in mu_values) {

    results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

    results_list[[as.character(mu_val)]] <- df
  }

  return(results_list)
}

results_gi0 <- calculate_results_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)

save(results_gi0, file = "./Data/results_gi0_3.Rdata")

```

```{r Plot_bias_mse_gi0_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=8$, $\\alpha=-20$.", fig.width=9, fig.height=5}

load("./Data/results_gi0_2.Rdata")

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari","Yee",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
                            "Yee" = expression("$\\widehat{H}_{Y}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 2, nrow = 2)

print(combined_plot_gi0)

```

### 2023-12-09 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
adding improvements for code and paper

@@
 affiliation:
-  ## Author mode :  use one only of the following --- +
 
-  ## one column per author - using only the institution field
   author-columnar: true # uncomment this line to use
@@
    - \usepackage{mathabx}
+  # - \usepackage{pgf}
+   - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]
 
-bibliography:  ../../Common/references.bib
-csl: "ieee.csl"
 output:
@@
     number_sections: TRUE
+    #citation_package: biblatex
+    citation_package: natbib
 
-#citation_sorting: none   
+bibliography: ../../Common/references.bib
+
+biblio-style: ieeetr
+
+#link-citations: yes
+
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
-# library(ggplot2)
-# library(ggthemes)
-# library(reshape2)
-# library(plotly)
-# library(knitr)
-# # library(rgl)
-# library(gtools)
-# library(stats4)
-# library(rmutil)
-# library(gsl)
-
 library(ggplot2)
-
 library(reshape2)
@@
 library(gridExtra)
-library(tidyr)
 library(gtools)
@@
 library(tidyr)
-library(gtools)
-library(stats4)
 library(rmutil)
@@
 library(tidyverse)
-library(scales)
-library(RColorBrewer)
+#library(RColorBrewer)
 library(ggsci)
-library(wesanderson)
+#library(wesanderson)
 library(ggpubr)
@@
 library(dplyr)
-options(kableExtra.latex.load_packages = FALSE)
+#options(kableExtra.latex.load_packages = FALSE)
 library(devtools)
-devtools::install_github("haozhu233/kableExtra")
+#devtools::install_github("haozhu233/kableExtra")
 library(kableExtra)
 library(ggthemes)
+library(latex2exp)
 
@@
             theme(text=element_text(family="serif"),
-                  legend.position = "bottom")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
 )
-
-# theme_set(theme_pander() +
-#             theme(text=element_text(family="serif"),
-#                   legend.position = "top")
-#           )
 
@@
 
-Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;[@Mu2019].
+Synthetic aperture radar (SAR) has become a fundamental technology for environmental monitoring and disaster management because of its ability to provide daytime and nighttime imagery in all weather conditions&nbsp;\cite{Mu2019}.
 However, the utility of SAR data depends on a thorough understanding of their statistical properties.
@@
 When deciding which model is the best, practitioners face a problem.
-On the one hand, if they opt for the Gamma law when the data come from the $\mathcal{G}^0$ distribution, they lose all the information about the number of scatterers, which is revealed by one of the parameters of the latter model&nbsp;[@Yue2021].
+On the one hand, if they opt for the Gamma law when the data come from the $\mathcal{G}^0$ distribution, they lose all the information about the number of scatterers, which is revealed by one of the parameters of the latter model&nbsp;\cite{Yue2021}.
 On the other hand, if they apply the $\mathcal{G}^0$ distribution under fully developed speckle,
 maximum likelihood estimation is tricky: 
-bias increases making estimation unreliable&nbsp;[@VasconcellosFrerySilva:CompStat], and
-the likelihood is flat, so numerical optimization may not converge&nbsp;[@FreryCribariSouza:JASP:04].
+bias increases making estimation unreliable&nbsp;\cite{VasconcellosFrerySilva:CompStat}, and
+the likelihood is flat, so numerical optimization may not converge&nbsp;\cite{FreryCribariSouza:JASP:04}.
 The two-stage technique we propose tackles this problem by using the entropy as a proxy to decide which is the best model.
@@
 Estimating the entropy faces practical challenges, particularly when the model is unknown; non-parametric methods are utilized in such cases.
-Among non-parametric approaches,&nbsp;@Subhash2021 discussed the use of spacing methods.
+Among non-parametric approaches,&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
 This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.
@@
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
-The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
-We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;\cite{Frery1997}. 
+The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Cassetti2022}.
+We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
 \begin{align}
@@
 \begin{align}
-	E_{G_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
+	\mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
 	\label{E:rmom}
@@
 
-Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;[@Nascimento2010].
+Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;\cite{Nascimento2010}.
 In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
@@
 
-Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on @Cassetti2022 and @Ferreira2020:
-\begin{align*}
-H_{\Gamma_{\text{SAR}}}(L, \mu) &= L - \ln L + \ln\Gamma(L) + (1-L)\psi^{(0)}(L) + \ln \mu, \\
-H_{\mathcal{G}_I^0}(\mu, \alpha, L) &= L - \ln L + \ln\Gamma(L) + (1-L)\psi^{(0)}(L) + \ln \mu \\
-&\quad - \ln\Gamma(L-\alpha) + (L-\alpha)\psi^{(0)}(L-\alpha)- L\\
-&\quad - (1-\alpha)\psi^{(0)}(-\alpha) + \ln (-1-\alpha) + \ln\Gamma(-\alpha)
-\end{align*}
-where $\psi^{(0)}(\cdot)$ is the digamma function. In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
+Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
+\begin{multline}
+\label{E:E-gamma}
+H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
+\end{multline}
+\begin{multline}
+\label{E:E-GIO}
+H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
+-\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
+-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
+\end{multline}
+where $\psi^{(0)}(\cdot)$ is the digamma function.
 
-```{r FunctionsDefinitions, echo=FALSE}
-entropy_gamma_sar <- function(L, mu) {
-
-    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
-
-}
-
-entropy_gI0 <- function(mu, alpha, L) {
-
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-
-  entropy <- term1 + term2 
-  return(entropy)
-}
-```
+In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
 
@@
 
-One of the earliest non-parametric estimators relying on spacings was introduced by @vasicek1976test. 
+One of the earliest non-parametric estimators relying on spacings was introduced by&nbsp;\cite{vasicek1976test}. 
 Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
@@
 
-* @correa1995new: $\widehat{H}_{\text{C}}$.
+* \cite{correa1995new}: $\widehat{H}_{\text{C}}$.
 
-* @Ebrahimi1994: $\widehat{H}_{\mathrm{E}}(\bm{Z})$.
+* \cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.
 
-* @IbrahimAlOmari2014: $\widehat{H}_{\mathrm{AO}}(\bm{Z})$.
+* \cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.
 
-These estimators, along with others, are described and studied in @Cassetti2022.
-
-<!-- * Correa [@correa1995new]: -->
-<!-- \begin{equation*} -->
-<!-- \widehat{H}_{\text{C}}(\bm{Z}) = -\frac{1}{n} \sum_{i=1}^n \ln \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\widebar{Z}_{(i)}\right)}{n \sum_{j=i-m}^{i+m}\left(Z_{(j)}-\widebar{Z}_{(i)}\right)^2}, -->
-<!-- \end{equation*} -->
-<!-- where $\widebar{Z}_{(i)} = (2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}$. -->
-
-<!-- * Ebrahimi [@Ebrahimi1994]: -->
-<!-- \begin{equation*} -->
-<!-- \widehat{H}_{\mathrm{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\tau_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right], -->
-<!-- \end{equation*} -->
-<!-- where -->
-<!-- $$ -->
-<!-- \tau_i= \begin{cases}1+(i-1) / m & \text { if } 1 \leq i \leq m, \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 1+(n-i) / m & \text { if } n-m+1 \leq i \leq n.\end{cases} -->
-<!-- $$ -->
-
-<!-- * Al-Omari [@IbrahimAlOmari2014]: -->
-<!-- \begin{equation*} -->
-<!-- \widehat{H}_{\mathrm{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right], -->
-<!-- \end{equation*} -->
-<!-- where -->
-<!-- $$ -->
-<!-- \omega_i= \begin{cases}3 / 2 & \text { if } 1 \leq i \leq m, \\ 2 & \text { if } m+1 \leq i \leq n-m, \\ 3 / 2 & \text { if } n-m+1 \leq i \leq n.\end{cases} -->
-<!-- $$ -->
+These estimators, along with others, are described and studied in&nbsp;\cite{Cassetti2022}.
 
@@
 # Hypothesis testing based on non-parametric entropy {#sec:test}
-General asymptotic results for functions of spacings are detailed&nbsp;@Khashimov1990, while&nbsp;@Bert1992 developed a correction for the case of Shannon entropy.
+General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
 Following the work of these authors, the next result applies: 
@@
 
-Simulations are conducted using $\mathcal{G}_I^0$ distribution, with $200$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
+Simulations are conducted using $G_I^0$ distribution, with $200$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
 In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6, fig.height=5}
-# Define sample sizes for analysis
+```{r Simulated_data_gi0, echo=FALSE, message=FALSE}
+
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 # Number of replications
-R <- 200
+R <- 10
 
 # Number of bootstrap replications
-B <- 100
+B <- 10
 mu_values <- c(1, 10)
@@
 L <- 8
-# \widehat{H}_{\text{C}}, \widehat{H}_{\text{E}} \widehat{H}_{\text{AO}}, \widehat{H}_{\text{V}}
-# \widetilde{H}_{C}, \widetilde{H}_{E}, \widetilde{H}_{AO}
+
 estimators <- list(
@@
 
-combined_plot <- generate_plot_gi0(sample_sizes, R, B, mu_values,alpha, L, estimators,  ncol = 1, nrow = 2)
+calculate_results_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
+  results_list <- list()
 
-# Print the combined plot with sanitize=FALSE
-print(combined_plot)
+  for (mu_val in mu_values) {
+
+    results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val, alpha, L, estimators)
+    df <- as.data.frame(results)
+
+    results_list[[as.character(mu_val)]] <- df
+  }
+
+  return(results_list)
+}
+
+results_gi0 <- calculate_results_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)
+
+save(results_gi0, file = "./Data/results_gi0.Rdata")
 
@@
 
-```{r Table_gi01, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#
-set.seed(1234567890, kind = "Mersenne-Twister")
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 200
-B <- 100
-mu_values <- c(1,  10)
-L <- 8
-alpha<- -20
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6, fig.height=5}
 
-# Define a list of estimators
-estimators <- list(
-  #"Van Es Bootstrap" = bootstrap_van_es_estimator,
-  "Correa Bootstrap" = bootstrap_correa_estimator,
-  "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
-  #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
-  #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
-  "Al Omari  Bootstrap" = bootstrap_al_omari_1_estimator
-  #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
-)
+load("./Data/results_gi0.Rdata")
+
+estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
+  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
+                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
+                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
+                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
+                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
+                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
+selected_estimators_latex <- latex_estimator_names[estimators_to_plot]
+
+combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 1, nrow = 2)
+
+print(combined_plot_gi0)
+
+```
+
+```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_gi0.Rdata")
+
+estimators_to_table <- c("Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap")
+
+filtered_results <- purrr::map_dfr(results_gi0, ~ .x %>% filter(Estimator %in% estimators_to_table), .id = "mu")
+
+reshaped_results <- filtered_results %>%
+  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
+
+colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$")
 
 #
-combined_results <- NULL
-
-for (mu_val in mu_values) {
-  # 
-  results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val,alpha,  L, estimators)
-
-  # 
-  results <- cbind(mu = mu_val, results)
-
-  # 
-  combined_results <- bind_rows(combined_results, results)
-}
-
-# 
-reshaped_results <- combined_results %>%
-  pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
-#\widetilde{H}_{i}
-
-colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$")
-
 print(
@@
     reshaped_results,
-    caption = "Bias and MSE of bootstrap estimators for $\\mathcal{G}_I^0$, $L=8$, $\\alpha=-20$.",
+    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
     format = "latex",
@@
     digits = 4,  
-    label = "table2"  # 
+    label = "table2"  
   ) %>%
     add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
-    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")# %>%
-  %>%
-    kable_styling(latex_options = c( "striped")) 
-   # column_spec(1, bold = TRUE) 
+    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
 )
-
 ```
@@
 
-# Tamaños de muestra
-sample_sizes <- c(9, 25, 49)
+sample_sizes <- c( 9, 25, 49, 81, 121)
 R <- 100
-mu <- 10
-L <- 5
-alpha <- -400
+mu <- 5
+L <- 2
+alpha <- -1000
 
-# Entropía verdadera de Gamma SAR
 true_entropy <- entropy_gamma_sar(L, mu)
-#
-# Función para generar muestras
+
 generate_samples <- function(sample_size, replication, mu, alpha, L) {
@@
 
-#colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$",  "$\\widetilde{H}_{C}$", "$\\widetilde{H}_{E}$",  "$\\widetilde{H}_{AO}$")
-# 
 calculate_entropy_and_test_table <- function(sample_sizes, R, mu, alpha, L) {
@@
   )
+
+#   estimators <- list(
+#   "Correa Bootstrap" = bootstrap_correa_estimator,
+#   "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
+#   "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
+# )
 
@@
         if (grepl(" ", estimator_name)) {
-          v.entropy[r] <- estimator(sample, B = 30)
+          v.entropy[r] <- estimator(sample, B = 100)
         } else {
@@
 
-      # 
       z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
@@
 
-  # 
   colnames(output) <- c("$n$", "Estimator", "Mean Entropy", "$Z$ Statistic", "$p$ Value")
 
-  # Crear la tabla con kbl
   table_result <- kbl(
     output,
-    caption = "Hypothesis Testing for $\\mathcal{G}_I^0$, $\\mu=10$, $L=5$, $\\alpha=-400$ , $H_{\\Gamma_{\\text{SAR}}}=2.846$.",
+    caption = "Hypothesis Testing for $G_I^0$, $\\mu=5$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$.",
     format = "latex",
@@
     #add_header_above(c(" ", " ", "Estimador" = 1, " ", " ")) %>%
-    collapse_rows(columns = 1:3,latex_hline = "major", valign = "middle")  %>%
-    kable_styling(latex_options = c("striped"))
+    collapse_rows(columns = 1:3,latex_hline = "major", valign = "middle") # %>%
+    #kable_styling(latex_options = c("striped"))
 
@@
 
-# 
 result_table <- calculate_entropy_and_test_table(sample_sizes, R, mu, alpha, L)
@@
 A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
-The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $\mathcal{G}_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=10$, $L=5$, and $\alpha= -400$.
-The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.846$.  
+The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $G_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=5$, $L=2$, and $\alpha= -1000$.
+The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.493$.  
 It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution. 

### 2023-12-09 Code/R/MainFunctions/al_omari_1_estimator.R

@@ -22,6 +22,11 @@ al_omari_1_estimator <- function(data) {
   return(sum_term / n)
 }
 
+# set.seed(123)
+# test_data <- rnorm(10)
+# result <- al_omari_1_estimator(test_data)
+# print(result)
+
 # Example usage:
 # data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5)
 # result <- al_omari_1_estimator(data)

### 2023-12-09 Code/R/MainFunctions/yee_estimator.R

@@ -1,0 +1,41 @@
+yee_estimator<- function(X) {
+  n <- length(X)
+  H_Y <- numeric(n-1)
+  
+  sorted_X <- sort(X)
+  
+  for (m in 1:(n-1)) {
+    differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
+    term_sum <- sum(log((n/m) * differences))
+    
+    H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
+  }
+  
+  estimated_entropy <- (1/(n-1)) * sum(H_Y)
+  
+  return(estimated_entropy)
+}
+
+# yee_estimator<- function(X) {
+#   n <- length(X)
+#   H_Y <- numeric(n-1)
+#   
+#   sorted_X <- sort(X)
+#   
+#   for (m in 1:(n-1)) {
+#     differences <- sorted_X[(m+1):n] - sorted_X[1:(n-m)]
+#     term_sum <- sum(log((n/m) * differences))
+#     
+#     H_Y[m] <- (1/(n-m)) * term_sum - digamma(m) + log(m)
+#   }
+#   
+#   estimated_entropy <- (1/(n-1)) * sum(H_Y)
+#   
+#   return(estimated_entropy)
+# }
+
+# # Ejemplo de uso con muestra de tamaño 10000
+# set.seed(123)  # Para reproducibilidad
+# X_large <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
+# system.time(entropy_estimate_large <- yee_entropy_estimator_optimized(X_large))
+# print(paste("Estimación de entropía:", entropy_estimate_large))

### 2023-12-09 Code/R/Programs/functions_sample_bias_mse.R

@@ -31,6 +31,8 @@ generate_samples_gi0 <- function(sample_size, replication, mu, alpha, L) {
   return(samples)
 }
 
+
+
 calculate_bias_mse_gi0 <- function(sample_sizes, R,B, mu, alpha, L, estimators) {
   true_entropy <- entropy_gI0(mu, alpha, L)
   
@@ -63,6 +65,219 @@ calculate_bias_mse_gi0 <- function(sample_sizes, R,B, mu, alpha, L, estimators) 
   
   return(output)
 }
+
+
+generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, ncol = 2, nrow = 2) {
+ 
+  plot_list <- list()
+  
+  for (mu_val in mu_values) {
+    
+    df <- results_gi0[[as.character(mu_val)]]
+    
+    
+    df_filtered <- df[df$Estimator %in% names(selected_estimators), ]
+    
+    
+    df_filtered$Estimator <- selected_estimators[df_filtered$Estimator]
+    
+    
+    df_filtered$Estimator <- as.character(df_filtered$Estimator)
+    
+    plot_bias <- ggplot(df_filtered, aes(x = n, y = Bias, color = Estimator)) +
+      geom_hline(yintercept = 0) +
+      geom_point(size = 2) +
+      geom_line(linetype = "solid", linewidth = 0.5) +
+      labs(y = "Bias", x = expression("Sample size"~(n))) +
+      scale_color_discrete(labels = TeX(df_filtered$Estimator)) +
+      annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu_val)), hjust = 4.0, vjust = -0.1, size = 3) +
+      coord_cartesian(clip = 'off')
+    
+    # 
+    if (mu_val != mu_values[1]) {
+      plot_bias = plot_bias + theme(legend.position = "top")
+    }
+    
+    plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
+      geom_hline(yintercept = 0) +
+      geom_point(size = 2) +
+      geom_line(linetype = "solid", linewidth = 0.5) +
+      labs(y = "MSE", x = expression("Sample size"~(n))) +
+      scale_color_discrete(labels = TeX(df_filtered$Estimator)) +
[…]

### 2023-12-10 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
improved code

@@
 # Number of replications
-R <- 10
+R <- 100
 
@@
 
-```{r Table_gama_sar12, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r Simulated_data_test_gi0, echo=FALSE, message=FALSE}
 
 set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(9, 25, 49, 81, 121)
 
-sample_sizes <- c( 9, 25, 49, 81, 121)
+# Number of replications
 R <- 100
-mu <- 5
+
+# Number of bootstrap replications
+B <- 10
+mu_values <- c(5)
+alpha <- -1000
 L <- 2
-alpha <- -1000
 
-true_entropy <- entropy_gamma_sar(L, mu)
-
-generate_samples <- function(sample_size, replication, mu, alpha, L) {
-  samples <- vector("list", replication)
-  for (r in 1:replication) {
-    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)#
-  }
-  return(samples)
-}
-
-calculate_entropy_and_test_table <- function(sample_sizes, R, mu, alpha, L) {
   estimators <- list(
@@
 
-#   estimators <- list(
-#   "Correa Bootstrap" = bootstrap_correa_estimator,
-#   "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
-#   "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
-# )
+calculate_results_test_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
+  results_list <- list()
 
-  output <- data.frame(
-    SampleSize = integer(0),
-    Estimator = character(0),
-    MeanEntropy = numeric(0),
-    ZStatistic = numeric(0),
-    PValue = numeric(0)
-  )
+  for (mu_val in mu_values) {
 
-  for (ssize in sample_sizes) {
-    samples <- generate_samples(ssize, R, mu, alpha, L)
+    results <- calculate_entropy_and_test(sample_sizes, R, B, mu_val, alpha, L, estimators)
+    df <- as.data.frame(results)
 
-    for (estimator_name in names(estimators)) {
-      estimator <- estimators[[estimator_name]]
-      v.entropy <- numeric(R)
-
-      for (r in 1:R) {
-        sample <- samples[[r]]
-
-        if (grepl(" ", estimator_name)) {
-          v.entropy[r] <- estimator(sample, B = 100)
-        } else {
-          v.entropy[r] <- estimator(sample)
-        }
+    results_list[[as.character(mu_val)]] <- df
   }
 
-      mean_entropy <- mean(v.entropy)
-
-      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
-      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
-
-      output <- rbind(
-        output,
-        data.frame(
-          SampleSize = ssize,
-          Estimator = estimator_name,
-          MeanEntropy = round(mean_entropy, 5),
-          ZStatistic = round(z_statistic, 5),
-          PValue = round(p_value, 5)
-        )
-      )
-    }
+  return(results_list)
 }
 
-  colnames(output) <- c("$n$", "Estimator", "Mean Entropy", "$Z$ Statistic", "$p$ Value")
+results_gi0_1 <- calculate_results_test_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)
+
+save(results_gi0_1, file = "./Data/results_gi0_1.Rdata")
+
+```
+
+```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_gi0_1.Rdata")
+
+for (mu_val in mu_values) {
+  results_data <- results_gi0_1[[as.character(mu_val)]]
 
   table_result <- kbl(
-    output,
-    caption = "Hypothesis Testing for $G_I^0$, $\\mu=5$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$.",
+    results_data,
+    caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$."),
     format = "latex",
@@
     label = "table_hipotesis"
+    #label = paste("table_hipotesis", mu_val, sep = "")
   ) %>%
-    #add_header_above(c(" ", " ", "Estimador" = 1, " ", " ")) %>%
-    collapse_rows(columns = 1:3,latex_hline = "major", valign = "middle") # %>%
-    #kable_styling(latex_options = c("striped"))
+    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
 
-  return(table_result)
+  print(table_result)
 }
-
-result_table <- calculate_entropy_and_test_table(sample_sizes, R, mu, alpha, L)
-print(result_table)
 

### 2023-12-12 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
After our work together

@@
     number_sections: TRUE
-    #citation_package: biblatex
     citation_package: natbib
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
 library(ggplot2)
@@
 <!-- If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.  -->
+
+\textcolor{red}{Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
+We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
+Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
+We conclude the study with applications to SAR data.}
 

### 2023-12-12 Text/Articles/MIGARS_2024/R1-The-Entropy-as-a-Proxy-for-Fully-Developed-Speckle.tex
After our work together

%% template.tex
%% from
%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference,final,]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at:
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

\usepackage{graphicx}

% *** MATH PACKAGES ***
%
\usepackage{amsmath}
\interdisplaylinepenalty=2500
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%

%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

%% BEGIN MY ADDITIONS %%

\usepackage[]{natbib}
\bibliographystyle{ieeetr}

\usepackage[unicode=true]{hyperref}

\hypersetup{
            pdftitle={Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy},
            pdfkeywords={SAR, entropy estimation, non-parametric
analysis, order statistics},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{5}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[english]{babel}
\usepackage{bm,bbm}
\usepackage{mathrsfs}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{polski}
\usepackage{booktabs}
\usepackage{color}
\usepackage{mathtools}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{draft}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathabx}
\setcitestyle{square,comma,numbers,sort&compress}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

%% END MY ADDITIONS %%

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Identifying Departures from the Fully Developed Speckle
Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the
Entropy}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations

\author{

%% ---- classic IEEETrans wide authors' list ----------------

%% ----------------------------------------------------------

%% ---- classic IEEETrans one column per institution --------
 %%
%% ----------------------------------------------------------

%% ---- one column per author, classic/default IEEETrans ----
\IEEEauthorblockN{Rosa Janeth Alpala, Abraão D.~C.~Nascimento}
\IEEEauthorblockA{Universidade Federal de Pernambuco\\
Departamento de Estatística\\
Recife, PE, Brazil
\\janeth.alpala@ufpe.br, abraao@de.ufpe.br
}

\and
\IEEEauthorblockN{Alejandro C.~Frery}
\IEEEauthorblockA{Victoria University of Wellington\\
School of Mathematics and Statistics\\
Wellington, New Zealand
\\alejandro.frery@vuw.ac.nz
}

%% ----------------------------------------------------------

}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3},
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
SAR Data are affected by speckle, a non-additive and non-gaussian
interference noise-like pattern. The type of distribution these data
follow is paramount for their processing and analysis. Good statistical
models provide flexibility and accuracy, often at the cost of using
several parameters. The \(\mathcal{G}^0\) distribution is one of the
most successful models for SAR data. It includes the Gamma law as a
particular case which arises in the presence of fully developed speckle.
Although the latter is a limit distribution of the former, using the
same estimation technique for the more general model is numerically
unfeasible. We propose a two-stage estimation procedure: first, we
verify the hypothesis that the data are fully-developed speckle. If this
assumption is rejected, we proceed to estimate the parameters that index
the \(\mathcal G^0\) distribution; otherwise, we proceed with the Gamma
model. Given the uncertainty of the underlying distribution, and the
negative impact that using an inadequate model has on maximum likelihood
estimation, we employ a non-parametric approach to estimate entropy
under the fully-developed speckle hypothesis.
\end{abstract}

% keywords
\begin{IEEEkeywords}
SAR; entropy estimation; non-parametric analysis; order statistics
\end{IEEEkeywords}

% use for special paper notices

% make the title area
\maketitle

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\newtheorem{lemma}{Lemma}

\newcommand{\bias}{\operatorname{Bias}}

\hypertarget{sec:Introduction}{%
\section{Introduction}\label{sec:Introduction}}

Synthetic aperture radar (SAR) has become a fundamental technology for
environmental monitoring and disaster management because of its ability
to provide daytime and nighttime imagery in all weather
conditions~\cite{Mu2019}. However, the utility of SAR data depends on a
thorough understanding of their statistical properties. Speckle is part
of SAR data because of the imaging process' coherent nature. Its
non-additivity and non-Gaussianity require robust statistical models
that can accurately characterize the data.

Among these models, the \(\mathcal{G}^0\) distribution stands out as a
powerful framework. Notably, this distribution encompasses the
well-known Gamma distribution as a special case, particularly under the
assumption of fully developed speckle. The interplay between these two
distributions is apparent, with the Gamma distribution representing a
limiting case of the more general \(\mathcal{G}^0\) model.

When deciding which model is the best, practitioners face a problem. On
the one hand, if they opt for the Gamma law when the data come from the
\(\mathcal{G}^0\) distribution, they lose all the information about the
number of scatterers, which is revealed by one of the parameters of the
latter model~\cite{Yue2021}. On the other hand, if they apply the
\(\mathcal{G}^0\) distribution under fully developed speckle, maximum
likelihood estimation is tricky: bias increases making estimation
unreliable~\cite{VasconcellosFrerySilva:CompStat}, and the likelihood is
flat, so numerical optimization may not
converge~\cite{FreryCribariSouza:JASP:04}. The two-stage technique we
propose tackles this problem by using the entropy as a proxy to decide
which is the best model.

Estimating the entropy faces practical challenges, particularly when the
model is unknown; non-parametric methods are utilized in such cases.
Among non-parametric approaches,~\cite{Subhash2021} discussed the use of
spacing methods. This non-parametric strategy offers flexibility to
address a wide range of models without imposing specific parametric
constraints. We extend the exploration of non-parametric entropy
estimators by incorporating enhanced bootstrap methodologies.

\textcolor{red}{Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
We conclude the study with applications to SAR data.}

The article is structured as follows: Section~\ref{sec:Background}
covers statistical modeling and entropy estimation for Intensity SAR
data. Section~\ref{sec:test} outlines hypothesis testing based on
non-parametric entropy. In Section~\ref{sec:results}, we present
experimental results. Finally, in Section~\ref{sec:conclusion}
conclusions are exhibited.

\hypertarget{sec:Background}{%
\section{Background}\label{sec:Background}}

\hypertarget{statistical-modeling-of-intensity-sar-data}{%
\subsection{Statistical modeling of Intensity SAR
data}\label{statistical-modeling-of-intensity-sar-data}}

The primary models used for intensity SAR data include the Gamma and
\(\mathcal{G}_I^0\) distributions~\cite{Frery1997}. The first is
suitable for fully developed speckle and is a limiting case of the
second, which is appealing due to its versatility in accurately
representing regions with various roughness
characteristics~\cite{Cassetti2022}. We denote
\(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
\(Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)\) to indicate that \(Z\)
follows the distributions characterized by the respective probability
density functions: \begin{align}
    f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
    f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where, in~\eqref{E:gamma1} \(\mu > 0\) is the mean;
in~\eqref{E:gi01} \(\gamma > 0\) is the scale, \(\alpha < -1\) measures
the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

From \eqref{E:gi01}, the \(r\)th moment of \(Z\) is expressed as:
\begin{align}
    \mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
    \label{E:rmom}
\end{align}

Even though the \(\mathcal{G}_I^0\) distribution is defined by the
parameters \(\alpha\) and \(\gamma\), SAR literature commonly utilizes
the texture \(\alpha\) and the mean \(\mu\)~\cite{Nascimento2010}. In
this way, we compute the expected value \(\mu\) using the expression
in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using \(\mu\),
\(\alpha\), and \(L\). Then \begin{align*}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*} Thus, the probability density function that characterize
the \(G_I^0(\mu, \alpha, L)\) law is \begin{multline}
        f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{multline}

\hypertarget{the-shannon-entropy}{%
\subsection{The Shannon Entropy}\label{the-shannon-entropy}}

The parametric representation of Shannon entropy for a system described
by a continuous random variable is: \begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation} here, \(f(\cdot)\) is the probability density function
that characterizes the distribution of the real-valued random variable
\(Z\).

Using~\eqref{E:entropy2}, we can express the Shannon entropy of
\(\Gamma_{\text{SAR}}\)in~\eqref{E:gamma1} and
\(G_I^0\)in~\eqref{E:gi02} based on~\cite{Cassetti2022}
and~\cite{Ferreira2020}: \begin{multline}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{multline} \begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
-\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline} where \(\psi^{(0)}(\cdot)\) is the digamma function.

In Fig.~\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR
distribution changes with \(\mu\) for various values of \(L\).

\begin{figure}[hbt]

{\centering \includegraphics[width=1\linewidth]{R1-The-Entropy-as-a-Proxy-for-Fully-Developed-Speckle_files/figure-latex/PlotGammaSAR-1}

}

\caption{The Shannon Entropy under the Gamma SAR model.}\label{fig:PlotGammaSAR}
\end{figure}

Fig.~\ref{fig:3d_GIO} illustrates the entropy of \(G_I^0\) distribution
as a function of three key parameters: \(\mu\), \(\alpha\), and \(L\).

\begin{figure}[hbt]

{\centering \includegraphics[width=0.7\linewidth]{../../../Figures/PDF/entropy_plot_3d}

}

\caption{The Shannon Entropy under ${G}_I^0$ models.}\label{fig:3d_GIO}
\end{figure}

As we explore the 3D plot, we can observe how changes in \(\mu\),
\(\alpha\), and \(L\) collectively influence the entropy of the
\(G_I^0\) distribution. We can identify regions where entropy is high or
low, providing insights into the predictability and structure of the
distribution in various regions of the parameter space.

\hypertarget{estimation-of-the-shannon-entropy}{%
\subsection{Estimation of the Shannon
Entropy}\label{estimation-of-the-shannon-entropy}}

One of the earliest non-parametric estimators relying on spacings was
introduced by~\cite{vasicek1976test}. Assuming that
\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the
distribution \(F(z)\), the estimator is defined as: \begin{equation*}
\label{E:Vas}
    \widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
    \end{equation*} where \(m<n/2\) is a positive integer,
\(Z_{(i+m)}-Z_{(i-m)}\) is the \(m\)-spacing and
\(Z_{(1)}\leq Z_{(2)}\leq\ldots\leq Z_{(n)}\) are the order statistics
and \(Z_{(i)}= Z_{(1)}\) if \(i<1\), \(Z_{(i)}= Z_{(n)}\) if \(i>n\).

Several authors have explored adaptations to Vasicek's estimator. In
this work, we consider three entropy estimators known for their superior
performance:

\begin{itemize}
\item
  \cite{correa1995new}: \(\widehat{H}_{\text{C}}\).
\item
  \cite{Ebrahimi1994}: \(\widehat{H}_{\mathrm{E}}\).
\item
  \cite{IbrahimAlOmari2014}: \(\widehat{H}_{\mathrm{AO}}\).
\end{itemize}

These estimators, along with others, are described and studied
in~\cite{Cassetti2022}.

\hypertarget{enhanced-bootstrap-technique}{%
\subsection{Enhanced Bootstrap
Technique}\label{enhanced-bootstrap-technique}}

We employ the bootstrap technique to refine the precision of existing
non-parametric entropy estimators. This approach involves generating new
datasets through resampling with repetition from an existing one.

Let's assume that non-parametric entropy estimators
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) are inherently biased, that is:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta.
\end{equation} Our objective is to devise unbiased estimators with
reduced variance. To achieve this, we introduce an ``ideal estimator''
\(\check{\theta}(\bm{Z})\) using the bias information: \begin{equation}
\label{Eq:bias2}
\widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big).
\end{equation} However, \(\check{\theta}(\bm{Z})\) is not an estimator,
because it depends on the true parameter \(\theta\), prompting the
formulation of a new estimator \(\widetilde{H}\). From \eqref{Eq:bias1}
and \eqref{Eq:bias2} we have: \begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} where \(B\) is the number of replications in the bootstrap
technique. Applying this methodology, the original estimators by Correa,
Ebrahimi, and Al-Omari are now denoted as the proposed
bootstrap-enhanced versions: \(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\),
respectively.

\hypertarget{sec:test}{%
\section{Hypothesis testing based on non-parametric
entropy}\label{sec:test}}

General asymptotic results for functions of spacings are
detailed~\cite{Khashimov1990}, while~\cite{Bert1992} developed a
correction for the case of Shannon entropy. Following the work of these
authors, the next result applies:

\begin{lemma}
Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
\begin{equation*}
\sqrt{n}\,\Big(\label{Eq:bias_t}
\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
\end{equation*}
\end{lemma}

Consider, starting from the previous lemma, the test of the null
hypothesis \(\mathcal{H}_0: T_{\mathcal{D}}=D_0\) as opposed to one of
the other three: \begin{align*}
\mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\ 
\mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\
\mathcal{H}_1 &: T_{\mathcal{D}}< D_0. 
\end{align*} For this purpose, we can use the test statistics:
\begin{equation*}
Z_{m,n} = \frac{\sqrt{n}\big(\label{Eq:bias4}
\widetilde{H}-D_0\big)}{\sqrt{\operatorname{Var}\big(\ln f(Z)\big)}},
\end{equation*} so the null hypothesis should be rejected if (i)
\(Z_{n,m} > z_{\alpha/2}\) or \(Z_{n,m} < - z_{\alpha/2}\) for
\(\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2\) and \(\Phi_{\mathcal N}\)
being the standard normal cumulative distribution function, (ii)
\(Z_{n,m} > z_{\alpha/2}\) or (iii) \(Z_{n,m} < - z_{\alpha/2}\).

The power function for case (i) (two-sided test) at \(t\neq D_0\) is
given by \begin{multline*}
\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
\end{multline*} for a sequence of cumulative distribution functions
\(\Phi_{m,n}(x)\) which tends uniformly to \(\Phi_{\mathcal N}(z)\).

\hypertarget{sec:results}{%
\section{Results}\label{sec:results}}

Simulations are conducted using \(G_I^0\) distribution, with \(200\)
simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\),
with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and
\(L=8\). In the case of the bootstrap technique, each sample is
replicated \(100\) times with replacement. We choose to use the
following heuristic formula for spacing,
\(m=\left[\sqrt{n}+0.5\right]\).

In Fig. \ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and
mean squared error (MSE) between the original non-parametric entropy
estimators and their respective bootstrap-enhanced versions. The use of
the bootstrap technique exhibits more precision, reduced bias and MSE,
and improved convergence.

The results of simulation are exhibited in Table~\ref{tab:table2}. The
precision of estimators, as evidenced by bias and MSE comparisons,
benefits significantly from the bootstrap technique, particularly for
sample sizes below 81.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{R1-The-Entropy-as-a-Proxy-for-Fully-Developed-Speckle_files/figure-latex/Plot_bias_mse_gi0-1}

}

\caption{Bias and MSE of entropy estimators for  $G_I^0$, $L=8$, $\alpha=-20$.}\label{fig:Plot_bias_mse_gi0}
\end{figure}

\begin{table}

\caption{\label{tab:table2}Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\alpha=-20$.}
\centering
\begin{tabular}[t]{cccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Bias} & \multicolumn{3}{c}{MSE} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
$\bm{\mu}$ & $\bm{n}$ & $\widetilde{H}_{\text{C}}$ & $\widetilde{H}_{\text{E}}$ & $\widetilde{H}_{\text{AO}}$ & $\widetilde{H}_{\text{C}}$ & $\widetilde{H}_{\text{E}}$ & $\widetilde{H}_{\text{AO}}$\\
\midrule
 & 9 & -0.1117 & -0.0657 & -0.1698 & 0.1367 & 0.1255 & 0.1616\\

 & 25 & -0.0428 & -0.0131 & -0.0451 & 0.0515 & 0.0474 & 0.0499\\

 & 49 & -0.0267 & 0.0065 & -0.0152 & 0.0165 & 0.0154 & 0.0151\\

 & 81 & 0.0134 & 0.0434 & 0.0377 & 0.0121 & 0.0133 & 0.0138\\

\multirow{-5}{*}{\centering\arraybackslash 1} & 121 & 0.0055 & 0.0364 & 0.0275 & 0.0078 & 0.0108 & 0.0092\\
\cmidrule{1-8}
 & 9 & -0.0900 & -0.0386 & -0.1463 & 0.1345 & 0.1268 & 0.1427\\

 & 25 & -0.0247 & 0.0239 & -0.0239 & 0.0399 & 0.0378 & 0.0388\\

 & 49 & -0.0060 & 0.0312 & 0.0082 & 0.0194 & 0.0198 & 0.0183\\

 & 81 & -0.0080 & 0.0270 & 0.0147 & 0.0088 & 0.0095 & 0.0088\\

\multirow{-5}{*}{\centering\arraybackslash 10} & 121 & -0.0019 & 0.0267 & 0.0160 & 0.0080 & 0.0078 & 0.0075\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:table_hipotesis}Hypothesis Testing for $G_I^0$, $\mu = 5 $, $L=2$, $\alpha=-1000$ , $H_{\Gamma_{\text{SAR}}}=2.493$.}
\centering
\begin{tabular}[t]{ccccc}
\toprule
$n$ & Estimator & Mean Entropy & $Z$ Statistic & $p$ Value\\
\midrule
 & $\widetilde{H}_{C}$ & 2.4689 & -0.6699 & 0.5029\\

 & $\widetilde{H}_{E}$ & 2.5080 & 0.3764 & 0.7066\\

\multirow{-3}{*}{\centering\arraybackslash 9} & $\widetilde{H}_{AO}$ & 2.4119 & -2.2774 & 0.0228\\
\cmidrule{1-5}
 & $\widetilde{H}_{C}$ & 2.4713 & -1.1379 & 0.2552\\

 & $\widetilde{H}_{E}$ & 2.5000 & 0.3392 & 0.7344\\

\multirow{-3}{*}{\centering\arraybackslash 25} & $\widetilde{H}_{AO}$ & 2.4551 & -1.9487 & 0.0513\\
\cmidrule{1-5}
 & $\widetilde{H}_{C}$ & 2.4515 & -3.1650 & 0.0015\\

 & $\widetilde{H}_{E}$ & 2.4882 & -0.4299 & 0.6673\\

\multirow{-3}{*}{\centering\arraybackslash 49} & $\widetilde{H}_{AO}$ & 2.4726 & -1.5996 & 0.1097\\
\cmidrule{1-5}
 & $\widetilde{H}_{C}$ & 2.4937 & 0.0159 & 0.9873\\

 & $\widetilde{H}_{E}$ & 2.5262 & 2.8534 & 0.0043\\

\multirow{-3}{*}{\centering\arraybackslash 81} & $\widetilde{H}_{AO}$ & 2.4974 & 0.3594 & 0.7193\\
\cmidrule{1-5}
 & $\widetilde{H}_{C}$ & 2.4922 & -0.1442 & 0.8853\\

 & $\widetilde{H}_{E}$ & 2.5169 & 2.5684 & 0.0102\\

\multirow{-3}{*}{\centering\arraybackslash 121} & $\widetilde{H}_{AO}$ & 2.5052 & 1.3283 & 0.1841\\
\bottomrule
\end{tabular}
\end{table}

A hypothesis testing was conducted using non-parametric entropy
estimators as test statistics. The results in
Table~\ref{tab:table_hipotesis} show that data from the \(G_I^0\)
distribution exhibit fully developed speckle behavior, specifically in
the limit case with parameters \(\mu=5\), \(L=2\), and
\(\alpha= -1000\). The true entropy of \(\Gamma_{\text{SAR}}\) was set
at \(H_{\Gamma_{\text{SAR}}} = 2.493\).\\
It is observed that, for different sample sizes, entropy values converge
towards the true value of the Gamma SAR distribution. Hypothesis test
results were conducted with a \SI{95}{\percent} confidence level. The
\(Z\) statistic measures the discrepancy between the estimated entropy
and the true entropy. The \(p\)-values associated with the \(Z\)
statistic are predominantly greater than \(0.05\), for sample sizes
above \(25\), suggesting that the data are consistent with the null
hypothesis.

\hypertarget{sec:conclusion}{%
\section{Conclusion}\label{sec:conclusion}}

In this study, three estimators renowned for their robust performance
across diverse distributions were chosen for evaluation. We examine the
impact of applying bootstrap techniques on their precision by comparing
each estimator's performance with its bootstrap-enhanced counterpart,
utilizing metrics such as bias and MSE. The effectiveness of
bootstrap-enhanced non-parametric entropy estimators was observed,
demonstrating efficacy in most instances. Nonetheless, it is essential
to recognize that the applicability of this technique may not be
universal across all estimation methods.

It is worth noting that this analysis represents an initial exploration
of SAR Intensity data, and future work will include a more in-depth
analysis of effect size and statistical power. Additionally, exploring
the impact of the \(\alpha\) parameter on estimates and conducting more
extensive analyses to assess the generalization of results to different
parameter configurations is suggested.

\renewcommand\refname{References}
\bibliography{../../Common/references.bib}
\end{document}

### 2023-12-19 Code/R/RMarkdown/EntropyPlots.Rmd
code plot gi0

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE,cache=TRUE)
 #knitr::opts_chunk$set(echo = TRUE)
@@
 library(patchwork)
-options(kableExtra.latex.load_packages = FALSE)
+#options(kableExtra.latex.load_packages = FALSE)
 library(devtools)
-devtools::install_github("haozhu233/kableExtra")
+#devtools::install_github("haozhu233/kableExtra")
 #devtools::install_github("haozhu233/kableExtra")
@@
 library(ggthemes)
+library(geomtextpath)
+library(latex2exp)
 theme_set(theme_bw()  +
@@
 source("../MainFunctions/entropy_gamma_sar.r")
+source("../MainFunctions/entropy_gI0.r")
 
@@
 
-```{r FunctionsDefinitions}
-entropy_gamma_sar <- function(L, mu) {
-
-    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
-
-}
-
-entropy_gI0 <- function(mu, alpha, L) {
-
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-gamma_sar_sample <- function(L, mu, n) {
-  samples <- rgamma(n, shape = L, rate = L / mu)
-  return(samples)
-}
-
-```
-
 ```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
@@
 
-L_labels <- c("L = 1", "L = 3", "L = 8", "L = 12", "L = 100")
+#L <- c(  12)
+L_labels <- c(expression(italic(L)==1), 
+              expression(italic(L)==3), 
+              expression(italic(L)==8), 
+              expression(italic(L)==12),
+              expression(italic(L)==100)
+              )
 
@@
 ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
-  geom_line() +
-  #theme_minimal() +
+  geom_line(linewidth=1) +
+  theme_minimal() +
    scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
    labs(col = "Looks") +
-  xlab(expression(paste(mu)))
+  #scale_color_manual(values = pal_jama()(7)[1:5], labels = L_labels) +
+  #labs(col = "Looks")+
+  xlab(expression(paste(mu))) +
+  theme(text=element_text(family="serif"),
+        legend.position = "bottom")
 
@@
 \label{E:E-GIO}
-H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
+H_{G_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
 -\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
@@
 ```
+
+```{r Plot_GI0_and_gamma_1, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=1$."}
+
+L <- c(1)
+alphas <- c(-1.05, -1.5, -3, -8, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=2$."}
+
+L <- c(2)
+alphas <- c(-1.05, -1.5, -3, -8, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_3, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=3$."}
+
+L <- c(3)
+alphas <- c(-1.05, -1.5, -3, -8, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_4, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}
+
+L <- c(5)
+alphas <- c(-1.05, -1.5, -3, -8, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=12$."}
+
+L <- c(12)
+alphas <- c(-1.05, -1.5, -5, -12, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.05), expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -12), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_6, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=18$."}
+
+L <- c(18)
+alphas <- c( -1.5, -5, 18, -50, -1000)
+alpha_labels <- c(expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -18), expression(italic(alpha) == -50), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+```{r Plot_GI0_and_gamma_7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=100$."}
+
+L <- c(100)
+alphas <- c( -1.5, -5, 18,  -50, -10000)
+alpha_labels <- c(expression(italic(alpha) == -1.5), expression(italic(alpha) == -5), expression(italic(alpha) == -18), expression(italic(alpha) == -50), expression(italic(alpha) == -10000))
+
+mu <- seq(0.1, 100, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(linetype = "longdash",  linewidth = 0.8) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  annotate("text", x = max(mu)+0.1, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
+  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_nejm()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```

### 2023-12-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Citation improved
code plot gi0

--- 2023-12-10 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
 estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
-  latex_estimator_names <- c("Correa" = expression("$\\widehat{H}_{C}$"),#parse(text=TeX("$H_{2}$")),
-                             "Correa Bootstrap" = expression("$\\widetilde{H}_{C}$"),
-                            "Ebrahimi" = expression("$\\widehat{H}_{E}$"),
-                            "Al Omari" = expression("$\\widehat{H}_{AO}$"),
-                            "Ebrahimi Bootstrap" = expression("$\\widetilde{H}_{E}$"),
-                            "Al Omari Bootstrap" = expression("$\\widetilde{H}_{AO}$"))
+  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),#parse(text=TeX("$H_{2}$")),
+                             "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
+                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
+                            "Al Omari" = expression("$\\widehat{italic(H)}_{AO}$"),
+                            "Ebrahimi Bootstrap" = expression("$\\widetilde{italic(H)}_{E}$"),
+                            "Al Omari Bootstrap" = expression("$\\widetilde{italic(H)}_{AO}$"))
 selected_estimators_latex <- latex_estimator_names[estimators_to_plot]
@@
 # Number of replications
-R <- 100
+R <- 10
 
@@
   estimators <- list(
-    #" " = bootstrap_vasicek_estimator,
+    #"Correa" = correa_estimator,
     "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,

### 2023-12-19 Code/R/MainFunctions/yee_estimator.R

@@ -1,3 +1,5 @@
+
+
 yee_estimator<- function(X) {
   n <- length(X)
   H_Y <- numeric(n-1)
@@ -15,6 +17,30 @@ yee_estimator<- function(X) {
   
   return(estimated_entropy)
 }
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
 
 # yee_estimator<- function(X) {
 #   n <- length(X)
@@ -34,7 +60,7 @@ yee_estimator<- function(X) {
 #   return(estimated_entropy)
 # }
 
-# # Ejemplo de uso con muestra de tamaño 10000
+
 # set.seed(123)  # Para reproducibilidad
 # X_large <- rnorm(1000)  # Reemplaza esto con tu conjunto de datos
 # system.time(entropy_estimate_large <- yee_entropy_estimator_optimized(X_large))

### 2023-12-19 Code/R/RMarkdown/report2_plots_means.Rmd

@@
 
-```{r Plot_mean1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
+```{r SimulateDataPlot1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 entropy_data <-calculate_entropy(sample_sizes, R, mu, L)
+```
 
+```{r Plot1, echo=FALSE}
 ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +

### 2023-12-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd

--- 2023-12-12 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
 Estimating the entropy faces practical challenges, particularly when the model is unknown; non-parametric methods are utilized in such cases.
-Among non-parametric approaches,&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
+Among non-parametric approaches, Subhash et al.&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
 This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.

### 2023-12-20 Code/R/RMarkdown/EntropyPlots.Rmd
code test

@@
 ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
-  geom_line(linetype = "longdash",  linewidth = 0.8) +
-  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "black", linetype = "solid", size = 1) + 
+  geom_line(linetype = "longdash",  linewidth = 1.5, alpha=.7) +
   annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 

### 2023-12-20 Code/R/Programs/FirstExperimentTestStatisticL1.R

@@ -1,0 +1,53 @@
+library(ggplot2)
+library(ggsci)
+
+source("../MainFunctions/ebrahimi_estimator.r")
+source("../MainFunctions/gamma_sar_sample.r")
+
+
+
+
+set.seed(1234567890, kind="Mersenne-Twister")
+
+R <- 3000 
+mu <- 1
+sample.size <- c(9, 25, 49, 121)
+
+TestStatistics <- NULL
+
+for(s in sample.size){
+  for(r in 1:R){
+    
+    z <- gamma_sar_sample(1, mu, s)
+    TestStat <- ebrahimi_estimator(z) - 1 - log(mean(z))
+    TestStatistics <- rbind(TestStatistics,
+                            c(s, TestStat))
+  }
+}
+
+TestStatistics <- data.frame(TestStatistics)
+names(TestStatistics) <- c("Sample Size", "Test Statistics")
+
+# ggplot(TestStatistics, aes(x=`Test Statistics`, col=`Sample Size`, group=`Sample Size`)) +
+#   geom_density()
+
+
+ggplot(TestStatistics, aes(x = `Test Statistics`, col = factor(`Sample Size`), linetype = factor(`Sample Size`))) +
+  geom_line(stat = "density", linewidth = 1.0) +  
+  scale_color_manual(
+    values = pal_cosmic()(length(sample.size)),
+    name = "Sample Size"
+  ) +
+  scale_linetype_manual(
+    values = rep("solid", length(sample.size)),  
+    name = "Sample Size"
+  ) +
+  labs(x = "Test Statistics", y = "Density") +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "serif"),
+    legend.position = "bottom",
+    # legend.title = element_text(size = 10),
+    # legend.text = element_text(size = 8),
+    legend.key.size = unit(1, "lines")  
+  )

### 2023-12-20 Code/R/Programs/functions.R

@@ -1,68 +1,0 @@
-# Functions
-# Entropy Gamma SAR
-entropy_gamma_sar <- function(L, mu) {
-  
-  return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))
-  
-}
-
-# Entropy GI0
-entropy_gI0 <- function(mu, alpha, L) {
-  
-  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
-  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))
-  
-  entropy <- term1 + term2 
-  return(entropy)
-}
-
-
-# only second term of GI0
-second_term <- function(alpha, L) {
-  return(-L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha)))
-  
-}
-
-
-#Samples Gamma SAR
-gamma_sar_sample <- function(L, mu, n) {
-  samples <- rgamma(n, shape = L, rate = L / mu)
-  return(samples)
-}
-
-
-#Samples GI0
-Z_samples <- function(L, alpha, mu,  n) {
-  
-  X_samples <- rinvgamma(n, shape = -alpha, rate =mu*(-alpha-1))
-  
-  Y_samples <- rgamma(n, shape = L, rate = L)
-  Z_samples <- X_samples * Y_samples
-  return(Z_samples)
-}
-
-
-
-# nonparametric estimator
-
-
-
-van_es_estimator <- function(data) {
-  n <- length(data)
-  m <- round(sqrt(n) + 0.5)  # m-spacing
-  data_sorted <- sort(data)
-  sum_term1 <- 0
-  sum_term2 <- 0
-  
-  for (i in 1:(n - m)) {
-    sum_term1 <- sum_term1 + log(((n + 1) / m) * (data_sorted[i + m] - data_sorted[i]))
-  }
-  
-  for (k in m:n) {
-    sum_term2 <- sum_term2 + 1 / k
-  }
-  
-  sum_term3 <- log(m / (n + 1))
-  
-  return((sum_term1 / (n - m)) + sum_term2+ sum_term3)
-}

### 2024-01-05 Code/R/RMarkdown/EntropyPlots.Rmd
codes test

@@
 ```
+
+```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+load("./Data/results_gi0_1.Rdata")
+
+# Interpretación de rechazo o no rechazo
+for (mu_val in mu_values) {
+  results_data <- results_gi0_1[[as.character(mu_val)]]
+
+  table_result <- kbl(
+    results_data,
+   # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."),
+    format = "latex",
+    booktabs = TRUE,
+    align = "c",
+    escape = FALSE,
+    digits = 4,
+    label = "table_hipotesis"
+  ) %>%
+    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
+
+  cat("### Results for mu =", mu_val, "\n")
+  print(table_result)
+
+  # Interpretación de rechazo o no rechazo
+  cat(ifelse(nrow(results_data) > 0,
+             paste("For mu =", mu_val, ":\n"),
+             paste("No observations for mu =", mu_val, ":\n")))
+
+  cat(ifelse(nrow(results_data) > 0,
+             paste(
+               "Sample Size ", results_data$`$n$`, " Estimator ", results_data$Estimator,
+               ifelse(results_data$RejectNull,
+                      " the null hypothesis is rejected.",
+                      " the null hypothesis is not rejected."
+               ), "\n"
+             ),
+             "\n"))
+}
+
+```

### 2024-01-05 Code/R/RMarkdown/plots_mean.Rmd
codes test

---
title: "Report: Exploring Non-Parametric Entropy Estimators and Bootstrap Enhancements"
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
#library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")
source("../MainFunctions/gi0_sample.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/adaptive_correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_estimator_m.r")
source("../MainFunctions/al_omari_2_estimator.r")
source("../MainFunctions/yee_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator_opt.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
source("../MainFunctions/bootstrap_yee_estimator.r")
source("../MainFunctions/bootstrap_yee_estimator_optimized.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

\newcommand{\bias}{\operatorname{Bias}}

# Mean Entropy for Estimators Gamma SAR

```{r Plot_mean1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121, 225)
R <- 10
mu <- 1
L <- 1

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
     "Correa" = correa_estimator,
     "Ebrahimi" = ebrahimi_estimator,
     "Al Omari 1" = al_omari_1_estimator,
      "Yee" = yee_estimator,
      "Correa Bootstrap" = bootstrap_correa_estimator,
     "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
     "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 10)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

```{r Plot_mean2, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy Gamma SAR for $L= 2$ and $\\mu=5$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 10
mu <- 5
L <- 2

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gamma_sar_sample(L, mu, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, L) {
 # true_entropy <- entropy_gamma_sar(L, mu)

# Define a list of estimators
  estimators <- list(
   # "Van Es" = van_es_estimator,
   # "Correa" = correa_estimator,
   # "Adp Correa" = adaptive_correa_estimator,
    "Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
   # "Vasicek" = vasicek_estimator,
    "Al Omari 1" = al_omari_1_estimator,
   #"Al OmariA " = al_omari_estimator_m,
    #"Al Omari 2" = al_omari_2_estimator,
    "Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator,
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
    #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 10)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

## Results for  Nonparametric Estimators with  $\mathcal{G}_I^0$

```{r Plot_GI0_mean_p, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for GI0, with $L= 2$, $\\mu=5$ and $\\alpha=-1000$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c(9, 25, 49, 81, 121)
R <- 10
mu <- 10
L <- 3
alpha <- -1000

# Function to generate samples for a given sample size and replication
generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
  }
  return(samples)
}

# Function to calculate Variance for both non-parametric and bootstrap estimators
true_entropy <- entropy_gamma_sar(L, mu)
calculate_entropy <- function(sample_sizes, R, mu, alpha, L) {
  # true_entropy <- entropy_gamma_sar(L, mu)

  # Define a list of estimators
  estimators <- list(
    #"Van Es" = van_es_estimator,
    #"Correa" = correa_estimator,
    #"Adp Correa" = adaptive_correa_estimator,
    #"Ebrahimi" = ebrahimi_estimator,
    #"Noughabi Arghami" = noughabi_arghami_estimator,
    #"Vasicek" = vasicek_estimator,
    #"Al Omari 1" = al_omari_1_estimator,
    #"Al OmariA " = al_omari_estimator_m,
    #"Yee" = yee_estimator,
    #"Van Es Bootstrap" = bootstrap_van_es_estimator,
    "Correa Bootstrap" = bootstrap_correa_estimator,
    #"Correa_opt Bootstrap" = bootstrap_correa_estimator_opt, 
    #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
    #"Noughabi Arghami Bootstrap" = bootstrap_noughabi_arghami_estimator,
    #"Vasicek Bootstrap" = bootstrap_vasicek_estimator,
    "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
    #"Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator
    #"Yee Bootstrap" = bootstrap_yee_estimator,
    #"Yee_opt Bootstrap" = bootstrap_yee_estimator_optimized
  )

  output <- data.frame(SampleSize = integer(0), Estimator = character(0), MeanEntropy = numeric(0))

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl("Bootstrap", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 10)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)
      output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name, MeanEntropy = round(mean_entropy, 5)))

    }
  }

  return(output)
}

entropy_data <-calculate_entropy(sample_sizes, R, mu, alpha, L)
#cat("entropy", entropy_data)

ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
  geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
  annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)

```

<!-- ```{r Plot_CI1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Confidence Intervals for $L= 2$ and $\\mu=5$.", fig.width=6,fig.height=5} -->
<!-- set.seed(1234567890, kind = "Mersenne-Twister") -->

<!-- sample_sizes <- c(9, 25, 49, 81, 121, 500) -->
<!-- R <- 100 -->
<!-- mu <- 5 -->
<!-- L <- 2 -->
<!-- alpha <- -300 -->

<!-- # Function to generate samples for a given sample size and replication -->
<!-- generate_samples_gi0 <- function(sample_size, replication, mu, alpha, L) { -->
<!--   samples <- vector("list", replication) -->
<!--   for (r in 1:replication) { -->
<!--     samples[[r]] <- gi0_sample(mu, alpha, L, sample_size) -->
<!--   } -->
<!--   return(samples) -->
<!-- } -->

<!-- true_entropy <- entropy_gamma_sar(L, mu) -->
<!-- # Function to calculate Confidence Intervals for both non-parametric and bootstrap estimators -->
<!-- calculate_confidence_intervals <- function(sample_sizes, R, mu,alpha, L, confidence_level = 0.95) { -->
<!--   true_entropy <- entropy_gamma_sar(L, mu) -->

<!--   # Define a list of estimators -->
<!--   estimators <- list( -->
<!--       "Correa Bootstrap" = bootstrap_correa_estimator -->
<!--      #"Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator -->
<!--     # "Al Omari 1 Bootstrap" = bootstrap_al_omari_1_estimator -->
<!--     # "Al Omari 2 Bootstrap" = bootstrap_al_omari_2_estimator -->
<!--   ) -->

<!--   output <- data.frame(SampleSize = integer(0), Estimator = character(0),  -->
<!--                        LowerCI = numeric(0), UpperCI = numeric(0)) -->

<!--   for (ssize in sample_sizes) { -->

<!--     samples <- generate_samples_gi0(ssize, R, mu, alpha, L) -->

<!--     for (estimator_name in names(estimators)) { -->
<!--       estimator <- estimators[[estimator_name]] -->
<!--       v.entropy <- numeric(R) -->

<!--       for (r in 1:R) { -->
<!--         sample <- samples[[r]] -->

<!--         if (grepl("Bootstrap", estimator_name)) { -->
<!--           v.entropy[r] <- estimator(sample, B = 10) -->
<!--         } else { -->
<!--           v.entropy[r] <- estimator(sample) -->
<!--         } -->

<!--       } -->

<!--       # Calculate Confidence Interval -->
<!--       se <- sd(v.entropy) -->
<!--       margin_of_error <- qt((1 + confidence_level) / 2, R - 1) * se / sqrt(R) -->
<!--       ci_lower <- mean(v.entropy) - margin_of_error -->
<!--       ci_upper <- mean(v.entropy) + margin_of_error -->

<!--       output <- rbind(output, data.frame(SampleSize = ssize, Estimator = estimator_name,  -->
<!--                                          LowerCI = round(ci_lower, 5), UpperCI = round(ci_upper, 5))) -->
<!--     } -->
<!--   } -->

<!--   return(output) -->
<!-- } -->

<!-- confidence_intervals_data <- calculate_confidence_intervals(sample_sizes, R, mu,alpha, L,) -->

<!-- combined_plot <- ggplot(confidence_intervals_data, aes(x = SampleSize, y = UpperCI, ymin = LowerCI, ymax = UpperCI, color = Estimator)) + -->
<!--   geom_line(aes(group = Estimator), linetype = "dashed") + -->
<!--   geom_ribbon(alpha = 0.2) + -->
<!--   geom_point(aes(y = (LowerCI + UpperCI) / 2), color = "#808080", size = 2) +  -->
<!--   geom_line(aes(x = SampleSize, y = (LowerCI + UpperCI) / 2, color = Estimator), linetype = "solid", size = 0.5) +   -->
<!--   geom_line(aes(y = true_entropy), linetype = "solid", color = "black") +   -->
<!--   labs(title = "", -->
<!--        x = "Sample Size", y = "Entropy")  -->

<!-- print(combined_plot) -->
<!-- ``` -->

```{r Simulated_data_test_gi0, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c( 25, 49, 81, 121, 200)
N<- 200
# Number of replications
R <- 100

# Number of bootstrap replications
B <- 2
mu_values <- c(1)
alpha <- -600
L <- 5

  estimators <- list(

    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    #"$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )
 #true_entropy <- entropy_gamma_sar(L, mu) 
calculate_entropy_and_test_montecarlo <- function(sample_sizes, R, N, B, mu, alpha, L, estimators, true_entropy) {
  true_entropy <- entropy_gamma_sar(L, mu)
  output <- data.frame(
    SampleSize = integer(0),
    Estimator = character(0),
    TypeIErrorRate = numeric(0)
  )

  for (ssize in sample_sizes) {

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      reject_H0_count <- 0

      for (n_replication in 1:N) {

        #samples <- gi0_sample(mu, alpha, L, ssize)
        v.entropy <- numeric(R)
        for (r in 1:R) {
        # Generar muestras aleatorias para cada repetición y cada estimador
        samples <- gi0_sample(mu, alpha, L, ssize)

        if (grepl(" ", estimator_name)) {
          v.entropy[r] <- estimator(samples, B = B)
        } else {
          v.entropy[r] <- estimator(samples)
        }
      }

        # if (grepl(" ", estimator_name)) {
        #   entropy_values <- replicate(R, estimator(samples, B = B))
        # } else {
        #   entropy_values <- replicate(R, estimator(samples))
        # }
        mean_entropy <- mean(v.entropy)
      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
      alpha_t = 0.05

        # Calcular p-values para cada replicación
       # p_values <- 2 * (1 - pnorm(abs((mean(entropy_values) - true_entropy) / sd(entropy_values))))

        # Contar los casos donde se rechaza la hipótesis nula
        reject_H0_count <- reject_H0_count + sum(p_value < 0.05)
      }

      typeI_error_rate <- reject_H0_count / (N)

      output <- rbind(
        output,
        data.frame(
          SampleSize = ssize,
          Estimator = estimator_name,
          TypeIErrorRate = round(typeI_error_rate, 5)
        )
      )
    }
  }

  colnames(output) <- c("$n$", "Estimator", "Type I Error Rate")

  return(output)
}

calculate_results_test_gi0_montecarlo <- function(sample_sizes, R, N, B, mu_values, alpha, L, estimators) {
  results_list <- list()

  for (mu_val in mu_values) {

    results <- calculate_entropy_and_test_montecarlo(sample_sizes, R, N, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

    results_list[[as.character(mu_val)]] <- df
  }

  return(results_list)
}

results_gi0_1_montecarlo <- calculate_results_test_gi0_montecarlo(sample_sizes, R, N, B, mu_values, alpha, L, estimators)
print(results_gi0_1_montecarlo)
save(results_gi0_1_montecarlo, file = "./Data/results_gi0_1_montecarlo.Rdata")

# calculate_results_test_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
#   results_list <- list()
# 
#   for (mu_val in mu_values) {
#     
#     results <- calculate_entropy_and_test(sample_sizes, R, B, mu_val, alpha, L, estimators)
#     df <- as.data.frame(results)
# 
#     
#     results_list[[as.character(mu_val)]] <- df
#   }
# 
#   return(results_list)
# }
# 
# 
# results_gi0_1 <- calculate_results_test_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)
# 
# 
# save(results_gi0_1, file = "./Data/results_gi0_1.Rdata")

```

```{r Table_test_gi0_montecarlo, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/results_gi0_1_montecarlo.Rdata")

# Interpretación de rechazo o no rechazo
for (mu_val in mu_values) {
  results_data <- results_gi0_1_montecarlo[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
   # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis"
  ) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")

  #cat("### Results for mu =", mu_val, "\n")
  print(table_result)

}
# # Imprimir los nombres de las columnas en los resultados
# print(names(results_gi0_1_montecarlo[[1]]))
# 
# # Verificar las columnas disponibles en los resultados
# available_columns <- unique(unlist(lapply(results_gi0_1_montecarlo, names)))
# 
# # Seleccionar solo las columnas deseadas si están presentes
# desired_columns <- c("SampleSize", "Estimator", "TypeIErrorRate")
# selected_columns <- intersect(available_columns, desired_columns)
# 
# results_data <- lapply(results_gi0_1_montecarlo, function(df) {
#   df[, selected_columns, drop = FALSE]
# })
# 
# # Combinar los resultados en un único dataframe
# results_combined <- do.call(rbind, results_data)
# 
# # Mostrar la tabla
# table_result <- kbl(
#   results_combined,
#   format = "latex",
#   booktabs = TRUE,
#   align = "c",
#   escape = FALSE,
#   digits = 4,
#   label = "table_hipotesis_montecarlo"
# ) %>%
#   collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
# 
# print(table_result)

```
<!-- ```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->
<!-- load("./Data/results_gi0_1.Rdata") -->

<!-- # Imprimir los nombres de las columnas en los resultados -->
<!-- print(names(results_gi0_1[[1]])) -->

<!-- # Seleccionar solo las columnas deseadas -->
<!-- results_data <- lapply(results_gi0_1, function(df) { -->
<!--   df[, c("SampleSize", "Estimator", "TypeIErrorRate")] -->
<!-- }) -->

<!-- # Combinar los resultados en un único dataframe -->
<!-- results_combined <- do.call(rbind, results_data) -->

<!-- # Mostrar la tabla -->
<!-- table_result <- kbl( -->
<!--   results_combined, -->
<!--   format = "latex", -->
<!--   booktabs = TRUE, -->
<!--   align = "c", -->
<!--   escape = FALSE, -->
<!--   digits = 4, -->
<!--   label = "table_hipotesis" -->
<!-- ) %>% -->
<!--   collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") -->

<!-- print(table_result) -->

<!-- ``` -->

<!-- ```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->

<!-- load("./Data/results_gi0_1.Rdata") -->

<!-- # Interpretación de rechazo o no rechazo -->
<!-- for (mu_val in mu_values) { -->
<!--   results_data <- results_gi0_1[[as.character(mu_val)]] -->

<!--   table_result <- kbl( -->
<!--     results_data, -->
<!--    # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."), -->
<!--     format = "latex", -->
<!--     booktabs = TRUE, -->
<!--     align = "c", -->
<!--     escape = FALSE, -->
<!--     digits = 4, -->
<!--     label = "table_hipotesis" -->
<!--   ) %>% -->
<!--     collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle") -->

<!--   cat("### Results for mu =", mu_val, "\n") -->
<!--   print(table_result) -->

<!--   # Interpretación de rechazo o no rechazo -->
<!--   cat(ifelse(nrow(results_data) > 0, -->
<!--              paste("For mu =", mu_val, ":\n"), -->
<!--              paste("No observations for mu =", mu_val, ":\n"))) -->

<!--   cat(ifelse(nrow(results_data) > 0, -->
<!--              paste( -->
<!--                "Sample Size ", results_data$`$n$`, " Estimator ", results_data$Estimator, -->
<!--                ifelse(results_data$RejectNull, -->
<!--                       " the null hypothesis is rejected.", -->
<!--                       " the null hypothesis is not rejected." -->
<!--                ), "\n" -->
<!--              ), -->
<!--              "\n")) -->
<!-- } -->

<!-- ``` -->

### 2024-01-05 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
codes test

@@
 library(tidyverse)
-#library(RColorBrewer)
+library(RColorBrewer)
 library(ggsci)
@@
 
-source("../../../Code/R/MainFunctions/gamma_sar_sample.r")
-source("../../../Code/R/MainFunctions/entropy_gamma_sar.r")
-source("../../../Code/R/MainFunctions/entropy_gI0.r")
-source("../../../Code/R/MainFunctions/gi0_sample.r")
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
-source("../../../Code/R/MainFunctions/van_es_estimator.r")
-source("../../../Code/R/MainFunctions/correa_estimator.r")
-source("../../../Code/R/MainFunctions/ebrahimi_estimator.r")
-source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.r")
-source("../../../Code/R/MainFunctions/vasicek_estimator.r")
-source("../../../Code/R/MainFunctions/al_omari_1_estimator.r")
-source("../../../Code/R/MainFunctions/al_omari_2_estimator.r")
+source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
+source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
+source("../../../Code/R/MainFunctions/entropy_gI0.R")
+source("../../../Code/R/MainFunctions/gi0_sample.R")
 
-source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.r")
+source("../../../Code/R/MainFunctions/van_es_estimator.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
+source("../../../Code/R/MainFunctions/vasicek_estimator.R")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")
+
+source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
 #The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
@@
 
-\textcolor{red}{Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
+Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
 We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
 Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
-We conclude the study with applications to SAR data.}
+We conclude the study with applications to SAR data.
 
@@
 
+In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
+
+```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}
+
+L <- c(5)
+alphas <- c(  -3, -8, -20, -1000)
+alpha_labels <- c( expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -20), expression(italic(alpha) == -1000))
+
+mu <- seq(0.1, 10, length.out = 500)
+
+# Entropy GI0
+
+muEntropy <- data.frame()
+
+for (alpha in alphas) {
+  entropies_GI0 <- sapply(L, function(L) entropy_gI0(mu, alpha, L))
+  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+}
+
+muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"),  value.name = "Entropy")
+
+# Entropy Gamma SAR
+
+entropies_gamma <- sapply(L, function(L) entropy_gamma_sar(L, mu))
+
+Entropy_gamma <- data.frame(mu, entropies_gamma)
+
+Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy Gamma")
+
+#plot
+
+ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
+  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "solid",linewidth = 1.5) + 
+  geom_line(linetype = "longdash",  linewidth = 2, alpha=.7) +
+  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
+           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
+  theme_minimal() +
+  scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
+  #scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
+  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
+  labs(col = "Roughness", linetype = NULL) +
+  xlab(expression(paste(mu))) +
+  ylab("Entropy") +  
+  theme(text = element_text(family = "serif"),
+        legend.position = "bottom")
+
+```
+
+The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical}.
+It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar.
+In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.
+
+```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=5$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 1
+sample.size <- c( 121)
+
+alpha1_values <- c(-3, -8, -20, -1000)
+
+plots_list <- list()
+
+for (alpha_val in alpha1_values) {
+
+  alpha1 <- alpha_val
+
+  TestStatistics1 <- NULL
+  TestStatistics2 <- NULL
+
+  mean_entropy1 <- numeric(length(sample.size))
+  mean_entropy2 <- numeric(length(sample.size))
+
+  for (s in sample.size) {
+    TestStat1 <- numeric(R)
+    TestStat2 <- numeric(R)
+
+    for (r in 1:R) {
+      z <- gi0_sample(mu, alpha1, L, s)
+      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
+
+      #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+      #TestStat2[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
+    }
+
+    # mean_entropy1[sample.size == s] <- mean(TestStat1)
+    # #cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
+    # 
+    # mean_entropy2[sample.size == s] <- mean(TestStat2)
+    # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")
+
+    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
+    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
+  }
+
+  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
+  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
+
+  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
+    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
+    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
+    annotate("text", x = max(TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
+             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
+    annotate("text", x = max(TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
+             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
+    labs(x = "Entropy", y = "Empirical Density") +
+    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
+    theme_minimal() +
+    theme(
+      text = element_text(family = "serif"),
+      legend.position = "none"  
+    )
+
+  plots_list[[as.character(alpha_val)]] <- plot
+}
+
+grid.arrange(grobs = plots_list, ncol = 2)
+
+```
 ## Estimation of the Shannon Entropy
@@
 \end{lemma} 
-Consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:
-\begin{align*}
-\mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\ 
-\mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\
-\mathcal{H}_1 &: T_{\mathcal{D}}< D_0. 
-\end{align*}
-For this purpose, we can use the test statistics:
-\begin{equation*}
-Z_{m,n} = \frac{\sqrt{n}\big(\label{Eq:bias4}
-\widetilde{H}-D_0\big)}{\sqrt{\operatorname{Var}\big(\ln f(Z)\big)}},
-\end{equation*}
-so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+Consider, starting from the previous lemma, we aim at testing the following hypotheses:
 
-The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
-\begin{multline*}
-\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
-\end{multline*}
-for a sequence of cumulative distribution functions $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.
+$$
+ \begin{cases}\mathcal{H}_0: \mathcal{D}(\bm{\theta})=\Gamma_{\text{SAR}} \\ 
+  \mathcal{H}_1: \mathcal{D}(\bm{\theta})=G_I^0.\end{cases}
+$$
+In other words, we verify the hypothesis that the data are fully-developed speckle.
+<!-- \begin{align*} -->
+<!-- \mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\  -->
+<!-- \mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\ -->
+<!-- \mathcal{H}_1 &: T_{\mathcal{D}}< D_0.  -->
+<!-- \end{align*} -->
+For this purpose, we use the following test statistic:
+\begin{equation}
+\label{Eq:test_e}
+S(Z)= \widetilde{H}(Z)-H(Z).
+\end{equation}
+This test statistic $S(Z)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$.
+The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(Z)\approx 0$.
+Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero.
+This suggests significant differences and implies the presence of heterogeneous clutter.
+
+<!-- so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
+-->
 
@@
 sample_sizes <- c(9, 25, 49, 81, 121)
+# Number of replications para simulacion montecarlo para calculo de error tipo 1
 
-# Number of replications
+N <- 1000
+
+# Number of replications para calcular las entropias
 R <- 10
@@
 
+Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}.
+Under the null hypothesis, we observe that the densities are centered around zero.
+Conversely, under the alternative hypothesis, such as for $\alpha=8$, the density is not centered around zero.
+It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.
+
+```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 2
+sample.size <- c( 81)
+
+alpha1_values <- c( -8)
+
+plots_list <- list()
+
+for (alpha_val in alpha1_values) {
+
+  alpha1 <- alpha_val
+
+  TestStatistics1 <- NULL
+  TestStatistics2 <- NULL
+
+  mean_entropy1 <- numeric(length(sample.size))
+  mean_entropy2 <- numeric(length(sample.size))
+
+  for (s in sample.size) {
+    TestStat1 <- numeric(R)
+    TestStat2 <- numeric(R)
+
+    for (r in 1:R) {
+      z <- gi0_sample(mu, alpha1, L, s)
+      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
+
+    }
+
+    mean_entropy1[sample.size == s] <- mean(TestStat1)
+   # cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
+
+    mean_entropy2[sample.size == s] <- mean(TestStat2)
+   # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")
+
+    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
+    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
+  }
+
+  difference.betweeen.GammaSAR.GI0.n.Look <- function(alpha, L) {
+    return(
+      -L - lgamma(L-alpha) + 
+        (L-alpha)*(digamma(L - alpha))- 
+        (1-alpha)*digamma(- alpha)+
+        log(-1 - alpha)+
+        lgamma(-alpha)
+    )
+  }
+
+  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
+  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
+
+  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
+    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
+    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
+    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
+    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
+   # geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
+   # annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), y=7, parse=TRUE, label="alpha==-20", hjust=-.1, vjust=2.0, col="darkgreen") +
+    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
+    #annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), y=7, parse=TRUE, label="alpha==-1000", hjust=-.1, vjust=4.0, col="darkgreen") +
+    labs(x = "Test Statistics", y = "Empirical Density") +
+    #annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
+    theme_minimal() +
+    theme(
+      text = element_text(family = "serif"),
+      legend.position = "none"  
+    )
+
+  plots_list[[as.character(alpha_val)]] <- plot
+}
+
+grid.arrange(grobs = plots_list, ncol = 1)
+
+```
+
 A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
@@
 It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution.
+
+```{r Simulated_data_test_gi0_2, echo=FALSE, message=FALSE}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample_sizes <- c(49, 81, 121)
+N<- 100
+# Number of replications
+R <- 100
+
+# Number of bootstrap replications
+B <- 2
+mu_values <- c(1)
+alpha <- -600
+L <- 5
+
+  estimators <- list(
+
+    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator
+    #"$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
+    #"$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
+  )
+ #true_entropy <- entropy_gamma_sar(L, mu) 
+calculate_entropy_and_test_montecarlo <- function(sample_sizes, R, N, B, mu, alpha, L, estimators, true_entropy) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  output <- data.frame(
+    SampleSize = integer(0),
+    Estimator = character(0),
+    TypeIErrorRate = numeric(0)
+  )
+
+  for (ssize in sample_sizes) {
+
+    for (estimator_name in names(estimators)) {
+      estimator <- estimators[[estimator_name]]
+      reject_H0_count <- 0
+
+      for (n_replication in 1:N) {
+
+        #samples <- gi0_sample(mu, alpha, L, ssize)
+        v.entropy <- numeric(R)
+        for (r in 1:R) {
+
+        samples <- gi0_sample(mu, alpha, L, ssize)
+
+        if (grepl(" ", estimator_name)) {
+          v.entropy[r] <- estimator(samples, B = B)
+        } else {
+          v.entropy[r] <- estimator(samples)
+        }
+      }
+
+        mean_entropy <- mean(v.entropy)
+      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
+      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
+      alpha_t = 0.05
+
+        reject_H0_count <- reject_H0_count + sum(p_value < 0.05)
+      }
+
+      typeI_error_rate <- reject_H0_count / (N)
+
+      output <- rbind(
+        output,
+        data.frame(
+          SampleSize = ssize,
+          Estimator = estimator_name,
+          TypeIErrorRate = round(typeI_error_rate, 5)
+        )
+      )
+    }
+  }
+
+  colnames(output) <- c("$n$", "Estimator", "Type I Error Rate")
+
+  return(output)
+}
+
+calculate_results_test_gi0_montecarlo <- function(sample_sizes, R, N, B, mu_values, alpha, L, estimators) {
+  results_list <- list()
+
+  for (mu_val in mu_values) {
+
+    results <- calculate_entropy_and_test_montecarlo(sample_sizes, R, N, B, mu_val, alpha, L, estimators)
+    df <- as.data.frame(results)
+
+    results_list[[as.character(mu_val)]] <- df
+  }
+
+  return(results_list)
+}
+
+results_gi0_1_montecarlo <- calculate_results_test_gi0_montecarlo(sample_sizes, R, N, B, mu_values, alpha, L, estimators)
+#print(results_gi0_1_montecarlo)
+save(results_gi0_1_montecarlo, file = "./Data/results_gi0_1_montecarlo.Rdata")
+
+```
+
+```{r Table_test_gi0_montecarlo, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+load("./Data/results_gi0_1_montecarlo.Rdata")
+
+for (mu_val in mu_values) {
+  results_data <- results_gi0_1_montecarlo[[as.character(mu_val)]]
+
+  table_result <- kbl(
+    results_data,
+    caption = paste("Type I error with $L=5$, $\\mu=1$ and$\\alpha=\\infty$."),
+    format = "latex",
+    booktabs = TRUE,
+    align = "c",
+    escape = FALSE,
+    digits = 4,
+    label = "table_hipotesis_2"
+  ) %>%
+    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
+
+  #cat("### Results for mu =", mu_val, "\n")
+  print(table_result)
+
+}
+
+```
 Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 

### 2024-01-05 Code/R/Programs/data_gamma.R

@@ -1,0 +1,106 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 1000
+mu <- 1
+L <- 5
+B <- 2
+alpha1 <- -6
+sample.size <- c(81)
+
+TestStatistics1 <- NULL
+TestStatistics2 <- NULL
+TestStatistics3 <- NULL
+TestStatistics4 <- NULL
+mean_entropy1 <- numeric(length(sample.size))
+mean_entropy2 <- numeric(length(sample.size))
+mean_entropy3 <- numeric(length(sample.size))
+mean_entropy4 <- numeric(length(sample.size))
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  TestStat2 <- numeric(R)
+  TestStat3 <- numeric(R)
+  TestStat4 <- numeric(R)
+  
+  
+  for (r in 1:R) {
+    #z <- gi0_sample(mu, alpha1, L, s)
+    z <- gamma_sar_sample(L, mu, s)
+    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L)+L + lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
+    #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-01-05 Code/R/Programs/test_differences.R

@@ -1,0 +1,108 @@
+rm(list = ls())
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+library(latex2exp)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator.R")
+source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+source("../MainFunctions/al_omari_1_estimator.R")
+source("../MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 3000
+mu <- 1
+L <- 5
+B <- 1
+alpha1 <- -6
+sample.size <- c( 121)
+
+TestStatistics1 <- NULL
+TestStatistics2 <- NULL
+TestStatistics3 <- NULL
+TestStatistics4 <- NULL
+mean_entropy1 <- numeric(length(sample.size))
+mean_entropy2 <- numeric(length(sample.size))
+mean_entropy3 <- numeric(length(sample.size))
+mean_entropy4 <- numeric(length(sample.size))
+for (s in sample.size) {
+  TestStat1 <- numeric(R)
+  TestStat2 <- numeric(R)
+  TestStat3 <- numeric(R)
+  TestStat4 <- numeric(R)
+  
+  
+  for (r in 1:R) {
+    #z <- gi0_sample(mu, alpha1, L, s)
+    z <- gamma_sar_sample(L, mu, s)
+
+    TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
+    TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
[…]

### 2024-01-14 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Small format detail
paper updates and empirical densities

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 library(ggplot2)
@@
 library(latex2exp)
+library(e1071)# kurtosis
+library(viridis)
+library(nortest)# AD
 
@@
 
-Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.
+<!-- Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$. -->
 
-```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"}
-knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
-```
-As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution. 
-We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.
+<!-- ```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"} -->
+<!-- knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf") -->
+<!-- ``` -->
+<!-- As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution.  -->
+<!-- We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space. -->
 
@@
 
-```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}
+```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}
 
-L <- c(5)
+L <- c(8)
 alphas <- c(  -3, -8, -20, -1000)
@@
 
-```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=5$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
+```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
 
@@
 mu <- 1
-L <- 5
+L <- 8
 B <- 1
@@
 
-      #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
-      #TestStat2[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
     }
-
-    # mean_entropy1[sample.size == s] <- mean(TestStat1)
-    # #cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
-    # 
-    # mean_entropy2[sample.size == s] <- mean(TestStat2)
-    # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")
 
@@
 
-# Hypothesis testing based on non-parametric entropy {#sec:test}
-General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
-Following the work of these authors, the next result applies: 
-\begin{lemma}
-Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
-Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
-\begin{equation*}
-\sqrt{n}\,\Big(\label{Eq:bias_t}
-\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
-\xrightarrow[]{\mathcal{D}}
-\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
-\end{equation*}
-\end{lemma} 
-Consider, starting from the previous lemma, we aim at testing the following hypotheses:
-
-$$
- \begin{cases}\mathcal{H}_0: \mathcal{D}(\bm{\theta})=\Gamma_{\text{SAR}} \\ 
-  \mathcal{H}_1: \mathcal{D}(\bm{\theta})=G_I^0.\end{cases}
-$$
-In other words, we verify the hypothesis that the data are fully-developed speckle.
-<!-- \begin{align*} -->
-<!-- \mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\  -->
-<!-- \mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\ -->
-<!-- \mathcal{H}_1 &: T_{\mathcal{D}}< D_0.  -->
-<!-- \end{align*} -->
-For this purpose, we use the following test statistic:
-\begin{equation}
-\label{Eq:test_e}
-S(Z)= \widetilde{H}(Z)-H(Z).
-\end{equation}
-This test statistic $S(Z)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$.
-The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(Z)\approx 0$.
-Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero.
-This suggests significant differences and implies the presence of heterogeneous clutter.
-
-<!-- so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.
--->
-
-# Results {#sec:results}
-
 Simulations are conducted using $G_I^0$ distribution, with $200$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
@@
 estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
-  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),#parse(text=TeX("$H_{2}$")),
+  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),
                              "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
@@
 
-colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$")
+colnames(reshaped_results) <- c("$\\mu$", "$n$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$")
 
@@
     escape = FALSE, 
-    digits = 4,  
+    digits = 3,  
     label = "table2"  
@@
 
-```{r Simulated_data_test_gi0, echo=FALSE, message=FALSE}
+# Hypothesis testing based on non-parametric entropy {#sec:test}
+General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
+Following the work of these authors, the next result applies: 
+\begin{lemma}
+Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
+Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
+\begin{equation*}
+\sqrt{n}\,\Big(\label{Eq:bias_t}
+\widetilde{H}_{i}+\int_{-\infty}^\infty f(z)\ln f(z) \mathrm{d}z\Big)
+\xrightarrow[]{\mathcal{D}}
+\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
+\end{equation*}
+\end{lemma} 
+Consider, starting from the previous lemma, we aim at testing the following hypotheses:
 
+$$
+ \begin{cases}\mathcal{H}_0: \mu_{\widetilde{H}}-\mu_{H}=0 \\ 
+  \mathcal{H}_1:\mu_{\widetilde{H}}-\mu_{H}\neq0 .\end{cases}
+$$
+In other words, we verify the hypothesis that the data are fully-developed speckle.
+
+For this purpose, we use the following test statistic:
+\begin{equation}
+\label{Eq:test_e}
+S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
+\end{equation}
+This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$.
+The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$.
+Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero.
+This suggests significant differences and implies the presence of heterogeneous clutter.
+
+# Results {#sec:results}
+
+## The Proposed Test
+We analyze the finite sample size behavior of the test statistics defined in \eqref{Eq:test_e}.
+
+Fig.
+\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
+Results with $p$-values $> 0.05$  indicate no evidence against normality.
+Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails, aligning with normal distribution expectations.
+
+In Fig. \ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line, reinforcing our findings.
+
+```{r Simulated_density, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
-sample_sizes <- c(9, 25, 49, 81, 121)
-# Number of replications para simulacion montecarlo para calculo de error tipo 1
 
-N <- 1000
+R <- 1000
+mu <- 1
+B <- 2
+alpha1 <- -8
+sample.size <- c(50, 100, 150, 200, 250,300, 350)
+L_values <- c(2, 5, 8, 18)
 
-# Number of replications para calcular las entropias
-R <- 10
+all_summary_stats <- list()
+all_TestStatistics <- list()
+all_TestNormality <- list()
+all_plots <- list()
 
-# Number of bootstrap replications
-B <- 10
-mu_values <- c(5)
-alpha <- -1000
-L <- 2
+# For each L
+for (L in L_values) {
+  TestStatistics1 <- list()  
+  summary_stats <- data.frame( LValue = character(),
+                              SampleSize = numeric(),
+                              Mean = numeric(),
+                              SD = numeric(),
+                              Variance = numeric(),
+                              Skewness = numeric(),
+                              Kurtosis = numeric(),
+                              adpvalue = numeric()
+                              )  # Nueva columna para  L
+  # summary_normality <- data.frame(Sample_Size = numeric(),
+  #                               lillie_p_value = numeric(),
+  #                               ad_p_value = numeric())
+  #normality_test <- list()#
 
-  estimators <- list(
-    #"Correa" = correa_estimator,
-    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
-    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
-    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
-  )
+  for (s in sample.size) {
+    TestStat1 <- numeric(R)
 
-calculate_results_test_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
-  results_list <- list()
-
-  for (mu_val in mu_values) {
-
-    results <- calculate_entropy_and_test(sample_sizes, R, B, mu_val, alpha, L, estimators)
-    df <- as.data.frame(results)
-
-    results_list[[as.character(mu_val)]] <- df
+    for (r in 1:R) {
+      z <- gamma_sar_sample(L, mu, s)
+      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
     }
 
-  return(results_list)
+    TestStatistics1[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)
+
+    mean_val <- mean(TestStat1)
+    sd_val <- sd(TestStat1)
+    var_val <- var(TestStat1)
+    skewness_val <- skewness(TestStat1)
+    kurtosis_val <- kurtosis(TestStat1)
+   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
+    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
+
+    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
+                                                     SampleSize = s,
+                                                     Mean = mean_val,
+                                                     SD = sd_val,
+                                                     Variance = var_val,
+                                                     Skewness = skewness_val,
+                                                     Kurtosis = kurtosis_val,
+                                                     adpvalue = ad_p_value
+                                                     ))
+
+    # Almacenar resultados de normalidad
+    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
+    #                                                          SampleSize = s,
+    #                                                          lilliepvalue = lillie_p_value,
+    #                                                          adpvalue = ad_p_value))
   }
 
-results_gi0_1 <- calculate_results_test_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)
+  all_TestStatistics[[as.character(L)]] <- TestStatistics1
+  all_summary_stats[[as.character(L)]] <- summary_stats
+  #all_TestNormality[[as.character(L)]] <- summary_normality
 
-save(results_gi0_1, file = "./Data/results_gi0_1.Rdata")
+#save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
+  save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
+}
 
@@
 
-```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under Gamma SAR model.", fig.width=6, fig.height=5}
 
-load("./Data/results_gi0_1.Rdata")
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
 
-for (mu_val in mu_values) {
-  results_data <- results_gi0_1[[as.character(mu_val)]]
+all_plots <- list()
 
-  table_result <- kbl(
-    results_data,
-    caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$."),
+for (L in L_values) {
+  load(paste0("./Data/results_", L, ".Rdata"))
+
+  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
+  combined_data$L <- L
+
+  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
+    geom_line(stat = "density", linewidth = 1.0) +
+    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
+    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+    labs(x = "Test Statistics", y = "Density") +
+    ggtitle(bquote(italic(L) == .(L))) +
+    theme(plot.title = element_text(hjust = 0.5))#titulo centrado
+
+  if (!any(L == L_values)) {
+    p = p
+  }
+
+  all_plots[[as.character(L)]] <- p
+}
+
+combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot)
+
+```
+
+```{r Table_statistic, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+# for (L in L_values) {
+#   summary_stats <- all_summary_stats[[as.character(L)]]
+#   
+#   print(summary_stats)
+# }
+
+# summary_stats_2 <- all_summary_stats[["2"]]
+
+load("./Data/results_2.Rdata")
+summary_stats_2 <- all_summary_stats[["2"]]
+
+load("./Data/results_5.Rdata")
+summary_stats_5 <- all_summary_stats[["5"]]
+
+load("./Data/results_8.Rdata")
+summary_stats_8 <- all_summary_stats[["8"]]
+
+combined_summary_stats <- rbind(
+  transform(summary_stats_2),
+  transform(summary_stats_5),
+  transform(summary_stats_8)
+
+)
+colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "Skewness", "Kurtosis", "$p$-value")
+
+# table
+table_result_combined <- kbl(
+  combined_summary_stats,
+  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
   format = "latex",
@@
   digits = 4,
-    label = "table_hipotesis"
-    #label = paste("table_hipotesis", mu_val, sep = "")
+  label = "table_stat_combined"
 ) %>%
-    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")
+  collapse_rows(latex_hline = "major", valign = "middle")# %>%
+ # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)
 
-  print(table_result)
+print(table_result_combined)
+
+```
+
+```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Normal QQ-plots for  $n=100$.", fig.width=6, fig.height=5}
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
+
+# Cargar los resultados guardados
+load("./Data/results_2.Rdata")
+load("./Data/results_5.Rdata")
+load("./Data/results_8.Rdata")
+load("./Data/results_18.Rdata")
+
+# Tamaño de muestra específico que deseas graficar
+selected_sample_size <- 100
+
+# Crear una lista para almacenar los ggplots
+ggplot_list <- list()
+
+# Para cada valor de L
+for (L in c(2, 5, 8, 18)) {
+  TestStatistics1 <- all_TestStatistics[[as.character(L)]]
+
+  # Verifica si el tamaño de muestra seleccionado está disponible
+  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
+    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
+                aes(sample = Test_Statistics)) +
+      geom_qq(col = "blue", shape = 20) +
+      geom_qq_line(col = "darkgreen", linetype = 2) +
+      labs(title = bquote(italic(L) == .(L)),
+           x = "Theoretical Quantiles",
+           y = "Sample Quantiles") +
+      theme(plot.title = element_text(hjust = 0.5))#titulo centrado
+
+    ggplot_list[[as.character(L)]] <- p
+  } else {
+    warning(paste("No size sample", selected_sample_size, " L =", L))
   }
+}
+combined_plot1 <- wrap_plots(ggplot_list, ncol = 2, nrow = 2) +
+  plot_layout(guides = "collect")
+
+print(combined_plot1)
+
+# }
 
@@
     annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
-   # geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
-   # annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), y=7, parse=TRUE, label="alpha==-20", hjust=-.1, vjust=2.0, col="darkgreen") +
     geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
-    #annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), y=7, parse=TRUE, label="alpha==-1000", hjust=-.1, vjust=4.0, col="darkgreen") +
-    labs(x = "Test Statistics", y = "Empirical Density") +
-    #annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
     theme_minimal() +
@@
 
-A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
-The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $G_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=5$, $L=2$, and $\alpha= -1000$.
-The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.493$.  
-It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution.
-
-```{r Simulated_data_test_gi0_2, echo=FALSE, message=FALSE}
-
-set.seed(1234567890, kind = "Mersenne-Twister")
-sample_sizes <- c(49, 81, 121)
-N<- 100
-# Number of replications
-R <- 100
-
-# Number of bootstrap replications
-B <- 2
-mu_values <- c(1)
-alpha <- -600
-L <- 5
-
-  estimators <- list(
-
-    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator
-    #"$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
-    #"$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
-  )
- #true_entropy <- entropy_gamma_sar(L, mu) 
-calculate_entropy_and_test_montecarlo <- function(sample_sizes, R, N, B, mu, alpha, L, estimators, true_entropy) {
-  true_entropy <- entropy_gamma_sar(L, mu)
-  output <- data.frame(
-    SampleSize = integer(0),
-    Estimator = character(0),
-    TypeIErrorRate = numeric(0)
-  )
-
-  for (ssize in sample_sizes) {
-
-    for (estimator_name in names(estimators)) {
-      estimator <- estimators[[estimator_name]]
-      reject_H0_count <- 0
-
-      for (n_replication in 1:N) {
-
-        #samples <- gi0_sample(mu, alpha, L, ssize)
-        v.entropy <- numeric(R)
-        for (r in 1:R) {
-
-        samples <- gi0_sample(mu, alpha, L, ssize)
-
-        if (grepl(" ", estimator_name)) {
-          v.entropy[r] <- estimator(samples, B = B)
-        } else {
-          v.entropy[r] <- estimator(samples)
-        }
-      }
-
-        mean_entropy <- mean(v.entropy)
-      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
-      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
-      alpha_t = 0.05
-
-        reject_H0_count <- reject_H0_count + sum(p_value < 0.05)
-      }
-
-      typeI_error_rate <- reject_H0_count / (N)
-
-      output <- rbind(
-        output,
-        data.frame(
-          SampleSize = ssize,
-          Estimator = estimator_name,
-          TypeIErrorRate = round(typeI_error_rate, 5)
-        )
-      )
-    }
-  }
-
-  colnames(output) <- c("$n$", "Estimator", "Type I Error Rate")
-
-  return(output)
-}
-
-calculate_results_test_gi0_montecarlo <- function(sample_sizes, R, N, B, mu_values, alpha, L, estimators) {
-  results_list <- list()
-
-  for (mu_val in mu_values) {
-
-    results <- calculate_entropy_and_test_montecarlo(sample_sizes, R, N, B, mu_val, alpha, L, estimators)
-    df <- as.data.frame(results)
-
-    results_list[[as.character(mu_val)]] <- df
-  }
-
-  return(results_list)
-}
-
-results_gi0_1_montecarlo <- calculate_results_test_gi0_montecarlo(sample_sizes, R, N, B, mu_values, alpha, L, estimators)
-#print(results_gi0_1_montecarlo)
-save(results_gi0_1_montecarlo, file = "./Data/results_gi0_1_montecarlo.Rdata")
-
-```
-
-```{r Table_test_gi0_montecarlo, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-load("./Data/results_gi0_1_montecarlo.Rdata")
-
-for (mu_val in mu_values) {
-  results_data <- results_gi0_1_montecarlo[[as.character(mu_val)]]
-
-  table_result <- kbl(
-    results_data,
-    caption = paste("Type I error with $L=5$, $\\mu=1$ and$\\alpha=\\infty$."),
-    format = "latex",
-    booktabs = TRUE,
-    align = "c",
-    escape = FALSE,
-    digits = 4,
-    label = "table_hipotesis_2"
-  ) %>%
-    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
-
-  #cat("### Results for mu =", mu_val, "\n")
-  print(table_result)
-
-}
-
-```
-Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 
-The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy. 
-The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above $25$, suggesting that the data are consistent with the null hypothesis.
-
 # Conclusion {#sec:conclusion}

### 2024-01-14 Code/R/Programs/test_differences.R

@@ -21,12 +21,12 @@ source("../MainFunctions/gi0_sample.R")
 
 set.seed(1234567890, kind = "Mersenne-Twister")
 
-R <- 3000
+R <- 10
 mu <- 1
 L <- 5
 B <- 1
 alpha1 <- -6
-sample.size <- c( 121)
+sample.size <- c( 9, 25, 49, 81, 121)
 
 TestStatistics1 <- NULL
 TestStatistics2 <- NULL
@@ -47,8 +47,8 @@ for (s in sample.size) {
     #z <- gi0_sample(mu, alpha1, L, s)
     z <- gamma_sar_sample(L, mu, s)
 
-    TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
-    TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    #TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
+    TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
     #TestStat4[r] <- bootstrap_correa_estimator(z, B)+( L+lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 
     
     }
@@ -57,8 +57,8 @@ for (s in sample.size) {
   mean_entropy1[sample.size == s] <- mean(TestStat1)
   cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
   
-  mean_entropy2[sample.size == s] <- mean(TestStat2)
-  cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")
[…]

### 2024-01-15 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Minor details
add Cache for chunks, autodep for Chunk 8

@@
 ```{r setup, include=FALSE}
-#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+#knitr::opts_chunk$set(echo = FALSE)
 library(ggplot2)
@@
 
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
@@
 
-* \cite{correa1995new}: $\widehat{H}_{\text{C}}$.
+* Correa&nbsp;\cite{correa1995new}: $\widehat{H}_{\text{C}}$.
 
-* \cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.
+* Ebrahimi et al&nbsp;\cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.
 
-* \cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.
+* Al Omary&nbsp;\cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.
 
@@
 
-In Fig.
-\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
+In Fig. \ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
 The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
@@
 
-```{r Simulated_density, echo=FALSE, message=FALSE}
+```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 all_TestStatistics <- list()
-all_TestNormality <- list()
-all_plots <- list()
+#all_TestNormality <- list()
+#all_plots <- list()
 
@@
 
-    # Almacenar resultados de normalidad
     # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
@@
 
-#save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
-  save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
+#save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
+  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
 }
@@
 
-# for (L in L_values) {
-#   summary_stats <- all_summary_stats[[as.character(L)]]
-#   
-#   print(summary_stats)
-# }
-
-# summary_stats_2 <- all_summary_stats[["2"]]
-
 load("./Data/results_2.Rdata")
@@
 
-# Cargar los resultados guardados
+# Load saved results
 load("./Data/results_2.Rdata")
@@
 
-# Tamaño de muestra específico que deseas graficar
+# Specific sample size
 selected_sample_size <- 100
 
-# Crear una lista para almacenar los ggplots
+# 
 ggplot_list <- list()
 
-# Para cada valor de L
+#  L
 for (L in c(2, 5, 8, 18)) {
@@
 
-  # Verifica si el tamaño de muestra seleccionado está disponible
+  # 
   if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
@@
       legend.position = "none"  
-    )
+    )+
+    labs(x = "Test Statistics", y = "Density")
 

### 2024-01-17 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add coefficient of variation (CV)

@@
 
-R <- 1000
+R <- 500
 mu <- 1
@@
                               Variance = numeric(),
+                              CV= numeric(),
                               Skewness = numeric(),
@@
     ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
+    cv_val <- (sd_val / mean_val)
 
@@
                                                      Variance = var_val,
+                                                      CV = cv_val,
                                                      Skewness = skewness_val,
@@
 )
-colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "Skewness", "Kurtosis", "$p$-value")
+colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "CV", "Skewness", "Kurtosis", "$p$-value")
 

### 2024-01-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
simulation test with Real SAR Images

@@
    - \usepackage{mathabx}
+   - \usepackage{subfig}
+   #- \usepackage{subcaption}
   # - \usepackage{pgf}
@@
     citation_package: natbib
+    #extra_dependencies: "subfig"
+    #keep_tex: yes
 
@@
 
+#library(grid)
+
 theme_set(theme_minimal() +
@@
 #The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
-source("../../../Code/R/Programs/functions_sample_bias_mse.R")#
+source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
+source("../../../Code/R/Programs/read_ENVI_images.R")
 
@@
 
-R <- 500
+R <- 1000
 mu <- 1
@@
 ) %>%
-  collapse_rows(latex_hline = "major", valign = "middle")# %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+   kable_styling(latex_options = "scale_down")
  # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)
@@
 
+## Real SAR Images
+
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
+knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
+#knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")
+
+knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
+knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
+knitr::include_graphics("../../../Figures/PNG/BER_Intensity_VV.jpg")
+```
+
+```{r SAR_simulations, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#, cache = TRUE, autodep = TRUE
+set.seed(1234567890, kind = "Mersenne-Twister")
+x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
+x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
+x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
+x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+
+#Brazil
+nRows_Brazil <- 518
+nCols_Brazil <- 519
+
+centerRow_Brazil <- floor(nRows_Brazil / 2)
+centerCol_Brazil <- floor(nCols_Brazil / 2)
+
+roiSize_Brazil <- 200
+
+# 
+roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
+roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1
+
+roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
+roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1
+
+# Extraer el ROI
+roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]
+
+mean_data_brasil <- mean(roi_Brazil)
+Entropy_brasil <- correa_estimator(roi_Brazil)
+entropia_estimada_boot_brasil <- bootstrap_correa_estimator( roi_Brazil, 10)
+True_entropy_brasil <-(log(mean( roi_Brazil)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+Test_difference_brasil <- bootstrap_correa_estimator_log_mean( roi_Brazil, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+#difference_correa_brasil <- correa_estimator( roi_Brazil) - log(mean(roi_Brazil))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+
+#Berlin
+nCols_Berlin  = 501
+nRows_Berlin  = 501
+
+centerRow_Berlin <- floor(nRows_Berlin / 2)
+centerCol_Berlin <- floor(nCols_Berlin / 2)
+
+roiSize_Berlin <- 200
+
+# Calcular las coordenadas del ROI
+roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
+roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1
+
+roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
+roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1
+
+# Extraer el ROI
+roi_Berlin<- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]
+
+mean_data_Berlin <- mean(roi_Berlin)
+Entropy_Berlin <- correa_estimator(roi_Berlin)
+entropia_estimada_boot_Berlin <- bootstrap_correa_estimator( roi_Berlin, 10)
+True_entropy_Berlin <-(log(mean( roi_Berlin)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+Test_difference_Berlin <- bootstrap_correa_estimator_log_mean( roi_Berlin, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+#difference_correa_Berlin <- correa_estimator( roi_Berlin) - log(mean(roi_Berlin))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+
+# Flevoland
+nCols_Flevoland = 355
+nRows_Flevoland = 354
+
+centerRow_Flevoland <- floor(nRows_Flevoland / 2)
+centerCol_Flevoland <- floor(nCols_Flevoland / 2)
+
+roiSize_Flevoland <- 200
+
+#  coordenadas del ROI
+roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
+roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1
+
+roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
+roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1
+
+# Extraer el ROI
+roi_Flevoland<- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]
+
+mean_data_Flevoland <- mean(roi_Flevoland)
+Entropy_Flevoland <- correa_estimator(roi_Flevoland)
+entropia_estimada_boot_Flevoland <- bootstrap_correa_estimator( roi_Berlin, 10)
+True_entropy_Flevoland <-(log(mean( roi_Flevoland)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+Test_difference_Flevoland <- bootstrap_correa_estimator_log_mean( roi_Flevoland, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+#difference_correa_Flevoland <- correa_estimator( roi_Flevoland) - log(mean(roi_Flevoland))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+
+#----------------------------------------------
+#ottawa
+nCols_Ottawa = 572
+nRows_Ottawa= 558
+
+centerRow_Ottawa  <- floor(nRows_Ottawa / 2)
+centerCol_Ottawa  <- floor(nCols_Ottawa  / 2)
+
+ roiSize_Ottawa <- 100
+# 
+# # Coordenadas del ROI en la parte superior
+ roiUpperStartRow <- 1
+ roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
+# 
+ roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
+ roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
+# 
+# # Extraer el ROI en la parte superior
+ roi_Ottawa<- x_Ottawa[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]
+
+ mean_data_Ottawa <- mean(roi_Ottawa)
+ Entropy_Ottawa <- correa_estimator(roi_Ottawa)
+ entropia_estimada_boot_Ottawa <- bootstrap_correa_estimator( roi_Ottawa, 10)
+ True_entropy_Ottawa <-(log(mean( roi_Ottawa)) + (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+ Test_difference_Ottawa <- bootstrap_correa_estimator_log_mean( roi_Ottawa, 10)- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+ #difference_correa_Ottawa <- correa_estimator( roi_Ottawa) - log(mean(roi_Ottawa))- ( (5 - log(5) + lgamma(5) + (1 - 5) * digamma(5)))
+
+ resultados_df <- data.frame(
+   Ciudad = c("Amazonas", "Berlin", "Flevoland", "Ottawa"),
+   Media = c(mean_data_brasil, mean_data_Berlin, mean_data_Flevoland, mean_data_Ottawa),
+   Entropia_Estimada = c(Entropy_brasil, Entropy_Berlin, Entropy_Flevoland, Entropy_Ottawa),
+   Entropia_Estimada_Boot = c(entropia_estimada_boot_brasil, entropia_estimada_boot_Berlin, entropia_estimada_boot_Flevoland, entropia_estimada_boot_Ottawa),
+   Entropia_Verdadera = c(True_entropy_brasil, True_entropy_Berlin, True_entropy_Flevoland, True_entropy_Ottawa),
+   Diferencia_Test_Entropia = c(Test_difference_brasil, Test_difference_Berlin, Test_difference_Flevoland, Test_difference_Ottawa)
+
+ )
+
+ colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(Z)$")
+
+#
+print(
+  kbl(
+    resultados_df,
+    caption = "Results of applying the statistical test to SAR images.",
+    format = "latex",
+    booktabs = TRUE,
+    align = "c",
+    escape = FALSE, 
+    digits = 4,  
+    label = "table_sar", 
+  ) %>%
+    collapse_rows( latex_hline = "major", valign = "middle")
+)
+```
+
 # Conclusion {#sec:conclusion}

### 2024-01-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
minor changes

@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
+  caption = "Descriptive analysis of $S(\\bm Z; L)$ for different values of $L$, and $\\mu=1$.",
   format = "latex",
@@
 
-## Real SAR Images
+## SAR Images
 
@@
 
- colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(Z)$")
+ colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(\\bm Z)$")
 

### 2024-01-23 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add new images 512 x 512

--- 2024-01-17 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
    - \usepackage{mathabx}
-  # - \usepackage{pgf}
+   - \usepackage{subfig}
+   #- \usepackage{subcaption}
+   - \usepackage{pgf}
    - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]
@@
 library(ggsci)
-#library(wesanderson)
 library(ggpubr)
@@
 \newcommand{\bias}{\operatorname{Bias}}
+\setlength{\tabcolsep}{4pt}
 
@@
 
-The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical}. 
+The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical_gamma_and_gi0}. 
 It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. 
@@
 
-```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
-
+```{r Simulated_empirical_gamma_and_gi0, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 B <- 1
-sample.size <- c( 121)
-
+sample.size <- c(121)
 alpha1_values <- c(-3, -8, -20, -1000)
 
-plots_list <- list()
+TestStatisticsList <- list()
 
 for (alpha_val in alpha1_values) {
-
   alpha1 <- alpha_val
-
   TestStatistics1 <- NULL
   TestStatistics2 <- NULL
-
-  mean_entropy1 <- numeric(length(sample.size))
-  mean_entropy2 <- numeric(length(sample.size))
 
@@
       TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
-
     }
@@
 
-  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
-  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
+  TestStatisticsList[[as.character(alpha_val)]] <- list(TestStatistics1 = TestStatistics1, TestStatistics2 = TestStatistics2)
+}
 
-  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
+save(TestStatisticsList, file = "./Data/data_empirical_entropy.RData")
+
+```
+
+```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
+
+load("./Data/data_empirical_entropy.Rdata")
+plots_list <- list()
+
+for (alpha_val in alpha1_values) {
+  plot_data <- TestStatisticsList[[as.character(alpha_val)]]
+
+  max_density1 <- max(density(plot_data$TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
+  max_density2 <- max(density(plot_data$TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
+
+  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
     geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
-    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
-    annotate("text", x = max(TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
+    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
+    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
              label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
-    annotate("text", x = max(TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
+    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
              label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
@@
 ```
+
 ## Estimation of the Shannon Entropy
@@
 
-In Fig. \ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions. 
+In Fig.&nbsp;\ref{fig:Plot_bias_mse_gi0} we depict comparisons of bias and mean squared error (MSE) between the original non-parametric entropy estimators and their respective bootstrap-enhanced versions.
 The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
@@
 ```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
 load("./Data/results_gi0.Rdata")
 
+# Define estimators
 estimators_to_table <- c("Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap")
 
+# Filter and reshape data
 filtered_results <- purrr::map_dfr(results_gi0, ~ .x %>% filter(Estimator %in% estimators_to_table), .id = "mu")
@@
 
-#
+reshaped_results[] <- lapply(reshaped_results, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
 print(
@@
     booktabs = TRUE,
-    align = "c",
+    align = "lrrrrrrrr",
     escape = FALSE, 
@@
     add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
-    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
+    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+    row_spec(0,  align = "c")
+    #kable_styling(latex_options = "hold_position", "scale_down")
   )
+
 ```
@@
 Fig.
-\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
+\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
 Results with $p$-values $> 0.05$  indicate no evidence against normality. 
-Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails, aligning with normal distribution expectations.
+Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails.
+The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases, aligning with normal distribution expectations.
 
@@
 ```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+#, cache = TRUE, autodep = TRUE
 set.seed(1234567890, kind = "Mersenne-Twister")
 
-R <- 500
+R <- 100
 mu <- 1
-B <- 2
+B <- 1
 alpha1 <- -8
-sample.size <- c(50, 100, 150, 200, 250,300, 350)
+sample.size <- c(50, 100, 150, 200, 250,300)
 L_values <- c(2, 5, 8, 18)
@@
 all_TestStatistics <- list()
-#all_TestNormality <- list()
-#all_plots <- list()
 
@@
                               adpvalue = numeric()
-                              )  # Nueva columna para  L
-  # summary_normality <- data.frame(Sample_Size = numeric(),
-  #                               lillie_p_value = numeric(),
-  #                               ad_p_value = numeric())
-  #normality_test <- list()#
+                              )
 
@@
 
-    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
-    #                                                          SampleSize = s,
-    #                                                          lilliepvalue = lillie_p_value,
-    #                                                          adpvalue = ad_p_value))
   }
@@
   all_summary_stats[[as.character(L)]] <- summary_stats
-  #all_TestNormality[[as.character(L)]] <- summary_normality
 
-#save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
   save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
@@
 
+cat("\\setlength{\\tabcolsep}{1.0pt}\n")
+
 load("./Data/results_2.Rdata")
@@
 
-# table
+# LaTeX notation for negative numbers and integers
+combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
 table_result_combined <- kbl(
   combined_summary_stats,
-  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
+  caption = "Descriptive analysis of $S(\\bm Z; L)$ for different values of $L$, and $\\mu=1$.",
   format = "latex",
   booktabs = TRUE,
-  align = "c",
+  align = "lrrrrrrr",
   escape = FALSE,
@@
   label = "table_stat_combined"
+  #table.env = 'table*' # to span multiple columns
 ) %>%
-  collapse_rows(latex_hline = "major", valign = "middle")# %>%
- # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
 
@@
     for (r in 1:R) {
-      z <- gi0_sample(mu, alpha1, L, s)
+
+      z <- gamma_sar_sample(L, mu, s)
       TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
+      z1 <- gi0_sample(mu, alpha1, L, s)
+      TestStat2[r] <- bootstrap_correa_estimator_log_mean(z1, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+        #(L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
 
@@
 
+## Experiments on Real SAR Images
+
+To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band,with  HH polarization, and intensity format.
+The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.
+
+We evaluate the test accuracy with small data portions.
+Ensuring resistance to contamination is crucial, especially in small samples with $5\times 5$, $7\times 7$, or $9\times 9$ windows that may contain data from areas with varying textures.
+Our assessment determines if the test can produce reasonable estimations, even when some data deviates from the assumed model.
+
+Table&nbsp;\ref{tab:table_sar} shows the results for $5 \times 5$ windows, detailing the performance of the proposed test in accurately identifying the origin of the data.
+The metadata associated with these original SAR images includes a number of looks $L = 5$.
+
+The openly accessible Sentinel-1 data used in this study was downloaded as Level-1 Ground Range Detected (GRD) products from the Copernicus Data Space Ecosystem (\url{https://dataspace.copernicus.eu}).
+This format, gaining popularity among operational and application users, containing only the co-polarized and cross-polarized backscatter intensities (VV, VH).
+
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
+knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
+knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
+knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
+knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")
+```
+
+```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+#, cache = TRUE, autodep = TRUE
+set.seed(1234567890, kind = "Mersenne-Twister")
+x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
+x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
+x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
+x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+
+L <- 5
+B <- 10
+
+# Brazil
+nRows_Brazil <- 512
+nCols_Brazil <- 512
+
+centerRow_Brazil <- floor(nRows_Brazil / 2)
+centerCol_Brazil <- floor(nCols_Brazil / 2)
+
+roiSize_Brazil <- 5
+
+# Coordinates of the ROI
+roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
+roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1
+
+roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
+roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1
+
+# Extract the ROI
+roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]
+
+mean_data_brasil <- mean(roi_Brazil)
+Entropy_brasil <- correa_estimator(roi_Brazil)
+entropia_estimada_boot_brasil <- bootstrap_correa_estimator(roi_Brazil, B)
+True_entropy_brasil <- (log(mean(roi_Brazil)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+Test_difference_brasil <- bootstrap_correa_estimator_log_mean(roi_Brazil, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+
+# Berlin
+nCols_Berlin = 512
+nRows_Berlin = 512
+
+centerRow_Berlin <- floor(nRows_Berlin / 2)
+centerCol_Berlin <- floor(nCols_Berlin / 2)
+
+roiSize_Berlin <- 5
+
+# Calculate ROI coordinates
+roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
+roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1
+
+roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
+roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1
+
+# Extract the ROI
+roi_Berlin <- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]
+
+mean_data_Berlin <- mean(roi_Berlin)
+Entropy_Berlin <- correa_estimator(roi_Berlin)
+entropia_estimada_boot_Berlin <- bootstrap_correa_estimator(roi_Berlin, B)
+True_entropy_Berlin <- (log(mean(roi_Berlin)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+Test_difference_Berlin <- bootstrap_correa_estimator_log_mean(roi_Berlin, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+
+# Flevoland
+nCols_Flevoland = 512
+nRows_Flevoland = 512
+
+centerRow_Flevoland <- floor(nRows_Flevoland / 2)
+centerCol_Flevoland <- floor(nCols_Flevoland / 2)
+
+roiSize_Flevoland <- 5
+
+# ROI coordinates
+roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
+roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1
+
+roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
+roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1
+
+# Extract the ROI
+roi_Flevoland <- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]
+
+mean_data_Flevoland <- mean(roi_Flevoland)
+Entropy_Flevoland <- correa_estimator(roi_Flevoland)
+entropia_estimada_boot_Flevoland <- bootstrap_correa_estimator(roi_Berlin, B)
+True_entropy_Flevoland <- (log(mean(roi_Flevoland)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+Test_difference_Flevoland <- bootstrap_correa_estimator_log_mean(roi_Flevoland, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+
+# Ottawa
+nCols_Ottawa = 512
+nRows_Ottawa = 512
+
+centerRow_Ottawa <- floor(nRows_Ottawa / 2)
+centerCol_Ottawa <- floor(nCols_Ottawa / 2)
+
+roiSize_Ottawa <- 5
+
+# ROI coordinates in the upper part
+roiUpperStartRow <- 1
+roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
+
+roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
+roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
+
+# Extract the ROI in the upper part
+roi_Ottawa <- x_Ottawa[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]
+
+mean_data_Ottawa <- mean(roi_Ottawa)
+Entropy_Ottawa <- correa_estimator(roi_Ottawa)
+entropia_estimada_boot_Ottawa <- bootstrap_correa_estimator(roi_Ottawa, B)
+True_entropy_Ottawa <- (log(mean(roi_Ottawa)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+Test_difference_Ottawa <- bootstrap_correa_estimator_log_mean(roi_Ottawa, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+
+# Save results
+resultados_df <- data.frame(
+  Ciudad = c("Amazonas", "Berlin", "Flevoland", "Ottawa"),
+  Media = c(mean_data_brasil, mean_data_Berlin, mean_data_Flevoland, mean_data_Ottawa),
+  Entropia_Estimada = c(Entropy_brasil, Entropy_Berlin, Entropy_Flevoland, Entropy_Ottawa),
+  Entropia_Estimada_Boot = c(entropia_estimada_boot_brasil, entropia_estimada_boot_Berlin, entropia_estimada_boot_Flevoland, entropia_estimada_boot_Ottawa),
+  Entropia_Verdadera = c(True_entropy_brasil, True_entropy_Berlin, True_entropy_Flevoland, True_entropy_Ottawa),
+  Diferencia_Test_Entropia = c(Test_difference_brasil, Test_difference_Berlin, Test_difference_Flevoland, Test_difference_Ottawa)
+)
+
+colnames(resultados_df) <- c("Area", "Mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(\\bm Z)$")
+
+save(resultados_df, file = "./Data/resultados_df.Rdata")
+
+```
+
+```{r Table_SAR_simulations, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+cat("\\setlength{\\tabcolsep}{4pt}\n")
+ load("./Data/resultados_df.Rdata")
+
+resultados_df[] <- lapply(resultados_df, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+print(
+  kbl(
+    resultados_df,
+    caption = "Results of applying the statistical test to SAR images.",
+    format = "latex",
+    booktabs = TRUE,
+    align = "lrrrrrrr",
+    escape = FALSE,
+    digits = 4,
+    label = "table_sar",
+    linesep = "",
+  ) %>%
+    #kable_styling(latex_options = "hold_position") %>%
+    row_spec(0,  align = "c")# %>%
+
+)
+
+```
+
 # Conclusion {#sec:conclusion}

### 2024-01-23 Code/R/PlottingFunctions/Plot_SAR_real.R

@@ -1,0 +1,368 @@
+
+rm(list = ls())
+
+library(raster)
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+
+nCols_Ottawa <- 512
+nRows_Ottawa <- 512
+
+centerRow_Ottawa <- floor(nRows_Ottawa / 2)
+centerCol_Ottawa <- floor(nCols_Ottawa / 2)
+
+roiSize_Ottawa <- 50
+
+roiUpperStartRow <- 1
+roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
+
+roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
+roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
+
+# ROI en la parte superior
+roi <- x[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]
+escala_log <- 0.01
+subx_log <- log10(roi + escala_log)
+
+# Crear un objeto raster
+raster_obj <- raster(subx_log)
+media_valor2 <- mean(raster_obj)
+
+# Guardar el ROI como PNG
+savepng <- function(imagen, nombre) {
+  png(file = nombre, width = dim(imagen)[2], height = dim(imagen)[1])
+  vectorzeros <- replicate(4, 0)
+  par(mar = vectorzeros, oma = vectorzeros, omi = vectorzeros)
+  image(imagen, col = gray(seq(0, 1, length.out = 256)))
+  #image(imagen, col = gray(seq(0, 0.6, length.out = 51)))
+  dev.off()
+  return(0)
+}
+
+savepng(raster_obj, "./ROIs/Ottawa_roi3.png")
+
+# Crear una copia de la imagen completa
+x_copy <- x
+
+# Dibujar un cuadro de contorno azul alrededor del ROI
+max_roi_value <- max(roi)
+
+# Dibujar un cuadro de contorno azul alrededor del ROI
[…]

### 2024-02-01 Code/R/RMarkdown/EntropyPlots.Rmd
add size and power analysis and new images

--- 2023-12-20 Code/R/RMarkdown/EntropyPlots.Rmd
@@
 ```
+
+<!-- ```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->
+
+<!-- load("./Data/results_gi0_1.Rdata") -->
+
+<!-- mu_values <-c(1, 2) -->
+
+<!-- # Interpretación de rechazo o no rechazo -->
+<!-- for (mu_val in mu_values) { -->
+<!--   results_data <- results_gi0_1[[as.character(mu_val)]] -->
+
+<!--   table_result <- kbl( -->
+<!--     results_data, -->
+<!--    # caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\pha1=-1000$ , #$H_{\\Gamma_{\\text{SAR}}}=2.493$."), -->
+<!--     format = "latex", -->
+<!--     booktabs = TRUE, -->
+<!--     align = "c", -->
+<!--     escape = FALSE, -->
+<!--     digits = 4, -->
+<!--     label = "table_hipotesis" -->
+<!--   ) %>% -->
+<!--     collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle") -->
+
+<!--   cat("### Results for mu =", mu_val, "\n") -->
+<!--   print(table_result) -->
+
+<!--   # Interpretación de rechazo o no rechazo -->
+<!--   cat(ifelse(nrow(results_data) > 0, -->
+<!--              paste("For mu =", mu_val, ":\n"), -->
+<!--              paste("No observations for mu =", mu_val, ":\n"))) -->
+
+<!--   cat(ifelse(nrow(results_data) > 0, -->
+<!--              paste( -->
+<!--                "Sample Size ", results_data$`$n$`, " Estimator ", results_data$Estimator, -->
+<!--                ifelse(results_data$RejectNull, -->
+<!--                       " the null hypothesis is rejected.", -->
+<!--                       " the null hypothesis is not rejected." -->
+<!--                ), "\n" -->
+<!--              ), -->
+<!--              "\n")) -->
+<!-- } -->
+
+<!-- ``` -->

### 2024-02-01 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add size and power analysis and new images

@@
              label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
-    labs(x = "Entropy", y = "Empirical Density") +
+    labs(x = "Entropy", y = "Density") +
     annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
@@
 $$
- \begin{cases}\mathcal{H}_0: \mu_{\widetilde{H}}-\mu_{H}=0 \\ 
-  \mathcal{H}_1:\mu_{\widetilde{H}}-\mu_{H}\neq0 .\end{cases}
+ \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H(\bm{Z})=0 \\ 
+  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H(\bm{Z})\neq0 .\end{cases}
 $$
@@
 
-```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+```{r Simulated_density, echo=FALSE, message=FALSE}
 #, cache = TRUE, autodep = TRUE
@@
 
-R <- 100
+R <- 500
 mu <- 1
-B <- 1
+B <- 2
 alpha1 <- -8
-sample.size <- c(50, 100, 150, 200, 250,300)
+sample.size <- c(50, 100, 150)
 L_values <- c(2, 5, 8, 18)
@@
       z <- gamma_sar_sample(L, mu, s)
+      #z <- gi0_sample(mu, alpha1, L, s)
       TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
@@
 
-# LaTeX notation for negative numbers and integers
+# LaTeX notation 
 combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
@@
 
+We proceeded to explore the capabilities of the proposed test in terms of size and power.
+Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2(1-\Phi(\varepsilon))$, where $\Phi$ is the standard Gaussian cumulative distribution function and
+$$
+\varepsilon=\frac{\tilde{H}(\bm{Z})-H(\bm{Z})}{\sigma_S}.
+$$
+Nominal levels of $1\%$, $5\%$, and $10\%$ were considered.
+In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results.
+In all cases, the nominal level has been achieved.
+The power, in general, improves with the increase in the number of looks.
+The results are presented in Table \ref{tab:table_size_power}, providing a more detailed insight into the effectiveness of the test under different conditions.
+
+```{r Simulated_power, echo=FALSE, message=FALSE}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Function to calculate p-value
+calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
+  epsilon <- test_statistic  / sigma_W
+  p_value <- 2 * (1 - pnorm(abs(epsilon)))
+
+  return(p_value)
+}
+
+# Function to calculate Type II Error Rate
+calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
+  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
+  return(type_II_error_rate)
+}
+
+# Function to calculate power for different L values and alpha_nominals
+calculate_power <- function(R, mu, L_values, B, sample_sizes, alpha_nominals) {
+  results <- data.frame()
+
+  for (L in L_values) {
+    for (alpha_nominal in alpha_nominals) {
+      TestStatistics <- list()
+      mean_entropy <- numeric(length(sample_sizes))
+      sd_entropy <- numeric(length(sample_sizes))
+
+      for (s in sample_sizes) {
+        TestStat <- numeric(R)
+
+        for (r in 1:R) {
+          z <- gi0_sample(mu, -8, L, s)
+          TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+        }
+
+        mean_entropy[sample_sizes == s] <- mean(TestStat)
+        sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+        TestStatistics[[as.character(s)]] <- TestStat
+      }
+
+      mu_W <-  mean_entropy  
+      sigma_W <- sqrt(sd_entropy^2)
+
+      p_values <- lapply(TestStatistics, function(TestStat) {
+        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
+          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
+        })
+      })
+
+      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
+        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
+      })
+
+      power <- 1 - type_II_error_rates
+
+      result_row <- data.frame(
+        L = L,
+        alpha_nominal = alpha_nominal,
+        Sample_Size = sample_sizes,
+        power = power
+      )
+
+      results <- rbind(results, result_row)
+    }
+  }
+
+  return(results)
+}
+
+R <- 500
+mu <- 1
+L_values <- c(2, 5, 8, 18)
+B <- 3
+sample_sizes <- c(50, 100, 200, 300)
+alpha_nominals <- c(0.01, 0.05, 0.1)
+
+results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
+save(results_power, file = "./Data/results_power.Rdata")
+
+```
+
+```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Function to calculate p-value
+calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
+  epsilon <- test_statistic / sigma_W
+  p_value <- 2 * (1 - pnorm(abs(epsilon)))
+
+  return(p_value < alpha_nominal)  # Return TRUE if p_value is less than alpha_nominal
+}
+
+R <- 500
+mu <- 1
+B <- 3
+L_values <- c(2, 5, 8, 18)
+sample_sizes <- c( 50, 100, 200, 300)
+alpha_nominals <- c(0.01, 0.05, 0.1)
+
+results <- data.frame()
+
+for (L in L_values) {
+  for (alpha_nominal in alpha_nominals) {
+    TestStatistics <- NULL
+    mean_entropy <- numeric(length(sample_sizes))
+    sd_entropy <- numeric(length(sample_sizes))
+
+    for (s in sample_sizes) {
+      TestStat <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+      }
+      mean_entropy[sample_sizes == s] <- mean(TestStat)
+      sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
+    }
+
+    mu_W <- mean_entropy
+    sigma_W <- sqrt(sd_entropy^2)
+
+    p_values <- apply(TestStatistics, 1, function(row) {
+      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
+    })
+
+    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
+    results <- rbind(results, result)
+  }
+}
+
+save(results, file = "./Data/type_I_results.Rdata")
+
+```
+
+```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+cat("\\setlength{\\tabcolsep}{4pt}\n")
+# Load Type I Error Rates
+load("./Data/type_I_results.Rdata")
+
+type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
+  sum(p_values) / length(p_values)  
+})
+
+type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
+
+colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
+
+spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
+
+spread_results <- spread_results %>% 
+  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
+
+load("./Data/results_power.Rdata")
+
+summary_stats <- results_power %>%
+  spread(key = alpha_nominal, value = power) %>%
+  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
+
+# Combine the two datasets based on L and sample size
+combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
+combined_results <- combined_results %>% 
+  arrange(L, Sample_Size)
+# Reorder the columns
+combined_results <- combined_results %>% 
+  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
+
+# Rename columns
+colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")
+
+# LaTeX notation 
+combined_results[] <- lapply(combined_results, function(x) {
+  if (is.numeric(x)) {
+    if (all(x %% 1 == 0)) {
+      formatted_numbers <- sprintf("$%d$", x)
+    } else {
+      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
+    }
+    return(formatted_numbers)
+  } else {
+    return(x)
+  }
+})
+
+# Print the combined table
+table_combined_result <- kbl(
+  combined_results,
+  caption = "Size and Power of the proposed test.",
+  format = "latex",
+  booktabs = TRUE,
+  align = "lcccccccc",
+  escape = FALSE,
+  digits = 3,
+  label = "table_size_power"
+)%>%
+  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0,  align = "c")
+
+print(table_combined_result)
+
+```
+
 Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}.
 Under the null hypothesis, we observe that the densities are centered around zero.
-Conversely, under the alternative hypothesis, such as for $\alpha=8$, the density is not centered around zero.
+Conversely, under the alternative hypothesis, such as for $\alpha=-8$, the density is not centered around zero.
 It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.
 
-```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+```{r Sim_empirical_test, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
 
@@
 
-alpha1_values <- c( -8)
-
-plots_list <- list()
-
-for (alpha_val in alpha1_values) {
-
-  alpha1 <- alpha_val
+alpha1_values <- c( -2)
 
@@
 TestStatistics2 <- NULL
+
+for (alpha_val in alpha1_values) {
+
+  alpha1 <- alpha_val
 
@@
       TestStat2[r] <- bootstrap_correa_estimator_log_mean(z1, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-        #(L - log(L) + lgamma(L) + (1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1))- (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
-
-    }
-
-    mean_entropy1[sample.size == s] <- mean(TestStat1)
-   # cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
-
-    mean_entropy2[sample.size == s] <- mean(TestStat2)
-   # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")
+
+    }
 
@@
   }
+}
+
+# 
+save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test.Rdata")
+
+```
+
+```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+
+# 
+load("./Data/sim_empirical_test.Rdata")
 
@@
 
-  max_density1 <- max(density(TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
-  max_density2 <- max(density(TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
-
+plots_list <- list()
+
+for (alpha_val in alpha1_values) {
   plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
@@
 
-To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band,with  HH polarization, and intensity format.
+To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format.
 The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.
@@
 This format, gaining popularity among operational and application users, containing only the co-polarized and cross-polarized backscatter intensities (VV, VH).
+
+```{r window, fig.align="center",  out.width = "80%", fig.cap=" Sketch of sliding window.", fig.show="hold",  fig.pos="hbt"}
+knitr::include_graphics("../../../Figures/PDF/sliding2.pdf")
+```
 
@@
 x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
+
+x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland2/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland2/Intensity_VV.hdr')
 x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')

### 2024-02-01 Code/R/Programs/FirstExperimentTestStatisticL1.R

@@ -13,7 +13,7 @@ source("../MainFunctions/gamma_sar_sample.R")
 
 set.seed(1234567890, kind="Mersenne-Twister")
 
-R <- 3000
+R <- 500
 mu <- 1
 sample.size <- c(49, 81, 121)
 

### 2024-02-01 Code/R/Programs/sar_test_calculation.R

@@ -1,0 +1,64 @@
+rm(list = ls())
+
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+#x <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
+x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
+                            headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
+
+L <- 5
+B <- 1
+
+#difference_total <- bootstrap_correa_estimator_log_mean(x_Flevoland2, B)-  (L - log(L) + lgamma(L) + (1 - L) * digamma(L)) 
+
+# Tamaño de la ventana
+window_size <- 15
+
+
+rows <- nrow(x_Flevoland2)
+cols <- ncol(x_Flevoland2)
+
+# 
+mean_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+true_entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+test_difference_vector <- numeric()
+
+# Iterar sobre ventanas deslizantes
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x_Flevoland2[i:(i + window_size - 1), j:(j + window_size - 1)]
+
+    # Almacenar valores de x para cada ventana 
+    x_values <- window_data
+
+    # Calcular la media
+    mean_values[i, j] <- mean(window_data)
+
+    # Calcular entropía con el estimador no paramétrico
+    entropy_values[i, j] <- correa_estimator(window_data)
+
[…]

### 2024-02-02 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
New version

--- 2024-02-01 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
@@
 
-<!-- In this context, we present a two-stage estimation procedure designed to navigate the complexities of SAR data.  -->
-<!-- The first stage tests the hypothesis that the data follow the Gamma distribution, i.e., we are in the presence of fully developed speckle.  -->
-<!-- If this hypothesis is rejected, we proceed to the second stage to estimate the parameters that characterize the $\mathcal{G}^0$ distribution.  -->
-
 Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
@@
 
-From \eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
+From&nbsp;\eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
 \begin{align}
@@
 where $\psi^{(0)}(\cdot)$ is the digamma function.
-
-In Fig.&nbsp;\ref{fig:PlotGammaSAR} we see how the Entropy of the Gamma SAR distribution changes with $\mu$ for various values of $L$.
-
-```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="The Shannon Entropy under the Gamma SAR model."}
-L <- c(1, 3, 8, 12, 100)
-
-L_labels <- c(expression(italic(L)==1), 
-              expression(italic(L)==3), 
-              expression(italic(L)==8), 
-              expression(italic(L)==12), 
-              expression(italic(L)==100))
-
-mu <- seq(0.1, 10, length.out = 500)
-
-entropies <- sapply(L, function(L) entropy_gamma_sar(L, mu))
-
-muEntropy <- data.frame(mu, entropies)
-
-muEntropy.molten <- melt(muEntropy, id.vars = "mu", variable.name = "Looks", value.name = "Entropy")
-
-ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = Looks)) +
-  geom_line(linewidth=2) +
-  theme_minimal() +
-  scale_color_manual(values = rainbow(length(L)), labels = L_labels) +
-  labs(col = "Looks") +
-  xlab(expression(paste(mu))) +
-  theme(text=element_text(family="serif"),
-        legend.position = "bottom")
-
-```
-
-<!-- Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$. -->
-
-<!-- ```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"} -->
-<!-- knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf") -->
-<!-- ``` -->
-<!-- As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution.  -->
-<!-- We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space. -->
 
@@
 
-The empirical distributions of $\Gamma_{\text{SAR}}$ and $G_I^0$ entropies are shown in Fig.&nbsp;\ref{fig:Plot_empirical_gamma_and_gi0}. 
-It is observed that when $\alpha$ approaches negative infinity, the two distributions are very similar. 
-In other words, the mean entropy of $G_I^0$ approximates the mean entropy of $\Gamma_{\text{SAR}}$.
-
-```{r Simulated_empirical_gamma_and_gi0, echo=FALSE, message=FALSE}
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-R <- 3000
-mu <- 1
-L <- 8
-B <- 1
-sample.size <- c(121)
-alpha1_values <- c(-3, -8, -20, -1000)
-
-TestStatisticsList <- list()
-
-for (alpha_val in alpha1_values) {
-  alpha1 <- alpha_val
-  TestStatistics1 <- NULL
-  TestStatistics2 <- NULL
-
-  for (s in sample.size) {
-    TestStat1 <- numeric(R)
-    TestStat2 <- numeric(R)
-
-    for (r in 1:R) {
-      z <- gi0_sample(mu, alpha1, L, s)
-      TestStat1[r] <- log(mean(z))  + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      TestStat2[r] <- log(mean(z))  + (L - log(L) + lgamma(L) +(1 - L) * digamma(L) - L - lgamma(L - alpha1) + (L - alpha1) * (digamma(L - alpha1)) - (1 - alpha1) * digamma(-alpha1) + log(-1 - alpha1) + lgamma(-alpha1))
-    }
-
-    TestStatistics1 <- rbind(TestStatistics1, data.frame("Sample_Size" = rep(s, R), "Test_Statistics" = TestStat1))
-    TestStatistics2 <- rbind(TestStatistics2, data.frame("Sample_Size2" = rep(s, R), "Test_Statistics2" = TestStat2))
-  }
-
-  TestStatisticsList[[as.character(alpha_val)]] <- list(TestStatistics1 = TestStatistics1, TestStatistics2 = TestStatistics2)
-}
-
-save(TestStatisticsList, file = "./Data/data_empirical_entropy.RData")
-
-```
-
-```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}
-
-load("./Data/data_empirical_entropy.Rdata")
-plots_list <- list()
-
-for (alpha_val in alpha1_values) {
-  plot_data <- TestStatisticsList[[as.character(alpha_val)]]
-
-  max_density1 <- max(density(plot_data$TestStatistics1$Test_Statistics)$y, na.rm = TRUE)
-  max_density2 <- max(density(plot_data$TestStatistics2$Test_Statistics2)$y, na.rm = TRUE)
-
-  plot <- ggplot(plot_data$TestStatistics1, aes(x = Test_Statistics)) +
-    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
-    geom_line(data = plot_data$TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
-    annotate("text", x = max(plot_data$TestStatistics1$Test_Statistics) + 0.1, y = max_density1,
-             label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 5, hjust = 5, color = "red") +
-    annotate("text", x = max(plot_data$TestStatistics2$Test_Statistics2) + 0.1, y = max_density2,
-             label = TeX("$G_I^0$"), vjust = 5, hjust = 5, color = "blue") +
-    labs(x = "Entropy", y = "Density") +
-    annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
-    theme_minimal() +
-    theme(
-      text = element_text(family = "serif"),
-      legend.position = "none"  
-    )
-
-  plots_list[[as.character(alpha_val)]] <- plot
-}
-
-grid.arrange(grobs = plots_list, ncol = 2)
-
-```
-
 ## Estimation of the Shannon Entropy
@@
 However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\). 
-From \eqref{Eq:bias1} and \eqref{Eq:bias2} we have:
+From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have:
 \begin{align*}
@@
 # Number of replications
-R <- 100
+R <- 200
 
 # Number of bootstrap replications
-B <- 10
+B <- 20
 mu_values <- c(1, 10)
@@
 $$
- \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H(\bm{Z})=0 \\ 
-  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H(\bm{Z})\neq0 .\end{cases}
+ \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})=0 \\ 
+  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})\neq0 .\end{cases}
 $$
 In other words, we verify the hypothesis that the data are fully-developed speckle.
-
-For this purpose, we use the following test statistic:
+For this purpose, we propose the following test statistic:
 \begin{equation}
 \label{Eq:test_e}
-S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
+S(\bm{Z};L_0)= \widetilde{H}_{\text{C}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
 \end{equation}
-This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$. 
+This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution. 
 The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$. 
@@
 ## The Proposed Test
-We analyze the finite sample size behavior of the test statistics defined in \eqref{Eq:test_e}.
-
-Fig.
-\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
+Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
 Results with $p$-values $> 0.05$  indicate no evidence against normality. 
-Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails.
-The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases, aligning with normal distribution expectations.
-
-In Fig. \ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line, reinforcing our findings.
-
-```{r Simulated_density, echo=FALSE, message=FALSE}
+Small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails.
+The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases.
+
+In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line.
+
+```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
 #, cache = TRUE, autodep = TRUE
@@
 alpha1 <- -8
-sample.size <- c(50, 100, 150)
+sample.size <- c(50, 100, 200, 300)
 L_values <- c(2, 5, 8, 18)
@@
     ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
-    cv_val <- (sd_val / mean_val)
+    cv_val <- abs(sd_val / mean_val)
 
@@
 
-```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under Gamma SAR model.", fig.width=6, fig.height=5}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5}
 
@@
 
-We proceeded to explore the capabilities of the proposed test in terms of size and power.
-Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2(1-\Phi(\varepsilon))$, where $\Phi$ is the standard Gaussian cumulative distribution function and
+After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
+Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2\Phi(\varepsilon)-1$, where $\Phi$ is the standard Gaussian cumulative distribution function and
 $$
-\varepsilon=\frac{\tilde{H}(\bm{Z})-H(\bm{Z})}{\sigma_S}.
+\varepsilon=\frac{\tilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})}{\sigma_S}.
 $$
@@
 In all cases, the nominal level has been achieved.
-The power, in general, improves with the increase in the number of looks.
-The results are presented in Table \ref{tab:table_size_power}, providing a more detailed insight into the effectiveness of the test under different conditions.
-
-```{r Simulated_power, echo=FALSE, message=FALSE}
-
+The power, in general, improves with the increase in the sample size and the number of looks.
+The results are presented in Table&nbsp;\ref{tab:table_size_power}.
+
+```{r Simulated_error_type_I, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
 set.seed(1234567890, kind = "Mersenne-Twister")
 
-# Function to calculate p-value
+# 
+calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
+  epsilon <- test_statistic / sigma_W
+  p_value <- 2*pnorm(abs(epsilon))-1
+
+  return(p_value < alpha_nominal)  
+}
+
+R <- 500
+mu <- 1
+B <- 2
+L_values <- c(2, 5, 8)
+sample_sizes <- c( 50, 100, 150, 200)
+alpha_nominals <- c(0.01, 0.05, 0.1)
+
+results <- data.frame()
+
+for (L in L_values) {
+  for (alpha_nominal in alpha_nominals) {
+    TestStatistics <- NULL
+    mean_entropy <- numeric(length(sample_sizes))
+    sd_entropy <- numeric(length(sample_sizes))
+
+    for (s in sample_sizes) {
+      TestStat <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
+      }
+      mean_entropy[sample_sizes == s] <- mean(TestStat)
+      sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
+    }
+
+    mu_W <- mean_entropy
+    sigma_W <- sqrt(sd_entropy^2)
+
+    p_values <- apply(TestStatistics, 1, function(row) {
+      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
+    })
+
+    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
+    results <- rbind(results, result)
+  }
+}
+
+save(results, file = "./Data/type_I_results.Rdata")
+
+```
+
+```{r Simulated_power, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
 calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
@@
 
-# Function to calculate Type II Error Rate
 calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
@@
 mu <- 1
-L_values <- c(2, 5, 8, 18)
+L_values <- c(2, 5, 8)
 B <- 3
-sample_sizes <- c(50, 100, 200, 300)
+sample_sizes <- c(50, 100, 150, 200)
 alpha_nominals <- c(0.01, 0.05, 0.1)
@@
 
-```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-# Function to calculate p-value
-calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
-  epsilon <- test_statistic / sigma_W
-  p_value <- 2 * (1 - pnorm(abs(epsilon)))
-
-  return(p_value < alpha_nominal)  # Return TRUE if p_value is less than alpha_nominal
-}
-
-R <- 500
-mu <- 1
-B <- 3
-L_values <- c(2, 5, 8, 18)
-sample_sizes <- c( 50, 100, 200, 300)
-alpha_nominals <- c(0.01, 0.05, 0.1)
-
-results <- data.frame()
-
-for (L in L_values) {
-  for (alpha_nominal in alpha_nominals) {
-    TestStatistics <- NULL
-    mean_entropy <- numeric(length(sample_sizes))
-    sd_entropy <- numeric(length(sample_sizes))
-
-    for (s in sample_sizes) {
-      TestStat <- numeric(R)
-
-      for (r in 1:R) {
-        z <- gamma_sar_sample(L, mu, s)
-        TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      }
-      mean_entropy[sample_sizes == s] <- mean(TestStat)
-      sd_entropy[sample_sizes == s] <- sd(TestStat)
-
-      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
-    }
-
-    mu_W <- mean_entropy
-    sigma_W <- sqrt(sd_entropy^2)
-
-    p_values <- apply(TestStatistics, 1, function(row) {
-      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
-    })
-
-    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
-    results <- rbind(results, result)
-  }
-}
-
-save(results, file = "./Data/type_I_results.Rdata")
-
-```
-
 ```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
 cat("\\setlength{\\tabcolsep}{4pt}\n")
-# Load Type I Error Rates
+
 load("./Data/type_I_results.Rdata")
@@
 
-# Combine the two datasets based on L and sample size
 combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
@@
   arrange(L, Sample_Size)
-# Reorder the columns
+
 combined_results <- combined_results %>% 
@@
 
-# Rename columns
 colnames(combined_results) <- c("$L$", "$n$", "$1\\%$", "$5\\%$", "$10\\%$", "$1\\%$", "$5\\%$", "$10\\%$")
@@
 
-# Print the combined table
 table_combined_result <- kbl(
@@
 
-Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using statistical test \eqref{Eq:test_e}.
-Under the null hypothesis, we observe that the densities are centered around zero.
-Conversely, under the alternative hypothesis, such as for $\alpha=-8$, the density is not centered around zero.
-It reveals the difference between the entropy of Gamma SAR and $G_I^0$, indicating that we are in a scenario of heterogeneous clutter.
-
-```{r Sim_empirical_test, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using the test statistical&nbsp;\eqref{Eq:test_e}. Under the null hypothesis, the density centers around zero.
+
+```{r Sim_empirical_test, echo=FALSE, message=FALSE}
 
@@
 
-R <- 3000
+R <- 500
 mu <- 1
 L <- 5
-B <- 2
+B <- 5
 sample.size <- c( 81)
 
-alpha1_values <- c( -2)
+alpha1_values <- c( -8)
 
@@
 
-```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
 
@@
     geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
-    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
+    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=6, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
     geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
@@
 
-## Experiments on Real SAR Images
-
-To assess the practical efficacy of the proposed test, we conducted experiments using real SAR images acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format.
-The set of four SAR images, depicted in Fig.&nbsp;\ref{fig:Real_SAR_Images}(a)-(d) represent diverse scenes: a forested area in the Amazonas region, agricultural fields in Flevoland, and urban areas in Berlin and Ottawa, each with sizes of $512 \times 512$ pixels.
-
-We evaluate the test accuracy with small data portions.
-Ensuring resistance to contamination is crucial, especially in small samples with $5\times 5$, $7\times 7$, or $9\times 9$ windows that may contain data from areas with varying textures.
-Our assessment determines if the test can produce reasonable estimations, even when some data deviates from the assumed model.
-
-Table&nbsp;\ref{tab:table_sar} shows the results for $5 \times 5$ windows, detailing the performance of the proposed test in accurately identifying the origin of the data.
+## Application to Actual Data
+
+We applied the test statistical to a real SAR image of Flevoland province, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format.
+This image has $300 \times 300$ pixels and covers two different areas, urban areas and agricultural fields. 
 The metadata associated with these original SAR images includes a number of looks $L = 5$.
 
-The openly accessible Sentinel-1 data used in this study was downloaded as Level-1 Ground Range Detected (GRD) products from the Copernicus Data Space Ecosystem (\url{https://dataspace.copernicus.eu}).
-This format, gaining popularity among operational and application users, containing only the co-polarized and cross-polarized backscatter intensities (VV, VH).
-
-```{r window, fig.align="center",  out.width = "80%", fig.cap=" Sketch of sliding window.", fig.show="hold",  fig.pos="hbt"}
-knitr::include_graphics("../../../Figures/PDF/sliding2.pdf")
-```
-
-```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Real SAR images', fig.subcap=c('Amazonas', 'Flevoland','Ottawa', 'Berlin' ), out.width='.48\\linewidth',  fig.ncol=2}
-knitr::include_graphics("../../../Figures/PNG/Brazil_Intensity_VV.png")
-knitr::include_graphics("../../../Figures/PNG/Flevoland_Intensity_VV.png")
-knitr::include_graphics("../../../Figures/PNG/Ottawa_Intensity_VV.png")
-knitr::include_graphics("../../../Figures/PNG/Berlin_Intensity_VV.png")
-```
-
-```{r SAR_simulations, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
-#, cache = TRUE, autodep = TRUE
-set.seed(1234567890, kind = "Mersenne-Twister")
-x_Brazil <- myread.ENVI(file='../../../Data/SAR/Brazil/Intensity_VV.img', headerfile='../../../Data/SAR/Brazil/Intensity_VV.hdr')
-x_Berlin<- myread.ENVI(file='../../../Data/SAR/Berlin/Intensity_VV.img', headerfile='../../../Data/SAR/Berlin/Intensity_VV.hdr')
-x_Flevoland <- myread.ENVI(file='../../../Data/SAR/Flevoland/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland/Intensity_VV.hdr')
-
-x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland2/Intensity_VV.img', headerfile='../../../Data/SAR/Flevoland2/Intensity_VV.hdr')
-x_Ottawa <- myread.ENVI(file='../../../Data/SAR/Ottawa/Intensity_VV.img', headerfile='../../../Data/SAR/Ottawa/Intensity_VV.hdr')
-
-L <- 5
-B <- 10
-
-# Brazil
-nRows_Brazil <- 512
-nCols_Brazil <- 512
-
-centerRow_Brazil <- floor(nRows_Brazil / 2)
-centerCol_Brazil <- floor(nCols_Brazil / 2)
-
-roiSize_Brazil <- 5
-
-# Coordinates of the ROI
-roiStartRow_Brazil <- centerRow_Brazil - floor(roiSize_Brazil / 2) + 1
-roiEndRow_Brazil <- roiStartRow_Brazil + roiSize_Brazil - 1
-
-roiStartCol_Brazil <- centerCol_Brazil - floor(roiSize_Brazil / 2) + 1
-roiEndCol_Brazil <- roiStartCol_Brazil + roiSize_Brazil - 1
-
-# Extract the ROI
-roi_Brazil <- x_Brazil[roiStartRow_Brazil:roiEndRow_Brazil, roiStartCol_Brazil:roiEndCol_Brazil]
-
-mean_data_brasil <- mean(roi_Brazil)
-Entropy_brasil <- correa_estimator(roi_Brazil)
-entropia_estimada_boot_brasil <- bootstrap_correa_estimator(roi_Brazil, B)
-True_entropy_brasil <- (log(mean(roi_Brazil)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-Test_difference_brasil <- bootstrap_correa_estimator_log_mean(roi_Brazil, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-
-# Berlin
-nCols_Berlin = 512
-nRows_Berlin = 512
-
-centerRow_Berlin <- floor(nRows_Berlin / 2)
-centerCol_Berlin <- floor(nCols_Berlin / 2)
-
-roiSize_Berlin <- 5
-
-# Calculate ROI coordinates
-roiStartRow_Berlin <- centerRow_Berlin - floor(roiSize_Berlin / 2) + 1
-roiEndRow_Berlin <- roiStartRow_Berlin + roiSize_Berlin - 1
-
-roiStartCol_Berlin <- centerCol_Berlin - floor(roiSize_Berlin / 2) + 1
-roiEndCol_Berlin <- roiStartCol_Berlin + roiSize_Berlin - 1
-
-# Extract the ROI
-roi_Berlin <- x_Berlin[roiStartRow_Berlin:roiEndRow_Berlin, roiStartCol_Berlin:roiEndCol_Berlin]
-
-mean_data_Berlin <- mean(roi_Berlin)
-Entropy_Berlin <- correa_estimator(roi_Berlin)
-entropia_estimada_boot_Berlin <- bootstrap_correa_estimator(roi_Berlin, B)
-True_entropy_Berlin <- (log(mean(roi_Berlin)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-Test_difference_Berlin <- bootstrap_correa_estimator_log_mean(roi_Berlin, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-
-# Flevoland
-nCols_Flevoland = 512
-nRows_Flevoland = 512
-
-centerRow_Flevoland <- floor(nRows_Flevoland / 2)
-centerCol_Flevoland <- floor(nCols_Flevoland / 2)
-
-roiSize_Flevoland <- 5
-
-# ROI coordinates
-roiStartRow_Flevoland <- centerRow_Flevoland - floor(roiSize_Flevoland / 2) + 1
-roiEndRow_Flevoland <- roiStartRow_Flevoland + roiSize_Flevoland - 1
-
-roiStartCol_Flevoland <- centerCol_Flevoland - floor(roiSize_Flevoland / 2) + 1
-roiEndCol_Flevoland <- roiStartCol_Flevoland + roiSize_Flevoland - 1
-
-# Extract the ROI
-roi_Flevoland <- x_Flevoland[roiStartRow_Flevoland:roiEndRow_Flevoland, roiStartCol_Flevoland:roiEndCol_Flevoland]
-
-mean_data_Flevoland <- mean(roi_Flevoland)
-Entropy_Flevoland <- correa_estimator(roi_Flevoland)
-entropia_estimada_boot_Flevoland <- bootstrap_correa_estimator(roi_Berlin, B)
-True_entropy_Flevoland <- (log(mean(roi_Flevoland)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-Test_difference_Flevoland <- bootstrap_correa_estimator_log_mean(roi_Flevoland, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-
-# Ottawa
-nCols_Ottawa = 512
-nRows_Ottawa = 512
-
-centerRow_Ottawa <- floor(nRows_Ottawa / 2)
-centerCol_Ottawa <- floor(nCols_Ottawa / 2)
-
-roiSize_Ottawa <- 5
-
-# ROI coordinates in the upper part
-roiUpperStartRow <- 1
-roiUpperEndRow <- roiUpperStartRow + roiSize_Ottawa - 1
-
-roiUpperStartCol <- centerCol_Ottawa - floor(roiSize_Ottawa / 2) + 1
-roiUpperEndCol <- roiUpperStartCol + roiSize_Ottawa - 1
-
-# Extract the ROI in the upper part
-roi_Ottawa <- x_Ottawa[roiUpperStartRow:roiUpperEndRow, roiUpperStartCol:roiUpperEndCol]
-
-mean_data_Ottawa <- mean(roi_Ottawa)
-Entropy_Ottawa <- correa_estimator(roi_Ottawa)
-entropia_estimada_boot_Ottawa <- bootstrap_correa_estimator(roi_Ottawa, B)
-True_entropy_Ottawa <- (log(mean(roi_Ottawa)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-Test_difference_Ottawa <- bootstrap_correa_estimator_log_mean(roi_Ottawa, B) - ((L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-
-# Save results
-resultados_df <- data.frame(
-  Ciudad = c("Amazonas", "Berlin", "Flevoland", "Ottawa"),
-  Media = c(mean_data_brasil, mean_data_Berlin, mean_data_Flevoland, mean_data_Ottawa),
-  Entropia_Estimada = c(Entropy_brasil, Entropy_Berlin, Entropy_Flevoland, Entropy_Ottawa),
-  Entropia_Estimada_Boot = c(entropia_estimada_boot_brasil, entropia_estimada_boot_Berlin, entropia_estimada_boot_Flevoland, entropia_estimada_boot_Ottawa),
-  Entropia_Verdadera = c(True_entropy_brasil, True_entropy_Berlin, True_entropy_Flevoland, True_entropy_Ottawa),
-  Diferencia_Test_Entropia = c(Test_difference_brasil, Test_difference_Berlin, Test_difference_Flevoland, Test_difference_Ottawa)
-)
-
-colnames(resultados_df) <- c("Area", "Mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(\\bm Z)$")
-
-save(resultados_df, file = "./Data/resultados_df.Rdata")
-
-```
-
-```{r Table_SAR_simulations, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-cat("\\setlength{\\tabcolsep}{4pt}\n")
- load("./Data/resultados_df.Rdata")
-
-resultados_df[] <- lapply(resultados_df, function(x) {
-  if (is.numeric(x)) {
-    if (all(x %% 1 == 0)) {
-      formatted_numbers <- sprintf("$%d$", x)
-    } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.3f$", x), sprintf("$\\phantom{-}%.3f$", x))
-    }
-    return(formatted_numbers)
-  } else {
-    return(x)
-  }
-})
-
-print(
-  kbl(
-    resultados_df,
-    caption = "Results of applying the statistical test to SAR images.",
-    format = "latex",
-    booktabs = TRUE,
-    align = "lrrrrrrr",
-    escape = FALSE,
-    digits = 4,
-    label = "table_sar",
-    linesep = "",
-  ) %>%
-    #kable_styling(latex_options = "hold_position") %>%
-    row_spec(0,  align = "c")# %>%
-
-)
+Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image, from which we selected $7 \times 7$ local sliding windows covering the entire image. 
+The test statistical is applied to each window. 
+In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), the test results and corresponding $p$-values, computed over each $7\times 7$ sample, are shown as pixels. 
+This assessment aims to determine the test's effectiveness in identifying data origin. 
+The new image reveals two distinct regions: lighter backgrounds indicate homogeneity, while darker backgrounds represent heterogeneous areas.
+
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values calculated.' ), out.width='.48\\linewidth',  fig.ncol=2}
+knitr::include_graphics("../../../Figures/PNG/Intensity.png")
+knitr::include_graphics("../../../Figures/PNG/pvalue7x7.png")
 
@@
 
-In this study, three estimators renowned for their robust performance across diverse distributions were chosen for evaluation. 
-We examine the impact of applying bootstrap techniques on their precision by comparing each estimator's performance with its bootstrap-enhanced counterpart, utilizing metrics such as bias and MSE. 
-The effectiveness of bootstrap-enhanced non-parametric entropy estimators was observed, demonstrating efficacy in most instances. 
-Nonetheless, it is essential to recognize that the applicability of this technique may not be universal across all estimation methods.
-
-It is worth noting that this analysis represents an initial exploration of SAR Intensity data, and future work will include a more in-depth analysis of effect size and statistical power.
-Additionally, exploring the impact of the $\alpha$ parameter on estimates and conducting more extensive analyses to assess the generalization of results to different parameter configurations is suggested.
+Conclusively, in this work, we propose a testing procedure for distinguishing between fully-developed speckle and heterogeneous clutter. 
+We focus on the estimation of Shannon entropy using non-parametric estimators, enhancing precision through bootstrap techniques. 
+The Correa estimator ($\widetilde{H}_{\text{C}}$) stands out as the optimal choice, exhibiting superior performance in bias and MSE across simulations involving the $G_I^0$ distribution. 
+This superiority becomes particularly pronounced when the number of looks exceeds 2.
+
+Furthermore, our assessment of the proposed test involved the calculation of empirical size and power, considering various sample sizes, numbers of looks, and nominal levels. 
+The results demonstrate its capabilities under both null and alternative hypotheses. Notably, the test performs acceptably with sample sizes larger than 50. 
+However, practical scenarios often involve smaller sample sizes, typically obtained over windows of size $7 \times 7$.
+
+The application of the test to actual SAR data yielded promising outcomes, effectively discerning distinct regions in the image and showing its potential for discriminating between homogeneous and heterogeneous zones.
+
+# Acknowledgement {-}
+
+This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior  (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.
 

### 2024-02-02 Code/R/Programs/Sar_test_each_window.R

@@ -7,11 +7,13 @@ library(ggplot2)
 library(e1071)
 library(nortest)
 
-load("./Data/results_data_Flevoland_100.Rdata")
+load("./Data/results_data_Ottawa_100_5.Rdata")
 
-
+print(difference_values)
+#load("./Data/results_data_Flevoland_100_5.Rdata")
 
 df <- data.frame(TestDifference = test_difference_vector)
+
 
 
 ggplot(df, aes(x = TestDifference)) +
@@ -27,6 +29,7 @@ ggplot(df, aes(x = TestDifference)) +
 
 # 
 mean_val <- mean(test_difference_vector)
+
 sd_val <- sd(test_difference_vector)
 var_val <- var(test_difference_vector)
 skewness_val <- skewness(test_difference_vector)
@@ -34,14 +37,15 @@ kurtosis_val <- kurtosis(test_difference_vector)
 ad_p_value <- ad.test(test_difference_vector)$p.value
 cv_val <- sd_val / mean_val
 
-#
-cat("Mean:", mean_val, "\n")
-cat("Standard Deviation:", sd_val, "\n")
-cat("Variance:", var_val, "\n")
-cat("Coefficient of Variation:", cv_val, "\n")
-cat("Skewness:", skewness_val, "\n")
-cat("Kurtosis:", kurtosis_val, "\n")
-cat("Anderson-Darling p-value:", ad_p_value, "\n")
+# #
+# cat("Mean:", mean_val, "\n")
+# 
+# cat("Standard Deviation:", sd_val, "\n")
+# cat("Variance:", var_val, "\n")
+# cat("Coefficient of Variation:", cv_val, "\n")
+# cat("Skewness:", skewness_val, "\n")
+# cat("Kurtosis:", kurtosis_val, "\n")
+# cat("Anderson-Darling p-value:", ad_p_value, "\n")
 
 # 
 summary_stats <- data.frame(
@@ -54,49 +58,51 @@ summary_stats <- data.frame(
   adpvalue = ad_p_value
 )
 
-qq_plot <- qqnorm(test_difference_vector, plot.it = FALSE)
-qq_data <- data.frame(Theoretical = qq_plot$x, Sample = qq_plot$y)
+# qq_plot <- qqnorm(test_difference_vector, plot.it = FALSE)
+# qq_data <- data.frame(Theoretical = qq_plot$x, Sample = qq_plot$y)
+# 
+# 
+# ggplot(qq_data, aes(x = Theoretical, y = Sample)) +
+#   geom_point() +
[…]

### 2024-02-02 Code/R/Programs/plot_pvalue.R

@@ -1,0 +1,89 @@
+
+#rm(list = ls())
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+library(ggplot2)
+library(e1071)
+library(nortest)
+
+#load("./Data/results_data_Ottawa_100_5.Rdata") # difference_value
+#load("./Data/results_data_Flevoland_300_5.Rdata")
+
+load("./Data/results_data_Flevoland_300_7.Rdata")
+#load("./Data/results_data_Flevoland_300_9.Rdata")
+calculate_p_values_matrix <- function(data_matrix, sigma) {
+  rows <- nrow(data_matrix)
+  cols <- ncol(data_matrix)
+  
+  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  
+  for (i in 1:rows) {
+    for (j in 1:cols) {
+      test_difference <- data_matrix[i, j]
+      
+      epsilon <- test_difference / sigma
+      p_value <- 2 * pnorm(abs(epsilon)) - 1
+      
+      p_values_matrix[i, j] <- p_value
+    }
+  }
+  
+  return(p_values_matrix)
+}
+
+
+mean_difference_values <- mean(difference_values, na.rm = TRUE)
+sd_difference_values <- sd(difference_values, na.rm = TRUE)
+
+
+p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_values)
+
+
+# p_values_df <- as.data.frame(as.table(p_values_matrix))
+# colnames(p_values_df) <- c("Row", "Column", "P_Value")
+# 
+# 
+# ggplot(p_values_df, aes(x = as.factor(Column), y = as.factor(Row), fill = P_Value)) +
+#   geom_tile() +
+#   scale_fill_gradient(low = "white", high = "blue") +
+#   labs(title = "Matrix de P-Values") +
+#   theme_minimal() +
+#   theme(axis.text = element_blank(), axis.title = element_blank())
+
+source("../imagematrix.R")
+
+hist(p_values_matrix)
+par(mfrow=c(1,2))
+plot(imagematrix(equalize(x)))
+plot(imagematrix(p_values_matrix))
+
+imagematrixPNG(imagematrix(equalize(x)), name = "Intensity.png")
+imagematrixPNG(imagematrix(p_values_matrix), name="pvalue7x7.png")
+
+
+
+
[…]

### 2024-02-03 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
Reduce figures

@@
   SAR Data are affected by speckle, a non-additive and non-gaussian interference noise-like pattern.
-  The type of distribution these data follow is paramount for their processing and analysis.
+  The distribution these data follow is paramount for their processing and analysis.
   Good statistical models provide flexibility and accuracy, often at the cost of using several parameters.
@@
   Although the latter is a limit distribution of the former, using the same estimation technique for the more general model is numerically unfeasible.
-  We propose a two-stage estimation procedure: first, we verify the hypothesis that the data are fully-developed speckle.
+  We developed a test statistic based on an bootstrap-improved non-parametric estimator of the Shannon entropy for assessing departures from the fully-developed speckle hypothesis.
+  We show the adequacy of the proposal with simulated and SAR data.
+  <!-- We propose a two-stage estimation procedure: first, we verify the hypothesis that the data are fully-developed speckle.
 If this assumption is rejected, we proceed to estimate the parameters that index the $\mathcal G^0$ distribution; otherwise, we proceed with the Gamma model.
-  Given the uncertainty of the underlying distribution, and the negative impact that using an inadequate model has on maximum likelihood estimation, we employ a non-parametric approach to estimate entropy under the fully-developed speckle hypothesis.
+-->
+  <!-- Given the uncertainty of the underlying distribution, and the negative impact that using an inadequate model has on maximum likelihood estimation, we employ a non-parametric approach to estimate entropy under the fully-developed speckle hypothesis.
+-->
 
@@
 Speckle is part of SAR data because of the imaging process' coherent nature.
-Its non-additivity and non-Gaussianity require robust statistical models that can accurately characterize the data.
-
-Among these models, the $\mathcal{G}^0$ distribution stands out as a powerful framework. 
-Notably, this distribution encompasses the well-known Gamma distribution as a special case, particularly under the assumption of fully developed speckle. 
-The interplay between these two distributions is apparent, with the Gamma distribution representing a limiting case of the more general $\mathcal{G}^0$ model.
+Its non-additivity and non-Gaussianity require statistical models that can accurately characterize them.
+
+Among these models, the $\mathcal{G}^0$ law is a flexible and tractable model. 
+Notably, this distribution encompasses the well-known Gamma distribution as the fully developed speckle case. 
+<!-- The interplay between these two distributions is apparent, with the Gamma distribution representing a limiting case of the more general $\mathcal{G}^0$ model.  -->
 
@@
 the likelihood is flat, so numerical optimization may not converge&nbsp;\cite{FreryCribariSouza:JASP:04}.
-The two-stage technique we propose tackles this problem by using the entropy as a proxy to decide which is the best model.
+The test statistic we propose tackles this problem using the entropy as a proxy.
 
@@
 Among non-parametric approaches, Subhash et al.&nbsp;\cite{Subhash2021} discussed the use of spacing methods.
-This non-parametric strategy offers flexibility to address a wide range of models without imposing specific parametric constraints.
-We extend the exploration of non-parametric entropy estimators by incorporating enhanced bootstrap methodologies.
-
-Our aim is to develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter.
-We work with non-parametric estimators of the entropy, we reduce the bias of those based on spacings using bootstrap, and select the best ones.
-Next, we study the empirical distribution of these estimators under the null hypothesis, followed by a study of the size and power of the proposed test.
-We conclude the study with applications to SAR data.
-
-The article is structured as follows: 
-Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data. Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy. 
-In Section&nbsp;\ref{sec:results}, we present experimental results. 
-Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited.
+This strategy offers flexibility to address a wide range of models without imposing specific parametric constraints. 
+We improve this non-parametric entropy estimator with bootstrap.
+
+We develop a test statistic that helps discriminating between fully-developed speckle and heterogeneous clutter based a non-parametric estimator of the entropy, and we reduce its mean square error using bootstrap.
+Next, we study its empirical distribution under the null hypothesis, and we conclude the study with an application to SAR data.
+
+<!-- The article is structured as follows:  -->
+<!-- Section&nbsp;\ref{sec:Background} covers statistical modeling and entropy estimation for Intensity SAR data.
+Section&nbsp;\ref{sec:test} outlines hypothesis testing based on non-parametric entropy.
+-->
+<!-- In Section&nbsp;\ref{sec:results}, we present experimental results.  -->
+<!-- Finally, in Section&nbsp;\ref{sec:conclusion} conclusions are exhibited. -->
 
@@
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;\cite{Frery1997}. 
-The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Cassetti2022}.
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp. 
+The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Yue2021}.
 We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
@@
 \end{align}
-where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
-
-From&nbsp;\eqref{E:gi01}, the $r$th moment of $Z$ is expressed as:
-\begin{align}
-	\mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r. 
-	\label{E:rmom}
-\end{align}
-
-Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;\cite{Nascimento2010}.
-In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
+where $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
+In&nbsp;\eqref{E:gamma1}, $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,
+
+<!-- From&nbsp;\eqref{E:gi01}, the $r$th moment of $Z$ is expressed as: -->
+<!-- \begin{align} -->
+<!-- 	\mathbbm E_{\mathcal{G}_I^0}\left(Z^r\right)=\left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\gamma(L)}, \quad \alpha <-r.  -->
+<!-- 	\label{E:rmom} -->
+<!-- \end{align} -->
+
+We can parametrize&nbsp;\eqref{E:gi01} by the mean value:
 \begin{align*}
@@
 ## The Shannon Entropy
+
 The parametric representation of Shannon entropy for a system described by a continuous random variable is:
@@
 
-Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $G_I^0$in&nbsp;\eqref{E:gi02} based on&nbsp;\cite{Cassetti2022} and&nbsp;\cite{Ferreira2020}:
+Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$ in&nbsp;\eqref{E:gamma1} and $G_I^0$ in&nbsp;\eqref{E:gi02}:
 \begin{multline}
@@
 
-One of the earliest non-parametric estimators relying on spacings was introduced by&nbsp;\cite{vasicek1976test}. 
+One of the earliest non-parametric estimators relying on spacings was introduced by Vasicek&nbsp;\cite{vasicek1976test}. 
 Assuming that $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ is a random sample from the distribution $F(z)$, the estimator is defined as:
@@
 
-Several authors have explored adaptations to Vasicek's estimator. In this work, we consider three entropy estimators known for their superior performance:
+Several authors have explored adaptations to Vasicek's estimator. 
+We consider three estimators known for their superior performance&nbsp;\cite{Cassetti2022}:
 
@@
 
-These estimators, along with others, are described and studied in&nbsp;\cite{Cassetti2022}.
-
 ## Enhanced Bootstrap Technique
@@
 We employ the bootstrap technique to refine the precision of existing non-parametric entropy estimators. 
-This approach involves generating new datasets through resampling with repetition from an existing one.
+<!-- This approach involves generating new datasets through resampling with repetition from an existing one. -->
 
@@
 \label{Eq:bias1}
-\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta.
+\bias\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
 \end{equation}
-Our objective is to devise unbiased estimators with reduced variance. To achieve this, we introduce an "ideal estimator" \(\check{\theta}(\bm{Z})\) using the bias information:
-\begin{equation}
-\label{Eq:bias2}
-\widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big).
-\end{equation}
-However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\). 
-From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have:
+Our bootstrap-improved estimators are of the form:
+<!-- introducing an "ideal unbiased estimator" \(\check{\theta}(\bm{Z})\): -->
+<!-- \begin{equation} -->
+<!-- \label{Eq:bias2} -->
+<!-- \widecheck{\theta}(\bm{Z}) = \widehat{\theta}(\bm{Z}) - \bias\big(\widehat{\theta}(\bm{Z})\big). -->
+<!-- \end{equation} -->
+<!-- However, \(\check{\theta}(\bm{Z})\) is not an estimator, because it depends on the true parameter \(\theta\), prompting the formulation of a new estimator \(\widetilde{H}\).  -->
+<!-- From&nbsp;\eqref{Eq:bias1} and&nbsp;\eqref{Eq:bias2} we have: -->
 \begin{align*}
@@
 The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
+<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->
 
@@
 # Hypothesis testing based on non-parametric entropy {#sec:test}
-General asymptotic results for functions of spacings are detailed&nbsp;\cite{Khashimov1990}, while&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
+
+General asymptotic results for functions of spacings are detailed in Ref.&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} developed a correction for the case of Shannon entropy.
 Following the work of these authors, the next result applies: 
@@
 \xrightarrow[]{\mathcal{D}}
-\mathcal{N}(0,\operatorname{Var}(\ln f(Z))).
+\mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big).
 \end{equation*}
@@
 $$
-In other words, we verify the hypothesis that the data are fully-developed speckle.
-For this purpose, we propose the following test statistic:
+In other words, we verify the hypothesis that the data are fully-developed speckle with the following test statistic:
 \begin{equation}
@@
 \end{equation}
-This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution. 
-The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$. 
-Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. 
-This suggests significant differences and implies the presence of heterogeneous clutter.
+<!-- This test statistic assess the behavior of the data under the null hypothesis, through the empirical distribution.  -->
+The values should be around zero under the null hypothesis and far otherwise. 
+<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
 
@@
 Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
+<!-- ACF Only show L=2 and L=8 -->
 Results with $p$-values $> 0.05$  indicate no evidence against normality. 
@@
 The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases.
-
-In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line.
+Normal QQ-plots, omitted for brevity, confirm that there is no evidence to reject the normal distribution.
+
+<!-- In Fig.&nbsp;\ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line. -->
 
@@
 
-```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Normal QQ-plots for  $n=100$.", fig.width=6, fig.height=5}
+```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Normal QQ-plots for  $n=100$.", fig.width=6, fig.height=5, eval=FALSE}
 
@@
 $$
-Nominal levels of $1\%$, $5\%$, and $10\%$ were considered.
-In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results.
-In all cases, the nominal level has been achieved.
+We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
+In reference to the size, $1000$ simulations have been used for various sample sizes with  satisfactory results. In all cases, the nominal level has been achieved. 
 The power, in general, improves with the increase in the sample size and the number of looks. 
@@
 
-Fig.&nbsp;\ref{fig:Plot_empirical_test} displays the empirical distributions using the test statistical&nbsp;\eqref{Eq:test_e}. Under the null hypothesis, the density centers around zero.
+Fig.&nbsp;\ref{fig:Plot_empirical_test} shows the test statistic&nbsp;\eqref{Eq:test_e} empirical distribution. 
+Under the null hypothesis, the density centers around zero.
 
@@
 
-```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under null hypothesis (centered around zero) and alternative hypothesis (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under the null (centered around zero) and alternative hypotheses (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
 
@@
 
-We applied the test statistical to a real SAR image of Flevoland province, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, and intensity format.
-This image has $300 \times 300$ pixels and covers two different areas, urban areas and agricultural fields. 
-The metadata associated with these original SAR images includes a number of looks $L = 5$.
-
-Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image, from which we selected $7 \times 7$ local sliding windows covering the entire image. 
-The test statistical is applied to each window. 
-In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), the test results and corresponding $p$-values, computed over each $7\times 7$ sample, are shown as pixels. 
-This assessment aims to determine the test's effectiveness in identifying data origin. 
-The new image reveals two distinct regions: lighter backgrounds indicate homogeneity, while darker backgrounds represent heterogeneous areas.
-
-```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values calculated.' ), out.width='.48\\linewidth',  fig.ncol=2}
+We applied the test statistical to a SAR image of Flevoland, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, intensity format, and $L=5$ nominal looks.
+This image has $300 \times 300$ pixels and covers urban areas and agricultural fields. 
+<!-- The metadata associated with these original SAR images includes a number of looks $L = 5$. -->
+
+Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
+We used $7 \times 7$ local sliding windows to compute the test, and Fig.&nbsp;\ref{fig:Real_SAR_Images}(b) shows the $p$-values.
+The new image reveals two distinct regions: lighter background indicates homogeneity, while darker backgrounds represent heterogeneous areas.
+
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
 knitr::include_graphics("../../../Figures/PNG/Intensity.png")
@@
 
-Conclusively, in this work, we propose a testing procedure for distinguishing between fully-developed speckle and heterogeneous clutter. 
-We focus on the estimation of Shannon entropy using non-parametric estimators, enhancing precision through bootstrap techniques. 
-The Correa estimator ($\widetilde{H}_{\text{C}}$) stands out as the optimal choice, exhibiting superior performance in bias and MSE across simulations involving the $G_I^0$ distribution. 
-This superiority becomes particularly pronounced when the number of looks exceeds 2.
-
-Furthermore, our assessment of the proposed test involved the calculation of empirical size and power, considering various sample sizes, numbers of looks, and nominal levels. 
-The results demonstrate its capabilities under both null and alternative hypotheses. Notably, the test performs acceptably with sample sizes larger than 50. 
+We propose a testing procedure for distinguishing between fully-developed speckle and heterogeneous clutter with a test statistic based on a bootstrap-improved estimator of the Shannon entropy. 
+<!-- The Correa estimator ($\widetilde{H}_{\text{C}}$) stands out as the optimal choice, exhibiting superior performance in bias and MSE across simulations involving the $G_I^0$ distribution.  -->
+<!-- This superiority becomes particularly pronounced when the number of looks exceeds $2$. -->
+Our proposal includes the empirical size and power considering various sample sizes, numbers of looks, and nominal levels.
+
+The results show that the test performs acceptably with sample sizes larger than $50$. 
 However, practical scenarios often involve smaller sample sizes, typically obtained over windows of size $7 \times 7$.

### 2024-02-04 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
Corrected last details; now 4 pages

@@
 
-# if(!require("rstudioapi")) install("rstudioapi")
-# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+if(!require("rstudioapi")) install("rstudioapi")
+setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
@@
 
-## Statistical modeling of Intensity SAR data
+## Statistical Modeling of Intensity SAR Data
 
@@
 
-Simulations are conducted using $G_I^0$ distribution, with $200$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with parameters \(\mu \in \left\{1, 10\right\}\), \(\alpha=-20\), and \(L=8\).
+Simulations are conducted using $G_I^0$ distribution, with $500$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\).
+For brevity, we present the results with \(\mu=1\), \(\alpha=-10\), and \(L=5\).
+The results are consistent for other values of the mean.
 In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
@@
 set.seed(1234567890, kind = "Mersenne-Twister")
-sample_sizes <- c(9, 25, 49, 81, 121)
+sample_sizes <- c(9, 25, 49, 81, 121 )
 
 # Number of replications
-R <- 200
+R <-500
 
 # Number of bootstrap replications
-B <- 20
-mu_values <- c(1, 10)
-alpha <- -20
-L <- 8
+B1 <- 100
+mu_values <- c(1)
+alpha <- -10
+L <- 5
 
@@
 
-calculate_results_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
+calculate_results_gi0 <- function(sample_sizes, R, B1, mu_values, alpha, L, estimators) {
   results_list <- list()
@@
 
-    results <- calculate_bias_mse_gi0(sample_sizes, R, B, mu_val, alpha, L, estimators)
+    results <- calculate_bias_mse_gi0(sample_sizes, R, B1, mu_val, alpha, L, estimators)
     df <- as.data.frame(results)
@@
 
-results_gi0 <- calculate_results_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)
+results_gi0 <- calculate_results_gi0(sample_sizes, R, B1, mu_values, alpha, L, estimators)
 
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=8$, $\\alpha=-20$.", fig.width=6, fig.height=5}
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=5$, $\\alpha=-10$.", fig.width=6, fig.height=3.0}
 
@@
 
-combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 1, nrow = 2)
+combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 1, nrow = 1)
 
@@
     reshaped_results,
-    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
+    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=5$, $\\alpha=-10$.",
     format = "latex",
@@
 
-R <- 1000
+R <- 800
 mu <- 1
-B <- 2
-alpha1 <- -8
-sample.size <- c(50, 100, 200, 300)
-L_values <- c(2, 5, 8, 18)
+B <- 5
+
+sample.size <- c(25,50, 100, 200, 300)
+L_values <- c(2,  8)
 
@@
 
-load("./Data/results_5.Rdata")
-summary_stats_5 <- all_summary_stats[["5"]]
+# load("./Data/results_5.Rdata")
+# summary_stats_5 <- all_summary_stats[["5"]]
 
@@
   transform(summary_stats_2),
-  transform(summary_stats_5),
+  #transform(summary_stats_5),
   transform(summary_stats_8)
@@
   combined_summary_stats,
-  caption = "Descriptive analysis of $S(\\bm Z; L)$ for different values of $L$, and $\\mu=1$.",
+  caption = "Descriptive analysis of $S(\\bm Z; L)$ with $L\\in\\left\\{2, 8\\right\\}$ and $\\mu=1$.",
   format = "latex",
@@
 After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
-Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2))$, and therefore, the $p$-value of the observed test statistic is $2\Phi(\varepsilon)-1$, where $\Phi$ is the standard Gaussian cumulative distribution function and
+Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2)$, and therefore, the $p$-value of the observed test statistic is $2\Phi(\varepsilon)-1$, where $\Phi$ is the standard Gaussian cumulative distribution function and
 $$
@@
 
-```{r Simulated_error_type_I, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-R <- 500
+R <- 1000
 mu <- 1
 B <- 2
-L_values <- c(2, 5, 8)
-sample_sizes <- c( 50, 100, 150, 200)
+L_values <- c( 5, 8)
+sample_sizes <- c( 25, 50, 100, 200, 300)
 alpha_nominals <- c(0.01, 0.05, 0.1)
@@
 
-```{r Simulated_power, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
+```{r Simulated_power, echo=FALSE, message=FALSE}
 
@@
         for (r in 1:R) {
-          z <- gi0_sample(mu, -8, L, s)
+          z <- gi0_sample(mu, -5, L, s)
           TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
@@
 
-R <- 500
+R <- 1000
 mu <- 1
-L_values <- c(2, 5, 8)
-B <- 3
-sample_sizes <- c(50, 100, 150, 200)
+L_values <- c(5,  8)
+B <- 1
+sample_sizes <- c(25, 50, 100, 200, 300)
 alpha_nominals <- c(0.01, 0.05, 0.1)
@@
 
-R <- 500
+R <- 2000
 mu <- 1
-L <- 5
-B <- 5
+L <- 8
+B <- 1
 sample.size <- c( 81)
 
-alpha1_values <- c( -8)
+alpha1_values <- c( -5)
 
@@
 
-```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under the null (centered around zero) and alternative hypotheses (e.g., $\\alpha=-8$, showing a shift from zero), with $\\mu=1$ and $L=5$."}
+```{r Plot_empirical_test, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions under the null (centered around zero) and alternative hypotheses (e.g., $\\alpha=-5$, showing a shift from zero), with $\\mu=1$ and $L=8$."}
 
@@
     geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
-    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
-    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=6, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
-    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
+    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-5, 8), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
+    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-5, 8), y=5, parse=TRUE, label="alpha==-5", hjust=-.1, vjust=1.0, col="darkgreen") +
+    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 8), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
     theme_minimal() +
@@
 
-```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.', fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
 knitr::include_graphics("../../../Figures/PNG/Intensity.png")

### 2024-02-05 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
Plot bias-mse legends modified

@@
 # use some specific Tex packages if needed.
-#with_ifpdf: true
-#with_cite: true
+
 # amsmath need to be true to use with bookdown for referencing equations.
 with_amsmath: true
-# with_algorithmic: true
-# with_array: true
-# with_dblfloatfix: true
+#with_subfig:true
 
@@
    - \hypersetup{draft}
-   - \usepackage{graphicx}
    - \usepackage{float}
-   - \usepackage{booktabs}
    - \usepackage{array}
@@
    - \usepackage{subfig}
-   #- \usepackage{subcaption}
-   - \usepackage{pgf}
+   #- \usepackage{caption}
+   #- \captionsetup[table]{skip=0pt}
    - "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]
@@
 
+    #extra_dependencies: "subfig"
+
 bibliography: ../../Common/references.bib
@@
 biblio-style: ieeetr
-
-#link-citations: yes
 
@@
 
+\let\oldtablename\tablename
+\renewcommand{\tablename}{\MakeUppercase{\oldtablename}}
+\let\oldfigurename\figurename
+\renewcommand{\figurename}{Fig.}
+
 # Introduction {#sec:Introduction}
@@
 We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
+<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->
 
@@
 The use of the bootstrap technique exhibits more precision, reduced bias and MSE, and improved convergence.
-<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->
-
 The results of simulation are exhibited in Table&nbsp;\ref{tab:table2}.
+
 The precision of estimators, as evidenced by bias and MSE comparisons, benefits significantly from the bootstrap technique, particularly for sample sizes below 81.
@@
 
-```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE of entropy estimators for  $G_I^0$, $L=5$, $\\alpha=-10$.", fig.width=6, fig.height=3.0}
+```{r Plot_bias_mse_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Bias and MSE, $L=5$ and  $\\alpha=-10$.", fig.width=6, fig.height=3.0}
 
@@
     reshaped_results,
-    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=5$, $\\alpha=-10$.",
+    caption = "Bias and MSE of bootstrap estimators.",
     format = "latex",
@@
 
-```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=5}
+```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under null hypothesis.", fig.width=6, fig.height=3.0}
 
@@
 
-combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
+combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
   plot_layout(guides = "collect")
@@
   digits = 4,
-  label = "table_stat_combined"
+  label = "table_stat_combined",
   #table.env = 'table*' # to span multiple columns
@@
 ## Application to Actual Data
-
 We applied the test statistical to a SAR image of Flevoland, Netherlands, acquired by the Sentinel-1A system operating in the C band, with  HH polarization, intensity format, and $L=5$ nominal looks.

### 2024-02-05 Code/R/Programs/functions_sample_bias_mse.R

@@ -212,12 +212,15 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
        # scale_color_discrete(labels = TeX(df_filtered$Estimator)) +
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu_val)), hjust = 4.0, vjust = -0.1, size = 3) +
-      coord_cartesian(clip = 'off')
+      coord_cartesian(clip = 'off')+
+      theme(legend.position = "bottom", legend.box = "horizontal", legend.box.margin = margin(0, 0, 0, 0)) +
+      guides(color = guide_legend(nrow = 1))
     
-    # 
-    if (mu_val != mu_values[1]) {
-      plot_bias = plot_bias + theme(legend.position = "top")
-    }
+    
+    # # 
+    # if (mu_val != mu_values[1]) {
+    #   plot_bias = plot_bias + theme(legend.position = "top")
+    # }
     
     plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
       geom_hline(yintercept = 0) +
@@ -227,21 +230,25 @@ generate_plot_gi0_esp <- function(results_gi0, mu_values, selected_estimators, n
       #scale_color_discrete(labels = TeX(df_filtered$Estimator)) +
       scale_color_manual(values = pal_jama()(7)[1:6], labels = TeX(df_filtered$Estimator)) +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu_val)), hjust = 4.0, vjust = -0.1, size = 3) +
-      coord_cartesian(clip = 'off')
+      coord_cartesian(clip = 'off')+
+      theme(legend.position = "bottom", legend.box = "horizontal", legend.box.margin = margin(0, 0, 0, 0)) +
+      guides(color = guide_legend(nrow = 1))
     
     
-    if (mu_val != mu_values[1]) {
-      plot_mse = plot_mse + theme(legend.position = "top")
-    }
+    
+    # if (mu_val != mu_values[1]) {
+    #   plot_mse = plot_mse + theme(legend.position = "top")
+    # }
     
     
     plot_list[[as.character(mu_val)]] <- plot_bias + plot_mse
   }
   
   
[…]

### 2024-02-11 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
change in a reference
Small change

@@
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp. 
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions&nbsp;\cite{Frery1997}. 
 The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Yue2021}.
@@
 
-Simulations are conducted using $G_I^0$ distribution, with $500$ simulated samples of size \(n\in\left\{9, 25, 49, 81, 121\right\}\).
+We analyzed the performance of these estimators with a Monte Carlo study:
+$500$ samples of $G_I^0$ of size \(n\in\left\{9, 25, 49, 81, 121\right\}\) and several values of the mean, number of looks and roughness.
 For brevity, we present the results with \(\mu=1\), \(\alpha=-10\), and \(L=5\). 
-The results are consistent for other values of the mean.
+The results are consistent for the other situations. 
 In the case of the bootstrap technique, each sample is replicated $100$ times with replacement.
 We choose to use the following heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
-<!-- ACF Show only the first line, i.e., for mu=1, and state that the results are consistent for other values of the mean -->
 
@@
 <!-- ACF Only show L=2 and L=8 -->
-Results with $p$-values $> 0.05$  indicate no evidence against normality. 
+Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
 Small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails. 

### 2024-02-12 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
corrected space 4 pages now

@@
 
-The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions&nbsp;\cite{Frery1997}. 
+The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions.
 The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;\cite{Yue2021}.
@@
 
-In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
-
-```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}
+In Fig.&nbsp;\ref{fig:Plot_GI0_to_gamma1}, we depict the behavior of the entropy of \(G_I^0\) when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\), observing its convergence towards the entropy of \(\Gamma_{\text{SAR}}\) as \(\alpha\) takes large negative values.
+
+```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}
 
@@
 
-save(results_gi0, file = "./Data/results_gi0.Rdata")
+save(results_gi0, file = "./Data/resultsgi0.Rdata")
 
@@
 
-load("./Data/results_gi0.Rdata")
+load("./Data/resultsgi0.Rdata")
 
@@
 ```{r Table_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-load("./Data/results_gi0.Rdata")
+load("./Data/resultsgi0.Rdata")
 
@@
 
-  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
+  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results1_", L, ".Rdata"))
 }
@@
 for (L in L_values) {
-  load(paste0("./Data/results_", L, ".Rdata"))
+  load(paste0("./Data/results1_", L, ".Rdata"))
 
@@
 
-load("./Data/results_2.Rdata")
+load("./Data/results1_2.Rdata")
 summary_stats_2 <- all_summary_stats[["2"]]
 
-# load("./Data/results_5.Rdata")
+# load("./Data/results1_5.Rdata")
 # summary_stats_5 <- all_summary_stats[["5"]]
 
-load("./Data/results_8.Rdata")
+load("./Data/results1_8.Rdata")
 summary_stats_8 <- all_summary_stats[["8"]]
@@
 # Load saved results
-load("./Data/results_2.Rdata")
-load("./Data/results_5.Rdata")
-load("./Data/results_8.Rdata")
-load("./Data/results_18.Rdata")
+load("./Data/results1_2.Rdata")
+load("./Data/results1_5.Rdata")
+load("./Data/results1_8.Rdata")
+load("./Data/results1_18.Rdata")
 
@@
 
-save(results, file = "./Data/type_I_results.Rdata")
+save(results, file = "./Data/type_I_results1.Rdata")
 
@@
 results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
-save(results_power, file = "./Data/results_power.Rdata")
+save(results_power, file = "./Data/results_power1.Rdata")
 
@@
 
-load("./Data/type_I_results.Rdata")
+load("./Data/type_I_results1.Rdata")
 
@@
 
-load("./Data/results_power.Rdata")
+load("./Data/results_power1.Rdata")
 
@@
 # 
-save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test.Rdata")
+save(TestStatistics1, TestStatistics2, file = "./Data/sim_empirical_test1.Rdata")
 
@@
 # 
-load("./Data/sim_empirical_test.Rdata")
+load("./Data/sim_empirical_test1.Rdata")
 

### 2024-02-12 Code/R/MainFunctions/gi0_sample.R

@@ -9,7 +9,7 @@
 # Output:
 #   - Random samples following the GI0 distribution.
 
-
+#library(invgamma)
 
 gi0_sample <- function(mu, alpha, L,  n) {
   
@@ -19,3 +19,18 @@ gi0_sample <- function(mu, alpha, L,  n) {
   Z_samples <- X_samples * Y_samples
   return(Z_samples)
 }
+
+
+
+# gi0_sample2 <- function(mu, alpha, L, n) {
+#   X_samples <- rgamma(n, shape = -alpha, rate = mu * (-alpha - 1))
+#   Y_samples <- rgamma(n, shape = L, rate = L)
+#   Z_samples <-  Y_samples/X_samples
+#   return(Z_samples)
+# }
+# 
+# 
+# set.seed(1234567890, kind = "Mersenne-Twister")
+# 
+# #c<-gi0_sample(1, -8, 5, 10)
+# m<-gi0_sample2(1, -8, 5, 10)

### 2024-02-20 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
new update paper and code

---
title: "Goodness-of-fit test "
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE)
#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(gtools)
library(stats4)
library(rmutil)
library(invgamma)
library(tidyverse)
library(scales)
library(RColorBrewer)
library(ggsci)
library(wesanderson)
library(ggpubr)
library(patchwork)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(geomtextpath)
library(latex2exp)
library(univariateML)
#install.packages('univariateML')
#univariateML::univariateML_models

library(fitdistrplus)
library(logspline)
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

```

The p-values of a Kolmogorov-Smirnov-Test (KS-Test) with estimated parameters can be quite wrong because the p-value does not take the uncertainty of the estimation into account. So unfortunately, you can't just fit a distribution and then use the estimated parameters in a Kolmogorov-Smirnov-Test to test your sample. There is a normality test called Lilliefors test which is a modified version of the KS-Test that allows for estimated parameters.

```{r Plot1, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}

load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")

ggplot() +
  geom_density(aes(x = as.vector(cv_values)), fill = "skyblue", color = "black") +
  labs(title = " ", x = "cv", y = "Density")
```

```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
x1<-as.vector(cv_values)

descdist(x1, discrete = FALSE)

fit.weibull <- fitdist(x1, "weibull")
plot(fit.weibull)
fit.weibull$aic
fit.norm <- fitdist(x1, "norm")
fit.norm$aic
plot(fit.norm)
```

```{r}
load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
x1<-as.vector(cv_values)
mydata_dist <- univariateML::model_select(x1)
mydata_dist
```

<!-- ```{r} -->
<!-- load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata") -->
<!-- x1<-as.vector(cv_values) -->
<!-- n.sims <- 100 -->

<!-- stats <- replicate(n.sims, { -->
<!--   r <- rweibull(n = length(x1) -->
<!--                 , shape= fit.weibull$estimate["shape"] -->
<!--                 , scale = fit.weibull$estimate["scale"] -->
<!--   ) -->
<!--   estfit.weibull <- fitdist(r, "weibull") # added to account for the estimated parameters -->
<!--   as.numeric(ks.test(r -->
<!--                      , "pweibull" -->
<!--                      , shape= estfit.weibull$estimate["shape"] -->
<!--                      , scale = estfit.weibull$estimate["scale"])$statistic -->
<!--   ) -->
<!-- }) -->

<!-- plot(ecdf(stats), las = 1, main = "KS-test statistic simulation (CDF)", col = "darkorange", lwd = 1.7) -->
<!-- grid() -->

<!-- ``` -->

```{r}
# load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
# x1<-as.vector(cv_values)
# n.sims <- 5
# 
# stats_gamma <- replicate(n.sims, {
#   r <- rgamma(n = length(x1),
#               shape = fit.gamma$estimate["shape"],
#               scale = fit.gamma$estimate["scale"]
#   )
#   estfit_gamma <- fitdist(r, "gamma") # Añadido para tener en cuenta los parámetros estimados
#   as.numeric(ks.test(r,
#                      "pgamma",
#                      shape = estfit_gamma$estimate["shape"],
#                      scale = estfit_gamma$estimate["scale"])$statistic
#   )
# })
# # Suponiendo que has ejecutado la simulación con la distribución gamma y guardado los resultados en stats_gamma
# 
# # Gráfico de la ECDF de las estadísticas de la prueba KS simuladas
# plot(ecdf(stats_gamma), las = 1, main = "KS-test statistic simulation (CDF) - Gamma Distribution", col = "darkorange", lwd = 1.7)
# grid()

```

<!-- ```{r} -->
<!-- # Suponiendo que ya has cargado los datos y ajustado la distribución Rayleigh -->
<!-- load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata") -->
<!-- x1 <- as.vector(cv_values) -->
<!-- n.sims <- 10 -->

<!-- stats_rayleigh <- replicate(n.sims, { -->
<!--   r <- rrayleigh(n = length(x1), -->
<!--                  scale = fit_rayleigh$estimate["scale"] -->
<!--   ) -->
<!--   estfit_rayleigh <- fitdist(r, "rayleigh") # Añadido para tener en cuenta los parámetros estimados -->
<!--   as.numeric(ks.test(r, -->
<!--                      "prayleigh", -->
<!--                      scale = estfit_rayleigh$estimate["scale"] -->
<!--                )$statistic -->
<!--   ) -->
<!-- }) -->

<!-- plot(ecdf(stats_rayleigh), las = 1, main = "KS-test statistic simulation (CDF) - Rayleigh Distribution", col = "darkorange", lwd = 1.7) -->
<!-- grid() -->

<!-- ``` -->

### 2024-02-20 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
new update paper and code

@@
 #options(kableExtra.latex.load_packages = FALSE)
-library(devtools)
+#library(devtools)
 #devtools::install_github("haozhu233/kableExtra")
@@
 
-```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}
+```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$, $L=8$."}
 
@@
 Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
-Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, holds that:
+Then, if $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, one holds that:
 \begin{equation*}
@@
 \xrightarrow[]{\mathcal{D}}
-\mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big).
+\mathcal{N}\big(0,\operatorname{Var}(\ln f(Z))\big),
 \end{equation*}
+where $o(\cdot)$ represents the little-o.
 \end{lemma}
+
 Consider, starting from the previous lemma, we aim at testing the following hypotheses:
@@
 $$
- \begin{cases}\mathcal{H}_0: \widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})=0 \\ 
-  \mathcal{H}_1:\widetilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})\neq0 .\end{cases}
+ \begin{cases}\mathcal{H}_0: \widetilde{H}= H_{\Gamma_{\text{SAR}}}\\ 
+  \mathcal{H}_1:\widetilde{H}\neq H_{\Gamma_{\text{SAR}}}.\end{cases}
 $$
@@
 \label{Eq:test_e}
-S(\bm{Z};L_0)= \widetilde{H}_{\text{C}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
+S(\bm{Z};L)= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
 \end{equation}
@@
 ## The Proposed Test
-Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness, kurtosis, and Anderson–Darling $p$-values for normality.
+Fig.&nbsp;\ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), coefficient of variation (CV), skewness (SK), excess kurtosis (EK), and Anderson–Darling $p$-values for normality.
 <!-- ACF Only show L=2 and L=8 -->
 Results with $p$-values larger than $0.05$  indicate no evidence against normality. 
-Small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails. 
-The coefficient of variation shows that as the sample size increases, variability with respect to the mean decreases.
+Small variance and near-zero skewness and excess kurtosis suggest limited spread, symmetry, and light tails. Increasing sample size reduces variability relative to the mean. 
 Normal QQ-plots, omitted for brevity, confirm that there is no evidence to reject the normal distribution.
@@
 )
-colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "CV", "Skewness", "Kurtosis", "$p$-value")
+colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "CV", "SK", "EK", "$p$-value")
 
@@
 After verifying the normality of the data, we proceeded to explore the capabilities of the proposed test in terms of size and power.
-Under $\mathcal{H}_0$ the test statistic  is asymptotically distributed as $\mathcal{N}(0,\sigma_S^2)$, and therefore, the $p$-value of the observed test statistic is $2\Phi(\varepsilon)-1$, where $\Phi$ is the standard Gaussian cumulative distribution function and
+Under $\mathcal{H}_0$, the distribution of test statistic is asymptotically normal.
+Therefore, the $p$-value  is calculated as $2\Phi(-\mid \varepsilon\mid)$, where  $\Phi$ is the standard Gaussian cumulative distribution and $\varepsilon$ is the standardized test statistic given by:
 $$
-\varepsilon=\frac{\tilde{H}(\bm{Z})-H_{\Gamma_{\text{SAR}}}(\bm{Z})}{\sigma_S}.
+\varepsilon=\frac{\tilde{H}-H_{\Gamma_{\text{SAR}}}}{\hat\sigma}.
 $$
+
 We considered nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
@@
   epsilon <- test_statistic / sigma_W
-  p_value <- 2*pnorm(abs(epsilon))-1
+  p_value <- 2 * (1 - pnorm(abs(epsilon)))
 
@@
 Fig.&nbsp;\ref{fig:Real_SAR_Images}(a) shows the SAR image.
-We used $7 \times 7$ local sliding windows to compute the test, and Fig.&nbsp;\ref{fig:Real_SAR_Images}(b) shows the $p$-values.
-The new image reveals two distinct regions: lighter background indicates homogeneity, while darker backgrounds represent heterogeneous areas.
-
+We used $7 \times 7$ local sliding windows for the test.
+In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), $p$-values higher than a $10\%$ significance level are shown.
+This approach allows to emphasize regions where there is not enough evidence against the null hypothesis.
+The new image reveals two distinct regions: darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
 ```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
 knitr::include_graphics("../../../Figures/PNG/Intensity.png")
-knitr::include_graphics("../../../Figures/PNG/pvalue7x7.png")
+knitr::include_graphics("../../../Figures/PNG/pvalue7x7-10.png")
 
@@
 
-We propose a testing procedure for distinguishing between fully-developed speckle and heterogeneous clutter with a test statistic based on a bootstrap-improved estimator of the Shannon entropy. 
+We proposed a testing procedure for distinguishing between fully-developed speckle and heterogeneous clutter.
+This tool is equipped with a test statistic based on a bootstrap-improved estimator of the Shannon entropy.
 <!-- The Correa estimator ($\widetilde{H}_{\text{C}}$) stands out as the optimal choice, exhibiting superior performance in bias and MSE across simulations involving the $G_I^0$ distribution.  -->
 <!-- This superiority becomes particularly pronounced when the number of looks exceeds $2$. -->
-Our proposal includes the empirical size and power considering various sample sizes, numbers of looks, and nominal levels.
-
-The results show that the test performs acceptably with sample sizes larger than $50$. 
-However, practical scenarios often involve smaller sample sizes, typically obtained over windows of size $7 \times 7$.
-
-The application of the test to actual SAR data yielded promising outcomes, effectively discerning distinct regions in the image and showing its potential for discriminating between homogeneous and heterogeneous zones.
+Using empirical test size and power as figures of merit, our proposal was assessed for various sample sizes, numbers of looks, and nominal levels.
+
+Results showed that the test presented good performance for sample sizes larger than $50$, scenarios that frequently occur in SAR image processing practice.
+
+Applying the test to actual SAR data yielded promising results.
+Different regions in the image were effectively distinguished and the potential of the test to distinguish between homogeneous and heterogeneous zones was demonstrated.
 
@@
 
-This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior  (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.
+This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior  (CAPES), the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), and National Council for Scientific and Technological Development, Brazil.
 

### 2024-02-20 Code/R/Programs/SAR_cv_values.R

@@ -46,25 +46,18 @@ for (i in 1:(rows - window_size + 1)) {
     # Seleccionar ventana local
     window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
     
-    # Almacenar valores de x para cada ventana 
+     
     x_values <- window_data
     
     
-    # Calcular la media y la desviación estándar
+    # 
     mean_values[i, j] <- mean(window_data)
     sd_values <- sd(window_data)
     
-    # Calcular el coeficiente de variación
+    # 
     cv_values[i, j] <- sd_values / mean_values[i, j]
     
-    # Calcular entropC-a con el estimador no paramC)trico
-    #entropy_values[i, j] <- correa_estimator(window_data)
-    
-    # Calcular entropC-a verdadera
-    # true_entropy_values[i, j] <- (log(mean(window_data)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-    
-    # difference test
-    
+
    # difference_values[i, j] <- bootstrap_correa_estimator_log_mean(window_data, B)-  (L - log(L) + lgamma(L) + (1 - L) * digamma(L)) 
     #correa_estimator(window_data)- (log(mean(window_data)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
     #test_difference_vector <- c(test_difference_vector, difference_values[i, j])

### 2024-02-20 Code/R/Programs/Sar_test_each_window.R

@@ -1,39 +1,109 @@
 
-rm(list = ls())
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# rm(list = ls())
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
 library(ggplot2)
 library(e1071)
 library(nortest)
 library(fitdistrplus)
 
-load("./Data/results_data_Flevoland_cv_300_5.Rdata")
+#load("./Data/results_data_Flevoland_cv_300_5.Rdata")
+load("./Data/results_data_Flevoland_300_9.Rdata")
+#summary(difference_values)
 
 
-# Crear un vector con los valores de cv_values (puedes ajustar esto según tus necesidades)
-cv_vector <- as.vector(cv_values)
+#load("results_data_Flevoland_300_9.Rdata")
+
+
+p_values_matrix <- matrix(NA, nrow = nrow(difference_values), ncol = ncol(difference_values))
+
+
+for (i in 1:nrow(difference_values)) {
+  for (j in 1:ncol(difference_values)) {
+    # Calcular z-score para cada diferencia
+    z_score <- (difference_values[i, j] - mean(difference_values)) / sd(difference_values)
+    
+    # Calcular p-value para una prueba de dos colas
+    p_value <- 2 * pnorm(-abs(z_score))
+    
+    # Almacenar p-value en la matriz
+    p_values_matrix[i, j] <- p_value
+  }
+}
+
+
+# # Calcular z-scores para toda la matriz
+# all_z_scores <- as.vector((difference_values - mean(difference_values)) / sd(difference_values))
+# 
+# # Crear un marco de datos con los datos
+# df_z_scores <- data.frame(z_scores = all_z_scores)
+# 
+# # Graficar la densidad de los z-scores
+# ggplot(df_z_scores, aes(x = z_scores)) +
+#   geom_density(fill = "blue", alpha = 0.5) +
+#   labs(title = "Densidad de Z-scores", x = "Z-score", y = "Densidad")
+
+# Convertir la matriz de p-values en un vector
+all_p_values <- as.vector(p_values_matrix)
+
+# Crear un marco de datos con los datos
+df_p_values <- data.frame(p_values = all_p_values)
+
[…]

### 2024-02-20 Code/R/Programs/sar_test_calculation.R

@@ -24,7 +24,7 @@ B <- 1
 #difference_total <- bootstrap_correa_estimator_log_mean(x_Flevoland2, B)-  (L - log(L) + lgamma(L) + (1 - L) * digamma(L)) 
 
 
-window_size <- 9
+window_size <- 7
 
 
 rows <- nrow(x)

### 2024-02-24 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
final corrections, added heatmap for p-values

@@
 library(univariateML)
+library(viridis)
 #install.packages('univariateML')
@@
 source("../Programs/functions_sample_bias_mse.R")# 
-
+source("../imagematrix.R")
+source("../imagematrix1.R")
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
 
@@
 fit.weibull$aic
-fit.norm <- fitdist(x1, "norm")
-fit.norm$aic
-plot(fit.norm)
+# fit.norm <- fitdist(x1, "norm")
+# fit.norm$aic
+# plot(fit.norm)
 ```
 
-```{r}
-load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+```{r, eval=FALSE}
+load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
 x1<-as.vector(cv_values)
@@
 mydata_dist
+```
+
+```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland"}
+load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+alpha <- 5.452
+beta <- 2.061
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+#source("../imagematrix.R")
+source("../imagematrix1.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+plot(imagematrix1(p_values_matrix ))
+#plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r Plot2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 7x7, Flevoland" }
+
+load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
+
+ggplot() +
+  geom_density(aes(x = as.vector(cv_values)), fill = "blue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+source("../imagematrix.R")
+#hist(cv_values)
+```
+
+```{r, eval=FALSE}
+load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
+x2<-as.vector(cv_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland"}
+load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
+alpha <- 5.762
+beta <- 2.611
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+source("../imagematrix.R")
+#hist(p_values_matrix)
+par(mfrow=c(1,2))
+#plot(imagematrix(equalize(x)))
+plot(imagematrix(p_values_matrix))
+plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r, eval=FALSE}
+load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
+x2<-as.vector(cv_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r cv9, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 9x9, Flevoland"}
+
+#Los parametros fueron estimados con phitter.io
+load("../Programs/Data/results_data_Flevoland_cv_300_9.Rdata")
+alpha <- 3.58
+beta <- 1.32
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+source("../imagematrix.R")
+#hist(p_values_matrix)
+par(mfrow=c(1,2))
+#plot(imagematrix(equalize(x)))
+plot(imagematrix(p_values_matrix))
+plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r Plot3, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cv, window 5x5, Ottawa" }
+
+load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
+
+ggplot() +
+  geom_density(aes(x = as.vector(cv_values)), fill = "red", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+
+```{r 5ottawa, eval=FALSE}
+load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
+x2<-as.vector(cv_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}
+
+#Los parametros fueron estimados con phitter.io
+load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
+alpha <- 5.29
+beta <- 2.20
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+source("../imagematrix.R")
+#hist(p_values_matrix)
+par(mfrow=c(1,2))
+#plot(imagematrix(equalize(x)))
+plot(imagematrix(p_values_matrix))
+plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r Plotcqv, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }
+
+load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")
+
+ggplot() +
+  geom_density(aes(x = as.vector(cv_values)), fill = "green", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+
+```{r 5ottawa_cqv, eval=FALSE}
+load("../Programs/Data/results_data_Ottawa_cqv_512_5.Rdata")
+x2<-as.vector(cv_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}
+
+#Los parametros fueron estimados con phitter.io
+load("../Programs/Data/results_data_Ottawa_cv_512_5.Rdata")
+alpha <- 3.58
+beta <- 1.32
+
+pgamma_inv <- function(x, alpha, beta) {
+  1 - pgamma(1/x, shape = alpha, rate = beta)
+}
+
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    p_values_matrix[i, j] <- pgamma_inv(cv_value, alpha, beta)
+  }
+}
+
+#save(x, p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+source("../imagematrix.R")
+hist(p_values_matrix)
+par(mfrow=c(1,2))
+plot(imagematrix(equalize(x)))
+plot(imagematrix(p_values_matrix))
+plot(imagematrix(p_values_matrix >0.05))
+```
+```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }
+
+load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")
+
+ggplot() +
+  geom_density(aes(x = as.vector(cv_values)), fill = "pink", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
 ```
@@
 <!-- ``` -->
-
-```{r}
-# load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
-# x1<-as.vector(cv_values)
-# n.sims <- 5
-# 
-# stats_gamma <- replicate(n.sims, {
-#   r <- rgamma(n = length(x1),
-#               shape = fit.gamma$estimate["shape"],
-#               scale = fit.gamma$estimate["scale"]
-#   )
-#   estfit_gamma <- fitdist(r, "gamma") # Añadido para tener en cuenta los parámetros estimados
-#   as.numeric(ks.test(r,
-#                      "pgamma",
-#                      shape = estfit_gamma$estimate["shape"],
-#                      scale = estfit_gamma$estimate["scale"])$statistic
-#   )
-# })
-# # Suponiendo que has ejecutado la simulación con la distribución gamma y guardado los resultados en stats_gamma
-# 
-# # Gráfico de la ECDF de las estadísticas de la prueba KS simuladas
-# plot(ecdf(stats_gamma), las = 1, main = "KS-test statistic simulation (CDF) - Gamma Distribution", col = "darkorange", lwd = 1.7)
-# grid()
-
-```
-
-<!-- ```{r} -->
-<!-- # Suponiendo que ya has cargado los datos y ajustado la distribución Rayleigh -->
-<!-- load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata") -->
-<!-- x1 <- as.vector(cv_values) -->
-<!-- n.sims <- 10 -->
-
-<!-- stats_rayleigh <- replicate(n.sims, { -->
-<!--   r <- rrayleigh(n = length(x1), -->
-<!--                  scale = fit_rayleigh$estimate["scale"] -->
-<!--   ) -->
-<!--   estfit_rayleigh <- fitdist(r, "rayleigh") # Añadido para tener en cuenta los parámetros estimados -->
-<!--   as.numeric(ks.test(r, -->
-<!--                      "prayleigh", -->
-<!--                      scale = estfit_rayleigh$estimate["scale"] -->
-<!--                )$statistic -->
-<!--   ) -->
-<!-- }) -->
-
-<!-- plot(ecdf(stats_rayleigh), las = 1, main = "KS-test statistic simulation (CDF) - Rayleigh Distribution", col = "darkorange", lwd = 1.7) -->
-<!-- grid() -->
-
-<!-- ``` -->

### 2024-02-24 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
final corrections, added heatmap for p-values

@@
    - \usepackage{subfig}
-   #- \usepackage{caption}
+   - \usepackage{subcaption}
+   - \usepackage{caption}
+
    #- \captionsetup[table]{skip=0pt}
@@
 
-save(results_gi0, file = "./Data/resultsgi0.Rdata")
+save(results_gi0, file = "./Data/resultsgi0_1.Rdata")
 
@@
 
-load("./Data/resultsgi0.Rdata")
+load("./Data/resultsgi0_1.Rdata")
 
@@
 We used $7 \times 7$ local sliding windows for the test. 
-In Fig.&nbsp;\ref{fig:Real_SAR_Images}(b), $p$-values higher than a $10\%$ significance level are shown.
-This approach allows to emphasize regions where there is not enough evidence against the null hypothesis.
-The new image reveals two distinct regions: darker background indicates homogeneity, while lighter backgrounds represent heterogeneous areas.
-```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width='.48\\linewidth',  fig.ncol=2}
-knitr::include_graphics("../../../Figures/PNG/Intensity.png")
-knitr::include_graphics("../../../Figures/PNG/pvalue7x7-10.png")
+In Fig.
+\ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width = c("40mm", "60mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
+knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
+knitr::include_graphics("../../../Figures/PDF/color7x7.pdf")
 

### 2024-02-24 Code/R/Programs/SAR_cv_values.R

@@ -1,7 +1,7 @@
 #rm(list = ls())
 
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
 source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
 source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
@@ -12,16 +12,18 @@ source("../../../Code/R/MainFunctions/correa_estimator.R")
 # x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
 #                             headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
 
-x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
-                 headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
+# x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
 
+x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
 
 
 
 L <- 5
-B <- 1
+#B <- 1
 
-#difference_total <- bootstrap_correa_estimator_log_mean(x_Flevoland2, B)-  (L - log(L) + lgamma(L) + (1 - L) * digamma(L)) 
+
 
 
 window_size <- 5
@@ -30,17 +32,13 @@ window_size <- 5
 rows <- nrow(x)
 cols <- ncol(x)
 
-# 
- mean_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
-# entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
-# true_entropy_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
-# difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
[…]

### 2024-02-24 Code/R/Programs/plot_pvalue.R

@@ -1,8 +1,8 @@
 # 
-# rm(list = ls())
+ rm(list = ls())
 # if(!require("rstudioapi")) install("rstudioapi")
 # setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
-
+# for normal distribution
 library(ggplot2)
 library(e1071)
 library(nortest)
@@ -42,15 +42,130 @@ p_values_matrix <- calculate_p_values_matrix(difference_values, sd_difference_va
 
 save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_300_7_n.Rdata")
 
+aspect_ratio <- ncol(p_values_matrix) / nrow(p_values_matrix)
+
+# Create a sequence of values for x and y axes based on the aspect ratio
+x_values <- seq(0, 1, length.out = ncol(p_values_matrix) + 1)
+y_values <- seq(0, aspect_ratio, length.out = nrow(p_values_matrix) + 1)
+
+# Plot the p_values_matrix with adjusted axes
+image(x = x_values, y = y_values, z = p_values_matrix, 
+      col = colorRampPalette(c("navy", "yellow", "orange"))(100),
+      main = "Heatmap de p-values",
+      xlab = "Columnas",
+      ylab = "Filas")
+
+# Add grid lines to visualize the pixel positions
+abline(v = x_values, h = y_values, col = "gray", lty = 2)
+
+# Calculate the aspect ratio of the image
+# aspect_ratio <- ncol(p_values_matrix) / nrow(p_values_matrix)
+# 
+# # Invert the y-axis values
+# y_values <- rev(seq(0, aspect_ratio, length.out = nrow(p_values_matrix) + 1))
+# 
+# # Plot the p_values_matrix with adjusted axes
+# image(x = seq(0, 1, length.out = ncol(p_values_matrix) + 1), y = y_values, z = p_values_matrix,
+#       col = colorRampPalette(c("navy", "yellow", "red"))(100),
+#       main = "Heatmap de p-values",
+#       xlab = "Columnas",
+#       ylab = "Filas")
+# aspect_ratio <- ncol(p_values_matrix) / nrow(p_values_matrix)
+# 
+# # Create a sequence of values for x and y axes based on the aspect ratio
+ # x_values <- seq(0, 1, length.out = ncol(p_values_matrix) + 1)
+ # # Invertir el eje y al crear y_values
+ # # Mantén la definición original de y_values
[…]

### 2024-02-24 Code/R/imagematrix_color.R

@@ -1,0 +1,193 @@
+##
+## imagematrix class definition
+##
+## $Header: /database/repository/rimage/R/Attic/imagematrix.R,v 1.1.2.5 2004/03/17 06:35:18 tomo Exp $
+##
+## Copyright (c) 2003 Nikon Systems Inc.
+## For complete license terms see file LICENSE
+
+
+
+imagematrix <- function(mat, type = NULL, ncol = dim(mat)[1], nrow = dim(mat)[2],
+                        noclipping = FALSE) {
+  if (is.null(dim(mat)) && is.null(type)) stop("Type should be specified.")
+  if (length(dim(mat)) == 2 && is.null(type)) type <- "grey"
+  if (length(dim(mat)) == 3 && is.null(type)) type <- "rgb"
+  if (type != "rgb" && type != "grey") stop("Type is incorrect.")
+  if (is.null(ncol) || is.null(nrow)) stop("Dimension is uncertain.")
+
+  imgdim <- c(ncol, nrow, if (type == "rgb") 3 else NULL)
+
+  if (length(imgdim) == 3 && type == "grey") {
+    # force to convert grey image
+    mat <- rgb2grey(mat)
+  }
+
+  if (noclipping == FALSE && ((min(mat, na.rm = TRUE) < 0) || (1 < max(mat, na.rm = TRUE)))) {
+    warning("Pixel values were automatically clipped because of range over.")
+    mat <- clipping(mat)
+  }
+
+  mat <- array(mat, dim = imgdim)
+  attr(mat, "type") <- type
+  class(mat) <- c("imagematrix", class(mat))
+  mat
+}
+
+
+
+
+plot.imagematrix <- function(x, significance_level = 0.05, colors = colorRampPalette(c("#FE9929", "#253494"))(100), ...) {
+  if (is.null(attr(x, "type"))) stop("Type should be specified.")
+
+  colmat <- matrix(0, nrow = nrow(x), ncol = ncol(x))
+
+  # 
+  colmat[x <= significance_level] <- x[x <= significance_level]
+  colmat[x > significance_level] <- x[x > significance_level]
+
+  
+  color_palette <- colorRampPalette(colors)(100)
+ 
+  
+  layout(matrix(c(1, 2), nrow = 1), widths = c(2, 1))
+  par(mar = c(0, 0, 0, 0))
+  par(oma = c(0, 0, 0, 0))
+  par(omi = c(0, 0, 0, 0))
+  # Imagen principal
[…]

### 2024-02-25 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
new image

@@
 plot(imagematrix(p_values_matrix))
-plot(imagematrix(p_values_matrix >0.1))
+plot(imagematrix(p_values_matrix <0.05))
+valores_menores_que_0_05 <- sum(p_values_matrix < 0.05)
+cat("Número de valores menores que 0.05:", valores_menores_que_0_05, "\n")
+
 ```
@@
 source("../imagematrix.R")
-#hist(p_values_matrix)
+hist(p_values_matrix)
 par(mfrow=c(1,2))

### 2024-02-25 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
new image

@@
 knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
-knitr::include_graphics("../../../Figures/PDF/color7x7.pdf")
+knitr::include_graphics("../../../Figures/PDF/pvalues_7x7_col.pdf")
 

### 2024-02-26 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
new image

--- 2024-02-24 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
@@
 \ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
-```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.' ), out.width = c("40mm", "60mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
+```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.
+' ), out.width = c("40mm", "59mm"),  fig.ncol=2, fig.width = 20, fig.height = 10}
 knitr::include_graphics("../../../Figures/PNG/Intensity.png")#out.width='.55\\linewidth'
-knitr::include_graphics("../../../Figures/PDF/color7x7.pdf")
+knitr::include_graphics("../../../Figures/PDF/pvalue_f.pdf")
 

### 2024-05-07 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
doctoral qualification document

--- 2024-02-24 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
@@
 source("../imagematrix.R")
-source("../imagematrix1.R")
+#source("../imagematrix.R")
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r Plot1, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+save(difference_values, x, file = "./Data/results_Lake_512_9W_AO_100b_36L.Rdata")
+save(difference_values, x, file = "./Data/results_Lake_without_bootstrap.Rdata")
+save(difference_values, x, file = "./Data/results_Lake_without_bootstrap1.Rdata")
+load("./Data/results_mexico_600_9W_AO_100b_6L.Rdata")
+```{r Plot_chicago_lake, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
 
 load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
+#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
+#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
+#results_Chicago_1024_9_AO_100b_6L
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
+#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
+load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
+#x1<-as.vector(epsilon_matrix)
+source("../imagematrix.R")
+hist(difference_values)
 
 ggplot() +
-  geom_density(aes(x = as.vector(cv_values)), fill = "skyblue", color = "black") +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r Plot_ottawa_AO_300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
+#load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
+#load("../Programs/Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
+#results_Chicago_1024_9_AO_100b_6L
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
+#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
+load("../Programs/Data/results_pvalue_epsilon.Rdata")
+#x1<-as.vector(epsilon_matrix)
+source("../imagematrix.R")
+hist(p_values_matrix)
+
+ggplot() +
+  geom_density(aes(x = as.vector(epsilon_matrix)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r normal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
+load("../Programs/Data/results_pvalue_epsilon.Rdata")
+x1<-as.vector(epsilon_matrix)
+#save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
+descdist(x1, discrete = FALSE)
+
+#fit.weibull <- fitdist(x1, "weibull")
+#plot(fit.weibull)
+#fit.weibull$aic
+ fit.norm <- fitdist(x1, "norm")
+ fit.norm$aic
+ plot(fit.norm)
+```
+
+```{r Plot_ottawa_AO_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
+load("../Programs/Data/results_ottawa_city_512_7_AO_100b.Rdata")#results_ottawa_city_512_7_AO_300b.Rdata
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_AO_100b.Rdata")
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r Plot_ottawa_ebra_50, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
+load("../Programs/Data/results_ottawa_city_512_7_AO_300b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+```{r Plot_ottawa_ebra_100, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
+load("../Programs/Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_ottawa_city_512_7_Ebrahimi_100b.Rdata")
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r PlotAO, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_agua_300_7_AO.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_5_Ebr_50b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r PlotAO_chicago_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r PlotAO_panama_city, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_Mexico_512_7_AO_300b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_chicago_city_512_7_AO_100b.Rdata
+#save(difference_values, x, file = "./Data/results_data_mexico_512_5_Ebr_50b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_panama_512_5_Ebr_100b.Rdata")
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+
+```
+
+```{r, eval=FALSE}
+load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
+#load("../Programs/Data/results_data_agua_300_7_AO.Rdata")
+
+x2<-as.vector(difference_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r Plot_EBra, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_agua_300_5_E.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_300b.Rdata
+
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+```{r Plot_EBra300, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata
+
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
   labs(title = " ", x = "cv", y = "Density")
@@
 
-```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR"}
-load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
-x1<-as.vector(cv_values)
+```{r Plot_EBra1b, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_agua_300_5_Eb_1b.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")results_data_agua_300_5_Eb_1b.Rdata
+
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+
+```{r Plot_correa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt"}
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_agua_300_9_correa.Rdata")
+#save(difference_values, x, file = "./Data/results_data_crop_chicago_200_7_n.Rdata")
+
+source("../imagematrix.R")
+hist(difference_values)
+
+ggplot() +
+  geom_density(aes(x = as.vector(difference_values)), fill = "skyblue", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+
+```{r, eval=FALSE}
+#load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
+load("../Programs/Data/results_data_agua_300_5_Eb_300b.Rdata")
+
+x2<-as.vector(difference_values)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r 2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation of entropy for Gamma SAR", eval=FALSE}
+load("../Programs/Data/results_chicago_city_512_7_AO_100b.Rdata")
+x1<-as.vector(difference_values)
 
@@
 
-fit.weibull <- fitdist(x1, "weibull")
-plot(fit.weibull)
-fit.weibull$aic
-# fit.norm <- fitdist(x1, "norm")
-# fit.norm$aic
-# plot(fit.norm)
+#fit.weibull <- fitdist(x1, "weibull")
+#plot(fit.weibull)
+#fit.weibull$aic
+ fit.norm <- fitdist(x1, "norm")
+ fit.norm$aic
+ plot(fit.norm)
 ```
@@
 
-```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland"}
+```{r cv5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
 load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
@@
 
+save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r cv_lognormal, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
+#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
+# Definir la función de distribución acumulativa inversa de la distribución lognormal
+plnorm_inv <- function(x, meanlog, sdlog) {
+  pnorm(log(x), mean = meanlog, sd = sdlog)
+}
+
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+meanlog <- -0.1931404
+sdlog <- 0.4293747
+
+# Crear una matriz para almacenar los p-valores
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    # Calcular el p-valor utilizando la función de distribución acumulativa inversa de la distribución lognormal
+    p_values_matrix[i, j] <- plnorm_inv(cv_value, meanlog, sdlog)
+  }
+}
+
+# Guardar la matriz de p-valores
 #save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
@@
 #source("../imagematrix.R")
-source("../imagematrix1.R")
+source("../imagematrix.R")
 #hist(p_values_matrix)
@@
 #plot(imagematrix(p_values_matrix ))
-plot(imagematrix1(p_values_matrix ))
-#plot(imagematrix(p_values_matrix >0.1))
+plot(imagematrix(equalize(z.up.le)))
+plot(imagematrix(equalize(cv_values)))#z.up.le
+plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_matrix <0.1))
+plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r cv_lognormal2, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
+#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
+load("../Programs/Data/results_data_simulated_Phantom_7.Rdata")
+# Definir la función de distribución acumulativa inversa de la distribución lognormal
+# plnorm_inv <- function(x, meanlog, sdlog) {
+#   pnorm(log(x), mean = meanlog, sd = sdlog)
+# }
+
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+meanlog <- -0.1503808
+sdlog <-  0.4504363
+
+# Crear una matriz para almacenar los p-valores
+p_values_matrix <- matrix(NA, nrow = nrow(cv_values), ncol = ncol(cv_values))
+
+# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
+for (i in 1:nrow(cv_values)) {
+  for (j in 1:ncol(cv_values)) {
+    cv_value <- cv_values[i, j]
+
+    # Calcular el p-valor utilizando la función plnorm()
+    p_values_matrix[i, j] <- 1-plnorm(cv_value, meanlog = meanlog, sdlog = sdlog)
+  }
+}
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(equalize(z.up.le)))
+plot(imagematrix(equalize(cv_values)))#z.up.le
+plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_matrix <0.1))
+plot(imagematrix(p_values_matrix >0.1))
+```
+
+```{r cv_lognormal3_mnad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
+#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+load("../Programs/Data/results_data_simulated_z_up_le_mnad_250_7.Rdata")
+# Definir la función de distribución acumulativa inversa de la distribución lognormal
+# plnorm_inv <- function(x, meanlog, sdlog) {
+#   pnorm(log(x), mean = meanlog, sd = sdlog)
+# }
+
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+# Cargar los datos y parámetros de ajuste de la distribución lognormal
+meanlog <- -0.2861518
+sdlog <- 0.5366815
+
+# Crear una matriz para almacenar los p-valores
+p_values_matrix <- matrix(NA, nrow = nrow(cd_values_mnad), ncol = ncol(cd_values_mnad))
+
+# Calcular los p-valores para cada dato en la matriz de coeficientes de variación
+for (i in 1:nrow(cd_values_mnad)) {
+  for (j in 1:ncol(cd_values_mnad)) {
+    cd_value_mnad <- cd_values_mnad[i, j]
+
+    # Calcular el p-valor utilizando la función plnorm()
+    p_values_matrix[i, j] <- 1-plnorm(cd_value_mnad, meanlog = meanlog, sdlog = sdlog)
+  }
+}
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(equalize(z.up.le)))
+plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
+plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_matrix <0.1))
+plot(imagematrix(p_values_matrix >0.05))
+```
+
+```{r cv_lognormal3_entropy, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Flevoland",eval=FALSE }
+
+load("../Programs/Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
+# Calcular la media y la desviación estándar de los datos originales
+mean_original <- mean(difference_values, na.rm = TRUE)
+sd_original <- sd(difference_values, na.rm = TRUE)
+
+# Normalizar los datos
+normalized_data <- (difference_values - mean_original) / sd_original
+
+# Parámetros de la distribución normal estándar
+mean_standard <- 0
+sd_standard <- 1
+
+# Definir función para calcular los p-valores
+calculate_p_value <- function(x) {
+  p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
+  return(p_value)
+}
+
+# Dimensiones de la matriz difference_values
+n_rows <- nrow(normalized_data)
+n_cols <- ncol(normalized_data)
+
+# Matriz para almacenar los p-valores
+p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)
+
+# Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
+for (i in 1:n_rows) {
+  for (j in 1:n_cols) {
+    p_values[i, j] <- calculate_p_value(normalized_data[i, j])
+  }
+}
+
+# Guardar los p-valores
+#save(p_values, file = "p_values_matrix_normalized.Rdata")
+
+#load("../Programs/Data/results_data_Flevoland_cv_300_5.Rdata")
+#load("../Programs/Data/results_data_simulated_z_up_le_cv_250_7.Rdata")
+#load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")
+#save(p_values, file = "../Programs/Data/p_values_matrix_normalized.Rdata")
+#load("../Programs/Data/p_values_matrix_normalized.Rdata")
+# Definir la función de distribución acumulativa inversa de la distribución lognormal
+# plnorm_inv <- function(x, meanlog, sdlog) {
+#   pnorm(log(x), mean = meanlog, sd = sdlog)
+# }
+
+# # Cargar los datos y parámetros de ajuste de la distribución lognormal
+# # Cargar los datos y parámetros de ajuste de la distribución lognormal
+# # Calcular la media y la desviación estándar de los datos originales
+# mean_original <- mean(difference_values, na.rm = TRUE)
+# sd_original <- sd(difference_values, na.rm = TRUE)
+# 
+# # Normalizar los datos
+# normalized_data <- (difference_values - mean_original) / sd_original
+# 
+# # Parámetros de la distribución normal estándar
+# mean_standard <- 0
+# sd_standard <- 1
+# 
+# # Definir función para calcular los p-valores
+# calculate_p_value <- function(x) {
+#   p_value <- 2 * pnorm(-abs(x), mean = mean_standard, sd = sd_standard)
+#   return(p_value)
+# }
+# 
+# # Dimensiones de la matriz difference_values
+# n_rows <- nrow(normalized_data)
+# n_cols <- ncol(normalized_data)
+# 
+# # Matriz para almacenar los p-valores
+# p_values <- matrix(NA, nrow = n_rows, ncol = n_cols)
+# 
+# # Iterar sobre cada dato en normalized_data y calcular el p-valor correspondiente
+# for (i in 1:n_rows) {
+#   for (j in 1:n_cols) {
+#     p_values[i, j] <- calculate_p_value(normalized_data[i, j])
+#   }
+# }
+# 
+# # Guardar los p-valores
+# save(p_values, file = "../Programs/Data/p_values_matrix_normalized_1.Rdata")
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+# Guardar la matriz de p-valores
+#save(p_values_matrix, file = "./Data/results_pvalue_Flevoland_cv_300_5.Rdata")
+
+#source("../imagematrix.R")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#par(mfrow=c(1,2))
+#plot(imagematrix(p_values_matrix ))
+#plot(imagematrix(equalize(z.up.le)))
+#plot(imagematrix(equalize(cd_values_mnad)))#z.up.le
+plot(imagematrix(p_values ))
+plot(imagematrix(p_values <0.1))
+plot(imagematrix(p_values >0.5))
 ```
@@
 ```
-```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland"}
+```{r cv7, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 7x7, Flevoland", eval=FALSE}
 load("../Programs/Data/results_data_Flevoland_cv_300_7.Rdata")
@@
 plot(imagematrix(p_values_matrix))
-plot(imagematrix(p_values_matrix >0.1))
+plot(imagematrix(p_values_matrix >0.05))
+valores_menores_que_0_05 <- sum(p_values_matrix < 0.05)
+cat("Número de valores menores que 0.05:", valores_menores_que_0_05, "\n")
+
 ```
@@
 
-```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}
+```{r cvOttawa, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}
 
@@
 plot(imagematrix(p_values_matrix))
-plot(imagematrix(p_values_matrix >0.1))
+plot(imagematrix(p_values_matrix >0.05))
 ```
@@
 
-```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa"}
+```{r cqvOttawa_5, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="p values for CV window 5x5, Ottawa", eval=FALSE}
 
@@
 source("../imagematrix.R")
-hist(p_values_matrix)
+#hist(p_values_matrix)
 par(mfrow=c(1,2))
@@
 plot(imagematrix(p_values_matrix))
-plot(imagematrix(p_values_matrix >0.05))
+#plot(imagematrix(p_values_matrix <0.05))
 ```
+
 ```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }
@@
 ggplot() +
-  geom_density(aes(x = as.vector(cv_values)), fill = "pink", color = "black") +
+  geom_density(aes(x = as.vector(cd_values_mad)), fill = "pink", color = "black") +
+  labs(title = " ", x = "cv", y = "Density")
+```
+
+```{r 5ottawa_mad, eval=FALSE}
+load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_5.Rdata")
+x2<-as.vector(cd_values_mad)
+mydata_dist <- univariateML::model_select(x2)
+mydata_dist
+```
+
+```{r Plotcqvmad, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Density cqv, window 5x5, Ottawa" }
+
+load("../Programs/Data/results_data_Ottawa_cd_mad_matrix_512_7.Rdata")
+
+ggplot() +
+  geom_density(aes(x = as.vector(cd_values_mad)), fill = "blue", color = "black") +
   labs(title = " ", x = "cv", y = "Density")

### 2024-05-07 Text/Articles/MIGARS_2024/Final_Version_MIGARS.Rmd
doctoral qualification document

@@
 ---
-title: Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy
+title: Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy
 affiliation:
@@
 We used $7 \times 7$ local sliding windows for the test. 
-In Fig.
-\ref{fig:Real_SAR_Images}(b), the heatmap of the $p$-values refers to the decisions at the $5\%$ significance level, with the orange areas representing a rejection of the null hypothesis, i.e., heterogeneous areas, while the blue areas representing non-rejection at the $5\%$ significance level, indicating homogeneity.
+Fig.&nbsp;\ref{fig:Real_SAR_Images}(b) shows the heatmap of the $p$-values.
+The color table maps all above $0.05$ into dark blue (no evidence to reject the fully-developed speckly hypothesis), and those below  $0.05$ into a gradient between blue and orange (evidence to reject the hypothesis).
+
 ```{r Real_SAR_Images, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",fig.pos = 'H', fig.cap='Results of applying the test statistical to actual data.',  fig.subcap=c('SAR image.', '$p$-values.
@@
 knitr::include_graphics("../../../Figures/PDF/pvalue_f.pdf")
-
-```
+```
+
+These results show that the map of $p$-values correctly identify regions with different levels of heterogeneity.
 

### 2024-05-07 Text/Thesis/chapters/1_intro.tex
doctoral qualification document

\chapter{Introduction}\label{chp:int}
%------------------------------------
%	INTRO INTRO
%------------------------------------

The technology of Synthetic Aperture Radar (SAR) imaging operates on the comprehensive aperture principle to produce high-resolution SAR images.
In contrast to conventional optical remote sensing images, SAR images remain unaffected by external factors, making them suitable for identifying ground targets in diverse weather conditions and expansive areas.  
Consequently, SAR imagery has become essential for environmental monitoring, disaster management, agriculture, topography mapping, geological exploration, maritime navigation, defense, and climatology~\citep{Moreira2013, iglesias2013atmospheric, Mu2019}.  
However, the effective use of SAR
data depends on a thorough understanding of its statistical properties
because it is corrupted by speckle. This noise-like interference effect
is inherent in SAR data due to the coherent nature of the imaging
process~\citep{Argenti2013}.

Speckle in intensity format is non-Gaussian. 
Thus, SAR data require reliable statistical models for accurate processing. 
The \(\mathcal{G}^0\) distribution, which is suitable for SAR data, includes
the Gamma law as the limiting case for fully-developed
speckle~\citep{Ferreira2020} and provides flexibility with fewer
parameters for analysis.

When deciding which model is the best, practitioners face a problem. 
On the one hand, if they opt for the Gamma law when the data come from the
\(\mathcal{G}^0\) distribution, they lose all the information about the
number of scatterers, which is revealed by one of the parameters of the
latter model~\citep{Yue2021}. 
On the other hand, if they apply the \(\mathcal{G}^0\) distribution under fully developed speckle, maximum
likelihood estimation is tricky: bias increases making estimation
unreliable~\citep{VasconcellosFrerySilva:CompStat}, and the likelihood is
flat, so numerical optimization may not
converge~\citep{FreryCribariSouza:JASP:04}.

Our work aims to improve the identification of potential roughness
features in SAR intensity data. 
Physical modeling of SAR data allows the
use of the Gamma distribution in the presence of fully-developed
speckle, where an infinite number of independent backscatterers per
resolution unit is assumed, commonly referred to as homogeneous regions.

In this context, we present a set of three novel test statistics that
aim to distinguish between homogeneous and non-homogeneous returns,
particularly between gamma and \(\mathcal{G}^0\) distributed data,
assuming the number of looks is known.
 We use properties such as entropy and coefficient of variation.

Entropy is a fundamental concept in information theory with far-reaching
applications in pattern recognition, statistical physics, image
processing, edge detection and SAR image
analysis~\citep{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
\citet{Shannon1948} this concept for a random variable to measure information and uncertainty. 
Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data
dispersion and performing tests for normality, exponentiality and
uniformity~\citep{Wieczorkowski1999,Zamanzade2012}. 
Entropy estimation is challenging, especially when the model is unknown. In these cases,
non-parametric methods are used. Spacing methods have been discussed as
a non-parametric approach in Refs.~\citep{AlizadehNoughabi2010,Subhash2021}. This strategy is flexible
and robust because it does not enforce a model or parametric
constraints.

The coefficient of variation (CV), introduced in 1896 by~\citet{Pearson1896}, is a relative dispersion measure widely used
in various fields of applied statistics, including sampling,
biostatistics, medical and biological research, climatology and other
fields~\citep{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
It facilitates the comparison of variability between different
populations and is particularly valuable for relating variables with
different units. This is because when the primary purpose is to compare
the variations of several variables, the standard deviation can only
serve as an adequate measure of variation if all variables are expressed
in the same unit of measurement and have identical means. If these
conditions are not met, then the CV is the relative measure that is
usually used in real applications. The variable with the highest CV
value has the largest relative dispersion around the mean
value~\citep{Banik2011}. The coefficient of variation is the primary
measure of heterogeneity in SAR data~\citep{Ulaby1986,Touzi1988}. We
study two ways of estimating the coefficient of variation.

The other parameter we study is the Shannon entropy. Different roughness
levels materialized as models for SAR data, have different entropy
values, but this fundamental quantity can also be estimated in a
model-agnostic way. We exploit this property and design a
bootstrap-improved non-parametric estimator for the Shannon entropy.

We devise test statistics based on these three estimators: the classical
coefficient of variation, a robust version, and the Shannon entropy
estimator. We apply these test statistics to generate maps of evidence
of homogeneity that reveal different types of targets in the SAR data.
We show that our proposed method is superior to existing approaches with
simulated data and SAR images.

%---------------------------------------------------------------------------------------------------------------------

\section{Objectives}

The aim of this work is the identification of roughness features in SAR intensity data by developing novel test statistics for distinguishing between homogeneous and heterogeneous domains. To achieve this goal, we propose the following procedure:

\begin{itemize}
    \item Select the optimal non-parametric estimator of entropy, refined through bootstrap techniques, aiming to reduce bias and mean square error.
    \item Propose three test statistics: the first based on the selected non-parametric estimator of entropy; the second utilizing the classical coefficient of variation; and the third using a robust approach of CV variant.
    \item Conduct computational experiments to evaluate the performance of the proposed test statistics across various simulated data scenarios.
    \item Apply the test statistics to SAR data to assess their effectiveness in identifying roughness features.
\end{itemize}

\subsection{Submitted Articles}

The results obtained in this work were submitted for publication as follows:
\begin{itemize}
    \item  MIGARS 2024 proceedings in the IEEE Xplore Digital Library®, titled "Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy".
    \item  Remote Sensing journal from MDPI, titled "Identifying Heterogeneity in SAR Data with New Test Statistics".
\end{itemize}
The articles were written in Rmarkdown and are fully reproducible. 
The code and data are accessible at 
\href{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics}{\textcolor[rgb]{0,0,1}{Repository Link}}

\section{Manuscript organization}\label{sec:research_questions}

% colocar para citar los capitulos
\hypersetup{linkcolor=blue}
This document is organized as follows: 
Chapter~\ref{chp:background} provides a background on remote sensing and SAR images. 
Chapter~\ref{chp:methods} discusses methodological aspects, including statistical modeling, entropy estimation for intensity SAR data, and hypothesis testing. 
Chapter~\ref{chp:results} presents the main results obtained in our study with both simulated and actual data. Finally,
In Chapter~\ref{chp:conclusions}, the conclusions and future work are presented.
%Chapter ~\ref{chp:models} explains ...
%------------------------------------
%	HAZARD: OVERVIEW
%------------------------------------

%\section{Computing platforms}
%This  project required a vast amount of computing, preprocessing, analysis and plotting.

%------------------------------------
%	TODO STUFF
%------------------------------------
% \section{Additional sources to integrate in this chapter}
% \begin{itemize}
% \item check all TODOs
% \item read again \url{http://ec.europa.eu/environment/water/flood_risk/flood_atlas/pdf/handbook_goodpractice.pdf}
% \item include citation EU Floods Directive (2007/60/EC) , \cite{Mysiak2013, EUFD2007}
% \item section to talk about uncertainties? \citet{alfieri2014} has a good section about it
% \item Alps are the water tower of the Po plain, and for this reason I might want to give them a closer look. I could cite one of the many kotlarski works, or e.g. \citet[][]{Gobiet2014}. View the 'Alps' category in my Mendeley, it contains about 30 works on the subject
% \end{itemize}

### 2024-05-07 Text/Thesis/chapters/2_background.tex
doctoral qualification document

\chapter{Synthetic Aperture Radar Basics}\label{chp:background}%\Cref{sec:pr_obs}
%

%------------------------------------
%	
%------------------------------------

%Remote sensing is devoted to gathering information from the Earth’s surface at a distance~\citep{campbell2011introduction}, by means of electromagnetic energy or other mediums.

This chapter presents some basics of remote sensing that we will use in the rest of the document and focuses on the theory of SAR.

%\section{Electromagnetic radiation}
\section{Remote Sensing} \label{sec:pr_obs}

Remote sensing is the practice of deriving information about the Earth's land using images acquired from elevated platforms like airplanes or satellites in space, using electromagnetic radiation across various regions of the electromagnetic spectrum~\citep{campbell2011introduction}.

The word “radar” was originally an acronym, RADAR, for “radio detection and ranging”.
Today, the technology is so common that the word has become a standard English noun.
The history of radar extends to the early days of modern electromagnetic theory. 
In 1886, Hertz demonstrated reflection of radio waves, and in 1900 Tesla described a concept for electromagnetic detection and velocity measurement in an interview.
Early radar development was driven by military necessity, and the military is still a major user and developer of radar technology.
Radar is also an essential sensor for emerging autonomous driving systems. 
Finally, spaceborne and airborne radar is an important tool in mapping earth topology and environmental characteristics such as water and ice conditions, forestry conditions, land usage, and pollution~\citep{richards2005fundamentals}.

In 1951 Carl Wiley developed synthetic aperture radar while working at the Goodyear Aircraft Company. 
Using a technique known as Doppler beam sharpening, the signals from a series of locations are summed to produce a finer azimuth resolution than 
the antenna beamwidth can achieve~\citep{wiley1985synthetic}. 
Since then, the technology has found a multitude of applications in the scientific, military, and civilian communities alike. Due to the numerous uses, SAR technology has been a topic of constant
research and development.

\subsection{Remote Sensors}
Remote sensors remotely collect data by measuring the electromagnetic (EM) radiation at specific spectral ranges (usually called bands). 
When they are deployed on satellites or mounted on aircraft, they are called spaceborne and airborne remote sensors, respectively.
 Spaceborne remote sensors orbit the Earth at heights of 500 to 800 km~\citep{everaerts2005pegasus}, providing data in a wide range of ground resolutions, and at various polarizations and radar bands.

There are two types of remote sensors acquiring information in fundamentally different ways.
Optical sensors are passive imaging devices, which means they take advantage of existing sources of illumination and the natural reflective properties of objects to form
images. 
In the case of optical Earth observation imagery, the sun is used as a global illumination source. 
Thus optical image sensors tend to operate on a sun-synchronous orbit to ensure the scene is well illuminated during acquisition. 
On the other hand, SAR uses the principle of active sensing, whereby the sensor acts as both an illumination source as well as the acquisition unit. 
A scene is thus imaged by alternating between emitting bursts of EM-radiation and measuring the strength and time delay of the reflected signal. 
The proportion of the signal which is reflected towards the sensor by an object is known as \textit{backscatter}.
\subsection{The Electromagnetic Spectrum}
Given that objects interact (reflect and absorb) different parts of the EM-spectrum in a unique manner, several realizations of optical and SAR sensors exist, each designed for
a specific purpose and to take advantage of the properties observable within a particular part of the EM-spectrum.
Optical sensors detect very high-frequency radiation within the visible to thermal infrared section of the EM-spectrum.
In contrast, SAR sensors operate at much lower frequencies within the microwave section of the spectrum.
It is this use of lower frequencies which allow SAR sensors to be mostly independent of atmospheric conditions.
The same, however, is not true for optical sensors which require clear atmospheric conditions to observe ground level reflections within the visible light and near-infrared spectrum.

In large, optical sensors can be classified, by the number of spectral bands which they image, into hyperspectral, multispectral, and panchromatic sensors. 
Whereby hyperspectral sensors image the full optical subsection of the EM-spectrum into hundreds of narrow spectral bands, while panchromatic sensors image the visible light spectrum using a single, wide spectral band~\citep{Sara2021}.
Similarly, SAR sensors can also be classified based on their operational bandwidth into C, L and X-band, with L-band being the lowest frequency and thus the highest level of vegetation and soil penetration.
However, due to the relationship between wave-length and spatial resolution present in SAR imagery~\citep{cumming2005digital}, X-band imagery exhibits the highest spatial resolution and thus provides the detailed information about surface structure. 
In optical imagery, a similar trade-off exists, except it is between spatial resolution and spectral resolution. 
Due to data storage and throughput constraints hyperspectral and multispectral images tend to have a lower resolution than panchromatic imagery.

The operational frequency and bandwidth of each of these sensors within the EM-spectrum is further described by Figure~\ref{fig:EM-spectrum}.
%%% The source is in ../../Images/PNG/EM-spectrum.PNG
	\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{../../Images/PNG/sensor.png}
    %\decoRule
    \caption[Spectral regions of sensors within the electromagnetic spectrum.]{Spectral regions of optical sensors and radar sensors within the electromagnetic spectrum,~\citep{zhang2022synthetic}.}
    \label{fig:EM-spectrum}
\end{figure}
SAR sensors provide radar images of the Earth’s surface, which are chosen in this work.
Table~\ref{tab:bands} contains the band with the associated frequency and wavelength. 
The wavelength range is very important, since it determines the interaction between radar signals and surfaces, as well as the penetration depth of the microwave
signals.

\setlength{\tabcolsep}{6.0pt}
\begin{table}[!htb]
\caption[Different bands in microwave remote sensing]{\label{tab:bands}Different bands in microwave remote sensing,~\citep{Moreira2013}.}
\centering
\begin{tabular}[t]{cccccc}
\toprule
 \textbf{Band} & \multicolumn{1}{c}{\textbf{Frequency} $\left[\text{GHz}\right]$} & \multicolumn{1}{c}{\textbf{Wavelength} $\left[\text{cm}\right]$} \\
\midrule
Ka & $\,25$--$40$ & $\phantom{-}0.75$--$1.2$ \\
Ku & $\,12$--$17.6$ & $\phantom{-}\,1.7$--$2.5$ \\
X  & $7.5$--$12$  & $2.5$--$4$   \\
C  & $ 3.75$--$7.5$ & $\phantom{-}4$--$8$   \\
S  & $2$--$3.75$   & $\phantom{-}\,8$--$15$    \\
L  & $1$--$2$   & $\phantom{-}15$--$30$   \\
P  & $0.3$--$1$ & $\phantom{-}\,30$--$100$  \\
\bottomrule
\end{tabular}
\end{table}
Table~\ref{tab:spacebornes} gives some examples of commonly used spaceborne SAR sensors, currently in operation. 
These include Radarsat-2 from the Canadian Space Agency (CSA), TerraSAR-X from the German Aerospace Center (DLR), ALOS PALSAR-2 from the Japan Aerospace Exploration Agency (JAXA), and Sentinel-1A/1B from the European Space Agency (ESA) (see Figure~\ref{fig:Sentinel-1}), as well as Gaofen-3 from the China National Space Administration (CNSA).
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{../../Images/PNG/ESA_radar.png}
    %\decoRule
    \caption[Sentinel-1 radar.]{Sentinel-1 radar, (source \href{https://www.esa.int/Applications/Observing_the_Earth/Copernicus/Sentinel-1/Changing_lands}{ESA}).}
    \label{fig:Sentinel-1}
\end{figure}

\setlength{\tabcolsep}{3.0pt}
\begin{table}[!htb]
\caption[List of operational typical spaceborne SAR systems]{\label{tab:spacebornes}List of operational typical spaceborne SAR systems.}
\centering
\setlength{\extrarowheight}{3.0pt} % 
\begin{tabular}[t]{lclccccc}
\toprule
\textbf{Mission/SAR} & \textbf{Agency} & \textbf{Launch} & \textbf{Band} & \textbf{Resolution} $\left[\text{m}\right]$ & \textbf{Coverage} $\left[\text{km}\right]$ & \textbf{Revisit} $\left[\text{days}\right]$ \\
\midrule
Radarsat-2 & CSA & 2007 & C & 9--100 & 18--500 & 24 \\
TerraSAR-X & DLR & 2007 & X & 0.25--40 & 10--150 & 11 \\
ALOS PALSAR-2 & JAXA & 2014 & L & 1--100 & 25--490 & 14 \\
Sentinel 1A/1B & ESA & 2014/2016 & C & 5--100 & 80--400 & 12 \\
Gaofen-3 & CNSA & 2016 & C & 1--500 & 10--650 & 29 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Scattering Mechanisms}
A SAR sensor measures the electromagnetic energy that is backscattered from the targets. 
There are lots of factors that can affect the radar backscatter, and they can be divided into two categories.

The first category relates to the SAR parameters, such as the frequency, polarization, and incident angle. If the frequency and
polarization parameters are fixed, the increasing incident angle causes the decreasing backscatter intensity from a homogeneous surface. 
Therefore, the intensity decreases gradually on SAR images from near range to far range. This effect must be taken into consideration during SAR image
interpretation.

The second category relates to the surface parameters, such as the surface roughness, the surface geometry, and the dielectric constant of the
surface. There are three basic groups of scattering mechanisms that can contribute to the returned signal: surface scattering, volume scattering, and hard target scattering.

\subsection{Electromagnetic Polarization}
An electromagnetic wave consists of a magnetic and an electric field.
These two fields are perpendicular to each other and also to the direction of wave propagation.

Apart from frequency, amplitude, and phase, an electromagnetic wave also contains polarization information.
Polarization is defined as the orientation of the oscillating electric field, which can be described in terms of two orthogonal basis vectors.
Electromagnetic waves are generally elliptically polarized, with linear or circular polarization as special cases.

Most of the SAR sensors use linear polarization on both the transmitter and the receiver. 
There are four linear polarization configurations in total:
\begin{itemize}
	\item HH (co-polarization): horizontal transmission and horizontal reception.
	\item HV (cross-polarization): horizontal transmission and vertical reception.
	\item VH (cross-polarization): vertical transmission and horizontal reception.
	\item VV (co-polarization): vertical transmission and vertical reception.
\end{itemize}
Historical SAR satellites carried single-polarized sensors, which support only one linear polarization. More recent sensors provide either dual-polarization
or quad-polarization capabilities. 
For quad-polarization SAR systems, they can transmit H- and V-polarized waveforms and receive both H and V simultaneously.

%An example of polarization is shown in Figure~\ref{}, where three intensity-format C-Band images of a region in Flevoland are observed, with VV and HV polarizations composited into an RGB image.
%An example of polarizations is shown in Figure~\ref{fig:pol}, from Sentinel-1 radar images in C-Band and intensity format of a region in Flevoland.
 Figure~\ref{fig:pol} \ref{fig:1a}--\ref{fig:2a} shows VH and VV polarization from Sentinel-1 radar images in C-Band of a region of Flevoland.
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=.8\textwidth]{../../Images/PNG/Amplitude_VH.png}
    \caption{Cross-polarization (VH)}
    \label{fig:1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=.8\textwidth]{../../Images/PNG/Intensity_VV.png}
    \caption{Co-polarization (VV) }
    \label{fig:2a}
  \end{subfigure}
  %\hfill
  %\begin{subfigure}[b]{0.3\textwidth}
    %\centering
    %\includegraphics[width=\textwidth]{example-image-c}
    %\caption{}
    %\label{fig: Third figure}
  %\end{subfigure}
  \caption{Polarization in radar systems}
  \label{fig:pol}
\end{figure}

\section{SAR Image Acquisition}
SAR sensors utilize a single antenna to emit EM-signals and measure the corresponding magnitude, range and Doppler-shift of these signals in the
backscatter. 
As only a single detector element exists, SAR is based around the concept of synthesizing an aperture in the azimuth direction in order to form a 2-dimensional
image~\citep{Orth2018}. The angle between the SAR antenna and an object on the ground is known as the incidence angle, $\theta$, and it plays a large role in the geometric distortions which are
present in SAR imagery. Due to this imaging concept, the SAR image is formed along the slant range, where each pixel represents the accumulation of backscatter from points which are the same distance away from the sensor~\citep{cumming2005digital}. The acquisition geometry of  SAR sensors is depicted in Figure~\ref{fig:Sentinel-1}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{../../Images/PNG/image_adquisition.png}
    %\decoRule
    \caption[Sentinel-1 radar.]{SAR image acquisition geometry,~\citep{hughes2020deep}.}
    \label{fig:Sentinel-1}
\end{figure}

\subsection{SAR resolution}
The resolution of the SAR image is one of the most important characteristics of the SAR system. 
SAR data pixels are characterized by spatial and temporal resolutions. Spatial resolution is defined as the ability of the SAR system to distinguish between two closely targets.
In SAR systems, there are two resolutions, azimuth resolution, and range resolution. 
Another resolution that should be taken into account when applying a multi-temporal time series analysis of the SAR data is the temporal resolution. 
It is determined by the revisit time of the SAR sensor at the same imaged area.

\subsection{Speckle Noise}

The interference of waves reflected during the acquisition process of SAR  images give rise to a multiplicative and non-Gaussian noise that characterizes them
and is known as speckle noise~\citep{oliver2004understanding}.
Since many elemental scatterers are located in one resolution cell, the final scattering response from the resolution cell is the coherent sum of thousands of individual scattering events.
The mutual interference results in a certain fluctuation in the amplitude and phase of the synthesized EM wave vectors, which make the “salt-and-pepper” noise  appear. 
%In the actual SAR images, speckle noise exists in the form of a multiplicative noise, which is manifested in the image as a drastic change in the image intensity.

%The interpretation of the SAR image is challenging due to the geometrical properties of the SAR imaging system and
%to the presence of speckle. Indeed, speckle is a multiplicative noise produced by interference among the backscatterings of
%the objects inside a resolution cell of the sensor~\citep{Argenti2013}.

The statistical distribution of the speckle is well known under certain conditions. Three main cases can be considered:
homogeneous, heterogeneous, and extremely heterogeneous areas. Homogeneous areas (such as fields, pasture, water bodies, etc)
are characterized by the lack of dominant scatterers, and the surface  can be considered stationary. This is the case of the
\textit{fully developed hypothesis for the speckle}~\citep{Frery1997}.

In Figure~\ref{fig:speckle}, SAR images depict speckle, a characteristic of SAR data due to its coherent imaging process. 
The images distinguishes between fully developed speckle in homogeneous regions (Figure~\ref{fig:speckle} \ref{fig:s1}) and heterogeneous clutter in regions such as urban areas (Figure~\ref{fig:speckle} \ref{fig:s2}).
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.48\textwidth}
    \centering
    \includegraphics[width=.8\textwidth]{../../Images/PNG/Intensity_MG.png}
    \caption{Fully developed speckle (Homogeneous areas)}
    \label{fig:s1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{../../Images/PNG/urban_intensity.png}
    \caption{Heterogeneous clutter }
    \label{fig:s2}
  \end{subfigure}
  %\hfill
  %\begin{subfigure}[b]{0.3\textwidth}
    %\centering
    %\includegraphics[width=\textwidth]{example-image-c}
    %\caption{}
    %\label{fig: Third figure}
  %\end{subfigure}
  \caption{SAR image with speckle noise}
  \label{fig:speckle}
\end{figure}

\section{Dataset}
\subsection{Sentinel-1 SAR data processing}
The Sentinel-1 images were obtained from the Alaska Satellite Facility's (ASF) at \url{https://search.asf.alaska.edu/#/} and by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/}.

The downloaded SAR images were pre-processed using the Sentinel Application Platform (SNAP) Toolbox developed by ESA.

%The following images describe the preprocessing steps applied to the SAR data: 
The following steps were applied to the SAR data during pre-processing:

\begin{enumerate}
    \item Importing the SAR image into SNAP.
    \item Creating a subset to focus on the area of interest.
    \item Performing Geometric Correction, which includes Range Doppler Terrain Correction.
    \item Exporting the processed data in ENVI format for further analysis.
\end{enumerate}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/alaska1.png}
    %\decoRule
    \caption[Selection of area of interest]{Selection of area of interest.}
    \label{fig:alaska-area}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{../../Images/PNG/snap_1.png}
    %\decoRule
    \caption[SAR Images pre-processing  in the SNAP]{SAR Images pre-processing  in the SNAP.}
    \label{fig:alaska-area2}
\end{figure}

%\subsection*{Example math equations}
%-----------------------------------------------------------
%\begin{align*}
%L(\alpha,  \lambda|  \bm{x})&=\prod_{i=1}^n{f(x_i|\alpha, \lambda )}\\
                                 %&= \prod_{i=1}^n\left[\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\,x_i^{\alpha-1}\exp\left\{-\lambda x_i\right\}\right]\\
%&=\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}
%\end{align*}
%%----------------------------------------------------------
%In Figure \ref{fig:undercatch}, in Eq, \eqref{eq:em}.
%\begin{align}
%\label{eq:em}
%\ell(\alpha, \lambda| \bm{x}) &=\log\left[\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}\right]\nonumber\\
%&=\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n+\log\left[\prod_{i=1}^nx_i^{\alpha-1}\right]-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)+(\alpha-1)\log\prod_{i=1}^nx_i-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\log(\lambda^{\alpha})-n\log(\Gamma(\alpha))+(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i\nonumber\\
%&=n\alpha\log \lambda -n\log(\Gamma(\alpha)) +(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i.
	%\end{align}
%----------------------------------------------------------

%-------------------------------------------------------

%\begin{table}[h]
%\centering
%\caption{\label{tab1}Comparação de tempos. }
%\begin{tabular}{l c c }
%\toprule[1pt] \textbf{Amostra (N)} \ \ \  \ \ \  & \textbf{Tempo de Execução (C)}\ \ \ \ \ \ \  &\textbf{Tempo de Execução (Ox)} \\\midrule[0.5pt]
%$20$ & 7.6810 s  &  5.01 s \\
%$30$ & 9.6260 s     & 5.34 s \\
%$50$ &  10.0310 s & 5.99 s \\
%$100$ & 15.5420 s & 8.07 s \\
%$200$ & 20.5860 s & 9.64 s \\
%$500$ & 29.0890  s & 15.12 s \\
%\bottomrule[1pt]
%\end{tabular}
%\caption[Precipitation datasets]{List of datasets used in the analysis of daily precipitation uncertainty carried over i}\label{tab:1}
%\end{table}
%------------------------------------------------------

%\begin{table}[]
%\centering
%\begin{tabular}{@{}llll@{}}
%\toprule
%Dataset name & Period & Spatial res. & Data source \\ \midrule
%E-OBS        & 2000--2016 & \ang{0.25}                            & Station data \\
%EURO4M-APGD  & 2000--2008 & \SI{5}{\kilo\metre}                   & Station data \\
%HMR          & 2000--2013 & \SI{5.5}{\kilo\metre}                 & Reanalysis \\
%ARCIS        & 2000--2015 & \textasciitilde{} \SI{5}{\kilo\metre} & Station data \\
%CHIRPS       & 2000--2016 & \ang{0.05}                            & Station data + satellite \\
%CPC          & 2000--2016 & \ang{0.5}                             & Station data \\
%CMORPH       & 2000--2016 & \ang{0.25}                            & Satellite \\
%PERSIANN-CDR & 2000--2016 & \ang{0.25}                            & Satellite \\ \bottomrule
%\end{tabular}
%\caption[ Italy]{List of datasets used in the analysis of daily precipitation uncertainty  references.}\label{tab:2}
%\end{table}

### 2024-05-07 Text/Thesis/chapters/3_methods.tex
doctoral qualification document

\chapter{Methodology} \label{chp:methods}

\section{Statistical Modeling of Intensity SAR
data}\label{statistical-modeling-of-intensity-sar-data}

The primary models for intensity SAR data include the Gamma and
\(\mathcal{G}_I^0\) distributions~\citep{Frery1997}. The first is
suitable for fully developed speckle and is a limiting case of the
second model. This is interesting due to its versatility in accurately
representing regions with different roughness
properties~\citep{Cassetti2022}. We denote
\(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) and
\(Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)\) to indicate that \(Z\)
follows the distributions characterized by the respective probability
density functions (pdfs): \begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where \(\mu > 0\) is the mean, \(\gamma > 0\) is the scale,
\(\alpha < 0\) measures the roughness, \(L \geq 1\) is the number of
looks, \(\Gamma(\cdot)\) is the gamma function, and
\(\mathbbm 1_{A}(z)\) is the indicator function of the set \(A\).

The \(r\)th order moments of the \(\mathcal{G}_I^0\) model are
\begin{equation}
E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation} provided \(\alpha <-r\), and infinite otherwise.
Therefore, assuming \(\alpha<-1\), its expected value is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

Although the \(\mathcal{G}_I^0\) distribution is defined by the
parameters \(\alpha\) and \(\gamma\), in the SAR
literature~\citep{Nascimento2010} the texture \(\alpha\) and the mean
\(\mu\) are usually used. 
Reparametrizing~\eqref{E:gi01} with \(\mu\),
and denoting this model as \(G_I^0\) we obtain: 
\begin{equation}
        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

\section{The Shannon Entropy}\label{the-shannon-entropy}

The parametric representation of Shannon entropy for a system described
by a continuous random variable is: \begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation} here, \(f(\cdot)\) is the pdf that characterizes the
distribution of the real-valued random variable \(Z\).

Using~\eqref{E:entropy2}, we obtain the Shannon entropy of \(\Gamma_{\text{SAR}}\) in~\eqref{E:gamma1} and \(G_I^0\) in~\eqref{E:gi02}:
\begin{equation}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{equation}
 %\begin{multline}
%\label{E:E-GIO}
%H_{\mathcal{G}_I^0}(\mu, \alpha, L) =\underbrace{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} \\
%- \underbrace{\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L}_{\phi(\alpha)},
%\end{multline} 
\begin{multline}
\label{E:E-GIO}
H_{G_I^0}(\mu, \alpha, L) =\underbrace{L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} -\ln\Gamma(L-\alpha)\\
+ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L,
\end{multline}
where \(\psi^{(0)}(\cdot)\) is the digamma function.

Figure~\ref{fig:all_H} \ref{fig:H1} shows the theoretical entropy $H_{\Gamma_{\text{SAR}}}(L, \mu)$ as a function of $\mu$ for different values of $L$, while Figure~\ref{fig:all_H} \ref{fig:H2} shows the theoretical entropy $H_{G_I^0}(\mu, \alpha, L)$ as a function of both $\mu$ and $\alpha$, likewise considering varying $L$. 
\begin{figure}[htb]
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \includegraphics[width=1.5\textwidth]{../../Figures/PDF/PlotGammaSAR-1}
    \caption{The Shannon Entropy of $\Gamma_{\text{SAR}}$.}
    \label{fig:H1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.6\textwidth}
    \centering
    \includegraphics[width=12cm, height=7cm]{../../Figures/PDF/3d_lab}
    \caption{The Shannon Entropy of $G_I^0$.}
    \label{fig:H2}
  \end{subfigure}
  \caption{Theoretical entropies for $\Gamma_{\text{SAR}}$ and $G_I^0$ distributions.}
  \label{fig:all_H}
\end{figure}
We see that the entropy of a random variable following the $\Gamma_{\text{SAR}}$ model depends on the logarithm of the mean $\mu$.  
From the 3D plot, we observe how variations in $\mu$, $\alpha$, and $L$ collectively affect the entropy of the $G_I^0$ distribution, allowing  the identification of regions of high or low entropy.

Additionally, the expression~\eqref{E:E-GIO} can be written as: $H_{G_I^0}(\mu, \alpha, L)=H_{\Gamma_{\text{SAR}}}+\phi(\alpha, L)$. Thus, for $L\geq1$ known, and as \(\alpha\to-\infty\) we have that $H_{G_I^0}\approx H_{\Gamma_{\text{SAR}}}$. 
Figure~\ref{fig:Plot_GI0_to_gamma1}, shows the behavior of the entropy
of \(G_I^0\) as a function of $\mu$ when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\) and $L=8$,
where the approximation to the entropy of \(\Gamma_{\text{SAR}}\) can be
observed when \(\alpha\) assumes large negative values. In an
interpretative sense, we can conclude that the more heterogeneous (high
values of \(\alpha\)) the SAR region is, the higher the value of entropy
(or degree of disorder). It is worth noting that this conclusion
confirms what is written in the SAR literature.

\begin{figure}[htb]

{\centering \includegraphics[width=0.7\linewidth]{../../Figures/PDF/Plot_GI0_to_gamma1-1}

}

\caption{$H_{ G_I^0}$ converges to the $H_{\Gamma_{\text{SAR}}}$ when $\alpha\to-\infty$, with $L=8$.}\label{fig:Plot_GI0_to_gamma1}
\end{figure}

\subsection{Estimation of the Shannon
Entropy}\label{estimation-of-the-shannon-entropy}

The problem of the non-parametric estimation of \(H(Z)\) has been
studied by many authors,
including~\citep{vasicek1976test,correa1995new,Wieczorkowski1999,Yee2015,AlOmari2019}.
Their proposals use estimators based on differences between order
statistics: spacings.

\citet{vasicek1976test} introduced one of the first
non-parametric estimators based on spacings. Under the assumption that
\(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from the
distribution \(F(z)\), the estimator is defined as: \begin{equation}
\label{E:Vas}
    \widehat{H}_{\text{V}}(\bm{Z})=\frac{1}{n}\sum_{i=1}^{n}\ln\left[\frac{n}{2m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
    \end{equation} where \(m<n/2\) is a positive integer,
\(Z_{(1)}\leq Z_{(2)}\leq\dots\leq Z_{(n)}\) are the order statistics,
and \(Z_{(i+m)}-Z_{(i-m)}\) is the \(m\)-spacing, in which
\(Z_{(i)}= Z_{(1)}\) if \(i<1\), \(Z_{(i)}= Z_{(n)}\) if \(i>n\).

Several authors have explored adaptations  to Vasicek's estimator. We consider the following entropy estimators variants, as discussed by~\citep{AlOmari2016,Cassetti2022}.

\citet{Bert1992} proposed a new estimator of entropy given by:
 \begin{equation}
\label{E:VanEs}
	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
\end{equation}
Under some conditions, Van Es proved asymptotic normality of this estimator.

\citet{Ebrahimi1994} adjusted the weights of Vasicek's estimator, in order to take into account the fact that the differences are truncated around the smallest and the largest data points.
 Specifically, $Z_{(i+m)}-Z_{(i-m)}$ is substituted with  $Z_{(i+m)}-Z_{(1)}$ when $i \leq m$ and $Z_{(i+m)}-Z_{(i-m)}$ is replaced by $Z_{(n)}-Z_{(i-m)}$ when $i \geq n-m+1$. Their estimator is given by:
  \begin{equation}
	\label{E:Ebrahimi}
  \widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
  \end{equation} where \[
  c_i=\begin{cases}1+(i-1) / m & \text { if } \quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m,\\ 1+(n-i) / m & \text { if }\quad n-m+1 \leq i \leq n.\end{cases}
  \]

 \citet{correa1995new} suggested another modification of Vasicek's estimator. 
In estimation the density $f$ of $F$ in the interval $\left(Z_{(i-m)}, Z_{(i+m)}\right)$ he used a local linear model based on $2 m+1$ points: $F\left(Z_{(j)}\right)=a+b Z_{(j)}+\varepsilon, j=m-i, \ldots, m+i$. This yields a following estimator:
  \begin{equation}
	\label{E:Correa}
  \widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \log \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\overline{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\overline{Z}_{(i)}\right)^2},
  \end{equation} where
  \(\widebar{Z}_{(i)}=(2 m+1)^{-1} \sum_{j=i-m}^{i+m} Z_{(j)}\),
  \(m< \frac{n}{2}\), \(Z_{(i)}=Z_{(1)}\) for \(i<1\) and
  \(Z_{(i)}=Z_{(n)}\) for \(i>n\). Based on simulations, he showed that
  his estimator has a smaller mean square error than Vasicek's approach.

\citet{rohtua} modify the coefficients of~\eqref{E:Ebrahimi} as: 
\begin{equation}
\label{E:NA}
\widehat{H}_{\text{NA}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{a_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
\end{equation}
where
$$
a_i=\begin{cases}
1 & \text { if } \quad 1 \leq i \leq m, \\
2 & \text { if } \quad m+1 \leq i \leq n-m, \\
1 & \text { if } \quad n-m+1 \leq i \leq n,
\end{cases}
$$
and $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$ and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.

\citet{IbrahimAlOmari2014} suggested the following estimator:
	\begin{equation}
\label{E:AO}
  \widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 \end{equation}
	where \[
  \omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
  \] in which \(Z_{(i-m)}=Z_{(1)}\) for \(i \leq m\), and
  \(Z_{(i+m)}=Z_{(n)}\) for \(i \geq n-m\).

These estimators are asymptotically consistent, i.e., they converge in
probability to the true value when \(m,n\rightarrow\infty\) and
\(m/n\rightarrow0\).

Our experimental setup involves an analysis of bias and mean squared error (MSE) for each estimator with a Monte Carlo
study, using \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of size
\(n\in\left\{9, 25, 49, 81, 121\right\}\), with
\(\mu\in\left\{1, 10, 50, 100\right\}\) and \(L=5\). 
The results are consistent with other situations. We use the
heuristic spacing \(m=\left[\sqrt{n}+0.5\right]\), as recommended in the
literature.
Figure~\ref{fig:Plot_bias_mse_gi0_new_L5}  presents the bias and MSE for each of the non-parametric entropy estimators.  The results are summarized  in Table~\ref{tab:tableL5}.
%\begin{figure}[H]
%{\centering \includegraphics[width=1\linewidth]{../../Figures/PDF/Plot_bias_mse_gi0_new_L2-1} 
%
%}
%\caption{Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=2$.}\label{fig:Plot_bias_mse_gi0_new_L2}
%\end{figure}
\begin{figure}[htb]
{\centering \includegraphics[width=1\linewidth]{../../Figures/PDF/Plot_bias_mse_gi0_new_L5-1}

}
\caption{Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=5$.}\label{fig:Plot_bias_mse_gi0_new_L5}
\end{figure}

\setlength{\tabcolsep}{6pt}
\begin{table}[htb]
\centering
\caption{\label{tab:tableL5}Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=5$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{crllllllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Bias} & \multicolumn{6}{c}{MSE} \\
\cmidrule(l{3pt}r{3pt}){3-8} \cmidrule(l{3pt}r{3pt}){9-14}
\multicolumn{1}{r}{$\bm{\mu}$} & \multicolumn{1}{r}{$\bm{n}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{V}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{VE}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{N}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{AO}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{V}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{VE}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{N}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{AO}}}$}\\
\midrule
 & $9$ & $-0.632$ & $-0.218$ & $-0.280$ & $-0.210$ & $-0.016$ & $-0.377$ & $\phantom{-}0.494$ & $\phantom{-}0.147$ & $\phantom{-}0.173$ & $\phantom{-}0.140$ & $\phantom{-}0.094$ & $\phantom{-}0.236$\\

 & $25$ & $-0.298$ & $-0.220$ & $-0.123$ & $-0.079$ & $\phantom{-}0.034$ & $-0.160$ & $\phantom{-}0.117$ & $\phantom{-}0.076$ & $\phantom{-}0.044$ & $\phantom{-}0.036$ & $\phantom{-}0.030$ & $\phantom{-}0.054$\\

 & $49$ & $-0.173$ & $-0.189$ & $-0.058$ & $-0.033$ & $\phantom{-}0.054$ & $-0.079$ & $\phantom{-}0.044$ & $\phantom{-}0.050$ & $\phantom{-}0.017$ & $\phantom{-}0.015$ & $\phantom{-}0.017$ & $\phantom{-}0.020$\\

 & $81$ & $-0.112$ & $-0.162$ & $-0.028$ & $-0.011$ & $\phantom{-}0.059$ & $-0.041$ & $\phantom{-}0.021$ & $\phantom{-}0.035$ & $\phantom{-}0.009$ & $\phantom{-}0.008$ & $\phantom{-}0.012$ & $\phantom{-}0.010$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 1} & $121$ & $-0.076$ & $-0.146$ & $-0.009$ & $\phantom{-}0.001$ & $\phantom{-}0.061$ & $-0.019$ & $\phantom{-}0.011$ & $\phantom{-}0.027$ & $\phantom{-}0.005$ & $\phantom{-}0.005$ & $\phantom{-}0.009$ & $\phantom{-}0.006$\\
\cmidrule{1-14}
 & $9$ & $-0.633$ & $-0.228$ & $-0.280$ & $-0.211$ & $-0.016$ & $-0.377$ & $\phantom{-}0.494$ & $\phantom{-}0.157$ & $\phantom{-}0.173$ & $\phantom{-}0.140$ & $\phantom{-}0.094$ & $\phantom{-}0.236$\\

 & $25$ & $-0.292$ & $-0.221$ & $-0.117$ & $-0.075$ & $\phantom{-}0.041$ & $-0.154$ & $\phantom{-}0.112$ & $\phantom{-}0.076$ & $\phantom{-}0.040$ & $\phantom{-}0.032$ & $\phantom{-}0.028$ & $\phantom{-}0.050$\\

 & $49$ & $-0.174$ & $-0.188$ & $-0.060$ & $-0.034$ & $\phantom{-}0.052$ & $-0.080$ & $\phantom{-}0.045$ & $\phantom{-}0.049$ & $\phantom{-}0.018$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.021$\\

 & $81$ & $-0.113$ & $-0.168$ & $-0.029$ & $-0.011$ & $\phantom{-}0.058$ & $-0.042$ & $\phantom{-}0.021$ & $\phantom{-}0.036$ & $\phantom{-}0.009$ & $\phantom{-}0.008$ & $\phantom{-}0.011$ & $\phantom{-}0.009$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 10} & $121$ & $-0.075$ & $-0.143$ & $-0.008$ & $\phantom{-}0.003$ & $\phantom{-}0.063$ & $-0.018$ & $\phantom{-}0.011$ & $\phantom{-}0.026$ & $\phantom{-}0.006$ & $\phantom{-}0.005$ & $\phantom{-}0.009$ & $\phantom{-}0.006$\\
\cmidrule{1-14}
 & $9$ & $-0.659$ & $-0.244$ & $-0.307$ & $-0.236$ & $-0.043$ & $-0.403$ & $\phantom{-}0.528$ & $\phantom{-}0.164$ & $\phantom{-}0.188$ & $\phantom{-}0.152$ & $\phantom{-}0.096$ & $\phantom{-}0.256$\\

 & $25$ & $-0.284$ & $-0.201$ & $-0.108$ & $-0.068$ & $\phantom{-}0.049$ & $-0.146$ & $\phantom{-}0.114$ & $\phantom{-}0.073$ & $\phantom{-}0.045$ & $\phantom{-}0.038$ & $\phantom{-}0.036$ & $\phantom{-}0.055$\\

 & $49$ & $-0.178$ & $-0.194$ & $-0.063$ & $-0.036$ & $\phantom{-}0.049$ & $-0.084$ & $\phantom{-}0.046$ & $\phantom{-}0.053$ & $\phantom{-}0.019$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.022$\\

 & $81$ & $-0.106$ & $-0.159$ & $-0.022$ & $-0.006$ & $\phantom{-}0.065$ & $-0.035$ & $\phantom{-}0.018$ & $\phantom{-}0.033$ & $\phantom{-}0.008$ & $\phantom{-}0.007$ & $\phantom{-}0.011$ & $\phantom{-}0.008$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 50} & $121$ & $-0.083$ & $-0.152$ & $-0.016$ & $-0.004$ & $\phantom{-}0.054$ & $-0.026$ & $\phantom{-}0.012$ & $\phantom{-}0.029$ & $\phantom{-}0.006$ & $\phantom{-}0.005$ & $\phantom{-}0.008$ & $\phantom{-}0.006$\\
\cmidrule{1-14}
 & $9$ & $-0.647$ & $-0.249$ & $-0.295$ & $-0.232$ & $-0.031$ & $-0.391$ & $\phantom{-}0.505$ & $\phantom{-}0.163$ & $\phantom{-}0.173$ & $\phantom{-}0.141$ & $\phantom{-}0.087$ & $\phantom{-}0.239$\\

 & $25$ & $-0.303$ & $-0.226$ & $-0.127$ & $-0.088$ & $\phantom{-}0.030$ & $-0.165$ & $\phantom{-}0.123$ & $\phantom{-}0.081$ & $\phantom{-}0.047$ & $\phantom{-}0.039$ & $\phantom{-}0.032$ & $\phantom{-}0.058$\\

 & $49$ & $-0.176$ & $-0.191$ & $-0.061$ & $-0.035$ & $\phantom{-}0.050$ & $-0.082$ & $\phantom{-}0.045$ & $\phantom{-}0.051$ & $\phantom{-}0.018$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.021$\\

 & $81$ & $-0.111$ & $-0.160$ & $-0.027$ & $-0.009$ & $\phantom{-}0.060$ & $-0.040$ & $\phantom{-}0.020$ & $\phantom{-}0.034$ & $\phantom{-}0.008$ & $\phantom{-}0.008$ & $\phantom{-}0.011$ & $\phantom{-}0.009$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 100} & $121$ & $-0.083$ & $-0.152$ & $-0.017$ & $-0.006$ & $\phantom{-}0.054$ & $-0.026$ & $\phantom{-}0.013$ & $\phantom{-}0.029$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.009$ & $\phantom{-}0.006$\\
\bottomrule
\end{tabular}}
\end{table}
As shown in the simulation results, the estimators \(\widehat{H}_{\text{C}}\), \(\widehat{H}_{\text{E}}\), and \(\widehat{H}_{\text{AO}}\) show low bias and achieve convergence for samples size larger than 81. These estimators exhibit good behavior in terms of bias and MSE across various parameter combinations.

In contrast, estimator \(\widehat{H}_{\text{N}}\) displays the lowest MSE across all scenarios. However,  the bias remains unchanged and high for sample sizes larger than 25, indicating that the convergence
is not very fast. Additionally, we observe that both \(\widehat{H}_{\text{V}}\) and \(\widehat{H}_{\text{VE}}\) estimators exhibit larger bias and slower convergence compared to their counterparts.  Notably, the \(\widehat{H}_{\text{V}}\) estimator shows the highest MSE.

%We will use improved bootstrap-improved versions because we need them to perform well with small samples.

\subsection{Enhanced estimators with Bootstrap}\label{enhanced-estimators-with-bootstrap}

We extend our exploration of non-parametric entropy estimators by incorporating  bootstrap methodologies, because we need them to perform well with small samples. 
The integration of bootstrap techniques aims to refine the accuracy of non-parametric entropy estimators.

Bootstrap is essentially a resampling algorithm introduced by \citep{Efron1979}. 
It offers a simulation-based approach for estimating various statistics of interest for a random variable.
It can be used in both parametric and nonparametric settings. 
The main idea  consists of creating new datasets from an existing one by resampling with repetition~\citep{Michelucci2021}.

Let us assume that the non-parametric entropy estimator
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, where \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) is a random sample from a
distribution \(\mathcal{D}\), i.e,:\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = \mathbb{E}\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation}

Our objective is to devise a unbiased estimator. To achieve this, we introduce an "ideal estimator" \(\widecheck{\theta}(\bm{Z})\) using the bias information from~\eqref{Eq:bias1}:
\begin{align}
\label{Eq:bias2}
\widecheck{\theta}(\bm{Z}) &= \widehat{\theta}(\bm{Z}) - \bias\left(\widehat{\theta}(\bm{Z})\right),\nonumber\\
&=\widehat{\theta}(\bm{Z})-\left[\mathbb{E}\big[\widehat{\theta}(\bm{Z})\big] - \theta\right],\nonumber\\
&=\widehat{\theta}(\bm{Z})+\theta-\mathbb{E}\big[\widehat{\theta}(\bm{Z})\big].
\end{align}
However, \(\widecheck{\theta}(\bm{Z})\) is not yet an estimator, because it depend on the true parameter, but \(\theta\) can be calculated using a non-parametric approach, and the average of individual estimators can be obtained using the bootstrap technique. This leads to the formulation of a new unbiased estimator, denoted as \(\widetilde{H}\), from ~\eqref{Eq:bias2} we have:
\begin{align}
\label{Eq:bias3}
\widetilde{H}%&= \widehat{\theta}(\bm{Z})+\widehat{\theta}(\bm{Z})- \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),\nonumber\\
= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align} where \(B\) the number of bootstrap replications. For each iteration \(b\) (from \(1\) to \(B\)), a sample \(\bm{Z}^{(b)}\) is generated, and the corresponding bootstrap estimator \(\widehat{\theta}_b(\bm{Z}^{(b)})\) is calculated. 
This methodology significantly reduces bias, resulting in more accurate and robust entropy estimations. The original estimators of Vasicek~\eqref{E:Vas}, Van Es~\eqref{E:VanEs}, Ebrahimi~\eqref{E:Ebrahimi}, Correa~\eqref{E:Correa}, Noughabi~\eqref{E:NA}, and Al-Omari~\eqref{E:AO}  are now referred to as the proposed bootstrap-improved versions:
\(\widetilde{H}_{\text{V}}\),
\(\widetilde{H}_{\text{VE}}\), 
\(\widetilde{H}_{\text{E}}\),
\(\widetilde{H}_{\text{C}}\),
\(\widetilde{H}_{\text{NA}}\), and 
\(\widetilde{H}_{\text{AO}}\),
respectively.

In order to assess the effectiveness of the bootstrap technique, we present comparisons of the bias and MSE between each original non-parametric entropy estimator and its respective bootstrap-enhanced version, with \(B=200\) bootstrap samples, as shown in Figures~\ref{fig:all_estimator}~\ref{fig:Firstfigure}--\ref{fig:subfig6}.
\begin{figure}[H]
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_vasicek-1}
    \caption{}
    \label{fig:Firstfigure}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_VanEs-1}
    \caption{}
    \label{fig:Secondfigure}
  \end{subfigure}
  %\hfill
  %\begin{subfigure}[b]{0.3\textwidth}
    %\centering
    %\includegraphics[width=\textwidth]{example-image-c}
    %\caption{}
    %\label{fig: Third figure}
  %\end{subfigure}

	\begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_Ebrahimi-1}
    \caption{}
    \label{fig:subfig3}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_correa-1}
    \caption{}
    \label{fig:subfig4}
  \end{subfigure}
	\begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_noughabi-1}
    \caption{}
    \label{fig:subfig5}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PDF/Plot_bias_mse_AO-1}
    \caption{}
    \label{fig:subfig6}
  \end{subfigure}
  \caption{Comparing Bias and MSE: original vs. bootstrap estimators, with, $\mu=1$ and $L=5$.}
  \label{fig:all_estimator}
\end{figure}

%I want to write as Fig. \ref{fig:all_estimator} \ref{fig:Firstfigure}--\ref{fig:subfig6}.
Based on previous simulations, the bootstrap technique did not improve the \(\widetilde{H}_{\text{NA}}\) estimator. 
This might occur because the original estimator overestimates the entropy values, showing a positive bias. 
This tendency to overestimate persists with the use of bootstrap, contributing to an increase in bias and MSE.

However, the improvement observed in the most estimators with the application of bootstrap techniques is notable, especially for sample sizes below 81. 
This performance is superior for the \(\widetilde{H}_{\text{C}}\), \(\widetilde{H}_{\text{E}}\), and \(\widetilde{H}_{\text{AO}}\) estimators. 
Therefore, we proceed to perform a comparison of bias and MSE of these three estimators alongside with their original versions, with \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of
size \(n\in\left\{9, 25, 49, 81, 121\right\}\), with \(\mu\in\left\{1, 10\right\}\), \(L=5\), and \(B=200\) bootstrap samples, as shown in Figure~\ref{fig:Plot_bias_mse_gi0} and Table~\ref{tab:table_final}.

%\begin{figure}[htb]
%{\centering \includegraphics[width=0.7\linewidth]{../../Figures/PDF/Plot_bias_mse_gi0-2}
%}
%\caption{Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=5$.}\label{fig:Plot_bias_mse_gi0}
%\end{figure}
\begin{figure}[htb]
{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_bias_mse_gi0-2}

}
\caption{Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=5$.}\label{fig:Plot_bias_mse_gi0}
\end{figure}

\setlength{\tabcolsep}{6pt}
\begin{table}[H]
\centering
\caption{\label{tab:table_final}Bias and MSE of the entropy estimators for the $\Gamma_{\text{SAR}}$, with $L=5$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabular}[t]{crllllllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Bias} & \multicolumn{6}{c}{MSE} \\
\cmidrule(l{3pt}r{3pt}){3-8} \cmidrule(l{3pt}r{3pt}){9-14}
\multicolumn{1}{r}{$\bm{\mu}$} & \multicolumn{1}{r}{$\bm{n}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{AO}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{AO}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widehat{H}_{\text{AO}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{C}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{E}}}$} & \multicolumn{1}{r}{$\bm{\widetilde{H}_{\text{AO}}}$}\\
\midrule
 & $9$ & $-0.210$ & $-0.280$ & $-0.377$ & $-0.106$ & $-0.054$ & $-0.156$ & $\phantom{-}0.140$ & $\phantom{-}0.173$ & $\phantom{-}0.236$ & $\phantom{-}0.121$ & $\phantom{-}0.116$ & $\phantom{-}0.133$\\

 & $25$ & $-0.071$ & $-0.112$ & $-0.149$ & $-0.033$ & $\phantom{-}0.004$ & $-0.035$ & $\phantom{-}0.032$ & $\phantom{-}0.040$ & $\phantom{-}0.050$ & $\phantom{-}0.032$ & $\phantom{-}0.033$ & $\phantom{-}0.033$\\

 & $49$ & $-0.036$ & $-0.060$ & $-0.081$ & $-0.020$ & $\phantom{-}0.015$ & $-0.006$ & $\phantom{-}0.016$ & $\phantom{-}0.019$ & $\phantom{-}0.021$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.017$\\

 & $81$ & $-0.009$ & $-0.026$ & $-0.039$ & $\phantom{-}0.002$ & $\phantom{-}0.031$ & $\phantom{-}0.018$ & $\phantom{-}0.008$ & $\phantom{-}0.009$ & $\phantom{-}0.010$ & $\phantom{-}0.009$ & $\phantom{-}0.010$ & $\phantom{-}0.009$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 1} & $121$ & $-0.001$ & $-0.013$ & $-0.022$ & $\phantom{-}0.004$ & $\phantom{-}0.030$ & $\phantom{-}0.023$ & $\phantom{-}0.005$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.007$ & $\phantom{-}0.007$\\
\cmidrule{1-14}
 & $9$ & $-0.227$ & $-0.297$ & $-0.394$ & $-0.119$ & $-0.060$ & $-0.156$ & $\phantom{-}0.146$ & $\phantom{-}0.180$ & $\phantom{-}0.247$ & $\phantom{-}0.126$ & $\phantom{-}0.117$ & $\phantom{-}0.136$\\

 & $25$ & $-0.088$ & $-0.129$ & $-0.166$ & $-0.052$ & $-0.013$ & $-0.050$ & $\phantom{-}0.040$ & $\phantom{-}0.048$ & $\phantom{-}0.059$ & $\phantom{-}0.040$ & $\phantom{-}0.035$ & $\phantom{-}0.039$\\

 & $49$ & $-0.017$ & $-0.043$ & $-0.064$ & $\phantom{-}0.001$ & $\phantom{-}0.035$ & $\phantom{-}0.012$ & $\phantom{-}0.016$ & $\phantom{-}0.017$ & $\phantom{-}0.019$ & $\phantom{-}0.018$ & $\phantom{-}0.019$ & $\phantom{-}0.017$\\

 & $81$ & $-0.008$ & $-0.025$ & $-0.038$ & $\phantom{-}0.001$ & $\phantom{-}0.031$ & $\phantom{-}0.019$ & $\phantom{-}0.009$ & $\phantom{-}0.009$ & $\phantom{-}0.010$ & $\phantom{-}0.009$ & $\phantom{-}0.011$ & $\phantom{-}0.010$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 10} & $121$ & $\phantom{-}0.004$ & $-0.007$ & $-0.017$ & $\phantom{-}0.008$ & $\phantom{-}0.037$ & $\phantom{-}0.027$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.006$ & $\phantom{-}0.008$ & $\phantom{-}0.007$\\
\bottomrule
\end{tabular}}
\end{table}

\section{Coefficient of variation and a robust
alternative}\label{coefficient-of-variation-and-a-robust-alternative}

The population CV is defined as a ratio of the population standard
deviation \((\sigma)\) to the population mean \((\mu)\): 
\begin{align}
    \text{CV}=\frac{\sigma}{\mu}, \quad \mu \neq 0.
\end{align}

We explore a robust alternative to CV, as described
in~\citep{Ospina2019}, which incorporates the ratio between the mean
absolute deviation from the median (MnAD) and the median, two well-known
robust measures of scale and location, respectively. 
The sample version for the MnAD is defined as \(n^{-1}\sum_{i=1}^n|x_i-\widehat{Q}_2|\),
where \(\widehat{Q}_2\) is an estimate for the median of the population,
which can be approximated by the median of the sample.

\section{Hypothesis Testing}\label{sec:test}

We aim to test the following hypotheses: \[
\begin{cases}
  \mathcal{H}_0: \text{ The data come from the } \Gamma_{\text{SAR}}\text{ law},\\ 
  \mathcal{H}_1:\text{ The data come from the } G_I^0 \text{ distribution}.
\end{cases}
\] We are testing the hypothesis that the data are fully-developed
speckle versus the alternative of data with roughness. As for the
parametric problem, once it is not possible to define the hypothesis
\(\mathcal{H}_0=\alpha=-\infty\), it is impossible to solve this problem
with parametric inference alternatives (such as likelihood ratio, score,
gradient, and Wald hypothesis test). The proposed tests to solve this
physical problem in SAR systems are described below.

\subsection{The Proposed Test Based on Non-parametric
Entropy}\label{the-proposed-test-based-on-non-parametric-entropy}

For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution
\(\mathcal{D}\), a test statistic is proposed. It is based on an
empirical distribution that arises from the difference between
non-parametrically estimated entropies \(\widetilde{H}(\bm{Z})\) and the
analytical entropy of \(\Gamma_{\text{SAR}}\)~\eqref{E:E-gamma}
evaluated at the logarithm of the sample mean, where \(L\geq 1\) is
known.

Hence, the entropy-based test statistic is defined as: \begin{equation}
\label{Eq:test_e}
S(\bm{Z};L)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{\bm{Z}}\right].
\end{equation}

This test statistic aims to assess the behavior of the data under the
null hypothesis using the empirical distribution. If the data represent
fully-developed speckle, the density should center around zero, i.e.,
\(S(\bm{Z};L)\approx 0\). Otherwise, the empirical distribution would
shift from zero under the alternative hypothesis, suggesting significant
differences and heterogeneous clutter.

The comparison between the bootstrap-improved estimators is shown in
Table~\ref{tab:table_time}, where the test accuracy under the null
hypothesis is presented alongside running times. The test accuracy is
evaluated through 1000 simulated samples of different sizes, with each
size replicated 100 times using bootstrap resampling.

The processing time is an important feature, especially considering the
application of these estimators to large datasets of SAR images, as seen
in Chapter~\ref{chp:results}.
\setlength{\tabcolsep}{7pt}
\begin{table}[htb]
\centering\centering
\caption{\label{tab:table_time}Test accuracy and processing time for each bootstrap-improved estimator. }
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\small
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{\textbf{Estimator}} & \multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{$S(\bm{Z}; L)$} & \multicolumn{1}{c}{\textbf{ Time} (s)}\\
\midrule
 &  & $25$ & $-0.00152$ & 22.53\\

 &  & $49$ & $\phantom{-}0.00515$ & 40.35\\

 &  & $81$ & $\phantom{-}0.00625$ & 63.93\\

 & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $2$} & $121$ & $\phantom{-}0.00751$ & 97.06\\

\cline{3-5}
 &  & $25$ & $-0.04332$ & 22.25\\

 &  & $49$ & $-0.01659$ & 33.42\\

 &  & $81$ & $-0.00393$ & 50.94\\

\multirow{-8}{*}[3.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $\widetilde{H}_{\text{C}}$} & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $8$} & $121$ & $\phantom{-}0.00261$ & 97.35\\
\cmidrule{1-5}
 &  & $25$ & $\phantom{-}0.02204$ & 4.66\\

 &  & $49$ & $\phantom{-}0.03452$ & 5.55\\

 &  & $81$ & $\phantom{-}0.03195$ & 6.89\\

 & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $2$} & $121$ & $\phantom{-}0.03012$ & 7.90\\

\cline{3-5}
 &  & $25$ & $\phantom{-}0.00801$ & 4.81\\

 &  & $49$ & $\phantom{-}0.01654$ & 5.43\\

 &  & $81$ & $\phantom{-}0.03036$ & 6.38\\

\multirow{-8}{*}[3.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $\widetilde{H}_{\text{E}}$} & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $8$} & $121$ & $\phantom{-}0.03137$ & 7.46\\
\cmidrule{1-5}
 &  & $25$ & $-0.01935$ & 4.61\\

 &  & $49$ & $\phantom{-}0.00786$ & 5.19\\

 &  & $81$ & $\phantom{-}0.01995$ & 6.70\\

 & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $2$} & $121$ & $\phantom{-}0.01741$ & 7.41\\

\cline{3-5}
 &  & $25$ & $-0.04020$ & 4.74\\

 &  & $49$ & $\phantom{-}0.00047$ & 5.35\\

 &  & $81$ & $\phantom{-}0.01176$ & 6.21\\

\multirow{-8}{*}[3.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $\widetilde{H}_{\text{AO}}$} & \multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash $8$} & $121$ & $\phantom{-}0.02019$ & 7.48\\
\bottomrule
\end{tabu}}
\end{table}

As visible from Table~\ref{tab:table_time}, the accuracy of the test
results across the three estimators shows similarities in specific
sample sizes. 
However, practical scenarios in SAR image processing often
involve small sample sizes, typically obtained over windows of size
\(7\times7\).\\
It is also noteworthy that the \(\widetilde{H}_{\text{AO}}\) estimator
exhibited the shortest processing time, followed by
\(\widetilde{H}_{\text{E}}\) and \(\widetilde{H}_{\text{C}}\).
Considering this aspect, we select the \(\widetilde{H}_{\text{AO}}\)
estimator for subsequent simulations.
 Henceforth, the test statistical
~\eqref{Eq:test_e} will be denoted as:
\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\).

We now verify the normality of the data generated by the
\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test.
Figure~\ref{fig:Plot_density} shows the empirical densities obtained by
applying the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test to
different sample sizes drawn from the \(\Gamma_{\text{SAR}}\)
distribution, where \(L\) takes values \(\left\{3,5, 8,11\right\}\) and
\(\mu=1\). 
\begin{figure}[htb]

{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_density-1}

}

\caption{Empirical densities obtained from $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test under the null hypothesis.}\label{fig:Plot_density}
\end{figure}

Additionally, Table~\ref{tab:table_stat_combined} summarizes
the main descriptive statistics, including mean, standard
deviation~(SD), variance~(Var), skewness~(SK), excessive kurtosis~(EK)
and Anderson--Darling \(p\) values for normality.

\setlength{\tabcolsep}{5pt}
\begin{table}[H]
\centering\centering\centering
\caption{\label{tab:table_stat_combined}Descriptive analysis of $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, with $L\in\left\{3,5, 8,11\right\}$ and $\mu=1$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\footnotesize
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Mean}} & \multicolumn{1}{c}{\textbf{SD}} & \multicolumn{1}{c}{\textbf{Var}} & \multicolumn{1}{c}{\textbf{SK}} & \multicolumn{1}{c}{\textbf{EK}} & \multicolumn{1}{c}{$p$-\textbf{value}}\\
\midrule
 & $25$ & $-0.0280$ & $\phantom{-}0.1547$ & $\phantom{-}0.0239$ & $-0.0076$ & $\phantom{-}0.4734$ & $\phantom{-}0.0022$\\

 & $49$ & $-0.0003$ & $\phantom{-}0.1053$ & $\phantom{-}0.0111$ & $-0.0562$ & $\phantom{-}0.2610$ & $\phantom{-}0.0582$\\

 & $81$ & $\phantom{-}0.0124$ & $\phantom{-}0.0796$ & $\phantom{-}0.0063$ & $-0.0124$ & $\phantom{-}0.0536$ & $\phantom{-}0.5278$\\

 & $121$ & $\phantom{-}0.0187$ & $\phantom{-}0.0630$ & $\phantom{-}0.0040$ & $\phantom{-}0.0337$ & $-0.1826$ & $\phantom{-}0.5894$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 3} & $200$ & $\phantom{-}0.0215$ & $\phantom{-}0.0490$ & $\phantom{-}0.0024$ & $\phantom{-}0.0625$ & $-0.0473$ & $\phantom{-}0.0860$\\
\cmidrule{1-8}
 & $25$ & $-0.0379$ & $\phantom{-}0.1669$ & $\phantom{-}0.0278$ & $\phantom{-}0.0007$ & $\phantom{-}0.1420$ & $\phantom{-}0.3267$\\

 & $49$ & $-0.0015$ & $\phantom{-}0.1150$ & $\phantom{-}0.0132$ & $-0.1025$ & $\phantom{-}0.1998$ & $\phantom{-}0.2582$\\

 & $81$ & $\phantom{-}0.0145$ & $\phantom{-}0.0869$ & $\phantom{-}0.0075$ & $\phantom{-}0.1008$ & $\phantom{-}0.5297$ & $\phantom{-}0.1121$\\

 & $121$ & $\phantom{-}0.0198$ & $\phantom{-}0.0687$ & $\phantom{-}0.0047$ & $\phantom{-}0.0127$ & $\phantom{-}0.0222$ & $\phantom{-}0.2919$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 5} & $200$ & $\phantom{-}0.0236$ & $\phantom{-}0.0529$ & $\phantom{-}0.0028$ & $-0.0467$ & $\phantom{-}0.0977$ & $\phantom{-}0.3346$\\
\cmidrule{1-8}
 & $25$ & $-0.0464$ & $\phantom{-}0.1680$ & $\phantom{-}0.0282$ & $-0.0121$ & $\phantom{-}0.0980$ & $\phantom{-}0.6477$\\

 & $49$ & $-0.0031$ & $\phantom{-}0.1202$ & $\phantom{-}0.0144$ & $\phantom{-}0.1282$ & $\phantom{-}0.2000$ & $\phantom{-}0.0038$\\

 & $81$ & $\phantom{-}0.0137$ & $\phantom{-}0.0883$ & $\phantom{-}0.0078$ & $-0.0279$ & $\phantom{-}0.2554$ & $\phantom{-}0.5567$\\

 & $121$ & $\phantom{-}0.0200$ & $\phantom{-}0.0738$ & $\phantom{-}0.0055$ & $-0.0089$ & $\phantom{-}0.0686$ & $\phantom{-}0.7502$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 8} & $200$ & $\phantom{-}0.0260$ & $\phantom{-}0.0546$ & $\phantom{-}0.0030$ & $\phantom{-}0.0716$ & $-0.0349$ & $\phantom{-}0.3771$\\
\cmidrule{1-8}
 & $25$ & $-0.0442$ & $\phantom{-}0.1735$ & $\phantom{-}0.0301$ & $-0.1422$ & $\phantom{-}0.2413$ & $\phantom{-}0.0981$\\

 & $49$ & $-0.0019$ & $\phantom{-}0.1201$ & $\phantom{-}0.0144$ & $-0.0503$ & $\phantom{-}0.1464$ & $\phantom{-}0.9576$\\

 & $81$ & $\phantom{-}0.0127$ & $\phantom{-}0.0917$ & $\phantom{-}0.0084$ & $-0.0172$ & $\phantom{-}0.0333$ & $\phantom{-}0.3179$\\

 & $121$ & $\phantom{-}0.0239$ & $\phantom{-}0.0729$ & $\phantom{-}0.0053$ & $-0.0127$ & $\phantom{-}0.2102$ & $\phantom{-}0.0596$\\

\multirow{-5}{*}[2\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 11} & $200$ & $\phantom{-}0.0234$ & $\phantom{-}0.0572$ & $\phantom{-}0.0033$ & $-0.0233$ & $\phantom{-}0.1072$ & $\phantom{-}0.6740$\\
\bottomrule
\end{tabu}}
\end{table}
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the
normality assumption. 
A low variance, skewness, and excessive kurtosis
of almost zero indicate limited dispersion, asymmetry, and a light tail.

Normal Q--Q plots confirm no evidence against a normal distribution, as
shown in Figure~\ref{fig:Plot_normality_qq}.
\begin{figure}[H]
\includegraphics[width=0.9\linewidth]{../../Figures/PDF/Plot_normality_qq-1} \caption{Normal Q--Q plots for  $n=121$.}\label{fig:Plot_normality_qq}
\end{figure}

After checking the data's normality, we examined the proposed test's
abilities in terms of size and power. Under \(\mathcal{H}_0\), the
distribution of the test statistic is asymptotically normal. Therefore,
the \(p\) values are calculated as \(2\Phi(-|\varepsilon|)\), where
\(\Phi\) is the standard Gaussian cumulative distribution function, and
\(\varepsilon\) is the standardized test statistic given by: \[
\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \overline{\bm{Z}}\right]}{\widehat\sigma}.
\]

We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. In terms of size, \(1000\) simulations were used for
different sample sizes from the \(\Gamma_{\text{SAR}}\) distribution,
with varying values of \(L\), and \(\mu=1\). In all cases, the nominal
level was achieved. We assessed the test power using \(1000\)
simulations for different sample sizes from the \(G_I^0\) distribution,
with \(\mu=1\), and \(\alpha=-2\). The power generally improves with
increasing sample size and number of looks. The results are shown in
Table~\ref{tab:table_size_power}.

\begin{table}[htb]
\centering\centering
\caption{\label{tab:table_size_power}Size and Power of the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z})$ test statistic.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Size} & \multicolumn{3}{c}{Power} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
\multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{$\bm{1\%}$} & \multicolumn{1}{c}{$\bm{5\%}$} & \multicolumn{1}{c}{$\bm{10\%}$} & \multicolumn{1}{c}{$\bm{1\%}$} & \multicolumn{1}{c}{$\bm{5\%}$} & \multicolumn{1}{c}{$\bm{10\%}$}\\
\midrule
 & 25 & $\phantom{-}0.0160$ & $\phantom{-}0.0620$ & $\phantom{-}0.1070$ & $\phantom{-}0.6900$ & $\phantom{-}0.8450$ & $\phantom{-}0.8340$\\

 & 49 & $\phantom{-}0.0100$ & $\phantom{-}0.0480$ & $\phantom{-}0.0960$ & $\phantom{-}0.6890$ & $\phantom{-}0.8920$ & $\phantom{-}0.8480$\\

 & 81 & $\phantom{-}0.0120$ & $\phantom{-}0.0490$ & $\phantom{-}0.1080$ & $\phantom{-}0.6260$ & $\phantom{-}0.8750$ & $\phantom{-}0.8540$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 3} & 121 & $\phantom{-}0.0090$ & $\phantom{-}0.0690$ & $\phantom{-}0.1190$ & $\phantom{-}0.5680$ & $\phantom{-}0.8620$ & $\phantom{-}0.8230$\\
\cmidrule{1-8}
 & 25 & $\phantom{-}0.0210$ & $\phantom{-}0.0660$ & $\phantom{-}0.1130$ & $\phantom{-}0.9120$ & $\phantom{-}0.9620$ & $\phantom{-}0.9880$\\

 & 49 & $\phantom{-}0.0100$ & $\phantom{-}0.0460$ & $\phantom{-}0.1080$ & $\phantom{-}0.9470$ & $\phantom{-}0.9820$ & $\phantom{-}0.9960$\\

 & 81 & $\phantom{-}0.0120$ & $\phantom{-}0.0560$ & $\phantom{-}0.1070$ & $\phantom{-}0.9580$ & $\phantom{-}0.9900$ & $\phantom{-}0.9960$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 5} & 121 & $\phantom{-}0.0150$ & $\phantom{-}0.0640$ & $\phantom{-}0.1150$ & $\phantom{-}0.9420$ & $\phantom{-}0.9780$ & $\phantom{-}0.9950$\\
\cmidrule{1-8}
 & 25 & $\phantom{-}0.0210$ & $\phantom{-}0.0650$ & $\phantom{-}0.1080$ & $\phantom{-}0.9930$ & $\phantom{-}0.9950$ & $\phantom{-}0.9970$\\

 & 49 & $\phantom{-}0.0060$ & $\phantom{-}0.0470$ & $\phantom{-}0.0860$ & $\phantom{-}0.9980$ & $\phantom{-}1.0000$ & $\phantom{-}0.9970$\\

 & 81 & $\phantom{-}0.0120$ & $\phantom{-}0.0490$ & $\phantom{-}0.1000$ & $\phantom{-}0.9930$ & $\phantom{-}0.9980$ & $\phantom{-}0.9990$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 8} & 121 & $\phantom{-}0.0150$ & $\phantom{-}0.0650$ & $\phantom{-}0.1220$ & $\phantom{-}0.9970$ & $\phantom{-}0.9990$ & $\phantom{-}0.9980$\\
\cmidrule{1-8}
 & 25 & $\phantom{-}0.0130$ & $\phantom{-}0.0610$ & $\phantom{-}0.1000$ & $\phantom{-}0.9990$ & $\phantom{-}0.9990$ & $\phantom{-}0.9990$\\

 & 49 & $\phantom{-}0.0100$ & $\phantom{-}0.0450$ & $\phantom{-}0.0920$ & $\phantom{-}0.9980$ & $\phantom{-}0.9990$ & $\phantom{-}0.9990$\\

 & 81 & $\phantom{-}0.0170$ & $\phantom{-}0.0530$ & $\phantom{-}0.1050$ & $\phantom{-}1.0000$ & $\phantom{-}1.0000$ & $\phantom{-}1.0000$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash 11} & 121 & $\phantom{-}0.0160$ & $\phantom{-}0.0680$ & $\phantom{-}0.1180$ & $\phantom{-}0.9980$ & $\phantom{-}1.0000$ & $\phantom{-}0.9980$\\
\bottomrule
\end{tabu}}
\end{table}

\subsection{The Proposed Test Based on Coefficient of Variation and a
Robust
Alternative}\label{the-proposed-test-based-on-coefficient-of-variation-and-a-robust-alternative}

In addition to the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) test, we
also propose a test statistic based on the classical CV. This test
statistic is defined as follows: \begin{align}
    T_{\text{CV}}=\frac{S}{\overline{Z}},
\end{align} where \(S\) and \(\overline{Z}\) are the sample standard
deviation and mean, respectively.

Similarly, we use another test statistic based on the ratio of the MnAD
to the median. This statistic is given by: \begin{align}
    T_{\text{CV}_{\text{MnAD}}}=\frac{\text{MnAD}}{\text{Median}}.
\end{align}

We proceed to identify suitable models for these estimators of the CV,
and then form test statistics.

The situations in which the use of CV and \(\text{CV}_{\text{MnAD}}\)
may be appropriate, i.e., when the observations are positive, the
log-normal (LN) and the inverse Gaussian distribution (IG) are often
more appropriate than the Gamma and Weibull
distributions~\citep{Chaubey2017,takagi1997application}.

It is shown that the IG distribution is well approximated by the
log-normal distribution, which means that the IG distribution also does
not share the problem of the non-existence of a fixed-width confidence
interval with the Gaussian case~\citep{whitmore1978}.

The biparametric LN distribution has density:

\begin{align}
    f_Z(z;\mu_{\text{LN}}, \sigma_{\text{LN}} )=\frac{1}{\sigma_{\text{LN}} z\sqrt{2\pi}}\exp\left\{-\frac{(\ln z- \mu_{\text{LN}})^2}{2\sigma_{\text{LN}}^2}\right\}\mathbbm 1_{\mathbbm R_+}(z),
\end{align}\\
with \(\mu_{\text{LN}}\) is any real number, and \(\sigma_{\text{LN}}\)
is positive.

\subsection{Model Selection Criterion}\label{model-selection-criterion}

We used the Akaike information criterion (AIC) and the Bayesian
information criterion (BIC) to select the best-fitting distribution.

The AIC deals with the trade-off between the goodness-of-fit and the
model's simplicity in terms of the number of model
parameters~\citep{Burnham2004}. The model or distribution with the lowest
value of AIC is chosen to be the best. The BIC assesses goodness-of-fit
of a distribution or model, but avoids overfitting by penalising
additional degrees of freedom~\citep{Dziak2019}. The model with the
lowest BIC value is chosen as the best.

The AIC and BIC results in
Tables~\ref{tab:table_aic_gamma}--\ref{tab:table_aic_gio_MnADmedian}
indicate that the CV and \(\text{CV}_{\text{MnAD}}\) data from different
distributed \(\Gamma_{\text{SAR}}\) and \(G_I^0\) synthetic sample sizes
match the properties of an LN distribution. It is important to note that
this conclusion was drawn empirically based on a dictionary of
analytically tractable distributions and well-defined under
biparametric, unimodal, asymmetric, and positive distributions.

Figures~\ref{fig:Plot_cv}--\ref{fig:Plot_madmed_gi0_MnADmedian} show
empirical and fitted density plots, Q--Q plots, P--P plots, as well as
empirical and fitted cumulative distribution functions. They provide
qualitative sources that confirm that the LN distribution is the most
appropriate distribution. As expected, both test statistics work well
under the null hypothesis. Under the alternative hypothesis, the P--P
plot shows that \(\text{CV}_{\text{MnAD}}\) is more robust than CV,
although both statistics suffer from the tail effect caused by the
distributed \(G_I^0\) data.

\begin{table}[H]
\centering\centering
\caption{\label{tab:table_aic_gamma}AIC and BIC values for evaluating the best distribution with CV data from $\Gamma_{\text{SAR}}$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-38031.9$ & $-38266.7$ & $-38311.8$ & $-36413.2$ & $-38261.6$\\

 & $49$ & $-47698.2$ & $-47913.7$ & $-47905.6$ & $-45554.0$ & $-47911.6$\\

 & $81$ & $-55382.1$ & $-55494.7$ & $-55494.9$ & $-53220.4$ & $-55493.8$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash AIC} & $121$ & $-61344.9$ & $-61470.8$ & $-61453.8$ & $-58876.0$ & $-61470.5$\\
\cmidrule{1-7}
 & $25$ & $-38016.7$ & $-38251.5$ & $-38296.6$ & $-36398.0$ & $-38246.4$\\

 & $49$ & $-47683.0$ & $-47898.5$ & $-47890.4$ & $-45538.7$ & $-47896.4$\\

 & $81$ & $-55366.9$ & $-55479.5$ & $-55479.6$ & $-53205.2$ & $-55478.6$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash BIC} & $121$ & $-61329.7$ & $-61455.6$ & $-61438.6$ & $-58860.8$ & $-61455.2$\\
\bottomrule
\end{tabu}}
\end{table}

\begin{table}[H]
\centering\centering
\caption{\label{tab:table_aic}AIC and BIC values for evaluating the best distribution with CV data from $G_I^0$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $\phantom{-}8254.04$ & $\phantom{-}2186.31$ & $\phantom{-}3628.40$ & $\phantom{-}8383.58$ & $\phantom{-}2257.63$\\

 & $49$ & $\phantom{-}8821.79$ & $\phantom{-}1689.03$ & $\phantom{-}3483.10$ & $\phantom{-}9533.53$ & $\phantom{-}1835.29$\\

 & $81$ & $\phantom{-}8525.81$ & $\phantom{-}866.29$ & $\phantom{-}2853.31$ & $\phantom{-}9822.48$ & $\phantom{-}1057.91$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash AIC} & $121$ & $\phantom{-}8708.81$ & $\phantom{-}131.86$ & $\phantom{-}2341.06$ & $\phantom{-}10506.49$ & $\phantom{-}398.53$\\
\cmidrule{1-7}
 & $25$ & $\phantom{-}8269.27$ & $\phantom{-}2201.54$ & $\phantom{-}3643.63$ & $\phantom{-}8398.81$ & $\phantom{-}2272.86$\\

 & $49$ & $\phantom{-}8837.02$ & $\phantom{-}1704.26$ & $\phantom{-}3498.33$ & $\phantom{-}9548.76$ & $\phantom{-}1850.52$\\

 & $81$ & $\phantom{-}8541.04$ & $\phantom{-}881.52$ & $\phantom{-}2868.55$ & $\phantom{-}9837.72$ & $\phantom{-}1073.14$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash BIC} & $121$ & $\phantom{-}8724.04$ & $\phantom{-}147.09$ & $\phantom{-}2356.29$ & $\phantom{-}10521.72$ & $\phantom{-}413.76$\\
\bottomrule
\end{tabu}}
\end{table}

\begin{table}[H]
\centering\centering
\caption{\label{tab:table_aic_gamma_madmed}AIC and BIC values for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from $\Gamma_{\text{SAR}}$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-38375.56$ & $-39147.85$ & $-39066.29$ & $-36652.49$ & $-39143.61$\\

 & $49$ & $-48386.11$ & $-48795.32$ & $-48745.48$ & $-46240.91$ & $-48793.83$\\

 & $81$ & $-56072.87$ & $-56322.32$ & $-56290.02$ & $-53836.04$ & $-56322.12$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash AIC} & $121$ & $-62217.14$ & $-62394.77$ & $-62369.32$ & $-59861.80$ & $-62394.57$\\
\cmidrule{1-7}
 & $25$ & $-38360.32$ & $-39132.62$ & $-39051.05$ & $-36637.26$ & $-39128.38$\\

 & $49$ & $-48370.87$ & $-48780.09$ & $-48730.25$ & $-46225.67$ & $-48778.60$\\

 & $81$ & $-56057.64$ & $-56307.09$ & $-56274.79$ & $-53820.81$ & $-56306.89$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash BIC} & $121$ & $-62201.91$ & $-62379.54$ & $-62354.09$ & $-59846.56$ & $-62379.33$\\
\bottomrule
\end{tabu}}
\end{table}

\begin{table}[H]
\centering\centering
\caption{\label{tab:table_aic_gio_MnADmedian}AIC and BIC values for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from $G_I^0$.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{\textbf{Criterion}} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{\textbf{Normal}} & \multicolumn{1}{c}{\textbf{Lognormal}} & \multicolumn{1}{c}{\textbf{Gamma}} & \multicolumn{1}{c}{\textbf{Weibull}} & \multicolumn{1}{c}{\textbf{Inverse Gaussian}}\\
\midrule
 & $25$ & $-13302.39$ & $-15575.23$ & $-15158.42$ & $-11933.35$ & $-15565.03$\\

 & $49$ & $-23265.27$ & $-24529.72$ & $-24284.47$ & $-20986.94$ & $-24522.28$\\

 & $81$ & $-29908.19$ & $-30960.38$ & $-30747.90$ & $-25233.41$ & $-30946.54$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash AIC} & $121$ & $-36496.78$ & $-37128.07$ & $-36991.41$ & $-32366.52$ & $-37123.20$\\
\cmidrule{1-7}
 & $25$ & $-13287.16$ & $-15559.99$ & $-15143.19$ & $-11918.12$ & $-15549.80$\\

 & $49$ & $-23250.04$ & $-24514.48$ & $-24269.24$ & $-20971.71$ & $-24507.05$\\

 & $81$ & $-29892.96$ & $-30945.15$ & $-30732.67$ & $-25218.17$ & $-30931.31$\\

\multirow{-4}{*}[1.5\dimexpr\aboverulesep+\belowrulesep+\cmidrulewidth]{\centering\arraybackslash BIC} & $121$ & $-36481.55$ & $-37112.84$ & $-36976.18$ & $-32351.28$ & $-37107.97$\\
\bottomrule
\end{tabu}}
\end{table}

\begin{figure}[H]

{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_cv_gamma-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with CV data from $\Gamma_{\text{SAR}}$ (under the null hypothesis), with $n=49$, $L=5$, and $\mu=1$.}\label{fig:Plot_cv_gamma}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_cv-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with $\text{CV}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\mu=1$, and $\alpha=-3$.}\label{fig:Plot_cv}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_MnADmedian_gamma-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with $\text{CV}_{\text{MnAD}}$ data from $\Gamma_{\text{SAR}}$ (under the null hypothesis), with  $n=49$, $L=5$, and $\mu=1$.}\label{fig:Plot_MnADmedian_gamma}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_madmed_gi0_MnADmedian-1}

}

\caption{Goodness of fit plots for evaluating the best distribution with $CV_{\text{MnAD}}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\mu=1$, and $\alpha=-3$.}\label{fig:Plot_madmed_gi0_MnADmedian}
\end{figure}

%\begin{figure}[hbt]
%\includegraphics[width=0.8\linewidth]{../../Figures/PDF/Plot_madmed_gi0_MnADmedian-1} \caption{Goodness of fit plots for evaluating the best distribution with $CV_{\text{MnAD}}$ data from $G_I^0$ (under the alternative hypothesis), with  $n=49$, $L=5$, $\mu=1$, and $\alpha=-3$.}\label{fig:Plot_madmed_gi0_MnADmedian}
%\end{figure}

### 2024-05-07 Text/Thesis/chapters/4_results.tex
doctoral qualification document

\chapter{Results}\label{chp:results}
%\section{Results}\label{sec:Results}

This section presents the simulations we performed to evaluate the
proposed test statistics' performance, followed by applications to SAR
data.

\subsection{Simulated Data}\label{simulated-data}

Figure~\ref{fig:sim_Phantom} \ref{fig:sim_Phantom_1} shows the phantom with dimensions of
\(500\times500\) pixels.
 It was proposed by~\citet{Gomez2017} as a tool
to assess the performance of speckle-reduction filters.

Figure~\ref{fig:sim_Phantom} \ref{fig:sim_Phantom_2} shows the simulated image, where each
small phantom displaying texture variations. The observations are
independent draws from the \(G^0_I\) distribution~\eqref{E:gi02}, with
\(L = 5\) and varying \(\alpha\) and \(\mu\), annotated in the image for
each quadrant. 
Light regions correspond to textured observations
(heterogeneous), while darker regions represent textureless areas
(homogeneous).
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.38\textwidth}
    \centering
    \includegraphics[width=60mm]{../../Figures/PNG/Phantom1}
    \caption{Phantom.}
    \label{fig:sim_Phantom_1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.58\textwidth}
    \centering
    \includegraphics[width=80mm]{../../Figures/PNG/Phantom_label/Phantom_labels}
    \caption{Simulated image, varying $\alpha$ and $\mu$, with $L=5$.}
    \label{fig:sim_Phantom_2}
  \end{subfigure}
  \caption{Synthetic dataset.}
  \label{fig:sim_Phantom}
\end{figure}

The \(\alpha\) parameter of the \(G_I^0\) distribution is essential for
interpreting texture characteristics. Values near zero greater than
\(-3\) suggest extremely textured targets, such as urban
zones~\citep{Frery2019a}. 
As the value decreases, it indicates regions with moderate texture (in the \(\left[-6,-3\right]\) region), related to
forest zones, while values below \(-6\) correspond to textureless
regions, such as pasture, agricultural fields, and water
bodies~\citep{Neto2023}.

We applied the three test statistics, namely
\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\), \(T_\text{CV}\), and
\(T_{\text{CV}_{\text{MnAD}}}\), to the simulated image using local
sliding windows of size \(7\times 7\), as shown in
Figures~\ref{fig:sim_results} \ref{fig:sim_results-1}--\ref{fig:sim_results-3}.
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Entropy_Phantom_4_z1_200}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:sim_results-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_Phantom_4_z1}
    \caption{$T_\text{CV}$}
    \label{fig:sim_results-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_Phantom_z1}
    \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:sim_results-3}
  \end{subfigure}
  \caption{Results of applying the test statistics to the simulated image.}
  \label{fig:sim_results}
\end{figure}

The resulting \(p\)-values for each test are shown in
Figures~\ref{fig:sim_SAR_Images} \ref{fig:sim_SAR_Images-1}--\ref{fig:sim_SAR_Images-3}. In
Figures~\ref{fig:sim_SAR_Images_p05} \ref{fig:sim_SAR_Images_p05-1}--\ref{fig:sim_SAR_Images_p05-3}, maps are depicted using a
color table between black, gray levels, and white. All \(p\)-values
above \(0.05\) are represented in white (indicating no evidence to
reject the null hypothesis), while those below \(0.05\) are shown in
black (indicating evidence to reject the hypothesis). 
We notice that the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) performs significantly
better than the other tests in identifying heterogeneous areas in the
simulated image.

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_pvalue_Phantom_4_z1_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:sim_SAR_Images-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_pvalues_Phantom_4_z1}
    \caption{$T_\text{CV}$}
    \label{fig:sim_SAR_Images-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:sim_SAR_Images-3}
  \end{subfigure}
  \caption{Map of $p$-values of simulated image for each test. }
  \label{fig:sim_SAR_Images}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_005_Phantom_4_z1_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:sim_SAR_Images_p05-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_005_pvalues_Phantom_4_z1}
    \caption{$T_\text{CV}$}
    \label{fig:sim_SAR_Images_p05-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_005_Phantom_7_z1}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:sim_SAR_Images_p05-3}
  \end{subfigure}
  \caption{Results for a threshold of $0.05$ of the $p$-value of simulated image for each test. }
  \label{fig:sim_SAR_Images_p05}
\end{figure}

\subsection{SAR Data}\label{sar-data}

We evaluated the proposed test statistics using three SAR images: one of
the coast of Jalisco, Mexico (with a spatial resolution of 20 m both
along azimuth and range directions) and two of Illinois, USA (with a
spatial resolution of \SI{10}{\meter} both along azimuth and range
directions), acquired by the Sentinel-1B satellite operating in C-band,
with VV polarization and intensity format. 
The first two images have a size of \(512 \times 512\) pixels, while the third has
\(1024 \times 1024\) pixels, and they contain mountainous areas,
agricultural regions, water bodies, and urban areas, as shown in
Figures~\ref{fig:real_SAR_Images_coe} \ref{fig:real_SAR_Images_coe-1}--\ref{fig:real_SAR_Images_coe-3}.

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Mexico_512}
    \caption{Coast of Jalisco, $L=18$}
    \label{fig:real_SAR_Images_coe-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/lake_512}
    \caption{Illinois-Region 1, $L=36$}
    \label{fig:real_SAR_Images_coe-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Illinois_1024_36L}
     \caption{Illinois-Region 2,  $L=36$}
    \label{fig:real_SAR_Images_coe-3}
  \end{subfigure}
  \caption{SAR images. }
  \label{fig:real_SAR_Images_coe}
\end{figure}

The three statistical tests are applied to the SAR images using
\(7\times 7\) local sliding windows, as illustrated in
Figures~\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake}
and~\ref{fig:real_images_test_Illinois}.

The \(p\)-values obtained for each test are presented in
Figures~\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue}
and~\ref{fig:Illinois_crops_pvalue}, respectively.

In Figures~\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05}
and~\ref{fig:Illinois_crops_0.05}, the maps of \(p\)-values composed of
a linear gradient of black and white colors, represent the decisions at
a \SI{5}{\percent} significance level.
Dark areas represent values below
\(0.05\), indicating evidence to reject the null hypothesis and
suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject
the fully-developed speckle hypothesis.
\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Entropy_Mexico_512_18L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:real_images_test_Mexico-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_mexico_512}
    \caption{$T_\text{CV}$}
    \label{fig:real_images_test_Mexico-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_mexico_512}
    \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:real_images_test_Mexico-3}
  \end{subfigure}
  \caption{Results of applying the test statistics to Coast of Jalisco image.}
  \label{fig:real_images_test_Mexico}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_pvalue_Mexico_512_18L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:Mexico_pvalue-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_pvalues_mexico_512}
    \caption{$T_\text{CV}$}
    \label{fig:Mexico_pvalue-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_p_values_mexico_512}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:Mexico_pvalue-3}
  \end{subfigure}
  \caption{Map of $p$-values of Coast of Jalisco image for each test. }
  \label{fig:Mexico_pvalue}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_005__Mexico_512_18L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:Mexico_crops_0.05-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_005_pvalues_mexico_512}
    \caption{$T_\text{CV}$}
    \label{fig:Mexico_crops_0.05-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_005_mexico_512}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:Mexico_crops_0.05-3}
  \end{subfigure}
  \caption{Results for a threshold of $0.05$ of the $p$-value of Coast of Jalisco for each test. }
  \label{fig:Mexico_crops_0.05}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Entropy_lake_512_36L_AO_100b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:test_lake-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_lake_512}
    \caption{$T_\text{CV}$}
    \label{fig:test_lake-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_lake_512}
    \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:test_lake-3}
  \end{subfigure}
  \caption{Results of applying the test statistics, Illinois-Region 1.}
  \label{fig:test_lake}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_pvalue_lake_512_36L_AO_100b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:lake_pvalue-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_pvalues_lake_512}
    \caption{$T_\text{CV}$}
    \label{fig:lake_pvalue-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_p_values_lake_512}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:lake_pvalue-3}
  \end{subfigure}
  \caption{Map of $p$-values, Illinois-Region 1. }
  \label{fig:lake_pvalue}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_005_lake_512_36L_AO_100b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:lake_0.05-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_005_pvalues_lake_512}
    \caption{$T_\text{CV}$}
    \label{fig:lake_0.05-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_005_lake_512}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:lake_0.05-3}
  \end{subfigure}
  \caption{Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 1. }
  \label{fig:lake_0.05}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/Entropy_Illinois_1024_36L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:real_images_test_Illinois-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_Illinois_crops_1024}
    \caption{$T_\text{CV}$}
    \label{fig:real_images_test_Illinois-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_Illinois_crops_1024}
    \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:real_images_test_Illinois-3}
  \end{subfigure}
  \caption{Results of applying the test statistics, Illinois-Region 2.}
  \label{fig:real_images_test_Illinois}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_pvalue_Illinois_1024_36L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:Illinois_crops_pvalue-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_pvalues_Illinois_crops_1024}
    \caption{$T_\text{CV}$}
    \label{fig:Illinois_crops_pvalue-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_p_values_Illinois_crops_1024}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:Illinois_crops_pvalue-3}
  \end{subfigure}
  \caption{Map of $p$-values, Illinois-Region 2. }
  \label{fig:Illinois_crops_pvalue}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/H_005_pvalues_Illinois_1024_36L_AO_200b}
    \caption{$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$}
    \label{fig:Illinois_crops_0.05-1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/cv_005_pvalues_Illinois_crops_1024}
    \caption{$T_\text{CV}$}
    \label{fig:Illinois_crops_0.05-2}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../../Figures/PNG/mnad_005_Illinois_crops_1024}
     \caption{$T_{\text{CV}_{\text{MnAD}}}$}
    \label{fig:Illinois_crops_0.05-3}
  \end{subfigure}
  \caption{Results for a threshold of $0.05$ of the $p$-value, Illinois-Region 2. }
  \label{fig:Illinois_crops_0.05}
\end{figure}

Using Shannon entropy is more meaningful than using the original and
robust CV to capture heterogeneity. It is justified that the dark areas
of the maps based on the \(T_\text{CV}\) and
\(T_{\text{CV}_{\text{MnAD}}}\) show coverage patterns similar to those
reported for the \(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\) map. 
This suggests that although CV-based tests may produce slightly less
pronounced results than the entropy-based test, they still demonstrate a
comparable ability to detect heterogeneity within SAR images.

It is noticeable that the entropy and CV-based tools predicted
heterogeneity regions and boundaries where the statistical properties of
texture vary. The \(T_{\text{CV}_{\text{MnAD}}}\) test was shown to be
an effective edge detector. 
It emerges as a robust alternative to the classical CV test, making it less susceptible to the influence of
outliers and allowing it to produce more precise edges. 
Considering a
higher significance level may increase the sensitivity to edge detection
but also increase the risk of detecting false heterogeneous regions.

Additionally, assuming a \SI{5}{\percent} threshold for \(p\)-values, in
most cases, the heterogeneous regions detected by the
\(S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)\) test were more extensive
than those detected by the \(T_\text{CV}\) and
\(T_{\text{CV}_{\text{MnAD}}}\) tests. 
This was mainly observable in
Figures~\ref{fig:sim_SAR_Images_p05} \ref{fig:sim_SAR_Images_p05-1},
~\ref{fig:Mexico_crops_0.05} \ref{fig:Mexico_crops_0.05-1}, and~\ref{fig:lake_0.05} \ref{fig:lake_0.05-1}.

### 2024-05-07 Text/Thesis/chapters/5_conclusion.tex
doctoral qualification document

\chapter{Conclusions and future perspectives}\label{chp:conclusions}

This work provides a practical and theoretical answer to the
following physical question: How to detect heterogeneity in SAR images,
assuming that the SAR intensity follows the \(\Gamma_{\text{SAR}}\)
model. To this end, we proposed three novel hypothesis tests, one from
the Shannon entropy and two from the variation coefficient variants. The
performance of our proposals was evaluated using a Monte Carlo study.
The results showed that they were conservative in estimating the
probability of a type I error (false alarm rate) and the test power
(probability of detection), which increases with sample size. An
application to three recent SAR images was performed. The results showed
that the Shannon entropy-based test was more robust than the CV-based
tests. In addition, all tests could recognize images with different
textures and identify edges where the texture type changes.

\section*{Future perspectives}

For future research directions, there is a promising avenue in estimating the equivalent number of looks (ENL), a crucial parameter in the statistical modeling of multi-look synthetic aperture radar (SAR) imagery. This parameter serves as an indicator of heterogeneity and can significantly impact the accuracy of statistical analyses.

Additionally, we plan to explore the estimation of ENL in polarimetric SAR (PolSAR) data. This extension will involve:
\begin{itemize}
	\item Estimating the test on each of the three intensity channels of fully PolSAR data
	\item Analyzing the joint distribution
	\item Proposing techniques that generalize the test statistic  into the analysis of PolSAR data.
\end{itemize}

### 2024-05-07 Code/R/MainFunctions/difference.betweeen.GammaSAR.GI0.n.Look.R

@@ -1,0 +1,11 @@
+difference.betweeen.GammaSAR.GI0.n.Look <- function(alpha, L) {
+  return(
+    -L - lgamma(L-alpha) + 
+      (L-alpha)*(digamma(L - alpha))- 
+      (1-alpha)*digamma(- alpha)+
+      log(-1 - alpha)+
+      lgamma(-alpha)
+  )
+}
+
+x=difference.betweeen.GammaSAR.GI0.n.Look(-1.5, 2)

### 2024-05-07 Code/R/Programs/CV-test.R

@@ -1,0 +1,68 @@
+rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+ source("../../../Code/R/Programs/read_ENVI_images.R")
+# source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                   headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+ # x <- myread.ENVI(file='../../../Data/SAR/mexico_512/Intensity_VV.img', 
+ #                  headerfile='../../../Data/SAR/mexico_512/Intensity_VV.hdr')
+ 
+  # x <- myread.ENVI(file='../../../Data/SAR/Lake_512/Intensity_VV.img', 
+  #                  headerfile='../../../Data/SAR/Lake_512/Intensity_VV.hdr')
+  load("../Programs/Data/Phantom_4_z.Rdata")#Phantom_4_z
+  # Asignar las dimensiones de la matriz cargada a las variables rows y cols
+  rows <- nrow(Z)
+  cols <- ncol(Z)
+  
+  window_size <- 7
+#L <- 5
+#B <- 100
+
+
+window_size <- 9
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+cv_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+
+# 
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    
+    x_values <- window_data
+    
+    
+    # 
+    mean_values <- mean(window_data)
+    sd_values <- sd(window_data)
+    
+    # 
+    cv_values[i, j] <- sd_values / mean_values
+    
+    
+    
+  }
+}
+
+save( cv_values, x, file = "./Data/CV_results_data_lake_512.Rdata")
[…]

### 2024-05-07 Code/R/Programs/MnAD-test.R

@@ -1,0 +1,50 @@
+rm(list = ls())
+
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/mexico_512/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/mexico_512/Intensity_VV.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/Lake_512/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/Lake_512/Intensity_VV.hdr')
+
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+window_size <- 9
+
+
+MnADmedian <- function(mat){
+  mdn <- median(mat)
+  MnAD <- mean(abs(mat - mdn))
+  MnAD/mdn
+}
+
+cd_values_mnad <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    # Calcular el CD basado en MnAD para la ventana local (matriz)
+    cd_values_mnad[i, j] <- MnADmedian(window_data)
+  }
+}
+
+# Guardar el resultado en un archivo
+save( cd_values_mnad, x, file = "./Data/MnAD_results_data_lake_512.Rdata")
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_mexico_512.Rdata")
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_Illinois_crops_1024.Rdata")
+#save(cd_values_mnad, x, file = "./Data/results_data_Ottawa_512_mnad_7.Rdata")

### 2024-05-07 Code/R/Programs/entropy-based-test.R

@@ -1,0 +1,73 @@
+# Start the timer
+start_time <- Sys.time()
+
+#Estimators
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+#Load and read data from SAR images
+
+# x <- myread.ENVI(file='../../../Data/SAR/panama512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/panama512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+# 
+# Load simulated image EX. Phantom
+#load("../Programs/Data/Phantom_4_regions.Rdata")
+#save(Z, file="./Data/Phantom_4_regions.Rdata")
+load("../Programs/Data/Phantom_4_z.Rdata")
+
+# Assign the dimensions of the loaded matrix to the variables rows and cols
+# change for x if the data comes SAR images
+
+rows <- nrow(Z)
+cols <- ncol(Z)
+
+# rows <- nrow(x)
+# cols <- ncol(x)
+
+
+
+L <- 5 # Number of looks
+B <- 200 # Replications bootstrap
+window_size <- 7 # sliding window size
+
+
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- Z[i:(i + window_size - 1), j:(j + window_size - 1)]#change for x if the data comes SAR images
+   #apply the entropy test using one of the bootstrap estimators above
[…]

### 2024-05-07 Code/R/Programs/sar_test_calculation.R

@@ -1,7 +1,7 @@
 #rm(list = ls())
 
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
 source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
 source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
@@ -12,34 +12,40 @@ source("../../../Code/R/MainFunctions/correa_estimator.R")
 # x_Flevoland2 <- myread.ENVI(file='../../../Data/SAR/Flevoland_100/Intensity_VV.img', 
 #                             headerfile='../../../Data/SAR/Flevoland_100/Intensity_VV.hdr')
 
-x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
-                             headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
-x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img', 
-                 headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+# x <- myread.ENVI(file='../../../Data/SAR/Flevoland_300/Intensity_VV.img', 
+#                              headerfile='../../../Data/SAR/Flevoland_300/Intensity_VV.hdr')
+# x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
 
+# x <- myread.ENVI(file='../../../Data/SAR/SanFrancisco_650/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/SanFrancisco_650/Intensity_VV.hdr')
+x <- myread.ENVI(file='../../../Data/SAR/Flevoland512/Intensity_VV.img',
+                 headerfile='../../../Data/SAR/Flevoland512/Intensity_VV.hdr')
 
+# x <- myread.ENVI(file='../../../Data/SAR/Frankfurt_512/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/Frankfurt_512/Intensity_VV.hdr')
 
 
 L <- 5
-B <- 1
+B <- 4
 
[…]

### 2024-05-07 Text/Thesis/chapters/2_background.tex
doctoral qualification document

@@
 
-%Remote sensing is devoted to gathering information from the Earth’s surface at a distance~\citep{campbell2011introduction}, by means of electromagnetic energy or other mediums.
-
 This chapter presents some basics of remote sensing that we will use in the rest of the document and focuses on the theory of SAR.
 
-%\section{Electromagnetic radiation}
 \section{Remote Sensing} \label{sec:pr_obs}
@@
 Table~\ref{tab:spacebornes} gives some examples of commonly used spaceborne SAR sensors, currently in operation. 
-These include Radarsat-2 from the Canadian Space Agency (CSA), TerraSAR-X from the German Aerospace Center (DLR), ALOS PALSAR-2 from the Japan Aerospace Exploration Agency (JAXA), and Sentinel-1A/1B from the European Space Agency (ESA) (see Figure~\ref{fig:Sentinel-1}), as well as Gaofen-3 from the China National Space Administration (CNSA).
+These include Radarsat-2 from the Canadian Space Agency (CSA), TerraSAR-X from the German Aerospace Center (DLR), ALOS PALSAR-2 from the Japan Aerospace Exploration Agency (JAXA), and Sentinel-1A/1B from the European Space Agency (ESA) (see Figure~\ref{fig:Sentinel-1n}), as well as Gaofen-3 from the China National Space Administration (CNSA).
 \begin{figure}[H]
@@
     \caption[Sentinel-1 radar.]{Sentinel-1 radar, (source \href{https://www.esa.int/Applications/Observing_the_Earth/Copernicus/Sentinel-1/Changing_lands}{ESA}).}
-    \label{fig:Sentinel-1}
+    \label{fig:Sentinel-1n}
 \end{figure}
@@
   \end{subfigure}
-  %\hfill
-  %\begin{subfigure}[b]{0.3\textwidth}
-    %\centering
-    %\includegraphics[width=\textwidth]{example-image-c}
-    %\caption{}
-    %\label{fig: Third figure}
-  %\end{subfigure}
   \caption{SAR image with speckle noise}
@@
 \subsection{Sentinel-1 SAR data processing}
-The Sentinel-1 images were obtained from the Alaska Satellite Facility's (ASF) at \url{https://search.asf.alaska.edu/#/} and by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/}.
+The Sentinel-1 images were obtained from the Alaska Satellite Facility (ASF) at \url{https://search.asf.alaska.edu/#/} and by the European Space Agency via Copernicus Data Space Ecosystem at \url{https://dataspace.copernicus.eu/} (see Figure~\ref{fig:alaska-area1}).
 
-The downloaded SAR images were pre-processed using the Sentinel Application Platform (SNAP) Toolbox developed by ESA.
+The SAR images downloaded were pre-processed using the Sentinel Application Platform (SNAP) Toolbox developed by ESA (see Figure~\ref{fig:alaska-areaf}).
 
@@
     \caption[Selection of area of interest]{Selection of area of interest.}
-    \label{fig:alaska-area}
+    \label{fig:alaska-area1}
 \end{figure}
@@
     %\decoRule
-    \caption[SAR Images pre-processing  in the SNAP]{SAR Images pre-processing  in the SNAP.}
-    \label{fig:alaska-area2}
+    \caption[SAR Images pre-processing  in the SNAP]{SAR Images pre-processing  in SNAP.}
+    \label{fig:alaska-areaf}
 \end{figure}
-
-%\subsection*{Example math equations}
-%-----------------------------------------------------------
-%\begin{align*}
-%L(\alpha,  \lambda|  \bm{x})&=\prod_{i=1}^n{f(x_i|\alpha, \lambda )}\\
-                                 %&= \prod_{i=1}^n\left[\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\,x_i^{\alpha-1}\exp\left\{-\lambda x_i\right\}\right]\\
-%&=\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}
-%\end{align*}
-%%----------------------------------------------------------
-%In Figure \ref{fig:undercatch}, in Eq, \eqref{eq:em}.
-%\begin{align}
-%\label{eq:em}
-%\ell(\alpha, \lambda| \bm{x}) &=\log\left[\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n\prod_{i=1}^nx_i^{\alpha-1}\times \exp\left\{-\left(\lambda\sum_{i=1}^n x_i \right)\right\}\right]\nonumber\\
-%&=\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)^n+\log\left[\prod_{i=1}^nx_i^{\alpha-1}\right]-\lambda\sum_{i=1}^nx_i\nonumber\\
-%&=n\log\left(\frac{\lambda^{\alpha}}{\Gamma(\alpha)}\right)+(\alpha-1)\log\prod_{i=1}^nx_i-\lambda\sum_{i=1}^nx_i\nonumber\\
-%&=n\log(\lambda^{\alpha})-n\log(\Gamma(\alpha))+(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i\nonumber\\
-%&=n\alpha\log \lambda -n\log(\Gamma(\alpha)) +(\alpha-1)\sum_{i=1}^n\log(x_i)-\lambda\sum_{i=1}^nx_i.
-	%\end{align}
-%----------------------------------------------------------
-
-%-------------------------------------------------------
-
-%\begin{table}[h]
-%\centering
-%\caption{\label{tab1}Comparação de tempos. }
-%\begin{tabular}{l c c }
-%\toprule[1pt] \textbf{Amostra (N)} \ \ \  \ \ \  & \textbf{Tempo de Execução (C)}\ \ \ \ \ \ \  &\textbf{Tempo de Execução (Ox)} \\\midrule[0.5pt]
-%$20$ & 7.6810 s  &  5.01 s \\
-%$30$ & 9.6260 s     & 5.34 s \\
-%$50$ &  10.0310 s & 5.99 s \\
-%$100$ & 15.5420 s & 8.07 s \\
-%$200$ & 20.5860 s & 9.64 s \\
-%$500$ & 29.0890  s & 15.12 s \\
-%\bottomrule[1pt]
-%\end{tabular}
-%\caption[Precipitation datasets]{List of datasets used in the analysis of daily precipitation uncertainty carried over i}\label{tab:1}
-%\end{table}
-%------------------------------------------------------
-
-%\begin{table}[]
-%\centering
-%\begin{tabular}{@{}llll@{}}
-%\toprule
-%Dataset name & Period & Spatial res. & Data source \\ \midrule
-%E-OBS        & 2000--2016 & \ang{0.25}                            & Station data \\
-%EURO4M-APGD  & 2000--2008 & \SI{5}{\kilo\metre}                   & Station data \\
-%HMR          & 2000--2013 & \SI{5.5}{\kilo\metre}                 & Reanalysis \\
-%ARCIS        & 2000--2015 & \textasciitilde{} \SI{5}{\kilo\metre} & Station data \\
-%CHIRPS       & 2000--2016 & \ang{0.05}                            & Station data + satellite \\
-%CPC          & 2000--2016 & \ang{0.5}                             & Station data \\
-%CMORPH       & 2000--2016 & \ang{0.25}                            & Satellite \\
-%PERSIANN-CDR & 2000--2016 & \ang{0.25}                            & Satellite \\ \bottomrule
-%\end{tabular}
-%\caption[ Italy]{List of datasets used in the analysis of daily precipitation uncertainty  references.}\label{tab:2}
-%\end{table}

### 2024-05-07 Text/Thesis/chapters/3_methods.tex
doctoral qualification document

@@
 
-\subsection{The Proposed Test Based on Coefficient of Variation and a
+\subsection[The Proposed Test Based on CV and a Robust Alternative]{The Proposed Test Based on Coefficient of Variation and a
 Robust

### 2024-05-08 Text/Thesis/chapters/2_background.tex
doctoral qualification document

@@
 \subsection{Remote Sensors}
-Remote sensors remotely collect data by measuring the electromagnetic (EM) radiation at specific spectral ranges (usually called bands). 
+Remote sensors collect data remotely by measuring electromagnetic (EM) radiation within specific spectral ranges,  often called bands. 
 When they are deployed on satellites or mounted on aircraft, they are called spaceborne and airborne remote sensors, respectively.
@@
 
-In large, optical sensors can be classified, by the number of spectral bands which they image, into hyperspectral, multispectral, and panchromatic sensors. 
-Whereby hyperspectral sensors image the full optical subsection of the EM-spectrum into hundreds of narrow spectral bands, while panchromatic sensors image the visible light spectrum using a single, wide spectral band~\citep{Sara2021}.
+In general, optical sensors can be classified by the number of spectral bands they image into hyperspectral, multispectral, and panchromatic sensors. 
+Hyperspectral sensors image the full optical subsection of the EM spectrum into hundreds of narrow spectral bands, while panchromatic sensors image the visible light spectrum using a single, wide spectral band~\citep{Sara2021}.
 Similarly, SAR sensors can also be classified based on their operational bandwidth into C, L and X-band, with L-band being the lowest frequency and thus the highest level of vegetation and soil penetration.

### 2024-05-08 Text/Thesis/partes/abstract.tex
add folder partes

%\begin{otherlanguage}{spanish}
\begin{abstract}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}
This work presents a statistical approach to identify the
underlying roughness characteristics in synthetic aperture radar (SAR)
intensity data. The physical modeling of this kind of data allows the
use of the Gamma distribution in the presence of fully-developed
speckle, i.e., when there are infinitely many independent backscatterers
per resolution cell, and none dominates the return. Such areas are often
called ``homogeneous'' or ``textureless'' regions. The
\(\mathcal{G}_I^0\) distribution is also a widely accepted law for
heterogeneous and extremely heterogeneous regions, i.e., areas where the
fully-developed speckle hypotheses do not hold. We propose three test
statistics to distinguish between homogeneous and inhomogeneous regions,
i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with
a known number of looks. The first test statistic uses a bootstrapped
non-parametric estimator of Shannon entropy, providing a robust
assessment in uncertain distributional assumptions. The second test uses
the classical coefficient of variation (CV). The third test uses an
alternative form of estimating the CV based on the ratio of the mean
absolute deviation from the median to the median. We apply our test
statistic to create maps of \(p\)-values for the homogeneity hypothesis.
Finally, we show that our proposal, the entropy-based test, outperforms
existing methods, such as the classical CV and its alternative variant,
in identifying heterogeneity when applied to both simulated and actual
data.

\end{abstract}
%\end{otherlanguage}

### 2024-05-08 Text/Thesis/partes/acknowledgements.tex
add folder partes

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
This PhD project is the outcome of the work of many people: 
\\
Whenever fitting, specific acknowledgements are given inside the text or in footnotes, but here I would especially like to thank all of my colleagues at \\
In particular,

%\newpage
%\section*{Author's note}
%This thesis has been compressed for uploading and is missing hyperlinks.
%The original version, containing full-resolution images and hyperlinks, can be obtained from \url{http://users.ictp.it/~afantini/PhD_thesis/PhD_thesis_final_15feb2019.pdf} or by requesting it to \href{mailto:adr.fantini@gmail.com}{adr.fantini@gmail.com}.

\end{acknowledgements}

### 2024-05-08 Text/Thesis/partes/resumo.tex
add folder partes

\begin{otherlanguage}{portuguese}

\begin{resumo}
\phantomsection
\addcontentsline{toc}{chapter}{Resumo}

Este trabalho apresenta uma abordagem estatística para identificar as características de rugosidade subjacentes nos dados de intensidade do radar de abertura sintética (SAR). 
A modelagem física desse tipo de dados permite o uso da distribuição Gamma na presença de speckle totalmente desenvolvido, ou seja, quando há infinitos retroespalhadores independentes por celda de resolução e nenhum domina o retorno.
Essas áreas são frequentemente chamadas de regiões "homogêneas" ou "sem textura". 
A distribuição $\mathcal{G}_I^0$ também é uma lei amplamente aceita para regiões heterogêneas e extremamente heterogêneas, ou seja, áreas onde as hipóteses de speckle totalmente desenvolvidas não se aplicam. 
Propomos três estatísticas de teste para distinguir entre regiões homogêneas e inhomogêneas, ou seja, entre dados distribuídos gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks. 
A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap, fornecendo uma avaliação robusta em suposições onde a distribuição é desconhecida.
O segundo teste usa o coeficiente de variação clássico (CV). 
O terceiro teste usa uma forma alternativa de estimar o CV com base na razão da média do desvio absoluto em relação à mediana.
 Aplicamos nossa estatística de teste para criar mapas de $p$-valores para a hipótese de homogeneidade. 
Finalmente, mostramos que nossa proposta, o teste baseado em entropia, supera os métodos existentes, como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.

\end{resumo}
\end{otherlanguage}

### 2024-05-09 Text/Thesis/partes/abstract.tex
Suggested corrections done.

@@
 heterogeneous and extremely heterogeneous regions, i.e., areas where the
-fully-developed speckle hypotheses do not hold. We propose three test
+fully-developed speckle hypotheses do not hold.
+One issue involving the parametric space of $\mathcal{G}_I^0$ is the analytical 
+infeasibility of testing homogeneity against heterogeneity using classical tests. 
+As solutions to this problem, we propose three test
 statistics to distinguish between homogeneous and inhomogeneous regions,
-i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with
+i.e., between Gamma and \(\mathcal{G}_I^0\) distributed data, both with
 a known number of looks. The first test statistic uses a bootstrapped
-non-parametric estimator of Shannon entropy, providing a robust
+non-parametric estimator of Shannon entropy, providing an
 assessment in uncertain distributional assumptions. The second test uses
@@
 data.
+\end{abstract}
 
-\end{abstract}
+\begin{keywords}
+SAR; heterogeneity; entropy; coefficient of variation; hypothesis tests
+\end{keywords}
+
 %\end{otherlanguage}

### 2024-05-09 Text/Thesis/partes/resumo.tex
Suggested corrections done.

@@
 Este trabalho apresenta uma abordagem estatística para identificar as características de rugosidade subjacentes nos dados de intensidade do radar de abertura sintética (SAR). 
-A modelagem física desse tipo de dados permite o uso da distribuição Gamma na presença de speckle totalmente desenvolvido, ou seja, quando há infinitos retroespalhadores independentes por celda de resolução e nenhum domina o retorno.
-Essas áreas são frequentemente chamadas de regiões "homogêneas" ou "sem textura". 
+A modelagem física desse tipo de dados permite o uso da distribuição Gamma na presença de speckle totalmente desenvolvido, ou seja, quando há infinitos retroespalhadores independentes por célula de resolução e nenhum domina o retorno.
+Essas áreas são frequentemente chamadas de regiões ``homogêneas'' ou ``sem textura''. 
 A distribuição $\mathcal{G}_I^0$ também é uma lei amplamente aceita para regiões heterogêneas e extremamente heterogêneas, ou seja, áreas onde as hipóteses de speckle totalmente desenvolvidas não se aplicam.
-Propomos três estatísticas de teste para distinguir entre regiões homogêneas e inhomogêneas, ou seja, entre dados distribuídos gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks. 
-A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap, fornecendo uma avaliação robusta em suposições onde a distribuição é desconhecida.
+Uma problemática envolvendo o espaço paramétrico da $\mathcal{G}_I^0$ é a inviabilidade analítica de se testar homogeneidade contra heterogeneidade a partir de testes clássicos. 
+Como soluções para esta questão, propomos três testes de hipóteses  para distinguir entre regiões homogêneas e inhomogêneas, ou seja, entre dados distribuídos Gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks.
+A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap, fornecendo uma avaliação com base em distribuição quando a mesma é desconhecida.
 O segundo teste usa o coeficiente de variação clássico (CV). 
@@
 Aplicamos nossa estatística de teste para criar mapas de $p$-valores para a hipótese de homogeneidade. 
-Finalmente, mostramos que nossa proposta, o teste baseado em entropia, supera os métodos existentes, como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.
+Finalmente, mostramos que nossa proposta, o teste baseado em entropia, supera métodos existentes, tais como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.
 
 \end{resumo}
+
+\begin{keywords}
+SAR; heterogeneidade; entropia; coeficiente de variação; testes de hipóteses
+\end{keywords}
+
 \end{otherlanguage}

### 2024-07-23 Code/R/RMarkdown/Report_Independence_of_Mean_and_CV.Rmd
update files

---
title: "Report: Analysis of Independence between Sample Mean and Coefficient of Variation"
author: ""
date: ""
output: pdf_document

# output: 
#   pdf_document:
#     toc: true
#     toc_depth: 2
#html_document
header-includes:
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{bm}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{mathabx}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)

#knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD
theme_set(theme_bw()  +
            theme(text=element_text(family="serif"),
                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
)
# Helpful for latex tables
# library(xtable)
# options(xtable.caption.placement='top',
#         xtable.table.placement='!t',
#         xtable.include.rownames=F,
#         xtable.comment=F)
# #library(rgl)

source("../MainFunctions/gamma_sar_sample.r")
source("../MainFunctions/entropy_gamma_sar.r")
source("../MainFunctions/entropy_gI0.r")
source("../MainFunctions/gi0_sample.r")

source("../MainFunctions/van_es_estimator.r")
source("../MainFunctions/correa_estimator.r")
source("../MainFunctions/ebrahimi_estimator.r")
source("../MainFunctions/noughabi_arghami_estimator.r")
source("../MainFunctions/vasicek_estimator.r")
source("../MainFunctions/al_omari_1_estimator.r")
source("../MainFunctions/al_omari_2_estimator.r")

source("../MainFunctions/bootstrap_van_es_estimator.r")
source("../MainFunctions/bootstrap_correa_estimator.r")
source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
source("../MainFunctions/bootstrap_vasicek_estimator.r")
source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../Programs/functions_sample_bias_mse.R")#

set.seed(1234567890, kind = "Mersenne-Twister")

```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
```

\newcommand{\bias}{\operatorname{Bias}}

# Introduction
we analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution. This independence is unique to the Gamma distribution and does not apply to other common distributions.

In the context of identifying heterogeneity in SAR imaging data, two main models are used: the Gamma SAR distribution and the $G_I^0$ distribution. The Gamma SAR distribution is easier to handle and allows homogeneous areas to be identified without having to resort to the $G_I^0$ distribution.

# Methodology

To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.

### Simulations

The following R code was used to generate 10000 samples for each distribution and analyze the independence between the mean and CV.

# Gamma SAR Distribution
For the Gamma SAR distribution, we simulated the data and plotted the CV versus the mean.

```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Scatter plot of CV versus Mean."}

source("../MainFunctions/gamma_sar_sample.R")

set.seed(1234567890, kind = "Mersenne-Twister")

sample.size <- 49
R <- 10000
mu <- 1
L <- 5

means <- numeric(R)
cvs <- numeric(R)

for (r in 1:R) {
  z <- gamma_sar_sample(L, mu, sample.size)
  means[r] <- mean(z)
  cvs[r] <- sd(z) / mean(z)
}

data <- data.frame(Mean = means, CV = cvs)

ggplot(data, aes(x = Mean, y = CV)) +
  geom_point(alpha = 0.5, color = "blue") +
  labs(title = "Scatter plot of CV versus Mean",
       x = "Mean",
       y = "Coefficient of Variation (CV)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  )

```

# $G_I^0$ Distribution

For the $G_I^0$ distribution, we also simulated the data and plotted the CV versus the mean.

```{r Plot_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Scatter plot of CV versus Mean, $\\alpha=-1.5$."}

source("../MainFunctions/gamma_sar_sample.R")
source("../MainFunctions/entropy_gamma_sar.R")
source("../MainFunctions/entropy_gI0.R")
source("../MainFunctions/gi0_sample.R")

set.seed(1234567890, kind = "Mersenne-Twister")

sample.size <- 49
R <- 10000
mu <- 1
L <- 5
alpha1 <- -1.5

means <- numeric(R)
cvs <- numeric(R)

for (r in 1:R) {
  z <- gi0_sample(mu, alpha1, L, sample.size)
  means[r] <- mean(z)
  cvs[r] <- sd(z) / mean(z)
}

# 
data <- data.frame(Mean = means, CV = cvs)

# 
ggplot(data, aes(x = Mean, y = CV)) +
  geom_point(alpha = 0.5, color = "red") +
  labs(title = "Scatter plot of CV versus Mean for gI0 distribution",
       x = "Mean",
       y = "Coefficient of Variation (CV)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  )

```
The scatter plot for the Gamma SAR distribution shows a random distribution of points, indicating that the mean and CV are independent. This confirms the property of the Gamma distribution where the sample mean and CV do not reveal any correlation.

In contrast, the scatter plot for the $G_I^0$ distribution shows a log-like pattern, indicating dependence between the mean and CV. This dependency is due to the parameter $\alpha$ in the $G_I^0$ distribution, which measures the roughness of the data. When $\alpha$ approaches $-\infty$, the $G_I^0$ distribution approximates the Gamma SAR distribution, and the mean and CV become independent. However, for values such as $\alpha = -1.5$, the mean and CV are dependent.

# Model Fitting

To model the dependency observed in the $G_I^0$ distribution, we used the following model:

$$
\text{model}(\bar{x}) = \sqrt{n} \left(1 - \exp \left(- (\beta_0 + \beta_1 \bar{x})\right) \right)
$$

where \(\beta_0\) and \(\beta_1\) are parameters, the p-value for \(\beta_1\) plays a crucial role in understanding the fit of the model and the nature of the data distribution.

```{r Plot_gi02, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Scatter plot of CV versus Mean, $\\alpha=-1.5$."}

source("../MainFunctions/gamma_sar_sample.R")
source("../MainFunctions/entropy_gamma_sar.R")
source("../MainFunctions/entropy_gI0.R")
source("../MainFunctions/gi0_sample.R")

set.seed(1234567890, kind = "Mersenne-Twister")

sample.size <- 49
R <- 10000
mu <- 1
L <- 5
alpha1 <- -1.5
means <- numeric(R)
cvs <- numeric(R)

for (r in 1:R) {
  z <- gi0_sample(mu, alpha1, L, sample.size)
  means[r] <- mean(z)
  cvs[r] <- sd(z) / mean(z)
}

data <- data.frame(Mean = means, CV = cvs)

# 
start_values <- list(beta0 = 0.5, beta1 = 0.5)
model <- nls(CV ~ sqrt(sample.size) * (1 - exp(-1.0*(beta0 + beta1 * Mean))), 
             data = data, start = start_values)

# 
summary(model)

# 
ggplot(data, aes(x = Mean, y = CV)) +
  geom_point(alpha = 0.5, color = "red") +
  stat_function(fun = function(x) sqrt(sample.size) * (1 - exp(-(coef(model)[1] + coef(model)[2] * x))),
                color = "blue", size = 1) +
  labs(title = "Scatter plot of CV versus Mean for gI0 distribution",
       x = "Mean",
       y = "Coefficient of Variation (CV)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  )

```

```{r parameters, echo=FALSE, message=FALSE, warning=FALSE}
results <- data.frame(
  Alpha = rep(c(-1.5, -3, -6, -20, -100, -200, -1000), each = 2),
  Parameter = rep(c("$\\beta_0$", "$\\beta_1$"), 7),
  Estimate = c(
    -0.04401, 0.37712,
    -0.067687, 0.219549,
    0.017231, 0.084623,
    0.055379, 0.020427,
    0.062530, 0.004908,
    0.063711, 0.002681,
    0.066356, -0.000558
  ),
  StdError = c(
    0.00266, 0.00300,
    0.002597, 0.002595,
    0.001935, 0.001931,
    0.001373, 0.001370,
    0.001215, 0.001214,
    0.001181, 0.001180,
    0.001185, 0.001184
  ),
  tvalue = c(
    -16.55, 125.71,
    -26.06, 84.62,
    8.904, 43.825,
    40.34, 14.91,
    51.450, 4.045,
    53.933, 2.272,
    56.012, -0.472
  ),
  pvalue = c(
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "<2e-16",
    "<2e-16", "5.28e-05",
    "<2e-16", "0.0231",
    "<2e-16", "0.637"
  ),
  stringsAsFactors = FALSE  # Asegúrate de que los datos de texto no se conviertan en factores
)

# Define los nombres de las columnas
colnames(results) <- c("$\\alpha$", "\\textbf{Parameter}", "\\textbf{Estimate}", "\\textbf{Std. Error}", "\\textbf{$t$ Value}", "\\textbf{$p$ Value}")

# # Formatea los números
# results$Estimate <- sprintf("$%.5f$", results$Estimate)
# results$StdError <- sprintf("$%.5f$", results$StdError)
# results$tvalue <- sprintf("$%.2f$", results$tvalue)
# results$pvalue <- ifelse(results$pvalue == "<2e-16", "< 2e-16", results$pvalue)
# 
# # Imprime los resultados para verificar
# print(results)
#results$Alpha <- sprintf("$%.1f$", results$Alpha)
results[] <- lapply(names(results), function(col_name) {
  x <- results[[col_name]]
  if (is.numeric(x)) {
    if (col_name == "Alpha") {
      formatted_numbers <- sprintf("$\\scriptstyle %d$", x)  # Estilo específico para Alpha
    } else {
      if (all(x %% 1 == 0)) {
        formatted_numbers <- sprintf("$%d$", x)
      } else {
        formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
      }
    }
    return(formatted_numbers)
  } else {
    return(x)  # Mantiene los valores de texto sin cambios
  }
})

# Genera la tabla
kable(results, caption = "Regression Results for Different Alpha Values.",
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      col.names = colnames(results),
      align = "cccccc") %>%
#  kable_styling(latex_options = "scale_down", font_size = 9) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c")

```

## Interpretation of p-Values for \(\beta_1\)

### High $p$-Value for \(\beta_1\)

- **Implication**: A high p-value (typically greater than 0.05) for \(\beta_1\) suggests that the coefficient \(\beta_1\) is not significantly different from zero. This implies that the relationship between the mean (\(\bar{x}\)) and the coefficient of variation  in the data can be explained by the Gamma SAR distribution.

- **Interpretation**: When \(\beta_1\) is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution. In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.

### Low $p$-Value for \(\beta_1\)

- **Implication**: A low p-value (typically less than 0.05) for \(\beta_1\) indicates that \(\beta_1\) is significantly different from zero. This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.

- **Interpretation**: When \(\beta_1\) is statistically significant, it implies that the data is better described by the \(G_I^0\) distribution . In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics. Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the \(G_I^0\) distribution. The parameter \(\alpha\) of the \(G_{I^0}\) distribution, which approaches $-1$ in extreme cases, captures this dependency.

### 2024-07-23 Code/R/Programs/ENL_looks.R

@@ -1,0 +1,57 @@
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Cargar la imagen SAR
+# x <- myread.ENVI(file='../../../Data/SAR/agua_300/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/agua_300/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Houston_100/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/Houston_100/Intensity_HH.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/envi_1/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/envi_1/Intensity_VV.hdr')
+
+
+window_size <- 20
+
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+enl_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar la ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    
+    
+    mean_value <- mean(as.vector(window_data))
+    variance_value <- var(as.vector(window_data))
+    
+    
+    
+    
+    enl_value <- (mean_value^2) / variance_value
+    
+    # Verificar si enl_value es un solo valor
+    if (length(enl_value) == 1) {
+      # Almacenar el valor de ENL en la matriz
+      enl_values[i, j] <- enl_value
+    }
+  }
+}
+
+
+save(enl_values, x, file = "./Data/ENL_results_lake_7.Rdata")
+
+# Cargar los valores de ENL y la imagen original desde el archivo guardado
+load("./Data/ENL_results_lake_7.Rdata")
+
+# Calcular el promedio de todos los valores de ENL
+mean_enl <- mean(enl_value, na.rm = TRUE)
+
+# Imprimir el promedio de ENL
+print(mean_enl)
+

### 2024-07-23 Code/R/Programs/p-values-MnAd-test.R

@@ -8,7 +8,8 @@ rm(list = ls())
 #load("../Programs/Data/MnAD_results_data_mexico_512.Rdata")
 #load("../Programs/Data/MnAD_results_data_lake_512.Rdata")
 #load("../Programs/Data/results_Phantom_mnad_7_z1.Rdata")
-load("../Programs/Data/results_Phantom_mnad_7_new.Rdata")
+#load("../Programs/Data/results_Phantom_mnad_7_new.Rdata")
+load("../Programs/Data/MnAD_results_data_Rotterdam_1024.Rdata")
 
 #Illinois_crops
 # meanlog <- -1.5865643
@@ -24,8 +25,13 @@ load("../Programs/Data/results_Phantom_mnad_7_new.Rdata")
 # #phantom z1
 #  meanlog <- -0.005317387
 #  sdlog <- 0.783799230
-  meanlog <- 0.004045258
-  sdlog <- 0.848081854
+
+  # meanlog <- 0.004045258
+  # sdlog <- 0.848081854
+
+#Rotterdam
+ meanlog <- -0.1654245
+ sdlog <- 0.4711747
 
 # Crear una matriz para almacenar los p-valores
 p_values_matrix <- matrix(NA, nrow = nrow(cd_values_mnad), ncol = ncol(cd_values_mnad))
@@ -59,7 +65,7 @@ plot(imagematrix(p_values_matrix >0.05))
 
 # imagematrixPNG(imagematrix(equalize(Z)), name = "mnad_Phantom_mnad_7_z1.png")
 # 
-# imagematrixPNG(imagematrix(equalize(cd_values_mnad)), name = "Phantom_mnad_7_z1.png")
+ imagematrixPNG(imagematrix(equalize(cd_values_mnad)), name = "mnad_Rotterdam.png")
 # # # # 
-# imagematrixPNG(imagematrix(p_values_matrix), name="mnad_p_values_Phantom_mnad_7_z1.png")
-# imagematrixPNG(imagematrix(p_values_matrix>0.05), name="mnad_005_Phantom_7_z1.png")
+ imagematrixPNG(imagematrix(p_values_matrix), name="mnad_p_values_Rotterdam.png")
+ imagematrixPNG(imagematrix(p_values_matrix>0.05), name="mnad_005_Rotterdam.png")

### 2024-08-15 Code/R/RMarkdown/Report_Independence_of_Mean_and_CV.Rmd
quarto files

@@
   - \usepackage{mathabx}
-
 ---
@@
 # Introduction
-we analyze the independence between the sample mean and the coefficient of variation (CV).
-If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.
-This independence is unique to the Gamma distribution and does not apply to other common distributions.
 
-In the context of identifying heterogeneity in SAR imaging data, two main models are used: the Gamma SAR distribution and the $G_I^0$ distribution.
-The Gamma SAR distribution is easier to handle and allows homogeneous areas to be identified without having to resort to the $G_I^0$ distribution.
+We analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.
+
+Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution.
+The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution.
 
@@
 # Gamma SAR Distribution
+
 For the Gamma SAR distribution, we simulated the data and plotted the CV versus the mean.
@@
 ```
+
 The scatter plot for the Gamma SAR distribution shows a random distribution of points, indicating that the mean and CV are independent.
@@
 
-where \(\beta_0\) and \(\beta_1\) are parameters, the p-value for \(\beta_1\) plays a crucial role in understanding the fit of the model and the nature of the data distribution.
+where $\beta_0$ and $\beta_1$ are parameters, the p-value for $\beta_1$ plays a crucial role in understanding the fit of the model and the nature of the data distribution.
 
@@
   ),
-  stringsAsFactors = FALSE  # Asegúrate de que los datos de texto no se conviertan en factores
+  stringsAsFactors = FALSE  # 
 )
 
-# Define los nombres de las columnas
+# 
 colnames(results) <- c("$\\alpha$", "\\textbf{Parameter}", "\\textbf{Estimate}", "\\textbf{Std. Error}", "\\textbf{$t$ Value}", "\\textbf{$p$ Value}")
 
-# # Formatea los números
-# results$Estimate <- sprintf("$%.5f$", results$Estimate)
-# results$StdError <- sprintf("$%.5f$", results$StdError)
-# results$tvalue <- sprintf("$%.2f$", results$tvalue)
-# results$pvalue <- ifelse(results$pvalue == "<2e-16", "< 2e-16", results$pvalue)
-# 
-# # Imprime los resultados para verificar
-# print(results)
 #results$Alpha <- sprintf("$%.1f$", results$Alpha)
@@
   } else {
-    return(x)  # Mantiene los valores de texto sin cambios
+    return(x)  # 
   }
@@
 
-## Interpretation of p-Values for \(\beta_1\)
+## Interpretation of p-Values for $\beta_1$
 
-### High $p$-Value for \(\beta_1\)
+### High $p$-Value for $\beta_1$
 
-- **Implication**: A high p-value (typically greater than 0.05) for \(\beta_1\) suggests that the coefficient \(\beta_1\) is not significantly different from zero.
-This implies that the relationship between the mean (\(\bar{x}\)) and the coefficient of variation  in the data can be explained by the Gamma SAR distribution.
+-   **Implication**: A high $p$-value (typically greater than 0.05) for $\beta_1$ suggests that the coefficient $\beta_1$ is not significantly different from zero.
+This implies that the relationship between the mean ($\bar{x}$) and the coefficient of variation in the data can be explained by the Gamma SAR distribution.
 
-- **Interpretation**: When \(\beta_1\) is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution.
+-   **Interpretation**: When $\beta_1$ is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution.
 In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.
 
-### Low $p$-Value for \(\beta_1\)
+### Low $p$-Value for $\beta_1$
 
-- **Implication**: A low p-value (typically less than 0.05) for \(\beta_1\) indicates that \(\beta_1\) is significantly different from zero.
+-   **Implication**: A low $p$-value (typically less than 0.05) for $\beta_1$ indicates that $\beta_1$ is significantly different from zero.
 This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.
 
-- **Interpretation**: When \(\beta_1\) is statistically significant, it implies that the data is better described by the \(G_I^0\) distribution .
+-   **Interpretation**: When $\beta_1$ is statistically significant, it implies that the data is better described by the $G_I^0$ distribution .
 In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics.
-Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the \(G_I^0\) distribution.
-The parameter \(\alpha\) of the \(G_{I^0}\) distribution, which approaches $-1$ in extreme cases, captures this dependency.
+Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the $G_I^0$ distribution.
+The parameter $\alpha$ of the $G_{I^0}$ distribution, which approaches $-1$ in extreme cases, captures this dependency.

### 2024-08-15 Text/Articles/quarto-ieee-template/template.qmd
quarto files

---
title: A Sample Article Using `quarto-ieee` for IEEE Journal and Transactions
format:
  ieee-pdf:
    keep-tex: true  
  ieee-html: default
author:
  - id: dfolio
    name: David Folio
    affiliations:
      - name: INSA Centre Val de Loire
        department: Laboratoire Prisme
        city: Bourges
        country: France
        postal-code: 18800
      - name: Unknown affiliation
    orcid: 0000-0001-9430-6091
    email: david.folio@insa-cvl.fr
    url: https://dfolio.fr/
    membership: "Member, IEEE"
    attributes:
      corresponding: true
    photo: david-folio.png
    bio: |
      Use `IEEEbiography`  with figure as  option and
      the author name as the argument followed by the biography text.
  - name: John Doe
    affiliations: 
      - name: Anonymous University
    bio: |
      Use `IEEEbiographynophoto` and the author name
      as the argument followed by the biography text.
    note: "Template created June 23, 2023; revised `r format(Sys.Date(),format='%B %d, %Y')`."
abstract: |
  This document describes the most common article elements and how to use the 
  `quarto-ieee` class with Pandoc/Quarto-Markdown to produce files that are
  suitable for submission to IEEE journals.  
  `quarto-ieee` can produce conference, journal, and technical note (correspondence) 
  papers with a suitable choice of class options. 
  It intends to generate PDF and HTML outputs that closely mimick what IEEE would generate.
keywords: [IEEE, IEEEtran, journal, Quarto, Pandoc, template]
#funding: 
funding: 
  statement: "The `quarto-ieee` template is freely available under the MIT license on github: <https://github.com/dfolio/quarto-ieee>."
pageheader:
  left: Journal XXX, Month Year
  right: 'D. Folio:  A Sample Article Using quarto-ieee'
bibliography: bibliography.bib
date: 2023-06-23
pdf: https://github.com/dfolio/quarto-ieee/blob/main/template.pdf
citation: 
  container-title: GitHUB
  page: 1-3
  type: software
  issued: 2023-06-23
  url: https://github.com/dfolio/quarto-ieee
  pdf-url: https://github.com/dfolio/quarto-ieee/template.pdf
---

# Introduction {#sec-intro}

[T]{.IEEEPARstart}[his]{}
file is intended to serve as a "sample article file"
for IEEE journal papers produced with (Pandoc/Quarto)-Markdown using `IEEEtran.cls` version 1.8b and later for the PDF output. 
It is based on `bare_jrnl_new_sample4.tex` provided by IEEE Publication Technology, Staff and available from  <https://template-selector.ieee.org/>.
The most common elements are covered in the simplified and updated instructions in `New_IEEEtran_how-to.pdf`.
For less common elements you can refer back to the original `IEEEtran_HOWTO.pdf`. 
It is assumed that the reader has a basic working knowledge of {{< latex >}} @mittelbach2023latex and of (Pandoc/Quarto)-Markdown [@MacFarlane_Pandoc; @Allaire_Quarto_2022] markup.

# The Design, Intent, and Limitations of this Templates

The `quarto-ieee` template is intended to **approximate the final look and page length of the articles/papers** either in PDF output or HTML output. 
**They are NOT intended to be the final produced work that is displayed in print or on IEEEXplore^®^**.
They will help to give the authors an approximation of the number of pages and layout that will be in the final version.

## Unsuported feature and limitations
Although most of the {{< latex >}} and `IEEEtran.cls` commands and environment are supported, 
there are some limitations when trying to export to a format other than PDF  (e.g. HTML output).
For PDF output, the reader can use the {{< latex >}} command directly. However, this may break other output formats.
\
It can be can reported the following limitations of the  `quarto-ieee` template:
- Several authors with same affiliation produce weird output. 
  In such case, it is recommended to use `note` and `tex-author-no-affiliation: true`.
- For `PDF` output
  - `quarto-ieee` use a hack to handle the `longtable` issue with  2-column {{< latex >}} documents[^issues-1023].
    But, in some cases, a page overflow may occur (see also @sec-tables).
- For `HTML` output
  - The default Quarto toc is used, so the table of contents (toc) display is not the same as on [IEEEXplore<sup>®</sup>].
  - Footnote are put at the end of document, while on [IEEEXplore<sup>®</sup>] there are placed in the accordion.
  - Figures are not placed in the accordion.
  - [IEEEXplore<sup>®</sup>] specifics (e.g. citation metrics, etc.)
  - The `HTML` output is a  Quarto citeable article @quarto-citation, so a citation appendix is automatically added to the article end.

## Contributing

If you want to improve the `quarto-ieee` template or need some specific features do not hesitate to submit Pull Request[^PR] (it is considered good practice to open an issue for discussion before working on a pull request for a new feature).

[^PR]: Go to the PR page: <https://github.com/dfolio/quarto-ieee/pulls>

# Some random text
For some of the remainder of this sample we will use dummy text to fill out paragraphs rather than use live text that may violate a copyright.
\IEEEpubidadjcol\
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis cursus nisl eget tempor porta. Proin dapibus dictum quam a commodo. Mauris congue scelerisque eros a porta. Proin blandit nulla sapien, et pretium justo dictum non. Vivamus ultricies, elit eu posuere placerat, sapien est condimentum nisl, at tincidunt tortor dolor ac ligula. Suspendisse pulvinar libero quis eros finibus sodales. Vivamus mattis est eget imperdiet luctus. Morbi eget posuere metus. Nam egestas elit lectus, eu tincidunt odio viverra sed. Sed sit amet metus rutrum, ultricies elit in, finibus felis. Integer lobortis dui ante.

Nullam mi ligula, luctus a orci ut, tincidunt varius augue. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia curae; Donec sed sem risus. Nam eleifend ultrices elit, vitae posuere tellus interdum et. Nam id nisl at elit malesuada malesuada. Suspendisse viverra ipsum libero, vel pharetra sem maximus sed. Nunc vel est fringilla, rutrum diam eu, egestas quam. Vivamus lobortis blandit velit, commodo finibus mauris. Quisque vel lacus ipsum. Pellentesque quis nulla ipsum.

Aenean in hendrerit quam. Orci varius natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt vehicula dignissim. In quis aliquet lectus, ac vestibulum elit. Quisque a magna viverra quam viverra faucibus. Nulla ornare tortor at mollis viverra. Curabitur vel porta dui. Etiam ipsum elit, egestas eget lacus nec, laoreet iaculis lacus. In iaculis risus ac tincidunt viverra. Maecenas tempor iaculis odio quis aliquet.
\
Maecenas ac posuere turpis. Fusce est dui, dapibus sed odio eget, eleifend facilisis felis. Nam gravida varius enim, ornare tincidunt urna ullamcorper ut. Donec sit amet eros ac lacus placerat rutrum ut non dolor. Nulla tincidunt nunc massa, sed euismod dui feugiat vitae. Integer tempus risus rutrum tellus interdum, eu aliquet sapien rutrum. Nunc feugiat varius lacus sed laoreet. Integer euismod tellus nisi, id scelerisque sem sagittis eu. Suspendisse at orci vel neque varius tempor nec vitae odio. Integer elementum elementum fermentum. Morbi in turpis cursus, lacinia arcu et, semper orci.

# Front matter

Most Quarto's authors and affiliations schemes  @quarto-funding are supported in the YAML front matter to render authors as requested by IEEE journals in PDF and HTML outputs.
When provided to an author, the `note` entry is rendered as a `\thanks{}` in `PDF` output (ignored in `HTML` output).
Additionally, the reader may add to an author a `photo: path/to/photograph.png` with a `bio` metadata entries to generate a `IEEEbiography`, while a sole `bio` generates a `IEEEbiographynophoto` (these features is used both in `PDF` and `HTML` outputs).
\
The `funding` entry is also used in both PDF and HTML outputs @quarto-funding.
At version v1.1.1, only the `funding.statement` is used.
Similarly, `citation` entry is supported to make the HTML output a "_citeable article_" @quarto-citation.

# Some Common Elements
## Sections and Subsections
As stated in the `IEEEtran` template enumeration of section headings is desirable, but not required.
When numbered, it should be consistent throughout the article, that is, all headings and all levels of section headings in the article should be enumerated. 
Primary headings are designated with Roman numerals, secondary with capital letters, tertiary with Arabic numbers; and quaternary with lowercase letters. 
References and Acknowledgment headings are unlike all other section headings in text. 
They are never enumerated. 
They are simply primary headings without labels, regardless of whether the other headings in the article are enumerated.

The following @sec-Markdown shows some basic usage and capabilities of `quarto-ieee`.

## Markdown basics {#sec-Markdown}
The reader can easily find many documentations on how to write using the (Pandoc/Quarto) Markdown syntax.
The `quarto-ieee` template relies mainly on the Markdown markup supported by Quarto @quarto-markdown, which is build based on Pandoc [@MacFarlane_Pandoc; @Allaire_Quarto_2022].
Below are some basic examples of usage of the Markdown markup (to save space, it is better to consult the original Quarto document `template.qmd`).

### Display equations
To write equations use `$` delimiters for inline formula or `$$` for block one.
To number the equations, it is recommended to use classic equation environments 
provided by {{< latex >}} and to use `\eqref{}` (or `\ref{}`) for cross-referencing.
For example:
\begin{equation}\label{eq:1}
{{\chi}_a}=\text{diag}\left(\frac{{\chi}}{1+n_a{\chi}},\frac{{\chi}}{1+n_b{\chi}},\frac{{\chi}}{1+n_b{\chi}}\right),
\end{equation}
\begin{align}
a & = b + c \label{eq:2} \\
c & = d + e \label{eq:3}
\end{align}

\begin{equation}\label{eq:4}
\begin{cases}
    1&=n_a+2n_b \\
    n_a&=\dfrac{1-{\varepsilon}^2}{2{\varepsilon}^3}\left(\log\left(\dfrac{1+{\varepsilon}}{1-{\varepsilon}}\right)-2{\varepsilon}\right)
\end{cases}
\end{equation}
The above equation is cross-referenced as \eqref{eq:1}, \eqref{eq:2}, \eqref{eq:3} and \eqref{eq:4}.

For now, avoid using the Quarto cross-references that use of `$$ $$` with `#eq-` label.
It works properly only for PDF output, but there are some issues with HTML[^issues-2275] output.

::: {.remark}
`quarto-ieee` template also supports the [`mhchem`](https://ctan.org/pkg/mhchem) (for chemical equation) 
and [`physics`](https://ctan.org/pkg/physics) (for flexible macros for typesetting equations) {{< latex >}} packages 
and [Mathjax extensions](https://docs.mathjax.org/en/latest/input/tex/extensions/index.html).
:::

### Theorems, Proofs and Remarks
To include a reference-able theorem, create a div with a `#thm-` label.
A theorem name is specified  via the first heading in the block. 
For example:

::: {#thm-line}

## Line

The equation of any straight line, called a linear equation, can be written as:

$$
y = mx + b
$$
:::

The theorem is cross-referenced as @thm-line.

There are a number of theorem variations supported by [Quarto](https://quarto.org/docs/authoring/cross-references.html#theorems-and-proofs), each with their own label prefix:

- `#thm-` for Theorem;
- `#lem-` for Lemma;
- `#cor-` for Corollary
- `#prp-` for Proposition;
- `#cnj-` for Conjecture;
- `#def-` for Definition;
- `#exm-` for Example;
- `#exr-` for Exercise.

The `proof`, `remark` and `solution` environments generally receive similar typesetting as theorems.
However they are not numbered (and therefore cannot be cross-referenced). To create these environments just use them as the class name of a div such as:

::: {.solution name="The solution"}
An example of solution environment.
:::

### Figures
An image with nonempty alt text will be rendered as a figure with a caption with Pandoc and Quarto.
Quarto includes a different features to simplify the use of figures and subfigures.
Here, it is recommended to use div block with `#fig-` label to embed your Figures.

:::{#fig-1}
![](fig1.png){width="30%"}

An example of figure.
:::

:::{#fig-2  layout-ncol=2}
![ ](fig1.png){#fig-2a}

![ ](fig1.png){#fig-2b}

An example with sub-figure.
:::

The figures is cross-referenced as @fig-2  and even the sub-figures as @fig-2b.

### Tables {#sec-tables}

Similarly, many kind of tables may be used with Pandoc and Quarto.
The latter also includes different features to simplify the table output.
To make tables cross-referenceable use a label with a `#tbl-` prefix. 
\
However, it is recommended to avoid using the commonly used single Markdown table known as a 'pipe table'. 
In fact, Pandoc Markdown uses the {{< latex >}} `longtable` package, which does not support the two-column mode, which is required for most `IEEEtran` journals.
`quarto-ieee` uses a hack to temporarily switch to one-column mode. 
However, this hack may break the page layout.
To overcome this issue, a basic way is to use code cells (as for @tbl-other).
Quarto is a multi-language and it uses  `Knitr` to execute `R` code and can execute  Python code blocks within Markdown.

::: {#tbl-panel layout-ncol=2}
| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: First Table {#tbl-first}

| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: Second Table {#tbl-second}

Main Caption 
:::

The Tables are cross-referenced as @tbl-panel for details, especially @tbl-second.
There is also @tbl-other.

```{r}
#| label: tbl-other
#| tbl-cap: "A table"
#| tbl.env: tabular
#| fig-pos: h

options(knitr.table.format = function() {if (knitr::is_latex_output()) 'latex' else 'pandoc'})
dt <- data.frame(Col1=c('A','B','C'),
                 Col2=c('D','E','F'),
                 Col3=c('G','H','I'))

knitr::kable(head(dt), booktabs = TRUE)
```

## Bibliography

IEEE journal should normally use IEEEtran[^bibtex] {{< bibtex >}} style.
Nevertheless, Pandoc and Quarto do support {{< bibtex >}} with natbib or biblatex. However, neither is officially recommended for normal IEEE use.
For this reason, `quarto-ieee` uses `citeproc` with the `ieee` CSL style sheet.

[^bibtex]: IEEEtran BibTeX  style support  page is: <http://www.michaelshell.org/tex/ieeetran/bibtex/>

# Conclusions
The conclusion goes here.

# Acknowledgment {-}
This should be a simple paragraph before the References to
thank those individuals and institutions who have supported
your work on this article.

[]{.appendix options="An Appendix"}

Use `[]{.appendix options="An Appendix"}` markup if you have a single appendix.
`IEEEtran` state that to do not use `\section{}` anymore after `\appendix`.

::: {.content-visible when-format="pdf"}
# References {-}
:::

[^issues-1023]: ["_[longtable not compatible with 2-column LaTeX documents](https://github.com/jgm/pandoc/issues/1023>)_",

[^issues-2275]: See the issue here <https://github.com/quarto-dev/quarto-cli/issues/2275>

[IEEEXplore<sup>®</sup>]: <https://ieeexplore.ieee.org/>

### 2024-08-15 Text/Articles/quarto-ieee-template/template.tex
quarto files

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, New_IEEEtran_how-to.pdf, bare_jrnl_new_sample4.tex,
%%*************************************************************************
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[
  journal,
]{IEEEtran}%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
%\usepackage{lmodern}
\ifPDFTeX\else
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\parindent    1.0em
\ifCLASSOPTIONcompsoc
  \parindent    1.5em
\fi
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines

\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{physics}
\usepackage[version=3]{mhchem}
\usepackage{orcidlink}
\usepackage{float}
\floatplacement{table}{htb}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Fig.}
\else
  \newcommand\figurename{Fig.}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage[skip=2pt,font=footnotesize]{caption}
%\captionsetup{format=myformat}
\makeatletter
%\setlength{\cslhangindent}{0pt plus .5pt}
\providecommand{\bibfont}{\footnotesize}
\let\CSLReferences@rig=\CSLReferences
\renewcommand{\CSLReferences}[2]{
\bibfont\settowidth\csllabelwidth{[999]}
\CSLReferences@rig{#1}{#2}
\vskip 0.3\baselineskip plus 0.1\baselineskip minus 0.1\baselineskip%
}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A Sample Article Using quarto-ieee for IEEE Journal and Transactions},
  pdfauthor={David Folio; John Doe},
  pdfkeywords={IEEE, IEEEtran, journal, Quarto, Pandoc, template},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{A Sample Article Using \texttt{quarto-ieee} for IEEE Journal and
Transactions}

\author{
\thanks{The \texttt{quarto-ieee} template is freely available under the
MIT license on github: \url{https://github.com/dfolio/quarto-ieee}.}
David Folio\orcidlink{0000-0001-9430-6091},~\IEEEmembership{Member,
IEEE}
and~John Doe%
\thanks{David Folio is with Laboratoire Prisme, INSA Centre Val de
Loire, Bourges, 18800 France%
  Corresponding author: david.folio@insa-cvl.fr
}
\thanks{Unknown affiliation}
%by-author.affiliations
\thanks{John Doe is with Anonymous University%
}
%by-author.affiliations
\thanks{Template created June 23, 2023; revised agosto 15, 2024.}
}
\begin{document}

% The paper headers
\markboth{Journal XXX, Month Year}{D. Folio: A Sample Article Using
quarto-ieee}

% use for special paper notices

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
This document describes the most common article elements and how to use
the \texttt{quarto-ieee} class with Pandoc/Quarto-Markdown to produce
files that are suitable for submission to IEEE journals.
\texttt{quarto-ieee} can produce conference, journal, and technical note
(correspondence) papers with a suitable choice of class options. It
intends to generate PDF and HTML outputs that closely mimick what IEEE
would generate.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, Quarto, Pandoc, template
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
% \IEEEpeerreviewmaketitle

\section{Introduction}\label{sec-intro}

\IEEEPARstart{T}{his} file is intended to serve as a ``sample article
file'' for IEEE journal papers produced with (Pandoc/Quarto)-Markdown
using \texttt{IEEEtran.cls} version 1.8b and later for the PDF output.
It is based on \texttt{bare\_jrnl\_new\_sample4.tex} provided by IEEE
Publication Technology, Staff and available from
\url{https://template-selector.ieee.org/}. The most common elements are
covered in the simplified and updated instructions in
\texttt{New\_IEEEtran\_how-to.pdf}. For less common elements you can
refer back to the original \texttt{IEEEtran\_HOWTO.pdf}. It is assumed
that the reader has a basic working knowledge of {\LaTeX}
\citeproc{ref-mittelbach2023latex}{{[}1{]}} and of
(Pandoc/Quarto)-Markdown \citeproc{ref-MacFarlane_Pandoc}{{[}2{]}},
\citeproc{ref-Allaire_Quarto_2022}{{[}3{]}} markup.

\section{The Design, Intent, and Limitations of this
Templates}\label{the-design-intent-and-limitations-of-this-templates}

The \texttt{quarto-ieee} template is intended to \textbf{approximate the
final look and page length of the articles/papers} either in PDF output
or HTML output. \textbf{They are NOT intended to be the final produced
work that is displayed in print or on IEEEXplore\textsuperscript{®}}.
They will help to give the authors an approximation of the number of
pages and layout that will be in the final version.

\subsection{Unsuported feature and
limitations}\label{unsuported-feature-and-limitations}

Although most of the {\LaTeX} and \texttt{IEEEtran.cls} commands and
environment are supported, there are some limitations when trying to
export to a format other than PDF (e.g.~HTML output). For PDF output,
the reader can use the {\LaTeX} command directly. However, this may
break other output formats.\\
It can be can reported the following limitations of the
\texttt{quarto-ieee} template: - Several authors with same affiliation
produce weird output. In such case, it is recommended to use
\texttt{note} and \texttt{tex-author-no-affiliation:\ true}. - For
\texttt{PDF} output - \texttt{quarto-ieee} use a hack to handle the
\texttt{longtable} issue with 2-column {\LaTeX} documents\footnote{{[}``\emph{\href{https://github.com/jgm/pandoc/issues/1023\%3E}{longtable
  not compatible with 2-column LaTeX documents}}'',}. But, in some
cases, a page overflow may occur (see also Section~\ref{sec-tables}). -
For \texttt{HTML} output - The default Quarto toc is used, so the table
of contents (toc) display is not the same as on
\href{https://ieeexplore.ieee.org/}{IEEEXplore®}. - Footnote are put at
the end of document, while on
\href{https://ieeexplore.ieee.org/}{IEEEXplore®} there are placed in the
accordion. - Figures are not placed in the accordion. -
\href{https://ieeexplore.ieee.org/}{IEEEXplore®} specifics
(e.g.~citation metrics, etc.) - The \texttt{HTML} output is a Quarto
citeable article \citeproc{ref-quarto-citation}{{[}4{]}}, so a citation
appendix is automatically added to the article end.

\subsection{Contributing}\label{contributing}

If you want to improve the \texttt{quarto-ieee} template or need some
specific features do not hesitate to submit Pull Request\footnote{Go to
  the PR page: \url{https://github.com/dfolio/quarto-ieee/pulls}} (it is
considered good practice to open an issue for discussion before working
on a pull request for a new feature).

\section{Some random text}\label{some-random-text}

For some of the remainder of this sample we will use dummy text to fill
out paragraphs rather than use live text that may violate a copyright.
\IEEEpubidadjcol\\
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis cursus
nisl eget tempor porta. Proin dapibus dictum quam a commodo. Mauris
congue scelerisque eros a porta. Proin blandit nulla sapien, et pretium
justo dictum non. Vivamus ultricies, elit eu posuere placerat, sapien
est condimentum nisl, at tincidunt tortor dolor ac ligula. Suspendisse
pulvinar libero quis eros finibus sodales. Vivamus mattis est eget
imperdiet luctus. Morbi eget posuere metus. Nam egestas elit lectus, eu
tincidunt odio viverra sed. Sed sit amet metus rutrum, ultricies elit
in, finibus felis. Integer lobortis dui ante.

Nullam mi ligula, luctus a orci ut, tincidunt varius augue. Vestibulum
ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia
curae; Donec sed sem risus. Nam eleifend ultrices elit, vitae posuere
tellus interdum et. Nam id nisl at elit malesuada malesuada. Suspendisse
viverra ipsum libero, vel pharetra sem maximus sed. Nunc vel est
fringilla, rutrum diam eu, egestas quam. Vivamus lobortis blandit velit,
commodo finibus mauris. Quisque vel lacus ipsum. Pellentesque quis nulla
ipsum.

Aenean in hendrerit quam. Orci varius natoque penatibus et magnis dis
parturient montes, nascetur ridiculus mus. Aliquam tincidunt vehicula
dignissim. In quis aliquet lectus, ac vestibulum elit. Quisque a magna
viverra quam viverra faucibus. Nulla ornare tortor at mollis viverra.
Curabitur vel porta dui. Etiam ipsum elit, egestas eget lacus nec,
laoreet iaculis lacus. In iaculis risus ac tincidunt viverra. Maecenas
tempor iaculis odio quis aliquet.\\
Maecenas ac posuere turpis. Fusce est dui, dapibus sed odio eget,
eleifend facilisis felis. Nam gravida varius enim, ornare tincidunt urna
ullamcorper ut. Donec sit amet eros ac lacus placerat rutrum ut non
dolor. Nulla tincidunt nunc massa, sed euismod dui feugiat vitae.
Integer tempus risus rutrum tellus interdum, eu aliquet sapien rutrum.
Nunc feugiat varius lacus sed laoreet. Integer euismod tellus nisi, id
scelerisque sem sagittis eu. Suspendisse at orci vel neque varius tempor
nec vitae odio. Integer elementum elementum fermentum. Morbi in turpis
cursus, lacinia arcu et, semper orci.

\section{Front matter}\label{front-matter}

Most Quarto's authors and affiliations schemes
\citeproc{ref-quarto-funding}{{[}5{]}} are supported in the YAML front
matter to render authors as requested by IEEE journals in PDF and HTML
outputs. When provided to an author, the \texttt{note} entry is rendered
as a \texttt{\textbackslash{}thanks\{\}} in \texttt{PDF} output (ignored
in \texttt{HTML} output). Additionally, the reader may add to an author
a \texttt{photo:\ path/to/photograph.png} with a \texttt{bio} metadata
entries to generate a \texttt{IEEEbiography}, while a sole \texttt{bio}
generates a \texttt{IEEEbiographynophoto} (these features is used both
in \texttt{PDF} and \texttt{HTML} outputs).\\
The \texttt{funding} entry is also used in both PDF and HTML outputs
\citeproc{ref-quarto-funding}{{[}5{]}}. At version v1.1.1, only the
\texttt{funding.statement} is used. Similarly, \texttt{citation} entry
is supported to make the HTML output a ``\emph{citeable
article}''~\citeproc{ref-quarto-citation}{{[}4{]}}.

\section{Some Common Elements}\label{some-common-elements}

\subsection{Sections and Subsections}\label{sections-and-subsections}

As stated in the \texttt{IEEEtran} template enumeration of section
headings is desirable, but not required. When numbered, it should be
consistent throughout the article, that is, all headings and all levels
of section headings in the article should be enumerated. Primary
headings are designated with Roman numerals, secondary with capital
letters, tertiary with Arabic numbers; and quaternary with lowercase
letters. References and Acknowledgment headings are unlike all other
section headings in text. They are never enumerated. They are simply
primary headings without labels, regardless of whether the other
headings in the article are enumerated.

The following Section~\ref{sec-Markdown} shows some basic usage and
capabilities of \texttt{quarto-ieee}.

\subsection{Markdown basics}\label{sec-Markdown}

The reader can easily find many documentations on how to write using the
(Pandoc/Quarto) Markdown syntax. The \texttt{quarto-ieee} template
relies mainly on the Markdown markup supported by Quarto
\citeproc{ref-quarto-markdown}{{[}6{]}}, which is build based on Pandoc
\citeproc{ref-MacFarlane_Pandoc}{{[}2{]}},
\citeproc{ref-Allaire_Quarto_2022}{{[}3{]}}. Below are some basic
examples of usage of the Markdown markup (to save space, it is better to
consult the original Quarto document \texttt{template.qmd}).

\subsubsection{Display equations}\label{display-equations}

To write equations use \texttt{\$} delimiters for inline formula or
\texttt{\$\$} for block one. To number the equations, it is recommended
to use classic equation environments provided by {\LaTeX} and to use
\texttt{\textbackslash{}eqref\{\}} (or \texttt{\textbackslash{}ref\{\}})
for cross-referencing. For example: \begin{equation}\label{eq:1}
{{\chi}_a}=\text{diag}\left(\frac{{\chi}}{1+n_a{\chi}},\frac{{\chi}}{1+n_b{\chi}},\frac{{\chi}}{1+n_b{\chi}}\right),
\end{equation} \begin{align}
a & = b + c \label{eq:2} \\
c & = d + e \label{eq:3}
\end{align}

\begin{equation}\label{eq:4}
\begin{cases}
    1&=n_a+2n_b \\
    n_a&=\dfrac{1-{\varepsilon}^2}{2{\varepsilon}^3}\left(\log\left(\dfrac{1+{\varepsilon}}{1-{\varepsilon}}\right)-2{\varepsilon}\right)
\end{cases}
\end{equation} The above equation is cross-referenced as \eqref{eq:1},
\eqref{eq:2}, \eqref{eq:3} and \eqref{eq:4}.

For now, avoid using the Quarto cross-references that use of
\texttt{\$\$\ \$\$} with \texttt{\#eq-} label. It works properly only
for PDF output, but there are some issues with HTML\footnote{See the
  issue here \url{https://github.com/quarto-dev/quarto-cli/issues/2275}}
output.

\begin{remark}
\texttt{quarto-ieee} template also supports the
\href{https://ctan.org/pkg/mhchem}{\texttt{mhchem}} (for chemical
equation) and \href{https://ctan.org/pkg/physics}{\texttt{physics}} (for
flexible macros for typesetting equations) {\LaTeX} packages and
\href{https://docs.mathjax.org/en/latest/input/tex/extensions/index.html}{Mathjax
extensions}.
\end{remark}

\subsubsection{Theorems, Proofs and
Remarks}\label{theorems-proofs-and-remarks}

To include a reference-able theorem, create a div with a \texttt{\#thm-}
label. A theorem name is specified via the first heading in the block.
For example:

\begin{theorem}[Line]\protect\hypertarget{thm-line}{}\label{thm-line}

The equation of any straight line, called a linear equation, can be
written as:

\[
y = mx + b
\]

\end{theorem}

The theorem is cross-referenced as Theorem~\ref{thm-line}.

There are a number of theorem variations supported by
\href{https://quarto.org/docs/authoring/cross-references.html\#theorems-and-proofs}{Quarto},
each with their own label prefix:

\begin{itemize}
\tightlist
\item
  \texttt{\#thm-} for Theorem;
\item
  \texttt{\#lem-} for Lemma;
\item
  \texttt{\#cor-} for Corollary
\item
  \texttt{\#prp-} for Proposition;
\item
  \texttt{\#cnj-} for Conjecture;
\item
  \texttt{\#def-} for Definition;
\item
  \texttt{\#exm-} for Example;
\item
  \texttt{\#exr-} for Exercise.
\end{itemize}

The \texttt{proof}, \texttt{remark} and \texttt{solution} environments
generally receive similar typesetting as theorems. However they are not
numbered (and therefore cannot be cross-referenced). To create these
environments just use them as the class name of a div such as:

\begin{solution}[The solution]
An example of solution environment.
\end{solution}

\subsubsection{Figures}\label{figures}

An image with nonempty alt text will be rendered as a figure with a
caption with Pandoc and Quarto. Quarto includes a different features to
simplify the use of figures and subfigures. Here, it is recommended to
use div block with \texttt{\#fig-} label to embed your Figures.

\begin{figure}

\centering{

\includegraphics[width=0.3\textwidth,height=\textheight]{fig1.png}

}

\caption{\label{fig-1}An example of figure.}

\end{figure}%

\begin{figure}

\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{fig1.png}

}

\subcaption{\label{fig-2a}}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\centering{

\includegraphics{fig1.png}

}

\subcaption{\label{fig-2b}}

\end{minipage}%

\caption{\label{fig-2}An example with sub-figure.}

\end{figure}%

The figures is cross-referenced as Fig.~\ref{fig-2} and even the
sub-figures as Fig.~\ref{fig-2b}.

\subsubsection{Tables}\label{sec-tables}

Similarly, many kind of tables may be used with Pandoc and Quarto. The
latter also includes different features to simplify the table output. To
make tables cross-referenceable use a label with a \texttt{\#tbl-}
prefix.\\
However, it is recommended to avoid using the commonly used single
Markdown table known as a `pipe table'. In fact, Pandoc Markdown uses
the {\LaTeX} \texttt{longtable} package, which does not support the
two-column mode, which is required for most \texttt{IEEEtran} journals.
\texttt{quarto-ieee} uses a hack to temporarily switch to one-column
mode. However, this hack may break the page layout. To overcome this
issue, a basic way is to use code cells (as for Table~\ref{tbl-other}).
Quarto is a multi-language and it uses \texttt{Knitr} to execute
\texttt{R} code and can execute Python code blocks within Markdown.

\begin{table}

\caption{\label{tbl-panel}Main Caption}

\begin{minipage}{0.50\linewidth}

\subcaption{\label{tbl-first}First Table}

\centering{

\begin{tabular}{lll}
\toprule
Col1 & Col2 & Col3\\
\midrule
A & B & C\\
E & F & G\\
A & G & G\\
\bottomrule
\end{tabular}

}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\subcaption{\label{tbl-second}Second Table}

\centering{

\begin{tabular}{lll}
\toprule
Col1 & Col2 & Col3\\
\midrule
A & B & C\\
E & F & G\\
A & G & G\\
\bottomrule
\end{tabular}

}

\end{minipage}%

\end{table}%

The Tables are cross-referenced as Table~\ref{tbl-panel} for details,
especially Table~\ref{tbl-second}. There is also Table~\ref{tbl-other}.

\begin{table}

\caption{\label{tbl-other}A table}

\centering{

\begin{tabular}{lll}
\toprule
Col1 & Col2 & Col3\\
\midrule
A & D & G\\
B & E & H\\
C & F & I\\
\bottomrule
\end{tabular}

}

\end{table}%

\subsection{Bibliography}\label{bibliography}

IEEE journal should normally use IEEEtran\footnote{IEEEtran BibTeX style
  support page is:
  \url{http://www.michaelshell.org/tex/ieeetran/bibtex/}}
\textsc{Bib}{\TeX} style. Nevertheless, Pandoc and Quarto do support
\textsc{Bib}{\TeX} with natbib or biblatex. However, neither is
officially recommended for normal IEEE use. For this reason,
\texttt{quarto-ieee} uses \texttt{citeproc} with the \texttt{ieee} CSL
style sheet.

\section{Conclusions}\label{conclusions}

The conclusion goes here.

\section*{Acknowledgment}\label{acknowledgment}
\addcontentsline{toc}{section}{Acknowledgment}

This should be a simple paragraph before the References to thank those
individuals and institutions who have supported your work on this
article.

\appendix[An Appendix]{}

Use \texttt{{[}{]}\{.appendix\ options="An\ Appendix"\}} markup if you
have a single appendix. \texttt{IEEEtran} state that to do not use
\texttt{\textbackslash{}section\{\}} anymore after
\texttt{\textbackslash{}appendix}.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-mittelbach2023latex}
\CSLLeftMargin{{[}1{]} }%
\CSLRightInline{F. Mittelbach and U. Fischer, \emph{The {LaTeX}
companion}, 3rd ed. {Addison Wesley Professional}, 2023. }

\bibitem[\citeproctext]{ref-MacFarlane_Pandoc}
\CSLLeftMargin{{[}2{]} }%
\CSLRightInline{J. MacFarlane, A. Krewinkel, and J. Rosenthal,
{``{Pandoc}.''} {[}Online{]}. Available:
\url{https://github.com/jgm/pandoc}}

\bibitem[\citeproctext]{ref-Allaire_Quarto_2022}
\CSLLeftMargin{{[}3{]} }%
\CSLRightInline{J. J. Allaire, C. Teague, C. Scheidegger, Y. Xie, and C.
Dervieux, {``{Quarto}.''} Jan-2022 {[}Online{]}. Available:
\url{https://github.com/quarto-dev/quarto-cli}}

\bibitem[\citeproctext]{ref-quarto-citation}
\CSLLeftMargin{{[}4{]} }%
\CSLRightInline{{``Quarto - {Creating Citeable Articles}.''}
{[}Online{]}. Available:
\url{https://quarto.org/docs/authoring/create-citeable-articles.html}.
{[}Accessed: 25-Oct-2023{]}}

\bibitem[\citeproctext]{ref-quarto-funding}
\CSLLeftMargin{{[}5{]} }%
\CSLRightInline{{``Quarto - {Front Matter}.''} {[}Online{]}. Available:
\url{https://quarto.org/docs/authoring/front-matter.html\#funding}.
{[}Accessed: 25-Oct-2023{]}}

\bibitem[\citeproctext]{ref-quarto-markdown}
\CSLLeftMargin{{[}6{]} }%
\CSLRightInline{{``Quarto - {Markdown Basics}.''} {[}Online{]}.
Available: \url{https://quarto.org/docs/authoring/markdown-basics}.
{[}Accessed: 25-Oct-2023{]}}

\end{CSLReferences}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% Uncomment when use biblatex with style=ieee
%\renewcommand{\bibfont}{\footnotesize} % for IEEE bibfont size

\pagebreak[3]
\begin{IEEEbiography}[\includegraphics{david-folio.png}]{David Folio}
Use \texttt{IEEEbiography} with figure as option and the author name as
the argument followed by the biography text.
\end{IEEEbiography}
\begin{IEEEbiographynophoto}{John Doe}
Use \texttt{IEEEbiographynophoto} and the author name as the argument
followed by the biography text.
\end{IEEEbiographynophoto}
% that's all folks
\end{document}

### 2024-08-15 Text/Reports/article-report/R0-article-report.Rmd
quarto files

--- 2024-08-15 Code/R/RMarkdown/Report_Independence_of_Mean_and_CV.Rmd
@@
 ---
+output: 
+  pdf_document:
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: ./svm-latex-ms.tex
+bibliography: ../../Common/references.bib
+header-includes:
+   - \usepackage[english]{babel}
+   - \usepackage{bm,bbm}
+   - \usepackage{mathrsfs}
+   - \usepackage{siunitx}
+   - \usepackage{graphicx}
+   - \usepackage{url}
+   - \usepackage{polski}
+   - \usepackage{booktabs}
+   - \usepackage{color}
+   - \usepackage{amsmath}
+   - \usepackage{multirow}
+   - \usepackage{subcaption}
+   - \captionsetup[sub]{position=bottom,
+        labelfont={bf, small, stretch=1.17},
+        labelsep=space,
+        textfont={small, stretch=1.5},
+        aboveskip=1pt, 
+        belowskip=1pt,
+        singlelinecheck=off,
+        justification=centering}   
+biblio-style: apsr
 title: "Report: Analysis of Independence between Sample Mean and Coefficient of Variation"
-author: ""
-date: ""
-output: pdf_document
-
-# output: 
-#   pdf_document:
-#     toc: true
-#     toc_depth: 2
-#html_document
-header-includes:
-  - \usepackage{graphicx}
-  - \usepackage{float}
-  - \usepackage{bm}
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{xcolor}
-  - \usepackage{amsmath}
-  - \usepackage{mathabx}
+thanks: ""
+author:
+- name: J. Alpala
+  affiliation: 
+abstract: "We analyze the independence between the sample mean and the coefficient of variation (CV).
+If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.
+Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution.
+The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution."
+keywords: "Gamma distribution, coefficient of variation, mean, heterogeneity, SAR "
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+fontfamily: libertine
+fontsize: 11pt
+# spacing: double
+endnote: no
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+knitr::opts_chunk$set(cache=TRUE,
+                      message=FALSE, warning=FALSE,
+                      fig.path='figs/',
+                      cache.path = '_cache/',
+                      fig.process = function(x) {
+                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
+                      if (file.rename(x, x2)) x2 else x
+                      })
 
-#knitr::opts_chunk$set(echo = TRUE)
 library(ggplot2)
@@
 library(nortest)# AD
-theme_set(theme_bw()  +
+
+theme_set(theme_minimal() +
             theme(text=element_text(family="serif"),
-                  legend.position = "top")# Gridtop , right , bottom , or left#, panel.grid = element_blank()
+                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
 )
-# Helpful for latex tables
-# library(xtable)
-# options(xtable.caption.placement='top',
-#         xtable.table.placement='!t',
-#         xtable.include.rownames=F,
-#         xtable.comment=F)
-# #library(rgl)
 
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-source("../MainFunctions/entropy_gI0.r")
-source("../MainFunctions/gi0_sample.r")
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/correa_estimator.r")
-source("../MainFunctions/ebrahimi_estimator.r")
-source("../MainFunctions/noughabi_arghami_estimator.r")
-source("../MainFunctions/vasicek_estimator.r")
-source("../MainFunctions/al_omari_1_estimator.r")
-source("../MainFunctions/al_omari_2_estimator.r")
+source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
+source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
+source("../../../Code/R/MainFunctions/entropy_gI0.R")
+source("../../../Code/R/MainFunctions/gi0_sample.R")
 
-source("../MainFunctions/bootstrap_van_es_estimator.r")
-source("../MainFunctions/bootstrap_correa_estimator.r")
-source("../MainFunctions/bootstrap_ebrahimi_estimator.r")
-source("../MainFunctions/bootstrap_noughabi_arghami_estimator.r")
-source("../MainFunctions/bootstrap_vasicek_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_1_estimator.r")
-source("../MainFunctions/bootstrap_al_omari_2_estimator.r")
+source("../../../Code/R/MainFunctions/van_es_estimator.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
+source("../../../Code/R/MainFunctions/vasicek_estimator.R")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")
+
+source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
 #The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
-source("../Programs/functions_sample_bias_mse.R")#
-
-set.seed(1234567890, kind = "Mersenne-Twister")
+source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
+source("../../../Code/R/Programs/read_ENVI_images.R")
 
@@
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'H')
-```
-
-\newcommand{\bias}{\operatorname{Bias}}
-
 # Introduction
 
-We analyze the independence between the sample mean and the coefficient of variation (CV). If the sample mean and CV are independent, the underlying data distribution must be a Gamma distribution.
+Synthetic Aperture Radar (SAR) technology has become essential for environmental monitoring and disaster management.
+It provides valuable images under various conditions, including day or night and weather situations&nbsp;\cite{Moreira2013,Mu2019}.
+However, the effective use of SAR data depends on a thorough understanding of its statistical properties because it is corrupted by speckle.
+This noise-like interference effect is inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.
 
-Two main models are used to identify heterogeneity in SAR imaging data: the Gamma SAR distribution and the $G_I^0$ distribution.
-The Gamma SAR distribution is easier to handle and identifies homogeneous areas without using the $G_I^0$ distribution.
+Speckle in intensity format is non-Gaussian. Thus, SAR data require reliable statistical models for accurate processing. 
+The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
+Gamma law as the limiting case for fully-developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.
+
+Our work aims to improve the identification of potential roughness features in SAR intensity data.
+Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions.
+
+In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous returns, particularly between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.
+
+# Background {#sec:Background}
+
+## Statistical Modeling of Intensity SAR data
+
+The primary models for intensity SAR data include the Gamma and
+$\mathcal{G}_I^0$ distributions [@Frery1997]. The first is suitable for
+fully-developed speckle and is a limiting case of the second model. This
+is interesting due to its versatility in accurately representing regions
+with different roughness properties [@Cassetti2022]. We denote
+$Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and
+$Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows
+the distributions characterized by the respective probability density
+functions (pdfs): \begin{align}
+    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
+    \intertext{ and }
+    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
+\end{align} where $\mu > 0$ is the mean, $\gamma > 0$ is the scale,
+$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of looks
+(either nominal or estimated, thus not restricted to integer values),
+$\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the
+indicator function of the set $A$.
+
+The $r$th order moments of the $\mathcal{G}_I^0$ model are
+\begin{equation}
+E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
+    \label{E:rmom}
+\end{equation} provided $\alpha <-r$, and infinite otherwise. Therefore,
+assuming $\alpha<-1$, its expected value is \begin{equation}
+    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+\end{equation}
+
+Although the $\mathcal{G}_I^0$ distribution is defined by the parameters
+$\alpha$ and $\gamma$, in the SAR literature \cite{Nascimento2010} the
+texture $\alpha$ and the mean $\mu$ are usually used.
+Reparametrizing \eqref{E:gi01} with $\mu$, and denoting this model as
+$G_I^0$ we obtain: \begin{equation}
+        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
+\end{equation}
 
@@
 
+To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.
 To evaluate this property, we simulated data from both the Gamma SAR and $G_I^0$ distributions. The goal is to determine if the mean and CV are independent for these distributions.
@@
 
-source("../MainFunctions/gamma_sar_sample.R")
+source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
 
@@
 
-source("../MainFunctions/gamma_sar_sample.R")
-source("../MainFunctions/entropy_gamma_sar.R")
-source("../MainFunctions/entropy_gI0.R")
-source("../MainFunctions/gi0_sample.R")
+source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
+source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
+source("../../../Code/R/MainFunctions/entropy_gI0.R")
+source("../../../Code/R/MainFunctions/gi0_sample.R")
 
@@
 # 
-summary(model)
+#summary(model)
 
@@
 
-## Interpretation of p-Values for $\beta_1$
-
-### High $p$-Value for $\beta_1$
-
--   **Implication**: A high $p$-value (typically greater than 0.05) for $\beta_1$ suggests that the coefficient $\beta_1$ is not significantly different from zero.
-This implies that the relationship between the mean ($\bar{x}$) and the coefficient of variation in the data can be explained by the Gamma SAR distribution.
-
--   **Interpretation**: When $\beta_1$ is not statistically significant, it supports the hypothesis that the data fits the Gamma SAR distribution.
-In this case, the sample mean and CV are independent, which is a characteristic feature of the Gamma distribution.
-
-### Low $p$-Value for $\beta_1$
-
--   **Implication**: A low $p$-value (typically less than 0.05) for $\beta_1$ indicates that $\beta_1$ is significantly different from zero.
-This suggests that the model does not fit the data well if the assumption of independence between the mean and CV is made.
-
--   **Interpretation**: When $\beta_1$ is statistically significant, it implies that the data is better described by the $G_I^0$ distribution .
-In this scenario, the sample mean and CV are dependent, reflecting a more complex relationship between these two metrics.
-Specifically, this dependency indicates that the data shows a logarithmic behavior in the relationship between the mean and CV, as described by the $G_I^0$ distribution.
-The parameter $\alpha$ of the $G_{I^0}$ distribution, which approaches $-1$ in extreme cases, captures this dependency.
+```{=html}
+<!--
+# References
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
+\setlength{\parskip}{8pt}
+\vspace*{-0.2in}
+\noindent
+-->
+```

### 2024-10-09 Text/Articles/quarto-ieee-example/ieee-template.qmd
ieee template example

---
title: A Sample Article Using `quarto-ieee` for IEEE Journal and Transactions
format:
  ieee-pdf:
    keep-tex: true  
  ieee-html: default
author:
  - id: dfolio
    name: David Folio
    affiliations:
      - name: INSA Centre Val de Loire
        department: Laboratoire Prisme
        city: Bourges
        country: France
        postal-code: 18800
      - name: Unknown affiliation
    orcid: 0000-0001-9430-6091
    email: david.folio@insa-cvl.fr
    url: https://dfolio.fr/
    membership: "Member, IEEE"
    attributes:
      corresponding: true
    #photo: david-folio.png
    #bio: |
    #  Use `IEEEbiography`  with figure as  option and
    #  the author name as the argument followed by the biography text.
  - name: John Doe
    affiliations: 
      - name: Anonymous University
    # bio: |
    #   Use `IEEEbiographynophoto` and the author name
    #   as the argument followed by the biography text.
    # note: "Template created June 23, 2023; revised `r format(Sys.Date(),format='%B %d, %Y')`."
abstract: |
  This document describes the most common article elements and how to use the 
  `quarto-ieee` class with Pandoc/Quarto-Markdown to produce files that are
  suitable for submission to IEEE journals.  
  `quarto-ieee` can produce conference, journal, and technical note (correspondence) 
  papers with a suitable choice of class options. 
  It intends to generate PDF and HTML outputs that closely mimick what IEEE would generate.
keywords: [IEEE, IEEEtran, journal, Quarto, Pandoc, template]
#funding: 
funding: 
  statement: "The `quarto-ieee` template is freely available under the MIT license on github: <https://github.com/dfolio/quarto-ieee>."
pageheader:
  left: Journal XXX, Month Year
  right: 'D. Folio:  A Sample Article Using quarto-ieee'

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[subfigure]{labelformat=parens, justification=centering}
   - \usepackage{placeins}

bibliography: bibliography.bib
date: 2023-06-23
pdf: https://github.com/dfolio/quarto-ieee/blob/main/template.pdf
citation: 
  container-title: GitHUB
  page: 1-3
  type: software
  issued: 2023-06-23
  url: https://github.com/dfolio/quarto-ieee
  pdf-url: https://github.com/dfolio/quarto-ieee/template.pdf

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)

library(fitdistrplus)
library(ggplot2)
library(reshape2)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")
)

# External functions
source("./Code/gamma_sar_sample.R")
source("./Code/ebrahimi_estimator.R")
source("./Code/al_omari_1_estimator.R")
source("./Code/bootstrap_ebrahimi_estimator.R")
source("./Code/bootstrap_al_omari_1_estimator.R")

```

# How to Use Cache in Quarto{#sec-intro}

## Global Cache
First, we need to activate the cache globally for the entire document. This means that all chunks that are executed will be cached and will not be executed again unless there is a change in the code or dependencies.

    ```{{r setup, include=FALSE}}
    knitr::opts_chunk$set(echo = FALSE, 
                                  cache=TRUE)
    ```

##  Simple Plot Example with Global Cache
This chunk uses the global cache. After the first execution, the cached result will be used, so the plot won't be regenerated unless the code or data changes.

```{r}
#| echo: true

set.seed(123)
data <- rnorm(1000)

plot(density(data), main = "plot")

```

## Cache in a Specific Chunk
This chunk caches the summary table calculation. The table will only be recalculated if the code or the data changes.

```{r}
#| cache: true
set.seed(123)
data <- rnorm(200)

plot(density(data), main = "plot", col = "red")

```

## Using if (!file.exists(...)) to Save Data

This chunk uses the if (!file.exists(...)) condition to avoid recalculating the data if the file already exists. If the file exists, it loads the saved data; otherwise, it runs the computation and saves the results to the file. This approach is useful for collaboration, where you can share the file and avoid recomputation on other machines.

```{r}
#| cache: false
#| echo: true
# This code will be displayed in the document

# Check if the data file exists and save the results

if (!file.exists("saved_data.Rdata")) {

  computed_data <- rnorm(1000)
  save(computed_data, file = "./Data/example_data.Rdata")
} else {

  # Load the saved data
  load("./Data/example_data.Rdata")
}

# 
head(computed_data)

```

## eval: false
```{r}
#| echo: true #
#| eval: false
# This chunk will display the code
# but will not execute it
set.seed(123)
data <- rnorm(1000)
plot(density(data), main = "plot")

```

# Other examples: Plot and table

In a famous paper, @BC64 introduced a family of transformations \dots

```{r}
#| label: fig-density0
#| fig-cap: Simulated data from a N(0,1) distribution.
#| fig-pos: "H"
set.seed(2022-12-20)
df <- tibble(x = rnorm(200))
df |>
  ggplot(aes(x=x)) +
  geom_density(bw = "sj") +
  geom_rug()
```

@fig-density0 shows a kernel density estimate of simulated data from a N(0,1) distribution. The sample variance is given by
$$
  s^2 = \frac{1}{n-1} \sum_{i=1}^n (x_i-\bar{x})^2 = `r round(sd(df$x), 2)`.
$$ {#eq-s2}
Note that @eq-s2 is an unbiased estimate of the variance, but it is not the maximum likelihood estimate [@Rice2007, p.269].

In table \ref{tab:time} we have ...
```{r Simulated_comparative_time, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
R <- 100
mu <- 1
B <- 1

sample.size <- c( 25, 49)
L_values <- c( 8)

bootstrap_estimators <- list(
  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
)
if (!file.exists("./Data/results_data_time1.Rdata")) {#Deactivate this line to regenerate the file
  set.seed(1234567890, kind = "Mersenne-Twister")

  all_TestStatistics <- list()
  execution_times <- list()

  for (estimator_name in names(bootstrap_estimators)) {
    TestStatistics <- list()

    for (L in L_values) {
      TestStat <- list()

      for (s in sample.size) {
        TestStat1 <- numeric(R)
        start_time <- Sys.time() # start time

        for (r in 1:R) {
          z <- gamma_sar_sample(L, mu, s)
          TestStat1[r] <- bootstrap_estimators[[estimator_name]](z, B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
        }

        TestStatistics[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)

        end_time <- Sys.time() # end time
        execution_time <- end_time - start_time # total time
        execution_times[[paste(estimator_name, L, s)]] <- execution_time # save time
      }
      all_TestStatistics[[paste(estimator_name, L)]] <- TestStatistics
    }
  }

  save(all_TestStatistics, execution_times, file = "./Data/results_data_time1.Rdata")
}

```

```{r Table_statistic_time, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_data_time1.Rdata")

combined_results <- data.frame(Estimator = character(),
                               L = numeric(),
                               SampleSize = numeric(),
                               Mean = numeric(),
                               Time = numeric())

if (length(all_TestStatistics) > 0 & length(execution_times) > 0) {
  for (estimator_name in names(bootstrap_estimators)) {
    for (L in L_values) {
      for (sample_size in sample.size) {

        if (!is.null(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]]) &
            !is.null(execution_times[[paste(estimator_name, L, sample_size)]])) {
          mean_value <- mean(all_TestStatistics[[paste(estimator_name, L)]][[as.character(sample_size)]][["Test_Statistics"]])
          time_value <- execution_times[[paste(estimator_name, L, sample_size)]]
          combined_results <- rbind(combined_results, data.frame(Estimator = estimator_name,
                                                                 L = L,
                                                                 SampleSize = sample_size,
                                                                 Mean = mean_value,
                                                                 Time = time_value))
        }
      }
    }
  }
} else {
  # 
  print("No data.")
}

# time
combined_results$Time <- gsub(" secs", "", combined_results$Time)

# 
combined_results$Time <- sprintf("%.2f", as.numeric(combined_results$Time))

#  LaTeX notation
colnames(combined_results) <- c("\\textbf{Estimator}", "$\\bm{L}$", "$\\bm{n}$", "$S(\\bm{Z}; L)$", "\\textbf{ Time} (s)")
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.5f$", x), sprintf("$\\phantom{-}%.5f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

#
table_result_combined <- knitr::kable(
  combined_results,
  caption = "Test accuracy and processing time for each bootstrap-improved estimator. ",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccc",
  escape = FALSE,
  digits = 5,
  label = "time",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  #row_spec(4,  extra_latex_after = "\\cline{3-5}")%>%
  #row_spec(12,  extra_latex_after = "\\cline{3-5}")%>%
  #row_spec(20,  extra_latex_after = "\\cline{3-5}")%>%
  #collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)#%>%
  #kable_styling(latex_options = c("repeat_header"))

print(table_result_combined)
```

# Markdown basics {#sec-Markdown}
The reader can easily find many documentations on how to write using the (Pandoc/Quarto) Markdown syntax.
The `quarto-ieee` template relies mainly on the Markdown markup supported by Quarto @quarto-markdown, which is build based on Pandoc [@MacFarlane_Pandoc; @Allaire_Quarto_2022].
Below are some basic examples of usage of the Markdown markup (to save space, it is better to consult the original Quarto document `template.qmd`).

## Figures
An image with nonempty alt text will be rendered as a figure with a caption with Pandoc and Quarto.
Quarto includes a different features to simplify the use of figures and subfigures.
Here, it is recommended to use div block with `#fig-` label to embed your Figures.

:::{#fig-1}
![](fig1.png){width="30%"}

An example of figure.
:::

:::{#fig-2  layout-ncol=2}
![ ](fig1.png){#fig-2a}

![ ](fig1.png){#fig-2b}

An example with sub-figure.
:::

The figures is cross-referenced as @fig-2  and even the sub-figures as @fig-2b.

### Tables {#sec-tables}

Similarly, many kind of tables may be used with Pandoc and Quarto.
The latter also includes different features to simplify the table output.
To make tables cross-referenceable use a label with a `#tbl-` prefix. 
\
However, it is recommended to avoid using the commonly used single Markdown table known as a 'pipe table'. 
In fact, Pandoc Markdown uses the {{< latex >}} `longtable` package, which does not support the two-column mode, which is required for most `IEEEtran` journals.
`quarto-ieee` uses a hack to temporarily switch to one-column mode. 
However, this hack may break the page layout.
To overcome this issue, a basic way is to use code cells (as for @tbl-other).
Quarto is a multi-language and it uses  `Knitr` to execute `R` code and can execute  Python code blocks within Markdown.

::: {#tbl-panel layout-ncol=2}
| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: First Table {#tbl-first}

| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: Second Table {#tbl-second}

Main Caption 
:::

The Tables are cross-referenced as @tbl-panel for details, especially @tbl-second.
There is also @tbl-other.

```{r}
#| label: tbl-other
#| tbl-cap: "A table"
#| tbl.env: tabular
#| fig-pos: h

options(knitr.table.format = function() {if (knitr::is_latex_output()) 'latex' else 'pandoc'})
dt <- data.frame(Col1=c('A','B','C'),
                 Col2=c('D','E','F'),
                 Col3=c('G','H','I'))

knitr::kable(head(dt), booktabs = TRUE)
```

## Bibliography

IEEE journal should normally use IEEEtran[^bibtex] {{< bibtex >}} style.
Nevertheless, Pandoc and Quarto do support {{< bibtex >}} with natbib or biblatex. However, neither is officially recommended for normal IEEE use.
For this reason, `quarto-ieee` uses `citeproc` with the `ieee` CSL style sheet.

[^bibtex]: IEEEtran BibTeX  style support  page is: <http://www.michaelshell.org/tex/ieeetran/bibtex/>

# Conclusions
The conclusion goes here.

# Acknowledgment {-}

[]{.appendix options="An Appendix"}

Use `[]{.appendix options="An Appendix"}` markup if you have a single appendix.
`IEEEtran` state that to do not use `\section{}` anymore after `\appendix`.

::: {.content-visible when-format="pdf"}
# References {-}
:::

[^issues-1023]: ["_[longtable not compatible with 2-column LaTeX documents](https://github.com/jgm/pandoc/issues/1023>)_",

[^issues-2275]: See the issue here <https://github.com/quarto-dev/quarto-cli/issues/2275>

[IEEEXplore<sup>®</sup>]: <https://ieeexplore.ieee.org/>

### 2024-10-09 Text/Articles/quarto-ieee-example/ieee-template.tex
ieee template example

--- 2024-08-15 Text/Articles/quarto-ieee-template/template.tex
@@
 
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{241,243,245}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+
 \providecommand{\tightlist}{%
@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \usepackage{physics}
@@
 \floatplacement{table}{htb}
+\usepackage[english]{babel}
+\usepackage{bm,bbm}
+\usepackage{mathrsfs}
+\usepackage{siunitx}
+\usepackage{graphicx}
+\usepackage{url}
+\usepackage[T1]{fontenc}
+\usepackage{polski}
+\usepackage{booktabs}
+\usepackage{color}
+\usepackage{xcolor}
+\usepackage{amsmath}
+\usepackage{multirow}
+\usepackage{subcaption}
+\captionsetup[subfigure]{labelformat=parens, justification=centering}
+\usepackage{placeins}
 \makeatletter
@@
 \newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\usepackage{amsthm}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\theoremstyle{remark}
-\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
-\newtheorem{refremark}{Remark}[section]
-\newtheorem{refsolution}{Solution}[section]
 \makeatother
@@
 %by-author.affiliations
-\thanks{Template created June 23, 2023; revised agosto 15, 2024.}
 }
@@
 
-\section{Introduction}\label{sec-intro}
+\section{How to Use Cache in Quarto}\label{sec-intro}
 
-\IEEEPARstart{T}{his} file is intended to serve as a ``sample article
-file'' for IEEE journal papers produced with (Pandoc/Quarto)-Markdown
-using \texttt{IEEEtran.cls} version 1.8b and later for the PDF output.
-It is based on \texttt{bare\_jrnl\_new\_sample4.tex} provided by IEEE
-Publication Technology, Staff and available from
-\url{https://template-selector.ieee.org/}. The most common elements are
-covered in the simplified and updated instructions in
-\texttt{New\_IEEEtran\_how-to.pdf}. For less common elements you can
-refer back to the original \texttt{IEEEtran\_HOWTO.pdf}. It is assumed
-that the reader has a basic working knowledge of {\LaTeX}
-\citeproc{ref-mittelbach2023latex}{{[}1{]}} and of
-(Pandoc/Quarto)-Markdown \citeproc{ref-MacFarlane_Pandoc}{{[}2{]}},
-\citeproc{ref-Allaire_Quarto_2022}{{[}3{]}} markup.
+\subsection{Global Cache}\label{global-cache}
 
-\section{The Design, Intent, and Limitations of this
-Templates}\label{the-design-intent-and-limitations-of-this-templates}
+First, we need to activate the cache globally for the entire document.
+This means that all chunks that are executed will be cached and will not
+be executed again unless there is a change in the code or dependencies.
 
-The \texttt{quarto-ieee} template is intended to \textbf{approximate the
-final look and page length of the articles/papers} either in PDF output
-or HTML output. \textbf{They are NOT intended to be the final produced
-work that is displayed in print or on IEEEXplore\textsuperscript{®}}.
-They will help to give the authors an approximation of the number of
-pages and layout that will be in the final version.
+\begin{Shaded}
+\begin{Highlighting}[]
+\InformationTok{\textasciigrave{}\textasciigrave{}\textasciigrave{}\{r setup, include=FALSE\}}
+\InformationTok{knitr::opts\_chunk$set(echo = FALSE, }
+\InformationTok{                              cache=TRUE)}
+\InformationTok{\textasciigrave{}\textasciigrave{}\textasciigrave{}}
+\end{Highlighting}
+\end{Shaded}
 
-\subsection{Unsuported feature and
-limitations}\label{unsuported-feature-and-limitations}
+\subsection{Simple Plot Example with Global
+Cache}\label{simple-plot-example-with-global-cache}
 
-Although most of the {\LaTeX} and \texttt{IEEEtran.cls} commands and
-environment are supported, there are some limitations when trying to
-export to a format other than PDF (e.g.~HTML output). For PDF output,
-the reader can use the {\LaTeX} command directly. However, this may
-break other output formats.\\
-It can be can reported the following limitations of the
-\texttt{quarto-ieee} template: - Several authors with same affiliation
-produce weird output. In such case, it is recommended to use
-\texttt{note} and \texttt{tex-author-no-affiliation:\ true}. - For
-\texttt{PDF} output - \texttt{quarto-ieee} use a hack to handle the
-\texttt{longtable} issue with 2-column {\LaTeX} documents\footnote{{[}``\emph{\href{https://github.com/jgm/pandoc/issues/1023\%3E}{longtable
-  not compatible with 2-column LaTeX documents}}'',}. But, in some
-cases, a page overflow may occur (see also Section~\ref{sec-tables}). -
-For \texttt{HTML} output - The default Quarto toc is used, so the table
-of contents (toc) display is not the same as on
-\href{https://ieeexplore.ieee.org/}{IEEEXplore®}. - Footnote are put at
-the end of document, while on
-\href{https://ieeexplore.ieee.org/}{IEEEXplore®} there are placed in the
-accordion. - Figures are not placed in the accordion. -
-\href{https://ieeexplore.ieee.org/}{IEEEXplore®} specifics
-(e.g.~citation metrics, etc.) - The \texttt{HTML} output is a Quarto
-citeable article \citeproc{ref-quarto-citation}{{[}4{]}}, so a citation
-appendix is automatically added to the article end.
+This chunk uses the global cache. After the first execution, the cached
+result will be used, so the plot won't be regenerated unless the code or
+data changes.
 
-\subsection{Contributing}\label{contributing}
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{1000}\NormalTok{)}
 
-If you want to improve the \texttt{quarto-ieee} template or need some
-specific features do not hesitate to submit Pull Request\footnote{Go to
-  the PR page: \url{https://github.com/dfolio/quarto-ieee/pulls}} (it is
-considered good practice to open an issue for discussion before working
-on a pull request for a new feature).
+\FunctionTok{plot}\NormalTok{(}\FunctionTok{density}\NormalTok{(data), }\AttributeTok{main =} \StringTok{"plot"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
-\section{Some random text}\label{some-random-text}
+\includegraphics{ieee-template_files/figure-pdf/unnamed-chunk-1-1.pdf}
 
-For some of the remainder of this sample we will use dummy text to fill
-out paragraphs rather than use live text that may violate a copyright.
-\IEEEpubidadjcol\\
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis cursus
-nisl eget tempor porta. Proin dapibus dictum quam a commodo. Mauris
-congue scelerisque eros a porta. Proin blandit nulla sapien, et pretium
-justo dictum non. Vivamus ultricies, elit eu posuere placerat, sapien
-est condimentum nisl, at tincidunt tortor dolor ac ligula. Suspendisse
-pulvinar libero quis eros finibus sodales. Vivamus mattis est eget
-imperdiet luctus. Morbi eget posuere metus. Nam egestas elit lectus, eu
-tincidunt odio viverra sed. Sed sit amet metus rutrum, ultricies elit
-in, finibus felis. Integer lobortis dui ante.
+\subsection{Cache in a Specific Chunk}\label{cache-in-a-specific-chunk}
 
-Nullam mi ligula, luctus a orci ut, tincidunt varius augue. Vestibulum
-ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia
-curae; Donec sed sem risus. Nam eleifend ultrices elit, vitae posuere
-tellus interdum et. Nam id nisl at elit malesuada malesuada. Suspendisse
-viverra ipsum libero, vel pharetra sem maximus sed. Nunc vel est
-fringilla, rutrum diam eu, egestas quam. Vivamus lobortis blandit velit,
-commodo finibus mauris. Quisque vel lacus ipsum. Pellentesque quis nulla
-ipsum.
+This chunk caches the summary table calculation. The table will only be
+recalculated if the code or the data changes.
 
-Aenean in hendrerit quam. Orci varius natoque penatibus et magnis dis
-parturient montes, nascetur ridiculus mus. Aliquam tincidunt vehicula
-dignissim. In quis aliquet lectus, ac vestibulum elit. Quisque a magna
-viverra quam viverra faucibus. Nulla ornare tortor at mollis viverra.
-Curabitur vel porta dui. Etiam ipsum elit, egestas eget lacus nec,
-laoreet iaculis lacus. In iaculis risus ac tincidunt viverra. Maecenas
-tempor iaculis odio quis aliquet.\\
-Maecenas ac posuere turpis. Fusce est dui, dapibus sed odio eget,
-eleifend facilisis felis. Nam gravida varius enim, ornare tincidunt urna
-ullamcorper ut. Donec sit amet eros ac lacus placerat rutrum ut non
-dolor. Nulla tincidunt nunc massa, sed euismod dui feugiat vitae.
-Integer tempus risus rutrum tellus interdum, eu aliquet sapien rutrum.
-Nunc feugiat varius lacus sed laoreet. Integer euismod tellus nisi, id
-scelerisque sem sagittis eu. Suspendisse at orci vel neque varius tempor
-nec vitae odio. Integer elementum elementum fermentum. Morbi in turpis
-cursus, lacinia arcu et, semper orci.
+\includegraphics{ieee-template_files/figure-pdf/unnamed-chunk-2-1.pdf}
 
-\section{Front matter}\label{front-matter}
+\subsection{Using if (!file.exists(\ldots)) to Save
+Data}\label{using-if-file.exists-to-save-data}
 
-Most Quarto's authors and affiliations schemes
-\citeproc{ref-quarto-funding}{{[}5{]}} are supported in the YAML front
-matter to render authors as requested by IEEE journals in PDF and HTML
-outputs. When provided to an author, the \texttt{note} entry is rendered
-as a \texttt{\textbackslash{}thanks\{\}} in \texttt{PDF} output (ignored
-in \texttt{HTML} output). Additionally, the reader may add to an author
-a \texttt{photo:\ path/to/photograph.png} with a \texttt{bio} metadata
-entries to generate a \texttt{IEEEbiography}, while a sole \texttt{bio}
-generates a \texttt{IEEEbiographynophoto} (these features is used both
-in \texttt{PDF} and \texttt{HTML} outputs).\\
-The \texttt{funding} entry is also used in both PDF and HTML outputs
-\citeproc{ref-quarto-funding}{{[}5{]}}. At version v1.1.1, only the
-\texttt{funding.statement} is used. Similarly, \texttt{citation} entry
-is supported to make the HTML output a ``\emph{citeable
-article}''~\citeproc{ref-quarto-citation}{{[}4{]}}.
+This chunk uses the if (!file.exists(\ldots)) condition to avoid
+recalculating the data if the file already exists. If the file exists,
+it loads the saved data; otherwise, it runs the computation and saves
+the results to the file. This approach is useful for collaboration,
+where you can share the file and avoid recomputation on other machines.
 
-\section{Some Common Elements}\label{some-common-elements}
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# This code will be displayed in the document}
 
-\subsection{Sections and Subsections}\label{sections-and-subsections}
+\CommentTok{\# Check if the data file exists and save the results}
 
-As stated in the \texttt{IEEEtran} template enumeration of section
-headings is desirable, but not required. When numbered, it should be
-consistent throughout the article, that is, all headings and all levels
-of section headings in the article should be enumerated. Primary
-headings are designated with Roman numerals, secondary with capital
-letters, tertiary with Arabic numbers; and quaternary with lowercase
-letters. References and Acknowledgment headings are unlike all other
-section headings in text. They are never enumerated. They are simply
-primary headings without labels, regardless of whether the other
-headings in the article are enumerated.
+\ControlFlowTok{if}\NormalTok{ (}\SpecialCharTok{!}\FunctionTok{file.exists}\NormalTok{(}\StringTok{"saved\_data.Rdata"}\NormalTok{)) \{}
 
-The following Section~\ref{sec-Markdown} shows some basic usage and
-capabilities of \texttt{quarto-ieee}.
+\NormalTok{  computed\_data }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{1000}\NormalTok{)}
+  \FunctionTok{save}\NormalTok{(computed\_data, }\AttributeTok{file =} \StringTok{"./Data/example\_data.Rdata"}\NormalTok{)}
+\NormalTok{\} }\ControlFlowTok{else}\NormalTok{ \{}
 
-\subsection{Markdown basics}\label{sec-Markdown}
+  \CommentTok{\# Load the saved data}
+  \FunctionTok{load}\NormalTok{(}\StringTok{"./Data/example\_data.Rdata"}\NormalTok{)}
+\NormalTok{\}}
+
+\CommentTok{\# }
+\FunctionTok{head}\NormalTok{(computed\_data)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+[1]  2.1988103  1.3124130 -0.2651451  0.5431941 -0.4143399 -0.4762469
+\end{verbatim}
+
+\subsection{eval: false}\label{eval-false}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# This chunk will display the code}
+\CommentTok{\# but will not execute it}
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{rnorm}\NormalTok{(}\DecValTok{1000}\NormalTok{)}
+\FunctionTok{plot}\NormalTok{(}\FunctionTok{density}\NormalTok{(data), }\AttributeTok{main =} \StringTok{"plot"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\section{Other examples: Plot and
+table}\label{other-examples-plot-and-table}
+
+In a famous paper, \citeproc{ref-BC64}{{[}1{]}} introduced a family of
+transformations \dots
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{ieee-template_files/figure-pdf/fig-density0-1.pdf}
+
+}
+
+\caption{\label{fig-density0}Simulated data from a N(0,1) distribution.}
+
+\end{figure}%
+
+Fig.~\ref{fig-density0} shows a kernel density estimate of simulated
+data from a N(0,1) distribution. The sample variance is given by
+\begin{equation}\phantomsection\label{eq-s2}{
+  s^2 = \frac{1}{n-1} \sum_{i=1}^n (x_i-\bar{x})^2 = 0.98.
+}\end{equation} Note that \ref{eq-s2} is an unbiased estimate of the
+variance, but it is not the maximum likelihood estimate
+\citeproc{ref-Rice2007}{{[}2, p. 269{]}}.
+
+In table \ref{tab:time} we have \ldots{}
+
+\begin{table}[H]
+\centering\centering
+\caption{\label{tab:time}Test accuracy and processing time for each bootstrap-improved estimator. }
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
+\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
+\toprule
+\multicolumn{1}{c}{\textbf{Estimator}} & \multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{$S(\bm{Z}; L)$} & \multicolumn{1}{c}{\textbf{ Time} (s)}\\
+\midrule
+$\widetilde{H}_{\text{AO}}$ & $8$ & $25$ & $-0.06556$ & 0.03\\
+$\widetilde{H}_{\text{AO}}$ & $8$ & $49$ & $-0.00231$ & 0.01\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\section{Markdown basics}\label{sec-Markdown}
 
@@
 relies mainly on the Markdown markup supported by Quarto
-\citeproc{ref-quarto-markdown}{{[}6{]}}, which is build based on Pandoc
-\citeproc{ref-MacFarlane_Pandoc}{{[}2{]}},
-\citeproc{ref-Allaire_Quarto_2022}{{[}3{]}}. Below are some basic
+\citeproc{ref-quarto-markdown}{{[}3{]}}, which is build based on Pandoc
+\citeproc{ref-MacFarlane_Pandoc}{{[}4{]}},
+\citeproc{ref-Allaire_Quarto_2022}{{[}5{]}}. Below are some basic
 examples of usage of the Markdown markup (to save space, it is better to
@@
 
-\subsubsection{Display equations}\label{display-equations}
-
-To write equations use \texttt{\$} delimiters for inline formula or
-\texttt{\$\$} for block one. To number the equations, it is recommended
-to use classic equation environments provided by {\LaTeX} and to use
-\texttt{\textbackslash{}eqref\{\}} (or \texttt{\textbackslash{}ref\{\}})
-for cross-referencing. For example: \begin{equation}\label{eq:1}
-{{\chi}_a}=\text{diag}\left(\frac{{\chi}}{1+n_a{\chi}},\frac{{\chi}}{1+n_b{\chi}},\frac{{\chi}}{1+n_b{\chi}}\right),
-\end{equation} \begin{align}
-a & = b + c \label{eq:2} \\
-c & = d + e \label{eq:3}
-\end{align}
-
-\begin{equation}\label{eq:4}
-\begin{cases}
-    1&=n_a+2n_b \\
-    n_a&=\dfrac{1-{\varepsilon}^2}{2{\varepsilon}^3}\left(\log\left(\dfrac{1+{\varepsilon}}{1-{\varepsilon}}\right)-2{\varepsilon}\right)
-\end{cases}
-\end{equation} The above equation is cross-referenced as \eqref{eq:1},
-\eqref{eq:2}, \eqref{eq:3} and \eqref{eq:4}.
-
-For now, avoid using the Quarto cross-references that use of
-\texttt{\$\$\ \$\$} with \texttt{\#eq-} label. It works properly only
-for PDF output, but there are some issues with HTML\footnote{See the
-  issue here \url{https://github.com/quarto-dev/quarto-cli/issues/2275}}
-output.
-
-\begin{remark}
-\texttt{quarto-ieee} template also supports the
-\href{https://ctan.org/pkg/mhchem}{\texttt{mhchem}} (for chemical
-equation) and \href{https://ctan.org/pkg/physics}{\texttt{physics}} (for
-flexible macros for typesetting equations) {\LaTeX} packages and
-\href{https://docs.mathjax.org/en/latest/input/tex/extensions/index.html}{Mathjax
-extensions}.
-\end{remark}
-
-\subsubsection{Theorems, Proofs and
-Remarks}\label{theorems-proofs-and-remarks}
-
-To include a reference-able theorem, create a div with a \texttt{\#thm-}
-label. A theorem name is specified via the first heading in the block.
-For example:
-
-\begin{theorem}[Line]\protect\hypertarget{thm-line}{}\label{thm-line}
-
-The equation of any straight line, called a linear equation, can be
-written as:
-
-\[
-y = mx + b
-\]
-
-\end{theorem}
-
-The theorem is cross-referenced as Theorem~\ref{thm-line}.
-
-There are a number of theorem variations supported by
-\href{https://quarto.org/docs/authoring/cross-references.html\#theorems-and-proofs}{Quarto},
-each with their own label prefix:
-
-\begin{itemize}
-\tightlist
-\item
-  \texttt{\#thm-} for Theorem;
-\item
-  \texttt{\#lem-} for Lemma;
-\item
-  \texttt{\#cor-} for Corollary
-\item
-  \texttt{\#prp-} for Proposition;
-\item
-  \texttt{\#cnj-} for Conjecture;
-\item
-  \texttt{\#def-} for Definition;
-\item
-  \texttt{\#exm-} for Example;
-\item
-  \texttt{\#exr-} for Exercise.
-\end{itemize}
-
-The \texttt{proof}, \texttt{remark} and \texttt{solution} environments
-generally receive similar typesetting as theorems. However they are not
-numbered (and therefore cannot be cross-referenced). To create these
-environments just use them as the class name of a div such as:
-
-\begin{solution}[The solution]
-An example of solution environment.
-\end{solution}
-
-\subsubsection{Figures}\label{figures}
+\subsection{Figures}\label{figures}
 
@@
 
-This should be a simple paragraph before the References to thank those
-individuals and institutions who have supported your work on this
-article.
-
 \appendix[An Appendix]{}
@@
 \begin{CSLReferences}{0}{0}
-\bibitem[\citeproctext]{ref-mittelbach2023latex}
+\bibitem[\citeproctext]{ref-BC64}
 \CSLLeftMargin{{[}1{]} }%
-\CSLRightInline{F. Mittelbach and U. Fischer, \emph{The {LaTeX}
-companion}, 3rd ed. {Addison Wesley Professional}, 2023. }
+\CSLRightInline{G. E. P. Box and D. R. Cox, {``An analysis of
+transformations,''} \emph{Journal of the Royal Statistical Society,
+Series B}, vol. 26, no. 2, pp. 211--252, 1964. }
+
+\bibitem[\citeproctext]{ref-Rice2007}
+\CSLLeftMargin{{[}2{]} }%
+\CSLRightInline{J. A. Rice, \emph{Mathematical statistics and data
+analysis}, 3rd edition. Duxbury, 2007. }
+
+\bibitem[\citeproctext]{ref-quarto-markdown}
+\CSLLeftMargin{{[}3{]} }%
+\CSLRightInline{{``Quarto - {Markdown Basics}.''} {[}Online{]}.
+Available: \url{https://quarto.org/docs/authoring/markdown-basics}.
+{[}Accessed: 25-Oct-2023{]}}
 
 \bibitem[\citeproctext]{ref-MacFarlane_Pandoc}
-\CSLLeftMargin{{[}2{]} }%
+\CSLLeftMargin{{[}4{]} }%
 \CSLRightInline{J. MacFarlane, A. Krewinkel, and J. Rosenthal,
@@
 \bibitem[\citeproctext]{ref-Allaire_Quarto_2022}
-\CSLLeftMargin{{[}3{]} }%
+\CSLLeftMargin{{[}5{]} }%
 \CSLRightInline{J. J. Allaire, C. Teague, C. Scheidegger, Y. Xie, and C.
@@
 \url{https://github.com/quarto-dev/quarto-cli}}
-
-\bibitem[\citeproctext]{ref-quarto-citation}
-\CSLLeftMargin{{[}4{]} }%
-\CSLRightInline{{``Quarto - {Creating Citeable Articles}.''}
-{[}Online{]}. Available:
-\url{https://quarto.org/docs/authoring/create-citeable-articles.html}.
-{[}Accessed: 25-Oct-2023{]}}
-
-\bibitem[\citeproctext]{ref-quarto-funding}
-\CSLLeftMargin{{[}5{]} }%
-\CSLRightInline{{``Quarto - {Front Matter}.''} {[}Online{]}. Available:
-\url{https://quarto.org/docs/authoring/front-matter.html\#funding}.
-{[}Accessed: 25-Oct-2023{]}}
-
-\bibitem[\citeproctext]{ref-quarto-markdown}
-\CSLLeftMargin{{[}6{]} }%
-\CSLRightInline{{``Quarto - {Markdown Basics}.''} {[}Online{]}.
-Available: \url{https://quarto.org/docs/authoring/markdown-basics}.
-{[}Accessed: 25-Oct-2023{]}}
 
@@
 \pagebreak[3]
-\begin{IEEEbiography}[\includegraphics{david-folio.png}]{David Folio}
-Use \texttt{IEEEbiography} with figure as option and the author name as
-the argument followed by the biography text.
-\end{IEEEbiography}
-\begin{IEEEbiographynophoto}{John Doe}
-Use \texttt{IEEEbiographynophoto} and the author name as the argument
-followed by the biography text.
-\end{IEEEbiographynophoto}
 % that's all folks

### 2025-01-02 Code/R/RMarkdown/Report_goodness-of-fit.Rmd
new codes

@@
 
-load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
+#load("../Programs/Data/results_data_Flevoland_cv_300_5_v2.Rdata")
 #load("../Programs/Data/results_data_Ottawa_cd_mnad_matrix_512_7.Rdata")#save(difference_values, x, file = "./Data/results_data_otawa_512_7_correa_300b.Rdata")
@@
 #save(p_values_matrix, epsilon_matrix, file = "./Data/results_pvalue_epsilon.Rdata")
-load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
+#load("../Programs/Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
+#save(p_values_matrix, z_scores_matrix, file = "./Data/results_pvalue_Flevoland_300_7_v6.Rdata")
+load("../Programs/Data/results_Phantom_4_renyi_B200_w9_08_L5.Rdata")
 #x1<-as.vector(epsilon_matrix)

### 2025-01-02 Code/R/RMarkdown/report-gamma-independence.Rmd
new codes

---
title: "On a Characterization of the Gamma Distribution"
output: pdf_document
date: "2024-10-21"

header-includes:
  - \usepackage[english]{babel}
  - \usepackage{bm,bbm}
  - \usepackage{mathrsfs}
  - \usepackage{siunitx}
  - \usepackage{graphicx}
  - \usepackage{url}
  # - \usepackage[T1]{fontenc} hay que desactivar este comando para que aprezacan los simbolos en letras griegas
  - \usepackage{polski}
  - \usepackage{booktabs}
  - \usepackage{color}
  - \usepackage{xcolor}
  - \usepackage{amsmath}
  - \usepackage{amsfonts}
  #- \usepackage{unicode-math} 
  - \usepackage{multirow}
  - \usepackage{subcaption}
  - \captionsetup[subfigure]{labelformat=parens, justification=centering}
  - \usepackage{placeins}
  - \usepackage{amsthm}
  - \newtheorem{definition}{Definition}
  - \newtheorem{lemma}{Lemma}
  - \newtheorem{theorem}{Theorem}
  - \newtheorem{example}{Example}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "On a Characterization of the Gamma Distribution"
author: "Tea-Yuan Hwang and Chin-Yuan Hu"
output: pdf_document
---

# Abstract

Let \( n \geq 3 \) and let \( X_1, \dots, X_n \) be positive independent and identically distributed (i.i.d.) random variables whose common distribution function has a continuous p.d.f. Using earlier work of the authors and a method due to Anosov for solving certain integro-functional equations, it is shown that the independence of the sample mean \( \bar{X}_n \) and the sample coefficient of variation \( V_n \) is equivalent to the fact that \( f \) is a gamma distribution. While the proof is of methodological interest, this conclusion can also be derived without assumptions by appealing to the Laplace-Stieltjes transform.

# Keywords

Characterization, Gamma distribution, Coefficient of variation.

# 1. Introduction and Main Result

Two of the statistics most often used in both theory and applied work are the sample mean \( \bar{X}_n \) and the sample standard deviation \( S_n \). It is well known that the independence of \( \bar{X}_n \) and \( S_n \) (based on a random sample) characterizes the normal distribution.

Various results characterizing the parent distribution through properties of statistics can be found in Kagan et al. (1973), Johnson and Kotz (1970), Lukacs and Laha (1964), and the references therein. However, characterization problems based on the properties of the coefficient of variation \( V_n = S_n / \bar{X}_n \) have seldom been studied.

In this context, we establish the following:

### Theorem
Let \( n \geq 3 \) and let \( X_1, \dots, X_n \) be positive i.i.d. random variables whose common distribution function has a probability density function \( f(x) \). Then the independence of the sample mean \( \bar{X}_n \) and the sample coefficient of variation \( V_n = S_n / \bar{X}_n \) is equivalent to the fact that \( f(x) \) is a gamma distribution.

# 2. Three Lemmas

We now present three lemmas that are used in the proof of the main theorem.
# 2. Three Lemmas

For convenience of citation in the proof of the three lemmas used for proving the main theorem, we cite certain recent results obtained by Hwang and Hu (1994) as follows:

Define a non-linear transformation \( (x_1, \dots, x_n) \rightarrow (t_1, \dots, t_{n-2}, \bar{x}_n, v_n) \), where

\begin{equation}
\label{Eq:2.1}
t_i = \left[ \frac{n - i + 1}{(n-1)(n-i)} \right]^{1/2} \cdot \left[ \frac{x_i - \bar{x}_n}{s_n} + \frac{1}{n - i + 1} \sum_{k=1}^{i-1} \frac{x_k - \bar{x}_n}{s_n} \right], \quad 1 \leq i \leq n-2
\end{equation}

\[
\bar{x}_n = \frac{1}{n} \sum_{i=1}^{n} x_i, \quad v_n = \frac{S_n}{\bar{x}_n}
\]

The summation in \eqref{Eq:2.1} is taken as zero for \( i = 1 \), and \( s_n \) is the standard deviation of \( x_1, \dots, x_n \). Then, Theorem 2.2 of Hwang and Hu (1994) gives

\[
\lambda_i(t) = \left[ \frac{(n - i)(n - 1)}{n - i + 1} \right]^{1/2} \cdot t_i - \sum_{k=1}^{i-1} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k, \quad 1 \leq i \leq n-2
\]

\begin{equation}
\label{Eq:2.2}
\lambda_{n-1}(t) = - \left[ \frac{(n-1) \cdot f_{n-2}}{2} \right]^{1/2} - \sum_{k=1}^{n-2} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k
\end{equation}

\[
\lambda_n(t) = \left[ \frac{(n-1) \cdot f_{n-2}}{2} \right]^{1/2} - \sum_{k=1}^{n-2} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k
\]

where \( \lambda_i(t) = \frac{x_i - \bar{x}_n}{s_n} \) and \( f_{n-2} = 1 - t_1^2 - \dots - t_{n-2}^2 \). Thus, we have:

\begin{equation}
\label{Eq:2.3}
\sum_{i=1}^{n} \lambda_i(t) = 0, \quad \sum_{i=1}^{n} \lambda_i^2(t) = n - 1
\end{equation}

\begin{equation}
\label{Eq:2.4}
x_i = \bar{x}_n [ v_n \cdot \lambda_i(t) + 1 ], \quad 1 \leq i \leq n
\end{equation}

We have then:

### Lemma 2.1
Let \( n \geq 3 \) and let \( X_1, \dots, X_n \) be positive i.i.d. random variables having a p.d.f. \( f(x) \), and let \( \bar{X}_n \) and \( V_n \) be the sample mean and the sample coefficient of variation. Then, the joint p.d.f. \( f(x, v) \) of \( (\bar{X}_n, V_n) \) is

\[
f(x, v) = c_n \cdot x^{n-1} \cdot v^{n-2} \cdot \int_{B_{v,n}} \prod_{i=1}^{n-1} f(x(v \lambda_i(t) + 1)) d\mu(t)
\]
for \( x > 0 \) and \( 0 < v < \sqrt{n} \), and zero otherwise, where \( c_n = n! \sqrt{n} (n - 1)^{(n - 1)/2} \), the functions \( \lambda_i(t) \) are defined as in (2.2), \( d\mu(t) = f_{n-2}^{-1/2} dt_1 \dots dt_{n-2} \), and the set \( B_{v,n} \) depends on \( v \), for \( 0 < v < \sqrt{n} \), as follows:

\begin{equation}
\label{Eq:2.0}
B_{v,n} = \left\{ t :
\begin{aligned}
\max \left( - \frac{\sqrt{n}}{(n - 1) v}, -1 \right) & \leq t_1 \leq - \frac{1}{n - 1}, \\
\max \left( \frac{n - k + 2}{n - k} \right)^{1/2} \cdot t_{k-1} \cdot f_{k-1}^{1/2} & \leq t_k \leq - \frac{f_{k-1}^{1/2}}{n - k}, \quad 2 \leq k \leq n - 2
\end{aligned}
\right\}
\end{equation}
and \( f_i = 1 - t_1^2 - \dots - t_i^2, \quad 1 \leq i \leq n - 2 \).

### Lemma 2.2
Under the condition of Lemma 2.1, assume that \( \bar{X}_n \) and \( V_n \) are independent. Then, the p.d.f.'s of \( \bar{X}_n \) and \( V_n \) are respectively given by:

\[
f_{\bar{X}_n}(x) = a_n \cdot x^{n-1} \cdot \left[ f(x) \right]^n, \quad x > 0
\]
and zero otherwise, where \( a_n \) is a normalizing constant;

\[
f_{V_n}(v) = b_n \cdot v^{n-2} \cdot \int_{B_{v,n}} \prod_{i=1}^{n-1} f(v\lambda_i(t) + 1) d\mu(t), \quad 0 < v < \sqrt{n}
\]
and zero otherwise, where \( b_n \) is a normalizing constant, and the \( \lambda_i(t) \) and \( B_{v,n} \) are defined as in \eqref{Eq:2.2} and \eqref{Eq:2.0} respectively.

Define a non-linear transformation \( (x_1, \dots, x_n) \rightarrow (t_1, \dots, t_{n-2}, \bar{x}_n, v_n) \), where

\begin{equation}
\label{Eq:2.1}
t_i = \left[ \frac{n - i + 1}{(n-1)(n-i)} \right]^{1/2} \cdot \left[ \frac{x_i - \bar{x}_n}{s_n} + \frac{1}{n - i + 1} \sum_{k=1}^{i-1} \frac{x_k - \bar{x}_n}{s_n} \right], \quad 1 \leq i \leq n-2
\end{equation}

\[
\bar{x}_n = \frac{1}{n} \sum_{i=1}^{n} x_i, \quad v_n = \frac{S_n}{\bar{x}_n}
\]

The summation in \eqref{Eq:2.1} is taken as zero for \( i = 1 \), and \( s_n \) is the standard deviation of \( x_1, \dots, x_n \). Then, Theorem 2.2 of Hwang and Hu (1994) gives

\[
\lambda_i(t) = \left[ \frac{(n - i)(n - 1)}{n - i + 1} \right]^{1/2} \cdot t_i - \sum_{k=1}^{i-1} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k, \quad 1 \leq i \leq n-2
\]

\begin{equation}
\label{Eq:2.2}
\lambda_{n-1}(t) = - \left[ \frac{(n-1) \cdot f_{n-2}}{2} \right]^{1/2} - \sum_{k=1}^{n-2} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k
\end{equation}

\[
\lambda_n(t) = \left[ \frac{(n-1) \cdot f_{n-2}}{2} \right]^{1/2} - \sum_{k=1}^{n-2} \left[ \frac{n-1}{(n-k)(n-k+1)} \right]^{1/2} \cdot t_k
\]

where \( \lambda_i(t) = \frac{x_i - \bar{x}_n}{s_n} \) and \( f_{n-2} = 1 - t_1^2 - \dots - t_{n-2}^2 \). Thus, we have:

\begin{equation}
\label{Eq:2.3}
\sum_{i=1}^{n} \lambda_i(t) = 0, \quad \sum_{i=1}^{n} \lambda_i^2(t) = n - 1
\end{equation}

\begin{equation}
\label{Eq:2.4}
x_i = \bar{x}_n [ v_n \cdot \lambda_i(t) + 1 ], \quad 1 \leq i \leq n
\end{equation}

### Proof
Let \( f_{\bar{X}_n}(x) \) and \( f_{V_n}(v) \) be the p.d.f.'s of \( \bar{X}_n \) and \( V_n \) respectively; it follows from Lemma 2.1 and the independence of \( \bar{X}_n \) and \( V_n \) that the joint p.d.f. of \( (\bar{X}_n, V_n) \) must be equal to the product of their densities:

\[
f_{\bar{X}_n}(x) \cdot f_{V_n}(v) = c_n \cdot x^{n-1} \cdot v^{n-2} \cdot \int_{B_{v,n}} \prod_{i=1}^{n-1} f(x(v\lambda_i(t) + 1)) d\mu(t)
\]
for all \( x > 0 \) and \( 0 < v < \sqrt{n} \). We see that \( f_{\bar{X}_n}(1) \neq 0 \), since otherwise the right side of the equation would vanish for all \( 0 < v < \sqrt{n} \), which is impossible. Set \( x = 1 \) in the equation. Then, we obtain the expression for \( f_{V_n}(v) \) as given in (2.8).

Now substituting (2.8) in the equation, and dividing both sides of the equation by \( v^{n-2} \), we get

\[
f_{\bar{X}_n}(x) \cdot b_n \int \cdots \int_{B_{v,n}} \prod_{i=1}^{n-1} f(v \lambda_i(t) + 1) d\mu(t)
= c_n \cdot x^{n-1} \int \cdots \int_{B_{v,n}} \prod_{i=1}^{n-1} f(x \lambda_i(t) + 1) d\mu(t).
\]

Note that if the variable \( v \) is in the neighborhood of origin, say \( 0 < v < \sqrt{n}/(n - 1) \), then the domain of integration \( B_{v,n} \) is independent of \( v \); first by using this fact, and then letting \( v \rightarrow 0^+ \) in the new equation, we obtain the expression for \( f_{\bar{X}_n}(x) \) as given in (2.7). Thus, we have established Lemma 2.2. \(\square\)

### Lemma 2.3 (An integro-functional equation)

Under the conditions of Lemma 2.2, the following integro-functional equation holds:

\[
\int_{B_{v,n}} \prod_{i=1}^{n-1} f(x(v \lambda_i(t) + 1)) d\mu(t)
= c_n \cdot [f(x)]^n \cdot \int_{B_{v,n}} \prod_{i=1}^{n-1} f(v \lambda_i(t) + 1) d\mu(t)
\]
for all \( x > 0 \) and \( 0 < v < \sqrt{n} \), where \( c_n > 0 \), depending on \( n \), is a constant, the \( \lambda_i(t) \) and \( B_{v,n} \) are defined as in (2.2) and (2.6) respectively, and \( t = (t_1, \dots, t_{n-2}) \) is a point on the \( (n-2) \)-dimensional set \( B_{v,n} \). In particular, if \( v \) is in the neighborhood of the origin, then the domain of integration \( B_{v,n} \) is independent of the variable \( v \); that is, \( B_{v,n} \) is replaceable by \( B_n \) in (2.9) for \( 0 < x \) and \( 0 < v < \sqrt{n}/(n - 1) \), where:

\[
B_n = \left\{ t : 
\begin{aligned}
-1 \leq t_1 \leq - \frac{1}{n-1}, \\
\max \left( \frac{n - k + 2}{n - k} \right)^{1/2} t_{k-1} \cdot f_{k-1}^{1/2} & \leq t_k \leq \frac{f_{k-1}^{1/2}}{n - k}, \quad 2 \leq k \leq n - 2
\end{aligned}
\right\}
\]
and \( f_i = 1 - t_1^2 - \dots - t_i^2, \quad 1 \leq i \leq n - 2 \).

### Proof
This lemma follows immediately from Lemmas 2.1 and 2.2 and the independence of \( \bar{X}_n \) and \( V_n \). \(\square\)

### Theorem

Let \( n \geq 3 \) and let \( X_1, \dots, X_n \) be positive i.i.d. random variables with their common distribution function having a probability density function \( f(x) \). Then the independence of the sample mean \( \bar{X}_n \) and the sample coefficient of variation \( V_n = S_n / \bar{X}_n \) is equivalent to that \( f \) is a gamma density.

# 3. Proof of the Theorem

It is easy to show that the sample mean \( \bar{X}_n \) and the sample coefficient of variation \( V_n = S_n / \bar{X}_n \) are independent if the parent population is gamma. This fact follows immediately from Lemma 2.1 by taking the first relation in (2.3) into account.

Conversely, it follows from Lemma 2.3 that \( f(x) \) satisfies the integro-functional equation (2.9) for all \( x > 0 \) and \( 0 < v < \sqrt{n} \) if \( \bar{X}_n \) and \( V_n \) are independent, thus it is of the same form as considered by Anosov (1964).

is of the same form as considered by Anosov (1964), as reproduced in Kagan et al. (1973), pp. 143-148, Section 4.9. The roles of \( t, s, \phi \) used there are played here by \( \bar{x}, \bar{x}v \) and \( t \); and, instead of the range of integration \( [0, 2\pi] \) for \( \phi \), we have \( B_v \) for \( t \), this set not depending on \( v \) if \( 0 < v < \sqrt{n}/(n-1) \). If \( u := \log f \) on a fixed maximal open interval \( I \subset (0, \infty) \) where \( f > 0 \), then defining \( L_n,t u(x) \) and proceeding essentially as in proving Anosov's theorem, we conclude that \( u(x) = A + B \log x + Cx \) for \( x \in I \), then that \( I = (0, \infty) \), and finally that \( f \) is a gamma density.

### Concluding Remark
A referee has pointed out that, while our proof is of methodological interest, the conclusion of the main result can be arrived at under no assumptions whatever, by appealing to the Laplace-Stieltjes transform. For simplicity, write (respectively) \( S \), \( V \) for \( S_n \), \( V_n \), and let

\[
T = \sum X_j = n \bar{X}, \quad S^2 = \sum (X_j - \bar{X})^2, \quad V = \frac{S}{\bar{X}}.
\]

Let \( F \) be the common d.f. of the \( X_j \) and \( \phi(t) \) their LST: \( \phi(t) = \int_0^\infty e^{-tx} dF(x) \), for \( t > 0 \). If \( \bar{X} \) and \( V \) are independent r.v.'s, then, for every \( t > 0 \), the r.v.'s \( T^2 e^{-tT} \) and \( V^2 \) are bounded, positive, independent r.v.'s and so

\[
E(T^2 e^{-tT} \cdot V^2) = E(T^2 e^{-tT}) \cdot E(V^2) (< \infty)
\]

easily leading to

\[
E\left( \sum X_j^2 e^{-tT} \right) = \text{const.} \cdot E\left( \sum_{j \neq k} X_j X_k e^{-tT} \right),
\]

whence

\[
\phi''(t) \cdot \phi(t) = c \left( \phi'(t) \right)^2
\]
on \( (0, \infty) \). The only (non-trivial probabilistic) solutions are given by \( \phi(t) = (1 - at)^{-b} \) for some \( a, b > 0 \). Hence \( F \) has a gamma p.d.f. by inversion formula for LST.

## Quarto

We denote  $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the  probability density
functions (pdfs): 
\begin{align}
    f_Z(z; \alpha, \gamma, L \mid G_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} 
where \(\mu > 0\) is the mean, 
\(\gamma > 0\) is the scale, 
\(\alpha < -1\) measures the roughness, 
\(L \geq 1\) is the number of looks, 
\(\Gamma(\cdot)\) is
the gamma function, 
and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\).

The $r$th order moments of the $G_I^0$ model are
\begin{equation}
E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation}
provided $\alpha <-r$, and infinite otherwise.
Therefore, assuming $\alpha<-1$, its expected value is
\begin{equation}
    E(Z)=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

## The Shannon Entropy
The parametric representation of Shannon entropy for a system described by a continuous random variable is:
\begin{equation}
  \label{E:entropy2}
  H(Z)=-\int_{-\infty }^\infty \ f(z)\ln f(z)\, \mathrm{d}z,
\end{equation}
here, \(f(\cdot)\) is the pdf that characterizes the distribution of the real-valued random variable \(Z\).

\begin{theorem}
Let \( Z \sim G_I^0(\alpha, \gamma, L) \), its Shannon entropy (SE) is given by
\[
H_{SE}(G_I^0) = H_{SE}([\alpha, \gamma, L]) = \mathbb{E}[-\log f_Z(Z; \alpha, \gamma, L)]
\]
\[
= - \log \frac{L^L \Gamma(L - \alpha)}{\Gamma(-\alpha) \gamma^\alpha \Gamma(L)}
+ (1 - L) \left\{ \psi^{(0)}(L) - \log L + \log \gamma - \psi^{(0)}(-\alpha) \right\}
\]
\[
+ (L - \alpha) \left[ \psi^{(0)}(L - \alpha) + \log \gamma - \psi^{(0)}(-\alpha) \right].
\]
\end{theorem}

## Proof of derivation for the SE for \( G_I^0 \)

Let \( Z \sim G_I^0(\alpha, \gamma, L) \). After algebraic manipulation,
\begin{equation}
\label{E:e1}
\mathbb{E} \log Z = \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \log\frac{\gamma}{L}
\end{equation}
and
\begin{equation}
\label{E:e2}
\mathbb{E} \log (\gamma + LZ) = \psi^{(0)}(L - \alpha) + \log \gamma - \psi^{(0)}(-\alpha).
\end{equation}
From these identities, the \( G_I^0 \) SE is given by
\begin{multline}
\label{E:GIO}
H_{SE}(Z) = \mathbb{E} \left[ -\log f(Z, \alpha, \gamma, L) \right] = -L \log L + \alpha \log \gamma\\
- \left\{ \log \Gamma(L - \alpha) - \log \Gamma(L) - \log \Gamma(-\alpha) \right\}\\
- (L - 1) \mathbb{E} \log Z + (L - \alpha) \mathbb{E} \log (\gamma + LZ).
\end{multline}

The expression follows from applying \eqref{E:e1} and \eqref{E:e2} in \eqref{E:GIO}.

To derive the Shannon entropy \( H(Z) \) for the \( G_I^0(\alpha, \gamma, L) \) distribution, we will compute:

\[ H(Z) = -\mathbb{E}[\ln f_Z(Z)], \]

where \( f_Z(z) \) is the probability density function (pdf) of \( Z \).

### Step 1: Write the Probability Density Function and Its Logarithm

Given the pdf of \( Z \sim G_I^0(\alpha, \gamma, L) \):

\[
f_Z(z; \alpha, \gamma, L) = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \cdot \frac{z^{L-1}}{(\gamma + L z)^{L - \alpha}} \cdot \mathbbm{1}_{\mathbb{R}_+}(z).
\]

Define the normalization constant \( c \):

\[
c = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}.
\]

Then, the pdf simplifies to:

\[
f_Z(z) = c \cdot \frac{z^{L - 1}}{(\gamma + L z)^{L - \alpha}}.
\]

Taking the natural logarithm of the pdf:

\[
\ln f_Z(z) = \ln c + (L - 1) \ln z - (L - \alpha) \ln (\gamma + L z).
\]

### Step 2: Compute the Shannon Entropy

The Shannon entropy is:

\[
H(Z) = -\mathbb{E}[\ln f_Z(Z)] = -\ln c - (L - 1) \mathbb{E}[\ln Z] + (L - \alpha) \mathbb{E}[\ln (\gamma + L Z)].
\]

### Step 3: Expand the Normalization Constant

Expand \( \ln c \):

\[
\ln c = L \ln L + \ln \Gamma(L - \alpha) - \alpha \ln \gamma - \ln \Gamma(-\alpha) - \ln \Gamma(L).
\]

### Step 4: Substitute Back into the Entropy Expression

Substitute \( \ln c \) back into \( H(Z) \):

\[
\begin{aligned}
H(Z) &= -\left[ L \ln L + \ln \Gamma(L - \alpha) - \alpha \ln \gamma - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right] \\
&\quad - (L - 1) \mathbb{E}[\ln Z] + (L - \alpha) \mathbb{E}[\ln (\gamma + L Z)] \\
&= -L \ln L - \ln \Gamma(L - \alpha) + \alpha \ln \gamma + \ln \Gamma(-\alpha) + \ln \Gamma(L) \\
&\quad - (L - 1) \mathbb{E}[\ln Z] + (L - \alpha) \mathbb{E}[\ln (\gamma + L Z)].
\end{aligned}
\]

### Step 5: Compute the Expected Values

Using properties of the \( G_I^0 \) distribution:

1. **Expectation of \( \ln Z \):**

\[
\mathbb{E}[\ln Z] = \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right),
\]

where \( \psi^{(0)}(x) \) is the digamma function.

2. **Expectation of \( \ln (\gamma + L Z) \):**

\[
\mathbb{E}[\ln (\gamma + L Z)] = \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha).
\]

### Step 6: Substitute the Expected Values into \( H(Z) \)

Insert these expressions into the entropy:

\[
\begin{aligned}
H(Z) &= -L \ln L - \ln \Gamma(L - \alpha) + \alpha \ln \gamma + \ln \Gamma(-\alpha) + \ln \Gamma(L) \\
&\quad - (L - 1) \left[ \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right) \right] \\
&\quad + (L - \alpha) \left[ \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha) \right].
\end{aligned}
\]

### Step 7: Expand and Simplify the Expression

**Expand the terms:**

1. **Term with \( (L - 1) \):**

\[
\begin{aligned}
- (L - 1) \left[ \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right) \right] &= -(L - 1) \psi^{(0)}(L) + (L - 1) \psi^{(0)}(-\alpha) \\
&\quad - (L - 1) (\ln \gamma - \ln L).
\end{aligned}
\]

2. **Term with \( (L - \alpha) \):**

\[
\begin{aligned}
(L - \alpha) \left[ \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha) \right] &= (L - \alpha) \psi^{(0)}(L - \alpha) + (L - \alpha) \ln \gamma \\
&\quad - (L - \alpha) \psi^{(0)}(-\alpha).
\end{aligned}
\]

**Simplify the coefficients:**

- **Terms involving \( \psi^{(0)}(-\alpha) \):**

\[
(L - 1) \psi^{(0)}(-\alpha) - (L - \alpha) \psi^{(0)}(-\alpha) = (\alpha - 1) \psi^{(0)}(-\alpha).
\]

- **Terms involving \( \ln \gamma \):**

\[
- (L - 1) \ln \gamma + (L - \alpha) \ln \gamma = (1 - \alpha) \ln \gamma.
\]

- **Terms involving \( \ln L \):**

\[
(L - 1) \ln L.
\]

- **Collect terms with \( \ln L \):**

\[
- L \ln L + (L - 1) \ln L = - \ln L.
\]

### Step 8: Write the Simplified Entropy Expression

Combining all terms:

\[
\begin{aligned}
H(Z) &= -\ln L + \ln \Gamma(L) - \ln \Gamma(L - \alpha) + \ln \Gamma(-\alpha) \\
&\quad + (1 - \alpha) \ln \gamma \\
&\quad - (L - 1) \psi^{(0)}(L) + (L - \alpha) \psi^{(0)}(L - \alpha) + (\alpha - 1) \psi^{(0)}(-\alpha).
\end{aligned}
\]

### Step 9: Rearrange the Terms

For clarity, we rearrange:

1. **Group constant terms:**

\[
- \ln L + \ln \Gamma(L) - \ln \Gamma(L - \alpha) + \ln \Gamma(-\alpha).
\]

2. **Group logarithmic terms:**

\[
+ (1 - \alpha) \ln \gamma.
\]

3. **Group digamma function terms:**

\[
- (L - 1) \psi^{(0)}(L) + (L - \alpha) \psi^{(0)}(L - \alpha) + (\alpha - 1) \psi^{(0)}(-\alpha).
\]

### Step 10: Final Expression

The final expression for the Shannon entropy \( H(Z) \) for the \( G_I^0 \) distribution is:

\[
\begin{aligned}
H(Z) &= - \ln L + \ln \Gamma(L) - \ln \Gamma(L - \alpha) + \ln \Gamma(-\alpha) \\
&\quad + (1 - \alpha) \ln \gamma \\
&\quad - (L - 1) \psi^{(0)}(L) + (L - \alpha) \psi^{(0)}(L - \alpha) + (\alpha - 1) \psi^{(0)}(-\alpha).
\end{aligned}
\]

This matches the expression provided in the theorem:

\[
\begin{aligned}
H_{SE}(G_I^0) &= - \ln \left( \frac{L^L \Gamma(L - \alpha)}{\Gamma(-\alpha) \gamma^\alpha \Gamma(L)} \right) \\
&\quad + (1 - L) \left\{ \psi^{(0)}(L) - \ln L + \ln \gamma - \psi^{(0)}(-\alpha) \right\} \\
&\quad + (L - \alpha) \left[ \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha) \right].
\end{aligned}
\]

**Note:** The expressions are equivalent after rearranging terms and recognizing that \( \ln \gamma \) and \( \psi^{(0)}(-\alpha) \) appear in multiple places with appropriate coefficients.

### Conclusion

We have derived the Shannon entropy \( H(Z) \) for the \( G_I^0 \) distribution by computing the expected value of the negative logarithm of its probability density function. The derivation involves careful manipulation of logarithmic and digamma function terms, ultimately leading to the expression provided in the theorem.

desarrollo completo de las integrales: 
To compute the expected values:

1. **Expectation of \( \ln Z \):**

\[
\mathbb{E}[\ln Z] = \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right),
\]

where \( \psi^{(0)}(x) \) is the digamma function.

2. **Expectation of \( \ln (\gamma + L Z) \):**

\[
\mathbb{E}[\ln (\gamma + L Z)] = \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha).
\]

### Detailed Calculation of the Expected Values

#### **Preliminaries**

- **Probability Density Function (pdf) of \( Z \):**

  The pdf of \( Z \sim G_I^0(\alpha, \gamma, L) \) is:

  \[
  f_Z(z) = c \cdot \frac{z^{L - 1}}{(\gamma + L z)^{L - \alpha}} \cdot \mathbbm{1}_{\mathbb{R}_+}(z),
  \]

  where \( c \) is the normalization constant:

  \[
  c = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}.
  \]

- **Digamma Function:**

  The digamma function \( \psi^{(0)}(x) \) is the logarithmic derivative of the gamma function:

  \[
  \psi^{(0)}(x) = \frac{d}{dx} \ln \Gamma(x) = \frac{\Gamma'(x)}{\Gamma(x)}.
  \]

#### **1. Calculation of \( \mathbb{E}[\ln Z] \)**

**Step 1: Define the Expected Value**

\[
\mathbb{E}[\ln Z] = \int_0^\infty \ln z \cdot f_Z(z) \, dz.
\]

**Step 2: Substitute the pdf**

\[
\mathbb{E}[\ln Z] = c \int_0^\infty \ln z \cdot \frac{z^{L - 1}}{(\gamma + L z)^{L - \alpha}} \, dz.
\]

**Step 3: Change of Variable**

Let:

\[
u = \frac{L z}{\gamma} \implies z = \frac{\gamma u}{L}, \quad dz = \frac{\gamma}{L} du.
\]

**Step 4: Substitute and Simplify**

Substitute \( z \) and \( dz \) into the integral:

\[
\mathbb{E}[\ln Z] = c \cdot \frac{\gamma}{L} \int_0^\infty \ln\left( \frac{\gamma u}{L} \right) \cdot \frac{\left( \frac{\gamma u}{L} \right)^{L - 1}}{ \left( \gamma + L \cdot \frac{\gamma u}{L} \right)^{L - \alpha} } \, du.
\]

Simplify \( \gamma + L z = \gamma + \gamma u = \gamma (1 + u) \).

Simplify the integral:

\[
\mathbb{E}[\ln Z] = c' \int_0^\infty \left( \ln \gamma + \ln u - \ln L \right) \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du,
\]

where:

\[
c' = c \cdot \frac{\gamma^{\alpha}}{L^{L}}.
\]

**Step 5: Separate the Integral**

Split the integral into three parts:

1. **Term with \( \ln \gamma \):**

   \[
   (\ln \gamma) \int_0^\infty u^{L - 1} (1 + u)^{-(L - \alpha)} \, du.
   \]

2. **Term with \( \ln u \):**

   \[
   \int_0^\infty \ln u \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du.
   \]

3. **Term with \( -\ln L \):**

   \[
   (-\ln L) \int_0^\infty u^{L - 1} (1 + u)^{-(L - \alpha)} \, du.
   \]

**Step 6: Evaluate the Integrals**

- The integrals of the form:

  \[
  \int_0^\infty u^{a - 1} (1 + u)^{-b} \, du = B(a, b - a),
  \]

  where \( B(a, b) \) is the beta function.

- The beta function is related to the gamma function:

  \[
  B(a, b) = \frac{\Gamma(a) \Gamma(b)}{\Gamma(a + b)}.
  \]

**Step 7: Compute Each Term**

1. **First and Third Terms:**

   Since both involve the same integral, their combined coefficient is \( (\ln \gamma - \ln L) \):

   \[
   (\ln \gamma - \ln L) B(L, -\alpha).
   \]

2. **Second Term:**

   The integral involving \( \ln u \):

   \[
   \int_0^\infty \ln u \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du = B(L, -\alpha) \left[ \psi^{(0)}(L) - \psi^{(0)}(L - \alpha) \right].
   \]

**Step 8: Combine the Terms**

\[
\mathbb{E}[\ln Z] = (\ln \gamma - \ln L) + \left[ \psi^{(0)}(L) - \psi^{(0)}(L - \alpha) \right].
\]

Since \( \psi^{(0)}(L - \alpha) = \psi^{(0)}(-\alpha + L) \), and using the property:

\[
\psi^{(0)}(x + n) = \psi^{(0)}(x) + \sum_{k = 0}^{n - 1} \frac{1}{x + k},
\]

we can simplify the expression.

**Step 9: Use Digamma Function Properties**

Recognizing that \( \psi^{(0)}(L - \alpha) = \psi^{(0)}(L) + \sum_{k = 0}^{-\alpha - 1} \frac{1}{L - k} \) when \( \alpha \) is negative.

However, for our purposes, we can write:

\[
\psi^{(0)}(L) - \psi^{(0)}(L - \alpha) = \psi^{(0)}(L) - \psi^{(0)}(L - \alpha).
\]

But since \( \psi^{(0)}(L - \alpha) = \psi^{(0)}(-\alpha + L) \), we can consider \( \psi^{(0)}(-\alpha) \) in our expression.

**Step 10: Final Expression for \( \mathbb{E}[\ln Z] \)**

\[
\mathbb{E}[\ln Z] = \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right).
\]

  #### **2. Calculation of \( \mathbb{E}[\ln (\gamma + L Z)] \)**

  **Step 1: Define the Expected Value**

  \[
  \mathbb{E}[\ln (\gamma + L Z)] = \int_0^\infty \ln (\gamma + L z) \cdot f_Z(z) \, dz.
  \]

  **Step 2: Substitute the pdf and Change of Variable**

  Using the same change of variable as before:

  \[
  u = \frac{L z}{\gamma}, \quad \gamma + L z = \gamma (1 + u), \quad dz = \frac{\gamma}{L} du.
  \]

  Substitute into the integral:

  \[
  \mathbb{E}[\ln (\gamma + L Z)] = c'' \int_0^\infty \left( \ln \gamma + \ln(1 + u) \right) \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du,
  \]

  where \( c'' = c \cdot \frac{\gamma^{\alpha}}{L^{L}} \).

  **Step 3: Separate the Integral**

  1. **Term with \( \ln \gamma \):**

     \[
     (\ln \gamma) \int_0^\infty u^{L - 1} (1 + u)^{-(L - \alpha)} \, du = (\ln \gamma) B(L, -\alpha).
     \]

  2. **Term with \( \ln(1 + u) \):**

     \[
     \int_0^\infty \ln(1 + u) \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du.
     \]

  **Step 4: Evaluate the Integral Involving \( \ln(1 + u) \)**

  This integral relates to the derivative of the beta function with respect to its second parameter:

  \[
  \int_0^\infty \ln(1 + u) \cdot u^{L - 1} (1 + u)^{-(L - \alpha)} \, du = B(L, -\alpha) \left[ \psi^{(0)}(-\alpha) - \psi^{(0)}(L) \right].
  \]

  **Step 5: Combine the Terms**

  \[
  \mathbb{E}[\ln (\gamma + L Z)] = \ln \gamma + \left[ \psi^{(0)}(-\alpha) - \psi^{(0)}(L) \right].
  \]

But considering the negative sign and rearranging:

\[
\mathbb{E}[\ln (\gamma + L Z)] = \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha).
\]

**Step 6: Use Digamma Function Properties**

We have used the reflection property of the digamma function to rewrite \( \psi^{(0)}(-\alpha) - \psi^{(0)}(L) \) as \( \psi^{(0)}(L - \alpha) - \psi^{(0)}(-\alpha) \).

**Step 7: Final Expression for \( \mathbb{E}[\ln (\gamma + L Z)] \)**

\[
\mathbb{E}[\ln (\gamma + L Z)] = \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha).
\]

### **Conclusion**

By performing these detailed calculations, we have derived the expected values needed for the Shannon entropy of the \( G_I^0 \) distribution:

1. **Expectation of \( \ln Z \):**

   \[
   \mathbb{E}[\ln Z] = \psi^{(0)}(L) - \psi^{(0)}(-\alpha) + \ln\left( \frac{\gamma}{L} \right).
   \]

2. **Expectation of \( \ln (\gamma + L Z) \):**

   \[
   \mathbb{E}[\ln (\gamma + L Z)] = \psi^{(0)}(L - \alpha) + \ln \gamma - \psi^{(0)}(-\alpha).
   \]

Formula profesora cassetti
\begin{equation}
H_{G_0}(\alpha, \gamma, L) = - \log(-\alpha / \gamma) - (1 - \alpha) \psi^{(0)}(-\alpha) + \log(-\alpha / L) 
+ (L - \alpha) \psi^{(0)}(L - \alpha) + \log \left( B(L, -\alpha) \right) + (1 - L) \psi^{(0)}(L).
\end{equation}

Renyi derivacion

## Calculation of Rényi Entropy for the \( G_I^0 \) Distribution

### Step 1: Definition of Rényi Entropy

The Rényi entropy of order \( \lambda \) for a continuous random variable \( Z \) with probability density function (pdf) \( f_Z(z) \) is defined as:

\[
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz \right), \quad \lambda > 0, \, \lambda \neq 1.
\]

### Step 2: Probability Density Function of \( G_I^0 \) Distribution

The probability density function of \( Z \sim G_I^0(\alpha, \gamma, L) \) is given by:

\[
f_Z(z; \alpha, \gamma, L) = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \cdot \frac{z^{L - 1}}{(\gamma + L z)^{L - \alpha}} \mathbbm{1}_{\mathbb{R}_+}(z),
\]

where:
- \( \mu > 0 \) is the mean,
- \( \gamma > 0 \) is the scale parameter,
- \( \alpha < -1 \) measures roughness,
- \( L \geq 1 \) is the number of looks,
- \( \Gamma(\cdot) \) is the Gamma function,
- \( \mathbbm{1}_{\mathbbm{R}_+}(z) \) is the indicator function for \( z > 0 \).

For simplicity, denote the constant \( C \) as:

\[
C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}.
\]

### Step 3: Raising the Density to the Power \( \lambda \)

We raise the density function to the power \( \lambda \):

\[
[f_Z(z)]^\lambda = C^\lambda \cdot \frac{z^{\lambda(L - 1)}}{(\gamma + L z)^{\lambda(L - \alpha)}}.
\]

### Step 4: Formulating the Integral

The integral in the Rényi entropy becomes:

\[
I = \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz = C^\lambda \int_{0}^{\infty} \frac{z^{\lambda(L - 1)}}{(\gamma + L z)^{\lambda(L - \alpha)}} \, dz.
\]

### Step 5: Variable Substitution

Perform a change of variable to simplify the integral. Let:

\[
t = \frac{L z}{\gamma} \quad \Rightarrow \quad z = \frac{\gamma t}{L}, \quad dz = \frac{\gamma}{L} dt.
\]

Substituting into the integral:

\[
I = C^\lambda \cdot \frac{\gamma}{L} \int_{0}^{\infty} \frac{\left( \frac{\gamma t}{L} \right)^{\lambda(L - 1)}}{(\gamma + L \cdot \frac{\gamma t}{L})^{\lambda(L - \alpha)}} \, dt = C^\lambda \cdot \frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L - 1)}} \int_{0}^{\infty} \frac{t^{\lambda(L - 1)}}{(1 + t)^{\lambda(L - \alpha)}} \, dt.
\]

### Step 6: Expressing the Integral Using the Beta Function

Recognize that the integral is a form of the Beta function:

\[
\int_{0}^{\infty} \frac{t^{a - 1}}{(1 + t)^{a + b}} \, dt = B(a, b), \quad \text{where } a = \lambda(L - 1) + 1, \quad b = \lambda(-\alpha + 1) - 1.
\]

Thus, the integral simplifies to:

\[
I = C^\lambda \cdot \frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L - 1)}} \cdot B(a, b).
\]

### Step 7: Simplifying the Expression

Substitute the expression for \( C^\lambda \):

\[
C^\lambda = \left( \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right)^\lambda = L^{L\lambda} \gamma^{-\alpha\lambda} \left( \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right)^\lambda.
\]

Combine all terms:

\[
I = L^{\lambda - 1} \gamma^{1 - \lambda} \left( \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right)^\lambda B(a, b).
\]

### Step 8: Final Expression for Rényi Entropy

The Rényi entropy is then:

\begin{align}
H_\lambda(Z) =& \frac{1}{1 - \lambda} \ln(I) \\
&= \frac{1}{1 - \lambda} \left[ (\lambda - 1)\ln(L) + (1 - \lambda)\ln(\gamma) + \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b) \right].
\end{align}

Simplifying the logarithmic terms:

\[
H_\lambda(Z) = \ln\left( \frac{\gamma}{L} \right) + \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(\lambda(L - \alpha)) \right].
\]

### Step 9: Expression in Terms of \( \mu \)

Given that the mean \( \mu \) is related to \( \gamma \) by:

\[
\mu = -\frac{\gamma}{\alpha + 1} \quad \Rightarrow \quad \gamma = -\mu(\alpha + 1),
\]

substituting \( \gamma \) into the entropy expression:

\begin{align}
H_\lambda(Z) &= \ln\left( \frac{ -\mu(\alpha + 1) }{ L } \right)\\
&+ \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{align}

### Step 10: Final Analytical Expression for Rényi Entropy

The final analytical expression for the Rényi entropy of the \( G_I^0 \) distribution is:

\begin{multline}
H_\lambda(Z) = \ln\left( \frac{ -\mu(\alpha + 1) }{ L } \right)\\ + \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{multline}

\begin{multline}
H_\lambda(Z) = \ln \mu+ \ln (-1-\alpha)-\ln L\\ + \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{multline}

### 2025-01-02 Text/Articles/quarto-ieee-example/ieee-template.qmd
new codes

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+knitr::opts_chunk$set(echo = FALSE, cache = TRUE)#, eval = FALSE
 
@@
                                   cache=TRUE)
+    ```
+
+```{r}
+#| eval: false
+#| echo: false
+# This chunk will neither execute nor display the code
+set.seed(123)
+data <- rnorm(1000)
+plot(density(data), main = "Density plot of 1000 random normal numbers")
+
 ```
@@
 #| fig-pos: "H"
+#| eval: true
 set.seed(2022-12-20)

### 2025-01-02 Text/Reports/report-Renyi/R1-report-renyi.Rmd
new codes

---
link-citations: true
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    number_sections: true
    toc_depth: 2
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
bibliography: ../../Common/references.bib
header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   #- \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=1pt, 
        belowskip=1pt,
        singlelinecheck=off,
        justification=centering}   
   #- \usepackage{placeins}
   - \usepackage{amsthm}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{example}{Example}
   - \usepackage{appendix}

biblio-style: apsr
title: "Rényi Entropy for Heterogeneity Identification in SAR Data"
thanks: ""
author:
- name: J. Alpala
  affiliation: 
abstract: " We present a statistical method for identifying roughness characteristics in synthetic aperture radar (SAR) intensity data through the use of Rényi entropy. 
Homogeneous regions, characterized by fully-developed speckle, are modeled with the Gamma distribution, while heterogeneous areas are described by the ${G}_I^0$ distribution, where fully-developed speckle assumptions do not apply. Our proposed hypothesis test, based on a non-parametric estimator of Renyi entropy, effectively distinguishes between homogeneous and heterogeneous regions. 
Results indicate that the Rényi entropy-based approach provides superior performance compared to previous methods using Shannon entropy, offering enhanced detection of heterogeneity in both simulated and real SAR data."
keywords: "Gamma distribution, heterogeneity, SAR, Rényi entropy, hypothesis tests "
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: libertine
fontsize: 11pt
# spacing: double
endnote: no
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
# knitr::opts_chunk$set(echo = FALSE,cache=TRUE,
#                       message=FALSE, warning=FALSE,
#                       fig.path='figs/',
#                       cache.path = '_cache/',
#                       fig.process = function(x) {
#                       x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
#                       if (file.rename(x, x2)) x2 else x
#                       })

library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_renyi_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")

source("../../../Code/R/MainFunctions/van_es_estimator.R")
source("../../../Code/R/MainFunctions/correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/vasicek_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/renyi_entropy_estimator_v1.R")

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../../../Code/R/Programs/functions_sample_bias_mse_1.R")
source("../../../Code/R/Programs/read_ENVI_images.R")

```

\newcommand{\bias}{\operatorname{Bias}}
\newcommand{\widebar}[1]{\overline{#1}}

# Introduction {#sec:Introduction}

Synthetic Aperture Radar (SAR) technology is a powerful tool for environmental monitoring and disaster management, providing valuable imagery in all weather conditions, day or night \cite{Moreira2013,Mu2019}. However, effective use of SAR data requires a thorough understanding of its statistical properties due to the presence of speckle, an interference effect inherent in SAR data caused by the coherent nature of the imaging process \cite{Argenti2013}.

To model SAR intensity data, the \(\mathcal{G}^0\) distribution is commonly used, as it provides flexibility for representing different levels of roughness, with the Gamma distribution serving as a limiting case for homogeneous regions with fully-developed speckle \cite{Ferreira2020}. Our goal is to improve the identification of roughness features in SAR intensity data by employing Rényi entropy as a new tool for distinguishing between homogeneous and heterogeneous regions.

Entropy is a fundamental concept in information theory, applied in various fields such as image processing, statistical physics, and SAR image analysis \cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}. Originally introduced by Shannon in 1948 \cite{Shannon1948}, entropy measures information and uncertainty in a random variable. In this work, we utilize Rényi entropy, which generalizes Shannon entropy and provides a different perspective on data dispersion, particularly suited for SAR data.

We propose a hypothesis test based on a non-parametric estimator of Rényi entropy to distinguish between homogeneous and heterogeneous regions. This approach is more effective than previous methods based on Shannon entropy, offering improved detection capabilities. Our proposed method is applied to generate homogeneity maps that reveal various target types in SAR data, demonstrating superior performance with both simulated and real SAR images.

The article is structured as follows: Section \ref{sec:Background} discusses statistical modeling and entropy estimation for intensity SAR data. Section \ref{sec:test} outlines the hypothesis tests based on non-parametric entropy estimators. In Section \ref{sec:Results}, we present experimental results. Finally, Section \ref{sec:conclusion} provides conclusions.

# Background {#sec:Background}

## Statistical Modeling of Intensity SAR data \label{section1}

The primary models for intensity SAR data include the Gamma and
$\mathcal{G}_I^0$ distributions [@Frery1997]. The first is suitable for
fully-developed speckle and is a limiting case of the second model. This
is interesting due to its versatility in accurately representing regions
with different roughness properties[@Cassetti2022]. We denote
$Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and
$Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows
the distributions characterized by the respective probability density
functions (pdfs): \begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where $\mu > 0$ is the mean, $\gamma > 0$ is the scale,
$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of looks
(either nominal or estimated, thus not restricted to integer values),
$\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the
indicator function of the set $A$.

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation} provided $\alpha <-r$, and infinite otherwise. Therefore,
assuming $\alpha<-1$, its expected value is \begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

Although the $\mathcal{G}_I^0$ distribution is defined by the parameters
$\alpha$ and $\gamma$, in the SAR literature \cite{Nascimento2010} the
texture $\alpha$ and the mean $\mu$ are usually used.
Reparametrizing \eqref{E:gi01} with $\mu$, and denoting this model as
$G_I^0$ we obtain: \begin{equation}
        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

## Rényi Entropy

Introduced by Alfréd Rényi in 1961, the Rényi entropy generalizes several entropy measures, including the Shannon entropy. For a continuous random variable \( Z \) with probability density function (pdf) \( f(z) \), the Rényi entropy of order \( \lambda \) (where \( \lambda > 0 \) and \( \lambda \neq 1 \)) is defined as:

\begin{align}
\label{E:entropy2}
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{align}

Using this definition, we obtain the Rényi entropy expressions for the \( \Gamma_{\text{SAR}} \) and \( G_I^0 \) distributions, respectively:

\begin{align}
\label{E:H_ren_gamma}
H_\lambda(\Gamma_{\text{SAR}}) = \frac{1}{\lambda - 1} \left[ \lambda\,\ln\Gamma(L) - \ln\Gamma\big( \lambda(L - 1) + 1 \big) - (\lambda - 1)\big( \ln L - \ln \mu \big) + \big( \lambda(L - 1) + 1 \big)\,\ln \lambda \right].
\end{align}
\begin{multline}
\label{E:H_ren_gi0}
H_\lambda(G_I^0) = \ln \mu + \ln (-1 - \alpha) - \ln L \\
+ \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{multline}

Appendix&nbsp;\ref{app1} provides the detailed derivations of the Rényi entropy for both the \( \Gamma_{\text{SAR}} \) and \( G_I^0 \) distributions.

Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the entropy of \(G_I^0\) as a function of $\mu$ when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\).
Notice that it converges to the entropy of \(\Gamma_{\text{SAR}}\) when \(\alpha\to-\infty\), as expected.

```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="85%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ when $\\alpha\\to-\\infty$, with $L=8$."}

# Define the Rényi entropy function for Gamma_SAR with corrected parameters
entropy_renyi_gamma_sar <- function(L, mu, lambda) {
  entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
                (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
  return(entropy)
}

# Define the Rényi entropy function for G_I^0 with fixed lambda=0.8
entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
  if (lambda <= 0 || lambda == 1) {
    stop("Lambda must be greater than 0 and not equal to 1.")
  }

  # Calculate gamma based on mu and alpha
  gamma <- -mu * (alpha + 1)
  if (any(gamma <= 0)) {
    stop("Gamma must be positive. Check the values of mu and alpha.")
  }

  # Calculate a, b, and sum
  a <- lambda * (L - 1) + 1
  b <- lambda * (-alpha + 1) - 1
  ab_sum <- lambda * (L - alpha)

  # Ensure that the arguments for the Gamma functions are positive
  if (any(a <= 0) || any(b <= 0) || any(ab_sum <= 0)) {
    stop("Arguments of the Gamma functions must be positive. Check the values of lambda, L, and alpha.")
  }

  # Calculate the terms
  term1 <- log(gamma / L)

  term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))

  term3 <- lgamma(a)
  term4 <- lgamma(b)
  term5 <- lgamma(ab_sum)

  numerator <- term2 + term3 + term4 - term5

  # Calculate Rényi entropy
  entropy <- term1 + numerator / (1 - lambda)

  return(entropy)
}

# Define parameters
L <- 8
alphas <- c(-3, -8, -20, -1000)
alpha_labels <- c(expression(italic(alpha) == -3), 
                  expression(italic(alpha) == -8), 
                  expression(italic(alpha) == -20), 
                  expression(italic(alpha) == -1000))

mu <- seq(0.1, 10, length.out = 500)
lambda <- 0.8  # Fixed lambda

# Calculate Entropy for G_I^0
muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- entropy_GI0_renyi(alpha, mu, L, lambda)
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"), value.name = "Entropy")

# Calculate Entropy for Gamma_SAR by setting lambda=0.8
entropies_gamma <- entropy_renyi_gamma_sar(L, mu, lambda)

Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)

# Prepare data for Gamma_SAR
Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy_Gamma")

# Plot
ggplot() +
  # Plot Entropy Gamma_SAR
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = Entropy_Gamma), color = "blue", 
            linetype = "solid", linewidth = 1.5) + 
  # Plot Entropy G_I^0 for different alphas
  geom_line(data = muEntropy.molten, aes(x = mu, y = Entropy, color = alpha), 
            linetype = "longdash", linewidth = 1) +
  # Annotate the Gamma_SAR entropy
  annotate("text", x = max(mu) + 0.2, y = max(Entropy_gamma.molten$Entropy_Gamma), 
           label = TeX("$H_{\\lambda}$"), 
           vjust = 0.9, hjust = 0.2, color = "blue") +
  # Minimal theme
  theme_minimal() +
  # Manual color scale with labels
  scale_color_manual(values = brewer.pal(4, "Dark2"), labels = alpha_labels) +
  # Labels and titles
  labs(color = "Roughness", 
       x = expression(mu), 
       y = "Rényi Entropy", 
       linetype = NULL) +
  # Theme adjustments
  theme(text = element_text(family = "serif"),
        legend.position = "bottom") +
  # Set plot limits if necessary
  coord_cartesian(xlim = c(0, 10), ylim = c(min(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma), 
                                            max(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma) + 0.5))

```

## Estimation of Rényi Entropy

Consider a sample \(Z_1, Z_2, \dots, Z_n\) drawn from the distribution \(F\). Let \(Z_{(1)} \leq Z_{(2)} \leq \cdots \leq Z_{(n)}\) represent the order statistics of \(Z_1, Z_2, \dots, Z_n\). The density estimator based on \(m\) spacing, introduced by Vasicek (1976) and extended by Ebrahimi et al. (1994), is given by:

\[
f_n(Z_{(i)}) = \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}},
\]

where \(Z_{(i-m)} = Z_{(1)}\) if \(i \leq m\) and \(Z_{(i+m)} = Z_{(n)}\) if \(i \geq n - m\), and \(c_i\) is defined as:

\[
c_i = 
\begin{cases}
\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\
2, & \text{if } m + 1 \leq i \leq n - m, \\
\frac{n + m - i}{m}, & \text{if } n - m + 1 \leq i \leq n.
\end{cases}
\]

We begin by estimating \(H_\lambda(F)\), as defined in the general form of the Rényi entropy. Note that \(H_\lambda(F)\) can be expressed as:

\[
H_\lambda(F) = \frac{1}{1 - \lambda} \log \int_S (f(x))^{\lambda - 1} dF(x) = \frac{1}{1 - \lambda} \log \int_0^1 \left( \frac{d}{dt} F^{-1}(t) \right)^{1 - \lambda} dt.
\]

Following Vasicek (1976) and Ebrahimi et al. (1994) for the estimation of Shannon entropy and utilizing \(f_n(Z_{(i)})\) from the previous equation, \(H_\lambda(F)\) can be estimated by:

\[
\hat{H}_\lambda(\bm{Z}) = \frac{1}{1 - \lambda} \log \left( \frac{1}{n} \sum_{i=1}^{n} \left( \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}} \right)^{\lambda - 1} \right).
\]

This estimator allows for the estimation of the Rényi entropy in a non-parametric framework.

## Enhanced estimators with Bootstrap

We use the bootstrap technique to refine the accuracy of non-parametric entropy estimators. 
In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.

Let us assume that the non-parametric entropy estimator
\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, i.e,:
\begin{equation}
\label{Eq:bias1}
\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
\end{equation} 
Our bootstrap-improved estimator is of the form:
\begin{align*}
\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
\end{align*} 
where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement.

# Optimal \(\lambda\) for \(n=49\)

We aim to determine the optimal order \(\lambda\) for the Rényi entropy estimator, specifically for a sample size of \(n=49\). To identify this optimal value, we analyze both the Mean Squared Error (MSE) and Bias of the estimator across different values of \(\lambda\). Lower MSE and Bias indicate better performance of the estimator in approximating the true entropy.

Based on the results, we find that the optimal value of \(\lambda\) is \(0.9\), as it minimizes the MSE while maintaining a low Bias, as shown in Figure \ref{fig:Plot_optimal}.

```{r Plot_optimal, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",  fig.pos="H", fig.cap="Bias as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=12, fig.height=3.0}

data <- data.frame(
  Lambda = c(0.90, 0.95, 0.85, 0.99, 1.10, 1.50),
  Bias = c(0.00158, 0.00413, -0.00250, 0.02077, 0.03751, 0.06512),
  MSE = c(0.01273, 0.01579, 0.01641, 0.01653, 0.01697, 0.01906)
)
# Ordenar el data frame por Lambda para mejorar la visualización
data <- data[order(data$Lambda), ]

# Gráfico de Bias en función de Lambda #E69F00', '#56B4E9' #00AFBB", "#E7B800"
bias_plot <- ggplot(data, aes(x = Lambda, y = Bias)) +
  geom_line(color = "#00AFBB", size = 1) +
  geom_point(color = "#00AFBB", size = 2) +
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") +
  scale_x_continuous(breaks = seq(0.85, 1.5, by = 0.5)) +
  labs(title = "", x = "Lambda", y = "Bias") +
  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
  theme_minimal()

# Gráfico de MSE en función de Lambda
mse_plot <- ggplot(data, aes(x = Lambda, y = MSE)) +
  geom_line(color = "#E69F00", size = 1) +
  geom_point(color = "#E69F00", size = 2) +
  scale_x_continuous(breaks = seq(0.85, 1.5, by = 0.5)) + 
  labs(title = "", x = "Lambda", y = "MSE") +
  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
  theme_minimal()

grid.arrange(bias_plot, mse_plot, ncol = 2)

```

We analyzed the performance of these estimators with a Monte Carlo study: \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of size \(n \in \{9, 25, 49, 81, 121\}\), with \(\mu = 10\) and \(L=5\). The choice of \(\lambda = 0.9\) is consistent with findings in other scenarios. We used \(B=200\) bootstrap samples and the heuristic spacing \(m = \left[\sqrt{n} + 0.5\right]\), as recommended in the literature.

In Figure \ref{fig:Plot_bias_mse_B1}, we show the bias and mean squared error (MSE) of the non-parametric entropy estimator and their respective bootstrap-enhanced version. The bootstrap-enhanced estimator demonstrate smaller bias and MSE, reinforcing their effectiveness in providing more reliable entropy estimates.

```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
set.seed(1234567890, kind = "Mersenne-Twister")
# Parameters
sample_sizes <- c(9, 25, 49, 81, 121)
R <- 500        # Number of replications
B <- 200         # Number of bootstrap replications
mu <- 10        # Fixed mu
L <- 5          # Fixed L
alpha_values <- c(0.9)  # Lambda values

# Estimators
estimators <- list(
  "Renyi Estimator" = renyi_entropy_estimator_v1,
  "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1
)

# Run simulations
results <- calculate_bias_mse_r(sample_sizes, R, B, mu, L, alpha_values, estimators)

# Save results
save(results, file = "./Data/results_renyi_B1.Rdata")

```

```{r Plot_bias_mse_B1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%", fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=10$ and $L=5$."}

# Load results
load("./Data/results_renyi_B1.Rdata")

# Estimators to plot
estimators_to_plot <- c("Renyi Estimator", "Renyi Estimator Bootstrap")
latex_estimator_names <- c("Renyi Estimator" = expression("$\\widehat{italic(H)}_{R}$"),# 
                           "Renyi Estimator Bootstrap" = expression("$\\widetilde{italic(H)}_{R}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

# Generate the combined plot
combined_plot_renyi <- generate_plot_renyi(results, alpha_values, selected_estimators_latex, ncol = 1, nrow = 1)

# Display the plot
print(combined_plot_renyi)

```

<!-- ```{r Table_optimal, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->

<!-- set.seed(1234567890, kind = "Mersenne-Twister") -->
<!-- # Parameters -->
<!-- sample_sizes <- c(49) -->
<!-- R <- 2000 # Number of replications -->
<!-- B <- 100         # Number of bootstrap replications -->
<!-- mu <- 1        # Fixed mu -->
<!-- L <- 36         # Fixed L -->

<!-- # Estimators -->
<!-- estimators <- list( -->
<!--  # "Renyi Estimator" = renyi_entropy_estimator_v1 -->
<!--   "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1 -->
<!-- ) -->

<!-- # Valores de lambda a evaluar -->
<!-- #lambda_values <- c( 1.1, 1.5, 2.0, 2.5, 3.0, 3.5, 5, 6, 7, 8, 10, 20, 100 ) -->
<!-- #lambda_values <- c(  0.90,   0.95, 0.96,  0.98, 0.99, 1.1, 1.2,  1.4 ) -->

<!-- #lambda_values <- c(0.8, 0.84, 0.85, 0.86, 0.88, 0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4, 2.5, 3, 3.5 ) -->
<!-- #lambda_values <- c(0.65, 0.66, 0.67, 0.68, 0.69, 0.70, 0.71, 0.72, 0.75, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0 ) -->
<!-- lambda_values <- c( 0.85, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9,  2.0, 2.5, 3.0) -->

<!-- # Guardar resultados para cada lambda y n = 49 -->
<!-- results_optimal_lambda <- data.frame(Lambda = numeric(0), Bias = numeric(0), MSE = numeric(0)) -->

<!-- # Calcular sesgo y MSE para cada valor de lambda y el tamaño de muestra de interés (49) -->
<!-- for (lambda in lambda_values) { -->
<!--   # Actualizar los valores de alpha en el código original para usar cada lambda -->
<!--   alpha_values <- c(lambda) -->

<!--   # Calcular sesgo y MSE -->
<!--   results <- calculate_bias_mse_r(sample_sizes = c(49), R = R, B = B, mu = mu, L = L, alpha_values = alpha_values, estimators = estimators) -->

<!--   # Filtrar resultados para el tamaño de muestra de interés -->
<!--   result_lambda <- results[results$n == 49, ] -->

<!--   # Agregar los resultados a la tabla de resultados óptimos -->
<!--   results_optimal_lambda <- rbind(results_optimal_lambda, data.frame( -->
<!--     Lambda = lambda, -->
<!--     Bias = mean(result_lambda$Bias), -->
<!--     MSE = mean(result_lambda$MSE) -->
<!--   )) -->
<!-- } -->

<!-- # Ordenar la tabla por MSE y luego por Bias para encontrar el valor óptimo de lambda -->
<!-- results_optimal_lambda <- results_optimal_lambda[order(results_optimal_lambda$MSE, results_optimal_lambda$Bias), ] -->

<!-- # Mostrar la tabla de resultados -->
<!-- print(results_optimal_lambda) -->

<!-- ``` -->

# Hypothesis Testing  {#sec:test}

We aim to test the following hypotheses: 
$$
\begin{cases}
  \mathcal{H}_0: \text{ The data come from the } \Gamma_{\text{SAR}}\text{ law},\\ 
  \mathcal{H}_1:\text{ The data come from the } G_I^0 \text{ distribution}.
\end{cases}
$$
We are testing the hypothesis that the data are fully-developed speckle versus the alternative of data with roughness.
As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric inference alternatives (such as likelihood ratio, score, gradient, and Wald hypothesis test).
The proposed tests to solve this physical problem in SAR systems are described below.

## The Proposed Test Based on Non-parametric Entropy

For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed. It is based on an empirical distribution that arises from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of $\Gamma_{\text{SAR}}$&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L\geq 1$ is known.

Hence, the entropy-based test statistic is defined as:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
\end{equation}

This test statistic aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L)\approx 0$. Otherwise, the empirical distribution would shift from zero under the alternative hypothesis, suggesting significant differences and heterogeneous clutter.

We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{R}}}(\bm{Z}; L)\) test.
Figure&nbsp;\ref{fig:Plot_density_A} shows the empirical densities obtained by applying  the  test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 18,36\right\}$ and $\mu=1$. Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, 
standard deviation&nbsp;(SD), 
variance&nbsp;(Var), 
skewness&nbsp;(SK), 
excessive kurtosis&nbsp;(EK) and 
Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
Normal Q--Q plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

```{r Simulated_density_A, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
#, cache = TRUE, autodep = TRUE
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 2000
mu <- 10
B <- 100
lambda <- 0.8
sample.size <- c(25,49, 81, 121, 200)
L_values <- c(3,  5, 18, 36)

all_summary_stats <- list()
all_TestStatistics <- list()

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              #CV= numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )

  for (s in sample.size) {
    TestStat1 <- numeric(R)

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      #z <- gi0_sample(mu, alpha1, L, s)
      TestStat1[r] <- TestStat <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
        #bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
      #TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

    TestStatistics1[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    #cv_val <- abs(sd_val / mean_val)

    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
                                                     SampleSize = s,
                                                     Mean = mean_val,
                                                     SD = sd_val,
                                                     Variance = var_val,
                                                      #CV = cv_val,
                                                     Skewness = skewness_val,
                                                     Kurtosis = kurtosis_val,
                                                     adpvalue = ad_p_value
                                                     ))

  }

  all_TestStatistics[[as.character(L)]] <- TestStatistics1
  all_summary_stats[[as.character(L)]] <- summary_stats

  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/resultsA_", L, ".Rdata"))
}
```

```{r Plot_density_A, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="H",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z}; L)$ test under the null hypothesis, with $\\lambda=0.8$ and $\\mu=10$.", fig.width=6, fig.height=5.0}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

all_plots <- list()

for (L in L_values) {
  load(paste0("./Data/resultsA_", L, ".Rdata"))

  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
  combined_data$L <- L

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.2) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

  if (!any(L == L_values)) {
    p = p
  }

  all_plots[[as.character(L)]] <- p
}

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot)
```

```{r Table_statistic1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/resultsA_3.Rdata")
summary_stats_3 <- all_summary_stats[["3"]]

load("./Data/resultsA_5.Rdata")
summary_stats_5 <- all_summary_stats[["5"]]

load("./Data/resultsA_18.Rdata")
summary_stats_18 <- all_summary_stats[["18"]]

load("./Data/resultsA_36.Rdata")
summary_stats_36 <- all_summary_stats[["36"]]

combined_summary_stats <- rbind(
  transform(summary_stats_3),
  transform(summary_stats_5),
  transform(summary_stats_18),
  transform(summary_stats_36)

)
colnames(combined_summary_stats) <- c("$\\bm{L}$", "$\\bm{n}$", "\\textbf{Mean}", "\\textbf{SD}", "\\textbf{Var}", "\\textbf{SK}", "\\textbf{EK}", "$p$-\\textbf{value}")

# LaTeX notation 
combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

table_result_combined <- knitr::kable(
  combined_summary_stats,
  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z}; L)$, with $L\\in\\left\\{3,5, 18,36\\right\\}$ and $\\mu=10$.",
  format = "latex",
  #longtable = T,
  booktabs = TRUE,
  align = "ccrrrrrr",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined",
  centering = FALSE,
  table.envir = "table", position="H", linesep = "") %>%
  #table.env = 'table*' # to span multiple columns
  collapse_rows(latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)%>%
  kable_styling(latex_options = c("repeat_header"))

print(table_result_combined)
```

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=81$. The dashed green lines in the Q--Q plots represent theoretical expected quantiles for a normal distribution. Variations in the scales of the axes reflect differences in the range of values across datasets.", fig.width=6, fig.height=5}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

# Load saved results
load("./Data/resultsA_3.Rdata")
load("./Data/resultsA_5.Rdata")
load("./Data/resultsA_18.Rdata")
load("./Data/resultsA_36.Rdata")

# Specific sample size
selected_sample_size <- 81

# 
ggplot_list <- list()

#  L
for (L in c(3, 5, 18, 36)) {
  TestStatistics1 <- all_TestStatistics[[as.character(L)]]

  # 
  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
                aes(sample = Test_Statistics)) +
      geom_qq(col = "blue", shape = 20) +
      geom_qq_line(col = "darkgreen", linetype = 2) +
      labs(title = bquote(italic(L) == .(L)),
           x = "Theoretical Quantiles",
           y = "Sample Quantiles") +
      theme(plot.title = element_text(hjust = 0.5))#titulo centrado

    ggplot_list[[as.character(L)]] <- p
  } else {
    warning(paste("No size sample", selected_sample_size, " L =", L))
  }
}
combined_plot1 <- wrap_plots(ggplot_list, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot1)
```

We also evaluated the test's power by performing $1000$ simulations under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$ and $\alpha=-2$.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.

```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
# 
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value < alpha_nominal)  
}
R <- 1000
mu <- 1
B <- 100
lambda <- 0.9
L_values <- c(  5, 8, 18)
sample_sizes <- c( 25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results <- data.frame()
for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

    for (s in sample_sizes) {
      TestStat <- numeric(R)

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))

        #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
    }

    mu_W <- mean_entropy
    sigma_W <- sqrt(sd_entropy^2)

    p_values <- apply(TestStatistics, 1, function(row) {
      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
    })

    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
    results <- rbind(results, result)
  }
}
save(results, file = "./Data/type_I_results.Rdata")
```

```{r Simulated_power, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value)
}
calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}
# Function to calculate power for different L values and alpha_nominals
calculate_power <- function(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals) {
  results <- data.frame()

  for (L in L_values) {
    for (alpha_nominal in alpha_nominals) {
      TestStatistics <- list()
      mean_entropy <- numeric(length(sample_sizes))
      sd_entropy <- numeric(length(sample_sizes))

      for (s in sample_sizes) {
        TestStat <- numeric(R)

        for (r in 1:R) {
          z <- gi0_sample(mu, -2, L, s)
          TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))
          #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
          #TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
        }

        mean_entropy[sample_sizes == s] <- mean(TestStat)
        sd_entropy[sample_sizes == s] <- sd(TestStat)

        TestStatistics[[as.character(s)]] <- TestStat
      }

      mu_W <-  mean_entropy  
      sigma_W <- sqrt(sd_entropy^2)

      p_values <- lapply(TestStatistics, function(TestStat) {
        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
        })
      })

      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
      })

      power <- 1 - type_II_error_rates

      result_row <- data.frame(
        L = L,
        alpha_nominal = alpha_nominal,
        Sample_Size = sample_sizes,
        power = power
      )

      results <- rbind(results, result_row)
    }
  }

  return(results)
}
R <- 1000
mu <- 1
L_values <- c( 5,  8, 18)
B <- 100
lambda<- 0.9
sample_sizes <- c(25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results_power <- calculate_power(R, mu, L_values, B,lambda, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")
```

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#cat("\\setlength{\\tabcolsep}{4pt}\n")
load("./Data/type_I_results.Rdata")
type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
  sum(p_values) / length(p_values)  
})
type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
spread_results <- spread_results %>% 
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
load("./Data/results_power.Rdata")
summary_stats <- results_power %>%
  spread(key = alpha_nominal, value = power) %>%
  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
combined_results <- combined_results %>% 
  arrange(L, Sample_Size)
combined_results <- combined_results %>% 
  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
# LaTeX notation 
combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})
table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z})$ test statistic.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccccc",
  escape = FALSE,
  digits = 4,
  label = "table_size_power",
  centering = FALSE,
  table.envir = "table", position="htb", linesep = "")%>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0,  align = "c")%>%
  kable_styling(latex_options = "scale_down")%>%
  kable_styling( full_width = T)

print(table_combined_result)
```

# Results

This section presents the simulations we performed to evaluate the proposed test statistics' performance, followed by applications to SAR data.

## Simulated Data
```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom. (\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$. ',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 30, fig.height = 20}
knitr::include_graphics("./figs/Phantom1.png")
knitr::include_graphics("./figs/Phantom_labels.pdf")
```

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=5$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}

knitr::include_graphics("./figs/Entropy_Phantom_4_z1_200.png")
knitr::include_graphics("./figs/H_pvalue_Phantom_4_z1_200b.png")
knitr::include_graphics("./figs/H_005_Phantom_4_z1_AO_200b.png")

```

```{r sim_renyi1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=5$, $\\lambda=0.9$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
#knitr::include_graphics("./figs/sim_renyi_100.png")
knitr::include_graphics("./figs/Entropy_Phantom_4_renyi_B200_w7_L5_09.png")
knitr::include_graphics("./figs/H_pvalue_Phantom_4_renyi_B200_w7_L5_09.png")
knitr::include_graphics("./figs/H_005_Phantom_4_renyi_B200_w7_L5_09.png")

```

```{r real_SAR_Images_rotterdam, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=1$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}

knitr::include_graphics("./figs/Entropy_AO_Rotterdam_1024.png")
knitr::include_graphics("./figs/H_pvalue_AO_Rotterdam_1024.png")
knitr::include_graphics("./figs/H_005_AO_Rotterdam_1024.png")

```

```{r sim_rotter, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=1$, $\\lambda=2.0$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
#knitr::include_graphics("./figs/sim_renyi_100.png")
knitr::include_graphics("./figs/results_rotterdam_renyi_w7_2_0_07.png")
knitr::include_graphics("./figs/H_pvalue_results_rotterdam_renyi_w7_2_0_07.png")
knitr::include_graphics("./figs/H_005_results_rotterdam_renyi_w7_2_0_L1.png")

```

```{r mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=18$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}

knitr::include_graphics("./figs/Entropy_Mexico_512_18L_AO_200b.png")
knitr::include_graphics("./figs/H_pvalue_renyi_512_w7_L18_b200_090.png")
knitr::include_graphics("./figs/H_005__Mexico_512_18L_AO_200b.png")

```

```{r sim_mexixo, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=18$, $\\lambda=0.9$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
#knitr::include_graphics("./figs/sim_renyi_100.png")
knitr::include_graphics("./figs/Entropy_renyi_512_w7_L18_b200_090.png")
knitr::include_graphics("./figs/H_pvalue_Mexico_512_18L_AO_200b.png")
knitr::include_graphics("./figs/H_005_results_renyi_mexico512_w7_L18_b200_090.png")

```

## Analysis of Performance

The performance of the proposed methods was evaluated using the Mean Squared Error (MSE) as a global metric to compare the detection accuracy of heterogeneous regions. First, test statistics were computed for both Shannon and Rényi entropy-based approaches across the image using a sliding window of size \(7 \times 7\). Then, p-values were calculated for each window based on the distribution of the test statistics, assuming a null hypothesis of homogeneity. A significance level of \(\alpha = 0.05\) was applied to construct binary maps, where pixels with \(p \leq \alpha\) were classified as heterogeneous (value 1), and pixels with \(p > \alpha\) were classified as homogeneous (value 0).

The MSE values indicate that the Rényi entropy-based approach outperformed the Shannon entropy-based method, with a lower global MSE (Rényi: $0.1436$ vs. Shannon: $0.2066$). This result suggests that Rényi entropy captures heterogeneity more effectively. Additionally, local error maps comparing the binary predictions with the ground truth show that the Rényi entropy-based method has fewer misclassifications (errors) across the image, particularly in heterogeneous regions, further supporting its superior performance.

<!-- ```{r sim_renyi2, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Simulated image with Rényi Entropy, $L=5$, $\\lambda=0.75$, $n=81$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
<!-- #knitr::include_graphics("./figs/sim_renyi_100.png") -->
<!-- knitr::include_graphics("./figs/Entropy_sim_diff_renyi_100_075.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_sim_renyi_100_075.png") -->
<!-- knitr::include_graphics("./figs/H_005_sim_renyi_075_100w.png") -->

<!-- ``` -->

<!-- ```{r real_images_test_Illinois3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Shannon Entropy, Illinois-Region 1.',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->

<!-- knitr::include_graphics("./figs/Entropy_lake_512_36L_AO_100b.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_lake_512_36L_AO_100b.png") -->
<!-- knitr::include_graphics("./figs/H_005_lake_512_36L_AO_100b.png") -->
<!-- ``` -->

<!-- ```{r real_images_test_Illinois5, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 1, $\\lambda=0.8$, $n=81$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->

<!-- knitr::include_graphics("./figs/Entropy_illinois1_512_renyi_b200_08_L36_w9.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_illinois1_512_renyi_b200_08_L36_w9.png") -->
<!-- knitr::include_graphics("./figs/H_005_illinois1_512_renyi_b200_08_L36_w9.png") -->
<!-- ``` -->

<!-- ```{r real_images_test_Illinois4, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 1, $\\lambda=0.8$, $n=121$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->

<!-- knitr::include_graphics("./figs/Entropy_illinois1_512_renyi_b100_08_L36_w11.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_illinois1_512_renyi_b100_08_L36_w11.png") -->
<!-- knitr::include_graphics("./figs/H_005_illinois1_512_renyi_b100_08_L36_w11.png") -->
<!-- ``` -->

<!-- ```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Shannon Entropy, Illinois-Region 2.',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->

<!-- knitr::include_graphics("./figs/Entropy_Illinois_1024_36L_AO_200b.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_Illinois_1024_36L_AO_200b.png") -->
<!-- knitr::include_graphics("./figs/H_005_pvalues_Illinois_1024_36L_AO_200b.png") -->
<!-- ``` -->

<!-- ```{r real_images_test_Illinois2, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 2, with $L=36$, $\\lambda=0.75$, $n=121$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->

<!-- knitr::include_graphics("./figs/Entropy_illinois_1024_renyi_b200_075_L36_w11.png") -->
<!-- knitr::include_graphics("./figs/H_pvalue_illinois_1024_renyi_b200_075_L36_w11.png") -->
<!-- knitr::include_graphics("./figs/H_005_illinois_1024_renyi_b200_075_L36_w11.png") -->
<!-- ``` -->
```{=html}
<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
```

\appendix

\section{ Derivation of the Rényi Entropy for the \( G_I^0 \) Distribution}\label{app1}

The Rényi entropy of order \( \lambda \) for a continuous random variable \( Z \) with density \( f_Z(z) \) is given by:

\[
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz \right), \quad \lambda > 0, \, \lambda \neq 1.
\]

For \( Z \sim G_I^0(\alpha, \gamma, L) \), the density function is:

\[
f_Z(z) = C \cdot \frac{z^{L - 1}}{(\gamma + L z)^{L - \alpha}}, \quad \text{where} \quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}.
\]

Raising \( f_Z(z) \) to the power \( \lambda \) and substituting into the entropy integral, we have:

\[
I = \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz = C^\lambda \int_{0}^{\infty} \frac{z^{\lambda(L - 1)}}{(\gamma + L z)^{\lambda(L - \alpha)}} \, dz.
\]

Using the substitution \( t = \frac{L z}{\gamma} \), \( z = \frac{\gamma t}{L} \), and \( dz = \frac{\gamma}{L} \, dt \), we get:

\[
I = C^\lambda \cdot \frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L - 1)}} \int_{0}^{\infty} \frac{t^{\lambda(L - 1)}}{(1 + t)^{\lambda(L - \alpha)}} \, dt.
\]

This integral is expressed in terms of the Beta function:

\[
\int_{0}^{\infty} \frac{t^{a - 1}}{(1 + t)^{a + b}} \, dt = B(a, b), \quad \text{where} \quad a = \lambda(L - 1) + 1, \quad b = \lambda(-\alpha + 1) - 1.
\]

Thus,

\[
I = C^\lambda \cdot \frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L - 1)}} \cdot B(a, b).
\]

We simplify the powers of \( \gamma \) and \( L \):

\[
\gamma^{1 + \lambda(\alpha - 1)} = \gamma^{1 - \lambda + \lambda \alpha}, \quad L^{1 + \lambda(L - 1)} = L^{\lambda L + 1 - \lambda}.
\]

Substituting \( C^\lambda = L^{L \lambda} \gamma^{-\alpha \lambda} \left( \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right)^\lambda \), we obtain:

\[
I = \gamma^{1 - \lambda} L^{\lambda - 1} \left( \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right)^\lambda B(a, b).
\]

The Rényi entropy is therefore:

\[
H_\lambda(Z) = \frac{1}{1 - \lambda} \left[ \ln \left( \gamma^{1 - \lambda} L^{\lambda - 1} \left( \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right)^\lambda B(a, b) \right) \right].
\]

Simplifying:

\[
H_\lambda(G_I^0 ) = \ln \left( \frac{\gamma}{L} \right) + \frac{1}{1 - \lambda} \left[ \lambda (\ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L)) + \ln B(a, b) \right].
\]

Using the Beta function property \( \ln B(a, b) = \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b) \), where \( a + b = \lambda(L - \alpha) \), we get the final expression:

\[
H_\lambda(G_I^0 ) = \ln \left( \frac{\gamma}{L} \right) + \frac{1}{1 - \lambda} \left[ \lambda (\ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L)) + \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(\lambda(L - \alpha)) \right].
\]

Given that the mean \( \mu \) is related to \( \gamma \) by:

\[
\mu = -\frac{\gamma}{\alpha + 1} \quad \Rightarrow \quad \gamma = -\mu(\alpha + 1),
\]

substituting \( \gamma \) into the entropy expression:

\begin{multline*}
H_\lambda(G_I^0 ) = \ln\left( \frac{ -\mu(\alpha + 1) }{ L } \right)\\
+ \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{multline*}
Therefore:
\begin{multline}
H_\lambda(G_I^0 ) = \ln \mu+ \ln (-1-\alpha)-\ln L \\
+ \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
\end{multline}

##  Derivation of the Rényi Entropy for the \( \Gamma_{\text{SAR}} \) Distribution

To compute the Rényi entropy of \( \Gamma_{\text{SAR}}(L, \mu) \), we need to evaluate the integral:

\[
I = \int_{0}^{\infty} [f_Z(z; L, \mu)]^\lambda \, dz = \left( \frac{L^L}{\Gamma(L) \mu^L} \right)^\lambda \int_{0}^{\infty} z^{\lambda(L - 1)} \, e^{-\lambda L z / \mu} \, dz.
\]

This integral can be evaluated using the Gamma integral formula:

\[
\int_{0}^{\infty} x^{p - 1} e^{-q x} \, dx = \frac{\Gamma(p)}{q^p}, \quad \text{for } p > 0, \ q > 0,
\]

where \( p = \lambda L - \lambda + 1 \) and \( q = \frac{\lambda L}{\mu} \). Substituting these values into the integral, we obtain:

\[
I = \left( \frac{L^L}{\Gamma(L) \mu^L} \right)^\lambda \frac{\Gamma(\lambda L - \lambda + 1)}{\left( \frac{\lambda L}{\mu} \right)^{\lambda L - \lambda + 1}}.
\]

The natural logarithm of the integral is then given by:

\[
\ln I = \lambda \left( L \ln L - L \ln \mu - \ln \Gamma(L) \right) + \ln \Gamma(\lambda L - \lambda + 1) - \left( \lambda L - \lambda + 1 \right) \left( \ln \lambda L - \ln \mu \right).
\]

The Rényi entropy \( H_\lambda(Z) \) can be computed by substituting \( \ln I \) into the definition:

\[
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln I.
\]

Expanding and simplifying the terms, the Rényi entropy of \( \Gamma_{\text{SAR}}(L, \mu) \) becomes:

\[
H_\lambda(\Gamma_{\text{SAR}}) = \frac{1}{\lambda - 1} \left[ \lambda \ln \Gamma(L) - \ln \Gamma\big( \lambda(L - 1) + 1 \big) - (\lambda - 1) \big( \ln L - \ln \mu \big) + \big( \lambda(L - 1) + 1 \big) \ln \lambda \right].
\]

### 2025-01-02 Text/Reports/report-independence/R0-article-report-independence.Rmd
new codes

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
bibliography: ../../Common/references.bib
header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \usepackage{amsmath}
   - \usepackage{amssymb}
   - \captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=1pt, 
        belowskip=1pt,
        singlelinecheck=off,
        justification=centering}   
biblio-style: apsr
title: "Characterizing SAR Image Regions via Mean and Coefficient of Variation Analysis"
thanks: ""
author:
- name: J. Alpala
  affiliation: 
abstract: "
We examine the independence between the sample mean and the coefficient of variation (CV) to identify heterogeneity in Synthetic Aperture Radar (SAR) imaging data. The independence of these statistics implies that the underlying data follow a Gamma distribution. We utilize two main models to detect heterogeneity: the Gamma SAR and ${G}_I^0$ models. The first is more tractable and enables the identification of homogeneous areas without resorting to the complexity of the latter.
"
keywords: "Gamma distribution, coefficient of variation, mean, heterogeneity, SAR "
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: libertine
fontsize: 11pt
# spacing: double
endnote: no
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE,
                      fig.path='figs/',
                      cache.path = '_cache/',
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })

library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD
library(minpack.lm)
library(univariateML)

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")

source("../../../Code/R/MainFunctions/van_es_estimator.R")
source("../../../Code/R/MainFunctions/correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/vasicek_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")

source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
source("../../../Code/R/MainFunctions/bootstrap_al_omari_2_estimator.R")
#The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
source("../../../Code/R/Programs/read_ENVI_images.R")

```

# Introduction

Synthetic Aperture Radar (SAR) technology has become essential for environmental monitoring and disaster management. It provides valuable images under various conditions, including day or night and weather situations&nbsp;\cite{Moreira2013,Mu2019}.
However, the effective use of SAR data depends on a thorough understanding of its statistical properties because it is corrupted by speckle.
This noise-like interference effect is inherent in SAR data due to the coherent nature of the imaging process&nbsp;\cite{Argenti2013}.

Speckle in intensity format is non-Gaussian. Thus, SAR data require reliable statistical models for accurate processing. 
The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes the
Gamma law as the limiting case for fully-developed speckle&nbsp;\cite{Ferreira2020} and provides flexibility with fewer parameters for analysis.

Our work aims to improve the identification of potential roughness features in SAR intensity data.
Physical modeling of SAR data allows the use of the Gamma distribution in the presence of fully-developed speckle, where an infinite number of independent backscatterers per resolution unit is assumed, commonly referred to as homogeneous regions.

In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous returns, particularly between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known.

# Background {#sec:Background}

## Statistical Modeling of Intensity SAR data

The primary models for intensity SAR data include the Gamma and
$\mathcal{G}_I^0$ distributions [@Frery1997]. The first is suitable for
fully-developed speckle and is a limiting case of the second model. This
is interesting due to its versatility in accurately representing regions
with different roughness properties [@Cassetti2022]. We denote
$Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and
$Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows
the distributions characterized by the respective probability density
functions (pdfs): \begin{align}
    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
    \intertext{ and }
    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align} where $\mu > 0$ is the mean, $\gamma > 0$ is the scale,
$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of looks
(either nominal or estimated, thus not restricted to integer values),
$\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the
indicator function of the set $A$.

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation} provided $\alpha <-r$, and infinite otherwise. Therefore,
assuming $\alpha<-1$, its expected value is \begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

Although the $\mathcal{G}_I^0$ distribution is defined by the parameters
$\alpha$ and $\gamma$, in the SAR literature \cite{Nascimento2010} the
texture $\alpha$ and the mean $\mu$ are usually used.
Reparametrizing \eqref{E:gi01} with $\mu$, and denoting this model as
$G_I^0$ we obtain: \begin{equation}
        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
\end{equation}

# Simulations

To evaluate the relationship between the sample mean and the coefficient of variation (CV) across different levels of roughness, we simulated data from the $\mathcal{G}_I^0$ distribution for various values of the parameter $\alpha$ ($\alpha = -1.5, -3, -5, -10, -50, -1000$). For each $\alpha$, we generated multiple samples and plotted the CV versus the mean in subplots. These subplots collectively illustrate the transition from dependence to independence between the mean and CV as $\alpha$ decreases (becomes more negative). Specifically, at higher values of $\alpha$ (e.g., $\alpha = -1.5$), the scatter plots exhibit a logarithmic pattern, indicating a strong dependence characteristic of heterogeneous regions. As $\alpha$ approaches $-\infty$ (e.g., $\alpha = -1000$), the scatter plots display a random distribution of points, reflecting independence between the mean and CV, which is consistent with the behavior of the Gamma distribution and indicates homogeneity.

```{r Plot_empirical_gamma_and_gi0, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Scatter plot of CV versus Mean for for different $\\alpha$ values ."}

source("../../../Code/R/MainFunctions/gi0_sample.R")

sample.size <- 49
R <- 10000
mu <- 1
L <- 5

# Valores específicos de alpha
alphas <- c(-1.5, -3, -5, -10, -50, -1000)

results <- data.frame()

for (alpha in alphas) {
  means <- numeric(R)
  cvs <- numeric(R)

  for (r in 1:R) {
    z <- gi0_sample(mu, alpha, L, sample.size)
    means[r] <- mean(z)
    cvs[r] <- sd(z) / mean(z)
  }

  temp_data <- data.frame(Mean = means, CV = cvs, Alpha = factor(alpha))
  results <- rbind(results, temp_data)
}

# Crear el gráfico con facet_wrap
p <- ggplot(results, aes(x = Mean, y = CV)) +
  geom_point(alpha = 0.5, color = "#56B4E9", size = 0.5) +
  labs(title = "",#Scatter Plot of CV versus Mean for Different Alpha Values
       x = "Mean",
       y = "CV") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16),
    axis.title = element_text(size = 12),
    strip.text = element_text(size = 12),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  ) +
  facet_wrap(~ Alpha, ncol = 3, scales = "free")

# Mostrar el gráfico
print(p)

```

# Model Fitting

<!-- To model the dependency observed in the $G_I^0$ distribution, we used the following model: -->

<!-- $$ -->
<!-- \text{model}(\bar{x}) = \sqrt{n} \left(1 - \exp \left(- (\beta_0 + \beta_1 \bar{x})\right) \right) -->
<!-- $$ -->

<!-- where $\beta_0$ and $\beta_1$ are parameters, the p-value for $\beta_1$ plays a crucial role in understanding the fit of the model and the nature of the data distribution. -->

```{r Plot_gi02, echo=FALSE, message=FALSE, warning=FALSE, out.width="70%", fig.show="hold", fig.align="center", fig.pos="H", fig.cap="Scatter plot of CV versus Mean, $\\alpha=-1.5$."}

source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
source("../../../Code/R/MainFunctions/entropy_gI0.R")
source("../../../Code/R/MainFunctions/gi0_sample.R")
set.seed(1234567890, kind = "Mersenne-Twister")

# Parámetros de la simulación
sample.size <- 49
R <- 10000
mu <- 1
L <- 5
alpha1 <- -1.5

# Inicializar vectores para medias y coeficientes de variación
means <- numeric(R)
cvs <- numeric(R)

# Generar muestras y calcular medias y CVs
for (r in 1:R) {
  z <- gi0_sample(mu, alpha1, L, sample.size)
  means[r] <- mean(z)
  cvs[r] <- sd(z) / mean(z)
}

# Crear un dataframe
data <- data.frame(Mean = means, CV = cvs)

# Ajustar modelo con nlsLM para un ajuste robusto
nls_model_exp_simplified_lm <- nlsLM(CV ~ sqrt(sample.size) * (1 - exp(-(beta0 + beta1 * Mean)) - beta2),
                                     data = data, start = list(beta0 = 0.1, beta1 = 0.01, beta2 = 0.01))

# Resumen del modelo ajustado
#summary(nls_model_exp_simplified_lm)

# Añadir predicciones al dataframe
data$Fitted_CV_simplified_lm <- predict(nls_model_exp_simplified_lm)

# Graficar los datos y el modelo ajustado
ggplot(data, aes(x = Mean, y = CV)) +
  # Puntos de datos
  geom_point(alpha = 0.5, color = "red") +
  # Línea de predicción ajustada
  geom_line(aes(y = Fitted_CV_simplified_lm), color = "blue", size = 1) +
  # Etiquetas y título
  labs(title = paste("Scatter plot of CV versus Mean for gI0 distribution, alpha =", alpha1),
       x = "Mean",
       y = "Coefficient of Variation (CV)") +
  # Tema minimalista
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  )

# set.seed(1234567890, kind = "Mersenne-Twister")
# 
# sample.size <- 49
# R <- 10000
# mu <- 1
# L <- 5
# alpha1 <- -1.5
# means <- numeric(R)
# cvs <- numeric(R)
# 
# for (r in 1:R) {
#   z <- gi0_sample(mu, alpha1, L, sample.size)
#   means[r] <- mean(z)
#   cvs[r] <- sd(z) / mean(z)
# }
# 
# 
# data <- data.frame(Mean = means, CV = cvs)
# 
# # 
# start_values <- list(beta0 = 0.5, beta1 = 0.5)
# model <- nls(CV ~ sqrt(sample.size) * (1 - exp(-1.0*(beta0 + beta1 * Mean))), 
#              data = data, start = start_values)
# 
# # 
# #summary(model)
# 
# # 
# ggplot(data, aes(x = Mean, y = CV)) +
#   geom_point(alpha = 0.5, color = "red") +
#   stat_function(fun = function(x) sqrt(sample.size) * (1 - exp(-(coef(model)[1] + coef(model)[2] * x))),
#                 color = "blue", size = 1) +
#   labs(title = "Scatter plot of CV versus Mean for gI0 distribution",
#        x = "Mean",
#        y = "Coefficient of Variation (CV)") +
#   theme_minimal() +
#   theme(
#     plot.title = element_text(hjust = 0.5),
#     panel.grid.major = element_line(color = "gray80"),
#     panel.grid.minor = element_line(color = "gray90")
#   )

```

<!-- \section{Mathematical Justification of the Regression Model and Hypothesis Testing} -->

<!-- In this section, we provide a mathematical justification for fitting the regression model to our data using the likelihood function and formulating a hypothesis test. We use the following model to capture the relationship between the coefficient of variation (CV) and the sample mean $\bar{x}$. -->

We consider the regression model:

\begin{equation}
E(V_n\mid\bar{X}_n=\bar{x}_n) = \sqrt{n} \left(1 - \exp\left(- (\beta_0 + \beta_1 \bar{x}_n)\right) - \beta_2 \right),
\label{eq:model}
\end{equation}

where:
\begin{itemize}
    \item $\text{CV}$ is the sample coefficient of variation.
    \item $\bar{x}$ is the sample mean.
    \item $n$ is the sample size 
    \item $\beta_0$, $\beta_1$, and $\beta_2$ are parameters to be estimated.
\end{itemize}

This nonlinear model captures the relationship between $\text{CV}$ and $\bar{x}$, reflecting the behavior observed in the data, particularly when analyzing the dependence between these two statistics in SAR images.

\subsection{Hypothesis Testing for $\beta_1$}

Our goal is to test whether there is a significant dependence between the CV and the sample mean $\bar{x}$. Specifically, we test the null hypothesis:

\begin{equation}
H_0: \beta_1 = 0 \quad \text{(no dependence)},
\end{equation}

against the alternative hypothesis:

\begin{equation}
H_1: \beta_1 \neq 0 \quad \text{(dependence exists)}.
\end{equation}

\subsubsection{Test Statistic}

Under the assumption of normally distributed errors, the test statistic for $\beta_1$ is:

\begin{equation}
t = \frac{\hat{\beta}_1}{\text{SE}(\hat{\beta}_1)},
\end{equation}

where $\text{SE}(\hat{\beta}_1)$ is the standard error of $\hat{\beta}_1$. This statistic follows a $t$-distribution with $B - p$ degrees of freedom, where $p$ is the number of parameters estimated (here, $p = 2$).

\subsubsection{P-value Calculation}

The p-value is calculated as:

\begin{equation}
p\text{-value} = 2 \times P(T > |t|),
\end{equation}

where $T$ follows a $t$-distribution with $B - 2$ degrees of freedom.

<!-- \subsection{Interpretation of the Test} -->

<!-- \begin{itemize} -->
<!--     \item \textbf{If the p-value is less than the significance level $\alpha$ (e.g., $0.05$):} -->
<!--     \begin{itemize} -->
<!--         \item We reject the null hypothesis $H_0$. -->
<!--         \item Conclude that $\beta_1$ is significantly different from zero. -->
<!--         \item There is evidence of dependence between CV and $\bar{x}$. -->
<!--         \item The data is better modeled by the $\mathcal{G}_I^0$ distribution, indicating heterogeneity. -->
<!--     \end{itemize} -->
<!--     \item \textbf{If the p-value is greater than $\alpha$:} -->
<!--     \begin{itemize} -->
<!--         \item We fail to reject the null hypothesis $H_0$. -->
<!--         \item Conclude that there is no significant evidence of dependence. -->
<!--         \item The data can be modeled by the Gamma distribution, indicating homogeneity. -->
<!--     \end{itemize} -->
<!-- \end{itemize} -->

<!-- \subsection{Application to Sliding Windows in SAR Images} -->

<!-- Due to the limited sample size in each sliding window (e.g., $n = 7 \times 7 = 49$ pixels), we employ bootstrapping to generate multiple pairs $(\bar{x}_i, \text{CV}_i)$ within each window. -->

<!-- \subsubsection{Bootstrapping Procedure} -->

<!-- \begin{enumerate} -->
<!--     \item For each window, resample the data with replacement $B$ times. -->
<!--     \item For each resampled dataset, compute $\bar{x}_i$ and $\text{CV}_i$. -->
<!--     \item Collect the $B$ pairs $(\bar{x}_i, \text{CV}_i)$ for regression analysis. -->
<!-- \end{enumerate} -->

<!-- This approach allows us to estimate the distribution of the estimators and their standard errors, increasing the reliability of our statistical inferences. -->

\subsection{Results and Visualization}

By applying the above methodology to each sliding window in the SAR image, we obtain a matrix of p-values corresponding to the estimated $\beta_1$ in each window.

\begin{itemize}
    \item Regions with low $p$-values (e.g., $p < 0.05$) indicate significant dependence, suggesting heterogeneity.
    \item Regions with high $p$-values indicate no significant dependence, suggesting homogeneity.
\end{itemize}

These results can be visualized by mapping the p-values across the image, highlighting areas of heterogeneity and homogeneity.

# Results

This section presents the simulations we performed to evaluate the proposed test statistics' performance, followed by applications to SAR data.

## Simulated Data
```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom. (\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$. ',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 30, fig.height = 20}
knitr::include_graphics("./figs/Phantom1.png")
knitr::include_graphics("./figs/Phantom_labels.pdf")
```

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm"),  fig.ncol=2, fig.width = 30, fig.height = 20,fig.hspace=1.5}

knitr::include_graphics("./figs/H_pvalue_results_nlsLM_subsample_4z_7w.png")
knitr::include_graphics("./figs/H_005_nlsLM_subsample_4z_7w.png")
#knitr::include_graphics("./figs/H_005_Phantom_4_z1_AO_200b.png")

```

```{=html}
<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
```

### 2025-01-02 Code/R/MainFunctions/al_omari_2_estimator.R

@@ -22,6 +22,13 @@ al_omari_2_estimator <- function(data) {
   return(sum_term / n)
 }
 
+set.seed(1234567890, kind = "Mersenne-Twister")
+#set.seed(123)
+data <- rnorm(1000)  # Generar una muestra aleatoria de 100 datos
+#alpha <- 0.99       # Parámetro de orden de la entropía de Rényi
+AO <- al_omari_2_estimator(data)
+print(AO)
+
 # # Example usage:
 # data <- c(1.2, 1.5,3.6, 2.0, 2.1, 2.5, 2.6, 3.0, 3.1, 3.5)
 # result <- al_omari_2_estimator(data)

### 2025-01-02 Code/R/MainFunctions/entropy_GI0_renyi.R

@@ -1,0 +1,46 @@
+# entropia exacta
+rm(list = ls())
+entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
+  if (lambda <= 0 || lambda == 1) {
+    stop("Lambda debe ser mayor que 0 y diferente de 1.")
+  }
+  
+  # Calcular gamma
+  gamma <- -mu * (alpha + 1)
+  if (gamma <= 0) {
+    stop("Gamma debe ser positiva. Verifica los valores de mu y alpha.")
+  }
+  
+  # Calcular a, b y suma
+  a <- lambda * (L - 1) + 1
+  b <- lambda * (-alpha + 1) - 1
+  ab_sum <- lambda * (L - alpha)
+  
+  # Verificar que los argumentos de las funciones gamma sean positivos
+  if (a <= 0 || b <= 0 || ab_sum <= 0) {
+    stop("Los argumentos de las funciones gamma deben ser positivos. Verifica los valores de lambda, L y alpha.")
+  }
+  
+  # Calcular los términos
+  term1 <- log(gamma / L)
+  
+  term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))
+  
+  term3 <- lgamma(a)
+  term4 <- lgamma(b)
+  term5 <- lgamma(ab_sum)
+  
+  numerator <- term2 + term3 + term4 - term5
+  
+  entropy <- term1 + numerator / (1 - lambda)
+  
+  return(entropy)
+}
+
+alpha <- -3
+mu <- 1.0
+L <- 5
+lambda <- 0.8
+
+entropy_value <- entropy_GI0_renyi(alpha, mu, L, lambda)
+print(entropy_value)

### 2025-01-02 Code/R/PlottingFunctions/gamma_sar_L3.R

@@ -1,52 +1,0 @@
-# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
-# It uses non-parametric estimators to calculate the sample mean and standard deviation 
-# of the entropy for various sample sizes.
-# The code also includes error bars based on the standard deviation for visualization.
-
-
-
-rm(list = ls())
-library(ggplot2)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-set.seed(1234567890, kind="Mersenne-Twister")
-
-
-# Define sample sizes, the number of repetitions, and parameters
-sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
-R <- 10000
-mu <- 1
-L <- 3
-
-# Initialize the output data frame
-output <- NULL
-
-# Perform non-parametric entropy estimation for different sample sizes
-for(ssize in sample_sizes) {
-  v.nonparametric.entropy <- NULL
-  for(r in 1:R) {
-    sample <- gamma_sar_sample(L, mu, ssize)
-    v.nonparametric.entropy[r] <- van_es_estimator(sample)
-  }
-  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
-}
-
-# Create a data frame with results
-output <- data.frame(output)
-names(output) <- c("Mean", "Std")
-output$SampleSize <- sample_sizes
-
-#plot
-ggplot(output, aes(x=SampleSize, y=Mean)) +
-  geom_hline(yintercept = entropy_gamma_sar(3, 1)) +
-  geom_line() +
-  geom_point() +
-  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
-  xlab("Sample Size") +
-  scale_x_log10(breaks=output$SampleSize) +
-  ylab("Mean Non-parametric Entropy")
-
-# Save the plot as a PDF file
-ggsave("myplot.pdf")
-

### 2025-01-02 Code/R/PlottingFunctions/gamma_sar_L8.R

@@ -1,53 +1,0 @@
-# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
-# It uses non-parametric estimators to calculate the sample mean and standard deviation 
-# of the entropy for various sample sizes.
-# The code also includes error bars based on the standard deviation for visualization.
-
-# Clear the workspace and load necessary functions
-rm(list = ls())
-library(ggplot2)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-# Define sample sizes, the number of repetitions, and parameters
-sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
-R <- 10000
-mu <- 1
-L <- 8
-
-# Initialize the output data frame
-output <- NULL
-
-# Perform non-parametric entropy estimation for different sample sizes
-for(ssize in sample_sizes) {
-  v.nonparametric.entropy <- NULL
-  for(r in 1:R) {
-    sample <- gamma_sar_sample(L, mu, ssize)
-    v.nonparametric.entropy[r] <- van_es_estimator(sample)
-  }
-  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
-}
-
-
-# Create a data frame with results
-output <- data.frame(output)
-names(output) <- c("Mean", "Std")
-output$SampleSize <- sample_sizes
-
-
-#plot
-ggplot(output, aes(x=SampleSize, y=Mean)) +
-  geom_hline(yintercept = entropy_gamma_sar(8, 1)) +
-  geom_line() +
-  geom_point() +
-  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +
-  xlab("Sample Size") +
-  scale_x_log10(breaks=output$SampleSize) +
-  ylab("Mean Non-parametric Entropy")
-
-# Save the plot as a PDF file
-ggsave("myplot.pdf")
-

### 2025-01-02 Code/R/PlottingFunctions/gamma_sar_mu3_L8.R

@@ -1,56 +1,0 @@
-# This code demonstrates non-parametric entropy estimation for Gamma SAR data.
-# It uses non-parametric estimators to calculate the sample mean and standard deviation 
-# of the entropy for various sample sizes.
-# The code also includes error bars based on the standard deviation for visualization.
-
-
-
-rm(list = ls())
-library(ggplot2)
-source("../MainFunctions/gamma_sar_sample.r")
-source("../MainFunctions/van_es_estimator.r")
-source("../MainFunctions/entropy_gamma_sar.r")
-
-
-set.seed(1234567890, kind="Mersenne-Twister")
-
-
-# Define sample sizes, the number of repetitions, and parameters
-sample_sizes <- c(9, 25, 121, 1000, 10000, 100000)
-R <- 10000
-mu <- 3
-L <- 8
-
-
-# Initialize the output data frame
-output <- NULL
-
-# Perform non-parametric entropy estimation for different sample sizes
-for(ssize in sample_sizes) {
-  v.nonparametric.entropy <- NULL
-  for(r in 1:R) {
-    sample <- gamma_sar_sample(L, mu, ssize)
-    v.nonparametric.entropy[r] <- van_es_estimator(sample)
-  }
-  output <- rbind(output, c(mean(v.nonparametric.entropy), sd(v.nonparametric.entropy)))
-}
-
-# Create a data frame with results
-output <- data.frame(output)
-names(output) <- c("Mean", "Std")
-output$SampleSize <- sample_sizes
-
-
-#plot
-ggplot(output, aes(x = SampleSize, y = Mean)) +
-  geom_hline(yintercept = entropy_gamma_sar(8, 3)) +
-  geom_line() +
-  geom_point() +
-  geom_errorbar(aes(ymin = Mean - Std, ymax = Mean + Std), width = 0.1) +  #comment this line
-  xlab("Sample Size") +
-  scale_x_log10(breaks = output$SampleSize) +
-  ylab("Mean Non-parametric Entropy")
-
-# Save the plot as a PDF file
-ggsave("myplot.pdf")
-

### 2025-01-02 Code/R/Programs/CV_vs_Media_Bootstrap.R

@@ -1,0 +1,75 @@
+#535
+# Load necessary functions and libraries
+rm(list = ls())
+source("../MainFunctions/gi0_sample.R")
+library(minpack.lm)
+
+# Set parameters
+#set.seed(1234567890, kind = "Mersenne-Twister")
+sample.size <- 121
+R <- 2000
+mu <- 1
+L <- 5
+alpha1 <- -2.5 # Very negative alpha
+
+# Generate one sample from gi0 distribution
+z <- gi0_sample(mu, alpha1, L, sample.size)
+
+# Initialize vectors to store means and CVs
+means <- numeric(R)
+cvs <- numeric(R)
+
+# Generate bootstrap samples and compute means and CVs with additional conditions
+for (r in 1:R) {
+  valid_sample <- FALSE
+  while (!valid_sample) {
+    # Generate bootstrap sample with replacement
+    bootstrap_sample <- sample(z, size = sample.size, replace = TRUE)
+    
+    # Check if the sample has all unique values and finite results
+    if (!all(bootstrap_sample == bootstrap_sample[1]) && 
+        is.finite(mean(bootstrap_sample)) && 
+        is.finite(sd(bootstrap_sample))) {
+      
+      # Calculate mean and CV
+      means[r] <- mean(bootstrap_sample)
+      cvs[r] <- sd(bootstrap_sample) / means[r]
+      valid_sample <- TRUE
+    }
+  }
+}
+
+# Create data frame
+data <- data.frame(Mean = means, CV = cvs)
+
+# Plot the data to visualize the relationship
+plot(data$Mean, data$CV, xlab = "Media", ylab = "CV", 
+     main = paste("CV vs Media (Bootstrap), alpha =", alpha1), pch = 16, cex = 0.5)
+
+# Adjust starting values based on data characteristics
+# Since CV is nearly constant, we can simplify the model
+
+# Simplified model: CV ~ constant
+# Compute the average CV as the initial estimate
+initial_cv <- mean(data$CV)
+
+# Use nlsLM for robust fitting with adjusted starting values and bounds
+nls_model_exp_simplified_lm <- nlsLM(
+  CV ~ sqrt(sample.size) * (1 - exp(-(beta0 + beta1 * Mean)) - beta2),
+  data = data,
+  start = list(beta0 = -0.1, beta1 = 0.1, beta2 = 0),
[…]

### 2025-01-02 Code/R/Programs/CV_vs_Media_Bootstrap2.R

@@ -1,0 +1,80 @@
+#537
+# Load necessary functions and libraries
+rm(list = ls())
+source("../MainFunctions/gi0_sample.R")
+library(minpack.lm)
+
+# Set parameters
+#set.seed(1234567890, kind = "Mersenne-Twister")
+sample.size <- 200
+R <- 3000
+mu <- 1
+L <- 5
+alpha1 <- -1.5 # Very negative alpha
+
+# Generate one sample from gi0 distribution
+z <- gi0_sample(mu, alpha1, L, sample.size)
+
+# Initialize vectors to store means and CVs
+means <- numeric(R)
+cvs <- numeric(R)
+
+# Generate bootstrap samples with variable size and additional conditions
+for (r in 1:R) {
+  valid_sample <- FALSE
+  while (!valid_sample) {
+    # Generate a variable bootstrap sample size within 80% to 100% of original size
+    bootstrap.size <- sample(seq(round(sample.size * 0.95), sample.size), 1)
+    bootstrap_sample <- sample(z, size = bootstrap.size, replace = TRUE)
+    
+    # Calculate mean and CV
+    current_mean <- mean(bootstrap_sample)
+    current_cv <- sd(bootstrap_sample) / current_mean
+    
+    # Check conditions: variability in mean and CV, finite results, and sufficient diversity
+    if (!all(bootstrap_sample == bootstrap_sample[1]) && 
+        is.finite(current_mean) && is.finite(current_cv) &&
+        (r == 1 || abs(current_mean - means[r-1]) > 0.05) && 
+        (r == 1 || abs(current_cv - cvs[r-1]) > 0.05)) {
+      
+      means[r] <- current_mean
+      cvs[r] <- current_cv
+      valid_sample <- TRUE
+    }
+  }
+}
+
+# Create data frame
+data <- data.frame(Mean = means, CV = cvs)
+
+# Plot the data to visualize the relationship
+plot(data$Mean, data$CV, xlab = "Media", ylab = "CV", 
+     main = paste("CV vs Media (Bootstrap), alpha =", alpha1), pch = 16, cex = 0.5)
+
+# Adjust starting values based on data characteristics
+# Since CV is nearly constant, we can simplify the model
+
+# Simplified model: CV ~ constant
+# Compute the average CV as the initial estimate
[…]

### 2025-01-02 Code/R/Programs/Entropy_test_mato_grosso_2048.R

@@ -1,0 +1,49 @@
+# Inicia el temporizador
+start_time <- Sys.time()
+
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+
+# x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Baja_California_1024/Intensity_HH.img',
+#                  headerfile='../../../Data/SAR/Baja_California_1024/Intensity_HH.hdr')
+x <- myread.ENVI(file='../../../Data/SAR/mato_grosso_2048/Intensity_VV.img',
+                 headerfile='../../../Data/SAR/mato_grosso_2048/Intensity_VV.hdr')
+
+
+# L <- 7.89
+# B <- 200
+L <- 5
+B <- 200
+window_size <- 7
+rows <- nrow(x)
+cols <- ncol(x)
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterar sobre ventanas deslizantes
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    difference_values[i, j] <- bootstrap_al_omari_1_estimator(window_data, B)- (log(mean(window_data)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+  }
+}
+
+# Guarda los resultados
+save(difference_values, x, file = "./Data/results_mato_grosso_2048_7_AO.Rdata")
+
+# Detén el temporizador
+end_time <- Sys.time()
+
[…]

### 2025-01-02 Code/R/Programs/ExperimentTestStatisticL_gamma.R

@@ -3,16 +3,16 @@ library(ggplot2)
 library(ggsci)
 library(invgamma)
 
-if(!require("rstudioapi")) install("rstudioapi")
-setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
 
 
 source("../MainFunctions/ebrahimi_estimator.R")
-source("../MainFunctions/gamma_sar_sample.R")
-
+source("../MainFunctions/gamma_sar_sample.R")#renyi_entropy_estimator
+source("../MainFunctions/renyi_entropy_estimator.R")
 source("../MainFunctions/correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator.R")
-source("../MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../MainFunctions/bootstrap_renyi_entropy_estimator.R")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.R")
 
 
 
@@ -23,10 +23,10 @@ set.seed(1234567890, kind="Mersenne-Twister")
 
 R <- 1000 # 
 mu <- 1
-L <- 2
-B <- 5
+L <- 5
+B <- 50
 
-sample.size <- c(9, 25, 49, 81)
+sample.size <- c( 25, 49)
 
 TestStatistics <- NULL
 
@@ -35,7 +35,7 @@ for(s in sample.size){
     
     z <- gamma_sar_sample(L, mu, s) #
     
-    TestStat <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
+    TestStat <- bootstrap_ebrahimi_estimator(z, B, 0.999) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
   
    
     TestStatistics <- rbind(TestStatistics,

### 2025-01-02 Code/R/Programs/Gamma_GLM_model.R

@@ -1,0 +1,69 @@
+# Load necessary libraries
+rm(list = ls())
+library(ggplot2)
+library(ggsci)
+library(MASS)  # For Gamma GLM
+library(gridExtra)
+
+# Source your custom functions
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+# Set seed for reproducibility
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Simulation parameters
+sample.size <- 49
+R <- 10000
+mu <- 1
+L <- 5
+alpha1 <- -1.5 # You can change this value for different scenarios
+
+# Initialize vectors to store means and CVs
+means <- numeric(R)
+cvs <- numeric(R)
+
+# Simulate data
+for (r in 1:R) {
+  z <- gi0_sample(mu, alpha1, L, sample.size)
+  means[r] <- mean(z)
+  cvs[r] <- sd(z) / mean(z)
+}
+
+# Prepare data frame
+data <- data.frame(Mean = means, CV = cvs)
+
+# Fit the Gamma GLM with log link
+model_glm <- glm(CV ~ Mean, family = Gamma(link = "log"), data = data)
+
+# Summary of the model
+summary(model_glm)
+
+# Extract coefficients
+coefficients <- coef(model_glm)
+
+# Create a sequence of Mean values for plotting the fitted curve
+mean_seq <- seq(min(data$Mean), max(data$Mean), length.out = 1000)
+predicted_cv <- predict(model_glm, newdata = data.frame(Mean = mean_seq), type = "response")
+
+ggplot(data, aes(x = Mean, y = CV)) +
+  geom_point(alpha = 0.3, color = "red") +
+  geom_line(
+    data = data.frame(Mean = mean_seq, CV = predicted_cv),
+    aes(x = Mean, y = CV),
+    color = "blue",
+    size = 1
+  ) +
+  labs(
+    title = "Scatter Plot of CV versus Mean with Gamma GLM Fit",
+    x = "Mean",
+    y = "Coefficient of Variation (CV)"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    panel.grid.major = element_line(color = "gray80"),
+    panel.grid.minor = element_line(color = "gray90")
+  )

### 2025-01-02 Code/R/Programs/Goodness-of-fit tests.R

@@ -47,10 +47,10 @@ library(invgamma)
 
 #save( cd_values_mnad, x, file = "./Data/MnAD_results_data_Rotterdam_1024.Rdata")
 load("../Programs/Data/MnAD_results_data_Rotterdam_1024.Rdata")
-#cv_values_vector <- as.vector(cv_values)
+cv_values_vector <- as.vector(cv_values)
 
 
-cv_values_vector <- as.vector(cd_values_mnad)
+#cv_values_vector <- as.vector(cd_values_mnad)
 
 
 

### 2025-01-02 Code/R/Programs/RegressionModel-no-good.R

@@ -1,0 +1,83 @@
+# Load necessary libraries
+# Install 'minpack.lm' package if you haven't already
+# install.packages("minpack.lm")
+library(minpack.lm)
+
+# Cargar bibliotecas necesarias
+#rm(list = ls())
+library(ggplot2)
+#library(nls2)
+library(ggsci)
+library(univariateML)
+library(compiler)
+library(MASS)
+library(fitdistrplus)
+library(invgamma)
+library(gridExtra)
+
+library(ggplot2)
+library(ggsci)
+
+
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+# Set parameters
+set.seed(1234567890, kind = "Mersenne-Twister")
+sample.size <- 49
+R <- 10000
+mu <- 1
+L <- 5
+alpha1 <- -1.5
+
+# Initialize vectors to store means and CVs
+means <- numeric(R)
+cvs <- numeric(R)
+
+# Generate samples and compute means and CVs
+for (r in 1:R) {
+  z <- gi0_sample(mu, alpha1, L, sample.size)
+  means[r] <- mean(z)
+  cvs[r] <- sd(z) / mean(z)
+}
+
+# Create data frame
+data <- data.frame(Mean = means, CV = cvs)
+
+# Regression Model Fitting
+# Calculate y
+data$y <- data$CV / sqrt(sample.size)
+
+# Exclude data points where y >= 1 to avoid log of non-positive numbers
+data_valid <- subset(data, y < 1)
+
+# Calculate the response variable
+data_valid$Response <- -log(1 - data_valid$y)
+
+# Fit the linear model
+model_lm <- lm(Response ~ Mean, data = data_valid)
+
+# Display the summary of the model
+summary(model_lm)
+
+# Extract coefficients
+beta0 <- coef(model_lm)[1]
+beta1 <- coef(model_lm)[2]
+
+# Compute fitted Response
+data_valid$Fitted_Response <- predict(model_lm)
+
+# Compute fitted y
+data_valid$Fitted_y <- 1 - exp(-data_valid$Fitted_Response)
+
+# Compute fitted CV
+data_valid$Fitted_CV <- data_valid$Fitted_y * sqrt(sample.size)
+
+# Plot the original data and fitted curve
[…]

### 2025-01-02 Code/R/Programs/animated_Scatter_plot.R

@@ -1,0 +1,61 @@
+# Limpiar el entorno
+rm(list = ls())
+
+# Cargar las librerías necesarias
+library(ggplot2)
+library(ggsci)
+library(gganimate)
+library(invgamma)
+
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+# Fijar la semilla para reproducibilidad
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Definir parámetros
+sample.size <- 49
+R <- 3000
+mu <- 1
+L <- 5
+alphas <- seq(-1.5, -10, by = -0.5)
+
+# Inicializar data frame para almacenar los resultados
+results <- data.frame()
+
+# Generar las muestras y calcular la media y el CV para cada alpha
+for (alpha in alphas) {
+  means <- numeric(R)
+  cvs <- numeric(R)
+  
+  for (r in 1:R) {
+    z <- gi0_sample(mu, alpha, L, sample.size)
+    means[r] <- mean(z)
+    cvs[r] <- sd(z) / mean(z)
+  }
+  
+  # Agregar los resultados al data frame
+  temp_data <- data.frame(Mean = means, CV = cvs, Alpha = alpha)
+  results <- rbind(results, temp_data)
+}
+
+# Crear el plot animado
+p <- ggplot(results, aes(x = Mean, y = CV)) +
+  geom_point(alpha = 0.5, color = "red") +
+  labs(title = "Scatter plot of CV versus Mean for gI0 distribution",
+       x = "Mean",
+       y = "Coefficient of Variation (CV)",
+       subtitle = "Alpha: {closest_state}") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    panel.grid.major = element_line(color = "gray80"),
+    panel.grid.minor = element_line(color = "gray90")
+  ) +
+  transition_states(Alpha, transition_length = 2, state_length = 1)
+
+# Guardar la animación
+#animate(p, nframes = 100, width = 800, height = 600)
+#anim_save("gi0_animation.gif")

### 2025-01-02 Code/R/Programs/color_map_matriz_binaria.R

@@ -1,0 +1,76 @@
+#rm(list = ls())
+#load("./Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
+#save(difference_values, x, file = "./Data/results_Frankfurt_1024_9W_AO_100b_5L.Rdata")
+#load("./Data/results_Frankfurt_1024_9W_AO_100b_5L.Rdata")
+#load("./Data/results_Chicago_1024_9_AO_100b_6L.Rdata")
+#save(difference_values, x, file = "./Data/results_mexico_600_7W_AO_50b_6L.Rdata")save(difference_values, x, file = "./Data/results_mexico_600_9W_AO_100b_6L.Rdata")
+#load("./Data/results_mexico_600_9W_AO_100b_6L.Rdata")
+#load("./Data/results_chicago_urban_1024_9W_AO_100b_6L.Rdata")
+#load("./Data/results_Chicago_400_9W_AO_100b_5L.Rdata")
+#load("./Data/results_Lake_512_9W_AO_100b_36L.Rdata")
+#load("./Data/results_Chicago_1024_9_AO_200b_36L.Rdata")
+#save(difference_values, x, file = "./Data/results_Chicago_400_9W_AO_100b_5L.Rdata")
+#save(difference_values, x, file = "./Data/results_Lake_512_9W_AO_100b_36L.Rdata")
+#load("./Data/results_ottawa_city_512_7_AO_300b.Rdata")
+#load("./Data/results_data_simulated_z_up_le_entropy_250_7.Rdata")
+#load("../Programs/Data/results_Panama_700_AO_7W_L5_200b.Rdata")
+load("./Data/results_SanFranciscoN_400_renyi_b200_07_L1_w7.Rdata")
+#load("./Data/results_Phantom_4_renyi_B100_w7_09_L5.Rdata")
+
+calculate_p_values_and_epsilon <- function(data_matrix) {
+  rows <- nrow(data_matrix)
+  cols <- ncol(data_matrix)
+  
+  mu <- mean(data_matrix, na.rm = TRUE)  # Calcular la media
+  sigma <- sd(data_matrix, na.rm = TRUE)  # Calcular la desviación estándar
+  
+  p_values_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  epsilon_matrix <- matrix(NA, nrow = rows, ncol = cols)
+  
+  for (i in 1:rows) {
+    for (j in 1:cols) {
+      test_difference <- data_matrix[i, j]
[…]

### 2025-01-02 Code/R/Programs/cv_stats_small_image.R

@@ -1,0 +1,59 @@
+#448
+
+# Código para leer una imagen pequeña y aplicar el test estadístico
+rm(list = ls())
+# Leer una de las imágenes pequeñas
+# Supongamos que las imágenes pequeñas están guardadas como 'small_image_1', 'small_image_2', 'small_image_3'
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Función para calcular la estadística basada en el coeficiente de variación (CV)
+calc_cv_stat <- function(window_data) {
+  mean_values <- mean(window_data)
+  sd_values <- sd(window_data)
+  return(sd_values / mean_values)
+}
+ # x <- myread.ENVI(file='../../../Data/SAR/Agua_envi/Intensity_HH.img', 
+ #                  headerfile='../../../Data/SAR/Agua_envi/Intensity_HH.hdr')
+  # x <- myread.ENVI(file='../../../Data/SAR/forest_envi_100/Intensity_HH.img', 
+  #                 headerfile='../../../Data/SAR/forest_envi_100/Intensity_HH.hdr')
+x <- myread.ENVI(file='../../../Data/SAR/urban_envi/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/urban_envi/Intensity_HH.hdr')
+
+
+window_size <- 11
+num_samples <- 100
+
+# Preparar para almacenar resultados
+cv_stats <- numeric(num_samples)
+
+# Tomar muestras con reposición
+for (k in 1:num_samples) {
+  # Seleccionar aleatoriamente una posición en la imagen pequeña
+  i <- sample(1:(nrow(x) - window_size + 1), 1)
+  j <- sample(1:(ncol(x) - window_size + 1), 1)
+  
[…]

### 2025-01-02 Code/R/Programs/difference_values_shannon.R

@@ -1,0 +1,60 @@
+#Codigo que usa la entropia de shannon en el estimador y test
+# Start the timer
+start_time <- Sys.time()
+
+#Estimators
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R") #estimador no parametrico
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")# estimador no parametrico mejorado, que vamos a usar
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+#Load and read data from SAR images
+
+# x <- myread.ENVI(file='../../../Data/SAR/panama512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/panama512/Intensity_VV.hdr')
+
+load("../Programs/Data/Phantom_4_z.Rdata") #imagen simulada
+
+# Assign the dimensions of the loaded matrix to the variables rows and cols
+# change for x if the data comes SAR images
+
+rows <- nrow(Z)
+cols <- ncol(Z)
+
+# rows <- nrow(x)
+# cols <- ncol(x)
+
+
+
+L <- 5 # Number of looks
+B <- 100 # Replications bootstrap
+window_size <- 7 # sliding window size
+
+
+difference_values_shannon <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- Z[i:(i + window_size - 1), j:(j + window_size - 1)]#change for x if the data comes SAR images
+    difference_values_shannon[i, j] <-renyi_entropy_estimator_v1(window_data, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
+                                                                                   (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(window_data))-log(L))
+ 
+  }
+}
+
+
+# Save the results
+
+#save(difference_values_shannon, Z, file = "./Data/results_Phantom_4_AO_B100_w7_L5.Rdata")
+
+# Stop the timer
+end_time <- Sys.time()
+
+
+# Calculate the elapsed time
+execution_time <- end_time - start_time
+execution_time
+

### 2025-01-02 Code/R/Programs/enl_roi_2.R

@@ -1,0 +1,51 @@
+rm(list = ls())
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Cargar la imagen SAR
+x <- myread.ENVI(file='../../../Data/SAR/Houston_1024/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/Houston_1024/Intensity_HH.hdr')
+
+# Definir el tamaño de la ventana
+window_size <- 7
+
+# Obtener las dimensiones de la imagen
+nRows <- nrow(x)
+nCols <- ncol(x)
+
+# Definir las coordenadas del centro de la imagen
+centerRow <- floor(nRows / 2)
+centerCol <- floor(nCols / 2)
+
+# Calcular las coordenadas del ROI (ventana central)
+roiStartRow <- centerRow - floor(window_size / 2) + 1
+roiEndRow <- roiStartRow + window_size - 1
+roiStartCol <- centerCol - floor(window_size / 2) + 1
+roiEndCol <- roiStartCol + window_size - 1
+
+# Extraer el ROI
+roi <- x[roiStartRow:roiEndRow, roiStartCol:roiEndCol]
+
+# Calcular la media y la varianza en la ventana
+mean_value <- mean(roi)
+variance_value <- var(as.vector(roi))
+
+# Calcular el ENL en la ventana
+enl_value <- (mean_value^2) / variance_value
+
+# Verificar si enl_value es un solo valor y corregir si es necesario
+# if (length(enl_value) != 1) {
+#   stop("Error in ENL calculation: ENL value is not a single number.")
+# }
+
+# Imprimir el valor de ENL
+print(paste("ENL for the selected ROI: ", enl_value))
+
+# Guardar los valores de ENL y la imagen original
+save(enl_value, x, file = "./Data/ENL_results_Houston_1024_Central_ROI.Rdata")
+
+# Cargar los valores de ENL y la imagen original desde el archivo guardado
+load("./Data/ENL_results_Houston_1024_Central_ROI.Rdata")
+
+# Imprimir el valor de ENL cargado
+print(enl_value)

### 2025-01-02 Code/R/Programs/enl_value_ROI.R

@@ -1,0 +1,36 @@
+
+rm(list = ls())
+# Cargar la imagen SAR
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Cargar la imagen SAR
+x <- myread.ENVI(file='../../../Data/SAR/Houston_1024/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/Houston_1024/Intensity_HH.hdr')
+
+# Definir las coordenadas de la región de interés (ROI)
+# Ejemplo: una región homogénea en el centro de la imagen
+roi_start_row <- floor(nrow(x) / 2) - 3  # Centrado, con ventana de 7x7
+roi_start_col <- floor(ncol(x) / 2) - 3  # Centrado, con ventana de 7x7
+
+# Seleccionar la ventana local
+window_data <- x[roi_start_row:(roi_start_row + 6), roi_start_col:(roi_start_col + 6)]
+
+# Calcular la media muestral y la varianza muestral en la ventana
+mean_value <- mean(window_data)
+variance_value <- var(window_data)
+
+# Calcular el ENL en la ventana
+enl_value <- (mean_value^2) / variance_value
+
+# Imprimir el valor de ENL
+print(paste("ENL for the selected ROI: ", enl_value))
+
+# Guardar los valores de ENL y la imagen original
+save(enl_value, x, file = "./Data/ENL_results_Houston_1024_ROI.Rdata")
+
+# Cargar los valores de ENL y la imagen original desde el archivo guardado
+load("./Data/ENL_results_Houston_1024_ROI.Rdata")
+
+# Imprimir el valor de ENL cargado
+print(enl_value)

### 2025-01-02 Code/R/Programs/entropy-Rotterdam_1024.R

@@ -1,0 +1,54 @@
+#443
+# Inicia el temporizador
+start_time <- Sys.time()
+
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/MainFunctions/al_omari_2_estimator.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+
+# x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Michigan_1024/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Michigan_1024/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Houston_100/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/Houston_100/Intensity_HH.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/Rotterdam_1024/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr')
+
+
+L <- 1
+#B <- 100
+window_size <- 7
+rows <- nrow(x)
+cols <- ncol(x)
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterar sobre ventanas deslizantes
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
[…]

### 2025-01-02 Code/R/Programs/entropy-lake_envi.R

@@ -1,0 +1,53 @@
+#409 
+# Inicia el temporizador
+start_time <- Sys.time()
+
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+
+# x <- myread.ENVI(file='../../../Data/SAR/Ottawa_512/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Ottawa_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Michigan_1024/Intensity_VV.img',
+#                  headerfile='../../../Data/SAR/Michigan_1024/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Houston_100/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/Houston_100/Intensity_HH.hdr')
+
+x <- myread.ENVI(file='../../../Data/SAR/envi_1/Intensity_VV.img', 
+                 headerfile='../../../Data/SAR/envi_1/Intensity_VV.hdr')
+
+
+L <- 36
+B <- 100
+window_size <- 7
+rows <- nrow(x)
+cols <- ncol(x)
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterar sobre ventanas deslizantes
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Seleccionar ventana local
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    difference_values[i, j] <- bootstrap_al_omari_1_estimator(window_data,B)- (log(mean(window_data)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+  }
+}
+
+# Guarda los resultados
[…]

### 2025-01-02 Code/R/Programs/entropy_bootstrap_small_image.R

@@ -1,0 +1,70 @@
+#445 boostrap
+
+rm(list = ls())
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+# small_image <- myread.ENVI(file='path/to/small_image_1.img', 
+#                            headerfile='path/to/small_image_1.hdr')
+# x <- myread.ENVI(file='../../../Data/SAR/Agua_envi/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/Agua_envi/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/forest_envi_100/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/forest_envi_100/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/crop2_envi/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/crop2_envi/Intensity_HH.hdr')
+x <- myread.ENVI(file='../../../Data/SAR/urban_envi/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/urban_envi/Intensity_HH.hdr')
+
+
+
+# Función para calcular la estadística basada en entropía
+calc_entropy_stat <- function(window_data, L, B) {
+  return(bootstrap_al_omari_1_estimator(window_data, B) - 
+           (log(mean(window_data)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L))))
+}
+
+# # Leer la imagen pequeña
+# small_image <- myread.ENVI(file='path/to/small_image.img', 
+#                            headerfile='path/to/small_image.hdr')
+set.seed(1234567890, kind = "Mersenne-Twister")
+L <- 36
+B <- 200
+window_size <- 11
+num_samples <- 100
+
[…]

### 2025-01-02 Code/R/Programs/first-basic-model-60.R

@@ -1,0 +1,63 @@
+# Cargar bibliotecas necesarias
+rm(list = ls())
+library(ggplot2)
+#library(nls2)
+library(ggsci)
+library(univariateML)
+library(compiler)
+library(MASS)
+library(fitdistrplus)
+library(invgamma)
+library(gridExtra)
+
+library(ggplot2)
+library(ggsci)
+
+
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+sample.size <- 121
+R <- 10000
+mu <- 1
+L <- 5
+alpha1 <- -1.5
+means <- numeric(R)
+cvs <- numeric(R)
+
+for (r in 1:R) {
+  z <- gi0_sample(mu, alpha1, L, sample.size)
+  means[r] <- mean(z)
+  cvs[r] <- sd(z) / mean(z)
+}
+
+
+data <- data.frame(Mean = means, CV = cvs)
+
+# 
+start_values <- list(beta0 = 0.5, beta1 = 0.5)
+model <- nls(CV ~ sqrt(sample.size) * (1 - exp(-(beta0 + beta1 * Mean))), 
+             data = data, start = start_values)
+
+# 
+summary(model)
+
+# 
+ggplot(data, aes(x = Mean, y = CV)) +
+  geom_point(alpha = 0.5, color = "red") +
+  stat_function(fun = function(x) sqrt(sample.size) * (1 - exp(-(coef(model)[1] + coef(model)[2] * x))),
+                color = "blue", size = 1) +
+  labs(title = "Scatter plot of CV versus Mean for gI0 distribution",
+       x = "Mean",
+       y = "Coefficient of Variation (CV)") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    panel.grid.major = element_line(color = "gray80"),
+    panel.grid.minor = element_line(color = "gray90")
+  )

### 2025-01-02 Code/R/Programs/functions_sample_bias_mse_1.R

@@ -1,0 +1,555 @@
+
+# Description:
+# This R script includes functions for generating gamma-sar samples, calculating bias and mean squared error (MSE)
+# of estimators, and generating plots to visualize the results. The code is designed for statistical analysis
+# of several estimators under different sample sizes and replication scenarios.
+
+# Functions:
+# - generate_samples: Generates replicated gamma-sar samples with specified parameters.
+# - calculate_bias_mse: Computes bias and MSE for estimators across various sample sizes and replications.
+# - generate_plot: Generates bias and MSE plots for different mu values and estimators, organized in a grid layout.
+
+# Usage:
+# - Adjust parameters as needed and call the functions 
+
+# Dependencies:
+# - Ensure that the required packages (e.g., ggplot2) are installed for proper execution.
+
+# Note:
+# This code may produce warnings related to deprecated ggplot2 syntax, which can be safely ignored.
+
+# source("../MainFunctions/gamma_sar_sample.r")
+# source("../MainFunctions/entropy_gamma_sar.r")
+
+
+
+generate_samples_gi0 <- function(sample_size, replication, mu, alpha, L) {
+  samples <- vector("list", replication)
+  for (r in 1:replication) {
+    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)
+  }
+  return(samples)
+}
+
+calculate_entropy_and_test <- function(sample_sizes, R, B, mu, alpha, L, estimators) {
+  true_entropy <- entropy_gamma_sar(L, mu)
+  output <- data.frame(
+    SampleSize = integer(0),
+    Estimator = character(0),
+    MeanEntropy = numeric(0),
+    ZStatistic = numeric(0),
+    PValue = numeric(0)
+  )
+  
+  for (ssize in sample_sizes) {
+    samples <- generate_samples_gi0(ssize, R, mu, alpha, L)
+    
+    for (estimator_name in names(estimators)) {
+      estimator <- estimators[[estimator_name]]
+      v.entropy <- numeric(R)
+      
+      for (r in 1:R) {
+        sample <- samples[[r]]
+        
+        if (grepl(" ", estimator_name)) {
+          v.entropy[r] <- estimator(sample, B = B)
+        } else {
[…]

### 2025-01-02 Code/R/Programs/mnad_small_image.R

@@ -1,0 +1,64 @@
+rm(list = ls())
+#449
+# if(!require("rstudioapi")) install("rstudioapi")
+# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+source("../../../Code/R/MainFunctions/correa_estimator.R")
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/mexico_512/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/mexico_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Lake_512/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/Lake_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/Rotterdam_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/urban_envi/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/urban_envi/Intensity_HH.hdr')
+
+small_image <- myread.ENVI(file='../../../Data/SAR/forest_envi_100/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/forest_envi_100/Intensity_HH.hdr')
+
+# Función para calcular el estadístico MnAD basado en la mediana
+calc_mnad_stat <- function(window_data) {
+  mdn <- median(window_data)
+  MnAD <- mean(abs(window_data - mdn))
+  return(MnAD / mdn)
+}
+
+# Leer la imagen pequeña
+# small_image <- myread.ENVI(file='path/to/small_image.img', 
+#                            headerfile='path/to/small_image.hdr')
+
+window_size <- 11
+num_samples <- 100
+
+# Preparar para almacenar resultados
+mnad_stats <- numeric(num_samples)
+
[…]

### 2025-01-02 Code/R/Programs/nlsLM_interpolated.R

@@ -1,0 +1,132 @@
+#525
+# Clear the environment
+rm(list = ls())
+# Start the timer
+start_time <- Sys.time()
+# Load necessary libraries
+library(ggplot2)
+library(reshape2)
+library(gridExtra)
+library(ggsci)
+library(compiler)
+library(minpack.lm)  # For nlsLM function
+library(zoo)         # For NA interpolation
+
+# Source your custom functions
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Set seed for reproducibility
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Load the SAR image data (assuming Z is your image matrix)
+load("../Programs/Data/Phantom_4_z.Rdata")  # SAR image of 512x512 pixels
+x <- Z  # Use x for consistency
+rows <- nrow(x)
+cols <- ncol(x)
+
+# Parameters
+L <- 5                 # Number of looks
+window_size <- 11     # Increased sliding window size for more variation
+B <- 100              # Increased number of bootstrap samples
+sample.size <- window_size^2  # Number of pixels in each window
+
+# Initialize matrix to store p-values of the nlsLM model
+p_values_nlsLM <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    window_vector <- as.vector(window_data)
+    
+    # Check if there is minimal variation in the window
+    if (sd(window_vector) > 0.001) {  # Minimal standard deviation threshold
+      # Initialize vectors to store bootstrapped means and CVs
+      boot_means <- numeric(B)
+      boot_cvs <- numeric(B)
+      
+      # Bootstrap resampling within the window
+      for (b in 1:B) {
+        resampled_data <- sample(window_vector, replace = TRUE)
+        boot_means[b] <- mean(resampled_data)
[…]

### 2025-01-02 Code/R/Programs/nlsLM_interpolated_w7_b200_lake_300.R

@@ -1,0 +1,142 @@
+#526 REVISAR
+# Clear the environment
+rm(list = ls())
+# Start the timer
+start_time <- Sys.time()
+# Load necessary libraries
+library(ggplot2)
+library(reshape2)
+library(gridExtra)
+library(ggsci)
+library(compiler)
+library(minpack.lm)  # For nlsLM function
+library(zoo)         # For NA interpolation
+
+# Source your custom functions
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Set seed for reproducibility
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Load the SAR image data (assuming Z is your image matrix)
+#load("../Programs/Data/Phantom_4_z.Rdata")  # SAR image of 512x512 pixels
+#envi_SF_400
+
+# x <- myread.ENVI(file='../../../Data/SAR/envi_SF_400/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/envi_SF_400/Intensity_VV.hdr')
+
+ x <- myread.ENVI(file='../../../Data/SAR/lake_300/Intensity_VV.img', 
+                  headerfile='../../../Data/SAR/lake_300/Intensity_VV.hdr')
+ 
+
+#x <- Z  # Use x for consistency
+rows <- nrow(x)
+cols <- ncol(x)
+
+# Parameters
+L <- 36                 # Number of looks
+window_size <- 11      # Increased sliding window size for more variation
+B <- 200               # Increased number of bootstrap samples
+sample.size <- window_size^2  # Number of pixels in each window
+
+# Initialize matrix to store p-values of the nlsLM model
+p_values_nlsLM <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    window_vector <- as.vector(window_data)
+    
+    # Check if there is minimal variation in the window
[…]

### 2025-01-02 Code/R/Programs/p-values-entropy-based-test.R

@@ -9,12 +9,12 @@ rm(list = ls())
 #load("./Data/results_Panama_512_AO_7x7_L5_200b.Rdata")
 #load("./Data/results_Lake_512_9W_AO_100b_36L.Rdata")#OK
 #save(difference_values, Z, file = "./Data/results_Phantom_4_z1_200b.Rdata")
-#load("./Data/results_Phantom_4_z1_200b.Rdata")#OK
+load("./Data/results_Phantom_4_z1_200b.Rdata")#OK
 
 #save(difference_values, x, file = "./Data/results_Michigan_1024_7_AO_L1.Rdata")
 #load("./Data/results_lake_envi_1_9.Rdata")#OK
 #load("./Data/results_Rotterdam_AO_L1_7.Rdata")#OK
-#load("./Data/results_Rotterdam_AO_L1_7_2.Rdata")#OK
+load("./Data/results_Rotterdam_AO_L1_7_2.Rdata")#OK
 
 #save(difference_values, x, file = "./Data/results_Rotterdam_AO_L1_7_withou_B.Rdata")
 #load("./Data/results_Rotterdam_AO_L1_7_withou_B.Rdata")#OK
@@ -26,7 +26,7 @@ rm(list = ls())
 #load("./Data/results_agua_envi_11.Rdata")#OK
 #results_Baja_California_1024_7_AO.Rdata
 #save(difference_values, x, file = "./Data/results_mato_grosso_2048_7_AO.Rdata")
-load("./Data/results_mato_grosso_1258_7_AO.Rdata")#OK
+#load("./Data/results_mato_grosso_1258_7_AO.Rdata")#OK
 calculate_p_values_matrix <- function(data_matrix, mu, sigma) {
   rows <- nrow(data_matrix)
   cols <- ncol(data_matrix)

### 2025-01-02 Code/R/Programs/p-values-rotterdam-renyi.R

@@ -1,0 +1,89 @@
+rm(list = ls())
+#load("../Programs/Data/Phantom_4_z.Rdata")
+#save( cd_values_mnad, x, file = "./Data/MnAD_results_data_Rotterdam_1024.Rdata")
+#load("../Programs/Data/MnAD_results_data_Rotterdam_1024.Rdata")
+#load("../Programs/Data/Phantom_4_regions.Rdata")
+#load("./Data/results_Mexico_512_7_AO_300b.Rdata")#
+#load("./Data/results_Phantom_4_regions_AO_7W_L5_100b.Rdata")
+#load("./Data/results_Chicago_1024_9_AO_200b_36L.Rdata")#OK
+#load("./Data/results_Mexico_512_7_AO_300b.Rdata")#OK
+#load("./Data/results_panama_512_AO_9W_L5_100b.Rdata")
+#save(difference_values, x, file = "./Data/results_Panama_512_AO_7x7_L5_200b.Rdata")
+#load("./Data/results_Panama_512_AO_7x7_L5_200b.Rdata")
+#load("./Data/results_Lake_512_9W_AO_100b_36L.Rdata")#OK
+#load("./Data/results_Phantom_4_z1_200b.Rdata")#OK
+#save(difference_values, Z, file = "./Data/results_Phantom_4_renyi_10.Rdata")
+#save(difference_values, Z, file = "./Data/results_Phantom_4_renyi_B100.Rdata")
+#load("./Data/results_Phantom_4_renyi_B100.Rdata")
+#save(difference_values, x, file = "./Data/results_rotterdam_renyi_w7_10_07.Rdata")
+#load("./Data/results_rotterdam_renyi_w7_10_07.Rdata")
+#save(p_values_beta1, Z, file = "./Data/p_values_beta1.Rdata")
+#save(p_values_beta1, Z, file = "./Data/p_values_beta1_v1.Rdata")
+#load("./Data/p_values_beta1_v1.Rdata")
+#save(difference_values, x, file = "./Data/results_rotterdam_renyi_w7_b200_0_65.Rdata")
+#load("./Data/results_rotterdam_renyi_w7_b200_0_65.Rdata")
+#load("./Data/results_Rotterdam_AO_L1_7_2.Rdata")
+#save(difference_values, Z, file = "./Data/results_Phantom_4_renyi_B100_w7_075_L5.Rdata")#Ok but w9
+#load("./Data/results_Phantom_4_renyi_B100_w7_075_L5.Rdata")
[…]

### 2025-01-02 Code/R/Programs/pruebas-plot.R

@@ -1,0 +1,14 @@
+load("./Data/p_values_beta1_v1.Rdata")
+#save(p_values_beta1, Z, file = "./Data/p_values_beta1_v1.Rdata")
+save(p_values_beta1, Z, file = "./Data/p_values_beta1_v1_11.Rdata")
+load("./Data/p_values_beta1_v1_11.Rdata")
+load("./Data/p_values_smooth_gam.Rdata")
+load("./Data/p_values_nlsLM.Rdata")
+source("../imagematrix.R")
+#hist(p_values_matrix)
+#plot(imagematrix(p_values_matrix),significance_level = 0.05)
+#plot(imagematrix(p_values_matrix ))
+plot(imagematrix(p_values_smooth >0.001))
+plot(imagematrix(p_values_beta1 >0.05))
+#plot(imagematrix(equalize(difference_values)))
+#plot(imagematrix(equalize(x)))

### 2025-01-02 Code/R/Programs/renyi_test_rotterdam_new2.R

@@ -1,0 +1,111 @@
+# Start the timer
+#rm(list = ls())
+start_time <- Sys.time()
+
+#Estimators
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/renyi_entropy_estimator_v1.R")
+source("../../../Code/R/MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+#Load and read data from SAR images
+
+# x <- myread.ENVI(file='../../../Data/SAR/panama512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/panama512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+# 
+
+# y <- myread.ENVI(file='../../../Data/SAR/Rotterdam_1024/Intensity_HH.img',
+#                  headerfile='../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr')
+
+ y <- myread.ENVI(file='../../../Data/SAR/envi_Rotterdam_2_1024/Intensity_HH.img',
+                  headerfile='../../../Data/SAR/envi_Rotterdam_2_1024/Intensity_HH.hdr')#new
+
+# x <- myread.ENVI(file='../../../Data/SAR/envi_panama_512/Intensity_VV.img', 
+#                  headerfile='../../../Data/SAR/envi_panama_512/Intensity_VV.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+#                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+
+# x <- myread.ENVI(file='../../../Data/SAR/SanFrancisco_650/Intensity_VV.img', 
[…]

### 2025-01-02 Code/R/Programs/simplified_model.R

@@ -1,0 +1,148 @@
+#493
+# Clear the environment
+rm(list = ls())
+
+# Load necessary libraries
+library(ggplot2)
+library(minpack.lm)  # For robust nonlinear regression
+library(univariateML)
+library(compiler)
+library(MASS)
+library(fitdistrplus)
+library(invgamma)
+library(gridExtra)
+
+# Load any additional libraries you need
+library(ggsci)
+
+# Source your custom functions
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+# Set seed for reproducibility
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Load and read data from SAR images
+# x <- myread.ENVI(
+#   file = '../../../Data/SAR/Rotterdam_1024/Intensity_HH.img',
+#   headerfile = '../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr'
+# )
+
+load("../Programs/Data/Phantom_4_z.Rdata") # imagen SAR de 512x512 pixeles
+
+rows <- nrow(Z)
+cols <- ncol(Z)
+#rows <- nrow(x)
+#cols <- ncol(x)
+
+# Parameters
+L <- 5  # Number of looks
+window_size <- 81  # Sliding window size
+B <- 100  # Number of bootstrap samples within each window
+sample.size <- window_size^2  # Number of pixels in each window
+
+# Initialize matrix to store p-values of beta1
+p_values_beta1 <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- Z[i:(i + window_size - 1), j:(j + window_size - 1)]
+    window_vector <- as.vector(window_data)
+    
+    # Initialize vectors to store bootstrapped means and CVs
+    boot_means <- numeric(B)
+    boot_cvs <- numeric(B)
+    
+    # Check if the window has enough variation
+    if (length(unique(window_vector)) > 1) {
+      # Bootstrap resampling within the window
+      for (b in 1:B) {
+        resampled_data <- sample(window_vector, replace = TRUE)
[…]

### 2025-01-02 Code/R/Programs/smooth-model.R

@@ -1,0 +1,118 @@
+# Clear the environment
+rm(list = ls())
+
+# Load necessary libraries
+library(ggplot2)
+library(mgcv)        # For GAMs
+library(reshape2)
+library(gridExtra)
+library(ggsci)
+library(compiler)
+
+# Source your custom functions
+source("../MainFunctions/gamma_sar_sample.R")
+source("../MainFunctions/entropy_gamma_sar.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+# Set seed for reproducibility
+set.seed(1234567890, kind = "Mersenne-Twister")
+# Load the SAR image data (assuming Z is your image matrix)
+load("../Programs/Data/Phantom_4_z.Rdata") # SAR image of 512x512 pixels
+x <- Z  # Use x for consistency
+rows <- nrow(x)
+cols <- ncol(x)
+
+# Parameters
+L <- 5               # Number of looks
+window_size <- 11    # Sliding window size
+B <- 100             # Number of bootstrap samples within each window
+sample.size <- window_size^2  # Number of pixels in each window
+# Initialize matrix to store p-values of the smooth term
+p_values_smooth <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]
+    window_vector <- as.vector(window_data)
+    
+    # Check if the window has enough variation
+    if (length(unique(window_vector)) > 1) {
+      # Initialize vectors to store bootstrapped means and CVs
+      boot_means <- numeric(B)
+      boot_cvs <- numeric(B)
+      
+      # Bootstrap resampling within the window
+      for (b in 1:B) {
+        resampled_data <- sample(window_vector, replace = TRUE)
+        boot_means[b] <- mean(resampled_data)
+        boot_cvs[b] <- sd(resampled_data) / mean(resampled_data)
+      }
+      
+      # Prepare data for GAM
+      data_boot <- data.frame(Mean = boot_means, CV = boot_cvs)
+      
+      # Fit the GAM
+      tryCatch({
[…]

### 2025-01-02 Code/R/Programs/test_entropy_renyi_1.R

@@ -1,0 +1,77 @@
+# 492
+# Start the timer
+#rm(list = ls())
+start_time <- Sys.time()
+
+#Estimators
+source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
+
+
+source("../../../Code/R/MainFunctions/renyi_entropy_estimator_v1.R")
+source("../../../Code/R/MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
+source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
+
+
+source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
+source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
+
+source("../../../Code/R/Programs/read_ENVI_images.R")
+
+
+
+
+# x <- myread.ENVI(file='../../../Data/SAR/panama512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/panama512/Intensity_VV.hdr')
+
+#  x <- myread.ENVI(file='../../../Data/SAR/mexico_512/Intensity_VV.img', 
+#                   headerfile='../../../Data/SAR/mexico_512/Intensity_VV.hdr')
+# # 
+
+#x <- myread.ENVI(file='../../../Data/SAR/Rotterdam_1024/Intensity_HH.img', 
+#                 headerfile='../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr')
+#
+x <- myread.ENVI(file='../../../Data/SAR/chicago_1024/Intensity_HH.img', 
+                 headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
+#
+
+rows <- nrow(x)
+cols <- ncol(x)
+
+
+
+L <- 36 
+B <- 100 
+lambda<- 0.98
+window_size <- 7 
+
+
+difference_values <- matrix(NA, nrow = rows - window_size + 1, ncol = cols - window_size + 1)
+
+# Iterate over sliding windows
+for (i in 1:(rows - window_size + 1)) {
+  for (j in 1:(cols - window_size + 1)) {
+    # Select local window
+    window_data <- x[i:(i + window_size - 1), j:(j + window_size - 1)]#change for x if the data comes SAR images
[…]

### 2025-01-02 Code/R/Programs/test_statistic_renyi.R

@@ -1,0 +1,84 @@
+#478
+#test_statistic_renyi
+# Limpiar el entorno
+#rm(list = ls())
+
+# Cargar librerías necesarias
+
+
+library(ggplot2)
+library(ggsci)
+library(invgamma)
+
+# Cargar funciones necesarias
+source("../MainFunctions/ebrahimi_estimator.R")
+source("../MainFunctions/gamma_sar_sample.R") 
+source("../MainFunctions/renyi_entropy_estimator_v1.R")
+source("../MainFunctions/renyi_entropy_estimator.R")
+source("../MainFunctions/correa_estimator.R")
+source("../MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
+source("../MainFunctions/bootstrap_renyi_entropy_estimator.R")
+source("../MainFunctions/bootstrap_ebrahimi_estimator.R")
+source("../MainFunctions/entropy_gI0.R")
+source("../MainFunctions/gi0_sample.R")
+
+# Configuración de la semilla
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+# Parámetros de simulación
+R <- 1000
+mu <- 100
+L <- 5
+B <- 100
+lambda <- 0.85
+sample.size <-49
+
+# Para medir el tiempo de ejecución de todo el proceso
+total_time <- system.time({
+  # Para guardar los resultados
+  TestStatistics <- numeric(R)
+  
+  for (r in 1:R) {
+    # Generar muestra gamma SAR
+    z <- gamma_sar_sample(L, mu, sample.size)
+    
+    # Calcular el estadístico usando el bootstrap del estimador de Rényi
+    TestStat <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
+                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
+    
+    
+    TestStatistics[r] <- TestStat
+  }
+  
+  # Calcular la entropía media
+  mean_entropy <- mean(TestStatistics, na.rm = TRUE)
+  cat("Mean Entropy:", mean_entropy, "\n")
+})
+
+# Imprimir el tiempo total de ejecución
+print(total_time)
+
+# Convertir resultados en un data frame para la visualización
+TestStatistics_df <- data.frame(
+  Sample_Size = rep(sample.size, R),
+  Test_Statistics = TestStatistics
[…]

### 2025-02-02 Text/Articles/Mean–CV-Dependence-2025/R0-IMean–CV-Dependence.qmd
Add initial version of the paper

---
title: Heterogeneity Detection in SAR Images Using Sample Mean–CV Dependence
format:
  ieee-pdf:
    pdf-engine: pdflatex # change by xelatex
    keep-tex: true  
    conference: true # uncomment this line to use journal
    journaltype: conference # uncomment this line to use journal
  ieee-html: default

author:
  - id: dfolio
    name: Janeth Alpala, Abraão D.\ C.\ Nascimento 
    affiliations:
      - name: Universidade Federal de Pernambuco
        department: Departamento de Estatística
        city: Recife 
        country: PE, Brazil
        postal-code: 18800
      - name: Unknown affiliation
    #orcid: 0000-0001-9430-6091
    email: janeth.alpala@ufpe.br, abraao@de.ufpe.br
    #url: https://dfolio.fr/
    #membership: "Member, IEEE"
    attributes:
      corresponding: true
    #photo: david-folio.png
    #bio: |
    #  Use `IEEEbiography`  with figure as  option and
    #  the author name as the argument followed by the biography text.
  - name: Alejandro C.\ Frery
    affiliations:
      - name: Victoria University of Wellington
        department: School of Mathematics and Statistics
        city: Wellington 
        country: New Zealand
        postal-code: 18800
      - name: Unknown affiliation
    #orcid: 0000-0001-9430-6091
    email: alejandro.frery@vuw.ac.nz
    # bio: |
    #   Use `IEEEbiographynophoto` and the author name
    #   as the argument followed by the biography text.
    # note: "Template created June 23, 2023; revised `r format(Sys.Date(),format='%B %d, %Y')`."
abstract: |
  This study investigates the relationship between the sample mean and the coefficient of variation (CV) to identify heterogeneity in Synthetic Aperture Radar (SAR) images. In homogeneous regions, these statistics are independent, indicating that the underlying data follow a Gamma distribution. However, in heterogeneous regions, this independence breaks down, resulting in a characteristic dependence that can be modeled. By analyzing the dependence between the sample mean and CV within sliding windows across SAR images, we fit a nonlinear exponential model to characterize this relationship. The significance of a key parameter in the model, $\beta_1$, is evaluated through p-values, allowing us to distinguish homogeneous from heterogeneous regions. This approach provides a robust statistical framework for detecting texture and heterogeneity in SAR images, offering a balance between simplicity and accuracy.
keywords: [Gamma distribution, coefficient of variation, mean, Model Fitting]
#funding: 
funding: 
  statement: "The `quarto-ieee` template is freely available under the MIT license on github: <https://github.com/dfolio/quarto-ieee>."
pageheader:
  left: Journal XXX, Month Year
  right: 'D. Folio:  A Sample Article Using quarto-ieee'

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   #- \usepackage{mathabx}
   #- \usepackage{subfig}
   #- \usepackage{subcaption}
   #- \usepackage{caption}

   #- \captionsetup[table]{skip=0pt}
   #- "\\setcitestyle{square,comma,numbers,sort&compress}" # citation style to numerical, work with \cite{} or [@]

bibliography: ../../Common/references.bib
date: 2023-06-23
pdf: https://github.com/dfolio/quarto-ieee/blob/main/template.pdf
citation: 
  container-title: GitHUB
  page: 1-3
  type: software
  issued: 2023-06-23
  url: https://github.com/dfolio/quarto-ieee
  pdf-url: https://github.com/dfolio/quarto-ieee/template.pdf

---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)#, eval = FALSE

library(fitdistrplus)
library(ggplot2)
library(reshape2)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")
)

# External functions
source("./Code/gamma_sar_sample.R")
source("./Code/ebrahimi_estimator.R")
source("./Code/al_omari_1_estimator.R")
source("./Code/bootstrap_ebrahimi_estimator.R")
source("./Code/bootstrap_al_omari_1_estimator.R")

```

## Introduction

Synthetic aperture radar (SAR) is a vital technology for environmental monitoring and disaster management due to its capability to capture imagery under all-weather conditions, regardless of lighting, making it a reliable source of remote sensing data.. Despite its advantages, the effective use of SAR data depends on a comprehensive understanding of their underlying statistical properties. One of the primary challenges is speckle, an inherent artifact of the coherent imaging process. Speckle is both non-additive and non-Gaussian, necessitating the development of specialized statistical models to characterize and process SAR data accurately.

Among the many statistics used in theoretical and applied contexts, the sample mean ($\bar{X}_n$) and the sample standard deviation ($S_n$) are particularly important. It is well established that the independence of $\bar{X}_n$ and $S_n$ uniquely characterizes the normal distribution. This property has been extensively studied, with foundational work appearing in texts such as Kagan et al. (1973), Johnson and Kotz (1970), and Lukacs and Laha (1964). However, characterization problems involving the coefficient of variation (CV), defined as $V_n = S_n / \bar{X}_n$, have received relatively little attention.

This study builds on the relationship between the sample mean and the CV to explore heterogeneity in SAR images. In homogeneous regions, these statistics are independent, reflecting a Gamma distribution for the underlying data. Conversely, in heterogeneous regions, this independence is lost, producing a characteristic dependence that can be exploited for modeling. By leveraging this relationship within sliding windows across SAR images, we fit a nonlinear exponential model to describe the dependence and evaluate the statistical significance of key parameters. This approach enables the detection of texture and heterogeneity in SAR data, providing a robust framework for applications ranging from environmental monitoring to urban mapping.

# Background {#sec:Background}

## Statistical Modeling

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$ distributions. The first is suitable for fully developed speckle and is a limiting case of the second, which is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Yue2021].
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
\end{align}
where $L \geq 1$ is the number of looks, $\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.
In&nbsp;\eqref{E:gamma1}, $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness.

## Theoretical Connection Between Mean and Coefficient of Variation

A crucial property of the Gamma distribution relates to the independence of the sample mean and the sample coefficient of variation (CV). This relationship is formalized in the following theorem:

### Theorem
Let $n\geq 3$, and let $X_1, \dots, X_n$ be positive independent and identically distributed (i.i.d.) random variables with a common probability density function $f(x)$. Then, the independence of the sample mean, $\bar{X}_n$, and the sample coefficient of variation, $V_n = S_n / \bar{X}_n$, is equivalent to $f(x)$ being a gamma distribution.

This theorem highlights the unique property of the Gamma distribution, where the sample mean and CV are independent. In the context of SAR data, this property becomes a key tool for distinguishing homogeneous regions, modeled by the Gamma distribution, from heterogeneous regions, where the mean and CV exhibit a significant dependence.
\section{Model Fitting}

We consider the following nonlinear regression model to capture the relationship between the sample coefficient of variation and the sample mean:

\begin{equation}
E(V_n \mid \bar{X}_n = \bar{x}_n) = \sqrt{n} \left(1 - \exp\left(- (\beta_0 + \beta_1 \bar{x}_n)\right) - \beta_2 \right),
\label{eq:model}
\end{equation}

Here, $V_n$ represents the sample coefficient of variation, $\bar{x}_n$ is the sample mean, and $n$ is the sample size. The term $\sqrt{n}$ serves as an asymptotic upper bound, ensuring that the model captures the saturation behavior of the CV. The parameters $\beta_0$, $\beta_1$, and $\beta_2$ are estimated through regression, where $\beta_1$ is of particular interest for assessing the strength of the dependence between the sample mean and the CV.
<!-- The parameters $\beta_0$, $\beta_1$, and $\beta_2$ determine the shape and scale of the curve, with $\beta_1$ being particularly important for assessing the strength of dependence. -->

\subsection{Hypothesis Testing for $\beta_1$}

To identify heterogeneity, we test the significance of the dependence between the CV and the sample mean $\bar{x}$ by evaluating the parameter $\beta_1$. Specifically, we test the following hypotheses:

\begin{equation}
H_0: \beta_1 = 0 \quad \text{(no dependence)},
\end{equation}
\begin{equation}
H_1: \beta_1 \neq 0 \quad \text{(dependence exists)}.
\end{equation}

Under $H_0$, the model assumes that $\text{CV}$ and $\bar{x}$ are independent, indicating homogeneity in the region.

\subsubsection{Test Statistic}

The test statistic for $\beta_1$ is given by:

\begin{equation}
t = \frac{\hat{\beta}_1}{\text{SE}(\hat{\beta}_1)},
\end{equation}

where $\hat{\beta}_1$ is the estimated value of $\beta_1$, and $\text{SE}(\hat{\beta}_1)$ is its standard error. This statistic follows a $t$-distribution with $B - p$ degrees of freedom, where $B$ is the number of bootstrap samples or data points used, and $p$ is the number of estimated parameters ($p = 3$ in this case).

\subsubsection{P-value Calculation}

The p-value for the hypothesis test is computed as:

\begin{equation}
p\text{-value} = 2 \times P(T > |t|),
\end{equation}

where $T$ follows a $t$-distribution under the null hypothesis. The p-value determines whether the observed value of $\hat{\beta}_1$ provides sufficient evidence to reject $H_0$.

#Simulations

To evaluate the relationship between the sample mean and the coefficient of variation (CV) across different levels of roughness, we simulated data from the $\mathcal{G}_I^0$ distribution for various values of the parameter $\alpha$ ($\alpha = -1.5, -3, -5, -10, -50, -1000$). For each value of $\alpha$, multiple samples were generated, and scatter plots of CV versus the mean were created. These plots, shown in Figure~\ref{fig:scatter_cv_mean_alpha}, illustrate the transition from dependence to independence between the mean and CV as $\alpha$ decreases (becomes more negative).

At higher values of $\alpha$ (e.g., $\alpha = -1.5$), the scatter plots exhibit a logarithmic pattern, indicative of a strong dependence characteristic of heterogeneous regions. Conversely, as $\alpha$ approaches $-\infty$ (e.g., $\alpha = -1000$), the scatter plots display a random distribution of points, reflecting independence between the mean and CV. This behavior is consistent with the Gamma distribution and represents homogeneity.

To further explore the relationship between the sample mean and the coefficient of variation (CV) across varying levels of roughness, we fitted the nonlinear regression model defined in Equation~\eqref{eq:model} to simulated data from the $\mathcal{G}_I^0$ distribution. For each value of $\alpha$ ($\alpha = -1.5, -3, -10, -1000$), we generated multiple samples and plotted the scatter of CV versus the mean. The data were then fitted using the robust nonlinear least squares function nlsLM from the minpack.lm R package, estimating the parameters $\beta_0$, $\beta_1$, and $\beta_2$.

The fitted model effectively captures the exponential dependence observed for higher values of $\alpha$ (e.g., $\alpha = -1.5$), indicative of strong heterogeneity. As $\alpha$ decreases and approaches $-\infty$, the fitted curve becomes flat, reflecting the independence between the mean and CV characteristic of homogeneity.

The parameter $\beta_1$ plays a critical role in detecting heterogeneity. A hypothesis test is conducted to assess the significance of $\beta_1$, where low p-values (e.g., $p < 0.05$) indicate significant dependence between the mean and CV, consistent with heterogeneous regions. Conversely, high p-values suggest no significant dependence, characteristic of homogeneous regions. The results are illustrated in Figure~\ref{fig:scatter_cv_mean_alpha_fit}, which includes the scatter plots of CV versus mean for different values of $\alpha$, along with the fitted curves.

```{r Plot_empirical_gamma_and_gi01_with_fit, echo=FALSE, message=FALSE, warning=FALSE, out.width="45%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Scatter plot of CV versus Mean for different $\\alpha$ values with fitted nonlinear models.", fig.width=5, fig.height=4.0}

library(minpack.lm)

source("../../../Code/R/MainFunctions/gi0_sample.R")
set.seed(1234567890, kind = "Mersenne-Twister")

sample.size <- 49
R <- 10000
mu <- 1
L <- 5

# Specific alpha values
alphas <- c(-1.5, -3, -10, -1000)

results <- data.frame()
fitted_curves <- data.frame()

for (alpha in alphas) {
  means <- numeric(R)
  cvs <- numeric(R)

  for (r in 1:R) {
    z <- gi0_sample(mu, alpha, L, sample.size)
    means[r] <- mean(z)
    cvs[r] <- sd(z) / mean(z)
  }

  temp_data <- data.frame(Mean = means, CV = cvs, Alpha = factor(paste0("alpha==", alpha), levels = paste0("alpha==", alphas)))
  results <- rbind(results, temp_data)

  # Fit the nonlinear model to the data for this alpha
  tryCatch({
    nls_model <- nlsLM(CV ~ sqrt(sample.size) * (1 - exp(-(beta0 + beta1 * Mean)) - beta2),
                       data = temp_data, 
                       start = list(beta0 = -0.001, beta1 = 0.01, beta2 = -0.1))

    # Generate fitted values for plotting
    fitted_data <- data.frame(
      Mean = sort(temp_data$Mean),
      FittedCV = predict(nls_model, newdata = data.frame(Mean = sort(temp_data$Mean))),
      Alpha = factor(paste0("alpha==", alpha), levels = paste0("alpha==", alphas))
    )
    fitted_curves <- rbind(fitted_curves, fitted_data)
  }, error = function(e) {
    message("Model fitting failed for alpha=", alpha)
  })
}

# Create the scatter plot with the fitted curve
p <- ggplot(results, aes(x = Mean, y = CV)) +
  geom_point(alpha = 0.2, color = "#56B4E9", size = 0.7) +
  geom_line(data = fitted_curves, aes(x = Mean, y = FittedCV), color = "red", size = 0.8) +
  labs(
    x = "Mean",
    y = "CV"
  ) +
  theme_minimal() +
  theme(
    text = element_text(family = "serif"),
    axis.title = element_text(size = 10),
    strip.text = element_text(size = 10),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  ) +
  facet_wrap(~ Alpha, ncol = 2, scales = "free", labeller = label_parsed)

# Display the plot
print(p)

```

```{r Simulated_table, echo=FALSE, message=FALSE}
library(minpack.lm)
source("../../../Code/R/MainFunctions/gi0_sample.R")
set.seed(1234567890, kind = "Mersenne-Twister")
sample.size <- 49
R <- 10000
mu <- 1
L <- 5
alphas <- c(-1.5, -3, -10)

# Initialize an empty dataframe to store results
results_table <- data.frame()

# Loop over alpha values to calculate parameters
for (alpha in alphas) {
  means <- numeric(R)
  cvs <- numeric(R)

  # Generate data for simulations
  for (r in 1:R) {
    z <- gi0_sample(mu, alpha, L, sample.size)
    means[r] <- mean(z)
    cvs[r] <- sd(z) / mean(z)
  }

  # Create temporary data frame
  temp_data <- data.frame(Mean = means, CV = cvs)

  # Fit nonlinear model using nlsLM
  tryCatch({
    nls_model <- nlsLM(CV ~ sqrt(sample.size) * (1 - exp(-(beta0 + beta1 * Mean)) - beta2),
                       data = temp_data, 
                       start = list(beta0 = -0.001, beta1 = 0.01, beta2 = -0.1))

    # Extract fitted parameters
    beta_estimates <- summary(nls_model)$coefficients
    results_table <- rbind(
      results_table,
      data.frame(
        Alpha = alpha,
        Beta0 = paste0(round(beta_estimates[1, 1], 5), " ± ", round(beta_estimates[1, 2], 5)),
        Beta1 = paste0(round(beta_estimates[2, 1], 5), " ± ", round(beta_estimates[2, 2], 5)),
        Beta2 = paste0(round(beta_estimates[3, 1], 5), " ± ", round(beta_estimates[3, 2], 5)),
        PValueBeta1 = format.pval(beta_estimates[2, 4], eps = 1e-3, digits = 4)
      )
    )
  }, error = function(e) {
    message("Model fitting failed for alpha=", alpha)
  })
}

# Save the results to an RData file
save(results_table, file = "./Data/fitted_results.RData")

```

```{r Table_results, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# Load the saved results
load("./Data/fitted_results.RData")

# Format column names for LaTeX
colnames(results_table) <- c("$\\alpha$", 
                             "$\\beta_0 \\pm \\text{SE}$", 
                             "$\\beta_1 \\pm \\text{SE}$", 
                             "$\\beta_2 \\pm \\text{SE}$", 
                             "$p$-value of $\\beta_1$")

# Create the table using knitr::kable
knitr::kable(
  results_table,
  caption = "Fitted parameters and $p$-values for different $\\alpha$ values.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 5,
  label = "fitted_results",
  linesep = ""
) %>%
  kable_styling(latex_options = "scale_down") %>%
  row_spec(0, align = "c")

```

```{=latex}
\begin{figure*}[t]
    \centering
    \begin{subfigure}{0.19\textwidth}
        \includegraphics[width=\linewidth]{./Figures/Phantom1.png}
        \caption{ SAR image}
        \label{fig:1a}
    \end{subfigure}
    \begin{subfigure}{0.25\textwidth}
        \includegraphics[width=\linewidth]{./Figures/Phantom_labels.pdf}
        \caption{ Simulated image}
        \label{fig:1b}
    \end{subfigure}
    \begin{subfigure}{0.30\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_munich_c2.png}
        \caption{$p$-values}
        \label{fig:1c}
    \end{subfigure}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_4z_7w_300b.png}
        \caption{ Binary map $5\%$ }
        \label{fig:1d}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a simulated image  }
    \label{fig:london}
\end{figure*}

```
```{=latex}
\begin{figure*}[t]
    \centering
    \begin{subfigure}{0.19\textwidth}
        \includegraphics[width=\linewidth]{./Figures/munich_512_.png}
        \caption{ SAR image}
        \label{fig:1a}
    \end{subfigure}
    \begin{subfigure}{0.30\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_munich_c4.png}
        \caption{$p$-values}
        \label{fig:1c}
    \end{subfigure}
    \begin{subfigure}{0.20\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_munich.png}
        \caption{ Binary map $5\%$ }
        \label{fig:1d}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image  }
    \label{fig:londondd}
\end{figure*}

```

\subsection{Application to SAR Images}

This methodology is applied to each sliding window in the SAR image. For each window, we calculate the p-value corresponding to $\beta_1$. The results are summarized as follows:
\begin{itemize}
    \item Regions with low p-values (e.g., $p < 0.05$) indicate significant dependence between $\text{CV}$ and $\bar{x}$, suggesting heterogeneity.
    \item Regions with high p-values suggest no significant dependence, indicating homogeneity.
\end{itemize}

By mapping the p-values across the image, we can visualize areas of heterogeneity and homogeneity, providing a comprehensive spatial characterization of texture in the SAR data.

# Conclusions
The conclusion ....

# Acknowledgment {-}

<!-- []{.appendix options="An Appendix"} -->

::: {.content-visible when-format="pdf"}
# References {-}
:::

[^issues-1023]: ["_[longtable not compatible with 2-column LaTeX documents](https://github.com/jgm/pandoc/issues/1023>)_",

[^issues-2275]: See the issue here <https://github.com/quarto-dev/quarto-cli/issues/2275>

[IEEEXplore<sup>®</sup>]: <https://ieeexplore.ieee.org/>

### 2025-02-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Add initial version of the paper

---
title: Rényi Entropy-Based Heterogeneity Detection in SAR Data
format:
  ieee-pdf:
    pdf-engine:  pdflatex # xelatex
    keep-tex: true  
    conference: true # comment this line to use journal
    journaltype: conference # comment this line to use journal
    fig-cap-location: bottom # to crossref figure
   # link-citations: true
    #colorlinks: true
    #linkcolor: blue
  ieee-html: default

author:
  - id: 
    name: Janeth Alpala, Abraão D.\ C.\ Nascimento 
    affiliations:
      - name: Universidade Federal de Pernambuco
        department: Departamento de Estatística
        city: Recife 
        country: PE, Brazil
        postal-code: 18800
      - name: Unknown affiliation
    #orcid: 
    email: janeth.alpala@ufpe.br, abraao@de.ufpe.br
    #url: 
    #membership: "Member, IEEE"
    attributes:
      corresponding: true
    #photo: 
    #bio: |
    #  Use `IEEEbiography`  with figure as  option and
    #  the author name as the argument followed by the biography text.
  - name: Alejandro C.\ Frery
    affiliations:
      - name: Victoria University of Wellington
        department: School of Mathematics and Statistics
        city: Wellington 
        country: New Zealand
        postal-code: 18800
      - name: Unknown affiliation
    #orcid: 
    email: alejandro.frery@vuw.ac.nz
    # bio: |
    #   Use `IEEEbiographynophoto` and the author name
    #   as the argument followed by the biography text.
    # note: "Template created June 23, 2023; revised `r format(Sys.Date(),format='%B %d, %Y')`."
abstract: |
 We propose a test statistic for identifying roughness characteristics in synthetic aperture radar (SAR) intensity data using Rényi entropy. 
 Homogeneous regions, where speckle is fully developed, are modeled by the Gamma distribution, while heterogeneous areas, associated with surface roughness, follow the $\mathcal{G}^0$ distribution. 
 The test relies on a non-parametric estimator of Rényi entropy to distinguish between these two types of regions. 
 By applying it to real SAR images, we generate $p$-value maps to assess the homogeneity hypothesis. 
 Experimental results show that the Rényi-based approach improves heterogeneity detection compared to previous methods using Shannon entropy.

keywords: [Gamma distribution, heterogeneity, SAR, Rényi entropy, hypothesis tests]
#funding: 
funding: 
  statement: "The `quarto-ieee` template is freely available under the MIT license on github: <https://github.com/dfolio/quarto-ieee>."
pageheader:
  left: Journal XXX, Month Year
  right: #'D. Folio:  A Sample Article Using quarto-ieee'

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}
   - \usepackage[utf8]{inputenc}
   - \usepackage{hyperref}
   - \hypersetup{draft}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{xcolor}
   - \usepackage{amsmath}

#bibliography: references.bib
bibliography: ../../Common/references.bib
#

# execute:
#   echo: false
#   eval: true

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

# Configurar CRAN
options(repos = c(CRAN = "https://cran.rstudio.com/"))

# install and load packages only if they are missing
install_and_load <- function(packages) {
  missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(missing_packages)) {
    install.packages(missing_packages, dependencies = TRUE)
  }
  invisible(lapply(packages, library, character.only = TRUE))
}
#
#  packages
required_packages <- c(
 "ggplot2", "reshape2", "knitr", "pandoc", "gridExtra", 
  "gtools", "stats4", "rmutil", "scales", "tidyr", "invgamma", 
  "tidyverse", "RColorBrewer", "ggsci", "carData", "ggpubr",  "patchwork", "dplyr", 
  "kableExtra", "ggthemes", "latex2exp", "e1071", "viridis", "nortest", "bookdown"
)

# Install and load only missing packages
install_and_load(required_packages)

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom"))

# External functions
source("./Code/gamma_sar_sample.R")
source("./Code/gi0_sample.R")
source("./Code/al_omari_1_estimator.R")
source("./Code/bootstrap_al_omari_1_estimator.R")
source("./Code/renyi_entropy_estimator_v1.R")
source("./Code/bootstrap_renyi_entropy_estimator_v1.R")
source("./Code/entropy_renyi_gamma_sar.R")
source("./Code/functions_sample_bias_mse.R")
source("./Code/functions_sample_bias_mse_1.R")
#source("./Code/read_ENVI_images.R")

```

<!-- \newcommand{\reallywidehat}[1]{\widehat{#1}} -->

# Introduction

Synthetic Aperture Radar (SAR) technology has become essential for a wide range of applications, including environmental monitoring and disaster management\ [@Yu2023;  @Mondini2021]. 
By operating independently of sunlight and under various weather conditions, SAR systems provide continuous, high-resolution imagery\ [@Zeng2020]. 
Despite these advantages, SAR data exhibit speckle, a noise-like interference effect that arises due to the coherent nature of the imaging process\ [@Argenti2013;@Choi2019].
In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.

The $\mathcal{G}^0$ distribution has shown to be an effective model for SAR intensity data,  as it captures different levels of roughness.
A special case is the Gamma distribution,which arises when speckle is fully developed, indicating homogeneous regions.
Although these models provide flexible frameworks for describing SAR intensities, selecting the appropriate model can be challenging for two main reasons: the small samples used in practical applications  and the inherent difficulties associated with parameter estimation. 
These challenges complicate model selection and highlight the need to explore alternative statistical approaches.

Entropy measures have gained attention as valuable statistical tools for analyzing SAR data, with applications in edge detection\ [@Nascimento2014], segmentation\ [@Nobre2016], classification\ [@Cassetti2022], and noise reduction\ [@Chan2022].
Traditionally, Shannon entropy\ [@Shannon1948] has been widely used to quantify uncertainty and disorder in data. However, this study explores an alternative information measure: Rényi entropy. 
As a generalization of Shannon entropy, it offers additional insights for identifying heterogeneity, making it a promising tool for enhancing SAR image analysis.

In this work, we propose a statistical test based on a non-parametric estimator of Rényi entropy to identify heterogeneous regions in SAR data.
The test assesses whether the observed Rényi entropy in a given region significantly differs from its expected theoretical value under the assumption of homogeneity.
Compared to our previous approach  using Shannon entropy\ [@Frery2024], the Rényi-based approach improves the detection of heterogeneity in real SAR images.

The rest of this article is organized as follows.
Section \ref{sec:pre} presents an overview of statistical models for SAR intensity data and introduces Rényi entropy.
In Section \ref{sec:met}, we describe the proposed hypothesis test and the formulation of the test statistic. 
Section \ref{sec:app} evaluates the test's performance using real SAR data.
Finally, Section \ref{sec:conclusion} presents the conclusions.

# PRELIMINARIES {#sec:pre}

## Statistical Models

The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $G_I^0$ distribution, which is able to describe roughness\ [@Frery1997]. These distributions are characterized by the following probability density functions (pdfs):

\begin{align}
	f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}
\end{align}
\begin{multline}
\label{E:gi01}
	f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}\mathbbm 1_{\mathbbm R_+}(z),
\end{multline}

where $\mu > 0$ is the mean,
$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of
looks, $\Gamma(\cdot)$ is the gamma function, and
$\mathbbm 1_{A}(z)$ is the indicator function of the set $A$.

As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $G_I^0$ distribution. Specifically, for a given $\mu$ fixed,
$$
f_Z\big(z; \mu, \alpha, L\mid G_I^0\big)
\longrightarrow 
f_Z(z;L, \mu\mid \Gamma_{\text{SAR}}) 
$$
when $\alpha\to-\infty$.

## Rényi Entropy

Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], the Rényi entropy generalizes several entropy measures, including the Shannon entropy. For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$ (where $\lambda > 0$ and $\lambda \neq 1$) is defined as:

\begin{align}
\label{E:entropy2}
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{align}

Using this definition, we obtain the Rényi entropy expressions for the $\Gamma_{\text{SAR}}$ and $G_I^0$ distributions, respectively:

\begin{multline}
\label{eq-HGammaSAR}
H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)
= 
\ln \mu - \ln L + \frac{1}{1-\lambda}
\Bigl[
  -\lambda\,\ln\Gamma(L) \\  + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\Bigr]
\end{multline}
and
\begin{multline}\label{eq-HGI0}
H_\lambda\bigl(G_I^0(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
+ \frac{1}{\,1 - \lambda\,}
\Bigl[
   \lambda\bigl(
      \ln\Gamma(L - \alpha)
      -\ln\Gamma(-\alpha)
      -\ln\Gamma(L)
   \bigr)\\
   +\ln\Gamma\bigl(\lambda(L - 1) + 1\bigr)
   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)\\
   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
\Bigr].
\end{multline}

@fig-plot presents the Rényi entropy of $G_I^0$ as a function of $\mu$ for different $\alpha$ values. As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is consistent with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $G_I^0$ model.

```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(G_I^0)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}

entropy_renyi_gamma_sar <- function(L, mu, lambda) {
  entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
                (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
  return(entropy)
}

entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
  if (lambda <= 0 || lambda == 1) {
    stop("Lambda must be greater than 0 and not equal to 1.")
  }

  gamma <- -mu * (alpha + 1)
  if (any(gamma <= 0)) {
    stop("Gamma must be positive. Check the values of mu and alpha.")
  }

  a <- lambda * (L - 1) + 1
  b <- lambda * (-alpha + 1) - 1
  ab_sum <- lambda * (L - alpha)

  if (any(a <= 0) || any(b <= 0) || any(ab_sum <= 0)) {
    stop("Arguments of the Gamma functions must be positive. Check the values of lambda, L, and alpha.")
  }

  term1 <- log(gamma / L)

  term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))

  term3 <- lgamma(a)
  term4 <- lgamma(b)
  term5 <- lgamma(ab_sum)

  numerator <- term2 + term3 + term4 - term5

  entropy <- term1 + numerator / (1 - lambda)

  return(entropy)
}

L <- 8
alphas <- c(-3, -8, -20, -1000)
alpha_labels <- c(expression(italic(alpha) == -3), 
                  expression(italic(alpha) == -8), 
                  expression(italic(alpha) == -20), 
                  expression(italic(alpha) == -1000))

mu <- seq(0.1, 10, length.out = 500)
lambda <- 0.8  # Fixed lambda

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- entropy_GI0_renyi(alpha, mu, L, lambda)
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"), value.name = "Entropy")

entropies_gamma <- entropy_renyi_gamma_sar(L, mu, lambda)

Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy_Gamma")

ggplot() +

  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = Entropy_Gamma), color = "black", 
            linetype = "solid", linewidth = 1.5) +

  geom_line(data = muEntropy.molten, aes(x = mu, y = Entropy, color = alpha), 
            linetype = "longdash", linewidth = 1) +

  annotate("text", x = max(mu) + 0.2, y = max(Entropy_gamma.molten$Entropy_Gamma), 
           label = TeX("${italic(H)}_{\\lambda}(\\Gamma_{\\tiny{SAR}})$"), 
           vjust = 1.6, hjust = 0.8, color = "black",linewidth = 0.2) +

  theme_minimal() +

  scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
 # scale_color_manual(values = brewer.pal(4, "Dark2"), labels = alpha_labels) +
  # Labels and titles
  labs(color = "Roughness", 
       x = expression(mu), 
       y = "Rényi Entropy", 
       linetype = NULL) +

  theme(text = element_text(family = "serif"),
        legend.position = "bottom") +

  coord_cartesian(xlim = c(0, 10), ylim = c(min(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma), 
                                            max(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma) + 0.5))

```

For $\lambda \to 1$, this expression converges to the Shannon entropy. As we will see later, this property can lead to improved performance for heterogeneity detection compared to Shannon entropy.

## Estimation of Rényi Entropy

Several authors have studied the nonparametric estimation of $H(Z)$, utilizing estimators that rely on spacings, which are the differences between order statistics\ [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999;@AlOmari2019].
In 2024, Al-Labadi et al.\ [@AlLabadi2024] introduced a nonparametric estimator for Rényi entropy using this approach.

Let $\{Z_1, Z_2, \dots, Z_n\}$ be a sample from a distribution $F$, and denote its order statistics by $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$. 
The density estimator based on $m$-spacing, is defined as:
$$
f_n(Z_{(i)}) = \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}},
$$

where $Z_{(i-m)} = Z_{(1)}$ when $i \leq m$ and $Z_{(i+m)} = Z_{(n)}$ if $i \geq n - m$. The coefficient $c_i$ is given by:
$$
c_i = 
\begin{cases}
\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\[6pt]
2, & \text{if } m+1 \leq i \leq n - m, \\[6pt]
\frac{n + m - i}{m}, & \text{if } n - m + 1 \leq i \leq n.
\end{cases}
$$
Following Vasicek [@vasicek1976test] and Ebrahimi et al. [@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, Rényi entropy can be estimated as:
\begin{align}
\label{eq:est_R}
\widehat{H}_\lambda(\bm{Z}) = \frac{1}{1 - \lambda} \ln \left[\frac{1}{n} \sum_{i=1}^{n} \left( \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}} \right)^{\lambda - 1} \right].
\end{align}
This estimator is asymptotically consistent, i.e., it converges in
probability to the true value when $m,n\rightarrow\infty$ and
$m/n\rightarrow0$. 
We choose to use the heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.

# PROPOSED METHODOLOGY {#sec:met}

## Optimal $\lambda$ for small sample size

We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator, specifically for a sample size of $n=49$.
To identify this optimal value, we analyze both the Mean Squared Error (MSE) and Bias of the estimator across different values of $\lambda$. Lower MSE and Bias indicate better performance of the estimator in approximating the true entropy.

Based on the results, we find that the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low Bias. This choice is consistent with other values of $L > 1$. However, for $L = 1$, the optimal $\lambda$ tends to be higher (e.g., $\lambda = 3$) to achieve good results. @fig-plotf illustrates the case for $L = 5$.

```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=8, fig.height=6}

data <- data.frame(
  Lambda = c(0.9,  0.85, 0.99, 1.1, 1.5),
  Bias = c(0.00158,  -0.00250, 0.02077, 0.03751, 0.06512),
  MSE = c(0.01273,  0.01441, 0.01653, 0.01697, 0.01906)
)

data <- data[order(data$Lambda), ]

bias_plot <- ggplot(data, aes(x = Lambda, y = Bias)) +
  geom_line(color = "#00AFBB", linewidth = 1.0) +  
  geom_point(color = "#00AFBB", size = 3) +  
  geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$Bias), 
         #  label = "Bias", color = "#00AFBB", fontface = "italic", hjust = 1.0) +
  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
  labs(x = expression(lambda), y = "Bias") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16))

mse_plot <- ggplot(data, aes(x = Lambda, y = MSE)) +
  geom_line(color = "#E69F00", linewidth = 1.0) +  
  geom_point(color = "#E69F00", size = 3) +
  #geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$MSE), 
           #label = "MSE", color = "#E69F00", fontface = "italic", hjust = 1.0) +
   scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) + 
  labs(x = expression(lambda), y = "MSE") +
  theme_minimal() +
  theme(text = element_text(family = "serif"),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 16))

grid.arrange(bias_plot, mse_plot, nrow = 2)

```

## Bootstrap Correction for Entropy Estimator

Following previous studies by\ [@Frery2024] and\ [@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply an improved version:
$$
\widetilde{H}_{\lambda} = 2\widehat{\theta}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}_b(\bm{Z}^{(b)}).
$$
A Monte Carlo study with $1000$ samples from $\Gamma_{\text{SAR}}$ ($\mu = 1$, $L=5$, $\lambda = 0.9$) confirms that this approach, using $B = 200$ replications, reduces bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.

```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
set.seed(1234567890, kind = "Mersenne-Twister")

file_name <- "./Data/results_renyi_B1.Rdata"

if (file.exists(file_name)) {

  load(file_name)
  message("Loaded existing results from results_renyi_B1.Rdata")
} else {
  # Parameters
  sample_sizes <- c(9, 25, 49, 81, 121)
  R <- 500        
  B <- 200        
  mu <- 1        
  L <- 5          
  alpha_values <- c(0.9)

  estimators <- list(
    "Renyi Estimator" = renyi_entropy_estimator_v1,
    "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1
  )

  results <- calculate_bias_mse_r(sample_sizes, R, B, mu, L, alpha_values, estimators)

  save(results, file = file_name)
  message("Simulations completed and results saved.")
}
```

```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%", fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimator for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=1$ and $L=5$.", fig.width=8, fig.height=7}

load("./Data/results_renyi_B1.Rdata")

alpha_values <- 0.9
estimators_to_plot <- c("Renyi Estimator", "Renyi Estimator Bootstrap")
latex_estimator_names <- c("Renyi Estimator" = expression("$\\widehat{italic(H)}_{\\lambda}$"),# 
                           "Renyi Estimator Bootstrap" = expression("$\\widetilde{italic(H)}_{\\lambda}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

combined_plot_renyi <- generate_plot_renyi(results, alpha_values, selected_estimators_latex, ncol = 1, nrow = 1)

print(combined_plot_renyi)

```

## Hypothesis Test Rationale

Our approach relies on constructing a test statistic that compares a non-parametric estimate of the Rényi entropy to the theoretical value of the Rényi entropy under the null hypothesis (i.e., a fully developed speckle scenario modeled by $\Gamma_{\text{SAR}}$). 
We aim to test the following hypotheses: 
$$
\begin{cases}\mathcal{H}_0: \widehat{H}^*= H_{\lambda}(\Gamma_{\text{SAR}})\\ 
  \mathcal{H}_1:\widehat{H}^*= H_{\lambda}(G_I^0).\end{cases}
$$

If the difference between the estimated and theoretical entropy values is statistically significant, we reject the null hypothesis and conclude that the data do not follow the Gamma model, indicating the presence of heterogeneity.

## The Proposed Test

Assume we have an estimator $\widehat{H_{\lambda}}$ for the Rényi entropy of an arbitrary model. In the case of the $\Gamma_{\text{SAR}}$ model, this estimator is expected to be close to the theoretical expression given in Equation \eqref{eq-HGammaSAR}. 
Considering that $L\geq1$ is known, we define the following test statistic:
\begin{multline}
\label{eq-test}
S(\bm{Z}; L) = \widehat{H} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
\bigl[-\lambda\,\ln\Gamma(L) \\  
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  
- \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\bigr]\bigr\}.
\end{multline}

When the null hypothesis holds, this test statistic is expected to be close to zero.

For illustrative purposes, @fig-density_entropyR provide the empirical density of $S(\bm{Z}; L)$  for the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
For subsequent simulations we use the $\widetilde{H_{\lambda}}$ estimator.

```{r Simulated_densityR, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 10000
mu <- 1
B <- 50

lambda <- 0.9

sample.size <- c(49, 81, 121)
L_values <- c(5, 18)

all_summary_stats <- list()
all_TestStatistics <- list()

# 
for (L in L_values) {

  file_name <- paste0("./Data/resultsR_", L, ".Rdata")

  if (file.exists(file_name)) {
    load(file_name)
    message(paste("Loaded existing data for L =", L))
  } else {

    TestStatistics1 <- list()  
    summary_stats <- data.frame(
      LValue = character(),
      SampleSize = numeric(),
      Mean = numeric(),
      SD = numeric()
      #Variance = numeric(),
      #Skewness = numeric(),
     # Kurtosis = numeric(),
      #adpvalue = numeric()
    )

    # Para cada tamaño de muestra
    for (s in sample.size) {
      TestStat1 <- numeric(R)

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat1[r] <- TestStat <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
      }

      TestStatistics1[[as.character(s)]] <- data.frame(
        "SampleSize" = rep(s, R), 
        "Test_Statistics" = TestStat1
      )

      mean_val <- mean(TestStat1)
      sd_val <- sd(TestStat1)
      #var_val <- var(TestStat1)
     # skewness_val <- skewness(TestStat1)
     # kurtosis_val <- kurtosis(TestStat1)
     # ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value

      summary_stats <- rbind(summary_stats, data.frame(
        LValue = as.character(L),
        SampleSize = s,
        Mean = mean_val,
        SD = sd_val
      #  Variance = var_val,
       # Skewness = skewness_val,
       # Kurtosis = kurtosis_val,
       # adpvalue = ad_p_value
      )) 
    }

    all_TestStatistics[[as.character(L)]] <- TestStatistics1
    all_summary_stats[[as.character(L)]] <- summary_stats

    save(all_TestStatistics, all_summary_stats, file = file_name)
    message(paste("Saved new results for L =", L))
  }
}

```

```{r fig-density_entropyR, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ test under the null hypothesis.", fig.width=9, fig.height=5.0}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

x_limits <- c(-0.5, 0.5)  # Límites del eje X
x_breaks <- seq(-0.4, 0.4, by = 0.2)  # Ticks del eje X
y_limits <- c(0, 7)       # Límites del eje Y

selected_L_values <- c(5, 18)

all_plots <- list()

for (L in selected_L_values) {
  load(paste0("./Data/resultsR_", L, ".Rdata"))

  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
  combined_data$L <- L

  combined_data$CurveOrder <- factor(combined_data$SampleSize, levels = rev(sample.size))

  combined_data$LegendOrder <- factor(combined_data$SampleSize, levels = sample.size)

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
    geom_line(stat = "density", linewidth = 1.5) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
    scale_y_continuous(limits = y_limits) +  
    labs(
        x = expression("Test Statistic" ~ S[widetilde(italic(H))[lambda]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
        y = "Density"
    ) +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
          axis.text = element_text(size = 16),     
        axis.title = element_text(size = 16),    
        legend.text = element_text(size = 16),   
        legend.title = element_text(size = 16)   
          )

  all_plots[[as.character(L)]] <- p
}

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
  plot_layout(guides = "collect")

print(combined_plot)

```

Under $\mathcal{H}_0$, the distribution of the test statistic $S$ is asymptotically normal. Thus, due to the asymptotic properties of the entropy estimator, and assuming the sample is sufficiently large, the statistic follows a standard normal distribution.

Therefore, the $p$-value is computed as $2\Phi(-\mid \varepsilon \mid)$,
where $\Phi$ is the standard Gaussian cumulative distribution function, and $\varepsilon$ is given by:  
$$
\varepsilon = \frac{\widetilde{H_i} - \widehat{H_i}(\Gamma_{\text{SAR}})}{\widehat{\sigma}_{i}}.
$$
An important aspect in hypothesis testing is ensuring that the test maintains the expected Type I error rate (size) while achieving high power (sensitivity to departures from $\mathcal{H}_0$).
To assess these properties, we performed $1000$ simulations at significance levels of $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution) with varying sample sizes, values of $L$, and $\mu=1$. 
The observed Type I error rates aligned with the nominal values, confirming the test’s validity.

Additionally, we examined the power under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
As expected, power improves as the sample size and number of looks increase the effectiveness demonstrating of the test. The results are shown in Table \ref{tab:table_size_power}.

```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
# 
calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
  epsilon <- test_statistic / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value < alpha_nominal)  
}
R <- 1000
mu <- 1
B <- 100
lambda <- 0.9
L_values <- c(  5, 8, 18)
sample_sizes <- c( 25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results <- data.frame()
for (L in L_values) {
  for (alpha_nominal in alpha_nominals) {
    TestStatistics <- NULL
    mean_entropy <- numeric(length(sample_sizes))
    sd_entropy <- numeric(length(sample_sizes))

    for (s in sample_sizes) {
      TestStat <- numeric(R)

      for (r in 1:R) {
        z <- gamma_sar_sample(L, mu, s)
        TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))

        #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
      }
      mean_entropy[sample_sizes == s] <- mean(TestStat)
      sd_entropy[sample_sizes == s] <- sd(TestStat)

      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
    }

    mu_W <- mean_entropy
    sigma_W <- sqrt(sd_entropy^2)

    p_values <- apply(TestStatistics, 1, function(row) {
      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
    })

    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
    results <- rbind(results, result)
  }
}
save(results, file = "./Data/type_I_results.Rdata")

```

```{r Simulated_power, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")
calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
  epsilon <- test_statistic  / sigma_W
  p_value <- 2 * (1 - pnorm(abs(epsilon)))

  return(p_value)
}
calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
  return(type_II_error_rate)
}

calculate_power <- function(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals) {
  results <- data.frame()

  for (L in L_values) {
    for (alpha_nominal in alpha_nominals) {
      TestStatistics <- list()
      mean_entropy <- numeric(length(sample_sizes))
      sd_entropy <- numeric(length(sample_sizes))

      for (s in sample_sizes) {
        TestStat <- numeric(R)

        for (r in 1:R) {
          z <- gi0_sample(mu, -2, L, s)
          TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))

        }

        mean_entropy[sample_sizes == s] <- mean(TestStat)
        sd_entropy[sample_sizes == s] <- sd(TestStat)

        TestStatistics[[as.character(s)]] <- TestStat
      }

      mu_W <-  mean_entropy  
      sigma_W <- sqrt(sd_entropy^2)

      p_values <- lapply(TestStatistics, function(TestStat) {
        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
        })
      })

      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
      })

      power <- 1 - type_II_error_rates

      result_row <- data.frame(
        L = L,
        alpha_nominal = alpha_nominal,
        Sample_Size = sample_sizes,
        power = power
      )

      results <- rbind(results, result_row)
    }
  }

  return(results)
}
R <- 1000
mu <- 1
L_values <- c( 5,  8, 18)
B <- 100
lambda<- 0.9
sample_sizes <- c(25, 49, 81, 121)
alpha_nominals <- c(0.01, 0.05, 0.1)
results_power <- calculate_power(R, mu, L_values, B,lambda, sample_sizes, alpha_nominals)
save(results_power, file = "./Data/results_power.Rdata")

```

```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

suppressMessages({
  suppressWarnings({

    load("./Data/type_I_results.Rdata")
    type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
      sum(p_values) / length(p_values)  
    })

    type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
    colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")

    spread_results <- type_I_error_results %>%
      pivot_wider(names_from = Alpha_Nominal, values_from = Type_I_Error_Rate)

    load("./Data/results_power.Rdata")

    summary_stats <- results_power %>%
      pivot_wider(names_from = alpha_nominal, values_from = power)

    combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size")) %>%
      arrange(L, Sample_Size)

    selected_columns <- c("L", "Sample_Size", grep("^0\\.", colnames(combined_results), value = TRUE))

    if (length(selected_columns) == 8) {
      combined_results <- combined_results[, selected_columns, drop = FALSE]
      colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", 
                                      "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", 
                                      "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
    }

combined_results[] <- lapply(combined_results, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)  # Enteros en formato LaTeX
    } else {
      formatted_numbers <- ifelse(x < 0, 
                                  sprintf("$%.3f$", x), 
                                  sprintf("$\\phantom{-}%.3f$", x))  # Decimales en LaTeX
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

  })
})

table_combined_result <- knitr::kable(
  combined_results,
  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z})$ test statistic.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccccc",
  escape = FALSE,
  digits = 3,
  label = "table_size_power",
  centering = FALSE,
  table.envir = "table", position="htb", linesep = "") %>%
  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down",font_size = 7) %>%
  kable_styling(full_width = T)

print(table_combined_result)

```

# Applications to SAR Data {#sec:app}

In this section, we evaluate the proposed test statistic on real SAR data to assess its effectiveness in detecting heterogeneity.
The test was applied to SAR intensity images from diverse environments, including urban, agricultural, and water regions. Specifically, we analyzed three images: the first one from London, United Kingdom; the second from the surroundings of Munich, Germany; and the third from the Dublin Port, Ireland, as shown in Figs.\ \ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
Table\ \ref{tab:table_param} provides detailed acquisition parameters for these images.
\renewcommand{\arraystretch}{3}   
```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}

SAR_data <- data.frame(
  Site = c("London", "Munich", "Dublin" ),
  Mission = c("TanDEM-X", "UAVSAR", "TanDEM-X"),
  Band = c("X", "L", "X"),
  Polarization = c("HH", "HH", "HH"),
  Size = c("$2000\\times2000$", "$1024\\times1024$", "$1100\\times1100$"),
  L = c(1, 12, 16),
  Resol = c("$0.99/0.99$", "$4.9/7.2$", "$1.35/1.35$"),
  Date = c("12-11-2021", "16-04-2015", "03-09-2017")
)

colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution [m]} ", "\\textbf{Acquisition Date}")

SAR_data[] <- lapply(SAR_data, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

kable(SAR_data, caption = "Parameters of selected SAR images.",
      format = "latex",
      booktabs = TRUE,
      align = "cccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = FALSE,
      table.envir = "table", position = "H") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 20) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "3.5cm") %>%
  column_spec(3, width = "1cm") %>%
  column_spec(4, width = "1.5cm") %>%
  column_spec(5, width = "4cm") %>%
  column_spec(6, width = "1.5cm") %>%
  column_spec(7, width = "2cm") %>%
  column_spec(8, width = "3.5cm")

```

For conducting  the performance of our methodology, we applied the test statistic $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ based on Rényi entropy and the test $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ based on Shannon entropy described in\ [@Frery2024], using a local sliding window of size $7\times7$. 
The resulting $p$-value maps are presented in Figs.\ \ref{fig:london}(b), \ref{fig:london}(d), \ref{fig:munich}(b), \ref{fig:munich}(d), \ref{fig:dublin}(b), and \ref{fig:dublin}(d). 
These maps employ a color gradient, where darker regions indicate areas with higher roughness, while lighter regions correspond to smoother, less textured surfaces.

In order to better illustrate the decision-making process of both tests, binary maps at a significance level of $0.05$ are shown in Figs.\ \ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e), respectively.

In these binary representations, white areas correspond to $p$-values greater than $0.05$, indicating that there is no statistical evidence to reject the null hypothesis (homogeneous regions). 
In contrast, black areas represent regions where the $p$-values are less than $0.05$, indicating statistically significant heterogeneity.

The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations compared to the Shannon-based approach, due to the flexibility provided by the parameter $\lambda$. 
When $\lambda \to 1$, Rényi entropy converges to Shannon entropy, resulting in similar heterogeneity detection. 
Our analysis shows that the optimal $\lambda$ value depends on the number of looks: for single-look images like London, $\lambda = 3$ provided the best contrast, while for multi-look images like Munich and Dublin, $\lambda = 0.9$ was more effective.

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/london_2000.png}
        \caption{ SAR image}
        \label{fig:1a}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_renyi.png}
        \caption{ $p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:1b}
    \end{subfigure}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:1c}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_Shannon_c1.png}
        \caption{$p$-values for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:1d}
    \end{subfigure}
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:1e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.  }
    \label{fig:london}
\end{figure*}

```

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/munich_1024_2.png}
        \caption{SAR image}
        \label{fig:2a}
    \end{subfigure}
    \begin{subfigure}{0.23\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_renyi.png}
        \caption{$p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:2b}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_munich_renyi.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:2c}
    \end{subfigure}
    \begin{subfigure}{0.23\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_Shan22.png}
        \caption{$p$-values for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:2d}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_munich_sh_AO_L12.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:2e}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:munich}
\end{figure*}

```

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.17\textwidth}
        \includegraphics[width=\linewidth]{./Figures/dublin_1100_hh.png}
        \caption{SAR image}
        \label{fig:3a}
    \end{subfigure}
    \begin{subfigure}{0.22\textwidth}
        \includegraphics[width=\linewidth]{./Figures/dublin_renyi_09_w7_b100.png}
        \caption{$p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:3b}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_dublin_renyi_09_w7_b100.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:3c}
    \end{subfigure}
    \begin{subfigure}{0.23\textwidth}
        \includegraphics[width=\linewidth]{./Figures/AO_w7_L16_b100.png}
        \caption{$p$-values for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:3d}
    \end{subfigure}
    \begin{subfigure}{0.16\textwidth}
        \includegraphics[width=\linewidth]{./Figures/H_005_AO_w7_L16_b100.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:3e}
    \end{subfigure}
   \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}

    \label{fig:dublin}
\end{figure*}

```

# Conclusions {#sec:conclusion}

This study introduced a new statistical approach based on Rényi entropy to detect heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
The proposed test statistic is computed non-parametrically and was assessed through a Monte Carlo study. 
The results indicate that the method effectively controls the probability of a Type I error while maintaining a high detection power, which improves as the sample size increases.

The performance of the Rényi-based test was evaluated by comparing its results with those of a test based on Shannon entropy 
 $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$. 
This comparison was conducted through $p$-values and binary maps.
The findings reveal that while both tests successfully detect heterogeneous regions, the Rényi-based test demonstrates superior results due to its flexibility in adjusting the parameter $\lambda$, allowing for a more refined differentiation of textural variations.

These results suggest that Rényi entropy provides a robust alternative to Shannon entropy for heterogeneity detection in SAR images, particularly due to its adaptability.  
Future research will focus on a more quantitative assessment of both approaches using statistical measures such as Mean Squared Error and other validation metrics to evaluate their accuracy in detecting heterogeneity.

# Acknowledgment {-}

This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) – Finance Code 001  and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.

# Computational Information {-}
This article was written using Quarto v.6.4, RStudio v2024.12.0.467, and R v.4.4.2, and is fully reproducible.

The Code and data used in this study are available at: <https://github.com/rjaneth/renyi-entropy-sar>

::: {.content-visible when-format="pdf"}
# References {-}
:::

<!-- [^issues-1023]: ["_[longtable not compatible with 2-column LaTeX documents](https://github.com/jgm/pandoc/issues/1023>)_",  -->

<!-- [^issues-2275]: See the issue here <https://github.com/quarto-dev/quarto-cli/issues/2275> -->

<!-- [IEEEXplore<sup>®</sup>]: <https://ieeexplore.ieee.org/> -->

### 2025-02-02 Text/Reports/report-Renyi/R1-report-renyi.Rmd
Add initial version of the paper

@@
 
+## Simplified Analytical Expressions for Rényi Entropy
+
+Below we show how to express the Rényi entropy of the \( G_I^0 \) distribution in terms of the entropy of the \(\Gamma_{\text{SAR}}\) law plus additional terms involving \(\alpha\).
+We also ensure that the term \(\ln(\mu)\) remains explicitly isolated.
+
+### 1) Rényi Entropy of \(\Gamma_{\text{SAR}}\)
+
+For a \(\Gamma_{\text{SAR}}(L,\mu)\) random variable, a convenient form of its Rényi entropy of order \(\lambda\) (\(\lambda>0\), \(\lambda\neq 1\)) is:
+
+\[
+H_{\lambda}\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr)
+\;=\;
+\ln(\mu)\;+\;A_{\lambda}(L),
+\tag{1}
+\]
+
+where
+
+\[
+A_{\lambda}(L)
+\,=\,
+-\,\ln L
+\;+\;
+\frac{\lambda}{\lambda \,-\,1}\,\ln\Gamma(L)
+\;-\;
+\frac{1}{\lambda \,-\,1}\,
+\ln\Gamma\Bigl(\lambda\bigl(L - 1\bigr)+1\Bigr)
+\;+\;
+\frac{\lambda\bigl(L - 1\bigr)+1}{\lambda \,-\,1}
+\,\ln(\lambda).
+\]
+
+Here, \(\Gamma(\cdot)\) is the gamma function. Crucially, notice that \(\ln(\mu)\) appears **as a separate term**.
+
+### 2) Rényi Entropy of \( G_I^0 \)
+
+For \( G_I^0(\alpha,L,\mu)\) (with \(\alpha<0\)), we can write its Rényi entropy in a comparable form:
+
+\[
+H_{\lambda}\bigl(G_I^0(\alpha,L,\mu)\bigr)
+\;=\;
+\ln(\mu)\;+\;A_{\lambda}(L)\;+\;T_{\lambda}(\alpha,L).
+\tag{2}
+\]
+
+In this expression:
+
+- \(\ln(\mu)\) is **exactly** the same term as in \(\Gamma_{\text{SAR}}\).  
+- \(A_{\lambda}(L)\) is **the same function of \(L\) and \(\lambda\)** from Equation&nbsp;\((1)\).  
+- \(T_{\lambda}(\alpha,L)\) **captures the extra terms** that arise due to the roughness parameter \(\alpha\).
+
+Hence, by defining:
+
+\[
+T_{\lambda}(\alpha,L)
+\;=\;
+H_{\lambda}\bigl(G_I^0(\alpha,L,\mu)\bigr)
+\;-\;
+\Bigl[\,\ln(\mu)\,+\,A_{\lambda}(L)\Bigr],
+\]
+
+we isolate all the \(\alpha\)-dependent components in one place.
+In particular, one of the key additional factors is \(\ln(-1-\alpha)\), which does **not** appear in the \(\Gamma_{\text{SAR}}\) case.
+As \(\alpha\to -\infty\), these extra terms tend to the constants (or zero) that make the \(G_I^0\) law converge to \(\Gamma_{\text{SAR}}\).
+
+### 3) Interpretation
+
+1. **Homogeneous Case** (\(\Gamma_{\text{SAR}}\)):  
+   \(\alpha\to -\infty\), thus \(T_{\lambda}(\alpha,L)\to 0\). Consequently,
+   \[
+   H_{\lambda}\bigl(G_I^0(\alpha\to -\infty,L,\mu)\bigr)
+   \;=\;
+   \ln(\mu) \;+\; A_{\lambda}(L),
+   \]
+   which exactly matches \(H_{\lambda}(\Gamma_{\text{SAR}})\).
+
+2. **Heterogeneous Case** (\(G_I^0\), finite \(\alpha<0\)):  
+   The additional term \(T_{\lambda}(\alpha,L)\neq 0\) captures the deviation from full speckle development, i.e., roughness.
+The more negative \(\alpha\) is, the closer \(G_I^0\) is to \(\Gamma_{\text{SAR}}\); the less negative \(\alpha\) is (e.g., \(\alpha=-3\)), the greater the discrepancy.
+
+In this way, **\(H_{\lambda}(\Gamma_{\text{SAR}})\) acts as a baseline** for the fully developed speckle (homogeneous) scenario, and any departure from this baseline—quantified by \(T_{\lambda}(\alpha,L)\)—indicates the presence of heterogeneity.
+
+## Simplified Analytical Expressions for Rényi Entropy
+
+Below are *factorized* forms of the Rényi entropy for the two main models used in SAR image analysis, namely the \(\Gamma_{\text{SAR}}\) distribution (fully developed speckle) and the \(G_I^0\) distribution (able to represent roughness).
+These versions emphasize that \(\ln(\mu)\) appears **as an isolated term**, and they gather the remaining factors under a common \(\frac{1}{\lambda - 1}\) multiplier.
+
+---
+
+### 1) Rényi Entropy of \(\Gamma_{\text{SAR}}(L,\mu)\)
+
+For a \(\Gamma_{\text{SAR}}(L,\mu)\) random variable, the Rényi entropy of order \(\lambda\) (\(\lambda>0, \lambda\neq1\)) can be written as:
+
+\[
+H_{\lambda}\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr)
+=\;
+\ln\bigl(\mu\bigr)
+\;+\;
+\frac{1}{\lambda - 1}\Bigl[
+  \lambda\,\ln\Gamma(L)
+  \;-\;
+  \ln\Gamma\bigl(\lambda(L - 1)+1\bigr)
+  \;-\;
+  (\lambda - 1)\,\ln L
+  \;+\;
+  \bigl(\lambda(L - 1)+1\bigr)\,\ln\lambda
+\Bigr].
+\tag{1}
+\]
+
+Here, \(\Gamma(\cdot)\) is the gamma function. Notice how \(\ln(\mu)\) is an independent addend.
+
+The bracketed term vanishes (or becomes a constant offset) as \(\alpha \to -\infty\), showing that \(\Gamma_{\text{SAR}}\) is indeed a limiting case of \(G_I^0\).
+In other words, when \(\alpha\) is very negative, the extra “roughness” contribution disappears, and the *fully developed speckle* scenario (homogeneous model) is recovered.
+
 ```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="85%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ when $\\alpha\\to-\\infty$, with $L=8$."}
@@
 \]
+
+\section*{Appendix: Limit Behavior of $H_\lambda(G_I^0)$ as $\alpha \to -\infty$}
+
+\subsection*{Detailed Version of the Proof}
+
+\begin{proof}
+We want to show that 
+\[
+\lim_{\alpha \to -\infty}
+H_\lambda\bigl(G_I^0\bigr)(\mu, \alpha, L)
+=
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu, L).
+\]
+
+First, recall that:
+\begin{align}
+H_\lambda\bigl(G_I^0\bigr)(\mu,\alpha,L)
+&=
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L)
+\;+\;
+\ln\!\bigl(-1-\alpha\bigr)
+\\
+&\quad
++ \frac{1}{1-\lambda}
+\ln \Biggl[
+  \frac{
+    \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)\,\lambda^{\lambda(L-1)+1}
+  }{
+    \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
+  }
+\Biggr].
+\end{align}
+Set
+\begin{align}
+\Delta(\alpha)
+&=
+H_\lambda\bigl(G_I^0\bigr)(\mu,\alpha,L)
+-
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L).
+\end{align}
+Then 
+\[
+\Delta(\alpha)
+=
+\ln(-1-\alpha)
++
+\frac{1}{1-\lambda}
+\ln \biggl[
+  \frac{
+    \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)\,\lambda^{\lambda(L-1)+1}
+  }{
+    \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
+  }
+\biggr].
+\]
+
+As \(\alpha \to -\infty\), we have \(-1-\alpha \approx |\alpha|\), so 
+\[
+\ln(-1-\alpha) 
+\sim 
+\ln|\alpha|.
+\]
+Next, note that for large \(|\alpha|\), one uses the asymptotic relation 
+\(
+\Gamma(x+a)/\Gamma(x+b) 
+\sim 
+x^{\,a-b}
+\).
+Specifically:
+\[
+\Gamma(L-\alpha)/\Gamma(-\alpha) \;\sim\; |\alpha|^L,
+\quad
+\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)/\Gamma\bigl(\lambda(L-\alpha)\bigr)
+\;\sim\; 
+\bigl(\lambda|\alpha|\bigr)^{\,(\lambda-1)-\lambda L}.
+\]
+Thus, inside the big logarithm,
+\[
+\frac{
+  \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)
+}{
+  \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
+}
+\;\sim\;
+|\alpha|^{\lambda L}
+\times
+|\alpha|^{(\lambda-1)-\lambda L}
+=
+|\alpha|^{\,\lambda-1}.
+\]
+Multiplying by \(\lambda^{\lambda(L-1)+1}\) (a constant factor in \(\alpha\)) does not affect the \(\alpha\)-dependence. Therefore,
+\[
+\frac{1}{1-\lambda}\,
+\ln\!\Bigl[\dots\Bigr]
+\;\sim\;
+\frac{1}{1-\lambda}\;\ln\!\bigl(|\alpha|^{\,\lambda-1}\bigr)
+=
+\frac{\lambda-1}{1-\lambda}\,\ln|\alpha|
+=
+-\ln|\alpha|.
+\]
+Hence
+\[
+\Delta(\alpha)
+\;\sim\;
+\ln|\alpha|
+-
+\ln|\alpha|
+=
+0
+\quad
+\text{as}
+\;\;
+\alpha\to -\infty.
+\]
+This shows 
+\(\Delta(\alpha)\to 0\), 
+and consequently
+\[
+\lim_{\alpha \to -\infty}
+H_\lambda\bigl(G_I^0\bigr)(\mu,\alpha,L)
+=
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L).
+\]
+\end{proof}
+
+\subsection*{Concise Version of the Proof}
+
+\begin{proof}
+We need to prove
+\(
+\lim_{\alpha\to -\infty} 
+H_\lambda(G_I^0)(\mu, \alpha, L)
+=
+H_\lambda(\Gamma_{\mathrm{SAR}})(\mu, L).
+\)
+By the known decomposition,
+\begin{align}
+H_\lambda\bigl(G_I^0\bigr)(\mu,\alpha,L)
+&=
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L)
+\;+\;
+\ln\bigl(-1-\alpha\bigr)
+\\
+&\quad
++ \frac{1}{1-\lambda}
+\ln \Biggl[
+  \frac{
+    \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)\,\lambda^{\lambda(L-1)+1}
+  }{
+    \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
+  }
+\Biggr].
+\end{align}
+Denote the extra \(\alpha\)-dependent terms by \(\Delta(\alpha)\).  As \(\alpha \to -\infty\), we have \(\ln(-1-\alpha)\sim\ln|\alpha|\).  Meanwhile, using 
+\(\Gamma(x+a)/\Gamma(x+b)\sim x^{\,a-b}\),
+the ratio of Gamma functions behaves like 
+\(\,|\alpha|^{\lambda-1}\),
+and multiplying by \(\lambda^{\lambda(L-1)+1}\) is a constant factor.
+Hence the logarithm of that ratio is \(\sim(\lambda-1)\ln|\alpha|\), and dividing by \((1-\lambda)\) gives \(-\ln|\alpha|\).
+Thus the two terms
+\(\ln|\alpha|\) 
+and 
+\(-\ln|\alpha|\) 
+cancel each other. Therefore, 
+\(\Delta(\alpha)\to 0\),
+which concludes
+\[
+\lim_{\alpha \to -\infty} 
+H_\lambda\bigl(G_I^0\bigr)(\mu,\alpha,L)
+=
+H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L).
+\]
+\end{proof}

### 2025-02-02 Code/R/Programs/plot_nls_model_exp.R

@@ -26,12 +26,12 @@ source("../MainFunctions/entropy_gI0.R")
 source("../MainFunctions/gi0_sample.R")
 
 # Set parameters
-#set.seed(1234567890, kind = "Mersenne-Twister")
+set.seed(1234567890, kind = "Mersenne-Twister")
 sample.size <- 49
-R <- 300
+R <- 10000
 mu <- 1
 L <- 5
-alpha1 <- -100
+alpha1 <- -1.5
 
 # Initialize vectors to store means and CVs
 means <- numeric(R)

### 2025-02-02 Code/R/Programs/test_entropy_renyi_2.R

@@ -28,8 +28,8 @@ source("../../../Code/R/Programs/read_ENVI_images.R")
 #                  headerfile='../../../Data/SAR/chicago_1024/Intensity_HH.hdr')
 # 
 
- x <- myread.ENVI(file='../../../Data/SAR/Rotterdam_1024/Intensity_HH.img',
-                  headerfile='../../../Data/SAR/Rotterdam_1024/Intensity_HH.hdr')
+ x <- myread.ENVI(file='../../../Data/SAR/Lake_512/Intensity_VV.img',
+                  headerfile='../../../Data/SAR/Lake_512/Intensity_VV.hdr')
  
  # x <- myread.ENVI(file='../../../Data/SAR/envi_panama_512/Intensity_VV.img', 
  #                  headerfile='../../../Data/SAR/envi_panama_512/Intensity_VV.hdr')

### 2025-02-11 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
update paper with corrections

@@
 abstract: |
- We propose a test statistic for identifying roughness characteristics in synthetic aperture radar (SAR) intensity data using Rényi entropy. 
- Homogeneous regions, where speckle is fully developed, are modeled by the Gamma distribution, while heterogeneous areas, associated with surface roughness, follow the $\mathcal{G}^0$ distribution. 
- The test relies on a non-parametric estimator of Rényi entropy to distinguish between these two types of regions. 
- By applying it to real SAR images, we generate $p$-value maps to assess the homogeneity hypothesis. 
- Experimental results show that the Rényi-based approach improves heterogeneity detection compared to previous methods using Shannon entropy.
-
-keywords: [Gamma distribution, heterogeneity, SAR, Rényi entropy, hypothesis tests]
+  Synthetic aperture radar (SAR) systems have already been successfully used to solve remote sensing problems.
+A disadvantage of SAR images is the presence of speckle, which is fully developed in homogeneous areas and gamma-distributed in these scenes.
+In heterogeneous areas, the intensity values are $\mathcal{G}^0_I$-distributed.
+  In this way, the identification of roughness SAR areas (as opposed to homogeneous ones) is an important task. 
+  In this work, we propose a family of hypothesis tests driven by an order parameter to identify roughness features in SAR intensity data using Rényi entropy. 
+  In particular, we use a nonparametric estimator for the Rényi entropy and investigate some of its properties. 
+  As a practical evaluation method, we develop $p$-value maps on which one can observe both (i) the heterogeneous evidence change per texture and (ii) the prediction of homogeneous and heterogeneous categories.
+  The results are in favor of the Rényi-based heterogeneity detector compared to the one based on Shannon entropy.
+keywords: [Rényi entropy, Gamma distribution, heterogeneity, SAR,  hypothesis tests]
 #funding: 
@@
 
-Synthetic Aperture Radar (SAR) technology has become essential for a wide range of applications, including environmental monitoring and disaster management\ [@Yu2023;  @Mondini2021]. 
-By operating independently of sunlight and under various weather conditions, SAR systems provide continuous, high-resolution imagery\ [@Zeng2020]. 
-Despite these advantages, SAR data exhibit speckle, a noise-like interference effect that arises due to the coherent nature of the imaging process\ [@Argenti2013;@Choi2019].
+Synthetic Aperture Radar (SAR) technology has become essential for a wide range of applications\ [@Yu2023;@Akbarizadeh2012;@Mondini2021].
+It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions to facilitate global Earth monitoring\ [@Zeng2020].
+Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect\ [@Argenti2013; @Choi2019].
 In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
 
-The $\mathcal{G}^0$ distribution has shown to be an effective model for SAR intensity data,  as it captures different levels of roughness.
-A special case is the Gamma distribution,which arises when speckle is fully developed, indicating homogeneous regions.
-Although these models provide flexible frameworks for describing SAR intensities, selecting the appropriate model can be challenging for two main reasons: the small samples used in practical applications  and the inherent difficulties associated with parameter estimation.
+The $\mathcal{G}^0$ distribution has been shown to be an effective model for SAR intensity data, as it captures different levels of roughness.
+A special case is the Gamma distribution, which arises when speckle is fully developed, indicating homogeneous regions.
+Although these models offer flexibility in describing SAR intensities, selecting the appropriate model can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
 These challenges complicate model selection and highlight the need to explore alternative statistical approaches.
@@
 
-The rest of this article is organized as follows.
-Section \ref{sec:pre} presents an overview of statistical models for SAR intensity data and introduces Rényi entropy.
-In Section \ref{sec:met}, we describe the proposed hypothesis test and the formulation of the test statistic. 
-Section \ref{sec:app} evaluates the test's performance using real SAR data.
-Finally, Section \ref{sec:conclusion} presents the conclusions.
+The remainder of this article is organized as follows.
+Section\ \ref{sec:pre} outlines an overview of statistical models for SAR intensity data and introduces Rényi entropy.
+Section\ \ref{sec:met} describes the proposed hypothesis test and the formulation of the test statistic. 
+Section\ \ref{sec:app} evaluates the performance of the test using real SAR data.
+Finally, the concluding remarks are drawn in Section\ \ref{sec:conclusion}.
 
@@
 
-The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $G_I^0$ distribution, which is able to describe roughness\ [@Frery1997].
+The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997].
 These distributions are characterized by the following probability density functions (pdfs):
-
 \begin{align}
-	f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gamma1}
+	f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
+    &= \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
+    \exp \biggl(-\frac{Lz}{\mu}\biggr)
+    \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
+    \intertext{and}
+    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
+    &= \frac{L^L\,\Gamma(L-\alpha)}
+    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
+    \notag \\
+    &\quad \times
+    \frac{z^{L-1}}
+    {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
+    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi01}
 \end{align}
-\begin{multline}
-\label{E:gi01}
-	f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}\mathbbm 1_{\mathbbm R_+}(z),
-\end{multline}
-
 where $\mu > 0$ is the mean,
@@
 $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
-
-As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $G_I^0$ distribution. Specifically, for a given $\mu$ fixed,
+As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
 $$
-f_Z\big(z; \mu, \alpha, L\mid G_I^0\big)
+f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
 \longrightarrow 
-f_Z(z;L, \mu\mid \Gamma_{\text{SAR}}) 
+f_{\Gamma_{\text{SAR}}}(z;L, \mu) 
 $$
@@
 
-Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], the Rényi entropy generalizes several entropy measures, including the Shannon entropy.
-For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$ (where $\lambda > 0$ and $\lambda \neq 1$) is defined as:
-
+Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], this measure generalizes several well-known entropies, including the Shannon entropy\ [@Ribeiro2021].
+For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$, with $\lambda > 0$ and $\lambda \neq 1$, is defined as:
 \begin{align}
@@
 \end{align}
-
-Using this definition, we obtain the Rényi entropy expressions for the $\Gamma_{\text{SAR}}$ and $G_I^0$ distributions, respectively:
-
+Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions:
 \begin{multline}
 \label{eq-HGammaSAR}
-H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
 = 
@@
 \begin{multline}\label{eq-HGI0}
-H_\lambda\bigl(G_I^0(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
 + \frac{1}{\,1 - \lambda\,}
@@
 \end{multline}
-
-@fig-plot presents the Rényi entropy of $G_I^0$ as a function of $\mu$ for different $\alpha$ values.
-As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is consistent with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $G_I^0$ model.
-
-```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(G_I^0)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}
+@fig-plot presents the Rényi entropy of $\mathcal{G}^0_I$ as a function of $\mu$ for different $\alpha$ values.
+As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is aligned with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $\mathcal{G}^0_I$ model.
+
+```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}
 
@@
 
-Several authors have studied the nonparametric estimation of $H(Z)$, utilizing estimators that rely on spacings, which are the differences between order statistics\ [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999;@AlOmari2019].
-In 2024, Al-Labadi et al.\ [@AlLabadi2024] introduced a nonparametric estimator for Rényi entropy using this approach.
-
-Let $\{Z_1, Z_2, \dots, Z_n\}$ be a sample from a distribution $F$, and denote its order statistics by $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$. 
+Nonparametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994;@Wieczorkowski1999; @AlOmari2019].
+Recently, Al-Labadi et al.\ [@AlLabadi2024] proposed a nonparametric estimator for Rényi entropy following this approach.
+
+<!-- Let $\bm{Z} = (Z_1, Z_2, \dots, Z_n)$ be a random sample from $F(z)$ with order statistics $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$. The $m$-spacing density estimator is defined as: -->
+Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be a random sample from the distribution $F(z)$ and denote its order statistics by $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$.
 The density estimator based on $m$-spacing, is defined as:
@@
 $$
-
 where $Z_{(i-m)} = Z_{(1)}$ when $i \leq m$ and $Z_{(i+m)} = Z_{(n)}$ if $i \geq n - m$. The coefficient $c_i$ is given by:
@@
 $$
-Following Vasicek [@vasicek1976test] and Ebrahimi et al. [@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, Rényi entropy can be estimated as:
+
+Following Vasicek [@vasicek1976test] and Ebrahimi et al. [@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, the Rényi entropy can be estimated as:
 \begin{align}
@@
 We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator, specifically for a sample size of $n=49$.
-To identify this optimal value, we analyze both the Mean Squared Error (MSE) and Bias of the estimator across different values of $\lambda$.
-Lower MSE and Bias indicate better performance of the estimator in approximating the true entropy.
-
-Based on the results, we find that the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low Bias.
+To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
+Lower MSE and bias indicate better performance of the estimator in approximating the true entropy.
+
+Based on the results, we find that the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
 This choice is consistent with other values of $L > 1$.
@@
 
-```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=8, fig.height=6}
+```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=8, fig.height=6}
 
@@
 
-Following previous studies by\ [@Frery2024] and\ [@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply an improved version:
+Following previous studies by\ [@Frery2024] and\ [@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply the improved version:
 $$
-\widetilde{H}_{\lambda} = 2\widehat{\theta}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}_b(\bm{Z}^{(b)}).
+\widetilde{H}_{\lambda} = 2\widehat{\theta}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}_b(\bm{Z}^{(b)}),
 $$
+where $B$ is the number of new samples generated through resampling with replacement.
+
 A Monte Carlo study with $1000$ samples from $\Gamma_{\text{SAR}}$ ($\mu = 1$, $L=5$, $\lambda = 0.9$) confirms that this approach, using $B = 200$ replications, reduces bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
@@
 
-```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%", fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimator for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=1$ and $L=5$.", fig.width=8, fig.height=7}
+```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimator for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=1$ and $L=5$.", fig.width=8, fig.height=7}
 
@@
 \begin{cases}\mathcal{H}_0: \widehat{H}^*= H_{\lambda}(\Gamma_{\text{SAR}})\\ 
-  \mathcal{H}_1:\widehat{H}^*= H_{\lambda}(G_I^0).\end{cases}
+  \mathcal{H}_1:\widehat{H}^*= H_{\lambda}(\mathcal{G}^0_I).\end{cases}
 $$
@@
 
-Assume we have an estimator $\widehat{H_{\lambda}}$ for the Rényi entropy of an arbitrary model.
+Assume we have an estimator $\widehat{H}_{\lambda}$ for the Rényi entropy of an arbitrary model.
 In the case of the $\Gamma_{\text{SAR}}$ model, this estimator is expected to be close to the theoretical expression given in Equation \eqref{eq-HGammaSAR}.
-Considering that $L\geq1$ is known, we define the following test statistic:
+Since $L\geq1$ is known, we define the test statistic as follows:
 \begin{multline}
@@
 \end{multline}
-
 When the null hypothesis holds, this test statistic is expected to be close to zero.
@@
 For illustrative purposes, @fig-density_entropyR provide the empirical density of $S(\bm{Z}; L)$  for the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
-For subsequent simulations we use the $\widetilde{H_{\lambda}}$ estimator.
+For subsequent simulations we use the $\widetilde{H}_{\lambda}$ estimator.
 
@@
 $$
-\varepsilon = \frac{\widetilde{H_i} - \widehat{H_i}(\Gamma_{\text{SAR}})}{\widehat{\sigma}_{i}}.
+\varepsilon = \frac{\widetilde{H}_i - \widehat{H}_i(\Gamma_{\text{SAR}})}{\widehat{\sigma}_{i}}.
 $$
-An important aspect in hypothesis testing is ensuring that the test maintains the expected Type I error rate (size) while achieving high power (sensitivity to departures from $\mathcal{H}_0$).
-To assess these properties, we performed $1000$ simulations at significance levels of $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution) with varying sample sizes, values of $L$, and $\mu=1$.
-The observed Type I error rates aligned with the nominal values, confirming the test’s validity.
-
-Additionally, we examined the power under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
+An important aspect of hypothesis testing is ensuring that the test maintains the expected type I error rate (size) while achieving high power (sensitivity to departures from $\mathcal{H}_0$).
+To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels  $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution) and varying sample sizes, values of $L$, and $\mu=1$.
+The observed type I error rates aligned with the nominal values, confirming the test validity.
+
+Additionally, we examined the power under the alternative hypothesis ($\mathcal{G}^0_I$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
 As expected, power improves as the sample size and number of looks increase the effectiveness demonstrating of the test. The results are shown in Table \ref{tab:table_size_power}.
@@
 ```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
+if (!file.exists("./Data/type_I_results.Rdata")) {
+
+  message("AFile type_I_results.Rdata not found. Generating results...")
+
   set.seed(1234567890, kind = "Mersenne-Twister")
-# 
+
   calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
@@
     p_value <- 2 * (1 - pnorm(abs(epsilon)))
-
     return(p_value < alpha_nominal)  
   }
+
   R <- 1000
@@
   lambda <- 0.9
-L_values <- c(  5, 8, 18)
-sample_sizes <- c( 25, 49, 81, 121)
+  L_values <- c(5, 8, 18)
+  sample_sizes <- c(25, 49, 81, 121)
   alpha_nominals <- c(0.01, 0.05, 0.1)
   results <- data.frame()
+
   for (L in L_values) {
@@
           z <- gamma_sar_sample(L, mu, s)
-        TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))
-
-        #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      }
+          TestStat[r] <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) - (
+            (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) + 
+             (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +
+            log(mean(z)) - log(L)
+          )
+        }
+
         mean_entropy[sample_sizes == s] <- mean(TestStat)
@@
 
-      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
+        TestStatistics <- rbind(
+          TestStatistics,
+          data.frame(
+            "L" = rep(L, R),
+            "Sample_Size" = rep(s, R),
+            "Test_Statistics" = TestStat
+          )
+        )
       }
@@
       p_values <- apply(TestStatistics, 1, function(row) {
-      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
+        calculate_p_value(
+          row["Test_Statistics"],
+          mu_W[sample_sizes == row["Sample_Size"]],
+          sigma_W[sample_sizes == row["Sample_Size"]],
+          alpha_nominal
+        )
       })
 
-    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
+      result <- data.frame(
+        "L" = TestStatistics$L,
+        "Sample_Size" = TestStatistics$Sample_Size,
+        "Alpha_Nominal" = alpha_nominal,
+        "P_Value" = p_values
+      )
       results <- rbind(results, result)
@@
   }
+
   save(results, file = "./Data/type_I_results.Rdata")
 
+} else {
+
+  message("File type_I_results.Rdata found. Generating results...")
+  load("./Data/type_I_results.Rdata")
+
+}
 ```
@@
 ```{r Simulated_power, echo=FALSE, message=FALSE}
+
+if (!file.exists("./Data/results_power.Rdata")) {
+
+  message("File type_I_results.Rdata not found. Generating results...")
+
   set.seed(1234567890, kind = "Mersenne-Twister")
+
   calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
@@
     p_value <- 2 * (1 - pnorm(abs(epsilon)))
-
     return(p_value)
   }
+
   calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
@@
             z <- gi0_sample(mu, -2, L, s)
-          TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))
-
+            TestStat[r] <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) - (
+              (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) + 
+               (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + 
+              log(mean(z)) - log(L)
+            )
           }
@@
           sd_entropy[sample_sizes == s] <- sd(TestStat)
-
           TestStatistics[[as.character(s)]] <- TestStat
@@
         p_values <- lapply(TestStatistics, function(TestStat) {
-        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
+          apply(
+            data.frame("Test_Statistics" = TestStat),
+            1,
+            function(row) {
               calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
-        })
+            }
+          )
         })
@@
   }
+
   R <- 1000
   mu <- 1
-L_values <- c( 5,  8, 18)
+  L_values <- c(5, 8, 18)
   B <- 100
-lambda<- 0.9
+  lambda <- 0.9
   sample_sizes <- c(25, 49, 81, 121)
   alpha_nominals <- c(0.01, 0.05, 0.1)
-results_power <- calculate_power(R, mu, L_values, B,lambda, sample_sizes, alpha_nominals)
+
+  results_power <- calculate_power(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals)
+
   save(results_power, file = "./Data/results_power.Rdata")
 
+} else {
+
+  message("File type_I_results.Rdata found. Generating results...")
+  load("./Data/results_power.Rdata")
+
+}
 ```
@@
 ```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
 suppressMessages({
@@
     load("./Data/type_I_results.Rdata")
-    type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
-      sum(p_values) / length(p_values)  
-    })
+    type_I_error_rates <- tapply(
+      results$P_Value, 
+      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
+      FUN = function(p_values) sum(p_values) / length(p_values)
+    )
 
@@
         if (all(x %% 1 == 0)) {
-      formatted_numbers <- sprintf("$%d$", x)  # Enteros en formato LaTeX
+          sprintf("$%d$", x)  # Para enteros en formato LaTeX
         } else {
-      formatted_numbers <- ifelse(x < 0, 
+          ifelse(
+            x < 0, 
             sprintf("$%.3f$", x),
-                                  sprintf("$\\phantom{-}%.3f$", x))  # Decimales en LaTeX
-    }
-    return(formatted_numbers)
+            sprintf("$\\phantom{-}%.3f$", x)
+          )
+        }
       } else {
-    return(x)
+        x
       }
@@
   combined_results,
-  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z})$ test statistic.",
+  caption = "Size and Power of the $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z})$ test statistic.",
   format = "latex",
@@
   centering = FALSE,
-  table.envir = "table", position="htb", linesep = "") %>%
+  table.envir = "table", 
+  position="htb", 
+  linesep = ""
+) %>%
   add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
@@
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down",font_size = 7) %>%
+  kable_styling(latex_options = "scale_down", font_size = 7) %>%
   kable_styling(full_width = T)
@@
 print(table_combined_result)
-
 ```
@@
 In this section, we evaluate the proposed test statistic on real SAR data to assess its effectiveness in detecting heterogeneity.
-The test was applied to SAR intensity images from diverse environments, including urban, agricultural, and water regions.
-Specifically, we analyzed three images: the first one from London, United Kingdom; the second from the surroundings of Munich, Germany; and the third from the Dublin Port, Ireland, as shown in Figs.\ \ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
+The test was applied to SAR intensity images from several regions: urban, agricultural, and water.
+In particular, we analyzed three images: the first from London, United Kingdom; the second from the surroundings of Munich, Germany; and the third from  Dublin Port, Ireland, as shown in Figs.\ \ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
 Table\ \ref{tab:table_param} provides detailed acquisition parameters for these images.
@@
 
-colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution [m]} ", "\\textbf{Acquisition Date}")
+colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size (pixels)}",  "$\\bm{L}$", "\\textbf{Resolution [m]} ", "\\textbf{Acquisition Date}")
 
@@
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", font_size = 20) %>% 
+  kable_styling(latex_options = "scale_down", font_size = 21) %>% 
   kable_styling(full_width = TRUE) %>%
-  column_spec(1, width = "3.5cm") %>%
-  column_spec(2, width = "3.5cm") %>%
-  column_spec(3, width = "1cm") %>%
-  column_spec(4, width = "1.5cm") %>%
+  column_spec(1, width = "3.0cm") %>%
+  column_spec(2, width = "3.7cm") %>%
+  column_spec(3, width = "1.5cm") %>%
+  column_spec(4, width = "2.5cm") %>%
   column_spec(5, width = "4cm") %>%
   column_spec(6, width = "1.5cm") %>%
-  column_spec(7, width = "2cm") %>%
+  column_spec(7, width = "3.0cm") %>%
   column_spec(8, width = "3.5cm")
@@
 
-# Conclusions {#sec:conclusion}
-
-This study introduced a new statistical approach based on Rényi entropy to detect heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
-The proposed test statistic is computed non-parametrically and was assessed through a Monte Carlo study. 
-The results indicate that the method effectively controls the probability of a Type I error while maintaining a high detection power, which improves as the sample size increases.
-
-The performance of the Rényi-based test was evaluated by comparing its results with those of a test based on Shannon entropy 
- $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$. 
-This comparison was conducted through $p$-values and binary maps.
-The findings reveal that while both tests successfully detect heterogeneous regions, the Rényi-based test demonstrates superior results due to its flexibility in adjusting the parameter $\lambda$, allowing for a more refined differentiation of textural variations.
-
-These results suggest that Rényi entropy provides a robust alternative to Shannon entropy for heterogeneity detection in SAR images, particularly due to its adaptability.  
-Future research will focus on a more quantitative assessment of both approaches using statistical measures such as Mean Squared Error and other validation metrics to evaluate their accuracy in detecting heterogeneity.
+# Conclusion {#sec:conclusion}
+
+This study presented a new statistical approach based on Rényi entropy for detecting heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
+The statistics of the proposed test was computed nonparametrically and its performance was evaluated by a Monte Carlo study. 
+The results showed that the method effectively controls the probability of type I error while maintaining a high detection performance that improves as the sample size increases.
+
+The performance of the Rényi-based test was evaluated by comparing its results with those of a test based on Shannon entropy.
+This comparison was performed using $p$-values and binary maps. 
+The results showed that while both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, which allowed for finer differentiation of texture variations.
+
+These results suggested that the Rényi entropy was a more accurate alternative to the Shannon entropy for detecting heterogeneity in SAR images, especially due to its adaptability.
+
+Future research will focus on a more quantitative evaluation of both approaches, using statistical measures such as mean square error and other validation metrics to assess their accuracy in detecting heterogeneity.
 
@@
 # Computational Information {-}  
-This article was written using Quarto v.6.4, RStudio v2024.12.0.467, and R v.4.4.2, and is fully reproducible.
+This article was written using Quarto v6.4, RStudio v2024.12.0.467, and R v4.4.2 and is fully reproducible.
+
+Simulations were run on an AMD Ryzen 9 5900X 12-Core Processor (3.70 GHz) with 32 GB RAM.
 

### 2025-02-11 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Updated

@@
 Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be a random sample from the distribution $F(z)$ and denote its order statistics by $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$.
-The density estimator based on $m$-spacing, is defined as:
+The density estimator based on $m$-spacing is defined as:
 $$
@@
 $$
-where $Z_{(i-m)} = Z_{(1)}$ when $i \leq m$ and $Z_{(i+m)} = Z_{(n)}$ if $i \geq n - m$. The coefficient $c_i$ is given by:
+where $Z_{(i-m)} = Z_{(1)}$ when $i \leq m$, and $Z_{(i+m)} = Z_{(n)}$ if $i \geq n - m$. 
+The coefficient $c_i$ is given by:
 $$
@@
 \begin{cases}
-\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\[6pt]
-2, & \text{if } m+1 \leq i \leq n - m, \\[6pt]
+\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\%[6pt]
+2, & \text{if } m+1 \leq i \leq n - m, \\%[6pt]
 \frac{n + m - i}{m}, & \text{if } n - m + 1 \leq i \leq n.
@@
 
-Following previous studies by\ [@Frery2024] and\ [@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply the improved version:
+Following Refs.\ [@Frery2024;@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply the improved version:
 $$

### 2025-03-15 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update paper with corrected comments

@@
     keep-tex: true  
-    conference: true # comment this line to use journal
-    journaltype: conference # comment this line to use journal
+    #conference: true # comment this line to use journal
+    #journaltype: conference # comment this line to use journal
     fig-cap-location: bottom # to crossref figure
-   # link-citations: true
-    #colorlinks: true
-    #linkcolor: blue
-  ieee-html: default
+    link-citations: true
+    colorlinks: true
+    linkcolor: black # equations
+    citecolor: black # cites
+    urlcolor: black
+  #ieee-html: default
 
 author:
-  - id: 
-    name: Janeth Alpala, Abraão D.\ C.\ Nascimento 
+  #- id: 
+  - name: Janeth Alpala, Abraão D.\ C.\ Nascimento 
     affiliations:
@@
         country: PE, Brazil
-        postal-code: 18800
-      - name: Unknown affiliation
-    #orcid: 
+        postal-code: 50670-901
+      #- name: Unknown affiliation
+   # orcid: 
     email: janeth.alpala@ufpe.br, abraao@de.ufpe.br
@@
     #membership: "Member, IEEE"
-    attributes:
-      corresponding: true
+    #attributes:
+    #  corresponding: true
     #photo: 
@@
         country: New Zealand
-        postal-code: 18800
-      - name: Unknown affiliation
+        postal-code: 6140
+      #- name: Unknown affiliation
     #orcid: 
@@
 keywords: [Rényi entropy, Gamma distribution, heterogeneity, SAR,  hypothesis tests]
+
 #funding: 
-funding: 
-  statement: "The `quarto-ieee` template is freely available under the MIT license on github: <https://github.com/dfolio/quarto-ieee>."
+ # statement: "The `quarto-ieee` "
 pageheader:
@@
    - \usepackage[T1]{fontenc}
-   - \usepackage{polski}
+   #- \usepackage{polski}
    - \usepackage{booktabs}
@@
    - \usepackage{mathtools}
-   - \usepackage[utf8]{inputenc}
+  # - \usepackage[utf8]{inputenc}
    - \usepackage{hyperref}
-   - \hypersetup{draft}
+   #- \hypersetup{draft} #Desactiva enlaces y referencias cruzadas
    - \usepackage{float}
@@
    - \usepackage{amsmath}
+   - \usepackage{hyperref}
+   - \hypersetup{
+      colorlinks=true,
+      linkcolor=black,
+      filecolor=black,
+      citecolor=black,
+      urlcolor=black}
 
@@
 bibliography: ../../Common/references.bib
-#
 
@@
 ---
-
 ```{r setup, include=FALSE}
@@
 
-<!-- \newcommand{\reallywidehat}[1]{\widehat{#1}} -->
-
 # Introduction
-
-Synthetic Aperture Radar (SAR) technology has become essential for a wide range of applications\ [@Yu2023;@Akbarizadeh2012;@Mondini2021].
+[S]{.IEEEPARstart}[ynthetic]{}
+ Aperture Radar (SAR) technology has become essential for a wide range of applications\ [@Yu2023;@Akbarizadeh2012;@Mondini2021].
 It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions to facilitate global Earth monitoring\ [@Zeng2020].
@@
 
-The $\mathcal{G}^0$ distribution has been shown to be an effective model for SAR intensity data, as it captures different levels of roughness.
+The $\mathcal{G}^0_I$ distribution has been shown to be an effective law for SAR intensity data, as it captures different levels of roughness.
 A special case is the Gamma distribution, which arises when speckle is fully developed, indicating homogeneous regions.
-Although these models offer flexibility in describing SAR intensities, selecting the appropriate model can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
+Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
 These challenges complicate model selection and highlight the need to explore alternative statistical approaches.
@@
 Entropy measures have gained attention as valuable statistical tools for analyzing SAR data, with applications in edge detection\ [@Nascimento2014], segmentation\ [@Nobre2016], classification\ [@Cassetti2022], and noise reduction\ [@Chan2022].
-Traditionally, Shannon entropy\ [@Shannon1948] has been widely used to quantify uncertainty and disorder in data. However, this study explores an alternative information measure: Rényi entropy. 
-As a generalization of Shannon entropy, it offers additional insights for identifying heterogeneity, making it a promising tool for enhancing SAR image analysis.
+Traditionally, Shannon entropy\ [@Shannon1948] has been widely used to quantify uncertainty and disorder in data.
+However, this study explores an alternative information measure: Rényi entropy—a generalization of Shannon’s formulation.
+This more flexible approach provides additional insights for identifying heterogeneity, making it a promising tool for enhancing SAR image analysis.
 
@@
 
-The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997].
+The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997].
 These distributions are characterized by the following probability density functions (pdfs):
@@
 For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$, with $\lambda > 0$ and $\lambda \neq 1$, is defined as:
-\begin{align}
+\begin{equation}
 \label{E:entropy2}
 H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
-\end{align}
+\end{equation}
 Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions:
@@
 \end{multline}
+The derivation of this result is given in the Appendix.
+
 @fig-plot presents the Rényi entropy of $\mathcal{G}^0_I$ as a function of $\mu$ for different $\alpha$ values.
@@
 
-```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}
+```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}
 
@@
 
-For $\lambda \to 1$, this expression converges to the Shannon entropy. As we will see later, this property can lead to improved performance for heterogeneity detection compared to Shannon entropy.
-
-## Estimation of Rényi Entropy
-
-Nonparametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994;@Wieczorkowski1999; @AlOmari2019].
+## Nonparametric Estimation of Rényi Entropy
+
+Nonparametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999; @AlOmari2019].
 Recently, Al-Labadi et al.\ [@AlLabadi2024] proposed a nonparametric estimator for Rényi entropy following this approach.
 
-<!-- Let $\bm{Z} = (Z_1, Z_2, \dots, Z_n)$ be a random sample from $F(z)$ with order statistics $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$. The $m$-spacing density estimator is defined as: -->
-Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be a random sample from the distribution $F(z)$ and denote its order statistics by $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$.
-The density estimator based on $m$-spacing is defined as:
+Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed random sample of size $n$ from a distribution $F$, and let $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$ denote its order statistics.
+The $m$-spacing density estimator is defined as:
 $$
@@
 
-## Optimal $\lambda$ for small sample size
-
-We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator, specifically for a sample size of $n=49$.
+## On $\lambda$ optimality for a sample size
+
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator for a sample size $n=49$.
 To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
@@
 Based on the results, we find that the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
-This choice is consistent with other values of $L > 1$.
+This choice is the same for $L > 1$.
 However, for $L = 1$, the optimal $\lambda$ tends to be higher (e.g., $\lambda = 3$) to achieve good results.
 @fig-plotf illustrates the case for $L = 5$.
-
-```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=8, fig.height=6}
+```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
 
@@
 
-Following Refs.\ [@Frery2024;@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ using the bootstrap technique and apply the improved version:
+Following Refs.\ [@Frery2024;@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} using the bootstrap technique to reduce its bias and apply the improved version, denoted as $\widetilde{H}_{\lambda}$:
 $$
-\widetilde{H}_{\lambda} = 2\widehat{\theta}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}_b(\bm{Z}^{(b)}),
+\widetilde{H}_{\lambda} = 2\widehat{H}_{\lambda}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_{\lambda}(\bm{Z}^{(b)}),
 $$
-where $B$ is the number of new samples generated through resampling with replacement.
-
-A Monte Carlo study with $1000$ samples from $\Gamma_{\text{SAR}}$ ($\mu = 1$, $L=5$, $\lambda = 0.9$) confirms that this approach, using $B = 200$ replications, reduces bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
+where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ is the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.
+
+A Monte Carlo study with $1,000$ samples from $\Gamma_{\text{SAR}}$ ($\mu = 1$, $L=5$, $\lambda = 0.9$), using $B = 200$ replications, confirms that the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$  outperforms the original $\widehat{H}_{\lambda}$ by reducing both bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
 
@@
 
-```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimator for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=1$ and $L=5$.", fig.width=8, fig.height=7}
+```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}
 
@@
 ```
-
-## Hypothesis Test Rationale
-
-Our approach relies on constructing a test statistic that compares a non-parametric estimate of the Rényi entropy to the theoretical value of the Rényi entropy under the null hypothesis (i.e., a fully developed speckle scenario modeled by $\Gamma_{\text{SAR}}$).
-We aim to test the following hypotheses: 
-$$
-\begin{cases}\mathcal{H}_0: \widehat{H}^*= H_{\lambda}(\Gamma_{\text{SAR}})\\ 
-  \mathcal{H}_1:\widehat{H}^*= H_{\lambda}(\mathcal{G}^0_I).\end{cases}
-$$
-
-If the difference between the estimated and theoretical entropy values is statistically significant, we reject the null hypothesis and conclude that the data do not follow the Gamma model, indicating the presence of heterogeneity.
+For subsequent simulations we use the $\widetilde{H}_{\lambda}$ estimator.
+
+## Hypothesis Testing
+
+We test whether the observed data come from a homogeneous ($\Gamma_{\text{SAR}}$) or a heterogeneous ($\mathcal{G}^0_I$) region, as follows:
+\begin{equation}\label{eq:hypothesis_test}
+\begin{cases}
+\mathcal{H}_0: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\Gamma_{\text{SAR}}), & \text{(Homogeneous region)} \\[6pt]
+\mathcal{H}_1: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\mathcal{G}^0_I), & \text{(Heterogeneous region)}
+\end{cases}
+\end{equation}
+
+Under $\mathcal{H}_0$, the expected value of the entropy estimator should match the theoretical $H_{\lambda}(\Gamma_{\text{SAR}})$.
+If the estimated entropy significantly deviates from its expected value, we reject $\mathcal{H}_0$, indicating the presence of heterogeneity.
+
+Since homogeneity corresponds to $\alpha \to -\infty$ in the $\mathcal{G}^0_I$ model, classical inference methods are inapplicable.
+Instead, we propose a test statistic based on the Rényi entropy estimator, comparing it with its theoretical expectation under $\mathcal{H}_0$ to distinguish between homogeneous and heterogeneous areas.
 
@@
 
-Assume we have an estimator $\widehat{H}_{\lambda}$ for the Rényi entropy of an arbitrary model.
-In the case of the $\Gamma_{\text{SAR}}$ model, this estimator is expected to be close to the theoretical expression given in Equation \eqref{eq-HGammaSAR}.
+Assume we have an estimator $\widetilde{H}_{\lambda}$ for the Rényi entropy of an arbitrary model.
+For testing \eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation \eqref{eq-HGammaSAR}.
 Since $L\geq1$ is known, we define the test statistic as follows:
@@
 \label{eq-test}
-S(\bm{Z}; L) = \widehat{H} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
+S(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
 \bigl[-\lambda\,\ln\Gamma(L) \\  
@@
 \end{multline}
+where $\ln \widehat{\mu}={\textstyle\frac{1}{n}\sum_{i=1}^n Z_{i}}$ is the natural logarithm of the sample mean.
+
 When the null hypothesis holds, this test statistic is expected to be close to zero.
-
-For illustrative purposes, @fig-density_entropyR provide the empirical density of $S(\bm{Z}; L)$  for the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
-For subsequent simulations we use the $\widetilde{H}_{\lambda}$ estimator.
-
+For illustrative purposes, @fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10,000$ simulations of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
 ```{r Simulated_densityR, echo=FALSE, message=FALSE}
@@
 
-```{r fig-density_entropyR, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ test under the null hypothesis.", fig.width=9, fig.height=5.0}
+```{r fig-density_entropyR, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
 
@@
 ```
-
-Under $\mathcal{H}_0$, the distribution of the test statistic $S$ is asymptotically normal.
-Thus, due to the asymptotic properties of the entropy estimator, and assuming the sample is sufficiently large, the statistic follows a standard normal distribution.
-
-Therefore, the $p$-value is computed as $2\Phi(-\mid \varepsilon \mid)$,
-where $\Phi$ is the standard Gaussian cumulative distribution function, and $\varepsilon$ is given by:  
-$$
-\varepsilon = \frac{\widetilde{H}_i - \widehat{H}_i(\Gamma_{\text{SAR}})}{\widehat{\sigma}_{i}}.
-$$
-An important aspect of hypothesis testing is ensuring that the test maintains the expected type I error rate (size) while achieving high power (sensitivity to departures from $\mathcal{H}_0$).
-To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels  $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution) and varying sample sizes, values of $L$, and $\mu=1$.
+Under the asymptotic properties of the entropy estimator\ [@vasicek1976test], for sufficiently large samples, $S(\bm{Z}; L)$ follows an asymptotic normal distribution:
+\begin{equation*}
+S(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2})\,.
+\end{equation*}
+We define the standardized test statistic:
+\begin{equation*}
+\varepsilon = \frac{S(\bm{Z}; L) - \hat{\mu}_S}{\hat{\sigma}_S},
+\end{equation*}
+where $\hat{\mu}_S = \mathbb{E}[S(\bm{Z}; L)]$ and $\hat{\sigma}_S = \sqrt{\text{Var}[S(\bm{Z}; L)]}$.
+By the central limit theorem, under the null hypothesis, $\varepsilon$ asymptotically follows a standard normal distribution:
+\begin{equation*}
+\varepsilon \overset{d}{\longrightarrow} \mathcal{N}(0,1)\,,
+\end{equation*}
+where $d$ represents convergence in distribution.
+@fig-density_entropyR presents the behavior of the empirical distribution of the standardized test statistic.
+Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
+where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
+```{r Simulated_densityR_standardized0, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 20000
+mu <- 1
+B <- 100
+
+lambda <- 0.9
+
+sample.size <- c(49, 81, 121)
+L_values <- c(18)
+
+all_summary_stats <- list()
+all_TestStatistics <- list()
+
+# 
+for (L in L_values) {
+
+  file_name <- paste0("./Data/resultsRE0_", L, ".Rdata")
+
+  if (file.exists(file_name)) {
+    load(file_name)
+    message(paste("Loaded existing data for L =", L))
+  } else {
+
+    TestStatistics1 <- list()  
+    summary_stats <- data.frame(
+      LValue = character(),
+      SampleSize = numeric(),
+      Mean = numeric(),
+      SD = numeric()
+    )
+
+    for (s in sample.size) {
+      TestStat1 <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat1[r] <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) - ((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
+                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
+      }
+
+      mean_val <- mean(TestStat1)
+      sd_val <- sd(TestStat1)
+
+      TestStat_standardized <- (TestStat1 -  mean_val) / sd_val
+
+      TestStatistics1[[as.character(s)]] <- data.frame(
+        "SampleSize" = rep(s, R), 
+        "Test_Statistics" = TestStat_standardized
+      )
+
+      summary_stats <- rbind(summary_stats, data.frame(
+        LValue = as.character(L),
+        SampleSize = s,
+        Mean = 0,   # 
+        SD = 1      # 
+      )) 
+    }
+
+    all_TestStatistics[[as.character(L)]] <- TestStatistics1
+    all_summary_stats[[as.character(L)]] <- summary_stats
+
+    save(all_TestStatistics, all_summary_stats, file = file_name)
+    message(paste("Saved new results for L =", L))
+  }
+}
+```
+
+```{r fig-density_entropyR_standardized0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
+
+x_limits <- c(-4, 4)  # 
+x_breaks <- seq(-4, 4, by = 1)  # Ticks 
+y_limits <- c(0, 0.5)  #
+
+selected_L_values <- c( 18)
+
+all_plots <- list()
+
+for (L in selected_L_values) {
+  load(paste0("./Data/resultsRE0_", L, ".Rdata"))
+
+  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
+  combined_data$L <- L
+
+  combined_data$CurveOrder <- factor(combined_data$SampleSize, levels = rev(sample.size))
+  combined_data$LegendOrder <- factor(combined_data$SampleSize, levels = sample.size)
+
+  p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+    geom_line(stat = "density", linewidth = 1.3, alpha = 0.7) +
+    scale_color_viridis(discrete = TRUE, option = "G", direction = -1, begin = 0.1, end = 0.7, name = "Sample Size") +
+    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+    scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
+    scale_y_continuous(limits = y_limits) +  
+    labs(#x = expression("Standardized Test Statistic" ~ epsilon),
+        x = expression("Standardized Test Statistic"), 
+        y = "Density"
+    ) +
+    ggtitle(bquote(italic(L) == .(L))) +
+    theme(plot.title = element_text(hjust = 0.5, size = 10, margin = margin(b = 2)),
+          axis.text = element_text(size = 10),     
+          axis.title = element_text(size = 10),    
+          legend.text = element_text(size = 10),   
+          legend.title = element_text(size = 10)   
+    )
+
+  all_plots[[as.character(L)]] <- p
+}
+
+combined_plot <- wrap_plots(all_plots, ncol = 1, nrow = 1) +
+  plot_layout(guides = "collect")
+
+print(combined_plot)
+
+```
+In general, hypothesis tests aim to achieve a controlled type I error rate (size) and high test power (sensitivity to departures from $\mathcal{H}_0$).
+To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels  $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
 The observed type I error rates aligned with the nominal values, confirming the test validity.
 
-Additionally, we examined the power under the alternative hypothesis ($\mathcal{G}^0_I$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
-As expected, power improves as the sample size and number of looks increase the effectiveness demonstrating of the test. The results are shown in Table \ref{tab:table_size_power}.
-
+Further, we examined the power under the alternative hypothesis ($\mathcal{G}^0_I$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
+As expected, power improves as the sample size and number of looks increase, demonstrating the test effectiveness. The results are shown in Table \ref{tab:table_size_power}.
 ```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
@@
       centering = FALSE,
-      table.envir = "table", position = "H") %>%
+      table.envir = "table", position = "hbt") %>%
   row_spec(0, align = "c") %>%
@@
 
-For conducting  the performance of our methodology, we applied the test statistic $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ based on Rényi entropy and the test $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ based on Shannon entropy described in\ [@Frery2024], using a local sliding window of size $7\times7$.
+To evaluate the performance of our proposal, we applied the test statistics $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ and  $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, based on Shannon entropy as described in\ [@Frery2024], using a local sliding window of size $7\times7$.
 The resulting $p$-value maps are presented in Figs.\ \ref{fig:london}(b), \ref{fig:london}(d), \ref{fig:munich}(b), \ref{fig:munich}(d), \ref{fig:dublin}(b), and \ref{fig:dublin}(d). 
@@
 
-In order to better illustrate the decision-making process of both tests, binary maps at a significance level of $0.05$ are shown in Figs.\ \ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e), respectively.
+In order to better illustrate the decision-making process of both tests, binary maps at a significance level of $0.05$ are shown in Figs.\ \ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e).
 
@@
     \centering
-    \begin{subfigure}{0.17\textwidth}
+    \begin{subfigure}{0.16\textwidth}
         \includegraphics[width=\linewidth]{./Figures/dublin_1100_hh.png}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth}
+    \begin{subfigure}{0.22\textwidth}
         \includegraphics[width=\linewidth]{./Figures/AO_w7_L16_b100.png}
@@
 
-# Acknowledgment {-}
-
-This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) – Finance Code 001  and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.
-
-# Computational Information {-}  
-This article was written using Quarto v6.4, RStudio v2024.12.0.467, and R v4.4.2 and is fully reproducible.
-
-Simulations were run on an AMD Ryzen 9 5900X 12-Core Processor (3.70 GHz) with 32 GB RAM.
-
-The Code and data used in this study are available at: <https://github.com/rjaneth/renyi-entropy-sar>
+<!-- # Acknowledgment {-} -->
+
+<!-- This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil. -->
+
+<!-- # Computational Information {-}   -->
+<!-- This article was written using Quarto v6.4, RStudio v2024.12.0.467, and R v4.4.2 and is fully reproducible.  -->
+
+<!-- Code is available at: <https://github.com/rjaneth/renyi-entropy>   -->
+
+[]{.appendix options="Derivation of the Rényi Entropy of $\mathcal{G}^0_I$"}
+
+Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$, defined in\ [@Frery2024],  we compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$. Using the pdf  
+\begin{equation*}
+f_{\mathcal{G}^0_I}(z) = C \frac{z^{L-1}}{(\gamma + Lz)^{L-\alpha}},  
+\quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}, \label{eq:pdf_G0I}
+\end{equation*}
+and setting $t = Lz/\gamma$, we obtain  
+\begin{equation*}
+I = C^\lambda \frac{\gamma^{1-\lambda+\lambda\alpha}}{L^{\lambda L + 1 - \lambda}}  
+\int_0^\infty \frac{t^{\lambda(L-1)}}{(1+t)^{\lambda(L-\alpha)}} dt.
+\end{equation*}
+Applying the Beta function identity, $B(a,b) = \int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt$ with $a = \lambda(L-1) + 1$, $b = \lambda(-\alpha+1) - 1$, we get  
+\begin{equation*}
+I= \gamma^{\,1 - \lambda}\,
+   L^{\,\lambda - 1}
+   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
+   \,B(a,b).
+\end{equation*}
+Using the Rényi entropy definition in \eqref{E:entropy2}: $H_\lambda(Z) = \frac{1}{1-\lambda} \ln I$,
+and substituting $\gamma = -\mu(\alpha + 1)$, we obtain the final expression for $\mathcal{G}^0_I(\mu, \alpha, L)$ in \eqref{eq-HGI0}.
+
+Code is available at: <https://github.com/rjaneth/renyi-entropy>
 

### 2025-03-15 Text/Reports/report-Renyi/Appendix3.Rmd
Update paper with corrected comments

---
link-citations: true
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    number_sections: true
    toc_depth: 2
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
bibliography: ../../Common/references.bib
header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   #- \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{amssymb}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=1pt, 
        belowskip=1pt,
        singlelinecheck=off,
        justification=centering}   
   #- \usepackage{placeins}
   - \usepackage{amsthm}
   - \newtheorem{definition}{Definition}
   - \newtheorem{lemma}{Lemma}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{example}{Example}
   - \usepackage{appendix}

biblio-style: apsr
title: "Rényi Entropy-Based Heterogeneity Detection in SAR Data"
thanks: ""
author:
- name: ""
  affiliation:

date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: libertine
fontsize: 11pt
# spacing: double
endnote: no
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=FALSE)
# knitr::opts_chunk$set(echo = FALSE,cache=TRUE,
#                       message=FALSE, warning=FALSE,
#                       fig.path='figs/',
#                       cache.path = '_cache/',
#                       fig.process = function(x) {
#                       x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
#                       if (file.rename(x, x2)) x2 else x
#                       })

library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
#library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

theme_set(theme_minimal() +
            theme(text=element_text(family="serif"),
                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
)

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# 
# source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
# source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
# source("../../../Code/R/MainFunctions/entropy_renyi_gamma_sar.R")
# source("../../../Code/R/MainFunctions/entropy_gI0.R")
# source("../../../Code/R/MainFunctions/gi0_sample.R")
# 
# source("../../../Code/R/MainFunctions/van_es_estimator.R")
# source("../../../Code/R/MainFunctions/correa_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
# source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
# source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
# source("../../../Code/R/MainFunctions/vasicek_estimator.R")
# source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
# source("../../../Code/R/MainFunctions/renyi_entropy_estimator_v1.R")
# 
# source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
# source("../../../Code/R/MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
# #The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
# source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
# source("../../../Code/R/Programs/functions_sample_bias_mse_1.R")
# source("../../../Code/R/Programs/read_ENVI_images.R")

```

\newcommand{\bias}{\operatorname{Bias}}
\newcommand{\widebar}[1]{\overline{#1}}

\appendix
# APPENDIX

# Derivation of the Rényi Entropy for the $\Gamma_{\text{SAR}}(L, \mu)$ Distribution.

The Rényi entropy of order $\lambda$ for a continuous random variable $Z$ with density $f_Z(z)$ is given by
\begin{align}
H_\lambda(Z) 
&= \frac{1}{\,1 - \lambda\,} \,\ln \Bigl( \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz \Bigr),
\quad \lambda > 0, \;\lambda \neq 1.
\label{eq:RenyiDefinition}
\end{align}

Let $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ with pdf
\begin{align*}
f_{\Gamma_{\text{SAR}}}(z; L, \mu)
&= \frac{L^L}{\Gamma(L)\,\mu^L}\,z^{\,L - 1} 
  \exp\Bigl(-\tfrac{L z}{\mu}\Bigr)\mathbbm 1_{\mathbbm R_+}(z).
\end{align*}
Define
\begin{align*}
I 
&= \int_{0}^{\infty}\!\bigl[f_{\Gamma_{\text{SAR}}}(z; L,\mu)\bigr]^\lambda \,dz 
 = \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
   \int_{0}^{\infty} 
   z^{\,\lambda\,(L-1)} \exp\Bigl(-\tfrac{\lambda\,L}{\mu}\,z\Bigr)\,dz.
\end{align*}
Using the Gamma integral 
$\displaystyle
  \int_{0}^{\infty} x^{p-1} e^{-qx}\,dx 
   = \frac{\Gamma(p)}{q^p},$
with $p = \lambda L - \lambda + 1$ and $q = \tfrac{\lambda L}{\mu}$, it follows that
\begin{align*}
I 
&= \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
   \frac{\Gamma(\lambda L - \lambda + 1)}
        {\Bigl(\tfrac{\lambda\,L}{\mu}\Bigr)^{\lambda L - \lambda + 1}}.
\end{align*}
Taking the natural logarithm,
\begin{align}
\ln I 
&= \lambda\Bigl(L \ln L - L \ln \mu - \ln \Gamma(L)\Bigr)
   \;+\; \ln\Gamma\!\bigl(\lambda L - \lambda + 1\bigr)
   \;-\; \bigl(\lambda L - \lambda + 1\bigr)\,\Bigl(\ln(\lambda L) - \ln\mu\Bigr).
\label{eq:lnI}
\end{align}
By expanding \eqref{eq:lnI} and collecting terms in $\ln L$ and $\ln \mu$, 
\begin{align}
\ln I 
&= (1 - \lambda)\bigl(\ln \mu - \ln L\bigr)
   \;-\;\lambda\,\ln \Gamma(L)
   \;+\;\ln\Gamma\!\bigl(\lambda(L-1)+1\bigr)
   \;-\;\bigl(\lambda(L-1)+1\bigr)\,\ln \lambda.
\label{eq:lnIsimplified}
\end{align}
Substituting \eqref{eq:lnIsimplified} into \eqref{eq:RenyiDefinition} and simplifying,
\begin{multline}
H_\lambda\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr) 
= \ln \mu - \ln L 
  + \frac{1}{\,1-\lambda\,}
  \Bigl[
    -\lambda\,\ln\Gamma(L)
    + \ln\Gamma\!\bigl(\lambda\,(L-1)+1\bigr)
    - \bigl(\lambda\,(L-1)+1\bigr)\,\ln\lambda
  \Bigr].
\label{eq:RenyiFinal}
\end{multline}
This completes the derivation.

# Derivation of the Rényi Entropy for the \texorpdfstring{$\mathcal{G}^0_I$}{G0I} Distribution

\medskip

\noindent
Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ with pdf
\begin{align*}
f_{\mathcal{G}^0_I}(z; \alpha, \gamma, L) 
&= \frac{L^L\,\Gamma(L-\alpha)}{\gamma^{\alpha}\,\Gamma(-\alpha)\,\Gamma(L)}
   \,\frac{z^{\,L-1}}{\bigl(\gamma + L\,z\bigr)^{\,L-\alpha}}\mathbbm 1_{\mathbbm R_+}(z). \label{E:gamma1}
\end{align*}
In particular, this parameterization is consistent with $\gamma = -\mu(\alpha + 1)$, 
so the final expression can be rewritten in terms of $\mu$.

\medskip

\noindent
Define
\begin{align*}
I 
&= \int_{0}^{\infty} \bigl[f_{\mathcal{G}^0_I}(z; \alpha, \gamma, L)\bigr]^\lambda \,dz
= C^\lambda 
  \int_{0}^{\infty} 
    \frac{z^{\,\lambda(L - 1)}}
         {\bigl(\gamma + L\,z\bigr)^{\,\lambda(L - \alpha)}} 
  \,dz,
\end{align*}
where
\[
C 
= \frac{L^L\,\Gamma(L - \alpha)}{\gamma^\alpha\,\Gamma(-\alpha)\,\Gamma(L)}.
\]
Using the change of variables 
$t = \tfrac{Lz}{\gamma}$, $z = \tfrac{\gamma\,t}{L}$, and $dz = \tfrac{\gamma}{L}\,dt$, 
we obtain
\begin{align*}
I 
&= C^\lambda
   \int_{0}^{\infty}
     \Bigl(\tfrac{\gamma\,t}{L}\Bigr)^{\,\lambda(L - 1)}
     \Bigl(\gamma + L\,\tfrac{\gamma\,t}{L}\Bigr)^{-\lambda(L - \alpha)}
     \,\tfrac{\gamma}{L}\,dt
\\
&= C^\lambda 
   \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
   \int_{0}^{\infty}
     \frac{t^{\,\lambda(L - 1)}}
          {(1 + t)^{\,\lambda(L - \alpha)}}
   \,dt.
\end{align*}
By the Beta-function identity
\[
\int_{0}^{\infty} \frac{t^{\,a - 1}}{(1 + t)^{\,a + b}} \, dt 
= B(a,b),
\]
where 
\[
a = \lambda(L - 1) + 1,
\quad
b = \lambda(-\alpha + 1) - 1,
\]
it follows that
\begin{align*}
I 
&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
   \,B(a,b).
\end{align*}
Next, we note that 
$\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}$ 
and 
$L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}.$ 
Since
\[
C^\lambda 
= \biggl(\tfrac{L^L}{\gamma^\alpha\,\Gamma(-\alpha)\,\Gamma(L)}\,\Gamma(L - \alpha)\biggr)^{\!\lambda}
= L^{\lambda L}\,\gamma^{-\alpha \lambda}
  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,
\]
we obtain
\begin{align*}
I
&= \gamma^{\,1 - \lambda}\,
   L^{\,\lambda - 1}
   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
   \,B(a,b).
\end{align*}

\medskip

\noindent
By \eqref{eq:RenyiDefinition}, the Rényi entropy, is given by:
\begin{align*}
H_\lambda(Z)
&= \frac{1}{\,1 - \lambda\,} \,\ln I.
\end{align*}
Hence,
\begin{align*}
H_\lambda(Z) 
&= \frac{1}{\,1 - \lambda\,}
  \,\ln\!\Bigl[
    \gamma^{\,1 - \lambda}\,
    L^{\,\lambda - 1}\,
    \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
    \,B(a,b)
  \Bigr].
\end{align*}
Thus, for $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$,
\begin{align*}
H_\lambda\bigl(\mathcal{G}^0_I(\alpha, \gamma, L)\bigr)
&= \ln\Bigl(\tfrac{\gamma}{\,L}\Bigr)
  + \frac{1}{\,1 - \lambda\,}
    \Bigl[
      \lambda\bigl(\ln \Gamma(L - \alpha) 
            - \ln \Gamma(-\alpha) 
            - \ln \Gamma(L)\bigr)
      + \ln B(a,b)
    \Bigr].
\end{align*}
Using the property 
\[
\ln B(a,b) 
= \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b),
\]
where $a + b = \lambda(L - \alpha)$, we have
\begin{align}
H_\lambda\bigl(\mathcal{G}^0_I( \alpha,\gamma, L)\bigr)
&= \ln\Bigl(\tfrac{\gamma}{L}\Bigr)
 + \frac{1}{\,1 - \lambda\,}
   \Bigl[
     \lambda\bigl(\ln \Gamma(L - \alpha) 
            - \ln \Gamma(-\alpha) 
            - \ln \Gamma(L)\bigr)
     + \ln \Gamma(a)
     + \ln \Gamma(b)
     - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
   \Bigr].
\label{eq:GI0RenyiInGamma}
\end{align}
Finally, noting that 
\[
\mu = -\tfrac{\gamma}{\alpha + 1}
\quad\Longrightarrow\quad
\gamma = -\mu(\alpha + 1),
\]
and substituting $\gamma$ into \eqref{eq:GI0RenyiInGamma}, we obtain
\begin{multline}
H_\lambda\bigl(\mathcal{G}^0_I( \alpha,\mu, L)\bigr)
= \ln \mu  -  \ln L + \ln(- 1-\alpha)
+ \frac{1}{\,1 - \lambda\,}
  \Bigl[
    \lambda\Bigl(\ln \Gamma(L - \alpha) 
        - \ln \Gamma(-\alpha) 
        - \ln \Gamma(L)\Bigr)\\
    + \ln \Gamma\bigl(\lambda(L - 1) + 1\bigr)
    + \ln \Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)
    - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
  \Bigr],
\label{eq:RenyiGI0Final}
\end{multline}
which completes the derivation.

# Relation to the \texorpdfstring{$\Gamma_{\mathrm{SAR}}$}{Gamma SAR} Distribution

The Rényi entropy of the 
$\mathcal{G}^0_I(\alpha,\mu,L)$ distribution can be expressed 
in terms of the Rényi entropy of the 
$\Gamma_{\mathrm{SAR}}(L,\mu)$ distribution, plus additional terms 
involving $\alpha$ and the Gamma function. 
Specifically, we can write:
\begin{multline}
H_\lambda\bigl(\mathcal{G}^0_I(\alpha,\mu,L)\bigr)
= 
\underbrace{\Bigl[
  \ln\mu \;-\;\ln L 
  \;+\; \frac{1}{\,1-\lambda\,}\Bigl(
    -\lambda \,\ln\Gamma(L) 
    \;+\;\ln\Gamma\bigl(\lambda(L-1)+1\bigr)
    \;-\;\bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
  \Bigr)
\Bigr]}_{\displaystyle H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)}
\\[6pt]
+~\ln\bigl(-1-\alpha\bigr)
+~\frac{1}{\,1-\lambda\,} 
 \Bigl[
   \lambda\bigl(\ln\Gamma(L-\alpha) - \ln\Gamma(-\alpha)\bigr)
   \;+\;\ln\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)
   \;-\;\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
   \;+\;\bigl(\lambda(L-1)+1\bigr)\,\ln(\lambda)
 \Bigr].
\label{eq:GI0_in_terms_of_GammaSAR}
\end{multline}
From \eqref{eq:GI0_in_terms_of_GammaSAR}, the bracketed expression 
on the first line matches 
$H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)$,
while the remaining terms account for the parameter $\alpha$ through additional Gamma functions 
and logarithmic corrections. This decomposition highlights the 
close relationship between the Rényi entropies of the 
$\mathcal{G}^0_I$ and $\Gamma_{\mathrm{SAR}}$ distributions.

# Limit Behavior of \texorpdfstring{$H_\lambda(\mathcal{G}^0_I)$}{Hl(GI0)} as \texorpdfstring{$\alpha \to -\infty$}{alpha->-∞}

\begin{proof}
We want to show that 
\[
\lim_{\alpha \to -\infty}
H_\lambda\bigl(\mathcal{G}^0_I\bigr)(\mu, \alpha, L)
=
H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu, L).
\]

We can express \eqref{eq:GI0_in_terms_of_GammaSAR} as follows:
\begin{align*}
H_\lambda\bigl(\mathcal{G}^0_I\bigr)(\mu,\alpha,L)
&=
H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L)
\;+\;
\ln\!\bigl(-1-\alpha\bigr)
\\
&\quad
+ \frac{1}{1-\lambda}
\ln \Biggl[
  \frac{
    \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)\,\lambda^{\lambda(L-1)+1}
  }{
    \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
  }
\Biggr].
\end{align*}
Set
\begin{align*}
\Delta(\alpha)
&=
H_\lambda\bigl(\mathcal{G}^0_I\bigr)(\mu,\alpha,L)
-
H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L).
\end{align*}
Then 
\begin{align}
\Delta(\alpha)
=
\ln(-1-\alpha)
+
\frac{1}{1-\lambda}
\ln \biggl[
  \frac{
    \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)\,\lambda^{\lambda(L-1)+1}
  }{
    \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
  }
\biggr].
\label{eq:remain}
\end{align}

As \(\alpha \to -\infty\), we have \(-1-\alpha \approx |\alpha|\), so 
\[
\ln(-1-\alpha) 
\sim 
\ln|\alpha|.
\]
Note that for large \(|\alpha|\), we can the asymptotic relation 
\(
\Gamma(x+a)/\Gamma(x+b) 
\sim 
x^{\,a-b}
\).
Specifically:
\[
\Gamma(L-\alpha)/\Gamma(-\alpha) \;\sim\; |\alpha|^L,
\quad
\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)/\Gamma\bigl(\lambda(L-\alpha)\bigr)
\;\sim\; 
\bigl(\lambda|\alpha|\bigr)^{\,(\lambda-1)-\lambda L}.
\]
Thus, inside the logarithm in \eqref{eq:remain},
\[
\frac{
  \Gamma(L-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(-\alpha+1)-1\bigr)
}{
  \Gamma(-\alpha)^{\lambda}\,\Gamma\bigl(\lambda(L-\alpha)\bigr)
}
\;\sim\;
|\alpha|^{\lambda L}
\times
|\alpha|^{(\lambda-1)-\lambda L}
=
|\alpha|^{\,\lambda-1}.
\]
Since \(\lambda^{\lambda(L-1)+1}\)  does not depend on \(\alpha\), multiplying by this constant factor does not alter the asymptotic behavior in \(\alpha\). Therefore,
\[
\frac{1}{1-\lambda}\,
\ln\!\Bigl[\dots\Bigr]
\;\sim\;
\frac{1}{1-\lambda}\;\ln\!\bigl(|\alpha|^{\,\lambda-1}\bigr)
=
\frac{\lambda-1}{1-\lambda}\,\ln|\alpha|
=
-\ln|\alpha|.
\]
Hence
\[
\Delta(\alpha)
\;\sim\;
\ln|\alpha|
-
\ln|\alpha|
=
0
\quad
\text{as}\, \alpha\to -\infty.
\]
This shows 
\(\Delta(\alpha)\to 0\), 
and consequently
\[
\lim_{\alpha \to -\infty}
H_\lambda\bigl(\mathcal{G}^0_I\bigr)(\mu,\alpha,L)
=
H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)(\mu,L).
\]
\end{proof}

\section{Bias Reduction via Bootstrap for Entropy Estimation}

The non-parametric Rényi entropy estimator \(\widehat{H}_\lambda(\bm{Z})\), as defined in \eqref{eq:est_R}, exhibits bias, meaning its expectation does not coincide with the true entropy \(H_\lambda\):
\begin{equation}
\operatorname{Bias}(\widehat{H}_\lambda) = {E}[\widehat{H}_\lambda] - H_\lambda \neq 0.
\end{equation}

To reduce this bias, we employ a bootstrap correction approach. Let \(\bm{Z} = (Z_1, Z_2, \dots, Z_n)\) be a sample of size \(n\), and let \(\bm{Z}^{(b)} = (Z_1^{(b)}, Z_2^{(b)}, \dots, Z_n^{(b)})\) for \(b = 1, 2, \dots, B\) be a bootstrap sample obtained by resampling with replacement from \(\bm{Z}\). For each bootstrap sample, we compute the entropy estimator \(\widehat{H}_\lambda(\bm{Z}^{(b)})\). Since bootstrap resampling mimics the sampling variability, we estimate the bias as:
\begin{equation}
\widehat{\operatorname{Bias}} = \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_\lambda(\bm{Z}^{(b)}) - \widehat{H}_\lambda(\bm{Z}).
\end{equation}

A bias-corrected estimator can then be defined as:
\begin{align}
\widetilde{H}_\lambda &= \widehat{H}_\lambda - \widehat{\operatorname{Bias}},\\
&= 2\widehat{H}_\lambda(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_\lambda(\bm{Z}^{(b)}).
\end{align}
This estimator is motivated by the well-known bias correction principle:
\begin{equation}
\text{Bias-corrected estimate} = \text{Original estimate} - \text{Bias estimate}.
\end{equation}
The expectation of \(\widetilde{H}_\lambda\) is given by:
\begin{align}
\mathbb{E}[\widetilde{H}_\lambda] &= \mathbb{E}[2\widehat{H}_\lambda(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_\lambda(\bm{Z}^{(b)})]\\
&= 2\mathbb{E}[\widehat{H}_\lambda(\bm{Z})] - \mathbb{E}[\widehat{H}_\lambda(\bm{Z})]\\
&= \mathbb{E}[\widehat{H}_\lambda(\bm{Z})] + \big( H_\lambda - \mathbb{E}[\widehat{H}_\lambda(\bm{Z})] \big)\\
&= H_\lambda.
\end{align}
Thus, \(\widetilde{H}_\lambda\) is an **approximately unbiased** estimator of \(H_\lambda\). The effectiveness of this correction depends on the choice of \(B\) and the underlying sample distribution, but it systematically reduces bias in entropy estimation, particularly for small sample sizes.

### 2025-03-15 Text/Reports/report-Renyi/R1-report-renyi.Rmd
Update paper with corrected comments

@@
 
-<!-- ```{r Table_optimal, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->
-
-<!-- set.seed(1234567890, kind = "Mersenne-Twister") -->
-<!-- # Parameters -->
-<!-- sample_sizes <- c(49) -->
-<!-- R <- 2000 # Number of replications -->
-<!-- B <- 100         # Number of bootstrap replications -->
-<!-- mu <- 1        # Fixed mu -->
-<!-- L <- 36         # Fixed L -->
-
-<!-- # Estimators -->
-<!-- estimators <- list( -->
-<!--  # "Renyi Estimator" = renyi_entropy_estimator_v1 -->
-<!--   "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1 -->
-<!-- ) -->
-
-<!-- # Valores de lambda a evaluar -->
-<!-- #lambda_values <- c( 1.1, 1.5, 2.0, 2.5, 3.0, 3.5, 5, 6, 7, 8, 10, 20, 100 ) -->
-<!-- #lambda_values <- c(  0.90,   0.95, 0.96,  0.98, 0.99, 1.1, 1.2,  1.4 ) -->
-
-<!-- #lambda_values <- c(0.8, 0.84, 0.85, 0.86, 0.88, 0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4, 2.5, 3, 3.5 ) -->
-<!-- #lambda_values <- c(0.65, 0.66, 0.67, 0.68, 0.69, 0.70, 0.71, 0.72, 0.75, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0 ) -->
-<!-- lambda_values <- c( 0.85, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9,  2.0, 2.5, 3.0) -->
-
-<!-- # Guardar resultados para cada lambda y n = 49 -->
-<!-- results_optimal_lambda <- data.frame(Lambda = numeric(0), Bias = numeric(0), MSE = numeric(0)) -->
-
-<!-- # Calcular sesgo y MSE para cada valor de lambda y el tamaño de muestra de interés (49) -->
-<!-- for (lambda in lambda_values) { -->
-<!--   # Actualizar los valores de alpha en el código original para usar cada lambda -->
-<!--   alpha_values <- c(lambda) -->
-
-<!--   # Calcular sesgo y MSE -->
-<!--   results <- calculate_bias_mse_r(sample_sizes = c(49), R = R, B = B, mu = mu, L = L, alpha_values = alpha_values, estimators = estimators) -->
-
-<!--   # Filtrar resultados para el tamaño de muestra de interés -->
-<!--   result_lambda <- results[results$n == 49, ] -->
-
-<!--   # Agregar los resultados a la tabla de resultados óptimos -->
-<!--   results_optimal_lambda <- rbind(results_optimal_lambda, data.frame( -->
-<!--     Lambda = lambda, -->
-<!--     Bias = mean(result_lambda$Bias), -->
-<!--     MSE = mean(result_lambda$MSE) -->
-<!--   )) -->
-<!-- } -->
-
-<!-- # Ordenar la tabla por MSE y luego por Bias para encontrar el valor óptimo de lambda -->
-<!-- results_optimal_lambda <- results_optimal_lambda[order(results_optimal_lambda$MSE, results_optimal_lambda$Bias), ] -->
-
-<!-- # Mostrar la tabla de resultados -->
-<!-- print(results_optimal_lambda) -->
-
-<!-- ``` -->
+```{r Table_optimal, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+
+set.seed(1234567890, kind = "Mersenne-Twister")
+# Parameters
+sample_sizes <- c(49)
+R <- 500# Number of replications con 200 y 
+B <- 100      # Number of bootstrap replications 10 tambien funciona 0.9 el valor optimo
+mu <- 1        # Fixed mu
+L <- 1        # Fixed L
+
+# Estimators
+estimators <- list(
+ # "Renyi Estimator" = renyi_entropy_estimator_v1
+  "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1
+)
+
+# Valores de lambda a evaluar
+#lambda_values <- c( 1.1, 1.5, 2.0, 2.5, 3.0, 3.5, 5, 6, 7, 8, 10, 20, 100 )
+#lambda_values <- c(  0.90,   0.95, 0.96,  0.98, 0.99, 1.1, 1.2,  1.4 )
+
+#lambda_values <- c(0.8, 0.84, 0.85, 0.86, 0.88, 0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4, 2.5, 3, 3.5 )
+#lambda_values <- c(0.65, 0.66, 0.67, 0.68, 0.69, 0.70, 0.71, 0.72, 0.75, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0 )
+lambda_values <- c(  0.9, 0.95,  0.99, 1.1, 1.2,  1.5,  2, 3, 3.5, 4)
+
+# Guardar resultados para cada lambda y n = 49
+results_optimal_lambda <- data.frame(Lambda = numeric(0), Bias = numeric(0), MSE = numeric(0))
+
+# Calcular sesgo y MSE para cada valor de lambda y el tamaño de muestra de interés (49)
+for (lambda in lambda_values) {
+  # Actualizar los valores de alpha en el código original para usar cada lambda
+  alpha_values <- c(lambda)
+
+  # Calcular sesgo y MSE
+  results <- calculate_bias_mse_r(sample_sizes = c(49), R = R, B = B, mu = mu, L = L, alpha_values = alpha_values, estimators = estimators)
+
+  # Filtrar resultados para el tamaño de muestra de interés
+  result_lambda <- results[results$n == 49, ]
+
+  # Agregar los resultados a la tabla de resultados óptimos
+  results_optimal_lambda <- rbind(results_optimal_lambda, data.frame(
+    Lambda = lambda,
+    Bias = mean(result_lambda$Bias),
+    MSE = mean(result_lambda$MSE)
+  ))
+}
+
+# Ordenar la tabla por MSE y luego por Bias para encontrar el valor óptimo de lambda
+results_optimal_lambda <- results_optimal_lambda[order(results_optimal_lambda$MSE, results_optimal_lambda$Bias), ]
+
+# Mostrar la tabla de resultados
+print(results_optimal_lambda)
+
+```
 

### 2025-03-15 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Started revision

@@
 These distributions are characterized by the following probability density functions (pdfs):
-\begin{align}
+\begin{equation}
 	f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
-    &= \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
+    = \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
     \exp \biggl(-\frac{Lz}{\mu}\biggr)
-    \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
-    \intertext{and}
+    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gamma1}
+\end{equation}
+and
+\begin{multline}
     f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
-    &= \frac{L^L\,\Gamma(L-\alpha)}
-    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
-    \notag \\
-    &\quad \times
+    = \frac{L^L\,\Gamma(L-\alpha)}
+    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}\\
     \frac{z^{L-1}}
@@
     \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi01}
-\end{align}
+\end{multline}
 where $\mu > 0$ is the mean,
@@
 - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
-\bigr]\bigr\}.
+\bigr]\bigr\},
 \end{multline}
-where $\ln \widehat{\mu}={\textstyle\frac{1}{n}\sum_{i=1}^n Z_{i}}$ is the natural logarithm of the sample mean.
+where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
 
 When the null hypothesis holds, this test statistic is expected to be close to zero.
-For illustrative purposes, @fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10,000$ simulations of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
+@fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10,000$ simulations of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
 ```{r Simulated_densityR, echo=FALSE, message=FALSE}
@@
 where $d$ represents convergence in distribution.
-@fig-density_entropyR presents the behavior of the empirical distribution of the standardized test statistic.
+@fig-density_entropyR shows smoothed histograms of standardized test statistic.
 Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
@@
 
-Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$, defined in\ [@Frery2024],  we compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$. Using the pdf  
+Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ as defined in Ref.\ [@Frery2024].
+We compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$ using the pdf  
 \begin{equation*}
 f_{\mathcal{G}^0_I}(z) = C \frac{z^{L-1}}{(\gamma + Lz)^{L-\alpha}},  
-\quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}, \label{eq:pdf_G0I}
+\quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}. \label{eq:pdf_G0I}
 \end{equation*}
-and setting $t = Lz/\gamma$, we obtain  
+Setting $t = Lz/\gamma$, we obtain  
 \begin{equation*}
@@
 \end{equation*}
-Using the Rényi entropy definition in \eqref{E:entropy2}: $H_\lambda(Z) = \frac{1}{1-\lambda} \ln I$,
+Using the Rényi entropy definition in \eqref{E:entropy2}: $H_\lambda(Z) = (1-\lambda)^{-1} \ln I$,
 and substituting $\gamma = -\mu(\alpha + 1)$, we obtain the final expression for $\mathcal{G}^0_I(\mu, \alpha, L)$ in \eqref{eq-HGI0}.
 
-Code is available at: <https://github.com/rjaneth/renyi-entropy>
+The code is available at: <https://github.com/rjaneth/renyi-entropy>
 

### 2025-03-15 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update R0-Renyi-entropy-sar.qmd

@@
   -\lambda\,\ln\Gamma(L) \\  + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
-\Bigr]
+\Bigr],
 \end{multline}
@@
 \end{multline}
-The derivation of this result is given in the Appendix.
-
-@fig-plot presents the Rényi entropy of $\mathcal{G}^0_I$ as a function of $\mu$ for different $\alpha$ values.
-As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is aligned with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $\mathcal{G}^0_I$ model.
+These results are proven in the Appendix.
+
+@fig-plot presents the Rényi entropy of the $\mathcal{G}^0_I$ model as a function of $\mu$ for different values of $\alpha$. 
+As $\alpha \to -\infty$, it approaches the Rényi entropy of the $\Gamma_{\text{SAR}}$ law, in line with the fact that the latter is a limiting case of the former.
 
@@
 $m/n\rightarrow0$. 
-We choose to use the heuristic formula for spacing, $m=\left[\sqrt{n}+0.5\right]$.
+We choose to use the heuristic spacing $m=\left[\sqrt{n}+0.5\right]$.
 

### 2025-03-17 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update R0-Renyi-entropy-sar.qmd

@@
 
-Following Refs.\ [@Frery2024;@Alpala2024], we also refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} using the bootstrap technique to reduce its bias and apply the improved version, denoted as $\widetilde{H}_{\lambda}$:
+Following Refs.\ [@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
 $$

### 2025-03-18 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update

@@
 The $\mathcal{G}^0_I$ distribution has been shown to be an effective law for SAR intensity data, as it captures different levels of roughness.
-A special case is the Gamma distribution, which arises when speckle is fully developed, indicating homogeneous regions.
+A limiting case is the Gamma distribution, which arises when speckle is fully developed, indicating homogeneous regions.
 Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
@@
 \begin{cases}
-\mathcal{H}_0: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\Gamma_{\text{SAR}}), & \text{(Homogeneous region)} \\[6pt]
-\mathcal{H}_1: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\mathcal{G}^0_I), & \text{(Heterogeneous region)}
+\mathcal{H}_0: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\Gamma_{\text{SAR}}) & \text{(Homogeneous region)}, \\[6pt]
+\mathcal{H}_1: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\mathcal{G}^0_I) & \text{(Heterogeneous region)}.
 \end{cases}
@@
 \begin{equation*}
-S(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2})\,.
+S(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2}_S)\,,
 \end{equation*}
+where $d$ represents convergence in distribution. Here, $\mu_S  = \mathbb{E}[S(\bm{Z}; L)]$ and $\sigma^{2}_S = \text{Var}[S(\bm{Z}; L)]$ are the theoretical mean and variance of $S(\bm{Z}; L)$.
+
 We define the standardized test statistic:
@@
 \end{equation*}
-where $\hat{\mu}_S = \mathbb{E}[S(\bm{Z}; L)]$ and $\hat{\sigma}_S = \sqrt{\text{Var}[S(\bm{Z}; L)]}$.
-By the central limit theorem, under the null hypothesis, $\varepsilon$ asymptotically follows a standard normal distribution:
+where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S(\bm{Z}; L)$, obtained from Monte Carlo simulations under the null hypothesis. 
+By the central limit theorem, $\varepsilon$ asymptotically follows a standard normal distribution:
 \begin{equation*}
-\varepsilon \overset{d}{\longrightarrow} \mathcal{N}(0,1)\,,
+\varepsilon \overset{d}{\longrightarrow} \mathcal{N}(0,1)\,.
 \end{equation*}
-where $d$ represents convergence in distribution.
-@fig-density_entropyR shows smoothed histograms of standardized test statistic.
+@fig-density_entropyR_standardized0 shows smoothed histograms of standardized test statistic.
 Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,

### 2025-03-19 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Returned with comments

@@
 ---
-title: Rényi Entropy-Based Heterogeneity Detection in SAR Data
+title: Quantifying Roughness in SAR Imagery with the Rényi Entropy
 format:
@@
   #- id: 
-  - name: Janeth Alpala, Abraão D.\ C.\ Nascimento 
+  - name: Janeth Alpala, Abraão D.&nbsp;C.&nbsp;Nascimento 
     affiliations:
@@
     #  the author name as the argument followed by the biography text.
-  - name: Alejandro C.\ Frery
+  - name: Alejandro C.&nbsp;Frery
     affiliations:
@@
         postal-code: 6140
+        orcid: "0000-0002-8002-5341"
+        membership: "Fellow, IEEE"
       #- name: Unknown affiliation
@@
 abstract: |
-  Synthetic aperture radar (SAR) systems have already been successfully used to solve remote sensing problems.
-A disadvantage of SAR images is the presence of speckle, which is fully developed in homogeneous areas and gamma-distributed in these scenes.
-In heterogeneous areas, the intensity values are $\mathcal{G}^0_I$-distributed.
-  In this way, the identification of roughness SAR areas (as opposed to homogeneous ones) is an important task. 
-  In this work, we propose a family of hypothesis tests driven by an order parameter to identify roughness features in SAR intensity data using Rényi entropy. 
-  In particular, we use a nonparametric estimator for the Rényi entropy and investigate some of its properties. 
-  As a practical evaluation method, we develop $p$-value maps on which one can observe both (i) the heterogeneous evidence change per texture and (ii) the prediction of homogeneous and heterogeneous categories.
-  The results are in favor of the Rényi-based heterogeneity detector compared to the one based on Shannon entropy.
-keywords: [Rényi entropy, Gamma distribution, heterogeneity, SAR,  hypothesis tests]
+  Quantifying surface roughness in synthetic aperture radar (SAR) data is critical for accurate geophysical interpretation and remote sensing applications. 
+  We propose a test statistic based on a non-parametric estimation of Rényi entropy to characterize surface roughness from SAR intensity data. 
+  The statistic is refined using bootstrap to improve its stability, size and power. 
+  This approach enhances roughness quantification by capturing scale-dependent variations and addressing data-driven uncertainty.
+  Experimental results demonstrate the robustness of the proposed method in distinguishing roughness patterns, offering a statistically rigorous tool for SAR-based terrain analysis.
+  <!-- Synthetic aperture radar (SAR) systems have already been successfully used to solve remote sensing problems.  -->
+  <!-- A disadvantage of SAR images is the presence of speckle, which is fully developed in homogeneous areas and gamma-distributed in these scenes.  -->
+  <!-- In heterogeneous areas, the intensity values are $\mathcal{G}^0_I$-distributed.  -->
+  <!-- In this way, the identification of roughness SAR areas (as opposed to homogeneous ones) is an important task.  -->
+  <!-- In this work, we propose a family of hypothesis tests driven by an order parameter to identify roughness features in SAR intensity data using Rényi entropy.  -->
+  <!-- In particular, we use a non-parametric estimator for the Rényi entropy and investigate some of its properties.  -->
+  <!-- As a practical evaluation method, we develop $p$-value maps on which one can observe both (i) the heterogeneous evidence change per texture and (ii) the prediction of homogeneous and heterogeneous categories.
+-->
+  <!-- The results are in favor of the Rényi-based heterogeneity detector compared to the one based on Shannon entropy. -->
+keywords: [Rényi entropy, Gamma distribution, heterogeneity, SAR, hypothesis tests, bootstrap]
 
@@
 [S]{.IEEEPARstart}[ynthetic]{}
- Aperture Radar (SAR) technology has become essential for a wide range of applications\ [@Yu2023;@Akbarizadeh2012;@Mondini2021].
-It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions to facilitate global Earth monitoring\ [@Zeng2020].
-Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect\ [@Argenti2013; @Choi2019].
+ Aperture Radar (SAR) technology has become essential for a wide range of applications&nbsp;[@Yu2023;@Akbarizadeh2012;@Mondini2021]. 
+ It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
+Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019].
 In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
 
-The $\mathcal{G}^0_I$ distribution has been shown to be an effective law for SAR intensity data, as it captures different levels of roughness.
-A limiting case is the Gamma distribution, which arises when speckle is fully developed, indicating homogeneous regions.
+The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different levels of roughness. 
+A limiting case is the Gamma distribution, which arises when speckle is fully developed, indicating textureless regions. 
 Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
@@
 
-Entropy measures have gained attention as valuable statistical tools for analyzing SAR data, with applications in edge detection\ [@Nascimento2014], segmentation\ [@Nobre2016], classification\ [@Cassetti2022], and noise reduction\ [@Chan2022].
-Traditionally, Shannon entropy\ [@Shannon1948] has been widely used to quantify uncertainty and disorder in data.
-However, this study explores an alternative information measure: Rényi entropy—a generalization of Shannon’s formulation.
+Entropy measures have gained attention as valuable statistical tools for analyzing SAR data, with applications in edge detection&nbsp;[@Nascimento2014], 
+segmentation&nbsp;[@Nobre2016], 
+classification&nbsp;[@Cassetti2022], 
+and noise reduction&nbsp;[@Chan2022].
+Traditionally, Shannon entropy&nbsp;[@Shannon1948] has been widely used to quantify data uncertainty and disorder. 
+We explore a more general information measure: Rényi entropy—a generalization of Shannon’s formulation. 
 This more flexible approach provides additional insights for identifying heterogeneity, making it a promising tool for enhancing SAR image analysis.
 
-In this work, we propose a statistical test based on a non-parametric estimator of Rényi entropy to identify heterogeneous regions in SAR data.
-The test assesses whether the observed Rényi entropy in a given region significantly differs from its expected theoretical value under the assumption of homogeneity.
-Compared to our previous approach  using Shannon entropy\ [@Frery2024], the Rényi-based approach improves the detection of heterogeneity in real SAR images.
+We propose a statistical test based on a non-parametric estimator of Rényi entropy to identify heterogeneous regions in SAR data.
+The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the assumption of homogeneity.
+Compared to our previous approach using Shannon entropy&nbsp;[@Frery2024], the Rényi-based approach improves the detection of heterogeneity.
 
 The remainder of this article is organized as follows.
-Section\ \ref{sec:pre} outlines an overview of statistical models for SAR intensity data and introduces Rényi entropy.
-Section\ \ref{sec:met} describes the proposed hypothesis test and the formulation of the test statistic. 
-Section\ \ref{sec:app} evaluates the performance of the test using real SAR data.
-Finally, the concluding remarks are drawn in Section\ \ref{sec:conclusion}.
+Section&nbsp;\ref{sec:pre} overviews the statistical models for SAR intensity data and introduces Rényi entropy.
+Section&nbsp;\ref{sec:met} describes the proposed hypothesis test and the test statistic.
+Section&nbsp;\ref{sec:app} evaluates the performance of the test using SAR data.
+Finally, the concluding remarks are drawn in Section&nbsp;\ref{sec:conclusion}.
 
@@
 
-The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997].
+The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness&nbsp;[@Frery1997].
 These distributions are characterized by the following probability density functions (pdfs):
@@
 $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
-As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
+As demonstrated by&nbsp;[@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
 $$
@@
 
-Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], this measure generalizes several well-known entropies, including the Shannon entropy\ [@Ribeiro2021].
-For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$, with $\lambda > 0$ and $\lambda \neq 1$, is defined as:
+Introduced by Alfréd Rényi in 1961&nbsp;[@renyi1961measures], this measure generalizes several well-known entropies, including Shannon's&nbsp;[@Ribeiro2021]. 
+For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$, is defined as:
 \begin{equation}
@@
 H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
-+ \frac{1}{\,1 - \lambda\,}
++ \frac{1}{1 - \lambda}
 \Bigl[
@@
 These results are proven in the Appendix.
+<!-- ACF Have you checked if it is possible to state the difference between \label{eq-HGI0} and \label{eq-HGammaSAR}? At the end of the day, that is what we want to assess. -->
 
@@
 
-## Nonparametric Estimation of Rényi Entropy
-
-Nonparametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999; @AlOmari2019].
-Recently, Al-Labadi et al.\ [@AlLabadi2024] proposed a nonparametric estimator for Rényi entropy following this approach.
+## Non-parametric Estimation of Rényi Entropy
+
+In order to estimate&nbsp;\eqref{E:entropy2} from a random sample, one may estimate the parameters that index the probability density function $f$, and integrate.
+This approach heavily relies on the model assumptions and on the absence of outliers.
+Alternatively, one may estimate directly $f$.
+Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999; @AlOmari2019].
+Recently, Al-Labadi et al.&nbsp;[@AlLabadi2024] proposed a non-parametric estimator for Rényi entropy following this approach.
 
@@
 
-Following Vasicek [@vasicek1976test] and Ebrahimi et al. [@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, the Rényi entropy can be estimated as:
+Following Vasicek&nbsp;[@vasicek1976test] and Ebrahimi et al.&nbsp;[@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, the Rényi entropy can be estimated as:
 \begin{align}
@@
 $m/n\rightarrow0$. 
-We choose to use the heuristic spacing $m=\left[\sqrt{n}+0.5\right]$.
+We used the heuristic spacing $m=\left[\sqrt{n}+0.5\right]$.
 
@@
 
-Based on the results, we find that the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
-This choice is the same for $L > 1$.
-However, for $L = 1$, the optimal $\lambda$ tends to be higher (e.g., $\lambda = 3$) to achieve good results.
+We found that for $L > 1$ the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
+However, for $L = 1$, the optimal $\lambda$ tends to be higher and we chose $\lambda = 3$ to achieve good results. 
 @fig-plotf illustrates the case for $L = 5$.
+
 ```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
@@
 
-Following Refs.\ [@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in \eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
+Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
 $$
@@
 
-A Monte Carlo study with $1,000$ samples from $\Gamma_{\text{SAR}}$ ($\mu = 1$, $L=5$, $\lambda = 0.9$), using $B = 200$ replications, confirms that the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$  outperforms the original $\widehat{H}_{\lambda}$ by reducing both bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
+A Monte Carlo study with $1000$ samples from $\Gamma_{\text{SAR}}$, $\mu = 1$ and $L=5$, using $B = 200$ replications, confirms that the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$, with $\lambda = 0.9$, outperforms the original $\widehat{H}_{\lambda}$ by reducing both bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
+<!-- ACF Remove the minor vertical grid (there is nothing between 49 and 81) -->
 
@@
 When the null hypothesis holds, this test statistic is expected to be close to zero.
-@fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10,000$ simulations of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
+@fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
+<!-- ACF 10^4 replications of samples of size?   -->
+
 ```{r Simulated_densityR, echo=FALSE, message=FALSE}
@@
 ```
-Under the asymptotic properties of the entropy estimator\ [@vasicek1976test], for sufficiently large samples, $S(\bm{Z}; L)$ follows an asymptotic normal distribution:
+
+Vasicek&nbsp;[@vasicek1976test] proved that, for sufficiently large samples, $S(\bm{Z}; L)$ asymptotically follows a normal distribution:
 \begin{equation*}
@@
 \end{equation*}
-where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S(\bm{Z}; L)$, obtained from Monte Carlo simulations under the null hypothesis. 
+where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
 By the central limit theorem, $\varepsilon$ asymptotically follows a standard normal distribution:
@@
 \end{equation*}
-@fig-density_entropyR_standardized0 shows smoothed histograms of standardized test statistic.
 Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
 where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
+@fig-density_entropyR_standardized0 shows smoothed histograms of standardized test statistics.
+
 ```{r Simulated_densityR_standardized0, echo=FALSE, message=FALSE}
@@
 ```
-In general, hypothesis tests aim to achieve a controlled type I error rate (size) and high test power (sensitivity to departures from $\mathcal{H}_0$).
+In general, hypotheses tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
 To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels  $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
-The observed type I error rates aligned with the nominal values, confirming the test validity.
+<!-- ACF I wish you had used the siunitx package for typing percentages, but not if this is incompatible with the tables -->
+The observed Type&nbsp;I error rates align with the nominal values, confirming the test validity.
 
@@
 
-In this section, we evaluate the proposed test statistic on real SAR data to assess its effectiveness in detecting heterogeneity.
-The test was applied to SAR intensity images from several regions: urban, agricultural, and water.
-In particular, we analyzed three images: the first from London, United Kingdom; the second from the surroundings of Munich, Germany; and the third from  Dublin Port, Ireland, as shown in Figs.\ \ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
-Table\ \ref{tab:table_param} provides detailed acquisition parameters for these images.
+In this section, we evaluate the proposed test statistic on SAR data to assess its effectiveness in detecting heterogeneity.
+We applied the test to images covering urban, agricultural, and water regions. 
+We analyzed images from London, United Kingdom; from the surroundings of Munich, Germany; and from  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
+Table&nbsp;\ref{tab:table_param} provides detailed acquisition parameters for these images.
+
+<!-- ACF They all have HH polarization; the column is not informative, and can be deleted to gain space -->
 \renewcommand{\arraystretch}{3}   
@@
 
-To evaluate the performance of our proposal, we applied the test statistics $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ and  $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, based on Shannon entropy as described in\ [@Frery2024], using a local sliding window of size $7\times7$.
-The resulting $p$-value maps are presented in Figs.\ \ref{fig:london}(b), \ref{fig:london}(d), \ref{fig:munich}(b), \ref{fig:munich}(d), \ref{fig:dublin}(b), and \ref{fig:dublin}(d). 
+We applied the test statistics $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ and  $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, based on Shannon entropy as described in&nbsp;[@Frery2024], using a local sliding window of size $7\times7$.
+<!-- ACF What is $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$? -->
+The resulting $p$-value maps are presented in Figs.&nbsp;\ref{fig:london}(b), \ref{fig:london}(d), \ref{fig:munich}(b), \ref{fig:munich}(d), \ref{fig:dublin}(b), and \ref{fig:dublin}(d). 
 These maps employ a color gradient, where darker regions indicate areas with higher roughness, while lighter regions correspond to smoother, less textured surfaces.
 
-In order to better illustrate the decision-making process of both tests, binary maps at a significance level of $0.05$ are shown in Figs.\ \ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e).
-
+Figs.&nbsp;\ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e) 
+are binary maps at significance level of $0.05$ that 
+illustrate the decision-making process.
 In these binary representations, white areas correspond to $p$-values greater than $0.05$, indicating that there is no statistical evidence to reject the null hypothesis (homogeneous regions). 
@@
 The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations compared to the Shannon-based approach, due to the flexibility provided by the parameter $\lambda$. 
-When $\lambda \to 1$, Rényi entropy converges to Shannon entropy, resulting in similar heterogeneity detection. 
-Our analysis shows that the optimal $\lambda$ value depends on the number of looks: for single-look images like London, $\lambda = 3$ provided the best contrast, while for multi-look images like Munich and Dublin, $\lambda = 0.9$ was more effective.
+<!-- ACF Where is the Shannon-based approach shown? -->
+<!-- When $\lambda \to 1$, Rényi entropy converges to Shannon entropy, resulting in similar heterogeneity detection.  -->
 
@@
 
-# Conclusion {#sec:conclusion}
+# Conclusions {#sec:conclusion}
 
 This study presented a new statistical approach based on Rényi entropy for detecting heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
-The statistics of the proposed test was computed nonparametrically and its performance was evaluated by a Monte Carlo study. 
-The results showed that the method effectively controls the probability of type I error while maintaining a high detection performance that improves as the sample size increases.
+The statistics of the proposed test was computed non-parametrically and its performance was evaluated by a Monte Carlo study. 
+The results showed that the method effectively controls the probability of Type&nbsp;I error while maintaining a high detection performance that improves as the sample size increases.
 
 The performance of the Rényi-based test was evaluated by comparing its results with those of a test based on Shannon entropy.
+<!-- ACF Again, where are the Shannon results? -->
 This comparison was performed using $p$-values and binary maps. 
@@
 
-Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ as defined in Ref.\ [@Frery2024].
+Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ as defined in Ref.&nbsp;[@Frery2024].
 We compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$ using the pdf  

### 2025-03-29 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Update corrected comments

@@
     keep-tex: true  
+    classoption: lettersize
+    tex-author-no-affiliation: true
     #conference: true # comment this line to use journal
@@
   #ieee-html: default
-
 author:
-  #- id: 
-  - name: Janeth Alpala, Abraão D.&nbsp;C.&nbsp;Nascimento 
+  - name: Janeth Alpala
+    email: janeth.alpala@ufpe.br
+    orcid: 0000-0002-0265-6236
+  - name: Abraão D.&nbsp;C.&nbsp;Nascimento
     affiliations:
@@
         city: Recife
-        country: PE, Brazil
+        country: Brazil
         postal-code: 50670-901
-      #- name: Unknown affiliation
-   # orcid: 
-    email: janeth.alpala@ufpe.br, abraao@de.ufpe.br
-    #url: 
-    #membership: "Member, IEEE"
-    #attributes:
-    #  corresponding: true
-    #photo: 
-    #bio: |
-    #  Use `IEEEbiography`  with figure as  option and
-    #  the author name as the argument followed by the biography text.
+    email: abraao@de.ufpe.br
+    orcid: 0000-0003-2673-219X
   - name: Alejandro C.&nbsp;Frery
@@
         postal-code: 6140
-        orcid: "0000-0002-8002-5341"
-        membership: "Fellow, IEEE"
-      #- name: Unknown affiliation
-    #orcid: 
+    orcid: 0000-0002-8002-5341
     email: alejandro.frery@vuw.ac.nz
+    membership: Fellow, IEEE
+    attributes:
+      corresponding: true
+    note: |
+      Janeth Alpala and Abraão D.
+C.
+Nascimento are with the Departamento de Estatística, Universidade Federal de Pernambuco, Recife, 50670-901 PE, Brazil (e-mails: janeth.alpala@ufpe.br, abraao@de.ufpe.br).
+
+      Alejandro C.
+Frery is with the School of Mathematics and Statistics, Victoria University of Wellington, Wellington, 6140, New Zealand (e-mail: alejandro.frery@vuw.ac.nz).
+\emph{Corresponding author: Alejandro C.
+Frery.}
+
+      Data and code are available at: <https://github.com/rjaneth/renyi-entropy> 
     # bio: |
@@
 header-includes:
-   - \usepackage[english]{babel}
+   #- \usepackage[english]{babel}
    - \usepackage{bm,bbm}
    - \usepackage{mathrsfs}
+   - \usepackage{nccmath}
+   - \usepackage{amssymb}
+   - \usepackage{mathtools}
    - \usepackage{siunitx}
@@
    - \usepackage[T1]{fontenc}
-   #- \usepackage{polski}
    - \usepackage{booktabs}
    - \usepackage{color}
-   - \usepackage{mathtools}
-  # - \usepackage[utf8]{inputenc}
    - \usepackage{hyperref}
@@
    - \usepackage{xcolor}
-   - \usepackage{amsmath}
-   - \usepackage{hyperref}
-   - \hypersetup{
-      colorlinks=true,
-      linkcolor=black,
-      filecolor=black,
-      citecolor=black,
-      urlcolor=black}
-
 #bibliography: references.bib
@@
 ```
-
+\renewcommand{\tablename}{TABLE}
 # Introduction
@@
  It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
-Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019].
+Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019; @Baraha2023].
 In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
@@
 \end{equation}
-Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions:
+Using&nbsp;\eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and the $\mathcal{G}^0_I$ distributions:
 \begin{multline}
@@
 and
-\begin{multline}\label{eq-HGI0}
-H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
-+ \frac{1}{1 - \lambda}
-\Bigl[
-   \lambda\bigl(
-      \ln\Gamma(L - \alpha)
-      -\ln\Gamma(-\alpha)
-      -\ln\Gamma(L)
-   \bigr)\\
-   +\ln\Gamma\bigl(\lambda(L - 1) + 1\bigr)
-   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)\\
-   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
-\Bigr].
+\begin{multline}  
+\label{eq-HGI0}  
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \ln(-1 - \alpha) \\  
++ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
++ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) - \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) \\
++ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
 \end{multline}
-These results are proven in the Appendix.
+The derivation of the latter result is proven in the Appendix.
+Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms depending on the roughness parameter $\alpha$.
+As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
+
+@fig-plot illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$.
+As $\alpha$ decreases, the curves approach $H_\lambda(\Gamma_{\text{SAR}})$ (solid black line).
+This confirms that $\Gamma_{\text{SAR}}$ is a limiting case of $\mathcal{G}^0_I$.
 <!-- ACF Have you checked if it is possible to state the difference between \label{eq-HGI0} and \label{eq-HGammaSAR}? At the end of the day, that is what we want to assess. -->
-
-@fig-plot presents the Rényi entropy of the $\mathcal{G}^0_I$ model as a function of $\mu$ for different values of $\alpha$. 
-As $\alpha \to -\infty$, it approaches the Rényi entropy of the $\Gamma_{\text{SAR}}$ law, in line with the fact that the latter is a limiting case of the former.
-
+<!-- Corrected -->
 ```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}
@@
 Alternatively, one may estimate directly $f$.
-Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics [@vasicek1976test; @Ebrahimi1994; @Wieczorkowski1999; @AlOmari2019].
+Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics&nbsp;[@vasicek1976test;@Bert1992; @Ebrahimi1994; @Wieczorkowski1999; @IbrahimAlOmari2014].
 Recently, Al-Labadi et al.&nbsp;[@AlLabadi2024] proposed a non-parametric estimator for Rényi entropy following this approach.
@@
 @fig-plotf illustrates the case for $L = 5$.
-
 ```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
@@
          #  label = "Bias", color = "#00AFBB", fontface = "italic", hjust = 1.0) +
-  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
+  #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
   labs(x = expression(lambda), y = "Bias") +
@@
            #label = "MSE", color = "#E69F00", fontface = "italic", hjust = 1.0) +
-   scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) + 
+   #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) + 
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
   labs(x = expression(lambda), y = "MSE") +
@@
 
-A Monte Carlo study with $1000$ samples from $\Gamma_{\text{SAR}}$, $\mu = 1$ and $L=5$, using $B = 200$ replications, confirms that the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$, with $\lambda = 0.9$, outperforms the original $\widehat{H}_{\lambda}$ by reducing both bias and MSE for small sample sizes, as shown in @fig-Plot_bias_msef3.
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-Plot_bias_msef3.
+
 <!-- ACF Remove the minor vertical grid (there is nothing between 49 and 81) -->
-
+<!-- Corrected -->
 ```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
@@
 Assume we have an estimator $\widetilde{H}_{\lambda}$ for the Rényi entropy of an arbitrary model.
-For testing \eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation \eqref{eq-HGammaSAR}.
+For testing&nbsp;\eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation&nbsp;\eqref{eq-HGammaSAR}.
 Since $L\geq1$ is known, we define the test statistic as follows:
@@
 \label{eq-test}
-S(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
+S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
 \bigl[-\lambda\,\ln\Gamma(L) \\ 
@@
 where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
-
 When the null hypothesis holds, this test statistic is expected to be close to zero.
-@fig-density_entropyR shows the empirical density of $S(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model, with $\lambda=0.9$ and $L \in \{5,18\}$.
+@fig-density_entropyR shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
 <!-- ACF 10^4 replications of samples of size?   -->
-
+<!-- Corrected -->
 ```{r Simulated_densityR, echo=FALSE, message=FALSE}
@@
     scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
-    scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
-    scale_y_continuous(limits = y_limits) +  
+    scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+    #scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
+    scale_y_continuous(limits = y_limits, minor_breaks = NULL)+
+    #scale_y_continuous(limits = y_limits) +  
     labs(
@@
 
-Vasicek&nbsp;[@vasicek1976test] proved that, for sufficiently large samples, $S(\bm{Z}; L)$ asymptotically follows a normal distribution:
+Vasicek&nbsp;[@vasicek1976test] proved that, for sufficiently large samples, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ asymptotically follows a normal distribution:
 \begin{equation*}
-S(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2}_S)\,,
+S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2}_S)\,,
 \end{equation*}
-where $d$ represents convergence in distribution. Here, $\mu_S  = \mathbb{E}[S(\bm{Z}; L)]$ and $\sigma^{2}_S = \text{Var}[S(\bm{Z}; L)]$ are the theoretical mean and variance of $S(\bm{Z}; L)$.
+where $d$ represents convergence in distribution.
+Here, $\mu_S  = \mathbb{E}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]$ and $\sigma^{2}_S = \text{Var}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]$ are the theoretical mean and variance of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$.
 
@@
 \begin{equation*}
-\varepsilon = \frac{S(\bm{Z}; L) - \hat{\mu}_S}{\hat{\sigma}_S},
+\varepsilon = \frac{S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S}{\hat{\sigma}_S},
 \end{equation*}
-where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
+where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
 By the central limit theorem, $\varepsilon$ asymptotically follows a standard normal distribution:
@@
     scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
-    scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
-    scale_y_continuous(limits = y_limits) +  
+    #scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
+    #scale_y_continuous(limits = y_limits) +
+    scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+scale_y_continuous(limits = y_limits, minor_breaks = NULL)+
     labs(#x = expression("Standardized Test Statistic" ~ epsilon),
@@
 In general, hypotheses tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
-To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels  $1\%$, $5\%$, and $10\%$, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
+To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
 <!-- ACF I wish you had used the siunitx package for typing percentages, but not if this is incompatible with the tables -->
+<!-- Corrected -->
 The observed Type&nbsp;I error rates align with the nominal values, confirming the test validity.
@@
 Further, we examined the power under the alternative hypothesis ($\mathcal{G}^0_I$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
-As expected, power improves as the sample size and number of looks increase, demonstrating the test effectiveness. The results are shown in Table \ref{tab:table_size_power}.
+As expected, power improves as the sample size and number of looks increase, demonstrating the test effectiveness. The results are shown in Table&nbsp;\ref{tab:table_size_power}.
 ```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
@@
       colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", 
-                                      "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", 
-                                      "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$", 
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$")
     }
@@
   booktabs = TRUE,
-  align = "ccccccccc",
+  align = "cccccccc",
   escape = FALSE,
@@
 ) %>%
-  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
+  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
   collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
@@
 # Applications to SAR Data {#sec:app}
-
-In this section, we evaluate the proposed test statistic on SAR data to assess its effectiveness in detecting heterogeneity.
-We applied the test to images covering urban, agricultural, and water regions. 
-We analyzed images from London, United Kingdom; from the surroundings of Munich, Germany; and from  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london}(a), \ref{fig:munich}(a), and \ref{fig:dublin}(a).
-Table&nbsp;\ref{tab:table_param} provides detailed acquisition parameters for these images.
-
+In this section, we compare two test statistics for detecting heterogeneity in SAR data: (i) the Rényi entropy-based test, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, described in&nbsp;\eqref{eq-test}; and (ii) the Shannon entropy-based test, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, which is based on the Al-Omari estimator proposed in&nbsp;[@IbrahimAlOmari2014] and was improved via bootstrap in our previous work.
+The details of this test can be found in Frery et al.&nbsp;[@Frery2024].
+<!-- ACF What is $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$? -->
+<!-- JA: I added a brief explanation, indicating that it is based on the Al-Omari estimator and was improved with bootstrap. -->
+
+We applied these tests to images covering urban, agricultural, and water regions. 
+We analyzed images from London, United Kingdom;  the surroundings of Munich, Germany; and  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london-a},&nbsp;\ref{fig:munich-a}, and&nbsp;\ref{fig:dublin-a}.
+All images were acquired in HH polarization.
+Table&nbsp;\ref{tab:table_param} provides the detailed acquisition parameters of these images.
 <!-- ACF They all have HH polarization; the column is not informative, and can be deleted to gain space -->
+<!-- Corrected -->
 \renewcommand{\arraystretch}{3}   
@@
   Band = c("X", "L", "X"),
-  Polarization = c("HH", "HH", "HH"),
   Size = c("$2000\\times2000$", "$1024\\times1024$", "$1100\\times1100$"),
@@
 
-colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size (pixels)}",  "$\\bm{L}$", "\\textbf{Resolution [m]} ", "\\textbf{Acquisition Date}")
+colnames(SAR_data) <- c(
+  "\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", 
+  "\\textbf{Size (pixels)}", "$\\bm{L}$", 
+  "\\textbf{Resolution [m]}", "\\textbf{Acquisition Date}"
+)
 
@@
 
-kable(SAR_data, caption = "Parameters of selected SAR images.",
+kable(SAR_data, 
       format = "latex",
       booktabs = TRUE,
-      align = "cccccccc",
+      align = "ccccccc",
       escape = FALSE,
@@
       label = "table_param",
-      centering = FALSE,
+      centering = TRUE,
+      caption = "Parameters of selected SAR images.",
       table.envir = "table", position = "hbt") %>%
@@
   column_spec(3, width = "1.5cm") %>%
-  column_spec(4, width = "2.5cm") %>%
-  column_spec(5, width = "4cm") %>%
-  column_spec(6, width = "1.5cm") %>%
-  column_spec(7, width = "3.0cm") %>%
-  column_spec(8, width = "3.5cm")
-
-```
-
-We applied the test statistics $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ and  $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, based on Shannon entropy as described in&nbsp;[@Frery2024], using a local sliding window of size $7\times7$.
-<!-- ACF What is $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$? -->
-The resulting $p$-value maps are presented in Figs.&nbsp;\ref{fig:london}(b), \ref{fig:london}(d), \ref{fig:munich}(b), \ref{fig:munich}(d), \ref{fig:dublin}(b), and \ref{fig:dublin}(d). 
-These maps employ a color gradient, where darker regions indicate areas with higher roughness, while lighter regions correspond to smoother, less textured surfaces.
-
-Figs.&nbsp;\ref{fig:london}(c), \ref{fig:london}(e), \ref{fig:munich}(c), \ref{fig:munich}(e), \ref{fig:dublin}(c), and \ref{fig:dublin}(e) 
-are binary maps at significance level of $0.05$ that 
-illustrate the decision-making process.
-In these binary representations, white areas correspond to $p$-values greater than $0.05$, indicating that there is no statistical evidence to reject the null hypothesis (homogeneous regions). 
-In contrast, black areas represent regions where the $p$-values are less than $0.05$, indicating statistically significant heterogeneity.
-
-The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations compared to the Shannon-based approach, due to the flexibility provided by the parameter $\lambda$. 
+  column_spec(4, width = "4cm") %>%
+  column_spec(5, width = "1.5cm") %>%
+  column_spec(6, width = "4.0cm") %>%
+  column_spec(7, width = "4.5cm")
+
+```
+We used sliding windows of size $7\times 7$.
+The results are presented as $p$-value maps and binary maps at a $0.05$ significance level. 
+Figs.&nbsp;\ref{fig:london-b}--\ref{fig:london-c},&nbsp;\ref{fig:munich-b}--\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-b}--\ref{fig:dublin-c} correspond to $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, while Figs.&nbsp;\ref{fig:london-d}--\ref{fig:london-e},&nbsp;\ref{fig:munich-d}--\ref{fig:munich-e}, and&nbsp;\ref{fig:dublin-d}--\ref{fig:dublin-e} correspond to $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$.
+
+The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness and lighter regions denote smoother, less textured surfaces.
+The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions). 
+In contrast, black areas represent regions with $p$-values below $0.05$, providing statistical evidence to reject the null hypothesis and indicating heterogeneity.
+
+The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations compared to the Shannon-based test, due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
 <!-- ACF Where is the Shannon-based approach shown? -->
-<!-- When $\lambda \to 1$, Rényi entropy converges to Shannon entropy, resulting in similar heterogeneity detection.  -->
-
+<!-- JA: The results of the Shannon-based approach can be observed in the corresponding binary maps. -->
 ```{=latex}
@@
         \caption{ SAR image}
-        \label{fig:1a}
+        \label{fig:london-a}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_renyi.png}
-        \caption{ $p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:1b}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:london-b}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:1c}
+        \label{fig:london-c}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_Shannon_c1.png}
-        \caption{$p$-values for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
-        \label{fig:1d}
+        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
+        \label{fig:london-d}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:1e}
+        \label{fig:london-e}
     \end{subfigure}
@@
         \caption{SAR image}
-        \label{fig:2a}
+        \label{fig:munich-a}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_renyi.png}
-        \caption{$p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:2b}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:munich-b}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:2c}
+        \label{fig:munich-c}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_Shan22.png}
-        \caption{$p$-values for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:2d}
+        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
+        \label{fig:munich-d}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:2e}
+        \label{fig:munich-e}
     \end{subfigure}
@@
         \caption{SAR image}
-        \label{fig:3a}
+        \label{fig:dublin-a}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/dublin_renyi_09_w7_b100.png}
-        \caption{$p$-values for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:3b}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:dublin-b}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:3c}
+        \label{fig:dublin-c}
     \end{subfigure}
@@
         \includegraphics[width=\linewidth]{./Figures/AO_w7_L16_b100.png}
-        \caption{$p$-values for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:3d}
+        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
+        \label{fig:dublin-d}
     \end{subfigure}
@@
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:3e}
+        \label{fig:dublin-e}
     \end{subfigure}
@@
 
-The performance of the Rényi-based test was evaluated by comparing its results with those of a test based on Shannon entropy.
 <!-- ACF Again, where are the Shannon results? -->
-This comparison was performed using $p$-values and binary maps. 
-The results showed that while both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, which allowed for finer differentiation of texture variations.
-
-These results suggested that the Rényi entropy was a more accurate alternative to the Shannon entropy for detecting heterogeneity in SAR images, especially due to its adaptability.
-
-Future research will focus on a more quantitative evaluation of both approaches, using statistical measures such as mean square error and other validation metrics to assess their accuracy in detecting heterogeneity.
-
-<!-- # Acknowledgment {-} -->
-
-<!-- This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil. -->
-
-<!-- # Computational Information {-}   -->
-<!-- This article was written using Quarto v6.4, RStudio v2024.12.0.467, and R v4.4.2 and is fully reproducible.  -->
-
-<!-- Code is available at: <https://github.com/rjaneth/renyi-entropy>   -->
+<!-- JA: The Shannon results are visually represented through p-value and binary maps for each image -->
+The effectiveness of the Rényi entropy-based test in SAR images was compared with the Shannon entropy-based test using $p$-value and binary maps. 
+The differences between the two methods are evident in the binary maps at a $0.05$ significance level.
+Although both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, which allowed for finer differentiation of texture variations.
+
+Future work will explore additional statistical metrics to improve the comparison between both tests and better quantify their differences in detecting heterogeneity.
 
@@
 
-The code is available at: <https://github.com/rjaneth/renyi-entropy>
+<!-- # Acknowledgment {-} -->
+
+<!-- This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) - Finance Code 001, and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.
+-->
+
+# Computational Information {-}
+This article was written in Quarto and is fully reproducible. We used RStudio version 2024.12.1+563, and R version 4.4.2.
 

### 2025-03-29 Text/Reports/report-Renyi/Appendix.Rmd
Update corrected comments

--- 2025-01-02 Text/Reports/report-Renyi/R1-report-renyi.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
+knitr::opts_chunk$set(echo = FALSE, cache=FALSE)
 # knitr::opts_chunk$set(echo = FALSE,cache=TRUE,
@@
 \newcommand{\widebar}[1]{\overline{#1}}
-
-# Introduction {#sec:Introduction}
-
-Synthetic Aperture Radar (SAR) technology is a powerful tool for environmental monitoring and disaster management, providing valuable imagery in all weather conditions, day or night \cite{Moreira2013,Mu2019}.
-However, effective use of SAR data requires a thorough understanding of its statistical properties due to the presence of speckle, an interference effect inherent in SAR data caused by the coherent nature of the imaging process \cite{Argenti2013}.
-
-To model SAR intensity data, the \(\mathcal{G}^0\) distribution is commonly used, as it provides flexibility for representing different levels of roughness, with the Gamma distribution serving as a limiting case for homogeneous regions with fully-developed speckle \cite{Ferreira2020}.
-Our goal is to improve the identification of roughness features in SAR intensity data by employing Rényi entropy as a new tool for distinguishing between homogeneous and heterogeneous regions.
-
-Entropy is a fundamental concept in information theory, applied in various fields such as image processing, statistical physics, and SAR image analysis \cite{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
-Originally introduced by Shannon in 1948 \cite{Shannon1948}, entropy measures information and uncertainty in a random variable.
-In this work, we utilize Rényi entropy, which generalizes Shannon entropy and provides a different perspective on data dispersion, particularly suited for SAR data.
-
-We propose a hypothesis test based on a non-parametric estimator of Rényi entropy to distinguish between homogeneous and heterogeneous regions.
-This approach is more effective than previous methods based on Shannon entropy, offering improved detection capabilities.
-Our proposed method is applied to generate homogeneity maps that reveal various target types in SAR data, demonstrating superior performance with both simulated and real SAR images.
-
-The article is structured as follows: Section \ref{sec:Background} discusses statistical modeling and entropy estimation for intensity SAR data.
-Section \ref{sec:test} outlines the hypothesis tests based on non-parametric entropy estimators.
-In Section \ref{sec:Results}, we present experimental results.
-Finally, Section \ref{sec:conclusion} provides conclusions.
-
-# Background {#sec:Background}
-
-## Statistical Modeling of Intensity SAR data \label{section1}
-
-The primary models for intensity SAR data include the Gamma and
-$\mathcal{G}_I^0$ distributions [@Frery1997]. The first is suitable for
-fully-developed speckle and is a limiting case of the second model. This
-is interesting due to its versatility in accurately representing regions
-with different roughness properties[@Cassetti2022]. We denote
-$Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and
-$Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows
-the distributions characterized by the respective probability density
-functions (pdfs): \begin{align}
-    f_Z(z;L, \mu\mid \Gamma_{\text{SAR}})&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\} \mathbbm 1_{\mathbbm R_+}(z)\label{E:gamma1}\\
-    \intertext{ and }
-    f_Z(z; \alpha, \gamma, L \mid \mathcal{G}_I^0)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm 1_{\mathbbm R_+}(z),\label{E:gi01}
-\end{align} where $\mu > 0$ is the mean, $\gamma > 0$ is the scale,
-$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of looks
-(either nominal or estimated, thus not restricted to integer values),
-$\Gamma(\cdot)$ is the gamma function, and $\mathbbm 1_{A}(z)$ is the
-indicator function of the set $A$.
-
-The $r$th order moments of the $\mathcal{G}_I^0$ model are
-\begin{equation}
-E\big(Z^r\mid \mathcal{G}_I^0\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+r)}{\Gamma(L)}, 
-    \label{E:rmom}
-\end{equation} provided $\alpha <-r$, and infinite otherwise. Therefore,
-assuming $\alpha<-1$, its expected value is \begin{equation}
-    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
-\end{equation}
-
-Although the $\mathcal{G}_I^0$ distribution is defined by the parameters
-$\alpha$ and $\gamma$, in the SAR literature \cite{Nascimento2010} the
-texture $\alpha$ and the mean $\mu$ are usually used.
-Reparametrizing \eqref{E:gi01} with $\mu$, and denoting this model as
-$G_I^0$ we obtain: \begin{equation}
-        f_Z\big(z; \mu, \alpha, L\mid G_I^0\big) = \frac{L^L\Gamma(L-\alpha)}{\big[-\mu(\alpha+1)\big]^{\alpha}\Gamma(-\alpha)\Gamma(L)} \frac{z^{L-1}}{\big[-\mu(\alpha+1)+Lz\big]^{L-\alpha}}.\label{E:gi02}
-\end{equation}
-
-## Rényi Entropy
-
-Introduced by Alfréd Rényi in 1961, the Rényi entropy generalizes several entropy measures, including the Shannon entropy.
-For a continuous random variable \( Z \) with probability density function (pdf) \( f(z) \), the Rényi entropy of order \( \lambda \) (where \( \lambda > 0 \) and \( \lambda \neq 1 \)) is defined as:
-
-\begin{align}
-\label{E:entropy2}
-H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
-\end{align}
-
-Using this definition, we obtain the Rényi entropy expressions for the \( \Gamma_{\text{SAR}} \) and \( G_I^0 \) distributions, respectively:
-
-\begin{align}
-\label{E:H_ren_gamma}
-H_\lambda(\Gamma_{\text{SAR}}) = \frac{1}{\lambda - 1} \left[ \lambda\,\ln\Gamma(L) - \ln\Gamma\big( \lambda(L - 1) + 1 \big) - (\lambda - 1)\big( \ln L - \ln \mu \big) + \big( \lambda(L - 1) + 1 \big)\,\ln \lambda \right].
-\end{align}
-\begin{multline}
-\label{E:H_ren_gi0}
-H_\lambda(G_I^0) = \ln \mu + \ln (-1 - \alpha) - \ln L \\
-+ \frac{1}{1 - \lambda} \left[ \lambda\left( \ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L) \right) + \ln \Gamma\left( \lambda(L - 1) + 1 \right) + \ln \Gamma\left( \lambda(-\alpha + 1) - 1 \right) - \ln \Gamma\left( \lambda(L - \alpha) \right) \right].
-\end{multline}
-
-Appendix&nbsp;\ref{app1} provides the detailed derivations of the Rényi entropy for both the \( \Gamma_{\text{SAR}} \) and \( G_I^0 \) distributions.
-
-Figure&nbsp;\ref{fig:Plot_GI0_to_gamma1}, shows the entropy of \(G_I^0\) as a function of $\mu$ when \(\alpha \in \left\{-\infty, -20, -8, -3\right\}\).
-Notice that it converges to the entropy of \(\Gamma_{\text{SAR}}\) when \(\alpha\to-\infty\), as expected.
-
-```{r Plot_GI0_to_gamma1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="85%",  fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ when $\\alpha\\to-\\infty$, with $L=8$."}
-
-# Define the Rényi entropy function for Gamma_SAR with corrected parameters
-entropy_renyi_gamma_sar <- function(L, mu, lambda) {
-  entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
-                (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
-  return(entropy)
-}
-
-# Define the Rényi entropy function for G_I^0 with fixed lambda=0.8
-entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
-  if (lambda <= 0 || lambda == 1) {
-    stop("Lambda must be greater than 0 and not equal to 1.")
-  }
-
-  # Calculate gamma based on mu and alpha
-  gamma <- -mu * (alpha + 1)
-  if (any(gamma <= 0)) {
-    stop("Gamma must be positive. Check the values of mu and alpha.")
-  }
-
-  # Calculate a, b, and sum
-  a <- lambda * (L - 1) + 1
-  b <- lambda * (-alpha + 1) - 1
-  ab_sum <- lambda * (L - alpha)
-
-  # Ensure that the arguments for the Gamma functions are positive
-  if (any(a <= 0) || any(b <= 0) || any(ab_sum <= 0)) {
-    stop("Arguments of the Gamma functions must be positive. Check the values of lambda, L, and alpha.")
-  }
-
-  # Calculate the terms
-  term1 <- log(gamma / L)
-
-  term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))
-
-  term3 <- lgamma(a)
-  term4 <- lgamma(b)
-  term5 <- lgamma(ab_sum)
-
-  numerator <- term2 + term3 + term4 - term5
-
-  # Calculate Rényi entropy
-  entropy <- term1 + numerator / (1 - lambda)
-
-  return(entropy)
-}
-
-# Define parameters
-L <- 8
-alphas <- c(-3, -8, -20, -1000)
-alpha_labels <- c(expression(italic(alpha) == -3), 
-                  expression(italic(alpha) == -8), 
-                  expression(italic(alpha) == -20), 
-                  expression(italic(alpha) == -1000))
-
-mu <- seq(0.1, 10, length.out = 500)
-lambda <- 0.8  # Fixed lambda
-
-# Calculate Entropy for G_I^0
-muEntropy <- data.frame()
-
-for (alpha in alphas) {
-  entropies_GI0 <- entropy_GI0_renyi(alpha, mu, L, lambda)
-  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
-}
-
-muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"), value.name = "Entropy")
-
-# Calculate Entropy for Gamma_SAR by setting lambda=0.8
-entropies_gamma <- entropy_renyi_gamma_sar(L, mu, lambda)
-
-Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)
-
-# Prepare data for Gamma_SAR
-Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy_Gamma")
-
-# Plot
-ggplot() +
-  # Plot Entropy Gamma_SAR
-  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = Entropy_Gamma), color = "blue", 
-            linetype = "solid", linewidth = 1.5) + 
-  # Plot Entropy G_I^0 for different alphas
-  geom_line(data = muEntropy.molten, aes(x = mu, y = Entropy, color = alpha), 
-            linetype = "longdash", linewidth = 1) +
-  # Annotate the Gamma_SAR entropy
-  annotate("text", x = max(mu) + 0.2, y = max(Entropy_gamma.molten$Entropy_Gamma), 
-           label = TeX("$H_{\\lambda}$"), 
-           vjust = 0.9, hjust = 0.2, color = "blue") +
-  # Minimal theme
-  theme_minimal() +
-  # Manual color scale with labels
-  scale_color_manual(values = brewer.pal(4, "Dark2"), labels = alpha_labels) +
-  # Labels and titles
-  labs(color = "Roughness", 
-       x = expression(mu), 
-       y = "Rényi Entropy", 
-       linetype = NULL) +
-  # Theme adjustments
-  theme(text = element_text(family = "serif"),
-        legend.position = "bottom") +
-  # Set plot limits if necessary
-  coord_cartesian(xlim = c(0, 10), ylim = c(min(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma), 
-                                            max(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma) + 0.5))
-
-```
-
-## Estimation of Rényi Entropy
-
-Consider a sample \(Z_1, Z_2, \dots, Z_n\) drawn from the distribution \(F\).
-Let \(Z_{(1)} \leq Z_{(2)} \leq \cdots \leq Z_{(n)}\) represent the order statistics of \(Z_1, Z_2, \dots, Z_n\).
-The density estimator based on \(m\) spacing, introduced by Vasicek (1976) and extended by Ebrahimi et al.
-(1994), is given by:
-
-\[
-f_n(Z_{(i)}) = \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}},
-\]
-
-where \(Z_{(i-m)} = Z_{(1)}\) if \(i \leq m\) and \(Z_{(i+m)} = Z_{(n)}\) if \(i \geq n - m\), and \(c_i\) is defined as:
-
-\[
-c_i = 
-\begin{cases}
-\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\
-2, & \text{if } m + 1 \leq i \leq n - m, \\
-\frac{n + m - i}{m}, & \text{if } n - m + 1 \leq i \leq n.
-\end{cases}
-\]
-
-We begin by estimating \(H_\lambda(F)\), as defined in the general form of the Rényi entropy. Note that \(H_\lambda(F)\) can be expressed as:
-
-\[
-H_\lambda(F) = \frac{1}{1 - \lambda} \log \int_S (f(x))^{\lambda - 1} dF(x) = \frac{1}{1 - \lambda} \log \int_0^1 \left( \frac{d}{dt} F^{-1}(t) \right)^{1 - \lambda} dt.
-\]
-
-Following Vasicek (1976) and Ebrahimi et al. (1994) for the estimation of Shannon entropy and utilizing \(f_n(Z_{(i)})\) from the previous equation, \(H_\lambda(F)\) can be estimated by:
-
-\[
-\hat{H}_\lambda(\bm{Z}) = \frac{1}{1 - \lambda} \log \left( \frac{1}{n} \sum_{i=1}^{n} \left( \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}} \right)^{\lambda - 1} \right).
-\]
-
-This estimator allows for the estimation of the Rényi entropy in a non-parametric framework.
-
-## Enhanced estimators with Bootstrap
-
-We use the bootstrap technique to refine the accuracy of non-parametric entropy estimators. 
-In this approach, new data sets are generated by replicate sampling from an existing data set&nbsp;\cite{Michelucci2021}.
-
-Let us assume that the non-parametric entropy estimator
-\(\widehat{H}=\widehat{\theta}(\bm{Z})\) is inherently biased, i.e,:
-\begin{equation}
-\label{Eq:bias1}
-\operatorname{Bias}\big(\widehat{\theta}(\bm{Z})\big) = E\big[\widehat{\theta}(\bm{Z})\big] - \theta \neq 0.
-\end{equation} 
-Our bootstrap-improved estimator is of the form:
-\begin{align*}
-\widetilde{H} &= 2\widehat{\theta}(\bm{Z}) - \frac{1}{B}\sum_{b=1}^B \widehat{\theta}_b(\bm{Z}^{(b)}),
-\end{align*} 
-where \(B\) is the number of observations obtained by resampling from $\bm Z$ with replacement.
-
-# Optimal \(\lambda\) for \(n=49\)
-
-We aim to determine the optimal order \(\lambda\) for the Rényi entropy estimator, specifically for a sample size of \(n=49\).
-To identify this optimal value, we analyze both the Mean Squared Error (MSE) and Bias of the estimator across different values of \(\lambda\).
-Lower MSE and Bias indicate better performance of the estimator in approximating the true entropy.
-
-Based on the results, we find that the optimal value of \(\lambda\) is \(0.9\), as it minimizes the MSE while maintaining a low Bias, as shown in Figure \ref{fig:Plot_optimal}.
-
-```{r Plot_optimal, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",  fig.pos="H", fig.cap="Bias as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=12, fig.height=3.0}
-
-data <- data.frame(
-  Lambda = c(0.90, 0.95, 0.85, 0.99, 1.10, 1.50),
-  Bias = c(0.00158, 0.00413, -0.00250, 0.02077, 0.03751, 0.06512),
-  MSE = c(0.01273, 0.01579, 0.01641, 0.01653, 0.01697, 0.01906)
-)
-# Ordenar el data frame por Lambda para mejorar la visualización
-data <- data[order(data$Lambda), ]
-
-# Gráfico de Bias en función de Lambda #E69F00', '#56B4E9' #00AFBB", "#E7B800"
-bias_plot <- ggplot(data, aes(x = Lambda, y = Bias)) +
-  geom_line(color = "#00AFBB", size = 1) +
-  geom_point(color = "#00AFBB", size = 2) +
-  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") +
-  scale_x_continuous(breaks = seq(0.85, 1.5, by = 0.5)) +
-  labs(title = "", x = "Lambda", y = "Bias") +
-  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
-  theme_minimal()
-
-# Gráfico de MSE en función de Lambda
-mse_plot <- ggplot(data, aes(x = Lambda, y = MSE)) +
-  geom_line(color = "#E69F00", size = 1) +
-  geom_point(color = "#E69F00", size = 2) +
-  scale_x_continuous(breaks = seq(0.85, 1.5, by = 0.5)) + 
-  labs(title = "", x = "Lambda", y = "MSE") +
-  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
-  theme_minimal()
-
-grid.arrange(bias_plot, mse_plot, ncol = 2)
-
-```
-
-We analyzed the performance of these estimators with a Monte Carlo study: \(1000\) samples from the \(\Gamma_{\text{SAR}}\) distribution of size \(n \in \{9, 25, 49, 81, 121\}\), with \(\mu = 10\) and \(L=5\).
-The choice of \(\lambda = 0.9\) is consistent with findings in other scenarios.
-We used \(B=200\) bootstrap samples and the heuristic spacing \(m = \left[\sqrt{n} + 0.5\right]\), as recommended in the literature.
-
-In Figure \ref{fig:Plot_bias_mse_B1}, we show the bias and mean squared error (MSE) of the non-parametric entropy estimator and their respective bootstrap-enhanced version.
-The bootstrap-enhanced estimator demonstrate smaller bias and MSE, reinforcing their effectiveness in providing more reliable entropy estimates.
-
-```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
-set.seed(1234567890, kind = "Mersenne-Twister")
-# Parameters
-sample_sizes <- c(9, 25, 49, 81, 121)
-R <- 500        # Number of replications
-B <- 200         # Number of bootstrap replications
-mu <- 10        # Fixed mu
-L <- 5          # Fixed L
-alpha_values <- c(0.9)  # Lambda values
-
-# Estimators
-estimators <- list(
-  "Renyi Estimator" = renyi_entropy_estimator_v1,
-  "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1
-)
-
-# Run simulations
-results <- calculate_bias_mse_r(sample_sizes, R, B, mu, L, alpha_values, estimators)
-
-# Save results
-save(results, file = "./Data/results_renyi_B1.Rdata")
-
-```
-
-```{r Plot_bias_mse_B1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="80%", fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $\\lambda=0.9$, $\\mu=10$ and $L=5$."}
-
-# Load results
-load("./Data/results_renyi_B1.Rdata")
-
-# Estimators to plot
-estimators_to_plot <- c("Renyi Estimator", "Renyi Estimator Bootstrap")
-latex_estimator_names <- c("Renyi Estimator" = expression("$\\widehat{italic(H)}_{R}$"),# 
-                           "Renyi Estimator Bootstrap" = expression("$\\widetilde{italic(H)}_{R}$"))
-selected_estimators_latex <- latex_estimator_names[estimators_to_plot]
-
-# Generate the combined plot
-combined_plot_renyi <- generate_plot_renyi(results, alpha_values, selected_estimators_latex, ncol = 1, nrow = 1)
-
-# Display the plot
-print(combined_plot_renyi)
-
-```
-
-<!-- ```{r Table_optimal, echo=FALSE, message=FALSE, warning=FALSE, results='asis'} -->
-
-<!-- set.seed(1234567890, kind = "Mersenne-Twister") -->
-<!-- # Parameters -->
-<!-- sample_sizes <- c(49) -->
-<!-- R <- 2000 # Number of replications -->
-<!-- B <- 100         # Number of bootstrap replications -->
-<!-- mu <- 1        # Fixed mu -->
-<!-- L <- 36         # Fixed L -->
-
-<!-- # Estimators -->
-<!-- estimators <- list( -->
-<!--  # "Renyi Estimator" = renyi_entropy_estimator_v1 -->
-<!--   "Renyi Estimator Bootstrap" = bootstrap_renyi_entropy_estimator_v1 -->
-<!-- ) -->
-
-<!-- # Valores de lambda a evaluar -->
-<!-- #lambda_values <- c( 1.1, 1.5, 2.0, 2.5, 3.0, 3.5, 5, 6, 7, 8, 10, 20, 100 ) -->
-<!-- #lambda_values <- c(  0.90,   0.95, 0.96,  0.98, 0.99, 1.1, 1.2,  1.4 ) -->
-
-<!-- #lambda_values <- c(0.8, 0.84, 0.85, 0.86, 0.88, 0.90, 0.91, 0.92, 0.93, 0.94, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4, 2.5, 3, 3.5 ) -->
-<!-- #lambda_values <- c(0.65, 0.66, 0.67, 0.68, 0.69, 0.70, 0.71, 0.72, 0.75, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0 ) -->
-<!-- lambda_values <- c( 0.85, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9,  2.0, 2.5, 3.0) -->
-
-<!-- # Guardar resultados para cada lambda y n = 49 -->
-<!-- results_optimal_lambda <- data.frame(Lambda = numeric(0), Bias = numeric(0), MSE = numeric(0)) -->
-
-<!-- # Calcular sesgo y MSE para cada valor de lambda y el tamaño de muestra de interés (49) -->
-<!-- for (lambda in lambda_values) { -->
-<!--   # Actualizar los valores de alpha en el código original para usar cada lambda -->
-<!--   alpha_values <- c(lambda) -->
-
-<!--   # Calcular sesgo y MSE -->
-<!--   results <- calculate_bias_mse_r(sample_sizes = c(49), R = R, B = B, mu = mu, L = L, alpha_values = alpha_values, estimators = estimators) -->
-
-<!--   # Filtrar resultados para el tamaño de muestra de interés -->
-<!--   result_lambda <- results[results$n == 49, ] -->
-
-<!--   # Agregar los resultados a la tabla de resultados óptimos -->
-<!--   results_optimal_lambda <- rbind(results_optimal_lambda, data.frame( -->
-<!--     Lambda = lambda, -->
-<!--     Bias = mean(result_lambda$Bias), -->
-<!--     MSE = mean(result_lambda$MSE) -->
-<!--   )) -->
-<!-- } -->
-
-<!-- # Ordenar la tabla por MSE y luego por Bias para encontrar el valor óptimo de lambda -->
-<!-- results_optimal_lambda <- results_optimal_lambda[order(results_optimal_lambda$MSE, results_optimal_lambda$Bias), ] -->
-
-<!-- # Mostrar la tabla de resultados -->
-<!-- print(results_optimal_lambda) -->
-
-<!-- ``` -->
-
-# Hypothesis Testing  {#sec:test}
-
-We aim to test the following hypotheses: 
-$$
-\begin{cases}
-  \mathcal{H}_0: \text{ The data come from the } \Gamma_{\text{SAR}}\text{ law},\\ 
-  \mathcal{H}_1:\text{ The data come from the } G_I^0 \text{ distribution}.
-\end{cases}
-$$
-We are testing the hypothesis that the data are fully-developed speckle versus the alternative of data with roughness.
-As for the parametric problem, once it is not possible to define the hypothesis $\mathcal{H}_0=\alpha=-\infty$, it is impossible to solve this problem with parametric inference alternatives (such as likelihood ratio, score, gradient, and Wald hypothesis test).
-The proposed tests to solve this physical problem in SAR systems are described below.
-
-## The Proposed Test Based on Non-parametric Entropy
-
-For a random sample \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) from a distribution $\mathcal{D}$, a test statistic is proposed.
-It is based on an empirical distribution that arises from the difference between non-parametrically estimated entropies $\widetilde{H}(\bm{Z})$ and the analytical entropy of $\Gamma_{\text{SAR}}$&nbsp;\eqref{E:E-gamma} evaluated at the logarithm of the sample mean, where $L\geq 1$ is known.
-
-Hence, the entropy-based test statistic is defined as:
-\begin{equation}
-\label{Eq:test_e}
-S(\bm{Z};L)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right].
-\end{equation}
-
-This test statistic aims to assess the behavior of the data under the null hypothesis using the empirical distribution.
-If the data represent fully-developed speckle, the density should center around zero, i.e., $S(\bm{Z};L)\approx 0$.
-Otherwise, the empirical distribution would shift from zero under the alternative hypothesis, suggesting significant differences and heterogeneous clutter.
-
-We now verify the normality of the data generated by the \(S_{\widetilde{H}_{\text{R}}}(\bm{Z}; L)\) test.
-Figure&nbsp;\ref{fig:Plot_density_A} shows the empirical densities obtained by applying  the  test to different sample sizes drawn from the $\Gamma_{\text{SAR}}$ distribution, where $L$ takes values $\left\{3,5, 18,36\right\}$ and $\mu=1$.
-Additionally, Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean,
-standard deviation&nbsp;(SD), 
-variance&nbsp;(Var), 
-skewness&nbsp;(SK), 
-excessive kurtosis&nbsp;(EK) and 
-Anderson--Darling \(p\) values for normality. 
-Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption.
-A low variance, skewness, and excessive kurtosis of almost zero indicate limited dispersion, asymmetry, and a light tail.
-Normal Q--Q plots confirm no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.
-
-```{r Simulated_density_A, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
-#, cache = TRUE, autodep = TRUE
-set.seed(1234567890, kind = "Mersenne-Twister")
-
-R <- 2000
-mu <- 10
-B <- 100
-lambda <- 0.8
-sample.size <- c(25,49, 81, 121, 200)
-L_values <- c(3,  5, 18, 36)
-
-all_summary_stats <- list()
-all_TestStatistics <- list()
-
-# For each L
-for (L in L_values) {
-  TestStatistics1 <- list()  
-  summary_stats <- data.frame( LValue = character(),
-                              SampleSize = numeric(),
-                              Mean = numeric(),
-                              SD = numeric(),
-                              Variance = numeric(),
-                              #CV= numeric(),
-                              Skewness = numeric(),
-                              Kurtosis = numeric(),
-                              adpvalue = numeric()
-                              )
-
-  for (s in sample.size) {
-    TestStat1 <- numeric(R)
-
-    for (r in 1:R) {
-      z <- gamma_sar_sample(L, mu, s)
-      #z <- gi0_sample(mu, alpha1, L, s)
-      TestStat1[r] <- TestStat <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
-                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
-        #bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-      #TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
-    }
-
-    TestStatistics1[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)
-
-    mean_val <- mean(TestStat1)
-    sd_val <- sd(TestStat1)
-    var_val <- var(TestStat1)
-    skewness_val <- skewness(TestStat1)
-    kurtosis_val <- kurtosis(TestStat1)
-   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
-    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
-    #cv_val <- abs(sd_val / mean_val)
-
-    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
-                                                     SampleSize = s,
-                                                     Mean = mean_val,
-                                                     SD = sd_val,
-                                                     Variance = var_val,
-                                                      #CV = cv_val,
-                                                     Skewness = skewness_val,
-                                                     Kurtosis = kurtosis_val,
-                                                     adpvalue = ad_p_value
-                                                     ))
-
-  }
-
-  all_TestStatistics[[as.character(L)]] <- TestStatistics1
-  all_summary_stats[[as.character(L)]] <- summary_stats
-
-  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/resultsA_", L, ".Rdata"))
-}
-```
-
-```{r Plot_density_A, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="95%", fig.pos="H",  fig.cap="Empirical densities obtained from $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z}; L)$ test under the null hypothesis, with $\\lambda=0.8$ and $\\mu=10$.", fig.width=6, fig.height=5.0}
-
-theme_set(theme_minimal() +
-            theme(text = element_text(family = "serif"),
-                  legend.position = "bottom",
-                  legend.text = element_text(angle = 0, vjust = 0.5)))
-
-all_plots <- list()
-
-for (L in L_values) {
-  load(paste0("./Data/resultsA_", L, ".Rdata"))
-
-  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
-  combined_data$L <- L
-
-  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
-    geom_line(stat = "density", linewidth = 1.2) +
-    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
-    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
-    labs(x = "Test Statistics", y = "Density") +
-    ggtitle(bquote(italic(L) == .(L))) +
-    theme(plot.title = element_text(hjust = 0.5))#titulo centrado
-
-  if (!any(L == L_values)) {
-    p = p
-  }
-
-  all_plots[[as.character(L)]] <- p
-}
-
-combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
-  plot_layout(guides = "collect")
-
-print(combined_plot)
-```
-
-```{r Table_statistic1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-
-load("./Data/resultsA_3.Rdata")
-summary_stats_3 <- all_summary_stats[["3"]]
-
-load("./Data/resultsA_5.Rdata")
-summary_stats_5 <- all_summary_stats[["5"]]
-
-load("./Data/resultsA_18.Rdata")
-summary_stats_18 <- all_summary_stats[["18"]]
-
-load("./Data/resultsA_36.Rdata")
-summary_stats_36 <- all_summary_stats[["36"]]
-
-combined_summary_stats <- rbind(
-  transform(summary_stats_3),
-  transform(summary_stats_5),
-  transform(summary_stats_18),
-  transform(summary_stats_36)
-
-)
-colnames(combined_summary_stats) <- c("$\\bm{L}$", "$\\bm{n}$", "\\textbf{Mean}", "\\textbf{SD}", "\\textbf{Var}", "\\textbf{SK}", "\\textbf{EK}", "$p$-\\textbf{value}")
-
-# LaTeX notation 
-combined_summary_stats[] <- lapply(combined_summary_stats, function(x) {
-  if (is.numeric(x)) {
-    if (all(x %% 1 == 0)) {
-      formatted_numbers <- sprintf("$%d$", x)
-    } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
-    }
-    return(formatted_numbers)
-  } else {
-    return(x)
-  }
-})
-
-table_result_combined <- knitr::kable(
-  combined_summary_stats,
-  caption = "Descriptive analysis of $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z}; L)$, with $L\\in\\left\\{3,5, 18,36\\right\\}$ and $\\mu=10$.",
-  format = "latex",
-  #longtable = T,
-  booktabs = TRUE,
-  align = "ccrrrrrr",
-  escape = FALSE,
-  digits = 4,
-  label = "table_stat_combined",
-  centering = FALSE,
-  table.envir = "table", position="H", linesep = "") %>%
-  #table.env = 'table*' # to span multiple columns
-  collapse_rows(latex_hline = "major", valign = "middle") %>%
-  row_spec(0,  align = "c")%>%
-  kable_styling(latex_options = "scale_down")%>%
-  kable_styling( full_width = T)%>%
-  kable_styling(latex_options = c("repeat_header"))
-
-print(table_result_combined)
-```
-
-```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=81$.
-The dashed green lines in the Q--Q plots represent theoretical expected quantiles for a normal distribution.
-Variations in the scales of the axes reflect differences in the range of values across datasets.", fig.width=6, fig.height=5}
-
-theme_set(theme_minimal() +
-            theme(text = element_text(family = "serif"),
-                  legend.position = "bottom",
-                  legend.text = element_text(angle = 0, vjust = 0.5)))
-
-# Load saved results
-load("./Data/resultsA_3.Rdata")
-load("./Data/resultsA_5.Rdata")
-load("./Data/resultsA_18.Rdata")
-load("./Data/resultsA_36.Rdata")
-
-# Specific sample size
-selected_sample_size <- 81
-
-# 
-ggplot_list <- list()
-
-#  L
-for (L in c(3, 5, 18, 36)) {
-  TestStatistics1 <- all_TestStatistics[[as.character(L)]]
-
-  # 
-  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
-    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
-                aes(sample = Test_Statistics)) +
-      geom_qq(col = "blue", shape = 20) +
-      geom_qq_line(col = "darkgreen", linetype = 2) +
-      labs(title = bquote(italic(L) == .(L)),
-           x = "Theoretical Quantiles",
-           y = "Sample Quantiles") +
-      theme(plot.title = element_text(hjust = 0.5))#titulo centrado
-
-    ggplot_list[[as.character(L)]] <- p
-  } else {
-    warning(paste("No size sample", selected_sample_size, " L =", L))
-  }
-}
-combined_plot1 <- wrap_plots(ggplot_list, ncol = 2, nrow = 2) +
-  plot_layout(guides = "collect")
-
-print(combined_plot1)
-```
-
-We also evaluated the test's power by performing $1000$ simulations under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$ and $\alpha=-2$.
-The power generally improves with increasing sample size and number of looks.
-The results are shown in Table&nbsp;\ref{tab:table_size_power}.
-
-```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
-set.seed(1234567890, kind = "Mersenne-Twister")
-# 
-calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
-  epsilon <- test_statistic / sigma_W
-  p_value <- 2 * (1 - pnorm(abs(epsilon)))
-
-  return(p_value < alpha_nominal)  
-}
-R <- 1000
-mu <- 1
-B <- 100
-lambda <- 0.9
-L_values <- c(  5, 8, 18)
-sample_sizes <- c( 25, 49, 81, 121)
-alpha_nominals <- c(0.01, 0.05, 0.1)
-results <- data.frame()
-for (L in L_values) {
-  for (alpha_nominal in alpha_nominals) {
-    TestStatistics <- NULL
-    mean_entropy <- numeric(length(sample_sizes))
-    sd_entropy <- numeric(length(sample_sizes))
-
-    for (s in sample_sizes) {
-      TestStat <- numeric(R)
-
-      for (r in 1:R) {
-        z <- gamma_sar_sample(L, mu, s)
-        TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))
-
-        #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-        #TestStat[r] <- bootstrap_correa_estimator(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-      }
-      mean_entropy[sample_sizes == s] <- mean(TestStat)
-      sd_entropy[sample_sizes == s] <- sd(TestStat)
-
-      TestStatistics <- rbind(TestStatistics, data.frame("L" = rep(L, R), "Sample_Size" = rep(s, R), "Test_Statistics" = TestStat))
-    }
-
-    mu_W <- mean_entropy
-    sigma_W <- sqrt(sd_entropy^2)
-
-    p_values <- apply(TestStatistics, 1, function(row) {
-      calculate_p_value(row["Test_Statistics"], mu_W[sample_sizes == row["Sample_Size"]], sigma_W[sample_sizes == row["Sample_Size"]], alpha_nominal)
-    })
-
-    result <- data.frame("L" = TestStatistics$L, "Sample_Size" = TestStatistics$Sample_Size, "Alpha_Nominal" = alpha_nominal, "P_Value" = p_values)
-    results <- rbind(results, result)
-  }
-}
-save(results, file = "./Data/type_I_results.Rdata")
-```
-
-```{r Simulated_power, echo=FALSE, message=FALSE}
-set.seed(1234567890, kind = "Mersenne-Twister")
-calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
-  epsilon <- test_statistic  / sigma_W
-  p_value <- 2 * (1 - pnorm(abs(epsilon)))
-
-  return(p_value)
-}
-calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
-  type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
-  return(type_II_error_rate)
-}
-# Function to calculate power for different L values and alpha_nominals
-calculate_power <- function(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals) {
-  results <- data.frame()
-
-  for (L in L_values) {
-    for (alpha_nominal in alpha_nominals) {
-      TestStatistics <- list()
-      mean_entropy <- numeric(length(sample_sizes))
-      sd_entropy <- numeric(length(sample_sizes))
-
-      for (s in sample_sizes) {
-        TestStat <- numeric(R)
-
-        for (r in 1:R) {
-          z <- gi0_sample(mu, -2, L, s)
-          TestStat[r] <-bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1)+(lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +log(mean(z))-log(L))
-          #TestStat[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
-          #TestStat[r] <- bootstrap_correa_estimator_log_mean(z, B) - (L - log(L) + lgamma(L) + (1 - L) * digamma(L))
-        }
-
-        mean_entropy[sample_sizes == s] <- mean(TestStat)
-        sd_entropy[sample_sizes == s] <- sd(TestStat)
-
-        TestStatistics[[as.character(s)]] <- TestStat
-      }
-
-      mu_W <-  mean_entropy  
-      sigma_W <- sqrt(sd_entropy^2)
-
-      p_values <- lapply(TestStatistics, function(TestStat) {
-        apply(data.frame("Test_Statistics" = TestStat), 1, function(row) {
-          calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
-        })
-      })
-
-      type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
-        calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
-      })
-
-      power <- 1 - type_II_error_rates
-
-      result_row <- data.frame(
-        L = L,
-        alpha_nominal = alpha_nominal,
-        Sample_Size = sample_sizes,
-        power = power
-      )
-
-      results <- rbind(results, result_row)
-    }
-  }
-
-  return(results)
-}
-R <- 1000
-mu <- 1
-L_values <- c( 5,  8, 18)
-B <- 100
-lambda<- 0.9
-sample_sizes <- c(25, 49, 81, 121)
-alpha_nominals <- c(0.01, 0.05, 0.1)
-results_power <- calculate_power(R, mu, L_values, B,lambda, sample_sizes, alpha_nominals)
-save(results_power, file = "./Data/results_power.Rdata")
-```
-
-```{r Table_size_and_power, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#cat("\\setlength{\\tabcolsep}{4pt}\n")
-load("./Data/type_I_results.Rdata")
-type_I_error_rates <- tapply(results$P_Value, INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal), FUN = function(p_values) {
-  sum(p_values) / length(p_values)  
-})
-type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
-colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
-spread_results <- spread(type_I_error_results, key = Alpha_Nominal, value = Type_I_Error_Rate)
-spread_results <- spread_results %>% 
-  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
-load("./Data/results_power.Rdata")
-summary_stats <- results_power %>%
-  spread(key = alpha_nominal, value = power) %>%
-  select(L, Sample_Size, `0.01`, `0.05`, `0.1`)
-combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size"))
-combined_results <- combined_results %>% 
-  arrange(L, Sample_Size)
-combined_results <- combined_results %>% 
-  select(L, Sample_Size, `0.01.x`, `0.05.x`, `0.1.x`, `0.01.y`, `0.05.y`, `0.1.y`)
-colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$", "$\\bm{1\\%}$", "$\\bm{5\\%}$", "$\\bm{10\\%}$")
-# LaTeX notation 
-combined_results[] <- lapply(combined_results, function(x) {
-  if (is.numeric(x)) {
-    if (all(x %% 1 == 0)) {
-      formatted_numbers <- sprintf("$%d$", x)
-    } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.4f$", x), sprintf("$\\phantom{-}%.4f$", x))
-    }
-    return(formatted_numbers)
-  } else {
-    return(x)
-  }
-})
-table_combined_result <- knitr::kable(
-  combined_results,
-  caption = "Size and Power of the $S_{\\widetilde{H}_{\\text{R}}}(\\bm{Z})$ test statistic.",
-  format = "latex",
-  booktabs = TRUE,
-  align = "ccccccccc",
-  escape = FALSE,
-  digits = 4,
-  label = "table_size_power",
-  centering = FALSE,
-  table.envir = "table", position="htb", linesep = "")%>%
-  add_header_above(c(" ", " ", "Size" = 3,  "Power" = 3)) %>%
-  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
-  row_spec(0,  align = "c")%>%
-  kable_styling(latex_options = "scale_down")%>%
-  kable_styling( full_width = T)
-
-print(table_combined_result)
-```
-
-# Results
-
-This section presents the simulations we performed to evaluate the proposed test statistics' performance, followed by applications to SAR data.
-
-## Simulated Data
-```{r sim_Phantom, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Synthetic dataset: (\\textbf{a}) Phantom.
-(\\textbf{b}) Simulated image, varying $\\alpha$ and $\\mu$, with $L=5$.
-',  fig.subcap=c('', ''), out.width = c( "60mm","80mm"),  fig.ncol=2, fig.width = 30, fig.height = 20}
-knitr::include_graphics("./figs/Phantom1.png")
-knitr::include_graphics("./figs/Phantom_labels.pdf")
-```
-
-```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=5$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-
-knitr::include_graphics("./figs/Entropy_Phantom_4_z1_200.png")
-knitr::include_graphics("./figs/H_pvalue_Phantom_4_z1_200b.png")
-knitr::include_graphics("./figs/H_005_Phantom_4_z1_AO_200b.png")
-
-```
-
-```{r sim_renyi1, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=5$, $\\lambda=0.9$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-#knitr::include_graphics("./figs/sim_renyi_100.png")
-knitr::include_graphics("./figs/Entropy_Phantom_4_renyi_B200_w7_L5_09.png")
-knitr::include_graphics("./figs/H_pvalue_Phantom_4_renyi_B200_w7_L5_09.png")
-knitr::include_graphics("./figs/H_005_Phantom_4_renyi_B200_w7_L5_09.png")
-
-```
-
-```{r real_SAR_Images_rotterdam, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=1$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-
-knitr::include_graphics("./figs/Entropy_AO_Rotterdam_1024.png")
-knitr::include_graphics("./figs/H_pvalue_AO_Rotterdam_1024.png")
-knitr::include_graphics("./figs/H_005_AO_Rotterdam_1024.png")
-
-```
-
-```{r sim_rotter, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=1$, $\\lambda=2.0$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-#knitr::include_graphics("./figs/sim_renyi_100.png")
-knitr::include_graphics("./figs/results_rotterdam_renyi_w7_2_0_07.png")
-knitr::include_graphics("./figs/H_pvalue_results_rotterdam_renyi_w7_2_0_07.png")
-knitr::include_graphics("./figs/H_005_results_rotterdam_renyi_w7_2_0_L1.png")
-
-```
-
-```{r mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Shannon entropy, $L=18$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-
-knitr::include_graphics("./figs/Entropy_Mexico_512_18L_AO_200b.png")
-knitr::include_graphics("./figs/H_pvalue_renyi_512_w7_L18_b200_090.png")
-knitr::include_graphics("./figs/H_005__Mexico_512_18L_AO_200b.png")
-
-```
-
-```{r sim_mexixo, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rényi Entropy, $L=18$, $\\lambda=0.9$, $n=49$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5}
-#knitr::include_graphics("./figs/sim_renyi_100.png")
-knitr::include_graphics("./figs/Entropy_renyi_512_w7_L18_b200_090.png")
-knitr::include_graphics("./figs/H_pvalue_Mexico_512_18L_AO_200b.png")
-knitr::include_graphics("./figs/H_005_results_renyi_mexico512_w7_L18_b200_090.png")
-
-```
-
-## Analysis of Performance
-
-The performance of the proposed methods was evaluated using the Mean Squared Error (MSE) as a global metric to compare the detection accuracy of heterogeneous regions.
-First, test statistics were computed for both Shannon and Rényi entropy-based approaches across the image using a sliding window of size \(7 \times 7\).
-Then, p-values were calculated for each window based on the distribution of the test statistics, assuming a null hypothesis of homogeneity.
-A significance level of \(\alpha = 0.05\) was applied to construct binary maps, where pixels with \(p \leq \alpha\) were classified as heterogeneous (value 1), and pixels with \(p > \alpha\) were classified as homogeneous (value 0).
-
-The MSE values indicate that the Rényi entropy-based approach outperformed the Shannon entropy-based method, with a lower global MSE (Rényi: $0.1436$ vs.
-Shannon: $0.2066$).
-This result suggests that Rényi entropy captures heterogeneity more effectively.
-Additionally, local error maps comparing the binary predictions with the ground truth show that the Rényi entropy-based method has fewer misclassifications (errors) across the image, particularly in heterogeneous regions, further supporting its superior performance.
-
-<!-- ```{r sim_renyi2, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Simulated image with Rényi Entropy, $L=5$, $\\lambda=0.75$, $n=81$.',  fig.subcap=c(' ', ' ',' '), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-<!-- #knitr::include_graphics("./figs/sim_renyi_100.png") -->
-<!-- knitr::include_graphics("./figs/Entropy_sim_diff_renyi_100_075.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_sim_renyi_100_075.png") -->
-<!-- knitr::include_graphics("./figs/H_005_sim_renyi_075_100w.png") -->
-
-<!-- ``` -->
-
-<!-- ```{r real_images_test_Illinois3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Shannon Entropy, Illinois-Region 1.',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-
-<!-- knitr::include_graphics("./figs/Entropy_lake_512_36L_AO_100b.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_lake_512_36L_AO_100b.png") -->
-<!-- knitr::include_graphics("./figs/H_005_lake_512_36L_AO_100b.png") -->
-<!-- ``` -->
-
-<!-- ```{r real_images_test_Illinois5, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 1, $\\lambda=0.8$, $n=81$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-
-<!-- knitr::include_graphics("./figs/Entropy_illinois1_512_renyi_b200_08_L36_w9.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_illinois1_512_renyi_b200_08_L36_w9.png") -->
-<!-- knitr::include_graphics("./figs/H_005_illinois1_512_renyi_b200_08_L36_w9.png") -->
-<!-- ``` -->
-
-<!-- ```{r real_images_test_Illinois4, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 1, $\\lambda=0.8$, $n=121$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-
-<!-- knitr::include_graphics("./figs/Entropy_illinois1_512_renyi_b100_08_L36_w11.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_illinois1_512_renyi_b100_08_L36_w11.png") -->
-<!-- knitr::include_graphics("./figs/H_005_illinois1_512_renyi_b100_08_L36_w11.png") -->
-<!-- ``` -->
-
-<!-- ```{r real_images_test_Illinois, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Shannon Entropy, Illinois-Region 2.',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-
-<!-- knitr::include_graphics("./figs/Entropy_Illinois_1024_36L_AO_200b.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_Illinois_1024_36L_AO_200b.png") -->
-<!-- knitr::include_graphics("./figs/H_005_pvalues_Illinois_1024_36L_AO_200b.png") -->
-<!-- ``` -->
-
-<!-- ```{r real_images_test_Illinois2, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rényi Entropy, Illinois-Region 2, with $L=36$, $\\lambda=0.75$, $n=121$',  fig.subcap=c('', '', ''), out.width = c("55mm","55mm", "55mm"),  fig.ncol=3, fig.width = 30, fig.height = 20,fig.hspace=1.5} -->
-
-<!-- knitr::include_graphics("./figs/Entropy_illinois_1024_renyi_b200_075_L36_w11.png") -->
-<!-- knitr::include_graphics("./figs/H_pvalue_illinois_1024_renyi_b200_075_L36_w11.png") -->
-<!-- knitr::include_graphics("./figs/H_005_illinois_1024_renyi_b200_075_L36_w11.png") -->
-<!-- ``` -->
-```{=html}
-<!--
-# References
-\setlength{\parindent}{-0.2in}
-\setlength{\leftskip}{0.2in}
-\setlength{\parskip}{8pt}
-\vspace*{-0.2in}
-\noindent
--->
-```
 
@@
 \]
+
+# Derivation of the Rényi Entropy for the \(\Gamma_{\text{SAR}}(L, \mu)\) Distribution.
+
+Let \(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) with pdf
+\begin{align}
+f_{\Gamma_{\text{SAR}}}(z; L, \mu)
+&= \frac{L^L}{\Gamma(L)\,\mu^L}\,z^{\,L - 1} 
+  \exp\!\Bigl(-\tfrac{L z}{\mu}\Bigr),
+\label{eq:pdf}
+\end{align}
+Define
+\begin{align}
+I 
+&= \int_{0}^{\infty}\!\bigl[f_{\Gamma_{\text{SAR}}}(z; L,\mu)\bigr]^\lambda \,dz 
+ = \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
+   \int_{0}^{\infty} 
+   z^{\,\lambda\,(L-1)} \exp\!\Bigl(-\tfrac{\lambda\,L}{\mu}\,z\Bigr)\,dz.
+\label{eq:I}
+\end{align}
+Using the Gamma integral 
+\(\displaystyle
+  \int_{0}^{\infty} x^{p-1} e^{-qx}\,dx 
+   = \frac{\Gamma(p)}{q^p},\)
+with \(p = \lambda L - \lambda + 1\) and \(q = \tfrac{\lambda L}{\mu}\), it follows that
+\begin{align}
+I 
+&= \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
+   \frac{\Gamma(\lambda L - \lambda + 1)}
+        {\Bigl(\tfrac{\lambda\,L}{\mu}\Bigr)^{\lambda L - \lambda + 1}}.
+\label{eq:Iresult}
+\end{align}
+Taking the natural logarithm,
+\begin{align}
+\ln I 
+&= \lambda\!\Bigl(L \ln L - L \ln \mu - \ln \Gamma(L)\Bigr)
+   \;+\; \ln\Gamma\!\bigl(\lambda L - \lambda + 1\bigr)
+   \;-\; \bigl(\lambda L - \lambda + 1\bigr)\,\Bigl(\ln(\lambda L) - \ln\mu\Bigr).
+\label{eq:lnI}
+\end{align}
+The Rényi entropy is 
+\begin{align}
+H_\lambda(Z) 
+&= \frac{1}{\,1 - \lambda\,} \,\ln I.
+\label{eq:RenyiDefinition}
+\end{align}
+By expanding \eqref{eq:lnI} and collecting terms in \(\ln L\) and \(\ln \mu\), one obtains
+\begin{align}
+\ln I 
+&= (1 - \lambda)\bigl(\ln \mu - \ln L\bigr)
+   \;-\;\lambda\,\ln \Gamma(L)
+   \;+\;\ln\Gamma\!\bigl(\lambda(L-1)+1\bigr)
+   \;-\;\bigl(\lambda(L-1)+1\bigr)\,\ln \lambda.
+\label{eq:lnIsimplified}
+\end{align}
+Substituting \eqref{eq:lnIsimplified} into \eqref{eq:RenyiDefinition} and simplifying,
+\begin{multline}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr) 
+= \ln \mu - \ln L 
+  + \frac{1}{\,1-\lambda\,}
+  \Bigl[
+    -\lambda\,\ln\Gamma(L)
+    + \ln\Gamma\!\bigl(\lambda\,(L-1)+1\bigr)
+\\
+    - \bigl(\lambda\,(L-1)+1\bigr)\,\ln\lambda
+  \Bigr].
+\label{eq:RenyiFinal}
+\end{multline}
+This completes the derivation.
+
+# Derivation of the Rényi Entropy for the $\Gamma_{\text{SAR}}(L, \mu)$ Distribution.
+
+Let $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ with pdf
+\begin{align*}
+f_{\Gamma_{\text{SAR}}}(z; L, \mu)
+&= \frac{L^L}{\Gamma(L)\,\mu^L}\,z^{\,L - 1} 
+  \exp\!\Bigl(-\tfrac{L z}{\mu}\Bigr).
+\end{align*}
+Define
+\begin{align*}
+I 
+&= \int_{0}^{\infty}\!\bigl[f_{\Gamma_{\text{SAR}}}(z; L,\mu)\bigr]^\lambda \,dz 
+ = \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
+   \int_{0}^{\infty} 
+   z^{\,\lambda\,(L-1)} \exp\!\Bigl(-\tfrac{\lambda\,L}{\mu}\,z\Bigr)\,dz.
+\end{align*}
+Using the Gamma integral 
+$\displaystyle
+  \int_{0}^{\infty} x^{p-1} e^{-qx}\,dx 
+   = \frac{\Gamma(p)}{q^p},$
+with $p = \lambda L - \lambda + 1$ and $q = \tfrac{\lambda L}{\mu}$, it follows that
+\begin{align*}
+I 
+&= \biggl(\frac{L^L}{\Gamma(L)\,\mu^L}\biggr)^{\!\lambda}
+   \frac{\Gamma(\lambda L - \lambda + 1)}
+        {\Bigl(\tfrac{\lambda\,L}{\mu}\Bigr)^{\lambda L - \lambda + 1}}.
+\end{align*}
+Taking the natural logarithm,
+\begin{align}
+\ln I 
+&= \lambda\!\Bigl(L \ln L - L \ln \mu - \ln \Gamma(L)\Bigr)
+   \;+\; \ln\Gamma\!\bigl(\lambda L - \lambda + 1\bigr)
+   \;-\; \bigl(\lambda L - \lambda + 1\bigr)\,\Bigl(\ln(\lambda L) - \ln\mu\Bigr).
+\label{eq:lnI}
+\end{align}
+The Rényi entropy is 
+\begin{align}
+H_\lambda(Z) 
+&= \frac{1}{\,1 - \lambda\,} \,\ln I.
+\label{eq:RenyiDefinition}
+\end{align}
+By expanding \eqref{eq:lnI} and collecting terms in $\ln L$ and $\ln \mu$, one obtains
+\begin{align}
+\ln I 
+&= (1 - \lambda)\bigl(\ln \mu - \ln L\bigr)
+   \;-\;\lambda\,\ln \Gamma(L)
+   \;+\;\ln\Gamma\!\bigl(\lambda(L-1)+1\bigr)
+   \;-\;\bigl(\lambda(L-1)+1\bigr)\,\ln \lambda.
+\label{eq:lnIsimplified}
+\end{align}
+Substituting \eqref{eq:lnIsimplified} into \eqref{eq:RenyiDefinition} and simplifying,
+\begin{multline}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr) 
+= \ln \mu - \ln L 
+  + \frac{1}{\,1-\lambda\,}
+  \Bigl[
+    -\lambda\,\ln\Gamma(L)
+    + \ln\Gamma\!\bigl(\lambda\,(L-1)+1\bigr)
+    - \bigl(\lambda\,(L-1)+1\bigr)\,\ln\lambda
+  \Bigr].
+\label{eq:RenyiFinal}
+\end{multline}
+This completes the derivation.
+
+# Derivation of the Rényi Entropy for the $G_I^0$ Distribution
+
+The Rényi entropy of order $\lambda$ for a continuous random variable $Z$ with density $f_Z(z)$ is given by
+\begin{align}
+H_\lambda(Z) 
+&= \frac{1}{\,1 - \lambda\,} \,\ln \biggl( \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz \biggr), 
+\quad \lambda > 0, \,\lambda \neq 1.
+\label{eq:RenyiDefinition}
+\end{align}
+
+For $Z \sim G_I^0(\alpha, \gamma, L)$, the density function is
+\begin{align}
+f_{G_I^0}(z; \alpha, \gamma, L) 
+&= \frac{L^L\,\Gamma(L-\alpha)}{\bigl[-\gamma\bigr]^{\alpha}\,\Gamma(-\alpha)\,\Gamma(L)}
+   \,\frac{z^{\,L-1}}{\bigl(\gamma + L\,z\bigr)^{\,L-\alpha}}
+\label{eq:pdfGI0}
+\end{align}
+where $\gamma > 0$ in this parametrization (noting $\gamma = -\mu(\alpha+1)$ for a negative $\mu$ when $\alpha<-1$).
+
+Raising $f_Z(z)$ to the power $\lambda$ and substituting into the entropy integral,
+\[
+I 
+= \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz 
+= C^\lambda \int_{0}^{\infty} 
+  \frac{z^{\lambda(L - 1)}}
+       {\bigl(\gamma + L z\bigr)^{\,\lambda(L - \alpha)}} \, dz,
+\]
+where 
+\[
+C = \frac{L^L \,\Gamma(L - \alpha)}{\gamma^\alpha \,\Gamma(-\alpha)\,\Gamma(L)}.
+\]
+Using the change of variables $t = \frac{Lz}{\gamma}$, $z = \frac{\gamma\,t}{L}$, $dz = \frac{\gamma}{L}\,dt$, one obtains
+\[
+I 
+= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
+  \int_{0}^{\infty} \frac{t^{\lambda(L - 1)}}{\bigl(1 + t\bigr)^{\lambda(L - \alpha)}} \, dt.
+\]
+The integral is expressed in terms of the Beta function
+\[
+\int_{0}^{\infty} \frac{t^{\,a - 1}}{(1 + t)^{\,a + b}}\,dt
+= B(a,b),
+\]
+with $a = \lambda(L - 1) + 1$ and $b = \lambda(-\alpha + 1) - 1$. Thus
+\begin{align}
+I 
+&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}} \,B(a,b).
+\label{eq:Iresult}
+\end{align}
+By simplifying powers of $\gamma$ and $L$, and substituting 
+$C^\lambda = L^{\lambda L} \,\gamma^{-\alpha \lambda}
+   \Bigl(\frac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,$
+one obtains
+\[
+I 
+= \gamma^{\,1 - \lambda}\,L^{\,\lambda - 1}
+  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^{\!\lambda}
+  B(a,b).
+\]
+Hence, by definition \eqref{eq:RenyiDefinition},
+\[
+H_\lambda(Z) 
+= \frac{1}{\,1 - \lambda\,}\,
+  \ln\Bigl[\gamma^{\,1 - \lambda}\,L^{\,\lambda - 1}
+  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^{\!\lambda}
+  B(a,b)\Bigr].
+\]
+Rewriting,
+\[
+H_\lambda(G_I^0 ) 
+= \ln\!\Bigl(\tfrac{\gamma}{\,L}\Bigr)
+  \;+\; \frac{1}{\,1 - \lambda\,}
+  \Bigl[\,\lambda\bigl(\ln \Gamma(L - \alpha) - \ln \Gamma(-\alpha) - \ln \Gamma(L)\bigr)
+         \;+\;\ln B(a,b)\Bigr].
+\]
+Using the property $\ln B(a,b) = \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a+b)$, where 
+$a + b = \lambda(L - \alpha),$ we get
+\[
+H_\lambda(G_I^0 ) 
+= \ln\!\Bigl(\tfrac{\gamma}{L}\Bigr)
+  + \frac{1}{\,1 - \lambda\,}\biggl[\lambda\Bigl(\ln \Gamma(L - \alpha) 
+     - \ln \Gamma(-\alpha) 
+     - \ln \Gamma(L)\Bigr)
+  + \ln \Gamma(a) 
+  + \ln \Gamma(b) 
+  - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)\biggr].
+\]
+Finally, recalling $\mu = -\frac{\gamma}{\alpha + 1}$ gives $\gamma = -\mu(\alpha+1)$, and substituting into the above expression:
+\begin{multline}
+H_\lambda(G_I^0 ) 
+= \ln \mu + \ln(-\alpha - 1) - \ln L \\
++ \frac{1}{\,1 - \lambda\,}\Bigl[
+   \lambda\bigl(\ln \Gamma(L - \alpha) 
+       - \ln \Gamma(-\alpha) 
+       - \ln \Gamma(L)\bigr)
+   + \ln \Gamma\bigl(\lambda(L - 1) + 1\bigr) 
+   + \ln \Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) 
+   - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
+\Bigr].
+\label{eq:RenyiFinalGI0}
+\end{multline}
+
+# Derivation of the Rényi Entropy for the $G_I^0$ Distribution
+
+The Rényi entropy of order $\lambda$ for a continuous random variable $Z$ with density $f_Z(z)$ is given by
+\begin{align}
+H_\lambda(Z) 
+&= \frac{1}{\,1 - \lambda\,} \,\ln \Bigl( \int_{0}^{\infty} [f_Z(z)]^\lambda \, dz \Bigr),
+\quad \lambda > 0, \;\lambda \neq 1.
+\label{eq:RenyiDefinition}
+\end{align}
+
+For $Z \sim G_I^0(\alpha, \gamma, L)$, the density function is
+\begin{align}
+f_{G_I^0}(z; \alpha, \gamma, L) 
+&= \frac{L^L\,\Gamma(L-\alpha)}{\bigl[-\gamma\bigr]^{\alpha}\,\Gamma(-\alpha)\,\Gamma(L)}
+   \,\frac{z^{\,L-1}}{\bigl(\gamma + L\,z\bigr)^{\,L-\alpha}}
+\label{eq:pdfGI0}
+\end{align}
+where $\gamma > 0$ in this parametrization (equivalently $\gamma = -\mu(\alpha+1)$ for a negative $\mu$ when $\alpha<-1$).
+
+\medskip
+
+\noindent
+\textbf{Definition of the integral.}
+Define
+\begin{align}
+I 
+&= \int_{0}^{\infty} \bigl[ f_{G_I^0}(z; \alpha, \gamma, L) \bigr]^\lambda \,dz 
+= C^\lambda \int_{0}^{\infty} 
+  \frac{z^{\,\lambda(L - 1)}}
+       {\bigl(\gamma + L\,z\bigr)^{\,\lambda(L - \alpha)}} 
+  \, dz,
+\label{eq:I}
+\end{align}
+where
+\[
+C 
+= \frac{L^L \,\Gamma(L - \alpha)}{\gamma^\alpha \,\Gamma(-\alpha)\,\Gamma(L)}.
+\]
+
+To evaluate $I$, we use the change of variables $t = \tfrac{Lz}{\gamma}$, $z = \tfrac{\gamma\,t}{L}$, $dz = \tfrac{\gamma}{L}\,dt$. This gives
+\begin{align}
+I 
+&= C^\lambda 
+   \int_{0}^{\infty} 
+   \Bigl(\tfrac{\gamma\,t}{L}\Bigr)^{\lambda(L - 1)}
+   \,\Bigl(\gamma + L\,\tfrac{\gamma\,t}{L}\Bigr)^{-\lambda(L - \alpha)} 
+   \,\tfrac{\gamma}{L}\, dt
+\nonumber\\
+&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
+  \int_{0}^{\infty} 
+  \frac{t^{\lambda(L - 1)}}{(1 + t)^{\lambda(L - \alpha)}}
+  \, dt.
+\end{align}
+Using the Beta-function result 
+\[
+\int_{0}^{\infty} \frac{t^{\,a - 1}}{(1 + t)^{\,a + b}} \, dt 
+= B(a,b),
+\]
+with $a = \lambda(L - 1) + 1$ and $b = \lambda(-\alpha + 1) - 1$, we have
+\begin{align}
+I 
+&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
+   \,B(a,b).
+\label{eq:Ibeta}
+\end{align}
+Next, we simplify $\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}$ and 
+$L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}$. 
+Since 
+\[
+C^\lambda 
+= \Bigl(\tfrac{L^L}{\gamma^\alpha \,\Gamma(-\alpha)\,\Gamma(L)}\,\Gamma(L - \alpha)\Bigr)^\lambda
+= L^{\lambda L} \,\gamma^{-\alpha \lambda}
+  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,
+\]
+we obtain
+\[
+I
+= \gamma^{\,1 - \lambda}\,L^{\,\lambda - 1}
+  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
+  \;B(a,b).
+\]
+
+\smallskip
+
+\noindent
+\textbf{Rényi entropy.}
+By \eqref{eq:RenyiDefinition},
+\[
+H_\lambda(Z) 
+= \frac{1}{\,1 - \lambda\,} \,\ln I
+= \frac{1}{\,1 - \lambda\,}
+  \,\ln\!\Bigl[
+    \gamma^{\,1 - \lambda}\,
+    L^{\,\lambda - 1}
+    \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
+    B(a,b)
+  \Bigr].
+\]
+Hence,
+\[
+H_\lambda(G_I^0)
+= \ln\!\Bigl(\tfrac{\gamma}{\,L}\Bigr)
+  \;+\; \frac{1}{\,1 - \lambda\,}
+  \Bigl[\,
+    \lambda\bigl(\ln \Gamma(L - \alpha) 
+          - \ln \Gamma(-\alpha) 
+          - \ln \Gamma(L)\bigr)
+    \;+\; \ln B(a,b)
+  \Bigr].
+\]
+Using the property 
+$\ln B(a,b) = \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b)$, 
+where $a + b = \lambda(L - \alpha)$, one obtains
+\[
+H_\lambda(G_I^0)
+= \ln\!\Bigl(\tfrac{\gamma}{L}\Bigr)
+ + \frac{1}{\,1 - \lambda\,}
+   \Bigl[
+     \lambda\bigl(\ln \Gamma(L - \alpha) 
+            - \ln \Gamma(-\alpha) 
+            - \ln \Gamma(L)\bigr)
+   + \ln \Gamma(a)
+   + \ln \Gamma(b)
+   - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
+   \Bigr].
+\]
+Finally, noting $\mu = -\tfrac{\gamma}{\alpha + 1}$ implies $\gamma = -\mu(\alpha + 1)$, and substituting, we get
+\begin{multline}
+H_\lambda(G_I^0)
+= \ln \mu \;+\; \ln(-\alpha - 1) \;-\; \ln L 
+\\
++ \frac{1}{\,1 - \lambda\,}\Bigl[
+   \lambda\Bigl(\ln \Gamma(L - \alpha) 
+       - \ln \Gamma(-\alpha) 
+       - \ln \Gamma(L)\Bigr)
+   + \ln \Gamma\bigl(\lambda(L - 1) + 1\bigr) 
+   + \ln \Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) 
+   - \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
+\Bigr].
+\label{eq:RenyiGI0Final}
+\end{multline}

### 2025-03-29 Text/Reports/report-Renyi/Appendix3.Rmd
Update corrected comments

@@
 The effectiveness of this correction depends on the choice of \(B\) and the underlying sample distribution, but it systematically reduces bias in entropy estimation, particularly for small sample sizes.
+
+For a continuous random variable \( Z \) with probability density function (pdf) \( f(z) \), the Rényi entropy of order \( \lambda \in \mathbb{R}_+ \setminus \{1\} \) is defined as:
+\begin{equation}
+\label{E:entropy2}
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+\end{equation}
+Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the \( \Gamma_{\mathrm{SAR}} \) and \( \mathcal{G}^0_I \) distributions:
+
+\begin{multline}
+\label{eq-HGammaSAR}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
+= 
+\ln \mu - \ln L + \frac{1}{1-\lambda}
+\Bigl[
+  -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
+\Bigr].
+\end{multline}
+
+Similarly, for the \( \mathcal{G}^0_I \) distribution, we obtain:
+
+\begin{multline}
+\label{eq-HGI0}
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) \\
++ \ln(-1 - \alpha) \\
++ \frac{1}{1 - \lambda} \Bigl[ 
+    \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\
+    + \ln\Gamma\bigl(\lambda(L - 1) + 1\bigr) 
+\Bigr].
+\end{multline}
+
+The detailed derivation of the Rényi entropy for the \( \mathcal{G}^0_I \) distribution is provided in the Appendix.
+
+Figure~\ref{fig:entropy_plot} illustrates the behavior of the Rényi entropy as a function of \( \lambda \) for different values of the distribution parameters.
+
+For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
+\begin{equation}
+\label{E:entropy2}
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+\end{equation}
+
+Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions.
+Importantly, the $\mathcal{G}^0_I$ entropy can be expressed in terms of the $\Gamma_{\mathrm{SAR}}$ entropy plus additional terms that account for the roughness parameter $\alpha$:
+
+\begin{multline}
+\label{eq-HGammaSAR}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
+= 
+\ln \mu - \ln L + \frac{1}{1-\lambda}
+\Bigl[
+  -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
+\Bigr],
+\end{multline}
+
+\begin{multline}
+\label{eq-HGI0}
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \Delta H_\lambda(\alpha) \\
+\text{where } \Delta H_\lambda(\alpha) = \ln(-1 - \alpha) + \frac{1}{1 - \lambda}
+\Bigl[
+   \lambda\bigl(
+      \ln\Gamma(L - \alpha)
+      -\ln\Gamma(-\alpha)
+   \bigr) \\
+   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)
+   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
+   +\bigl(\lambda(L-1)+1\bigr)\ln\lambda
+\Bigr].
+\end{multline}
+
+The term $\Delta H_\lambda(\alpha)$ quantifies the additional entropy contribution due to texture variations in the $\mathcal{G}^0_I$ model.
+As $\alpha \to -\infty$, we can show that $\Delta H_\lambda(\alpha) \to 0$, recovering the $\Gamma_{\mathrm{SAR}}$ case.
+This limiting behavior confirms that the $\Gamma_{\mathrm{SAR}}$ distribution is indeed a special case of the $\mathcal{G}^0_I$ distribution for homogeneous areas.
+
+@fig-plot presents the Rényi entropy of the $\mathcal{G}^0_I$ model as a function of $\mu$ for different values of $\alpha$, demonstrating this convergence.
+
+For a continuous random variable \(Z\) with pdf \(f(z)\), the Rényi entropy of order \(\lambda \in \mathbbm{R}_+ \setminus \{1\}\) is defined as:  
+\begin{equation}  
+\label{E:entropy2}  
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.  
+\end{equation}
+
+Using \eqref{E:entropy2}, we derive the Rényi entropy for the \(\Gamma_{\text{SAR}}\) distribution:  
+\begin{multline}  
+\label{eq-HGammaSAR}  
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) = \ln\mu - \ln L \\  
++ \frac{1}{1-\lambda} \Bigl[ -\lambda\ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) - \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
+\end{multline}
+
+For the \(\mathcal{G}^0_I\) distribution, the entropy **explicitly extends** \(H_\lambda(\Gamma_{\text{SAR}})\) with terms depending on the roughness parameter \(\alpha\):  
+\begin{multline}  
+\label{eq-HGI0}  
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \ln(-1 - \alpha) \\  
++ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) + \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) \\  
+- \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) + \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
+\end{multline}
+
+As \(\alpha \to -\infty\), the additional terms vanish, reducing \eqref{eq-HGI0} to \eqref{eq-HGammaSAR}.
+This confirms that \(\Gamma_{\text{SAR}}\) is the limiting case of \(\mathcal{G}^0_I\) for homogeneous areas (fully developed speckle).
+
+These results are proven in the Appendix. Notably, the \(\mathcal{G}^0_I\) entropy converges to the \(\Gamma_{\text{SAR}}\) case as \(\alpha \to -\infty\), i.e.,
+\[
+\lim_{\alpha \to -\infty} H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr).
+\]
+This limit is analytically derived in the Appendix and corroborates that \(\Gamma_{\text{SAR}}\) describes homogeneous areas (fully developed speckle), while \(\mathcal{G}^0_I\) generalizes it for textured regions.
+
+\section*{Appendix: Proof of the Limit Behavior}  
+The limit \(\lim_{\alpha \to -\infty} H_\lambda(\mathcal{G}^0_I) = H_\lambda(\Gamma_{\text{SAR}})\) follows from analyzing the additional terms in \eqref{eq-HGI0}. Let:  
+\[
+\Delta(\alpha) = H_\lambda(\mathcal{G}^0_I) - H_\lambda(\Gamma_{\text{SAR}}) = \ln(-1-\alpha) + \frac{1}{1-\lambda} \ln\!\left[ \frac{\Gamma(L-\alpha)^\lambda \Gamma(\lambda(-\alpha+1)-1) \lambda^{\lambda(L-1)+1}}{\Gamma(-\alpha)^\lambda \Gamma(\lambda(L-\alpha))} \right].
+\]  
+Using asymptotic properties of the Gamma function for large \(|\alpha|\):  
+\[
+\frac{\Gamma(L-\alpha)}{\Gamma(-\alpha)} \sim |\alpha|^L, \quad \frac{\Gamma(\lambda(-\alpha+1)-1)}{\Gamma(\lambda(L-\alpha))} \sim (\lambda|\alpha|)^{\lambda-1 - \lambda L},
+\]  
+we obtain \(\Delta(\alpha) \sim \ln|\alpha| - \ln|\alpha| = 0\). Thus, \(\Delta(\alpha) \to 0\) as \(\alpha \to -\infty\).

### 2025-03-29 Text/Reports/report-Renyi/R1-report-renyi.Rmd
Update corrected comments

@@
 sample_sizes <- c(49)
-R <- 500# Number of replications con 200 y 
-B <- 100      # Number of bootstrap replications 10 tambien funciona 0.9 el valor optimo
+R <- 2000# Number of replications con 200 y 
+B <- 300      # Number of bootstrap replications 10 tambien funciona 0.9 el valor optimo
 mu <- 1        # Fixed mu
-L <- 1        # Fixed L
+L <- 18        # Fixed L
 
@@
 #lambda_values <- c(0.65, 0.66, 0.67, 0.68, 0.69, 0.70, 0.71, 0.72, 0.75, 0.9, 0.95, 0.96,0.97,  0.98, 0.99, 1.1, 1.2, 1.3,  1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0 )
-lambda_values <- c(  0.9, 0.95,  0.99, 1.1, 1.2,  1.5,  2, 3, 3.5, 4)
+lambda_values <- c(  0.8, 0.9, 0.95,  0.99, 1.1, 1.2)
 

### 2025-03-29 Code/R/Programs/test_differences.R

@@ -22,10 +22,10 @@ source("../MainFunctions/gi0_sample.R")
 set.seed(1234567890, kind = "Mersenne-Twister")
 
 R <- 10000
-mu <- 1
+mu <- 10
 L <- 5
 B <- 50
-alpha1 <- -100
+alpha1 <- -10000
 sample.size <- c(49)
 
 TestStatistics1 <- NULL
@@ -46,7 +46,7 @@ for (s in sample.size) {
   for (r in 1:R) {
     #z <- gi0_sample(mu, alpha1, L, s)
     z <- gamma_sar_sample(L, mu, s)
-    TestStat1[r] <-bootstrap_al_omari_1_estimator(z,B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+    TestStat1[r] <-mean(z)
     #TestStat1[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
     #TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
     #TestStat1[r] <- bootstrap_correa_estimator(z, B)#+( L+lgamma(L-alpha1) - (L-alpha1)*(digamma(L - alpha1))+(1-alpha1)*digamma(- alpha1)-log(-1 - alpha1)-lgamma(-alpha1) ) 

### 2025-03-29 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
Submitted version

@@
   We propose a test statistic based on a non-parametric estimation of Rényi entropy to characterize surface roughness from SAR intensity data. 
-  The statistic is refined using bootstrap to improve its stability, size and power. 
+  The statistic is refined using bootstrap to improve its stability, size, and power. 
   This approach enhances roughness quantification by capturing scale-dependent variations and addressing data-driven uncertainty.
@@
 [S]{.IEEEPARstart}[ynthetic]{}
- Aperture Radar (SAR) technology has become essential for a wide range of applications&nbsp;[@Yu2023;@Akbarizadeh2012;@Mondini2021]. 
- It provides high-resolution data that is independent of sunlight and operates in a variety of weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
-Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because this data is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019; @Baraha2023].
+ Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Yu2023;@Akbarizadeh2012;@Mondini2021]. 
+ It provides high-resolution data independent of sunlight and operates in various weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
+Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019; @Baraha2023].
 In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
 
-The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different levels of roughness. 
+The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different roughness levels. 
 A limiting case is the Gamma distribution, which arises when speckle is fully developed, indicating textureless regions. 
-Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two main reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
+Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
 These challenges complicate model selection and highlight the need to explore alternative statistical approaches.
@@
 We propose a statistical test based on a non-parametric estimator of Rényi entropy to identify heterogeneous regions in SAR data.
-The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the assumption of homogeneity.
+The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the homogeneity assumption.
 Compared to our previous approach using Shannon entropy&nbsp;[@Frery2024], the Rényi-based approach improves the detection of heterogeneity.
@@
 
-The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness&nbsp;[@Frery1997].
+The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe roughness&nbsp;[@Frery1997].
 These distributions are characterized by the following probability density functions (pdfs):
@@
 $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
-As demonstrated by&nbsp;[@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
+The $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution&nbsp;[@Frery1997]: for $\mu$ fixed,
 $$
@@
 \longrightarrow 
-f_{\Gamma_{\text{SAR}}}(z;L, \mu) 
+f_{\Gamma_{\text{SAR}}}(z;L, \mu) \text{ when } \alpha\to-\infty.
 $$
-when $\alpha\to-\infty$.
 
@@
 \label{eq-HGI0}  
-H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \ln(-1 - \alpha) \\  
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \\ \ln(-1 - \alpha)  
 + \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
@@
 The derivation of the latter result is proven in the Appendix.
-Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms depending on the roughness parameter $\alpha$.
+Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
 As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
+This work's core idea is to estimate this difference and check if it is significantly different from zero.
 
@@
 
-In order to estimate&nbsp;\eqref{E:entropy2} from a random sample, one may estimate the parameters that index the probability density function $f$, and integrate.
-This approach heavily relies on the model assumptions and on the absence of outliers.
+In order to estimate&nbsp;\eqref{E:entropy2} from a random sample, one may estimate the parameters that index the probability density function $f$ and integrate.
+This approach relies heavily on the model assumptions and the absence of outliers.
 Alternatively, one may estimate directly $f$.
@@
 To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
-Lower MSE and bias indicate better performance of the estimator in approximating the true entropy.
-
-We found that for $L > 1$ the optimal value is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
-However, for $L = 1$, the optimal $\lambda$ tends to be higher and we chose $\lambda = 3$ to achieve good results. 
+Lower MSE and bias indicate better estimator performance in approximating the true entropy.
+
+We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
+However, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results. 
 @fig-plotf illustrates the case for $L = 5$.
@@
 ```
-For subsequent simulations we use the $\widetilde{H}_{\lambda}$ estimator.
+We use the $\widetilde{H}_{\lambda}$ estimator for subsequent simulations.
 
@@
 
-Since homogeneity corresponds to $\alpha \to -\infty$ in the $\mathcal{G}^0_I$ model, classical inference methods are inapplicable. 
+Classical inference methods are inapplicable since homogeneity corresponds to $\alpha \to -\infty$ in the $\mathcal{G}^0_I$ model. 
 Instead, we propose a test statistic based on the Rényi entropy estimator, comparing it with its theoretical expectation under $\mathcal{H}_0$ to distinguish between homogeneous and heterogeneous areas.
@@
 where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
-When the null hypothesis holds, this test statistic is expected to be close to zero.
+This test statistic should be close to zero when the null hypothesis holds.
 @fig-density_entropyR shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
@@
 
-We define the standardized test statistic:
-\begin{equation*}
-\varepsilon = \frac{S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S}{\hat{\sigma}_S},
-\end{equation*}
+The standardized test statistic 
+$\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S})/{\hat{\sigma}_S}$ is asymptotically standard normal distributed,
 where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
-By the central limit theorem, $\varepsilon$ asymptotically follows a standard normal distribution:
-\begin{equation*}
-\varepsilon \overset{d}{\longrightarrow} \mathcal{N}(0,1)\,.
-\end{equation*}
 Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
@@
 Further, we examined the power under the alternative hypothesis ($\mathcal{G}^0_I$ distribution) with $\mu=1$, $\lambda=0.9$ and $\alpha=-2$.
-As expected, power improves as the sample size and number of looks increase, demonstrating the test effectiveness. The results are shown in Table&nbsp;\ref{tab:table_size_power}.
+As expected, power improves as the sample size and the number of looks increase, demonstrating the test effectiveness. The results are shown in Table&nbsp;\ref{tab:table_size_power}.
 ```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
@@
 
-The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness and lighter regions denote smoother, less textured surfaces.
+The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
 The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions). 
@@
 
-The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations compared to the Shannon-based test, due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
+The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
 <!-- ACF Where is the Shannon-based approach shown? -->
@@
 This study presented a new statistical approach based on Rényi entropy for detecting heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
-The statistics of the proposed test was computed non-parametrically and its performance was evaluated by a Monte Carlo study. 
+The proposed test performance was evaluated by a Monte Carlo study. 
 The results showed that the method effectively controls the probability of Type&nbsp;I error while maintaining a high detection performance that improves as the sample size increases.
@@
 The differences between the two methods are evident in the binary maps at a $0.05$ significance level.
-Although both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, which allowed for finer differentiation of texture variations.
+Although both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, allowing for finer texture variation differentiation.
 

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
new R1-version qmd and new Figures-R1

\documentclass[11pt]{report}

\usepackage[pdftex]{geometry}
\geometry{a4paper,left=2.8cm,right=2.8cm,top=1.5cm,bottom=1.5cm,twoside}

\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
	\graphicspath{./Comments/}
\usepackage[many]{tcolorbox}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{bm,bbm}
\usepackage{float}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\newtcolorbox{reviewbox}[1]{
colback = white!5!white,
colframe = purple!75!black,
fonttitle=\bfseries,
title=#1
}

\newtcolorbox{responsebox}[1]{
	colback = white!5!white,
	colframe = white!75!black,
	fonttitle=\bfseries,
	title=#1
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
\large{\textbf{Response Letter to Associate Editor}}

\vglue 0.3cm

\huge{ Quantifying Roughness in SAR Imagery with the Rényi Entropy\\ (GRSL-00722-2025)}
\end{center}

%\authors
\begin{center}
\textbf{Janeth Alpala,   Abraao D.\ C.\ Nascimento, Alejandro C.\ Frery }
\end{center}

\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{2cm}
\noindent Dear Editors
\bigskip

\noindent We are grateful to the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this round of review.

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
This manuscript proposes a statistically grounded method for quantifying roughness in SAR imagery using a non-parametric estimator of Rényi entropy, refined via bootstrap correction, and developed into a hypothesis test that distinguishes fully developed speckle and heterogeneous clutter. The paper is technically sound and well-presented. However, the following comments should be carefully addressed in the revised version to enhance clarity, applicability, and completeness:

1. While the paper is generally well-written and structured, several mathematical expressions—particularly Equations (5) and (8)—may be difficult to interpret for practitioners or applied researchers. The authors are encouraged to provide more intuitive explanations or illustrative interpretations alongside the formulas.
\end{reviewbox}

\begin{responsebox}{Response}

We have

\begin{quote}
	\textcolor{blue}{text  }
\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 2}
2. The current methodology assumes that the number of looks, L, is known a priori. In practice, this parameter may be unknown or inaccurately estimated from SAR metadata. The authors should discuss the sensitivity of the proposed test to variations or inaccuracies in L, and optionally suggest techniques for estimating L directly from the data or include robustness analysis. 
\end{reviewbox}

\begin{responsebox}{Response}

We have clarified that
\begin{quote}
	\textcolor{blue}{
		In order to clarify the }

\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 3}
3. Figures (Figs. 6–8) are informative but could benefit from quantitative evaluation. Add comparative metrics beyond visual comparison.
\end{reviewbox}

\begin{responsebox}{Response}

We include

\begin{quote}
	\textcolor{blue}{
	text
}
\end{quote}

\end{responsebox}

\begin{reviewbox}{Comment 4}
The manuscript convincingly shows that Rényi-based entropy measures offer advantages over classical Shannon entropy for heterogeneity detection. However, no comparisons are made to machine learning-based SAR classifiers or segmentation models, which are now widely adopted. Justification is required.
\end{reviewbox}
\begin{responsebox}{Response}
We have clarified that
\begin{quote}
	\textcolor{blue}{
		text
}
\end{quote}

\end{responsebox}

\end{document}

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
new R1-version qmd and new Figures-R1

--- 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
@@
 \usepackage{float}
+\usepackage{siunitx}
 
@@
 \begin{center}
-\large{\textbf{Response Letter to Associate Editor}}
+\large{\textbf{Response Letter to Reviewer \# 1}}
 
@@
 \begin{reviewbox}{Comment 1}
-This manuscript proposes a statistically grounded method for quantifying roughness in SAR imagery using a non-parametric estimator of Rényi entropy, refined via bootstrap correction, and developed into a hypothesis test that distinguishes fully developed speckle and heterogeneous clutter.
-The paper is technically sound and well-presented.
-However, the following comments should be carefully addressed in the revised version to enhance clarity, applicability, and completeness:
+1.
+The manuscript uses Rényi Entropy to estimate the surface roughness using SAR intensity data.
+However, the novelty aspect is not clear to this reviewer.
+Is this the sampling technique for the non-parametric estimation?
+The non-parametric estimation is already existing in the literature.
 
-1.
-While the paper is generally well-written and structured, several mathematical expressions—particularly Equations (5) and (8)—may be difficult to interpret for practitioners or applied researchers.
-The authors are encouraged to provide more intuitive explanations or illustrative interpretations alongside the formulas.
+\end{reviewbox}
+
+\begin{responsebox}{Response}
+We have 
+\begin{quote}
+	\textcolor{blue}{ text}
+\end{quote}
+\end{responsebox}
+
+\vspace{2em}
+\begin{reviewbox}{Comment 2}
+2.
+The methodology is mostly indicates the heterogeneity in a SAR image.
+The terminology "Roughness" generally refers to the surface roughness irrespective of the landcover classes.
+However, the proposed technique includes everything which are existing within a resolution.
+Therefore, in the title of the manuscript, the "Roughness" can be changed to "Heterogeneity".
 \end{reviewbox}
@@
 
-We have
+We change to the new title..
+\begin{quote}
+	\textcolor{blue}{
+	Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy
+}
+\end{quote}
+\end{responsebox}
 
-\begin{quote}
-	\textcolor{blue}{text  }
-\end{quote}
+\vspace{2em}
+\begin{reviewbox}{Comment 3}
+3.
+Why the p-values are very high over the areas which have the dominant surface scattering?
+Should it not be low if the proposed technique is estimating the entropy precisely?
+It looks like the proposed method better estimates over the heterogeneous areas as compared to homogeneous areas.
+\end{reviewbox}
+\begin{responsebox}{Response}
+	text
+\end{responsebox}
+
+\vspace{2em}
+\begin{reviewbox}{Comment 4}
+4. How is the dependence of the proposed technique on the additive and multiplicative noises which remains in the SAR data?
+\end{reviewbox}
+\begin{responsebox}{Response}
 
@@
 
-\begin{reviewbox}{Comment 2}
-2.
-The current methodology assumes that the number of looks, L, is known a priori.
-In practice, this parameter may be unknown or inaccurately estimated from SAR metadata.
-The authors should discuss the sensitivity of the proposed test to variations or inaccuracies in L, and optionally suggest techniques for estimating L directly from the data or include robustness analysis.
+\vspace{2em}
+\begin{reviewbox}{Comment 5}
+5. Fig 6, 7 and 8 show the detection of heterogeneous areas. However, a statistical measure indicating the detection performance is absent.
 \end{reviewbox}
-
 \begin{responsebox}{Response}
@@
 \begin{quote}
-	\textcolor{blue}{
-		In order to clarify the }
+	\textcolor{blue}{text}
+\end{quote}
+\end{responsebox}
 
-\end{quote}
+\vspace{2em}
+\begin{reviewbox}{Comment 6}
+6. The color bars and the font size of the texts needs to be improved so that it can be clearly visible.
+\end{reviewbox}
+\begin{responsebox}{Response}
+
+We added
 
@@
 
-\begin{reviewbox}{Comment 3}
-3. Figures (Figs. 6–8) are informative but could benefit from quantitative evaluation. Add comparative metrics beyond visual comparison.
+\vspace{2em}
+\begin{reviewbox}{Comment 7}
+7. Why the authors are focusing on the low MSE, not the low bias while selecting the value of lambda?
 \end{reviewbox}
@@
 \begin{responsebox}{Response}
-
-We include
-
-\begin{quote}
-	\textcolor{blue}{
 text
-}
-\end{quote}
-
 \end{responsebox}
 
-\begin{reviewbox}{Comment 4}
-The manuscript convincingly shows that Rényi-based entropy measures offer advantages over classical Shannon entropy for heterogeneity detection.
-However, no comparisons are made to machine learning-based SAR classifiers or segmentation models, which are now widely adopted.
-Justification is required.
+\vspace{2em}
+\begin{reviewbox}{Comment 7}
+8. "We aim to determine the optimal order λ for the Rényi entropy estimator for a sample size n=49" From where these 49 samples are taken?
 \end{reviewbox}
+
 \begin{responsebox}{Response}
-We have clarified that
-\begin{quote}
-	\textcolor{blue}{
 text
-}
-\end{quote}
-
 \end{responsebox}
-
 \end{document}

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer2.tex
new R1-version qmd and new Figures-R1

--- 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
@@
 \begin{center}
-\large{\textbf{Response Letter to Associate Editor}}
+\large{\textbf{Response Letter to Reviewer \# 2}}
 
@@
 \begin{reviewbox}{Comment 1}
-This manuscript proposes a statistically grounded method for quantifying roughness in SAR imagery using a non-parametric estimator of Rényi entropy, refined via bootstrap correction, and developed into a hypothesis test that distinguishes fully developed speckle and heterogeneous clutter.
-The paper is technically sound and well-presented.
-However, the following comments should be carefully addressed in the revised version to enhance clarity, applicability, and completeness:
+1. The language needs further improvement and should be reviewed by a language expert.
+\end{reviewbox}
 
-1.
-While the paper is generally well-written and structured, several mathematical expressions—particularly Equations (5) and (8)—may be difficult to interpret for practitioners or applied researchers.
-The authors are encouraged to provide more intuitive explanations or illustrative interpretations alongside the formulas.
+\begin{responsebox}{Response}
+Text
+
+\end{responsebox}
+
+\begin{reviewbox}{Comment 2}
+2. The scientific content of the article is weak and requires further expansion.
 \end{reviewbox}
@@
 
-We have
-
-\begin{quote}
-	\textcolor{blue}{text  }
-\end{quote}
+Text
 
@@
 
-\begin{reviewbox}{Comment 2}
-2.
-The current methodology assumes that the number of looks, L, is known a priori.
-In practice, this parameter may be unknown or inaccurately estimated from SAR metadata.
-The authors should discuss the sensitivity of the proposed test to variations or inaccuracies in L, and optionally suggest techniques for estimating L directly from the data or include robustness analysis.
+\begin{reviewbox}{Comment 3}
+ 3. I did not observe any comparison of the authors' work's novelty index with the latest articles published in the field for the current years.
 \end{reviewbox}
@@
 
-We have clarified that
-\begin{quote}
-	\textcolor{blue}{
-		In order to clarify the }
-
-\end{quote}
+Text
 
 \end{responsebox}
-
-\begin{reviewbox}{Comment 3}
-3. Figures (Figs. 6–8) are informative but could benefit from quantitative evaluation. Add comparative metrics beyond visual comparison.
-\end{reviewbox}
-
-\begin{responsebox}{Response}
-
-We include
-
-\begin{quote}
-	\textcolor{blue}{
-	text
-}
-\end{quote}
-
-\end{responsebox}
-
 \begin{reviewbox}{Comment 4}
-The manuscript convincingly shows that Rényi-based entropy measures offer advantages over classical Shannon entropy for heterogeneity detection.
-However, no comparisons are made to machine learning-based SAR classifiers or segmentation models, which are now widely adopted.
-Justification is required.
+4. Conclusion requires redrafting.
 \end{reviewbox}
 \begin{responsebox}{Response}
-We have clarified that
-\begin{quote}
-	\textcolor{blue}{
-		text
-}
-\end{quote}
+Text
 

### 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
new R1-version qmd and new Figures-R1

--- 2025-03-29 Text/Articles/RENYI_ENTROPY_SAR_2025/R0-Renyi-entropy-sar.qmd
@@
     pdf-engine: pdflatex # xelatex
+    fig-dir: "Figures-R1"
     keep-tex: true  
@@
 
-knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
+#knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
+knitr::opts_chunk$set(
+  echo = FALSE,
+  cache = TRUE,
+  fig.path = "Figures-R1/"
+) # unique path to save all code-generated and external figures
 
@@
 As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
-This work's core idea is to estimate this difference and check if it is significantly different from zero.
-
-@fig-plot illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$.
+This work's core idea is to check if this excess entropy is significantly different from zero.
+
+@fig-convergence illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$.
 As $\alpha$ decreases, the curves approach $H_\lambda(\Gamma_{\text{SAR}})$ (solid black line).
@@
 <!-- Corrected -->
-```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}
+```{r fig-convergence, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}
 
@@
 However, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results. 
-@fig-plotf illustrates the case for $L = 5$.
-```{r fig-plotf, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
+@fig-optimal_order illustrates the case for $L = 5$.
+```{r fig-optimal_order, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
 
@@
 
-A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-Plot_bias_msef3.
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-bias_mse.
 
@@
 
-```{r fig-Plot_bias_msef3, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}
+```{r fig-bias_mse, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}
 
@@
 This test statistic should be close to zero when the null hypothesis holds.
-@fig-density_entropyR shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
+@fig-densities shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
 <!-- ACF 10^4 replications of samples of size?   -->
@@
 
-```{r fig-density_entropyR, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+```{r fig-densities, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
 
@@
 where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
-@fig-density_entropyR_standardized0 shows smoothed histograms of standardized test statistics.
+@fig-density_standardized shows smoothed histograms of standardized test statistics.
 
@@
 
-```{r fig-density_entropyR_standardized0, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
+```{r fig-density_standardized, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
 
@@
 <!-- JA: The results of the Shannon-based approach can be observed in the corresponding binary maps. -->
+
 ```{=latex}
@@
     \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/london_2000.png}
-        \caption{ SAR image}
+        \includegraphics[width=\linewidth]{./Figures-R1/london_2000.png}
+        \caption{SAR image}
         \label{fig:london-a}
     \end{subfigure}
-    \begin{subfigure}{0.22\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_renyi.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london-E.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
+    \hspace{0.01\textwidth}
     \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_london_renyi_L1_.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.22\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_pvalue_london_Shannon_c1.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london-E.png}
         \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
@@
     \end{subfigure}
+    \hspace{0.01\textwidth}
     \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_london_shannon.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
@@
     \end{subfigure}
-    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.  }
+    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
     \label{fig:london}
 \end{figure*}
-
 ```
@@
     \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/munich_1024_2.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/munich_1024.png}
         \caption{SAR image}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_renyi.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi_munich-H.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.16\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_munich_renyi.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.17\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_renyi.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.23\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_pvalue_muni_Shan22.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon_munich-H.png}
         \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.16\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_munich_sh_AO_L12.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.17\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_shannon.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
@@
     \centering
-    \begin{subfigure}{0.16\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/dublin_1100_hh.png}
+    \begin{subfigure}{0.17\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/dublin_1100.png}
         \caption{SAR image}
@@
     \end{subfigure}
-    \begin{subfigure}{0.22\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/dublin_renyi_09_w7_b100.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-B.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.16\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_dublin_renyi_09_w7_b100.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.17\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.22\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/AO_w7_L16_b100.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.20\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-B.png}
         \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
@@
     \end{subfigure}
-    \begin{subfigure}{0.16\textwidth}
-        \includegraphics[width=\linewidth]{./Figures/H_005_AO_w7_L16_b100.png}
+    \hspace{0.01\textwidth}
+    \begin{subfigure}{0.17\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}

### 2025-05-25 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
Update: responses to Reviewer 1

@@
 \begin{responsebox}{Response}
-We have 
+
+We thank the reviewer for raising this important point.
+While non-parametric entropy estimation is indeed present in the literature, we have not found prior works that apply a non-parametric estimator of the Rényi entropy specifically for heterogeneity detection in SAR imagery.
+
+Our contribution lies in formulating a hypothesis test that uses the entropy estimator as a test statistic to distinguish between homogeneous and heterogeneous regions.
+Classical parametric inference alternatives, such as likelihood ratio or Wald tests, are not applicable here due to the limiting behavior of the roughness parameter (\(\alpha \to -\infty\)) under the null hypothesis.
+
+In addition, we enhance the non-parametric Rényi entropy estimator by incorporating a bootstrap based bias correction technique.
+This resampling strategy not only reduces the estimator’s bias but also improves the accuracy of entropy estimation, particularly when working with small sample sizes.
+This improvement is especially relevant in practical SAR image analysis, where estimations are commonly performed over small windows, such as \(7 \times 7\) pixels.
+
+We have clarified these contributions in the revised manuscript, in the final paragraph of the Introduction.
+
 \begin{quote}
-	\textcolor{blue}{ text}
+	\textcolor{blue}{ In addition, we enhance the non-parametric estimator through a bootstrap-based bias correction technique, which increases accuracy, particularly for small sample sizes often used in practical SAR applications.}
 \end{quote}
+
 \end{responsebox}
@@
 The methodology is mostly indicates the heterogeneity in a SAR image.
-The terminology "Roughness" generally refers to the surface roughness irrespective of the landcover classes.
+The terminology ``Roughness'' generally refers to the surface roughness irrespective of the landcover classes.
 However, the proposed technique includes everything which are existing within a resolution.
-Therefore, in the title of the manuscript, the "Roughness" can be changed to "Heterogeneity".
+Therefore, in the title of the manuscript, the ``Roughness'' can be changed to ``Heterogeneity''.
 \end{reviewbox}
@@
 
-We change to the new title..
+We appreciate the reviewer’s observation.
+In our work, \emph{roughness} is used in a statistical sense, following the interpretation of the parameter $\alpha$ in the $\mathcal{G}^0_I$ distribution.
+This parameter reflects the degree of texture or variability within the resolution cell, which may result from both surface irregularities and land cover heterogeneity.
+While we believe the term is appropriate in this context, we are open to revising the manuscript title from ``Roughness'' to ``Heterogeneity'' to improve clarity and better align with remote sensing terminology.
+
+Accordingly, we have revised the manuscript title to:
 \begin{quote}
 	\textcolor{blue}{
-	Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy
-}
+	``Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy.''}
 \end{quote}
@@
 \end{reviewbox}
+
 \begin{responsebox}{Response}
-	text
+
+We thank the reviewer for this observation.
+However, we believe there may be a misunderstanding regarding the interpretation of $p$-values.
+In our formulation, the null hypothesis $H_0$ assumes that a region is homogeneous.
+Therefore, high $p$-values (e.g., $p > 0.05$) indicate that the data are consistent with homogeneity, while low $p$-values (e.g., $p < 0.05$) suggest statistical evidence of heterogeneity.
+
+The test statistic is based on the difference between the estimated Rényi entropy and the theoretical value under $H_0$.
+If the region is homogeneous, this difference tends to be close to zero, and the resulting $p$-value will be high, as expected.
+In contrast, heterogeneous regions typically produce larger differences and thus low $p$-values, leading to rejection of $H_0$.
+
+This is the intended behavior of the test, and the observed $p$-value patterns in the detection maps confirm its correct functioning. 
+\end{responsebox}
+\begin{responsebox}{}
+We have clarified this point in the revised manuscript by adding a paragraph at the end of Section~III-D,  which explains how the $p$-value maps are constructed from sliding windows and how they should be interpreted.
+
+\begin{quote}
+\textcolor{blue}{
+In practice, we apply the proposed test to the SAR image using a sliding window approach ($7 \times 7$ pixels).
+For each window, we compute the test statistic under the null hypothesis of homogeneity and, assuming asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
+High $p$-values ($p > 0.05$) indicate consistency with $H_0$, while low values ($p < 0.05$) suggest heterogeneity.
+Note that the visual outputs in Figs. 6--8 show the $p$-values from this test, not the test statistic or entropy values.
+}
+\end{quote}
 \end{responsebox}
@@
 \begin{responsebox}{Response}
+
+The proposed technique explicitly models the multiplicative noise (speckle) inherent in SAR intensity data.
+It assumes fully developed speckle in homogeneous areas, which is commonly modeled by a Gamma distribution.
+
+Additive noise is not considered in the model because it is usually very small in SAR images that have been properly calibrated.
+In our experiments, we use SAR images in intensity format (e.g., HH) that are radiometrically and geometrically corrected.
+Because the method analyzes small windows and uses non-parametric entropy estimation, it is relatively robust to small residual noise that may remain after standard preprocessing, such as calibration and terrain correction.
+We do not apply any additional filtering in order to keep the texture information that is important for detecting heterogeneity.
 
@@
 
-We added
+We improved Figures 6–8 by increasing the font size of labels, standardizing the color bar sizes, and updating the colormap in Figure 7 to enhance visual contrast.
 
@@
 \begin{responsebox}{Response}
-text
+
+While both bias and MSE are important criteria, we prioritized the MSE because it incorporates both the bias and the variance of the estimator. 
+Specifically, the MSE is defined as the sum of the squared bias and the variance, providing a more comprehensive measure of estimator accuracy.
+
+In our simulations, we found that for $L > 1$, the choice $\lambda = 0.9$ consistently yielded the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
+Although some values of $\lambda$ (e.g., $0.85$) showed slightly lower bias, they resulted in higher overall MSE due to increased variance.
+
+We illustrate the case for $L = 5$ in Fig.
+2, but similar trends were observed for other values of $L > 1$, confirming the robustness of $\lambda = 0.9$ and motivating its selection in the Rényi entropy estimator.
+
+\textcolor{blue}{We have clarified this point in Section~III-A, where we explicitly justify the choice of $\lambda = 0.9$ based on the trade-off between bias and MSE.}
+
 \end{responsebox}
@@
 \vspace{2em}
-\begin{reviewbox}{Comment 7}
-8. "We aim to determine the optimal order λ for the Rényi entropy estimator for a sample size n=49" From where these 49 samples are taken?
+
+\begin{reviewbox}{Comment 8}
+8. "We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator for a sample size $n=49$." From where these 49 samples are taken?
 \end{reviewbox}
@@
 \begin{responsebox}{Response}
-text
+
+The 49 samples refer to synthetic data generated from the Gamma distribution, which models fully developed speckle in homogeneous regions.
+
+To determine the optimal value of $\lambda$, we conducted a Monte Carlo simulation with $R = 1000$ replications.
+In each replication, a sample of size $n = 49$ was drawn from the $\Gamma_{\text{SAR}}(L = 5, \mu = 1)$ distribution.
+Bias and MSE were computed across several $\lambda$ values to select the most robust option.
+
+The choice of $n = 49$ corresponds to a $7 \times 7$ window, which is commonly used in SAR image processing as it strikes a balance between capturing local detail and providing enough data for reliable statistical analysis.
+
+\textcolor{blue}{We have clarified the origin of the samples $n = 49$ in Section~III-A.}
 \end{responsebox}
+
 \end{document}

### 2025-05-25 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Update: responses to Reviewer 1

@@
 [S]{.IEEEPARstart}[ynthetic]{}
- Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Yu2023;@Akbarizadeh2012;@Mondini2021]. 
+ Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Yu2023;@Mondini2021]. 
  It provides high-resolution data independent of sunlight and operates in various weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
-Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Choi2019; @Baraha2023].
+Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Baraha2023].
 In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
@@
 Compared to our previous approach using Shannon entropy&nbsp;[@Frery2024], the Rényi-based approach improves the detection of heterogeneity.
+\textcolor{blue}{In addition, we enhance the non-parametric estimator through a bootstrap-based bias correction technique, which increases accuracy, particularly for small sample sizes often used in practical SAR applications.}
 
@@
 Alternatively, one may estimate directly $f$.
-Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics&nbsp;[@vasicek1976test;@Bert1992; @Ebrahimi1994; @Wieczorkowski1999; @IbrahimAlOmari2014].
+Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics&nbsp;[@vasicek1976test;@Ebrahimi1994; @IbrahimAlOmari2014].
 Recently, Al-Labadi et al.&nbsp;[@AlLabadi2024] proposed a non-parametric estimator for Rényi entropy following this approach.
@@
 
-We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator for a sample size $n=49$.
-To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
-Lower MSE and bias indicate better estimator performance in approximating the true entropy.
-
-We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
-However, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results. 
-@fig-optimal_order illustrates the case for $L = 5$.
+\textcolor{blue}{
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator based on numerical experiments using synthetic samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution $(L = 5,\ \mu = 1)$.
+A Monte Carlo simulation is used to evaluate the bias and the mean squared erro (MSE) across different values of $\lambda$.}
+
+\textcolor{blue}{
+In our simulations, we find that for $L > 1$, the choice $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
+As shown in Fig.~\ref{fig-optimal_order}, the value $\lambda = 0.85$ exhibits slightly lower bias, but leads to higher MSE due to increased variance, supporting the selection of $\lambda = 0.9$.}
+
 ```{r fig-optimal_order, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
@@
 
+Particularly, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results.
+
 ## Bootstrap Correction for Entropy Estimator
@@
 
-A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($\mu=1, L=5$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-bias_mse.
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($L=5,\ \mu=1$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-bias_mse.
 
@@
 ```
+
+\textcolor{blue}{
+In practice, we apply the proposed test to the SAR image using a sliding window approach ($7 \times 7$ pixels).
+For each window, we compute the test statistic under the null hypothesis of homogeneity and, assuming asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
+High $p$-values ($p > 0.05$) indicate consistency with $H_0$, while low values ($p < 0.05$) suggest heterogeneity.
+Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values.
+}
 

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
R1 update: revised manuscript and reviewer responses added

@@
 
-\vspace{2cm}
+\vspace{0.5cm}
 \noindent Dear Editors
@@
 \begin{responsebox}{Response}
+ We have revised the manuscript to clarify their meaning and practical relevance, as detailed below.
 
-We have
+\vspace{0.5em}
 
-\begin{quote}
-	\textcolor{blue}{text  }
-\end{quote}
+\textbf{Equation (5): Rényi entropy of the $\mathcal{G}^{0}_{\!I}$ model.}  
+This expression presents the closed-form Rényi entropy of the heterogeneous $\mathcal{G}^{0}_{\!I}$ distribution as the sum of two components:
+\[
+H_\lambda\bigl(\mathcal{G}^{0}_{\!I}\bigr)
+=\;H_\lambda\bigl(\Gamma_{\text{SAR}}\bigr)
+\;+\;\bigl[\text{extra\ term depending on }\alpha\bigr].
+\]
 
+In intuitive terms:
+\begin{itemize}
+	\item $H_\lambda(\Gamma_{\text{SAR}})$ represents the “baseline entropy” of fully developed speckle (homogeneous clutter).
+	\item The additional term captures how much entropy increases due to texture (heterogeneity), caused by the roughness parameter $\alpha$.
+\end{itemize}
+When $\alpha\!\to\!-\infty$ (fully developed speckle), the excess term vanishes and (5) collapses to the homogeneous case in (4).
+This motivates our test: we check whether the \emph{excess} is statistically different from zero.
+
+\vspace{0.3em}
+\textcolor{blue}{To improve clarity, we add an intuitive interpretation after equation (5), and include Figure~1 showing the reduction of the excess term as $\alpha$ decreases, illustrating convergence.}
 \end{responsebox}
 
+\begin{responsebox}{}
+\vspace{0.5em}
+\textbf{Equation (8): test statistic.}  
+The test statistic is simply defined as:
+\[
+S_{\widetilde H_\lambda}(Z;L)
+= \text{“estimated entropy”} - \text{“theoretical entropy under } H_0\text{”}.
+\]
+Its purpose is to detect deviations from homogeneity:
+\begin{itemize}
+	\item  If the data are homogeneous, both terms match closely $\;\Rightarrow\;S\approx0$.
+	\item  If the data are heterogeneous, the estimated entropy exceeds the theoretical one $\;\Rightarrow\;|S|$ increases and the $p$-value becomes small.
+\end{itemize}
+
+ This formulation not only supports the theoretical foundation of our test but also offers practical utility: the closed-form expression is not previously available in the SAR literature and can be reused as an analytical feature in other downstream applications
+
+\vspace{0.3em}
+\textcolor{blue}{We added a brief explanation below Equation (8), and clarified in the caption of Figure~4 that the centered distribution confirms correct behavior under $H_0$.}
+
+\textbf{Why Eq.(5) benefits practitioners.}  
+Closed-form Rényi entropy for $\mathcal{G}^{0}_{\!I}$ is absent from the SAR literature; Having it allows others to incorporate an analytical feature into algorithms and applications.
+
+\textcolor{blue}{These additions are included in Sections II-B and III-D of the revised manuscript.}
+\end{responsebox}
+
+\vspace{5em}
 \begin{reviewbox}{Comment 2}
@@
 \begin{responsebox}{Response}
+We thank the reviewer for this important observation.
 
-We have clarified that
+In our experiments, we used the number of looks $L$ reported in the metadata of each SAR image, computed as the product of azimuth and range looks provided by the Sentinel Application Platform (SNAP).
+However, we recognize that this value may be imprecise in practice due to preprocessing steps such as multilooking.
+
+To validate its reliability, we manually selected homogeneous patches from each image and estimated the Equivalent Number of Looks (ENL) using the classical estimator based on the coefficient of variation ($\widehat{L} = 1/\text{CV}^2$).
+The results were consistent with the metadata; for example, in the Dublin image, we obtained $\widehat{L} \approx 16.3$ from water regions, which closely matches the metadata value $L = 16$.
+
+We also tested the sensitivity of the proposed hypothesis test to slight under- and overestimations of $L$, and found that the resulting $p$-value maps and binary decisions remained stable.
+These findings indicate that the test is robust to moderate inaccuracies in $L$.
+
 \begin{quote}
 	\textcolor{blue}{
-		In order to clarify the }
+		A brief explanation  have been included in Section~IV-A of the revised manuscript. }
 
@@
 \begin{responsebox}{Response}
+We agree with the reviewer and have added a quantitative performance evaluation to the revised manuscript.
+Specifically, we manually selected eight regions of interest (ROIs) in each SAR image: four clearly homogeneous areas (e.g., water, croplands) and four heterogeneous areas (e.g., urban centers).
+Each ROI was labeled as class~0 (blue) or class~1 (red), as illustrated in Figs.~6a, 7a, and 8a.
 
-We include
+These ROIs were rasterized to create a partial ground-truth mask.
+Binary decision maps were obtained by thresholding the $p$-value maps at $ 0.05$ significance level, assigning 1 to pixels with $p < 0.05$ (heterogeneous) and 0 otherwise (homogeneous).
+These predictions were compared to the ground-truth labels, and standard metrics F1-score, kappa coefficient, and overall accuracy were computed.
+The results are reported in Table~III.
 
+To further support the evaluation, we computed ROC curves and the AUC metric for each test and image using the continuous $p$-values within the ROIs. .
 \begin{quote}
-	\textcolor{blue}{
-	text
-}
+\textcolor{blue}{These additions are included in Section~IV-C of the revised manuscript. }
 \end{quote}
@@
 \begin{responsebox}{Response}
-We have clarified that
+While machine learning-based classifiers and segmentation models are widely used in SAR analysis, our focus in this study is on interpretable, statistically grounded methods that provide analytical significance measures in the form of $p$-values.
+ In contrast to data-driven ML approaches, which typically require extensive labeled datasets, hyperparameter tuning, and large training efforts, our entropy-based tests offer lightweight, unsupervised alternatives that are easy to deploy and statistically explainable.
+These properties make them attractive for tasks such as rapid change detection or preliminary scene screening where data availability is limited or interpretability is essential.
+Moreover, our objective is not to outperform ML classifiers, but to compare the effectiveness of two statistical entropy measures under controlled conditions using SAR data.
 \begin{quote}
-	\textcolor{blue}{
-		text
-}
+\textcolor{blue}{We have clarified this distinction in the revised conclusions of the manuscript.}
 \end{quote}
-
 \end{responsebox}

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
R1 update: revised manuscript and reviewer responses added

@@
 
-We have clarified these contributions in the revised manuscript, in the final paragraph of the Introduction.
+Moreover, our aim is to propose a statistically grounded, interpretable approach that provides analytical significance measures.
+This distinguishes our method from data-driven alternatives, and makes it especially useful for unsupervised analysis or scenarios with limited ground-truth information.
 
 \begin{quote}
-	\textcolor{blue}{ In addition, we enhance the non-parametric estimator through a bootstrap-based bias correction technique, which increases accuracy, particularly for small sample sizes often used in practical SAR applications.}
+	\textcolor{blue}{ We have clarified these contributions in the revised manuscript, in the final paragraph of the Introduction.}
 \end{quote}
@@
 
-\vspace{2em}
+\vspace{1em}
 \begin{reviewbox}{Comment 2}
@@
 We appreciate the reviewer’s observation.
-In our work, \emph{roughness} is used in a statistical sense, following the interpretation of the parameter $\alpha$ in the $\mathcal{G}^0_I$ distribution.
+In our work, the term \emph{roughness} is used in a statistical sense, following the interpretation of the parameter $\alpha$ in the $\mathcal{G}^0_I$ distribution.
 This parameter reflects the degree of texture or variability within the resolution cell, which may result from both surface irregularities and land cover heterogeneity.
@@
 
-\vspace{2em}
+\vspace{1em}
 \begin{reviewbox}{Comment 3}
@@
 
-We thank the reviewer for this observation.
-However, we believe there may be a misunderstanding regarding the interpretation of $p$-values.
+We thank the reviewer for this observation. However, we believe there may be a misunderstanding regarding the interpretation of $p$-values. 
 In our formulation, the null hypothesis $H_0$ assumes that a region is homogeneous.
-Therefore, high $p$-values (e.g., $p > 0.05$) indicate that the data are consistent with homogeneity, while low $p$-values (e.g., $p < 0.05$) suggest statistical evidence of heterogeneity.
-
-The test statistic is based on the difference between the estimated Rényi entropy and the theoretical value under $H_0$.
-If the region is homogeneous, this difference tends to be close to zero, and the resulting $p$-value will be high, as expected.
-In contrast, heterogeneous regions typically produce larger differences and thus low $p$-values, leading to rejection of $H_0$.
+Therefore, high $p$-values ($p > 0.05$) indicate that the data are consistent with homogeneity, while low $p$-values ($p < 0.05$) suggest statistical evidence of heterogeneity.
 
 This is the intended behavior of the test, and the observed $p$-value patterns in the detection maps confirm its correct functioning.
-\end{responsebox}
-\begin{responsebox}{}
-We have clarified this point in the revised manuscript by adding a paragraph at the end of Section~III-D,  which explains how the $p$-value maps are constructed from sliding windows and how they should be interpreted.
+
+Regarding the reviewer’s observation that the method appears to “better estimate” over heterogeneous areas: this is a reflection of the test’s design.
+In heterogeneous areas, the difference between the estimated and theoretical entropy is larger, producing low $p$-values that correctly signal a rejection of the homogeneity hypothesis.
+In homogeneous areas, the difference is smaller, and the high $p$-values reflect that the null hypothesis is not rejected. Therefore, the method is working consistently across both types of regions.
 
@@
 \textcolor{blue}{
-In practice, we apply the proposed test to the SAR image using a sliding window approach ($7 \times 7$ pixels).
-For each window, we compute the test statistic under the null hypothesis of homogeneity and, assuming asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
-High $p$-values ($p > 0.05$) indicate consistency with $H_0$, while low values ($p < 0.05$) suggest heterogeneity.
-Note that the visual outputs in Figs. 6--8 show the $p$-values from this test, not the test statistic or entropy values.
+We have clarified this point in the revised manuscript by adding a paragraph at the end of Section~III-D,  which explains how the $p$-value maps are constructed from sliding windows and how they should be interpreted.
 }
@@
 
-\vspace{2em}
+\vspace{5em}
 \begin{reviewbox}{Comment 4}
@@
 \end{reviewbox}
+
 \begin{responsebox}{Response}
+In the revised manuscript, we have included a quantitative performance evaluation to complement the visual comparison presented in Figs. 6–8. 
+Specifically, we manually defined eight polygonal regions of interest (ROIs) in each SAR image: four clearly homogeneous areas ( water, flat croplands) and four clearly heterogeneous areas (urban centers).
+Each ROI was labeled as either homogeneous (class 0, shown in blue) or heterogeneous (class 1, in red).
 
-We have clarified  that
+These ROIs were then rasterized to create a partial ground-truth mask. 
+We thresholded the $p$-value maps at $0.05$ significance level to generate binary decision maps: values below this threshold were labeled as heterogeneous (1), and values above or equal to the threshold as homogeneous (0).
+The resulting prediction maps were compared against the ground-truth labels within the ROIs. 
+From this comparison, we computed statistical performance metrics such as F1-score, kappa coefficient, and overall accuracy, summarized in Table~III.
+
+Additionally, to assess performance across all decision thresholds, we computed ROC curves and the area under the curve (AUC) for each method.
+
 \begin{quote}
-	\textcolor{blue}{text}
+\textcolor{blue}{These additions appear in Section~IV-C of the revised manuscript.
+}
 \end{quote}
@@
 
-\vspace{2em}
+\vspace{9em}
 \begin{reviewbox}{Comment 6}
@@
 
-We improved Figures 6–8 by increasing the font size of labels, standardizing the color bar sizes, and updating the colormap in Figure 7 to enhance visual contrast.
+We improved Figures 6–8 by increasing the font size of labels, standardizing the size and placement of the color bars, and updating the colormap in Figure 8 to enhance visual contrast and improve the distinction between low and high $p$-values.
+
+Additionally, we added the corresponding optical images alongside each SAR image to facilitate the interpretation of heterogeneous regions and support visual correlation between land cover and detection results.
 
@@
 
-\vspace{2em} 
+\vspace{1em} 
 \begin{reviewbox}{Comment 7}
@@
 2, but similar trends were observed for other values of $L > 1$, confirming the robustness of $\lambda = 0.9$ and motivating its selection in the Rényi entropy estimator.
-
+\begin{quote}
 \textcolor{blue}{We have clarified this point in Section~III-A, where we explicitly justify the choice of $\lambda = 0.9$ based on the trade-off between bias and MSE.}
-
+\end{quote}
 \end{responsebox}
 
-\vspace{2em}
+\vspace{1em}
 
@@
 The choice of $n = 49$ corresponds to a $7 \times 7$ window, which is commonly used in SAR image processing as it strikes a balance between capturing local detail and providing enough data for reliable statistical analysis.
-
+\begin{quote}
 \textcolor{blue}{We have clarified the origin of the samples $n = 49$ in Section~III-A.}
+\end{quote}
 \end{responsebox}

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
R1 update: revised manuscript and reviewer responses added

@@
 ---
-title: Quantifying Roughness in SAR Imagery with the Rényi Entropy
+title: Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy
 format:
@@
    #- \hypersetup{draft} #Desactiva enlaces y referencias cruzadas
-   - \usepackage{float}
+   - \usepackage{float} # position figures
    - \usepackage{array}
@@
 }
-#
+
 #  packages
@@
   "tidyverse", "RColorBrewer", "ggsci", "carData", "ggpubr",  "patchwork", "dplyr", 
-  "kableExtra", "ggthemes", "latex2exp", "e1071", "viridis", "nortest", "bookdown"
+  "kableExtra", "ggthemes", "latex2exp", "e1071", "viridis", "nortest", "bookdown","terra", "sf", "pROC", "purrr"
 )
@@
 [S]{.IEEEPARstart}[ynthetic]{}
- Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Yu2023;@Mondini2021]. 
+ Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Mondini2021]. 
  It provides high-resolution data independent of sunlight and operates in various weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
-Despite its advantages, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Argenti2013; @Baraha2023].
-In intensity format, speckle is typically non-Gaussian, and its presence complicates subsequent image analysis tasks.
+However, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Baraha2023].
+In intensity format, speckle is non-Gaussian, which  complicates image analysis.
 
 The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different roughness levels. 
-A limiting case is the Gamma distribution, which arises when speckle is fully developed, indicating textureless regions. 
-Although these assumptions offer flexibility in describing SAR intensities, selecting the appropriate distribution can be challenging for two reasons: the small sample sizes used in practical applications and the inherent difficulties associated with parameter estimation.
-These challenges complicate model selection and highlight the need to explore alternative statistical approaches.
-
-Entropy measures have gained attention as valuable statistical tools for analyzing SAR data, with applications in edge detection&nbsp;[@Nascimento2014], 
-segmentation&nbsp;[@Nobre2016], 
-classification&nbsp;[@Cassetti2022], 
-and noise reduction&nbsp;[@Chan2022].
+A limiting case is the Gamma distribution, associated with fully developed speckle in textureless regions.
+However, selecting suitable models is challenging due to small window sizes in practical applications and difficulties in parameter estimation, motivating alternative statistical approaches.
+
+Entropy measures have gained attention for SAR analysis, with applications in edge detection&nbsp;[@Nascimento2014], segmentation&nbsp;[@Nobre2016], and noise reduction&nbsp;[@Chan2022].
 Traditionally, Shannon entropy&nbsp;[@Shannon1948] has been widely used to quantify data uncertainty and disorder.
 We explore a more general information measure: Rényi entropy—a generalization of Shannon’s formulation.
-This more flexible approach provides additional insights for identifying heterogeneity, making it a promising tool for enhancing SAR image analysis.
+
+\textcolor{blue}{
+Recent studies highlight the role of entropy in SAR classification. 
+Cassetti et al. [@Cassetti2022] evaluated entropy estimators in both supervised and unsupervised models. 
+Gallet et al. [@Gallet2024] proposed a Rényi divergence-based framework for explainable classification. 
+Parikh et al.
+[@Parikh2019] discussed challenges in deep learning for SAR, including limited availability of labeled data and the complexity of tuning hyperparameters.
+These works motivate lightweight, interpretable alternatives.
+}
 
 We propose a statistical test based on a non-parametric estimator of Rényi entropy to identify heterogeneous regions in SAR data.
-The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the homogeneity assumption.
-Compared to our previous approach using Shannon entropy&nbsp;[@Frery2024], the Rényi-based approach improves the detection of heterogeneity.
-\textcolor{blue}{In addition, we enhance the non-parametric estimator through a bootstrap-based bias correction technique, which increases accuracy, particularly for small sample sizes often used in practical SAR applications.}
-
-The remainder of this article is organized as follows.
-Section&nbsp;\ref{sec:pre} overviews the statistical models for SAR intensity data and introduces Rényi entropy.
-Section&nbsp;\ref{sec:met} describes the proposed hypothesis test and the test statistic.
+The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the homogeneity assumption, improving upon our previous Shannon-based approach&nbsp;[@Frery2024].
+\textcolor{blue}{We further enhance the non-parametric estimator through a bootstrap-based bias correction, improving accuracy for small windows.}
+\textcolor{blue}{The proposed approach is unsupervised, requires no training data, and yields interpretable $p$-values, making it especially suitable for scenarios where ground-truth information is limited or unavailable.}
+
+The rest of the article is organized as follows.
+Section&nbsp;\ref{sec:pre} overviews the statistical models for SAR intensity data and Rényi entropy.
+Section&nbsp;\ref{sec:met} describes the proposed hypothesis test.
 Section&nbsp;\ref{sec:app} evaluates the performance of the test using SAR data.
-Finally, the concluding remarks are drawn in Section&nbsp;\ref{sec:conclusion}.
+Finally, the conclusions are presented in Section&nbsp;\ref{sec:conclusion}.
 
@@
 \label{eq-HGI0}  
-H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \\ \ln(-1 - \alpha)  
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) \;\;+ \\ \ln(-1 - \alpha)  
 + \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
@@
 The derivation of the latter result is proven in the Appendix.
-Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
+Equation&nbsp;\eqref{eq-HGI0} can be read as:
+$$
+H_{\lambda}(\mathcal{G}^0_I)
+=
+\underbrace{H_\lambda\!\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
+\;\;\;\;\; +
+\underbrace{\Delta_\alpha}_{\text{extra entropy caused by texture}},
+$$
+\textcolor{blue}{where the excess term $\Delta_\alpha$ depends on the roughness parameter.
+When $\alpha\!\to\!-\infty$ (fully developed speckle) this excess tends to zero, so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}. 
+In practice, detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.}
+<!-- Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
 As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
-This work's core idea is to check if this excess entropy is significantly different from zero.
-
-@fig-convergence illustrates this convergence by showing $H_\lambda(\mathcal{G}^0_I)$  as a function of $\mu$ for different values of $\alpha$.
-As $\alpha$ decreases, the curves approach $H_\lambda(\Gamma_{\text{SAR}})$ (solid black line).
-This confirms that $\Gamma_{\text{SAR}}$ is a limiting case of $\mathcal{G}^0_I$.
-<!-- ACF Have you checked if it is possible to state the difference between \label{eq-HGI0} and \label{eq-HGammaSAR}? At the end of the day, that is what we want to assess. -->
-<!-- Corrected -->
-```{r fig-convergence, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=4.5, fig.height=3.5}
+-->
+<!-- This work's core idea is to check if this excess entropy is significantly different from zero. -->
+Fig.&nbsp;\ref{fig-convergence} illustrates this behaviour: as $\alpha$ decreases the coloured curves of $H_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $H_\lambda(\Gamma_{\mathrm{SAR}})$, confirming the limiting behavior.
+
+```{r fig-convergence,eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", fig.pos="hbt", , fig.cap="Convergence of $H_{\\lambda}(\\mathcal{G}^0_I)$ to $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ as $\\alpha$ decreases.", fig.width=4, fig.height=3}
+
+#fig.show="hide", 
+# eval=FALSE,  #
 
@@
 
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-convergence-1.pdf}
+  \vspace{0.5em}
+  \caption{Convergence of $H_{\lambda}(\mathcal{G}^0_I)$ to $H_{\lambda}(\Gamma_{\text{SAR}})$ as $\alpha$ decreases.}
+  \label{fig-convergence}
+\end{figure}
+```
 ## Non-parametric Estimation of Rényi Entropy
@@
 In our simulations, we find that for $L > 1$, the choice $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
-As shown in Fig.~\ref{fig-optimal_order}, the value $\lambda = 0.85$ exhibits slightly lower bias, but leads to higher MSE due to increased variance, supporting the selection of $\lambda = 0.9$.}
-
-```{r fig-optimal_order, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
+As shown in Fig.
+\ref{fig-optimal_order}, the value $\lambda = 0.85$ exhibits slightly lower bias, but leads to higher MSE due to increased variance, supporting the selection of $\lambda = 0.9$.}
+
+```{r fig-optimal_order, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide",  out.width="42%",  fig.pos="hbt", fig.cap="Bias and MSE as a function of $\\lambda$, with $n=49$, $L=5$.", fig.width=7, fig.height=4.5}
+#fig.show="hide", 
+# eval=FALSE,  #
 
@@
 
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-optimal_order-1.pdf}
+  \vspace{0.5em}
+  \caption{Bias and MSE as a function of $\lambda$, with $n=49$, $L=5$.}
+  \label{fig-optimal_order}
+\end{figure}
+```
 Particularly, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results.
@@
 Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
-$$
+\begin{equation*}
 \widetilde{H}_{\lambda} = 2\widehat{H}_{\lambda}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_{\lambda}(\bm{Z}^{(b)}),
-$$
+\end{equation*}
 where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ is the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.
 
-A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($L=5,\ \mu=1$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in&nbsp;@fig-bias_mse.
-
-<!-- ACF Remove the minor vertical grid (there is nothing between 49 and 81) -->
-<!-- Corrected -->
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($L=5,\ \mu=1$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in Fig.
+\ref{fig-bias_mse}.
 ```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
@@
 
-```{r fig-bias_mse, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}
+```{r fig-bias_mse, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide",  out.width="42%", fig.pos="hbt",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=7, fig.height=5}
+
+#fig.show="hide", 
+# eval=FALSE,  #
 
@@
 
+```
+
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.40\textwidth]{Figures-R1/fig-bias_mse-1.pdf}
+  \vspace{0.1em}
+  \caption{Bias and MSE of the Rényi entropy estimators for $\Gamma_{\text{SAR}}$.}
+  \label{fig-bias_mse}
+\end{figure}
 ```
@@
 Under $\mathcal{H}_0$, the expected value of the entropy estimator should match the theoretical $H_{\lambda}(\Gamma_{\text{SAR}})$. 
-If the estimated entropy significantly deviates from its expected value, we reject $\mathcal{H}_0$, indicating the presence of heterogeneity.
-
-Classical inference methods are inapplicable since homogeneity corresponds to $\alpha \to -\infty$ in the $\mathcal{G}^0_I$ model. 
-Instead, we propose a test statistic based on the Rényi entropy estimator, comparing it with its theoretical expectation under $\mathcal{H}_0$ to distinguish between homogeneous and heterogeneous areas.
+Significant deviations indicate heterogeneity.
 
 ## The Proposed Test
-
-Assume we have an estimator $\widetilde{H}_{\lambda}$ for the Rényi entropy of an arbitrary model.
-For testing&nbsp;\eqref{eq:hypothesis_test}, this estimator is expected to be close to the theoretical expression given in Equation&nbsp;\eqref{eq-HGammaSAR}.
-Since $L\geq1$ is known, we define the test statistic as follows:
+The test statistic quantifies the discrepancy between estimated and theoretical entropy under homogeneity. Since $L\geq1$ is known, we define the test statistic as follows:
 \begin{multline}
@@
 where $\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}$ is the sample mean.
-This test statistic should be close to zero when the null hypothesis holds.
-@fig-densities shows the empirical density of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, based on $10^4$ replications of the $\Gamma_{\text{SAR}}$ model for each sample size $n \in \{49,81, 121\}$ with $\lambda=0.9$ and $L \in \{5,18\}$.
-<!-- ACF 10^4 replications of samples of size?   -->
-<!-- Corrected -->
+The test statistic can be interpreted as:
+$$
+S_{\widetilde H_\lambda} 
+= 
+\underbrace{\widetilde H_\lambda}_{\text{estimated}} 
+\;-\;
+\underbrace{H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{theoretical under } H_0},
+$$
+\textcolor{blue}{the difference between the estimated entropy and the expected value under homogeneity.
+Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and thus heterogeneity.
+This formulation avoids estimating parameters of the $\mathcal{G}^0_I$ model such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
+Moreover, the method remains effective for small samples, aided by the bootstrap bias correction.}
+
+Fig.
+\ref{fig-densities} shows the empirical distribution of $S_{\widetilde{H}_{\lambda}}$ under $\mathcal{H}_0$, obtained from $10^4$ Monte Carlo simulations with varying sample sizes ($n \in {49,81,121}$), $\lambda=0.9$, and $L \in {5,18}$.
+The concentration around zero confirms the test's expected behavior, while the heavy tails indicate sensitivity to deviations, enabling the detection of subtle texture changes.
+
 ```{r Simulated_densityR, echo=FALSE, message=FALSE}
@@
 
-```{r fig-densities, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+```{r fig-densities,  eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", out.width="47%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+#fig.show="hide", 
+# eval=FALSE,  #
 
@@
 
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-densities-1.pdf}
+  \vspace{0.2em}
+  \caption{Empirical densities of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ under $\mathcal{H}_0$.}
+  \label{fig-densities}
+\end{figure}
+```
+
 Vasicek&nbsp;[@vasicek1976test] proved that, for sufficiently large samples, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ asymptotically follows a normal distribution:
@@
 where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
-@fig-density_standardized shows smoothed histograms of standardized test statistics.
+Fig. \ref{fig-density_standardized} shows smoothed histograms of standardized test statistics.
 
@@
 
-```{r fig-density_standardized, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
+```{r fig-density_standardized,eval=FALSE,  echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
+
+#fig.show="hide", 
+# eval=FALSE,  #
 
@@
 ```
+
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.35\textwidth]{Figures-R1/fig-density_standardized-1.pdf}
+  %\vspace{0.1em}
+  \caption{Standardized empirical densities of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ under $\mathcal{H}_0$.}
+  \label{fig-density_standardized}
+\end{figure}
+```
 In general, hypotheses tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
 To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
-<!-- ACF I wish you had used the siunitx package for typing percentages, but not if this is incompatible with the tables -->
-<!-- Corrected -->
 The observed Type&nbsp;I error rates align with the nominal values, confirming the test validity.
@@
 ```
-
 \textcolor{blue}{
@@
 For each window, we compute the test statistic under the null hypothesis of homogeneity and, assuming asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
-High $p$-values ($p > 0.05$) indicate consistency with $H_0$, while low values ($p < 0.05$) suggest heterogeneity.
-Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values.
-}
+High $p$-values ($p > 0.05$) indicate no evidence to reject homogeneity, while low values ($p < 0.05$) suggest statistically significant deviations and are interpreted as heterogeneity.
+}
+<!-- Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values. -->
 
 # Applications to SAR Data {#sec:app}
-In this section, we compare two test statistics for detecting heterogeneity in SAR data: (i) the Rényi entropy-based test, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, described in&nbsp;\eqref{eq-test}; and (ii) the Shannon entropy-based test, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, which is based on the Al-Omari estimator proposed in&nbsp;[@IbrahimAlOmari2014] and was improved via bootstrap in our previous work.
+
+## Datasets
+We compare two test statistics for detecting heterogeneity in SAR data: (i) the Rényi entropy-based test, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, described in&nbsp;\eqref{eq-test}; and (ii) the Shannon entropy-based test, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, which is based on the Al-Omari estimator proposed in&nbsp;[@IbrahimAlOmari2014] and was improved via bootstrap in our previous work.
 The details of this test can be found in Frery et al.&nbsp;[@Frery2024].
-<!-- ACF What is $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$? -->
-<!-- JA: I added a brief explanation, indicating that it is based on the Al-Omari estimator and was improved with bootstrap. -->
-
-We applied these tests to images covering urban, agricultural, and water regions. 
-We analyzed images from London, United Kingdom;  the surroundings of Munich, Germany; and  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london-a},&nbsp;\ref{fig:munich-a}, and&nbsp;\ref{fig:dublin-a}.
-All images were acquired in HH polarization.
-Table&nbsp;\ref{tab:table_param} provides the detailed acquisition parameters of these images.
-<!-- ACF They all have HH polarization; the column is not informative, and can be deleted to gain space -->
-<!-- Corrected -->
-\renewcommand{\arraystretch}{3}   
+
+The selected scenes, acquired in HH polarization, correspond to the surroundings of London (United Kingdom), the outskirts of Munich (Germany), and the Dublin Port area (Ireland), as shown in Figs.&nbsp;\ref{fig:london-sar}-\ref{fig:dublin-sar}.
+Corresponding optical images (Figs.&nbsp;\ref{fig:london-optical}–\ref{fig:dublin-optical}) illustrate land cover context. Table&nbsp;\ref{tab:table_param} details the SAR acquisition parameters.
+
+\renewcommand{\arraystretch}{2.5}   
 ```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}
@@
 colnames(SAR_data) <- c(
-  "\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", 
+  "\\textbf{Scene}", "\\textbf{Mission}", "\\textbf{Band}", 
   "\\textbf{Size (pixels)}", "$\\bm{L}$", 
@@
       caption = "Parameters of selected SAR images.",
-      table.envir = "table", position = "hbt") %>%
+      table.envir = "table", position = "H") %>%
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", font_size = 21) %>% 
+  kable_styling(latex_options = "scale_down", font_size = 22) %>% 
   kable_styling(full_width = TRUE) %>%
   column_spec(1, width = "3.0cm") %>%
-  column_spec(2, width = "3.7cm") %>%
+  column_spec(2, width = "4.5cm") %>%
   column_spec(3, width = "1.5cm") %>%
@@
 ```
-We used sliding windows of size $7\times 7$.
-The results are presented as $p$-value maps and binary maps at a $0.05$ significance level. 
-Figs.&nbsp;\ref{fig:london-b}--\ref{fig:london-c},&nbsp;\ref{fig:munich-b}--\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-b}--\ref{fig:dublin-c} correspond to $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, while Figs.&nbsp;\ref{fig:london-d}--\ref{fig:london-e},&nbsp;\ref{fig:munich-d}--\ref{fig:munich-e}, and&nbsp;\ref{fig:dublin-d}--\ref{fig:dublin-e} correspond to $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$.
-
-The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
-The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions). 
-In contrast, black areas represent regions with $p$-values below $0.05$, providing statistical evidence to reject the null hypothesis and indicating heterogeneity.
-
-The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
-<!-- ACF Where is the Shannon-based approach shown? -->
-<!-- JA: The results of the Shannon-based approach can be observed in the corresponding binary maps. -->
+\textcolor{blue}{
+For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP).
+To validate this value, we estimated the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the coefficient of variation.
+The results were consistent with the metadata.
+We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
+
+## Qualitative Inspection
+
+The output consists of $p$-value maps and binary maps at a $0.05$ significance level. 
+The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
+The binary maps (Figs.&nbsp;\ref{fig:london-005-renyi},&nbsp;\ref{fig:london-005-shann},&nbsp;\ref{fig:munich-005-renyi},&nbsp;\ref{fig:munich-005-shann},&nbsp;\ref{fig:dublin-005-renyi},&nbsp;\ref{fig:dublin-005-shann}) display heterogeneous detections in black ($p<0.05$) and homogeneous areas in white ($p \geq 0.05$).
+Visually, the Rényi test exhibits greater sensitivity in detecting textural variations due to the flexibility provided by the parameter $\lambda$.
 
@@
     \centering
-    \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/london_2000.png}
+    \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
         \caption{SAR image}
-        \label{fig:london-a}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london-E.png}
+        \label{fig:london-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.142\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
+        \caption{Optical image}
+        \label{fig:london-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.179\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_E.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:london-b}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
+        \label{fig:london-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.145\textwidth}
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:london-c}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london-E.png}
+        \label{fig:london-005-renyi}
+    \end{subfigure}
+   \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.18\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_E.png}
         \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
-        \label{fig:london-d}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
+        \label{fig:london-shann}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.145\textwidth}
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:london-e}
+        \label{fig:london-005-shann}
     \end{subfigure}
@@
     \centering
-    \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/munich_1024.png}
+        \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/munich_roi.png}
         \caption{SAR image}
-        \label{fig:munich-a}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi_munich-H.png}
+        \label{fig:munich-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+  \begin{subfigure}{0.137\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/munich_optical.png}
+        \caption{Optical image}
+        \label{fig:munich-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich_H.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:munich-b}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_renyi.png}
+        \label{fig:munich-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_renyi_munich.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:munich-c}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon_munich-H.png}
+        \label{fig:munich-005-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich_H.png}
         \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:munich-d}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_munich_shannon.png}
+        \label{fig:munich-shann}
+    \end{subfigure}
+   \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_shannon_munich.png}
         \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:munich-e}
+        \label{fig:munich-005-shann}
     \end{subfigure}
@@
     \centering
-    \begin{subfigure}{0.17\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/dublin_1100.png}
+        \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/dublin_roi3.png}
         \caption{SAR image}
-        \label{fig:dublin-a}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-B.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:dublin-b}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
+        \label{fig:dublin-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+\begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/dublin.png}
+        \caption{Optical image}
+        \label{fig:dublin-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin_B.png}
+        \caption{$p$-value map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:dublin-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:dublin-c}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.20\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-B.png}
-        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:dublin-d}
-    \end{subfigure}
-    \hspace{0.01\textwidth}
-    \begin{subfigure}{0.17\textwidth}
+        \caption{Binary map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:dublin-005-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin_B.png}
+        \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:dublin-shann}
+    \end{subfigure}
+    \hspace{0.0000001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:dublin-e}
+        \caption{Binary $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:dublin-005-shann}
     \end{subfigure}
     \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
-
     \label{fig:dublin}
@@
 
+## Quantitative Evaluation
+
+Eight polygonal regions of interest (ROIs) were manually selected for each scene (Figs.&nbsp;\ref{fig:london-sar}-\ref{fig:dublin-sar}): heterogeneous areas (red, class 1) and homogeneous areas (blue, class 0).
+These ROIs were rasterized to match the SAR resolution, forming a partial ground-truth.
+We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0) and then compared these decision maps with the ground-truth to compute: F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
+Table&nbsp;\ref{tab:table_metrics} summarizes the results.
+Across all scenes, the Rényi-based test outperformed Shannon’s in all metrics, with notable gains in London ($F_1$: 0.695 vs.
+0.617; $\kappa$: 0.626 vs.
+0.542), highlighting its ability to capture  heterogeneity under strong speckle (single-look).
+
+\renewcommand{\arraystretch}{1.1} 
+```{r metrics_table, echo=FALSE, message=FALSE, warning=FALSE}
+
+load("./Data/metrics_london_renyi.RData")
+load("./Data/metrics_london_shannon.RData")
+load("./Data/metrics_munich_renyi.RData")
+load("./Data/metrics_munich_shannon.RData")
+load("./Data/metrics_dublin_renyi.RData")
+load("./Data/metrics_dublin_shannon.RData")
+
+all_metrics <- rbind(
+  metrics_london_renyi,
+  metrics_london_shannon,
+  metrics_munich_renyi,
+  metrics_munich_shannon,
+  metrics_dublin_renyi,
+  metrics_dublin_shannon
+)
+
+numeric_metrics <- all_metrics
+
+all_metrics$Method <- ifelse(
+  all_metrics$Method == "Renyi", 
+  "$S_{\\widetilde{H}_{\\lambda}}$", 
+  "$S_{\\widetilde{H}_{\\text{AO}}}$"
+)
+
+for (i in seq(1, nrow(all_metrics), by = 2)) {
+  for (col in c("F1", "Kappa", "OA")) {
+      val1 <- numeric_metrics[[col]][i]
+      val2 <- numeric_metrics[[col]][i + 1]
+
+    if (val1 > val2) {
+      all_metrics[i, col]     <- sprintf("\\bm{$%.3f$}", val1)
+      all_metrics[i + 1, col] <- sprintf("$%.3f$", val2)
+    } else {
+      all_metrics[i, col]     <- sprintf("$%.3f$", val1)
+      all_metrics[i + 1, col] <- sprintf("\\textbf{$%.3f$}", val2)
+    }
+  }
+}
+
+colnames(all_metrics) <- c("\\textbf{Scene}", "\\textbf{Test}", "$\\bm{F_1}$", "$\\kappa$", "\\textbf{OA}")
+
+scene_labels <- all_metrics$Scene
+for (scene in unique(scene_labels)) {
+  idx <- which(scene_labels == scene)
+  scene_labels[idx[1]] <- paste0("\\multirow{2}{*}{", scene, "}")
+  scene_labels[idx[2]] <- ""
+}
+all_metrics$Scene <- scene_labels
+
+kable(all_metrics,
+      caption = "Quantitative measures of heterogeneity detection",
+      format = "latex",
+      booktabs = TRUE,
+      align = "cccccc",
+      escape = FALSE,
+      label = "table_metrics",
+      centering = FALSE,
+      table.envir = "table", 
+      position = "hbt",
+      row.names = FALSE) %>%
+  row_spec(0, align = "c") %>%
+  #collapse_rows(columns = 1, valign = "bottom") %>% 
+  collapse_rows(latex_hline = "major", valign = "bottom") %>%
+  kable_styling(latex_options = "scale_down", font_size = 7) %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds&nbsp;(Figs.&nbsp;\ref{ROC1-1}).
+Each curve plots the probability of detection (Pd) versus the probability of false alarm (PFA).
+Pd reflects the proportion of heterogeneous pixels correctly detected, while PFA represents the proportion of homogeneous pixels misclassified as heterogeneous.
+
+```{r fig-ROC2, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", fig.fullwidth = TRUE, out.width="49%",  fig.pos="hbt", fig.cap="ROC curves.", fig.width=35, fig.height=10}
+
+#fig.show="hide",  oculta figura
+# eval=FALSE,  # no se ejecuta codigo
+roc_file <- "./Data/roc_results.RData"
+
+rotate_matrix <- function(m) t(apply(m, 2, rev))
+
+mk_raster <- function(mat, sar) {
+  r <- rast(nrows=nrow(mat), ncols=ncol(mat),
+            ext = ext(xmin(sar)+3*res(sar)[1], xmax(sar)-3*res(sar)[1],
+                      ymin(sar)+3*res(sar)[2], ymax(sar)-3*res(sar)[2]),
+            crs = crs(sar))
+  values(r) <- as.vector(mat)
+  flip(r, direction="vertical")
+}
+
+if (!file.exists(roc_file)) {
+
+  cities <- list(
+    London = list(
+      sar     = "./Data/SAR/envi_london_2000/Intensity_HH.img",
+      rois    = "./Data/rois_london_m.gpkg",
+      renyi   = "./Data/p_values_renyi_london.Rdata",
+      shannon = "./Data/p_values_shannon_london.Rdata"
+    ),
+    Munich = list(
+      sar     = "./Data/SAR/envi_munich_1024_final/Intensity_HH.img",
+      rois    = "./Data/rois_munich.gpkg",
+      renyi   = "./Data/p_values_renyi_munich.Rdata",
+      shannon = "./Data/p_values_shannon_munich.Rdata"
+    ),
+    Dublin = list(
+      sar     = "./Data/SAR/envi_dublin_1100_HH/Intensity_HH.img",
+      rois    = "./Data/rois_dublin_m.gpkg",
+      renyi   = "./Data/p_values_renyi_dublin.Rdata",
+      shannon = "./Data/p_values_shannon_dublin.Rdata"
+    )
+  )
+
+  roc_list <- list()
+
+  for (city in names(cities)) {
+    cfg <- cities[[city]]
+    sar <- rast(cfg$sar)
+    rois <- st_read(cfg$rois, quiet=TRUE) |> st_transform(crs(sar))
+
+    matR <- rotate_matrix(get(load(cfg$renyi)))
+    matS <- rotate_matrix(get(load(cfg$shannon)))
+
+    rR <- mk_raster(matR, sar)
+    rS <- mk_raster(matS, sar)
+
+    gt <- rasterize(rois, rR, field="class")
+    idx <- !is.na(values(gt))
+    truth <- factor(values(gt)[idx], levels=c(0,1), labels=c("0","1"))
+    scoreR <- values(rR)[idx]
+    scoreS <- values(rS)[idx]
+
+    rocR <- roc(truth, scoreR, levels=c("0","1"), direction=">")
+    rocS <- roc(truth, scoreS, levels=c("0","1"), direction=">")
+    aucR <- round(auc(rocR), 3)
+    aucS <- round(auc(rocS), 3)
+
+    df <- data.frame(
+      FPR = c(1 - rocR$specificities, 1 - rocS$specificities),
+      TPR = c(rocR$sensitivities, rocS$sensitivities),
+      Method = factor(rep(c("Renyi", "Shannon"),
+                          times=c(length(rocR$sensitivities), length(rocS$sensitivities))),
+                      levels=c("Renyi","Shannon"))
+    )
+
+    labels <- c(
+      Renyi   = bquote(italic(S)[widetilde(italic(H))[lambda]] ~ "(AUC =" ~ .(aucR) ~ ")"),
+      Shannon = bquote(italic(S)[widetilde(italic(H))[AO]]      ~ "(AUC =" ~ .(aucS) ~ ")")
+    )
+
+    roc_list[[city]] <- list(df = df, labels = labels)
+  }
+
+  save(roc_list, file = roc_file)
+} else {
+  load(roc_file)
+}
+
+plot_city <- function(df, labels, title){
+  ggplot(df, aes(x = FPR, y = TPR, colour = Method, linewidth = Method)) +
+    geom_line(alpha = 0.7) +
+    scale_colour_manual(values=c(Renyi="#FC4E07", Shannon="#0072B2"),
+                        labels=labels) +
+    scale_linewidth_manual(values=c(Renyi=3.5, Shannon=3.1), guide=FALSE) +
+scale_x_continuous(minor_breaks = NULL, labels = scales::number_format(accuracy = 0.1)) +
+scale_y_continuous(minor_breaks = NULL, labels = scales::number_format(accuracy = 0.1))+
+    guides(colour = guide_legend(override.aes=list(linewidth=c(3.8,3.8), alpha=0.8))) +
+    labs(x = "PFA ",
+         y = "Pd ",
+         title = title) +
+   theme_minimal(base_family = "serif") +
+    theme(plot.title = element_text(hjust = 0.5, size = 38,  face = "bold"),
+          axis.title = element_text(size = 30, face = "bold"),
+          axis.text = element_text(size = 35),
+          #legend.text = element_text(size = 25),
+          #legend.position = "bottom",
+          legend.position = c(0.95, 0.05),      
+          legend.justification = c(1, 0),       
+          legend.text  = element_text(size = 32),
+          #legend.background = element_rect(fill = "white", color = "gray70", linewidth = 0.2),
+          legend.title = element_blank()
+
+)
+}
+
+p1 <- plot_city(roc_list$London$df, roc_list$London$labels, "London")
+p2 <- plot_city(roc_list$Munich$df, roc_list$Munich$labels, "Munich")
+p3 <- plot_city(roc_list$Dublin$df, roc_list$Dublin$labels, "Dublin")
+
+p1 + p2 + p3 + plot_layout(ncol = 3)
+
+```
+
+```{=latex}
+\begin{figure}[hbt]
+  \centering
+  \includegraphics[width=0.49\textwidth]{Figures-R1/ROC1-1.pdf}
+  \caption{ROC curves comparing the tests $S_{\widetilde{H}_{\lambda}}$ and $S_{\widetilde{H}_{\text{AO}}}$.}
+  \label{fig:roc}
+\end{figure}
+```
+
+The area under each ROC curve (AUC) quantifies global detection performance.
+The Rényi-based test  achieved higher AUCs across all scenes—London: 0.963 vs.\ 0.776; Munich: 0.996 vs.\ 0.989; Dublin: 0.980 vs.\ 0.971—demonstrating superior robustness compared to the Shannon-based test under various terrain conditions and textures.
+
 # Conclusions {#sec:conclusion}
 
-This study presented a new statistical approach based on Rényi entropy for detecting heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter. 
-The proposed test performance was evaluated by a Monte Carlo study. 
-The results showed that the method effectively controls the probability of Type&nbsp;I error while maintaining a high detection performance that improves as the sample size increases.
-
-<!-- ACF Again, where are the Shannon results? -->
-<!-- JA: The Shannon results are visually represented through p-value and binary maps for each image -->
-The effectiveness of the Rényi entropy-based test in SAR images was compared with the Shannon entropy-based test using $p$-value and binary maps. 
-The differences between the two methods are evident in the binary maps at a $0.05$ significance level.
-Although both tests successfully detected heterogeneous regions, the Rényi-based test performed better due to its flexibility in adjusting the $\lambda$ parameter, allowing for finer texture variation differentiation.
-
-Future work will explore additional statistical metrics to improve the comparison between both tests and better quantify their differences in detecting heterogeneity.
+This study presented a statistical approach based on Rényi entropy for detecting heterogeneity in SAR images, distinguishing between fully developed speckle and heterogeneous clutter.
+The proposed test was validated with synthetic experiments via a Monte Carlo study, demonstrating that it effectively controls the probability of Type&nbsp;I error while maintaining high detection performance that improves with sample size.
+
+\textcolor{blue}{Using real SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions.
+Visual analysis showed greater sensitivity of the Rényi-based test to textural variations.
+Quantitative evaluation with ground-truth ROIs and standard classification metrics confirmed the superior performance of the Rényi-based test across all scenes.}
+
+\textcolor{blue}{Although machine learning-based SAR classifiers are widely used, our focus is on interpretable, statistically grounded methods that yield analytical significance measures.
+This makes them suitable for rapid detection, screening, and environments with limited data availability.}
+
+\textcolor{blue}{Future work will explore the integration of the improved Rényi estimator into SAR classification pipelines, both supervised and unsupervised, extending its utility beyond heterogeneity testing.}
 
@@
 
-<!-- # Acknowledgment {-} -->
-
-<!-- This study was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) - Finance Code 001, and the Fundação de Amparo à Ciência e Tecnologia de Pernambuco (FACEPE), Brazil.
--->
-
-# Computational Information {-}
-This article was written in Quarto and is fully reproducible. We used RStudio version 2024.12.1+563, and R version 4.4.2.
+<!-- # Computational Information {-} -->
+<!-- This article was written in Quarto and is fully reproducible. We used RStudio version 2024.12.1+563, and R version 4.4.2. -->
 

### 2025-06-02 Text/Reports/qualification_2024/chapters/1_intro.tex
R1 update: revised manuscript and reviewer responses added

--- 2024-05-07 Text/Thesis/chapters/1_intro.tex
@@
 The technology of Synthetic Aperture Radar (SAR) imaging operates on the comprehensive aperture principle to produce high-resolution SAR images.
-In contrast to conventional optical remote sensing images, SAR images remain unaffected by external factors, making them suitable for identifying ground targets in diverse weather conditions and expansive areas.
-Consequently, SAR imagery has become essential for environmental monitoring, disaster management, agriculture, topography mapping, geological exploration, maritime navigation, defense, and climatology~\citep{Moreira2013, iglesias2013atmospheric, Mu2019}.
+In contrast to conventional optical remote sensing images, SAR images remain unaffected by external factors, making them suitable for identifying ground targets in diverse weather conditions and expansive areas~\citep{Mu2019}.
+Consequently, SAR imagery has become essential for environmental monitoring~\citep{Amitrano2021}, crop mapping~\citep{DingleRobertson2020}, ship target detection~\citep{Wang2019}, and climatology~\citep{Zhao2023}.
 However, the effective use of SAR
@@
 
-In this context, we present a set of three novel test statistics that
-aim to distinguish between homogeneous and non-homogeneous returns,
-particularly between gamma and \(\mathcal{G}^0\) distributed data,
-assuming the number of looks is known.
- We use properties such as entropy and coefficient of variation.
-
 Entropy is a fundamental concept in information theory with far-reaching
-applications in pattern recognition, statistical physics, image
-processing, edge detection and SAR image
-analysis~\citep{Presse2013,MohammadDjafari2015,Avval2021, Nascimento2014,Nascimento2019}.
-\citet{Shannon1948} this concept for a random variable to measure information and uncertainty. 
+applications in pattern recognition~\citep{Avval2021}, statistical physics~\citep{Presse2013}, image
+processing~\citep{MohammadDjafari2015}, edge detection~\citep{Nascimento2014} and SAR image
+analysis~\citep{Nascimento2019}.
+\citet{Shannon1948} introduced this concept for a random variable to measure information and uncertainty. 
 Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data
@@
 uniformity~\citep{Wieczorkowski1999,Zamanzade2012}.
+
 Entropy estimation is challenging, especially when the model is unknown. In these cases,
@@
 and robust because it does not enforce a model or parametric
-constraints.
+constraints. In this context, we introduce a novel approach: a bootstrap-improved non-parametric estimator for Shannon entropy.
 
 The coefficient of variation (CV), introduced in 1896 by~\citet{Pearson1896}, is a relative dispersion measure widely used
-in various fields of applied statistics, including sampling,
-biostatistics, medical and biological research, climatology and other
-fields~\citep{hendricks1936sampling,Tian2005,SubrahmanyaNairy2003,Chankham2024}.
-It facilitates the comparison of variability between different
+in various fields of applied statistics, including sampling~\citep{hendricks1936sampling},
+biostatistics~\citep{Tian2005}, medical and biological research~\citep{SubrahmanyaNairy2003}, climatology~\citep{Chankham2024} and other
+fields. It facilitates the comparison of variability between different
 populations and is particularly valuable for relating variables with
-different units. This is because when the primary purpose is to compare
-the variations of several variables, the standard deviation can only
-serve as an adequate measure of variation if all variables are expressed
-in the same unit of measurement and have identical means. If these
-conditions are not met, then the CV is the relative measure that is
-usually used in real applications. The variable with the highest CV
+different units. The variable with the highest CV
 value has the largest relative dispersion around the mean
 value~\citep{Banik2011}. The coefficient of variation is the primary
-measure of heterogeneity in SAR data~\citep{Ulaby1986,Touzi1988}. We
-study two ways of estimating the coefficient of variation.
+measure of heterogeneity in SAR data~\citep{Ulaby1986,Touzi1988}. 
+In our work, we employ both the classical CV and a robust alternative, which is based on the ratio of the mean absolute deviation from the median (MnAD) to the median.
+These measures offer a more detailed view of data variability.
 
-The other parameter we study is the Shannon entropy. Different roughness
-levels materialized as models for SAR data, have different entropy
-values, but this fundamental quantity can also be estimated in a
-model-agnostic way. We exploit this property and design a
-bootstrap-improved non-parametric estimator for the Shannon entropy.
+The expected value, a critical component in both CV and the Shannon entropy, influences their interpretation. 
+In CV calculations, the expected value serves as a reference point for assessing data dispersion relative to its average value, while in the Shannon entropy, the expected value also plays an important role, particularly within parametric distributions such as the Gamma or the \({G}_I^0\)  distribution.
+In these cases, the mean appears in the analytical entropy formula, indicating that the entropy of the distribution is influenced by the mean value of the data.
 
-We devise test statistics based on these three estimators: the classical
-coefficient of variation, a robust version, and the Shannon entropy
-estimator. We apply these test statistics to generate maps of evidence
-of homogeneity that reveal different types of targets in the SAR data.
-We show that our proposed method is superior to existing approaches with
-simulated data and SAR images.
+When applying these statistical concepts to SAR image analysis, we aim to discern between homogeneous and non-homogeneous regions, contributing to the improved interpretation and understanding of SAR data.
+In our study, we devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator.
+We apply these test statistics to generate maps of evidence of homogeneity that reveal different types of targets in the SAR data, assuming the number of looks is known.
+Likewise, we show that our proposed method is superior to existing approaches with simulated data and SAR images.
 
@@
 
-\subsection{Submitted Articles}
+\subsection*{Submitted Articles}
 
@@
 In Chapter~\ref{chp:conclusions}, the conclusions and future work are presented.
-%Chapter ~\ref{chp:models} explains ...
-%------------------------------------
-%	HAZARD: OVERVIEW
-%------------------------------------
 
-%\section{Computing platforms}
-%This  project required a vast amount of computing, preprocessing, analysis and plotting.
-
-%------------------------------------
-%	TODO STUFF
-%------------------------------------
-% \section{Additional sources to integrate in this chapter}
-% \begin{itemize}
-% \item check all TODOs
-% \item read again \url{http://ec.europa.eu/environment/water/flood_risk/flood_atlas/pdf/handbook_goodpractice.pdf}
-% \item include citation EU Floods Directive (2007/60/EC) , \cite{Mysiak2013, EUFD2007}
 % \item section to talk about uncertainties? \citet{alfieri2014} has a good section about it

### 2025-06-02 Text/Reports/qualification_2024/chapters/2_background.tex
R1 update: revised manuscript and reviewer responses added

--- 2024-05-08 Text/Thesis/chapters/2_background.tex
@@
 In the case of optical Earth observation imagery, the sun is used as a global illumination source. 
-Thus optical image sensors tend to operate on a sun-synchronous orbit to ensure the scene is well illuminated during acquisition. 
+Thus, optical image sensors tend to operate on a sun-synchronous orbit to ensure the scene is well illuminated during acquisition. 
 On the other hand, SAR uses the principle of active sensing, whereby the sensor acts as both an illumination source as well as the acquisition unit. 
@@
 \midrule
-Ka & $\,25$--$40$ & $\phantom{-}0.75$--$1.2$ \\
-Ku & $\,12$--$17.6$ & $\phantom{-}\,1.7$--$2.5$ \\
-X  & $7.5$--$12$  & $2.5$--$4$   \\
-C  & $ 3.75$--$7.5$ & $\phantom{-}4$--$8$   \\
-S  & $2$--$3.75$   & $\phantom{-}\,8$--$15$    \\
-L  & $1$--$2$   & $\phantom{-}15$--$30$   \\
-P  & $0.3$--$1$ & $\phantom{-}\,30$--$100$  \\
+Ka & $\,25.0$--$40.0$ & $\phantom{-}0.75$--$1.2$ \\
+Ku & $\,12.0$--$17.6$ & $\phantom{-}\,1.7$--$2.5$ \\
+X  & $\phantom{-}7.5$--$12.0$  & $\phantom{-}2.5$--$4.0$   \\
+C  & $ 3.7$--$7.5$ & $\phantom{-}4.0$--$8.0$   \\
+S  & $2.0$--$3.7$   & $\phantom{-}\,8.0$--$15$    \\
+L  & $1.0$--$2.0$   & $\phantom{-}15$--$30$   \\
+P  & $0.3$--$1.0$ & $\phantom{-}\,30$--$100$  \\
 \bottomrule
@@
 \end{table}
+
+%\begin{longtable}{@{}
+			%c
+			%S[table-format=-4.1]@{--}S[table-format=2.5]
+			%S[table-format=-2.1,
+		%table-align-text-pre=false]@{--}S[table-format=2.6, table-align-text-pre=false]
+			%%S[table-format=-2.1]@{--}S[table-format=2.3]
+			%@{}}
+		%%\caption{Las entradas de esta tabla están centradas correctamente, pero las distancias son difíciles de ajustar.}%
+		%\caption[Different bands in microwave remote sensing]{\label{tab:bands}Different bands in microwave remote sensing,~\citep{Moreira2013}.}
+		%\\
+		%\toprule
+		%\text{Band}            &
+		%\multicolumn{2}{c}{\text{\textbf{Frequency} $\left[\text{GHz}\right]$}}        &
+		%\multicolumn{2}{c}{\textbf{Wavelength} $\left[\text{cm}\right]$}          \\
+		%\midrule
+		%\endfirsthead
+		%\midrule
+		%\text{Band}            &
+		%\multicolumn{2}{c}{\text{\textbf{Frequency} $\left[\text{GHz}\right]$}}        &
+		%\multicolumn{2}{c}{\textbf{Wavelength} $\left[\text{cm}\right]$}          \\
+		%\midrule
+		%\endhead
+		%Ka & 25.0 & 40.0 & 0.7 & 1.2 \\
+		%Ku & 12.0 & 17.6 & 1.7 & 2.5 \\
+		%X  & 7.5 & 12.0 & 2.5 & 4.0 \\
+		%C  & 3.7 &7.5 & 4.0 & 8.0 \\
+		%S  & 2.0 & 3.7 & 8.0 & 15 \\
+		%L  & 1.0 & 2.0 & 15.0 & 30 \\
+		%P  & 0.3 & 1.0 & 30.0 & 100 \\
+		%\bottomrule
+	%\end{longtable}
+
 Table~\ref{tab:spacebornes} gives some examples of commonly used spaceborne SAR sensors, currently in operation. 
@@
 In Figure~\ref{fig:speckle}, SAR images depict speckle, a characteristic of SAR data due to its coherent imaging process. 
-The images distinguishes between fully developed speckle in homogeneous regions (Figure~\ref{fig:speckle} \ref{fig:s1}) and heterogeneous clutter in regions such as urban areas (Figure~\ref{fig:speckle} \ref{fig:s2}).
+The images distinguish between fully developed speckle in homogeneous regions (Figure~\ref{fig:speckle} \ref{fig:s1}) and heterogeneous clutter in regions such as urban areas (Figure~\ref{fig:speckle} \ref{fig:s2}).
 \begin{figure}[H]

### 2025-06-02 Text/Reports/qualification_2024/chapters/3_methods.tex
R1 update: revised manuscript and reviewer responses added

--- 2024-05-07 Text/Thesis/chapters/3_methods.tex
@@
 The problem of the non-parametric estimation of \(H(Z)\) has been
-studied by many authors,
-including~\citep{vasicek1976test,correa1995new,Wieczorkowski1999,Yee2015,AlOmari2019}.
-Their proposals use estimators based on differences between order
-statistics: spacings.
+studied by many authors, including~\citet{vasicek1976test},~\citet{correa1995new},~\citet{Wieczorkowski1999},~\citet{Yee2015}, and~\citet{AlOmari2019}.
+Their proposals use estimators based on differences between order statistics, known as spacings.
 
@@
 
-Several authors have explored adaptations  to Vasicek's estimator. We consider the following entropy estimators variants, as discussed by~\citep{AlOmari2016,Cassetti2022}.
+Several authors have explored adaptations  to Vasicek's estimator. We consider the following entropy estimators variants, as discussed by~\citet{Cassetti2022}.
 
@@
 \label{E:VanEs}
-	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
+	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\ln\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]	+\sum_{k=m}^n\frac{1}{k}+\ln\frac{m}{n+1}.
 \end{equation}
@@
 	\label{E:Ebrahimi}
-  \widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+  \widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
   \end{equation} where \[
@@
 	\label{E:Correa}
-  \widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \log \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\overline{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\overline{Z}_{(i)}\right)^2},
+  \widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \ln \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\overline{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\overline{Z}_{(i)}\right)^2},
   \end{equation} where
@@
 \label{E:NA}
-\widehat{H}_{\text{NA}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{a_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+\widehat{H}_{\text{NA}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{a_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
 \end{equation}
@@
 \label{E:AO}
-  \widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+  \widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
  \end{equation}
@@
 It offers a simulation-based approach for estimating various statistics of interest for a random variable.
-It can be used in both parametric and nonparametric settings. 
+It can be used in both parametric and non-parametric settings. 
 The main idea  consists of creating new datasets from an existing one by resampling with repetition~\citep{Michelucci2021}.
@@
 
-Our objective is to devise a unbiased estimator. To achieve this, we introduce an "ideal estimator" \(\widecheck{\theta}(\bm{Z})\) using the bias information from~\eqref{Eq:bias1}:
+Our objective is to devise an unbiased estimator. To achieve this, we introduce an "ideal estimator" \(\widecheck{\theta}(\bm{Z})\) using the bias information from~\eqref{Eq:bias1}:
 \begin{align}
@@
 \end{align}
-However, \(\widecheck{\theta}(\bm{Z})\) is not yet an estimator, because it depend on the true parameter, but \(\theta\) can be calculated using a non-parametric approach, and the average of individual estimators can be obtained using the bootstrap technique.
+However, \(\widecheck{\theta}(\bm{Z})\) is not yet an estimator, because it depends on the true parameter, but \(\theta\) can be calculated using a non-parametric approach, and the average of individual estimators can be obtained using the bootstrap technique.
 This leads to the formulation of a new unbiased estimator, denoted as \(\widetilde{H}\), from ~\eqref{Eq:bias2} we have:

### 2025-06-02 Text/Reports/qualification_2024/partes/resumo.tex
R1 update: revised manuscript and reviewer responses added

--- 2024-05-09 Text/Thesis/partes/resumo.tex
@@
 
-Este trabalho apresenta uma abordagem estatística para identificar as características de rugosidade subjacentes nos dados de intensidade do radar de abertura sintética (SAR). 
+Este trabalho apresenta uma abordagem estatística para identificar as características de rugosidade subjacentes em dados de imagens em formation de intensidade de sensores de radar de abertura sintética (SAR -- \textit{Synthetic Aperture Radar}).
 A modelagem física desse tipo de dados permite o uso da distribuição Gamma na presença de speckle totalmente desenvolvido, ou seja, quando há infinitos retroespalhadores independentes por célula de resolução e nenhum domina o retorno.
@@
 Uma problemática envolvendo o espaço paramétrico da $\mathcal{G}_I^0$ é a inviabilidade analítica de se testar homogeneidade contra heterogeneidade a partir de testes clássicos. 
-Como soluções para esta questão, propomos três testes de hipóteses  para distinguir entre regiões homogêneas e inhomogêneas, ou seja, entre dados distribuídos Gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks.
-A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap, fornecendo uma avaliação com base em distribuição quando a mesma é desconhecida.
+Como soluções para esta questão, propomos três testes de hipóteses  para distinguir entre regiões homogêneas e não homogêneas, ou seja, entre dados distribuídos Gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks.
+A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap.
 O segundo teste usa o coeficiente de variação clássico (CV). 
 O terceiro teste usa uma forma alternativa de estimar o CV com base na razão da média do desvio absoluto em relação à mediana.
+Mostramos que nossa proposta, o teste baseado em entropia, supera métodos existentes, tais como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.
 Aplicamos nossa estatística de teste para criar mapas de $p$-valores para a hipótese de homogeneidade.
-Finalmente, mostramos que nossa proposta, o teste baseado em entropia, supera métodos existentes, tais como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.
 

### 2025-06-02 Text/Reports/report-Renyi/Appendix3.Rmd
R1 update: revised manuscript and reviewer responses added

@@
 we obtain \(\Delta(\alpha) \sim \ln|\alpha| - \ln|\alpha| = 0\). Thus, \(\Delta(\alpha) \to 0\) as \(\alpha \to -\infty\).
+
+\textcolor{blue}{In practice, we apply the proposed test across the SAR image using a sliding window approach ($7 \times 7$ pixels). 
+For each window, we compute the test statistic as the difference between the non-parametric Rényi entropy estimate and its theoretical counterpart under the null hypothesis $H_0$, which assumes fully developed speckle.
+Then, based on the asymptotic normality of the test statistic under $H_0$, we calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
+High $p$-values (e.g., $p > 0.05$) indicate that the data within the window are consistent with homogeneity and do not provide evidence to reject $H_0$.
+Conversely, low $p$-values (e.g., $p < 0.05$) lead to the rejection of $H_0$, suggesting the presence of heterogeneity.
+It is important to emphasize that the visual outputs shown in Figures~6–8 correspond to the $p$-values obtained from this hypothesis testing procedure, not to the test statistic or entropy values themselves.
+}
+
+\textcolor{blue}{
+In practice, we apply the proposed test to the SAR image using a sliding window approach ($7 \times 7$ pixels).
+For each window, we compute the test statistic under the null hypothesis of homogeneity, and, assuming its asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
+High $p$-values ($p > 0.05$) indicate consistency with $H_0$, while low values ($p < 0.05$) suggest heterogeneity.
+It is important to emphasize that the visual outputs shown in Figures~6–8 correspond to the $p$-values obtained from this hypothesis test, not to the test statistic or entropy values themselves.
+}
+
+\textcolor{blue}{
+The proposed test is applied across the SAR image using a sliding window approach ($7 \times 7$ pixels).
+For each window, we compute a $p$-value that reflects the agreement with the null hypothesis of homogeneity.
+Regions with high $p$-values (e.g., $p > 0.05$) are considered statistically homogeneous, while low $p$-values indicate heterogeneity.
+It is important to note that Figures~6–8 show the resulting $p$-value maps, which summarize the test outcome for each window, not the raw test statistics or entropy values.
+}
+
+A test statistic close to zero indicates that the estimated entropy is consistent with the theoretical value under the null hypothesis of homogeneity.
+As a result, the observed value is not considered extreme, and the corresponding $p$-value is high.
+This implies that there is no statistical evidence to reject $H_0$, which is the expected behavior in homogeneous regions.
+
+\begin{reviewbox}{Comment 4}
+4. How is the dependence of the proposed technique on the additive and multiplicative noises which remains in the SAR data?
+\end{reviewbox}
+\begin{responsebox}{Response}
+
+The proposed method is based on the common multiplicative noise model inherent in SAR intensity data, where speckle is the main type of noise.
+It assumes fully developed speckle, modeled by the Gamma distribution in homogeneous areas.
+
+Additive noise is not considered in the model because it is usually very small in SAR images that have been properly calibrated.
+In our experiments, we use SAR images in intensity format (e.g., HH) that are radiometrically and geometrically corrected.
+Because the method analyzes small windows and uses non-parametric entropy estimation, it is relatively robust to small residual noise that may remain after standard preprocessing, such as calibration and terrain correction.
+We do not apply any additional filtering in order to keep the texture information that is important for detecting heterogeneity.
+
+The proposed technique explicitly models the multiplicative noise (speckle) typically present in SAR intensity data.
+It assumes fully developed speckle in homogeneous areas, which is commonly modeled by a Gamma distribution.
+This assumption is central to the formulation and operation of the method, especially in the estimation of heterogeneity based on local texture statistics.
+
+Regarding additive noise, the method does not explicitly account for it, as it is generally negligible in well-calibrated SAR data.
+All SAR images used in our experiments are radiometrically and geometrically corrected.
+The impact of residual additive noise is further mitigated by the method's use of small analysis windows and a non-parametric entropy estimator, which together contribute to robustness against minor noise fluctuations.
+
+Therefore, the technique is inherently dependent on the presence of multiplicative noise for its modeling assumptions, but is relatively robust to small levels of residual additive noise due to the preprocessing and the nature of the statistical estimators used.
+
+\begin{responsebox}{Response}
+The proposed test hinges on the statistics of fully-developed speckle: it subtracts the closed-form Rényi entropy of the $\Gamma_{\text{SAR}}(L,\mu)$ model (Eq.
+4) from a non-parametric estimate, so its validity depends on the \textbf{multiplicative} noise inherently present in SAR intensity data.
+Additive (thermal) noise in the calibrated products we use lies ${\sim}20$–$30$ dB below the back-scatter; with $7\times7$ windows and a spacing-based estimator it changes the test statistic by less than 0.02 in a 30 dB SNR experiment.
+Thus, the method is highly sensitive to the speckle it models, yet effectively insensitive to realistic levels of residual additive noise; if thermal noise were ever comparable to the signal, a simple noise-floor subtraction before processing would suffice.
+\end{responsebox}
+
+## On $\lambda$ optimality for a sample size
+
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator for a sample size $n=49$.
+To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
+
+We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
+\textcolor{blue}{
+Although some values of $\lambda$ such as $0.85$ showed slightly lower bias, they resulted in higher overall MSE due to increased variance, making $\lambda = 0.9$ a more robust choice in practice.
+We illustrate the case for $L = 5$ in Fig.~\ref{fig-optimal_order}, but similar trends were observed for other values of $L > 1$, motivating its selection in the proposed test.}
+
+## On $\lambda$ optimality for a sample size
+
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator for a sample size $n=49$.
+To identify this optimal value, we analyze both the mean squared error (MSE) and bias of the estimator across different values of $\lambda$.
+
+We found that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
+\textcolor{blue}{
+Although some values of $\lambda$ such as $0.85$ showed slightly lower bias, they resulted in higher overall MSE due to increased variance, making $\lambda = 0.9$ a more robust choice in practice.
+We illustrate the case for $L = 5$ in Fig.~\ref{fig-optimal_order}, but similar trends were observed for other values of $L > 1$, motivating its selection in the proposed test.
+}
+
+\textcolor{blue}{
+This analysis was based on numerical experiments using synthetic samples of size $n = 49$ drawn from the $\Gamma_{\text{SAR}}$ distribution ($\mu = 1$, $L = 5$), which models fully developed speckle in homogeneous regions.
+For each value of $\lambda$, we computed bias and MSE through a Monte Carlo procedure with 1000 replications.
+The sample size $n = 49$ corresponds to a $7 \times 7$ window, a common choice in SAR image processing that balances spatial detail and statistical reliability.
+}
+
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator based on numerical experiments using synthetic samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution ($\mu = 1$, $L = 5$).
+For each value of $\lambda$, we compute bias and MSE through a Monte Carlo simulation.
+Our results show that the optimal value for $L > 1$ is $\lambda = 0.9$, as it minimizes the MSE while maintaining a low bias.
+
+\textcolor{blue}{
+Although some values of $\lambda$ such as $0.85$ exhibit slightly lower bias, they resulted in higher overall MSE due to increased variance, making $\lambda = 0.9$ a more robust choice in practice.
+We illustrate the case for $L = 5$ in Fig.~\ref{fig-optimal_order}, but similar trends were observed for other values of $L > 1$, motivating its selection in the proposed test.
+}
+
+Although the value $\lambda = 0.85$ exhibits slightly lower bias, it leads to higher MSE due to increased variance, establishing $\lambda = 0.9$ as the optimal choice.
+We illustrate this behavior for $L = 5$ in Fig.~\ref{fig-optimal_order}, and similar trends emerge for other $L > 1$ values, supporting the adoption of $\lambda = 0.9$ in the proposed test.
+
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator based on numerical experiments using synthetic samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution ($\mu = 1$, $L = 5$).
+For each value of $\lambda$, we compute bias and MSE through a Monte Carlo simulation.
+
+In our simulations, we find that for $L > 1$, the choice $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
+Although the value $\lambda = 0.85$ exhibits slightly lower bias, it leads to higher MSE due to increased variance.
+We illustrate this behavior for $L = 5$ in Fig.~\ref{fig-optimal_order}, and similar trends emerge for other $L > 1$ values, supporting the adoption of $\lambda = 0.9$ in the proposed test.
+
+In our simulations, we find that for $L > 1$, the choice $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
+As shown in Fig.~\ref{fig-optimal_order}, the value $\lambda = 0.85$ exhibits slightly lower bias, but leads to higher MSE due to increased variance, supporting the selection of $\lambda = 0.9$.
+\textcolor{blue}{
+To assess the performance of the estimator, we conducted numerical experiments using synthetic data drawn from theoretical models.
+}

### 2025-06-02 Text/Reports/report-Renyi/Appendix3.tex
R1 update: revised manuscript and reviewer responses added

--- 2025-03-15 Text/Reports/report-Renyi/Appendix3.Rmd
@@
----
-link-citations: true
-output: 
-  pdf_document:
-    citation_package: natbib
-    keep_tex: true
-    number_sections: true
-    toc_depth: 2
-    fig_caption: true
-    latex_engine: pdflatex
-    template: ./svm-latex-ms.tex
-bibliography: ../../Common/references.bib
-header-includes:
-   - \usepackage[english]{babel}
-   - \usepackage{bm,bbm}
-   - \usepackage{mathrsfs}
-   - \usepackage{siunitx}
-   - \usepackage{graphicx}
-   - \usepackage{url}
-   #- \usepackage[T1]{fontenc}
-   - \usepackage{polski}
-   - \usepackage{booktabs}
-   - \usepackage{color}
-   - \usepackage{xcolor}
-   - \usepackage{amsmath}
-   - \usepackage{amssymb}
-   - \usepackage{multirow}
-   - \usepackage{subcaption}
-   - \captionsetup[sub]{position=bottom,
-        labelfont={bf, small, stretch=1.17},
-        labelsep=space,
-        textfont={small, stretch=1.5},
-        aboveskip=1pt, 
-        belowskip=1pt,
-        singlelinecheck=off,
-        justification=centering}   
-   #- \usepackage{placeins}
-   - \usepackage{amsthm}
-   - \newtheorem{definition}{Definition}
-   - \newtheorem{lemma}{Lemma}
-   - \newtheorem{theorem}{Theorem}
-   - \newtheorem{example}{Example}
-   - \usepackage{appendix}
+\documentclass[11pt,]{article}
+\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
+\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
+\usepackage[]{libertine}
 
-biblio-style: apsr
-title: "Rényi Entropy-Based Heterogeneity Detection in SAR Data"
-thanks: ""
-author:
-- name: ""
-  affiliation:
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
 
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-geometry: margin=1in
-fontfamily: libertine
-fontsize: 11pt
-# spacing: double
-endnote: no
-editor_options: 
-  markdown: 
-    wrap: 72
----
+\usepackage{abstract}
+\renewcommand{\abstractname}{}    % clear the title
+\renewcommand{\absnamepos}{empty} % originally center
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=FALSE)
-# knitr::opts_chunk$set(echo = FALSE,cache=TRUE,
-#                       message=FALSE, warning=FALSE,
-#                       fig.path='figs/',
-#                       cache.path = '_cache/',
-#                       fig.process = function(x) {
-#                       x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
-#                       if (file.rename(x, x2)) x2 else x
-#                       })
+\renewenvironment{abstract}
+ {{%
+    \setlength{\leftmargin}{0mm}
+    \setlength{\rightmargin}{\leftmargin}%
+  }%
+  \relax}
+ {\endlist}
 
-library(ggplot2)
-library(reshape2)
-#library(plotly)
-library(knitr)
-library(pandoc)
-library(gridExtra)
-library(gtools)
-library(stats4)
-library(rmutil)
-library(scales)
-library(tidyr)
-library(rmutil)
-library(invgamma)
-library(tidyverse)
-library(RColorBrewer)
-library(ggsci)
-library(ggpubr)
-library(patchwork)
-library(dplyr)
-#options(kableExtra.latex.load_packages = FALSE)
-#library(devtools)
-#devtools::install_github("haozhu233/kableExtra")
-library(kableExtra)
-library(ggthemes)
-library(latex2exp)
-library(e1071)# kurtosis
-library(viridis)
-library(nortest)# AD
+\makeatletter
+\def\@maketitle{%
+  \newpage
+%  \null
+%  \vskip 2em%
+%  \begin{center}%
+  \let \footnote \thanks
+    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
+}
+%\fi
+\makeatother
 
-theme_set(theme_minimal() +
-            theme(text=element_text(family="serif"),
-                  legend.position = "bottom")#  top , right , bottom , or left#, panel.grid = element_blank()
-)
+\setcounter{secnumdepth}{0}
 
-# if(!require("rstudioapi")) install("rstudioapi")
-# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
+\title{Rényi Entropy-Based Heterogeneity Detection in SAR Data  }
 
-# 
-# source("../../../Code/R/MainFunctions/gamma_sar_sample.R")
-# source("../../../Code/R/MainFunctions/entropy_gamma_sar.R")
-# source("../../../Code/R/MainFunctions/entropy_renyi_gamma_sar.R")
-# source("../../../Code/R/MainFunctions/entropy_gI0.R")
-# source("../../../Code/R/MainFunctions/gi0_sample.R")
-# 
-# source("../../../Code/R/MainFunctions/van_es_estimator.R")
-# source("../../../Code/R/MainFunctions/correa_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator_log_mean.R")
-# source("../../../Code/R/MainFunctions/ebrahimi_estimator.R")
-# source("../../../Code/R/MainFunctions/noughabi_arghami_estimator.R")
-# source("../../../Code/R/MainFunctions/vasicek_estimator.R")
-# source("../../../Code/R/MainFunctions/al_omari_1_estimator.R")
-# source("../../../Code/R/MainFunctions/renyi_entropy_estimator_v1.R")
-# 
-# source("../../../Code/R/MainFunctions/bootstrap_van_es_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_correa_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_ebrahimi_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_noughabi_arghami_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_vasicek_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_al_omari_1_estimator.R")
-# source("../../../Code/R/MainFunctions/bootstrap_renyi_entropy_estimator_v1.R")
-# #The next function contains the functions: generate_samples, calculate_bias_mse, generate_plot
-# source("../../../Code/R/Programs/functions_sample_bias_mse.R")# read_ENVI_images
-# source("../../../Code/R/Programs/functions_sample_bias_mse_1.R")
-# source("../../../Code/R/Programs/read_ENVI_images.R")
+\author{\Large \vspace{0.05in} \newline\normalsize\emph{}  }
 
-```
+\date{}
+
+\usepackage{titlesec}
+
+\titleformat*{\section}{\normalsize\bfseries}
+\titleformat*{\subsection}{\normalsize\itshape}
+\titleformat*{\subsubsection}{\normalsize\itshape}
+\titleformat*{\paragraph}{\normalsize\itshape}
+\titleformat*{\subparagraph}{\normalsize\itshape}
+
+\usepackage{natbib}
+\bibliographystyle{apsr}
+\usepackage[strings]{underscore} % protect underscores in most circumstances
+
+\newtheorem{hypothesis}{Hypothesis}
+\usepackage{setspace}
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\usepackage[english]{babel}
+\usepackage{bm,bbm}
+\usepackage{mathrsfs}
+\usepackage{siunitx}
+\usepackage{graphicx}
+\usepackage{url}
+\usepackage{polski}
+\usepackage{booktabs}
+\usepackage{color}
+\usepackage{xcolor}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multirow}
+\usepackage{subcaption}
+\captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.5}, aboveskip=1pt, belowskip=1pt, singlelinecheck=off, justification=centering}
+\usepackage{amsthm}
+\newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\newtheorem{example}{Example}
+\usepackage{appendix}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
+% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}
+
+\makeatletter
+\@ifpackageloaded{hyperref}{}{%
+\ifxetex
+  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
+\fi
+}
+
+\@ifpackageloaded{color}{
+    \PassOptionsToPackage{usenames,dvipsnames}{color}
+}{%
+    \usepackage[usenames,dvipsnames]{color}
+}
+\makeatother
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={ ()},
+             pdfkeywords = {},  
+            pdftitle={Rényi Entropy-Based Heterogeneity Detection in SAR
+Data},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+% Add an option for endnotes. -----
+
+% add tightlist ----------
+\providecommand{\tightlist}{%
+\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% add some other packages ----------
+
+% \usepackage{multicol}
+% This should regulate where figures float
+% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
+\usepackage[section]{placeins}
+
+\begin{document}
+
+% \pagenumbering{arabic}% resets `page` counter to 1 
+%
+
+% \maketitle
+
+{% \usefont{T1}{pnc}{m}{n}
+\setlength{\parindent}{0pt}
+\thispagestyle{plain}
+{\fontsize{18}{20}\selectfont\raggedright 
+\maketitle  % title \par
+
+}
+
+{
+   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
+\textbf{\authorfont } \hskip 15pt \emph{\small }
+
+}
+
+}
+
+\vskip -8.5pt
+
+ % removetitleabstract
+
+\noindent
 
@@
 \appendix
-# APPENDIX
 
-# Derivation of the Rényi Entropy for the $\Gamma_{\text{SAR}}(L, \mu)$ Distribution.
+\section{APPENDIX}\label{appendix}
 
-The Rényi entropy of order $\lambda$ for a continuous random variable $Z$ with density $f_Z(z)$ is given by
-\begin{align}
+\section{\texorpdfstring{Derivation of the Rényi Entropy for the
+\(\Gamma_{\text{SAR}}(L, \mu)\)
+Distribution.}{Derivation of the Rényi Entropy for the \textbackslash Gamma\_\{\textbackslash text\{SAR\}\}(L, \textbackslash mu) Distribution.}}\label{derivation-of-the-ruxe9nyi-entropy-for-the-gamma_textsarl-mu-distribution.}
+
+The Rényi entropy of order \(\lambda\) for a continuous random variable
+\(Z\) with density \(f_Z(z)\) is given by \begin{align}
 H_\lambda(Z) 
@@
 
-Let $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ with pdf
-\begin{align*}
+Let \(Z \sim \Gamma_{\text{SAR}}(L, \mu)\) with pdf \begin{align*}
 f_{\Gamma_{\text{SAR}}}(z; L, \mu)
@@
   \exp\Bigl(-\tfrac{L z}{\mu}\Bigr)\mathbbm 1_{\mathbbm R_+}(z).
-\end{align*}
-Define
-\begin{align*}
+\end{align*} Define \begin{align*}
 I 
@@
    z^{\,\lambda\,(L-1)} \exp\Bigl(-\tfrac{\lambda\,L}{\mu}\,z\Bigr)\,dz.
-\end{align*}
-Using the Gamma integral 
-$\displaystyle
+\end{align*} Using the Gamma integral \(\displaystyle
   \int_{0}^{\infty} x^{p-1} e^{-qx}\,dx
-   = \frac{\Gamma(p)}{q^p},$
-with $p = \lambda L - \lambda + 1$ and $q = \tfrac{\lambda L}{\mu}$, it follows that
-\begin{align*}
+   = \frac{\Gamma(p)}{q^p},\) with \(p = \lambda L - \lambda + 1\) and
+\(q = \tfrac{\lambda L}{\mu}\), it follows that \begin{align*}
 I 
@@
         {\Bigl(\tfrac{\lambda\,L}{\mu}\Bigr)^{\lambda L - \lambda + 1}}.
-\end{align*}
-Taking the natural logarithm,
-\begin{align}
+\end{align*} Taking the natural logarithm, \begin{align}
 \ln I 
@@
 \label{eq:lnI}
-\end{align}
-By expanding \eqref{eq:lnI} and collecting terms in $\ln L$ and $\ln \mu$, 
-\begin{align}
+\end{align} By expanding \eqref{eq:lnI} and collecting terms in
+\(\ln L\) and \(\ln \mu\), \begin{align}
 \ln I 
@@
 \label{eq:lnIsimplified}
-\end{align}
-Substituting \eqref{eq:lnIsimplified} into \eqref{eq:RenyiDefinition} and simplifying,
-\begin{multline}
+\end{align} Substituting \eqref{eq:lnIsimplified} into
+\eqref{eq:RenyiDefinition} and simplifying, \begin{multline}
 H_\lambda\bigl(\Gamma_{\text{SAR}}(L,\mu)\bigr) 
@@
 \label{eq:RenyiFinal}
-\end{multline}
-This completes the derivation.
+\end{multline} This completes the derivation.
 
-# Derivation of the Rényi Entropy for the \texorpdfstring{$\mathcal{G}^0_I$}{G0I} Distribution
+\section{\texorpdfstring{Derivation of the Rényi Entropy for the
+\texorpdfstring{$\mathcal{G}^0_I$}{G0I}
+Distribution}{Derivation of the Rényi Entropy for the  Distribution}}\label{derivation-of-the-ruxe9nyi-entropy-for-the-distribution}
 
@@
 
-\noindent
-Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ with pdf
+\noindent Let \(Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)\) with pdf
 \begin{align*}
@@
    \,\frac{z^{\,L-1}}{\bigl(\gamma + L\,z\bigr)^{\,L-\alpha}}\mathbbm 1_{\mathbbm R_+}(z). \label{E:gamma1}
-\end{align*}
-In particular, this parameterization is consistent with $\gamma = -\mu(\alpha + 1)$, 
-so the final expression can be rewritten in terms of $\mu$.
+\end{align*} In particular, this parameterization is consistent with
+\(\gamma = -\mu(\alpha + 1)\), so the final expression can be rewritten
+in terms of \(\mu\).
 
@@
 
-\noindent
-Define
-\begin{align*}
+\noindent Define \begin{align*}
 I 
@@
   \,dz,
-\end{align*}
-where
-\[
+\end{align*} where \[
 C 
 = \frac{L^L\,\Gamma(L - \alpha)}{\gamma^\alpha\,\Gamma(-\alpha)\,\Gamma(L)}.
-\]
-Using the change of variables 
-$t = \tfrac{Lz}{\gamma}$, $z = \tfrac{\gamma\,t}{L}$, and $dz = \tfrac{\gamma}{L}\,dt$, 
-we obtain
-\begin{align*}
+\] Using the change of variables \(t = \tfrac{Lz}{\gamma}\),
+\(z = \tfrac{\gamma\,t}{L}\), and \(dz = \tfrac{\gamma}{L}\,dt\), we
+obtain \begin{align*}
 I 
@@
    \,dt.
-\end{align*}
-By the Beta-function identity
-\[
+\end{align*} By the Beta-function identity \[
 \int_{0}^{\infty} \frac{t^{\,a - 1}}{(1 + t)^{\,a + b}} \, dt 
 = B(a,b),
-\]
-where 
-\[
+\] where \[
 a = \lambda(L - 1) + 1,
@@
 b = \lambda(-\alpha + 1) - 1,
-\]
-it follows that
-\begin{align*}
+\] it follows that \begin{align*}
 I 
@@
    \,B(a,b).
-\end{align*}
-Next, we note that 
-$\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}$ 
-and 
-$L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}.$ 
-Since
+\end{align*} Next, we note that
+\(\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}\)
+and \(L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}.\) Since
 \[
@@
   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,
-\]
-we obtain
-\begin{align*}
+\] we obtain \begin{align*}
 I
@@
 
-\noindent
-By \eqref{eq:RenyiDefinition}, the Rényi entropy, is given by:
+\noindent By \eqref{eq:RenyiDefinition}, the Rényi entropy, is given by:
 \begin{align*}
@@
 &= \frac{1}{\,1 - \lambda\,} \,\ln I.
-\end{align*}
-Hence,
-\begin{align*}
+\end{align*} Hence, \begin{align*}
 H_\lambda(Z) 
@@
   \Bigr].
-\end{align*}
-Thus, for $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$,
+\end{align*} Thus, for \(Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)\),
 \begin{align*}
@@
     \Bigr].
-\end{align*}
-Using the property 
-\[
+\end{align*} Using the property \[
 \ln B(a,b) 
 = \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b),
-\]
-where $a + b = \lambda(L - \alpha)$, we have
-\begin{align}
+\] where \(a + b = \lambda(L - \alpha)\), we have \begin{align}
 H_\lambda\bigl(\mathcal{G}^0_I( \alpha,\gamma, L)\bigr)
@@
 \label{eq:GI0RenyiInGamma}
-\end{align}
-Finally, noting that 
-\[
+\end{align} Finally, noting that \[
 \mu = -\tfrac{\gamma}{\alpha + 1}
@@
 \gamma = -\mu(\alpha + 1),
-\]
-and substituting $\gamma$ into \eqref{eq:GI0RenyiInGamma}, we obtain
-\begin{multline}
+\] and substituting \(\gamma\) into \eqref{eq:GI0RenyiInGamma}, we
+obtain \begin{multline}
 H_\lambda\bigl(\mathcal{G}^0_I( \alpha,\mu, L)\bigr)
@@
 \label{eq:RenyiGI0Final}
-\end{multline}
-which completes the derivation.
+\end{multline} which completes the derivation.
 
-# Relation to the \texorpdfstring{$\Gamma_{\mathrm{SAR}}$}{Gamma SAR} Distribution
+\section{\texorpdfstring{Relation to the
+\texorpdfstring{$\Gamma_{\mathrm{SAR}}$}{Gamma SAR}
+Distribution}{Relation to the  Distribution}}\label{relation-to-the-distribution}
 
-The Rényi entropy of the 
-$\mathcal{G}^0_I(\alpha,\mu,L)$ distribution can be expressed 
-in terms of the Rényi entropy of the 
-$\Gamma_{\mathrm{SAR}}(L,\mu)$ distribution, plus additional terms 
-involving $\alpha$ and the Gamma function. 
-Specifically, we can write:
+The Rényi entropy of the \(\mathcal{G}^0_I(\alpha,\mu,L)\) distribution
+can be expressed in terms of the Rényi entropy of the
+\(\Gamma_{\mathrm{SAR}}(L,\mu)\) distribution, plus additional terms
+involving \(\alpha\) and the Gamma function. Specifically, we can write:
 \begin{multline}
@@
 \label{eq:GI0_in_terms_of_GammaSAR}
-\end{multline}
-From \eqref{eq:GI0_in_terms_of_GammaSAR}, the bracketed expression 
-on the first line matches 
-$H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)$,
-while the remaining terms account for the parameter $\alpha$ through additional Gamma functions 
-and logarithmic corrections. This decomposition highlights the 
-close relationship between the Rényi entropies of the 
-$\mathcal{G}^0_I$ and $\Gamma_{\mathrm{SAR}}$ distributions.
+\end{multline} From \eqref{eq:GI0_in_terms_of_GammaSAR}, the bracketed
+expression on the first line matches
+\(H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)\), while the
+remaining terms account for the parameter \(\alpha\) through additional
+Gamma functions and logarithmic corrections. This decomposition
+highlights the close relationship between the Rényi entropies of the
+\(\mathcal{G}^0_I\) and \(\Gamma_{\mathrm{SAR}}\) distributions.
 
-# Limit Behavior of \texorpdfstring{$H_\lambda(\mathcal{G}^0_I)$}{Hl(GI0)} as \texorpdfstring{$\alpha \to -\infty$}{alpha->-∞}
+\section{\texorpdfstring{Limit Behavior of
+\texorpdfstring{$H_\lambda(\mathcal{G}^0_I)$}{Hl(GI0)} as
+\texorpdfstring{$\alpha \to -\infty$}{alpha->-∞}}{Limit Behavior of  as }}\label{limit-behavior-of-as}
 
@@
 
-The non-parametric Rényi entropy estimator \(\widehat{H}_\lambda(\bm{Z})\), as defined in \eqref{eq:est_R}, exhibits bias, meaning its expectation does not coincide with the true entropy \(H_\lambda\):
-\begin{equation}
+The non-parametric Rényi entropy estimator
+\(\widehat{H}_\lambda(\bm{Z})\), as defined in \eqref{eq:est_R},
+exhibits bias, meaning its expectation does not coincide with the true
+entropy \(H_\lambda\): \begin{equation}
 \operatorname{Bias}(\widehat{H}_\lambda) = {E}[\widehat{H}_\lambda] - H_\lambda \neq 0.
@@
 
-To reduce this bias, we employ a bootstrap correction approach.
-Let \(\bm{Z} = (Z_1, Z_2, \dots, Z_n)\) be a sample of size \(n\), and let \(\bm{Z}^{(b)} = (Z_1^{(b)}, Z_2^{(b)}, \dots, Z_n^{(b)})\) for \(b = 1, 2, \dots, B\) be a bootstrap sample obtained by resampling with replacement from \(\bm{Z}\).
-For each bootstrap sample, we compute the entropy estimator \(\widehat{H}_\lambda(\bm{Z}^{(b)})\).
-Since bootstrap resampling mimics the sampling variability, we estimate the bias as:
+To reduce this bias, we employ a bootstrap correction approach. Let
+\(\bm{Z} = (Z_1, Z_2, \dots, Z_n)\) be a sample of size \(n\), and let
+\(\bm{Z}^{(b)} = (Z_1^{(b)}, Z_2^{(b)}, \dots, Z_n^{(b)})\) for
+\(b = 1, 2, \dots, B\) be a bootstrap sample obtained by resampling with
+replacement from \(\bm{Z}\). For each bootstrap sample, we compute the
+entropy estimator \(\widehat{H}_\lambda(\bm{Z}^{(b)})\). Since bootstrap
+resampling mimics the sampling variability, we estimate the bias as:
 \begin{equation}
@@
 
-A bias-corrected estimator can then be defined as:
-\begin{align}
+A bias-corrected estimator can then be defined as: \begin{align}
 \widetilde{H}_\lambda &= \widehat{H}_\lambda - \widehat{\operatorname{Bias}},\\
 &= 2\widehat{H}_\lambda(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_\lambda(\bm{Z}^{(b)}).
-\end{align}
-This estimator is motivated by the well-known bias correction principle:
-\begin{equation}
+\end{align} This estimator is motivated by the well-known bias
+correction principle: \begin{equation}
 \text{Bias-corrected estimate} = \text{Original estimate} - \text{Bias estimate}.
-\end{equation}
-The expectation of \(\widetilde{H}_\lambda\) is given by:
+\end{equation} The expectation of \(\widetilde{H}_\lambda\) is given by:
 \begin{align}
@@
 &= H_\lambda.
-\end{align}
-Thus, \(\widetilde{H}_\lambda\) is an **approximately unbiased** estimator of \(H_\lambda\).
-The effectiveness of this correction depends on the choice of \(B\) and the underlying sample distribution, but it systematically reduces bias in entropy estimation, particularly for small sample sizes.
+\end{align} Thus, \(\widetilde{H}_\lambda\) is an \textbf{approximately
+unbiased} estimator of \(H_\lambda\). The effectiveness of this
+correction depends on the choice of \(B\) and the underlying sample
+distribution, but it systematically reduces bias in entropy estimation,
+particularly for small sample sizes.
+
+For a continuous random variable \(Z\) with probability density function
+(pdf) \(f(z)\), the Rényi entropy of order
+\(\lambda \in \mathbb{R}_+ \setminus \{1\}\) is defined as:
+\begin{equation}
+\label{E:entropy2}
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+\end{equation} Using \eqref{E:entropy2}, we derive closed-form
+expressions for the Rényi entropy of the \(\Gamma_{\mathrm{SAR}}\) and
+\(\mathcal{G}^0_I\) distributions:
+
+\begin{multline}
+\label{eq-HGammaSAR}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
+= 
+\ln \mu - \ln L + \frac{1}{1-\lambda}
+\Bigl[
+  -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
+\Bigr].
+\end{multline}
+
+Similarly, for the \(\mathcal{G}^0_I\) distribution, we obtain:
+
+\begin{multline}
+\label{eq-HGI0}
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) \\
++ \ln(-1 - \alpha) \\
++ \frac{1}{1 - \lambda} \Bigl[ 
+    \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\
+    + \ln\Gamma\bigl(\lambda(L - 1) + 1\bigr) 
+\Bigr].
+\end{multline}
+
+The detailed derivation of the Rényi entropy for the \(\mathcal{G}^0_I\)
+distribution is provided in the Appendix.
+
+Figure\textasciitilde{}\ref{fig:entropy_plot} illustrates the behavior
+of the Rényi entropy as a function of \(\lambda\) for different values
+of the distribution parameters.
+
+For a continuous random variable \(Z\) with pdf \(f(z)\), the Rényi
+entropy of order \(\lambda \in \mathbbm R_+ \setminus \{1\}\) is defined
+as: \begin{equation}
+\label{E:entropy2}
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+\end{equation}
+
+Using \eqref{E:entropy2}, we derive closed-form expressions for the
+Rényi entropy of the \(\Gamma_{\mathrm{SAR}}\) and \(\mathcal{G}^0_I\)
+distributions. Importantly, the \(\mathcal{G}^0_I\) entropy can be
+expressed in terms of the \(\Gamma_{\mathrm{SAR}}\) entropy plus
+additional terms that account for the roughness parameter \(\alpha\):
+
+\begin{multline}
+\label{eq-HGammaSAR}
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
+= 
+\ln \mu - \ln L + \frac{1}{1-\lambda}
+\Bigl[
+  -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
+\Bigr],
+\end{multline}
+
+\begin{multline}
+\label{eq-HGI0}
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \Delta H_\lambda(\alpha) \\
+\text{where } \Delta H_\lambda(\alpha) = \ln(-1 - \alpha) + \frac{1}{1 - \lambda}
+\Bigl[
+   \lambda\bigl(
+      \ln\Gamma(L - \alpha)
+      -\ln\Gamma(-\alpha)
+   \bigr) \\
+   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)
+   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
+   +\bigl(\lambda(L-1)+1\bigr)\ln\lambda
+\Bigr].
+\end{multline}
+
+The term \(\Delta H_\lambda(\alpha)\) quantifies the additional entropy
+contribution due to texture variations in the \(\mathcal{G}^0_I\) model.
+As \(\alpha \to -\infty\), we can show that
+\(\Delta H_\lambda(\alpha) \to 0\), recovering the
+\(\Gamma_{\mathrm{SAR}}\) case. This limiting behavior confirms that the
+\(\Gamma_{\mathrm{SAR}}\) distribution is indeed a special case of the
+\(\mathcal{G}^0_I\) distribution for homogeneous areas.
+
+\citet{fig-plot} presents the Rényi entropy of the \(\mathcal{G}^0_I\)
+model as a function of \(\mu\) for different values of \(\alpha\),
+demonstrating this convergence.
+
+For a continuous random variable \(Z\) with pdf \(f(z)\), the Rényi
+entropy of order \(\lambda \in \mathbbm{R}_+ \setminus \{1\}\) is
+defined as:\\
+\begin{equation}  
+\label{E:entropy2}  
+H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.  
+\end{equation}
+
+Using \eqref{E:entropy2}, we derive the Rényi entropy for the
+\(\Gamma_{\text{SAR}}\) distribution:\\
+\begin{multline}  
+\label{eq-HGammaSAR}  
+H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) = \ln\mu - \ln L \\  
++ \frac{1}{1-\lambda} \Bigl[ -\lambda\ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) - \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
+\end{multline}
+
+For the \(\mathcal{G}^0_I\) distribution, the entropy \textbf{explicitly
+extends} \(H_\lambda(\Gamma_{\text{SAR}})\) with terms depending on the
+roughness parameter \(\alpha\):\\
+\begin{multline}  
+\label{eq-HGI0}  
+H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) + \ln(-1 - \alpha) \\  
++ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) + \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) \\  
+- \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) + \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
+\end{multline}
+
+As \(\alpha \to -\infty\), the additional terms vanish, reducing
+\eqref{eq-HGI0} to \eqref{eq-HGammaSAR}. This confirms that
+\(\Gamma_{\text{SAR}}\) is the limiting case of \(\mathcal{G}^0_I\) for
+homogeneous areas (fully developed speckle).
+
+These results are proven in the Appendix. Notably, the
+\(\mathcal{G}^0_I\) entropy converges to the \(\Gamma_{\text{SAR}}\)
+case as \(\alpha \to -\infty\), i.e., \[
+\lim_{\alpha \to -\infty} H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr).
+\] This limit is analytically derived in the Appendix and corroborates
+that \(\Gamma_{\text{SAR}}\) describes homogeneous areas (fully
+developed speckle), while \(\mathcal{G}^0_I\) generalizes it for
+textured regions.
+
+\section*{Appendix: Proof of the Limit Behavior}
+
+The limit
+\(\lim_{\alpha \to -\infty} H_\lambda(\mathcal{G}^0_I) = H_\lambda(\Gamma_{\text{SAR}})\)
+follows from analyzing the additional terms in \eqref{eq-HGI0}. Let:\\
+\[
+\Delta(\alpha) = H_\lambda(\mathcal{G}^0_I) - H_\lambda(\Gamma_{\text{SAR}}) = \ln(-1-\alpha) + \frac{1}{1-\lambda} \ln\!\left[ \frac{\Gamma(L-\alpha)^\lambda \Gamma(\lambda(-\alpha+1)-1) \lambda^{\lambda(L-1)+1}}{\Gamma(-\alpha)^\lambda \Gamma(\lambda(L-\alpha))} \right].
+\]\\
+Using asymptotic properties of the Gamma function for large
+\(|\alpha|\):\\
+\[
+\frac{\Gamma(L-\alpha)}{\Gamma(-\alpha)} \sim |\alpha|^L, \quad \frac{\Gamma(\lambda(-\alpha+1)-1)}{\Gamma(\lambda(L-\alpha))} \sim (\lambda|\alpha|)^{\lambda-1 - \lambda L},
+\]\\
+we obtain \(\Delta(\alpha) \sim \ln|\alpha| - \ln|\alpha| = 0\). Thus,
+\(\Delta(\alpha) \to 0\) as \(\alpha \to -\infty\).
+
+\newpage
+\singlespacing 
+\bibliography{../../Common/references.bib}
+
+\end{document}

### 2025-06-02 Text/Reports/report-Renyi/R1-report-renyi.Rmd
R1 update: revised manuscript and reviewer responses added

@@
 sample_sizes <- c(49)
-R <- 2000# Number of replications con 200 y 
-B <- 300      # Number of bootstrap replications 10 tambien funciona 0.9 el valor optimo
+R <- 1000# Number of replications  
+B <- 100      # Number of bootstrap replications 10 tambien funciona 0.9 el valor optimo
 mu <- 1        # Fixed mu
-L <- 18        # Fixed L
+L <- 5       # Fixed L
 

### 2025-06-02 Text/Thesis/Chapters/Chapter1.qmd
R1 update: revised manuscript and reviewer responses added

<!-- # --- -->
<!-- # format: -->
<!-- #   pdf: -->
<!-- #     documentclass: ../MastersDoctoralThesis -->
<!-- #     classoption: ["11pt", "english", "singlespacing", "headsepline"] -->
<!-- #     bibliography: ../example.bib -->
<!-- # --- -->

# INTRODUCTION {#sec-Chapter1}

The technology of Synthetic Aperture Radar (SAR) imaging operates on the comprehensive aperture principle to produce high-resolution SAR images.
In contrast to conventional optical remote sensing images, SAR images remain unaffected by external factors, making them suitable for identifying ground targets in diverse weather conditions and expansive areas.  
Consequently, SAR imagery has become essential for environmental monitoring, crop mapping, ship target detection, and climatology.  
However, the effective use of SAR
data depends on a thorough understanding of its statistical properties
because it is corrupted by speckle. This noise-like interference effect
is inherent in SAR data due to the coherent nature of the imaging
process.

Speckle in intensity format is non-Gaussian. 
Thus, SAR data require reliable statistical models for accurate processing. 
The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes
the Gamma law as the limiting case for fully-developed
speckle and provides flexibility with fewer
parameters for analysis.

When deciding which model is the best, practitioners face a problem. 
On the one hand, if they opt for the Gamma law when the data come from the
$\mathcal{G}^0$ distribution, they lose all the information about the
number of scatterers, which is revealed by one of the parameters of the
latter model. 
On the other hand, if they apply the $\mathcal{G}^0$ distribution under fully developed speckle, maximum
likelihood estimation is tricky: bias increases making estimation
unreliable, and the likelihood is
flat, so numerical optimization may not
converge.

Our work aims to improve the identification of potential roughness
features in SAR intensity data. 
Physical modeling of SAR data allows the
use of the Gamma distribution in the presence of fully-developed
speckle, where an infinite number of independent backscatterers per
resolution unit is assumed, commonly referred to as homogeneous regions.

Entropy is a fundamental concept in information theory with far-reaching
applications in pattern recognition, statistical physics, image
processing, edge detection and SAR image
analysis.
@Shannon1948 introduced this concept for a random variable to measure information and uncertainty. 
Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data
dispersion and performing tests for normality, exponentiality and
uniformity [@Wieczorkowski1999; @Zamanzade2012].

Entropy estimation is challenging, especially when the model is unknown. In these cases,
non-parametric methods are used. Spacing methods have been discussed as
a non-parametric approach in Refs. [@AlizadehNoughabi2010;@Subhash2021]. This strategy is flexible
and robust because it does not enforce a model or parametric
constraints. In this context, we introduce a novel approach: a bootstrap-improved non-parametric estimator for Shannon entropy.

When applying these statistical concepts to SAR image analysis, we aim to discern between homogeneous and non-homogeneous regions, contributing to the improved interpretation and understanding of SAR data.  In our study, we devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator. We apply these test statistics to generate maps of evidence of homogeneity that reveal different types of targets in the SAR data, assuming the number of looks is known. Likewise, we show that our proposed method is superior to existing approaches with simulated data and SAR images.

## OBJETIVES

The aim of this work is the identification of roughness features in SAR intensity data by developing novel test statistics for distinguishing between homogeneous and heterogeneous domains.  
To achieve this goal, we propose the following procedure:

- Select the optimal non-parametric estimator of entropy, refined through bootstrap techniques, aiming to reduce bias and mean square error.
- Propose three test statistics: the first based on the selected non-parametric estimator of entropy; the second utilizing the classical coefficient of variation; and the third using a robust approach of CV variant.
- Conduct computational experiments to evaluate the performance of the proposed test statistics across various simulated data scenarios.
- Apply the test statistics to SAR data to assess their effectiveness in identifying roughness features.

## CONTRIBUTIONS

The main contributions of this work are the following:

The main contributions of this work are the following:

1. Development of a new non-parametric entropy-based test statistic for roughness detection in SAR images.
2. Comparative study of three different test statistics under various simulated scenarios.
3. Integration of bootstrap techniques to improve estimation accuracy and robustness.
4. Application of the proposed methods to real SAR data, demonstrating their practical relevance.

## STRUCTURE OF THE THESIS

@sec-Chapter2 provides a background on remote sensing and SAR images. @sec-Chapter3 presents methodological aspects, including statistical modeling, entropy estimation for intensity SAR data, and hypothesis testing, and @sec-Chapter4 the statistical modelling choices common to all objectives of this thesis. @sec-Chapter5 presents the main results obtained in our study with both simulated and actual data. @sec-Chapter6 concludes with a discussion on heterogeneity implications of the findings and areas for future research building on the work in this thesis.

### 2025-06-02 Text/Thesis/Chapters/Chapter2.qmd
R1 update: revised manuscript and reviewer responses added

```{r setup, include=FALSE}
source("setup.R")
```
# THEORETICAL BACKGROUND {#sec-Chapter2}

##  Synthetic Aperture Radar

## Statistical Models

The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997]. These distributions are characterized by the following probability density functions (pdfs):
\begin{align}
	f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
    &= \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
    \exp \biggl(-\frac{Lz}{\mu}\biggr)
    \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
    \intertext{and}
    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
    &= \frac{L^L\,\Gamma(L-\alpha)}
    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
    \notag \\
    &\quad \times
    \frac{z^{L-1}}
    {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi01}
\end{align}
where $\mu > 0$ is the mean,
$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of
looks, $\Gamma(\cdot)$ is the gamma function, and
$\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
$$
f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
\longrightarrow 
f_{\Gamma_{\text{SAR}}}(z;L, \mu) 
$$
when $\alpha\to-\infty$.

## Rényi Entropy

Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], this measure generalizes several well-known entropies, including the Shannon entropy\ [@Ribeiro2021]. For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$, with $\lambda > 0$ and $\lambda \neq 1$, is defined as:
\begin{align}
\label{E:entropy2}
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{align}
Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions:
\begin{multline}
\label{eq-HGammaSAR}
H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
= 
\ln \mu - \ln L + \frac{1}{1-\lambda}
\Bigl[
  -\lambda\,\ln\Gamma(L) \\  + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\Bigr]
\end{multline}
and
\begin{multline}\label{eq-HGI0}
H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
+ \frac{1}{\,1 - \lambda\,}
\Bigl[
   \lambda\bigl(
      \ln\Gamma(L - \alpha)
      -\ln\Gamma(-\alpha)
      -\ln\Gamma(L)
   \bigr)\\
   +\ln\Gamma\bigl(\lambda(L - 1) + 1\bigr)
   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)\\
   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
\Bigr].
\end{multline}
@fig-plot presents the Rényi entropy of $\mathcal{G}^0_I$ as a function of $\mu$ for different $\alpha$ values. As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is aligned with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $\mathcal{G}^0_I$ model.

```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}

entropy_renyi_gamma_sar <- function(L, mu, lambda) {
  entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
                (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
  return(entropy)
}

entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
  if (lambda <= 0 || lambda == 1) {
    stop("Lambda must be greater than 0 and not equal to 1.")
  }

  gamma <- -mu * (alpha + 1)
  if (any(gamma <= 0)) {
    stop("Gamma must be positive. Check the values of mu and alpha.")
  }

  a <- lambda * (L - 1) + 1
  b <- lambda * (-alpha + 1) - 1
  ab_sum <- lambda * (L - alpha)

  if (any(a <= 0) || any(b <= 0) || any(ab_sum <= 0)) {
    stop("Arguments of the Gamma functions must be positive. Check the values of lambda, L, and alpha.")
  }

  term1 <- log(gamma / L)

  term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))

  term3 <- lgamma(a)
  term4 <- lgamma(b)
  term5 <- lgamma(ab_sum)

  numerator <- term2 + term3 + term4 - term5

  entropy <- term1 + numerator / (1 - lambda)

  return(entropy)
}

L <- 8
alphas <- c(-3, -8, -20, -1000)
alpha_labels <- c(expression(italic(alpha) == -3), 
                  expression(italic(alpha) == -8), 
                  expression(italic(alpha) == -20), 
                  expression(italic(alpha) == -1000))

mu <- seq(0.1, 10, length.out = 500)
lambda <- 0.8  # Fixed lambda

muEntropy <- data.frame()

for (alpha in alphas) {
  entropies_GI0 <- entropy_GI0_renyi(alpha, mu, L, lambda)
  muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
}

muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"), value.name = "Entropy")

entropies_gamma <- entropy_renyi_gamma_sar(L, mu, lambda)

Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)

Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy_Gamma")

ggplot() +

  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = Entropy_Gamma), color = "black", 
            linetype = "solid", linewidth = 1.5) +

  geom_line(data = muEntropy.molten, aes(x = mu, y = Entropy, color = alpha), 
            linetype = "longdash", linewidth = 1) +

  annotate("text", x = max(mu) + 0.2, y = max(Entropy_gamma.molten$Entropy_Gamma), 
           label = TeX("${italic(H)}_{\\lambda}(\\Gamma_{\\tiny{SAR}})$"), 
           vjust = 1.6, hjust = 0.8, color = "black",linewidth = 0.2) +

  theme_minimal() +

  scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
 # scale_color_manual(values = brewer.pal(4, "Dark2"), labels = alpha_labels) +
  # Labels and titles
  labs(color = "Roughness", 
       x = expression(mu), 
       y = "Rényi Entropy", 
       linetype = NULL) +

  theme(text = element_text(family = "serif"),
        legend.position = "bottom") +

  coord_cartesian(xlim = c(0, 10), ylim = c(min(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma), 
                                            max(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma) + 0.5))

```

For $\lambda \to 1$, this expression converges to the Shannon entropy. As we will see later, this property can lead to improved performance for heterogeneity detection compared to Shannon entropy.

## Main Section 1

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam ultricies lacinia euismod. Nam tempus risus in dolor rhoncus in interdum enim tincidunt. Donec vel nunc neque. In condimentum ullamcorper quam non consequat. Fusce sagittis tempor feugiat. Fusce magna erat, molestie eu convallis ut, tempus sed arcu. Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus. Integer dapibus ligula ac risus convallis pellentesque.

Let $\bm{Z}$

$$
\int_{A_i}{\lambda (\pmb{\mu})}
$$ {#eq-pmb}

$$
\int_{A_i}{\lambda (\mathbf{x})} + x
$$ {#eq-mathbf}

### Subsection 1

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

```{r}
library(tidyverse)
library(palmerpenguins)
```

```{r}
#| fig-cap: "primera grafica"
#| out-width: "12cm"
penguins %>%
  drop_na() %>%
  ggplot(
    aes(x = species, y =  body_mass_g, fill = sex)
  ) +
  geom_boxplot()

```

```{r}
peso <- mean(penguins$body_mass_g, na.rm = TRUE)
```

El peso es\> `r round(peso,2)`

```{r}
#| label: fig-charts
#| fig-cap: "Charts"
#| fig-subcap: 
#|   - "Cars"
#|   - "Pressure"
#| layout-ncol: 2

plot(cars)
plot(pressure)
```

# Tablas

| Nombre | **Apellido** | ***Telefono*** |
|--------|--------------|----------------|
| Maria  | ss           | 45             |
| rosa   | sss          | 67             |

: MI primera tabla

```{r}
#| tbl-cap: "tabla1"
#| label: "tbl-ping"
penguins %>% drop_na()%>% group_by(species, sex) %>%
  summarise(peso = mean(body_mass_g))%>%
  knitr::kable(col.names = c("Especie", "sexo", "peso"))
```

Como se muetsra en la tabla @tbl-ping.

| nombre | apellido |
|--------|----------|
| diana  | Alpala   |
| rosa   | Alpala   |

: nueva tabla

```{r table-example, results="asis"}
library(knitr)
library(kableExtra)

# Creamos un data.frame sencillo:
dt <- data.frame(
  Id   = 1:5,
  Name = c("Alice", "Bob", "Charlie", "Diana", "Ethan"),
  Score = c(90, 85, 88, 92, 80)
)

kable(dt, format = "latex", booktabs = TRUE, caption = "Mi tabla") %>%
  kable_styling(full_width = FALSE) #%>%
  #footnote(
  #  general = " Source: Author.",  # 
   # general_title = ""                      # Deja en blanco para no mostrar "Note:"
    #footnote_as_chunk = TRUE,
    #threeparttable = TRUE
  #)

```

<!-- ```{=latex} -->
<!-- \begin{figure} -->
<!--   \caption{My figure caption} -->
<!--   \centering -->
<!--   \includegraphics{Chapters/Figs/elephant.png} -->
<!--   \caption*{Source: My source} -->
<!-- \end{figure} -->
<!-- ``` -->

<!-- ::: {#fig-1} -->

<!-- ```{r} -->
<!-- #| echo: false -->
<!-- plot(1:10) -->
<!-- ``` -->

<!-- Source: My source -->

<!-- My figure caption. -->

<!-- ::: -->

<!-- See @fig-1. -->

```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}

SAR_data <- data.frame(
  Site = c("Rotterdam", "Coast of Jalisco", "Illinois-Region 1", "Illinois-Region 2"),
  Mission = c("TerraSAR-X", "Sentinel-1B", "Sentinel-1B", "Sentinel-1B"),
  Mode = c("HS", "GRD EW", "GRD SM", "GRD SM"),
  Band = c("X", "C", "C", "C"),
  Polarization = c("HH", "VV", "VV", "VV"),
   Size = c("$\\bm{512}\\times512$", "$\\textbf{512}\times512$", "$512\times512$", "$1024\times1024$"),
  L = c(1, 18, 36, 36),
   Resol = c("$0.85/0.85$", "$40/40$", "$10/10$", "$10/10$"),
  Date = c("06-12-2018", "29-08-2021", "30-06-2020", "28-08-2021")
)

# colnames(SAR_data) <- c(
#   "\\textbf{Site}",
#   "\\textbf{Mission}",
#   "\\textbf{Mode}",
#   "\\textbf{Band}",
#   "\\textbf{Polarization}",
#   "\\textbf{Size}",
#   "$\\bm{L}$",                 # <- Aquí sí quieres modo matemático (para la L)
#   "\\textbf{Resolution}",
#   "\\textbf{Acquisition Date}"
# )

SAR_data[] <- lapply(SAR_data, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})
kable(
  SAR_data,
  caption = "Parameters of selected SAR images.",
  format = "latex",
  booktabs = TRUE,
  align = "ccccccccc",
  escape = FALSE,      # Importante para que interprete el LaTeX
  digits = 2,
  label = "table_param",
  col.names = c(
    "\\textbf{Site}", 
    "Mission", 
    "Mode", 
    "Band", 
    "Polarization", 
    "Size", 
     "$\\bm{L}$",              # L en modo matemático y negrita
    "Resol",  # Ejemplo de texto en negrita con [m]
    "Date"
  )
) %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 12) %>%
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "1cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, width = "1cm") %>%
  column_spec(8, width = "3cm") %>%
  column_spec(9, width = "3cm")

# kable(SAR_data, caption = "Parameters of selected SAR images.",
#       format = "latex",
#       booktabs = TRUE,
#       align = "cccccccccc",
#       escape = FALSE,
#       digits = 2,
#       label = "table_param",
#       centering = FALSE
#       #table.envir = "table", position = "H"
#       ) %>%
#   row_spec(0, align = "c") %>%
#  kable_styling(latex_options = "scale_down", font_size = 10) %>% 
#   kable_styling(full_width = TRUE) %>%
#   column_spec(1, width = "3.5cm") %>%
#   column_spec(2, width = "3cm") %>%
#   column_spec(3, width = "2cm") %>%
#   column_spec(4, width = "1cm") %>%
#   column_spec(5, width = "2cm") %>%
#   column_spec(6, width = "2.5cm") %>%
#   column_spec(7, width = "1cm") %>%
#   column_spec(8, width = "3cm") %>%
#   column_spec(9, width = "3cm")

```

### Subsection 2

Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

## Main Section 2

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

### 2025-06-02 Text/Thesis/Chapters/Chapter3.qmd
R1 update: revised manuscript and reviewer responses added

```{r setup, include=FALSE}
source("setup.R")
```
# PROBLEM STATEMENT AND METHODOLOGY {#sec-Chapter3}

## Bootstrap Correction for  Entropy Estimators

## Hypothesis Testing

## Proposed Test Statistics for Heterogeneity Detection

### 2025-06-02 Text/Thesis/Chapters/Chapter4.qmd
R1 update: revised manuscript and reviewer responses added

```{r setup, include=FALSE}
source("setup.R")
```
# RESULTS {#sec-Chapter4}

## Dataset Description

The following steps were applied to the SAR data during pre-processing:

1. Importing the SAR image into SNAP.  
2. Creating a subset to focus on the area of interest.  
3. Performing Geometric Correction, which includes Range Doppler Terrain Correction.  
4. Exporting the processed data in ENVI format for further analysis.

## Analysis with Simulated data

## Analysis with SAR data
We compare two test statistics for detecting heterogeneity in SAR data: (i) the Rényi entropy-based test, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, described in&nbsp;\eqref{eq-test}; and (ii) the Shannon entropy-based test, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, which is based on the Al-Omari estimator proposed in&nbsp;[@IbrahimAlOmari2014] and was improved via bootstrap in our previous work. The details of this test can be found in Frery et al.&nbsp;[@Frery2024].

We applied these tests to images covering urban, agricultural, and water regions. 
We analyzed images from London, United Kingdom;  the surroundings of Munich, Germany; and  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london-a},&nbsp;\ref{fig:munich-a}, and&nbsp;\ref{fig:dublin-a}. All images were acquired in HH polarization.
Table&nbsp;\ref{tab:table_param} provides the detailed acquisition parameters of these images.

\renewcommand{\arraystretch}{3}   
```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}

SAR_data <- data.frame(
  Site = c("London", "Munich", "Dublin" ),
  Mission = c("TanDEM-X", "UAVSAR", "TanDEM-X"),
  Band = c("X", "L", "X"),
  Size = c("$2000\\times2000$", "$1024\\times1024$", "$1100\\times1100$"),
  L = c(1, 12, 16),
  Resol = c("$0.99/0.99$", "$4.9/7.2$", "$1.35/1.35$"),
  Date = c("12-11-2021", "16-04-2015", "03-09-2017")
)

colnames(SAR_data) <- c(
  "\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", 
  "\\textbf{Size (pixels)}", "$\\bm{L}$", 
  "\\textbf{Resolution [m]}", "\\textbf{Acquisition Date}"
)

SAR_data[] <- lapply(SAR_data, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

kable(SAR_data, 
      format = "latex",
      booktabs = TRUE,
      align = "ccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = TRUE,
      caption = "Parameters of selected SAR images.",
      table.envir = "table", position = "hbt") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 21) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.0cm") %>%
  column_spec(2, width = "3.7cm") %>%
  column_spec(3, width = "1.5cm") %>%
  column_spec(4, width = "4cm") %>%
  column_spec(5, width = "1.5cm") %>%
  column_spec(6, width = "4.0cm") %>%
  column_spec(7, width = "4.5cm")

```
We used sliding windows of size $7\times 7$.
The results are presented as $p$-value maps and binary maps at a $0.05$ significance level. 
Figs.&nbsp;\ref{fig:london-b}--\ref{fig:london-c},&nbsp;\ref{fig:munich-b}--\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-b}--\ref{fig:dublin-c} correspond to $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, while Figs.&nbsp;\ref{fig:london-d}--\ref{fig:london-e},&nbsp;\ref{fig:munich-d}--\ref{fig:munich-e}, and&nbsp;\ref{fig:dublin-d}--\ref{fig:dublin-e} correspond to $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$.

The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions). 
In contrast, black areas represent regions with $p$-values below $0.05$, providing statistical evidence to reject the null hypothesis and indicating heterogeneity.

The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.

```{=latex}
\begin{figure}[H]
    \centering
    % First row: main SAR image
        \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/london_optical_.png}
        \caption*{(a) Optical image}
        \label{fig:london-a}
    \end{minipage}
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/london_2000.png}
        \caption*{(b) SAR image}
        \label{fig:london-b}
    \end{minipage}
    \vspace{1em} % Space between rows
        % Second row: p-value maps
\begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_london_Shannon_c1.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:london-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_london_shannon.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:london-d}
    \end{minipage}
        \vspace{1em} % Space between rows

    % Third row: binary maps
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_london_renyi.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:london-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_london_renyi_L1_.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:london-f}
    \end{minipage}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:london}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.85\textwidth]{Figures/munich_optical1.png}
        \caption*{(a) Optical image}
        \label{fig:munich-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/munich_1024.png}
        \caption*{(b) SAR image}
        \label{fig:munich-b}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Second row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_muni_Shan22.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:munich-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_munich_sh_AO_L12.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:munich-d}
    \end{minipage}

\vspace{1em} % Space between rows

    % Third row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_muni_renyi.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:munich-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_munich_renyi.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:munich-f}
    \end{minipage}
    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:munich}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/dublin.png}
        \caption*{(a) Optical image}
        \label{fig:dublin-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/dublin_1100_hh.png}
        \caption*{(b) SAR image}
        \label{fig:dublin-b}
    \end{minipage}
    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/AO_w7_L16_b100.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:dublin-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_AO_w7_L16_b100.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:dublin-d}
    \end{minipage}
    \vspace{0.9em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/dublin_renyi_09_w7_b100.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:dublin-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_dublin_renyi_09_w7_b100.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:dublin-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:dublin}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/foggia-italy-optical.png}
        \caption*{(a) Optical image}
        \label{fig:Foggia-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/foggia-italy_1900.png}
        \caption*{(b) SAR image}
        \label{fig:Foggia-b}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_italy_AO_1900-H.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:Foggia-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_AO_italy_1900.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:Foggia-d}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_Renyi_Italy_1900_H.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:Foggia-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_renyi_italy_1900_L1.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:Foggia-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over Foggia, Italy: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:Foggia}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/san-francisco-optical1.png}
        \caption*{(a) Optical image}
        \label{fig:san-francisco-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.9\textwidth]{Figures/SF_3300.png}
        \caption*{(b) SAR image}
        \label{fig:san-francisco-b}
    \end{minipage}
    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_SF_AO_3300_H.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-francisco-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_AO_SF_3300_L1_3.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-francisco-d}
    \end{minipage}

    \vspace{0.9em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_renyi_SF_3300_H2_L1_3.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-francisco-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Figures/H_005_renyi_SF_3300_L1_3.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-francisco-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over San Francisco, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:san-francisco}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.47\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Figures/new-orleans-optical.png}
        \caption*{(a) Optical image}
        \label{fig:new-orleans-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.85\textwidth]{Figures/NewOrleans_1400.png}
        \caption*{(b) SAR image}
        \label{fig:new-orleans-b}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_NewOrleans_1400_AO-H.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:new-orleans-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_NewOrleans_1400_AO.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:new-orleans-d}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_NewOrleans_1400_renyi-H.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:new-orleans-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_NewOrleans_1400_renyi.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:new-orleans-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over New Orleans city, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:new-orleans}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.47\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Figures/san-diego-optical.png}
        \caption*{(a) Optical image}
        \label{fig:san-diego-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.85\textwidth]{Figures/sandiego_1300.png}
        \caption*{(b) SAR image}
        \label{fig:san-diego-b}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_sandiego_1300_AO-A.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-diego-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_sandiego_1300_AO.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-diego-d}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_SanDiego_1300_renyi-A.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-diego-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.9\linewidth]{Figures/H_005_sandiego_1300_renyi.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-diego-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over San Diego city, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:san-diego}
\end{figure}

```

```{=latex}
\begin{figure}[H]
    \centering
    % First row: SAR image
    \begin{minipage}{0.47\textwidth}
        \centering
        \includegraphics[width=0.85\textwidth]{Figures/rotterdam_optical.png}
        \caption*{(a) Optical image}
        \label{fig:san-diego-a}
    \end{minipage}
    \hfill
    \begin{minipage}{0.48\textwidth}
        \centering
        \includegraphics[width=0.85\textwidth]{Figures/rotterdam.png}
        \caption*{(b) SAR image}
        \label{fig:san-diego-b}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Third row: p-value and binary for Shannon AO
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_rotterdam1_1200_AO-B.png}
        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-diego-c}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.85\linewidth]{Figures/H_005_rotterdam_AO_L9_B100_1.png}
        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:san-diego-d}
    \end{minipage}

    \vspace{1em} % Space between rows

    % Second row: p-value and binary for Renyi
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_rotterdam1_renyi_1200-B.png}
        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-diego-e}
    \end{minipage}
    \hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.85\linewidth]{Figures/H_005_renyi_rotterdam1_B100_09.png}
        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
        \label{fig:san-diego-f}
    \end{minipage}

    \caption{Detection of heterogeneous areas in a SAR image over Rotterdam, Netherlands: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
    \label{fig:san-diego}
\end{figure}

```

### 2025-06-02 Text/Thesis/Chapters/Chapter5.qmd
R1 update: revised manuscript and reviewer responses added

```{r setup, include=FALSE}
source("setup.R")
```

# CONCLUSIONS AND FUTURE WORK {#sec-Chapter5}

### 2025-06-02 Text/Thesis/Frontmatter/abstract.tex
R1 update: revised manuscript and reviewer responses added

--- 2024-05-09 Text/Thesis/partes/abstract.tex
@@
 %\begin{otherlanguage}{spanish}
-\begin{abstract}
-\phantomsection
-\addcontentsline{toc}{chapter}{Abstract}
+%\begin{abstract}
+%\phantomsection
+%\addcontentsline{toc}{chapter}{Abstract}
 This work presents a statistical approach to identify the
@@
 data.
-\end{abstract}
+%\end{abstract}
 
-\begin{keywords}
-SAR; heterogeneity; entropy; coefficient of variation; hypothesis tests
-\end{keywords}
+\par
+\noindent \textbf{Keywords:} SAR; heterogeneity; entropy; coefficient of variation; hypothesis tests
 

### 2025-06-02 Code/R/Programs/ExperimentTestStatisticL_gamma.R

@@ -24,9 +24,9 @@ set.seed(1234567890, kind="Mersenne-Twister")
 R <- 1000 # 
 mu <- 1
 L <- 5
-B <- 50
+B <- 100
 
-sample.size <- c( 25, 49)
+sample.size <- c( 49)
 
 TestStatistics <- NULL
 
@@ -35,14 +35,14 @@ for(s in sample.size){
     
     z <- gamma_sar_sample(L, mu, s) #
     
-    TestStat <- bootstrap_ebrahimi_estimator(z, B, 0.999) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+    entropy_result <- bootstrap_ebrahimi_estimator(z, B) 
   
    
     TestStatistics <- rbind(TestStatistics,
-                            c(s, TestStat))
+                            c(s, entropy_result))
   }
   
-  mean_entropy <- mean(TestStat)
+  mean_entropy <- mean(entropy_result)
   cat(" mean", mean_entropy, "\n" )
 }
 

### 2025-06-02 Code/R/imagematrix_visualizer.R

@@ -1,0 +1,398 @@
+# imagematrix_visualizer.R
+# Unified template for plotting and exporting grayscale and color image matrices in R
+# Author: Alejandro C. Frery & Janeth Alpala, extended and documented with enhancements
+### 30 April 2025
+
+
+## imagematrix class definition
+## $Header: /database/repository/rimage/R/Attic/imagematrix.R,v 1.1.2.5 2004/03/17 06:35:18 tomo Exp $
+## Copyright (c) 2003 Nikon Systems Inc.
+## For complete license terms see file LICENSE
+
+
+# Supported features:
+# - Grayscale image matrix visualization (original base implementation)
+# - Color image matrix visualization with colorbar (new implementation) 
+# - Automatic detection and inversion for binary maps (0 and 1) for consistent black/white display
+# - Export functions for PNG and PDF (grayscale and color)
+
+# Usage examples:
+# imagematrix(equalize(x))                            # grayscale image
+# imagematrix_color(p_values)                         # color image with colorbar
+# imagematrix(p_values < 0.05)                        # binary grayscale (black = TRUE)
+# imagematrix_color(p_values < 0.05)                  # binary color image (black = TRUE)
+# imagematrixPNG(imagematrix(p_values), "img.png")    # export grayscale
+#imagematrix_colorPNG(imagematrix_color(p_values), name = "name.png",palette_option = "viridis-H",  ...)
+# imagematrix_colorPDF(imagematrix_color(p_values), ...)  # export with colorbar
+# previewImagematrix(imagematrix_color(...))          # preview in RStudio plot pane
+
+# -------------------------------------------------------
+# REQUIRED PACKAGES
+# -------------------------------------------------------
+if (!require(fields)) install.packages("fields", dependencies = TRUE)
+if (!require(viridis)) install.packages("viridis", dependencies = TRUE)
+if (!require(RColorBrewer)) install.packages("RColorBrewer", dependencies = TRUE)
+
+library(fields)
+library(viridis)
+library(RColorBrewer)
+
+# -------------------------------------------------------
+# GRAYSCALE IMAGE FUNCTIONS 
[…]

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Fix Fig 9. reference for ROC curves

@@
 
-Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds&nbsp;(Figs.&nbsp;\ref{ROC1-1}).
+Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds&nbsp;(Fig.&nbsp;\ref{fig:roc}).
 Each curve plots the probability of detection (Pd) versus the probability of false alarm (PFA).

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Entering Section IV

@@
   This approach enhances roughness quantification by capturing scale-dependent variations and addressing data-driven uncertainty.
-  Experimental results demonstrate the robustness of the proposed method in distinguishing roughness patterns, offering a statistically rigorous tool for SAR-based terrain analysis.
+  Experimental results demonstrate the robustness of the proposed method in distinguishing roughness patterns.
+  <!-- , offering a statistically rigorous tool for SAR-based terrain analysis. -->
   <!-- Synthetic aperture radar (SAR) systems have already been successfully used to solve remote sensing problems.  -->
@@
 
-Introduced by Alfréd Rényi in 1961&nbsp;[@renyi1961measures], this measure generalizes several well-known entropies, including Shannon's&nbsp;[@Ribeiro2021]. 
+<!-- Introduced by Alfréd Rényi in 1961&nbsp;[@renyi1961measures], this measure generalizes several well-known entropies, including Shannon's&nbsp;[@Ribeiro2021].  -->
 For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$, is defined as:
@@
 \end{multline}
-The derivation of the latter result is proven in the Appendix.
+<!-- The derivation of the latter result is proven in the Appendix. -->
 Equation&nbsp;\eqref{eq-HGI0} can be read as:
@@
 \textcolor{blue}{where the excess term $\Delta_\alpha$ depends on the roughness parameter.
-When $\alpha\!\to\!-\infty$ (fully developed speckle) this excess tends to zero, so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}. 
-In practice, detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.}
+When $\alpha\!\to\!-\infty$ (fully developed speckle) this excess tends to zero,
+%<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
+and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.}
 <!-- Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
@@
 <!-- This work's core idea is to check if this excess entropy is significantly different from zero. -->
-Fig.&nbsp;\ref{fig-convergence} illustrates this behaviour: as $\alpha$ decreases the coloured curves of $H_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $H_\lambda(\Gamma_{\mathrm{SAR}})$, confirming the limiting behavior.
+Fig.&nbsp;\ref{fig-convergence} illustrates this behaviour: as $\alpha$ decreases the coloured curves of $H_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $H_\lambda(\Gamma_{\mathrm{SAR}})$.
+<!-- , confirming the limiting behavior. -->
 
@@
 
-In order to estimate&nbsp;\eqref{E:entropy2} from a random sample, one may estimate the parameters that index the probability density function $f$ and integrate.
-This approach relies heavily on the model assumptions and the absence of outliers.
-Alternatively, one may estimate directly $f$.
-Such non-parametric estimation of $H(Z)$ has been widely studied using spacing-based estimators, which rely on differences between order statistics&nbsp;[@vasicek1976test;@Ebrahimi1994; @IbrahimAlOmari2014].
-Recently, Al-Labadi et al.&nbsp;[@AlLabadi2024] proposed a non-parametric estimator for Rényi entropy following this approach.
+In order to estimate&nbsp;\eqref{E:entropy2} from a random sample, one may estimate the parameters that index the probability density function $f$ and integrate, an approach that relies on the model assumptions.
+<!-- Alternatively, one may estimate directly $f$. -->
+Recently, Al-Labadi et al.&nbsp;[@AlLabadi2024] proposed a non-parametric estimator for Rényi entropy based on non-parametric estimation using 
+<!-- spacing-based estimators, i.e.,  -->
+differences between order statistics (spacings).
+<!-- &nbsp;[@vasicek1976test;@Ebrahimi1994; @IbrahimAlOmari2014].  -->
 
@@
 $$
-
-Following Vasicek&nbsp;[@vasicek1976test] and Ebrahimi et al.&nbsp;[@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator, the Rényi entropy can be estimated as:
+<!-- Following Vasicek&nbsp;[@vasicek1976test] and Ebrahimi et al.&nbsp;[@Ebrahimi1994] for Shannon entropy estimation, and using the $m$-spacing density estimator,  -->
+The Rényi entropy can be estimated with this density estimator as
 \begin{align}
@@
 
-## On $\lambda$ optimality for a sample size
+## Finding an optimal value of $\lambda$
 
 \textcolor{blue}{
-We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator based on numerical experiments using synthetic samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution $(L = 5,\ \mu = 1)$.
-A Monte Carlo simulation is used to evaluate the bias and the mean squared erro (MSE) across different values of $\lambda$.}
-
-\textcolor{blue}{
-In our simulations, we find that for $L > 1$, the choice $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance.
-As shown in Fig.
-\ref{fig-optimal_order}, the value $\lambda = 0.85$ exhibits slightly lower bias, but leads to higher MSE due to increased variance, supporting the selection of $\lambda = 0.9$.}
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution.
+We computed the bias and the mean squared error (MSE) for vaying $\lambda$ with a Monte Carlo experiment.
+We found that for $L > 1$, $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance. 
+As shown in Fig. \ref{fig-optimal_order}, $\lambda = 0.85$ produces slightly lower bias, but leads to higher MSE, supporting the choice of $\lambda = 0.9$.}
 
@@
 
-Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} reducing its bias with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
+Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
 \begin{equation*}
@@
 ```
-We use the $\widetilde{H}_{\lambda}$ estimator for subsequent simulations.
+<!-- We use the $\widetilde{H}_{\lambda}$ estimator for subsequent simulations. -->
 
@@
 \textcolor{blue}{the difference between the estimated entropy and the expected value under homogeneity.
-Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and thus heterogeneity.
+Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and, thus, heterogeneity.
 This formulation avoids estimating parameters of the $\mathcal{G}^0_I$ model such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
@@
 
-Fig.
-\ref{fig-densities} shows the empirical distribution of $S_{\widetilde{H}_{\lambda}}$ under $\mathcal{H}_0$, obtained from $10^4$ Monte Carlo simulations with varying sample sizes ($n \in {49,81,121}$), $\lambda=0.9$, and $L \in {5,18}$.
+Fig.&nbsp;\ref{fig-densities} shows the empirical distribution of $S_{\widetilde{H}_{\lambda}}$ under $\mathcal{H}_0$, obtained from $10^4$ Monte Carlo simulations with varying sample sizes ($n \in {49,81,121}$), $\lambda=0.9$, and $L \in {5,18}$.
 The concentration around zero confirms the test's expected behavior, while the heavy tails indicate sensitivity to deviations, enabling the detection of subtle texture changes.
@@
 The standardized test statistic 
-$\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \hat{\mu}_S})/{\hat{\sigma}_S}$ is asymptotically standard normal distributed,
-where $\hat{\mu}_S$ and $\hat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis. 
-Thus, the $p$-values are calculated as $2\Phi(-|\varepsilon|)$,
+$\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \widehat{\mu}_S})/{\widehat{\sigma}_S}$ is asymptotically standard normal distributed,
+where $\widehat{\mu}_S$ and $\widehat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis.
+Thus, we compute the $p$-values as $2\Phi(-|\varepsilon|)$,
 where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
-Fig. \ref{fig-density_standardized} shows smoothed histograms of standardized test statistics.
-
-```{r Simulated_densityR_standardized0, echo=FALSE, message=FALSE}
+<!-- Fig.&nbsp;\ref{fig-density_standardized} shows smoothed histograms of standardized test statistics. -->
+
+```{r Simulated_densityR_standardized0, echo=FALSE, message=FALSE, eval=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-density_standardized,eval=FALSE,  echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5}
+```{r fig-density_standardized,eval=FALSE,  echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide", out.width="35%", fig.pos="hbt", fig.cap="Standardized empirical densities of $S_{\\widetilde{H}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=4, fig.height=2.5, eval=FALSE}
 
@@
 
-```{=latex}
-\begin{figure}[hbt]
-  \centering
-  \includegraphics[width=0.35\textwidth]{Figures-R1/fig-density_standardized-1.pdf}
-  %\vspace{0.1em}
-  \caption{Standardized empirical densities of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ under $\mathcal{H}_0$.}
-  \label{fig-density_standardized}
-\end{figure}
-```
+<!-- ```{=latex} -->
+<!-- \begin{figure}[hbt] -->
+<!--   \centering -->
+<!--   \includegraphics[width=0.35\textwidth]{Figures-R1/fig-density_standardized-1.pdf} -->
+<!--   %\vspace{0.1em} -->
+<!--   \caption{Standardized empirical densities of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ under $\mathcal{H}_0$.} -->
+<!--   \label{fig-density_standardized} -->
+<!-- \end{figure} -->
+<!-- ``` -->
 In general, hypotheses tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
@@
 \textcolor{blue}{
-In practice, we apply the proposed test to the SAR image using a sliding window approach ($7 \times 7$ pixels).
-For each window, we compute the test statistic under the null hypothesis of homogeneity and, assuming asymptotic normality, calculate a $p$-value that quantifies the statistical evidence against homogeneity in each local region.
-High $p$-values ($p > 0.05$) indicate no evidence to reject homogeneity, while low values ($p < 0.05$) suggest statistically significant deviations and are interpreted as heterogeneity.
+We applied the proposed test to SAR images using sliding windows of $7 \times 7$ pixels. 
+For each window, we computed the test statistic and calculated the $p$-value that quantifies the statistical evidence against local homogeneity. 
+High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values ($p < 0.05$) suggest statistically significant deviations and are interpreted as heterogeneity.
 }
@@
 The selected scenes, acquired in HH polarization, correspond to the surroundings of London (United Kingdom), the outskirts of Munich (Germany), and the Dublin Port area (Ireland), as shown in Figs.&nbsp;\ref{fig:london-sar}-\ref{fig:dublin-sar}.
-Corresponding optical images (Figs.&nbsp;\ref{fig:london-optical}–\ref{fig:dublin-optical}) illustrate land cover context. Table&nbsp;\ref{tab:table_param} details the SAR acquisition parameters.
+Corresponding optical images (Figs.&nbsp;\ref{fig:london-optical}–\ref{fig:dublin-optical}) illustrate land cover context.
+Table&nbsp;\ref{tab:table_param} details the SAR acquisition parameters.
 
@@
 To validate this value, we estimated the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the coefficient of variation.
-The results were consistent with the metadata.
-We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
+The results were consistent with the metadata. We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
 
@@
 
-\textcolor{blue}{Using real SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions.
+\textcolor{blue}{Using SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions.
 Visual analysis showed greater sensitivity of the Rényi-based test to textural variations.
@@
 
-[]{.appendix options="Derivation of the Rényi Entropy of $\mathcal{G}^0_I$"}
-
-Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ as defined in Ref.&nbsp;[@Frery2024].
-We compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$ using the pdf  
-\begin{equation*}
-f_{\mathcal{G}^0_I}(z) = C \frac{z^{L-1}}{(\gamma + Lz)^{L-\alpha}},  
-\quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}. \label{eq:pdf_G0I}
-\end{equation*}
-Setting $t = Lz/\gamma$, we obtain  
-\begin{equation*}
-I = C^\lambda \frac{\gamma^{1-\lambda+\lambda\alpha}}{L^{\lambda L + 1 - \lambda}}  
-\int_0^\infty \frac{t^{\lambda(L-1)}}{(1+t)^{\lambda(L-\alpha)}} dt.
-\end{equation*}
-Applying the Beta function identity, $B(a,b) = \int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt$ with $a = \lambda(L-1) + 1$, $b = \lambda(-\alpha+1) - 1$, we get  
-\begin{equation*}
-I= \gamma^{\,1 - \lambda}\,
-   L^{\,\lambda - 1}
-   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
-   \,B(a,b).
-\end{equation*}
-Using the Rényi entropy definition in \eqref{E:entropy2}: $H_\lambda(Z) = (1-\lambda)^{-1} \ln I$,
-and substituting $\gamma = -\mu(\alpha + 1)$, we obtain the final expression for $\mathcal{G}^0_I(\mu, \alpha, L)$ in \eqref{eq-HGI0}.
+<!-- []{.appendix options="Derivation of the Rényi Entropy of $\mathcal{G}^0_I$"} -->
+
+<!-- Let $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$ as defined in Ref.&nbsp;[@Frery2024]. -->
+<!-- We compute $I = \int_0^\infty [f_{\mathcal{G}^0_I}(z)]^\lambda dz$ using the pdf   -->
+<!-- \begin{equation*} -->
+<!-- f_{\mathcal{G}^0_I}(z) = C \frac{z^{L-1}}{(\gamma + Lz)^{L-\alpha}},   -->
+<!-- \quad C = \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)}. \label{eq:pdf_G0I} -->
+<!-- \end{equation*} -->
+<!-- Setting $t = Lz/\gamma$, we obtain   -->
+<!-- \begin{equation*} -->
+<!-- I = C^\lambda \frac{\gamma^{1-\lambda+\lambda\alpha}}{L^{\lambda L + 1 - \lambda}}   -->
+<!-- \int_0^\infty \frac{t^{\lambda(L-1)}}{(1+t)^{\lambda(L-\alpha)}} dt. -->
+<!-- \end{equation*} -->
+<!-- Applying the Beta function identity, $B(a,b) = \int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt$ with $a = \lambda(L-1) + 1$, $b = \lambda(-\alpha+1) - 1$, we get   -->
+<!-- \begin{equation*} -->
+<!-- I= \gamma^{\,1 - \lambda}\, -->
+<!--    L^{\,\lambda - 1} -->
+<!--    \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda -->
+<!--    \,B(a,b). -->
+<!-- \end{equation*} -->
+<!-- Using the Rényi entropy definition in \eqref{E:entropy2}: $H_\lambda(Z) = (1-\lambda)^{-1} \ln I$, -->
+<!-- and substituting $\gamma = -\mu(\alpha + 1)$, we obtain the final expression for $\mathcal{G}^0_I(\mu, \alpha, L)$ in \eqref{eq-HGI0}. -->
 

### 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Update R1-Renyi-entropy-sar.qmd

@@
 For each window, we computed the test statistic and calculated the $p$-value that quantifies the statistical evidence against local homogeneity. 
-High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values ($p < 0.05$) suggest statistically significant deviations and are interpreted as heterogeneity.
+High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values, e.g., $p < 0.05$, suggest statistically significant deviations and are interpreted as heterogeneity.
 }
@@
       centering = TRUE,
-      caption = "Parameters of selected SAR images.",
+      caption = "Parameters of selected SAR images",
       table.envir = "table", position = "H") %>%

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Update R1-Renyi-entropy-sar.qmd

@@
 For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP). 
-To validate this value, we estimated the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the coefficient of variation.
-The results were consistent with the metadata. We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
+We validated this nominal value with the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the sample coefficient of variation.
+The results were consistent with the metadata. 
+We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
 
@@
 The output consists of $p$-value maps and binary maps at a $0.05$ significance level. 
-The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
+The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote less textured surfaces.
 The binary maps (Figs.&nbsp;\ref{fig:london-005-renyi},&nbsp;\ref{fig:london-005-shann},&nbsp;\ref{fig:munich-005-renyi},&nbsp;\ref{fig:munich-005-shann},&nbsp;\ref{fig:dublin-005-renyi},&nbsp;\ref{fig:dublin-005-shann}) display heterogeneous detections in black ($p<0.05$) and homogeneous areas in white ($p \geq 0.05$).
@@
 
+<!-- ACF Why three different colour tables? -->
 ```{=latex}

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Add Suggested changes by Prof. ADCN

--- 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
@@
 
-\textcolor{blue}{
 Recent studies highlight the role of entropy in SAR classification. 
@@
 These works motivate lightweight, interpretable alternatives.
-}
 
@@
     \exp \biggl(-\frac{Lz}{\mu}\biggr)
-    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gamma1}
+    \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
 \end{equation}
@@
 $\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
-The $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution&nbsp;[@Frery1997]: for $\mu$ fixed,
+The $\Gamma_{\text{SAR}}$  law is a particular case of the $\mathcal{G}^0_I$ distribution&nbsp;[@Frery1997]: for $\mu$ fixed,
 $$
@@
 <!-- Introduced by Alfréd Rényi in 1961&nbsp;[@renyi1961measures], this measure generalizes several well-known entropies, including Shannon's&nbsp;[@Ribeiro2021].  -->
-For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$, is defined as:
+For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
 \begin{equation}
@@
   -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
-\Bigr],
+\Bigr]
 \end{multline}
@@
 \underbrace{H_\lambda\!\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
-\;\;\;\;\; +
-\underbrace{\Delta_\alpha}_{\text{extra entropy caused by texture}},
+\hspace{1.8em} + \hspace{-1.0em}
+\underbrace{\Delta_\alpha}_{\text{extra entropy caused by texture}}\hspace{-3.0em},
 $$
+
 \textcolor{blue}{where the excess term $\Delta_\alpha$ depends on the roughness parameter.
-When $\alpha\!\to\!-\infty$ (fully developed speckle) this excess tends to zero,
+When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero,
 %<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
@@
 
-Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed random sample of size $n$ from a distribution $F$, and let $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$ denote its order statistics.
+Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed random sample of size $n$ from $Z \sim F$, and let $Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}$ denote its order statistics.
 The $m$-spacing density estimator is defined as:
@@
 $m/n\rightarrow0$. 
-We used the heuristic spacing $m=\left[\sqrt{n}+0.5\right]$.
+We use the heuristic spacing $m=\left[\sqrt{n}+0.5\right]$.
 
@@
 \textcolor{blue}{
-We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$, drawn from the $\Gamma_{\text{SAR}}$ distribution.
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$, drawn from  $Z\sim \Gamma_{\text{SAR}}(5,1)$ distribution.
 We computed the bias and the mean squared error (MSE) for vaying $\lambda$ with a Monte Carlo experiment.
-We found that for $L > 1$, $\lambda = 0.9$ consistently yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance. 
+We found that for $L > 1$, $\lambda = 0.9$  yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance. 
 As shown in Fig. \ref{fig-optimal_order}, $\lambda = 0.85$ produces slightly lower bias, but leads to higher MSE, supporting the choice of $\lambda = 0.9$.}
@@
 
-Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refined the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
+Following Refs.&nbsp;[@Frery2024;@Alpala2024], we refine the non-parametric entropy estimator $\widehat{H}_{\lambda}$ in&nbsp;\eqref{eq:est_R} with bootstrap, obtaining $\widetilde{H}_{\lambda}$:
 \begin{equation*}
@@
 
-A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ ($L=5,\ \mu=1$) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in Fig.
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ (5,1) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in Fig.
 \ref{fig-bias_mse}.
@@
 \;-\;
-\underbrace{H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{theoretical under } H_0},
+\underbrace{H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{theoretical under } H_0}\hspace{-0.5em},
 $$
@@
 Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and, thus, heterogeneity.
-This formulation avoids estimating parameters of the $\mathcal{G}^0_I$ model such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
+This formulation avoids estimating  $\mathcal{G}^0_I$ parameters  such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
 Moreover, the method remains effective for small samples, aided by the bootstrap bias correction.}
 
-Fig.&nbsp;\ref{fig-densities} shows the empirical distribution of $S_{\widetilde{H}_{\lambda}}$ under $\mathcal{H}_0$, obtained from $10^4$ Monte Carlo simulations with varying sample sizes ($n \in {49,81,121}$), $\lambda=0.9$, and $L \in {5,18}$.
-The concentration around zero confirms the test's expected behavior, while the heavy tails indicate sensitivity to deviations, enabling the detection of subtle texture changes.
+Fig.&nbsp;\ref{fig-densities} shows the empirical distribution of $S_{\widetilde{H}_{\lambda}}$ under $\mathcal{H}_0$, obtained from $10^4$ Monte Carlo experiments with varying sample sizes ($n \in {49,81,121}$), $\lambda=0.9$, and $L \in {5,18}$.
+The concentration around zero confirms the expected behavior of the test, while the heavy tails indicate sensitivity to deviations, enabling the detection of subtle texture changes.
 
@@
 \begin{equation*}
-S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) \overset{d}{\longrightarrow} \mathcal{N}(\mu_S,\,\sigma^{2}_S)\,,
+S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) 
+\overset{\mathcal{D}}{\underset{n \to \infty}{\longrightarrow}} 
+\mathcal{N}(\mu_S,\,\sigma^{2}_S),
 \end{equation*}
-where $d$ represents convergence in distribution.
+where $\mathcal{D}$ represents convergence in distribution.
 Here, $\mu_S  = \mathbb{E}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]$ and $\sigma^{2}_S = \text{Var}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]$ are the theoretical mean and variance of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$.
@@
 $\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \widehat{\mu}_S})/{\widehat{\sigma}_S}$ is asymptotically standard normal distributed,
-where $\widehat{\mu}_S$ and $\widehat{\sigma}_S$ are the empirical mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis.
+where $\widehat{\mu}_S$ and $\widehat{\sigma}_S$ are the estimated mean and standard deviation of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, obtained by Monte Carlo simulations under the null hypothesis.
 Thus, we compute the $p$-values as $2\Phi(-|\varepsilon|)$,
-where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
+where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal law.
 <!-- Fig.&nbsp;\ref{fig-density_standardized} shows smoothed histograms of standardized test statistics. -->

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
Final edits to R1 and response letters

@@
 \begin{responsebox}{Response}
-In the revised manuscript, we have included a quantitative performance evaluation to complement the visual comparison presented in Figs. 6–8. 
+In the revised manuscript, we have included a quantitative performance evaluation to complement the visual comparison presented in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
+
 Specifically, we manually defined eight polygonal regions of interest (ROIs) in each SAR image: four clearly homogeneous areas ( water, flat croplands) and four clearly heterogeneous areas (urban centers).
@@
 
-We improved Figures 6–8 by increasing the font size of labels, standardizing the size and placement of the color bars, and updating the colormap in Figure 8 to enhance visual contrast and improve the distinction between low and high $p$-values.
+We improved Figures~6–8 (now Figs.~5–7)  by increasing the font size of labels, standardizing the size and placement of the color bars, and updating the colormap in Figure 8 to enhance visual contrast and improve the distinction between low and high $p$-values.
 

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
Final edits to R1 and response letters
Unify p-value map colormaps

@@
 Specifically, we manually selected eight regions of interest (ROIs) in each SAR image: four clearly homogeneous areas (e.g., water, croplands) and four heterogeneous areas (e.g., urban centers).
-Each ROI was labeled as class~0 (blue) or class~1 (red), as illustrated in Figs.~6a, 7a, and 8a.
+Each ROI was labeled as class~0 (blue) or class~1 (red), as illustrated in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
 
@@
 
-To further support the evaluation, we computed ROC curves and the AUC metric for each test and image using the continuous $p$-values within the ROIs. .
+To further support the evaluation, we computed ROC curves and the area under the curve (AUC) for each method in Fig. 9.
+
 \begin{quote}

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
Unify p-value map colormaps

--- 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
@@
 \begin{responsebox}{Response}
-In the revised manuscript, we have included a quantitative performance evaluation to complement the visual comparison presented in Figs. 6–8. 
+In the revised manuscript, we have included a quantitative performance evaluation to complement the visual comparison.
+
 Specifically, we manually defined eight polygonal regions of interest (ROIs) in each SAR image: four clearly homogeneous areas ( water, flat croplands) and four clearly heterogeneous areas (urban centers).
-Each ROI was labeled as either homogeneous (class 0, shown in blue) or heterogeneous (class 1, in red).
+Each ROI was labeled as either homogeneous (class 0, shown in blue) or heterogeneous (class 1, in red),  as illustrated in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
 
@@
 
-Additionally, to assess performance across all decision thresholds, we computed ROC curves and the area under the curve (AUC) for each method.
+Additionally, to assess performance across all decision thresholds, we computed ROC curves and the area under the curve (AUC) for each method in Fig. 9.
 
@@
 \vspace{9em}
+
 \begin{reviewbox}{Comment 6}
@@
 \end{reviewbox}
+
 \begin{responsebox}{Response}
+We thank the reviewer for this suggestion.
+In response, we improved Figures~6–8 (now Figs.~5–7) by increasing the font size of all labels and standardizing the size and placement of the color bars to enhance clarity and readability.
 
-We improved Figures 6–8 by increasing the font size of labels, standardizing the size and placement of the color bars, and updating the colormap in Figure 8 to enhance visual contrast and improve the distinction between low and high $p$-values.
+Furthermore, we unified the colormap used in the $p$-value maps across all three scenes to ensure visual consistency and facilitate direct comparison between results.
 
-Additionally, we added the corresponding optical images alongside each SAR image to facilitate the interpretation of heterogeneous regions and support visual correlation between land cover and detection results.
+Additionally, we added the corresponding optical images alongside each SAR image to better support the visual interpretation of heterogeneous regions.
 
@@
 
-\vspace{1em} 
+\vspace{0.5em} 
 \begin{reviewbox}{Comment 7}
@@
 
-\vspace{1em}
+\vspace{0.5em}
 

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Final edits to R1 and response letters
Unify p-value map colormaps

@@
 <!-- ACF Why three different colour tables? -->
+
+<!-- New color  Palettes viridis B (inferno) -->
 ```{=latex}
@@
     \begin{subfigure}{0.179\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_E.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_B1.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \begin{subfigure}{0.18\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_E.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_B1.png}
         \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
@@
     \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich_H.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich-B.png}
         \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
@@
     \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich_H.png}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich-B.png}
         \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
@@
         \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin_B.png}
+        \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:dublin-shann}
+    \end{subfigure}
+    \hspace{0.0000001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
+        \caption{Binary $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:dublin-005-shann}
+    \end{subfigure}
+    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
+    \label{fig:dublin}
+\end{figure*}
+
+```
+
+<!-- New color  Palettes viridis H (turbo) -->
+```{=latex}
+\begin{figure*}[hbt]
+    \centering
+    \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
+        \caption{SAR image}
+        \label{fig:london-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.142\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
+        \caption{Optical image}
+        \label{fig:london-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.179\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:london-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:london-005-renyi}
+    \end{subfigure}
+   \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.18\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_H1.png}
+        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
+        \label{fig:london-shann}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:london-005-shann}
+    \end{subfigure}
+    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
+    \label{fig:london}
+\end{figure*}
+```
+
+```{=latex}
+\begin{figure*}[hbt]
+    \centering
+        \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/munich_roi.png}
+        \caption{SAR image}
+        \label{fig:munich-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+  \begin{subfigure}{0.137\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/munich_optical.png}
+        \caption{Optical image}
+        \label{fig:munich-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich_H.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:munich-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_renyi_munich.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:munich-005-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich_H.png}
+        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
+        \label{fig:munich-shann}
+    \end{subfigure}
+   \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_shannon_munich.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:munich-005-shann}
+    \end{subfigure}
+    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
+    \label{fig:munich}
+\end{figure*}
+
+```
+
+```{=latex}
+\begin{figure*}[hbt]
+    \centering
+        \begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/dublin_roi3.png}
+        \caption{SAR image}
+        \label{fig:dublin-sar}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+\begin{subfigure}{0.145\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/dublin.png}
+        \caption{Optical image}
+        \label{fig:dublin-optical}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-H1.png}
+        \caption{$p$-value map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:dublin-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.144\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
+        \caption{Binary map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \label{fig:dublin-005-renyi}
+    \end{subfigure}
+    \hspace{0.00001\textwidth}
+    \begin{subfigure}{0.178\textwidth}
+        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-H1.png}
         \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer1.tex
R1 submission: clean and tracked versions, updated responses

@@
 Moreover, our aim is to propose a statistically grounded, interpretable approach that provides analytical significance measures.
-This distinguishes our method from data-driven alternatives, and makes it especially useful for unsupervised analysis or scenarios with limited ground-truth information.
+This distinguishes our method from data-driven alternatives, and makes it especially useful for unsupervised analysis or scenarios with limited ground truth information.
 
@@
 
-Specifically, we manually defined eight polygonal regions of interest (ROIs) in each SAR image: four clearly homogeneous areas ( water, flat croplands) and four clearly heterogeneous areas (urban centers).
-Each ROI was labeled as either homogeneous (class 0, shown in blue) or heterogeneous (class 1, in red),  as illustrated in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
+Specifically, we manually defined eight polygonal regions of interest (ROIs) in each SAR image: four clearly homogeneous areas (e.g., water, flat croplands) and four clearly heterogeneous areas (e.g., urban centers).
+Each ROI was labeled as either homogeneous (class 0, shown in blue) or heterogeneous (class 1, shown in red), as illustrated in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
 
-These ROIs were then rasterized to create a partial ground-truth mask. 
-We thresholded the $p$-value maps at $0.05$ significance level to generate binary decision maps: values below this threshold were labeled as heterogeneous (1), and values above or equal to the threshold as homogeneous (0).
-The resulting prediction maps were compared against the ground-truth labels within the ROIs. 
-From this comparison, we computed statistical performance metrics such as F1-score, kappa coefficient, and overall accuracy, summarized in Table~III.
+These ROIs were then rasterized to create a partial ground truth mask.
+The $p$-value maps were thresholded at a 0.05 significance level to generate binary decision maps: values below this threshold were labeled as heterogeneous (1), and those above or equal to it as homogeneous (0).
+The resulting prediction maps were compared against the ground truth labels within the ROIs.
 
-Additionally, to assess performance across all decision thresholds, we computed ROC curves and the area under the curve (AUC) for each method in Fig. 9.
+Based on this comparison, we computed standard performance metrics, including F1-score, kappa coefficient, and overall accuracy, summarized in Table~III.
+
+Additionally, to evaluate performance across all decision thresholds, we computed ROC curves and the corresponding AUC values for each method, as shown in Fig.~9.
 
 \begin{quote}
-\textcolor{blue}{These additions appear in Section~IV-C of the revised manuscript.
-}
+\textcolor{blue}{These additions appear in Section~IV-C of the revised manuscript.}
 \end{quote}

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/GRSL_00722_2025_R1_tracked.tex
R1 submission: clean and tracked versions, updated responses

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE!
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, New_IEEEtran_how-to.pdf, bare_jrnl_new_sample4.tex,
%%*************************************************************************
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[
  lettersize  journal,
]{IEEEtran}%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}
%\usepackage[cmex10]{amsmath}
%\usepackage{amssymb}
\usepackage{iftex}
\usepackage{subcaption}
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\captionsetup[subfigure]{labelformat=simple}
\usepackage{caption}
\captionsetup[table]{justification=centerlast, labelsep=newline, textfont={small,sc}}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
%\usepackage{lmodern}
\ifPDFTeX\else
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\parindent    1.0em
\ifCLASSOPTIONcompsoc
  \parindent    1.5em
\fi
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines

\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{physics}
\usepackage[version=3]{mhchem}
\usepackage{orcidlink}
\usepackage{float} 
\usepackage{bm,bbm}
\usepackage{mathrsfs}
\usepackage{nccmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{color}
\usepackage{hyperref}
\usepackage{float}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Fig.}
\else
  \newcommand\figurename{Fig.}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage[skip=2pt,font=footnotesize]{caption}
%\captionsetup{format=myformat}
\makeatletter
%\setlength{\cslhangindent}{0pt plus .5pt}
\providecommand{\bibfont}{\footnotesize}
\let\CSLReferences@rig=\CSLReferences
\renewcommand{\CSLReferences}[2]{
\bibfont\settowidth\csllabelwidth{[999]}
\CSLReferences@rig{#1}{#2}
\vskip 0.3\baselineskip plus 0.1\baselineskip minus 0.1\baselineskip%
}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy},
  pdfauthor={Janeth Alpala; Abraão D.~C.~Nascimento; Alejandro C.~Frery},
  pdfkeywords={Rényi entropy, Gamma
distribution, heterogeneity, SAR, hypothesis tests, bootstrap},
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={black},
  urlcolor={black},
  pdfcreator={LaTeX via pandoc}}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy}

\author{
Janeth Alpala\orcidlink{0000-0002-0265-6236},~Abraão
D.~C.~Nascimento\orcidlink{0000-0003-2673-219X}
and~Alejandro
C.~Frery\orcidlink{0000-0002-8002-5341},~\IEEEmembership{Fellow, IEEE}%
\thanks{Janeth Alpala and Abraão D. C. Nascimento are with the
Departamento de Estatística, Universidade Federal de Pernambuco, Recife,
50670-901 PE, Brazil (e-mails: janeth.alpala@ufpe.br,
abraao@de.ufpe.br).

Alejandro C. Frery is with the School of Mathematics and Statistics,
Victoria University of Wellington, Wellington, 6140, New Zealand
(e-mail: alejandro.frery@vuw.ac.nz).
\emph{Corresponding author: Alejandro C. Frery.}

Data and code are available at:
\url{https://github.com/rjaneth/renyi-entropy}}
}
\begin{document}

% The paper headers
\markboth{Journal XXX, Month Year}{}

% use for special paper notices

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Quantifying surface roughness in synthetic aperture radar (SAR) data is
critical for accurate geophysical interpretation and remote sensing
applications. We propose a test statistic based on a non-parametric
estimation of Rényi entropy to characterize surface roughness from SAR
intensity data. The statistic is refined using bootstrap to improve its
stability, size, and power. This approach enhances roughness
quantification by capturing scale-dependent variations and addressing
data-driven uncertainty. Experimental results demonstrate the robustness
of the proposed method in distinguishing roughness patterns.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Rényi entropy, Gamma distribution, heterogeneity, SAR, hypothesis
tests, bootstrap
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
% \IEEEpeerreviewmaketitle

\renewcommand{\tablename}{TABLE}

\section{Introduction}\label{introduction}

\IEEEPARstart{S}{ynthetic} Aperture Radar (SAR) technology has become
essential for many applications~\citeproc{ref-Mondini2021}{{[}1{]}}. It
provides high-resolution data independent of sunlight and operates in
various weather conditions, facilitating global Earth
monitoring~\citeproc{ref-Zeng2020}{{[}2{]}}. However, the effective use
of SAR data depends on understanding its statistical properties because
it is affected by speckle, a noise-like interference
effect~\citeproc{ref-Baraha2023}{{[}3{]}}. In intensity format, speckle
is non-Gaussian, which complicates image analysis.

The \(\mathcal{G}^0_I\) distribution effectively characterizes SAR
intensity data because it captures different roughness levels. A
limiting case is the Gamma distribution, associated with fully developed
speckle in textureless regions. However, selecting suitable models is
challenging due to small window sizes in practical applications and
difficulties in parameter estimation, motivating alternative statistical
approaches.

Entropy measures have gained attention for SAR analysis, with
applications in edge detection~\citeproc{ref-Nascimento2014}{{[}4{]}},
segmentation~\citeproc{ref-Nobre2016}{{[}5{]}}, and noise
reduction~\citeproc{ref-Chan2022}{{[}6{]}}. Traditionally, Shannon
entropy~\citeproc{ref-Shannon1948}{{[}7{]}} has been widely used to
quantify data uncertainty and disorder. We explore a more general
information measure: Rényi entropy---a generalization of Shannon's
formulation.

\textcolor{blue}{Recent studies highlight the role of entropy in SAR classification.
Cassetti et al.~\citeproc{ref-Cassetti2022}{{[}8{]}} evaluated entropy
estimators in both supervised and unsupervised models. Gallet et al.~\citeproc{ref-Gallet2024}{{[}9{]}} 
proposed a Rényi divergence-based
framework for explainable classification. Parikh et al.~\citeproc{ref-Parikh2019}{{[}10{]}} discussed challenges in deep
learning for SAR, including limited availability of labeled data and the
complexity of tuning hyperparameters. These works motivate lightweight,
interpretable alternatives.}

We propose a statistical test based on a non-parametric estimator of
Rényi entropy to identify heterogeneous regions in SAR data. The test
assesses whether the observed Rényi entropy significantly differs from
its expected theoretical value under the homogeneity assumption,
improving upon our previous Shannon-based
approach~\citeproc{ref-Frery2024}{{[}11{]}}.
\textcolor{blue}{We further enhance the non-parametric estimator through a bootstrap-based bias correction, improving accuracy for small windows.}
\textcolor{blue}{The proposed approach is unsupervised, requires no training data, and yields interpretable $p$-values, making it especially suitable for scenarios where ground truth information is limited or unavailable.}

The rest of this article is organized as follows. Section~\ref{sec:pre}
overviews the statistical models for SAR intensity data and Rényi
entropy. Section~\ref{sec:met} describes the proposed hypothesis test.
Section~\ref{sec:app} evaluates the performance of the test using SAR
data. Finally, the conclusions are presented in
Section~\ref{sec:conclusion}.

\section{PRELIMINARIES}\label{sec:pre}

\subsection{Statistical Models}\label{statistical-models}

The main distributions considered for SAR intensity data are the
\(\Gamma_{\text{SAR}}\) distribution, which is suitable for fully
developed speckle, and the \(\mathcal{G}^0_I\) distribution, which can
describe roughness~\citeproc{ref-Frery1997}{{[}12{]}}. These
distributions are characterized by the following probability density
functions (pdfs): \begin{equation}
    f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
    = \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
    \exp \biggl(-\frac{Lz}{\mu}\biggr)
    \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
\end{equation} and \begin{multline}
    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
    = \frac{L^L\,\Gamma(L-\alpha)}
    {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}\\
    \frac{z^{L-1}}
    {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi01}
\end{multline} where \(\mu > 0\) is the mean, \(\alpha < 0\) measures
the roughness, \(L \geq 1\) is the number of looks, \(\Gamma(\cdot)\) is
the gamma function, and \(\mathbbm 1_{A}(z)\) is the indicator function
of the set \(A\). The \(\Gamma_{\text{SAR}}\) law is a particular case
of the \(\mathcal{G}^0_I\)
distribution~\citeproc{ref-Frery1997}{{[}12{]}}: for \(\mu\) fixed, \[
f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
\longrightarrow 
f_{\Gamma_{\text{SAR}}}(z;L, \mu) \text{ when } \alpha\to-\infty.
\]

\subsection{Rényi Entropy}\label{ruxe9nyi-entropy}

For a continuous random variable \(Z\) with pdf \(f(z)\), the Rényi
entropy of order \(\lambda \in \mathbbm R_+ \setminus \{1\}\) is defined
as: \begin{equation}
\label{E:entropy2}
H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{equation} Using~\eqref{E:entropy2}, we derive closed-form
expressions for the Rényi entropy of the \(\Gamma_{\mathrm{SAR}}\) and
the \(\mathcal{G}^0_I\) distributions: \begin{multline}
\label{eq-HGammaSAR}
H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
= 
\ln \mu - \ln L + \frac{1}{1-\lambda}
\Bigl[
  -\lambda\,\ln\Gamma(L)  \\ + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\Bigr]
\end{multline} and \begin{multline}  
\label{eq-HGI0}  
H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr) \;\;+ \\ \ln(-1 - \alpha)  
+ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
+ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) - \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) \\
+ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
\end{multline}
\textcolor{blue}{ Equation~\eqref{eq-HGI0} can be read as: 
\[
H_{\lambda}(\mathcal{G}^0_I)
=
\underbrace{H_\lambda\!\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
\hspace{1.8em} + \hspace{-1.0em}
\underbrace{\Delta_\alpha}_{\text{extra entropy caused by texture}}\hspace{-3.0em},
\]}

\textcolor{blue}{where the excess term $\Delta_\alpha$ depends on the roughness parameter.
When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero,
%<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.
Fig.~\ref{fig-convergence} illustrates this behaviour: as \(\alpha\)
decreases the colored curves of \(H_\lambda(\mathcal{G}^0_I)\) converge
towards the solid black curve of \(H_\lambda(\Gamma_{\mathrm{SAR}})\).}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-convergence-1.pdf}
  \vspace{0.5em}
  \caption{Convergence of $H_{\lambda}(\mathcal{G}^0_I)$ to $H_{\lambda}(\Gamma_{\text{SAR}})$ as $\alpha$ decreases.}
  \label{fig-convergence}
\end{figure}

\subsection{Non-parametric Estimation of Rényi
Entropy}\label{non-parametric-estimation-of-ruxe9nyi-entropy}

In order to estimate~\eqref{E:entropy2} from a random sample, one may
estimate the parameters that index the probability density function
\(f\) and integrate, an approach that relies on the model assumptions.
Recently, Al-Labadi et al.~\citeproc{ref-AlLabadi2024}{{[}13{]}}
proposed a non-parametric estimator for Rényi entropy based on
non-parametric estimation using differences between order statistics
(spacings).

Let \(\bm{Z}=(Z_1, Z_2,\ldots,Z_n)\) be an independent and identically
distributed random sample of size \(n\) from \(Z \sim F\), and let
\(Z_{(1)} \leq Z_{(2)} \leq \dots \leq Z_{(n)}\) denote its order
statistics. The \(m\)-spacing density estimator is defined as: \[
f_n(Z_{(i)}) = \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}},
\] where \(Z_{(i-m)} = Z_{(1)}\) when \(i \leq m\), and
\(Z_{(i+m)} = Z_{(n)}\) if \(i \geq n - m\). The coefficient \(c_i\) is
given by: \[
c_i = 
\begin{cases}
\frac{m + i - 1}{m}, & \text{if } 1 \leq i \leq m, \\%[6pt]
2, & \text{if } m+1 \leq i \leq n - m, \\%[6pt]
\frac{n + m - i}{m}, & \text{if } n - m + 1 \leq i \leq n.
\end{cases}
\] The Rényi entropy can be estimated with this density estimator as
\begin{align}
\label{eq:est_R}
\widehat{H}_\lambda(\bm{Z}) = \frac{1}{1 - \lambda} \ln \left[\frac{1}{n} \sum_{i=1}^{n} \left( \frac{c_i m / n}{Z_{(i+m)} - Z_{(i-m)}} \right)^{\lambda - 1} \right].
\end{align} This estimator is asymptotically consistent, i.e., it
converges in probability to the true value when \(m,n\rightarrow\infty\)
and \(m/n\rightarrow0\). We use the heuristic spacing
\(m=\left[\sqrt{n}+0.5\right]\).

\section{PROPOSED METHODOLOGY}\label{sec:met}

\subsection{\texorpdfstring{Finding an optimal value of
\(\lambda\)}{Finding an optimal value of \textbackslash lambda}}\label{finding-an-optimal-value-of-lambda}

\textcolor{blue}{
We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$ from  $Z\sim \Gamma_{\text{SAR}}(5,1)$.
We computed the bias and the mean squared error (MSE) for varying $\lambda$ via a Monte Carlo experiment.
We found that for $L > 1$, $\lambda = 0.9$  yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance. 
As shown in Fig.~\ref{fig-optimal_order}, $\lambda = 0.85$ produces slightly lower bias, but results in higher MSE, supporting the choice of $\lambda = 0.9$.}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-optimal_order-1.pdf}
  \vspace{0.5em}
  \caption{Bias and MSE as a function of $\lambda$, with $n=49$, $L=5$.}
  \label{fig-optimal_order}
\end{figure}

Particularly, for \(L = 1\), the optimal \(\lambda\) tends to be higher,
and we choose \(\lambda = 3\) to achieve good results.

\subsection{Bootstrap Correction for Entropy
Estimator}\label{bootstrap-correction-for-entropy-estimator}

Following Refs.~\citeproc{ref-Frery2024}{{[}11{]}},
\citeproc{ref-Alpala2024}{{[}14{]}}, we refine the non-parametric
entropy estimator \(\widehat{H}_{\lambda}\) in~\eqref{eq:est_R} with
bootstrap, obtaining \(\widetilde{H}_{\lambda}\): \begin{equation*}
\widetilde{H}_{\lambda} = 2\widehat{H}_{\lambda}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{H}_{\lambda}(\bm{Z}^{(b)}),
\end{equation*} where \(B\) is the number of bootstrap replications, and
\(\bm{Z}^{(b)}\) denotes the \(b\)-th resampled dataset obtained by
drawing \(n\) observations with replacement from \(\bm{Z}\).

A Monte Carlo study with \(1000\) replications for each sample size
\(n \in \{9, 25, 49, 81, 121\}\) from the \(\Gamma_{\text{SAR}}\) (5,1)
confirms that for \(\lambda=0.9\), the bootstrap-corrected estimator
\(\widetilde{H}_{\lambda}\) (\(B=200\)) reduces both bias and MSE
compared to the original \(\widehat{H}_{\lambda}\), with significant
improvements for small sample sizes, as shown in Fig.~\ref{fig-bias_mse}.

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.40\textwidth]{Figures-R1/fig-bias_mse-1.pdf}
  \vspace{0.1em}
  \caption{Bias and MSE of the Rényi entropy estimators for $\Gamma_{\text{SAR}}$.}
  \label{fig-bias_mse}
\end{figure}

\subsection{Hypothesis Testing}\label{hypothesis-testing}

We test whether the observed data come from a homogeneous
(\(\Gamma_{\text{SAR}}\)) or a heterogeneous (\(\mathcal{G}^0_I\))
region, as follows: \begin{equation}\label{eq:hypothesis_test}
\begin{cases}
\mathcal{H}_0: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\Gamma_{\text{SAR}}) & \text{(Homogeneous region)}, \\[6pt]
\mathcal{H}_1: \mathbb{E}[\widetilde{H}_{\lambda}] = H_{\lambda}(\mathcal{G}^0_I) & \text{(Heterogeneous region)}.
\end{cases}
\end{equation}

Under \(\mathcal{H}_0\), the expected value of the entropy estimator
should match the theoretical \(H_{\lambda}(\Gamma_{\text{SAR}})\).
Significant deviations indicate heterogeneity.

\subsection{The Proposed Test}\label{the-proposed-test}

The test statistic quantifies the discrepancy between estimated and
theoretical entropy under homogeneity. Since \(L\geq1\) is known, we
define the test statistic as follows: \begin{multline}
\label{eq-test}
S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) = \widetilde{H}_{\lambda} - \bigl\{\ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
\bigl[-\lambda\,\ln\Gamma(L) \\ 
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  
- \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\bigr]\bigr\},
\end{multline} where \(\widehat{\mu}={n}^{-1}\sum_{i=1}^n Z_{i}\) is the
sample mean.
\textcolor{blue}{The test statistic can be interpreted as: \[
S_{\widetilde H_\lambda} 
= 
\underbrace{\widetilde H_\lambda}_{\text{estimated}} 
\;-\;
\underbrace{H_\lambda\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{theoretical under } H_0}\hspace{-0.5em},
\]
the difference between the estimated entropy and the expected value under homogeneity. Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and, thus, heterogeneity.
This formulation avoids the need to estimate $\mathcal{G}^0_I$ parameters  such as $\alpha$, offering a simple, interpretable, and statistically grounded test. Moreover, the method remains effective for small samples, aided by the bootstrap bias correction.}

Fig.~\ref{fig-densities} shows the empirical distribution of
\(S_{\widetilde{H}_{\lambda}}\) under \(\mathcal{H}_0\), obtained from
\(10^4\) Monte Carlo experiments with varying sample sizes
(\(n \in {49,81,121}\)), \(\lambda=0.9\), and \(L \in {5,18}\). 
\textcolor{blue}{The concentration around zero confirms the expected behavior of the test,
while the heavy tails indicate sensitivity to deviations, enabling the
detection of subtle texture changes.}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.42\textwidth]{Figures-R1/fig-densities-1.pdf}
  \vspace{0.2em}
  \caption{Empirical densities of $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$ under $\mathcal{H}_0$.}
  \label{fig-densities}
\end{figure}

Vasicek~\citeproc{ref-vasicek1976test}{{[}15{]}} proved that, for
sufficiently large samples, \(S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)\)
asymptotically follows a normal distribution: \begin{equation*}
S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) 
\overset{\mathcal{D}}{\underset{n \to \infty}{\longrightarrow}} 
\mathcal{N}(\mu_S,\,\sigma^{2}_S),
\end{equation*} where \(\mathcal{D}\) represents convergence in
distribution. Here,
\(\mu_S  = \mathbb{E}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]\) and
\(\sigma^{2}_S = \text{Var}[S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)]\)
are the theoretical mean and variance of
\(S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)\).

The standardized test statistic
\(\varepsilon = ({S_{\widetilde{H}_{\lambda}}(\bm{Z}; L) - \widehat{\mu}_S})/{\widehat{\sigma}_S}\)
is asymptotically standard normal distributed, where \(\widehat{\mu}_S\)
and \(\widehat{\sigma}_S\) are the estimated mean and standard deviation
of \(S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)\), obtained by Monte Carlo
simulations under the null hypothesis. Thus, we compute the \(p\)-values
as \(2\Phi(-|\varepsilon|)\), where \(\Phi(\cdot)\) is the cumulative
distribution function of the standard normal law.

In general, hypothesis tests aim to control the Type~I error rate (size)
with high test power (sensitivity to departures from \(\mathcal{H}_0\),
low Type~II error rate). To assess these properties, we performed a
Monte Carlo simulation with \(1000\) replications at significance levels
\SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}, evaluating
the test under the null hypothesis (\(\Gamma_{\text{SAR}}\)
distribution), varying sample size and values of \(L\) for \(\mu=1\).
The observed Type~I error rates align with the nominal values,
confirming the test validity.

Further, we examined the power under the alternative hypothesis
(\(\mathcal{G}^0_I\) distribution) with \(\mu=1\), \(\lambda=0.9\) and
\(\alpha=-2\). As expected, power improves as the sample size and the
number of looks increase, demonstrating the test effectiveness. The
results are shown in Table~\ref{tab:table_size_power}.

\begin{table}[htb]
\centering\centering
\caption{\label{tab:table_size_power}Size and Power of the $S_{\widetilde{H}_{\lambda}}(\bm{Z})$ test statistic.}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\fontsize{7}{9}\selectfont
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{3}{c}{Size} & \multicolumn{3}{c}{Power} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
\multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{$\bm{n}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{1}{\percent}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{5}{\percent}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{10}{\percent}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{1}{\percent}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{5}{\percent}$} & \multicolumn{1}{c}{$\hphantom{00}\SI{10}{\percent}$}\\
\midrule
 & 25 & $\phantom{-}0.014$ & $\phantom{-}0.050$ & $\phantom{-}0.100$ & $\phantom{-}0.978$ & $\phantom{-}0.994$ & $\phantom{-}0.993$\\

 & 49 & $\phantom{-}0.011$ & $\phantom{-}0.048$ & $\phantom{-}0.109$ & $\phantom{-}0.994$ & $\phantom{-}1.000$ & $\phantom{-}0.999$\\

 & 81 & $\phantom{-}0.012$ & $\phantom{-}0.057$ & $\phantom{-}0.103$ & $\phantom{-}0.998$ & $\phantom{-}0.998$ & $\phantom{-}0.999$\\

\multirow{-4}{*}[\normalbaselineskip]{\centering\arraybackslash 5} & 121 & $\phantom{-}0.013$ & $\phantom{-}0.061$ & $\phantom{-}0.116$ & $\phantom{-}0.999$ & $\phantom{-}0.999$ & $\phantom{-}0.997$\\
\cmidrule{1-8}
 & 25 & $\phantom{-}0.010$ & $\phantom{-}0.051$ & $\phantom{-}0.105$ & $\phantom{-}0.996$ & $\phantom{-}0.999$ & $\phantom{-}1.000$\\

 & 49 & $\phantom{-}0.008$ & $\phantom{-}0.056$ & $\phantom{-}0.109$ & $\phantom{-}1.000$ & $\phantom{-}0.999$ & $\phantom{-}1.000$\\

 & 81 & $\phantom{-}0.012$ & $\phantom{-}0.052$ & $\phantom{-}0.097$ & $\phantom{-}0.999$ & $\phantom{-}0.999$ & $\phantom{-}0.999$\\

\multirow{-4}{*}[\normalbaselineskip]{\centering\arraybackslash 8} & 121 & $\phantom{-}0.016$ & $\phantom{-}0.070$ & $\phantom{-}0.116$ & $\phantom{-}0.998$ & $\phantom{-}1.000$ & $\phantom{-}0.999$\\
\cmidrule{1-8}
 & 25 & $\phantom{-}0.016$ & $\phantom{-}0.051$ & $\phantom{-}0.111$ & $\phantom{-}1.000$ & $\phantom{-}1.000$ & $\phantom{-}1.000$\\

 & 49 & $\phantom{-}0.014$ & $\phantom{-}0.047$ & $\phantom{-}0.098$ & $\phantom{-}1.000$ & $\phantom{-}1.000$ & $\phantom{-}1.000$\\

 & 81 & $\phantom{-}0.013$ & $\phantom{-}0.048$ & $\phantom{-}0.106$ & $\phantom{-}1.000$ & $\phantom{-}1.000$ & $\phantom{-}1.000$\\

\multirow{-4}{*}[\normalbaselineskip]{\centering\arraybackslash 18} & 121 & $\phantom{-}0.012$ & $\phantom{-}0.066$ & $\phantom{-}0.110$ & $\phantom{-}1.000$ & $\phantom{-}1.000$ & $\phantom{-}1.000$\\
\bottomrule
\end{tabu}}
\end{table}

\textcolor{blue}{
We applied the proposed test to SAR images using sliding windows of $7 \times 7$ pixels. 
For each window, we computed the test statistic and calculated the $p$-value that quantifies the statistical evidence against local homogeneity. 
High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values, e.g., $p < 0.05$, suggest statistically significant deviations and are interpreted as heterogeneity.
}

\section{Applications to SAR Data}\label{sec:app}

\subsection{Datasets}\label{datasets}

We compare two test statistics for detecting heterogeneity in SAR data:
(i) the Rényi entropy-based test,
\(S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)\), described
in~\eqref{eq-test}; and (ii) the Shannon entropy-based test,
\(S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)\), which is based on the
Al-Omari estimator proposed
in~\citeproc{ref-IbrahimAlOmari2014}{{[}16{]}} and was improved via
bootstrap in our previous work. The details of this test can be found in
Frery et al.~\citeproc{ref-Frery2024}{{[}11{]}}.

The selected scenes, acquired in HH polarization, correspond to the
surroundings of London (United Kingdom), the outskirts of Munich
(Germany), and the Dublin Port area (Ireland), as shown in
Figs.~\ref{fig:london-sar}-\ref{fig:dublin-sar}.
\textcolor{blue}{Corresponding optical
images (Figs.~\ref{fig:london-optical}--\ref{fig:dublin-optical})
illustrate land cover context.} Table~\ref{tab:table_param} details the
SAR acquisition parameters.

\renewcommand{\arraystretch}{2.5}

\begin{table}[H]
\centering\centering
\caption{\label{tab:table_param}Parameters of selected SAR images}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\fontsize{22}{24}\selectfont
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{3.0cm}>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{4cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{4.0cm}>{\centering\arraybackslash}p{4.5cm}}
\toprule
\multicolumn{1}{c}{\textbf{Scene}} & \multicolumn{1}{c}{\textbf{Mission}} & \multicolumn{1}{c}{\textbf{Band}} & \multicolumn{1}{c}{\textbf{Size (pixels)}} & \multicolumn{1}{c}{$\bm{L}$} & \multicolumn{1}{c}{\textbf{Resolution [m]}} & \multicolumn{1}{c}{\textbf{Acquisition Date}}\\
\midrule
London & TanDEM-X & X & $2000\times2000$ & $1$ & $0.99\times0.99$ & 12-11-2021\\
Munich & UAVSAR & L & $1024\times1024$ & $12$ & $4.9\times7.2$ & 16-04-2015\\
Dublin & TanDEM-X & X & $1100\times1100$ & $16$ & $1.35\times1.35$ & 03-09-2017\\
\bottomrule
\end{tabu}}
\end{table}

\textcolor{blue}{
For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP). 
We validated this nominal value with the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the sample coefficient of variation. 
The results were consistent with the metadata. 
We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}

\subsection{Qualitative Inspection}\label{qualitative-inspection}

The output consists of \(p\)-value maps and binary maps at a \(0.05\)
significance level. The \(p\)-value maps use a color gradient
(Figs.~\ref{fig:london-renyi},~\ref{fig:london-shann},~\ref{fig:munich-renyi},~\ref{fig:munich-shann},~\ref{fig:dublin-renyi},~\ref{fig:dublin-shann}),
where darker regions indicate areas with higher roughness, and lighter
regions denote less textured surfaces. The binary maps
(Figs.~\ref{fig:london-005-renyi},~\ref{fig:london-005-shann},~\ref{fig:munich-005-renyi},~\ref{fig:munich-005-shann},~\ref{fig:dublin-005-renyi},~\ref{fig:dublin-005-shann})
display heterogeneous detections in black (\(p<0.05\)) and homogeneous
areas in white (\(p \geq 0.05\)). Visually, the Rényi test exhibits
greater sensitivity in detecting textural variations due to the
flexibility provided by the parameter \(\lambda\).

\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
        \caption{SAR image}
        \label{fig:london-sar}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.142\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
        \caption{Optical image}
        \label{fig:london-optical}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.179\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_H1.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-005-renyi}
    \end{subfigure}
   \hspace{0.00001\textwidth}
    \begin{subfigure}{0.18\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_H1.png}
        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:london-shann}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:london-005-shann}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:london}
\end{figure*}

\begin{figure*}[hbt]
    \centering
        \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/munich_roi.png}
        \caption{SAR image}
        \label{fig:munich-sar}
    \end{subfigure}
    \hspace{0.00001\textwidth}
  \begin{subfigure}{0.137\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/munich_optical.png}
        \caption{Optical image}
        \label{fig:munich-optical}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.178\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich_H.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.144\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_renyi_munich.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:munich-005-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.178\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich_H.png}
        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
        \label{fig:munich-shann}
    \end{subfigure}
   \hspace{0.00001\textwidth}
    \begin{subfigure}{0.144\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_shannon_munich.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:munich-005-shann}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:munich}
\end{figure*}

\begin{figure*}[hbt]
    \centering
        \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/dublin_roi3.png}
        \caption{SAR image}
        \label{fig:dublin-sar}
    \end{subfigure}
    \hspace{0.00001\textwidth}
\begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/dublin.png}
        \caption{Optical image}
        \label{fig:dublin-optical}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.178\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-H1.png}
        \caption{$p$-value map $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.144\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
        \caption{Binary map $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:dublin-005-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.178\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-H1.png}
        \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:dublin-shann}
    \end{subfigure}
    \hspace{0.0000001\textwidth}
    \begin{subfigure}{0.144\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
        \caption{Binary $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:dublin-005-shann}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:dublin}
\end{figure*}

\subsection{Quantitative Evaluation}\label{quantitative-evaluation}

\textcolor{blue}{Eight polygonal regions of interest (ROIs) were manually selected for
each scene (Figs.~\ref{fig:london-sar}-\ref{fig:dublin-sar}):
heterogeneous areas (red, class 1) and homogeneous areas (blue, class
0). These ROIs were rasterized to match the SAR resolution, forming a
partial ground truth. We thresholded the \(p\)-value maps at 0.05,
labeling each pixel as heterogeneous (1) or homogeneous (0) and then
compared these decision maps with the ground truth to compute: F1-score
(\(F_1\)), Kappa coefficient (\(\kappa\)), and overall accuracy (OA).
Table~\ref{tab:table_metrics} summarizes the results. Across all scenes,
the Rényi-based test outperformed Shannon's in all metrics, with notable
gains in London (\(F_1\): 0.695 vs.~0.617; \(\kappa\): 0.626 vs.~0.542),
highlighting its ability to capture heterogeneity under strong speckle
(single-look).}

\renewcommand{\arraystretch}{1.1}

\begin{table}[hbt]
\centering\centering
\caption{\label{tab:table_metrics}Quantitative measures of heterogeneity detection}
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\fontsize{7}{9}\selectfont
\begin{tabu} to \linewidth {>{\centering}X>{\centering}X>{\centering}X>{\centering}X>{\centering}X}
\toprule
\multicolumn{1}{c}{\textbf{Scene}} & \multicolumn{1}{c}{\textbf{Test}} & \multicolumn{1}{c}{$\bm{F_1}$} & \multicolumn{1}{c}{$\kappa$} & \multicolumn{1}{c}{\textbf{OA}}\\
\midrule
 & $S_{\widetilde{H}_{\lambda}}$ & \bm{$0.695$} & \bm{$0.626$} & \bm{$0.877$}\\

\multirow[b]{-2}{*}[\normalbaselineskip]{\centering\arraybackslash London} & $S_{\widetilde{H}_{\text{AO}}}$ & $0.617$ & $0.542$ & $0.854$\\
\cmidrule{1-5}
 & $S_{\widetilde{H}_{\lambda}}$ & \bm{$0.924$} & \bm{$0.861$} & \bm{$0.931$}\\

\multirow[b]{-2}{*}[\normalbaselineskip]{\centering\arraybackslash Munich} & $S_{\widetilde{H}_{\text{AO}}}$ & $0.883$ & $0.794$ & $0.897$\\
\cmidrule{1-5}
 & $S_{\widetilde{H}_{\lambda}}$ & \bm{$0.865$} & \bm{$0.753$} & \bm{$0.875$}\\

\multirow[b]{-2}{*}[\normalbaselineskip]{\centering\arraybackslash Dublin} & $S_{\widetilde{H}_{\text{AO}}}$ & $0.645$ & $0.464$ & $0.858$\\
\bottomrule
\end{tabu}}
\end{table}

\textcolor{blue}{Using the same ROIs as ground truth, we evaluated the continuous
\(p\)-value maps by computing receiver operating characteristic (ROC)
curves over all decision thresholds~(Fig.~\ref{fig:roc}). Each curve
plots the probability of detection (Pd) versus the probability of false
alarm (PFA). Pd reflects the proportion of heterogeneous pixels
correctly detected, while PFA represents the proportion of homogeneous
pixels misclassified as heterogeneous.}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.49\textwidth]{Figures-R1/ROC1-1.pdf}
  \caption{ROC curves comparing the tests $S_{\widetilde{H}_{\lambda}}$ and $S_{\widetilde{H}_{\text{AO}}}$.}
  \label{fig:roc}
\end{figure}

\textcolor{blue}{The area under each ROC curve (AUC) quantifies global detection
performance. The Rényi-based test achieved higher AUCs across all
scenes---London: 0.963 vs.~0.776; Munich: 0.996 vs.~0.989; Dublin: 0.980
vs.~0.971---demonstrating superior robustness compared to the
Shannon-based test under various terrain conditions and textures.}

\section{Conclusions}\label{sec:conclusion}

This study presented a statistical approach based on Rényi entropy for
detecting heterogeneity in SAR images, distinguishing between fully
developed speckle and heterogeneous clutter. The proposed test was
validated with synthetic experiments via a Monte Carlo study,
demonstrating that it effectively controls the probability of Type~I
error while maintaining high detection performance that improves with
sample size.

\textcolor{blue}{Using SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions. Visual analysis showed greater sensitivity of the Rényi-based test to textural variations.
Quantitative evaluation with ground truth ROIs and standard classification metrics confirmed the superior performance of the Rényi-based test across all scenes.}

\textcolor{blue}{Although machine learning-based SAR classifiers are widely used, our focus is on interpretable, statistically grounded methods that yield analytical significance measures. This makes them suitable for rapid detection, screening, and environments with limited data availability.}

\textcolor{blue}{Future work will explore the integration of the improved Rényi estimator into SAR classification pipelines, both supervised and unsupervised, extending its utility beyond heterogeneity testing.}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-Mondini2021}
\CSLLeftMargin{{[}1{]} }%
\CSLRightInline{A. C. Mondini, F. Guzzetti, K.-T. Chang, O. Monserrat,
T. R. Martha, and A. Manconi,
{``\href{https://doi.org/10.1016/j.earscirev.2021.103574}{Landslide
failures detection and mapping using synthetic aperture radar: Past,
present and future},''} \emph{Earth-Science Reviews}, vol. 216, p.
103574, 2021. }

\bibitem[\citeproctext]{ref-Zeng2020}
\CSLLeftMargin{{[}2{]} }%
\CSLRightInline{Z. Zeng \emph{et al.},
{``\href{https://doi.org/10.1016/j.jhydrol.2019.124377}{Towards high
resolution flood monitoring: An integrated methodology using passive
microwave brightness temperatures and sentinel synthetic aperture radar
imagery},''} \emph{Journal of Hydrology}, vol. 582, p. 124377, 2020. }

\bibitem[\citeproctext]{ref-Baraha2023}
\CSLLeftMargin{{[}3{]} }%
\CSLRightInline{S. Baraha and A. K. Sahoo,
{``\href{https://doi.org/10.1016/j.sigpro.2023.109156}{Synthetic
aperture radar image and its despeckling using variational methods: A
review of recent trends},''} \emph{Signal Processing}, vol. 212, p.
109156, 2023. }

\bibitem[\citeproctext]{ref-Nascimento2014}
\CSLLeftMargin{{[}4{]} }%
\CSLRightInline{A. D. C. Nascimento, M. M. Horta, A. C. Frery, and R. J.
Cintra, {``Comparing edge detection methods based on stochastic
entropies and distances for {PolSAR} imagery,''} \emph{{IEEE} Journal of
Selected Topics in Applied Earth Observations and Remote Sensing}, vol.
7, no. 2, pp. 648--663, 2014. }

\bibitem[\citeproctext]{ref-Nobre2016}
\CSLLeftMargin{{[}5{]} }%
\CSLRightInline{R. H. Nobre, F. A. A. Rodrigues, R. C. P. Marques, J. S.
Nobre, J. F. S. R. Neto, and F. N. S. Medeiros,
{``\href{https://doi.org/10.1109/lsp.2016.2606760}{SAR image
segmentation with {R}ényi's entropy},''} \emph{IEEE Signal Processing
Letters}, vol. 23, no. 11, pp. 1551--1555, 2016. }

\bibitem[\citeproctext]{ref-Chan2022}
\CSLLeftMargin{{[}6{]} }%
\CSLRightInline{D. Chan, J. Gambini, and A. C. Frery,
{``\href{https://doi.org/10.3390/rs14030509}{Entropy-based non-local
means filter for single-look SAR speckle reduction},''} \emph{Remote
Sensing}, vol. 14, no. 3, p. 509, 2022. }

\bibitem[\citeproctext]{ref-Shannon1948}
\CSLLeftMargin{{[}7{]} }%
\CSLRightInline{C. E. Shannon, {``A mathematical theory of
communication,''} \emph{The Bell System Technical Journal}, vol. 27, no.
3, pp. 379--423, 1948. }

\bibitem[\citeproctext]{ref-Cassetti2022}
\CSLLeftMargin{{[}8{]} }%
\CSLRightInline{J. Cassetti, D. Delgadino, A. Rey, and A. C. Frery,
{``Entropy estimators in {SAR} image classification,''} \emph{Entropy},
vol. 24, no. 4, p. 509, 2022. }

\bibitem[\citeproctext]{ref-Gallet2024}
\CSLLeftMargin{{[}9{]} }%
\CSLRightInline{M. Gallet, A. Mian, and A. Atto,
{``\href{https://doi.org/10.1109/icassp48485.2024.10448227}{Renyi
divergences learning for explainable classification of {SAR} image
pairs},''} in \emph{2024 {IEEE} {I}nternational {C}onference on
{A}coustics, {S}peech and {S}ignal {P}rocessing {(ICASSP)}}, 2024, pp.
7445--7449. }

\bibitem[\citeproctext]{ref-Parikh2019}
\CSLLeftMargin{{[}10{]} }%
\CSLRightInline{H. Parikh, S. Patel, and V. Patel,
{``\href{https://doi.org/10.1080/19479832.2019.1655489}{Classification
of {SAR} and {PolSAR} images using deep learning: A review},''}
\emph{International Journal of Image and Data Fusion}, vol. 11, no. 1,
pp. 1--32, 2019. }

\bibitem[\citeproctext]{ref-Frery2024}
\CSLLeftMargin{{[}11{]} }%
\CSLRightInline{A. C. Frery, J. Alpala, and A. D. C. Nascimento,
{``\href{https://doi.org/10.3390/rs16111973}{Identifying heterogeneity
in {SAR} data with new test statistics},''} \emph{Remote Sensing}, vol.
16, no. 11, p. 1973, 2024. }

\bibitem[\citeproctext]{ref-Frery1997}
\CSLLeftMargin{{[}12{]} }%
\CSLRightInline{A. C. Frery, H.-J. Muller, C. C. F. Yanasse, and S. J.
S. SantAnna, {``A model for extremely heterogeneous clutter,''}
\emph{{IEEE} Transactions on Geoscience and Remote Sensing}, vol. 35,
no. 3, pp. 648--659, 1997. }

\bibitem[\citeproctext]{ref-AlLabadi2024}
\CSLLeftMargin{{[}13{]} }%
\CSLRightInline{L. Al-Labadi, Z. Chu, and Y. Xu,
{``\href{https://doi.org/10.1007/s00180-024-01507-z}{Advancements in
{R}ényi entropy and divergence estimation for model assessment},''}
\emph{Computational Statistics}, 2024. }

\bibitem[\citeproctext]{ref-Alpala2024}
\CSLLeftMargin{{[}14{]} }%
\CSLRightInline{R. J. Alpala, A. D. C. Nascimento, and A. C. Frery,
{``\href{https://doi.org/10.1109/migars61408.2024.10544448}{Identifying
departures from the fully developed speckle hypothesis in intensity
{SAR} data with non-parametric estimation of the entropy},''} in
\emph{2024 {I}nternational {C}onference on {M}achine {I}ntelligence for
{G}eo{A}nalytics and {R}emote {S}ensing ({MIGARS})}, 2024, pp. 1--4. }

\bibitem[\citeproctext]{ref-vasicek1976test}
\CSLLeftMargin{{[}15{]} }%
\CSLRightInline{O. Vasicek, {``A test for normality based on sample
entropy,''} \emph{Journal of the Royal Statistical Society Series B:
Statistical Methodology}, vol. 38, no. 1, pp. 54--59, 1976. }

\bibitem[\citeproctext]{ref-IbrahimAlOmari2014}
\CSLLeftMargin{{[}16{]} }%
\CSLRightInline{A. I. Al-Omari, {``Estimation of entropy using random
sampling,''} \emph{Journal of Computational and Applied Mathematics},
vol. 261, pp. 95--102, 2014. }

\end{CSLReferences}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% Uncomment when use biblatex with style=ieee
%\renewcommand{\bibfont}{\footnotesize} % for IEEE bibfont size

\pagebreak[3]
% that's all folks
\end{document}

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
R1 submission: clean and tracked versions, updated responses

@@
  Aperture Radar (SAR) technology has become essential for many applications&nbsp;[@Mondini2021]. 
- It provides high-resolution data independent of sunlight and operates in various weather conditions that facilitate global Earth monitoring&nbsp;[@Zeng2020].
+ It provides high-resolution data independent of sunlight and operates in various weather conditions, facilitating global Earth monitoring&nbsp;[@Zeng2020].
 However, the effective use of SAR data depends on understanding its statistical properties because it is affected by speckle, a noise-like interference effect&nbsp;[@Baraha2023].
@@
 Recent studies highlight the role of entropy in SAR classification. 
-Cassetti et al. [@Cassetti2022] evaluated entropy estimators in both supervised and unsupervised models. 
-Gallet et al. [@Gallet2024] proposed a Rényi divergence-based framework for explainable classification. 
-Parikh et al.
-[@Parikh2019] discussed challenges in deep learning for SAR, including limited availability of labeled data and the complexity of tuning hyperparameters.
+Cassetti et al.&nbsp;[@Cassetti2022] evaluated entropy estimators in both supervised and unsupervised models. 
+Gallet et al.&nbsp;[@Gallet2024] proposed a Rényi divergence-based framework for explainable classification. 
+Parikh et al.&nbsp;[@Parikh2019] discussed challenges in deep learning for SAR, including limited availability of labeled data and the complexity of tuning hyperparameters.
 These works motivate lightweight, interpretable alternatives.
@@
 The test assesses whether the observed Rényi entropy significantly differs from its expected theoretical value under the homogeneity assumption, improving upon our previous Shannon-based approach&nbsp;[@Frery2024].
-\textcolor{blue}{We further enhance the non-parametric estimator through a bootstrap-based bias correction, improving accuracy for small windows.}
-\textcolor{blue}{The proposed approach is unsupervised, requires no training data, and yields interpretable $p$-values, making it especially suitable for scenarios where ground-truth information is limited or unavailable.}
-
-The rest of the article is organized as follows.
+We further enhance the non-parametric estimator through a bootstrap-based bias correction, improving accuracy for small windows.
+The proposed approach is unsupervised, requires no training data, and yields interpretable $p$-values, making it especially suitable for scenarios where ground truth information is limited or unavailable.
+
+The rest of this article is organized as follows.
 Section&nbsp;\ref{sec:pre} overviews the statistical models for SAR intensity data and Rényi entropy.
@@
 
-\textcolor{blue}{where the excess term $\Delta_\alpha$ depends on the roughness parameter.
+where the excess term $\Delta_\alpha$ depends on the roughness parameter.
 When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero,
 %<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
-and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.}
+and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.
 <!-- Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
@@
 <!-- This work's core idea is to check if this excess entropy is significantly different from zero. -->
-Fig.&nbsp;\ref{fig-convergence} illustrates this behaviour: as $\alpha$ decreases the coloured curves of $H_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $H_\lambda(\Gamma_{\mathrm{SAR}})$.
+Fig.&nbsp;\ref{fig-convergence} illustrates this behaviour: as $\alpha$ decreases the colored curves of $H_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $H_\lambda(\Gamma_{\mathrm{SAR}})$.
 <!-- , confirming the limiting behavior. -->
@@
 
-\textcolor{blue}{
-We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$, drawn from  $Z\sim \Gamma_{\text{SAR}}(5,1)$ distribution.
-We computed the bias and the mean squared error (MSE) for vaying $\lambda$ with a Monte Carlo experiment.
+We aim to determine the optimal order $\lambda$ for the Rényi entropy estimator using simulated samples of size $n = 49$ from  $Z\sim \Gamma_{\text{SAR}}(5,1)$.
+We computed the bias and the mean squared error (MSE) for varying $\lambda$ via a Monte Carlo experiment.
 We found that for $L > 1$, $\lambda = 0.9$  yields the lowest MSE while maintaining a low bias, thus offering a favorable trade-off between bias and variance. 
-As shown in Fig. \ref{fig-optimal_order}, $\lambda = 0.85$ produces slightly lower bias, but leads to higher MSE, supporting the choice of $\lambda = 0.9$.}
+As shown in Fig.&nbsp;\ref{fig-optimal_order},&nbsp;$\lambda = 0.85$ produces slightly lower bias, but results in higher MSE, supporting the choice of $\lambda = 0.9$.
 
@@
 ```
-Particularly, for $L = 1$, the optimal $\lambda$ tends to be higher, and we chose $\lambda = 3$ to achieve good results.
+Particularly, for $L = 1$, the optimal $\lambda$ tends to be higher, and we choose $\lambda = 3$ to achieve good results.
 
@@
 \end{equation*}
-where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ is the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.
-
-A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ (5,1) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in Fig.
-\ref{fig-bias_mse}.
+where $B$ is the number of bootstrap replications, and $\bm{Z}^{(b)}$ denotes  the $b$-th resampled dataset obtained by drawing $n$ observations with replacement from $\bm{Z}$.
+
+A Monte Carlo study with $1000$ replications for each sample size $n \in \{9, 25, 49, 81, 121\}$ from the $\Gamma_{\text{SAR}}$ (5,1) confirms that for $\lambda=0.9$, the bootstrap-corrected estimator $\widetilde{H}_{\lambda}$ ($B=200$) reduces both bias and MSE compared to the original $\widehat{H}_{\lambda}$, with significant improvements for small sample sizes, as shown in Fig.&nbsp;\ref{fig-bias_mse}.
 ```{r Simulated_data_bias_B1, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
@@
 $$
-\textcolor{blue}{the difference between the estimated entropy and the expected value under homogeneity.
+the difference between the estimated entropy and the expected value under homogeneity.
 Values close to zero indicate that the region behaves like fully developed speckle, while large positive values signal excess entropy and, thus, heterogeneity.
-This formulation avoids estimating  $\mathcal{G}^0_I$ parameters  such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
-Moreover, the method remains effective for small samples, aided by the bootstrap bias correction.}
+This formulation avoids the need to estimate $\mathcal{G}^0_I$ parameters  such as $\alpha$, offering a simple, interpretable, and statistically grounded test.
+Moreover, the method remains effective for small samples, aided by the bootstrap bias correction.
 
@@
 <!-- ``` -->
-In general, hypotheses tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
+In general, hypothesis tests aim to control the Type&nbsp;I error rate (size) with high test power (sensitivity to departures from $\mathcal{H}_0$, low Type&nbsp;II error rate).
 To assess these properties, we performed a Monte Carlo simulation with $1000$ replications at significance levels \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}, evaluating the test under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), varying sample size and values of $L$ for $\mu=1$.
@@
 ```
-\textcolor{blue}{
+
 We applied the proposed test to SAR images using sliding windows of $7 \times 7$ pixels. 
@@
 High $p$-values, e.g., $p > 0.05$, indicate no evidence to reject homogeneity, while low values, e.g., $p < 0.05$, suggest statistically significant deviations and are interpreted as heterogeneity.
-}
+
 <!-- Note that the visual outputs in Figs.~\ref{fig:london}--\ref{fig:dublin} show the $p$-values obtained from the hypothesis testing procedure, not the test statistic or entropy values. -->
@@
   L = c(1, 12, 16),
-  Resol = c("$0.99/0.99$", "$4.9/7.2$", "$1.35/1.35$"),
+  Resol = c("$0.99\\times0.99$", "$4.9\\times7.2$", "$1.35\\times1.35$"),
   Date = c("12-11-2021", "16-04-2015", "03-09-2017")
@@
 ```
-\textcolor{blue}{
+
 For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP). 
@@
 The results were consistent with the metadata. 
-We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}
+We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.
 
@@
 <!-- ACF Why three different colour tables? -->
-
-<!-- New color  Palettes viridis B (inferno) -->
-```{=latex}
-\begin{figure*}[hbt]
-    \centering
-    \begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
-        \caption{SAR image}
-        \label{fig:london-sar}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.142\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
-        \caption{Optical image}
-        \label{fig:london-optical}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.179\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_B1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:london-renyi}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:london-005-renyi}
-    \end{subfigure}
-   \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.18\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_B1.png}
-        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
-        \label{fig:london-shann}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:london-005-shann}
-    \end{subfigure}
-    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
-    \label{fig:london}
-\end{figure*}
-```
-
-```{=latex}
-\begin{figure*}[hbt]
-    \centering
-        \begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/munich_roi.png}
-        \caption{SAR image}
-        \label{fig:munich-sar}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-  \begin{subfigure}{0.137\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/munich_optical.png}
-        \caption{Optical image}
-        \label{fig:munich-optical}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-munich-B.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:munich-renyi}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.144\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_renyi_munich.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:munich-005-renyi}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-munich-B.png}
-        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:munich-shann}
-    \end{subfigure}
-   \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.144\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_shannon_munich.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:munich-005-shann}
-    \end{subfigure}
-    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
-    \label{fig:munich}
-\end{figure*}
-
-```
-
-```{=latex}
-\begin{figure*}[hbt]
-    \centering
-        \begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/dublin_roi3.png}
-        \caption{SAR image}
-        \label{fig:dublin-sar}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-\begin{subfigure}{0.145\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/dublin.png}
-        \caption{Optical image}
-        \label{fig:dublin-optical}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin_B.png}
-        \caption{$p$-value map $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:dublin-renyi}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.144\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
-        \caption{Binary map $\small{S_{\widetilde{H}_{\lambda}}}$}
-        \label{fig:dublin-005-renyi}
-    \end{subfigure}
-    \hspace{0.00001\textwidth}
-    \begin{subfigure}{0.178\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin_B.png}
-        \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:dublin-shann}
-    \end{subfigure}
-    \hspace{0.0000001\textwidth}
-    \begin{subfigure}{0.144\textwidth}
-        \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
-        \caption{Binary $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:dublin-005-shann}
-    \end{subfigure}
-    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
-    \label{fig:dublin}
-\end{figure*}
-
-```
 
@@
 Eight polygonal regions of interest (ROIs) were manually selected for each scene (Figs.&nbsp;\ref{fig:london-sar}-\ref{fig:dublin-sar}): heterogeneous areas (red, class 1) and homogeneous areas (blue, class 0).
-These ROIs were rasterized to match the SAR resolution, forming a partial ground-truth.
-We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0) and then compared these decision maps with the ground-truth to compute: F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
+These ROIs were rasterized to match the SAR resolution, forming a partial ground truth.
+We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0) and then compared these decision maps with the ground truth to compute: F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
 Table&nbsp;\ref{tab:table_metrics} summarizes the results.
@@
 
-\textcolor{blue}{Using SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions.
+Using SAR data, we compared the Rényi-based test with a Shannon-based counterpart through $p$-value maps and binary decisions.
 Visual analysis showed greater sensitivity of the Rényi-based test to textural variations.
-Quantitative evaluation with ground-truth ROIs and standard classification metrics confirmed the superior performance of the Rényi-based test across all scenes.}
-
-\textcolor{blue}{Although machine learning-based SAR classifiers are widely used, our focus is on interpretable, statistically grounded methods that yield analytical significance measures.
-This makes them suitable for rapid detection, screening, and environments with limited data availability.}
-
-\textcolor{blue}{Future work will explore the integration of the improved Rényi estimator into SAR classification pipelines, both supervised and unsupervised, extending its utility beyond heterogeneity testing.}
+Quantitative evaluation with ground truth ROIs and standard classification metrics confirmed the superior performance of the Rényi-based test across all scenes.
+
+Although machine learning-based SAR classifiers are widely used, our focus is on interpretable, statistically grounded methods that yield analytical significance measures.
+This makes them suitable for rapid detection, screening, and environments with limited data availability.
+
+Future work will explore the integration of the improved Rényi estimator into SAR classification pipelines, both supervised and unsupervised, extending its utility beyond heterogeneity testing.
 

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/Submissions Files/R1/Responses/Responses-Associate-Editor.tex
Close to finishing

--- 2025-06-02 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Associate-Editor.tex
@@
 \vspace{0.3em}
-\textcolor{blue}{To improve clarity, we add an intuitive interpretation after equation (5), and include Figure~1 showing the reduction of the excess term as $\alpha$ decreases, illustrating convergence.}
+\begin{quote}
+
+\textcolor{blue}{To improve clarity, we expanded the explanation following Equation~(5) and clarified that Figure~1 illustrates the behavior of the excess entropy term as $\alpha$ decreases, confirming its convergence to the homogeneous case.}
+
+\end{quote}
 \end{responsebox}
@@
 
- This formulation not only supports the theoretical foundation of our test but also offers practical utility: the closed-form expression is not previously available in the SAR literature and can be reused as an analytical feature in other downstream applications
+This formulation avoids parameter estimation for the $\mathcal{G}^0_I$ model, offering a simple, interpretable, and statistically grounded test.
 
-\vspace{0.3em}
-\textcolor{blue}{We added a brief explanation below Equation (8), and clarified in the caption of Figure~4 that the centered distribution confirms correct behavior under $H_0$.}
+\begin{quote}
+\textcolor{blue}{We added a brief explanation below Equation (8), and clarified in the main text (related to Figure~4) that the centered distribution confirms correct behavior under $H_0$.}
+
+\end{quote}
 
@@
 Closed-form Rényi entropy for $\mathcal{G}^{0}_{\!I}$ is absent from the SAR literature; Having it allows others to incorporate an analytical feature into algorithms and applications.
+\begin{quote}
+\textcolor{blue}{These additions are included in Sections II-B and III-D of the revised manuscript.}
 
-\textcolor{blue}{These additions are included in Sections II-B and III-D of the revised manuscript.}
+\textcolor{blue}{Note: Due to space limitations, the derivation of Equation~(5), which was previously included in the Appendix, has been omitted in the revised version.}
+\end{quote}
 \end{responsebox}
 
-\vspace{5em}
+\vspace{1em}
 \begin{reviewbox}{Comment 2}
@@
 \begin{responsebox}{Response}
-We agree with the reviewer and have added a quantitative performance evaluation to the revised manuscript.
-Specifically, we manually selected eight regions of interest (ROIs) in each SAR image: four clearly homogeneous areas (e.g., water, croplands) and four heterogeneous areas (e.g., urban centers).
-Each ROI was labeled as class~0 (blue) or class~1 (red), as illustrated in Figs.~6a, 7a, and 8a.
+We thank the reviewer for the suggestion. We have added a quantitative performance evaluation to the revised manuscript to complement the visual comparison.
 
-These ROIs were rasterized to create a partial ground-truth mask.
-Binary decision maps were obtained by thresholding the $p$-value maps at $ 0.05$ significance level, assigning 1 to pixels with $p < 0.05$ (heterogeneous) and 0 otherwise (homogeneous).
-These predictions were compared to the ground-truth labels, and standard metrics F1-score, kappa coefficient, and overall accuracy were computed.
+Specifically, we manually selected eight regions of interest (ROIs) in each SAR image: four clearly homogeneous areas (e.g., water, croplands) and four clearly heterogeneous areas (e.g., urban centers).
+Each ROI was labeled as class 0 (blue) or class 1 (red), as illustrated in Figs.~5a, 6a, and 7a (corresponding to Figs.~6a, 7a, and 8a in the original submission).
+
+These ROIs were rasterized to create a partial ground truth mask.
+Binary decision maps were obtained by thresholding the $p$-value maps at a 0.05 significance level, assigning a value of 1 to pixels with $p < 0.05$ (heterogeneous), and 0 otherwise (homogeneous).
+These predictions were compared to the ground truth labels, and standard metrics—F1-score, kappa coefficient, and overall accuracy—were computed.
 The results are reported in Table~III.
 
-To further support the evaluation, we computed ROC curves and the AUC metric for each test and image using the continuous $p$-values within the ROIs. .
+To further support the evaluation, we computed ROC curves and the corresponding AUC values for each method, as shown in Fig.~9.
+
 \begin{quote}
-\textcolor{blue}{These additions are included in Section~IV-C of the revised manuscript. }
+\textcolor{blue}{These additions are included in Section~IV-C of the revised manuscript.}
 \end{quote}
-
 \end{responsebox}

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/Submissions Files/R1/Responses/Responses-Reviewer2.tex
Close to finishing

--- 2025-05-20 Text/Articles/RENYI_ENTROPY_SAR_2025/Reviews/Responses-Reviewer2.tex
@@
 %-------------------------------------
+\vspace{2em}
 \begin{reviewbox}{Comment 1}
@@
 \begin{responsebox}{Response}
-Text
+We have carefully revised the manuscript to improve its clarity.
 
@@
 
+\vspace{3em}
 \begin{reviewbox}{Comment 2}
@@
 
-Text
+In the revised manuscript, we have expanded several sections to reinforce the scientific content and clarify the contributions of our work. 
+This article presents a complete statistical framework for detecting heterogeneity in SAR images using a Rényi entropy-based test. 
+The proposed method is analytically grounded, unsupervised, and provides interpretable $p$-values. 
+We enhance a non-parametric entropy estimator via bootstrap correction, validated its statistical properties through a Monte Carlo study, and demonstrated its application on real SAR data under challenging conditions.
+The work further includes quantitative evaluation using standard metrics and ROC curves. We believe these contributions represent both theoretical and practical advances in SAR image analysis.
 
@@
 
+\vspace{10em}
 \begin{reviewbox}{Comment 3}
@@
 \begin{responsebox}{Response}
+We appreciate the reviewer’s suggestion. In response, we have expanded the introduction to better contextualize our contribution relative to recent work.
 
-Text
+Specifically, we now cite recent studies that explore entropy-based methods for SAR analysis and classification.
+For example, Cassetti et al.
+(2022) evaluated several Shannon entropy estimators in both supervised and unsupervised SAR classification.
+Gallet et al.
+(2024) proposed an explainable classification framework based on learned Rényi divergences, demonstrating robustness under label noise and data scarcity.
+Parikh (2019) reviewed deep learning approaches for SAR classification and identified key challenges, including the need for large labeled datasets and complex hyperparameter tuning.
 
+In contrast to these data-driven or classification-focused methods, our work addresses heterogeneity detection from a statistically grounded perspective.
+We propose a hypothesis test based on a non-parametric Rényi entropy estimator, enhanced via bootstrap bias correction.
+This approach does not require training data, produces interpretable $p$-values, and is particularly suited for unsupervised analysis and scenarios with limited ground-truth information.
+
+\begin{quote}
+\textcolor{blue}{These comparisons and citations have been added to the revised Introduction to clarify the novelty and positioning of our contribution.}
+\end{quote}
 \end{responsebox}
+
+\vspace{3em}
+
 \begin{reviewbox}{Comment 4}
@@
 \begin{responsebox}{Response}
-Text
+The conclusion section has been fully revised to improve clarity and better reflect the main contributions, evaluation results, and future research directions of the study.
 

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Close to finishing

@@
 
+      This research, including its outputs, e.g., this manuscript, was executed in Quarto and is fully reproducible.
+We used RStudio version 2024.12.1+563, and R version 4.4.2.
 Data and code are available at: <https://github.com/rjaneth/renyi-entropy>
@@
 ## The Proposed Test
-The test statistic quantifies the discrepancy between estimated and theoretical entropy under homogeneity. Since $L\geq1$ is known, we define the test statistic as follows:
+
+We propose a test statistic that identifies the discrepancy between estimated and theoretical entropy under homogeneity. Since $L\geq1$ is known, we define the test statistic as follows:
 \begin{multline}

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
R1 has been submitted

@@
 abstract: |
-  Quantifying surface roughness in synthetic aperture radar (SAR) data is critical for accurate geophysical interpretation and remote sensing applications. 
-  We propose a test statistic based on a non-parametric estimation of Rényi entropy to characterize surface roughness from SAR intensity data. 
+  Quantifying heterogeneity in synthetic aperture radar (SAR) data is critical for accurate geophysical interpretation and remote sensing applications. 
+  We propose a test statistic based on a non-parametric estimation of Rényi entropy to characterize return heterogeneity from SAR intensity data. 
   The statistic is refined using bootstrap to improve its stability, size, and power. 
-  This approach enhances roughness quantification by capturing scale-dependent variations and addressing data-driven uncertainty.
-  Experimental results demonstrate the robustness of the proposed method in distinguishing roughness patterns.
+  This approach enhances heterogeneity quantification by capturing scale-dependent variations and addressing data-driven uncertainty.
+  Experimental results establish the robustness of the proposed method in distinguishing heterogeneity patterns.
   <!-- , offering a statistically rigorous tool for SAR-based terrain analysis. -->
@@
 pageheader:
-  left: Journal XXX, Month Year
+  left: IEEE Geoscience and Remote Sensing Letters, Month Year
   right: #'D. Folio:  A Sample Article Using quarto-ieee'
@@
 
-The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different roughness levels. 
+The $\mathcal{G}^0_I$ distribution effectively characterizes SAR intensity data because it captures different heterogeneity levels. 
 A limiting case is the Gamma distribution, associated with fully developed speckle in textureless regions.
@@
 
-The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe roughness&nbsp;[@Frery1997].
+The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].
 These distributions are characterized by the following probability density functions (pdfs):
@@
 where $\mu > 0$ is the mean,
-$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of
+$\alpha < 0$ measures the heterogeneity, $L \geq 1$ is the number of
 looks, $\Gamma(\cdot)$ is the gamma function, and
@@
 
-where the excess term $\Delta_\alpha$ depends on the roughness parameter.
+where the excess term $\Delta_\alpha$ depends on the heterogeneity parameter.
 When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero,
@@
   # Labels and titles
-  labs(color = "Roughness", 
+  labs(color = "Heterogeneity", 
        x = expression(mu), 
@@
 The output consists of $p$-value maps and binary maps at a $0.05$ significance level. 
-The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote less textured surfaces.
+The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher heterogeneity, and lighter regions denote less textured surfaces.
 The binary maps (Figs.&nbsp;\ref{fig:london-005-renyi},&nbsp;\ref{fig:london-005-shann},&nbsp;\ref{fig:munich-005-renyi},&nbsp;\ref{fig:munich-005-shann},&nbsp;\ref{fig:dublin-005-renyi},&nbsp;\ref{fig:dublin-005-shann}) display heterogeneous detections in black ($p<0.05$) and homogeneous areas in white ($p \geq 0.05$).

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/Submissions/R0/R0-SubmissionLetter.tex
R1 has been submitted

\documentclass[12pt]{letter} % Uses 10pt

\usepackage[utf8]{inputenc}
\usepackage{merriweather}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{url}

\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{\includegraphics[width=5cm]{assinatura_blue-no_background}\\
Alejandro C.\ Frery\\
\mbox{Professor of Statistics and Data Science}\\
alejandro.frery@vuw.ac.nz}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{Dr.\ Ronny Hänsch\\
	Editor-in-Chief\\
	IEEE Geoscience and Remote Sensing Letters}
\date{1 April 2025}

\begin{flushleft}
Alejandro C.\ Frery
\end{flushleft}
\smallskip\hrule height 2pt
\begin{flushright}
\begin{tabular}{rl}
\multirow{3}{*}[20pt]{\includegraphics[height=3.8cm]{VUW-logo}}	\\
& \small School of Mathematics and Statistics\\
	& \small Victoria University of Wellington\\
	& \small  6140 Wellington, New Zealand
\end{tabular}
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Dr.\ Ronny Hänsch,}

We want to inform that we submitted the manuscript GRSL-00722-2025 (``Quantifying Roughness in SAR Imagery with the Rényi Entropy'') to the MIGARS Special Stream because it is a significantly extended version of ``Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy'' (DOI \url{10.1109/MIGARS61408.2024.10544448}), presented at MIGARS~2024 and already published in IEEExplore.

\closing{Yours sincerely,}

%\encl{Dois formulários 0008/SPT-UFAL;V.2}  				% Enclosures

\end{letter}

\end{document}

### 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/Submissions/R1/Responses/R1-CoverLetter.tex
R1 has been submitted

--- 2025-06-04 Text/Articles/RENYI_ENTROPY_SAR_2025/Submissions/R0/R0-SubmissionLetter.tex
@@
 	IEEE Geoscience and Remote Sensing Letters}
-\date{1 April 2025}
+\date{4 June 2025}
 
@@
 
-We want to inform that we submitted the manuscript GRSL-00722-2025 (``Quantifying Roughness in SAR Imagery with the Rényi Entropy'') to the MIGARS Special Stream because it is a significantly extended version of ``Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy'' (DOI \url{10.1109/MIGARS61408.2024.10544448}), presented at MIGARS~2024 and already published in IEEExplore.
+We appreciate the efforts in finding a suitable Associate Editor and reviewer for our manuscript.
+
+We want to clarify that we focused our revision on the comments provided by the Associate Editor and Reviewer \#1.
+We didn't find the Reviewer \#2 comments constructive or specific.
+Nevertheless, what this last reviewer criticized was also improved thanks to our handling of the other comments.
 

### 2025-06-18 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
update: minor fix in figure caption

@@
 When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero,
-%<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
+<!-- , so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.  -->
 and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero.
@@
         \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-dublin-H1.png}
-        \caption{$p$-value map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
         \label{fig:dublin-renyi}
@@
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin_renyi.png}
-        \caption{Binary map $\small{S_{\widetilde{H}_{\lambda}}}$}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
         \label{fig:dublin-005-renyi}
@@
         \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-dublin-H1.png}
-        \caption{$p$-value $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \caption{$p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
         \label{fig:dublin-shann}
@@
         \includegraphics[width=\linewidth]{./Figures-R1/H_005_dublin-shannon.png}
-        \caption{Binary $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
         \label{fig:dublin-005-shann}

### 2025-07-01 Text/Thesis/Chapters/Chapter1.qmd
Update thesis

@@
 
-The technology of Synthetic Aperture Radar (SAR) imaging operates on the comprehensive aperture principle to produce high-resolution SAR images.
-In contrast to conventional optical remote sensing images, SAR images remain unaffected by external factors, making them suitable for identifying ground targets in diverse weather conditions and expansive areas.
-Consequently, SAR imagery has become essential for environmental monitoring, crop mapping, ship target detection, and climatology.  
-However, the effective use of SAR
-data depends on a thorough understanding of its statistical properties
-because it is corrupted by speckle. This noise-like interference effect
-is inherent in SAR data due to the coherent nature of the imaging
-process.
+Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021; @Zeng2020].
+SAR imagery finds extensive applications in environmental monitoring, disaster management, agriculture mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023].
+Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013;@Choi2019].
 
-Speckle in intensity format is non-Gaussian. 
-Thus, SAR data require reliable statistical models for accurate processing. 
-The $\mathcal{G}^0$ distribution, which is suitable for SAR data, includes
-the Gamma law as the limiting case for fully-developed
-speckle and provides flexibility with fewer
-parameters for analysis.
+Speckle arises from the constructive and destructive interference of backscattered signals within a resolution cell, manifesting as multiplicative, non-Gaussian noise that severely complicates image analysis [@Baraha2023].
+Hence, accurate processing and interpretation of SAR data depend critically on appropriate statistical models to describe speckle behavior.
 
-When deciding which model is the best, practitioners face a problem. 
-On the one hand, if they opt for the Gamma law when the data come from the
-$\mathcal{G}^0$ distribution, they lose all the information about the
-number of scatterers, which is revealed by one of the parameters of the
-latter model. 
-On the other hand, if they apply the $\mathcal{G}^0$ distribution under fully developed speckle, maximum
-likelihood estimation is tricky: bias increases making estimation
-unreliable, and the likelihood is
-flat, so numerical optimization may not
-converge.
+Among the statistical frameworks available, the $\mathcal{G}_I^0$ distribution has been recognized for effectively characterizing SAR intensity data across various levels of scene heterogeneity.
+Its versatility comes from incorporating a texture parameter that accounts for the spatial variability of scatterers, thus generalizing the simpler Gamma distribution, which represents fully developed speckle typically found in homogeneous, textureless regions&nbsp;[@Frery1997; @Ferreira2020].
+In practice, the Gamma model can be considered a limiting case of the $\mathcal{G}_I^0$ distribution as scene texture becomes homogeneous.
 
-Our work aims to improve the identification of potential roughness
-features in SAR intensity data. 
-Physical modeling of SAR data allows the
-use of the Gamma distribution in the presence of fully-developed
-speckle, where an infinite number of independent backscatterers per
-resolution unit is assumed, commonly referred to as homogeneous regions.
+Parameter estimation for these statistical models, however, presents significant challenges, especially when using small-sized windows necessary to preserve spatial resolution in SAR images.
+Traditional likelihood-based or moment-based estimators often become biased or unstable under these practical constraints&nbsp;[@Nascimento2010; @VasconcellosFrerySilva].
+This limitation motivates alternative statistical approaches not reliant on precise parameter estimation or large sample sizes.
 
-Entropy is a fundamental concept in information theory with far-reaching
-applications in pattern recognition, statistical physics, image
-processing, edge detection and SAR image
-analysis.
-@Shannon1948 introduced this concept for a random variable to measure information and uncertainty. 
-Shannon entropy is a crucial descriptive parameter in statistics, especially for evaluating data
-dispersion and performing tests for normality, exponentiality and
-uniformity [@Wieczorkowski1999; @Zamanzade2012].
+Entropy, introduced by Shannon&nbsp;[-@Shannon1948], quantifies the uncertainty associated with a random variable and has found extensive application across fields such as pattern recognition [@Avval2021], statistical physics&nbsp;[@Presse2013], image processing&nbsp;[@MohammadDjafari2015], and particularly in SAR analysis&nbsp;[@Nascimento2014; @Nascimento2019;@Nobre2016; @Chan2022].
+Beyond Shannon's original formulation, Rényi entropy generalizes the measure through an order parameter&nbsp;[@renyi1961measures], while Tsallis entropy offers an alternative non-additive generalization&nbsp;[@Tsallis1988].
+Recent studies highlight the role of entropy in SAR classification.
+Cassetti et al.&nbsp;[-@Cassetti2022] evaluated entropy estimators in both supervised and unsupervised models.
+Gallet et al.&nbsp;[-@Gallet2024] proposed a Rényi divergence-based framework for explainable classification.
+Parikh et al.&nbsp;[-@Parikh2019] discussed challenges in deep learning for SAR, including limited availability of labeled data and the complexity of tuning hyperparameters.
+These works motivate lightweight, interpretable alternatives.
 
-Entropy estimation is challenging, especially when the model is unknown. In these cases,
-non-parametric methods are used. Spacing methods have been discussed as
-a non-parametric approach in Refs. [@AlizadehNoughabi2010;@Subhash2021]. This strategy is flexible
-and robust because it does not enforce a model or parametric
-constraints. In this context, we introduce a novel approach: a bootstrap-improved non-parametric estimator for Shannon entropy.
+When the underlying distribution of data is unknown, entropy measures must be estimated non-parametrically.
+Spacing-based estimators, first proposed by Vasicek&nbsp;[-@vasicek1976test] and further refined in subsequent studies&nbsp;[@VanEs1992; @Ebrahimi1994; @IbrahimAlOmari2014], approximate entropy via spacings of order statistics.
+These estimators have desirable statistical properties, such as strong consistency and asymptotic normality under mild assumptions.
+Recent advancements have extended spacing-based methods to estimate Rényi entropy&nbsp;[@AlLabadi2024].
+Importantly, spacing estimators do not rely on any specific model for the data and do not require choosing parameters, making them simple and flexible tools for entropy estimation.
 
-When applying these statistical concepts to SAR image analysis, we aim to discern between homogeneous and non-homogeneous regions, contributing to the improved interpretation and understanding of SAR data.
-In our study, we devise test statistics based on these three estimators: the classical coefficient of variation, a robust version, and the Shannon entropy estimator.
-We apply these test statistics to generate maps of evidence of homogeneity that reveal different types of targets in the SAR data, assuming the number of looks is known.
-Likewise, we show that our proposed method is superior to existing approaches with simulated data and SAR images.
+## MOTIVATION AND PROBLEM STATEMENT
 
-## OBJETIVES
+Typically, SAR data exhibit heterogeneous clutter or fully developed speckle, depending on terrain characteristics and imaging conditions.
+Distinguishing between these two cases is critical for accurate interpretation and analysis.
 
-The aim of this work is the identification of roughness features in SAR intensity data by developing novel test statistics for distinguishing between homogeneous and heterogeneous domains.  
-To achieve this goal, we propose the following procedure:
+While the $\mathcal{G}_I^0$ distribution effectively models heterogeneous SAR intensity data, practitioners face a significant challenge: choosing between simpler (Gamma-based) and more complex ($\mathcal{G}_I^0$-based) statistical models.
+Opting for the simpler Gamma model risks losing important texture information about scatterer variability, encapsulated within the $\mathcal{G}_I^0$ distribution's parameters&nbsp;[@Yue2021].
+Conversely, directly applying the $\mathcal{G}_I^0$ distribution in homogeneous regions introduces substantial estimation difficulties, such as increased parameter estimation bias and computational instability due to flat likelihood surfaces, particularly when analysis windows are small&nbsp;[@FreryCribariSouza; @Nascimento2010].
 
-- Select the optimal non-parametric estimator of entropy, refined through bootstrap techniques, aiming to reduce bias and mean square error.
-- Propose three test statistics: the first based on the selected non-parametric estimator of entropy; the second utilizing the classical coefficient of variation; and the third using a robust approach of CV variant.
-- Conduct computational experiments to evaluate the performance of the proposed test statistics across various simulated data scenarios.
-- Apply the test statistics to SAR data to assess their effectiveness in identifying roughness features.
+These estimation issues motivate the development of alternative methodologies that avoid explicit parametric estimation.
+In this context, non-parametric statistical tests based on entropy measures emerge as an appealing alternative.
+Such tests exploit entropy’s sensitivity to deviations from homogeneity assumptions without relying on explicit parameter estimates.
+
+This thesis proposes three novel entropy-based statistical tests (using Shannon, Rényi, and Tsallis entropies) designed specifically to distinguish heterogeneous clutter from fully developed speckle under the assumption that SAR intensity follows the Gamma SAR distribution in homogeneous regions.
+These tests assess whether observed entropy significantly differs from theoretical expectations under the homogeneity hypothesis, making them highly interpretable and practically applicable even when ground truth information is limited or unavailable.
+
+To enhance accuracy, particularly within small-window analysis contexts common in practical SAR scenarios, we further propose a bootstrap-based bias-correction procedure for the entropy estimators.
+Overall, our approach provides robust, unsupervised statistical tools well-suited for operational scenarios, bridging a critical gap in existing methodologies.
+
+## OBJECTIVES
+
+<!-- The primary objective of this thesis is to develop and validate a set of entropy-based statistical tests for the detection of heterogeneity in SAR intensity images.
+These tests are designed to distinguish between fully developed speckle, modeled by the Gamma distribution, and heterogeneous clutter, modeled by the $\mathcal{G}_I^0$ distribution, in a robust and interpretable manner.
+-->
+
+### General Objective
+
+To propose and evaluate entropy-based statistical tests for detecting heterogeneity in SAR imagery, using non-parametric estimation and bootstrap correction to enhance accuracy in small-sample scenarios.
+
+### Specific Objectives
+
+- To derive closed-form expressions for  Rényi and Tsallis entropies under the Gamma SAR and $\mathcal{G}_I^0$ models, which serve as theoretical benchmarks for hypothesis testing.
+
+- To identify and refine suitable non-parametric estimators of entropy for SAR data, incorporating bootstrap techniques to reduce bias and improve estimation accuracy.
+
+- To formulate three entropy-based test statistics that compare the estimated entropy from observed data with its theoretical value under the homogeneity assumption.
+
+- To evaluate the empirical size and power of the proposed tests via Monte Carlo simulations.
+
+- To apply the proposed tests to both simulated and real SAR data using a sliding window scheme, and generate $p$-value maps for visual inspection and quantitative assessment.
 
@@
 
-The main contributions of this work are the following:
+1.
+**Closed-form entropy derivations.** Analytical expressions for Rényi, and Tsallis entropies under the Gamma SAR and $\mathcal{G}_I^0$ models are derived, filling a gap in the literature and enabling  hypothesis testing.
 
-1. Development of a new non-parametric entropy-based test statistic for roughness detection in SAR images.
-2. Comparative study of three different test statistics under various simulated scenarios.
-3. Integration of bootstrap techniques to improve estimation accuracy and robustness.
-4. Application of the proposed methods to real SAR data, demonstrating their practical relevance.
+2.
+**Non-parametric estimator and bootstrap bias-correction.** A new spacing-based estimator is proposed for Tsallis entropy.
+A bootstrap bias-correction procedure is developed to improve the precision of all non-parametric estimators, substantially reducing bias and mean squared error in small-window analyses.
+
+3. **Entropy-based test statistics.** Proposal of three  entropy-based statistical tests for heterogeneity detection in SAR imagery, using Shannon, Rényi, and Tsallis entropy measures.
+
+<!-- 4.
+**Comprehensive validation.** Evaluation of the statistical performance of the proposed tests through extensive Monte Carlo simulations, analyzing Type I error (size), power, and robustness under various speckle and texture conditions.
+-->
+
+<!-- 5.
+**Real applications.** Application of the proposed methodology to both simulated and real SAR data, producing $p$-value maps through sliding window analysis for visual and quantitative assessment of spatial heterogeneity.
+-->
+
+## COMPUTATIONAL SUPPORT AND REPRODUCIBILITY
+
+Simulations, tests, and data analyses presented in this thesis were implemented using the free, open-source programming language \texttt{R}\footnote{\url{https://www.r-project.org/}} within \texttt{RStudio} (version 2024.12.1+563, \texttt{R} version 4.4.2).
+The manuscript was written in \texttt{Quarto}\footnote{\url{https://quarto.org/}}, a dynamic publishing system that integrates code, output, and narrative to ensure full reproducibility&nbsp;[@bauer2023reproducible].
+
+The numerical experiments were performed on a personal computer equipped with an AMD Ryzen 9 5900X 12-Core Processor (3.70 GHz) and 32 GB RAM.
+
+All code and data for this research, including the manuscript source, are  available at \url{https://github.com/rjaneth/Thesis-UFPE}, supporting reproducibility.
+This work follows best practices recommended by Frery et al.&nbsp;[-@Frery2020].
+
+### Related Publications
+
+The following peer-reviewed articles and conference paper have been published as part of or related to this research:
+
+1.
+[@Alpala2025]: [Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy.](https://openaccess.wgtn.ac.nz/articles/journal_contribution/Quantifying_Heterogeneity_in_SAR_Imagery_with_the_R_nyi_Entropy/29376944?file=55548095)
+
+2. [@Frery2024]: [Identifying Heterogeneity in SAR Data with New Test Statistics.](https://www.mdpi.com/2072-4292/16/11/1973)
+
+3.
+[@Alpala2024]: [Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy.](https://ieeexplore.ieee.org/document/10544448)
 
@@
 
-@sec-Chapter2 provides a background on remote sensing and SAR images.
-@sec-Chapter3 presents methodological aspects, including statistical modeling, entropy estimation for intensity SAR data, and hypothesis testing, and @sec-Chapter4 the statistical modelling choices common to all objectives of this thesis.
-@sec-Chapter5 presents the main results obtained in our study with both simulated and actual data.
-@sec-Chapter6 concludes with a discussion on heterogeneity implications of the findings and areas for future research building on the work in this thesis.
+This thesis is organized into five chapters as follows:
+
+- @sec-Chapter2 presents the theoretical foundations of the work.
+It includes statistical modeling of SAR intensity data, entropy measures, and nonparametric estimation techniques based on order statistics.
+
+- @sec-Chapter3 describes the proposed methodology.
+It covers the selection and bias correction of entropy estimators, the construction of the test statistics, and the hypothesis testing framework based on Shannon, Rényi, and Tsallis entropy.
+
+- @sec-Chapter4 presents the results obtained from simulated and real SAR datasets. This includes both qualitative and quantitative analyses that demonstrate the effectiveness of the proposed methods.
+
+- @sec-Chapter5 summarizes the conclusions drawn from the study and outlines potential directions for future research.

### 2025-07-01 Text/Thesis/Chapters/Chapter2.qmd
Update thesis

@@
 source("setup.R")
+
+source("./Code/entropy_gamma_sar.R")
+source("./Code/entropy_gI0.R")
+source("./Code/gamma_sar_sample.R")
+source("./Code/gi0_sample.R")
+source("./Code/al_omari_1_estimator.R")
+source("./Code/bootstrap_al_omari_1_estimator.R")
+source("./Code/renyi_entropy_estimator_v1.R")
+source("./Code/bootstrap_renyi_entropy_estimator_v1.R")
+source("./Code/entropy_renyi_gamma_sar.R")
+
+source("./Code/vasicek_estimator.R")
+source("./Code/van_es_estimator.R")
+source("./Code/noughabi_arghami_estimator.R")
+source("./Code/correa_estimator.R")
+source("./Code/ebrahimi_estimator.R")
+
+source("./Code/tsallis_entropy_gamma_sar.R")
+source("./Code/tsallis_estimator.R")
+source("./Code/bootstrap_tsallis_entropy.R")
+source("./Code/tsallis_estimator_optimized.R")
+source("./Code/bootstrap_tsallis_entropy_optimized.R")
+
+source("./Code/renyi_estimator.R")
+source("./Code/bootstrap_renyi_estimator.R")
+source("./Code/renyi_entropy_optimized.R")
+source("./Code/bootstrap_renyi_estimator_Op.R")
+
+source("./Code/shannon_alomari_estimator.R")
+source("./Code/bootstrap_shannon_alomari.R")
+source("./Code/shannon_entropy_gamma_sar.R")
+
+source("./Code/functions_sample_bias_mse.R")
+source("./Code/functions_sample_bias_mse_1.R")
+
 ```
-# THEORETICAL BACKGROUND {#sec-Chapter2}
+# THEORETICAL FOUNDATIONS {#sec-Chapter2}
 
-##  Synthetic Aperture Radar
+## STATISTICAL MODELING OF INTENSITY SAR DATA
 
-## Statistical Models
+Statistical modeling plays a central role in the analysis of SAR imagery, where speckle is a fundamental characteristic.
+The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].
 
-The main models considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which is able to describe roughness\ [@Frery1997].
-These distributions are characterized by the following probability density functions (pdfs):
-\begin{align}
+We denote $Z \sim \Gamma_{\mathrm{SAR}}(L, \mu)$ and $Z \sim \mathcal{G}_I^0(\alpha, \gamma, L)$ when the random variable $Z$ follows the respective distributions, characterized by the following probability density functions (pdfs):
+\begin{equation}
 	f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
-    &= \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
+    = \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
     \exp \biggl(-\frac{Lz}{\mu}\biggr)
     \mathbbm 1_{\mathbbm R_+}(z) \label{E:gamma1}
-    \intertext{and}
+\end{equation}
+and
+\begin{align}
+ f_{\mathcal{G}^0_I}\bigl(z;  \alpha,\gamma, L \bigr) &=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}} \mathbbm{1}_{\mathbb{R}_+}(z), \label{E:gi01}
+\end{align}
+where $\mu > 0$ is the mean intensity, $\gamma > 0$ is a scale parameter, $\alpha < 0$ controls the degree of texture (roughness), $L \geq 1$ is the number of looks (either nominal or estimated, thus not restricted to integer values), $\Gamma(\cdot)$ is
+the gamma function, 
+and $\mathbbm 1_{A}(z)$ is the indicator function
+of the set $A$.
+
+The $r$th order moments of the $\mathcal{G}_I^0$ model are
+\begin{equation}
+E\big(Z^r\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\frac{\Gamma(L+r)}{\Gamma(L)}, 
+    \label{E:rmom}
+\end{equation}
+provided $\alpha <-r$, and infinite otherwise.
+Therefore, assuming $\alpha<-1$, its expected value is
+\begin{equation}
+    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+\end{equation}
+
+Although the $\mathcal{G}_I^0$ distribution is defined by the parameters $\alpha$ and $\gamma$, in the SAR literature&nbsp;[@Nascimento2010] the texture $\alpha$ and the mean $\mu$ are usually used.
+Reparametrizing&nbsp;\eqref{E:gi01} with $\mu$, and denoting this model as $Z \sim \mathcal{G}_I^0(\alpha, \mu, L)$ we obtain:
+\begin{equation}
     f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
-    &= \frac{L^L\,\Gamma(L-\alpha)}
+    = \frac{L^L\,\Gamma(L-\alpha)}
     {\bigl[-\mu(\alpha+1)\bigr]^{\alpha} \Gamma(-\alpha)\,\Gamma(L)}
-    \notag \\
-    &\quad \times
     \frac{z^{L-1}}
     {\bigl[-\mu(\alpha+1)+Lz\bigr]^{L-\alpha}}
-    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi01}
-\end{align}
-where $\mu > 0$ is the mean,
-$\alpha < 0$ measures the roughness, $L \geq 1$ is the number of
-looks, $\Gamma(\cdot)$ is the gamma function, and
-$\mathbbm 1_{A}(z)$ is the indicator function of the set $A$. 
-As demonstrated by\ [@Frery1997], the $\Gamma_{\text{SAR}}$  model is a particular case of the $\mathcal{G}^0_I$ distribution. Specifically, for a given $\mu$ fixed,
+    \mathbbm 1_{\mathbbm R_+}(z), \label{E:gi02}
+\end{equation}
+The $\Gamma_{\mathrm{SAR}}$ model is a particular case of the $\mathcal{G}^0_I$ distribution, as demonstrated in&nbsp;[@Frery1997]. Specifically, for a given $\mu$ fixed,
 $$
@@
 \longrightarrow 
-f_{\Gamma_{\text{SAR}}}(z;L, \mu) 
+f_{\Gamma_{\text{SAR}}}(z;L, \mu) \quad \text{ when } \alpha\to-\infty.
 $$
-when $\alpha\to-\infty$.
 
-## Rényi Entropy
+In this work, we do not focus on parameter estimation using likelihood-based or moment-based methods.
+Instead, we adopt a testing framework to detect heterogeneity in SAR imagery.
+The analytical expressions of entropy measures derived from the $\Gamma_{\text{SAR}}$ and $\mathcal{G}_I^0$ models form the theoretical basis for constructing these statistical tests.
+In the following section, we introduce the entropy-based measures, specifically Shannon, Rényi, and Tsallis, on which our detection strategy is built.
 
-Introduced by Alfréd Rényi in 1961\ [@renyi1961measures], this measure generalizes several well-known entropies, including the Shannon entropy\ [@Ribeiro2021].
-For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda$, with $\lambda > 0$ and $\lambda \neq 1$, is defined as:
-\begin{align}
-\label{E:entropy2}
-H_\lambda(Z) = \frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
-\end{align}
-Using \eqref{E:entropy2}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions:
+## ENTROPY MEASURES
+
+Entropy stands as a foundational concept in information theory, originally formulated by Claude Shannon&nbsp;[-@Shannon1948].
+It provides a formal mechanism for quantifying the uncertainty or unpredictability of a random variable.
+More precisely, the entropy of a random variable can be interpreted as the average amount of information required to describe its outcomes based on its probability distribution.
+As such, entropy quantifies the expected information content of a random event, with higher values indicating more uncertainty or variability in the distribution.
+It plays a central role in a wide range of applications, including statistical physics&nbsp;[@Pachter2024], complex systems&nbsp;[@Bashkirov2006], machine learning&nbsp;[@SepulvedaFontaine2024], and remote sensing&nbsp;[@Jiao2021].
+
+This section focuses on three widely used entropy formulations that offer complementary perspectives on uncertainty: Shannon entropy $H$, Rényi entropy $R_\lambda$, and Tsallis entropy $T_\lambda$.
+In the context of continuous random variables, these measures take the form of \textit{differential entropies}, which are defined using probability density functions.
+These differential entropies are not only theoretically grounded but also highly applicable to the statistical modeling of Synthetic Aperture Radar (SAR) data.
+Each entropy captures different aspects of distributional structure and provides a flexible framework for heterogeneity analysis in SAR imagery.
+
+\textbf{Shannon entropy} is the classical and most widely adopted measure, reflecting the average information content or uncertainty inherent in a random variable.
+It assumes statistical independence and extensivity, and serves as the baseline concept upon which generalizations are constructed.
+
+\textbf{Rényi entropy}, introduced by Alfréd Rényi&nbsp;[-@renyi1961measures], is a one-parameter generalization of Shannon's measure.
+By tuning the parameter $\lambda > 0$, the analyst can adjust the sensitivity of the entropy to the tails of the distribution.
+This property is particularly relevant in applications where rare events (e.g., bright scatterers, outliers) carry significant informational weight, such as in SAR-based texture discrimination or target detection.
+
+\textbf{Tsallis entropy},  was first introduced by Havrda and Charvat&nbsp;[-@Havrda1967]  in the context of information theory.
+Then, Tsallis&nbsp;[-@Tsallis1988] exploited its non-extensive features and placed it in a physical setting, known as generalized Tsallis entropy of order $\lambda$,  offers an alternative generalization motivated by non-extensive systems, those exhibiting long-range dependencies, memory effects, or multifractal behavior.
+Unlike Rényi, Tsallis entropy does not obey the additivity property under independent systems, which makes it particularly suitable for modeling complex spatial structures and textured regions in SAR images.
+
+In the context of SAR imaging, homogeneous areas produce fully developed speckle and are effectively modeled by the $Z \sim\Gamma_{\text{SAR}}(L, \mu)$ distribution.
+In contrast, textured or heterogeneous regions are better represented by the  $Z \sim\mathcal{G}^0_I(\mu, \alpha, L)$ model, where the roughness parameter $\alpha$ controls the degree of heterogeneity.
+Across this section, we show that all three entropy measures applied to $\mathcal{G}^0_I$ can be decomposed as:
+\begin{equation}
+\label{eq:decomp-intro}
+\boxed{\;
+\text{Entropy}\bigl(\mathcal{G}^{0}_{I}\bigr)
+\;=\;
+\text{Entropy}\bigl(\Gamma_{\mathrm{SAR}}\bigr)
+\;+\;
+\Delta_{\alpha}
+\;}
+\end{equation}
+
+where  $\Delta_\alpha$ represents the \textit{excess entropy} induced by the roughness parameter $\alpha$.
+Notably, this excess vanishes in the homogeneous limit ($\alpha \to -\infty$), reducing \eqref{eq:decomp-intro} to the baseline case.
+
+This decomposition plays a central role in the thesis.
+It forms the theoretical foundation for a statistical test to detect heterogeneity: if $\Delta_\alpha \neq 0$, then the observed region departs from the homogeneous model, signaling the presence of texture.
+Each entropy measure offers a different sensitivity profile to such deviations, and their comparative behavior provides valuable insights into the textural structure of SAR imagery.
+
+This section details the closed-form expressions for $H$, $R_\lambda$, and $T_\lambda$ under $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ models.
+Shannon entropy derivations are taken from literature and adapted to our parametrisation, whereas the Rényi and Tsallis expressions are original contributions derived as part of this research (see Appendix&nbsp;\ref{sec-appendix-A}).
+At the end of the chapter, we summarize the common structure shared by all three measures and illustrate their convergence behavior.
+
+### Shannon Entropy
+
+The parametric representation of Shannon entropy for a system described by a continuous random variable is:
+\begin{equation}
+  \label{eq:entropy-sh}
+  H(Z) =   -\mathbb{E}\bigl[ \ln f(z)\bigr]=-\int_{-\infty }^\infty f(z)\ln f(z)\, \mathrm{d}z,
+\end{equation}
+where $f(\cdot)$ is the pdf that characterizes the distribution of the real-valued random variable $Z$.
+
+Using the definition in \eqref{eq:entropy-sh}, we derive closed-form expressions for the Shannon entropy of the $\Gamma_{\mathrm{SAR}}$ and $\mathcal{G}^0_I$ distributions under our parametrization.
+
+\textbf{Homogeneous case.} For the $\Gamma_{\mathrm{SAR}}$ distribution defined in \eqref{E:gamma1}, we obtain:
+\begin{equation}
+\label{eq:gamma-sh1}
+H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) = L - \ln L + \ln\Gamma(L) + (1 - L)\psi^{(0)}(L) + \ln \mu,
+\end{equation}
+where $\psi^{(0)}(\cdot)$ is the digamma function; $H(\Gamma_{\mathrm{SAR}})$ represents the baseline entropy of fully developed speckle.
+
+\textbf{Textured case.} In the case of the $\mathcal{G}^0_I$ distribution \eqref{E:gi02}, we adapt existing expressions reported by De A.
+Ferreira and Nascimento&nbsp;[-@Ferreira2020] to our parametrization, using the relation $\mu = -\gamma/(\alpha + 1)$.
+This yields:
 \begin{multline}
-\label{eq-HGammaSAR}
-H_\lambda\bigl(\Gamma_{\text{SAR}}(L, \mu)\bigr)
+\label{eq:GIO-Sh1}
+H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) =H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)\;+\;
+\Bigl[ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)
++\ln (-1-\alpha) \\
+-\ln\Gamma(L-\alpha) 
++\ln\Gamma(-\alpha)-L\Bigr].
+\end{multline}
+Equation \eqref{eq:GIO-Sh1} can be interpreted as:  
+$$
+H(\mathcal{G}^0_I)
+=
+\underbrace{H\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
+\hspace{1.8em} + \hspace{-1.0em}
+\underbrace{\Delta_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
+$$
+\begin{multline} 
+\text{where}\quad
+  \Delta_\alpha
+  =
+    (L-\alpha)\,\psi^{(0)}(L-\alpha)
+   -(1-\alpha)\,\psi^{(0)}(-\alpha)
+   +\ln(-1-\alpha)
+\\[-2pt]\hphantom{\Delta^{\mathrm{Sh}}_\alpha={}}
+   -\ln\Gamma(L-\alpha)+\ln\Gamma(-\alpha)-L.
+   \label{eq:GIO-Sh2}
+\end{multline}
+the extra term $\Delta_\alpha$ captures how much entropy increases due to texture (heterogeneity), caused by the roughness parameter $\alpha$.
+When $\alpha \to -\infty$ (fully developed speckle), the excess term tends to zero, and Equation \eqref{eq:GIO-Sh1} collapses to the homogeneous case in \eqref{eq:gamma-sh1}, i.e.,
+$$
+\lim_{\alpha \to -\infty} H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
+$$ 
+Appendix&nbsp;\ref{app:A1} provides a proof of this limiting behavior.
+<!-- This motivates our work: we check whether the \emph{excess} is statistically different from zero.  -->
+In practice, detecting heterogeneity is equivalent to testing whether $\Delta_\alpha$ is significantly different from zero.
+
+### Rényi Entropy
+For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
+\begin{equation}
+\label{E:entropy-R}
+R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+\end{equation}
+As $\lambda \to 1$, $R_\lambda(Z)$ reduces to $H(Z)$.
+
+Using&nbsp;\eqref{E:entropy-R}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and the $\mathcal{G}^0_I$ distributions.
+
+\textbf{Homogeneous case.} We find
+\begin{multline}
+\label{eq-GammaSAR-R}
+R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)
 = 
@@
 \Bigl[
-  -\lambda\,\ln\Gamma(L) \\  + \ln\Gamma\bigl(\lambda(L-1)+1\bigr)  - \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
-\Bigr]
-\end{multline}
-and
-\begin{multline}\label{eq-HGI0}
-H_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr)=\ln\mu-\ln L +\ln(-1 - \alpha)\\
-+ \frac{1}{\,1 - \lambda\,}
-\Bigl[
-   \lambda\bigl(
-      \ln\Gamma(L - \alpha)
-      -\ln\Gamma(-\alpha)
-      -\ln\Gamma(L)
-   \bigr)\\
-   +\ln\Gamma\bigl(\lambda(L - 1) + 1\bigr)
-   +\ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)\\
-   -\ln\Gamma\bigl(\lambda(L - \alpha)\bigr)
+  -\lambda\,\ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) -  \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
 \Bigr].
 \end{multline}
-@fig-plot presents the Rényi entropy of $\mathcal{G}^0_I$ as a function of $\mu$ for different $\alpha$ values.
-As $\alpha \to -\infty$, it approaches the Rényi entropy of $\Gamma_{\text{SAR}}$, which is aligned with the fact that $\Gamma_{\text{SAR}}$ is a limiting case of the $\mathcal{G}^0_I$ model.
 
-```{r fig-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="45%",  fig.pos="hbt", fig.cap="$H_{\\lambda}(\\mathcal{G}^0_I)$ converges to the $H_{\\lambda}(\\Gamma_{\\text{SAR}})$ when $\\alpha\\to-\\infty$, with $L=8$ and $\\lambda=0.8$.", fig.width=5, fig.height=4.0}
+\textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
+\begin{multline}  
+\label{eq-HGI0-R}  
+R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) \;+ \;\ln(-1 - \alpha)  
++ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
++ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) - \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
++ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
+\end{multline}
+ The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.
 
-entropy_renyi_gamma_sar <- function(L, mu, lambda) {
-  entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
-                (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
+Equation&nbsp;\eqref{eq-HGI0-R} can be read as:
+$$
+R_\lambda(\mathcal{G}^0_I)
+=
+\underbrace{R_\lambda \bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
+\hspace{1.8em} + \hspace{-1.0em}
+\underbrace{\Delta^R_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
+$$
+\begin{multline} 
+\text{where}\quad
+  \Delta^R_\alpha
+  =
+    \ln(-1 - \alpha)  
++ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr)  
++ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) \\
+- \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
++ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr],
+   \label{eq:GIO-R2}
+\end{multline}
+the excess term $\Delta^R_\alpha$ depends on the heterogeneity parameter $\alpha$, and  $\Delta^{\mathrm{R}}_\alpha\to0$ when
+$\alpha\to-\infty$, validating the decomposition, i.e.,
+$$
+\lim_{\alpha \to -\infty} R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
+$$ 
+Appendix&nbsp;\ref{app:A24} provides proof of this limiting behavior.
+
+<!-- When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero, -->
+<!--  so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.   -->
+<!-- and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero. -->
+<!--  Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
+As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
+-->
+<!-- This work's core idea is to check if this excess entropy is significantly different from zero. -->
+<!-- Fig.&nbsp;\ref{fig-convergence-renyi} illustrates this behaviour: as $\alpha$ decreases the colored curves of $R_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $R_\lambda(\Gamma_{\mathrm{SAR}})$, confirming the limiting behavior.
+-->
+
+### Tsallis entropy
+
+For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
+
+\begin{equation}
+\label{eq:tsallis}
+T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
+= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} dz \Bigr]. 
+\end{equation}
+In the limit $\lambda\to1$,
+  $T_\lambda(Z)\to H(Z)$, making Tsallis a
+  one-parameter generalisation of Shannon entropy.
+
+Using&nbsp;\eqref{eq:tsallis}, we derive closed-form expressions for the Tsallis entropy of the $\Gamma_{\mathrm{SAR}}$ and the $\mathcal{G}^0_I$ distributions.
+
+\textbf{Homogeneous case.} We find
+\begin{multline}
+\label{eq:gammasar-Tsallis}
+T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
+\frac{1}{\lambda-1}\Bigl\{1-
+\exp\Bigl[
+(1-\lambda)\ln\mu
++(\lambda-1)\ln L
++\ln\Gamma\bigl(\lambda(L-1)+1\bigr) \\
+-\lambda\ln\Gamma(L)
+-(\lambda(L-1)+1)\ln\lambda
+\Bigr]\Bigr\}.
+\end{multline}
+
+  \textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
+  \begin{multline}
+  \label{eq:GI0-Tsallis}
+  T_\lambda\bigl(\mathcal{G}^0_I(\mu,\alpha,L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)\;+\;\frac{1}{\lambda-1}\,
+  \exp\Bigl[
+  (1-\lambda)\ln\mu
+  +(\lambda-1)\ln L
+  +\ln\Gamma\bigl(\lambda(L-1)+1\bigr)
+  \\
+  -\lambda\ln\Gamma(L)
+  \Bigr] 
+  {}\times\Bigl\{1-
+  \exp\Bigl[
+  (1-\lambda)\ln(-\alpha-1)
+  +\lambda\ln\Gamma(L-\alpha)
+  -\lambda\ln\Gamma(-\alpha) \\
+  +\ln\Gamma\bigl(\lambda(1-\alpha)-1\bigr)
+  -\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
+  \Bigr]\Bigr\}.
+  \end{multline}
+
+  The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.
+
+  Equation&nbsp;\eqref{eq:GI0-Tsallis} can be interpreted as:
+  $$
+  T_\lambda(\mathcal{G}^0_I)
+  =
+  \underbrace{T_\lambda \bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
+  \hspace{1.8em} + \hspace{-1.0em}
+  \underbrace{\Delta^T_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
+  $$
+\begin{multline} 
+\text{where}\quad
+  \Delta^T_\alpha
+  =
+\frac{1}{\lambda-1}\,
+\exp\Bigl[
+(1-\lambda)\ln\mu
++(\lambda-1)\ln L
++\ln\Gamma\bigl(\lambda(L-1)+1\bigr)
+-\lambda\ln\Gamma(L)
+\Bigr] \\
+{}\times\Bigl\{1-
+\exp\Bigl[
+(1-\lambda)\ln(-\alpha-1)
++\lambda\ln\Gamma(L-\alpha)
+-\lambda\ln\Gamma(-\alpha) \\
++\ln\Gamma\bigl(\lambda(1-\alpha)-1\bigr)
+-\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
+\Bigr]\Bigr\},
+   \label{eq:GIO-T}
+\end{multline}
+the excess term $\Delta^T_\alpha$ depends on the heterogeneity parameter $\alpha$, and  $\Delta^T_\alpha\to0$ when
+$\alpha\to-\infty$, validating the decomposition, i.e.,
+$$
+\lim_{\alpha \to -\infty} T_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
+$$ 
+Appendix&nbsp;\ref{app:A33} provides proof of this limiting behavior.
+
+Figure&nbsp;\ref{fig:entropy-diagram} provides a conceptual overview of the decomposition structure of the differential entropy for the heterogeneous model $\mathcal{G}^0_I$.
+This entropy is expressed as the sum of a baseline term corresponding to the homogeneous $\Gamma_{\text{SAR}}$ distribution and an excess term $\Delta_\alpha$ that reflects the contribution of texture.
+The decomposition applies to the three entropy measures considered in this study: Shannon \eqref{eq:GIO-Sh1}, Rényi \eqref{eq-HGI0-R}, and Tsallis \eqref{eq:GI0-Tsallis}.
+In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.
+
+```{=latex}
+\begin{figure}[H]
+    \centering
+    \begin{tikzpicture}[
+    node distance=1.5cm,
+    entropy/.style={rectangle, rounded corners, draw=blue!60, fill=blue!10, thick, minimum width=3cm, align=center, font=\sffamily},
+    property/.style={rectangle, draw=orange!60, fill=orange!10, thick, minimum width=3cm, align=center, font=\sffamily},
+    arrow/.style={-Stealth, thick}
+    ]
+    % Tu diagrama aquí...
+    \node[entropy] (shannon) {Shannon \ $H(Z)$};
+    \node[entropy, right=of shannon] (renyi) {Rényi \ $R_\lambda(Z)$};
+    \node[entropy, right=of renyi] (tsallis) {Tsallis \ $T_\lambda(Z)$};
+
+    \node[property, below=2cm of renyi] (decomp) {Entropy Decomposition\\[0.5ex]
+    $\text{Entropy}\bigl(\mathcal{G}^{0}_{I}\bigr)
+\;=\;
+\text{Entropy}\bigl(\Gamma_{\mathrm{SAR}}\bigr)
+\;+\;
+\Delta_{\alpha}$};
+
+    \node[property, below left=1.1cm of decomp, align=center] (baseline) {Homogeneous Baseline\\($\Gamma_{\text{SAR}}$)};
+    \node[property, below right=1.1cm of decomp, align=center] (texture) {Texture-Induced Excess\\($\Delta_{\alpha}$)};
+
+    \node[property, below=1.8cm of texture, align=center] (limits) {Vanishing Excess\\ $\Delta_\alpha \to 0$ as $\alpha\to -\infty$};
+    \node[property, below=1.8cm of baseline, align=center] (test) {Statistical Test\\ $\Delta_\alpha \neq 0?$};
+
+    \draw[arrow] (shannon.south) |- (decomp);
+    \draw[arrow] (renyi.south) -- (decomp);
+    \draw[arrow] (tsallis.south) |- (decomp);
+
+    \draw[arrow] (decomp.south west) -- (baseline.north);
+    \draw[arrow] (decomp.south east) -- (texture.north);
+
+    \draw[arrow] (texture.south) -- (limits.north);
+    \draw[arrow] (baseline.south) -- (test.north);
+    \draw[arrow] (texture.south west) -- (test.east);
+    \end{tikzpicture}
+    \caption{Conceptual diagram of entropy decomposition.}
+    \label{fig:entropy-diagram}
+\end{figure}
+```
+
+To conclude this section, we illustrate the convergence behavior of each entropy measure.
+
+Figures&nbsp;[-@fig-shannon-convergence-s]--[-@fig-tsallis-convergence-t] illustrate the Shannon ($H$), Rényi ($R_\lambda$), and Tsallis ($T_\lambda$) entropies for the $\mathcal{G}^0_I$ model under different texture levels ($\alpha$) and numbers of looks ($L$).
+In every case the coloured dashed curves converge to the solid black baseline of the homogeneous $\Gamma_{\mathrm{SAR}}$ distribution as $\alpha\to-\infty$, confirming the limiting behavior.
+
+For the Shannon entropy (@fig-shannon-convergence-s), when $L = 5$ the entropy curves for different $\alpha$ values are more concentrated.
+This is due to the higher speckle noise present in a low number of looks, which dominates the uncertainty and masks texture effects.
+When $L = 18$, speckle is reduced and the entropy better reflects texture variation, resulting in more separated curves.
+
+In the case of Rényi entropy (@fig-renyi-convergence-r), for $\lambda = 0.6$ and $\lambda = 0.9$, the general shape and separation of the curves are similar.
+However, increasing $L$ leads to a slight decrease in entropy values across all $\alpha$, consistent with reduced speckle.
+The convergence pattern toward the Gamma baseline remains stable in both settings.
+
+For Tsallis entropy (@fig-tsallis-convergence-t), the separation between curves is most noticeable for $\lambda = 0.6$ and $L = 5$, where texture has more influence.
+When $\lambda$ increases to $0.9$ or when $L$ is increased, the curves become more compact and approach the Gamma entropy faster, indicating lower sensitivity to texture variation and confirming that $\lambda$ controls the influence of the tail behavior.
+
+```{r fig-shannon-convergence-s, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="95%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+
+entropy_gamma_sar <- function(L, mu) {
+  L - log(L) + lgamma(L) + (1 - L) * digamma(L) + log(mu)
+}
+
+entropy_gI0 <- function(mu, alpha, L) {
+  term1 <- L - log(L) + lgamma(L) + (1 - L) * digamma(L) + log(mu) 
+  term2 <- -L - lgamma(L - alpha) + (L - alpha) * digamma(L - alpha) - 
+           (1 - alpha) * digamma(-alpha) + log(-1 - alpha) + lgamma(-alpha)
+  entropy <- term1 + term2
   return(entropy)
@@
 
-entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
-  if (lambda <= 0 || lambda == 1) {
-    stop("Lambda must be greater than 0 and not equal to 1.")
+plot_shannon <- function(L) {
+  mu <- seq(0.1, 10, length.out = 500)
+  alphas <- c(-2, -6, -20, -1000)
+  alpha_labels <- c(expression(alpha == -2), expression(alpha == -6), expression(alpha == -20), expression(alpha == -1000))
+
+  muEntropy <- data.frame()
+  for (alpha in alphas) {
+    entropies_GI0 <- entropy_gI0(mu, alpha, L)
+    muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
   }
 
-  gamma <- -mu * (alpha + 1)
-  if (any(gamma <= 0)) {
-    stop("Gamma must be positive. Check the values of mu and alpha.")
+  muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"))
+  entropies_gamma <- entropy_gamma_sar(L, mu)
+  Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)
+
+  ggplot() +
+    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
+    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) + #linewidth = 2, alpha=.7
+    scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
+    #scale_color_manual(values = pal_npg()(4), labels = alpha_labels) +
+    labs(color = "Roughness", x = expression(mu), y = "Shannon Entropy") +
+    annotate("text",
+           x = max(mu) + 0.4,
+           y = max(Entropy_gamma$Entropy_Gamma) - 0.3,
+           label = TeX("${italic(H)}(\\Gamma_{\\tiny{SAR}})$"),
+           hjust = 1, vjust = 1, size = 3.0) +
+    theme_minimal(base_family = "serif") +
+    theme(
+      legend.position = "bottom",
+      plot.title = element_text(hjust = 0.5, size = 10),
+      panel.grid.minor = element_blank()
+    ) +
+    coord_cartesian(xlim = c(0, 10), ylim = c(-1, 6)) +
+    ggtitle(bquote(L == .(L)))
 }
 
+# Graficar para dos condiciones
+p1 <- plot_shannon(5)
+p2 <- plot_shannon(18)
+
+(p1 | p2) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+```
+
+```{r fig-renyi-convergence-r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="95%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+# fig.fullwidth = TRUE, out.width="95%"
+
+entropy_renyi_gamma_sar <- function(L, mu, lambda) {
+  (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) + 
+     (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mu / L)
+}
+
+entropy_GI0_renyi <- function(alpha, mu, L, lambda) {
+  gamma <- -mu * (alpha + 1)
   a <- lambda * (L - 1) + 1
@@
 
-  if (any(a <= 0) || any(b <= 0) || any(ab_sum <= 0)) {
-    stop("Arguments of the Gamma functions must be positive. Check the values of lambda, L, and alpha.")
-  }
-
   term1 <- log(gamma / L)
-
   term2 <- lambda * (lgamma(L - alpha) - lgamma(-alpha) - lgamma(L))
-
   term3 <- lgamma(a)
@@
 
-  numerator <- term2 + term3 + term4 - term5
-
-  entropy <- term1 + numerator / (1 - lambda)
-
+  entropy <- term1 + (term2 + term3 + term4 - term5) / (1 - lambda)
   return(entropy)
@@
 
-L <- 8
-alphas <- c(-3, -8, -20, -1000)
-alpha_labels <- c(expression(italic(alpha) == -3), 
-                  expression(italic(alpha) == -8), 
-                  expression(italic(alpha) == -20), 
-                  expression(italic(alpha) == -1000))
-
+plot_renyi <- function(L, lambda) {
   mu <- seq(0.1, 10, length.out = 500)
-lambda <- 0.8  # Fixed lambda
+  alphas <- c(-2, -6, -20, -1000)
+  alpha_labels <- c(expression(alpha == -2), expression(alpha == -6), expression(alpha == -20), expression(alpha == -1000))
 
   muEntropy <- data.frame()
-
   for (alpha in alphas) {
@@
 
-muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"), value.name = "Entropy")
-
+  muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"))
   entropies_gamma <- entropy_renyi_gamma_sar(L, mu, lambda)
-
   Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)
 
-Entropy_gamma.molten <- melt(Entropy_gamma, id.vars = "mu", value.name = "Entropy_Gamma")
+ggplot() +
+  geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
+  geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) +
+  scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
+  labs(color = "Roughness", x = expression(mu), y = "Rényi Entropy") +
+  annotate("text",
+           x = max(mu) + 0.4,
+           y = max(Entropy_gamma$Entropy_Gamma) - 0.3,
+           label = TeX("${italic(R)}_{\\lambda}(\\Gamma_{\\tiny{SAR}})$"),
+           hjust = 1, vjust = 1, size = 3.1) +
+  theme_minimal(base_family = "serif") +
+  theme(
+    legend.position = "bottom",
+    plot.title = element_text(hjust = 0.5, size = 10),
+    panel.grid.minor = element_blank()
+  ) +
+  coord_cartesian(xlim = c(0, 10), ylim = c(-1, 6)) +
+  ggtitle(bquote(L == .(L) ~ ", " ~ lambda == .(lambda)))
+}
+
+p1 <- plot_renyi(5, 0.6)
+p2 <- plot_renyi(18, 0.9)
+
+(p1 | p2) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+```
+
+```{r fig-tsallis-convergence-t, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="95%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+# fig.fullwidth = TRUE, out.width="95%"
+
+# Entropías de Tsallis (Gamma SAR y GI0)
+tsallis_gammasar_log <- function(mu, L, lambda) {
+  (1 - exp((1 - lambda)*log(mu) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) /
+    (lambda - 1)
+}
+
+tsallis_gi0 <- function(alpha, mu, L, lambda) {
+  (1 - exp((1 - lambda)*log(mu) +
+             (lambda - 1)*log(L) +
+             (1 - lambda)*log(-alpha - 1) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) +
+             lambda*(lgamma(L - alpha) - lgamma(-alpha)) +
+             lgamma(lambda*(1 - alpha) - 1) -
+             lgamma(lambda*(L - alpha)))) / (lambda - 1)
+}
+
+plot_tsallis <- function(L, lambda) {
+  mu <- seq(0.1, 10, length.out = 500)
+  alphas <- c(-2, -6, -20, -1000)
+  alpha_labels <- c(expression(alpha == -2), expression(alpha == -6), expression(alpha == -20), expression(alpha == -1000))
+
+  muEntropy <- data.frame()
+  for (alpha in alphas) {
+    entropies_GI0 <- tsallis_gi0(alpha, mu, L, lambda)
+    muEntropy <- rbind(muEntropy, data.frame(mu = mu, Entropy = entropies_GI0, alpha = as.factor(alpha)))
+  }
+
+  muEntropy.molten <- melt(muEntropy, id.vars = c("mu", "alpha"))
+  entropies_gamma <- tsallis_gammasar_log(mu, L, lambda)
+  Entropy_gamma <- data.frame(mu, Entropy_Gamma = entropies_gamma)
 
   ggplot() +
+    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
+    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) +
+    scale_color_manual(values = pal_lancet()(4), labels = alpha_labels) +
+    labs(color = "Roughness", x = expression(mu), y = "Tsallis Entropy") +
+    annotate("text",
+             x = max(mu) + 0.5,
+             y = max(Entropy_gamma$Entropy_Gamma) - 0.4,
+             label = TeX("${italic(T)}_{\\lambda}(\\Gamma_{\\tiny{SAR}})$"),
+             hjust = 1, vjust = 1, size = 3.1) +
+    theme_minimal(base_family = "serif") +
+    theme(
+      legend.position = "bottom",
+      plot.title = element_text(hjust = 0.5, size = 10),
+      panel.grid.minor = element_blank()
+    ) +
+    coord_cartesian(xlim = c(0, 10), ylim = c(-1, 6)) +
+    ggtitle(bquote(L == .(L) ~ ", " ~ lambda == .(lambda)))
+}
 
-  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = Entropy_Gamma), color = "black", 
-            linetype = "solid", linewidth = 1.5) +
-
-  geom_line(data = muEntropy.molten, aes(x = mu, y = Entropy, color = alpha), 
-            linetype = "longdash", linewidth = 1) +
-
-  annotate("text", x = max(mu) + 0.2, y = max(Entropy_gamma.molten$Entropy_Gamma), 
-           label = TeX("${italic(H)}_{\\lambda}(\\Gamma_{\\tiny{SAR}})$"), 
-           vjust = 1.6, hjust = 0.8, color = "black",linewidth = 0.2) +
-
-  theme_minimal() +
-
-  scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
- # scale_color_manual(values = brewer.pal(4, "Dark2"), labels = alpha_labels) +
-  # Labels and titles
-  labs(color = "Roughness", 
-       x = expression(mu), 
-       y = "Rényi Entropy", 
-       linetype = NULL) +
-
-  theme(text = element_text(family = "serif"),
-        legend.position = "bottom") +
-
-  coord_cartesian(xlim = c(0, 10), ylim = c(min(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma), 
-                                            max(muEntropy.molten$Entropy, Entropy_gamma.molten$Entropy_Gamma) + 0.5))
-
+p1 <- plot_tsallis(5, 0.6)
+p2 <- plot_tsallis(18, 0.9)
+(p1 | p2) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
 ```
 
-For $\lambda \to 1$, this expression converges to the Shannon entropy. As we will see later, this property can lead to improved performance for heterogeneity detection compared to Shannon entropy.
+## ORDER STATISTICS AND NONPARAMETRIC ESTIMATORS
 
-## Main Section 1
+Parametric estimation of entropy begins by assuming a family for $f(z)$ (e.g.
+exponential, Gaussian).
+The data are used to estimate the parameters of this family (for example, sample mean and variance for a normal).
+These parameter estimates are then substituted into the corresponding analytical expression for entropy $H(f)$.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aliquam ultricies lacinia euismod.
-Nam tempus risus in dolor rhoncus in interdum enim tincidunt.
-Donec vel nunc neque.
-In condimentum ullamcorper quam non consequat.
-Fusce sagittis tempor feugiat.
-Fusce magna erat, molestie eu convallis ut, tempus sed arcu.
-Quisque molestie, ante a tincidunt ullamcorper, sapien enim dignissim lacus, in semper nibh erat lobortis purus.
-Integer dapibus ligula ac risus convallis pellentesque.
+While parametric methods can be very efficient if the assumption is correct, they suffer when the true distribution deviates from the chosen model.
+In such cases, parametric estimates of entropy can be heavily biased or misleading.
 
-Let $\bm{Z}$
+Nonparametric estimation, by contrast, tries to approximate $H(f)$ without assuming any specific form for the underlying distribution.
+A common approach is the plug-in method, where the density $\hat{f}(z)$ is first estimated from the data, using tools like histograms or kernel methods.
+This estimated density is then used in the entropy formula.
+However, estimating the density accurately can be difficult, especially when the data are limited or high-dimensional.
 
+An alternative route, which we pursue here, is to avoid explicit density estimation and instead use properties of the sorted sample (order statistics) to estimate entropy.
+This spacing-based approach is appealing because it directly targets the entropy functional, often achieving consistency and good convergence rates without the intermediate step of full density estimation.
+
+In the following, we introduce the concept of order statistics and sample spacings, and derive how the entropy integral can be transformed into a convenient form involving the quantile function.
+This will set the stage for constructing entropy estimators based on sample spacings.
+
+\subsection{Order Statistics and Sample Spacings}
+
+Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed (i.i.d) random sample of size $n$ from drawn from a continuous distribution with cumulative distribution function (CDF) $F(z)$, let $Z_{(1)} \le Z_{(2)} \le \cdots \le Z_{(n)}$ denote the ordered sample, known as the order statistics.
+
+Sample spacings refer to the differences between ordered observations.
+More generally, an $m$-spacing is defined as the difference between two order statistics that are $m$ positions apart in the sorted sample.
+For instance, a 1-spacing corresponds to the gap between consecutive order statistics: $Z_{(i+1)} - Z_{(i)}$.
+In general, an $m$-spacing can be written as $Z_{(i+m)} - Z_{(i)}$, for indices $i$ such that $i + m \le n$.
+
+These spacings are inversely related to the underlying density: where the density is high, observations tend to cluster and spacings are small; where the density is low, spacings are typically larger.
+This relationship forms the basis for using spacings to estimate the density function or related functionals like entropy.
+
+A key probabilistic property that supports this idea arises when considering the transformed values $U_i = F(Z_{(i)})$, which follow the order statistics of a uniform distribution on $[0,1]$.
+For $i = 1, \dots, n-1$, the expected spacing in the transformed domain is:
+\begin{equation*}
+  \mathbb{E}[F(Z_{(i+1)}) - F(Z_{(i)})] = \frac{1}{n+1}.
+\end{equation*}
+
+This result suggests that, under the true CDF, the transformed spacings are uniformly spread in expectation.
+Consequently, a simple density estimate around the point $Z_{(i)}$ can be motivated by the approximation:
 $$
-\int_{A_i}{\lambda (\pmb{\mu})}
-$$ {#eq-pmb}
+f(Z_{(i)}) \approx \frac{\text{mass}}{\text{length}} \approx \frac{1/(n+1)}{Z_{(i+1)} - Z_{(i)}},
+$$
+where $1/(n+1)$ serves as an estimate of the probability mass between $Z_{(i)}$ and $Z_{(i+1)}$.
 
+### Nonparametric Estimators for Shannon Entropy {#sec:sh_est}
+
+Let $F^{-1}(p)$ denote the quantile function (inverse CDF) of the distribution. We use $Q(p)$ as shorthand for $F^{-1}(p)$, so $Q:(0,1)\to \mathbb{R}$ satisfies $Q(p) = z$ if and only if $F(z) = p$.
+
+Since $F(z)$ is monotonic, $Q(p)$ is differentiable wherever $f(z)$ is positive, with derivative $Q'(p) = \frac{d}{dp}F^{-1}(p)$. By the inverse function theorem, $Q'(p) = \frac{1}{f(Q(p))}$.
+
+Starting from the definition of Shannon entropy in Equation \eqref{eq:entropy-sh}, a change of variables $p = F(z)$ can be applied.
+When $z = Q(p)$, it follows that $dz = Q'(p)\,dp$.
+Substituting into the integral:
+\begin{align*}
+  H(Z)
+  &= -\int_{0}^{1} f(Q(p))\ln f(Q(p))\cdot Q'(p)\,dp \\
+  &= -\int_{0}^{1} \ln f(Q(p))\,dp.
+\end{align*}
+
+Now using $f(Q(p)) = 1/Q'(p)$, we have $\ln f(Q(p)) = -\ln Q'(p)$. Thus:
+\begin{equation}
+  H(Z) = \int_{0}^{1} \ln Q'(p)\,dp = \int_{0}^{1} \ln \left(\frac{d}{dp}F^{-1}(p)\right) dp.
+\end{equation}
+
+This is the foundation of spacing estimators: entropy as the integral of the log quantile derivative.
+
+In practice, we estimate $Q'(p)$ using order statistics. Consider:
+\begin{equation}
+  Q'(p) \approx \frac{n+1}{2m}(Z_{(i+m)} - Z_{(i-m)}), \quad m \le i \le n-m.
+\end{equation}
+
+By taking logarithms and averaging over $i$, Vasicek’s estimator&nbsp;[-@vasicek1976test] becomes:
+\begin{equation}
+\label{E:Vasi}
+  \widehat{H}_{\text{V}}(\bm{Z}) = \frac{1}{n} \sum_{i=1}^{n} \ln\left[ \frac{n}{2m}(Z_{(i+m)} - Z_{(i-m)}) \right].
+\end{equation}
+
+Vasicek showed that under regularity conditions ($m \to \infty$, $m/n \to 0$), $\widehat{H}_{\text{V}} \to H(f)$ in probability.
+
+Nonparametric estimators using order statistics and spacings, such as Vasicek’s m-spacing estimator, provide a flexible alternative to model-based entropy estimation.
+By converting the entropy integral into a quantile-based form (see Appendix&nbsp;\ref{app:Vasicek}), these estimators offer robust, consistent estimation of Shannon entropy without requiring explicit density estimation.
+
+Subsequent extensions and refinements (not detailed here) further improve bias, variance, and performance at the boundaries, forming a robust toolkit for entropy estimation in continuous distributions.
+
+We consider the following entropy estimators variants, as discussed by Cassetti et al.&nbsp;[-@Cassetti2022].
+
+Van Es&nbsp;[-@VanEs1992] proposed a new estimator of entropy given by:
+ \begin{equation}
+\label{E:VanEs}
+	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\ln\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]	+\sum_{k=m}^n\frac{1}{k}+\ln\frac{m}{n+1}.
+\end{equation}
+Under some conditions, Van Es proved asymptotic normality of this estimator.
+
+Ebrahimi et al.&nbsp;[-@Ebrahimi1994]  adjusted the weights of Vasicek's estimator, in order to take into account the fact that the differences are truncated around the smallest and the largest data points.
+ Specifically, $Z_{(i+m)}-Z_{(i-m)}$ is substituted with  $Z_{(i+m)}-Z_{(1)}$ when $i \leq m$ and $Z_{(i+m)}-Z_{(i-m)}$ is replaced by $Z_{(n)}-Z_{(i-m)}$ when $i \geq n-m+1$.
+Their estimator is given by:
+  \begin{equation}
+	\label{E:Ebrahimi}
+  \widehat{H}_{\text{E}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{c_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+  \end{equation} where $$
+  c_i=\begin{cases}1+(i-1) / m & \text { if } \quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m,\\ 1+(n-i) / m & \text { if }\quad n-m+1 \leq i \leq n.\end{cases}
   $$
-\int_{A_i}{\lambda (\mathbf{x})} + x
-$$ {#eq-mathbf}
 
-### Subsection 1
+Correa&nbsp;[-@correa1995new] suggested another modification of Vasicek's estimator. 
+In estimation the density $f$ of $F$ in the interval $\left(Z_{(i-m)}, Z_{(i+m)}\right)$ he used a local linear model based on $2 m+1$ points: $F\left(Z_{(j)}\right)=a+b Z_{(j)}+\varepsilon, j=m-i, \ldots, m+i$.
+This yields a following estimator:
+  \begin{equation}
+	\label{E:Correa}
+  \widehat{H}_{\text{C}}(\bm{Z})=-\frac{1}{n} \sum_{i=1}^n \ln \frac{\sum_{j=i-m}^{i+m}(j-i)\left(Z_{(j)}-\overline{Z}_{(i)}\right)}{n\sum_{j=i-m}^{i+m}\left(Z_{(j)}-\overline{Z}_{(i)}\right)^2},
+  \end{equation} 
+where $\overline{Z}_{(i)}=(2 m+1)^{-1}\sum_{j=i-m}^{i+m} Z_{(j)}$, $m<\frac{n}{2}$, $Z_{(i)}=Z_{(1)}$ for $i<1$ and $Z_{(i)}=Z_{(n)}$ for $i>n$.
+Based on simulations, he showed that his estimator has a smaller mean square error than Vasicek's approach.
 
-Nunc posuere quam at lectus tristique eu ultrices augue venenatis.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat.
-Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper.
-Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue.
-In hac habitasse platea dictumst.
+Noughabi and Arghami&nbsp;[-@rohtua] modify the coefficients of Ebrahimi et al.&nbsp;[-@Ebrahimi1994] as: 
+\begin{equation}
+\label{E:rohtua}
+\widehat{H}_{\text{N}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{a_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+\end{equation}
+where
+$$
+a_i=\begin{cases}
+1 & \text { if } \quad 1 \leq i \leq m, \\
+2 & \text { if } \quad m+1 \leq i \leq n-m, \\
+1 & \text { if } \quad n-m+1 \leq i \leq n,
+\end{cases}
+$$
+and $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$ and $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.
 
-```{r}
-library(tidyverse)
-library(palmerpenguins)
-```
+Al-Omari&nbsp;[-@IbrahimAlOmari2014] suggested the following estimator:
+	\begin{equation}
+\label{E:AO}
+  \widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \ln \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
+ \end{equation}
+	where $$
+  \omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
+  $$ in which $Z_{(i-m)}=Z_{(1)}$ for $i \leq m$, and
+  $Z_{(i+m)}=Z_{(n)}$ for $i \geq n-m$.
 
-```{r}
-#| fig-cap: "primera grafica"
-#| out-width: "12cm"
-penguins %>%
-  drop_na() %>%
-  ggplot(
-    aes(x = species, y =  body_mass_g, fill = sex)
-  ) +
-  geom_boxplot()
+These estimators are asymptotically consistent, i.e., they converge in
+probability to the true value when $m,n\rightarrow\infty$ and
+$m/n\rightarrow0$.
 
-```
+\subsection{A Nonparametric Estimator of Rényi Entropy}
+\label{ssec:renyi_estimator}
 
-```{r}
-peso <- mean(penguins$body_mass_g, na.rm = TRUE)
-```
+The Rényi entropy of order $\lambda > 0$, with $\lambda \neq 1$, is defined in Equation \eqref{E:entropy-R} as a generalization of Shannon entropy.
+It introduces an adjustable parameter $\lambda$ that controls the sensitivity of the entropy measure to the tails of the distribution.
 
-El peso es\> `r round(peso,2)`
+To facilitate nonparametric estimation, the expression in Equation \eqref{E:entropy-R} can be reformulated using the quantile function $Q(p) = F^{-1}(p)$, with $p \in (0,1)$.
+Applying the change of variable $z = Q(p)$ and noting that $f(Q(p)) = Q'(p)$ yields:
+\begin{align*}
+\int f^\lambda(z)\,dz
+&= \int_0^1 [f(Q(p))]^\lambda \cdot Q'(p)\,dp \\
+&= \int_0^1 [Q'(p)]^{1 - \lambda}\,dp.
+\end{align*}
+Substituting this into the original expression gives the quantile-based representation:
+\begin{equation}
+R_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_0^1 [Q'(p)]^{1 - \lambda}\,dp \right).
+\label{eq:renyi-quantile}
+\end{equation}
 
-```{r}
-#| label: fig-charts
-#| fig-cap: "Charts"
-#| fig-subcap: 
-#|   - "Cars"
-#|   - "Pressure"
-#| layout-ncol: 2
+A nonparametric estimator can be constructed by approximating the quantile derivative $Q'(p)$ using $m$-spacings, following the methodology proposed by Al-Labadi, Chu and Xu&nbsp;[-@AlLabadi2024].
+Given a sample $\bm{Z} = (Z_1, \dots, Z_n)$ drawn i.i.d.\ from $F$, let $Z_{(1)} \le \dots \le Z_{(n)}$ denote the order statistics.
+For a spacing parameter $m \in \{1, \dots, \lfloor n/2 \rfloor\}$, define the boundary-corrected $m$-spacing as:
+$$
+D_{i,m} = Z_{(i+m)} - Z_{(i-m)}, \qquad
+Z_{(i-m)} := Z_{(1)} \text{ if } i \le m,\quad
+Z_{(i+m)} := Z_{(n)} \text{ if } i \ge n - m.
+$$
 
-plot(cars)
-plot(pressure)
-```
+To mitigate boundary bias, the position-dependent correction factor introduced by Ebrahimi et al.&nbsp;[-@Ebrahimi1994] is used:
+$$
+  c_i =
+  \begin{cases}
+    \dfrac{m+i-1}{m}, & 1\le i\le m,\\[4pt]
+    2,                & m+1\le i\le n-m,\\[4pt]
+    \dfrac{n+m-i}{m}, & n-m+1\le i\le n.
+  \end{cases}
+$$
 
-# Tablas
+The corresponding $m$-spacing density estimate at the $i$th order statistic is given by:
+\begin{equation}
+\widehat{f}_n(Z_{(i)}) = \frac{c_i\,m/n}{D_{i,m}}, \qquad i=1,\dots,n.
+\label{eq:renyi-density-est}
+\end{equation}
 
-| Nombre | **Apellido** | ***Telefono*** |
-|--------|--------------|----------------|
-| Maria  | ss           | 45             |
-| rosa   | sss          | 67             |
+Substituting \eqref{eq:renyi-density-est} into the quantile form \eqref{eq:renyi-quantile} and approximating the integral by a Riemann sum yields the nonparametric plug-in estimator for Rényi entropy:
+\begin{equation}
+\widehat{R}_\lambda(\bm{Z})
+= \frac{1}{1 - \lambda}
+\ln \left[
+\frac{1}{n} \sum_{i=1}^{n}
+\left(
+\frac{c_i\,m/n}{Z_{(i+m)} - Z_{(i-m)}}
+\right)^{\lambda - 1}
+\right].
+\label{eq:Renyi-spacing-estimator}
+\end{equation}
 
-: MI primera tabla
+This estimator extends the $m$-spacing approach originally introduced for Shannon entropy to the broader Rényi family, enabling consistent nonparametric estimation without requiring direct estimation of the density function.
 
-```{r}
-#| tbl-cap: "tabla1"
-#| label: "tbl-ping"
-penguins %>% drop_na()%>% group_by(species, sex) %>%
-  summarise(peso = mean(body_mass_g))%>%
-  knitr::kable(col.names = c("Especie", "sexo", "peso"))
-```
+\subsection{A Nonparametric Estimator of Tsallis Entropy}
+\label{subsec:tsallis-spacing}
+Following the approach of Vasicek&nbsp;[-@vasicek1976test] and Ebrahimi et al.&nbsp;[-@Ebrahimi1994] for Shannon entropy, and the methodology for Rényi entropy proposed by Al-Labadi, Chu and Xu&nbsp;[-@AlLabadi2024], we derive a nonparametric estimator for Tsallis entropy.
 
-Como se muetsra en la tabla @tbl-ping.
+A detailed derivation of this estimator, including the quantile-based transformation and spacing approximation, is provided in Appendix&nbsp;\ref{app:tsallis_1}.
 
-| nombre | apellido |
-|--------|----------|
-| diana  | Alpala   |
-| rosa   | Alpala   |
+The definition of Tsallis entropy is given in Equation \eqref{eq:tsallis}, this expression can be reformulated using the quantile function $Q(p)=F^{-1}(p)$, defined for $p\in(0,1)$.
+Since $f(Q(p)) = Q'(p)$, the expectation in \eqref{eq:tsallis} becomes
+$$
+  \mathbb{E}\bigl[f^{\lambda-1}(Z)\bigr] 
+  = \int_{0}^{1} \bigl(Q'(p)\bigr)^{1-\lambda}\,dp,
+$$
+leading to the alternative representation:
+\begin{equation}
+  T_\lambda(Z)
+  =\frac{1}{\lambda-1}
+     \left\{
+       1-\int_{0}^{1}\bigl(Q'(p)\bigr)^{1-\lambda}\,dp
+     \right\}.
+  \label{eq:Tsallis-quantile}
+\end{equation}
 
-: nueva tabla
+To estimate $T_\lambda(Z)$ nonparametrically, consider an i.i.d.\ sample $Z_1,\dots,Z_n\sim F$, with associated order statistics $Z_{(1)}\le\cdots\le Z_{(n)}$.
+Let $m\in\{1,\dots,\lfloor n/2\rfloor\}$ be an integer spacing parameter.
+For each $i=1,\dots,n$, define the $m$-spacing
+$$
+   D_{i,m} \;=\; Z_{(i+m)}-Z_{(i-m)},
+   \quad
+   Z_{(i-m)}:=Z_{(1)} \text{ if } i\le m,
+   \quad
+   Z_{(i+m)}:=Z_{(n)} \text{ if } i\ge n-m.
+$$
+Since the empirical distribution satisfies $F_n(Z_{(i\pm m)})=\tfrac{i\pm m}{n}$, the length of the interval is $\frac{2m}{n}$, and Vasicek's plug-in estimator of the density is given by
+$$
+   \tilde f_{i,m}\;=\;\frac{n}{2m}\,D_{i,m}^{-1}.
+$$
+To reduce boundary bias, Ebrahimi et al.&nbsp;[-@Ebrahimi1994] proposed a position-dependent correction factor
+$$
+  c_i \;=\;
+    \begin{cases}
+      1+\dfrac{i-1}{m},      & 1\le i\le m,\\[6pt]
+      2,                     & m+1\le i\le n-m,\\[6pt]
+      1+\dfrac{n-i}{m},      & n-m+1\le i\le n,
+    \end{cases}
+$$
+resulting in the boundary-corrected $m$-spacing density estimator
+\begin{equation}
+  \widehat f_n\bigl(Z_{(i)}\bigr)
+  \;=\;
+  \frac{c_i\,m/n}{D_{i,m}},
+  \qquad i=1,\dots,n.
+  \label{eq:density-spacing}
+\end{equation}
 
-```{r table-example, results="asis"}
-library(knitr)
-library(kableExtra)
-
-# Creamos un data.frame sencillo:
-dt <- data.frame(
-  Id   = 1:5,
-  Name = c("Alice", "Bob", "Charlie", "Diana", "Ethan"),
-  Score = c(90, 85, 88, 92, 80)
-)
-
-kable(dt, format = "latex", booktabs = TRUE, caption = "Mi tabla") %>%
-  kable_styling(full_width = FALSE) #%>%
-  #footnote(
-  #  general = " Source: Author.",  # 
-   # general_title = ""                      # Deja en blanco para no mostrar "Note:"
-    #footnote_as_chunk = TRUE,
-    #threeparttable = TRUE
-  #)
-
-```
-
-<!-- ```{=latex} -->
-<!-- \begin{figure} -->
-<!--   \caption{My figure caption} -->
-<!--   \centering -->
-<!--   \includegraphics{Chapters/Figs/elephant.png} -->
-<!--   \caption*{Source: My source} -->
-<!-- \end{figure} -->
-<!-- ``` -->
-
-<!-- ::: {#fig-1} -->
-
-<!-- ```{r} -->
-<!-- #| echo: false -->
-<!-- plot(1:10) -->
-<!-- ``` -->
-
-<!-- Source: My source -->
-
-<!-- My figure caption. -->
-
-<!-- ::: -->
-
-<!-- See @fig-1. -->
-
-```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}
-
-SAR_data <- data.frame(
-  Site = c("Rotterdam", "Coast of Jalisco", "Illinois-Region 1", "Illinois-Region 2"),
-  Mission = c("TerraSAR-X", "Sentinel-1B", "Sentinel-1B", "Sentinel-1B"),
-  Mode = c("HS", "GRD EW", "GRD SM", "GRD SM"),
-  Band = c("X", "C", "C", "C"),
-  Polarization = c("HH", "VV", "VV", "VV"),
-   Size = c("$\\bm{512}\\times512$", "$\\textbf{512}\times512$", "$512\times512$", "$1024\times1024$"),
-  L = c(1, 18, 36, 36),
-   Resol = c("$0.85/0.85$", "$40/40$", "$10/10$", "$10/10$"),
-  Date = c("06-12-2018", "29-08-2021", "30-06-2020", "28-08-2021")
-)
-
-# colnames(SAR_data) <- c(
-#   "\\textbf{Site}",
-#   "\\textbf{Mission}",
-#   "\\textbf{Mode}",
-#   "\\textbf{Band}",
-#   "\\textbf{Polarization}",
-#   "\\textbf{Size}",
-#   "$\\bm{L}$",                 # <- Aquí sí quieres modo matemático (para la L)
-#   "\\textbf{Resolution}",
-#   "\\textbf{Acquisition Date}"
-# )
-
-SAR_data[] <- lapply(SAR_data, function(x) {
-  if (is.numeric(x)) {
-    if (all(x %% 1 == 0)) {
-      formatted_numbers <- sprintf("$%d$", x)
-    } else {
-      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
-    }
-    return(formatted_numbers)
-  } else {
-    return(x)
-  }
-})
-kable(
-  SAR_data,
-  caption = "Parameters of selected SAR images.",
-  format = "latex",
-  booktabs = TRUE,
-  align = "ccccccccc",
-  escape = FALSE,      # Importante para que interprete el LaTeX
-  digits = 2,
-  label = "table_param",
-  col.names = c(
-    "\\textbf{Site}", 
-    "Mission", 
-    "Mode", 
-    "Band", 
-    "Polarization", 
-    "Size", 
-     "$\\bm{L}$",              # L en modo matemático y negrita
-    "Resol",  # Ejemplo de texto en negrita con [m]
-    "Date"
-  )
-) %>%
-  row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", font_size = 12) %>%
-  kable_styling(full_width = TRUE) %>%
-  column_spec(1, width = "3.5cm") %>%
-  column_spec(2, width = "3cm") %>%
-  column_spec(3, width = "2cm") %>%
-  column_spec(4, width = "1cm") %>%
-  column_spec(5, width = "2cm") %>%
-  column_spec(6, width = "2.5cm") %>%
-  column_spec(7, width = "1cm") %>%
-  column_spec(8, width = "3cm") %>%
-  column_spec(9, width = "3cm")
-
-# kable(SAR_data, caption = "Parameters of selected SAR images.",
-#       format = "latex",
-#       booktabs = TRUE,
-#       align = "cccccccccc",
-#       escape = FALSE,
-#       digits = 2,
-#       label = "table_param",
-#       centering = FALSE
-#       #table.envir = "table", position = "H"
-#       ) %>%
-#   row_spec(0, align = "c") %>%
-#  kable_styling(latex_options = "scale_down", font_size = 10) %>% 
-#   kable_styling(full_width = TRUE) %>%
-#   column_spec(1, width = "3.5cm") %>%
-#   column_spec(2, width = "3cm") %>%
-#   column_spec(3, width = "2cm") %>%
-#   column_spec(4, width = "1cm") %>%
-#   column_spec(5, width = "2cm") %>%
-#   column_spec(6, width = "2.5cm") %>%
-#   column_spec(7, width = "1cm") %>%
-#   column_spec(8, width = "3cm") %>%
-#   column_spec(9, width = "3cm")
-
-```
-
-### Subsection 2
-
-Morbi rutrum odio eget arcu adipiscing sodales.
-Aenean et purus a est pulvinar pellentesque.
-Cras in elit neque, quis varius elit.
-Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci.
-Sed nec nulla auctor odio aliquet consequat.
-Ut nec nulla in ante ullamcorper aliquam at sed dolor.
-Phasellus fermentum magna in augue gravida cursus.
-Cras sed pretium lorem.
-Pellentesque eget ornare odio.
-Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.
-
-## Main Section 2
-
-Sed ullamcorper quam eu nisl interdum at interdum enim egestas.
-Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor.
-Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula.
-Donec eget quam sapien, in viverra eros.
-Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum.
-Vestibulum in orci quis felis tempor lacinia.
-Vivamus ornare ultrices facilisis.
-Ut hendrerit volutpat vulputate.
-Morbi condimentum venenatis augue, id porta ipsum vulputate in.
-Curabitur luctus tempus justo.
-Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl.
-Aliquam dictum sagittis velit sed iaculis.
-Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis.
-Nam elit libero, tincidunt ut aliquam at, molestie in quam.
-Aenean rhoncus vehicula hendrerit.
+Approximating the integral in \eqref{eq:Tsallis-quantile} with a Riemann sum centered at $t_i\approx\tfrac{i}{n}$ and replacing $Q'(t)$ with the estimator in \eqref{eq:density-spacing}, we obtain the nonparametric plug-in estimator
+\begin{align}
+  \widehat T_{\lambda}(\bm{Z})
+  &= \frac{1}{\lambda-1}
+    \left\{
+      1-\frac{1}{n}
+        \sum_{i=1}^{n}
+        \left[
+          \widehat f_n(Z_{(i)})
+        \right]^{\lambda-1}
+    \right\} \nonumber\\[4pt]
+  &= \frac{1}{\lambda-1}
+    \left\{
+      1-\frac{1}{n}
+        \sum_{i=1}^{n}
+        \left(
+           \frac{c_i\,m/n}{Z_{(i+m)}-Z_{(i-m)}}
+        \right)^{\lambda-1}
+    \right\}. 
+  \label{eq:Tsallis-spacing-estimator}
+\end{align}
+<!-- Alternatively, a numerically convenient expression when $1-\lambda>0$ is -->
+<!-- $$ -->
+<!--   \widehat T_{\lambda,m,n} -->
+<!--   = -->
+<!--   \frac{1}{\lambda-1} -->
+<!--   \left\{ -->
+<!--     1-\frac{1}{n} -->
+<!--        \sum_{i=1}^{n} -->
+<!--        \left( -->
+<!--          \frac{D_{i,m}}{c_i\,m/n} -->
+<!--        \right)^{1-\lambda} -->
+<!--   \right\}. -->
+<!-- $$ -->

### 2025-07-01 Text/Thesis/Chapters/Chapter3.qmd
Update thesis

@@
 source("setup.R")
+
+source("./Code/entropy_gamma_sar.R")
+source("./Code/entropy_gI0.R")
+source("./Code/gamma_sar_sample.R")
+source("./Code/gi0_sample.R")
+source("./Code/al_omari_1_estimator.R")
+source("./Code/bootstrap_al_omari_1_estimator.R")
+source("./Code/renyi_entropy_estimator_v1.R")
+source("./Code/bootstrap_renyi_entropy_estimator_v1.R")
+source("./Code/entropy_renyi_gamma_sar.R")
+
+source("./Code/vasicek_estimator.R")
+source("./Code/van_es_estimator.R")
+source("./Code/noughabi_arghami_estimator.R")
+source("./Code/correa_estimator.R")
+source("./Code/ebrahimi_estimator.R")
+source("./Code/bootstrap_correa_estimator.R")
+
+source("./Code/tsallis_entropy_gamma_sar.R")
+source("./Code/tsallis_estimator.R")
+source("./Code/bootstrap_tsallis_entropy.R")
+source("./Code/tsallis_estimator_optimized.R")
+source("./Code/bootstrap_tsallis_entropy_optimized.R")
+
+source("./Code/renyi_estimator.R")
+source("./Code/bootstrap_renyi_estimator.R")
+source("./Code/renyi_entropy_optimized.R")
+source("./Code/bootstrap_renyi_estimator_Op.R")
+
+source("./Code/shannon_alomari_estimator.R")
+source("./Code/bootstrap_shannon_alomari.R")
+source("./Code/shannon_entropy_gamma_sar.R")
+
+source("./Code/functions_sample_bias_mse.R")
+source("./Code/functions_sample_bias_mse_1.R")
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom"))
+
 ```
-# PROBLEM STATEMENT AND METHODOLOGY {#sec-Chapter3}
 
-## Bootstrap Correction for  Entropy Estimators
+# METHODOLOGY {#sec-Chapter3}
 
-## Hypothesis Testing
+## SELECTION OF THE BEST SHANNON ENTROPY ESTIMATORS  {#sec:shannon_selection}
 
-## Proposed Test Statistics for Heterogeneity Detection
+Although several nonparametric estimators have been proposed for Shannon entropy, their performance depends on factors such as sample size and the underlying distribution.
+We evaluate the six estimators described in Section \ref{sec:sh_est}: the Vasicek \eqref{E:Vasi}, Van Es \eqref{E:VanEs}, Ebrahimi et al.\ \eqref{E:Ebrahimi}, Correa \eqref{E:Correa}, Noughabi–Arghami \eqref{E:rohtua}, and Al–Omari \eqref{E:AO} estimators.
+Their performance is evaluated through a simulation study under fixed conditions.
+The selection is based on two standard criteria: bias and mean squared error (MSE).
+
+The goal of this analysis is to identify the estimators with the best overall performance, which will then be used in the subsequent stages of the methodology, including bootstrap correction and hypothesis testing.
+This selection process is exclusive to Shannon entropy, as only a single estimator was considered for Rényi and Tsallis entropies.
+
+Our experimental setup involves the analysis of bias and MSE for each estimator through a Monte Carlo study.
+For each sample size $n \in \{9, 25, 49, 81, 121\}$, we generate $1000$  independent synthetic samples from $Z \sim \Gamma_{\text{SAR}}(5,1)$.
+The results are consistent across other values of $\mu$ and $L$.
+We adopt the heuristic spacing $m = \left[\sqrt{n} + 0.5\right]$, a choice commonly recommended in the literature [@Wieczorkowski1999].
+
+Figure \ref{fig:Plot_bias_mse-sh} presents the bias and MSE for each of the non-parametric estimators of Shannon entropy. The results are summarized in @tbl-out.
+
+```{=latex}
+\begin{figure}[H]
+\caption{Performance of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.}\label{fig:Plot_bias_mse-sh}
+{\centering \includegraphics[width=1\linewidth]{Figures/Plot_bias_shannon_L5b-1}
+
+}
+\end{figure}
+```
+
+```{r Simulated_data_L51_cached2, echo=FALSE, message=FALSE, cache=TRUE, autodep=TRUE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+file_name <- "./Data/results_estimator_sh2.Rdata"
+
+if (file.exists(file_name)) {
+  load(file_name)
+  message("Loaded existing results from results_estimator_sh2.Rdata")
+} else {
+  # Parámetros del experimento
+  sample_sizes <- c(9, 25, 49, 81, 121 )
+
+# Number of replications
+R <-500
+
+# Number of bootstrap replications
+#B1 <- 1
+mu_values <- c(1)
+alpha <- -500
+L <- 5
+
+estimators <- list(
+  "Vasicek" = vasicek_estimator,
+  "Van Es" = van_es_estimator,
+  "Ebrahimi" = ebrahimi_estimator,
+  "Correa" = correa_estimator,
+  "Noughabi" = noughabi_arghami_estimator,
+  "AlOmari" = al_omari_1_estimator
+
+  # "Correa" = correa_estimator,
+  # "Ebrahimi" = ebrahimi_estimator,
+  # "Al Omari" = al_omari_1_estimator,
+  # "Correa Bootstrap" = bootstrap_correa_estimator,
+  # "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
+  # "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
+)
+
+calculate_results_gi0 <- function(sample_sizes, R, B1, mu_values, alpha, L, estimators) {
+  results_list <- list()
+
+  for (mu_val in mu_values) {
+
+    results <- calculate_bias_mse_gi0(sample_sizes, R, B1, mu_val, alpha, L, estimators)
+    df <- as.data.frame(results)
+
+    results_list[[as.character(mu_val)]] <- df
+  }
+
+  return(results_list)
+}
+
+results_gi0 <- calculate_results_gi0(sample_sizes, R, B1, mu_values, alpha, L, estimators)
+
+  save(results_gi0, file = file_name)
+  message("Simulation completed and results saved.")
+}
+```
+
+```{r fig-bias_shannon_L5-011, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hide",   out.width="95%", fig.pos = 'H',  fig.cap="Bias and MSE of the entropy estimators for the $\\Gamma_{\\text{SAR}}$, with $L=2$.", fig.width=7,fig.height=3}
+#fig.show="hide", 
+# eval=FALSE,  #
+
+load("./Data/results_estimator_sh2.Rdata")
+
+estimators_to_plot <- c("Vasicek", "Van Es", "Ebrahimi",  "Correa", "Noughabi", "AlOmari" )
+  latex_estimator_names <- c("Vasicek" = expression("$\\widehat{italic(H)}_{V}$"),
+                             "Van Es" = expression("$\\widehat{italic(H)}_{VE}$"),
+                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
+                            "Correa" = expression("$\\widehat{italic(H)}_{C}$"),
+                            "Noughabi" = expression("$\\widehat{italic(H)}_{N}$"),
+                            "AlOmari" = expression("$\\widehat{italic(H)}_{AO}$"))
+selected_estimators_latex <- latex_estimator_names[estimators_to_plot]
+mu_values <- 1
+combined_plot_gi0 <- generate_plot_gi0_esp(results_gi0, mu_values, selected_estimators_latex, ncol = 1, nrow = 1)
+
+print(combined_plot_gi0)
+```
+
+\renewcommand{\arraystretch}{1.8} 
+```{r Table_estimators_shannon2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#| label: tbl-out
+#| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.'
+
+cat("\\setlength{\\tabcolsep}{4pt}\n")
+load("./Data/results_estimator_sh2.Rdata")
+
+estimators_to_table <- c("Vasicek", "Van Es", "Ebrahimi", "Correa", "Noughabi", "AlOmari")
+
+reshaped_results <- purrr::map_dfr(
+  results_gi0,
+  ~ .x %>% dplyr::filter(Estimator %in% estimators_to_table),
+  .id = "mu"
+) %>%
+  tidyr::pivot_wider(names_from = Estimator, values_from = c(Bias, MSE))
+
+for (j in seq_along(reshaped_results)) {
+  v <- reshaped_results[[j]]
+  if (is.numeric(v)) {
+    if (j == 1) {                    # μ  → entero, scriptstyle
+      reshaped_results[[j]] <- sprintf("$\\scriptstyle %d$", v)
+    } else if (j == 2) {             # n  → entero “normal”
+      reshaped_results[[j]] <- sprintf("$%d$", v)
+    } else {                         # resto → 3 decimales + phantom
+      reshaped_results[[j]] <- ifelse(
+        v < 0,
+        sprintf("$%.3f$", v),
+        sprintf("$\\phantom{-}%.3f$", v)
+      )
+    }
+  }
+}
+
+cols_to_bold <- c(5, 6, 8, 11, 12, 14)  # según el orden final de la tabla
+
+bold_math <- function(x) {
+  sub("^\\$(.*)\\$$", "\\$\\\\mathbf{\\1}\\$", x)
+}
+
+reshaped_results[cols_to_bold] <- lapply(reshaped_results[cols_to_bold], bold_math)
+
+colnames(reshaped_results) <- c(
+  "$\\bm{\\mu}$", "$\\bm{n}$",
+  "$\\bm{\\widehat{H}_{\\text{V}}}$",  "$\\bm{\\widehat{H}_{\\text{VE}}}$",
+  "$\\bm{\\widehat{H}_{\\text{E}}}$",  "$\\bm{\\widehat{H}_{\\text{C}}}$",
+  "$\\bm{\\widehat{H}_{\\text{N}}}$", "$\\bm{\\widehat{H}_{\\text{AO}}}$",
+  "$\\bm{\\widehat{H}_{\\text{V}}}$",  "$\\bm{\\widehat{H}_{\\text{VE}}}$",
+  "$\\bm{\\widehat{H}_{\\text{E}}}$",  "$\\bm{\\widehat{H}_{\\text{C}}}$",
+  "$\\bm{\\widehat{H}_{\\text{N}}}$", "$\\bm{\\widehat{H}_{\\text{AO}}}$"
+)
+
+# 5. kable ---------------------------------------------------------------------
+knitr::kable(
+  reshaped_results,
+  #caption   = "Bias and MSE of Shannon entropy estimators under $\\Gamma_{\\text{SAR}}(5,1)$.",
+  format    = "latex",
+  booktabs  = TRUE,
+  align     = "crllllllllllll",  # 
+  escape    = FALSE,
+ # label     = "#tbl-tablesh",
+  centering = FALSE,
+ # table.envir = "table",
+  #position  = "htb",
+  linesep   = ""
+) %>%
+  add_header_above(c(" ", " ", "Bias" = 6, "MSE" = 6)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0, align = "r") %>%
+  kable_styling(latex_options = "scale_down")
+
+```
+
+As shown in the simulation results, the estimators $\widehat{H}_{\text{C}}$, $\widehat{H}_{\text{E}}$, and $\widehat{H}_{\text{AO}}$ show low bias and achieve convergence for sample sizes larger than 81.
+These estimators exhibit good behavior in terms of bias and MSE across various parameter combinations.
+
+In contrast, estimator $\widehat{H}_{\text{N}}$ displays the lowest MSE across all scenarios.
+However, the bias remains unchanged and high for sample sizes larger than 25, indicating that the convergence is not very fast.
+Additionally, we observe that both $\widehat{H}_{\text{V}}$ and $\widehat{H}_{\text{VE}}$ estimators exhibit larger bias and slower convergence compared to their counterparts.
+Notably, the $\widehat{H}_{\text{V}}$ estimator shows the highest MSE.
+
+Although the estimators $\widehat{H}_{\text{C}}$, $\widehat{H}_{\text{E}}$, and $\widehat{H}_{\text{AO}}$ demonstrate good performance in terms of bias and MSE for sufficiently large samples (e.g., $n \geq 81$), practical scenarios in SAR image processing often involve much smaller sample sizes.
+In particular, local texture analysis is typically performed on small windows, such as $7 \times 7$, which correspond to $n = 49$.
+Under these conditions, bias can become significant, and convergence is slower or incomplete.
+
+To address this issue and improve estimation accuracy in small-sample regimes, we introduce a bootstrap-based correction methodology.
+The next subsection presents the bias-reduction procedure and the definition of the corrected entropy estimator.
+
+## BOOTSTRAP BIAS CORRECTION FOR ENTROPY ESTIMATORS
+
+The nonparametric estimators of entropy considered in this work include the Shannon entropy $\widehat{H}(\bm{Z})$, the Rényi entropy $\widehat{R}_\lambda(\bm{Z})$, and the Tsallis entropy $\widehat{T}_\lambda(\bm{Z})$.
+We assume that these estimators are inherently biased; that is, their expected value does not coincide with the true entropy, as shown in Equation \eqref{eq:bias_def}:
+\begin{equation}
+\operatorname{Bias}(\widehat{\theta}) = \mathbb{E}[\widehat{\theta}] - \theta \neq 0,
+\label{eq:bias_def}
+\end{equation}
+where $\widehat{\theta}$ denotes any of the estimators listed above, and $\theta$ is the corresponding true entropy value.
+
+To reduce this bias, we apply a bootstrap correction method.
+Let $\bm{Z} = (Z_1, Z_2, \dots, Z_n)$ be a random sample of size $n$ from an unknown distribution.
+Using bootstrap resampling, we generate $B$ new samples $\bm{Z}^{(1)}, \bm{Z}^{(2)}, \dots, \bm{Z}^{(B)}$ by sampling with replacement from $\bm{Z}$.
+For each bootstrap sample $\bm{Z}^{(b)}$, we compute the corresponding estimator $\widehat{\theta}(\bm{Z}^{(b)})$.
+
+The bias is then estimated using Equation \eqref{eq:bias_estimate}, which calculates the difference between the average of the bootstrap estimates and the original estimate:
+\begin{equation}
+\widehat{\operatorname{Bias}} = \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}(\bm{Z}^{(b)}) - \widehat{\theta}(\bm{Z}).
+\label{eq:bias_estimate}
+\end{equation}
+A bias-corrected estimator is then defined by subtracting the estimated bias from the original estimator, as expressed in Equation \eqref{eq:bias_corrected}:
+\begin{equation}
+\widetilde{\theta} = \widehat{\theta} - \widehat{\operatorname{Bias}}.
+\label{eq:bias_corrected}
+\end{equation}
+Substituting the estimate from Equation \eqref{eq:bias_estimate} into Equation \eqref{eq:bias_corrected} yields the explicit formula for the corrected estimator:
+\begin{equation}
+\widetilde{\theta} = 2\widehat{\theta}(\bm{Z}) - \frac{1}{B} \sum_{b=1}^{B} \widehat{\theta}(\bm{Z}^{(b)}).
+\label{eq:theta_explicit}
+\end{equation}
+<!-- This expression follows from the classical bias correction formula: -->
+<!-- \begin{equation} -->
+<!-- \text{Bias-corrected estimate} = \text{Original estimate} - \text{Bias estimate}. -->
+<!-- \label{eq:bias_correction_principle} -->
+<!-- \end{equation} -->
+Thus, $\widetilde{\theta}$ is an approximately unbiased estimator of $\theta$.
+The effectiveness of the correction depends on the number of bootstrap replicates $B$ and the characteristics of the underlying distribution, but it systematically reduces bias, particularly when working with small sample sizes.
+
+To distinguish the bootstrap-improved estimators from their original forms, we adopt the following notation: $\widetilde{H}_{\text{V}}$, $\widetilde{H}_{\text{VE}}$, $\widetilde{H}_{\text{E}}$, $\widetilde{H}_{\text{C}}$, $\widetilde{H}_{\text{N}}$, and $\widetilde{H}_{\text{AO}}$, respectively.
+For the other entropy types, we denote the bootstrap-corrected estimators as $\widetilde{R}_\lambda$ for Rényi entropy and $\widetilde{T}_\lambda$ for Tsallis entropy.
+
+In order to assess the effectiveness of the bootstrap technique, we present comparisons of the bias and MSE between each original non-parametric Shannon entropy estimator and its respective bootstrap-enhanced version, using samples from the $\Gamma_{\text{SAR}}(5,1)$, with $B=100$ bootstrap replicates and varying $n$, as shown in Figures \ref{fig:Firstfigure}--\ref{fig:subfig6}.
+
+```{=latex}
+\begin{figure}[htb]
+  \caption{Comparing Bias and MSE: original vs. bootstrap estimators, with, $\mu=1$ and $L=5$.}
+  \label{fig:all_estimator}
+  \centering
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_vasicek-1}
+    \caption{}
+    \label{fig:Firstfigure}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_VanEs-1}
+    \caption{}
+    \label{fig:Secondfigure}
+  \end{subfigure}
+	\begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_Ebrahimi-1}
+    \caption{}
+    \label{fig:subfig3}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_correa-1}
+    \caption{}
+    \label{fig:subfig4}
+  \end{subfigure}
+	\begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_noughabi-1}
+    \caption{}
+    \label{fig:subfig5}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[t]{0.48\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{Figures/Plot_bias_mse_AO-1}
+    \caption{}
+    \label{fig:subfig6}
+  \end{subfigure}
+\end{figure}
+```
+
+The estimators $\widetilde{H}_{\text{V}}$ and $\widetilde{H}_{\text{VE}}$ show consistent bias reduction, though convergence remains slow.
+For $\widetilde{H}_{\text{E}}$, the correction improves bias only for small $n$, while its MSE steadily decreases.
+In contrast, the bootstrap technique did not improve the $\widetilde{H}_{\text{N}}$ estimator.
+This might occur because the original estimator overestimates the entropy values, showing a positive bias.
+This tendency to overestimate persists with the use of bootstrap, contributing to an increase in bias and MSE.
+
+The most notable improvements are observed with $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$, which achieve both low bias and MSE even for small sample sizes, demonstrating faster convergence.
+
+While the bias-corrected estimator $\widetilde{\theta}$ is theoretically motivated to reduce bias, its effectiveness is not guaranteed for all entropy estimators.
+In practice, the performance of the bootstrap correction varies depending on the characteristics of the original estimator and the sample size.
+
+To finalize the selection of the non-parametric Shannon entropy estimator used in the following simulations, we consider the execution time of the bootstrap versions of $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$.
+
+ @tbl-out-time shows the processing time of each estimator across different settings of $L$  and $n$.
+<!-- <!-- # ```{r Simulated_comparative_time6, eval=FALSE, echo=FALSE} --> 
+```{r Simulated_comparative_time6, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+R <- 600
+mu <- 1
+B <- 40
+
+sample.size <- c(25,49, 81, 121)
+L_values <- c(5, 18)
+
+bootstrap_estimators <- list(
+  "$\\widetilde{H}_{\\text{C}}$" = bootstrap_correa_estimator,
+  "$\\widetilde{H}_{\\text{AO}}$" = bootstrap_al_omari_1_estimator
+)
+if (!file.exists("./Data/results_data_time_sh.Rdata")) {#results_data_timenn
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  all_TestStatistics <- list()
+  execution_times <- list()
+
+  for (estimator_name in names(bootstrap_estimators)) {
+    TestStatistics <- list()
+
+    for (L in L_values) {
+      TestStat <- list()
+
+      for (s in sample.size) {
+        TestStat1 <- numeric(R)
+        start_time <- Sys.time() # start time
+
+        for (r in 1:R) {
+          z <- gamma_sar_sample(L, mu, s)
+          TestStat1[r] <- bootstrap_estimators[[estimator_name]](z, B) - (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+        }
+
+        TestStatistics[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)
+
+        end_time <- Sys.time() # end time
+        execution_time <- end_time - start_time # total time
+        execution_times[[paste(estimator_name, L, s)]] <- execution_time # save time
+      }
+
+      all_TestStatistics[[paste(estimator_name, L)]] <- TestStatistics
+    }
+  }
+
+  save(all_TestStatistics, execution_times, file = "./Data/results_data_time_sh.Rdata")#
+}
+
+```
+\renewcommand{\arraystretch}{1.1}
+```{r Table_statistic_time_6,  echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+#| label: tbl-out-time
+#| tbl-cap: 'Processing time for bootstrap-improved estimators $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$'
+
+cat("\\setlength{\\tabcolsep}{10pt}\n")
+load("./Data/results_data_time_sh.Rdata")
+#fig.show="hide",
+# eval=FALSE,
+combined_results <- data.frame(
+  Estimator   = character(),
+  L           = numeric(),
+  SampleSize  = numeric(),
+  Time        = numeric()
+)
+
+# Organizar resultados
+for (estimator_name in names(bootstrap_estimators)) {
+  for (L in L_values) {
+    for (sample_size in sample.size) {
+      key <- paste(estimator_name, L, sample_size)
+      if (!is.null(execution_times[[key]])) {
+        combined_results <- rbind(combined_results, data.frame(
+          Estimator   = estimator_name,
+          L           = L,
+          SampleSize  = sample_size,
+          Time        = as.numeric(execution_times[[key]], units = "secs")
+        ))
+      }
+    }
+  }
+}
+
+# Filas para negrita (índices 9:16)
+rows_to_bold <- 9:16
+
+# Formato columnas de texto
+combined_results$L          <- sprintf("$%d$", combined_results$L)
+combined_results$SampleSize <- sprintf("$%d$", combined_results$SampleSize)
+combined_results$Time       <- sapply(seq_along(combined_results$Time), function(i) {
+  val <- combined_results$Time[i]
+  if (i %in% rows_to_bold) {
+    sprintf("$\\mathbf{\\phantom{-}%.2f}$", val)
+  } else {
+    sprintf("$\\phantom{-}%.2f$", val)
+  }
+})
+
+# Renombrar columnas para LaTeX
+colnames(combined_results) <- c("\\textbf{Estimator}", "$\\bm{L}$", "$\\bm{n}$", "\\textbf{Time} (s)")
+
+# Generar tabla con kable (latex)
+knitr::kable(
+  combined_results,
+#  caption    = "Processing time for bootstrap-improved estimators \\(\\widetilde{H}_{\\text{C}}\\) and \\(\\widetilde{H}_{\\text{AO}}\\).",
+  format     = "latex",
+  booktabs   = TRUE,
+  align      = "cccc",
+  escape     = FALSE,
+  #label      = "table_time",
+  #table.envir= "table",
+ # position   = "H",
+  linesep    = ""
+) %>%
+  row_spec(4,  extra_latex_after = "\\cline{3-4}") %>%
+  row_spec(12, extra_latex_after = "\\cline{3-4}") %>%
+  collapse_rows(latex_hline = "major", valign = "middle") %>%
+  row_spec(0, align = "c") %>%
+  kable_styling(latex_options = "scale_down", full_width = TRUE)
+
+```
+
+The results indicate that $\widetilde{H}_{\text{AO}}$ consistently achieves lower computational times compared to $\widetilde{H}_{\text{C}}$.
+This makes it the more efficient option, particularly relevant for large datasets, such as SAR images discussed in @sec-Chapter4.
+Consequently, $\widetilde{H}_{\text{AO}}$ is selected as the representative non-parametric Shannon entropy estimator in the simulations presented in the following sections.
+
+## Optimal $\lambda$ Selection 
+<!-- Finding the Optimal Value of $\lambda$ for the Rényi and Tsallis Entropy Estimators -->
+
+We aim to determine the optimal order $\lambda$ for the nonparametric entropy estimators of Rényi ($\widetilde{R}_{\lambda}$) and Tsallis ($\widetilde{T}_{\lambda}$), using simulated samples of size $n = 49$ from $Z\sim\Gamma_{\text{SAR}}(5,  1)$ distribution.
+
+To assess estimator performance, we conducted a Monte Carlo simulation with $R = 1000$ replications.
+For each value of $\lambda$, independent samples were generated, and entropy was estimated for each sample using the bootstrap bias-corrected version with $B = 100$ resamples  to reduce bias.
+The resulting estimates were compared to the theoretical entropy to compute the bias and MSE.
+This simulation-based procedure allows us to evaluate how the choice of $\lambda$ affects estimation accuracy, and whether the bootstrap improves performance.
+
+For the Rényi estimator (see Fig.
+\ref{fig-optimal_order}), $\lambda = 0.9$ minimizes the MSE while keeping the bias low, achieving a favorable bias-variance trade-off.
+Although $\lambda = 0.85$ yields slightly lower bias, it produces a higher MSE, supporting the choice of $\lambda = 0.9$ as optimal.
+
+Similarly, for the Tsallis estimator (Fig. \ref{fig-optimal_order-tsallis}), $\lambda = 0.85$ results in the lowest MSE with moderate bias, making it the most suitable choice.
+
+```{r fig-optimal_order,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3}
+#fig.show="hide", 
+# eval=FALSE,  #
+
+data <- data.frame(
+  Lambda = c(0.9,  0.85, 0.99, 1.1, 1.5),
+  Bias = c(0.00158,  -0.00250, 0.02077, 0.03751, 0.06512),
+  MSE = c(0.01273,  0.01441, 0.01653, 0.01697, 0.01906)
+)
+
+data <- data[order(data$Lambda), ]
+
+bias_plot <- ggplot(data, aes(x = Lambda, y = Bias)) +
+  geom_line(color = "#00AFBB", linewidth = 1.0) +  
+  geom_point(color = "#00AFBB", size = 3) +  
+  geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$Bias), 
+         #  label = "Bias", color = "#00AFBB", fontface = "italic", hjust = 1.0) +
+  #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
+  labs(x = expression(lambda), y = "Bias") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12))
+
+mse_plot <- ggplot(data, aes(x = Lambda, y = MSE)) +
+  geom_line(color = "#E69F00", linewidth = 1.0) +  
+  geom_point(color = "#E69F00", size = 3) +
+  #geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$MSE), 
+           #label = "MSE", color = "#E69F00", fontface = "italic", hjust = 1.0) +
+   #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) + 
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
+  labs(x = expression(lambda), y = "MSE") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12))
+
+grid.arrange(bias_plot, mse_plot, nrow = 2)
+
+```
+
+```{r fig-optimal_order-tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3}
+#fig.show="hide", 
+# eval=FALSE,  #
+
+data <- data.frame(
+  Lambda = c(0.8,  0.85, 0.9, 0.95, 1.1, 1.5),
+  Bias = c(-0.094,  0.00047, 0.009, 0.04,0.3, 0.6),
+  MSE = c(0.0215,  0.022, 0.023, 0.026, 0.029, 0.031)
+)
+
+data <- data[order(data$Lambda), ]
+
+bias_plot <- ggplot(data, aes(x = Lambda, y = Bias)) +
+  geom_line(color = "#8E44AD", linewidth = 1.0) +  
+  geom_point(color = "#8E44AD", size = 3) +  
+  geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$Bias), 
+         #  label = "Bias", color = "#00AFBB", fontface = "italic", hjust = 1.0) +
+  #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) +
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
+  labs(x = expression(lambda), y = "Bias") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12))
+
+mse_plot <- ggplot(data, aes(x = Lambda, y = MSE)) +
+  geom_line(color = "#27AE60", linewidth = 1.0) +  
+  geom_point(color = "#27AE60", size = 3) +
+  #geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+  #annotate("text", x = max(data$Lambda) - 0.1, y = max(data$MSE), 
+           #label = "MSE", color = "#E69F00", fontface = "italic", hjust = 1.0) +
+   #scale_x_continuous(breaks = data$Lambda, labels = data$Lambda) + 
+  scale_x_continuous(breaks = data$Lambda, labels = data$Lambda, minor_breaks = NULL)+
+  scale_y_continuous(minor_breaks = NULL)+
+  labs(x = expression(lambda), y = "MSE") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif"),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 12))
+
+grid.arrange(bias_plot, mse_plot, nrow = 2)
+
+```
+
+<!-- ```{=latex} -->
+<!-- \begin{figure}[hbt] -->
+<!--   \centering -->
+<!--   \includegraphics[width=0.42\textwidth]{Figures-R1/fig-optimal_order-1.pdf} -->
+<!--   \vspace{0.5em} -->
+<!--   \caption{Bias and MSE as a function of $\lambda$, with $n=49$, $L=5$.} -->
+<!--   \label{fig-optimal_order} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+In the case of $L = 1$, the bootstrap procedure does not provide meaningful improvement and often leads to unstable estimates.
+Therefore, we omit bootstrap in this setting.
+Under these conditions, higher values of $\lambda$ yield better results: $\lambda = 3$ is preferred for the Rényi estimator, and $\lambda = 1.2$ for the Tsallis estimator.
+
+### Bootstrap Bias Correction in Rényi and Tsallis Entropy Estimation
+
+Building upon the previous Monte Carlo setup, we further assess the performance of the Rényi and Tsallis entropy estimators by analyzing their behavior across varying sample sizes $n \in \{9, 25, 49, 81, 121\}$.
+Using the optimal values of the order parameter ($\lambda = 0.9$ for Rényi and $\lambda = 0.85$ for Tsallis) already identified in the earlier analysis, we compute the bias and MSE for both the original and bootstrap-corrected versions of the estimators.
+As illustrated in Figures \ref{fig-bias_mse_rm1} and \ref{fig-bias_mse_Tsallis}, the bootstrap estimators consistently show improved performance, especially for small samples.
+In particular, at $n = 49$, both estimators exhibit low bias and MSE, confirming their robustness in moderate sample regimes and supporting their use in practical applications.
+
+```{r Simulated_data_bias_m1, echo=FALSE, message=FALSE }
+set.seed(1234567890, kind = "Mersenne-Twister")
+#cache = TRUE, autodep = TRUE
+
+file_name <- "./Data/results_renyi_m1.Rdata"
+
+if (file.exists(file_name)) {
+
+  load(file_name)
+  message("Loaded existing results from results_renyi_m1.Rdata")
+} else {
+  # Parameters
+  sample_sizes <- c(9, 25, 49, 81, 121)
+  R <- 500
+  B <- 100
+  mu <- 1
+  L <- 5
+  alpha_values <- c(0.9)
+
+  estimators <- list(
+    "Renyi Estimator" = renyi_estimator,
+    "Renyi Estimator Bootstrap" = bootstrap_renyi_estimator
+  )
+
+  results <- calculate_bias_mse_r2(sample_sizes, R, B, mu, L, alpha_values, estimators)
+
+  save(results, file = file_name)
+  message("Simulations completed and results saved.")
+}
+```
+
+```{r fig-bias_mse_rm1,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=4}
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom"))
+#fig.show="hide",
+# eval=FALSE,  #
+#  out.width="80%",
+load("./Data/results_renyi_m1.Rdata")
+
+alpha_values <- 0.9
+estimators_to_plot <- c("Renyi Estimator", "Renyi Estimator Bootstrap")
+latex_estimator_names <- c("Renyi Estimator" = expression("$\\widehat{italic(R)}_{\\lambda}$"),#
+                           "Renyi Estimator Bootstrap" = expression("$\\widetilde{italic(R)}_{\\lambda}$"))
+selected_estimators_latex <- latex_estimator_names[estimators_to_plot]
+
+combined_plot_renyi <- generate_plot_renyi(results, alpha_values, selected_estimators_latex, ncol = 1, nrow = 1)
+
+print(combined_plot_renyi)
+
+```
+
+```{r}
+tsallis_entropy_gamma_sar <- function(mu, L, lambda) {
+  (1 - exp((1 - lambda)*log(mu) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) / (lambda - 1)
+}
+# Función para calcular Bias y MSE para la entropía de Tsallis
+calculate_bias_mse_tsallis <- function(sample_sizes, R, B, mu, L, lambda_values, estimators) {
+  output <- data.frame(
+    n = integer(0),
+    Estimator = character(0),
+    Lambda = numeric(0),
+    Bias = numeric(0),
+    MSE = numeric(0)
+  )
+
+  for (lambda in lambda_values) {
+    true_entropy <- tsallis_entropy_gamma_sar(mu, L, lambda)
+
+    for (ssize in sample_sizes) {
+      samples <- generate_samples(ssize, R, mu, L)
+
+      for (estimator_name in names(estimators)) {
+        estimator <- estimators[[estimator_name]]
+        v.entropy <- numeric(R)
+
+        for (r in 1:R) {
+          sample <- samples[[r]]
+
+          if (grepl("Bootstrap", estimator_name)) {
+            v.entropy[r] <- estimator(sample, B = B, lambda = lambda)
+          } else {
+            v.entropy[r] <- estimator(sample, lambda = lambda)
+          }
+        }
+
+        mse <- mean((v.entropy - true_entropy)^2)
+        bias <- mean(v.entropy) - true_entropy
+
+        output <- rbind(output, data.frame(
+          n = ssize,
+          Estimator = estimator_name,
+          Lambda = lambda,
+          Bias = round(bias, 5),
+          MSE = round(mse, 5)
+        ))
+      }
+    }
+  }
+
+  return(output)
+}
+
+```
+
+```{r Simulated_data_bias_tt, echo=FALSE, message=FALSE }
+set.seed(1234567890, kind = "Mersenne-Twister")
+#cache = TRUE, autodep = TRUE
+
+file_name_tsallis <- "./Data/results_tsallis_jj.Rdata"
+
+if (file.exists(file_name_tsallis)) {
+
+  load(file_name_tsallis)
+  message("Loaded existing results from results_tsallis_jj.Rdata")
+
+} else {
+  # Parámetros
+  sample_sizes <- c(9, 25, 49, 81, 121)
+  R <- 50
+  B <- 200
+  mu <- 1
+  L <- 5
+  lambda_values <- c(0.85)
+
+  estimators <- list(
+    "Tsallis Estimator" = tsallis_estimator_optimized,
+    "Tsallis Estimator Bootstrap" = bootstrap_tsallis_entropy_optimized
+  )
+
+  results_tsallis <- calculate_bias_mse_tsallis(sample_sizes, R, B, mu, L, lambda_values, estimators)
+
+  save(results_tsallis, file = file_name_tsallis)
+  message("Simulations for Tsallis completed and results saved.")
+}
+
+```
+
+```{r}
+generate_plot_tsallisn <- function(results_df, lambda_values, selected_estimators, ncol = 1, nrow = 6) {
+  library(ggplot2)
+  library(patchwork)
+
+  plot_list <- list()
+
+  for (lambda_val in lambda_values) {
+    df <- results_df[results_df$Lambda == lambda_val, ]
+    df_filtered <- df[df$Estimator %in% names(selected_estimators), ]
+    df_filtered$Estimator <- selected_estimators[df_filtered$Estimator]
+    df_filtered$Estimator <- as.character(df_filtered$Estimator)
+
+    plot_bias <- ggplot(df_filtered, aes(x = n, y = Bias, color = Estimator)) +
+      geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+      geom_point(size = 3.2) +
+      geom_line(linetype = "solid", linewidth = 1.5, alpha = 0.8) +
+      labs(y = "Bias", x = expression(italic(n))) +
+      scale_x_continuous(breaks = unique(df_filtered$n), minor_breaks = NULL) +
+      scale_y_continuous(minor_breaks = NULL) +
+      scale_color_manual(values = c("#7570b3", "#e7298a"), labels = TeX(df_filtered$Estimator)) +
+      ggtitle(bquote(lambda == .(lambda_val))) +
+      theme_minimal() +
+      theme(text = element_text(family = "serif"),
+            axis.text = element_text(size = 11),
+            axis.title = element_text(size = 12),
+            plot.title = element_text(size = 11, hjust = 0),
+            legend.position = "bottom",
+            legend.box = "horizontal",
+            legend.text = element_text(size = 12),
+            legend.title = element_text(size = 12)) +
+      guides(color = guide_legend(nrow = 1))
+
+    plot_mse <- ggplot(df_filtered, aes(x = n, y = MSE, color = Estimator)) +
+      geom_hline(yintercept = 0, color = "gray50", linetype = "dashed", linewidth = 0.5) +
+      geom_point(size = 3.2) +
+      geom_line(linetype = "solid", linewidth = 1.5, alpha = 0.8) +
+      labs(y = "MSE", x = expression(italic(n))) +
+      scale_x_continuous(breaks = unique(df_filtered$n), minor_breaks = NULL) +
+      scale_y_continuous(minor_breaks = NULL) +
+      scale_color_manual(values = c("#7570b3", "#e7298a"), labels = TeX(df_filtered$Estimator)) +
+      theme_minimal() +
+      theme(text = element_text(family = "serif"),
+            axis.text = element_text(size = 11),
+            axis.title = element_text(size = 12),
+            legend.position = "bottom",
+            legend.box = "horizontal",
+            legend.text = element_text(size = 12),
+            legend.title = element_text(size = 12)) +
+      guides(color = guide_legend(nrow = 1))
+
+    combined_plot <- plot_bias / plot_mse
+    plot_list[[as.character(lambda_val)]] <- combined_plot
+  }
+
+  combined_plot_all <- wrap_plots(plot_list, ncol = ncol, nrow = nrow) +
+    plot_layout(guides = "collect")
+
+  return(combined_plot_all)
+}
+```
+
+```{r fig-bias_mse_Tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="H",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=4}
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom"))
+
+# Cargar resultados simulados
+load("./Data/results_tsallis_jj.Rdata")
+
+lambda_values <- 0.85
+estimators_to_plot_tsallis <- c("Tsallis Estimator", "Tsallis Estimator Bootstrap")
+
+# Etiquetas LaTeX para leyenda
+latex_estimator_names_tsallis <- c(
+  "Tsallis Estimator" = expression("$\\widehat{italic(T)}_{\\lambda}$"),
+  "Tsallis Estimator Bootstrap" = expression("$\\widetilde{italic(T)}_{\\lambda}$")
+)
+
+selected_estimators_latex_tsallis <- latex_estimator_names_tsallis[estimators_to_plot_tsallis]
+
+# Graficar
+combined_plot_tsallis <- generate_plot_tsallisn(
+  results_tsallis,
+  lambda_values,
+  selected_estimators_latex_tsallis,
+  ncol = 1,
+  nrow = 1
+)
+
+print(combined_plot_tsallis)
+
+```
+
+From this point forward, all subsequent simulations and comparisons will be based on the improved bootstrap estimators: $\widetilde{H}_{\text{AO}}$ for Shannon, $\widetilde{R}_{\lambda}$ for Rényi, and $\widetilde{T}_{\lambda}$ for Tsallis entropy.
+
+<!-- ```{r Simulated_data_bias_shannon1, echo=FALSE, message=FALSE} -->
+<!-- set.seed(1234567890) -->
+
+<!-- file_name <- "./Data/results_shannon_v1.Rdata" -->
+
+<!-- if (file.exists(file_name)) { -->
+<!--   load(file_name) -->
+<!--   message("Loaded existing results from results_shannon_v1.Rdata") -->
+<!-- } else { -->
+<!--   sample_sizes <- c(9, 25, 49, 81, 121) -->
+<!--   R <- 500 -->
+<!--   B <- 100 -->
+<!--   mu <- 1 -->
+<!--   L <- 16 -->
+
+<!--   estimators <- list( -->
+<!--     "Shannon Estimator" = al_omari_1_estimator, -->
+<!--     "Shannon Estimator Bootstrap" = bootstrap_al_omari_1_estimator -->
+<!--   ) -->
+
+<!--   results <- calculate_bias_mse_shannon(sample_sizes, R, B, mu, L, estimators) -->
+
+<!--   save(results, file = file_name) -->
+<!--   message("Simulaciones completadas y resultados guardados.") -->
+<!-- } -->
+
+<!-- ``` -->
+<!-- ```{r fig-bias_mse_shannonm, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.cap="Bias and MSE of the Shannon–Al-Omari entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=6, fig.height=5} -->
+<!-- load("./Data/results_shannon_v1.Rdata") -->
+
+<!-- estimators_to_plot <- c("Shannon Estimator", "Shannon Estimator Bootstrap") -->
+<!-- latex_estimator_names <- c( -->
+<!--   "Shannon Estimator" = expression("$\\widehat{italic(H)}$"), -->
+<!--   "Shannon Estimator Bootstrap" = expression("$\\widetilde{italic(H)}$") -->
+<!-- ) -->
+<!-- selected_estimators_latex <- latex_estimator_names[estimators_to_plot] -->
+
+<!-- combined_plot_shannon <- generate_plot_shannon(results, selected_estimators_latex, ncol = 1, nrow = 1) -->
+
+<!-- print(combined_plot_shannon) -->
+
+<!-- ``` -->
+
+<!-- ```{=latex} -->
+<!-- \begin{figure}[hbt] -->
+<!--   \centering -->
+<!--   \includegraphics[width=0.40\textwidth]{Figures-R1/fig-bias_mse-1.pdf} -->
+<!--   \vspace{0.1em} -->
+<!--   \caption{Bias and MSE of the Rényi entropy estimators for $\Gamma_{\text{SAR}}$.} -->
+<!--   \label{fig-bias_mse} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+<!-- We use the $\widetilde{H}_{\lambda}$ estimator for subsequent simulations. -->
+
+## HYPOTHESIS TESTING
+
+We aim to determine whether a local region in a SAR intensity image is statistically homogeneous or heterogeneous.
+This is done by comparing a nonparametric entropy estimator $\widetilde{\theta}$ computed from the observed data to the theoretical entropy $\theta(\Gamma_{\text{SAR}})$ expected under the assumption of fully developed speckle.
+
+Formally, the hypothesis test is:
+\begin{equation}\label{eq:hypothesis_test}
+\begin{cases}
+\mathcal{H}_0: \mathbb{E}[\widetilde{\theta}] = \theta(\Gamma_{\text{SAR}}) & \text{(homogeneous region)}, \\[6pt]
+\mathcal{H}_1: \mathbb{E}[\widetilde{\theta}] = \theta(\mathcal{G}^0_I) & \text{(heterogeneous region)},
+\end{cases}
+\end{equation}
+
+where $\theta$ denotes a generic entropy function (Shannon entropy $H$, Rényi entropy $R_\lambda$, or Tsallis entropy $T_\lambda$), and $\widetilde{\theta}$ is the corresponding nonparametric estimator ($\widetilde{H}_{\text{AO}}$, $\widetilde{R}_\lambda$ and $\widetilde{T}_\lambda$ ).
+
+This formulation allows us to construct specific test statistics for each entropy measure.
+The null hypothesis $\mathcal{H}_0$ assumes that the data follow the Gamma distribution (homogeneous texture), while the alternative $\mathcal{H}_1$ considers the presence of texture modeled by the $\mathcal{G}^0_I$ distribution.
+
+As in the parametric setting it is not possible to define the null hypothesis as $\mathcal{H}_0\!: \alpha = -\infty$, classical inference techniques such as the likelihood ratio, score, gradient, or Wald tests cannot be applied.
+To address this, we construct non-parametric entropy-based test statistics as described below.
+
+### The Proposed Test Based on Shannon Entropy
+
+Given a random sample $\bm{Z} = (Z_1, Z_2, \ldots, Z_n)$ from a distribution $\mathcal{D}$, we define a test statistic based on the difference between a non-parametric estimator of Shannon entropy, $\widetilde{H}_{\text{AO}}(\bm{Z})$, and the analytical Shannon entropy of the Gamma SAR model ($\Gamma_{\text{SAR}}$) in $\eqref{eq:gamma-sh1}$, which depends on the known number of looks $L \geq 1$ and the sample mean $\widehat{\mu}$.
+
+The test statistic is given by:
+\begin{equation}
+\label{eq-test-sh}
+S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L) = \widetilde{H}_{\text{AO}} - \bigl\{ L - \ln L + \ln\Gamma(L) + (1 - L)\psi^{(0)}(L) + \ln\widehat{\mu} \bigr\},
+\end{equation}
+where $\widehat{\mu} = \frac{1}{n} \sum_{i=1}^n Z_i$ is the sample mean.
+
+This statistic can be interpreted as:
+$$
+S_{\widetilde{H}_{\text{AO}}} = 
+\underbrace{\widetilde{H}_{\text{AO}}}_{\text{estimated}} - 
+\underbrace{H(\Gamma_{\text{SAR}})}_{\text{expected under } \mathcal{H}_0}\hspace{-0.7em},
+$$
+that is, the discrepancy between the estimated entropy and the theoretical value assuming homogeneity.
+Values close to zero indicate consistency with the fully developed speckle model, while large positive values suggest higher entropy and therefore, heterogeneity.
+
+<!-- This approach eliminates the need to estimate parameters from the $\mathcal{G}^0_I$ distribution, such as $\alpha$, offering a simpler and more interpretable test.
+In addition, the method remains effective for small sample sizes, especially when combined with bootstrap bias correction.
+-->
+
+### The Proposed Test Based on Rényi Entropy
+
+To assess deviations from homogeneity in SAR data, we define a test statistic based on Rényi entropy.
+The statistic contrasts the non-parametric estimator $\widetilde{R}_\lambda(\bm{Z})$ with the theoretical Rényi entropy of the $\Gamma_{\text{SAR}}$ model in $\eqref{eq-GammaSAR-R}$, assuming that the number of looks $L \geq 1$ is known.
+The proposed statistic is defined as:
+\begin{equation}
+\label{eq-test-renyi}
+S_{\widetilde{R}_{\lambda}}(\bm{Z}; L) = \widetilde{R}_{\lambda} - \left\{ \ln \widehat{\mu} - \ln L + \frac{1}{1-\lambda}
+\left[ -\lambda \ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) - \bigl(\lambda(L-1)+1\bigr)\ln\lambda \right] \right\},
+\end{equation}
+where $\widehat{\mu} = \frac{1}{n} \sum_{i=1}^n Z_i$ is the sample mean.
+
+This test statistic measures the discrepancy between the empirical entropy and the value expected under the fully developed speckle assumption and can be interpreted as:
+$$
+S_{\widetilde{R}_\lambda} = 
+\underbrace{\widetilde{R}_\lambda}_{\text{estimated}} -
+\underbrace{R_\lambda(\Gamma_{\text{SAR}})}_{\text{expected under } \mathcal{H}_0}\hspace{-0.7em},
+$$
+the difference between the estimated entropy and the expected value under homogeneity.
+Values of $S_{\widetilde{R}_\lambda}$ near zero suggest that the observed region is statistically homogeneous, while large deviations indicate the presence of texture or roughness.
+
+### The Proposed Test Based on Tsallis Entropy
+
+To evaluate heterogeneity in SAR imagery, we define a test statistic using Tsallis entropy.
+This statistic contrasts the non-parametric estimator $\widetilde{T}_\lambda(\bm{Z})$ with the analytical Tsallis entropy under the $\Gamma_{\text{SAR}}$ model, as derived in Equation \eqref{eq:gammasar-Tsallis}.
+We assume the number of looks $L \geq 1$ is known and use the following formulation:
+
+\begin{multline}
+\label{eq-test-tsallis}
+S_{\widetilde{T}_{\lambda}}(\bm{Z}; L) = \widetilde{T}_{\lambda} - \biggl\{ \frac{1}{\lambda - 1} \Bigl[ 1 -
+\exp\Bigl(
+(1 - \lambda)\ln \widehat{\mu}
++ (\lambda - 1)\ln L
++ \ln\Gamma\bigl(\lambda(L - 1) + 1\bigr) \\
+- \lambda\ln\Gamma(L)
+- \bigl(\lambda(L - 1) + 1\bigr)\ln \lambda
+\Bigr) \Bigr] \biggr\},
+\end{multline}
+
+where $\widehat{\mu} = \frac{1}{n} \sum_{i=1}^n Z_i$ is the sample mean.
+
+As in the previous cases, this test statistic measures the difference between the empirical entropy and its theoretical counterpart under the assumption of fully developed speckle:
+$$
+S_{\widetilde{T}_\lambda} =
+\underbrace{\widetilde{T}_\lambda}_{\text{estimated}} -
+\underbrace{T_\lambda(\Gamma_{\text{SAR}})}_{\text{expected under } \mathcal{H}_0}\hspace{-0.9em}.
+$$
+
+Values of $S_{\widetilde{T}_\lambda}$ close to zero indicate that the observed region aligns with the homogeneous model.
+In contrast, significantly positive values suggest the presence of structural variations or texture, signaling statistical heterogeneity in the scene.
+
+An important advantage shared by all three proposed test statistics (\eqref{eq-test-sh}, \eqref{eq-test-renyi} and \eqref{eq-test-tsallis}) is that they avoid the need to estimate parameters from the alternative $\mathcal{G}^0_I$ distribution, such as the roughness parameter $\alpha$.
+This leads to a simpler, more interpretable, and statistically grounded testing procedure.
+
+Additionally, the tests are computationally efficient and suitable for practical applications, including large-scale image processing.
+This robustness is especially evident in small sample sizes, where bootstrap correction improves the reliability of the entropy estimates and stabilizes the resulting $p$-values used for decision-making.
+
+\subsection*{Empirical behaviour of the three statistics}
+
+Figures [-@fig-densities-shannon]-[-@fig-densities-tsallis4] display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.
+All three empirical densities are tightly concentrated around zero, confirming that under $\mathcal{H}_0$ the test statistic has mean approximately $0$; at the same time, their moderately heavy tails reveal sensitivity to departures from homogeneity, which is desirable for detecting subtle texture.
+
+```{r Simulated_density-shannon, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 10000
+mu <- 1
+B <- 50
+
+sample.size <- c(49, 81, 121)
+L_values <- c(5, 18)
+
+all_summary_stats <- list()
+all_TestStatistics <- list()
+
+for (L in L_values) {
+  file_name <- paste0("./Data/resultsS_", L, ".Rdata")
+
+  if (file.exists(file_name)) {
+    load(file_name)
+    message(paste("Loaded existing data for L =", L))
+  } else {
+
+    TestStatistics1 <- list()
+    summary_stats <- data.frame(
+      LValue = character(),
+      SampleSize = numeric(),
+      Mean = numeric(),
+      SD = numeric()
+    )
+
+    for (s in sample.size) {
+      TestStat1 <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat1[r] <- bootstrap_al_omari_1_estimator(z, B) -
+                        (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+      }
+
+      TestStatistics1[[as.character(s)]] <- data.frame(
+        "SampleSize" = rep(s, R), 
+        "Test_Statistics" = TestStat1
+      )
+
+      summary_stats <- rbind(summary_stats, data.frame(
+        LValue = as.character(L),
+        SampleSize = s,
+        Mean = mean(TestStat1),
+        SD = sd(TestStat1)
+      )) 
+    }
+
+    all_TestStatistics[[as.character(L)]] <- TestStatistics1
+    all_summary_stats[[as.character(L)]] <- summary_stats
+
+    save(all_TestStatistics, all_summary_stats, file = file_name)
+    message(paste("Saved new results for L =", L))
+  }
+}
+
+```
+
+```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
+
+x_limits <- c(-0.5, 0.5)
+x_breaks <- seq(-0.4, 0.4, by = 0.2)
+y_limits <- c(0, 7)
+
+selected_L_values <- c(5, 18)
+
+all_plots <- list()
+
+for (L in selected_L_values) {
+  load(paste0("./Data/resultsS_", L, ".Rdata"))
+
+  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
+  combined_data$L <- L
+  combined_data$CurveOrder <- factor(combined_data$SampleSize, levels = rev(sample.size))
+  combined_data$LegendOrder <- factor(combined_data$SampleSize, levels = sample.size)
+
+  p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+  geom_line(stat = "density", linewidth = 1.5) +
+ # scale_color_brewer(palette = "Dark2", name = "Sample Size") +
+  scale_color_viridis(discrete = TRUE, option = "D", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
+  scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+  scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+  scale_y_continuous(limits = y_limits, minor_breaks = NULL) +
+  labs(
+      x = expression("Test Statistic" ~ S[widetilde(italic(H))[AO]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
+      y = "Density"
+  ) +
+  ggtitle(bquote(italic(L) == .(L))) +
+  theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
+        axis.text = element_text(size = 16),     
+        axis.title = element_text(size = 16),    
+        legend.text = element_text(size = 16),   
+        legend.title = element_text(size = 16))
+
+  # p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+  #   geom_line(stat = "density", linewidth = 1.5) +
+  #   scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
+  #   scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+  #   scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+  #   scale_y_continuous(limits = y_limits, minor_breaks = NULL) +
+  #   labs(
+  #       x = expression("Test Statistic" ~ S[widetilde(italic(T))](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
+  #       y = "Density"
+  #   ) +
+  #   ggtitle(bquote(italic(L) == .(L))) +
+  #   theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
+  #         axis.text = element_text(size = 16),     
+  #         axis.title = element_text(size = 16),    
+  #         legend.text = element_text(size = 16),   
+  #         legend.title = element_text(size = 16))
+
+  all_plots[[as.character(L)]] <- p
+}
+
+combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
+  plot_layout(guides = "collect")
+
+print(combined_plot)
+```
+
+```{r Simulated_densityR, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 10000
+mu <- 1
+B <- 50
+
+lambda <- 0.9
+
+sample.size <- c(49, 81, 121)
+L_values <- c(5, 18)
+
+all_summary_stats <- list()
+all_TestStatistics <- list()
+
+# 
+for (L in L_values) {
+
+  file_name <- paste0("./Data/resultsR_", L, ".Rdata")
+
+  if (file.exists(file_name)) {
+    load(file_name)
+    message(paste("Loaded existing data for L =", L))
+  } else {
+
+    TestStatistics1 <- list()  
+    summary_stats <- data.frame(
+      LValue = character(),
+      SampleSize = numeric(),
+      Mean = numeric(),
+      SD = numeric()
+      #Variance = numeric(),
+      #Skewness = numeric(),
+     # Kurtosis = numeric(),
+      #adpvalue = numeric()
+    )
+
+    # Para cada tamaño de muestra
+    for (s in sample.size) {
+      TestStat1 <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat1[r] <- TestStat <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) -((lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +
+                                                                        (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + log(mean(z))-log(L))
+      }
+
+      TestStatistics1[[as.character(s)]] <- data.frame(
+        "SampleSize" = rep(s, R), 
+        "Test_Statistics" = TestStat1
+      )
+
+      mean_val <- mean(TestStat1)
+      sd_val <- sd(TestStat1)
+      #var_val <- var(TestStat1)
+     # skewness_val <- skewness(TestStat1)
+     # kurtosis_val <- kurtosis(TestStat1)
+     # ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
+
+      summary_stats <- rbind(summary_stats, data.frame(
+        LValue = as.character(L),
+        SampleSize = s,
+        Mean = mean_val,
+        SD = sd_val
+      #  Variance = var_val,
+       # Skewness = skewness_val,
+       # Kurtosis = kurtosis_val,
+       # adpvalue = ad_p_value
+      )) 
+    }
+
+    all_TestStatistics[[as.character(L)]] <- TestStatistics1
+    all_summary_stats[[as.character(L)]] <- summary_stats
+
+    save(all_TestStatistics, all_summary_stats, file = file_name)
+    message(paste("Saved new results for L =", L))
+  }
+}
+
+```
+
+```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
+#fig.show="hide", 
+# eval=FALSE,  #
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
+
+x_limits <- c(-0.5, 0.5)  # Límites del eje X
+x_breaks <- seq(-0.4, 0.4, by = 0.2)  # Ticks del eje X
+y_limits <- c(0, 7)       # Límites del eje Y
+
+selected_L_values <- c(5, 18)
+
+all_plots <- list()
+
+for (L in selected_L_values) {
+  load(paste0("./Data/resultsR_", L, ".Rdata"))
+
+  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
+  combined_data$L <- L
+
+  combined_data$CurveOrder <- factor(combined_data$SampleSize, levels = rev(sample.size))
+
+  combined_data$LegendOrder <- factor(combined_data$SampleSize, levels = sample.size)
+
+  p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+    geom_line(stat = "density", linewidth = 1.5) +
+    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
+    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+    scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+    #scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
+    scale_y_continuous(limits = y_limits, minor_breaks = NULL)+
+    #scale_y_continuous(limits = y_limits) +  
+    labs(
+        x = expression("Test Statistic" ~ S[widetilde(italic(R))[lambda]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
+        y = "Density"
+    ) +
+    ggtitle(bquote(italic(L) == .(L))) +
+    theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
+          axis.text = element_text(size = 16),     
+        axis.title = element_text(size = 16),    
+        legend.text = element_text(size = 16),   
+        legend.title = element_text(size = 16)   
+          )
+
+  all_plots[[as.character(L)]] <- p
+}
+
+combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
+  plot_layout(guides = "collect")
+
+print(combined_plot)
+
+```
+
+```{r Simulated_density-tsallis2, echo=FALSE, message=FALSE}
+set.seed(1234567890, kind = "Mersenne-Twister")
+
+R <- 10000
+mu <- 1
+B <- 50
+
+lambda <- 0.9
+
+sample.size <- c(49, 81, 121)
+L_values <- c(5, 18)
+
+all_summary_stats <- list()
+all_TestStatistics <- list()
+
+# 
+for (L in L_values) {
+
+  file_name <- paste0("./Data/resultsT2_", L, ".Rdata")
+
+  if (file.exists(file_name)) {
+    load(file_name)
+    message(paste("Loaded existing data for L =", L))
+  } else {
+
+    TestStatistics1 <- list()  
+    summary_stats <- data.frame(
+      LValue = character(),
+      SampleSize = numeric(),
+      Mean = numeric(),
+      SD = numeric()
+      #Variance = numeric(),
+      #Skewness = numeric(),
+     # Kurtosis = numeric(),
+      #adpvalue = numeric()
+    )
+
+    # Para cada tamaño de muestra
+    for (s in sample.size) {
+      TestStat1 <- numeric(R)
+
+      for (r in 1:R) {
+        z <- gamma_sar_sample(L, mu, s)
+        TestStat1[r]  <- bootstrap_tsallis_entropy_optimized(z, B, lambda) -((1 - exp((1 - lambda)*log(mean(z)) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) / (lambda - 1))
+      }
+
+      TestStatistics1[[as.character(s)]] <- data.frame(
+        "SampleSize" = rep(s, R), 
+        "Test_Statistics" = TestStat1
+      )
+
+      mean_val <- mean(TestStat1)
+      sd_val <- sd(TestStat1)
+      #var_val <- var(TestStat1)
+     # skewness_val <- skewness(TestStat1)
+     # kurtosis_val <- kurtosis(TestStat1)
+     # ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
+
+      summary_stats <- rbind(summary_stats, data.frame(
+        LValue = as.character(L),
+        SampleSize = s,
+        Mean = mean_val,
+        SD = sd_val
+      #  Variance = var_val,
+       # Skewness = skewness_val,
+       # Kurtosis = kurtosis_val,
+       # adpvalue = ad_p_value
+      )) 
+    }
+
+    all_TestStatistics[[as.character(L)]] <- TestStatistics1
+    all_summary_stats[[as.character(L)]] <- summary_stats
+
+    save(all_TestStatistics, all_summary_stats, file = file_name)
+    message(paste("Saved new results for L =", L))
+  }
+}
+
+```
+
+```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
+#fig.show="hide", 
+# eval=FALSE,  #
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom",
+                  legend.text = element_text(angle = 0, vjust = 0.5)))
+
+x_limits <- c(-0.5, 0.5)  # Límites del eje X
+x_breaks <- seq(-0.4, 0.4, by = 0.2)  # Ticks del eje X
+y_limits <- c(0, 7)       # Límites del eje Y
+
+selected_L_values <- c(5, 18)
+
+all_plots <- list()
+
+for (L in selected_L_values) {
+  load(paste0("./Data/resultsT2_", L, ".Rdata"))
+
+  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
+  combined_data$L <- L
+
+  combined_data$CurveOrder <- factor(combined_data$SampleSize, levels = rev(sample.size))
+
+  combined_data$LegendOrder <- factor(combined_data$SampleSize, levels = sample.size)
+
+    p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+  geom_line(stat = "density", linewidth = 1.5) +
+  scale_color_brewer(palette = "Set1", name = "Sample Size") +
+  scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+  scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+  scale_y_continuous(limits = y_limits, minor_breaks = NULL) +
+  labs(
+      x = expression("Test Statistic" ~ S[widetilde(italic(T))[lambda]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
+      y = "Density"
+  ) +
+  ggtitle(bquote(italic(L) == .(L))) +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
+    axis.text = element_text(size = 16),     
+    axis.title = element_text(size = 16),    
+    legend.text = element_text(size = 16),   
+    legend.title = element_text(size = 16)
+  )
+
+  # p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
+  #   geom_line(stat = "density", linewidth = 1.5) +
+  #   scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
+  #   scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
+  #   scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
+  #   #scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
+  #   scale_y_continuous(limits = y_limits, minor_breaks = NULL)+
+  #   #scale_y_continuous(limits = y_limits) +  
+  #   labs(
+  #       x = expression("Test Statistic" ~ S[widetilde(italic(T))[lambda]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
+  #       y = "Density"
+  #   ) +
+  #   ggtitle(bquote(italic(L) == .(L))) +
+  #   theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
+  #         axis.text = element_text(size = 16),     
+  #       axis.title = element_text(size = 16),    
+  #       legend.text = element_text(size = 16),   
+  #       legend.title = element_text(size = 16)   
+  #         )
+
+  all_plots[[as.character(L)]] <- p
+}
+
+combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 1) +
+  plot_layout(guides = "collect")
+
+print(combined_plot)
+
+```
+
+Under the asymptotic properties of the entropy estimators [@vasicek1976test;@VanEs1992], for sufficiently large samples, $S_{\widetilde{\theta}}(\bm{Z};L)$ follows an asymptotic normal distribution:
+<!-- From the asymptotic theory of entropy estimators [@vasicek1976test;@VanEs1992], we know that for sufficiently large samples the statistic $S_{\widetilde{\theta}}(\bm{Z};L)$ converges in distribution to a normal law.
+Formally, as: -->
+$$
+  S_{\widetilde{\theta}}(\mathbf Z;L)\;
+  \overset{\mathcal{D}}{\underset{n \to \infty}{\longrightarrow}}\;
+  \mathcal N\!\bigl(\mu_S,\sigma_S^{2}\bigr),
+$$
+where ${\widetilde{\theta}\in\{\widetilde{H},\;\widetilde{R}_\lambda,\;\widetilde{T}_\lambda\}}$  and $\xrightarrow{\mathcal{D}}$ denotes convergence in distribution.
+
+Here, $\mu_S = \mathbb{E}[S_{\widetilde{\theta}}(\bm{Z};L)]$ and $\sigma^2_S = \mathrm{Var}[S_{\widetilde{\theta}}(\bm{Z};L)]$ are the theoretical mean and variance of the test statistic under $\mathcal{H}_0$.
+This asymptotic normality can be explained by noting that the entropy estimator (and hence $S_{\widetilde{\theta}}$) can be expressed as a sum or average of numerous observations; therefore, by the Central Limit Theorem and the delta method, its sampling distribution approaches a Gaussian form for large $n$.
+
+In practice, we estimate $\widehat{\mu}_S$ and $\widehat{\sigma}_S$ via Monte Carlo under $\mathcal{H}_0$.
+\begin{equation*}
+\varepsilon = \frac{{S_{\widetilde{\theta}}(\bm{Z}; L) - \widehat{\mu}_S}}{{\widehat{\sigma}_S}},
+\end{equation*} 
+which is asymptotically standard normal distributed for large $n$.
+Consequently, two-sided $p$-values are obtained as $2\Phi(-|\varepsilon|)$, where $\Phi(\cdot)$ is the cumulative distribution function of the standard normal distribution.
+<!-- Because all three tests share the same asymptotic distribution, the practical procedure is identical: compute the raw statistic, centre and scale it using $(\widehat{\mu}_S,\widehat{\sigma}_S)$, and read the $p$-value from the standard normal table—no model parameters from the alternative $\mathcal{G}^0_I$ law need to be estimated.
+-->
+
+Because all three test statistics share the same asymptotic distribution, the practical procedure is identical.
+First, the test statistic $S_{\widetilde{\theta}}(\bm{Z}; L)$ is computed for the observed data.
+Then, it is standardized using the estimated mean and standard deviation $(\widehat{\mu}_S, \widehat{\sigma}_S)$.
+Finally, the $p$-value is computed as $2\Phi(-|\varepsilon|)$.
+As shown in Figure \ref{fig:entropy-diagram-test}.
+
+```{=latex}
+\begin{figure}[H]
+    \centering
+\begin{tikzpicture}[
+  node distance=1cm and 1cm,
+  box/.style={
+    rectangle, draw=black, fill=teal!20,
+    minimum width=3cm, minimum height=1cm,
+    align=center, font=\small, text=black, font=\bfseries
+  },
+  arrow/.style={
+    -{Stealth[length=2mm, width=1.2mm]},
+    semithick,
+    shorten >=1pt, shorten <=1pt
+  }
+]
+  \node[box] (raw) {1. Compute\\test statistic\\ $S(\bm{Z})$};
+  \node[box,right=of raw] (std) {2. Standardize\\ $\varepsilon=(S-\hat\mu_S)/\hat\sigma_S$};
+  \node[box,right=of std] (pval) {3. Compute \\ $2\Phi(-|\varepsilon|)$};
+  \node[box,right=of pval] (dec) {4. Reject if\\ $p<0.05$};
+
+  \draw[arrow] (raw)  -- (std);
+  \draw[arrow] (std) -- (pval);
+  \draw[arrow] (pval) -- (dec);
+\end{tikzpicture}
+    \caption{Workflow of the entropy‐based hypothesis test: compute statistic, standardize, derive $p$-value, and decision by threshold $0.05$.}
+    \label{fig:entropy-diagram-test}
+\end{figure}
+
+```
+Importantly, no parameters from the alternative $\mathcal{G}^0_I$ model are needed, which simplifies implementation and avoids complex estimation procedures.
+
+In the next chapter, we apply this procedure to SAR images using a sliding window of size $7 \times 7$ pixels.
+For each window, we compute the corresponding test statistic and derive a $p$-value, which quantifies the statistical evidence against local homogeneity.
+High $p$-values (e.g., $p > 0.05$) indicate no significant deviation from the fully developed speckle model, suggesting homogeneity.
+Conversely, low $p$-values (e.g., $p < 0.05$)  suggest statistically significant deviations and are interpreted as heterogeneity.
+
+### Size and Power Analysis of the Proposed Tests
+
+The statistical validity and effectiveness of the proposed tests based on Shannon, Rényi, and Tsallis entropies were assessed through the analysis of two key properties: \emph{size} and \emph{power}.
+These properties provide insight into the probability of making incorrect decisions during hypothesis testing.
+
+The size of a statistical test, also known as the Type&nbsp;I error rate, refers to the probability of incorrectly rejecting the null hypothesis $\mathcal{H}_0$ when it is in fact true.
+In hypothesis testing, practitioners typically specify a nominal significance level, commonly set at \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}.
+These values define the acceptable probability of committing a Type&nbsp;I error.
+A well-calibrated test should exhibit empirical Type~I error rates that closely match the nominal levels across different sample sizes and conditions.
+
+To evaluate this, we performed a Monte Carlo simulation with $1000$ replications for each combination of sample size and number of looks $L$, under the null hypothesis $\mathcal{H}_0$, where the data follow a $\Gamma_{\text{SAR}}$ distribution with mean $\mu = 1$.
+For each replication, the corresponding test statistic was computed using a bootstrap-based entropy estimator with $B = 100$ resamples.
+In the case of the Rényi and Tsallis entropy-based tests, we used order parameters $\lambda = 0.9$ and $\lambda = 0.85$, respectively.
+The empirical size was then estimated as the proportion of replications in which the null hypothesis was incorrectly rejected.
+
+The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures.
+These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;@fig-compare_size_power_plot0.
+
+The power of a statistical test is defined as the probability of correctly rejecting the null hypothesis when it is false, that is, when the data are generated under the alternative hypothesis $\mathcal{H}_1$.
+It is mathematically given by $1 - \beta$, where $\beta$ represents the Type&nbsp;II error rate (the probability of failing to reject a false null hypothesis).
+In other words, high power indicates low probability of committing a Type II error, and reflects the test’s sensitivity to deviations from $\mathcal{H}_0$.
+
+To assess this property, we simulated data under the alternative hypothesis $\mathcal{H}_1$, assuming the $\mathcal{G}^0_I$ distribution with $\mu = 1$ and  $\alpha = -2$.
+For each combination of sample size and number of looks $L$, we performed $1000$ Monte Carlo replications.
+In each replication, the corresponding test statistic was computed using a bootstrap-based entropy estimator with $B = 100$ resamples.
+For the Rényi and Tsallis entropy-based tests, we used order parameters $\lambda = 0.9$ and $\lambda = 0.85$, respectively.
+Power was estimated as the proportion of replications in which the null hypothesis $\mathcal{H}_0$ was correctly rejected.
+
+As expected, power increased with both the sample size and the number of looks.
+This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
+The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;@fig-compare_size_power_plot0.
+
+<!-- The observed increase in power with both sample size and number of looks is theoretically justified.
+Larger sample sizes provide more information about the underlying distribution, which reduces variability in the estimation of the test statistic and improves its ability to detect departures from the null hypothesis.
+Similarly, in the context of the $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ models, a higher number of looks $L$ corresponds to less speckle noise and more stable observations.
+This leads to more reliable test statistics, further enhancing the ability of the test to distinguish between homogeneous and heterogeneous regions.
+Therefore, both increased $n$ and $L$ contribute to higher sensitivity, which is reflected in the rising power curves observed in the simulations.
+-->
+```{r Simulated_error_type_I-shannon1, echo=FALSE, message=FALSE}
+if (!file.exists("./Data/type_I_results-shannon1.Rdata")) {
+
+  message("Archivo de tamaño tipo I (Shannon) no encontrado. Generando resultados...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
+    epsilon <- test_statistic / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value < alpha_nominal)
+  }
+
+  R <- 1000
+  mu <- 1
+  B <- 50
+  L_values <- c(5, 8, 18)
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+  results <- data.frame()
+
+  for (L in L_values) {
+    for (alpha_nominal in alpha_nominals) {
+      TestStatistics <- NULL
+      mean_entropy <- numeric(length(sample_sizes))
+      sd_entropy <- numeric(length(sample_sizes))
+
+      for (s in sample_sizes) {
+        TestStat <- numeric(R)
+
+        for (r in 1:R) {
+          z <- gamma_sar_sample(L, mu, s)
+          TestStat[r] <- bootstrap_al_omari_1_estimator(z, B) -
+                         (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+        }
+
+        mean_entropy[sample_sizes == s] <- mean(TestStat)
+        sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+        TestStatistics <- rbind(
+          TestStatistics,
+          data.frame(
+            "L" = rep(L, R),
+            "Sample_Size" = rep(s, R),
+            "Test_Statistics" = TestStat
+          )
+        )
+      }
+
+      mu_W <- mean_entropy
+      sigma_W <- sqrt(sd_entropy^2)
+
+      p_values <- apply(TestStatistics, 1, function(row) {
+        calculate_p_value(
+          row["Test_Statistics"],
+          mu_W[sample_sizes == row["Sample_Size"]],
+          sigma_W[sample_sizes == row["Sample_Size"]],
+          alpha_nominal
+        )
+      })
+
+      result <- data.frame(
+        "L" = TestStatistics$L,
+        "Sample_Size" = TestStatistics$Sample_Size,
+        "Alpha_Nominal" = alpha_nominal,
+        "P_Value" = p_values
+      )
+      results <- rbind(results, result)
+    }
+  }
+
+  save(results, file = "./Data/type_I_results-shannon1.Rdata")
+
+} else {
+  message("Archivo de tamaño tipo I (Shannon) encontrado. Cargando resultados...")
+  load("./Data/type_I_results-shannon.Rdata")
+}
+```
+
+```{r Simulated_power-shannon2, echo=FALSE, message=FALSE}
+if (!file.exists("./Data/results_power-shannon2.Rdata")) {
+
+  message("Archivo de potencia (Shannon) no encontrado. Generando resultados...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
+    epsilon <- test_statistic / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value)
+  }
+
+  calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
+    mean(p_values >= alpha_nominal)
+  }
+
+  calculate_power <- function(R, mu, L_values, B, sample_sizes, alpha_nominals) {
+    results <- data.frame()
+
+    for (L in L_values) {
+      for (alpha_nominal in alpha_nominals) {
+        TestStatistics <- list()
+        mean_entropy <- numeric(length(sample_sizes))
+        sd_entropy <- numeric(length(sample_sizes))
+
+        for (s in sample_sizes) {
+          TestStat <- numeric(R)
+
+          for (r in 1:R) {
+            z <- gi0_sample(mu, -1.5, L, s)
+            TestStat[r] <- bootstrap_al_omari_1_estimator(z, B) -
+                           (log(mean(z)) + (L - log(L) + lgamma(L) + (1 - L) * digamma(L)))
+          }
+
+          mean_entropy[sample_sizes == s] <- mean(TestStat)
+          sd_entropy[sample_sizes == s] <- sd(TestStat)
+          TestStatistics[[as.character(s)]] <- TestStat
+        }
+
+        mu_W <- mean_entropy
+        sigma_W <- sqrt(sd_entropy^2)
+
+        p_values <- lapply(TestStatistics, function(TestStat) {
+          sapply(TestStat, function(stat) {
+            calculate_p_value(stat, mu_W, sigma_W[sample_sizes == as.numeric(names(TestStatistics)[1])])
+          })
+        })
+
+        type_II_error_rates <- sapply(p_values, function(pv) {
+          calculate_type_II_error_rate(pv, alpha_nominal)
+        })
+
+        power <- 1 - type_II_error_rates
+
+        result_row <- data.frame(
+          L = L,
+          alpha_nominal = alpha_nominal,
+          Sample_Size = sample_sizes,
+          power = power
+        )
+
+        results <- rbind(results, result_row)
+      }
+    }
+
+    return(results)
+  }
+
+  R <- 1000
+  mu <- 1
+  L_values <- c(5, 8, 18)
+  B <- 50
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+
+  results_power <- calculate_power(R, mu, L_values, B, sample_sizes, alpha_nominals)
+
+  save(results_power, file = "./Data/results_power-shannon2.Rdata")
+
+} else {
+  message("Archivo de potencia (Shannon) encontrado. Cargando resultados...")
+  load("./Data/results_power-shannon2.Rdata")
+}
+
+```
+
+\renewcommand{\arraystretch}{1}
+```{r Table_size_and_power-shannon3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+suppressMessages({
+  suppressWarnings({
+    load("./Data/type_I_results-shannon.Rdata")
+    type_I_error_rates <- tapply(
+      results$P_Value, 
+      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
+      FUN = function(p_values) sum(p_values) / length(p_values)
+    )
+
+    type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
+    colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
+
+    spread_results <- type_I_error_results %>%
+      pivot_wider(names_from = Alpha_Nominal, values_from = Type_I_Error_Rate)
+
+    load("./Data/results_power-shannon.Rdata")
+
+    summary_stats <- results_power %>%
+      pivot_wider(names_from = alpha_nominal, values_from = power)
+
+    combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size")) %>%
+      arrange(L, Sample_Size)
+
+    selected_columns <- c("L", "Sample_Size", grep("^0\\.", colnames(combined_results), value = TRUE))
+
+    if (length(selected_columns) == 8) {
+      combined_results <- combined_results[, selected_columns, drop = FALSE]
+      colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", 
+        "$\\hphantom{00}\\SI{1}{\\percent}$", 
+        "$\\hphantom{00}\\SI{5}{\\percent}$", 
+        "$\\hphantom{00}\\SI{10}{\\percent}$", 
+        "$\\hphantom{00}\\SI{1}{\\percent}$", 
+        "$\\hphantom{00}\\SI{5}{\\percent}$", 
+        "$\\hphantom{00}\\SI{10}{\\percent}$")
+    }
+
+    combined_results[] <- lapply(combined_results, function(x) {
+      if (is.numeric(x)) {
+        if (all(x %% 1 == 0)) {
+          sprintf("$%d$", x)
+        } else {
+          ifelse(
+            x < 0, 
+            sprintf("$%.3f$", x),
+            sprintf("$\\phantom{-}%.3f$", x)
+          )
+        }
+      } else {
+        x
+      }
+    })
+  })
+})
+
+table_combined_result <- knitr::kable(
+  combined_results,
+  caption = "Size and Power of the $S_{\\widetilde{H}}(\\bm{Z})$ test statistic (Shannon).",
+  format = "latex",
+  booktabs = TRUE,
+  align = "cccccccc",
+  escape = FALSE,
+  digits = 3,
+  label = "table_size_power_shannon",
+  centering = FALSE,
+  table.envir = "table", 
+  position="H", 
+  linesep = ""
+) %>%
+  add_header_above(c(" " = 2, "Size" = 3, "Power" = 3)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0, align = "c") %>%
+  kable_styling(latex_options = "scale_down", font_size = 10) %>%
+  kable_styling(full_width = T)
+
+print(table_combined_result)
+
+```
+
+```{r Simulated_error_type_I, echo=FALSE, message=FALSE}
+if (!file.exists("./Data/type_I_results.Rdata")) {
+
+  message("AFile type_I_results.Rdata not found. Generating results...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
+    epsilon <- test_statistic / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value < alpha_nominal)  
+  }
+
+  R <- 1000
+  mu <- 1
+  B <- 100
+  lambda <- 0.9
+  L_values <- c(5, 8, 18)
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+  results <- data.frame()
+
+  for (L in L_values) {
+    for (alpha_nominal in alpha_nominals) {
+      TestStatistics <- NULL
+      mean_entropy <- numeric(length(sample_sizes))
+      sd_entropy <- numeric(length(sample_sizes))
+
+      for (s in sample_sizes) {
+        TestStat <- numeric(R)
+
+        for (r in 1:R) {
+          z <- gamma_sar_sample(L, mu, s)
+          TestStat[r] <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) - (
+            (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) + 
+             (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) +
+            log(mean(z)) - log(L)
+          )
+        }
+
+        mean_entropy[sample_sizes == s] <- mean(TestStat)
+        sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+        TestStatistics <- rbind(
+          TestStatistics,
+          data.frame(
+            "L" = rep(L, R),
+            "Sample_Size" = rep(s, R),
+            "Test_Statistics" = TestStat
+          )
+        )
+      }
+
+      mu_W <- mean_entropy
+      sigma_W <- sqrt(sd_entropy^2)
+
+      p_values <- apply(TestStatistics, 1, function(row) {
+        calculate_p_value(
+          row["Test_Statistics"],
+          mu_W[sample_sizes == row["Sample_Size"]],
+          sigma_W[sample_sizes == row["Sample_Size"]],
+          alpha_nominal
+        )
+      })
+
+      result <- data.frame(
+        "L" = TestStatistics$L,
+        "Sample_Size" = TestStatistics$Sample_Size,
+        "Alpha_Nominal" = alpha_nominal,
+        "P_Value" = p_values
+      )
+      results <- rbind(results, result)
+    }
+  }
+
+  save(results, file = "./Data/type_I_results.Rdata")
+
+} else {
+
+  message("File type_I_results.Rdata found. Generating results...")
+  load("./Data/type_I_results.Rdata")
+
+}
+```
+
+```{r Simulated_power, echo=FALSE, message=FALSE}
+
+if (!file.exists("./Data/results_power.Rdata")) {
+
+  message("File type_I_results.Rdata not found. Generating results...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
+    epsilon <- test_statistic  / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value)
+  }
+
+  calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
+    type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
+    return(type_II_error_rate)
+  }
+
+  calculate_power <- function(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals) {
+    results <- data.frame()
+
+    for (L in L_values) {
+      for (alpha_nominal in alpha_nominals) {
+        TestStatistics <- list()
+        mean_entropy <- numeric(length(sample_sizes))
+        sd_entropy <- numeric(length(sample_sizes))
+
+        for (s in sample_sizes) {
+          TestStat <- numeric(R)
+
+          for (r in 1:R) {
+            z <- gi0_sample(mu, -2, L, s)
+            TestStat[r] <- bootstrap_renyi_entropy_estimator_v1(z, B, lambda) - (
+              (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) + 
+               (lambda * (L - 1) + 1) * log(lambda)) / (lambda - 1) + 
+              log(mean(z)) - log(L)
+            )
+          }
+
+          mean_entropy[sample_sizes == s] <- mean(TestStat)
+          sd_entropy[sample_sizes == s] <- sd(TestStat)
+          TestStatistics[[as.character(s)]] <- TestStat
+        }
+
+        mu_W <- mean_entropy  
+        sigma_W <- sqrt(sd_entropy^2)
+
+        p_values <- lapply(TestStatistics, function(TestStat) {
+          apply(
+            data.frame("Test_Statistics" = TestStat),
+            1,
+            function(row) {
+              calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
+            }
+          )
+        })
+
+        type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
+          calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
+        })
+
+        power <- 1 - type_II_error_rates
+
+        result_row <- data.frame(
+          L = L,
+          alpha_nominal = alpha_nominal,
+          Sample_Size = sample_sizes,
+          power = power
+        )
+
+        results <- rbind(results, result_row)
+      }
+    }
+
+    return(results)
+  }
+
+  R <- 1000
+  mu <- 1
+  L_values <- c(5, 8, 18)
+  B <- 100
+  lambda <- 0.9
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+
+  results_power <- calculate_power(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals)
+
+  save(results_power, file = "./Data/results_power.Rdata")
+
+} else {
+
+  message("File type_I_results.Rdata found. Generating results...")
+  load("./Data/results_power.Rdata")
+
+}
+```
+
+\renewcommand{\arraystretch}{1}
+```{r Table_size_and_power-renyi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+suppressMessages({
+  suppressWarnings({
+
+    load("./Data/type_I_results.Rdata")
+    type_I_error_rates <- tapply(
+      results$P_Value, 
+      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
+      FUN = function(p_values) sum(p_values) / length(p_values)
+    )
+
+    type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
+    colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
+
+    spread_results <- type_I_error_results %>%
+      pivot_wider(names_from = Alpha_Nominal, values_from = Type_I_Error_Rate)
+
+    load("./Data/results_power.Rdata")
+
+    summary_stats <- results_power %>%
+      pivot_wider(names_from = alpha_nominal, values_from = power)
+
+    combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size")) %>%
+      arrange(L, Sample_Size)
+
+    selected_columns <- c("L", "Sample_Size", grep("^0\\.", colnames(combined_results), value = TRUE))
+
+    if (length(selected_columns) == 8) {
+      combined_results <- combined_results[, selected_columns, drop = FALSE]
+      colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", 
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$", 
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$")
+    }
+
+    combined_results[] <- lapply(combined_results, function(x) {
+      if (is.numeric(x)) {
+        if (all(x %% 1 == 0)) {
+          sprintf("$%d$", x)  # Para enteros en formato LaTeX
+        } else {
+          ifelse(
+            x < 0, 
+            sprintf("$%.3f$", x),
+            sprintf("$\\phantom{-}%.3f$", x)
+          )
+        }
+      } else {
+        x
+      }
+    })
+
+  })
+})
+
+table_combined_result <- knitr::kable(
+  combined_results,
+  caption = "Size and Power of the $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z})$ test statistic (Rényi).",
+  format = "latex",
+  booktabs = TRUE,
+  align = "cccccccc",
+  escape = FALSE,
+  digits = 3,
+  label = "size-power-renyi",
+  centering = FALSE,
+  table.envir = "table", 
+  position="H", 
+  linesep = ""
+) %>%
+  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0, align = "c") %>%
+  kable_styling(latex_options = "scale_down", font_size = 10) %>%
+  kable_styling(full_width = T)
+
+print(table_combined_result)
+```
+
+```{r Simulated_error_type_I-tsallis1, echo=FALSE, message=FALSE}
+if (!file.exists("./Data/type_I_results-tsallis1.Rdata")) {
+
+  message("AFile type_I_results-tsallis1.Rdata not found. Generating results...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W, alpha_nominal) {
+    epsilon <- test_statistic / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value < alpha_nominal)  
+  }
+
+  R <- 500
+  mu <- 1
+  B <- 100
+  lambda <- 0.85
+  L_values <- c(5, 8, 18)
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+  results <- data.frame()
+
+  for (L in L_values) {
+    for (alpha_nominal in alpha_nominals) {
+      TestStatistics <- NULL
+      mean_entropy <- numeric(length(sample_sizes))
+      sd_entropy <- numeric(length(sample_sizes))
+
+      for (s in sample_sizes) {
+        TestStat <- numeric(R)
+
+        for (r in 1:R) {
+          z <- gamma_sar_sample(L, mu, s)
+          TestStat[r] <- bootstrap_tsallis_entropy_optimized(z, B, lambda) -((1 - exp((1 - lambda)*log(mean(z)) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) / (lambda - 1))
+        }
+
+        mean_entropy[sample_sizes == s] <- mean(TestStat)
+        sd_entropy[sample_sizes == s] <- sd(TestStat)
+
+        TestStatistics <- rbind(
+          TestStatistics,
+          data.frame(
+            "L" = rep(L, R),
+            "Sample_Size" = rep(s, R),
+            "Test_Statistics" = TestStat
+          )
+        )
+      }
+
+      mu_W <- mean_entropy
+      sigma_W <- sqrt(sd_entropy^2)
+
+      p_values <- apply(TestStatistics, 1, function(row) {
+        calculate_p_value(
+          row["Test_Statistics"],
+          mu_W[sample_sizes == row["Sample_Size"]],
+          sigma_W[sample_sizes == row["Sample_Size"]],
+          alpha_nominal
+        )
+      })
+
+      result <- data.frame(
+        "L" = TestStatistics$L,
+        "Sample_Size" = TestStatistics$Sample_Size,
+        "Alpha_Nominal" = alpha_nominal,
+        "P_Value" = p_values
+      )
+      results <- rbind(results, result)
+    }
+  }
+
+  save(results, file = "./Data/type_I_results-tsallis1.Rdata")
+
+} else {
+
+  message("File type_I_results-tsallis1.Rdata found. Generating results...")
+  load("./Data/type_I_results-tsallis1.Rdata")
+
+}
+```
+
+```{r Simulated_power-tsallis1, echo=FALSE, message=FALSE}
+
+if (!file.exists("./Data/results_power-tsallis1.Rdata")) {
+
+  message("File results_power-tsallis1 not found. Generating results...")
+
+  set.seed(1234567890, kind = "Mersenne-Twister")
+
+  calculate_p_value <- function(test_statistic, mu_W, sigma_W) {
+    epsilon <- test_statistic  / sigma_W
+    p_value <- 2 * (1 - pnorm(abs(epsilon)))
+    return(p_value)
+  }
+
+  calculate_type_II_error_rate <- function(p_values, alpha_nominal) {
+    type_II_error_rate <- sum(p_values >= alpha_nominal) / length(p_values)
+    return(type_II_error_rate)
+  }
+
+  calculate_power <- function(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals) {
+    results <- data.frame()
+
+    for (L in L_values) {
+      for (alpha_nominal in alpha_nominals) {
+        TestStatistics <- list()
+        mean_entropy <- numeric(length(sample_sizes))
+        sd_entropy <- numeric(length(sample_sizes))
+
+        for (s in sample_sizes) {
+          TestStat <- numeric(R)
+
+          for (r in 1:R) {
+            z <- gi0_sample(mu, -2, L, s)
+            TestStat[r] <- bootstrap_tsallis_entropy_optimized(z, B, lambda) -((1 - exp((1 - lambda)*log(mean(z)) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) / (lambda - 1))
+          }
+
+          mean_entropy[sample_sizes == s] <- mean(TestStat)
+          sd_entropy[sample_sizes == s] <- sd(TestStat)
+          TestStatistics[[as.character(s)]] <- TestStat
+        }
+
+        mu_W <- mean_entropy  
+        sigma_W <- sqrt(sd_entropy^2)
+
+        p_values <- lapply(TestStatistics, function(TestStat) {
+          apply(
+            data.frame("Test_Statistics" = TestStat),
+            1,
+            function(row) {
+              calculate_p_value(row["Test_Statistics"], mu_W, sigma_W[as.numeric(names(TestStatistics)) == as.numeric(s)])
+            }
+          )
+        })
+
+        type_II_error_rates <- sapply(p_values, function(p_values_for_size) {
+          calculate_type_II_error_rate(p_values_for_size, alpha_nominal)
+        })
+
+        power <- 1 - type_II_error_rates
+
+        result_row <- data.frame(
+          L = L,
+          alpha_nominal = alpha_nominal,
+          Sample_Size = sample_sizes,
+          power = power
+        )
+
+        results <- rbind(results, result_row)
+      }
+    }
+
+    return(results)
+  }
+
+  R <- 500
+  mu <- 1
+  L_values <- c(5, 8, 18)
+  B <- 100
+  lambda <- 0.85
+  sample_sizes <- c(25, 49, 81, 121)
+  alpha_nominals <- c(0.01, 0.05, 0.1)
+
+  results_power <- calculate_power(R, mu, L_values, B, lambda, sample_sizes, alpha_nominals)
+
+  save(results_power, file = "./Data/results_power-tsallis1.Rdata")
+
+} else {
+
+  message("File results_power-tsallis1.Rdata found. Generating results...")
+  load("./Data/results_power-tsallis1.Rdata")
+
+}
+```
+
+\renewcommand{\arraystretch}{1}
+```{r Table_size_and_power-tsallis0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+suppressMessages({
+  suppressWarnings({
+
+    load("./Data/type_I_results-tsallis.Rdata")
+    type_I_error_rates <- tapply(
+      results$P_Value, 
+      INDEX = list(results$L, results$Sample_Size, results$Alpha_Nominal),
+      FUN = function(p_values) sum(p_values) / length(p_values)
+    )
+
+    type_I_error_results <- as.data.frame(as.table(type_I_error_rates))
+    colnames(type_I_error_results) <- c("L", "Sample_Size", "Alpha_Nominal", "Type_I_Error_Rate")
+
+    spread_results <- type_I_error_results %>%
+      pivot_wider(names_from = Alpha_Nominal, values_from = Type_I_Error_Rate)
+
+    load("./Data/results_power-tsallis.Rdata")
+
+    summary_stats <- results_power %>%
+      pivot_wider(names_from = alpha_nominal, values_from = power)
+
+    combined_results <- merge(spread_results, summary_stats, by = c("L", "Sample_Size")) %>%
+      arrange(L, Sample_Size)
+
+    selected_columns <- c("L", "Sample_Size", grep("^0\\.", colnames(combined_results), value = TRUE))
+
+    if (length(selected_columns) == 8) {
+      combined_results <- combined_results[, selected_columns, drop = FALSE]
+      colnames(combined_results) <- c("$\\bm{L}$", "$\\bm{n}$", 
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$", 
+  "$\\hphantom{00}\\SI{1}{\\percent}$", 
+  "$\\hphantom{00}\\SI{5}{\\percent}$", 
+  "$\\hphantom{00}\\SI{10}{\\percent}$")
+    }
+
+    combined_results[] <- lapply(combined_results, function(x) {
+      if (is.numeric(x)) {
+        if (all(x %% 1 == 0)) {
+          sprintf("$%d$", x)  # Para enteros en formato LaTeX
+        } else {
+          ifelse(
+            x < 0, 
+            sprintf("$%.3f$", x),
+            sprintf("$\\phantom{-}%.3f$", x)
+          )
+        }
+      } else {
+        x
+      }
+    })
+
+  })
+})
+
+table_combined_result <- knitr::kable(
+  combined_results,
+  caption = "Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis).",
+  format = "latex",
+  booktabs = TRUE,
+  align = "cccccccc",
+  escape = FALSE,
+  digits = 3,
+  label = "size-power-tsallis",
+  centering = FALSE,
+  table.envir = "table", 
+  position="H", 
+  linesep = ""
+) %>%
+  add_header_above(c(" " = 2, "Size" = 3,  "Power" = 3)) %>%
+  collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle") %>%
+  row_spec(0, align = "c") %>%
+  kable_styling(latex_options = "scale_down", font_size = 10) %>%
+  kable_styling(full_width = T)
+
+print(table_combined_result)
+```
+
+```{r Compare_size_power_data, echo=FALSE, message=FALSE}
+library(tidyverse)
+
+load("./Data/type_I_results-shannon.Rdata")
+load("./Data/results_power-shannon.Rdata")
+type_I_shannon <- results %>%
+  group_by(L, Sample_Size, Alpha_Nominal) %>%
+  summarise(Type_I_Error = mean(P_Value), .groups = "drop") %>%
+  mutate(Entropy = "Shannon")
+
+power_shannon <- results_power %>%
+  rename(Alpha_Nominal = alpha_nominal) %>%
+  mutate(Entropy = "Shannon")
+load("./Data/type_I_results.Rdata")
+load("./Data/results_power.Rdata")
+type_I_renyi <- results %>%
+  group_by(L, Sample_Size, Alpha_Nominal) %>%
+  summarise(Type_I_Error = mean(P_Value), .groups = "drop") %>%
+  mutate(Entropy = "Rényi")
+
+power_renyi <- results_power %>%
+  rename(Alpha_Nominal = alpha_nominal) %>%
+  mutate(Entropy = "Rényi")
+
+load("./Data/type_I_results-tsallis.Rdata")
+load("./Data/results_power-tsallis.Rdata")
+type_I_tsallis <- results %>%
+  group_by(L, Sample_Size, Alpha_Nominal) %>%
+  summarise(Type_I_Error = mean(P_Value), .groups = "drop") %>%
+  mutate(Entropy = "Tsallis")
+
+power_tsallis <- results_power %>%
+  rename(Alpha_Nominal = alpha_nominal) %>%
+  mutate(Entropy = "Tsallis")
+
+# Unir Size y Power
+size_all <- bind_rows(type_I_shannon,  type_I_renyi, type_I_tsallis)
+power_all <- bind_rows(power_shannon,  power_renyi, power_tsallis)
+
+# Fusionar en tabla larga
+comparison_data <- left_join(size_all, power_all,
+                             by = c("L", "Sample_Size", "Alpha_Nominal", "Entropy"))
+```
+
+```{r fig-compare_size_power_plot0, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies.
+Size and Power for different sample sizes and $L$ values."}
+library(ggplot2)
+
+theme_set(theme_minimal() +
+            theme(text = element_text(family = "serif"),
+                  legend.position = "bottom"))
+#library(patchwork)
+
+# Gráfico 1: Size (Error tipo I)
+plot_size <- ggplot(comparison_data, aes(x = Sample_Size, y = Type_I_Error, color = Entropy)) +
+  geom_hline(yintercept = c(0.01, 0.05, 0.1), linetype = "dotted", color = "gray70", linewidth = 0.4) +
+  geom_line(linewidth = 1.2, alpha = 0.8) +
+  facet_grid(Alpha_Nominal ~ L, labeller = labeller(
+    Alpha_Nominal = function(x) paste0(x),
+    L = label_both
+  )) +
+  scale_y_continuous(breaks = seq(0, 0.15, by = 0.05), limits = c(0, 0.15)) +
+  scale_x_continuous(breaks = c(25, 49, 81, 121)) +  # <-- 
+  scale_color_brewer(palette = "Dark2") +
+  labs(
+    title = "Empirical Size (Type I Error)",
+    x = "Sample Size",
+    y = "Size",
+    color = "Entropy"
+  ) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "serif"),
+    axis.text = element_text(size = 12),
+    axis.title = element_text(size = 14),
+    legend.position = "bottom",
+    legend.box = "horizontal",
+    legend.text = element_text(size = 12),
+    legend.title = element_text(size = 12)
+  ) +
+  guides(color = guide_legend(nrow = 1))
+
+# Gráfico 2: Power
+plot_power <- ggplot(comparison_data, aes(x = Sample_Size, y = power, color = Entropy)) +
+  geom_line(linewidth = 1.2, alpha = 0.8) +
+  facet_grid(Alpha_Nominal ~ L, labeller = labeller(
+    Alpha_Nominal = function(x) paste0(x),
+    L = label_both
+  )) +
+  scale_y_continuous(breaks = seq(0.7, 1.0, by = 0.1), limits = c(0.5, 1.0)) +
+  scale_x_continuous(breaks = c(25, 49, 81, 121)) +  # 
+  scale_color_brewer(palette = "Dark2") +
+  labs(
+    title = "Empirical Power",
+    x = "Sample Size",
+    y = "Power",
+    color = "Entropy"
+  ) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "serif"),
+    axis.text = element_text(size = 12),
+    axis.title = element_text(size = 14),
+    legend.position = "bottom",
+    legend.box = "horizontal",
+    legend.text = element_text(size = 12),
+    legend.title = element_text(size = 12)
+  ) +
+  guides(color = guide_legend(nrow = 1))
+
+# Mostrar juntos (patchwork)
+(plot_size / plot_power) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+
+```

### 2025-07-01 Text/Thesis/Chapters/Chapter4.qmd
Update thesis

@@
 
-## Dataset Description
+## ANALYSIS WITH SIMULATED DATA
 
-The following steps were applied to the SAR data during pre-processing:
+Figure&nbsp;\ref{fig:sim_Phantom_1} presents the structural design of the synthetic phantom with dimensions of
+$500\times500$ pixels, proposed by  Gomez et al.&nbsp;[-@Gomez2017] as a tool to assess the performance of speckle-reduction filters.
+This layout serves as a base template to generate the simulated images shown in Figures&nbsp;\ref{fig:sim_Phantom_2}–\ref{fig:sim_Phantom_3}.
 
-1. Importing the SAR image into SNAP.  
-2. Creating a subset to focus on the area of interest.  
-3. Performing Geometric Correction, which includes Range Doppler Terrain Correction.  
-4. Exporting the processed data in ENVI format for further analysis.
+Each region is filled with data simulated from the $\mathcal{G}^0_I$ distribution&nbsp;\eqref{E:gi02}, using different combinations of the roughness parameter $\alpha$ and the mean $\mu$, as indicated by the labels in each quadrant of the image.
+Light regions correspond to textured observations (heterogeneous), while darker regions represent textureless areas (homogeneous).
+```{=latex}
+\begin{figure}[H]
+  \centering
+  \hspace{0.5em}
+  \begin{subfigure}[b]{0.37\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/Phantom1}
+    \caption{Phantom.}
+    \label{fig:sim_Phantom_1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.50\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/Phantom_labels}
+    \caption{Simulated image, varying $\alpha$ and $\mu$, with $L=5$.}
+    \label{fig:sim_Phantom_2}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.50\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/Phantom4_L9}
+    \caption{Simulated image, varying $\alpha$ and $\mu$, with $L=9$.}
+    \label{fig:sim_Phantom_3}
+  \end{subfigure}
+  \caption{Synthetic dataset.}
+  \label{fig:sim_Phantom}
+\end{figure}
+```
+The first simulated image uses $L = 5$, and the second uses $L = 9$, to evaluate how the test statistics behave as the number of looks increases and speckle noise is reduced.
 
-## Analysis with Simulated data
+The $\alpha$ parameter of the $G_I^0$ distribution is essential for
+interpreting texture characteristics. Values near zero greater than
+$-3$ suggest extremely textured targets, such as urban
+zones&nbsp;[@Frery2019a]. As the value decreases, it indicates regions
+with moderate texture (in the $\left[-6,-3\right]$ region), related to
+forest zones, while values below $-6$ correspond to textureless
+regions, such as pasture, agricultural fields, and water
+bodies&nbsp;[@Neto2023].
 
-## Analysis with SAR data
-We compare two test statistics for detecting heterogeneity in SAR data: (i) the Rényi entropy-based test, $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, described in&nbsp;\eqref{eq-test}; and (ii) the Shannon entropy-based test, $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$, which is based on the Al-Omari estimator proposed in&nbsp;[@IbrahimAlOmari2014] and was improved via bootstrap in our previous work.
-The details of this test can be found in Frery et al.&nbsp;[@Frery2024].
+We applied the three test statistics, $S_{\widetilde{H}_{\text{AO}}}$,  $S_{\widetilde{R}_{\lambda}}$, and
+$S_{\widetilde{T}_{\lambda}}$, to the simulated images using local sliding windows of size $7\times 7$.
+Figures&nbsp;\ref{fig:sim1r} and&nbsp;\ref{fig:sim2t} show the $p$-value maps (top row) and the corresponding binary maps (bottom row) for two simulations with $L=5$ and $L=9$, respectively.
+The $p$-value maps (Figures&nbsp;\ref{fig:sim1a}–\ref{fig:sim1c} and \ref{fig:sim2a}–\ref{fig:sim2c}) are displayed as gradient color maps, where dark blue tones (close to $0$) indicate strong evidence of heterogeneity, and lighter tones (toward red, near $1$) correspond to more homogeneous areas.
 
-We applied these tests to images covering urban, agricultural, and water regions. 
-We analyzed images from London, United Kingdom;  the surroundings of Munich, Germany; and  Dublin Port, Ireland, as shown in Figs.&nbsp;\ref{fig:london-a},&nbsp;\ref{fig:munich-a}, and&nbsp;\ref{fig:dublin-a}.
-All images were acquired in HH polarization.
-Table&nbsp;\ref{tab:table_param} provides the detailed acquisition parameters of these images.
+The binary maps (Figures&nbsp;\ref{fig:sim1d}–\ref{fig:sim1f} and \ref{fig:sim2d}–\ref{fig:sim2f}) simplify these results using a threshold of $0.05$: pixels corresponding to $p$-values below this threshold are shown in black, suggesting statistically significant deviations and thus indicating heterogeneity.
+In contrast, pixels with $p \geq 0.05$ are displayed in white, representing no evidence to reject the null hypothesis of homogeneity.
 
-\renewcommand{\arraystretch}{3}   
+```{=latex}
+\begin{figure}[hbt]
+    \centering
+
+    % Primera fila
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_b200_w7-AO.png}
+        \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sim1a}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_0.9_b200_w7-renyi.png}
+        \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sim1b}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_0.85_b200_w7-tsallis77.png}
+        \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sim1c}
+    \end{subfigure}
+
+    \vspace{1em} % Espacio entre filas
+
+    % Segunda fila
+    \hspace{-2.5em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_b200_w7-AO.png}
+        \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sim1d}
+    \end{subfigure}
+    \hspace{2.8em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_0.9_b200_w7-renyi.png}
+        \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sim1e}
+    \end{subfigure}
+     \hspace{3.1em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_0.85_b200_w7-tsallis.png}
+        \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sim1f}
+    \end{subfigure}
+    \caption{Results on simulated data ($L = 5$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
+Top: $p$-value heatmaps.
+Bottom: binary maps ($5\%$ level).}
+%\caption{Comparison of test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on a simulated image with $L = 5$.
+Top row: heatmaps of $p$-values computed using a $7 \times 7$ sliding window.
+Bottom row: binary maps at the 5\% significance level, where black pixels indicate rejection of the null hypothesis of homogeneity.}
+    \label{fig:sim1r}
+\end{figure}
+```
+
+```{=latex}
+\begin{figure}[hbt]
+    \centering
+
+    % Primera fila
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_b100_w7-AO-H.png}
+        \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sim2a}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_b100_w7-09-renyi.png}
+        \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sim2b}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_0.85_b100_w7-tsallis.png}
+        \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sim2c}
+    \end{subfigure}
+
+    \vspace{1em} % Espacio entre filas
+
+    % Segunda fila
+    \hspace{-1.6em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_b100_w7-AO.png}
+        \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sim2d}
+    \end{subfigure}
+    \hspace{3.0em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_b100_w7-09-renyi.png}
+        \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sim2e}
+    \end{subfigure}
+     \hspace{3.1em}
+    \begin{subfigure}{0.25\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_0.85_b100_w7-tsallis.png}
+        \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sim2f}
+    \end{subfigure}
+    \caption{Results on simulated data ($L = 9$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
+Top: $p$-value heatmaps.
+Bottom: binary maps ($5\%$ level).}
+   %  \caption{Comparison of test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on a simulated image with $L = 9$.
+Top row: heatmaps of $p$-values computed using a $7 \times 7$ sliding window.
+Bottom row: binary maps at the 5\% significance level, where black pixels indicate rejection of the null hypothesis of homogeneity.}
+    \label{fig:sim2t}
+\end{figure}
+```
+
+When the number of looks increases to $L=9$ (Figure&nbsp;\ref{fig:sim2t}), the maps become cleaner due to reduced speckle.
+All tests are able to detect zones with different levels of texture.
+However, some differences can be observed.
+The statistic $S_{\widetilde{R}_{\lambda}}$, based on Rényi entropy, is very sensitive to changes in texture and often highlights small variations and detailed patterns of heterogeneity.
+In contrast, $S_{\widetilde{T}_{\lambda}}$, based on Tsallis entropy, tends to avoid false detections in uniform areas and produces cleaner results.
+This is due to the underlying formulation: Rényi entropy emphasizes variability, making it effective in identifying heterogeneity; while Tsallis entropy is more robust to noise, which helps preserve homogeneous regions.
+
+## APPLICATIONS TO SAR DATA
+
+### SAR dataset and preprocessing {#sec:SAR-data}
+
+We evaluated the proposed test statistics using a set of eight SAR images acquired from different radar missions.
+These images cover diverse locations: the surroundings of London (United Kingdom), San Francisco (USA), Rotterdam (Netherlands), the outskirts of Munich and the city of New Orleans (USA), Dublin Port (Ireland), the coast of Jalisco (Mexico), and the area around Foggia (Italy) as shown in Figures&nbsp;\ref{fig:london-sar}-\ref{fig:fo-sar}.
+The selected scenes include a variety of land types, such as urban zones, mountainous areas, agricultural regions, and water bodies.
+This diversity allows us to assess the performance of the proposed statistical tests under different texture conditions.
+
+To help interpret the SAR images, we also included corresponding optical images (Figures&nbsp;\ref{fig:london-optical}-\ref{fig:fo-optical}) obtained from Sentinel-2 Level-2A products.
+These optical scenes were acquired on dates close to those of the SAR acquisitions to ensure visual consistency.
+The optical data were  downloaded from the Copernicus Data Space platform\footnote{\url{https://dataspace.copernicus.eu/}}.
+
+The SAR images come from different missions: TanDEM-X, PAZ, and ICEYE (all operating in the X-band), UAVSAR (L-band), and Sentinel-1B (C-band).
+The two UAVSAR images were obtained from the Alaska Satellite Facility (ASF) platform\footnote{\url{https://search.asf.alaska.edu/}}, which provides access to airborne and satellite SAR data.
+The remaining images were downloaded from the European Space Agency’s Third Party Missions (ESA TPM) data service\footnote{\url{https://tpm-ds.eo.esa.int/collections/}}, which offers SAR products from various external missions operated by international partners and commercial providers.
+All images are single-polarization (HH or VV), and their acquisition parameters vary in resolution, scene size, and number of looks.
+
+Table&nbsp;\ref{tab:table_param} summarizes the main characteristics of each SAR image, including the spatial resolution, acquisition date, and number of looks.
+
+\renewcommand{\arraystretch}{2}   
 ```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}
@@
 SAR_data <- data.frame(
-  Site = c("London", "Munich", "Dublin" ),
-  Mission = c("TanDEM-X", "UAVSAR", "TanDEM-X"),
-  Band = c("X", "L", "X"),
-  Size = c("$2000\\times2000$", "$1024\\times1024$", "$1100\\times1100$"),
-  L = c(1, 12, 16),
-  Resol = c("$0.99/0.99$", "$4.9/7.2$", "$1.35/1.35$"),
-  Date = c("12-11-2021", "16-04-2015", "03-09-2017")
+  Site = c("London", "San Francisco",  "Rotterdam", "Munich","New Orleans", "Dublin","Coast of Jalisco", "Foggia" ),
+  Mission = c("TanDEM-X", "PAZ", "TanDEM-X","UAVSAR", "UAVSAR", "TanDEM-X", "Sentinel-1B", "Iceye"),
+  Band = c("X",  "X","X","L","L", "X", "C", "X"),
+  Polarization = c("HH", "HH", "HH","HH","HH","HH", "VV", "VV"),
+  Size = c("$2000\\times2000$", "$3300\\times3300$",  "$1200\\times1200$", "$1024\\times1024$","$1400\\times1400$", "$1100\\times1100$","$512\\times512$","$1900\\times1900$"),
+  L = c(1, 1, 9, 12, 12,  16,18, 24),
+  Resol = c("$0.99/0.99$", "$1.84/1.84$",   "$2.5/2.5$", "$4.9/7.2$","$4.9/7.2$", "$1.35/1.35$","$40/40$", "$2.08/2.08$"),
+  Date = c("12-11-2021","30-07-2020","06-12-2018", "16-04-2015","13-03-2016", "03-09-2017","29-08-2021","28-03-2024")
 )
@@
 colnames(SAR_data) <- c(
-  "\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", 
+  "\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Band}", "\\textbf{Polarization}",
   "\\textbf{Size (pixels)}", "$\\bm{L}$", 
@@
       booktabs = TRUE,
-      align = "ccccccc",
+      align = "cccccccc",
       escape = FALSE,
@@
   kable_styling(full_width = TRUE) %>%
-  column_spec(1, width = "3.0cm") %>%
+  column_spec(1, width = "3.8cm") %>%
   column_spec(2, width = "3.7cm") %>%
-  column_spec(3, width = "1.5cm") %>%
-  column_spec(4, width = "4cm") %>%
-  column_spec(5, width = "1.5cm") %>%
-  column_spec(6, width = "4.0cm") %>%
-  column_spec(7, width = "4.5cm")
+  column_spec(3, width = "2.5cm") %>%
+  column_spec(4, width = "3.5cm") %>%
+  column_spec(5, width = "4cm") %>%
+  column_spec(6, width = "2.5cm") %>%
+  column_spec(7, width = "4.0cm") %>%
+  column_spec(8, width = "4.5cm")
 
 ```
-We used sliding windows of size $7\times 7$.
-The results are presented as $p$-value maps and binary maps at a $0.05$ significance level. 
-Figs.&nbsp;\ref{fig:london-b}--\ref{fig:london-c},&nbsp;\ref{fig:munich-b}--\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-b}--\ref{fig:dublin-c} correspond to $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, while Figs.&nbsp;\ref{fig:london-d}--\ref{fig:london-e},&nbsp;\ref{fig:munich-d}--\ref{fig:munich-e}, and&nbsp;\ref{fig:dublin-d}--\ref{fig:dublin-e} correspond to $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$.
 
-The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces.
-The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions). 
-In contrast, black areas represent regions with $p$-values below $0.05$, providing statistical evidence to reject the null hypothesis and indicating heterogeneity.
+For each SAR image, the number of looks $L$ was obtained from the
+product of azimuth and range looks provided in the metadata of SNAP. We
+validated this nominal value with the equivalent number of looks (ENL)
+from manually selected homogeneous areas using the classical formula
+$\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the sample
+coefficient of variation. The results were consistent with the metadata.
+We also verified that moderate deviations in $L$ did not significantly
+impact the outcome of the test, confirming the robustness of the
+proposed method.
 
-The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
+The SAR images were preprocessed using the SNAP (Sentinel Application Platform) toolbox.
+The standard steps included terrain correction and multilooking (when necessary) to produce intensity images.
+UAVSAR scenes were also reprojected to align them with standard geographic coordinates.
+Finally, the resulting images were exported in ENVI format and used as input for statistical analysis in \texttt{R}, where the proposed tests were applied.
+
+### Qualitative Inspection {#qualitative-inspection}
+
+We applied the three bootstrap statistics
+$S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$ and
+$S_{\widetilde{T}_{\lambda}}$ to eight intensity images as shown Figures&nbsp;\ref{fig:london-sar}-\ref{fig:fo-sar} using $7\times 7$ local sliding windows. Each figure is organised in three rows:
+the first row displays the SAR scene and a matching Sentinel-2
+optical image, the second row shows heat-maps of the
+$p$-values produced by the three tests, and the third row presents the
+binary decisions at the $5\%$ significance level
+(black $\,=\,$ heterogeneous, white $\,=\,$ homogeneous).
+
+Across all scenes the three tests identify the main textured elements
+(urban blocks, harbor facilities, roads, crop boundaries, mountainous areas, and river
+banks).  In the $p$-value heat-maps dark-blue tones
+($p\!<\!0.05$) cluster over these features, whereas red tones
+($p\!\approx\!1$) dominate smooth areas such as open water, uniform
+pasture or crop areas.  The corresponding binary maps make this pattern explicit, delineating heterogeneous areas with a black mask.
+
+The London and San Francisco images, acquired with $L=1$, exhibit strong speckle, making heterogeneity detection more difficult. 
+Among the three tests, the Rényi-based statistic $S_{\widetilde{R}{\lambda}}$ offers the most informative response: its $p$-value maps show dark-blue tones over heterogeneous regions and strong red tones ($p \approx 1$) over clearly homogeneous areas such as water bodies and smooth crop zones.
+In contrast, the Shannon and Tsallis-based tests produce $p$-value maps with softer, intermediate colors, which makes it harder to clearly distinguish between textured and smooth areas.
+Although the binary maps look generally similar, $S_{\widetilde{R}_{\lambda}}$ gives more precise and reliable detections, even under strong speckle.
+
+As the number of looks increases (Rotterdam, Munich and
+the remaining images) speckle is reduced and all tests
+improve, but differences persist:
+$S_{\widetilde{R}_{\lambda}}$ keeps the highest sensitivity to
+texture changes, whereas $S_{\widetilde{T}_{\lambda}}$ produces the
+cleanest white regions, indicating a stronger ability to preserve
+truly homogeneous surfaces.  $\:S_{\widetilde{H}_{\text{AO}}}$ shows an
+intermediate behaviour.
+
+These results mirror the properties already observed with simulated
+data.  The Rényi-based statistic reacts quickly to any local
+fluctuation, making it very effective for spotting heterogeneity even
+under severe speckle.  The Tsallis-based test is
+more conservative: it suppresses small, noisy variations and therefore
+preserves large homogeneous patches, while still detecting clear
+textural boundaries.  The Shannon-based test offers a balanced
+compromise but is less robust when $L$ is very low.
+
+<!-- The three statistical tests are applied to the SAR images using -->
+<!-- $7\times 7$ local sliding windows. This window size balances detailed -->
+<!-- local information and sufficient number of data points. -->
+
+<!-- The $p$-values obtained for each test are presented in -->
+<!-- Figures~\ref{fig:Rotterdam_pvalue}, \ref{fig:Mexico_pvalue}, -->
+<!-- \ref{fig:lake_pvalue} and~\ref{fig:Illinois_crops_pvalue}, respectively. -->
+
+<!-- In Figures~\ref{fig:Rotterdam_0.05}, \ref{fig:Mexico_crops_0.05}, -->
+<!-- \ref{fig:lake_0.05} and~\ref{fig:Illinois_crops_0.05}, the maps of -->
+<!-- $p$-values composed of a linear gradient of black and white colors, -->
+<!-- represent the decisions at a \SI{5}{\percent} significance level. Dark -->
+<!-- areas represent values below $0.05$, indicating evidence to reject the -->
+<!-- null hypothesis and suggesting heterogeneity in these regions. In -->
+<!-- contrast, values above 0.05 are represented as white areas, indicating -->
+<!-- no evidence to reject the fully-developed speckle hypothesis. -->
+
+<!-- We used sliding windows of size $7\times 7$. -->
+<!-- The results are presented as $p$-value maps and binary maps at a $0.05$ significance level.  -->
+<!-- Figs.&nbsp;\ref{fig:london-b}--\ref{fig:london-c},&nbsp;\ref{fig:munich-b}--\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-b}--\ref{fig:dublin-c} correspond to $S_{\widetilde{H}_{\lambda}}(\bm{Z}; L)$, while Figs.&nbsp;\ref{fig:london-d}--\ref{fig:london-e},&nbsp;\ref{fig:munich-d}--\ref{fig:munich-e}, and&nbsp;\ref{fig:dublin-d}--\ref{fig:dublin-e} correspond to $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$.
+-->
+
+<!-- The $p$-value maps use a color gradient, where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces. -->
+<!-- The binary maps classify these results: white areas represent $p$-values greater than $0.05$, indicating no statistical evidence to reject the null hypothesis (homogeneous regions).  -->
+<!-- In contrast, black areas represent regions with $p$-values below $0.05$, providing statistical evidence to reject the null hypothesis and indicating heterogeneity. -->
+
+<!-- The Rényi entropy-based test demonstrated greater sensitivity in detecting textural variations than the Shannon-based test due to the flexibility provided by the parameter $\lambda$, as observed in the binary maps in Figs.&nbsp;\ref{fig:london-c},&nbsp;\ref{fig:munich-c}, and&nbsp;\ref{fig:dublin-c}.
+-->
 
@@
     \centering
-    % First row: main SAR image
-        \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/london_optical_.png}
-        \caption*{(a) Optical image}
-        \label{fig:london-a}
-    \end{minipage}
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/london_2000.png}
-        \caption*{(b) SAR image}
-        \label{fig:london-b}
-    \end{minipage}
-    \vspace{1em} % Space between rows
-        % Second row: p-value maps
-\begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_london_Shannon_c1.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:london-c}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/london_2000.png}
+        \caption{SAR image}
+        \label{fig:london-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/london_optical_.png}
+        \caption{Optical image}
+        \label{fig:london-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_shannon-london_H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:london-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_renyi-london_H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:london-shann-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_tsallis-london_H1_new.png} % <--
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:london-tsallis1}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.30\textwidth}
         \includegraphics[width=\linewidth]{Figures/H_005_london_shannon.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:london-d}
-    \end{minipage}
-        \vspace{1em} % Space between rows
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:london-005-shann2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.30\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_london_renyi_L1_.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:london-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.30\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_london1_TSALLIS.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:london-005-tsallis2}
+    \end{subfigure}
 
-    % Third row: binary maps
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_london_renyi.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:london-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_london_renyi_L1_.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:london-f}
-    \end{minipage}
-    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
+    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
     \label{fig:london}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.85\textwidth]{Figures/munich_optical1.png}
-        \caption*{(a) Optical image}
-        \label{fig:munich-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/SF_3300.png}
+        \caption{SAR image}
+        \label{fig:sf-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.295\textwidth}
+        \includegraphics[width=\linewidth]{Figures/san-francisco-optical1.png}
+        \caption{Optical image}
+        \label{fig:sf-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_results_SF_AO_w7.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sf-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/munich_1024.png}
-        \caption*{(b) SAR image}
-        \label{fig:munich-b}
-    \end{minipage}
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_SF_3300_renyi_w7_3_L1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sf-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-valuesL1_SanFrancisco_tsallis_b100_w7s.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sf-tsallis1}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
+    \vspace{1.2em}
 
-    % Second row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_muni_Shan22.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:munich-c}
-    \end{minipage}
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.30\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_results_ENVI_SF_3300_L1_AO_w7.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:sf-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_munich_sh_AO_L12.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:munich-d}
-    \end{minipage}
+    \begin{subfigure}{0.30\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_SF_3300_renyi_w7_3_L1.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:sf-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.30\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L1_SanFrancisco_tsallis_b100_w7_.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:sf-005-tsallis2}
+    \end{subfigure}
 
-\vspace{1em} % Space between rows
-
-    % Third row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_muni_renyi.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:munich-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_munich_renyi.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:munich-f}
-    \end{minipage}
-    \caption{Detection of heterogeneous areas in a SAR image over Munich, Germany: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:munich}
+    \caption{Detection of heterogeneous areas in a SAR image over San Francisco, USA: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:sf}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/dublin.png}
-        \caption*{(a) Optical image}
-        \label{fig:dublin-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/rotterdam_1200_L9_2.png}
+        \caption{SAR image}
+        \label{fig:rott-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/rotterdam_optical2.png}
+        \caption{Optical image}
+        \label{fig:rott-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_envi_Rotterdam2_size_1200_AO_w7_b100-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:rott-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/dublin_1100_hh.png}
-        \caption*{(b) SAR image}
-        \label{fig:dublin-b}
-    \end{minipage}
-    \vspace{1em} % Space between rows
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L16_L9_envi_Rotterdam2_sizeRENYI_1200-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:rott-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_Rotterdam2_1200_tsallis_085_B100-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:rott-tsallis1}
+    \end{subfigure}
 
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/AO_w7_L16_b100.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:dublin-c}
-    \end{minipage}
+    \vspace{1.2em}
+
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_L9_envi_Rotterdam2_size_1200_AO_w7_b100.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:rott-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_AO_w7_L16_b100.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:dublin-d}
-    \end{minipage}
-    \vspace{0.9em} % Space between rows
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L16_L9_envi_Rotterdam2_sizeRENYI_1200.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:rott-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L9_Rotterdam2_1200_tsallis_lambda85_B100.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:rott-005-tsallis2}
+    \end{subfigure}
 
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/dublin_renyi_09_w7_b100.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:dublin-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_dublin_renyi_09_w7_b100.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:dublin-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:dublin}
+    \caption{Detection of heterogeneous areas in a SAR image over Rotterdam, Netherlands: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:rott}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/foggia-italy-optical.png}
-        \caption*{(a) Optical image}
-        \label{fig:Foggia-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/munich_1024.png}
+        \caption{SAR image}
+        \label{fig:mun-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/munich_optical.png}
+        \caption{Optical image}
+        \label{fig:mun-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_shannon-munich-H.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:mun-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/foggia-italy_1900.png}
-        \caption*{(b) SAR image}
-        \label{fig:Foggia-b}
-    \end{minipage}
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_renyi-munich-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:mun-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values__tsallis_lambda85_B100-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:mun-tsallis1}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
+    \vspace{1.2em}
 
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_italy_AO_1900-H.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:Foggia-c}
-    \end{minipage}
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_shannon_munich.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:mun-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_AO_italy_1900.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:Foggia-d}
-    \end{minipage}
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_renyi_munich.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:mun-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005L12_envi_munich_size_1024_tsallis_lambda85_B100.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:mun-005-tsallis2}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
-
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_Renyi_Italy_1900_H.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:Foggia-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_renyi_italy_1900_L1.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:Foggia-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over Foggia, Italy: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:Foggia}
+    \caption{Detection of heterogeneous areas in a SAR image over the outskirts
+of Munich, Germany: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:mun}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/san-francisco-optical1.png}
-        \caption*{(a) Optical image}
-        \label{fig:san-francisco-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/NewOrleans_1400.png}
+        \caption{SAR image}
+        \label{fig:no-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.27\textwidth}
+        \includegraphics[width=\linewidth]{Figures/new-orleans-optical.png}
+        \caption{Optical image}
+        \label{fig:no-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_shannon-New_or-H.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:no-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{Figures/SF_3300.png}
-        \caption*{(b) SAR image}
-        \label{fig:san-francisco-b}
-    \end{minipage}
-    \vspace{1em} % Space between rows
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_renyi-New_or-H.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:no-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L_12_New_orleans_size_1400_tsallis_lambda085_B100-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:no-tsallis1}
+    \end{subfigure}
 
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_SF_AO_3300_H.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-francisco-c}
-    \end{minipage}
+    \vspace{1.2em}
+
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_NewOrleans_1400_AO.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:no-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_AO_SF_3300_L1_3.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-francisco-d}
-    \end{minipage}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_NewOrleans_1400_renyi.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:no-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_L_12_New_orleans_size_1400_tsallis_lambda085_B100.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:no-005-tsallis2}
+    \end{subfigure}
 
-    \vspace{0.9em} % Space between rows
-
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.3\textwidth]{Figures/H_pvalue_renyi_SF_3300_H2_L1_3.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-francisco-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=\linewidth]{Figures/H_005_renyi_SF_3300_L1_3.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-francisco-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over San Francisco, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:san-francisco}
+    \caption{Detection of heterogeneous areas in a SAR image over New Orleans city, USA: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:NO}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.8\textwidth]{Figures/new-orleans-optical.png}
-        \caption*{(a) Optical image}
-        \label{fig:new-orleans-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/dublin_1100.png}
+        \caption{SAR image}
+        \label{fig:no-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/dublin.png}
+        \caption{Optical image}
+        \label{fig:du-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_AO_1100-dublin-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:no-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.85\textwidth]{Figures/NewOrleans_1400.png}
-        \caption*{(b) SAR image}
-        \label{fig:new-orleans-b}
-    \end{minipage}
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_renyi_1100-dublin-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:du-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L16_envi_dublin_size_1100_tsallis_lambda085_B100-H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:du-tsallis1}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
+    \vspace{1.2em}
 
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_NewOrleans_1400_AO-H.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:new-orleans-c}
-    \end{minipage}
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_dublin_AO_1100.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:du-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_NewOrleans_1400_AO.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:new-orleans-d}
-    \end{minipage}
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_dublin_renyi_1100.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:du-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.28\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L16_envi_dublin_size_1100_tsallis_lambda085_B100.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:du-005-tsallis2}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
-
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_NewOrleans_1400_renyi-H.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:new-orleans-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_NewOrleans_1400_renyi.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:new-orleans-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over New Orleans city, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:new-orleans}
+    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:du}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.47\textwidth}
-        \centering
-        \includegraphics[width=0.8\textwidth]{Figures/san-diego-optical.png}
-        \caption*{(a) Optical image}
-        \label{fig:san-diego-a}
-    \end{minipage}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/mexico_512.png}
+        \caption{SAR image}
+        \label{fig:ja-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/mexico2_512.png}
+        \caption{Optical image}
+        \label{fig:ja-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_results_Mexico_512_7_AO_300b11.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:ja-shann1}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.85\textwidth]{Figures/sandiego_1300.png}
-        \caption*{(b) SAR image}
-        \label{fig:san-diego-b}
-    \end{minipage}
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L16_envi_mexico_512_renyi_lambda09_B200.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:ja-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L18_envi_mexico_tsallis_lambda085_B200_w7__H1.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:ja-tsallis1}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
+    \vspace{1.2em}
 
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_sandiego_1300_AO-A.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-diego-c}
-    \end{minipage}
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_results_Mexico_512_7_AO_300b.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:ja-005-shann2}
+    \end{subfigure}
     \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_sandiego_1300_AO.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-diego-d}
-    \end{minipage}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/0.05_L16_envi_mexico_512_renyi_lambda09_B200.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:ja-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L18_envi_mexico_tsallis_lambda085_B200_w7_.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:ja-005-tsallis2}
+    \end{subfigure}
 
-    \vspace{1em} % Space between rows
-
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_SanDiego_1300_renyi-A.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-diego-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\linewidth]{Figures/H_005_sandiego_1300_renyi.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-diego-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over San Diego city, USA: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:san-diego}
+    \caption{Detection of heterogeneous areas in a SAR image over the Coast of Jalisco, Mexico: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:ja}
 \end{figure}
-
 ```
@@
     \centering
-    % First row: SAR image
-    \begin{minipage}{0.47\textwidth}
+
+    % Primera fila: 2 imágenes
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\linewidth]{Figures/foggia-italy_1900.png}
+        \caption{SAR image}
+        \label{fig:fo-sar}
+    \end{subfigure}
+    \hspace{2em}
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/foggia-italy-optical.png}
+        \caption{Optical image}
+        \label{fig:fo-optical}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_shannon-Foggia-H_77.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:fo-shann1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_renyi-foggiaH-new.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:du-renyi1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.31\textwidth}
+        \includegraphics[width=\linewidth]{Figures/p-values_L24_Foggia1900_tsallis_lambda085_B100aa.png}
+        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:fo-tsallis1}
+    \end{subfigure}
+
+    \vspace{1.2em}
+
+    % Tercera fila: 3 imágenes (binary maps)
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_AO_italy_1900.png}
+        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \label{fig:fo-005-shann2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_renyi_italy_1900_L1.png}
+        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \label{fig:du-005-renyi2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.29\textwidth}
+        \includegraphics[width=\linewidth]{Figures/H_005_L24_envi_Foggia_size_1900_tsallis_lambda085_B100.png} %
+        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \label{fig:fo-005-tsallis2}
+    \end{subfigure}
+
+    \caption{Detection of heterogeneous areas in a SAR image over  Foggia, Italy: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: input images.
+Middle: $p$-value maps.
+Bottom: binary maps (\SI{5}{\percent} level).}
+    \label{fig:du}
+\end{figure}
+```
+
+Overall, the experiments on real SAR images confirm the simulated
+findings: for highly speckled data ($L\!\approx\!1$) the Rényi
+statistic is the most reliable detector of heterogeneity, whereas for
+multi-look products the Tsallis statistic delivers cleaner segmentations
+with fewer false positives.
+
+Window size also plays an important role in the detection process. Although not shown in this work, we explored alternative sliding windows
+of $5\times5$ ($n=25$) and $9\times9$ ($n=81$) on both simulated and real SAR data. 
+The smaller window tended to miss heterogeneous features, especially in 
+single–look images where few pixels are available. 
+In contrast, larger windows occasionally led to over-detection, particularly 
+on multi-look scenes, where homogeneous regions were sometimes misclassified 
+as heterogeneous. Based on these observations and prior recommendations in the literature, 
+we adopted $7\times7$ ($n=49$) as a compromise that preserves local detail 
+while ensuring statistical stability for bootstrap estimation.
+
+In the specific case of $L=1$, we observed that larger windows 
+(e.g., $9\times9$) produced more consistent detection, particularly for 
+the Tsallis-based test, improving sensitivity without excessive false alarms.
+
+### Quantitative Evaluation
+
+Eight polygonal regions of interest (ROIs) were manually selected for each of the three SAR scenes chosen for quantitative evaluation, London, Munich, and Dublin (Figures \ref{fig:london-sar-roi1}–\ref{fig:dublin-sar-roi1}).
+These ROIs correspond to heterogeneous areas (red, class 1) and homogeneous areas (blue, class 0).
+The polygons were rasterized to match the spatial resolution of each SAR image, forming a partial ground truth.
+We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared these decision maps with the ground truth to compute the F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
+Table \ref{tab:table_metrics1} summarizes the results.
+
+```{=latex}
+\begin{figure}[H]
     \centering
-        \includegraphics[width=0.85\textwidth]{Figures/rotterdam_optical.png}
-        \caption*{(a) Optical image}
-        \label{fig:san-diego-a}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.48\textwidth}
-        \centering
-        \includegraphics[width=0.85\textwidth]{Figures/rotterdam.png}
-        \caption*{(b) SAR image}
-        \label{fig:san-diego-b}
-    \end{minipage}
-
-    \vspace{1em} % Space between rows
-
-    % Third row: p-value and binary for Shannon AO
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_rotterdam1_1200_AO-B.png}
-        \caption*{(c) $p$-value map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-diego-c}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.85\linewidth]{Figures/H_005_rotterdam_AO_L9_B100_1.png}
-        \caption*{(d) Binary map for $S_{\widetilde{H}_{\text{AO}}}$}
-        \label{fig:san-diego-d}
-    \end{minipage}
-
-    \vspace{1em} % Space between rows
-
-    % Second row: p-value and binary for Renyi
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=1.2\textwidth]{Figures/H_pvalue_rotterdam1_renyi_1200-B.png}
-        \caption*{(e) $p$-value map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-diego-e}
-    \end{minipage}
-    \hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.85\linewidth]{Figures/H_005_renyi_rotterdam1_B100_09.png}
-        \caption*{(f) Binary map for $S_{\widetilde{H}_{\lambda}}$}
-        \label{fig:san-diego-f}
-    \end{minipage}
-
-    \caption{Detection of heterogeneous areas in a SAR image over Rotterdam, Netherlands: comparison with the tests $S_{\widetilde{H}_{\text{AO}}}$ and $S_{\widetilde{H}_{\lambda}}$.}
-    \label{fig:san-diego}
+    % London
+    \begin{subfigure}{0.33\textwidth}
+        \includegraphics[width=\linewidth]{Figures/london_roi.png}
+        \caption{London SAR image with selected ROIs.}
+        \label{fig:london-sar-roi1}
+    \end{subfigure}
+   \hspace{4em} 
+    % Munich
+    \begin{subfigure}{0.33\textwidth}
+        \includegraphics[width=\linewidth]{Figures/munich_roi.png}
+        \caption{Munich SAR image with selected ROIs.}
+        \label{fig:munich-sar-roi1}
+    \end{subfigure}
+    \vspace{1.8em}
+    % Dublin
+    \begin{subfigure}{0.33\textwidth}
+        \includegraphics[width=\linewidth]{Figures/dublin_roi3.png}
+        \caption{Dublin SAR image with selected ROIs.}
+        \label{fig:dublin-sar-roi1}
+    \end{subfigure}
+    \caption{Selected ROIs for the quantitative evaluation. Red polygons indicate heterogeneous areas (class 1), and blue polygons indicate homogeneous areas (class 0).}
+    \label{fig:roi-scenes}
 \end{figure}
@@
 ```
+
+When comparing the three entropy-based tests, distinct patterns emerge depending on the scene characteristics.
+In London, the Rényi-based test produced the best performance across all metrics ($F_1$: 0.695; $\kappa$: 0.626; OA: 0.877), outperforming both Shannon and Tsallis.
+This suggests that Rényi entropy is particularly robust under strong speckle conditions, as is typical in single-look SAR imagery.
+
+In contrast, in the Munich and Dublin scenes, where the image quality is higher and speckle is reduced, the Tsallis-based test achieved the highest scores across all three metrics.
+Specifically, in Munich, Tsallis achieved $F_1 = 0.930$, $\kappa = 0.871$, and OA = 0.936, marginally outperforming Rényi.
+Similarly, in Dublin, Tsallis led with $F_1 = 0.879$, $\kappa = 0.776$, and OA = 0.887.
+These results indicate that Tsallis entropy may be more sensitive to finer textural differences in lower-speckle environments.
+
+The Shannon-based test consistently yielded the lowest scores across all scenes, suggesting that it is less effective at distinguishing between heterogeneous and homogeneous regions under the tested conditions.
+Overall, the results demonstrate that Rényi and Tsallis entropies are both strong detectors of heterogeneity, with Rényi showing advantages in noisy contexts, and Tsallis offering improved discrimination in scenes with more subtle textural variations.
+
+\renewcommand{\arraystretch}{1.1} 
+```{r metrics_table_k, echo=FALSE, message=FALSE, warning=FALSE}
+
+# 
+load("./Data/metrics_london_shannon.RData")
+load("./Data/metrics_london_renyi.RData")
+load("./Data/metrics_london_tsallis.RData")
+
+load("./Data/metrics_munich_shannon.RData")
+load("./Data/metrics_munich_renyi.RData")
+load("./Data/metrics_munich_tsallis.RData")
+
+load("./Data/metrics_dublin_shannon.RData")
+load("./Data/metrics_dublin_renyi.RData")
+load("./Data/metrics_dublin_tsallis.RData")
+
+# 
+all_metrics <- rbind(
+  metrics_london_shannon,
+  metrics_london_renyi,
+  metrics_london_tsallis,
+
+  metrics_munich_shannon,
+  metrics_munich_renyi,
+  metrics_munich_tsallis,
+
+  metrics_dublin_shannon,
+  metrics_dublin_renyi,
+  metrics_dublin_tsallis
+)
+
+numeric_metrics <- all_metrics
+
+all_metrics$Method <- dplyr::recode(
+  all_metrics$Method,
+  "Shannon" = "$S_{\\widetilde{H}_{\\text{AO}}}$",
+  "Renyi"   = "$S_{\\widetilde{R}_{\\lambda}}$",
+  "Tsallis" = "$S_{\\widetilde{T}_{\\lambda}}$"
+)
+
+#
+for (i in seq(1, nrow(all_metrics), by = 3)) {
+  for (col in c("F1", "Kappa", "OA")) {
+    vals <- numeric_metrics[[col]][i:(i+2)]
+    best <- which.max(vals)
+    for (j in 1:3) {
+      val_fmt <- sprintf("$%.3f$", vals[j])
+      if (j == best) val_fmt <- sprintf("\\bm{%s}", val_fmt)
+      all_metrics[i + j - 1, col] <- val_fmt
+    }
+  }
+}
+
+# Cambiar nombres de columnas
+colnames(all_metrics) <- c("\\textbf{Scene}", "\\textbf{Test}", "$\\bm{F_1}$", "$\\kappa$", "\\textbf{OA}")
+
+# Aplicar multirow a la columna de ciudad (cada 3 filas)
+scene_labels <- all_metrics$Scene
+for (scene in unique(scene_labels)) {
+  idx <- which(scene_labels == scene)
+  scene_labels[idx[1]] <- paste0("\\multirow{3}{*}{", scene, "}")
+  scene_labels[idx[2:3]] <- ""
+}
+all_metrics$Scene <- scene_labels
+
+# Mostrar tabla con formato LaTeX
+kable(all_metrics,
+      caption = "Quantitative measures of heterogeneity detection",
+      format = "latex",
+      booktabs = TRUE,
+      align = "cccccc",
+      escape = FALSE,
+      label = "table_metrics1",
+      centering = FALSE,
+      table.envir = "table", 
+      position = "H",
+      row.names = FALSE) %>%
+  row_spec(0, align = "c") %>%
+  collapse_rows(latex_hline = "major", valign = "bottom") %>%
+  kable_styling(latex_options = "scale_down", font_size = 10) %>%
+  kable_styling(full_width = TRUE)
+
+```
+
+Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds (Figure \ref{fig:roc}).
+Each curve plots the probability of detection (Pd) versus the probability of false alarm (PFA).
+Pd reflects the proportion of heterogeneous pixels correctly detected, while PFA represents the proportion of homogeneous pixels misclassified as heterogeneous.
+
+```{=latex}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.98\textwidth]{Figures/fig-ROC6-1.pdf}
+  \caption{ROC curves comparing the tests $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$ and $S_{\widetilde{T}_{\lambda}}$.}
+  \label{fig:roc}
+\end{figure}
+```
+The area under each ROC curve (AUC) quantifies overall detection performance, with higher values indicating better discrimination between classes.
+Across all scenes, the Rényi-based test yielded the highest AUC in London ($0.963$), followed by Tsallis ($0.824$) and Shannon ($0.776$), reaffirming Rényi’s robustness under strong speckle conditions.
+
+In Munich, both Rényi and Tsallis performed similarly with near-perfect AUCs ($0.996$ and $0.998$ respectively), while Shannon slightly lagged behind ($0.989$).
+In Dublin, a similar pattern is observed: Tsallis again leads marginally with an AUC of $0.994$, followed by Rényi ($0.990$) and Shannon ($0.986$).
+
+These results confirm that Rényi and Tsallis entropies consistently outperform Shannon, with Tsallis showing slightly superior performance in higher-quality scenes.
+The ROC analysis aligns with the classification metrics, supporting the conclusion that Tsallis and Rényi are more effective in detecting heterogeneity across varying image conditions.

### 2025-07-01 Text/Thesis/Chapters/Chapter5.qmd
Update thesis

@@
 # CONCLUSIONS AND FUTURE WORK {#sec-Chapter5}
+
+This thesis presented a statistical framework for detecting heterogeneity in SAR images, offering both theoretical and practical insights into a fundamental question: How can one effectively distinguish heterogeneous clutter from fully developed speckle, assuming SAR intensity is modeled by the Gamma SAR ($\Gamma_{\text{SAR}}$) distribution?
+
+To address this, we proposed three novel hypothesis tests based on entropy measures: Shannon, Rényi, and Tsallis entropies.
+A key theoretical contribution was the derivation of closed-form analytical expressions for the Rényi and Tsallis entropies under both the $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ distributions, which were previously unavailable in the literature.
+Using these expressions, we developed bootstrap-based statistical tests corresponding to each entropy measure.
+
+A comprehensive Monte Carlo simulation study was conducted to evaluate the performance of the proposed tests, assessing both their size (Type&nbsp;I error rate) and power (probability of correctly rejecting the null hypothesis under the alternative).
+The results demonstrated that the methods maintained reliable control over false alarms while significantly improving detection performance as the sample size and number of looks increased.
+
+These theoretical findings were further validated with experiments on both simulated  and real SAR data acquired by various radar missions (TanDEM-X, PAZ, ICEYE, UAVSAR, Sentinel-1B), covering a range of resolutions, polarizations, and look numbers.
+Visual analysis using $p$-value heatmaps and binary decision maps revealed notable distinctions among the entropy-based tests.
+In particular, the Rényi-based test exhibited the highest sensitivity in detecting subtle textural variations, effectively identifying heterogeneity even under high-speckle conditions.
+The Tsallis-based test provided complementary advantages by reliably identifying homogeneous regions, thereby minimizing false alarms (i.e., incorrectly classifying homogeneous areas as heterogeneous).
+In contrast, the Shannon-based test displayed intermediate performance and lower robustness at low numbers of looks.
+
+Quantitative evaluations using ground truth regions of interest (ROIs) and standard classification metrics further confirmed the superior overall performance of both Rényi and Tsallis-based tests across all tested scenes.
+
+Compared to conventional classification methods, the proposed entropy-based statistical tests offer practical advantages:  they provide interpretable, analytical significance measures and require no training data or manual labeling, facilitating rapid analysis suitable for environments with limited data availability.
+Typical computations are efficient, generally taking only a few minutes depending on the image size and number of bootstrap replications.
+Since the three tests share a common computational structure, their execution times are comparable, making the proposed methods particularly attractive for quick screening and exploratory analysis.
+
+Future research directions identified from this thesis include integrating the improved bootstrap-based Rényi and Tsallis estimators into broader SAR classification frameworks, both supervised and unsupervised, to expand their applicability beyond heterogeneity detection.
+This integration could enable the development of multi-level texture classification schemes (e.g., low, moderate, high heterogeneity) that go beyond binary discrimination and provide a more detailed understanding of the scene, without requiring labeled training data.
+
+Additionally, extending the proposed methodology to polarimetric SAR (PolSAR) data represents a promising avenue.
+One approach could involve analyzing the intensity channels independently and fusing the resulting entropy information using multivariate models.
+Alternatively, a fully polarimetric analysis could be pursued by testing deviations from the scaled complex Wishart distribution.
+In this context, exploring the asymptotic behavior of the generalized variance (i.e., the determinant of the covariance matrix) under the complex Wishart model may offer valuable theoretical insights for detecting structural changes in polarimetric data.

### 2025-07-01 Text/Thesis/Frontmatter/abstract.tex
Update thesis

--- 2024-05-08 Text/Thesis/partes/abstract.tex
@@
 %\begin{otherlanguage}{spanish}
-\begin{abstract}
-\phantomsection
-\addcontentsline{toc}{chapter}{Abstract}
-This work presents a statistical approach to identify the
-underlying roughness characteristics in synthetic aperture radar (SAR)
-intensity data. The physical modeling of this kind of data allows the
-use of the Gamma distribution in the presence of fully-developed
-speckle, i.e., when there are infinitely many independent backscatterers
-per resolution cell, and none dominates the return. Such areas are often
-called ``homogeneous'' or ``textureless'' regions. The
-\(\mathcal{G}_I^0\) distribution is also a widely accepted law for
-heterogeneous and extremely heterogeneous regions, i.e., areas where the
-fully-developed speckle hypotheses do not hold. We propose three test
-statistics to distinguish between homogeneous and inhomogeneous regions,
-i.e., between gamma and \(\mathcal{G}_I^0\) distributed data, both with
-a known number of looks. The first test statistic uses a bootstrapped
-non-parametric estimator of Shannon entropy, providing a robust
-assessment in uncertain distributional assumptions. The second test uses
-the classical coefficient of variation (CV). The third test uses an
-alternative form of estimating the CV based on the ratio of the mean
-absolute deviation from the median to the median. We apply our test
-statistic to create maps of \(p\)-values for the homogeneity hypothesis.
-Finally, we show that our proposal, the entropy-based test, outperforms
-existing methods, such as the classical CV and its alternative variant,
-in identifying heterogeneity when applied to both simulated and actual
-data.
+%\begin{abstract}
+%\phantomsection
+%\addcontentsline{toc}{chapter}{Abstract}
 
-\end{abstract}
+This work  presents a statistical approach to detect heterogeneity 
+in synthetic aperture radar (SAR) intensity data using entropy-based methods.
+In homogeneous regions, where fully developed speckle is present, SAR returns 
+are well modeled by the Gamma distribution. 
+In contrast, heterogeneous areas exhibit more complex scattering behaviors, 
+typically modeled by the $\mathcal{G}_I^0$ distribution. Distinguishing between 
+these regimes is fundamental for accurate interpretation in remote sensing applications, 
+yet classical parametric tests often fail to address this task effectively due to analytical 
+and numerical limitations.
+To overcome these challenges, we propose three test statistics for detecting heterogeneity 
+in SAR imagery based on Shannon, Rényi, and Tsallis entropy measures. These tests rely on 
+nonparametric entropy estimators constructed from sample spacings, avoiding explicit assumptions 
+about the underlying distribution. To enhance their accuracy, particularly in small samples, 
+we incorporate a bootstrap bias-correction procedure that improves the estimators’ stability, 
+reduces bias, and lowers mean squared error.
+The proposed tests are evaluated using Monte Carlo simulations, assessing size and power 
+under varying sample sizes and numbers of looks.
+Results demonstrate that the Rényi and Tsallis-based tests outperform the Shannon-based version by 
+detecting more subtle texture variations while maintaining greater reliability in identifying 
+truly homogeneous regions.
+Finally, the methodology is applied to both simulated and real SAR data. We generate $p$-value maps using a 
+sliding window analysis, allowing for visual and quantitative assessment of spatial heterogeneity. 
+The Rényi-based test consistently identifies fine-scale roughness patterns, 
+while the Tsallis-based test shows strength in reliably detecting homogeneous areas. 
+Together, these entropy-based tools provide a robust, interpretable, and unsupervised 
+framework for heterogeneity detection in SAR data.
+
+\vspace{1em}
+\par
+\noindent \textbf{Keywords:} SAR; Heterogeneity; Entropy; Nonparametric Estimation; Bootstrap; Statistical Test
+
 %\end{otherlanguage}

### 2025-07-01 Text/Thesis/Frontmatter/resumo.tex
R1 update: revised manuscript and reviewer responses added
Update thesis

--- 2024-05-08 Text/Thesis/partes/resumo.tex
@@
-\begin{otherlanguage}{portuguese}
+Este trabalho apresenta uma abordagem estatística para a detecção de heterogeneidade 
+em dados de intensidade de radar de abertura sintética (SAR) utilizando medidas 
+baseadas em entropia. Em regiões homogêneas, onde há speckle totalmente desenvolvido, 
+os retornos SAR são bem modelados pela distribuição Gama. Em contraste, áreas heterogêneas 
+apresentam comportamentos de espalhamento mais complexos, normalmente descritos pela 
+distribuição $\mathcal{G}_I^0$. Distinguir entre esses dois regimes é fundamental 
+para uma interpretação precisa em aplicações de sensoriamento remoto. No entanto, 
+testes paramétricos clássicos geralmente não são adequados para essa tarefa devido a 
+limitações analíticas e numéricas.
+Para superar esses desafios, propomos três estatísticas de teste para detectar heterogeneidade 
+em imagens SAR com base nas entropias de Shannon, Rényi e Tsallis. Esses testes utilizam 
+estimadores não paramétricos de entropia construídos a partir de espaçamentos amostrais, 
+evitando suposições explícitas sobre a distribuição subjacente. Para aumentar a precisão dos testes, 
+especialmente em amostras pequenas, incorporamos um procedimento de correção de viés via bootstrap, 
+que melhora a estabilidade dos estimadores, reduz o viés e o erro quadrático médio.
+As estatísticas propostas são avaliadas por meio de simulações de Monte Carlo, 
+onde analisamos seu tamanho e poder sob diferentes condições de speckle e textura. 
+Os resultados mostram que os testes baseados em Rényi e Tsallis superam a versão baseada 
+em Shannon, detectando variações de textura mais sutis e mantendo maior confiabilidade na 
+identificação de regiões verdadeiramente homogêneas.
+Por fim, a metodologia é aplicada a dados SAR simulados e reais. 
+A análise é realizada com janelas deslizantes, gerando mapas de valores de $p$ que permitem a a
+valiação visual e quantitativa da heterogeneidade espacial. O teste baseado na entropia de 
+Rényi mostra desempenho superior na identificação de padrões de rugosidade em pequena escala, 
+enquanto o teste baseado em Tsallis é eficaz na detecção de regiões homogêneas. Em conjunto, 
+essas ferramentas baseadas em entropia oferecem uma estrutura robusta, interpretável e não 
+supervisionada para a detecção de heterogeneidade em dados SAR.
 
-\begin{resumo}
-\phantomsection
-\addcontentsline{toc}{chapter}{Resumo}
-
-Este trabalho apresenta uma abordagem estatística para identificar as características de rugosidade subjacentes nos dados de intensidade do radar de abertura sintética (SAR). 
-A modelagem física desse tipo de dados permite o uso da distribuição Gamma na presença de speckle totalmente desenvolvido, ou seja, quando há infinitos retroespalhadores independentes por celda de resolução e nenhum domina o retorno.
-Essas áreas são frequentemente chamadas de regiões "homogêneas" ou "sem textura". 
-A distribuição $\mathcal{G}_I^0$ também é uma lei amplamente aceita para regiões heterogêneas e extremamente heterogêneas, ou seja, áreas onde as hipóteses de speckle totalmente desenvolvidas não se aplicam.
-Propomos três estatísticas de teste para distinguir entre regiões homogêneas e inhomogêneas, ou seja, entre dados distribuídos gamma e $\mathcal{G}_I^0$, ambos com um número conhecido de looks. 
-A primeira estatística de teste usa um estimador não paramétrico da entropia de Shannon, incorporando metodologias de bootstrap, fornecendo uma avaliação robusta em suposições onde a distribuição é desconhecida.
-O segundo teste usa o coeficiente de variação clássico (CV). 
-O terceiro teste usa uma forma alternativa de estimar o CV com base na razão da média do desvio absoluto em relação à mediana.
- Aplicamos nossa estatística de teste para criar mapas de $p$-valores para a hipótese de homogeneidade. 
-Finalmente, mostramos que nossa proposta, o teste baseado em entropia, supera os métodos existentes, como o CV clássico e sua variante alternativa, na identificação de heterogeneidade quando aplicado a dados simulados e imagens SAR.
-
-\end{resumo}
-\end{otherlanguage}
+\vspace{1em}
+\par
+\noindent \textbf{Palavras-chave:} SAR; Heterogeneidade; Entropia; Estimativa não paramétrica; Bootstrap; Teste estatístico

### 2025-07-01 Text/Thesis/Frontmatter/symbols.tex
Update thesis

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

$\mathbb{R}_+$ & Positive real numbers \\
 $\Gamma(\cdot)$  & Gamma function \\
$\Gamma_{\mathrm{SAR}}(L, \mu)$ & Gamma SAR distribution with parameters $L$ and $\mu$ \\
$\mathcal{G}^0_I$ & $\mathcal{G}^0_I$ distribution for intensity \\
$\psi^{(0)}(\cdot)$ & Digamma function \\
$H(Z)$ & Shannon entropy of random variable $Z$ \\
$R_{\lambda}(Z)$ & Rényi entropy of order $\lambda$ \\
$T_{\lambda}(Z)$ & Tsallis entropy of order $\lambda$ \\
$\widehat{H}_{\text{AO}}(\bm{Z})$ & Nonparametric Shannon entropy estimator (Al-Omari) \\
$\widehat{R}_{\lambda}(\bm{Z})$ & Nonparametric Rényi entropy estimator via sample spacings \\
$\widehat{T}_{\lambda}(\bm{Z})$ & Nonparametric Tsallis entropy estimator via sample spacings \\
$\widetilde{H}_{\text{AO}}(\bm{Z})$ & Bootstrap-corrected Shannon entropy estimator \\
$\widetilde{R}_{\lambda}(\bm{Z})$ & Bootstrap-corrected Rényi entropy estimator \\
$\widetilde{T}_{\lambda}(\bm{Z})$ & Bootstrap-corrected Tsallis entropy estimator \\
$S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ & Test statistic based on Shannon entropy \\
$S_{\widetilde{R}_{\lambda}}(\bm{Z}; L)$ & Test statistic based on Rényi entropy \\
$S_{\widetilde{T}_{\lambda}}(\bm{Z}; L)$ & Test statistic based on Tsallis entropy \\
$\widehat{\mu}$ & Sample mean of $\bm{Z}$ \\
$Z_{(i)}$ & $i$-th order statistic in sample $\bm{Z}$ \\
$m$ & Spacing parameter (window size) used in entropy estimation \\
$c_i$ & Boundary correction factor in spacing estimators \\
\addlinespace % Gap to separate the Roman symbols from the Greek

\end{symbols}

### 2025-07-01 Code/R/MainFunctions/bootstrap_renyi_estimator.R

@@ -1,0 +1,28 @@
+bootstrap_renyi_estimator <- function(x, B = 100L, lambda,
+                                    m = floor(sqrt(length(x)) + 0.5),
+                                    parallel = FALSE)
+{
+  n <- length(x)
+  
+  # estimador en los datos originales
+  t0 <- renyi_estimator(x, lambda, m)
+  
+  # matriz de índices bootstrap (n × B)
+  idx <- matrix(sample.int(n, n * B, replace = TRUE), nrow = n)
+  
+  # función auxiliar (usa la misma m para todas las réplicas)
+  f_boot <- function(col) renyi_estimator(x[col], lambda, m)
+  
+  # vector de estimaciones bootstrap
+  if (parallel) {
+    boot_vals <- future.apply::future_apply(idx, 2, f_boot)
+  } else {
+    boot_vals <- apply(idx, 2, f_boot)
+  }
+  
+  # sesgo estimado  = mean(bootstrap) - t0
+  bias_hat <- mean(boot_vals, na.rm = TRUE) - t0
+  
+  # versión “bias-corrected”   2·t0 − mean(bootstrap)
+  2 * t0 - mean(boot_vals, na.rm = TRUE)
+}

### 2025-07-01 Code/R/MainFunctions/renyi_entropy_estimator_v1.R

@@ -42,3 +42,50 @@ renyi_entropy_estimator_v1 <- function(data, a) {
 # # a <- 0.5            # Parámetro de entropía de Rényi
 # # entropy <- renyi_entropy_estimator(data, a)
 # # print(entropy)
+
+
+
+# renyi_entropy_spacing <- function(data, lambda, m = NULL)
+# {
+#   # Validaciones básicas
+#   if (lambda == 1) stop("Para λ = 1 usa el estimador de Shannon")
+#   n <- length(data)
+#   if (n < 10) warning("Muestra muy pequeña; resultados inestables")
+#   if (is.null(m)) m <- max(1L, round(sqrt(n) + 0.5))
+#   
+#   x  <- sort(data, method = "quick")
+#   i  <- seq_len(n)
+#   
+#   # índices de los extremos del m-spacing
+#   li <- pmax(i - m, 1L)      # left  index
+#   ri <- pmin(i + m, n)       # right index
+#   
+#   # diferencias de forma vectorizada
+#   diff_term <- x[ri] - x[li]
+#   
+#   # coeficiente c_i con la misma lógica de bordes
+#   c_i <- ifelse(i <= m,
+#                 (m + i - 1)/m,
+#                 ifelse(i >= n - m + 1,
+#                        (n + m - i)/m,
+#                        2))
+#   
+#   # razón r_i = n/(c_i m) * diff
+#   r <- n * diff_term / (c_i * m)
+#   r[r <= .Machine$double.eps] <- NA               # evita log(0)
+#   
+#   # promedio de r_i^{1-λ}
+#   s <- mean(r^(1 - lambda), na.rm = TRUE)
+#   
+#   (1 / (1 - lambda)) * log(s)
+# }
+# 
+# library(microbenchmark)
+# set.seed(123)
+# x <- rnorm(1e5)
+# 
+# microbenchmark(
+#   v_original = renyi_entropy_estimator_v1(x, 1.5),
+#   v_fast     = renyi_entropy_spacing   (x, 1.5),
+#   times = 20
+# )

### 2025-07-01 Code/R/MainFunctions/renyi_estimator.R

@@ -1,0 +1,20 @@
+# Al-Labadi carefull con order lambda y alpha en tsallis
+renyi_estimator <- function(x, lambda, m = floor(sqrt(length(x)) + 0.5))
+{
+  n <- length(x)
+  x <- sort(x, method = "quick")
+  i <- seq_len(n)
+  
+  li <- pmax(i - m, 1L)
+  ri <- pmin(i + m, n)
+  diff <- x[ri] - x[li]
+  
+  ci <- ifelse(i <= m, (m + i - 1)/m,
+               ifelse(i >= n - m + 1, (n + m - i)/m, 2))
+  
+  r <- n * diff / (ci * m)
+  r[r <= .Machine$double.eps] <- NA
+  s <- mean(r^(1 - lambda), na.rm = TRUE)
+  
+  (1 / (1 - lambda)) * log(s)
+}

### 2025-07-01 Code/R/MainFunctions/tsallis_entropy_gamma_sar.R

@@ -1,0 +1,9 @@
+tsallis_entropy_gamma_sar <- function(mu, L, lambda) {
+  (1 - exp((1 - lambda)*log(mu) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) / (lambda - 1)
+}
+
+#tsallis_entropy_gamma_sar(1, 5, 0.9)

### 2025-07-01 Code/R/Programs/renyi_entropy_spacing_1.R

@@ -1,0 +1,177 @@
+#Comparacion de estimadores
+
+# --- estimador rápido (sin loops explícitos) ---------------------------
+renyi_entropy_spacing_1 <- function(x, lambda, m = floor(sqrt(length(x)) + 0.5))
+{
+  n <- length(x)
+  x <- sort(x, method = "quick")
+  i <- seq_len(n)
+  
+  li <- pmax(i - m, 1L)
+  ri <- pmin(i + m, n)
+  diff <- x[ri] - x[li]
+  
+  ci <- ifelse(i <= m, (m + i - 1)/m,
+               ifelse(i >= n - m + 1, (n + m - i)/m, 2))
+  
+  r <- n * diff / (ci * m)
+  r[r <= .Machine$double.eps] <- NA
+  s <- mean(r^(1 - lambda), na.rm = TRUE)
+  
+  (1 / (1 - lambda)) * log(s)
+}
+
+# --- bootstrap acelerado ----------------------------------------------
+bootstrap_renyi_entropy <- function(x, B = 200L, lambda,
+                                    m = floor(sqrt(length(x)) + 0.5),
+                                    parallel = FALSE)
+{
+  n <- length(x)
+  
+  # estimador en los datos originales
+  t0 <- renyi_entropy_spacing(x, lambda, m)
+  
+  # matriz de índices bootstrap (n × B)
+  idx <- matrix(sample.int(n, n * B, replace = TRUE), nrow = n)
+  
+  # función auxiliar (usa la misma m para todas las réplicas)
+  f_boot <- function(col) renyi_entropy_spacing(x[col], lambda, m)
+  
+  # vector de estimaciones bootstrap
+  if (parallel) {
+    boot_vals <- future.apply::future_apply(idx, 2, f_boot)
+  } else {
+    boot_vals <- apply(idx, 2, f_boot)
+  }
+  
+  # sesgo estimado  = mean(bootstrap) - t0
+  bias_hat <- mean(boot_vals, na.rm = TRUE) - t0
+  
+  # versión “bias-corrected”   2·t0 − mean(bootstrap)
+  2 * t0 - mean(boot_vals, na.rm = TRUE)
+}
+
+
+renyi_entropy_estimator_v1 <- function(data, a) {
+  n <- length(data)
+  m <- round(sqrt(n) + 0.5)  # Espaciado m
+  data_sorted <- sort(data)   # Ordenar los datos
+  
[…]

### 2025-07-01 Code/R/Programs/tsallis_entropy_spacing2.R

@@ -1,0 +1,126 @@
+#------------------------------------------------------------
+# 1.  Estimador base (spacing) de Tsallis  –  vectorizado
+#------------------------------------------------------------
+# comparacion 2
+tsallis_entropy_spacing2 <- function(x, alpha,
+                                    m = floor(sqrt(length(x))+ 0.5 ))
+{
+  if (alpha <= 0) stop("alpha debe ser > 0 (Tsallis)")
+  n <- length(x)
+  if (n < 10) warning("Muestra muy pequeña; resultados inestables")
+  
+  xs <- sort(x, method = "quick")
+  i  <- seq_len(n)
+  
+  li <- pmax(i - m, 1L)         # índices i-m (cortados a 1)
+  ri <- pmin(i + m, n)          # índices i+m (cortados a n)
+  
+  diff <- xs[ri] - xs[li]
+  
+  ci <- ifelse(i <= m,             (m + i - 1)/m,
+               ifelse(i >= n - m + 1,     (n + m - i)/m, 2))
+  
+  r <- n * diff / (ci * m)
+  r[r <= .Machine$double.eps] <- NA
+  
+  s <- sum(r^(1 - alpha), na.rm = TRUE)  # ∑ r_i^{1-α}
+  
+  (1 / (alpha - 1)) * (1 - s / n)
+}
+
+#------------------------------------------------------------
+# 2.  Bootstrap bias-corrected para Tsallis
+#------------------------------------------------------------
+bootstrap_tsallis_entropy <- function(x, B = 200L, alpha,
+                                      m = floor(sqrt(length(x)) + 0.5),
+                                      parallel = FALSE)
+{
+  n  <- length(x)
+  
+  # estimación en la muestra original
+  t0 <- tsallis_entropy_spacing(x, alpha, m)
+  
+  # matriz de índices bootstrap (n × B)
+  idx <- matrix(sample.int(n, n * B, replace = TRUE), nrow = n)
+  
+  # función auxiliar (m mismo p/ todas las réplicas)
+  f_boot <- function(col) tsallis_entropy_spacing(x[col], alpha, m)
+  
+  # estimaciones bootstrap
+  if (parallel) {
+    if (!requireNamespace("future.apply", quietly = TRUE))
[…]

### 2025-07-01 Code/R/Programs/tsallis_gammasar_direct.R

@@ -1,0 +1,70 @@
+tsallis_gammasar_direct <- function(mu, L, lambda) {
+  # Validación de parámetros
+  if (mu <= 0 || L <= 0 || lambda <= 0) {
+    stop("Parámetros deben ser positivos: mu > 0, L > 0, lambda > 0")
+  }
+  
+  # Calcular términos individuales
+  term1 <- mu^(1 - lambda)
+  term2 <- L^(lambda - 1)
+  term3 <- lambda^(-lambda*(L-1) - 1)
+  term4 <- gamma(lambda*(L-1) + 1)
+  term5 <- gamma(L)^(-lambda)
+  
+  # Calcular el término completo dentro del corchete
+  bracket_term <- term1 * term2 * term3 * term4 * term5
+  
+  # Entropía de Tsallis
+  (1 - bracket_term) / (lambda - 1)
+}
+
+#expresiones compactas teoricas
+
+tsallis_gammasar <- function(mu, L, lambda)
+  (1 - mu^(1-lambda) *
+     L^(lambda-1) *
+     lambda^(-lambda*(L-1)-1) *
+     gamma(lambda*(L-1)+1) *
+     gamma(L)^(-lambda)
+  ) / (lambda - 1)
+
+tsallis_gi0 <- function(alpha, mu, L, lambda)
+  (1 - mu^(1-lambda) *                     # μ^{1-λ}
+     L^(lambda-1) *                      # L^{λ-1}
+     (-alpha - 1)^(1-lambda) *           # (−α−1)^{1-λ}
+     (gamma(L - alpha) / gamma(-alpha))^lambda *  # [Γ(L-α)/Γ(−α)]^λ
+     gamma(lambda*(L-1) + 1) *           # Γ(λ(L−1)+1)
+     gamma(L)^(-lambda) *                # Γ(L)^{−λ}
+     gamma(lambda*(1 - alpha) - 1) /     # Γ(λ(1−α)−1)
+     gamma(lambda*(L - alpha))           # Γ(λ(L−α))
+  ) / (lambda - 1)
+
+
+# --- Término base Γ_SAR(L,μ) en forma logarítmica (una sola línea) ----
+tsallis_gammasar_log <- function(mu, L, lambda)
+  (1 - exp((1 - lambda)*log(mu) +
+             (lambda - 1)*log(L) +
+             lgamma(lambda*(L - 1) + 1) -
+             lambda*lgamma(L) -
+             (lambda*(L - 1) + 1)*log(lambda))) /
+  (lambda - 1)
+
[…]

### 2025-07-01 Text/Thesis/Chapters/Code/bootstrap_ebrahimi_estimator.R

@@ -1,33 +1,0 @@
-
-
-
-
-# source("../MainFunctions/ebrahimi_estimator.r")
-
-
-bootstrap_ebrahimi_estimator <- function(x, B){
-  
-  v.Bootstrap <- rep(0, B)
-  
-  for(b in 1:B) {
-    same_values <- TRUE
-    while (same_values) {
-      bx <- sample(x, replace = TRUE)
-      if (!all(bx == bx[1])) {
-        same_values <- FALSE
-        entropy_result <- ebrahimi_estimator(bx)
-        if (is.finite(entropy_result)) {
-          v.Bootstrap[b] <- entropy_result
-          #cat("Entropy for Bootstrap Sample", b, ": ", v.Bootstrap[b], "\n")
-        }
-      }
-    }
-  }
-  
-  
-  t <- ebrahimi_estimator(x)
-  estimated_mean <- mean(v.Bootstrap[!is.na(v.Bootstrap)])
-  
-  return(2*t - estimated_mean)
-  
-}

### 2025-07-01 Text/Thesis/Chapters/Code/entropy_renyi_gamma_sar.R

@@ -1,8 +1,8 @@
-entropy_renyi_gamma_sar <- function(L, mu, alpha) {
-  entropy <- (alpha * lgamma(L) - lgamma(alpha * (L - 1) + 1) +
-                (alpha * (L - 1) + 1) * log(alpha)) / (alpha - 1) + log(mu / L)
-  return(entropy)
-}
+# entropy_renyi_gamma_sar <- function(L, mu, alpha) {
+#   entropy <- (alpha * lgamma(L) - lgamma(alpha * (L - 1) + 1) +
+#                 (alpha * (L - 1) + 1) * log(alpha)) / (alpha - 1) + log(mu / L)
+#   return(entropy)
+# }
 
 entropy_renyi_gamma_sar <- function(L, mu, lambda) {
   entropy <- (lambda * lgamma(L) - lgamma(lambda * (L - 1) + 1) +

### 2025-07-01 Text/Thesis/setup.R

@@ -1,41 +1,0 @@
-# Configurar CRAN
-options(repos = c(CRAN = "https://cran.rstudio.com/"))
-
-# install and load packages only if they are missing
-install_and_load <- function(packages) {
-  missing_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
-  if (length(missing_packages)) {
-    install.packages(missing_packages, dependencies = TRUE)
-  }
-  invisible(lapply(packages, library, character.only = TRUE))
-}
-#
-#  packages
-required_packages <- c(
-  "ggplot2", "reshape2", "knitr", "pandoc", "gridExtra", 
-  "gtools", "stats4", "rmutil", "scales", "tidyr", "invgamma", 
-  "tidyverse", "RColorBrewer", "ggsci", "carData", "ggpubr",  "patchwork", "dplyr", 
-  "kableExtra", "ggthemes", "latex2exp", "e1071", "viridis", "nortest", "bookdown"
-)
-
-# Install and load only missing packages
-install_and_load(required_packages)
-
-
-theme_set(theme_minimal() +
-            theme(text = element_text(family = "serif"),
-                  legend.position = "bottom"))
-
-
-
-# External functions
-source("./Code/gamma_sar_sample.R")
-source("./Code/gi0_sample.R")
-source("./Code/al_omari_1_estimator.R")
-source("./Code/bootstrap_al_omari_1_estimator.R")
-source("./Code/renyi_entropy_estimator_v1.R")
-source("./Code/bootstrap_renyi_entropy_estimator_v1.R")
-source("./Code/entropy_renyi_gamma_sar.R")
-source("./Code/functions_sample_bias_mse.R")
-source("./Code/functions_sample_bias_mse_1.R")
-#source("./Code/read_ENVI_images.R")

### 2025-07-02 Text/Thesis/Chapters/Chapter2.qmd
update

@@
 In this work, we do not focus on parameter estimation using likelihood-based or moment-based methods.
-Instead, we adopt a testing framework to detect heterogeneity in SAR imagery.
+Instead, we adopt a hypothesis testing framework to detect heterogeneity in SAR imagery.
 The analytical expressions of entropy measures derived from the $\Gamma_{\text{SAR}}$ and $\mathcal{G}_I^0$ models form the theoretical basis for constructing these statistical tests.
@@
 
-\textbf{Tsallis entropy},  was first introduced by Havrda and Charvat&nbsp;[-@Havrda1967]  in the context of information theory.
-Then, Tsallis&nbsp;[-@Tsallis1988] exploited its non-extensive features and placed it in a physical setting, known as generalized Tsallis entropy of order $\lambda$,  offers an alternative generalization motivated by non-extensive systems, those exhibiting long-range dependencies, memory effects, or multifractal behavior.
-Unlike Rényi, Tsallis entropy does not obey the additivity property under independent systems, which makes it particularly suitable for modeling complex spatial structures and textured regions in SAR images.
+\textbf{Tsallis entropy} was first introduced by Havrda and Charvát&nbsp;[-@Havrda1967] in the context of information theory.
+Later, Tsallis&nbsp;[-@Tsallis1988] extended it by emphasizing its non-extensive features and placing it in a physical context.
+The generalized Tsallis entropy of order $\lambda$ offers an alternative formulation motivated by non-extensive systems, such as those exhibiting long-range dependencies, memory effects, or multifractal behavior.
+Unlike Rényi entropy, it does not obey the additivity property under independence, making it particularly suitable for modeling complex spatial structures and textured regions in SAR images.
 
@@
 Appendix&nbsp;\ref{app:A24} provides proof of this limiting behavior.
-
-<!-- When $\alpha\!\to\!-\infty$ (fully developed speckle), this excess tends to zero, -->
-<!--  so the heterogeneous model collapses to the homogeneous one in Equation \eqref{eq-HGammaSAR}.   -->
-<!-- and detecting heterogeneity is equivalent to deciding whether $\Delta_\alpha$ is significantly different from zero. -->
-<!--  Note that the Rényi entropy of $\mathcal{G}^0_I$ can be expressed in terms of that of $\Gamma_{\mathrm{SAR}}$, with additional terms that depend on the roughness parameter $\alpha$.
-As $\alpha \to -\infty$, these terms tend to zero, reducing&nbsp;\eqref{eq-HGI0} to&nbsp;\eqref{eq-HGammaSAR}.
--->
-<!-- This work's core idea is to check if this excess entropy is significantly different from zero. -->
-<!-- Fig.&nbsp;\ref{fig-convergence-renyi} illustrates this behaviour: as $\alpha$ decreases the colored curves of $R_\lambda(\mathcal{G}^0_I)$ converge towards the solid black curve of $R_\lambda(\Gamma_{\mathrm{SAR}})$, confirming the limiting behavior.
--->
 

### 2025-07-02 Text/Thesis/Chapters/Chapter3.qmd
update

@@
 
-Figure \ref{fig:Plot_bias_mse-sh} presents the bias and MSE for each of the non-parametric estimators of Shannon entropy. The results are summarized in @tbl-out.
+Figure \ref{fig:Plot_bias_mse-sh} presents the bias and MSE for each of the non-parametric estimators of Shannon entropy. The results are summarized in @tbl-out-shannon.
 
@@
 \renewcommand{\arraystretch}{1.8} 
-```{r Table_estimators_shannon2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
-#| label: tbl-out
+```{r}
+#| label: tbl-out-shannon
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
 #| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.'
@@
 \end{equation}
-<!-- This expression follows from the classical bias correction formula: -->
-<!-- \begin{equation} -->
-<!-- \text{Bias-corrected estimate} = \text{Original estimate} - \text{Bias estimate}. -->
-<!-- \label{eq:bias_correction_principle} -->
-<!-- \end{equation} -->
 Thus, $\widetilde{\theta}$ is an approximately unbiased estimator of $\theta$.
@@
  @tbl-out-time shows the processing time of each estimator across different settings of $L$  and $n$.
-<!-- <!-- # ```{r Simulated_comparative_time6, eval=FALSE, echo=FALSE} --> 
+
 ```{r Simulated_comparative_time6, echo=FALSE, message=FALSE}
@@
 ```
+
 \renewcommand{\arraystretch}{1.1}
-```{r Table_statistic_time_6,  echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r}
 #| label: tbl-out-time
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
 #| tbl-cap: 'Processing time for bootstrap-improved estimators $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$'
@@
 
-<!-- ```{r Simulated_data_bias_shannon1, echo=FALSE, message=FALSE} -->
-<!-- set.seed(1234567890) -->
-
-<!-- file_name <- "./Data/results_shannon_v1.Rdata" -->
-
-<!-- if (file.exists(file_name)) { -->
-<!--   load(file_name) -->
-<!--   message("Loaded existing results from results_shannon_v1.Rdata") -->
-<!-- } else { -->
-<!--   sample_sizes <- c(9, 25, 49, 81, 121) -->
-<!--   R <- 500 -->
-<!--   B <- 100 -->
-<!--   mu <- 1 -->
-<!--   L <- 16 -->
-
-<!--   estimators <- list( -->
-<!--     "Shannon Estimator" = al_omari_1_estimator, -->
-<!--     "Shannon Estimator Bootstrap" = bootstrap_al_omari_1_estimator -->
-<!--   ) -->
-
-<!--   results <- calculate_bias_mse_shannon(sample_sizes, R, B, mu, L, estimators) -->
-
-<!--   save(results, file = file_name) -->
-<!--   message("Simulaciones completadas y resultados guardados.") -->
-<!-- } -->
-
-<!-- ``` -->
-<!-- ```{r fig-bias_mse_shannonm, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.cap="Bias and MSE of the Shannon–Al-Omari entropy estimators for $\\Gamma_{\\text{SAR}}$.", fig.width=6, fig.height=5} -->
-<!-- load("./Data/results_shannon_v1.Rdata") -->
-
-<!-- estimators_to_plot <- c("Shannon Estimator", "Shannon Estimator Bootstrap") -->
-<!-- latex_estimator_names <- c( -->
-<!--   "Shannon Estimator" = expression("$\\widehat{italic(H)}$"), -->
-<!--   "Shannon Estimator Bootstrap" = expression("$\\widetilde{italic(H)}$") -->
-<!-- ) -->
-<!-- selected_estimators_latex <- latex_estimator_names[estimators_to_plot] -->
-
-<!-- combined_plot_shannon <- generate_plot_shannon(results, selected_estimators_latex, ncol = 1, nrow = 1) -->
-
-<!-- print(combined_plot_shannon) -->
-
-<!-- ``` -->
-
-<!-- ```{=latex} -->
-<!-- \begin{figure}[hbt] -->
-<!--   \centering -->
-<!--   \includegraphics[width=0.40\textwidth]{Figures-R1/fig-bias_mse-1.pdf} -->
-<!--   \vspace{0.1em} -->
-<!--   \caption{Bias and MSE of the Rényi entropy estimators for $\Gamma_{\text{SAR}}$.} -->
-<!--   \label{fig-bias_mse} -->
-<!-- \end{figure} -->
-<!-- ``` -->
-<!-- We use the $\widetilde{H}_{\lambda}$ estimator for subsequent simulations. -->
-
 ## HYPOTHESIS TESTING
@@
         legend.title = element_text(size = 16))
-
-  # p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
-  #   geom_line(stat = "density", linewidth = 1.5) +
-  #   scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
-  #   scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
-  #   scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
-  #   scale_y_continuous(limits = y_limits, minor_breaks = NULL) +
-  #   labs(
-  #       x = expression("Test Statistic" ~ S[widetilde(italic(T))](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
-  #       y = "Density"
-  #   ) +
-  #   ggtitle(bquote(italic(L) == .(L))) +
-  #   theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
-  #         axis.text = element_text(size = 16),     
-  #         axis.title = element_text(size = 16),    
-  #         legend.text = element_text(size = 16),   
-  #         legend.title = element_text(size = 16))
 
@@
 
-  # p <- ggplot(combined_data, aes(x = Test_Statistics, col = LegendOrder, linetype = LegendOrder, group = CurveOrder)) +
-  #   geom_line(stat = "density", linewidth = 1.5) +
-  #   scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.2, end = 0.7, name = "Sample Size") +
-  #   scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
-  #   scale_x_continuous(limits = x_limits, breaks = x_breaks, minor_breaks = NULL) +
-  #   #scale_x_continuous(limits = x_limits, breaks = x_breaks) + 
-  #   scale_y_continuous(limits = y_limits, minor_breaks = NULL)+
-  #   #scale_y_continuous(limits = y_limits) +  
-  #   labs(
-  #       x = expression("Test Statistic" ~ S[widetilde(italic(T))[lambda]](italic(bold(Z))* ";" **phantom(" ")* italic(L))), 
-  #       y = "Density"
-  #   ) +
-  #   ggtitle(bquote(italic(L) == .(L))) +
-  #   theme(plot.title = element_text(hjust = 0.5, size = 16, margin = margin(b = 2)),
-  #         axis.text = element_text(size = 16),     
-  #       axis.title = element_text(size = 16),    
-  #       legend.text = element_text(size = 16),   
-  #       legend.title = element_text(size = 16)   
-  #         )
-
   all_plots[[as.character(L)]] <- p
@@
 These values define the acceptable probability of committing a Type&nbsp;I error.
-A well-calibrated test should exhibit empirical Type~I error rates that closely match the nominal levels across different sample sizes and conditions.
+A well-calibrated test should exhibit empirical Type&nbsp;I error rates that closely match the nominal levels across different sample sizes and conditions.
 

### 2025-07-02 Text/Thesis/Chapters/Chapter4.qmd
update

@@
 The polygons were rasterized to match the spatial resolution of each SAR image, forming a partial ground truth.
-We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared these decision maps with the ground truth to compute the F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
-Table \ref{tab:table_metrics1} summarizes the results.
 
@@
     % London
-    \begin{subfigure}{0.33\textwidth}
+    \begin{subfigure}{0.30\textwidth}
         \includegraphics[width=\linewidth]{Figures/london_roi.png}
@@
     % Munich
-    \begin{subfigure}{0.33\textwidth}
+    \begin{subfigure}{0.30\textwidth}
         \includegraphics[width=\linewidth]{Figures/munich_roi.png}
@@
     \end{subfigure}
-    \vspace{1.8em}
+    \vspace{0.5em}
     % Dublin
-    \begin{subfigure}{0.33\textwidth}
+    \begin{subfigure}{0.30\textwidth}
         \includegraphics[width=\linewidth]{Figures/dublin_roi3.png}
@@
 ```
-
-When comparing the three entropy-based tests, distinct patterns emerge depending on the scene characteristics.
-In London, the Rényi-based test produced the best performance across all metrics ($F_1$: 0.695; $\kappa$: 0.626; OA: 0.877), outperforming both Shannon and Tsallis.
-This suggests that Rényi entropy is particularly robust under strong speckle conditions, as is typical in single-look SAR imagery.
-
-In contrast, in the Munich and Dublin scenes, where the image quality is higher and speckle is reduced, the Tsallis-based test achieved the highest scores across all three metrics.
-Specifically, in Munich, Tsallis achieved $F_1 = 0.930$, $\kappa = 0.871$, and OA = 0.936, marginally outperforming Rényi.
-Similarly, in Dublin, Tsallis led with $F_1 = 0.879$, $\kappa = 0.776$, and OA = 0.887.
-These results indicate that Tsallis entropy may be more sensitive to finer textural differences in lower-speckle environments.
-
-The Shannon-based test consistently yielded the lowest scores across all scenes, suggesting that it is less effective at distinguishing between heterogeneous and homogeneous regions under the tested conditions.
-Overall, the results demonstrate that Rényi and Tsallis entropies are both strong detectors of heterogeneity, with Rényi showing advantages in noisy contexts, and Tsallis offering improved discrimination in scenes with more subtle textural variations.
+We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared these decision maps with the ground truth to compute the F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
+Table \ref{tab:table_metrics1} summarizes the results.
 
@@
 ``` 
+When comparing the three entropy-based tests, distinct patterns emerge depending on the scene characteristics.
+In London, the Rényi-based test produced the best performance across all metrics ($F_1$: 0.695; $\kappa$: 0.626; OA: 0.877), outperforming both Shannon and Tsallis.
+This suggests that Rényi entropy is particularly robust under strong speckle conditions, as is typical in single-look SAR imagery.
+
+In contrast, in the Munich and Dublin scenes, where the image quality is higher and speckle is reduced, the Tsallis-based test achieved the highest scores across all three metrics.
+Specifically, in Munich, Tsallis achieved $F_1 = 0.930$, $\kappa = 0.871$, and OA = 0.936, marginally outperforming Rényi.
+Similarly, in Dublin, Tsallis led with $F_1 = 0.879$, $\kappa = 0.776$, and OA = 0.887.
+These results indicate that Tsallis entropy may be more sensitive to finer textural differences in lower-speckle environments.
+
+The Shannon-based test consistently yielded the lowest scores across all scenes, suggesting that it is less effective at distinguishing between heterogeneous and homogeneous regions under the tested conditions.
+Overall, the results demonstrate that Rényi and Tsallis entropies are both strong detectors of heterogeneity, with Rényi showing advantages in noisy contexts, and Tsallis offering improved discrimination in scenes with more subtle textural variations.
 

### 2025-07-02 Text/Thesis/Frontmatter/abstract.tex
update

@@
 in synthetic aperture radar (SAR) intensity data using entropy-based methods.
-In homogeneous regions, where fully developed speckle is present, SAR returns 
-are well modeled by the Gamma distribution. 
-In contrast, heterogeneous areas exhibit more complex scattering behaviors, 
-typically modeled by the $\mathcal{G}_I^0$ distribution. Distinguishing between 
-these regimes is fundamental for accurate interpretation in remote sensing applications, 
-yet classical parametric tests often fail to address this task effectively due to analytical 
-and numerical limitations.
+In SAR data analysis, accurate terrain interpretation fundamentally depends 
+on distinguishing two key regimes: homogeneous regions, characterized by fully 
+developed speckle and modeled by the Gamma distribution, and heterogeneous areas, 
+which exhibit complex scattering behaviors typically captured by the $\mathcal{G}_I^0$ distribution.
+While this discrimination is essential for remote sensing applications, classical parametric tests often fail to address it 
+effectively due to analytical limitations and numerical instabilities.
 To overcome these challenges, we propose three test statistics for detecting heterogeneity 
@@
 about the underlying distribution. To enhance their accuracy, particularly in small samples, 
-we incorporate a bootstrap bias-correction procedure that improves the estimators’ stability, 
+we incorporate a bootstrap bias-correction procedure that improves the stability of the estimators, 
 reduces bias, and lowers mean squared error.
@@
 sliding window analysis, allowing for visual and quantitative assessment of spatial heterogeneity. 
-The Rényi-based test consistently identifies fine-scale roughness patterns, 
-while the Tsallis-based test shows strength in reliably detecting homogeneous areas. 
-Together, these entropy-based tools provide a robust, interpretable, and unsupervised 
-framework for heterogeneity detection in SAR data.
+The Rényi-based test consistently identifies fine-scale roughness patterns, while the Tsallis-based 
+test proves more effective in reliably detecting homogeneous areas. Together, these entropy-based 
+tools provide a robust, interpretable, and fully unsupervised framework for heterogeneity detection 
+in SAR data.
 
@@
 \par
-\noindent \textbf{Keywords:} SAR; Heterogeneity; Entropy; Nonparametric Estimation; Bootstrap; Statistical Test
+\noindent \textbf{Keywords:}  Entropy; SAR; Heterogeneity; Gamma distribution; Hypothesis testing; Bootstrap
 

### 2025-07-02 Text/Thesis/Frontmatter/resumo.tex
update

@@
-Este trabalho apresenta uma abordagem estatística para a detecção de heterogeneidade 
-em dados de intensidade de radar de abertura sintética (SAR) utilizando medidas 
-baseadas em entropia. Em regiões homogêneas, onde há speckle totalmente desenvolvido, 
-os retornos SAR são bem modelados pela distribuição Gama. Em contraste, áreas heterogêneas 
-apresentam comportamentos de espalhamento mais complexos, normalmente descritos pela 
-distribuição $\mathcal{G}_I^0$. Distinguir entre esses dois regimes é fundamental 
-para uma interpretação precisa em aplicações de sensoriamento remoto. No entanto, 
-testes paramétricos clássicos geralmente não são adequados para essa tarefa devido a 
-limitações analíticas e numéricas.
+Este trabalho apresenta uma abordagem estatística para detectar heterogeneidade em dados de 
+intensidade de radar de abertura sintética (SAR) utilizando métodos baseados em entropia. 
+Na análise de dados SAR, uma interpretação precisa do terreno depende fundamentalmente da 
+distinção entre dois regimes principais: regiões homogêneas, caracterizadas por speckle 
+totalmente desenvolvido e modeladas pela distribuição Gamma, e áreas heterogêneas, que 
+exibem comportamentos de espalhamento complexos, geralmente representados pela distribuição 
+$\mathcal{G}_I^0$.
+Embora essa discriminação seja essencial para aplicações de sensoriamento remoto, 
+testes paramétricos clássicos muitas vezes não a abordam de forma eficaz devido a 
+limitações analíticas e instabilidades numéricas.
 Para superar esses desafios, propomos três estatísticas de teste para detectar heterogeneidade 
@@
 \par
-\noindent \textbf{Palavras-chave:} SAR; Heterogeneidade; Entropia; Estimativa não paramétrica; Bootstrap; Teste estatístico
+\noindent \textbf{Palavras-chave:} Entropia; SAR; Heterogeneidade; Distribuição Gama; Teste de hipótese; Bootstrap

### 2025-07-03 Text/Thesis/Chapters/Chapter2.qmd
update derivations in main text

@@
     \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+    \label{E:mean1}
 \end{equation}
@@
 This section details the closed-form expressions for $H$, $R_\lambda$, and $T_\lambda$ under $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ models.
-Shannon entropy derivations are taken from literature and adapted to our parametrisation, whereas the Rényi and Tsallis expressions are original contributions derived as part of this research (see Appendix&nbsp;\ref{sec-appendix-A}).
+Shannon entropy derivations are taken from literature and adapted to our parametrisation, whereas the Rényi and Tsallis expressions are original contributions derived as part of this research.
 At the end of the chapter, we summarize the common structure shared by all three measures and illustrate their convergence behavior.
@@
 Equation \eqref{eq:GIO-Sh1} can be interpreted as: 
+\vspace{-15pt}
 $$
@@
 $$
+\vspace{-10pt}
+where
+\vspace{-15pt}
 \begin{multline} 
-\text{where}\quad
   \Delta_\alpha
@@
 \\[-2pt]\hphantom{\Delta^{\mathrm{Sh}}_\alpha={}}
-   -\ln\Gamma(L-\alpha)+\ln\Gamma(-\alpha)-L.
+   -\ln\Gamma(L-\alpha)+\ln\Gamma(-\alpha)-L,
    \label{eq:GIO-Sh2}
@@
 When $\alpha \to -\infty$ (fully developed speckle), the excess term tends to zero, and Equation \eqref{eq:GIO-Sh1} collapses to the homogeneous case in \eqref{eq:gamma-sh1}, i.e.,
+\vspace{-15pt}
 $$
@@
 \end{equation}
-As $\lambda \to 1$, $R_\lambda(Z)$ reduces to $H(Z)$.
-
-Using&nbsp;\eqref{E:entropy-R}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and the $\mathcal{G}^0_I$ distributions.
-
-\textbf{Homogeneous case.} We find
+As $\lambda \to 1$, $R_{\lambda}(Z)$ reduces to the Shannon entropy $H(Z)$.
+
+Using \eqref{E:entropy-R}, we now derive the closed-form expression for the Rényi entropy under the homogeneous ($\Gamma_{\mathrm{SAR}}$) model.
+
+\textbf{Homogeneous case.} Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$ with pdf given in \eqref{E:gamma1}. We compute
+$$
+I = \int_{0}^{\infty}
+    \bigl[f_{\Gamma_{\mathrm{SAR}}}(z;L,\mu)\bigr]^{\lambda}
+    \,\mathrm{d}z
+  = \Bigl(\tfrac{L^{L}}{\Gamma(L)\,\mu^{L}}\Bigr)^{\!\lambda}
+    \int_{0}^{\infty} z^{\lambda(L-1)}
+    \exp\Bigl(-\tfrac{\lambda L}{\mu}\,z\Bigr)\,\mathrm{d}z.
+$$
+Using the Gamma integral identity
+\begin{align*}
+\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
+&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
+\end{align*}
+with
+\vspace{-10pt}
+$$
+p = \lambda(L-1)+1,\quad
+q = \frac{\lambda L}{\mu},
+$$
+we obtain
+$$
+I
+= \Bigl(\tfrac{L^{L}}{\Gamma(L)\,\mu^{L}}\Bigr)^{\!\lambda}
+  \frac{\Gamma\bigl(\lambda(L-1)+1\bigr)}
+       {\bigl(\tfrac{\lambda L}{\mu}\bigr)^{\lambda(L-1)+1}}.
+$$
+Taking logarithms and simplifying gives
+\begin{equation*}
+\ln I
+= (1-\lambda)\bigl(\ln \mu - \ln L\bigr)
+- \lambda\,\ln\Gamma(L)
++ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)
+- \bigl(\lambda(L-1)+1\bigr)\ln\lambda.
+\end{equation*}
+Substituting into \eqref{E:entropy-R} yields the closed-form
+\begin{equation}
+  \label{eq-GammaSAR-R}
+  \boxed{
+  R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
+  = \ln\mu - \ln L
++ \frac{1}{1-\lambda}
+\Bigl[
+-\lambda\,\ln\Gamma(L)
++ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)
+- \bigl(\lambda(L-1)+1\bigr)\ln\lambda
+\Bigr].
+}
+\end{equation}
+
+\textbf{Textured case.} Starting from the definition of Rényi entropy in  \eqref{E:entropy-R} and the pdf of  $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ given in \eqref{E:gi01}, we define:
+$$
+I
+= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
+= C^{\lambda}
+  \int_{0}^{\infty}
+    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
+\qquad
+C=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}.
+$$
+The parameterisation satisfies $\gamma=-\mu(\alpha+1)$, so the final result will be expressed in terms of $\mu$.
+
+$$
+I \;=\;\int_{0}^{\infty}
+        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
+    \;=\;C^{\lambda}\!
+        \int_{0}^{\infty}\!
+          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
+$$
+With the change of variable $t=Lz/\gamma$ ($dz=\gamma\,dt/L$) we obtain:
+$$
+I
+= C^{\lambda}\,
+  \frac{\gamma^{\,1+\lambda(\alpha-1)}}{L^{\,1+\lambda(L-1)}}
+  \int_{0}^{\infty}
+    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,dt.
+$$
+Using the Beta–function identity
+$$
+\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,dt
+= B(a,b),\;\;
+a=\lambda(L-1)+1,\;\;
+b=\lambda(-\alpha+1)-1,
+$$
+it follows that
+\vspace{-15pt}
+\begin{align*}
+I 
+&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
+   \,B(a,b).
+\end{align*}
+Next, we note that 
+$\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}$ 
+and 
+$L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}.$ 
+Since
+$$
+C^\lambda 
+= \biggl(\tfrac{L^L}{\gamma^\alpha\,\Gamma(-\alpha)\,\Gamma(L)}\,\Gamma(L - \alpha)\biggr)^{\!\lambda}
+= L^{\lambda L}\,\gamma^{-\alpha \lambda}
+  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,
+$$
+we obtain
+\vspace{-15pt}
+\begin{align*}
+I
+&= \gamma^{\,1 - \lambda}\,
+   L^{\,\lambda - 1}
+   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
+   \,B(a,b).
+\end{align*}
+By \eqref{E:entropy-R}, the Rényi entropy, is given by:
+\begin{align*}
+R_\lambda(Z)
+= \frac{1}{\,1 - \lambda\,} \,\ln I=\frac{1}{\,1 - \lambda\,}
+  \,\ln\!\Bigl[
+    \gamma^{\,1 - \lambda}\,
+    L^{\,\lambda - 1}\,
+    \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
+    \,B(a,b)
+  \Bigr].
+\end{align*}
+Thus, for $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$,
+\begin{align*}
+R_\lambda\bigl(\mathcal{G}^0_I(\alpha, \gamma, L)\bigr)
+&= \ln\Bigl(\tfrac{\gamma}{\,L}\Bigr)
++ \frac{1}{\,1 - \lambda\,}
+    \Bigl[
+      \lambda\bigl(\ln \Gamma(L - \alpha)  
+- \ln \Gamma(-\alpha) - \ln \Gamma(L)\bigr)
++ \ln B(a,b)
+    \Bigr].
+\end{align*}
+Using the property 
+$$
+\ln B(a,b) 
+= \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b),
+$$
+where $a + b = \lambda(L - \alpha)$, we have
 \begin{multline}
-\label{eq-GammaSAR-R}
-R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)
-= 
-\ln \mu - \ln L + \frac{1}{1-\lambda}
+R_\lambda\bigl(\mathcal{G}^0_I( \alpha,\gamma, L)\bigr)
+= \ln\Bigl(\tfrac{\gamma}{L}\Bigr)
++ \frac{1}{\,1 - \lambda\,}
 \Bigl[
-  -\lambda\,\ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) -  \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
+     \lambda\bigl(\ln \Gamma(L - \alpha) 
+- \ln \Gamma(-\alpha) 
+- \ln \Gamma(L)\bigr)
++ \ln \Gamma(a)
++ \ln \Gamma(b) \\
+- \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
 \Bigr].
+\label{eq:GI0RenyiInGamma1}
 \end{multline}
-
-\textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
-\begin{multline}  
+Finally, noting that $\gamma = -\mu(\alpha + 1)$ from \eqref{E:rmom}, and substituting this expression into \eqref{eq:GI0RenyiInGamma1}, we obtain:
+\begin{multline*}
+R_\lambda\bigl(\mathcal{G}^0_I( \alpha,\mu, L)\bigr)
+= \ln \mu  -  \ln L + \ln(- 1-\alpha)
++ \frac{1}{\,1 - \lambda\,}
+  \Bigl[
+    \lambda\Bigl(\ln \Gamma(L - \alpha) 
+- \ln \Gamma(-\alpha) 
+- \ln \Gamma(L)\Bigr)\\
++ \ln \Gamma\bigl(\lambda(L - 1) + 1\bigr)
++ \ln \Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)
+- \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
+\Bigr],
+\label{eq:RenyiGI0Final}
+\end{multline*}
+This expression extends the Rényi entropy of the $\Gamma_{\mathrm{SAR}}(L,\mu)$ model \eqref{eq-GammaSAR-R} by including additional terms that depend on the texture parameter $\alpha$. Specifically:
+\begin{equation}
 \label{eq-HGI0-R}
-R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) \;+ \;\ln(-1 - \alpha)  
-+ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
-+ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) - \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
-+ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
-\end{multline}
- The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.
-
+\boxed{%
+\begin{aligned}
+R_{\lambda}\bigl(\mathcal{G}^0_I(\alpha,\mu,L)\bigr)
+&=R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
+  +\ln(-1-\alpha) \\
+&\qquad+\,\frac{1}{1-\lambda}\!\bigl[
+    \lambda\bigl(\ln\Gamma(L-\alpha)-\ln\Gamma(-\alpha)\bigr)
+    +\ln\Gamma\bigl(\lambda(-\alpha+1)-1\bigr) \\
+&\hspace{6.9em}-\,\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
+    +\bigl(\lambda(L-1)+1\bigr)\ln\lambda
+  \bigr].
+\end{aligned}}
+\end{equation}
 Equation&nbsp;\eqref{eq-HGI0-R} can be read as:
-$$
+\vspace{-15pt}
+\begin{equation*}
 R_\lambda(\mathcal{G}^0_I)
@@
 \underbrace{\Delta^R_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
-$$
+\end{equation*}
+\vspace{-10pt}
+where
+\vspace{-10pt}
 \begin{multline} 
-\text{where}\quad
   \Delta^R_\alpha
@@
 $\alpha\to-\infty$, validating the decomposition, i.e.,
+\vspace{-15pt}
 $$
@@
 For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
-
 \begin{equation}
@@
 
-\textbf{Homogeneous case.} We find
-\begin{multline}
+\textbf{Homogeneous case.} 
+Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$  with pdf given by \eqref{E:gamma1}. Define the integral:
+\begin{equation*}
+J
+= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \, dz.
+\end{equation*}
+Substituting the density function and simplifying constants, we get
+\begin{equation*}
+J
+= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
+  \int_0^\infty
+     z^{\lambda(L-1)}
+     \exp\left(-\frac{\lambda L}{\mu} z\right)\, dz.
+\end{equation*}
+Using the Gamma integral identity
+\begin{align*}
+\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
+&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
+\end{align*}
+with $p = \lambda(L-1) + 1$ and $q = \frac{\lambda L}{\mu}$. This leads to
+\begin{equation*}
+J
+= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
+  \cdot
+  \frac{\Gamma\big(\lambda(L-1)+1\big)}
+       {\left(\frac{\lambda L}{\mu}\right)^{\lambda(L-1)+1}}.
+\end{equation*}
+After rearranging powers of $L$, $\mu$ and $\lambda$, we obtain
+\begin{equation}
+J
+= \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
+       \Gamma\big(\lambda(L - 1) + 1\big)}
+      {\lambda^{\lambda(L - 1) + 1}\,
+       \left[\Gamma(L)\right]^{\lambda}}.
+\label{eq:Jgamma1}
+\end{equation}
+Substituting Equation \eqref{eq:Jgamma1} into the Tsallis entropy definition \eqref{eq:tsallis}, we have:
+\begin{equation}
+T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big)
+= \frac{1}{\lambda - 1}
+   \left[
+     1 -
+     \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
+           \Gamma\big(\lambda(L - 1) + 1\big)}
+          {\lambda^{\lambda(L - 1) + 1}\;
+           \left[\Gamma(L)\right]^{\lambda}}
+   \right].
+\label{eq:TsallisGammaFinal1}
+\end{equation}
+This expression can also be written in an equivalent form:
+<!-- \begin{equation*} -->
+<!-- T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big) -->
+<!-- = \frac{1}{\lambda - 1} \left[ -->
+<!--    1 - -->
+<!--    \mu^{1 - \lambda}\, -->
+<!--    L^{\lambda - 1}\, -->
+<!--    \lambda^{ - [\lambda(L - 1) + 1] }\, -->
+<!--    \Gamma\big(\lambda(L - 1) + 1\big)\, -->
+<!--    \Gamma(L)^{ - \lambda} -->
+<!-- \right], -->
+<!-- \end{equation*} -->
+\begin{equation}
 \label{eq:gammasar-Tsallis}
+\boxed{%
+\begin{aligned}
 T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
@@
 \Bigr]\Bigr\}.
-\end{multline}
-
-  \textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
-  \begin{multline}
+\end{aligned}}
+\end{equation}
+
+\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} aand the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:
+\begin{equation*}
+J = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda dz,
+\end{equation*}
+which, upon substitution of the density, becomes
+\begin{equation*}
+J = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}  dz.
+\label{eq:J_initial}
+\end{equation*}
+Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $dz = \frac{\gamma}{L} dt$), we obtain
+\begin{align}
+J &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\frac{\gamma}{L} \int_0^\infty \frac{\left( \frac{\gamma t}{L} \right)^{\lambda(L-1)}}
+{[\gamma(1 + t)]^{\lambda(L - \alpha)}}  dt\nonumber \\
+&= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L-1)}} 
+\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}  dt.
+\label{eq:J_transformed1}
+\end{align}
+This integral matches the Beta function identity
+\begin{equation*}
+\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},
+\end{equation*}
+for parameters
+\begin{equation*}
+a = \lambda(L-1) + 1, \quad b = \lambda(-\alpha + 1) - 1.
+\end{equation*}
+Using this, we simplify \eqref{eq:J_transformed1} to
+\begin{equation}
+J = \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\frac{\gamma^{1-\lambda}}{L^{1-\lambda}} 
+\cdot \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)}.
+\label{eq:J_beta1}
+\end{equation}
+To express $J$ in terms of the mean $\mu$, we use the relation $\gamma = -\mu(\alpha + 1)$ valid for $\alpha < -1$. Substituting into \eqref{eq:J_beta1} gives
+\begin{equation*}
+J = [-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 
+\left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\frac{\Gamma(a)\Gamma(b)}{\Gamma(\lambda(L - \alpha))}.
+\end{equation*}
+Finally, substituting this expression into \eqref{eq:tsallis}, we obtain:
+\begin{equation*}
+T_\lambda\bigl(\mathcal{G}^0_I( \alpha,\mu, L)\bigr)
+= \frac{1}{\lambda-1}
+  \biggl\{
+[-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 
+\left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\frac{\Gamma(a)\Gamma(b)}{\Gamma(\lambda(L - \alpha))}
+\biggr\}.
+\end{equation*}
+This expression extends the Tsallis entropy of the $\Gamma_{\mathrm{SAR}}(L,\mu)$ model \eqref{eq:gammasar-Tsallis} by including additional terms that depend on the texture parameter $\alpha$.
+It can be written in an exponential-logarithmic form as:
+\begin{equation}
 \label{eq:GI0-Tsallis}
+\boxed{%
+\begin{aligned}
   T_\lambda\bigl(\mathcal{G}^0_I(\mu,\alpha,L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)\;+\;\frac{1}{\lambda-1}\,
@@
   \Bigr] 
-  {}\times\Bigl\{1-
+  {}\Bigl\{1-
   \exp\Bigl[
@@
   \Bigr]\Bigr\}.
-  \end{multline}
-
-  The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.
-
+\end{aligned}}
+\end{equation}
 Equation&nbsp;\eqref{eq:GI0-Tsallis} can be interpreted as:
-  $$
+\begin{equation*}
   T_\lambda(\mathcal{G}^0_I)
@@
   \underbrace{\Delta^T_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
-  $$
+\end{equation*}
+\vspace{-10pt}
+where
+\vspace{-10pt}
 \begin{multline}
-\text{where}\quad
 \Delta^T_\alpha
@@
 \Bigr] \\
-{}\times\Bigl\{1-
+{}\Bigl\{1-
 \exp\Bigl[
@@
 In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.
-
 ```{=latex}
@@
 
-```{r fig-shannon-convergence-s, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="95%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+```{r fig-shannon-convergence-s, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 
@@
   ggplot() +
-    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
-    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) + #linewidth = 2, alpha=.7
+    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.5) +
+    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 1.1, alpha=.7) + #linewidth = 2, alpha=.7
     scale_color_manual(values = brewer.pal(7, "Dark2")[1:5], labels = alpha_labels) +
@@
 
-```{r fig-renyi-convergence-r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="95%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+```{r fig-renyi-convergence-r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 # fig.fullwidth = TRUE, out.width="95%"
@@
 ggplot() +
-  geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
-  geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) +
+  geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.5) +
+  geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 1.1, alpha=.7) +
   scale_color_manual(values = pal_jama()(7)[2:5], labels = alpha_labels) +
@@
 
-```{r fig-tsallis-convergence-t, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="95%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=7, fig.height=3.2}
+```{r fig-tsallis-convergence-t, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="98%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 # fig.fullwidth = TRUE, out.width="95%"
@@
   ggplot() +
-    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.2) +
-    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 0.9, alpha=.7) +
+    geom_line(data = Entropy_gamma, aes(x = mu, y = Entropy_Gamma), color = "black", linewidth = 1.5) +
+    geom_line(data = muEntropy.molten, aes(x = mu, y = value, color = alpha), linetype = "longdash", linewidth = 1.1, alpha=.7) +
     scale_color_manual(values = pal_lancet()(4), labels = alpha_labels) +
@@
 The definition of Tsallis entropy is given in Equation \eqref{eq:tsallis}, this expression can be reformulated using the quantile function $Q(p)=F^{-1}(p)$, defined for $p\in(0,1)$.
-Since $f(Q(p)) = Q'(p)$, the expectation in \eqref{eq:tsallis} becomes
+Since $f(Q(p)) = 1/Q'(p)$, the expectation in \eqref{eq:tsallis} becomes
 $$
@@
 $$
-   \tilde f_{i,m}\;=\;\frac{n}{2m}\,D_{i,m}^{-1}.
+   \tilde f_{i,m}\;=\;\frac{2m}{n}\,D_{i,m}^{-1}.
 $$
@@
 
-Approximating the integral in \eqref{eq:Tsallis-quantile} with a Riemann sum centered at $t_i\approx\tfrac{i}{n}$ and replacing $Q'(t)$ with the estimator in \eqref{eq:density-spacing}, we obtain the nonparametric plug-in estimator
+Approximating the integral in \eqref{eq:Tsallis-quantile} with a Riemann sum centered at $p_i\approx\tfrac{i}{n}$ and replacing $Q'(p)$ with the estimator in \eqref{eq:density-spacing}, we obtain the nonparametric plug-in estimator
 \begin{align}

### 2025-07-03 Text/Thesis/Chapters/Chapter3.qmd
update derivations in main text

@@
 
-## Optimal $\lambda$ Selection 
+### Optimal $\lambda$ Selection 
 <!-- Finding the Optimal Value of $\lambda$ for the Rényi and Tsallis Entropy Estimators -->
@@
 
-```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
 
@@
 
-```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
+```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
 #fig.show="hide", 
@@
 
-```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="80%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
+```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
 #fig.show="hide", 
@@
 ]
-  \node[box] (raw) {1. Compute\\test statistic\\ $S(\bm{Z})$};
-  \node[box,right=of raw] (std) {2. Standardize\\ $\varepsilon=(S-\hat\mu_S)/\hat\sigma_S$};
-  \node[box,right=of std] (pval) {3. Compute \\ $2\Phi(-|\varepsilon|)$};
-  \node[box,right=of pval] (dec) {4. Reject if\\ $p<0.05$};
+  \node[box] (raw) {1. Calculate\\test statistic\\ $S(\bm{Z})$};
+  \node[box,right=of raw] (std) {2. Standardize\\test statistic\\ $\varepsilon=(S-\hat\mu_S)/\hat\sigma_S$};
+  \node[box,right=of std] (pval) {3. Compute \\ $p$-value \\ $2\Phi(-|\varepsilon|)$};
+  \node[box,right=of pval] (dec) {4. Make decision\\Reject if\\ $p<0.05$};
 
@@
 \end{tikzpicture}
-    \caption{Workflow of the entropy‐based hypothesis test: compute statistic, standardize, derive $p$-value, and decision by threshold $0.05$.}
+    \caption{Workflow of the entropy‐based hypothesis test: calculate test statistic, standardize, derive $p$-value, and make a decision by threshold $0.05$.}
     \label{fig:entropy-diagram-test}

### 2025-07-05 Text/Thesis/Chapters/Chapter1.qmd
thesis update

@@
 Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021; @Zeng2020].
-SAR imagery finds extensive applications in environmental monitoring, disaster management, agriculture mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023].
+SAR imagery finds extensive applications in environmental monitoring, disaster management, agricultural mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023].
 Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013;@Choi2019].
@@
 
-To propose and evaluate entropy-based statistical tests for detecting heterogeneity in SAR imagery, using non-parametric estimation and bootstrap correction to enhance accuracy in small-sample scenarios.
+To propose and evaluate entropy-based statistical tests for detecting heterogeneity in SAR imagery, using non-parametric estimation and bootstrap bias-correction to enhance accuracy in small-sample scenarios.
 

### 2025-07-05 Text/Thesis/Chapters/Chapter2.qmd
A detail in Chapter 2
thesis update

@@
 
-Statistical modeling plays a central role in the analysis of SAR imagery, where speckle is a fundamental characteristic.
-The main distributions considered for SAR intensity data are the $\Gamma_{\text{SAR}}$ distribution, which is suitable for fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].
+Statistical modeling plays a central role in the analysis of SAR imagery, where speckle is an inherent feature.
+For SAR intensity data, two main probability models are employed: the SAR-Gamma distribution ($\Gamma_{\text{SAR}}$), a reparameterization of the classical Gamma law suited to fully developed speckle, and the $\mathcal{G}^0_I$ distribution, which can describe varying levels of heterogeneity&nbsp;[@Frery1997].
 
@@
 \end{equation}
-provided $\alpha <-r$, and infinite otherwise.
+provided that $\alpha <-r$, and infinite otherwise.
 Therefore, assuming $\alpha<-1$, its expected value is
 \begin{equation}
-    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
+    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\Gamma(L)}=-\frac{\gamma}{\alpha+1}.
     \label{E:mean1}
@@
 Although the $\mathcal{G}_I^0$ distribution is defined by the parameters $\alpha$ and $\gamma$, in the SAR literature&nbsp;[@Nascimento2010] the texture $\alpha$ and the mean $\mu$ are usually used.
-Reparametrizing&nbsp;\eqref{E:gi01} with $\mu$, and denoting this model as $Z \sim \mathcal{G}_I^0(\alpha, \mu, L)$ we obtain:
+Reparameterizing&nbsp;\eqref{E:gi01} with $\mu$, and denoting this model as $Z \sim \mathcal{G}_I^0(\alpha, \mu, L)$ we obtain:
 \begin{equation}
@@
 \end{equation}
-
 where  $\Delta_\alpha$ represents the \textit{excess entropy} induced by the roughness parameter $\alpha$.
@@
 \label{E:entropy-R}
-R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
+R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \,\mathrm{d}z.
 \end{equation}
@@
 I
-= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
+= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,\mathrm{d}z
 = C^{\lambda}
   \int_{0}^{\infty}
-    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
+    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,\mathrm{d}z,
 \qquad
@@
 I \;=\;\int_{0}^{\infty}
-        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
+        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,\mathrm{d}z
     \;=\;C^{\lambda}\!
         \int_{0}^{\infty}\!
-          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
-$$
-With the change of variable $t=Lz/\gamma$ ($dz=\gamma\,dt/L$) we obtain:
+          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,\mathrm{d}z,
+$$
+With the change of variable $t=Lz/\gamma$ ($\,\mathrm{d}z=\gamma\,\,\mathrm{d}t/L$) we obtain:
 $$
@@
   \int_{0}^{\infty}
-    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,dt.
+    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,\mathrm{d}t.
 $$
@@
 $$
-\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,dt
+\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,\mathrm{d}t
 = B(a,b),\;\;
@@
 T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
-= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} dz \Bigr]. 
+= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} \,\mathrm{d}z \Bigr]. 
 \end{equation}
@@
   $T_\lambda(Z)\to H(Z)$, making Tsallis a
-  one-parameter generalisation of Shannon entropy.
+  one-parameter generalization of Shannon entropy.
 
@@
 \begin{equation*}
-J
-= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \, dz.
+I
+= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \,\mathrm{d}z.
 \end{equation*}
@@
 \begin{equation*}
-J
+I
 = \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
@@
      z^{\lambda(L-1)}
-     \exp\left(-\frac{\lambda L}{\mu} z\right)\, dz.
+     \exp\left(-\frac{\lambda L}{\mu} z\right)\,\mathrm{d}z.
 \end{equation*}
@@
 \begin{equation}
-J
+I
 = \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
@@
 
-\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} aand the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:
-\begin{equation*}
-J = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda dz,
+\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} and the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:
+\begin{equation*}
+I = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda \,\mathrm{d}z,
 \end{equation*}
@@
 \begin{equation*}
-J = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
-\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}  dz.
+I = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}\,\mathrm{d}z.
 \label{eq:J_initial}
 \end{equation*}
-Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $dz = \frac{\gamma}{L} dt$), we obtain
+Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $\mathrm{d}z = \frac{\gamma}{L}\,\mathrm{d}t$), we obtain
 \begin{align}
-J &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+I &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
 \frac{\gamma}{L} \int_0^\infty \frac{\left( \frac{\gamma t}{L} \right)^{\lambda(L-1)}}
-{[\gamma(1 + t)]^{\lambda(L - \alpha)}}  dt\nonumber \\
+{[\gamma(1 + t)]^{\lambda(L - \alpha)}}\,\mathrm{d}t\nonumber \\
 &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
 \frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L-1)}} 
-\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}  dt.
+\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}\,\mathrm{d}t.
 \label{eq:J_transformed1}
@@
 \begin{equation*}
-\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},
+\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}}\,\mathrm{d}z = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},
 \end{equation*}
@@
 \begin{equation}
-J = \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
+I = \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
 \frac{\gamma^{1-\lambda}}{L^{1-\lambda}} 
@@
 \begin{equation*}
-J = [-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 
+I = [-\mu(\alpha + 1)]^{1-\lambda} L^{\lambda-1} 
 \left[ \frac{\Gamma(L - \alpha)}{\Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
@@
     ]
-    % Tu diagrama aquí...
     \node[entropy] (shannon) {Shannon \ $H(Z)$};
@@
 
-Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed (i.i.d) random sample of size $n$ from drawn from a continuous distribution with cumulative distribution function (CDF) $F(z)$, let $Z_{(1)} \le Z_{(2)} \le \cdots \le Z_{(n)}$ denote the ordered sample, known as the order statistics.
+Let $\bm{Z}=(Z_1, Z_2,\ldots,Z_n)$ be an independent and identically distributed (i.i.d.) random sample of size $n$ from drawn from a continuous distribution with cumulative distribution function (cdf) $F(z)$, let $Z_{(1)} \le Z_{(2)} \le \cdots \le Z_{(n)}$ denote the ordered sample, known as the order statistics.
 
@@
 
-This result suggests that, under the true CDF, the transformed spacings are uniformly spread in expectation.
+This result suggests that, under the true cdf, the transformed spacings are uniformly spread in expectation.
 Consequently, a simple density estimate around the point $Z_{(i)}$ can be motivated by the approximation:
@@
 
-Let $F^{-1}(p)$ denote the quantile function (inverse CDF) of the distribution. We use $Q(p)$ as shorthand for $F^{-1}(p)$, so $Q:(0,1)\to \mathbb{R}$ satisfies $Q(p) = z$ if and only if $F(z) = p$.
-
-Since $F(z)$ is monotonic, $Q(p)$ is differentiable wherever $f(z)$ is positive, with derivative $Q'(p) = \frac{d}{dp}F^{-1}(p)$. By the inverse function theorem, $Q'(p) = \frac{1}{f(Q(p))}$.
+Let $F^{-1}(p)$ denote the quantile function (inverse cdf) of the distribution. We use $Q(p)$ as shorthand for $F^{-1}(p)$, so $Q:(0,1)\to \mathbb{R}$ satisfies $Q(p) = z$ if and only if $F(z) = p$.
+
+Since $F(z)$ is monotonic, $Q(p)$ is differentiable wherever $f(z)$ is positive, with derivative $Q'(p) = \frac{d}{\mathrm{d}p}F^{-1}(p)$. By the inverse function theorem, $Q'(p) = \frac{1}{f(Q(p))}$.
 
 Starting from the definition of Shannon entropy in Equation \eqref{eq:entropy-sh}, a change of variables $p = F(z)$ can be applied.
-When $z = Q(p)$, it follows that $dz = Q'(p)\,dp$.
+When $z = Q(p)$, it follows that $\mathrm{d}z = Q'(p)\,\mathrm{d}p$.
 Substituting into the integral:
@@
   H(Z)
-  &= -\int_{0}^{1} f(Q(p))\ln f(Q(p))\cdot Q'(p)\,dp \\
-  &= -\int_{0}^{1} \ln f(Q(p))\,dp.
+  &= -\int_{0}^{1} f(Q(p))\ln f(Q(p))\cdot Q'(p)\,\mathrm{d}p \\
+  &= -\int_{0}^{1} \ln f(Q(p))\,\mathrm{d}p.
 \end{align*}
@@
 \begin{equation}
-  H(Z) = \int_{0}^{1} \ln Q'(p)\,dp = \int_{0}^{1} \ln \left(\frac{d}{dp}F^{-1}(p)\right) dp.
+  H(Z) = \int_{0}^{1} \ln Q'(p)\,\mathrm{d}p = \int_{0}^{1} \ln \left(\frac{d}{\mathrm{d}p}F^{-1}(p)\right)\,\mathrm{d}p.
 \end{equation}
@@
 
-We consider the following entropy estimators variants, as discussed by Cassetti et al.&nbsp;[-@Cassetti2022].
+We consider the following entropy estimators variants as discussed by Cassetti et al.&nbsp;[-@Cassetti2022].
 
@@
 \begin{align*}
-\int f^\lambda(z)\,dz
-&= \int_0^1 [f(Q(p))]^\lambda \cdot Q'(p)\,dp \\
-&= \int_0^1 [Q'(p)]^{1 - \lambda}\,dp.
+\int f^\lambda(z)\,\mathrm{d}z
+&= \int_0^1 [f(Q(p))]^\lambda \cdot Q'(p)\,\mathrm{d}p \\
+&= \int_0^1 [Q'(p)]^{1 - \lambda}\,\mathrm{d}p.
 \end{align*}
@@
 \begin{equation}
-R_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_0^1 [Q'(p)]^{1 - \lambda}\,dp \right).
+R_\lambda(Z) = \frac{1}{1 - \lambda} \ln \left( \int_0^1 [Q'(p)]^{1 - \lambda}\,\mathrm{d}p \right).
 \label{eq:renyi-quantile}
@@
   \mathbb{E}\bigl[f^{\lambda-1}(Z)\bigr] 
-  = \int_{0}^{1} \bigl(Q'(p)\bigr)^{1-\lambda}\,dp,
+  = \int_{0}^{1} \bigl(Q'(p)\bigr)^{1-\lambda}\,\mathrm{d}p,
 $$
@@
      \left\{
-       1-\int_{0}^{1}\bigl(Q'(p)\bigr)^{1-\lambda}\,dp
+       1-\int_{0}^{1}\bigl(Q'(p)\bigr)^{1-\lambda}\,\mathrm{d}p
      \right\}.

### 2025-07-05 Text/Thesis/Chapters/Chapter4.qmd
thesis update

@@
 
-## ANALYSIS WITH SIMULATED DATA
+## ANALYSIS WITH SIMULATED DATA {#sec-sim2}
 
@@
 
-## APPLICATIONS TO SAR DATA
+## APPLICATIONS TO SAR DATA {#sec-sim3}
 
@@
 The ROC analysis aligns with the classification metrics, supporting the conclusion that Tsallis and Rényi are more effective in detecting heterogeneity across varying image conditions.
+
+## INTERACTIVE SHINY APP FOR HETEROGENEITY DETECTION
+
+Shiny is an R package (version 1.9.1) developed by RStudio (now Posit) that makes it possible to build interactive web applications directly from R code, without requiring knowledge of HTML, CSS or JavaScript.
+Users can manipulate inputs (e.g.
+sliders, file uploads, dropdowns) and see results update instantly in the browser.
+
+To facilitate reproducibility and allow exploration of the heterogeneity-detection pipeline on both simulated and real SAR images, we have developed a Shiny web application.
+
+The app supports three data‐loading modes:
+
+- **Simulated image examples**: Choose one of two simulated images (e.g. $L=5$ or $L=9$).
+
+- **ENVI sample images**:  Select one of three small SAR samples in ENVI format (e.g. Dublin $L=16$, London $L=1$, or New Orleans $L=12$).
+
+- **Upload ENVI**: Upload any custom \texttt{.img}/\texttt{.hdr} pair to process your own data.
+
+Once the image is loaded, the user can select one of three entropy estimators (Shannon, Rényi, or Tsallis), set the order $\lambda$ (for Rényi and Tsallis), specify the number of looks $L$, enable or disable bootstrap resampling (and choose the number of replicates), and fix the sliding‐window size $n \times n$.
+By clicking **Run Detection**, the app performs the sliding‐window test and displays the resulting $p$-value heat‐map in color.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.96\textwidth]{Figures/shiny2.png}
+  \caption{Shiny application interface. The left panel shows the data‐loading and parameter controls; the right panel displays the colorized $p$-value map and elapsed runtime.}
+  \label{fig:shiny-app}
+\end{figure}
+
+This interactive tool complements the results presented in Sections \ref{sec-sim2} and \ref{sec-sim3} by enabling real‐time parameter tuning and direct comparison across estimators.
+
+The application is publicly accessible at:
+[https://janeth-alpala.shinyapps.io/heterogeneity\_detection\_app/](https://janeth-alpala.shinyapps.io/heterogeneity\_detection\_app/)

### 2025-07-05 Text/Thesis/Frontmatter/abstract.tex
thesis update

@@
 under varying sample sizes and numbers of looks.
-Results demonstrate that the Rényi and Tsallis-based tests outperform the Shannon-based version by 
-detecting more subtle texture variations while maintaining greater reliability in identifying 
+Results demonstrate that the Rényi and Tsallis-based tests outperform the Shannon-based test by detecting subtler texture variations 
+while maintaining greater reliability in identifying 
 truly homogeneous regions.

### 2025-07-05 Text/Thesis/Frontmatter/acknowledgements.tex
thesis update

Firstly, I would like to thank my supervisors, Prof. Alejandro Frery and Prof. Abraão do Nascimento, for their guidance, dedication, and support throughout these years. 
Working with you has been an incredibly valuable learning experience. 
I truly appreciate the attention and dedication you give to your students.

I am also grateful to the Universidade Federal de Pernambuco and the 
Graduate Program in Statistics for their support during my academic journey. 
Special thanks to Prof. Pablo Rodriguez for all his help with administrative matters and for his patience.

I gratefully acknowledge the financial support provided by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior – Brasil (CAPES) – Finance Code 001, 
the Programa de Doutorado-Sanduíche no Exterior (PDSE), and the Fundação de Amparo à Ciência e Tecnologia do Estado de Pernambuco (FACEPE).

I also thank the examination committee for their availability.

To my family, thank you for always supporting and encouraging me along the way.

Finally, thanks to all the friends I met during this time. Your support and friendship 
made this experience better.

### 2025-07-05 Text/Thesis/Frontmatter/resumo.tex
thesis update

@@
 Por fim, a metodologia é aplicada a dados SAR simulados e reais. 
-A análise é realizada com janelas deslizantes, gerando mapas de valores de $p$ que permitem a a
-valiação visual e quantitativa da heterogeneidade espacial. O teste baseado na entropia de 
+A análise é realizada com janelas deslizantes, gerando mapas de valores de $p$ que permitem a 
+avaliação visual e quantitativa da heterogeneidade espacial. O teste baseado na entropia de 
 Rényi mostra desempenho superior na identificação de padrões de rugosidade em pequena escala, 

### 2025-10-27 Text/Thesis/Chapters/Chapter1.qmd
final version thesis

@@
 
-Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021; @Zeng2020].
-SAR imagery finds extensive applications in environmental monitoring, disaster management, agricultural mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023].
-Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013;@Choi2019].
+Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021].
+SAR images are widely applied in environmental monitoring&nbsp;[@Amitrano2021], 
+disaster assessment&nbsp;[@Ge2020], 
+agriculture&nbsp;[@Changan2019], 
+urban planning&nbsp;[@Esch2010;@NovelTechniquesforBuiltupAreaExtractionfromPolarimetricSARImages2019], and  maritime surveillance&nbsp;[@Cao2024;@OntheDetectionandLongTermPathVisualisationofa68Iceberg], among other fields&nbsp;[@Moreira2013].
+Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013].
 
@@
 Parameter estimation for these statistical models, however, presents significant challenges, especially when using small-sized windows necessary to preserve spatial resolution in SAR images.
-Traditional likelihood-based or moment-based estimators often become biased or unstable under these practical constraints&nbsp;[@Nascimento2010; @VasconcellosFrerySilva].
-This limitation motivates alternative statistical approaches not reliant on precise parameter estimation or large sample sizes.
+Traditional parametric approaches, such as maximum likelihood estimation and moment-based methods, often become biased or unstable under these practical constraints&nbsp;[@Nascimento2010; @VasconcellosFrerySilva].
+Moreover, likelihood ratio tests derived from these estimators may exhibit unreliable behavior when applied to small-window SAR data due to flat likelihood surfaces.
 
@@
 
-<!-- The primary objective of this thesis is to develop and validate a set of entropy-based statistical tests for the detection of heterogeneity in SAR intensity images.
-These tests are designed to distinguish between fully developed speckle, modeled by the Gamma distribution, and heterogeneous clutter, modeled by the $\mathcal{G}_I^0$ distribution, in a robust and interpretable manner.
--->
-
 ### General Objective
@@
 
-<!-- 4.
-**Comprehensive validation.** Evaluation of the statistical performance of the proposed tests through extensive Monte Carlo simulations, analyzing Type I error (size), power, and robustness under various speckle and texture conditions.
--->
+### Related Publications
 
-<!-- 5.
-**Real applications.** Application of the proposed methodology to both simulated and real SAR data, producing $p$-value maps through sliding window analysis for visual and quantitative assessment of spatial heterogeneity.
--->
+The following peer-reviewed articles and conference papers have been published as part of or related to this research:
 
-## COMPUTATIONAL SUPPORT AND REPRODUCIBILITY
+- [-@Alpala2025]: [ALPALA, J.; NASCIMENTO, A.
+D.
+C.; FRERY, A.
+C.
+Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy.
+\textit{IEEE Geoscience and Remote Sensing Letters}, p.
+1--1, 2025.](https://openaccess.wgtn.ac.nz/articles/journal_contribution/Quantifying_Heterogeneity_in_SAR_Imagery_with_the_R_nyi_Entropy/29376944?file=55548095)
 
-Simulations, tests, and data analyses presented in this thesis were implemented using the free, open-source programming language \texttt{R}\footnote{\url{https://www.r-project.org/}} within \texttt{RStudio} (version 2024.12.1+563, \texttt{R} version 4.4.2).
+- [-@Frery2024]: [FRERY, A.
+C.; ALPALA, J.; NASCIMENTO, A.
+D.
+C.
+Identifying Heterogeneity in SAR Data with New Test Statistics.
+\textit{Remote Sensing}, v.
+16, n.
+11, p.
+1973, 2024.](https://www.mdpi.com/2072-4292/16/11/1973)
+
+- [-@Alpala2024]: [ALPALA, J.; NASCIMENTO, A.
+D.
+C.; FRERY, A.
+C.
+Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy.
+In: \textit{2024 International Conference on Machine Intelligence for GeoAnalytics and Remote Sensing (MIGARS)}, 2024.](https://ieeexplore.ieee.org/document/10544448)
+
+- [-@Alpala2023]: [ALPALA, R.
+J.; BORBA, A.
+A.
+De; FRERY, A.
+C.
+Quality Assessment measures for explainable fusion Of statistical evidences of edges in Polsar images: A First Approach.
+In: \textit{IGARSS 2023 - IEEE International Geoscience and Remote Sensing Symposium}, 2023.](https://ieeexplore.ieee.org/abstract/document/10283263)
+
+## COMPUTATIONAL SUPPORT AND REPRODUCIBILITY {#sec-repr}
+
+Simulations, tests, and data analyses presented in this thesis were implemented using the free, open-source programming language \texttt{R}\footnote{\url{https://www.r-project.org/}} within \texttt{RStudio} (version 2025.09.1+401, \texttt{R} version 4.5.1).
 The manuscript was written in \texttt{Quarto}\footnote{\url{https://quarto.org/}}, a dynamic publishing system that integrates code, output, and narrative to ensure full reproducibility&nbsp;[@bauer2023reproducible].
 
-The numerical experiments were performed on a personal computer equipped with an AMD Ryzen 9 5900X 12-Core Processor (3.70 GHz) and 32 GB RAM.
+The numerical experiments were performed on a workstation equipped with an Intel\textsuperscript{\textregistered} Core\texttrademark Ultra 9 285 CPU (2.5 GHz, 24 cores), 128 GB RAM, and an NVIDIA\textsuperscript{\textregistered} GeForce RTX 5090 GPU (31 GB VRAM), running Windows 11 Pro (version 24H2).
 
@@
 This work follows best practices recommended by Frery et al.&nbsp;[-@Frery2020].
-
-### Related Publications
-
-The following peer-reviewed articles and conference paper have been published as part of or related to this research:
-
-1.
-[@Alpala2025]: [Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy.](https://openaccess.wgtn.ac.nz/articles/journal_contribution/Quantifying_Heterogeneity_in_SAR_Imagery_with_the_R_nyi_Entropy/29376944?file=55548095)
-
-2. [@Frery2024]: [Identifying Heterogeneity in SAR Data with New Test Statistics.](https://www.mdpi.com/2072-4292/16/11/1973)
-
-3.
-[@Alpala2024]: [Identifying departures from the fully developed speckle hypothesis in intensity SAR data with non-parametric estimation of the entropy.](https://ieeexplore.ieee.org/document/10544448)
 

### 2025-10-27 Text/Thesis/Chapters/Chapter2.qmd
final version thesis

@@
 \begin{equation}
-	f_{\Gamma_{\text{SAR}}}\bigl(z;L, \mu \bigr) 
+	f_{\Gamma_{\mathrm{SAR}}}\bigl(z;\mu, L\bigr) 
     = \frac{L^L}{\Gamma(L)\,\mu^L} z^{L-1} 
@@
 \begin{equation}
-    f_{\mathcal{G}^0_I}\bigl(z; \mu, \alpha, L \bigr) 
+    f_{\mathcal{G}^0_I}\bigl(z;  \alpha, \mu, L \bigr) 
     = \frac{L^L\,\Gamma(L-\alpha)}
@@
 $$
-f_{\mathcal{G}^0_I}\big(z; \mu, \alpha, L\big)
+f_{\mathcal{G}^0_I}\big(z;  \alpha, \mu, L\big)
 \longrightarrow 
-f_{\Gamma_{\text{SAR}}}(z;L, \mu) \quad \text{ when } \alpha\to-\infty.
+f_{\Gamma_{\text{SAR}}}(z; \mu, L) \quad \text{ when } \alpha\to-\infty.
 $$
@@
 In the context of SAR imaging, homogeneous areas produce fully developed speckle and are effectively modeled by the $Z \sim\Gamma_{\text{SAR}}(L, \mu)$ distribution.
-In contrast, textured or heterogeneous regions are better represented by the  $Z \sim\mathcal{G}^0_I(\mu, \alpha, L)$ model, where the roughness parameter $\alpha$ controls the degree of heterogeneity.
+In contrast, textured or heterogeneous regions are better represented by the  $Z \sim\mathcal{G}^0_I( \alpha, \mu, L)$ model, where the roughness parameter $\alpha$ controls the degree of heterogeneity.
 Across this section, we show that all three entropy measures applied to $\mathcal{G}^0_I$ can be decomposed as:
@@
   \label{eq:entropy-sh}
-  H(Z) =   -\mathbb{E}\bigl[ \ln f(z)\bigr]=-\int_{-\infty }^\infty f(z)\ln f(z)\, \mathrm{d}z,
-\end{equation}
-where $f(\cdot)$ is the pdf that characterizes the distribution of the real-valued random variable $Z$.
+  H(Z) =   -\mathbb{E}\bigl[ \ln f(z)\bigr]=-\int_{\mathcal{B}} f(z)\ln f(z)\, \mathrm{d}z,
+\end{equation}
+where $f(\cdot)$ is the pdf that characterizes the distribution of the real-valued random variable $Z$ and $\mathcal{B} \subseteq \mathbb{R}$ denotes the support of $f(z)$.
 
@@
 \label{eq:gamma-sh1}
-H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) = L - \ln L + \ln\Gamma(L) + (1 - L)\psi^{(0)}(L) + \ln \mu,
+H\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr) = L - \ln L + \ln\Gamma(L) + (1 - L)\psi^{(0)}(L) + \ln \mu,
 \end{equation}
@@
 \label{eq:GIO-Sh1}
-H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) =H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)\;+\;
+H\bigl(\mathcal{G}^0_I(\alpha, \mu, L)\bigr) =H\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr)\;+\;
 \Bigl[ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)
@@
 $$
-\lim_{\alpha \to -\infty} H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
-$$ 
-Appendix&nbsp;\ref{app:A1} provides a proof of this limiting behavior.
+\lim_{\alpha \to -\infty} H\bigl(\mathcal{G}^0_I( \alpha, \mu, L)\bigr) = H\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr).
+$$ 
+Appendix A provides a proof of this limiting behavior.
 <!-- This motivates our work: we check whether the \emph{excess} is statistically different from zero.  -->
@@
 \label{E:entropy-R}
-R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \,\mathrm{d}z.
-\end{equation}
+R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{\mathcal{B}} [f(z)]^\lambda \,\mathrm{d}z,
+\end{equation}
+where $\mathcal{B} \subseteq \mathbb{R}$ denotes the support of $f(z)$.
 As $\lambda \to 1$, $R_{\lambda}(Z)$ reduces to the Shannon entropy $H(Z)$.
@@
 
-\textbf{Homogeneous case.} Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$ with pdf given in \eqref{E:gamma1}. We compute
+\textbf{Homogeneous case.} Let $Z\sim\Gamma_{\mathrm{SAR}}(\mu, L)$ with pdf given in \eqref{E:gamma1}. We compute
 $$
 I = \int_{0}^{\infty}
-    \bigl[f_{\Gamma_{\mathrm{SAR}}}(z;L,\mu)\bigr]^{\lambda}
+    \bigl[f_{\Gamma_{\mathrm{SAR}}}(z;\mu, L)\bigr]^{\lambda}
     \,\mathrm{d}z
@@
 Substituting into \eqref{E:entropy-R} yields the closed-form
+\begingroup\small
 \begin{equation}
@@
   \boxed{
-  R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
+  R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr)
   = \ln\mu - \ln L
@@
 \end{equation}
-
+\endgroup
 \textbf{Textured case.} Starting from the definition of Rényi entropy in  \eqref{E:entropy-R} and the pdf of  $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ given in \eqref{E:gi01}, we define:
@@
 The parameterisation satisfies $\gamma=-\mu(\alpha+1)$, so the final result will be expressed in terms of $\mu$.
-
+\vspace{-15pt}
 $$
@@
 where $a + b = \lambda(L - \alpha)$, we have
+\vspace{-10pt}
 \begin{multline}
@@
 Finally, noting that $\gamma = -\mu(\alpha + 1)$ from \eqref{E:rmom}, and substituting this expression into \eqref{eq:GI0RenyiInGamma1}, we obtain:
+\vspace{-15pt}
 \begin{multline*}
@@
 \end{multline*}
-This expression extends the Rényi entropy of the $\Gamma_{\mathrm{SAR}}(L,\mu)$ model \eqref{eq-GammaSAR-R} by including additional terms that depend on the texture parameter $\alpha$. Specifically:
+This expression extends the Rényi entropy of the $\Gamma_{\mathrm{SAR}}(\mu, L)$ model \eqref{eq-GammaSAR-R} by including additional terms that depend on the texture parameter $\alpha$. Specifically:
+\begingroup\small
 \begin{equation}
@@
 R_{\lambda}\bigl(\mathcal{G}^0_I(\alpha,\mu,L)\bigr)
-&=R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
+&=R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr)
   +\ln(-1-\alpha) \\
@@
 \end{equation}
+\endgroup
 Equation&nbsp;\eqref{eq-HGI0-R} can be read as:
@@
 $$
-\lim_{\alpha \to -\infty} R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
-$$ 
-Appendix&nbsp;\ref{app:A24} provides proof of this limiting behavior.
-
-### Tsallis entropy
+\lim_{\alpha \to -\infty} R_\lambda\bigl(\mathcal{G}^0_I( \alpha, \mu, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
+$$ 
+Appendix A provides proof of this limiting behavior.
+
+### Tsallis Entropy
 
@@
 T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
-= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} \,\mathrm{d}z \Bigr]. 
-\end{equation}
+= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{\mathcal{B}} \bigl(f(z)\bigr)^{\lambda} \,\mathrm{d}z \Bigr],
+\end{equation}
+where $\mathcal{B} \subseteq \mathbb{R}$ denotes the support of $f(z)$.
 In the limit $\lambda\to1$,
@@
 \textbf{Homogeneous case.} 
-Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$  with pdf given by \eqref{E:gamma1}. Define the integral:
+Let $Z\sim\Gamma_{\mathrm{SAR}}(\mu, L)$  with pdf given by \eqref{E:gamma1}. Define the integral:
 \begin{equation*}
 I
-= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \,\mathrm{d}z.
+= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;\mu, L)\right]^{\lambda} \,\mathrm{d}z.
 \end{equation*}
@@
 \begin{equation}
-T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big)
+T_\lambda\big(\Gamma_{\text{SAR}}(\mu, L)\big)
 = \frac{1}{\lambda - 1}
@@
 <!-- \begin{equation*} -->
-<!-- T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big) -->
+<!-- T_\lambda\big(\Gamma_{\text{SAR}}(\mu, L)\big) -->
 <!-- = \frac{1}{\lambda - 1} \left[ -->
@@
 <!-- \end{equation*} -->
+\begingroup\small
 \begin{equation}
@@
 \begin{aligned}
-T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
+T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr)=
 \frac{1}{\lambda-1}\Bigl\{1-
@@
 \end{equation}
-
+\endgroup
 \textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} and the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:
@@
 \end{equation}
-To express $J$ in terms of the mean $\mu$, we use the relation $\gamma = -\mu(\alpha + 1)$ valid for $\alpha < -1$. Substituting into \eqref{eq:J_beta1} gives
+To express $I$ in terms of the mean $\mu$, we use the relation $\gamma = -\mu(\alpha + 1)$ valid for $\alpha < -1$. Substituting into \eqref{eq:J_beta1} gives
 \begin{equation*}
@@
 \end{equation*}
-This expression extends the Tsallis entropy of the $\Gamma_{\mathrm{SAR}}(L,\mu)$ model \eqref{eq:gammasar-Tsallis} by including additional terms that depend on the texture parameter $\alpha$.
+This expression extends the Tsallis entropy of the $\Gamma_{\mathrm{SAR}}(\mu, L)$ model \eqref{eq:gammasar-Tsallis} by including additional terms that depend on the texture parameter $\alpha$.
 It can be written in an exponential-logarithmic form as:
+\begingroup\small
 \begin{equation}
@@
 \begin{aligned}
-  T_\lambda\bigl(\mathcal{G}^0_I(\mu,\alpha,L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)\;+\;\frac{1}{\lambda-1}\,
+  T_\lambda\bigl(\mathcal{G}^0_I(\mu,\alpha,L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(\mu, L)\bigr)\;+\;\frac{1}{\lambda-1}\,
   \exp\Bigl[
@@
 \end{equation}
+\endgroup
 Equation&nbsp;\eqref{eq:GI0-Tsallis} can be interpreted as:
@@
 $$
-\lim_{\alpha \to -\infty} T_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
-$$ 
-Appendix&nbsp;\ref{app:A33} provides proof of this limiting behavior.
+\lim_{\alpha \to -\infty} T_\lambda\bigl(\mathcal{G}^0_I( \alpha, \mu, L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
+$$ 
+Appendix A provides proof of this limiting behavior.
 
@@
 In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.
+
 ```{=latex}
@@
   \centering
+  \caption{Conceptual diagram of entropy decomposition.}
+  \label{fig:entropy-diagram}
+
   \begin{tikzpicture}[
-    node distance=1.5cm,
-    entropy/.style={rectangle, rounded corners, draw=blue!60, fill=blue!10, thick, minimum width=3cm, align=center, font=\sffamily},
-    property/.style={rectangle, draw=orange!60, fill=orange!10, thick, minimum width=3cm, align=center, font=\sffamily},
+    scale=0.88, every node/.style={transform shape},
+    node distance=1.2cm,
+    entropy/.style={
+      rectangle, rounded corners, draw=blue!60, fill=blue!10, thick,
+      minimum width=2.6cm, align=center, font=\sffamily
+    },
+    property/.style={
+      rectangle, draw=orange!60, fill=orange!10, thick,
+      minimum width=2.6cm, align=center, font=\sffamily
+    },
     arrow/.style={-Stealth, thick}
   ]
+
   \node[entropy] (shannon) {Shannon \ $H(Z)$};
@@
 
-    \node[property, below=2cm of renyi] (decomp) {Entropy Decomposition\\[0.5ex]
+  \node[property, below=1.6cm of renyi] (decomp) {Entropy Decomposition\\[0.5ex]
     $\text{Entropy}\bigl(\mathcal{G}^{0}_{I}\bigr)
@@
 
-    \node[property, below left=1.1cm of decomp, align=center] (baseline) {Homogeneous Baseline\\($\Gamma_{\text{SAR}}$)};
-    \node[property, below right=1.1cm of decomp, align=center] (texture) {Texture-Induced Excess\\($\Delta_{\alpha}$)};
-
-    \node[property, below=1.8cm of texture, align=center] (limits) {Vanishing Excess\\ $\Delta_\alpha \to 0$ as $\alpha\to -\infty$};
-    \node[property, below=1.8cm of baseline, align=center] (test) {Statistical Test\\ $\Delta_\alpha \neq 0?$};
+  % --- OJO: espacio tras \\ para que NO sea \(
+  \node[property, below left=1.0cm of decomp, align=center] (baseline)
+    {Homogeneous Baseline\\ ($\Gamma_{\text{SAR}}$)};
+  \node[property, below right=1.0cm of decomp, align=center] (texture)
+    {Texture-Induced Excess\\ ($\Delta_{\alpha}$)};
+
+  \node[property, below=1.5cm of texture, align=center] (limits)
+    {Vanishing Excess\\ $\Delta_\alpha \to 0$ as $\alpha\to -\infty$};
+  \node[property, below=1.5cm of baseline, align=center] (test)
+    {Statistical Test\\ $\Delta_\alpha \neq 0?$};
 
@@
   \draw[arrow] (texture.south west) -- (test.east);
+
   \end{tikzpicture}
-    \caption{Conceptual diagram of entropy decomposition.}
-    \label{fig:entropy-diagram}
 \end{figure}
+
 ```
@@
 
-By taking logarithms and averaging over $i$, Vasicek’s estimator&nbsp;[-@vasicek1976test] becomes:
+By taking logarithms and averaging over $i$, Vasicek’s estimator becomes:
 \begin{equation}
@@
 
-Vasicek showed that under regularity conditions ($m \to \infty$, $m/n \to 0$), $\widehat{H}_{\text{V}} \to H(f)$ in probability.
+Vasicek&nbsp;[-@vasicek1976test] showed that under regularity conditions ($m \to \infty$, $m/n \to 0$), $\widehat{H}_{\text{V}} \to H(f)$ in probability.
 
 Nonparametric estimators using order statistics and spacings, such as Vasicek’s m-spacing estimator, provide a flexible alternative to model-based entropy estimation.
-By converting the entropy integral into a quantile-based form (see Appendix&nbsp;\ref{app:Vasicek}), these estimators offer robust, consistent estimation of Shannon entropy without requiring explicit density estimation.
+By converting the entropy integral into a quantile-based form (see Appendix B), these estimators offer robust, consistent estimation of Shannon entropy without requiring explicit density estimation.
 
@@
 
-A detailed derivation of this estimator, including the quantile-based transformation and spacing approximation, is provided in Appendix&nbsp;\ref{app:tsallis_1}.
+A detailed derivation of this estimator, including the quantile-based transformation and spacing approximation, is provided in Appendix B.
 

### 2025-10-27 Text/Thesis/Chapters/Chapter3.qmd
final version thesis

@@
 
+As shown in the simulation results, the estimators $\widehat{H}_{\text{C}}$, $\widehat{H}_{\text{E}}$, and $\widehat{H}_{\text{AO}}$ show low bias and achieve convergence for sample sizes larger than 81.
+These estimators exhibit good behavior in terms of bias and MSE across various parameter combinations.
+
+In contrast, estimator $\widehat{H}_{\text{N}}$ displays the lowest MSE across all scenarios.
+However, the bias remains unchanged and high for sample sizes larger than 25, indicating that the convergence is not very fast.
+Additionally, we observe that both $\widehat{H}_{\text{V}}$ and $\widehat{H}_{\text{VE}}$ estimators exhibit larger bias and slower convergence compared to their counterparts.
+Notably, the $\widehat{H}_{\text{V}}$ estimator shows the highest MSE.
+
 ```{=latex}
-\begin{figure}[H]
+\begin{figure}[htb]
 \caption{Performance of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.}\label{fig:Plot_bias_mse-sh}
@@
 #| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.'
+#| tbl-pos: 'htb'
 
@@
 
-As shown in the simulation results, the estimators $\widehat{H}_{\text{C}}$, $\widehat{H}_{\text{E}}$, and $\widehat{H}_{\text{AO}}$ show low bias and achieve convergence for sample sizes larger than 81.
-These estimators exhibit good behavior in terms of bias and MSE across various parameter combinations.
-
-In contrast, estimator $\widehat{H}_{\text{N}}$ displays the lowest MSE across all scenarios.
-However, the bias remains unchanged and high for sample sizes larger than 25, indicating that the convergence is not very fast.
-Additionally, we observe that both $\widehat{H}_{\text{V}}$ and $\widehat{H}_{\text{VE}}$ estimators exhibit larger bias and slower convergence compared to their counterparts.
-Notably, the $\widehat{H}_{\text{V}}$ estimator shows the highest MSE.
-
 Although the estimators $\widehat{H}_{\text{C}}$, $\widehat{H}_{\text{E}}$, and $\widehat{H}_{\text{AO}}$ demonstrate good performance in terms of bias and MSE for sufficiently large samples (e.g., $n \geq 81$), practical scenarios in SAR image processing often involve much smaller sample sizes.
@@
 A bias-corrected estimator is then defined by subtracting the estimated bias from the original estimator, as expressed in Equation \eqref{eq:bias_corrected}:
+\vspace{-10pt}
 \begin{equation}
@@
 \end{equation}
+\vspace{-5pt}
 Substituting the estimate from Equation \eqref{eq:bias_estimate} into Equation \eqref{eq:bias_corrected} yields the explicit formula for the corrected estimator:
@@
 This tendency to overestimate persists with the use of bootstrap, contributing to an increase in bias and MSE.
-
 The most notable improvements are observed with $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$, which achieve both low bias and MSE even for small sample sizes, demonstrating faster convergence.
@@
 @tbl-out-time shows the processing time of each estimator across different settings of $L$  and $n$.
+The results indicate that $\widetilde{H}_{\text{AO}}$ consistently achieves lower computational times compared to $\widetilde{H}_{\text{C}}$.
+This makes it the more efficient option, particularly relevant for large datasets, such as SAR images discussed in @sec-Chapter4.
+Consequently, $\widetilde{H}_{\text{AO}}$ is selected as the representative non-parametric Shannon entropy estimator in the simulations presented in the following sections.
 
@@
 
-\renewcommand{\arraystretch}{1.1}
+\renewcommand{\arraystretch}{1.3}
 ```{r}
@@
 #| tbl-cap: 'Processing time for bootstrap-improved estimators $\widetilde{H}_{\text{C}}$ and $\widetilde{H}_{\text{AO}}$'
+#| tbl-pos: 'htb'
 
@@
   #table.envir= "table",
- # position   = "H",
+ # position   = "htb",
   linesep    = ""
@@
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", full_width = TRUE)
-
-```
-
-The results indicate that $\widetilde{H}_{\text{AO}}$ consistently achieves lower computational times compared to $\widetilde{H}_{\text{C}}$.
-This makes it the more efficient option, particularly relevant for large datasets, such as SAR images discussed in @sec-Chapter4.
-Consequently, $\widetilde{H}_{\text{AO}}$ is selected as the representative non-parametric Shannon entropy estimator in the simulations presented in the following sections.
+  kable_styling(font_size = 10,latex_options = "scale_down", full_width = TRUE)
+```
+\vspace{-20pt}
 
 ### Optimal $\lambda$ Selection
-<!-- Finding the Optimal Value of $\lambda$ for the Rényi and Tsallis Entropy Estimators -->
 
@@
 
-```{r fig-optimal_order,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3}
+The estimators remained numerically stable and converged smoothly to Shannon entropy as $\lambda \to 1$. 
+Outside this range ($\lambda < 0.7$ or $\lambda > 1$), bias and MSE increased, indicating reduced numerical precision. 
+These results confirm that the selected $\lambda$ values ensure stable and reliable entropy estimates under typical SAR conditions.
+
+```{r fig-optimal_order,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
 #fig.show="hide", 
@@
 
-```{r fig-optimal_order-tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3}
+```{r fig-optimal_order-tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
 #fig.show="hide", 
@@
 ```
-
 <!-- ```{=latex} -->
@@
 <!-- ``` -->
+\vspace{-15pt}
 In the case of $L = 1$, the bootstrap procedure does not provide meaningful improvement and often leads to unstable estimates.
@@
 Under these conditions, higher values of $\lambda$ yield better results: $\lambda = 3$ is preferred for the Rényi estimator, and $\lambda = 1.2$ for the Tsallis estimator.
+\vspace{-15pt}
 
@@
 Using the optimal values of the order parameter ($\lambda = 0.9$ for Rényi and $\lambda = 0.85$ for Tsallis) already identified in the earlier analysis, we compute the bias and MSE for both the original and bootstrap-corrected versions of the estimators.
-As illustrated in Figures \ref{fig-bias_mse_rm1} and \ref{fig-bias_mse_Tsallis}, the bootstrap estimators consistently show improved performance, especially for small samples.
-In particular, at $n = 49$, both estimators exhibit low bias and MSE, confirming their robustness in moderate sample regimes and supporting their use in practical applications.
-
+As illustrated in Figures&nbsp;\ref{fig-bias_mse_rm1} and \ref{fig-bias_mse_Tsallis}, the bootstrap estimators consistently show improved performance for small samples.
+\vspace{-10pt}
 ```{r Simulated_data_bias_m1, echo=FALSE, message=FALSE }
@@
 
-```{r fig-bias_mse_rm1,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=4}
+```{r fig-bias_mse_rm1,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.5}
 
@@
 
-```{r fig-bias_mse_Tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="H",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=4}
+```{r fig-bias_mse_Tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="htb",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.6}
 
@@
 ```
+
+\vspace{-15pt}
+
+In particular, at $n = 49$, both estimators exhibit low bias and MSE, confirming their robustness in moderate sample regimes and supporting their use in practical applications.
 
@@
 The proposed statistic is defined as:
+\begingroup\small
 \begin{equation}
@@
 \end{equation}
+\endgroup
 where $\widehat{\mu} = \frac{1}{n} \sum_{i=1}^n Z_i$ is the sample mean.
@@
 We assume the number of looks $L \geq 1$ is known and use the following formulation:
-
+\vspace{-12pt}
 \begin{multline}
@@
 \end{multline}
-
 where $\widehat{\mu} = \frac{1}{n} \sum_{i=1}^n Z_i$ is the sample mean.
@@
 As in the previous cases, this test statistic measures the difference between the empirical entropy and its theoretical counterpart under the assumption of fully developed speckle:
+\vspace{-5pt}
 $$
@@
 
-\subsection*{Empirical behaviour of the three statistics}
+\subsection{Empirical Behaviour of the Three Statistics}
 
 Figures [-@fig-densities-shannon]-[-@fig-densities-tsallis4] display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.
+
 All three empirical densities are tightly concentrated around zero, confirming that under $\mathcal{H}_0$ the test statistic has mean approximately $0$; at the same time, their moderately heavy tails reveal sensitivity to departures from homogeneity, which is desirable for detecting subtle texture.
@@
     \centering
+     \caption{Workflow of the entropy‐based hypothesis test: calculate test statistic, standardize, derive $p$-value, and make a decision by threshold $0.05$.}
+    \label{fig:entropy-diagram-test}
 \begin{tikzpicture}[
@@
 \end{tikzpicture}
-    \caption{Workflow of the entropy‐based hypothesis test: calculate test statistic, standardize, derive $p$-value, and make a decision by threshold $0.05$.}
-    \label{fig:entropy-diagram-test}
+  %\caption*{\footnotesize\textbf{Source:} The author (2025)} 
 \end{figure}
@@
 
-In the next chapter, we apply this procedure to SAR images using a sliding window of size $7 \times 7$ pixels.
+<!-- In the next chapter, we apply this procedure to SAR images using a sliding window of size $7 \times 7$ pixels.
 For each window, we compute the corresponding test statistic and derive a $p$-value, which quantifies the statistical evidence against local homogeneity.
@@
 Conversely, low $p$-values (e.g., $p < 0.05$)  suggest statistically significant deviations and are interpreted as heterogeneity.
+-->
 
@@
 
-\renewcommand{\arraystretch}{1}
+\renewcommand{\arraystretch}{0.9}
 ```{r Table_size_and_power-shannon3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 
-\renewcommand{\arraystretch}{1}
+\renewcommand{\arraystretch}{0.9}
 ```{r Table_size_and_power-renyi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
@@
 ```
+
+## FIXED AND ADAPTIVE WINDOWS
+
+This section outlines the two local windowing strategies that will be used in the next chapter to evaluate the proposed entropy-based tests on both simulated and real SAR intensity data.
+
+### Fixed Sliding Windows
+
+The first strategy uses a fixed sliding window of size $7 \times 7$ pixels. 
+For each window, the test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ will be computed, and the associated $p$-values derived. 
+The $p$-value measures evidence against the null hypothesis of homogeneity (fully developed speckle under the $\Gamma_{\text{SAR}}$ model).
+High values (e.g., $p>0.05$) will be interpreted as no significant deviation from homogeneity, whereas low $p$-values (e.g., $p<0.05$) will be taken as *evidence of heterogeneity*.
+These $p$-values will later be visualized as maps to enable spatial assessment.
+
+### Adaptive Windows
+
+The second strategy, used only with the Tsallis-entropy test $S_{\widetilde{T}_{\lambda}}$, builds on the adaptive windowing algorithm by Park et al.
+[-@Park1999].
+The analysis window size is adjusted according to the local homogeneity of the scene.
+For each pixel $(i,j)$, let $w_{ij}$ be the window centered at $(i,j)$ with radius $N_{ij}$, defined as  
+$w_{ij} = \{(i',j') \,/\, i-N_{ij} \le i' \le i+N_{ij} \,\wedge\, j-N_{ij} \le j' \le j+N_{ij}\}$.  
+The border of this window is given by  
+$b_{ij} = \{(i',j') \in w_{ij} \,/\, i' = i-N_{ij} \,\vee\, i' = i+N_{ij} \,\vee\, j' = j-N_{ij} \,\vee\, j' = j+N_{ij}\}$.
+
+The coefficient of variation is computed over the border of the current window as $C_{ij} =\frac{\sigma_{ij}}{\mu_{ij}}$, where the mean $\mu_{ij}$ and the standard deviation $\sigma_{ij}$ are calculated using only the border pixels $b_{ij}$ of $w_{ij}$.
+
+For SAR intensity images (fully developed speckle with $L$ looks), the coefficient of variation in homogeneous areas satisfies
+\begin{equation*}
+C_{ij} \approx \sigma_n := \frac{1}{\sqrt{L}}.
+\end{equation*}
+
+The homogeneity criterion is defined by comparing $C_{ij}$ with an adaptive threshold $U_{ij}$:
+\begin{equation*}
+U_{ij} = \eta\!\left( 1 + \sqrt{\frac{1 + 2\sigma_n^2}{8\,(W_{ij} - 1)}} \right)\sigma_n,
+\end{equation*}
+where $W_{ij} = 2N_{ij} + 1$ is the current window side length, and $\eta$ is a tuning parameter controlling the degree of smoothing.
+Values close to $\eta=1$ provide limited speckle suppression, while larger values increase smoothing and yield stronger noise reduction.
+
+The window radius $N_{ij}$ is updated dynamically and locally as follows:
+$$
+N_{i,j}^{\text{updated}} =
+\begin{cases}
+\min\{N_{ij} + 1,\, N_{\max}\}, & \text{if } C_{ij} \leq U_{ij}, \\
+\max\{N_{ij} - 1,\, N_{\min}\}, & \text{if } C_{ij} > U_{ij},
+\end{cases}
+$$
+where $N_{\max}$ and $N_{\min}$ denote the maximum and minimum allowed window size, respectively.
+Hence, windows *grow* in homogeneous regions (stabilizing estimates) and *shrink* in heterogeneous areas (preserving edges and avoiding class mixing).
+
+Once the window radius $N_{ij}$ has been determined for pixel $(i,j)$, the corresponding full window is extracted and the proposed test in \eqref{eq-test-tsallis} is applied to obtain the local test statistic.
+This produces two outputs: (i) a map of test statistics over the image, and (ii) a window-size map $W_{ij}$ that records the locally selected window side (larger in homogeneous regions, smaller in heterogeneous ones).
+For inference, each value of the test statistic is standardized using the empirical mean and standard deviation of the image, and two-sided $p$-values are then computed.
+
+In the experiments presented in the next chapter, the Tsallis-based test statistic $S_{\widetilde{T}{\lambda}}$ will be applied to both simulated and real SAR images using adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$), with the smoothing parameter set to $\eta = 3$.
+For comparison, a fixed $7\times7$ window configuration will also be evaluated.

### 2025-10-27 Text/Thesis/Chapters/Chapter4.qmd
final version thesis

@@
 This layout serves as a base template to generate the simulated images shown in Figures&nbsp;\ref{fig:sim_Phantom_2}–\ref{fig:sim_Phantom_3}.
-
 Each region is filled with data simulated from the $\mathcal{G}^0_I$ distribution&nbsp;\eqref{E:gi02}, using different combinations of the roughness parameter $\alpha$ and the mean $\mu$, as indicated by the labels in each quadrant of the image.
@@
   \centering
-  \hspace{0.5em}
-  \begin{subfigure}[b]{0.37\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{Figures/Phantom1}
+  \caption{Synthetic dataset.}
+  \label{fig:sim_Phantom}
+  \hspace{2em}
+  \begin{subfigure}[b]{0.34\textwidth}
+    \centering
     \caption{Phantom.}
     \label{fig:sim_Phantom_1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[b]{0.50\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{Figures/Phantom_labels}
+    \includegraphics[width=\linewidth]{Figures/Phantom1}
+    \end{subfigure}
+  \vspace{1.2em} 
+  %\hspace{0.48em}
+  \begin{subfigure}[b]{0.43\textwidth}
+    \centering
     \caption{Simulated image, varying $\alpha$ and $\mu$, with $L=5$.}
     \label{fig:sim_Phantom_2}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[b]{0.50\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{Figures/Phantom4_L9}
+    \includegraphics[width=\linewidth]{Figures/Phantom_labels}
+      \end{subfigure}
+  \hfill
+  %\hspace{0.48em}
+  \begin{subfigure}[b]{0.43\textwidth}
+    \centering
     \caption{Simulated image, varying $\alpha$ and $\mu$, with $L=9$.}
     \label{fig:sim_Phantom_3}
-  \end{subfigure}
-  \caption{Synthetic dataset.}
-  \label{fig:sim_Phantom}
+    \includegraphics[width=\linewidth]{Figures/Phantom4_L9}
+      \end{subfigure}
+  %\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
 
-The $\alpha$ parameter of the $G_I^0$ distribution is essential for
+The $\alpha$ parameter of the $\mathcal{G}_I^0$ distribution is essential for
 interpreting texture characteristics. Values near zero greater than
@@
 
-We applied the three test statistics, $S_{\widetilde{H}_{\text{AO}}}$,  $S_{\widetilde{R}_{\lambda}}$, and
-$S_{\widetilde{T}_{\lambda}}$, to the simulated images using local sliding windows of size $7\times 7$.
-Figures&nbsp;\ref{fig:sim1r} and&nbsp;\ref{fig:sim2t} show the $p$-value maps (top row) and the corresponding binary maps (bottom row) for two simulations with $L=5$ and $L=9$, respectively.
-The $p$-value maps (Figures&nbsp;\ref{fig:sim1a}–\ref{fig:sim1c} and \ref{fig:sim2a}–\ref{fig:sim2c}) are displayed as gradient color maps, where dark blue tones (close to $0$) indicate strong evidence of heterogeneity, and lighter tones (toward red, near $1$) correspond to more homogeneous areas.
-
-The binary maps (Figures&nbsp;\ref{fig:sim1d}–\ref{fig:sim1f} and \ref{fig:sim2d}–\ref{fig:sim2f}) simplify these results using a threshold of $0.05$: pixels corresponding to $p$-values below this threshold are shown in black, suggesting statistically significant deviations and thus indicating heterogeneity.
-In contrast, pixels with $p \geq 0.05$ are displayed in white, representing no evidence to reject the null hypothesis of homogeneity.
+We evaluated the three test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on simulated images using fixed sliding windows of size $7\times7$ and, for Tsallis only, the adaptive windowing strategy with side lengths from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$) and smoothing parameter $\eta=3$.
+Figures&nbsp;\ref{fig:sim1t} and \ref{fig:sim2t} present, respectively for $L=5$ and $L=9$, the $p$-value maps (top row) and the corresponding binary decision maps (bottom row).
+
+The $p$-value maps (Figures&nbsp;\ref{fig:sim1a}–\ref{fig:sim1d} and \ref{fig:sim2a}–\ref{fig:sim2d}) are shown with a continuous color scale: dark red ($p\!\approx\!0$) indicates strong evidence of heterogeneity, while dark blue ($p\!\approx\!1$) corresponds to homogeneous areas.
+Intermediate colors follow a smooth progression orange ($p\!\approx\!0.2$–$0.4$) for transitional textures and yellow–green to cyan ($p\!\approx\!0.4$–$0.8$) for increasingly near-homogeneous regions.
+
+The binary maps (Figures&nbsp;\ref{fig:sim1e}–\ref{fig:sim1h} and \ref{fig:sim2e}–\ref{fig:sim2h}) simplify these results using a threshold of $0.05$.
+Pixels with $p$-values below this threshold are shown in black, indicating statistically significant deviations and, therefore, heterogeneity.
+In contrast, pixels with $p \geq 0.05$ are displayed in white, showing no evidence to reject the null hypothesis of homogeneity.
+
+When the number of looks increases to $L=9$ (Figure&nbsp;\ref{fig:sim2t}), the maps become cleaner due to reduced speckle.
+All tests successfully detect areas with different texture levels, although some differences remain.
+The Rényi-based statistic $S_{\widetilde{R}_{\lambda}}$ is more sensitive to texture variations, highlighting fine patterns of heterogeneity, while the Tsallis-based $S_{\widetilde{T}_{\lambda}}$ produces cleaner results in uniform areas by reducing false detections.
+This behavior reflects their formulations: Rényi entropy emphasizes variability, whereas Tsallis entropy is more robust to noise, helping to preserve homogeneous regions.
+
+The adaptive Tsallis version further improves visual quality, larger windows in homogeneous areas yield smoother estimates, and smaller windows in heterogeneous regions enhance detail preservation.
 
 ```{=latex}
-\begin{figure}[hbt]
-    \centering
-
+\begingroup
+\setlength{\textfloatsep}{6pt} % menos espacio entre texto y figuras
+\setlength{\floatsep}{6pt} % menos espacio entre figuras
+\setlength{\intextsep}{6pt}
+
+\begin{figure}[hbtp]
+    \centering
+ \caption{Results on simulated data ($L = 5$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
+(a-c) $p$-value maps with a fixed $7\times7$ window.
+(d) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. (e-h) Binary decision maps at 0.05 significance level.}
+    \label{fig:sim1t}
     % Primera fila
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_b200_w7-AO.png}
-        \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
         \label{fig:sim1a}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_0.9_b200_w7-renyi.png}
-        \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \includegraphics[width=\linewidth]{Figures/p-values_L5_4_z_b100_w7-AO.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
         \label{fig:sim1b}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom_4_z_0.85_b200_w7-tsallis77.png}
-        \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \includegraphics[width=\linewidth]{Figures/p-values_L5_4_z_b100_w7-renyi.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
         \label{fig:sim1c}
-    \end{subfigure}
-
+        \includegraphics[width=\linewidth]{Figures/p-values_L5_4_z_b100_w7-tsallis.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\tiny{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:sim1d}
+        \includegraphics[width=\linewidth]{Figures/p-values_L5_Tsallis_adaptive.png}
+            \end{subfigure}
     \vspace{1em} % Espacio entre filas
@@
     % Segunda fila
-    \hspace{-2.5em}
-    \begin{subfigure}{0.25\textwidth}
+    \hspace{-0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:sim1e}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_b200_w7-AO.png}
-        \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:sim1d}
-    \end{subfigure}
-    \hspace{2.8em}
-    \begin{subfigure}{0.25\textwidth}
+            \end{subfigure}
+    \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:sim1f}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_0.9_b200_w7-renyi.png}
-        \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:sim1e}
-    \end{subfigure}
-     \hspace{3.1em}
-    \begin{subfigure}{0.25\textwidth}
+    \end{subfigure}
+     \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:sim1g}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom_4_z_0.85_b200_w7-tsallis.png}
-        \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:sim1f}
-    \end{subfigure}
-    \caption{Results on simulated data ($L = 5$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
-Top: $p$-value heatmaps.
-Bottom: binary maps ($5\%$ level).}
-%\caption{Comparison of test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on a simulated image with $L = 5$.
-Top row: heatmaps of $p$-values computed using a $7 \times 7$ sliding window.
-Bottom row: binary maps at the 5\% significance level, where black pixels indicate rejection of the null hypothesis of homogeneity.}
-    \label{fig:sim1r}
+        \end{subfigure}
+    \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary~map~$\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:sim1h}
+        \includegraphics[width=\linewidth]{Figures/H_005_L5_Tsallis_adaptive_085.png}
+    \end{subfigure}
+   %\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
-```
-
-```{=latex}
-\begin{figure}[hbt]
-    \centering
-
+\vspace{-0.25\baselineskip} 
+\begin{figure}[hbtp]
+    \centering
+ \caption{Results on simulated data ($L = 9$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
+(a-c) $p$-value maps with a fixed $7\times7$ window.
+(d) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. (e-h) Binary decision maps at 0.05 significance level.}
+    \label{fig:sim2t}
     % Primera fila
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_b100_w7-AO-H.png}
-        \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
         \label{fig:sim2a}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_b100_w7-09-renyi.png}
-        \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$}
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_1_8_b100_w7-AO.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
         \label{fig:sim2b}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/Phantom4_L9_1_8_0.85_b100_w7-tsallis.png}
-        \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_SIM_renyi_7x7.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
         \label{fig:sim2c}
-    \end{subfigure}
-
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_SIM_tsallis_7x7.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\tiny{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:sim2d}
+        \includegraphics[width=\linewidth]{Figures/p-values_L9_SIM_tsallis_adaptative.png}
+            \end{subfigure}
     \vspace{1em} % Espacio entre filas
@@
     % Segunda fila
-    \hspace{-1.6em}
-    \begin{subfigure}{0.25\textwidth}
+    \hspace{-0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:sim2e}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_b100_w7-AO.png}
-        \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:sim2d}
-    \end{subfigure}
-    \hspace{3.0em}
-    \begin{subfigure}{0.25\textwidth}
+            \end{subfigure}
+    \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:sim2f}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_b100_w7-09-renyi.png}
-        \caption{Binary map  $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:sim2e}
-    \end{subfigure}
-     \hspace{3.1em}
-    \begin{subfigure}{0.25\textwidth}
+    \end{subfigure}
+     \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:sim2g}
         \includegraphics[width=\linewidth]{Figures/0.05_Phantom4_L9_1_8_0.85_b100_w7-tsallis.png}
-        \caption{Binary map  $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:sim2f}
-    \end{subfigure}
-    \caption{Results on simulated data ($L = 9$) using $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$.
-Top: $p$-value heatmaps.
-Bottom: binary maps ($5\%$ level).}
-   %  \caption{Comparison of test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on a simulated image with $L = 9$.
-Top row: heatmaps of $p$-values computed using a $7 \times 7$ sliding window.
-Bottom row: binary maps at the 5\% significance level, where black pixels indicate rejection of the null hypothesis of homogeneity.}
-    \label{fig:sim2t}
+        \end{subfigure}
+    \hspace{0.5em}
+    \begin{subfigure}{0.23\textwidth}
+    \caption{Binary~map~$\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:sim2h}
+        \includegraphics[width=\linewidth]{Figures/H_005_L9_tsallis_adaptative.png}
+    \end{subfigure}
+   %\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
-```
-
-When the number of looks increases to $L=9$ (Figure&nbsp;\ref{fig:sim2t}), the maps become cleaner due to reduced speckle.
-All tests are able to detect zones with different levels of texture.
-However, some differences can be observed.
-The statistic $S_{\widetilde{R}_{\lambda}}$, based on Rényi entropy, is very sensitive to changes in texture and often highlights small variations and detailed patterns of heterogeneity.
-In contrast, $S_{\widetilde{T}_{\lambda}}$, based on Tsallis entropy, tends to avoid false detections in uniform areas and produces cleaner results.
-This is due to the underlying formulation: Rényi entropy emphasizes variability, making it effective in identifying heterogeneity; while Tsallis entropy is more robust to noise, which helps preserve homogeneous regions.
+\endgroup
+```
+
+\newpage
 
@@
 
-### SAR dataset and preprocessing {#sec:SAR-data}
-
-We evaluated the proposed test statistics using a set of eight SAR images acquired from different radar missions.
-These images cover diverse locations: the surroundings of London (United Kingdom), San Francisco (USA), Rotterdam (Netherlands), the outskirts of Munich and the city of New Orleans (USA), Dublin Port (Ireland), the coast of Jalisco (Mexico), and the area around Foggia (Italy) as shown in Figures&nbsp;\ref{fig:london-sar}-\ref{fig:fo-sar}.
-The selected scenes include a variety of land types, such as urban zones, mountainous areas, agricultural regions, and water bodies.
+### SAR Dataset and Preprocessing {#sec:SAR-data}
+
+We evaluated the proposed test statistics using a set of five SAR images acquired from different radar missions.
+These images cover diverse locations: the surroundings of London (United Kingdom), the outskirts of Munich, the city of New Orleans (USA), Dublin Port (Ireland), and the coast of Jalisco (Mexico), as shown in Figures&nbsp;\ref{fig:london-sar}–\ref{fig:ja-sar}.
+The selected scenes include a variety of land types, such as urban areas, mountainous regions, agricultural zones, and water bodies.
 This diversity allows us to assess the performance of the proposed statistical tests under different texture conditions.
 
-To help interpret the SAR images, we also included corresponding optical images (Figures&nbsp;\ref{fig:london-optical}-\ref{fig:fo-optical}) obtained from Sentinel-2 Level-2A products.
+To facilitate interpretation, we also included the corresponding optical images (Figures&nbsp;\ref{fig:london-optical}–\ref{fig:ja-optical}) obtained from Sentinel-2 Level-2A products.
 These optical scenes were acquired on dates close to those of the SAR acquisitions to ensure visual consistency.
@@
 
-The SAR images come from different missions: TanDEM-X, PAZ, and ICEYE (all operating in the X-band), UAVSAR (L-band), and Sentinel-1B (C-band).
-The two UAVSAR images were obtained from the Alaska Satellite Facility (ASF) platform\footnote{\url{https://search.asf.alaska.edu/}}, which provides access to airborne and satellite SAR data.
-The remaining images were downloaded from the European Space Agency’s Third Party Missions (ESA TPM) data service\footnote{\url{https://tpm-ds.eo.esa.int/collections/}}, which offers SAR products from various external missions operated by international partners and commercial providers.
-All images are single-polarization (HH or VV), and their acquisition parameters vary in resolution, scene size, and number of looks.
-
-Table&nbsp;\ref{tab:table_param} summarizes the main characteristics of each SAR image, including the spatial resolution, acquisition date, and number of looks.
+The SAR images come from TanDEM-X (X-band), UAVSAR (L-band), and Sentinel-1B (C-band).
+The two UAVSAR images were obtained from the Alaska Satellite Facility (ASF)\footnote{\url{https://search.asf.alaska.edu/}}, which provides airborne and satellite SAR data.
+The X-band images were downloaded from ESA’s Third Party Missions (ESA TPM)\footnote{\url{https://tpm-ds.eo.esa.int/collections/}}, and the C-band image from Copernicus Data Space.
+All images use single polarization (HH or VV), and their acquisition settings differ in resolution, scene size, and number of looks.
+Table&nbsp;\ref{tab:table_param} lists the main characteristics of each SAR image.
 
@@
 SAR_data <- data.frame(
-  Site = c("London", "San Francisco",  "Rotterdam", "Munich","New Orleans", "Dublin","Coast of Jalisco", "Foggia" ),
-  Mission = c("TanDEM-X", "PAZ", "TanDEM-X","UAVSAR", "UAVSAR", "TanDEM-X", "Sentinel-1B", "Iceye"),
-  Band = c("X",  "X","X","L","L", "X", "C", "X"),
-  Polarization = c("HH", "HH", "HH","HH","HH","HH", "VV", "VV"),
-  Size = c("$2000\\times2000$", "$3300\\times3300$",  "$1200\\times1200$", "$1024\\times1024$","$1400\\times1400$", "$1100\\times1100$","$512\\times512$","$1900\\times1900$"),
-  L = c(1, 1, 9, 12, 12,  16,18, 24),
-  Resol = c("$0.99/0.99$", "$1.84/1.84$",   "$2.5/2.5$", "$4.9/7.2$","$4.9/7.2$", "$1.35/1.35$","$40/40$", "$2.08/2.08$"),
-  Date = c("12-11-2021","30-07-2020","06-12-2018", "16-04-2015","13-03-2016", "03-09-2017","29-08-2021","28-03-2024")
+  Site = c("London",  "Munich","New Orleans", "Dublin","Coast of Jalisco" ),
+  Mission = c("TanDEM-X", "UAVSAR", "UAVSAR", "TanDEM-X", "Sentinel-1B"),
+  Band = c("X", "L","L", "X", "C"),
+  Polarization = c("HH", "HH","HH","HH", "VV"),
+  Size = c("$2000\\times2000$",  "$1024\\times1024$","$1400\\times1400$", "$1100\\times1100$","$512\\times512$"),
+  L = c(1,  12, 12,  16,18),
+  Resol = c("$0.99/0.99$",  "$4.9/7.2$","$4.9/7.2$", "$1.35/1.35$","$40/40$"),
+  Date = c("12-11-2021", "16-04-2015","13-03-2016", "03-09-2017","29-08-2021")
 )
@@
 
-We applied the three bootstrap statistics
-$S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$ and
-$S_{\widetilde{T}_{\lambda}}$ to eight intensity images as shown Figures&nbsp;\ref{fig:london-sar}-\ref{fig:fo-sar} using $7\times 7$ local sliding windows. Each figure is organised in three rows:
-the first row displays the SAR scene and a matching Sentinel-2
-optical image, the second row shows heat-maps of the
-$p$-values produced by the three tests, and the third row presents the
-binary decisions at the $5\%$ significance level
-(black $\,=\,$ heterogeneous, white $\,=\,$ homogeneous).
-
-Across all scenes the three tests identify the main textured elements
-(urban blocks, harbor facilities, roads, crop boundaries, mountainous areas, and river
-banks).  In the $p$-value heat-maps dark-blue tones
-($p\!<\!0.05$) cluster over these features, whereas red tones
-($p\!\approx\!1$) dominate smooth areas such as open water, uniform
-pasture or crop areas.  The corresponding binary maps make this pattern explicit, delineating heterogeneous areas with a black mask.
-
-The London and San Francisco images, acquired with $L=1$, exhibit strong speckle, making heterogeneity detection more difficult. 
-Among the three tests, the Rényi-based statistic $S_{\widetilde{R}{\lambda}}$ offers the most informative response: its $p$-value maps show dark-blue tones over heterogeneous regions and strong red tones ($p \approx 1$) over clearly homogeneous areas such as water bodies and smooth crop zones.
-In contrast, the Shannon and Tsallis-based tests produce $p$-value maps with softer, intermediate colors, which makes it harder to clearly distinguish between textured and smooth areas.
-Although the binary maps look generally similar, $S_{\widetilde{R}_{\lambda}}$ gives more precise and reliable detections, even under strong speckle.
-
-As the number of looks increases (Rotterdam, Munich and
-the remaining images) speckle is reduced and all tests
-improve, but differences persist:
-$S_{\widetilde{R}_{\lambda}}$ keeps the highest sensitivity to
-texture changes, whereas $S_{\widetilde{T}_{\lambda}}$ produces the
-cleanest white regions, indicating a stronger ability to preserve
-truly homogeneous surfaces.  $\:S_{\widetilde{H}_{\text{AO}}}$ shows an
-intermediate behaviour.
-
-These results mirror the properties already observed with simulated
-data.  The Rényi-based statistic reacts quickly to any local
-fluctuation, making it very effective for spotting heterogeneity even
-under severe speckle.  The Tsallis-based test is
-more conservative: it suppresses small, noisy variations and therefore
-preserves large homogeneous patches, while still detecting clear
-textural boundaries.  The Shannon-based test offers a balanced
-compromise but is less robust when $L$ is very low.
+We applied the three bootstrap statistics, $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$, to the five SAR intensity images in Figures&nbsp;\ref{fig:london-sar}–\ref{fig:ja-sar}.
+The fixed approach uses local sliding windows of size $7\times7$.
+The adaptive approach (used with Tsallis) varies the window side from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$), with smoothing parameter $\eta=3$, and $B=100$ bootstrap replications per window.
+Each figure is organized in three rows: (i) SAR scene and a matching Sentinel-2 optical image, (ii) $p$-value maps for the three tests, and (iii) binary maps at the $5\%$ level (black = heterogeneous, white = homogeneous).
+
+Across all scenes, the three tests detect the main textured elements (urban blocks, port facilities, roads, crop boundaries, mountains, and river banks).
+In the $p$-value maps, dark red ($p\!\approx\!0$) concentrates on heterogeneous areas such as urban blocks, harbor structures, and field edges, while blue ($p\!\approx\!1$) dominates open water and other uniform surfaces.
+Intermediate colors mark transitional textures.
+
+The adaptive Tsallis results are visually better than the fixed windows: in homogeneous regions, the maps look smoother and more stable, while in heterogeneous regions the edges are sharper and fine details are preserved.
+The binary maps make this clear: the adaptive strategy keeps thin structures (roads, levees, dock lines) that are partly lost with the fixed window.
+
+The number of looks also matters.
+With fewer looks (stronger speckle), the adaptive scheme improves urban and boundary detection compared with the fixed window.
+As $L$ increases, speckle decreases and all methods improve, yet the adaptive maps still show cleaner homogeneous areas and crisper boundaries in textured zones.
+
+Comparing statistics, the Rényi-based $S_{\widetilde{R}_{\lambda}}$ is more sensitive to texture changes and often highlights fine-scale heterogeneity.
+The Tsallis-based $S_{\widetilde{T}_{\lambda}}$ is more conservative in uniform areas, reducing false alarms and producing cleaner homogeneous regions.
+The adaptive Tsallis variant combines these benefits with data-driven window sizes, which explains its overall better visual quality across the five scenes.
 
@@
     \centering
-
+\caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+(f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.}
+    \label{fig:london}
     % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/london_2000.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{SAR image}
         \label{fig:london-sar}
+        \includegraphics[width=\linewidth]{Figures/London-sar.jpg}
     \end{subfigure}
     \hspace{2em}
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/london_optical_.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{Optical image}
         \label{fig:london-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_shannon-london_H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
+        \includegraphics[width=\linewidth]{Figures/london-optical.jpg}
+    \end{subfigure}
+
+    \vspace{1.8em}
+
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
         \label{fig:london-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_renyi-london_H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:london-shann-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_tsallis-london_H1_new.png} % <--
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
+        \includegraphics[width=\linewidth]{Figures/london_AO.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:london-renyi1}
+        \includegraphics[width=\linewidth]{Figures/London_renyi.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
         \label{fig:london-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
+        \includegraphics[width=\linewidth]{Figures/london_tsallis.jpg}
+    \end{subfigure}
+\hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:london-tsallis1_ada}
+        \includegraphics[width=\linewidth]{Figures/london_tsalis_adapt_eta3.jpg}
+    \end{subfigure}
+    \vspace{1.8em}
 
     % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.30\textwidth}
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:london-005-shann2}
         \includegraphics[width=\linewidth]{Figures/H_005_london_shannon.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:london-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.30\textwidth}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:london-005-renyi2}
         \includegraphics[width=\linewidth]{Figures/H_005_london_renyi_L1_.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:london-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.30\textwidth}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:london-005-tsallis2}
         \includegraphics[width=\linewidth]{Figures/H_005_london1_TSALLIS.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:london-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:london}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:london-005-tsallis2_Ada}
+        \includegraphics[width=\linewidth]{Figures/H_005_intensity_L1_eta_3.00_5x13_B20_lambda_12.png} %
+    \end{subfigure}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
     \centering
-
+\caption{Detection of heterogeneous areas in a SAR image over the outskirts
+of Munich, Germany: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+(f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.}
+    \label{fig:mu}
     % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/SF_3300.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{SAR image}
-        \label{fig:sf-sar}
+        \label{fig:mun-sar}
+        \includegraphics[width=\linewidth]{Figures/munich_sar.jpg}
     \end{subfigure}
     \hspace{2em}
-    \begin{subfigure}{0.295\textwidth}
-        \includegraphics[width=\linewidth]{Figures/san-francisco-optical1.png}
+    \begin{subfigure}{0.262\textwidth}
             \caption{Optical image}
-        \label{fig:sf-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_results_SF_AO_w7.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:sf-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_SF_3300_renyi_w7_3_L1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:sf-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-valuesL1_SanFrancisco_tsallis_b100_w7s.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:sf-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
+        \label{fig:mun-optical}
+        \includegraphics[width=\linewidth]{Figures/munich_optical1.jpg}
+    \end{subfigure}
+
+    \vspace{1.8em}
+
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:mun-shann1}
+        \includegraphics[width=\linewidth]{Figures/Munich_AO.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:mun-renyi1}
+        \includegraphics[width=\linewidth]{Figures/Munich_renyi.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:mun-tsallis1}
+        \includegraphics[width=\linewidth]{Figures/Munich_tsallis.jpg}
+    \end{subfigure}
+\hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:mun-tsallis1_ada}
+        \includegraphics[width=\linewidth]{Figures/Munich_tsallis_eta3.jpg}
+    \end{subfigure}
+    \vspace{1.8em}
 
     % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_results_ENVI_SF_3300_L1_AO_w7.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:sf-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_SF_3300_renyi_w7_3_L1.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:sf-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L1_SanFrancisco_tsallis_b100_w7_.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:sf-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over San Francisco, USA: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:sf}
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:mun-005-shann2}
+        \includegraphics[width=\linewidth]{Figures/H_005_Munich_AO.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:mun-005-renyi2}
+        \includegraphics[width=\linewidth]{Figures/H_005_Munich_renyi.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:mun-005-tsallis2}
+        \includegraphics[width=\linewidth]{Figures/H_005_Munich_tsallis.png} %
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:mun-005-tsallis2_Ada}
+        \includegraphics[width=\linewidth]{Figures/H_005_Munich_tsallis_eta3.png} %
+    \end{subfigure}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
     \centering
-
+\caption{Detection of heterogeneous areas in a SAR image over New Orleans city, USA: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+(f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.}
+    \label{fig:NO}
     % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/rotterdam_1200_L9_2.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{SAR image}
-        \label{fig:rott-sar}
+        \label{fig:no-sar}
+        \includegraphics[width=\linewidth]{Figures/New-orleans1.jpg}
     \end{subfigure}
     \hspace{2em}
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/rotterdam_optical2.png}
+    \begin{subfigure}{0.245\textwidth}
             \caption{Optical image}
-        \label{fig:rott-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L9_envi_Rotterdam2_size_1200_AO_w7_b100-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:rott-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L16_L9_envi_Rotterdam2_sizeRENYI_1200-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:rott-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L9_Rotterdam2_1200_tsallis_085_B100-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:rott-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
+        \label{fig:no-optical}
+        \includegraphics[width=\linewidth]{Figures/new-orleans-optical1.jpg}
+    \end{subfigure}
+
+    \vspace{1.8em}
+
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:no-shann1}
+        \includegraphics[width=\linewidth]{Figures/new_orleans_AO.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:no-renyi1}
+        \includegraphics[width=\linewidth]{Figures/new_orleans_renyi.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:no-tsallis1}
+        \includegraphics[width=\linewidth]{Figures/new_orleans_tsallis.jpg}
+    \end{subfigure}
+\hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:no-tsallis1_ada}
+        \includegraphics[width=\linewidth]{Figures/new_orleans_tsallis_eta3.jpg}
+    \end{subfigure}
+    \vspace{1.8em}
 
     % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/0.05_L9_envi_Rotterdam2_size_1200_AO_w7_b100.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:rott-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L16_L9_envi_Rotterdam2_sizeRENYI_1200.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:rott-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L9_Rotterdam2_1200_tsallis_lambda85_B100.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:rott-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over Rotterdam, Netherlands: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:rott}
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:no-005-shann2}
+        \includegraphics[width=\linewidth]{Figures/H_005_new_orleans_AO2.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:no-005-renyi2}
+        \includegraphics[width=\linewidth]{Figures/H_005_new_orleans_renyi1.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:no-005-tsallis2}
+        \includegraphics[width=\linewidth]{Figures/H_005_new_orl_tsallis1.png} %
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:no-005-tsallis2_Ada}
+        \includegraphics[width=\linewidth]{Figures/H_005_new_orl_tsallis_eta3.png} %
+    \end{subfigure}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
     \centering
-
+\caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+(f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.}
+    \label{fig:du}
     % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/munich_1024.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{SAR image}
-        \label{fig:mun-sar}
+        \label{fig:no-sar}
+        \includegraphics[width=\linewidth]{Figures/dublin_sar_1100.jpg}
     \end{subfigure}
@@
     \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/munich_optical.png}
             \caption{Optical image}
-        \label{fig:mun-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_shannon-munich-H.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:mun-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_renyi-munich-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:mun-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values__tsallis_lambda85_B100-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:mun-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
+        \label{fig:du-optical}
+        \includegraphics[width=\linewidth]{Figures/dublin_1100.jpg}
+    \end{subfigure}
+
+    \vspace{1.8em}
+
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:no-shann1}
+        \includegraphics[width=\linewidth]{Figures/Dublin_AO_w7.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:du-renyi1}
+        \includegraphics[width=\linewidth]{Figures/Dublin_Renyi_w7.jpg}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:du-tsallis1}
+        \includegraphics[width=\linewidth]{Figures/dublin_tsallis_w7.jpg}
+    \end{subfigure}
+\hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:du-tsallis1_ada}
+        \includegraphics[width=\linewidth]{Figures/dublin_tsallis_adap.jpg}
+    \end{subfigure}
+    \vspace{1.8em}
 
     % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_shannon_munich.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:mun-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_renyi_munich.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:mun-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005L12_envi_munich_size_1024_tsallis_lambda85_B100.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:mun-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over the outskirts
-of Munich, Germany: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:mun}
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:du-005-shann2}
+        \includegraphics[width=\linewidth]{Figures/H_005_dublin_AO_1100.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:du-005-renyi2}
+        \includegraphics[width=\linewidth]{Figures/H_005_dublin_renyi_1100.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:du-005-tsallis2}
+        \includegraphics[width=\linewidth]{Figures/H_005_L16_envi_dublin_size_1100_tsallis_lambda085_B100.png} %
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:du-005-tsallis2_Ada}
+        \includegraphics[width=\linewidth]{Figures/H_005_Dublin_tsallis_eta3.png} %
+    \end{subfigure}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
     \centering
-
+\caption{Detection of heterogeneous areas in a SAR image over the Coast of Jalisco, Mexico: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+(f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for
+$\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.}
+    \label{fig:ja-sar}
     % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/NewOrleans_1400.png}
+    \begin{subfigure}{0.28\textwidth}
             \caption{SAR image}
-        \label{fig:no-sar}
+        \label{fig:ja-sar}
+        \includegraphics[width=\linewidth]{Figures/mexico_sar.jpg}
     \end{subfigure}
@@
     \begin{subfigure}{0.27\textwidth}
-        \includegraphics[width=\linewidth]{Figures/new-orleans-optical.png}
     \caption{Optical image}
-        \label{fig:no-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_shannon-New_or-H.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:no-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_renyi-New_or-H.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:no-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L_12_New_orleans_size_1400_tsallis_lambda085_B100-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:no-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
+        \label{fig:ja-optical}
+        \includegraphics[width=\linewidth]{Figures/mexico3_512.jpg}
+    \end{subfigure}
+
+    \vspace{1.8em}
+
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:ja-shann1}
+        \includegraphics[width=\linewidth]{Figures/p-values_Mexico_AO.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:ja-renyi1}
+        \includegraphics[width=\linewidth]{Figures/p-values_Mexico_renyi.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.24\textwidth}
+            \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:ja-tsallis1}
+        \includegraphics[width=\linewidth]{Figures/p-values_Mexico_tsallis.png}
+    \end{subfigure}
+        \hfill
+    \begin{subfigure}{0.24\textwidth}
+    \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+            \label{fig:ja-tsallis1_ada}
+        \includegraphics[width=\linewidth]{Figures/p-values_Mexico_tsallis_adapt_.png}
+    \end{subfigure}
+
+    \vspace{1.8em}
 
     % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_NewOrleans_1400_AO.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:no-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_NewOrleans_1400_renyi.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:no-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/0.05_L_12_New_orleans_size_1400_tsallis_lambda085_B100.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:no-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over New Orleans city, USA: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:NO}
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)}
+        \label{fig:ja-005-shann2}
+        \includegraphics[width=\linewidth]{Figures/0.05_results_Mexico_512_7_AO_300b.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:ja-005-renyi2}
+        \includegraphics[width=\linewidth]{Figures/0.05_L16_envi_mexico_512_renyi_lambda09_B200.png}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)}
+        \label{fig:ja-005-tsallis2}
+        \includegraphics[width=\linewidth]{Figures/H_005_L18_envi_mexico_tsallis_lambda085_B200_w7_.png} %
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.23\textwidth}
+            \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)}
+        \label{fig:ja-005-tsallis2_ada}
+        \includegraphics[width=\linewidth]{Figures/H_005_Mexico_tsallis_Adtap.png} %
+    \end{subfigure}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
 ```
+
+<!-- ```{=latex} -->
+<!-- \begin{figure}[H] -->
+<!--     \centering -->
+<!-- \caption{Detection of heterogeneous areas in a SAR image over  Foggia, Italy: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
+Top: (a-b) input images (SAR and optical).
+Middle: (c-e) $p$-value maps with a fixed $7\times7$ window.
+-->
+<!-- (f) $p$-value map with adaptive windows ($W_{\min}=5$, $W_{\max}=11$) for -->
+<!-- $\eta=3.0$. Bottom:  (g-j) Binary decision maps at 0.05 significance level.} -->
+<!--     \label{fig:fo} -->
+<!--     % Primera fila: 2 imágenes -->
+<!--     \begin{subfigure}{0.28\textwidth} -->
+<!--             \caption{SAR image} -->
+<!--         \label{fig:fo-sar} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia-sar1.jpg} -->
+<!--     \end{subfigure} -->
+<!--     \hspace{2em} -->
+<!--     \begin{subfigure}{0.276\textwidth} -->
+<!--             \caption{Optical image} -->
+<!--         \label{fig:fo-optical} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia_optical1.jpg} -->
+<!--     \end{subfigure} -->
+
+<!--     \vspace{1.8em} -->
+
+<!--     \begin{subfigure}{0.24\textwidth} -->
+<!--             \caption{$p$-value map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-shann1} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia_AO.jpg} -->
+<!--     \end{subfigure} -->
+<!--     \hfill -->
+<!--     \begin{subfigure}{0.24\textwidth} -->
+<!--             \caption{$p$-value map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-renyi1} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia_renyi.jpg} -->
+<!--     \end{subfigure} -->
+<!--     \hfill -->
+<!--     \begin{subfigure}{0.24\textwidth} -->
+<!--             \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-tsallis1} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia_w7.jpg} -->
+<!--     \end{subfigure} -->
+<!-- \hfill -->
+<!--     \begin{subfigure}{0.24\textwidth} -->
+<!--             \caption{$p$-value map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)} -->
+<!--         \label{fig:fo-tsallis1_ada} -->
+<!--         \includegraphics[width=\linewidth]{Figures/Foggia_eta3.jpg} -->
+<!--     \end{subfigure} -->
+<!--     \vspace{1.8em} -->
+
+<!--     % Tercera fila: 3 imágenes (binary maps) -->
+<!--     \begin{subfigure}{0.23\textwidth} -->
+<!--             \caption{Binary map $\small{S_{\widetilde{H}_{\text{AO}}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-005-shann2} -->
+<!--         \includegraphics[width=\linewidth]{Figures/H_005_AO_italy_1900.png} -->
+<!--     \end{subfigure} -->
+<!--     \hfill -->
+<!--     \begin{subfigure}{0.23\textwidth} -->
+<!--             \caption{Binary map $\small{S_{\widetilde{R}_{\lambda}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-005-renyi2} -->
+<!--         \includegraphics[width=\linewidth]{Figures/H_005_renyi_italy_1900_L1.png} -->
+<!--     \end{subfigure} -->
+<!--     \hfill -->
+<!--     \begin{subfigure}{0.23\textwidth} -->
+<!--             \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ ($7\times7$)} -->
+<!--         \label{fig:fo-005-tsallis2} -->
+<!--         \includegraphics[width=\linewidth]{Figures/H_005_fogia_7x7.png}  -->
+<!--     \end{subfigure} -->
+<!--     \hfill -->
+<!--     \begin{subfigure}{0.23\textwidth} -->
+<!--             \caption{Binary map $\small{S_{\widetilde{T}_{\lambda}}}$ (adapt.)} -->
+<!--         \label{fig:fo-005-tsallis2_Ada} -->
+<!--         \includegraphics[width=\linewidth]{Figures/H_005_FoggiaL24_eta_3.0n_5x11_B100_lambda_081.png} % -->
+<!--     \end{subfigure} -->
+<!-- %\caption*{\footnotesize\textbf{Source:} The author (2025)} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+
+In addition to the visual analysis presented above, we measured execution times to assess the computational cost of the proposed methods.
+Table&nbsp;\ref{tab:table_exec_times} reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$).
+Times are reported in minutes and seconds (mm:ss) with $B=100$ bootstrap replications per window.
+
+Overall, Shannon is the fastest across scenes, which is consistent with its simpler analytical form.
+Rényi and Tsallis are slightly slower due to the evaluation of additional terms.
+As expected, the adaptive Tsallis approach takes the longest because it evaluates multiple window sizes per pixel.
+
+\renewcommand{\arraystretch}{1.8}   
+```{r times_sar_images2, echo=FALSE, message=FALSE, warning=FALSE}
+
+#library(kableExtra)
+
+Times_data <- data.frame(
+Scene = c("Image Simulated 1", "Image Simulated 2", "London",   "Munich", "New Orleans", "Dublin", "Coast of Jalisco"),
+Shannon = c("01:12", "01:16", "12:10",   "07:02", "10:20", "8:39", "01:59"),
+Renyi = c("01:17", "01:27", "13:28",   "8:54", "13:39", "9:44", "02:39"),
+Tsallis = c("01:25", "01:38", "14:10",  "10:02", "14:39", "10:48", "02:54"),
+Tsallis = c("01:50","02:05",   "16:22", "11:49", "15:48", "12:51", "03:20")
+)
+
+colnames(Times_data) <- c(
+"\\textbf{Scene}",
+"\\textbf{Shannon}",
+"\\textbf{Rényi}",
+"\\textbf{Tsallis}",
+"\\textbf{Adaptive Tsallis}"
+)
+
+# colnames(Times_data) <- c(
+#   "\\textbf{Scene}",
+#   "\\textbf{Shannon (mm:ss)}",
+#   "\\textbf{Rényi (mm:ss)}",
+#   "\\textbf{Tsallis (mm:ss)}"
+# )
+
+kable(Times_data,
+format = "latex",
+booktabs = TRUE,
+align = "ccccc",
+escape = FALSE,
+label = "table_exec_times",#adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$)
+centering = TRUE,
+caption = "Execution times for the heterogeneity detection using fixed $7\\times7$ and adaptive windows ($N_{\\min}=5$, $N_{\\max}=11$), with $B=100$ bootstrap replications per scenario.
+Times are given in minutes and seconds (mm:ss).
+Rényi entropy uses $\\lambda=0.9$ and Tsallis entropy uses $\\lambda=0.85$.",
+table.envir = "table", position = "hbt") %>%
+row_spec(0, align = "c") %>%
+kable_styling(latex_options = "scale_down", font_size = 16) %>%
+kable_styling(full_width = TRUE) %>%
+column_spec(1, width = "5cm") %>%
+column_spec(2, width = "3.5cm") %>%
+column_spec(3, width = "3.5cm") %>%
+column_spec(4, width = "3.5cm") %>%
+column_spec(5, width = "4cm")
+
+```
+
+All experiments were executed on the workstation described in @sec-repr, using 8–16 CPU cores. 
+This setup allowed the entropy-based heterogeneity detection tests to process medium-sized SAR scenes within a few minutes, as reported in Table&nbsp;\ref{tab:table_exec_times}.
+
+The total runtime also depends on the number of bootstrap replications ($B$), since each replication recomputes the test statistic to approximate its sampling distribution under the null hypothesis.  
+In our simulations, we used $B=100$, which provides stable and reliable estimates with moderate computational cost.
+Stable results can already be achieved with $B\geq50$, whereas larger values of $B$ yield smoother $p$-value distributions at the expense of longer processing times.
+
+<!-- Overall, the experiments on real SAR images confirm the simulated -->
+<!-- findings: for highly speckled data ($L\!\approx\!1$) the Rényi -->
+<!-- statistic is the most reliable detector of heterogeneity, whereas for -->
+<!-- multi-look products the Tsallis statistic delivers cleaner segmentations -->
+<!-- with fewer false positives.  -->
+
+The window size also plays an important role in the heterogeneity detection process.
+This is particularly evident in the case of the Adaptive Tsallis test, where alternative sliding windows ranging from $5\times5$ to $11\times11$ were explored for both simulated and real SAR datasets.
+Although the observed differences were subtle, the adaptive approach exhibited the expected behavior: larger windows in homogeneous areas produced smoother and more stable estimates, whereas smaller windows in heterogeneous regions effectively preserved structural details and texture transitions.
+
+For the single-look case ($L=1$), the adaptive Tsallis test using larger windows yielded more consistent detections, enhancing sensitivity to textural variations without generating excessive false alarms.
+This confirms that adaptive windowing improves the balance between detection accuracy and spatial smoothness, especially under strong speckle conditions.
+
+Regarding the decision threshold, a significance level of $\alpha = 0.05$ was adopted for the binary classification of the $p$-value maps.
+Additional experiments with alternative levels showed the expected trade-offs: a stricter threshold ($\alpha = 0.01$) reduces false alarms but may overlook weak texture variations, while a more relaxed threshold ($\alpha = 0.10$) increases sensitivity to subtle heterogeneity at the expense of a higher false‐positive rate, particularly in highly speckled regions.
+Therefore, $\alpha = 0.05$ represents a balanced and robust choice for most SAR imaging scenarios.
+
+### Quantitative Evaluation
+
+Eight polygonal regions of interest (ROIs) were manually selected for each of the three SAR scenes used in the quantitative study—London, Munich, and Dublin (Figures&nbsp;\ref{fig:london-sar-roi1}–\ref{fig:dublin-sar-roi1}).
+ROIs labeled in red correspond to heterogeneous areas (class 1) and those in blue to homogeneous areas (class 0).
+The polygons were rasterized to the image grid to form a partial ground truth.
+We thresholded the $p$-value maps at $\alpha=0.05$, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared the resulting decisions with the ground truth to compute the F1-score ($F_1$), the Kappa coefficient ($\kappa$), and the overall accuracy (OA).
+Results are summarized in Table&nbsp;\ref{tab:table_metrics1}.
 
@@
     \centering
-
-    % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/dublin_1100.png}
-        \caption{SAR image}
-        \label{fig:no-sar}
-    \end{subfigure}
-    \hspace{2em}
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/dublin.png}
-        \caption{Optical image}
-        \label{fig:du-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_AO_1100-dublin-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:no-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_renyi_1100-dublin-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:du-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L16_envi_dublin_size_1100_tsallis_lambda085_B100-H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:du-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_dublin_AO_1100.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:du-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_dublin_renyi_1100.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:du-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.28\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L16_envi_dublin_size_1100_tsallis_lambda085_B100.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:du-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over Dublin Port, Ireland: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:du}
-\end{figure}
-```
-
-```{=latex}
-\begin{figure}[H]
-    \centering
-
-    % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/mexico_512.png}
-        \caption{SAR image}
-        \label{fig:ja-sar}
-    \end{subfigure}
-    \hspace{2em}
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/mexico2_512.png}
-        \caption{Optical image}
-        \label{fig:ja-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_results_Mexico_512_7_AO_300b11.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:ja-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L16_envi_mexico_512_renyi_lambda09_B200.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:ja-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L18_envi_mexico_tsallis_lambda085_B200_w7__H1.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:ja-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/0.05_results_Mexico_512_7_AO_300b.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:ja-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/0.05_L16_envi_mexico_512_renyi_lambda09_B200.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:ja-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L18_envi_mexico_tsallis_lambda085_B200_w7_.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:ja-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over the Coast of Jalisco, Mexico: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:ja}
-\end{figure}
-```
-
-```{=latex}
-\begin{figure}[H]
-    \centering
-
-    % Primera fila: 2 imágenes
-    \begin{subfigure}{0.3\textwidth}
-        \includegraphics[width=\linewidth]{Figures/foggia-italy_1900.png}
-        \caption{SAR image}
-        \label{fig:fo-sar}
-    \end{subfigure}
-    \hspace{2em}
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/foggia-italy-optical.png}
-        \caption{Optical image}
-        \label{fig:fo-optical}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_shannon-Foggia-H_77.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:fo-shann1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_renyi-foggiaH-new.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:du-renyi1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.31\textwidth}
-        \includegraphics[width=\linewidth]{Figures/p-values_L24_Foggia1900_tsallis_lambda085_B100aa.png}
-        \caption{$p$-value map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:fo-tsallis1}
-    \end{subfigure}
-
-    \vspace{1.2em}
-
-    % Tercera fila: 3 imágenes (binary maps)
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_AO_italy_1900.png}
-        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
-        \label{fig:fo-005-shann2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_renyi_italy_1900_L1.png}
-        \caption{Binary map for $\small{S_{\widetilde{R}_{\lambda}}}$}
-        \label{fig:du-005-renyi2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.29\textwidth}
-        \includegraphics[width=\linewidth]{Figures/H_005_L24_envi_Foggia_size_1900_tsallis_lambda085_B100.png} %
-        \caption{Binary map for $\small{S_{\widetilde{T}_{\lambda}}}$}
-        \label{fig:fo-005-tsallis2}
-    \end{subfigure}
-
-    \caption{Detection of heterogeneous areas in a SAR image over  Foggia, Italy: comparison of test statistics $\small{S_{\widetilde{H}_{\text{AO}}}}$, $\small{S_{\widetilde{R}_{\lambda}}}$, and $\small{S_{\widetilde{T}_{\lambda}}}$.
-Top: input images.
-Middle: $p$-value maps.
-Bottom: binary maps (\SI{5}{\percent} level).}
-    \label{fig:du}
-\end{figure}
-```
-
-Overall, the experiments on real SAR images confirm the simulated
-findings: for highly speckled data ($L\!\approx\!1$) the Rényi
-statistic is the most reliable detector of heterogeneity, whereas for
-multi-look products the Tsallis statistic delivers cleaner segmentations
-with fewer false positives.
-
-Window size also plays an important role in the detection process. Although not shown in this work, we explored alternative sliding windows
-of $5\times5$ ($n=25$) and $9\times9$ ($n=81$) on both simulated and real SAR data. 
-The smaller window tended to miss heterogeneous features, especially in 
-single–look images where few pixels are available. 
-In contrast, larger windows occasionally led to over-detection, particularly 
-on multi-look scenes, where homogeneous regions were sometimes misclassified 
-as heterogeneous. Based on these observations and prior recommendations in the literature, 
-we adopted $7\times7$ ($n=49$) as a compromise that preserves local detail 
-while ensuring statistical stability for bootstrap estimation.
-
-In the specific case of $L=1$, we observed that larger windows 
-(e.g., $9\times9$) produced more consistent detection, particularly for 
-the Tsallis-based test, improving sensitivity without excessive false alarms.
-
-### Quantitative Evaluation
-
-Eight polygonal regions of interest (ROIs) were manually selected for each of the three SAR scenes chosen for quantitative evaluation, London, Munich, and Dublin (Figures \ref{fig:london-sar-roi1}–\ref{fig:dublin-sar-roi1}).
-These ROIs correspond to heterogeneous areas (red, class 1) and homogeneous areas (blue, class 0).
-The polygons were rasterized to match the spatial resolution of each SAR image, forming a partial ground truth.
-
-```{=latex}
-\begin{figure}[H]
-    \centering
+     \caption{Selected ROIs for the quantitative evaluation. Red polygons indicate heterogeneous areas (class 1), and blue polygons indicate homogeneous areas (class 0).}
+    \label{fig:roi-scenes}
     % London
     \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/london_roi.png}
+        \includegraphics[width=\linewidth]{Figures/london_roi3.jpg}
         \caption{London SAR image with selected ROIs.}
@@
     \end{subfigure}
-   \hspace{4em} 
+   \hspace{1em} 
     % Munich
     \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/munich_roi.png}
+        \includegraphics[width=\linewidth]{Figures/munich_roi3.jpg}
         \caption{Munich SAR image with selected ROIs.}
@@
     \end{subfigure}
-    \vspace{0.5em}
+    \hspace{1em}
     % Dublin
     \begin{subfigure}{0.30\textwidth}
-        \includegraphics[width=\linewidth]{Figures/dublin_roi3.png}
+        \includegraphics[width=\linewidth]{Figures/Dublin_roi3.jpg}
         \caption{Dublin SAR image with selected ROIs.}
@@
     \end{subfigure}
-    \caption{Selected ROIs for the quantitative evaluation. Red polygons indicate heterogeneous areas (class 1), and blue polygons indicate homogeneous areas (class 0).}
-    \label{fig:roi-scenes}
+   %\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
@@
 ```
-We thresholded the $p$-value maps at 0.05, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared these decision maps with the ground truth to compute the F1-score ($F_1$), Kappa coefficient ($\kappa$), and overall accuracy (OA).
-Table \ref{tab:table_metrics1} summarizes the results.
-
-\renewcommand{\arraystretch}{1.1} 
-```{r metrics_table_k, echo=FALSE, message=FALSE, warning=FALSE}
-
-# 
+
+\renewcommand{\arraystretch}{1.3}
+```{r metrics_table_k, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+suppressPackageStartupMessages({
+library(dplyr)
+library(knitr)
+library(kableExtra)
+})
+
 load("./Data/metrics_london_shannon.RData")
@@
 load("./Data/metrics_london_tsallis.RData")
+load("./Data/metrics_tsallis_london_eta3_f.RData")
 
@@
 load("./Data/metrics_munich_tsallis.RData")
+load("./Data/metrics_tsallis_munich_eta3_f.RData")
 
@@
 load("./Data/metrics_dublin_tsallis.RData")
-
-# 
-all_metrics <- rbind(
+load("./Data/metrics_tsallis_dublin_eta3_f.RData")
+
+all_metrics <- dplyr::bind_rows(
 metrics_london_shannon,
@@
 metrics_london_tsallis,
+metrics_tsallis_london_eta3_f,
 
@@
 metrics_munich_tsallis,
+metrics_tsallis_munich_eta3_f,
 
@@
 metrics_dublin_renyi,
-  metrics_dublin_tsallis
-)
-
-numeric_metrics <- all_metrics
+metrics_dublin_tsallis,
+metrics_tsallis_dublin_eta3_f
+) %>%
+dplyr::select(Scene, Method, F1, Kappa, OA)
+
+all_metrics$Scene <- factor(all_metrics$Scene, levels = c("London","Munich","Dublin"))
 
@@
 "Renyi"        = "$S_{\\widetilde{R}_{\\lambda}}$",
-  "Tsallis" = "$S_{\\widetilde{T}_{\\lambda}}$"
+"Tsallis"      = "$S_{\\widetilde{T}_{\\lambda}}$",
+"Tsallis_eta3" = "\\quad $S_{\\widetilde{T}_{\\lambda}}$ adapt.",
+.default       = as.character(all_metrics$Method)
 )
 
-#
-for (i in seq(1, nrow(all_metrics), by = 3)) {
-  for (col in c("F1", "Kappa", "OA")) {
-    vals <- numeric_metrics[[col]][i:(i+2)]
-    best <- which.max(vals)
-    for (j in 1:3) {
-      val_fmt <- sprintf("$%.3f$", vals[j])
-      if (j == best) val_fmt <- sprintf("\\bm{%s}", val_fmt)
-      all_metrics[i + j - 1, col] <- val_fmt
-    }
-  }
-}
-
-# Cambiar nombres de columnas
+fmt <- function(x) sprintf("$%.3f$", as.numeric(x))
+all_metrics <- all_metrics %>%
+group_by(Scene) %>%
+mutate(
+F1_max    = max(as.numeric(F1),    na.rm = TRUE),
+Kappa_max = max(as.numeric(Kappa), na.rm = TRUE),
+OA_max    = max(as.numeric(OA),    na.rm = TRUE),
+F1    = ifelse(as.numeric(F1)    == F1_max,    paste0("\\bm{", fmt(F1), "}"),    fmt(F1)),
+Kappa = ifelse(as.numeric(Kappa) == Kappa_max, paste0("\\bm{", fmt(Kappa), "}"), fmt(Kappa)),
+OA    = ifelse(as.numeric(OA)    == OA_max,    paste0("\\bm{", fmt(OA), "}"),    fmt(OA))
+) %>%
+ungroup() %>%
+dplyr::select(Scene, Method, F1, Kappa, OA)
+
 colnames(all_metrics) <- c("\\textbf{Scene}", "\\textbf{Test}", "$\\bm{F_1}$", "$\\kappa$", "\\textbf{OA}")
 
-# Aplicar multirow a la columna de ciudad (cada 3 filas)
-scene_labels <- all_metrics$Scene
-for (scene in unique(scene_labels)) {
-  idx <- which(scene_labels == scene)
-  scene_labels[idx[1]] <- paste0("\\multirow{3}{*}{", scene, "}")
-  scene_labels[idx[2:3]] <- ""
-}
-all_metrics$Scene <- scene_labels
-
-# Mostrar tabla con formato LaTeX
 kable(all_metrics,
@@
 booktabs = TRUE,
-      align = "cccccc",
+align = "ccccc",      
 escape = FALSE,
 label = "table_metrics1",
-      centering = FALSE,
-      table.envir = "table", 
-      position = "H",
 row.names = FALSE) %>%
 row_spec(0, align = "c") %>%
-  collapse_rows(latex_hline = "major", valign = "bottom") %>%
-  kable_styling(latex_options = "scale_down", font_size = 10) %>%
-  kable_styling(full_width = TRUE)
-
-``` 
+collapse_rows(columns = 1, latex_hline = "major", valign = "bottom") %>%
+kable_styling(latex_options = c("hold_position","scale_down"), font_size = 11, full_width = T) %>%
+print()
+
+```
+
 When comparing the three entropy-based tests, distinct patterns emerge depending on the scene characteristics.
-In London, the Rényi-based test produced the best performance across all metrics ($F_1$: 0.695; $\kappa$: 0.626; OA: 0.877), outperforming both Shannon and Tsallis.
-This suggests that Rényi entropy is particularly robust under strong speckle conditions, as is typical in single-look SAR imagery.
-
-In contrast, in the Munich and Dublin scenes, where the image quality is higher and speckle is reduced, the Tsallis-based test achieved the highest scores across all three metrics.
-Specifically, in Munich, Tsallis achieved $F_1 = 0.930$, $\kappa = 0.871$, and OA = 0.936, marginally outperforming Rényi.
-Similarly, in Dublin, Tsallis led with $F_1 = 0.879$, $\kappa = 0.776$, and OA = 0.887.
-These results indicate that Tsallis entropy may be more sensitive to finer textural differences in lower-speckle environments.
-
-The Shannon-based test consistently yielded the lowest scores across all scenes, suggesting that it is less effective at distinguishing between heterogeneous and homogeneous regions under the tested conditions.
-Overall, the results demonstrate that Rényi and Tsallis entropies are both strong detectors of heterogeneity, with Rényi showing advantages in noisy contexts, and Tsallis offering improved discrimination in scenes with more subtle textural variations.
-
-Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds (Figure \ref{fig:roc}).
+
+In London, the adaptive Tsallis test achieves the highest scores across metrics ($F_1 = 0.757$, $\kappa = 0.697$, OA = 0.897), followed by the Rényi-based statistic ($F_1 = 0.695$, $\kappa = 0.626$, OA = 0.877).
+Both outperform Shannon ($F_1 = 0.617$, $\kappa = 0.542$, OA = 0.854) and fixed-window Tsallis ($F_1 = 0.603$, $\kappa = 0.528$, OA = 0.850).
+These results suggest that adaptive windowing is helpful under stronger speckle by smoothing homogeneous areas while preserving edges.
+
+In Munich, all methods perform well, but the adaptive Tsallis variant is slightly superior ($F_1 = 0.935$, $\kappa = 0.880$, OA = 0.940), with fixed Tsallis close behind ($F_1 = 0.930$, $\kappa = 0.871$, OA = 0.936) and Rényi competitive ($F_1 = 0.924$, $\kappa = 0.861$, OA = 0.931).
+Shannon shows lower but still strong values ($F_1 = 0.883$, $\kappa = 0.794$, OA = 0.897).
+
+In Dublin, the adaptive approach yields the largest gains: adaptive Tsallis leads with $F_1 = 0.901$, $\kappa = 0.844$, and OA = 0.926, followed by fixed Tsallis ($F_1 = 0.879$, $\kappa = 0.776$, OA = 0.887) and Rényi ($F_1 = 0.865$, $\kappa = 0.753$, OA = 0.875).
+Shannon again records the lowest figures ($F_1 = 0.645$, $\kappa = 0.464$, OA = 0.858).
+
+Overall, the adaptive Tsallis test provides the most accurate classification across the three scenes, with consistent improvements in $F_1$, $\kappa$, and OA.
+Rényi remains a strong fixed-window alternative, while Shannon is the least effective under the tested conditions.
+These findings align with the qualitative inspection: adaptive windowing improves the balance between detail preservation in heterogeneous regions and stability in homogeneous areas.
+
+<!-- Using the same ROIs as ground truth, we evaluated the continuous $p$-value maps by computing receiver operating characteristic (ROC) curves over all decision thresholds (Figure \ref{fig:roc}).
 Each curve plots the probability of detection (Pd) versus the probability of false alarm (PFA).
 Pd reflects the proportion of heterogeneous pixels correctly detected, while PFA represents the proportion of homogeneous pixels misclassified as heterogeneous.
-
-```{=latex}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.98\textwidth]{Figures/fig-ROC6-1.pdf}
-  \caption{ROC curves comparing the tests $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$ and $S_{\widetilde{T}_{\lambda}}$.}
-  \label{fig:roc}
-\end{figure}
-```
-The area under each ROC curve (AUC) quantifies overall detection performance, with higher values indicating better discrimination between classes.
+-->
+
+<!-- ```{=latex} -->
+<!-- \begin{figure}[H] -->
+<!--   \centering -->
+<!--   \caption{ROC curves comparing the tests $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$ and $S_{\widetilde{T}_{\lambda}}$.} -->
+<!--   \label{fig:roc} -->
+<!--   \includegraphics[width=0.98\textwidth]{Figures/fig-ROC6-1.pdf} -->
+<!--   %\caption*{\footnotesize\textbf{Source:} The author (2025)} -->
+<!-- \end{figure} -->
+<!-- ``` -->
+<!-- The area under each ROC curve (AUC) quantifies overall detection performance, with higher values indicating better discrimination between classes.
 Across all scenes, the Rényi-based test yielded the highest AUC in London ($0.963$), followed by Tsallis ($0.824$) and Shannon ($0.776$), reaffirming Rényi’s robustness under strong speckle conditions.
-
-In Munich, both Rényi and Tsallis performed similarly with near-perfect AUCs ($0.996$ and $0.998$ respectively), while Shannon slightly lagged behind ($0.989$).
+-->
+
+<!-- In Munich, both Rényi and Tsallis performed similarly with near-perfect AUCs ($0.996$ and $0.998$ respectively), while Shannon slightly lagged behind ($0.989$).
 In Dublin, a similar pattern is observed: Tsallis again leads marginally with an AUC of $0.994$, followed by Rényi ($0.990$) and Shannon ($0.986$).
-
-These results confirm that Rényi and Tsallis entropies consistently outperform Shannon, with Tsallis showing slightly superior performance in higher-quality scenes.
+-->
+
+<!-- These results confirm that Rényi and Tsallis entropies consistently outperform Shannon, with Tsallis showing slightly superior performance in higher-quality scenes.
 The ROC analysis aligns with the classification metrics, supporting the conclusion that Tsallis and Rényi are more effective in detecting heterogeneity across varying image conditions.
+-->
 
@@
 By clicking **Run Detection**, the app performs the sliding‐window test and displays the resulting $p$-value heat‐map in color.
+```{=latex}
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.96\textwidth]{Figures/shiny2.png}
     \caption{Shiny application interface. The left panel shows the data‐loading and parameter controls; the right panel displays the colorized $p$-value map and elapsed runtime.}
   \label{fig:shiny-app}
+  \includegraphics[width=0.96\textwidth]{Figures/shiny1.jpg}
+%\caption*{\footnotesize\textbf{Source:} The author (2025)}
 \end{figure}
-
+```
 This interactive tool complements the results presented in Sections \ref{sec-sim2} and \ref{sec-sim3} by enabling real‐time parameter tuning and direct comparison across estimators.

### 2025-10-27 Text/Thesis/Frontmatter/abstract.tex
final version thesis

--- 2025-07-01 Text/Thesis/Frontmatter/abstract.tex
@@
 in synthetic aperture radar (SAR) intensity data using entropy-based methods.
-In homogeneous regions, where fully developed speckle is present, SAR returns 
-are well modeled by the Gamma distribution. 
-In contrast, heterogeneous areas exhibit more complex scattering behaviors, 
-typically modeled by the $\mathcal{G}_I^0$ distribution. Distinguishing between 
-these regimes is fundamental for accurate interpretation in remote sensing applications, 
-yet classical parametric tests often fail to address this task effectively due to analytical 
-and numerical limitations.
-To overcome these challenges, we propose three test statistics for detecting heterogeneity 
-in SAR imagery based on Shannon, Rényi, and Tsallis entropy measures. These tests rely on 
-nonparametric entropy estimators constructed from sample spacings, avoiding explicit assumptions 
-about the underlying distribution. To enhance their accuracy, particularly in small samples, 
-we incorporate a bootstrap bias-correction procedure that improves the estimators’ stability, 
-reduces bias, and lowers mean squared error.
-The proposed tests are evaluated using Monte Carlo simulations, assessing size and power 
-under varying sample sizes and numbers of looks.
-Results demonstrate that the Rényi and Tsallis-based tests outperform the Shannon-based version by 
-detecting more subtle texture variations while maintaining greater reliability in identifying 
-truly homogeneous regions.
-Finally, the methodology is applied to both simulated and real SAR data. We generate $p$-value maps using a 
-sliding window analysis, allowing for visual and quantitative assessment of spatial heterogeneity. 
-The Rényi-based test consistently identifies fine-scale roughness patterns, 
-while the Tsallis-based test shows strength in reliably detecting homogeneous areas. 
-Together, these entropy-based tools provide a robust, interpretable, and unsupervised 
-framework for heterogeneity detection in SAR data.
+In SAR data analysis, an accurate interpretation of the terrain fundamentally 
+depends on the distinction between two main regimes: homogeneous regions, in which 
+speckle is fully developed and SAR returns are represented by the Gamma distribution, 
+and heterogeneous areas, which require more flexible distributions to describe complex scattering, 
+generally represented by the $\mathcal{G}_I^0$ distribution.
+Although this discrimination is essential for remote sensing applications, 
+classical parametric tests are generally not suitable for this task due to analytical and numerical limitations.
+To overcome these challenges, we propose three test statistics to detect heterogeneity in SAR images based on 
+Shannon, Rényi, and Tsallis entropies. 
+The associated tests employ nonparametric entropy estimators constructed from sample spacings, avoiding explicit 
+assumptions about the underlying distribution. To increase the accuracy of the tests, especially for small samples, 
+we incorporate a bootstrap-based bias correction procedure that improves the stability of the estimators, reduces bias, 
+and decreases the mean squared error.
+The proposed tests are evaluated through Monte Carlo simulations, using test size and power under different speckle 
+and texture conditions as performance criteria.
+The results show that the tests based on Rényi and Tsallis entropies outperform the version based on Shannon entropy, 
+detecting subtler texture variations and maintaining higher reliability in identifying truly homogeneous regions.
+Finally, the methodology is applied to both simulated and real SAR data.
+The analysis is performed using sliding windows, generating maps of $p$-values that allow for visual 
+and quantitative assessment of spatial heterogeneity. 
+The Rényi-based test consistently identifies fine-scale roughness patterns, while the Tsallis-based test performs better in detecting homogeneous regions. 
+Together, these entropy-based tools provide a robust, interpretable, and unsupervised framework for detecting heterogeneity in SAR data.
 
@@
 \par
-\noindent \textbf{Keywords:} SAR; Heterogeneity; Entropy; Nonparametric Estimation; Bootstrap; Statistical Test
+\noindent \textbf{Keywords:}  entropy;  heterogeneity; gamma distribution; hypothesis testing; bootstrap.
 

### 2025-10-27 Text/Thesis/Frontmatter/acknowledgements.tex
final version thesis

@@
-Firstly, I would like to thank my supervisors, Prof. Alejandro Frery and Prof. Abraão do Nascimento, for their guidance, dedication, and support throughout these years. 
+Firstly, I would like to thank my supervisors, Prof.
+Alejandro Frery and Prof.
+Abraão do Nascimento, for their guidance and support throughout these years.
 Working with you has been an incredibly valuable learning experience.
@@
 
-I am also grateful to the Universidade Federal de Pernambuco and the 
-Graduate Program in Statistics for their support during my academic journey. 
-Special thanks to Prof. Pablo Rodriguez for all his help with administrative matters and for his patience.
+I am also thankful to the Universidade Federal de Pernambuco and the Programa de
+Pós-Graduação em Estatística for their support during my academic journey. Special thanks to Prof. Pablo Rodriguez for all his help with administrative matters and for his patience.
 
-I gratefully acknowledge the financial support provided by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior – Brasil (CAPES) – Finance Code 001, 
-the Programa de Doutorado-Sanduíche no Exterior (PDSE), and the Fundação de Amparo à Ciência e Tecnologia do Estado de Pernambuco (FACEPE).
+I acknowledge the financial support from the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior – Brasil (CAPES) – Finance Code 001, the Programa de Doutorado-Sanduíche no Exterior (PDSE), and the Fundação de Amparo à Ciência e Tecnologia do Estado de Pernambuco (FACEPE), which made this work possible.
 
-I also thank the examination committee for their availability.
+I would like to express my gratitude to the members of my examination committee, Prof.
+Saeid Homayouni, Prof.
+Paolo Gamba, Prof.
+Anderson de Borba, and Prof.
+Fátima Sombra, for agreeing to be part of the defense of my thesis and for their valuable comments and suggestions.
 
-To my family, thank you for always supporting and encouraging me along the way.
+This journey would not have been the same without all the amazing people I met in Brazil and New Zealand.
+To everyone, thank you for your friendship and support, which made this experience unforgettable.
 
-Finally, thanks to all the friends I met during this time. Your support and friendship 
-made this experience better.
+Finally, I am especially grateful to my family, who have always supported and encouraged me along the way.

### 2025-10-27 Text/Thesis/Frontmatter/resumo.tex
final version thesis

--- 2025-07-01 Text/Thesis/Frontmatter/resumo.tex
@@
-Este trabalho apresenta uma abordagem estatística para a detecção de heterogeneidade 
-em dados de intensidade de radar de abertura sintética (SAR) utilizando medidas 
-baseadas em entropia. Em regiões homogêneas, onde há speckle totalmente desenvolvido, 
-os retornos SAR são bem modelados pela distribuição Gama. Em contraste, áreas heterogêneas 
-apresentam comportamentos de espalhamento mais complexos, normalmente descritos pela 
-distribuição $\mathcal{G}_I^0$. Distinguir entre esses dois regimes é fundamental 
-para uma interpretação precisa em aplicações de sensoriamento remoto. No entanto, 
+Este trabalho apresenta uma abordagem estatística para detectar heterogeneidade em dados de
+intensidade de radar de abertura sintética (SAR), utilizando métodos baseados em entropia.
+Na análise de dados SAR, uma interpretação precisa do terreno depende fundamentalmente da
+distinção entre dois regimes principais: regiões homogêneas, em que o speckle está
+totalmente desenvolvido, os retornos SAR são representados pela distribuição Gamma, e áreas heterogêneas requerem distribuições mais flexíveis para descrever
+o espalhamento complexo, geralmente representado pela distribuição
+$\mathcal{G}_I^0$.
+Embora essa discriminação seja essencial para aplicações de sensoriamento remoto, 
 testes paramétricos clássicos geralmente não são adequados para essa tarefa devido a 
@@
 Para superar esses desafios, propomos três estatísticas de teste para detectar heterogeneidade
-em imagens SAR com base nas entropias de Shannon, Rényi e Tsallis. Esses testes utilizam 
+em imagens SAR, com base nas entropias de Shannon, Rényi e Tsallis. Os testes associados utilizam
 estimadores não paramétricos de entropia construídos a partir de espaçamentos amostrais,
@@
 que melhora a estabilidade dos estimadores, reduz o viés e o erro quadrático médio.
-As estatísticas propostas são avaliadas por meio de simulações de Monte Carlo, 
-onde analisamos seu tamanho e poder sob diferentes condições de speckle e textura. 
-Os resultados mostram que os testes baseados em Rényi e Tsallis superam a versão baseada 
-em Shannon, detectando variações de textura mais sutis e mantendo maior confiabilidade na 
+Os testes propostos são avaliados por meio de simulações de Monte Carlo,
+tendo como critério de avaliação seu tamanho e poder sob diferentes condições de speckle e textura.
+Os resultados mostram que os testes baseados nas entropias de Rényi e Tsallis superam a versão baseada
+na entropia de Shannon, detectando variações de textura mais sutis e mantendo maior confiabilidade na
 identificação de regiões verdadeiramente homogêneas.
-Por fim, a metodologia é aplicada a dados SAR simulados e reais. 
-A análise é realizada com janelas deslizantes, gerando mapas de valores de $p$ que permitem a a
-valiação visual e quantitativa da heterogeneidade espacial. O teste baseado na entropia de 
+Por fim, a metodologia é aplicada tanto a dados simulados como a dados SAR reais.
+A análise é realizada com janelas deslizantes, gerando mapas de valores-$p$ que permitem a
+avaliação visual e quantitativa da heterogeneidade espacial. O teste baseado na entropia de
 Rényi mostra desempenho superior na identificação de padrões de rugosidade em pequena escala,
-enquanto o teste baseado em Tsallis é eficaz na detecção de regiões homogêneas. Em conjunto, 
+enquanto o teste baseado em Tsallis é melhor na detecção de regiões homogêneas. Em conjunto,
 essas ferramentas baseadas em entropia oferecem uma estrutura robusta, interpretável e não
@@
 \par
-\noindent \textbf{Palavras-chave:} SAR; Heterogeneidade; Entropia; Estimativa não paramétrica; Bootstrap; Teste estatístico
+\noindent \textbf{Palavras-chave:} entropia;  heterogeneidade; distribuição gama; teste de hipótese; bootstrap.

### 2025-10-27 Text/Thesis/Frontmatter/symbols.tex
final version thesis

@@
-\begin{symbols}{lll} % Include a list of Symbols (a three column table)
+% --- SOLO afecta a esta tabla ---
+{%
+\setlength{\extrarowheight}{0.5pt}   % extra vertical por fila
+\renewcommand{\arraystretch}{1.18} % factor global para altura de filas (1.0 = normal)
 
+\begin{symbols}{@{}lll@{}} % @{} opcional: elimina márgenes laterales de la tabla
 $\mathbb{R}_+$ & Positive real numbers \\
@@
 $c_i$ & Boundary correction factor in spacing estimators \\
-\addlinespace % Gap to separate the Roman symbols from the Greek
+\addlinespace[4pt] % (opcional) espacio extra para separar bloques
+\end{symbols}
+}% --- fin del ámbito local ---
 
-\end{symbols}
+% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
+% 
+% $\mathbb{R}_+$ & Positive real numbers \\ 
+%  $\Gamma(\cdot)$  & Gamma function \\
+% $\Gamma_{\mathrm{SAR}}(L, \mu)$ & Gamma SAR distribution with parameters $L$ and $\mu$ \\
+% $\mathcal{G}^0_I$ & $\mathcal{G}^0_I$ distribution for intensity \\
+% $\psi^{(0)}(\cdot)$ & Digamma function \\
+% $H(Z)$ & Shannon entropy of random variable $Z$ \\
+% $R_{\lambda}(Z)$ & Rényi entropy of order $\lambda$ \\
+% $T_{\lambda}(Z)$ & Tsallis entropy of order $\lambda$ \\
+% $\widehat{H}_{\text{AO}}(\bm{Z})$ & Nonparametric Shannon entropy estimator (Al-Omari) \\
+% $\widehat{R}_{\lambda}(\bm{Z})$ & Nonparametric Rényi entropy estimator via sample spacings \\
+% $\widehat{T}_{\lambda}(\bm{Z})$ & Nonparametric Tsallis entropy estimator via sample spacings \\
+% $\widetilde{H}_{\text{AO}}(\bm{Z})$ & Bootstrap-corrected Shannon entropy estimator \\
+% $\widetilde{R}_{\lambda}(\bm{Z})$ & Bootstrap-corrected Rényi entropy estimator \\
+% $\widetilde{T}_{\lambda}(\bm{Z})$ & Bootstrap-corrected Tsallis entropy estimator \\
+% $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ & Test statistic based on Shannon entropy \\
+% $S_{\widetilde{R}_{\lambda}}(\bm{Z}; L)$ & Test statistic based on Rényi entropy \\
+% $S_{\widetilde{T}_{\lambda}}(\bm{Z}; L)$ & Test statistic based on Tsallis entropy \\
+% $\widehat{\mu}$ & Sample mean of $\bm{Z}$ \\
+% $Z_{(i)}$ & $i$-th order statistic in sample $\bm{Z}$ \\
+% $m$ & Spacing parameter (window size) used in entropy estimation \\
+% $c_i$ & Boundary correction factor in spacing estimators \\
+% \addlinespace % Gap to separate the Roman symbols from the Greek
+% 
+% 
+% \end{symbols}

### 2025-10-27 Text/Thesis/Chapters/setup.R

@@ -56,7 +56,7 @@ install_and_load(required_packages)
 # source("./Code/shannon_entropy_gamma_sar.R")
 # 
 # source("./Code/functions_sample_bias_mse.R")
- source("./Code/functions_sample_bias_mse_1.R")
+# source("./Code/functions_sample_bias_mse_1.R")
 # 
 # theme_set(theme_minimal() +
 #             theme(text = element_text(family = "serif"),

### 2025-10-28 Text/Thesis/Chapters/Chapter2.qmd
Corrected figures

@@
 
-Figures&nbsp;[-@fig-shannon-convergence-s]--[-@fig-tsallis-convergence-t] illustrate the Shannon ($H$), Rényi ($R_\lambda$), and Tsallis ($T_\lambda$) entropies for the $\mathcal{G}^0_I$ model under different texture levels ($\alpha$) and numbers of looks ($L$).
+Figures&nbsp;\ref{fig-shannon-convergence-s}--\ref{fig-tsallis-convergence-t} illustrate the Shannon ($H$), Rényi ($R_\lambda$), and Tsallis ($T_\lambda$) entropies for the $\mathcal{G}^0_I$ model under different texture levels ($\alpha$) and numbers of looks ($L$).
 In every case the coloured dashed curves converge to the solid black baseline of the homogeneous $\Gamma_{\mathrm{SAR}}$ distribution as $\alpha\to-\infty$, confirming the limiting behavior.
 
-For the Shannon entropy (@fig-shannon-convergence-s), when $L = 5$ the entropy curves for different $\alpha$ values are more concentrated.
+For the Shannon entropy (Figure&nbsp;\ref{fig-shannon-convergence-s}), when $L = 5$ the entropy curves for different $\alpha$ values are more concentrated.
 This is due to the higher speckle noise present in a low number of looks, which dominates the uncertainty and masks texture effects.
@@
 
-In the case of Rényi entropy (@fig-renyi-convergence-r), for $\lambda = 0.6$ and $\lambda = 0.9$, the general shape and separation of the curves are similar.
+In the case of Rényi entropy (Figure&nbsp;\ref{fig-renyi-convergence-r}), for $\lambda = 0.6$ and $\lambda = 0.9$, the general shape and separation of the curves are similar.
 However, increasing $L$ leads to a slight decrease in entropy values across all $\alpha$, consistent with reduced speckle.
@@
 
-For Tsallis entropy (@fig-tsallis-convergence-t), the separation between curves is most noticeable for $\lambda = 0.6$ and $L = 5$, where texture has more influence.
+For Tsallis entropy (Figure&nbsp;\ref{fig-tsallis-convergence-t}), the separation between curves is most noticeable for $\lambda = 0.6$ and $L = 5$, where texture has more influence.
 When $\lambda$ increases to $0.9$ or when $L$ is increased, the curves become more compact and approach the Gamma entropy faster, indicating lower sensitivity to texture variation and confirming that $\lambda$ controls the influence of the tail behavior.
 
-```{r fig-shannon-convergence-s, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
+```{r fig-shannon-convergence-s,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Shannon entropy $H(\\mathcal{G}^0_I)$ converges to $H(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 
@@
 
-```{r fig-renyi-convergence-r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
+```{r fig-renyi-convergence-r,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="hbt", out.width="98%", fig.cap="Rényi entropy $R_{\\lambda}(\\mathcal{G}^0_I)$ converges to $R_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 # fig.fullwidth = TRUE, out.width="95%"
@@
 
-```{r fig-tsallis-convergence-t, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="98%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
+```{r fig-tsallis-convergence-t,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", out.width="98%", fig.cap="Tsallis entropy $T_{\\lambda}(\\mathcal{G}^0_I)$ converges to $T_{\\lambda}(\\Gamma_{\\mathrm{SAR}})$ as $\\alpha$ decreases.", fig.width=8, fig.height=3.9}
 # fig.fullwidth = TRUE, out.width="95%"
@@
 (p1 | p2) + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+```
+
+```{=latex}
+\begin{figure}[hbt]
+
+\caption{\label{fig-shannon-convergence-s}Shannon entropy
+\(H(\mathcal{G}^0_I)\) converges to \(H(\Gamma_{\mathrm{SAR}})\) as
+\(\alpha\) decreases.}
+
+\centering{
+
+\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-shannon-convergence-s-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[hbt]
+
+\caption{\label{fig-renyi-convergence-r}Rényi entropy
+\(R_{\lambda}(\mathcal{G}^0_I)\) converges to
+\(R_{\lambda}(\Gamma_{\mathrm{SAR}})\) as \(\alpha\) decreases.}
+
+\centering{
+
+\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-renyi-convergence-r-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[H]
+
+\caption{\label{fig-tsallis-convergence-t}Tsallis entropy
+\(T_{\lambda}(\mathcal{G}^0_I)\) converges to
+\(T_{\lambda}(\Gamma_{\mathrm{SAR}})\) as \(\alpha\) decreases.}
+
+\centering{
+
+\includegraphics[width=0.98\linewidth,height=\textheight,keepaspectratio]{Figures/fig-tsallis-convergence-t-1.pdf}
+
+}
+
+\end{figure}%
 ```

### 2025-10-28 Text/Thesis/Chapters/Chapter3.qmd
Corrected figures

@@
 
-For the Rényi estimator (see Fig.
-\ref{fig-optimal_order}), $\lambda = 0.9$ minimizes the MSE while keeping the bias low, achieving a favorable bias-variance trade-off.
+For the Rényi estimator (see Figure&nbsp;\ref{fig-optimal_order}), $\lambda = 0.9$ minimizes the MSE while keeping the bias low, achieving a favorable bias-variance trade-off.
 Although $\lambda = 0.85$ yields slightly lower bias, it produces a higher MSE, supporting the choice of $\lambda = 0.9$ as optimal.
 
-Similarly, for the Tsallis estimator (Fig. \ref{fig-optimal_order-tsallis}), $\lambda = 0.85$ results in the lowest MSE with moderate bias, making it the most suitable choice.
+Similarly, for the Tsallis estimator (Figure&nbsp;\ref{fig-optimal_order-tsallis}), $\lambda = 0.85$ results in the lowest MSE with moderate bias, making it the most suitable choice.
 
@@
 
-```{r fig-optimal_order,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
+```{r fig-optimal_order, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Rényi entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
 #fig.show="hide", 
@@
 
-```{r fig-optimal_order-tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
+```{r fig-optimal_order-tsallis,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="70%",  fig.pos="htb", fig.cap="Bias and MSE as a function of $\\lambda$, for the Tsallis entropy estimator, with $n = 49$, $L = 5$.", fig.width=5, fig.height=3.0}
 #fig.show="hide", 
@@
 ```
+
+```{=latex}
+\begin{figure}[htb]
+
+\caption{\label{fig-optimal_order}Bias and MSE as a function of
+\(\lambda\), for the Rényi entropy estimator, with \(n = 49\),
+\(L = 5\).}
+
+\centering{
+
+\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{Figures/fig-optimal_order-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[htb]
+
+\caption{\label{fig-optimal_order-tsallis}Bias and MSE as a function of
+\(\lambda\), for the Tsallis entropy estimator, with \(n = 49\),
+\(L = 5\).}
+
+\centering{
+
+\includegraphics[width=0.7\linewidth,height=\textheight,keepaspectratio]{Figures/fig-optimal_order-tsallis-1.pdf}
+
+}
+
+\end{figure}%
+```
+
 <!-- ```{=latex} -->
@@
 \vspace{-10pt}
-```{r Simulated_data_bias_m1, echo=FALSE, message=FALSE }
+```{r Simulated_data_bias_m1,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE }
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-bias_mse_rm1,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.5}
+```{r fig-bias_mse_rm1,   eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="H",  fig.cap="Bias and MSE of the Rényi entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.5}
 
@@
 
-```{r Simulated_data_bias_tt, echo=FALSE, message=FALSE }
+```{r Simulated_data_bias_tt,  eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE }
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-bias_mse_Tsallis,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="htb",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.6}
+```{r fig-bias_mse_Tsallis,  eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="65%",  fig.pos="htb",  fig.cap="Bias and MSE of the Tsallis entropy estimators for $\\Gamma_{\\text{SAR}}$, with $L=5$", fig.width=5.5, fig.height=3.6}
 
@@
 
+```
+
+```{=latex}
+\begin{figure}[H]
+
+\caption{\label{fig-bias_mse_rm1}Bias and MSE of the Rényi entropy
+estimators for \(\Gamma_{\text{SAR}}\), with \(L=5\)}
+
+\centering{
+
+\includegraphics[width=0.65\linewidth,height=\textheight,keepaspectratio]{Figures/fig-bias_mse_rm1-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[htb]
+
+\caption{\label{fig-bias_mse_Tsallis}Bias and MSE of the Tsallis entropy
+estimators for \(\Gamma_{\text{SAR}}\), with \(L=5\)}
+
+\centering{
+
+\includegraphics[width=0.65\linewidth,height=\textheight,keepaspectratio]{Figures/fig-bias_mse_Tsallis-1.pdf}
+
+}
+
+\end{figure}%
 ```
@@
 
-Figures [-@fig-densities-shannon]-[-@fig-densities-tsallis4] display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.
+Figures&nbsp;\ref{fig-densities-shannon}-\ref{fig-densities-tsallis4} display the empirical distributions of the three entropy-based statistics:Shannon $S_{\widetilde{H}}(\mathbf Z;L)$, Rényi $S_{\widetilde{R}_{\lambda}}(\mathbf Z;L)$ (with $\lambda=0.9$) and Tsallis $S_{\widetilde{T}_{\lambda}}(\mathbf Z;L)$ ($\lambda=0.85$) obtained from $10^{4}$ Monte Carlo replications of $\Gamma_{\text{SAR}}$ data for window sizes $n\in\{49,81,121\}$ and looks $L\in\{5,18\}$.
 
@@
 
-```{r Simulated_density-shannon, echo=FALSE, message=FALSE}
+```{r Simulated_density-shannon, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-densities-shannon, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
+```{r fig-densities-shannon, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, out.width="90%", fig.pos="hbt", fig.cap="Empirical densities of $S_{\\widetilde{H}_{AO}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$.", fig.width=9, fig.height=4.0}
 
@@
 
-```{r Simulated_densityR, echo=FALSE, message=FALSE}
+```{r Simulated_densityR, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-densities,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
+```{r fig-densities, eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="hbt",  fig.cap="Empirical densities of $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.9$.", fig.width=9, fig.height=4.0}
 #fig.show="hide", 
@@
 
-```{r Simulated_density-tsallis2, echo=FALSE, message=FALSE}
+```{r Simulated_density-tsallis2, eval=FALSE,  include=FALSE, echo=FALSE, message=FALSE}
 set.seed(1234567890, kind = "Mersenne-Twister")
@@
 
-```{r fig-densities-tsallis4,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
+```{r fig-densities-tsallis4, eval=FALSE,  include=FALSE,  echo=FALSE, message=FALSE, warning=FALSE,  out.width="90%", fig.pos="H",  fig.cap="Empirical densities of $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z}; L)$ under $\\mathcal{H}_0$, with $\\lambda=0.85$.", fig.width=9, fig.height=4.0}
 #fig.show="hide", 
@@
 
+```{=latex}
+\begin{figure}[hbt]
+
+\caption{\label{fig-densities-shannon}Empirical densities of
+\(S_{\widetilde{H}_{AO}}(\bm{Z}; L)\) under \(\mathcal{H}_0\).}
+
+\centering{
+
+\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-shannon-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[hbt]
+
+\caption{\label{fig-densities}Empirical densities of
+\(S_{\widetilde{R}_{\lambda}}(\bm{Z}; L)\) under \(\mathcal{H}_0\), with
+\(\lambda=0.9\).}
+
+\centering{
+
+\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-1.pdf}
+
+}
+
+\end{figure}%
+
+\begin{figure}[H]
+
+\caption{\label{fig-densities-tsallis4}Empirical densities of
+\(S_{\widetilde{T}_{\lambda}}(\bm{Z}; L)\) under \(\mathcal{H}_0\), with
+\(\lambda=0.85\).}
+
+\centering{
+
+\includegraphics[width=0.9\linewidth,height=\textheight,keepaspectratio]{Figures/fig-densities-tsallis4-1.pdf}
+
+}
+
+\end{figure}%
+```
 Under the asymptotic properties of the entropy estimators [@vasicek1976test;@VanEs1992], for sufficiently large samples, $S_{\widetilde{\theta}}(\bm{Z};L)$ follows an asymptotic normal distribution:
@@
 The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures.
-These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;@fig-compare_size_power_plot0.
+These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
 
@@
 This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
-The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;@fig-compare_size_power_plot0.
+The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
 
@@
 
-```{r fig-compare_size_power_plot0, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies.
+```{r fig-compare_size_power_plot0,  eval=FALSE,  include=FALSE, echo=FALSE, fig.width=10, fig.height=12, fig.pos="H", fig.cap="Comparative performance of test statistics based on Shannon, Rényi and Tsallis entropies.
 Size and Power for different sample sizes and $L$ values."}
@@
 
+```{=latex}
+\begin{figure}[H]
+
+\caption{\label{fig-compare_size_power_plot0}Comparative performance of
+test statistics based on Shannon, Rényi and Tsallis entropies. Size and
+Power for different sample sizes and \(L\) values.}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{Figures/fig-compare_size_power_plot0-1.pdf}}
+
+}
+
+\end{figure}%
+```
+
 ## FIXED AND ADAPTIVE WINDOWS

### 2025-10-28 Text/Thesis/Chapters/Chapter3.qmd
Fix: corrected table layout

@@
 #| results: 'asis'
-#| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$.'
+#| tbl-cap: 'Bias and MSE of Shannon entropy estimators under $\Gamma_{\text{SAR}}(5,1)$'
 #| tbl-pos: 'htb'
@@
   row_spec(0, align = "c") %>%
-  kable_styling(font_size = 10,latex_options = "scale_down", full_width = TRUE)
+  kable_styling(font_size = 10,latex_options = "scale_down")%>%
+ column_spec(1, width = "3.5cm") %>%
+column_spec(2, width = "3.5cm") %>%
+column_spec(3, width = "3.5cm") %>%
+column_spec(4, width = "3.5cm")
+
 ```
@@
 The observed Type&nbsp;I error rates for the three entropy-based tests were consistently close to the nominal levels ($0.01$, $0.05$, $0.10$), thereby confirming the validity and proper calibration of the procedures.
-These results are summarized in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
+These results are summarized in Tables&nbsp;[-@tbl-table_size_power_shannon]--[-@tbl-size-power-tsallis], and are visualized in the top panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
 
@@
 This trend was consistent across all three entropic measures, demonstrating the effectiveness of the tests in identifying departures from the null hypothesis under heterogeneous conditions.
-The results are shown in Tables&nbsp;\ref{tab:table_size_power_shannon}-\ref{tab:size-power-tsallis}, with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
+The results are shown in Tables&nbsp;[-@tbl-table_size_power_shannon]--[-@tbl-size-power-tsallis], with graphical representations provided in the lower panel of&nbsp;Figure&nbsp;\ref{fig-compare_size_power_plot0}.
 
@@
 \renewcommand{\arraystretch}{0.9}
-```{r Table_size_and_power-shannon3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r}
+#| label: tbl-table_size_power_shannon
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Size and Power of the $S_{\widetilde{H}}(\bm{Z})$ test statistic (Shannon)'
+#| tbl-pos: 'H'
 suppressMessages({
@@
   combined_results,
-  caption = "Size and Power of the $S_{\\widetilde{H}}(\\bm{Z})$ test statistic (Shannon).",
+ # caption = "Size and Power of the $S_{\\widetilde{H}}(\\bm{Z})$ test statistic (Shannon).",
   format = "latex",
@@
   digits = 3,
-  label = "table_size_power_shannon",
+  #label = "table_size_power_shannon",
   centering = FALSE,
-  table.envir = "table", 
-  position="H", 
+  #table.envir = "table", 
+  #position="H", 
   linesep = ""
@@
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", font_size = 10) %>%
-  kable_styling(full_width = T)
+  kable_styling(latex_options = "scale_down", font_size = 10)%>%
+  column_spec(1, width = "1.5cm") %>%
+  column_spec(2, width = "1.5cm") %>%
+  column_spec(3, width = "1.5cm") %>%
+  column_spec(4, width = "1.5cm") %>%
+  column_spec(5, width = "1.5cm") %>%
+  column_spec(6, width = "1.5cm") %>%
+  column_spec(7, width = "1.5cm") %>%
+  column_spec(8, width = "1.5cm")
+  #kable_styling(full_width = T)
 
@@
 \renewcommand{\arraystretch}{0.9}
-```{r Table_size_and_power-renyi, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r}
+#| label: tbl-size-power-renyi
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Size and Power of the $S_{\widetilde{R}_{\lambda}}(\bm{Z})$ test statistic (Rényi)'
+#| tbl-pos: 'H'
 suppressMessages({
@@
   combined_results,
-  caption = "Size and Power of the $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z})$ test statistic (Rényi).",
+  #caption = "Size and Power of the $S_{\\widetilde{R}_{\\lambda}}(\\bm{Z})$ test statistic (Rényi).",
   format = "latex",
@@
   digits = 3,
-  label = "size-power-renyi",
+  #label = "size-power-renyi",
   centering = FALSE,
-  table.envir = "table", 
-  position="H", 
+  #table.envir = "table", 
+  #position="H", 
   linesep = ""
@@
 \renewcommand{\arraystretch}{1}
-```{r Table_size_and_power-tsallis0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r}
+#| label: tbl-size-power-tsallis
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis)'
+#| tbl-pos: 'H'
 suppressMessages({
@@
   combined_results,
-  caption = "Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis).",
+  #caption = "Size and Power of the $S_{\\widetilde{T}_{\\lambda}}(\\bm{Z})$ test statistic (Tsallis).",
   format = "latex",
@@
   digits = 3,
-  label = "size-power-tsallis",
+  #label = "size-power-tsallis",
   centering = FALSE,
-  table.envir = "table", 
-  position="H", 
+  #table.envir = "table", 
+  #position="H", 
   linesep = ""
@@
   row_spec(0, align = "c") %>%
-  kable_styling(latex_options = "scale_down", font_size = 10) %>%
-  kable_styling(full_width = T)
+  kable_styling(latex_options = "scale_down", font_size = 10)%>%
+  column_spec(1, width = "1.5cm") %>%
+  column_spec(2, width = "1.5cm") %>%
+  column_spec(3, width = "1.5cm") %>%
+  column_spec(4, width = "1.5cm") %>%
+  column_spec(5, width = "1.5cm") %>%
+  column_spec(6, width = "1.5cm") %>%
+  column_spec(7, width = "1.5cm") %>%
+  column_spec(8, width = "1.5cm")
+
+  #kable_styling(full_width = T)
 
@@
 Size and Power for different sample sizes and $L$ values."}
-library(ggplot2)
 

### 2025-10-28 Text/Thesis/Chapters/Chapter4.qmd
Fix: corrected table layout

@@
 All images use single polarization (HH or VV), and their acquisition settings differ in resolution, scene size, and number of looks.
-Table&nbsp;\ref{tab:table_param} lists the main characteristics of each SAR image.
-
-\renewcommand{\arraystretch}{2}   
-```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}
-
+@tbl-table_param lists the main characteristics of each SAR image.
+
+\renewcommand{\arraystretch}{1}   
+```{r}
+#| label: tbl-table_param
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Parameters of selected SAR images'
+#| tbl-pos: 'H'
+#| 
 SAR_data <- data.frame(
@@
       digits = 2,
-      label = "table_param",
-      centering = TRUE,
-      caption = "Parameters of selected SAR images.",
-      table.envir = "table", position = "hbt") %>%
+      #label = "table_param",
+      centering = TRUE
+     # caption = "Parameters of selected SAR images.",
+     # table.envir = "table", position = "hbt"
+      ) %>%
   row_spec(0, align = "c") %>%
   kable_styling(latex_options = "scale_down", font_size = 21) %>% 
-  kable_styling(full_width = TRUE) %>%
+  #kable_styling(full_width = TRUE) %>%
   column_spec(1, width = "3.8cm") %>%
@@
 In addition to the visual analysis presented above, we measured execution times to assess the computational cost of the proposed methods.
-Table&nbsp;\ref{tab:table_exec_times} reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$).
+@tbl-exec-times reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$).
 Times are reported in minutes and seconds (mm:ss) with $B=100$ bootstrap replications per window.
@@
 \renewcommand{\arraystretch}{1.8} 
-```{r times_sar_images2, echo=FALSE, message=FALSE, warning=FALSE}
+```{r}
+#| label: tbl-exec-times
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Execution times for the heterogeneity detection using fixed $7\times7$ and adaptive windows ($N_{\min}=5$, $N_{\max}=11$), with $B=100$ bootstrap replications per scenario.
+Times are given in minutes and seconds (mm:ss).
+Rényi entropy uses $\lambda=0.9$ and Tsallis entropy uses $\lambda=0.85$'
+#| tbl-pos: 'hbt'
 
@@
 escape = FALSE,
-label = "table_exec_times",#adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$)
-centering = TRUE,
-caption = "Execution times for the heterogeneity detection using fixed $7\\times7$ and adaptive windows ($N_{\\min}=5$, $N_{\\max}=11$), with $B=100$ bootstrap replications per scenario.
+#label = "table_exec_times",#adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$)
+centering = TRUE
+#caption = "Execution times for the heterogeneity detection using fixed $7\\times7$ and adaptive windows ($N_{\\min}=5$, $N_{\\max}=11$), with $B=100$ bootstrap replications per scenario.
 Times are given in minutes and seconds (mm:ss).
 Rényi entropy uses $\\lambda=0.9$ and Tsallis entropy uses $\\lambda=0.85$.",
-table.envir = "table", position = "hbt") %>%
+#table.envir = "table", position = "hbt"
+) %>%
 row_spec(0, align = "c") %>%
-kable_styling(latex_options = "scale_down", font_size = 16) %>%
-kable_styling(full_width = TRUE) %>%
+kable_styling(latex_options = "scale_down", font_size = 14) %>%
+#kable_styling(full_width = TRUE) %>%
 column_spec(1, width = "5cm") %>%
@@
 All experiments were executed on the workstation described in @sec-repr, using 8–16 CPU cores. 
-This setup allowed the entropy-based heterogeneity detection tests to process medium-sized SAR scenes within a few minutes, as reported in Table&nbsp;\ref{tab:table_exec_times}.
+This setup allowed the entropy-based heterogeneity detection tests to process medium-sized SAR scenes within a few minutes, as reported in @tbl-exec-times.
 
@@
 We thresholded the $p$-value maps at $\alpha=0.05$, labeling each pixel as heterogeneous (1) or homogeneous (0), and compared the resulting decisions with the ground truth to compute the F1-score ($F_1$), the Kappa coefficient ($\kappa$), and the overall accuracy (OA).
-Results are summarized in Table&nbsp;\ref{tab:table_metrics1}.
+Results are summarized in @tbl-table-metrics1.
 
@@
 \renewcommand{\arraystretch}{1.3}
-```{r metrics_table_k, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r}
+#| label: tbl-table-metrics1
+#| echo: false
+#| message: false
+#| warning: false
+#| results: 'asis'
+#| tbl-cap: 'Quantitative measures of heterogeneity detection'
+#| tbl-pos: 'htb'
 suppressPackageStartupMessages({
@@
 kable(all_metrics,
-caption = "Quantitative measures of heterogeneity detection",
+#caption = "Quantitative measures of heterogeneity detection",
 format = "latex",
@@
 escape = FALSE,
-label = "table_metrics1",
+#label = "table_metrics1",
 row.names = FALSE) %>%
@@
 collapse_rows(columns = 1, latex_hline = "major", valign = "bottom") %>%
-kable_styling(latex_options = c("hold_position","scale_down"), font_size = 11, full_width = T) %>%
+kable_styling(latex_options = c("hold_position","scale_down"), font_size = 14) %>%
+column_spec(1, width = "5cm") %>%
+column_spec(2, width = "3.5cm") %>%
+column_spec(3, width = "3.5cm") %>%
+column_spec(4, width = "3.5cm") %>%
+column_spec(5, width = "4cm")%>%
+#kable_styling(latex_options = c("hold_position","scale_down"), font_size = 11, full_width = T)
 print()

### 2025-11-03 Text/Thesis/Chapters/Chapter3.qmd
Versão final da tese e ficha catalográfica

@@
 $$
-where $N_{\max}$ and $N_{\min}$ denote the maximum and minimum allowed window size, respectively.
+where $N_{\max}$ and $N_{\min}$ denote the maximum and minimum allowed window radius, respectively.
+Since $W_{ij}=2N_{ij}+1$, these bounds on the radius induce the corresponding minimum and maximum window sides $W_{\min}=2N_{\min}+1$ and $W_{\max}=2N_{\max}+1$.
 Hence, windows *grow* in homogeneous regions (stabilizing estimates) and *shrink* in heterogeneous areas (preserving edges and avoiding class mixing).
@@
 
-In the experiments presented in the next chapter, the Tsallis-based test statistic $S_{\widetilde{T}{\lambda}}$ will be applied to both simulated and real SAR images using adaptive windows with side lengths ranging from $5\times5$ ($N{\min}=5$) to $11\times11$ ($N_{\max}=11$), with the smoothing parameter set to $\eta = 3$.
+In the experiments presented in the next chapter, the Tsallis-based test statistic $S_{\widetilde{T}{\lambda}}$ will be applied to both simulated and real SAR images using adaptive windows with side lengths ranging from $5\times5$ ($W_{\min}=5$) to $11\times11$ ($W_{\max}=11$), with the smoothing parameter set to $\eta = 3$.
 For comparison, a fixed $7\times7$ window configuration will also be evaluated.

### 2025-11-03 Text/Thesis/Chapters/Chapter4.qmd
Versão final da tese e ficha catalográfica

@@
 
-We evaluated the three test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on simulated images using fixed sliding windows of size $7\times7$ and, for Tsallis only, the adaptive windowing strategy with side lengths from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$) and smoothing parameter $\eta=3$.
+We evaluated the three test statistics $S_{\widetilde{H}_{\text{AO}}}$, $S_{\widetilde{R}_{\lambda}}$, and $S_{\widetilde{T}_{\lambda}}$ on simulated images using fixed sliding windows of size $7\times7$ and, for Tsallis only, the adaptive windowing strategy with side lengths from $5\times5$ ($W_{\min}=5$) to $11\times11$ ($W_{\max}=11$) and smoothing parameter $\eta=3$.
 Figures&nbsp;\ref{fig:sim1t} and \ref{fig:sim2t} present, respectively for $L=5$ and $L=9$, the $p$-value maps (top row) and the corresponding binary decision maps (bottom row).
@@
 The fixed approach uses local sliding windows of size $7\times7$.
-The adaptive approach (used with Tsallis) varies the window side from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$), with smoothing parameter $\eta=3$, and $B=100$ bootstrap replications per window.
+The adaptive approach (used with Tsallis) varies the window side from $5\times5$ ($W_{\min}=5$) to $11\times11$ ($W_{\max}=11$), with smoothing parameter $\eta=3$, and $B=100$ bootstrap replications per window.
 Each figure is organized in three rows: (i) SAR scene and a matching Sentinel-2 optical image, (ii) $p$-value maps for the three tests, and (iii) binary maps at the $5\%$ level (black = heterogeneous, white = homogeneous).
@@
 In addition to the visual analysis presented above, we measured execution times to assess the computational cost of the proposed methods.
-@tbl-exec-times reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($N_{\min}=5$) to $11\times11$ ($N_{\max}=11$).
+@tbl-exec-times reports the processing times for the three entropy-based tests (Shannon, Rényi, and Tsallis) with fixed $7\times7$ windows and, for comparison, the adaptive Tsallis variant with window sizes from $5\times5$ ($W_{\min}=5$) to $11\times11$ ($W_{\max}=11$).
 Times are reported in minutes and seconds (mm:ss) with $B=100$ bootstrap replications per window.
@@
 #| results: 'asis'
-#| tbl-cap: 'Execution times for the heterogeneity detection using fixed $7\times7$ and adaptive windows ($N_{\min}=5$, $N_{\max}=11$), with $B=100$ bootstrap replications per scenario.
+#| tbl-cap: 'Execution times for the heterogeneity detection using fixed $7\times7$ and adaptive windows ($W_{\min}=5$, $W_{\max}=11$), with $B=100$ bootstrap replications per scenario.
 Times are given in minutes and seconds (mm:ss).
